### 2016-11-15 abbDataPrep_Script.Rmd
initial commit

---
title: "AirBNB Data Preparation and Imputation"
output: html_notebook
---

### Introduction

This file details the initial data preparation and the missing daily observation imputation that we have applied to the AirBNB nightly data from www.AirDNA.co. This is not a 'data cleaning' exercise as we are not removing data points based on observed values, with one exception:  the removal of the small set of AirBNB properties considered as 'Other' (not a house or apartment).

&nbsp;
&nbsp;

### Setup

We begin by loading the necessary libraries, set the path to the data and loading a set of custom data munging functions.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE}

 ## Load libraries

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(ggmap)
  library(xtable)
  library(chron)
  library(RColorBrewer)
  library(plyr)

 ## Set location

  data.path <- 'c:/dropbox/research/airBNB/data/'

 ## Load sources

  source("c:/code/datamgmttools/dataMungetools.R")
  source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")

```

&nbsp;
&nbsp;

### Load data

Next we load the raw property level and nightly level AirBNB reservation data received from AirDNA.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Property Information

  prop.data <- read.csv(paste0(data.path, '/raw/melbproperties.csv'), header=T)

  ## Daily rental information

  daily.data  <- read.csv(paste0(data.path, '/raw/melbDaily.csv'), header=T)

```

&nbsp;
&nbsp;

### Data Transformations

To make future coding easier, we convert all field names to lower case.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  names(prop.data) <- tolower(names(prop.data))
  names(daily.data) <- tolower(names(daily.data))

```

We also then convert date values into correct R formatted dates. We also create a year created variable for the property data.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Daily data

  daily.data$date <- as.Date(daily.data$date)

 ## Property level data

  prop.data$created.date <- as.Date(prop.data$created.date)
  prop.data$created.year <- as.numeric(substr(prop.data$created.date, 1, 4))

```

&nbsp;
&nbsp;

### Remove those post Aug 31

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Daily data

  prop.data <- prop.data[prop.data$created.date <= '2016-08-31', ]

  daily.data <- daily.data[daily.data$property.id %in% prop.data$property.id, ]

```

### Add Summary Information

We now add summary information regarding the number of bookings, number of free and blocked nights to the property level data.  This information will assist in future imputation exercises and other analyses.

We start by splitting the daily date into a list where each object is a data.frame of daily observations for a particular property.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  daily.prop <- split(daily.data, daily.data$property.id)

```

Next, we apply the **abbAnalyzeDaily()** function to each data.frame of daily observations. This process produces a list of results, by property.id.  These lists are then collapsed into a single data.frame.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  daily.summ.list <- lapply(daily.prop, abbAnalyzeDaily)
  daily.summ <- rbind.fill(daily.summ.list)

```

Finally, we add the summarized data to the existing property-level information.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  prop.data <- merge(prop.data, daily.summ, by='property.id')

```

&nbsp;
&nbsp;

### Impute missing daily observations

Unfortunately, the data from AirDNA is missing observations.  According to conversations with AirDNA staff only certain Melbourne area properties were monitored for daily status conditions starting on October 1, 2014.  Over the next year, all properties were slowly brought on line.  From October 1, 2015 to October 1, 2016 observations are believed to be complete. To fill in the missing observations, we will impute the status of the missing dates based on the available data. Some properties will have a month or less of imputation, some a full year or so.

&nbsp;

#### Filter 'Other' Properties

AirBNB units are classified into a property type. There are 19 different property types within the Melbourne data.  The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type]. For the sake of this analysis, we will collapse these twenty types into three types:

1. **House**:  Includes properties labeled 'House' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.

The analyses that follow removes the **Other** category (3% of total) and only considers the **House** and **Apartment** unit types

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

prop.data$type <- 'Other'
prop.data$type[prop.data$property.type == 'Apartment' | 
                  prop.data$property.type == 'Condominium' ] <- 'Apartment'
prop.data$type[prop.data$property.type == 'House' | 
                  prop.data$property.type == 'Townhouse' ] <- 'House'

#prop.data <- prop.data[prop.data$type != 'Other', ]

```

&nbsp;

#### Prepping for Imputation

We begin the imputation process by creating a new variable indicating if the property itself was created before the data collection process began.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  prop.data$created.class <- ifelse(prop.data$created.date < '2014-10-01', 
                                  'pre', 'post')

```

Most properties (`r round(100*table(prop.data$created.class)[1]/nrow(prop.data),2)`%) were created (first offered on www.airbnb.com) after October 1, 2014.  We then add a field indicating whether or not the property needs to be imputed.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

prop.data$impute <- 'no'
prop.data$impute[prop.data$created.class == 'pre' & 
                   prop.data$min.date > '2014-10-01'] <- 'pre'
prop.data$impute[prop.data$created.class == 'post' & 
                   prop.data$min.date > prop.data$created.date] <- 'post'

```

About (`r round(100*(1-(table(prop.data$impute)[1]/nrow(prop.data))), 0)`%) of all properties need some measure of imputation.

&nbsp;

#### Imputation Process

In imputing the properties will use a multiple step process that considers the property's performance during the observed periods, the overall market during the non-observed periods and the type of the property itself.  More specifically, we follow the steps below:

1. Split all properties into *j* number of AirBNB submarkets

For each *j* submarket:

2. Calculate the average daily occupancy rate for each *j* submarket

For each individual property (*i*) in submarket *j*:

3. Calculate which days are observed and which are missing
4. Calculate the % of reserved, available and blocked days for the observed dates
5. Create an adjustment factor that notes the ratio of the submarket *j* reserved rate during the property's observed dates to those of the property's un-observed dates
6. Using the adjustment in #5, we then determine what percentage of the un-observed days should be alloted to each status type (reserved, available and blocked).  Blocked are based on the % of blocked days in the observed period.  Reserved are based on the observed occupancy rate during the observed dates multiplied by the overall expected occupancy rate during the unobserved days for the entire submarket as compared with the observed days. The available days are the remainder. This process creates a count of each status equal to the number of unobserved days.
7. The three status types are then assigned to the unobserved days.  First, blocked days are randomly assigned. Then the reserved days are randomly assigned to the remaining non-blocked days in a weighted fashion where the overall submarket's occupancy rate on a given day influences the probability of the impute status being reserved. The available days are the balance of the unobserved days. Note that we do not attempt to simulate actual bookings which are often multiple days.  The intent of the imputation is to correct capture the overall market and submarket trends, not to accurately re-create actual booking histories of any of the unobserved periods for this sample of properties. 
8. Prices for reserved rooms are taken to be the average nightly rate of that particular property over the observed period.

We begin this process by creating submarkets.  For each of the properties we determine the submarket to be a combination of the structure type (House vs Apartment) and the listing type (Entire vs Private Room vs Shared Room).  This creates six submarkets. These are assigned to the property and the daily data.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  prop.data$lp.type <- paste0(substr(prop.data$type, 1, 1), '.', 
                               substr(prop.data$listing.type, 1, 1))

  daily.data$lp.type <- prop.data$lp.type[match(daily.data$property.id,
                                                  prop.data$property.id)]

```

We then split the property and daily data into submarkets.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 o.prop <- prop.data[prop.data$type == 'Other', ]
 o.daily <- daily.data[daily.data$property.id %in% o.prop$property.id, ]

 prop.data <- prop.data[prop.data$type != 'Other', ]
 daily.data <- daily.data[daily.data$property.id %in% prop.data$property.id, ]

 subm.prop <- split(prop.data, prop.data$lp.type)
 subm.daily <- split(daily.data, daily.data$lp.type)

```

And then we calculate daily occupancy rates for each submarket.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  subm.rates <- lapply(subm.daily, abbCalcDateRates)

```

We take these three sets of submarket data (properties, daily and occupancy rates) and use a custom function (**abbImputeDaily()**) to impute the missing days. The results of each of these submarkets are then collapse into a single data.frame.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Create blank capture list

  subm.list <- list()

 ## Loop through submarkets

  for(j in 1:length(subm.prop)){
    subm.list[[j]] <- abbImputeDaily(prop.df=subm.prop[[j]],
                                     daily.df=subm.daily[[j]],
                                     rates.df=subm.rates[[j]])
  }

 ## Collapse into a data.frame

  imp.daily <- rbind.fill(subm.list)

```

After imputing the missing dates we join them to the observed daily data.  The imputed data can be recognized by the label 'imputed' in the booked.date field.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Combine all together

  all.daily <- rbind(daily.data, imp.daily, o.daily)

 ##

  prop.data <- rbind(prop.data, o.prop)

```

Finally, we write the amended daily and property data to .csv files for future analysis.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 write.csv(all.daily, paste0(data.path, 'prepared/dailydata.csv'), row.names=FALSE)

 write.csv(prop.data, paste0(data.path, 'prepared/propdata.csv'), row.names=FALSE)

```

### 2016-11-15 abbReturns_EDA.Rmd
initial commit

---
title: "R Notebook"
output: html_notebook
---

## Exploratory Spatial Analysis

As an initial look into the spatial properties of long and short term rental data we create a set of maps looking at prices by suburbs.

We begin by creating median rate and rent values for each suburb, broken into apartments and houses.

```{r med.price, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Create indicators of apartment or homes

  id.st <- which(abb.dataf$type == 'Apartment')
  id.lt <- which(rent.dataf$type == 'Apartment')

 ## Create dataframes of median values

  # Short term apartments
  st.subsA <- tapply2DF(abb.dataf$nightly.rate[id.st], 
                        abb.dataf$suburb[id.st], 
                        median, newName='med.price', idName='suburb')

  # Long term apartments

  lt.subsA <- tapply2DF(rent.dataf$event.price[id.lt], 
                        rent.dataf$suburb[id.lt], 
                        median, newName='med.price', idName='suburb')

  # Short term houses
  st.subsH <- tapply2DF(abb.dataf$nightly.rate[-id.st], 
                        abb.dataf$suburb[-id.st], 
                        median, newName='med.price', idName='suburb')

  # Long term houses
  lt.subsH <- tapply2DF(rent.dataf$event.price[-id.lt], 
                        rent.dataf$suburb[-id.lt], 
                        median, newName='med.price', idName='suburb')

```

We then convert these median values to a relative value and add them to the plotable map object.  We do this so that the maps may be compared between the long/short and apt/house breakdowns.  Relative values are made be comparing the suburb specific median to the median value in the popular St. Kilda suburbs.  As a result the values on the map that follow represent the ratio of the median price (rate or rent) in that suburb to the corresponding price in St. Kilda.

```{r med.price2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  ## Create relative prices

  st.subsA$rel.price <- (st.subsA$med.price /
                           st.subsA$med.price[st.subsA$suburb == 'St Kilda'])
  st.subsH$rel.price <- (st.subsH$med.price /
                           st.subsH$med.price[st.subsH$suburb == 'St Kilda'])
  lt.subsA$rel.price <- (lt.subsA$med.price /
                           lt.subsA$med.price[lt.subsA$suburb == 'St Kilda'])
  lt.subsH$rel.price <- (lt.subsH$med.price /
                           lt.subsH$med.price[lt.subsH$suburb == 'St Kilda'])

```

```{r med.price3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Create plotable map object

 ## Add relative price information

  subs$lapr <- lt.subsA$rel.price[match(subs$id, lt.subsA$suburb)]
  subs$lhpr <- lt.subsH$rel.price[match(subs$id, lt.subsH$suburb)]
  subs$sapr <- st.subsA$rel.price[match(subs$id, st.subsA$suburb)]
  subs$shpr <- st.subsH$rel.price[match(subs$id, st.subsH$suburb)]

```

In the maps that follow, green areas represent suburbs with higher relative prices and orange with lower.  From these maps we see a number of trends:

1. Long term house rents are highest in the south and east
2. Long term apartment rents are highest in the south and central 
3. Short term house rates are a bit sporadic, but do seem generally higher in the south along the beach.  Or at least, the high values in the non-coastal south east are not present in this market.
4. Short term apartment rental rates somewhat mirror the long term apartment rental rates.

A bit of caution:  Since we are not controlling for differences in compositions (sturctural differences) these maps could also be showing different products in different locations and their relationship to price.  This is simply an exploration of the data. We will address these issues later.

```{r med.price4, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Build map objects

  # Long term apartments
  lapr <- ggplot(subs, 
                 aes(x=long, y=lat, group=group, fill=lapr)) +
                 geom_polygon(color='gray30') +
                 scale_fill_gradient2(midpoint=1, 
                                      low='orange', 
                                      mid='white',
                                      high='green') +
                 ggtitle('Long Term Apts') +
                 #theme(legend.position='none') +
                 xlab('') +
                 ylab('')

  # Long term houses
  lhpr <- ggplot(subs, 
                 aes(x=long, y=lat, group=group, fill=lhpr)) +
                 geom_polygon(color='gray30') +
                 scale_fill_gradient2(midpoint=1, 
                                      low='orange', 
                                      mid='white',
                                      high='green') +
                 ggtitle('Long Term Houses') +
                 #theme(legend.position='none') +
                 xlab('') +
                 ylab('')

  # Short term apartments
  sapr <- ggplot(subs, 
                 aes(x=long, y=lat, group=group, fill=sapr)) +
                 geom_polygon(color='gray30') +
                 scale_fill_gradient2(midpoint=1, 
                                      low='orange', 
                                      mid='white',
                                      high='green') +
                 ggtitle('Short Term Apts') +
                 #theme(legend.position='none') +
                 xlab('') +
                 ylab('')

  # Short term houses
  shpr <- ggplot(subs, 
                 aes(x=long, y=lat, group=group, fill=shpr)) +
                 geom_polygon(color='gray30') +
                 scale_fill_gradient2(midpoint=1, 
                                      low='orange', 
                                      mid='white',
                                      high='green') +
                 ggtitle('Short Term Houses') +
                 #theme(legend.position='none') +
                 xlab('') +
                 ylab('')

 ## Make plots

  #ggMultiPlots(lhpr, lapr, shpr, sapr, cols=2)

```

```{r lhpr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
 lhpr
```

```{r lapr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
 lapr
```

```{r shpr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
 shpr
```

```{r sapr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
 sapr
```

### 2016-11-15 abbReturns_Script.Rmd
initial commit

---
title: "Should I AirBNB My Property?"
author: "Andy Krause and Gideon Aschwanden"
date: "1 November 2016"
output:
  html_notebook: default
  pdf_document: default
---

&nbsp;

## Introduction

&nbsp;

This document is intended the literate programming of our analysis for the 'Should I AirBNB My Property?' research project.  Below we document the complete data provenance, taking our data from the raw source data through to the final results. Data prepartion, modeling and visualization will be done in R (version 3.3.1). As a very brief overview, we will be comparing the financial returns of short-term (AirBNB-type) and long-term (traditional leases) leasing of residential properties in Melbourne, Australia.  We perform this comparison under a hypothetical condition where-in an investor purchases a property on Septemeber 1, 2015 and is looking to determine whether too lease out the property on a traditional long-term lease (12 months) or as an AirBNB property.  We examine the returns for the following 12 months.  Sensitivity to time frames, start dates, locations, property types, etc. are considered in this analysis as well.

Data on AirBNB (short-term) rentals has been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis. The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.

Throughout this document we will refer to the short-term data as **'short-term'** or **'AirBNB'** while the long-term data will be referred to as **'long-term'**, **'rental'** or **'lease'**.  Short-term nightly fees will be referenced as **'rates'** and long-term as **'rent'**.  We will use **'prices'** to collectively refer to **rates** and **rents**. Note that within the Melbourne market rentals are quoted in weekly rents (but are charged to tenants at a monthly rent equivalent to the 1/12 of 52 weeks of rent).

&nbsp;

### Preliminary Commands

&nbsp;

We begin with a number of preliminary commands that include setting the global options, loading necessary packages (libraries), setting the path to the raw data sources and reading in custom functions used later in the analysis.

```{r prelim_cmds, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

 ## Set global options

  options(xtable.comment = FALSE)

 ## Load libraries

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(chron)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)

 ## Set path location

  data.path <- 'c:/dropbox/research/airBNB/data/'

 ## Load sources (custom function files)

  source("c:/code/dataviztools/ggplottools.R")
  source("c:/code/datamgmttools/dataMungetools.R")
  source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
  source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")

```

```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

 ## Set basic color to use in palettes

  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

  sm.col <- abb.col[c(1, 3, 6, 5, 2)]

```

&nbsp;

### Data Pre-processing

&nbsp;

Both the AirBNB and the rental data require some measure of data pre-processing and due to the run times of these function they are done outside of this document.  For the AirBNB data, the pre-processing is primarily concerned with imputing missing daily observations for a small number of properties in the dataset.  Full information on this process can be found in the **airbnbDataClean.Rmd** and **dataCleanFunctions.R** files.  Do note that most of the imputed data is ignored by our choice of study time period later on.

The long term data received from the data provider is both wide and long and very inefficiently stored.  To aid in computation time, the pre-processing involves the trimming of fields, labeling of observation types and reconfiguration of data and can be found in the **fixAPMData.R** script.

&nbsp;

## Loading data

&nbsp;

Next we load in the raw data.  The short-term data is found in two separate files, one providing information on the property itself data and one providing a daily record of bookings.

```{r load_abb_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Property Information

  abb.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T)

  # Daily rental information

  daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T)

```

We then load the long term rental data.  This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.

```{r load_rent_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Property level long term rental information

  rent.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)

 ## Long term rental listing information

  listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T)

```

And, finally, we load two GIS shapefiles that denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River.]

```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## SA1 shapefile

  sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)

  ## Suburb shapefile

  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)

  ## Beach file

  beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)

```

&nbsp;

## Data Cleaning and Preparation

&nbsp;

In this section we remove, convert and/or transform a number of data fields.  We also remove observations if they are missing critical data or fall outside of the scope of our research question.

&nbsp;

### Trim Fields

&nbsp;

We start by converting all field names to lower case to simplify future coding.  This is important as R is case sensitive.

```{r lower_names, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short term data

  names(abb.data) <- tolower(names(abb.data))
  names(daily.data) <- tolower(names(daily.data))

 ## Long term data

  names(rent.data) <- tolower(names(rent.data))
  names(listing.data) <- tolower(names(listing.data))

 ## Geographic data

  names(sa1s.shp@data) <- tolower(names(sa1s.shp@data))
  names(suburbs.shp@data) <- tolower(names(suburbs.shp@data))

```

The data contain many fields that are either not fully observed and/or are not relevant to our research question.  Additionally, the field naming conventions differ between the two datasets.  We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.

We start by trimming the property-level short term data.  No fields need to be removed from the daily data.

```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Property Data

  abb.keep.flds <- c('property.id', 'host.id', 'listing.title', 'property.type',
                     'listing.type', 'created.date', 'latitude', 'longitude',
                     'last.scraped.date', 'average.daily.rate', 'overall.rating',
                     'max.guests', 'cancellation.policy', 'cleaning.fee',
                     'published.nightly.rate', 'published.weekly.rate', 
                     'published.monthly.rate', 'minimum.stay',
                     'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days',
                     'blocked.days', 'available.days', 'created.year')

  abb.data <- abb.data[ , abb.keep.flds]

```

We then limit the fields of the long-term property-specific data

```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Long term property Data

  rent.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid',
                      'flatnumber', 'streetnumber', 'streetname', 'streettype', 
                      'suburb', 'postcode', 'property_latitude',
                      'property_longitude', 'street_centroid_latitude',
                      'street_centroid_longitude', 'eventdate', 'eventprice',
                      'propertytype', 'areasize', 'bedrooms', 'baths', 'parking',
                      'hasstudy', 'hascourtyard', 'hasbalcony', 'hasairconditioning',
                      'hasgarage', 'dom')

  rent.data <- rent.data[ , rent.keep.flds]

```

&nbsp;

### Standardize Field Names

&nbsp;

Next we standardize the field names.  Here we follow the short-term data convention of placing a period between words in the name.  We also shorten a number of the fields to make future coding easier.  No changes are made to the monthly or daily data.

For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names.

```{r rename_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  names(abb.data) <- c('property.id', 'host.id', 'listing.title', 'property.type',
                       'listing.type', 'created.date', 'latitude', 'longitude',
                       'last.scraped.date', 'average.daily.rate', 'overall.rating',
                       'max.guests', 'cancel.policy', 'cleaning.fee',
                       'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay',
                       'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
                       'blocked.days', 'available.days', 'created.year')

```

Periods are inserted between relevant words for the rental data.

```{r rename_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  names(rent.data) <- c('id.key', 'geographical.id', 
                        'event.id', 'address.id', 'activity.id',
                        'flat.number', 'street.number', 'street.name', 'street.type',
                        'suburb', 'postcode', 'latitude', 'longitude',
                        'street.latitude', 'street.longitude', 'event.date',
                        'event.price', 'property.type', 'area.size', 'bedrooms',
                        'baths', 'parking', 'has.study', 'has.courtyard',
                        'has.balcony', 'has.aircond', 'has.garage')

  names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id', 
                           'of.record',
                           'event.date', 'event.price', 'first.adv.date', 
                           'first.adv.price', 'last.adv.date', 'last.adv.price',
                           'event.type')

```

&nbsp;

### Field Conversions

&nbsp;

Below we convert and coalate a number of the temporal and spatial variables.

&nbsp;

#### Convert Time Variables

We convert time variables across all dataset to an R date format.  For the AirBNB data this is a relatively straighforword process as the data are already standardized into a consistant date representation. We also create a year variable.

```{r fix_st_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Property Data Fields

  abb.data$created.date <- as.Date(abb.data$created.date)
  abb.data$last.scraped.date <- as.Date(abb.data$last.scraped.date)
  abb.data$min.date <- as.Date(abb.data$min.date)
  abb.data$max.date <- as.Date(abb.data$max.date)

  ## Daily Data

  daily.data$date <- as.Date(daily.data$date)

```

The dates in the long term data are not standardized.  To fix this issue we create a small function that will remove the unnecessary digits and spaces and then convert to a standard date form.  We then apply this formula to the three date fields in the long term data.  We also create a year field for the event date.

```{r fix_lt_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Build custom function

  fixLTDates <- function(x){
    temp.date <- as.character(x)
    temp.date <- str_replace_all(temp.date, ' 0:00', '')
    temp.date <- str_replace_all(temp.date, '/20', '/')
    return(as.Date(temp.date, "%d/%m/%y"))   
  }

 ## Convert event date

  # Date
  rent.data$event.date <- fixLTDates(rent.data$event.date)

  # Year
  rent.data$event.year <- as.numeric(substr(rent.data$event.date, 1, 4))

 ## Converted list data date fields

  listing.data$first.adv.date <- fixLTDates(listing.data$first.adv.date)
  listing.data$last.adv.date <- fixLTDates(listing.data$last.adv.date)

```

&nbsp;

#### Fix Boolean Variables

Next we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.

```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  rent.data$has.study <- ifelse(rent.data$has.study == 'True', 1, 0)
  rent.data$has.courtyard <- ifelse(rent.data$has.courtyard == 'True', 1, 0)
  rent.data$has.aircon <- ifelse(rent.data$has.aircon == 'True', 1, 0)
  rent.data$has.balcony <- ifelse(rent.data$has.balcony == 'True', 1, 0)
  rent.data$has.garage <- ifelse(rent.data$has.garage == 'True', 1, 0)

```

&nbsp;

### Standardize Property Types

&nbsp;

AirBNB units are classified into 19 different property type.  The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type]. For the sake of this analysis, we will collapse these twenty types into three types:

1. **House**:  Includes properties labeled 'House' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.

Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:

1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
3. **Other**: Includes properties labeled as 'Semi' and 'Villa'

Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.  This is most apparent when talking about apartment dwellings.  In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).  Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.

We then create a new variable in each dataset and give each one of the three categories discussed above.

```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short Term data

  abb.data$type <- 'Other'
  abb.data$type[abb.data$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
  abb.data$type[abb.data$property.type %in% c('House', 'Townhouse')] <- 'House'

 ## Long Term data

  rent.data$type <- 'Other'
  rent.data$type[rent.data$property.type %in% c('Duplex', 'House',
                                           'Terrace', 'Townhouse')] <- 'House'
  rent.data$type[rent.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'

```

The **Other** categories contain very small percentage of properties in both the AirBNB and the rental data.  As a result, we remove the 'Others' from the data.

```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}

  abb.data <- subset(abb.data, type != 'Other')
  rent.data <- subset(rent.data, type != 'Other')

```

Next, for the short term rentals units can be listed as one of three types relating to the extent of the property which is able to be booked:

1. **Entire Home/Apt**: The entire home or apartment is available
2. **Private Room**: One room within a house or apartment is available
3. **Shared Room**: A bed within a room shared by other occupants is available

As long-term rentals do not offer **Private Room** or **Shared Room** options and our purpose here is a comparison of the two we remove all short term properties that do not lease the entire home/apt. Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}

  abb.data$listing.type <- as.character(abb.data$listing.type)
  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'

  ggplot(abb.data, aes(x=listing.type)) + 
    geom_bar(color=abb.col[1], fill=abb.col[1]) +
    xlab('\nListing Type\n') + 
    ggtitle('\nShort Term Rentals\n')  +
    ylab('# of Properties\n')

```

```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]

```

### Trim by Time

Next we trim the observations by time.  Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.  To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.  Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factor).  In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.  Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2016.  While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.

```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Limit short term data

  abb.dataf <- abb.data[abb.data$min.date >= '2015-09-01', ]
  daily.dataf <- daily.data[daily.data$date >= '2015-09-01', ]

 ## Limit long term data

  rent.dataf <- rent.data[rent.data$event.date >= '2014-09-01' & 
                            rent.data$event.date <= '2015-08-31', ]
  listing.dataf <- listing.data[listing.data$id.key %in% rent.dataf$id.key, ]

```

### Locations and Submarkets

Location is clearly an important determinant in both the short and long term rental markets. At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.  In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.  Suburbs in Melbourne are much smaller than their North American counterparts.  The specific suburb of a property is the second, or finer scale, at which the market operates. The plot below shows the three large submarkets.

```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Convert shapefile to ggplot-able object

  # Fix lat/long

  # Limit to extent of data
  sub.table <- table(rent.dataf$suburb)
  sub.table <- sub.table[sub.table != 0]

  # Clip to only those with a rental observation
  study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]

  # Convert to an outer bound with holes
  ss.bound <- gUnaryUnion(study.suburbs)

  # Remove holes from the shapefile
  ssb <- slot(ss.bound, "polygons") 
  holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
                                          slot, "hole"))
  res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
  IDs <- row.names(ss.bound) 
  ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
   Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound)))

  # Identify which suburbs all in area covered by outer bound
  ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
  study.suburbs <- suburbs.shp[which(ss.in), ]

  # Convert into a ggplot-able format
  subs <- fortify(study.suburbs, region='name_2006')

  # Add suburb category
  subs$des <- suburbs.shp@data$suburbdesi[
    match(subs$id, suburbs.shp@data$name_2006)]

```

```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

 ## Build the map object

  # Set colors
  g.cols <- abb.col[c(2,10,9)]

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g.cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    ggtitle("Melbourne Suburb Classifications")

## Plot map

  loc.map

```

It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melboure:

1. Rural (Outer suburbs, not Beach)
2. Suburban (Middle suburbs, not Beach)
3. City (Inner Suburbs, not Beach, not Core)
4. City-Core (Select inner suburbs with tourist activities and near CBD)
5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)

We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.  This process is repeated for both the short and long term data.  We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on. Fainlly, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).

```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
                   'St Kilda West', 'West Melbourne', 'Windsor')

```

```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Determine centroid of study area

  latMid <- median(abb.dataf$latitude)
  longMid <- median(abb.dataf$longitude)

 ## Calculate Degress to Meters conversion

  m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
  m.long = 111132.954 * cos (latMid)
  m.conv <- mean(m.lat, m.long)

 ## Create the beach buffer

  beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)

```

```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short term data

  # Convert to point shapefile
  abb.prop.shp <- SpatialPointsDataFrame(cbind(abb.dataf$longitude,
                                               abb.dataf$latitude),
                                         abb.dataf,
                                         proj4string=CRS("+init=epsg:4283"))

  # Add suburb name 
  spJoin <- over(abb.prop.shp, suburbs.shp)
  abb.dataf$suburb <- as.character(spJoin$name_2006)
  abb.dataf$suburb[is.na(abb.dataf$suburb)] <- 'missing'

  # Add suburb designation
  abb.dataf$sub.class <- as.character(spJoin$suburbdesi)
  abb.dataf$sub.class[is.na(abb.dataf$sub.class)] <- 'missing'

  # Add SA1 designation
  spJoin <- over(abb.prop.shp, sa1s.shp)
  abb.dataf$sa1 <- spJoin$sa1_main11

  ## Add Beach Designation
  spJoin <- over(abb.prop.shp, beach.buffer)
  abb.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)

  # Remove those missing a suburb classification (out of area)
  abb.dataf <- abb.dataf[abb.dataf$sub.class != 'missing', ]
  abb.dataf <- abb.dataf[abb.dataf$sa1 != 'missing', ]

```

```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Add the submarket designations

  # Add individual classes
  abb.dataf$sub.mrkt <- 'rural'
  abb.dataf$sub.mrkt[abb.dataf$sub.class == 'Middle'] <- 'suburban'
  abb.dataf$sub.mrkt[abb.dataf$sub.class == 'Inner'] <- 'city'
  abb.dataf$sub.mrkt[abb.dataf$suburb %in% core.suburbs] <- 'city-core'
  abb.dataf$sub.mrkt[abb.dataf$beach == 1] <- 'beach'

  # Order the factors properly
  abb.dataf$sub.mrkt <- factor(abb.dataf$sub.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

```

```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Make map
  abb.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=abb.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3))) + 
    ggtitle('AirBNB Location\nBy Submarket')

```

About 5% of the long term rental observations have missing latitude and longitude values.  Half of these do, however, have a lat/long value for the centroid of the street that the property faces.  To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.  For those without either (3% of the total) we remove them from the dataset at this point.  After removing these, we apply the submarket designations.

```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Label those missing lat/long

  miss.LL <- which(is.na(rent.dataf$latitude))

 ## Create a field to indicate the approximate matches

  rent.dataf$miss.LL <- 0
  rent.dataf$miss.LL[miss.LL] <- 1

 ## Apply approximate match

  rent.dataf$latitude[miss.LL] <- rent.dataf$street.latitude[miss.LL]
  rent.dataf$longitude[miss.LL] <- rent.dataf$street.longitude[miss.LL]

 ## Remove those still missing latitude data

  rent.dataf <- rent.dataf[!is.na(rent.dataf$latitude), ]

```

```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Long term data

  # Convert to point shapefile
  rent.prop.shp <- SpatialPointsDataFrame(cbind(rent.dataf$longitude,
                                                rent.dataf$latitude),
                                         rent.dataf,
                                         proj4string=CRS("+init=epsg:4283"))

  # Add suburb name 
  spJoin <- over(rent.prop.shp, suburbs.shp)
  rent.dataf$suburb <- as.character(spJoin$name_2006)
  rent.dataf$suburb[is.na(rent.dataf$suburb)] <- 'missing'

  # Add suburb designation
  rent.dataf$sub.class <- as.character(spJoin$suburbdesi)
  rent.dataf$sub.class[is.na(rent.dataf$sub.class)] <- 'missing'

  # Add SA1 designation
  spJoin <- over(rent.prop.shp, sa1s.shp)
  rent.dataf$sa1 <- spJoin$sa1_main11

  ## Add Beach Designation
  spJoin <- over(rent.prop.shp, beach.buffer)
  rent.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)

  # Remove those missing a suburb classification (out of area)
  rent.dataf <- rent.dataf[rent.dataf$sub.class != 'missing', ]
  rent.dataf <- rent.dataf[rent.dataf$sa1 != 'missing', ]

```

```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Add the submarket designations

  # Add individual classes
  rent.dataf$sub.mrkt <- 'rural'
  rent.dataf$sub.mrkt[rent.dataf$sub.class == 'Middle'] <- 'suburban'
  rent.dataf$sub.mrkt[rent.dataf$sub.class == 'Inner'] <- 'city'
  rent.dataf$sub.mrkt[rent.dataf$suburb %in% core.suburbs] <- 'city-core'
  rent.dataf$sub.mrkt[rent.dataf$beach == 1] <- 'beach'

  # Order the factors properly
  rent.dataf$sub.mrkt <- factor(rent.dataf$sub.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

```

```{r rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Make map
  rent.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=rent.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3))) + 
    ggtitle('Long Term Rental Location\nBy Submarket')

```

```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}

  ggMultiPlots(abb.map, rent.map, cols=2)

```

```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}

  # Make map
  abbtype.map <- ggplot() +
    geom_bar(data=abb.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('AirBNB Property Type\nBy Submarket')

  # Make map
  renttype.map <- ggplot() +
    geom_bar(data=rent.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Long Term Property Type\nBy Submarket')

```

```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}

  ggMultiPlots(abbtype.map, renttype.map, cols=2)

```

## By Values (outliers, etc.)

We now filter both datasets by removing observed values unlikely to represent 'typical' short or long term rental properties.

### Bedrooms

We start by looking at bedrooms. We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms). We then plot the distribution of different bedrooms counts.  From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.

```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Remove missing and data errors

  # Long term data
  rent.dataf <- rent.dataf[!is.na(rent.dataf$bedrooms), ]
  rent.dataf <- rent.dataf[rent.dataf$bedrooms <= 10, ]

  # Short term data
  abb.dataf <- abb.dataf[!is.na(abb.dataf$bedrooms), ]
  abb.dataf <- abb.dataf[abb.dataf$bedrooms <= 10, ]

```

```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

 ## Build long term bar plot

  rentbed <- ggplot(rent.dataf, aes(x=bedrooms)) + 
    geom_bar(fill=abb.col[3], color=abb.col[3]) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Long Term Rentals')

 # Build short term bar plot

  abbbed <- ggplot(abb.dataf, aes(x=bedrooms)) + 
    geom_bar(fill=abb.col[1], color=abb.col[1]) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:10, breaks=0:10)+
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals')

 ## Make the comparison plot

  ggMultiPlots(abbbed, rentbed, cols=1)

```

For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.  We filter the data accordingly. Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom. We convert the 0 bed short term units to 1 bed units.

```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Remove all with more than 4 beds

  abb.dataf <- abb.dataf[abb.dataf$bedrooms < 5, ]
  rent.dataf <- rent.dataf[rent.dataf$bedrooms < 5, ]

 ## Remove apartments with more than 3

  abba <- which(abb.dataf$bedrooms > 3 & abb.dataf$type =='Apartment')
  renta <- which(rent.dataf$bedrooms > 3 & rent.dataf$type =='Apartment')
  if(length(abba)>0) abb.dataf <- abb.dataf[-abba, ]
  if(length(renta)>0) rent.dataf <- rent.dataf[-renta, ]

  # Convert 0 Bed to 1 Bed  
  abb.dataf$bedrooms[abb.dataf$bedrooms == 0] <- 1

```

### Bathrooms

We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.

```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Remove missing data
rent.dataf <- rent.dataf[!is.na(rent.dataf$baths), ]
abb.dataf <- abb.dataf[!is.na(abb.dataf$baths), ]

```

```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

 ## Build long term plot

  ltbath <- ggplot(rent.dataf, aes(x=baths)) + 
    geom_bar(fill=abb.col[3], color=abb.col[3]) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Long Term Rentals')

 ## Build short term plot

  stbath <- ggplot(abb.dataf, aes(x=baths)) + 
    geom_bar(fill=abb.col[1], color=abb.col[1]) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term Rentals')

 ## Make Plots

  ggMultiPlots(stbath, ltbath, cols=1)

```

Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly. A few short term properties state no baths, which is likely an error so we remove these as well. Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.  We round the baths up to whole integers.

```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Filter by bath count

  # Short term data
  abb.dataf <- abb.dataf[abb.dataf$baths < 4, ]
  abb.dataf <- abb.dataf[abb.dataf$baths > 0, ]

  # Long term data
  rent.dataf <- rent.dataf[rent.dataf$baths < 4, ]

 ## Round baths up

  abb.dataf$baths <- round(abb.dataf$baths + .01, 0)

```

### Bed/Bath Combination

In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.  In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.  As a result we examine the combinations of the two.

```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Create combination variable

  rent.dataf$bedbath <- paste0(rent.dataf$bedrooms, '..', rent.dataf$baths)
  abb.dataf$bedbath <- paste0(abb.dataf$bedrooms, '..', abb.dataf$baths)

```

```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

 ## Make long term plot

  ltb <- ggplot(rent.dataf, aes(x=bedbath)) + 
    geom_bar(fill=abb.col[3], color=abb.col[3]) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') + 
    facet_wrap(~type)

 ## Make short term plots

  stb <- ggplot(abb.dataf, aes(x=bedbath)) +
    geom_bar(fill=abb.col[1], color=abb.col[1]) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type)

 ## Plot

  ggMultiPlots(ltb, stb, cols=1)

```

From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.

```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Set level of acceptable combinations

  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')

 ## Filter data

  rent.dataf <- rent.dataf[rent.dataf$bedbath %in% acc.bb, ]
  abb.dataf <- abb.dataf[abb.dataf$bedbath %in% acc.bb, ]

```

### Rates and Rents

Finally, we turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.

```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  rent.dataf <- rent.dataf[!is.na(rent.dataf$event.price), ]
  abb.dataf <- abb.dataf[!is.na(abb.dataf$nightly.rate), ]

```

```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Rent Plot
  rent.plot <- ggplot(rent.dataf, aes(x=event.price)) + 
    geom_density(fill=abb.col[3],alpha=.8) +
    ylab('') +
    xlab('Weekly Rent') + 
    ggtitle('Long Term Rentals') + 
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

  # Nightly Rate plot
  rate.plot <- ggplot(abb.dataf, aes(x=nightly.rate)) + 
    geom_density(fill=abb.col[1], alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

```

```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

ggMultiPlots(rent.plot, rate.plot, cols=2)

```

From these density plots we see that most weekly rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $400 per night. We filter the data accordingly.

```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Filter the long term data

  rent.dataf <- rent.dataf[rent.dataf$event.price >= 200 & 
                         rent.dataf$event.price <= 1000, ]

 ## Filter the short term data

  abb.dataf <- abb.dataf[abb.dataf$nightly.rate >= 50 &
                         abb.dataf$nightly.rate <= 400, ]

```

## Filter Transaction Data

The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets

```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short term data

  daily.dataf <- daily.dataf[daily.dataf$property.id %in% abb.dataf$property.id,]

 ## Long term list data

  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% rent.dataf$activity.id,]

```

### Save Workspace for using in 'Working' script

```{r savewrkspc, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")

```

## Cross impute rates and rents

### Global

### By submarkets

### Matching for validation

### - Short to Long

### - Long to Short

## Vacancy Models

# Estimate the rental income for all properties

## Other costs/fees/income considerations

## Overall rate of return calculations and comparisons

### - Rates by Product Type (Bed/Bath)

### - Rates by Location (Suburb)

### - Rates by Proximity (Near train stations / beach / event grounds, etc.)

### 2016-11-15 abbReturns_Working.R

@@ -1,0 +1,234 @@
+
+### Preliminary Commands -----------------------------------------------------------------
+
+ ## Set global options
+
+  options(xtable.comment = FALSE)
+
+ ## Load libraries
+
+  library(spdep)
+  library(maptools)
+  library(gstat)
+  library(ggplot2)
+  library(geosphere)
+  library(ggmap)
+  library(xtable)
+  library(chron)
+  library(plyr)
+  library(sp)
+  library(rgeos)
+  library(reshape2)
+  library(stringr)
+  library(RColorBrewer)
+  library(Hmisc)
+
+ ## Set path location
+
+  data.path <- 'c:/dropbox/research/airBNB/data/'
+
+ ## Load sources (custom function files)
+
+  source("c:/code/dataviztools/ggplottools.R")
+  source("c:/code/datamgmttools/dataMungetools.R")
+  source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
+  source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
+
+### Load working workspace ---------------------------------------------------------------  
+  
+  load("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
+
+### Working analysis ---------------------------------------------------------------------  
+
+  
+  
+  
+  
+    
+## Impute prices
+
+#Before imputing the rents and rates, we fix the product factors so that the 
+  #models use a 2bed/2bath unit as the control unit against which others are 
+  #compared.  We also de-factorize the suburb variable for easier use in the 
+  #regression models that follow. 
+
+ 
+## Re-order factors
+
+abb.dataf$bedbath <- factor(abb.dataf$bedbath, 
+                            levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+rent.dataf$bedbath <- factor(rent.dataf$bedbath, 
+                             levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+## Convert suburbs from factor to character
+
+abb.dataf$suburb <- as.character(abb.dataf$suburb)
+rent.dataf$suburb <- as.character(rent.dataf$suburb)
+
+ 
+### Global model
+
+#We begin by imputing rents and rates for all properties using a global model with 
+#suburb fixed effects.  
+ 
+## Set model specifications
+
[…]

### 2016-11-15 analysis_functions.R

@@ -1,0 +1,159 @@
+
+
+
+calcOPQuantiles <- function(sm.df,
+                            daily.df){
+  
+  ## Extract limited daily data  
+  
+  daily.sm <- daily.df[daily.df$property.id %in% sm.df$property.id, ]  
+  
+  ## Calculate the number of open days  
+  
+  # Table all status types
+  status.table <- as.data.frame(table(daily.sm$status, daily.sm$property.id))
+  
+  # cast into a wide data frame
+  status.df <- dcast(status.table, Var2 ~ Var1)
+  
+  # All all.days and open days values
+  status.df$all.days <- rowSums(status.df[ ,2:4])
+  status.df$open.days <- status.df$all.days - status.df$B
+  
+  # Remove those with no open days or no reservations
+  #status.df <- status.df[status.df$open.days != 0, ]
+  #status.df <- status.df[status.df$R != 0, ]
+  
+ ## Calculate occupancy rates  
+  
+  # Calc property specific rate
+  status.df$occ.rate <- status.df$R / status.df$open.days
+  status.df$occ.rate[is.na(status.df$occ.rate)] <- 0
+  status.df$occ.rate[!is.finite(status.df$occ.rate)] <- 0
+
+  # Set up clean set for computation
+  status.comp <- status.df[!is.na(status.df$occ.rate), ]
+  status.comp <- status.comp[status.comp$occ.rate > 0, ]
+
+  # Quantiles for submarket occupancy rates
+  occ.qtl <- Hmisc::wtd.quantile(status.comp$occ.rate, 
+                                 weights=status.comp$open.days, 
+                                 probs=seq(0, 1, .01))
+  occ.qtl[[1]] <- -101/10000000
+  
+  ## Calculate rate quantiles
+  
+  # Limit to non-blocked days
+  open.daily <- daily.sm[daily.sm$status != 'B', ]
+  
+  # Calculate quantiles
+  rate.qtl <- quantile(open.daily$price, probs=seq(0, 1, .01))
+  
+ ## Add to sm data.frame
+  
+  # Add occupancy rate
+  sm.df$occ.rate <- status.df$occ.rate[match(sm.df$property.id, status.df$Var2)]
+  sm.df$occ.qtl <- as.numeric(as.factor(cut(sm.df$occ.rate, 
+                                            breaks=(occ.qtl + (1:101/10000000)))))
[…]

### 2016-11-15 apmDataPrep_Script.R

@@ -1,0 +1,93 @@
+
+ ## Load Libraries
+
+  library(stringr)
+  
+ ## Load custom functions  
+
+  source('c:/code/research/airbnbmelbourne/dataPrep_Functions.R')
+  
+ ## Load Data  
+  
+  raw.path <- 'c:/dropbox/research/airBNB/data/raw/'
+  rent16 <- read.csv(paste0(raw.path, 'rentData.csv'), header=T)
+
+ ## Remove observations without sufficient keys
+  
+  r16 <- rent16[!is.na(rent16$EventID), ]
+  r16 <- r16[!is.na(r16$AddressID), ]
+  r16 <- r16[!is.na(r16$ActivityID), ]
+  
+ ## Create Unique Key
+  
+  r16$id.key <- paste0(as.numeric(as.factor(r16$ActivityID)), '..',
+                       as.numeric(as.factor(r16$AddressID)))
+  r16$id.key <- as.numeric(as.factor(r16$id.key))
+  
+ ## Fix Dates  
+  
+  r16$lastdate <- apmFixDates(r16$LastAdvertisedEventDate)
+  r16$eventdate <- apmFixDates(r16$EventDate)
+  r16$eventyear <- as.numeric(substr(r16$eventdate, 1, 4))
+  
+ ## Remove those not occuring in 2015 or later
+  
+  r16 <- r16[r16$eventyear >= 2014, ]
+  
+ ## Add an identifier that signifies last record in a set of advertisements (of record)  
+    
+  r16 <- r16[order(r16$eventdate, decreasing=T), ]
+  r16 <- r16[order(r16$id.key), ]
+  r16$AID <- paste0(r16$id.key, '..', r16$lastdate)
+  r16$of.record <- ifelse(duplicated(r16$AID), 0 ,1)
+  
+ ## Split into property data and listing data
+  
+  prop.data <- r16[r16$of.record == 1,]
+  list.data <- r16[, c('id.key', 'EventID', 'ActivityID', 'AddressID', 'of.record',
+                       'eventdate', 'EventPrice', 'FirstAdvertisedEventDate',
+                       'FirstAdvertisedEventPrice', 'LastAdvertisedEventDate',
+                       'LastAdvertisedEventPrice', 'EventTypeCode')]
+  
+  ## Remove extra fields from property data
+  
+  prop.data <- prop.data[, c('id.key', 'GeographicalID', 'EventID', 'AddressID', 
[…]

### 2016-11-15 dataPrep_Functions.R

@@ -1,0 +1,204 @@
+##########################################################################################
+#                                                                                        #    
+#  Functions for working with APM and AirDNA data                                        #
+#                                                                                        #
+##########################################################################################
+
+### Analyze the daily data for each property ---------------------------------------------
+
+abbAnalyzeDaily <- function(daily.df){
+  
+ ## Calculate minimum and maximum dates in the range  
+  
+  min <- min(daily.df$date)
+  max <- max(daily.df$date)
+  
+ ## Calculate the Total days, and count each status  
+  
+  total.days <- nrow(daily.df)
+  blocked <- length(which(daily.df$status == 'B'))
+  available <- length(which(daily.df$status == 'A'))
+  reserved <- length(which(daily.df$status == 'R'))
+  
+ ## Return as a data.frame  
+  
+  return(data.frame(property.id = unique(daily.df$property.id),
+                    min.date = min,
+                    max.date = max,
+                    total.days = total.days,
+                    blocked.days = blocked,
+                    available.days = available,
+                    reserved.days = reserved))
+}
+
+### Calculate the occupancy rates for each date in a range -------------------------------
+
+abbCalcDateRates <- function(daily.df){
+  
+ ## Create table of counts by status
+  
+  status.table <- table(daily.df$date, daily.df$status)
+  
+ ## Convert to a data.frame  
+  
+  status.df <- data.frame(Avail=status.table[,1],
+                          Resv=status.table[,2],
+                          Block=status.table[,3],
+                          lp.type=daily.df$lp.type[1])
+  
+ ## Add date   
+  
+  status.df$date <- as.Date(rownames(status.df))
+  
+ ## Add reserved rate (occupancy rate)  
+  
+  status.df$occ.rate <- status.df$Resv / (status.df$Resv + status.df$Avail)
+  
+ ## Return values  
+  
+  return(status.df)
+  
+}
+
+### Impute the missing daily observations ------------------------------------------------
+
+abbImputeDaily <- function(prop.df, 
+                           daily.df, 
+                           rates.df){
+  
[…]

### 2016-11-16 analysis_functions.R
add rev calc

@@ -1,4 +1,129 @@
 
+crossImputeModel <- function(rent.df,
+                             abb.df,
+                             rent.mod.spec,
+                             abb.mod.spec,
+                             geo.field=NULL,
+                             geo.value=NULL,
+                             clip.field=NULL)
+{
+  
+ ## Arguments
+  
+  # rent.df:  data.frame of long term rental observations
+  # abb.df:  data.frame of airbnb properties
+  # rent.mod.spec:  specification for rent price model
+  # abb.mod.spec:  specification for airbnb properties
+  # geo.field: field to split submarkets by
+  # geo.value: specific geography to use
+  # clip.field: field to ensure factors match between rent and abb
+  
+ ## Extract Data from geo
+  
+  if(!is.null(geo.field)){
+    
+    # Create IDs for inclusion in the geo
+    id.rgeo <- which(rent.df[,geo.field] == geo.value)
+    id.ageo <- which(abb.df[,geo.field] == geo.value)
+    
+    # Extract and create new DFs
+    rent.df <- rent.df[id.rgeo, ]
+    abb.df <- abb.df[id.ageo, ]
+    
+  }
+  
+ ## Split data by Property Type  
+  
+  rent.house <- rent.df[rent.df$type == 'House', ]
+  rent.apt <- rent.df[rent.df$type == 'Apartment', ]
+  abb.house <- abb.df[abb.df$type == 'House', ]
+  abb.apt <- abb.df[abb.df$type == 'Apartment', ]
+  
+ ## Remove those within the clip field that isn't present in both  
+  
+  if(!is.null(clip.field)){
+    
+    # Find the fields that are used to clip
+    r.cf <- which(names(rent.df) == clip.field)
+    a.cf <- which(names(abb.df) == clip.field)
+    
+    # Get IDs for those to be removed
+    id.rh <- rent.house[ ,r.cf] %in% names(table(as.character(abb.house[ ,a.cf])))
+    id.ra <- rent.apt[ ,r.cf] %in% names(table(as.character(abb.apt[ ,a.cf])))
+    id.ah <- abb.house[ ,a.cf] %in% names(table(as.character(rent.house[ ,r.cf])))
[…]

### 2016-11-16 abbReturns_Working.R
calculating revenues

@@ -40,65 +40,80 @@
 
 ### Working analysis ---------------------------------------------------------------------  
 
+ ## Impute prices
+
+  # Before imputing the rents and rates, we fix the product factors so that the 
+   # models use a 2bed/2bath unit as the control unit against which others are 
+   # compared.  We also de-factorize the suburb variable for easier use in the 
+   # regression models that follow. 
+
+ ## Re-order factors
+
+  abb.dataf$bedbath <- factor(abb.dataf$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  rent.dataf$bedbath <- factor(rent.dataf$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+ ## Add product as a variable
+  
+  abb.dataf$product <- paste0(substr(abb.dataf$type, 1, 1), abb.dataf$bedbath)
+  rent.dataf$product <- paste0(substr(rent.dataf$type, 1, 1), rent.dataf$bedbath)
+
+ ## Convert suburbs from factor to character
+
+  abb.dataf$suburb <- as.character(abb.dataf$suburb)
+  rent.dataf$suburb <- as.character(rent.dataf$suburb)
+
+ ## Global model
+
+  # We begin by imputing rents and rates for all properties using a global model with 
+  # suburb fixed effects.  
+ 
+  # Set model specifications
+  rent.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
+ 
+ ## Impute globally 
+
+  glob.imp <- crossImputeModel(rent.df=rent.dataf, 
+                               abb.df=abb.dataf, 
+                               rent.mod.spec=rent.mod.spec, 
+                               abb.mod.spec=abb.mod.spec,
+                               clip.field='suburb')
+  
+ ## Calculate market occ and rate quantiles
+  
+  # Split into markets
+  abb.mrkt <- split(glob.imp$abb, glob.imp$abb$product)
+  rent.mrkt <- split(glob.imp$rent, glob.imp$rent$product)
+  
+  # Calculate AirBNB Quantiles
+  abb.qtls <- lapply(abb.mrkt, calcOPQuantiles, daily.df=daily.dataf)
[…]

### 2016-11-16 abbReturns_Script.Rmd
fix 'dom' bug

@@
                         'baths', 'parking', 'has.study', 'has.courtyard',
-                        'has.balcony', 'has.aircond', 'has.garage')
+                        'has.balcony', 'has.aircond', 'has.garage', 'dom')
 

### 2016-11-22 abbDataPrep_Script.Rmd
remove unnecessary source()
updating path code

@@
 
+  # Get computer names
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+  if(comp.name == '7020D-121777-W' | 
+      comp.name == 'DESKTOP-1D7JO4J'){
+
       data.path <- 'c:/dropbox/research/airBNB/data/'
+
+  } else {
+
+      data.path <- 'gideon path'
+
+  }
 
@@
 
-  source("c:/code/datamgmttools/dataMungetools.R")
   source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")

### 2016-11-22 abbReturns_Working.R
updating paths

@@ -25,7 +25,20 @@
 
  ## Set path location
 
-  data.path <- 'c:/dropbox/research/airBNB/data/'
+  # Get computer names
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+  if(comp.name == '7020D-121777-W' | 
+      comp.name == 'DESKTOP-1D7JO4J'){
+  
+    data.path <- 'c:/dropbox/research/airBNB/data/'
+  
+  } else {
+  
+    data.path <- 'gideon path'
+  
+  }
 
  ## Load working workspace   
   

### 2016-11-22 apmDataPrep_Script.R

@@ -9,7 +9,22 @@
   
  ## Load Data  
   
-  raw.path <- 'c:/dropbox/research/airBNB/data/raw/'
+  # Get computer names
+  comp.name <- Sys.info()['nodename']
+  
+  # Assign path based on computer name
+  if(comp.name == '7020D-121777-W' | 
+     comp.name == 'DESKTOP-1D7JO4J'){
+    
+    data.path <- 'c:/dropbox/research/airBNB/data/'
+    
+  } else {
+    
+    data.path <- 'gideon path'
+    
+  }
+  
+  raw.path <- paste0(data.path, '/raw/')
   rent16 <- read.csv(paste0(raw.path, 'rentData.csv'), header=T)
 
  ## Remove observations without sufficient keys

### 2016-11-23 abbReturns_Working.R
adding Revenue Engine function

@@ -51,7 +51,6 @@
   source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
   source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
 
-
 ### Working analysis ---------------------------------------------------------------------  
 
   exch.rate <- 1.32
@@ -129,6 +128,9 @@
   abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
  
  
+  
+  
+  
   glob <- compReturns(rent.df=rent.dataf, 
                          abb.df=abb.dataf, 
                          rent.mod.spec=rent.mod.spec, 

### 2016-11-23 analysis_functions.R

@@ -1,4 +1,44 @@
 
+
+revenueEngine <- function(abb.df,
+                          rent.df,
+                          rate.field='med.rate',
+                          rent.field='event.price',
+                          occ.field='occ.rate',
+                          dom.field='dom',
+                          cost.list=NULL)
+{
+  
+ ## Calculate Airbnb Revenues  
+  
+  abb.rev <- abb.df[ ,rate.field] * 365 * abb.df[ ,occ.field]
+
+ ## Calculate long term rental revenues  
+    
+  rent.rev <- rent.df[, rent.field] * (52 - (abb.df[ ,dom.field] /7))
+  
+ ## Save for future costs
+  
+ ## Return values  
+  
+  return(list(abb=abb.rev,
+              rent=rent.rev))
+  
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
 crossImputeModel <- function(rent.df,
                              abb.df,
                              rent.mod.spec,

### 2016-11-23 analysis_functions.R
update wtdQtl and imputeRR functions

@@ -1,7 +1,8 @@
 
+### Basic engine for calculating the revenues for abb and ltr ----------------------------
 
 revenueEngine <- function(abb.df,
-                          rent.df,
+                          ltr.df,
                           rate.field='med.rate',
                           rent.field='event.price',
                           occ.field='occ.rate',
@@ -15,33 +16,22 @@ revenueEngine <- function(abb.df,
 
  ## Calculate long term rental revenues  
     
-  rent.rev <- rent.df[, rent.field] * (52 - (abb.df[ ,dom.field] /7))
+  ltr.rev <- ltr.df[, rent.field] * (52 - (ltr.df[ ,dom.field] / 7))
   
  ## Save for future costs
   
  ## Return values  
   
   return(list(abb=abb.rev,
-              rent=rent.rev))
+              ltr=ltr.rev))
   
 }
 
+### Cross impute rates and rents ---------------------------------------------------------
 
-
-
-
-
-
-
-
-
-
-
-
-
-crossImputeModel <- function(rent.df,
+imputeRatesRents <- function(ltr.df,
                              abb.df,
-                             rent.mod.spec,
+                             ltr.mod.spec,
                              abb.mod.spec,
                              exch.rate,
                              clip.fields=NULL)
@@ -49,9 +39,9 @@ crossImputeModel <- function(rent.df,
   
  ## Arguments
   
-  # rent.df:  data.frame of long term rental observations
+  # ltr.df:  data.frame of long term rental observations
   # abb.df:  data.frame of airbnb properties
-  # rent.mod.spec:  specification for rent price model
+  # ltr.mod.spec:  specification for rent price model
   # abb.mod.spec:  specification for airbnb properties
   # clip.field: field to ensure factors match between rent and abb
   
@@ -62,15 +52,15 @@ crossImputeModel <- function(rent.df,
     for(i.cf in 1:length(clip.fields)){
     
       # Find the fields that are used to clip
-      r.cf <- which(names(rent.df) == clip.fields[i.cf])
+      l.cf <- which(names(ltr.df) == clip.fields[i.cf])
       a.cf <- which(names(abb.df) == clip.fields[i.cf])
     
[…]

### 2016-11-23 analysis_functions.R
reorg of analysis functions

@@ -102,7 +102,8 @@ imputeRatesRents <- function(ltr.df,
 ### Assign quartile values based on a give vector, weighted if necessary -----------------
 
 makeWtdQtl <- function(data.vec, 
-                       wgts=rep(1,length(data.vec)))
+                       wgts=rep(1,length(data.vec)),
+                       return.type='rank')
 {
   
  ## Load required library  
@@ -111,14 +112,26 @@ makeWtdQtl <- function(data.vec,
   
  ## Set the adjustment jitter to prevent identical breaks  
   
-  adj.jit <- abs(mean(data.vec) / 10000)
+  adj.jit <- abs(mean(data.vec) / 100000)
   
  ## Calculate the weighted quantiles 0  to 1000  
   
-  wtd.qtl <- Hmisc::wtd.quantile(data.vec + runif(length(data.vec), -adj.jit, adj.jit), 
+  wtd.qtl <- Hmisc::wtd.quantile(data.vec + runif(length(data.vec), 0, adj.jit), 
                                  weights=wgts, 
                                  probs=seq(0, 1, .01))
+
+ ## Fix the ends
   
+  # Minimum
+  if(wtd.qtl[1] > min(data.vec)){
+    wtd.qtl[1] <- min(data.vec) - adj.jit
+  }
+  
+  # Maximum
+  if(wtd.qtl[length(wtd.qtl)] < max(data.vec)){
+    wtd.qtl[length(wtd.qtl)] <- max(data.vec) + adj.jit
+  }
+    
  ##  Convert to a vector of quantile indicators 
   
   qtl.vec <- as.numeric(as.factor(cut(data.vec, 
@@ -126,295 +139,392 @@ makeWtdQtl <- function(data.vec,
   
  ## Return value
   
-  return(qtl.vec)
-  
-}
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-### Calculate the Airbnb quantiles -------------------------------------------------------
-
-calcABBQtls <- function(abb.df){
-  
- # Quantiles for market occupancy rates (with a small jitter)
- 
-  occ.qtl <- Hmisc::wtd.quantile(abb.df$occ.rate + runif(nrow(abb.df), -.0001, .0001), 
-                                 weights=(abb.df$bookings + abb.df$available.days), 
-                                 probs=seq(0, 1, .01))
-
- # Quantile for market nightly rates
-  
[…]

### 2016-11-23 abbReturns_Working.R
converting analytical stream to functions

@@ -51,6 +51,8 @@
   source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
   source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
 
+  ltr.dataf <- rent.dataf
+  
 ### Working analysis ---------------------------------------------------------------------  
 
   exch.rate <- 1.32
@@ -90,13 +92,13 @@
   # Remove those with no revenue
   abb.dataf <- abb.dataf[!is.na(abb.dataf$revenue), ]
   
- ## Calculate rental revenues  
+ ## Calculate ltral revenues  
   
   # Calculate the actual revenue
-  rent.dataf$revenue <- rent.dataf$event.price * (52 - rent.dataf$dom/7)
+  ltr.dataf$revenue <- ltr.dataf$event.price * (52 - ltr.dataf$dom/7)
   
   # Remove those with very low revenues (due to very long DOMs)
-  rent.dataf <- rent.dataf[rent.dataf$revenue > 5000, ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$revenue > 5000, ]
   
  ## Save for future costs
   
@@ -107,16 +109,16 @@
   # Re-order factors
   abb.dataf$bedbath <- factor(abb.dataf$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-  rent.dataf$bedbath <- factor(rent.dataf$bedbath, 
+  ltr.dataf$bedbath <- factor(ltr.dataf$bedbath, 
                                levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
 
   # Add product as a variable
   abb.dataf$product <- paste0(substr(abb.dataf$type, 1, 1), abb.dataf$bedbath)
-  rent.dataf$product <- paste0(substr(rent.dataf$type, 1, 1), rent.dataf$bedbath)
+  ltr.dataf$product <- paste0(substr(ltr.dataf$type, 1, 1), ltr.dataf$bedbath)
 
   # Convert suburbs from factor to character
   abb.dataf$suburb <- as.character(abb.dataf$suburb)
-  rent.dataf$suburb <- as.character(rent.dataf$suburb)
+  ltr.dataf$suburb <- as.character(ltr.dataf$suburb)
 
  ## Global model
 
@@ -124,68 +126,21 @@
   # suburb fixed effects.  
  
   # Set model specifications
[…]

### 2016-11-23 analysis_functions.R
table creation function

@@ -307,6 +307,38 @@ revCompWrapper <- function(ltr.df,
   
 }
 
+### Create comparison table --------------------------------------------------------------
+
+createCompTable <- function(abb.df, 
+                            ltr.df,
+                            split.field=NULL){
+  
+  if(is.null(split.field)){
+    
+  } else {
+    
+    # Calculate cross-tab values
+    abb.imp <- tapply2DF(abb.df$abb.imp, abb.df[ ,split.field], mean)
+    abb.act <- tapply2DF(abb.df$abb.act, abb.df[ ,split.field], mean)
+    ltr.imp <- tapply2DF(ltr.df$abb.imp, ltr.df[, split.field], mean)
+    ltr.act <- tapply2DF(ltr.df$abb.act, ltr.df[, split.field], mean)
+    
+    # Add names
+    abb.imp$est <- ltr.imp$est <- 'imputed'
+    abb.imp$data <- abb.act$data <- 'abb'
+    ltr.act$est <- abb.act$est <- 'actual'
+    ltr.act$data <- ltr.imp$data <- 'ltr'
+    
+    # Combine into table
+    rate.table <- rbind(abb.imp, abb.act, ltr.imp, ltr.act)
+    
+  }
+  
+  ## Return Values
+  
+  return(rate.table)
+  
+}
 
 
 

### 2016-11-26 abbReturns_Script.Rmd
updating paths
filled out data prep

--- 2016-11-15 abbReturns_Script.Rmd
@@
 
-Data on AirBNB (short-term) rentals has been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
+Data on AirBNB (short-term) ltrals has been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
 The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 
-Throughout this document we will refer to the short-term data as **'short-term'** or **'AirBNB'** while the long-term data will be referred to as **'long-term'**, **'rental'** or **'lease'**.
-Short-term nightly fees will be referenced as **'rates'** and long-term as **'rent'**.
-We will use **'prices'** to collectively refer to **rates** and **rents**.
-Note that within the Melbourne market rentals are quoted in weekly rents (but are charged to tenants at a monthly rent equivalent to the 1/12 of 52 weeks of rent).
+Throughout this document we will refer to the short-term data as **'short-term'** or **'AirBNB'** while the long-term data will be referred to as **'long-term'**, **'ltral'** or **'lease'**.
+Short-term nightly fees will be referenced as **'rates'** and long-term as **'ltr'**.
+We will use **'prices'** to collectively refer to **rates** and **ltrs**.
+Note that within the Melbourne market ltrals are quoted in weekly ltrs (but are charged to tenants at a monthly ltr equivalent to the 1/12 of 52 weeks of ltr).
 
@@
 
+  # Get computer names
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+  if(comp.name == '7020D-121777-W' | 
+      comp.name == 'DESKTOP-1D7JO4J'){
+
     data.path <- 'c:/dropbox/research/airBNB/data/'
+
+  } else {
+
+    data.path <- 'gideon path'
+
+  }
 
@@
   source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
+
+ ## Set a global parameter
+
+  exch.rate <- 1.32
 
@@
 
-Both the AirBNB and the rental data require some measure of data pre-processing and due to the run times of these function they are done outside of this document.
+Both the AirBNB and the ltral data require some measure of data pre-processing and due to the run times of these function they are done outside of this document.
 For the AirBNB data, the pre-processing is primarily concerned with imputing missing daily observations for a small number of properties in the dataset.
@@
 
-  # Daily rental information
+  # Daily ltral information
 
@@
 
-We then load the long term rental data.
+We then load the long term ltral data.
 This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.
 
-```{r load_rent_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Property level long term rental information
-
-  rent.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
-
- ## Long term rental listing information
+```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Property level long term ltral information
+
+  ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
+
+ ## Long term ltral listing information
 
@@
 
-  names(rent.data) <- tolower(names(rent.data))
+  names(ltr.data) <- tolower(names(ltr.data))
   names(listing.data) <- tolower(names(listing.data))
@@
 
-  rent.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid',
+  ltr.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid',
                       'flatnumber', 'streetnumber', 'streetname', 'streettype', 
@@
 
-  rent.data <- rent.data[ , rent.keep.flds]
+  ltr.data <- ltr.data[ , ltr.keep.flds]
 
@@
 
-Periods are inserted between relevant words for the rental data.
+Periods are inserted between relevant words for the ltral data.
 
@@
 
-  names(rent.data) <- c('id.key', 'geographical.id', 
+  names(ltr.data) <- c('id.key', 'geographical.id', 
                         'event.id', 'address.id', 'activity.id',
@@
   # Date
-  rent.data$event.date <- fixLTDates(rent.data$event.date)
+  ltr.data$event.date <- fixLTDates(ltr.data$event.date)
 
   # Year
-  rent.data$event.year <- as.numeric(substr(rent.data$event.date, 1, 4))
+  ltr.data$event.year <- as.numeric(substr(ltr.data$event.date, 1, 4))
 
@@
 
-  rent.data$has.study <- ifelse(rent.data$has.study == 'True', 1, 0)
-  rent.data$has.courtyard <- ifelse(rent.data$has.courtyard == 'True', 1, 0)
-  rent.data$has.aircon <- ifelse(rent.data$has.aircon == 'True', 1, 0)
-  rent.data$has.balcony <- ifelse(rent.data$has.balcony == 'True', 1, 0)
-  rent.data$has.garage <- ifelse(rent.data$has.garage == 'True', 1, 0)
+  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
+  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
+  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
+  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
+  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
 
@@
 
-AirBNB units are classified into 19 different property type.
+AirBNB units are classified into 19 diffeltr property type.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
@@
 
-Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+Within the long-term ltral data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
 
@@
 Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
-This is most apparent when talking about apartment dwellings.
+This is most appaltr when talking about apartment dwellings.
 In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
@@
 
-  rent.data$type <- 'Other'
-  rent.data$type[rent.data$property.type %in% c('Duplex', 'House',
+  ltr.data$type <- 'Other'
+  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
                                            'Terrace', 'Townhouse')] <- 'House'
-  rent.data$type[rent.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
-
-```
-
-The **Other** categories contain very small percentage of properties in both the AirBNB and the rental data.  As a result, we remove the 'Others' from the data.
+  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
+
+```
+
+The **Other** categories contain very small percentage of properties in both the AirBNB and the ltral data.  As a result, we remove the 'Others' from the data.
 
@@
   abb.data <- subset(abb.data, type != 'Other')
-  rent.data <- subset(rent.data, type != 'Other')
-
-```
-
-Next, for the short term rentals units can be listed as one of three types relating to the extent of the property which is able to be booked:
+  ltr.data <- subset(ltr.data, type != 'Other')
+
+```
+
+Next, for the short term ltrals units can be listed as one of three types relating to the extent of the property which is able to be booked:
 
@@
 
-As long-term rentals do not offer **Private Room** or **Shared Room** options and our purpose here is a comparison of the two we remove all short term properties that do not lease the entire home/apt.
+As long-term ltrals do not offer **Private Room** or **Shared Room** options and our purpose here is a comparison of the two we remove all short term properties that do not lease the entire home/apt.
 Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
@@
     xlab('\nListing Type\n') + 
-    ggtitle('\nShort Term Rentals\n')  +
+    ggtitle('\nShort Term ltrals\n')  +
     ylab('# of Properties\n')
@@
 Next we trim the observations by time.
-Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
-To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
+Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term ltral versus an AirBNB, short term ltral approach to generating income.
+To determine the likely long term ltral rate for any given property, we will use the observed ltral transactions from the market from September 1, 2014 to August 31, 2015.
 Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factor).
@@
 
-  rent.dataf <- rent.data[rent.data$event.date >= '2014-09-01' & 
-                            rent.data$event.date <= '2015-08-31', ]
-  listing.dataf <- listing.data[listing.data$id.key %in% rent.dataf$id.key, ]
+  ltr.dataf <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
+                            ltr.data$event.date <= '2015-08-31', ]
+  listing.dataf <- listing.data[listing.data$id.key %in% ltr.dataf$id.key, ]
 
@@
 
-Location is clearly an important determinant in both the short and long term rental markets.
+Location is clearly an important determinant in both the short and long term ltral markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
   # Limit to extent of data
-  sub.table <- table(rent.dataf$suburb)
+  sub.table <- table(ltr.dataf$suburb)
   sub.table <- sub.table[sub.table != 0]
 
-  # Clip to only those with a rental observation
+  # Clip to only those with a ltral observation
   study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
@@
 
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+It is likely that the short-term ltral market follows a similar market hierarchy, however, we can imagine that a few diffeltr spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melboure:
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
 
@@
 
-About 5% of the long term rental observations have missing latitude and longitude values.
+About 5% of the long term ltral observations have missing latitude and longitude values.
 Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
@@
 
-  miss.LL <- which(is.na(rent.dataf$latitude))
+  miss.LL <- which(is.na(ltr.dataf$latitude))
 
@@
 
-  rent.dataf$miss.LL <- 0
-  rent.dataf$miss.LL[miss.LL] <- 1
+  ltr.dataf$miss.LL <- 0
+  ltr.dataf$miss.LL[miss.LL] <- 1
 
@@
 
-  rent.dataf$latitude[miss.LL] <- rent.dataf$street.latitude[miss.LL]
-  rent.dataf$longitude[miss.LL] <- rent.dataf$street.longitude[miss.LL]
+  ltr.dataf$latitude[miss.LL] <- ltr.dataf$street.latitude[miss.LL]
+  ltr.dataf$longitude[miss.LL] <- ltr.dataf$street.longitude[miss.LL]
 
@@
 
-  rent.dataf <- rent.dataf[!is.na(rent.dataf$latitude), ]
+  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$latitude), ]
 
@@
   # Convert to point shapefile
-  rent.prop.shp <- SpatialPointsDataFrame(cbind(rent.dataf$longitude,
-                                                rent.dataf$latitude),
-                                         rent.dataf,
+  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.dataf$longitude,
+                                                ltr.dataf$latitude),
+                                         ltr.dataf,
                                          proj4string=CRS("+init=epsg:4283"))
@@
   # Add suburb name 
-  spJoin <- over(rent.prop.shp, suburbs.shp)
-  rent.dataf$suburb <- as.character(spJoin$name_2006)
-  rent.dataf$suburb[is.na(rent.dataf$suburb)] <- 'missing'
+  spJoin <- over(ltr.prop.shp, suburbs.shp)
+  ltr.dataf$suburb <- as.character(spJoin$name_2006)
+  ltr.dataf$suburb[is.na(ltr.dataf$suburb)] <- 'missing'
 
   # Add suburb designation
-  rent.dataf$sub.class <- as.character(spJoin$suburbdesi)
-  rent.dataf$sub.class[is.na(rent.dataf$sub.class)] <- 'missing'
+  ltr.dataf$sub.class <- as.character(spJoin$suburbdesi)
+  ltr.dataf$sub.class[is.na(ltr.dataf$sub.class)] <- 'missing'
 
   # Add SA1 designation
-  spJoin <- over(rent.prop.shp, sa1s.shp)
-  rent.dataf$sa1 <- spJoin$sa1_main11
+  spJoin <- over(ltr.prop.shp, sa1s.shp)
+  ltr.dataf$sa1 <- spJoin$sa1_main11
 
   ## Add Beach Designation
-  spJoin <- over(rent.prop.shp, beach.buffer)
-  rent.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
+  spJoin <- over(ltr.prop.shp, beach.buffer)
+  ltr.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
 
   # Remove those missing a suburb classification (out of area)
-  rent.dataf <- rent.dataf[rent.dataf$sub.class != 'missing', ]
-  rent.dataf <- rent.dataf[rent.dataf$sa1 != 'missing', ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$sub.class != 'missing', ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$sa1 != 'missing', ]
 
@@
   # Add individual classes
-  rent.dataf$sub.mrkt <- 'rural'
-  rent.dataf$sub.mrkt[rent.dataf$sub.class == 'Middle'] <- 'suburban'
-  rent.dataf$sub.mrkt[rent.dataf$sub.class == 'Inner'] <- 'city'
-  rent.dataf$sub.mrkt[rent.dataf$suburb %in% core.suburbs] <- 'city-core'
-  rent.dataf$sub.mrkt[rent.dataf$beach == 1] <- 'beach'
+  ltr.dataf$sub.mrkt <- 'rural'
+  ltr.dataf$sub.mrkt[ltr.dataf$sub.class == 'Middle'] <- 'suburban'
+  ltr.dataf$sub.mrkt[ltr.dataf$sub.class == 'Inner'] <- 'city'
+  ltr.dataf$sub.mrkt[ltr.dataf$suburb %in% core.suburbs] <- 'city-core'
+  ltr.dataf$sub.mrkt[ltr.dataf$beach == 1] <- 'beach'
 
   # Order the factors properly
-  rent.dataf$sub.mrkt <- factor(rent.dataf$sub.mrkt, 
+  ltr.dataf$sub.mrkt <- factor(ltr.dataf$sub.mrkt, 
                                levels=c('city-core', 'city', 'suburban', 
@@
 
-```{r rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
   # Make map
-  rent.map <- ggplot() +
+  ltr.map <- ggplot() +
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=rent.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
+    geom_point(data=ltr.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
     scale_color_manual(values=sm.col) +
@@
     guides(colour = guide_legend(override.aes = list(size=3))) + 
-    ggtitle('Long Term Rental Location\nBy Submarket')
+    ggtitle('Long Term ltral Location\nBy Submarket')
 
@@
 
-  ggMultiPlots(abb.map, rent.map, cols=2)
+  ggMultiPlots(abb.map, ltr.map, cols=2)
 
@@
   # Make map
-  renttype.map <- ggplot() +
-    geom_bar(data=rent.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
+  ltrtype.map <- ggplot() +
+    geom_bar(data=ltr.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
 
-  ggMultiPlots(abbtype.map, renttype.map, cols=2)
+  ggMultiPlots(abbtype.map, ltrtype.map, cols=2)
 
@@
 
-We now filter both datasets by removing observed values unlikely to represent 'typical' short or long term rental properties.
+We now filter both datasets by removing observed values unlikely to represent 'typical' short or long term ltral properties.
 
@@
 We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
-We then plot the distribution of different bedrooms counts.
+We then plot the distribution of diffeltr bedrooms counts.
 From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
@@
   # Long term data
-  rent.dataf <- rent.dataf[!is.na(rent.dataf$bedrooms), ]
-  rent.dataf <- rent.dataf[rent.dataf$bedrooms <= 10, ]
+  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$bedrooms), ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$bedrooms <= 10, ]
 
@@
 
-  rentbed <- ggplot(rent.dataf, aes(x=bedrooms)) + 
+  ltrbed <- ggplot(ltr.dataf, aes(x=bedrooms)) + 
     geom_bar(fill=abb.col[3], color=abb.col[3]) +
@@
     ylab('') +
-    ggtitle('Bedrooms in Long Term Rentals')
+    ggtitle('Bedrooms in Long Term ltrals')
 
@@
     ylab('') +
-    ggtitle('Bedrooms in Short Term Rentals')
+    ggtitle('Bedrooms in Short Term ltrals')
 
@@
 
-  ggMultiPlots(abbbed, rentbed, cols=1)
-
-```
-
-For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
+  ggMultiPlots(abbbed, ltrbed, cols=1)
+
+```
+
+For both short and long term ltrals we see that most apartments have less than 4 bedrooms and houses less than 5.
 We filter the data accordingly.
-Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
+Additionally, note that short term ltrals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
 We convert the 0 bed short term units to 1 bed units.
@@
   abb.dataf <- abb.dataf[abb.dataf$bedrooms < 5, ]
-  rent.dataf <- rent.dataf[rent.dataf$bedrooms < 5, ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$bedrooms < 5, ]
 
@@
   abba <- which(abb.dataf$bedrooms > 3 & abb.dataf$type =='Apartment')
-  renta <- which(rent.dataf$bedrooms > 3 & rent.dataf$type =='Apartment')
+  ltra <- which(ltr.dataf$bedrooms > 3 & ltr.dataf$type =='Apartment')
   if(length(abba)>0) abb.dataf <- abb.dataf[-abba, ]
-  if(length(renta)>0) rent.dataf <- rent.dataf[-renta, ]
+  if(length(ltra)>0) ltr.dataf <- ltr.dataf[-ltra, ]
 
@@
  ## Remove missing data
-rent.dataf <- rent.dataf[!is.na(rent.dataf$baths), ]
+ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$baths), ]
 abb.dataf <- abb.dataf[!is.na(abb.dataf$baths), ]
@@
 
-  ltbath <- ggplot(rent.dataf, aes(x=baths)) + 
+  ltbath <- ggplot(ltr.dataf, aes(x=baths)) + 
     geom_bar(fill=abb.col[3], color=abb.col[3]) +
@@
     ylab('') + 
-    ggtitle('Bathrooms in Long Term Rentals')
+    ggtitle('Bathrooms in Long Term ltrals')
 
@@
     ylab('') + 
-    ggtitle('Bathrooms in Short Term Rentals')
+    ggtitle('Bathrooms in Short Term ltrals')
 
@@
   # Long term data
-  rent.dataf <- rent.dataf[rent.dataf$baths < 4, ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$baths < 4, ]
 
@@
 In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
 As a result we examine the combinations of the two.
@@
 
-  rent.dataf$bedbath <- paste0(rent.dataf$bedrooms, '..', rent.dataf$baths)
+  ltr.dataf$bedbath <- paste0(ltr.dataf$bedrooms, '..', ltr.dataf$baths)
   abb.dataf$bedbath <- paste0(abb.dataf$bedrooms, '..', abb.dataf$baths)
@@
 
-  ltb <- ggplot(rent.dataf, aes(x=bedbath)) + 
+  ltb <- ggplot(ltr.dataf, aes(x=bedbath)) + 
     geom_bar(fill=abb.col[3], color=abb.col[3]) +
@@
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ggtitle('Long Term Rentals') + 
+    ggtitle('Long Term ltrals') + 
     facet_wrap(~type)
@@
     ylab('Number of Properties\n') +
-    ggtitle('Short Term Rentals') + 
+    ggtitle('Short Term ltrals') + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
@@
 
-  rent.dataf <- rent.dataf[rent.dataf$bedbath %in% acc.bb, ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$bedbath %in% acc.bb, ]
   abb.dataf <- abb.dataf[abb.dataf$bedbath %in% acc.bb, ]
@@
 
-### Rates and Rents
-
-Finally, we turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
+### Rates and ltrs
+
+Finally, we turn to filtering by the prices -- the nightly rates and weekly ltral values.  We start by removing observations missing price data.
 
@@
 
-  rent.dataf <- rent.dataf[!is.na(rent.dataf$event.price), ]
+  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$event.price), ]
   abb.dataf <- abb.dataf[!is.na(abb.dataf$nightly.rate), ]
@@
 
-  # Rent Plot
-  rent.plot <- ggplot(rent.dataf, aes(x=event.price)) + 
+  # ltr Plot
+  ltr.plot <- ggplot(ltr.dataf, aes(x=event.price)) + 
     geom_density(fill=abb.col[3],alpha=.8) +
     ylab('') +
-    xlab('Weekly Rent') + 
-    ggtitle('Long Term Rentals') + 
+    xlab('Weekly ltr') + 
+    ggtitle('Long Term ltrals') + 
     scale_x_continuous(limits=c(0, 1500)) +
@@
     xlab('Nightly Rate') +
-    ggtitle('Short Term Rentals') + 
+    ggtitle('Short Term ltrals') + 
     scale_x_continuous(limits=c(0, 600)) +
@@
 
-ggMultiPlots(rent.plot, rate.plot, cols=2)
-
-```
-
-From these density plots we see that most weekly rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $400 per night.
+ggMultiPlots(ltr.plot, rate.plot, cols=2)
+
+```
+
+From these density plots we see that most weekly ltrals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $400 per night.
 We filter the data accordingly.
@@
 
-  rent.dataf <- rent.dataf[rent.dataf$event.price >= 200 & 
-                         rent.dataf$event.price <= 1000, ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$event.price >= 200 & 
+                         ltr.dataf$event.price <= 1000, ]
 
@@
 
-  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% rent.dataf$activity.id,]
+  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% ltr.dataf$activity.id,]
+
+```
+
+Finally, we convert the prepared data back to the original object names.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  abb.data <- abb.dataf
+  daily.data <- daily.dataf
+  ltr.data <- ltr.dataf
+  listing.data <- listing.dataf
+
+```
+
+# Prepare for Revenue Estimation
+
+We now turn to calculating the revenues for each property under an Airbnb and a long term rental scenario.  Before we start, there are few additional data prepartion tasks to undertake.
+
+First we calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed for the Airbnb properties only.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Determine # of booking for each airbnb
+  abb.data$bookings <- (abb.data$total.days - 
+                          abb.data$blocked.days - 
+                           abb.data$available.days)
+
+  # Determine property specific occupancy rate
+  abb.data$occ.rate <- (abb.data$bookings / 
+                           (abb.data$total.days - abb.data$blocked.days))
+
+  # Set the blocked rate
+  abb.data$blocked.rate <- abb.data$blocked.days / abb.data$total.days
+
+  # Set the extrapolation parameter for those on the site for less than whole period
+  abb.data$extr.par <- 366 / abb.data$total.days
+
+```
+
+Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $600 per night.
+From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Get all of the reservations
+  resv.daily <- daily.data[daily.data$status == 'R' &
+                             daily.data$booked.date != 'imputed' &
+                              daily.data$price < 600, ]
+
+  # Calculate the property specific median nightly rate
+  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
+
+  # Add median rate to the property  
+  abb.data$med.rate <- med.daily$Var[match(abb.data$property.id, med.daily$ID)]
+
+```
+
+For the airbnb properties we then calculate the actual revenue over the Sep 1 2015 to Aug 31 2016 period. Those with no revenue are removed.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Calculate the total revenue  
+  abb.data$revenue <- (abb.data$med.rate * exch.rate * 
+                          abb.data$extr.par * abb.data$bookings)
+
+  # Remove those with no revenue
+  abb.data <- abb.data[!is.na(abb.data$revenue), ]
+
+```
+
+Next, we calculate the revenue for the long term rental data, saving only those with revenue of at least $5,000 (less than this represented properties with very long days on market.)
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Calculate ltral revenues
+
+  # Calculate the actual revenue
+  ltr.data$revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
+
+  # Remove those with very low revenues (due to very long DOMs)
+  ltr.data <- ltr.data[ltr.data$revenue > 5000, ]
+
+ ## Save for future costs
+
+```
+
+Finally, we create and fix three variables.
+One factor variable for bed/bath combination, a factor variable that splits bed/bath by house and apartment and then we convert suburb from a factor to a character.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Re-order factors
+  abb.data$bedbath <- factor(abb.data$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  ltr.data$bedbath <- factor(ltr.data$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+  # Add product as a variable
+  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
+  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
+
+  # Convert suburbs from factor to character
+  abb.data$suburb <- as.character(abb.data$suburb)
+  ltr.data$suburb <- as.character(ltr.data$suburb)
 
@@
 
-## Cross impute rates and rents
+## Cross impute rates and ltrs
 
@@
 
-# Estimate the rental income for all properties
+# Estimate the ltral income for all properties
 

### 2016-11-26 abbReturns_Working.R
remove data cleaning

@@ -55,70 +55,7 @@
   
 ### Working analysis ---------------------------------------------------------------------  
 
-  exch.rate <- 1.32
 
- ## Calculate actual revenue for study period for AirBnb
-  
-  # Determine # of booking for each airbnb
-  abb.dataf$bookings <- (abb.dataf$total.days - 
-                          abb.dataf$blocked.days - 
-                           abb.dataf$available.days)
-  
-  # Determine property specific occupancy rate
-  abb.dataf$occ.rate <- (abb.dataf$bookings / 
-                           (abb.dataf$total.days - abb.dataf$blocked.days))
-  
-  # Set the blocked rate
-  abb.dataf$blocked.rate <- abb.dataf$blocked.days / abb.dataf$total.days
-  
-  # Set the extrapolation parameter for those on the site for less than whole period
-  abb.dataf$extr.par <- 366 / abb.dataf$total.days
-  
-  # Get all of the reservations
-  resv.daily <- daily.dataf[daily.dataf$status == 'R' &
-                             daily.dataf$booked.date != 'imputed' &
-                              daily.dataf$price < 600, ]
-  
-  # Calculate the property specific median nightly rate
-  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-  
-  # Add median rate to the property  
-  abb.dataf$med.rate <- med.daily$Var[match(abb.dataf$property.id, med.daily$ID)] 
-  
-  # Calculate the total revenue  
-  abb.dataf$revenue <- (abb.dataf$med.rate * exch.rate * 
-                          abb.dataf$extr.par * abb.dataf$bookings)
-  
-  # Remove those with no revenue
-  abb.dataf <- abb.dataf[!is.na(abb.dataf$revenue), ]
-  
- ## Calculate ltral revenues  
-  
-  # Calculate the actual revenue
-  ltr.dataf$revenue <- ltr.dataf$event.price * (52 - ltr.dataf$dom/7)
-  
-  # Remove those with very low revenues (due to very long DOMs)
-  ltr.dataf <- ltr.dataf[ltr.dataf$revenue > 5000, ]
-  
- ## Save for future costs
-  
-### Comparison
-  
- ## Data prep
-    
-  # Re-order factors
-  abb.dataf$bedbath <- factor(abb.dataf$bedbath, 
[…]

### 2016-11-27 server.R
initial commit of ShinyApp

@@ -1,0 +1,407 @@
+################################################################################
+#                                                                              #
+#   Server for Reproducible Real Estate Analysis                               #
+#                                                                              #  
+################################################################################
+
+# load libraries
+
+library(shiny)
+library(xtable)
+library(sp)
+library(spdep)
+library(maptools)
+library(ggplot2)
+library(hexbin)
+library(Hmisc)
+
+load("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
+
+######################################################################################
+### Shiny Server ---------------------------------------------------------------------
+
+shinyServer(function(input, output) {
+
+## Extract the county data ---------------------------------------------------------------  
+    
+  getCountyData <- eventReactive(input$county, {
+    if(input$county != 'none'){
+      res.obj <- ww[[which(names(ww) == input$county)]]
+    } else {
+      res.obj <- 'none'
+    }
+    return(res.obj)
+  })
+  
+## Build the data for the plots ----------------------------------------------------------  
+  
+  buildData <- eventReactive(input$plot, {
+    
+  ## Get the county data
+    
+    if(input$county != 'none'){
+      res.obj <- getCountyData()
+    }
+    
+  ## Fix the input variables
+    
+    # Combine input variables
+    all.vars <- list(input$xVar, input$yVar, input$f1Var, input$col, input$shp,
+                     input$abserr, input$predType, input$hrb, input$timeRange,
+                     input$useMTB, input$useAVR, input$useRME, input$useSRS,
+                     input$useHED, input$useBAS, input$useROB, input$useWGT)
+    
+    # Provide Names
+    names(all.vars) <- c('xVar', 'yVar', 'f1Var', 'col', 'shp', 'abserr', 
+                         'predType', 'hrb', 'timeRange', 'useMTB', 'useAVR',
[…]

### 2016-12-11 abbReturns_Working.R
move data prep to script

@@ -51,74 +51,9 @@
   source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
   source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
 
-  ltr.dataf <- rent.dataf
-  
 ### Working analysis ---------------------------------------------------------------------  
 
-  exch.rate <- 1.32
-
- ## Calculate actual revenue for study period for AirBnb
-  
-  # Determine # of booking for each airbnb
-  abb.dataf$bookings <- (abb.dataf$total.days - 
-                          abb.dataf$blocked.days - 
-                           abb.dataf$available.days)
-  
-  # Determine property specific occupancy rate
-  abb.dataf$occ.rate <- (abb.dataf$bookings / 
-                           (abb.dataf$total.days - abb.dataf$blocked.days))
-  
-  # Set the blocked rate
-  abb.dataf$blocked.rate <- abb.dataf$blocked.days / abb.dataf$total.days
-  
-  # Set the extrapolation parameter for those on the site for less than whole period
-  abb.dataf$extr.par <- 366 / abb.dataf$total.days
-  
-  # Get all of the reservations
-  resv.daily <- daily.dataf[daily.dataf$status == 'R' &
-                             daily.dataf$booked.date != 'imputed' &
-                              daily.dataf$price < 600, ]
-  
-  # Calculate the property specific median nightly rate
-  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-  
-  # Add median rate to the property  
-  abb.dataf$med.rate <- med.daily$Var[match(abb.dataf$property.id, med.daily$ID)] 
-  
-  # Calculate the total revenue  
-  abb.dataf$revenue <- (abb.dataf$med.rate * exch.rate * 
-                          abb.dataf$extr.par * abb.dataf$bookings)
-  
-  # Remove those with no revenue
-  abb.dataf <- abb.dataf[!is.na(abb.dataf$revenue), ]
-  
- ## Calculate ltral revenues  
-  
-  # Calculate the actual revenue
-  ltr.dataf$revenue <- ltr.dataf$event.price * (52 - ltr.dataf$dom/7)
-  
-  # Remove those with very low revenues (due to very long DOMs)
-  ltr.dataf <- ltr.dataf[ltr.dataf$revenue > 5000, ]
-  
[…]

### 2016-12-11 abbReturns_Script.Rmd
REORG:  Preliminary commands

--- 2016-11-15 abbReturns_Script.Rmd
@@
 output:
+  pdf_document: default
   html_notebook: default
-  pdf_document: default
 ---
@@
 
-This document is intended the literate programming of our analysis for the 'Should I AirBNB My Property?' research project.
+This document is the literate programming of our analysis for the 'Should I AirBNB My Property?' research project.
 Below we document the complete data provenance, taking our data from the raw source data through to the final results.
@@
 As a very brief overview, we will be comparing the financial returns of short-term (AirBNB-type) and long-term (traditional leases) leasing of residential properties in Melbourne, Australia.
-We perform this comparison under a hypothetical condition where-in an investor purchases a property on Septemeber 1, 2015 and is looking to determine whether too lease out the property on a traditional long-term lease (12 months) or as an AirBNB property.
+We perform this comparison under a hypothetical condition where-in an investor purchases a property on Septemeber 1, 2015 and is looking to determine whether to lease out the property on a traditional long-term lease (12 months) or nightly as an AirBNB property.
 We examine the returns for the following 12 months.
@@
 
-Data on AirBNB (short-term) rentals has been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
+Data on AirBNB (short-term) rentals have been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
 The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
@@
 We will use **'prices'** to collectively refer to **rates** and **rents**.
-Note that within the Melbourne market rentals are quoted in weekly rents (but are charged to tenants at a monthly rent equivalent to the 1/12 of 52 weeks of rent).
+Note that within the Melbourne long term rentals are quoted in weekly rents but are charged to tenants at a monthly rent equivalent to 1/12 of 52 weeks of rent.
 
@@
 
-We begin with a number of preliminary commands that include setting the global options, loading necessary packages (libraries), setting the path to the raw data sources and reading in custom functions used later in the analysis.
-
-```{r prelim_cmds, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
- ## Set global options
-
-  options(xtable.comment = FALSE)
-
- ## Load libraries
+We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.
+
+```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
@@
 
- ## Set path location
+```
+
+We then set the paths to the data and the code, conditional on which of the authors is running the analysis.
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  # Get computer names
+
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+
+  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
 
     data.path <- 'c:/dropbox/research/airBNB/data/'
-
- ## Load sources (custom function files)
-
-  source("c:/code/dataviztools/ggplottools.R")
-  source("c:/code/datamgmttools/dataMungetools.R")
-  source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
-  source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
+    code.path <- 'c:/code/'
+
+  } else {
+
+    data.path <- 'alternate data path'
+    code.path <- 'alternate data path'
+
+  }
+
+```
+
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  source(paste0(code.path, "dataviztools/ggplottools.R"))
+  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
+
+```
+
+Finally, we set the constants used in this study:
+
+1.
+**Exchange rate**: The Airbnb rates are provided in US dollars.
+We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  exch.rate <- 1.32
 
@@
 
+Airbnb data in US dollars, so we must set an exchange rate.  Average of that period was 1.32 Australian dollars to US dollars.
+
+```{r exch_rate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+  exch.rate <- 1.32
+
+```
+
 &nbsp;
@@
 
-  rent.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
+  ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
 
@@
 
-  rent.data <- rent.data[ , rent.keep.flds]
+  ltr.data <- ltr.data[ ,ltr.keep.flds]
 
@@
 
-  rent.data$type <- 'Other'
-  rent.data$type[rent.data$property.type %in% c('Duplex', 'House',
+  ltr.data$type <- 'Other'
+  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
                                            'Terrace', 'Townhouse')] <- 'House'
-  rent.data$type[rent.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
+  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
 
@@
   abb.data <- subset(abb.data, type != 'Other')
-  rent.data <- subset(rent.data, type != 'Other')
+  ltr.data <- subset(ltr.data, type != 'Other')
 
@@
   # Limit to extent of data
-  sub.table <- table(rent.dataf$suburb)
+  sub.table <- table(ltr.dataf$suburb)
   sub.table <- sub.table[sub.table != 0]
@@
   # Convert to point shapefile
-  rent.prop.shp <- SpatialPointsDataFrame(cbind(rent.dataf$longitude,
-                                                rent.dataf$latitude),
-                                         rent.dataf,
+  rent.prop.shp <- SpatialPointsDataFrame(cbind(ltr.dataf$longitude,
+                                                ltr.dataf$latitude),
+                                         ltr.dataf,
                                          proj4string=CRS("+init=epsg:4283"))
@@
   spJoin <- over(rent.prop.shp, suburbs.shp)
-  rent.dataf$suburb <- as.character(spJoin$name_2006)
-  rent.dataf$suburb[is.na(rent.dataf$suburb)] <- 'missing'
+  ltr.dataf$suburb <- as.character(spJoin$name_2006)
+  ltr.dataf$suburb[is.na(ltr.dataf$suburb)] <- 'missing'
 
   # Add suburb designation
-  rent.dataf$sub.class <- as.character(spJoin$suburbdesi)
-  rent.dataf$sub.class[is.na(rent.dataf$sub.class)] <- 'missing'
+  ltr.dataf$sub.class <- as.character(spJoin$suburbdesi)
+  ltr.dataf$sub.class[is.na(ltr.dataf$sub.class)] <- 'missing'
 
@@
   spJoin <- over(rent.prop.shp, sa1s.shp)
-  rent.dataf$sa1 <- spJoin$sa1_main11
+  ltr.dataf$sa1 <- spJoin$sa1_main11
 
@@
   spJoin <- over(rent.prop.shp, beach.buffer)
-  rent.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
+  ltr.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
 
   # Remove those missing a suburb classification (out of area)
-  rent.dataf <- rent.dataf[rent.dataf$sub.class != 'missing', ]
-  rent.dataf <- rent.dataf[rent.dataf$sa1 != 'missing', ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$sub.class != 'missing', ]
+  ltr.dataf <- ltr.dataf[ltr.dataf$sa1 != 'missing', ]
 
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=rent.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
+    geom_point(data=ltr.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
     scale_color_manual(values=sm.col) +
@@
   renttype.map <- ggplot() +
-    geom_bar(data=rent.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=ltr.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
 
-  rentbed <- ggplot(rent.dataf, aes(x=bedrooms)) + 
+  rentbed <- ggplot(ltr.dataf, aes(x=bedrooms)) + 
     geom_bar(fill=abb.col[3], color=abb.col[3]) +
@@
   abba <- which(abb.dataf$bedrooms > 3 & abb.dataf$type =='Apartment')
-  renta <- which(rent.dataf$bedrooms > 3 & rent.dataf$type =='Apartment')
+  renta <- which(ltr.dataf$bedrooms > 3 & ltr.dataf$type =='Apartment')
   if(length(abba)>0) abb.dataf <- abb.dataf[-abba, ]
-  if(length(renta)>0) rent.dataf <- rent.dataf[-renta, ]
+  if(length(renta)>0) ltr.dataf <- ltr.dataf[-renta, ]
 
@@
   # Rent Plot
-  rent.plot <- ggplot(rent.dataf, aes(x=event.price)) + 
+  rent.plot <- ggplot(ltr.dataf, aes(x=event.price)) + 
     geom_density(fill=abb.col[3],alpha=.8) +
@@
 
-  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% rent.dataf$activity.id,]
-
-```
+  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% ltr.dataf$activity.id,]
+
+```
+
+## Calculate Observed Revenues
+
+```{r abb_revs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Calculate actual revenue for study period for AirBnb
+
+  # Determine # of booking for each airbnb
+  abb.dataf$bookings <- (abb.dataf$total.days - 
+                          abb.dataf$blocked.days - 
+                           abb.dataf$available.days)
+
+  # Determine property specific occupancy rate
+  abb.dataf$occ.rate <- (abb.dataf$bookings / 
+                           (abb.dataf$total.days - abb.dataf$blocked.days))
+
+  # Set the blocked rate
+  abb.dataf$blocked.rate <- abb.dataf$blocked.days / abb.dataf$total.days
+
+  # Set the extrapolation parameter for those on the site for less than whole period
+  abb.dataf$extr.par <- 366 / abb.dataf$total.days
+
+  # Get all of the reservations
+  resv.daily <- daily.dataf[daily.dataf$status == 'R' &
+                             daily.dataf$booked.date != 'imputed' &
+                              daily.dataf$price < 600, ]
+
+  # Calculate the property specific median nightly rate
+  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
+
+  # Add median rate to the property  
+  abb.dataf$med.rate <- med.daily$Var[match(abb.dataf$property.id, med.daily$ID)]
+
+  # Calculate the total revenue  
+  abb.dataf$revenue <- (abb.dataf$med.rate * exch.rate * 
+                          abb.dataf$extr.par * abb.dataf$bookings)
+
+  # Remove those with no revenue
+  abb.dataf <- abb.dataf[!is.na(abb.dataf$revenue), ]
+```
+
+```{r ltr_revs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Calculate ltral revenues
+
+  # Calculate the actual revenue
+  ltr.dataf$revenue <- ltr.dataf$event.price * (52 - ltr.dataf$dom / 7)
+
+  # Remove those with very low revenues (due to very long DOMs)
+  ltr.dataf <- ltr.dataf[ltr.dataf$revenue > 5000, ]
+
+```
+
+Data transformation steps
+
+```{r data_trans3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Re-order factors
+  abb.dataf$bedbath <- factor(abb.dataf$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  ltr.dataf$bedbath <- factor(ltr.dataf$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+  # Add product as a variable
+  abb.dataf$product <- paste0(substr(abb.dataf$type, 1, 1), abb.dataf$bedbath)
+  ltr.dataf$product <- paste0(substr(ltr.dataf$type, 1, 1), ltr.dataf$bedbath)
+
+  # Convert suburbs from factor to character
+  abb.dataf$suburb <- as.character(abb.dataf$suburb)
+  ltr.dataf$suburb <- as.character(ltr.dataf$suburb)
+
+```
+
+## Save for future costs
 

### 2016-12-12 abbReturns_Script.Rmd
REORG:  Through final

--- 2016-11-26 abbReturns_Script.Rmd
@@
 
-Data on AirBNB (short-term) ltrals has been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
+Data on AirBNB (short-term) rentals have been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
 The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 
-Throughout this document we will refer to the short-term data as **'short-term'** or **'AirBNB'** while the long-term data will be referred to as **'long-term'**, **'ltral'** or **'lease'**.
-Short-term nightly fees will be referenced as **'rates'** and long-term as **'ltr'**.
-We will use **'prices'** to collectively refer to **rates** and **ltrs**.
-Note that within the Melbourne market ltrals are quoted in weekly ltrs (but are charged to tenants at a monthly ltr equivalent to the 1/12 of 52 weeks of ltr).
+Throughout this document we will refer to the short-term data as **'short-term'** or **'AirBNB'** while the long-term data will be referred to as **'long-term'**, **'rental'** or **'lease'**.
+Short-term nightly fees will be referenced as **'rates'** and long-term as **'rent'**.
+We will use **'prices'** to collectively refer to **rates** and **rents**.
+Note that within the Melbourne long term rentals are quoted in weekly rents but are charged to tenants at a monthly rent equivalent to 1/12 of 52 weeks of rent.
 
@@
 
- ## Set path location
+```
+
+We then set the paths to the data and the code, conditional on which of the authors is running the analysis.
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
   # Get computer names
+
   comp.name <- Sys.info()['nodename']
@@
   # Assign path based on computer name
-  if(comp.name == '7020D-121777-W' | 
-      comp.name == 'DESKTOP-1D7JO4J'){
+
+  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
 
     data.path <- 'c:/dropbox/research/airBNB/data/'
+    code.path <- 'c:/code/'
 
@@
 
-    data.path <- 'gideon path'
+    data.path <- 'alternate data path'
+    code.path <- 'alternate data path'
 
@@
 
- ## Load sources (custom function files)
-
-  source("c:/code/dataviztools/ggplottools.R")
-  source("c:/code/datamgmttools/dataMungetools.R")
-  source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
-  source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
-
- ## Set a global parameter
+```
+
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  source(paste0(code.path, "dataviztools/ggplottools.R"))
+  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
+
+```
+
+We then set the constants used in this study:
+
+1.
+**Exchange rate**: The Airbnb rates are provided in US dollars.
+We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
@@
 
+Finally, we set the color to be used in the analysis.  We use AirBnb's official palette of 10 colors.
+
 ```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
- ## Set basic color to use in palettes
+ # Set all colors
 
@@
 
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+  # Set specific colors
+
+  str.col <- abb.col[1]
+  ltr.col <- abb.col[3]
 
@@
 
-Both the AirBNB and the ltral data require some measure of data pre-processing and due to the run times of these function they are done outside of this document.
+Both the AirBNB and the long term rental data require some measure of data pre-processing and due to the run times of these processes they are done outside of this document.
 For the AirBNB data, the pre-processing is primarily concerned with imputing missing daily observations for a small number of properties in the dataset.
 Full information on this process can be found in the **airbnbDataClean.Rmd** and **dataCleanFunctions.R** files.
-Do note that most of the imputed data is ignored by our choice of study time period later on.
+Do note that most of the imputed data is ignored by our choice of study time period.
 
@@
 
-Next we load in the raw data.  The short-term data is found in two separate files, one providing information on the property itself data and one providing a daily record of bookings.
-
+Next we load in the raw data.  The Airbnb data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.  
 ```{r load_abb_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
 
-We then load the long term ltral data.
+We then load the long term rental data.
 This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.
@@
 
- ## Property level long term ltral information
+ # Property level long term ltral information
 
@@
 
- ## Long term ltral listing information
+ # Long term ltral listing information
 
@@
 
-And, finally, we load two GIS shapefiles that denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
-We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River.]
+And, finally, we load three GIS shapefiles.
+The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
+We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]
 
@@
 
- ## SA1 shapefile
+  # Suburb shapefile
+
+  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
+                               proj4string=CRS("+init=epsg:4283"),
+                               delete_null_obj=TRUE)
+
+  # SA1 shapefile
 
@@
 
-  ## Suburb shapefile
-
-  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
-                               proj4string=CRS("+init=epsg:4283"),
-                               delete_null_obj=TRUE)
-
-  ## Beach file
+  # Beach file
 
@@
 
-## Data Cleaning and Preparation
+## Data Preparation
 
@@
 
-### Trim Fields
+### Trim and Standardize Fields
 
@@
 
- ## Short term data
+ # Short term data
 
@@
 
- ## Long term data
+ # Long term data
 
@@
 
- ## Geographic data
+ # Geographic data
 
@@
 ```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Property Data
 
@@
 
-  abb.data <- abb.data[ , abb.keep.flds]
+  abb.data <- abb.data[, abb.keep.flds]
 
@@
 ```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Long term property Data
 
@@
 
-  ltr.data <- ltr.data[ , ltr.keep.flds]
-
-```
-
-&nbsp;
-
-### Standardize Field Names
-
-&nbsp;
-
-Next we standardize the field names.
-Here we follow the short-term data convention of placing a period between words in the name.
-We also shorten a number of the fields to make future coding easier.
-No changes are made to the monthly or daily data.
-
-For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names.
+  ltr.data <- ltr.data[,ltr.keep.flds]
+
+```
+
+Next we standardize the field names.  Here we follow the short-term data convention of placing a period between words in the name.  We also shorten a number of the fields to make future coding easier.
+
+For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names. No changes are made to the names of the Airbnb daily data.
 
@@
   names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id', 
-                           'of.record',
-                           'event.date', 'event.price', 'first.adv.date', 
+                           'of.record', 'event.date', 'event.price', 'first.adv.date', 
                            'first.adv.price', 'last.adv.date', 'last.adv.price',
@@
 
-### Field Conversions
-
-&nbsp;
-
-Below we convert and coalate a number of the temporal and spatial variables.
+### Temporal Considerations
+
+&nbsp;
+
+Below we rename, transform and filter our data to fit the time period appropriate to our research question.
 
@@
 For the AirBNB data this is a relatively straighforword process as the data are already standardized into a consistant date representation.
-We also create a year variable.
+We fix dates in both the property and the daily data.
 
@@
 
- ## Property Data Fields
+  # Property Data Fields
 
@@
 
-  ## Daily Data
+  # Daily Data
 
@@
 To fix this issue we create a small function that will remove the unnecessary digits and spaces and then convert to a standard date form.
-We then apply this formula to the three date fields in the long term data.
+We then apply this formula to the three date fields in the long term data (both listing and rental).
 We also create a year field for the event date.
@@
 
- ## Build custom function
+ # Build custom function
 
@@
 
- ## Convert event date
-
-  # Date
+  # Convert event date
+
   ltr.data$event.date <- fixLTDates(ltr.data$event.date)
 
-  # Year
+  # Extract Year of event date
   ltr.data$event.year <- as.numeric(substr(ltr.data$event.date, 1, 4))
 
- ## Converted list data date fields
+  # Converted listing data date fields
 
@@
 
-&nbsp;
-
-#### Fix Boolean Variables
-
-Next we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
-
-```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
-  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
-  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
-  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
-  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
-
-```
-
-&nbsp;
+#### Trim by Time
+
+Next we trim the observations by time.
+Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
+To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
+Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
+In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
+Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.
+While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
+
+```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ # Limit short term data
+
+  abb.data <- abb.data[abb.data$min.date >= '2015-09-01', ]
+  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]
+
+ # Limit long term data
+
+  ltr.data <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
+                            ltr.data$event.date <= '2015-08-31', ]
+  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
+
+```
 
@@
 
-AirBNB units are classified into 19 diffeltr property type.
+AirBNB units are classified into 19 different property type.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
@@
 
-Within the long-term ltral data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
 
@@
 Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
-This is most appaltr when talking about apartment dwellings.
+This is most apparent when talking about apartment dwellings.
 In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
@@
 
- ## Short Term data
+ # Short Term data
 
@@
 
- ## Long Term data
+ # Long Term data
 
@@
 
-The **Other** categories contain very small percentage of properties in both the AirBNB and the ltral data.  As a result, we remove the 'Others' from the data.
+As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
+Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
+As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
+
+```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+  # Create Airbnb plot
+
+  abb.types <- ggplot(abb.data, aes(x=type)) + 
+    geom_bar(color=str.col, fill=str.col) +
+    xlab('\nProperty Type\n') + 
+    ggtitle('\nShort Term Rentals\n')  +
+    ylab('# of Properties\n')
+
+  # Create long term rental plot
+
+  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
+    geom_bar(color=ltr.col, fill=ltr.col) +
+    xlab('\nProperty Type\n') + 
+    ggtitle('\nLong Term Rentals\n')  +
+    ylab('# of Properties\n')
+
+  # Output plots
+
+  ggMultiPlots(abb.types, ltr.types, cols=2)
+
+```
 
@@
 
-Next, for the short term ltrals units can be listed as one of three types relating to the extent of the property which is able to be booked:
+Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
 
@@
 2. **Private Room**: One room within a house or apartment is available
-3. **Shared Room**: A bed within a room shared by other occupants is available
-
-As long-term ltrals do not offer **Private Room** or **Shared Room** options and our purpose here is a comparison of the two we remove all short term properties that do not lease the entire home/apt.
+3. **Shared Room**: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt.
 Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
@@
 ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+  # Fix data types and names
 
@@
   abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'
+
+  # Make Plot
 
@@
     xlab('\nListing Type\n') + 
-    ggtitle('\nShort Term ltrals\n')  +
+    ggtitle('\nShort Term Rentals by Listing Type\n')  +
     ylab('# of Properties\n')
@@
 
-### Trim by Time
-
-Next we trim the observations by time.
-Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term ltral versus an AirBNB, short term ltral approach to generating income.
-To determine the likely long term ltral rate for any given property, we will use the observed ltral transactions from the market from September 1, 2014 to August 31, 2015.
-Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factor).
-In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
-Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2016.
-While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
-
-```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- ## Limit short term data
-
-  abb.dataf <- abb.data[abb.data$min.date >= '2015-09-01', ]
-  daily.dataf <- daily.data[daily.data$date >= '2015-09-01', ]
-
- ## Limit long term data
-
-  ltr.dataf <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
-                            ltr.data$event.date <= '2015-08-31', ]
-  listing.dataf <- listing.data[listing.data$id.key %in% ltr.dataf$id.key, ]
-
-```
-
 ### Locations and Submarkets
 
-Location is clearly an important determinant in both the short and long term ltral markets.
+Location is clearly an important determinant in both the short and long term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
-The plot below shows the three large submarkets.
+The plot below shows the three large submarkets (Inner, Middle and Outer).
 
@@
 
- ## Convert shapefile to ggplot-able object
+ # Convert shapefile to ggplot-able object
 
@@
   # Limit to extent of data
-  sub.table <- table(ltr.dataf$suburb)
+  sub.table <- table(ltr.data$suburb)
   sub.table <- sub.table[sub.table != 0]
@@
 
-```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
   # Set colors
-  g.cols <- abb.col[c(2,10,9)]
+  g.cols <- abb.col[c(2, 10, 9)]
 
@@
 
-## Plot map
+```
+
+```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
 
@@
 
-It is likely that the short-term ltral market follows a similar market hierarchy, however, we can imagine that a few diffeltr spatial features can influence the short-term market.
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
@@
 We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
-Fainlly, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+
+We select the 18 suburbs below to represent the 'core' of the city.
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenties for tourists.
 
@@
 
+We then apply a 500 meter buffer to the beach along Port Phillip Bay.
+
 ```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
- ## Determine centroid of study area
-
-  latMid <- median(abb.dataf$latitude)
-  longMid <- median(abb.dataf$longitude)
-
- ## Calculate Degress to Meters conversion
+ # Determine centroid of study area
+
+  latMid <- median(abb.data$latitude)
+  longMid <- median(abb.data$longitude)
+
+ # Calculate Degress to Meters conversion
 
@@
 
- ## Create the beach buffer
+ # Create the beach buffer
 
@@
 
+Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
+
 ```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
   # Convert to point shapefile
-  abb.prop.shp <- SpatialPointsDataFrame(cbind(abb.dataf$longitude,
-                                               abb.dataf$latitude),
-                                         abb.dataf,
+  abb.prop.shp <- SpatialPointsDataFrame(cbind(abb.data$longitude,
+                                               abb.data$latitude),
+                                         abb.data,
                                          proj4string=CRS("+init=epsg:4283"))
@@
   spJoin <- over(abb.prop.shp, suburbs.shp)
-  abb.dataf$suburb <- as.character(spJoin$name_2006)
-  abb.dataf$suburb[is.na(abb.dataf$suburb)] <- 'missing'
+  abb.data$suburb <- as.character(spJoin$name_2006)
+  abb.data$suburb[is.na(abb.data$suburb)] <- 'missing'
 
   # Add suburb designation
-  abb.dataf$sub.class <- as.character(spJoin$suburbdesi)
-  abb.dataf$sub.class[is.na(abb.dataf$sub.class)] <- 'missing'
+  abb.data$sub.class <- as.character(spJoin$suburbdesi)
+  abb.data$sub.class[is.na(abb.data$sub.class)] <- 'missing'
 
@@
   spJoin <- over(abb.prop.shp, sa1s.shp)
-  abb.dataf$sa1 <- spJoin$sa1_main11
+  abb.data$sa1 <- spJoin$sa1_main11
 
@@
   spJoin <- over(abb.prop.shp, beach.buffer)
-  abb.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
+  abb.data$beach <- ifelse(is.na(spJoin), 0 ,1)
 
   # Remove those missing a suburb classification (out of area)
-  abb.dataf <- abb.dataf[abb.dataf$sub.class != 'missing', ]
-  abb.dataf <- abb.dataf[abb.dataf$sa1 != 'missing', ]
+  abb.data <- abb.data[abb.data$sub.class != 'missing', ]
+  abb.data <- abb.data[abb.data$sa1 != 'missing', ]
 
@@
   # Add individual classes
-  abb.dataf$sub.mrkt <- 'rural'
-  abb.dataf$sub.mrkt[abb.dataf$sub.class == 'Middle'] <- 'suburban'
-  abb.dataf$sub.mrkt[abb.dataf$sub.class == 'Inner'] <- 'city'
-  abb.dataf$sub.mrkt[abb.dataf$suburb %in% core.suburbs] <- 'city-core'
-  abb.dataf$sub.mrkt[abb.dataf$beach == 1] <- 'beach'
+  abb.data$sub.mrkt <- 'rural'
+  abb.data$sub.mrkt[abb.data$sub.class == 'Middle'] <- 'suburban'
+  abb.data$sub.mrkt[abb.data$sub.class == 'Inner'] <- 'city'
+  abb.data$sub.mrkt[abb.data$suburb %in% core.suburbs] <- 'city-core'
+  abb.data$sub.mrkt[abb.data$beach == 1] <- 'beach'
 
   # Order the factors properly
-  abb.dataf$sub.mrkt <- factor(abb.dataf$sub.mrkt, 
+  abb.data$sub.mrkt <- factor(abb.data$sub.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
@@
 
+Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
+For those without either (3% of the total) we remove them from the dataset at this point.
+
+```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Label those missing lat/long
+
+  miss.LL <- which(is.na(ltr.data$latitude))
+
+ # Create a field to indicate the approximate matches
+
+  ltr.data$miss.LL <- 0
+  ltr.data$miss.LL[miss.LL] <- 1
+
+ # Apply approximate match
+
+  ltr.data$latitude[miss.LL] <- ltr.data$street.latitude[miss.LL]
+  ltr.data$longitude[miss.LL] <- ltr.data$street.longitude[miss.LL]
+
+ # Remove those still missing latitude data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$latitude), ]
+
+```
+
+Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.
+
+```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Long term data
+
+  # Convert to point shapefile
+
+  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.data$longitude,
+                                               ltr.data$latitude),
+                                         ltr.data,
+                                         proj4string=CRS("+init=epsg:4283"))
+
+  # Add suburb name
+
+  spJoin <- over(ltr.prop.shp, suburbs.shp)
+  ltr.data$suburb <- as.character(spJoin$name_2006)
+  ltr.data$suburb[is.na(ltr.data$suburb)] <- 'missing'
+
+  # Add suburb designation
+
+  ltr.data$sub.class <- as.character(spJoin$suburbdesi)
+  ltr.data$sub.class[is.na(ltr.data$sub.class)] <- 'missing'
+
+  # Add SA1 designation
+
+  spJoin <- over(ltr.prop.shp, sa1s.shp)
+  ltr.data$sa1 <- spJoin$sa1_main11
+
+  ## Add Beach Designation
+
+  spJoin <- over(rent.prop.shp, beach.buffer)
+  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)
+
+  # Remove those missing a suburb classification (out of area)
+
+  ltr.data <- ltr.data[ltr.data$sub.class != 'missing', ]
+  ltr.data <- ltr.data[ltr.data$sa1 != 'missing', ]
+
+```
+
+```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Add the submarket designations
+
+  # Add individual classes
+  ltr.data$sub.mrkt <- 'rural'
+  ltr.data$sub.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
+  ltr.data$sub.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
+  ltr.data$sub.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
+  ltr.data$sub.mrkt[ltr.data$beach == 1] <- 'beach'
+
+  # Order the factors properly
+  ltr.data$sub.mrkt <- factor(ltr.data$sub.mrkt, 
+                              levels=c('city-core', 'city', 'suburban', 
+                                        'rural', 'beach'))
+
+```
+
+The location of the short and long term rentals, colored by submarket, are shown below
+
 ```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
+  # Set submarket colors
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
   # Make map
+
   abb.map <- ggplot() +
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=abb.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2) +
+    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
+               alpha=.2) +
     scale_color_manual(values=sm.col) +
@@
           legend.title = element_blank()) +
-    guides(colour = guide_legend(override.aes = list(size=3))) + 
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
     ggtitle('AirBNB Location\nBy Submarket')
@@
 
-About 5% of the long term ltral observations have missing latitude and longitude values.
-Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
-For those without either (3% of the total) we remove them from the dataset at this point.
-After removing these, we apply the submarket designations.
-
-```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Label those missing lat/long
-
-  miss.LL <- which(is.na(ltr.dataf$latitude))
-
- ## Create a field to indicate the approximate matches
-
-  ltr.dataf$miss.LL <- 0
-  ltr.dataf$miss.LL[miss.LL] <- 1
-
- ## Apply approximate match
-
-  ltr.dataf$latitude[miss.LL] <- ltr.dataf$street.latitude[miss.LL]
-  ltr.dataf$longitude[miss.LL] <- ltr.dataf$street.longitude[miss.LL]
-
- ## Remove those still missing latitude data
-
-  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$latitude), ]
-
-```
-
-```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Long term data
-
-  # Convert to point shapefile
-  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.dataf$longitude,
-                                                ltr.dataf$latitude),
-                                         ltr.dataf,
-                                         proj4string=CRS("+init=epsg:4283"))
-
-  # Add suburb name 
-  spJoin <- over(ltr.prop.shp, suburbs.shp)
-  ltr.dataf$suburb <- as.character(spJoin$name_2006)
-  ltr.dataf$suburb[is.na(ltr.dataf$suburb)] <- 'missing'
-
-  # Add suburb designation
-  ltr.dataf$sub.class <- as.character(spJoin$suburbdesi)
-  ltr.dataf$sub.class[is.na(ltr.dataf$sub.class)] <- 'missing'
-
-  # Add SA1 designation
-  spJoin <- over(ltr.prop.shp, sa1s.shp)
-  ltr.dataf$sa1 <- spJoin$sa1_main11
-
-  ## Add Beach Designation
-  spJoin <- over(ltr.prop.shp, beach.buffer)
-  ltr.dataf$beach <- ifelse(is.na(spJoin), 0 ,1)
-
-  # Remove those missing a suburb classification (out of area)
-  ltr.dataf <- ltr.dataf[ltr.dataf$sub.class != 'missing', ]
-  ltr.dataf <- ltr.dataf[ltr.dataf$sa1 != 'missing', ]
-
-```
-
-```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Add the submarket designations
-
-  # Add individual classes
-  ltr.dataf$sub.mrkt <- 'rural'
-  ltr.dataf$sub.mrkt[ltr.dataf$sub.class == 'Middle'] <- 'suburban'
-  ltr.dataf$sub.mrkt[ltr.dataf$sub.class == 'Inner'] <- 'city'
-  ltr.dataf$sub.mrkt[ltr.dataf$suburb %in% core.suburbs] <- 'city-core'
-  ltr.dataf$sub.mrkt[ltr.dataf$beach == 1] <- 'beach'
-
-  # Order the factors properly
-  ltr.dataf$sub.mrkt <- factor(ltr.dataf$sub.mrkt, 
-                               levels=c('city-core', 'city', 'suburban', 
-                                        'rural', 'beach'))
-
-```
-
 ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
   # Make map
+
   ltr.map <- ggplot() +
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=ltr.dataf, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1) +
+    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
+               alpha=.1) +
     scale_color_manual(values=sm.col) +
@@
           legend.title = element_blank()) +
-    guides(colour = guide_legend(override.aes = list(size=3))) + 
-    ggtitle('Long Term ltral Location\nBy Submarket')
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
+    ggtitle('Long Term Rental Location\nBy Submarket')
 
@@
 
+The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
+
 ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
 
-  # Make map
+  # Make Airbnb submarket map
+
   abbtype.map <- ggplot() +
@@
 
-  # Make map
+  # Make Long term rental map
+
   ltrtype.map <- ggplot() +
@@
 
-## By Values (outliers, etc.)
-
-We now filter both datasets by removing observed values unlikely to represent 'typical' short or long term ltral properties.
+Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Convert suburbs from factor to character
+  abb.data$suburb <- as.character(abb.data$suburb)
+  ltr.data$suburb <- as.character(ltr.data$suburb)
+
+```
+
+&nbsp;
+
+## Structural Characteristics
+
+&nbsp;
+
+In this section we transform and filter based on the structural characteristics of the properties.
+
+### Fix Boolean Variables
+
+Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
+
+```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
+  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
+  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
+  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
+  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
+
+```
+
+&nbsp;
 
@@
 
- ## Remove missing and data errors
+ # Remove missing and data errors
 
   # Long term data
-  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$bedrooms), ]
-  ltr.dataf <- ltr.dataf[ltr.dataf$bedrooms <= 10, ]
+  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
+  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
 
   # Short term data
-  abb.dataf <- abb.dataf[!is.na(abb.dataf$bedrooms), ]
-  abb.dataf <- abb.dataf[abb.dataf$bedrooms <= 10, ]
+  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
+  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
 
@@
 
- ## Build long term bar plot
-
-  ltrbed <- ggplot(ltr.dataf, aes(x=bedrooms)) + 
-    geom_bar(fill=abb.col[3], color=abb.col[3]) +
+ # Build long term bar plot
+
+   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
     facet_wrap(~type) +
@@
     ylab('') +
-    ggtitle('Bedrooms in Long Term ltrals')
+    ggtitle('Bedrooms in Long Term Rentals')
 
@@
 
-  abbbed <- ggplot(abb.dataf, aes(x=bedrooms)) + 
-    geom_bar(fill=abb.col[1], color=abb.col[1]) +
+  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
+    geom_bar(fill=str.col, color=str.col) +
     facet_wrap(~type) +
@@
     ylab('') +
-    ggtitle('Bedrooms in Short Term ltrals')
-
- ## Make the comparison plot
+    ggtitle('Bedrooms in Short Term Rentals')
+
+ # Make the comparison plot
 
@@
 
- ## Remove all with more than 4 beds
-
-  abb.dataf <- abb.dataf[abb.dataf$bedrooms < 5, ]
-  ltr.dataf <- ltr.dataf[ltr.dataf$bedrooms < 5, ]
-
- ## Remove apartments with more than 3
-
-  abba <- which(abb.dataf$bedrooms > 3 & abb.dataf$type =='Apartment')
-  ltra <- which(ltr.dataf$bedrooms > 3 & ltr.dataf$type =='Apartment')
-  if(length(abba)>0) abb.dataf <- abb.dataf[-abba, ]
-  if(length(ltra)>0) ltr.dataf <- ltr.dataf[-ltra, ]
+ # Remove all with more than 4 beds
+
+  abb.data <- abb.data[abb.data$bedrooms < 5, ]
+  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+
+ # Remove apartments with more than 3
+
+  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
+  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
+
+  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
+  if(length(renta) > 0) ltr.data <- ltr.data[-renta, ]
 
   # Convert 0 Bed to 1 Bed  
-  abb.dataf$bedrooms[abb.dataf$bedrooms == 0] <- 1
+  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
 
@@
 
- ## Remove missing data
-ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$baths), ]
-abb.dataf <- abb.dataf[!is.na(abb.dataf$baths), ]
+ # Remove missing data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
+  abb.data <- abb.data[!is.na(abb.data$baths), ]
 
@@
 
- ## Build long term plot
-
-  ltbath <- ggplot(ltr.dataf, aes(x=baths)) + 
-    geom_bar(fill=abb.col[3], color=abb.col[3]) +
+ # Build long term plot
+
+  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
     facet_wrap(~type) +
@@
     ylab('') + 
-    ggtitle('Bathrooms in Long Term ltrals')
-
- ## Build short term plot
-
-  stbath <- ggplot(abb.dataf, aes(x=baths)) + 
-    geom_bar(fill=abb.col[1], color=abb.col[1]) +
+    ggtitle('Bathrooms in Long Term Rentals')
+
+ # Build short term plot
+
+  stbath <- ggplot(abb.data, aes(x=baths)) + 
+    geom_bar(fill=str.col, color=str.col) +
     facet_wrap(~type) +
@@
 
- ## Make Plots
+ # Make Plots
 
@@
 
- ## Filter by bath count
+ # Filter by bath count
 
   # Short term data
-  abb.dataf <- abb.dataf[abb.dataf$baths < 4, ]
-  abb.dataf <- abb.dataf[abb.dataf$baths > 0, ]
+  abb.data <- abb.data[abb.data$baths < 4, ]
+  abb.data <- abb.data[abb.data$baths > 0, ]
 
   # Long term data
-  ltr.dataf <- ltr.dataf[ltr.dataf$baths < 4, ]
-
- ## Round baths up
-
-  abb.dataf$baths <- round(abb.dataf$baths + .01, 0)
+  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+
+ # Round baths up
+
+  abb.data$baths <- round(abb.data$baths + .01, 0)
 
@@
 
- ## Create combination variable
-
-  ltr.dataf$bedbath <- paste0(ltr.dataf$bedrooms, '..', ltr.dataf$baths)
-  abb.dataf$bedbath <- paste0(abb.dataf$bedrooms, '..', abb.dataf$baths)
+ # Create combination variable
+
+  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
+  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
 
@@
 
- ## Make long term plot
-
-  ltb <- ggplot(ltr.dataf, aes(x=bedbath)) + 
-    geom_bar(fill=abb.col[3], color=abb.col[3]) +
+ # Make long term plot
+
+  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
     xlab('\nBed/Bath Combo\n') +
@@
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ggtitle('Long Term ltrals') + 
+    ggtitle('Long Term Rentals') + 
     facet_wrap(~type)
 
- ## Make short term plots
-
-  stb <- ggplot(abb.dataf, aes(x=bedbath)) +
-    geom_bar(fill=abb.col[1], color=abb.col[1]) + 
+ # Make short term plots
+
+  stb <- ggplot(abb.data, aes(x=bedbath)) +
+    geom_bar(fill=str.col, color=str.col) + 
     xlab('\nBed/Bath Combo\n') +
     ylab('Number of Properties\n') +
-    ggtitle('Short Term ltrals') + 
+    ggtitle('Short Term Rentals') + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
@@
 
- ## Plot
+ # Plot
 
@@
 
- ## Set level of acceptable combinations
+ # Set level of acceptable combinations
 
@@
 
- ## Filter data
-
-  ltr.dataf <- ltr.dataf[ltr.dataf$bedbath %in% acc.bb, ]
-  abb.dataf <- abb.dataf[abb.dataf$bedbath %in% acc.bb, ]
-
-```
-
-### Rates and ltrs
-
-Finally, we turn to filtering by the prices -- the nightly rates and weekly ltral values.  We start by removing observations missing price data.
+ # Filter data
+
+  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
+  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
+
+```
+
+Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
+We additionally create a product variable that splits the bed/bath by apartment and house.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Re-order factors
+
+  abb.data$bedbath <- factor(abb.data$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  ltr.data$bedbath <- factor(ltr.data$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+  # Add product as a variable
+
+  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
+  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
+
+```
+
+## Rates and Rental values
+
+We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
 
@@
 
-  ltr.dataf <- ltr.dataf[!is.na(ltr.dataf$event.price), ]
-  abb.dataf <- abb.dataf[!is.na(abb.dataf$nightly.rate), ]
+  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
+  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
+
+```
+
+Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
+
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Property level data
+
+  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
+  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
+  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
+  abb.data$monthly.rate <- abb.data$monthly * exch.rate
+
+  # Daily data
+
+  daily.data$price <- daily.data$price * exch.rate
 
@@
   # ltr Plot
-  ltr.plot <- ggplot(ltr.dataf, aes(x=event.price)) + 
-    geom_density(fill=abb.col[3],alpha=.8) +
+
+  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
+    geom_density(fill=ltr.col, alpha=.8) +
     ylab('') +
-    xlab('Weekly ltr') + 
-    ggtitle('Long Term ltrals') + 
+    xlab('Weekly Rental') + 
+    ggtitle('Long Term Rentals') + 
     scale_x_continuous(limits=c(0, 1500)) +
@@
   # Nightly Rate plot
-  rate.plot <- ggplot(abb.dataf, aes(x=nightly.rate)) + 
-    geom_density(fill=abb.col[1], alpha=.8) + 
+  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
+    geom_density(fill=str.col, alpha=.8) + 
     ylab('') +
     xlab('Nightly Rate') +
-    ggtitle('Short Term ltrals') + 
+    ggtitle('Short Term Rentals') + 
     scale_x_continuous(limits=c(0, 600)) +
@@
 
-From these density plots we see that most weekly ltrals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $400 per night.
+From these density plots we see that most weekly Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
 We filter the data accordingly.
@@
 
-  ltr.dataf <- ltr.dataf[ltr.dataf$event.price >= 200 & 
-                         ltr.dataf$event.price <= 1000, ]
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
 
@@
 
-  abb.dataf <- abb.dataf[abb.dataf$nightly.rate >= 50 &
-                         abb.dataf$nightly.rate <= 400, ]
+  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
+                         abb.data$nightly.rate <= 500, ]
 
@@
 
-  daily.dataf <- daily.dataf[daily.dataf$property.id %in% abb.dataf$property.id,]
+  daily.data <- daily.data[daily.data$property.id %in% abb.data$property.id,]
 
@@
 
-  listing.dataf <- listing.dataf[listing.dataf$activity.id %in% ltr.dataf$activity.id,]
-
-```
-
-Finally, we convert the prepared data back to the original object names.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  abb.data <- abb.dataf
-  daily.data <- daily.dataf
-  ltr.data <- ltr.dataf
-  listing.data <- listing.dataf
-
-```
-
-# Prepare for Revenue Estimation
+  listing.data <- listing.data[listing.data$activity.id %in% ltr.data$activity.id,]
+
+```
+
+## Revenue Estimation
 
@@
 
-Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $600 per night.
+Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data.
+We do this step to remove those].
 From this information we calculate the median nightly reservation price for each property and append it to the property level data.
@@
                              daily.data$booked.date != 'imputed' &
-                              daily.data$price < 600, ]
+                              daily.data$price < 500, ]
 
@@
 
-For the airbnb properties we then calculate the actual revenue over the Sep 1 2015 to Aug 31 2016 period. Those with no revenue are removed.
+### Actual Revenues
+
+In this section we total up the actual revenues for each short and long term rental property.
+
+For the Airbnb properties we then calculate the actual revenue over the Sep 1 2015 to Aug 31 2016 period. Those with no revenue are removed.
 
@@
 
- ## Calculate ltral revenues
-
   # Calculate the actual revenue
@@
 
- ## Save for future costs
-
-```
+```
+
+#### Costs
+
+SAVE HERE FOR SUBTRACTION OF COSTS FROM REVENUE
 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Re-order factors
-  abb.data$bedbath <- factor(abb.data$bedbath, 
-                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-  ltr.data$bedbath <- factor(ltr.data$bedbath, 
-                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-
-  # Add product as a variable
-  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
-  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
-
-  # Convert suburbs from factor to character
-  abb.data$suburb <- as.character(abb.data$suburb)
-  ltr.data$suburb <- as.character(ltr.data$suburb)
-
-```
-
 ### Save Workspace for using in 'Working' script

### 2016-12-14 abbReturns_Script.Rmd
multiple bug fix

@@
 
-  spJoin <- over(rent.prop.shp, beach.buffer)
+  spJoin <- over(ltr.prop.shp, beach.buffer)
   ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)
@@
   abbtype.map <- ggplot() +
-    geom_bar(data=abb.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
   ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
   if(length(abba) > 0) abb.data <- abb.data[-abba, ]
-  if(length(renta) > 0) ltr.data <- ltr.data[-renta, ]
+  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
 

### 2016-12-15 abbReturns_Working.R
begin full explaination of global plots

@@ -53,25 +53,172 @@
 
 ### Working analysis ---------------------------------------------------------------------  
 
-<<<<<<< HEAD
-### Comparison
-=======
-
->>>>>>> origin/master
-
  ## Global model
 
-  # We begin by imputing rents and rates for all properties using a global model with 
-  # suburb fixed effects.  
- 
   # Set model specifications
   ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb))
   abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
  
+ # Make comparison between two markets  
+  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
+                               abb.df=abb.data, 
+                               ltr.mod.spec=ltr.mod.spec, 
+                               abb.mod.spec=abb.mod.spec,
+                               clip.field='suburb')
+  
+  # Extract out DFs (only those that imputed)
+  abb.imp <- imp.data$abb
+  ltr.imp <- imp.data$ltr
+  
+ # Within type imputation revenues
+  
+  imp.revs <- revenueEngine(abb.imp, 
+                            ltr.imp,
+                            rate.field='imp.rate',
+                            rent.field='imp.rent')
+  
+  # Add back to DFs
+  abb.imp$imp.revenue <- imp.revs$abb
+  ltr.imp$imp.revenue <- imp.revs$ltr
+  
+ # Cross type revenue estimation
+  
+  # Apply dom to abb
+  abb.imp$imp.dom <- imputeDOM(abb.imp, ltr.imp, calc.type='median')
+  
+  # Apply occ.rate to ltr
+  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, abb.imp, calc.type='median')
+  
+  # Estimate cross revenues
+  impx.revs <- revenueEngine(abb.df=ltr.imp, 
+                             ltr.df=abb.imp,
+                             rate.field='imp.rate',
+                             rent.field='imp.rent',
+                             occ.field='imp.occ',
+                             dom.field='imp.dom')
+  
+  # Add back to DFs
+  abb.imp$imp.ltr.revenue <- impx.revs$ltr
+  ltr.imp$imp.abb.revenue <- impx.revs$abb
+  
+  # Compare revenues
+  comp.revs <- compareRevenues(abb.imp, ltr.imp)
+  
+  # Extract
[…]

### 2016-12-15 analysis_functions.R
updating names, fixing bugs

@@ -33,7 +33,6 @@ imputeRatesRents <- function(ltr.df,
                              abb.df,
                              ltr.mod.spec,
                              abb.mod.spec,
-                             exch.rate,
                              clip.fields=NULL)
 {
   
@@ -89,7 +88,7 @@ imputeRatesRents <- function(ltr.df,
 
  ## Add the predicted values to the short term data
   
-  ltr.df$imp.rate <- exp(predict(abb.mod, ltr.df)) * exch.rate
+  ltr.df$imp.rate <- exp(predict(abb.mod, ltr.df))
 
  ## Return Values  
   
@@ -170,7 +169,7 @@ imputeDOM <- function(abb.df,
   
   ## Return Values
   
-  return(abb.df)
+  return(abb.df$imp.dom)
   
 }
 
@@ -199,7 +198,7 @@ imputeOccRate <- function(ltr.df,
   
   ## Return Values
   
-  return(ltr.df)
+  return(ltr.df$imp.occ)
   
 }
 
@@ -210,22 +209,22 @@ compareRevenues <- function(abb.df,
   
   ## Abb act (1) to abb imp ltr (4)
   
-  abb.df$abb.prem <- abb.df$abb.rev.act - abb.df$ltr.rev.imp
+  abb.df$abb.prem <- abb.df$revenue - abb.df$imp.ltr.revenue
   abb.df$abb.act <- ifelse(abb.df$abb.prem > 0, 1, 0)
   
   ## Abb imp (2) to abb imp ltr (4)
   
-  abb.df$abb.prem.imp <- abb.df$abb.rev.imp - abb.df$ltr.rev.imp
+  abb.df$abb.prem.imp <- abb.df$imp.revenue - abb.df$imp.ltr.revenue
   abb.df$abb.imp <- ifelse(abb.df$abb.prem.imp > 0, 1, 0)
   
   ## Abb imp (2) to ltr act (3)
   
-  ltr.df$abb.prem <- ltr.df$abb.rev.imp - ltr.df$ltr.rev.act
+  ltr.df$abb.prem <- ltr.df$imp.abb.revenue - ltr.df$revenue
   ltr.df$abb.act <- ifelse(ltr.df$abb.prem > 0, 1, 0)
   
   ## Abb imp (2) to ltr imp (4)
   
[…]

### 2016-12-15 analysis_functions.R
adding plot bug

@@ -404,6 +404,12 @@ makePrefPlot <- function(pref.data,
   
   pref.full <- rbind.fill(pref.list)
   
+  if(group.field == 'sub.mrkt'){
+    pref.full$ID <- factor(pref.full$ID, 
+                           levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+    
+  }
+  
  ## Creat the base plot  
   
   pref.plot <- ggplot(pref.full,
@@ -441,7 +447,7 @@ makeHeatMap <- function(hm.data,
   hm.plot <- ggplot(data=hm.data,
                     aes(x=x.var, y=y.var))
   if(add.points){
-    hm.plot <- hm.plot + geom_point(size=.1, color='gray50') 
+    hm.plot <- hm.plot + geom_point(size=.1, color='gray50', alpha=.2) 
   }
   
   hm.plot <- hm.plot + 

### 2016-12-15 abbReturns_Working.R
expanding global analysis + SVM

@@ -51,6 +51,8 @@
   source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
   source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
 
+  sm.col <- abb.col[c(2, 1, 3, 5, 6)]
+  
 ### Working analysis ---------------------------------------------------------------------  
 
  ## Global model
@@ -111,6 +113,8 @@
  ## Make a table  
   
   mrkt.table <- createCompTable(abb.revs, ltr.revs, 'sub.mrkt')
+  mrkt.table$ID <- factor(mrkt.table$ID, 
+                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
   
 ## make basic 2x2 comparison
   
@@ -206,6 +210,156 @@
     coord_cartesian(ylim=c(-.5,1))
   
   
+  ## Make a table  
+  
+  abb.act.table <- mrkt.table[mrkt.table$est == 'Actual Rates & Rents' &
+                               mrkt.table$data == 'Airbnb', ]
+  
+  ## make basic 2x2 comparison
+  
+  abb.act.plot <- 
+    ggplot(abb.act.table, 
+           aes(x=ID, weights=Var, fill=ID)) + 
+    geom_bar() +
+    scale_fill_manual(values=sm.col) +
+    xlab('') +
+    ylab('% of properties where Airbnb is more profitable') +
+    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') +
+    coord_cartesian(ylim=c(0,1))
+  
+  # Make pref plot
+  
+
+  rawocc.pplot <- makePrefPlot(abb.revs,
+                               x.field='occ.rate',
+                               y.field='abb.act',
+                               group.field='sub.mrkt',
+                               smooth=TRUE,
+                               smooth.span=.75)
+  rawocc.pplot <- rawocc.pplot +
+    xlab('\nOccupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col)
+  
+  ## Look at occupancy rates
[…]

### 2016-12-16 analysis_functions.R
updates to heat map

@@ -431,35 +431,196 @@ makePrefPlot <- function(pref.data,
 }
 
 ### Create heatmaps of profitability -----------------------------------------------------
-
 makeHeatMap <- function(hm.data,
                         x.field,
                         y.field,
-                        alpha.field,
+                        color.field,
                         bins=c(10, 10),
-                        add.points=FALSE){
+                        fill.colors=c('red', 'forestgreen'),
+                        alpha.count=TRUE,
+                        alpha.fill=1,
+                        add.points=FALSE,
+                        hexmap=FALSE,
+                        point.data=NULL,
+                        svm=FALSE,
+                        return.svm=FALSE,
+                        svm.opts=list(type='C-svc',
+                                      kernel='polydot',
+                                      poly.degree=4,
+                                      expand.factor=100)){
   
+ ## Prepare the plotting data  
   
-  hm.data$x.var <- hm.data[ ,x.field]
-  hm.data$y.var <- hm.data[ ,y.field]
-  hm.data$fill.var <- hm.data[ ,alpha.field]  
-  
-  hm.plot <- ggplot(data=hm.data,
-                    aes(x=x.var, y=y.var))
-  if(add.points){
-    hm.plot <- hm.plot + geom_point(size=.1, color='gray50', alpha=.2) 
+  # If SVM
+  if(svm){
+    
+    # create svm analysis
+    svm.obj <- makeSVM(hm.data,
+                       x.field=x.field,
+                       y.field=y.field,
+                       z.field=color.field,
+                       svm.type=svm.opts$type,
+                       svm.kernel=svm.opts$kernel,
+                       poly.degree=svm.opts$poly.degree,
+                       expand.factor=svm.opts$expand.factor)
+    
+    # Convert initial data to point data
+    point.data <- hm.data
+    point.data$x <- point.data[,x.field]
+    point.data$y <- point.data[,y.field]
+    
+    # Add predicted values to data
+    hm.data <- svm.obj$pred
+    names(hm.data) <- c('x.var', 'y.var', 'fill.var')
+    
+  # if not SVM  
+  } else {
+    
+    # Set up X, Y and fill variables
+    hm.data$x.var <- hm.data[ ,x.field]
+    hm.data$y.var <- hm.data[ ,y.field]
[…]

### 2016-12-16 abbReturns_Working.R
finalizing global analysis once-thru

@@ -22,6 +22,8 @@
   library(stringr)
   library(RColorBrewer)
   library(Hmisc)
+  library(kernlab)
+
 
  ## Set path location
 
@@ -270,6 +272,8 @@
   
   abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, 
                                       return.type='rank') 
+  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, 
+                                  return.type='rank') 
   
   ## Make quartile location plot
   
@@ -287,139 +291,114 @@
     scale_y_continuous(breaks=seq(0, 1, by=.25),
                        labels=c('0%', '25%', '50%', '75%', '100%')) +
     scale_color_manual(values=sm.col)
+
+ # Make the rate heatmap  
   
+  rate.hm <- makeHeatMap(abb.revs,
+                x.field='occ.rate',
+                y.field='nightly.rate',
+                color.field='abb.act',
+                bins=c(.05, 25),
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
   
-  # Make the rate heatmap  
-  
-  rate.heatmap <- makeHeatMap(abb.revs,
-                              x.field='occ.rate',
-                              y.field='med.rate',
-                              alpha.field='abb.act',
-                              bins=c(.05, 30),
-                              add.points=TRUE)
-  rate.heatmap <- rate.heatmap +
+  rate.hm <- rate.hm +
     xlab('\n Occupancy Rate') +
     ylab('\n Nightly Rate') +
     scale_x_continuous(breaks=seq(0, 1, by=.25),
                        labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none')
- 
-  ## Add the rate quartle location   
+    theme(legend.position='bottom')
   
-  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, 
-                                  return.type='rank') 
+ # Rate SVM heatmap
+  
+  rate.hm.svm <- makeHeatMap(abb.revs,
+                         x.field='occ.rate',
+                         y.field='nightly.rate',
+                         color.field='abb.act',
+                         bins=c(.05, 25),
+                         svm=T, 
+                         alpha.count=F,
+                         add.points=T,
[…]

### 2016-12-16 abbReturns_Working.R
final clean up of global analysis

@@ -402,3 +402,25 @@
                              svm=c(mean(svm.rate$pred$pred),
                                    mean(svm.qtl$pred$pred)))
   
+
+  
+abb.apt <- which(abb.revs$type == 'Apartment')
+ltr.apt <- which(ltr.revs$type == 'Apartment')
+
+    
+abc <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
+                          abb.df=abb.revs[-abb.apt, ],
+                          ltr.mod.spec=ltr.mod.spec,
+                          abb.mod.spec=abb.mod.spec,
+                          clip.field='suburb',
+                          market.field='sub.mrkt',
+                          mrkt.col=sm.col,
+                          heat.col=c(abb.col[1], abb.col[5]))
+
+    
+      
+  
+  
+  
+  
+  

### 2016-12-16 analysis_functions.R

@@ -242,21 +242,14 @@ revCompWrapper <- function(ltr.df,
                            abb.mod.spec,
                            clip.field='suburb'){  
   
- ## Calculate the actual revenues  
-  
-  act.revs <- revenueEngine(abb.df, ltr.df) 
-  
-  # Add back to DFs
-  abb.df$abb.rev.act <- act.revs$abb
-  ltr.df$ltr.rev.act <- act.revs$ltr
-  
+
  ## Impute rates and rents
   
   imp.data <- imputeRatesRents(ltr.df=ltr.df, 
                                abb.df=abb.df, 
                                ltr.mod.spec=ltr.mod.spec, 
                                abb.mod.spec=abb.mod.spec,
-                               clip.field='suburb')
+                               clip.field=clip.field)
   
   # Extract out DFs
   abb.df <- imp.data$abb
@@ -643,10 +636,14 @@ fullMarketAnalysis <- function(ltr.df,
                                abb.df,
                                ltr.mod.spec,
                                abb.mod.spec,
-                               exch.rate,
-                               clip.field
-)
+                               clip.field,
+                               market.field='sub.mrkt',
+                               mrkt.col=NULL,
+                               heat.col=c('red', 'green'))
+
 {  
+  
+ ## Fix null
   
  ## Make comparison between two markets  
   
@@ -654,69 +651,209 @@ fullMarketAnalysis <- function(ltr.df,
                               abb.df=abb.df,
                               ltr.mod.spec=ltr.mod.spec,
                               abb.mod.spec=abb.mod.spec,
-                              exch.rate=exch.rate,
                               clip.field='suburb')   
   
   
  ## Make a simple table of comparison
   
-  mrkt.table <- createCompTable(mrkt.comp$abb, mrkt.comp$ltr, 'sub.mrkt')
+  mrkt.table <- createCompTable(mrkt.comp$abb, mrkt.comp$ltr, market.field)
+  
+  if(market.field == 'sub.mrkt'){
+    mrkt.table$ID <- factor(mrkt.table$ID, 
+                            levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+  }
   
  ## make basic 2x2 comparison
   
-  twotwo.bar.plot <- ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
+  # Set colors
+  if(is.null(mrkt.col)){
+    mrkt.col <- 1:(nrow(mrkt.table)/4)
+  }
+  
+  # Make Plot
[…]

### 2016-12-16 abbReturns_Writeup.Rmd
initial commit of writeup

---
title: "Should I AirBNB My Property"
author: "Andy Krause"
date: "December 17, 2016"
output: html_document
---

## Intro

## Lit Review

## Method

### Scenario

You buy a property on Sept 1, 2015. In order to maximize the return over the next 12 months, should you rent long term or AirBNB?
- Does it depend on the property type or location?
- 'Market' sets LTR, you set STR.  
- We will not consider non-economic costs (time, liquidity, etc.) at this point.

### Equation

AirbnbRev = nightly rate * occupancy - (short costs + long costs)
-- short costs = cleaning, time
-- long costs = taxes and maintenance

LtRev = weekly rate * (52 - search time) - (short costs + long costs)
-- short costs = brokerage
-- long costs = taxes and maintenance

When is AirbnbRev > LtRev?

## Data

Airbnb data from AirDNA.  All of Melbourne.  Most of Oct 2014 to Aug 30th 2016.  Full data from Sept 1 2015 to Aug 30 2016.  Daily and property data.  Is scraped weekly or so for each property.  All prices in US dollars.

- Show example

Long-term data from Domain.  All of Melbourne.  June 2010 to June 2016.  Rental listings and final agreed prices. All property types.

- Show example

No direct link between data (no addresses given in AirBNB)

### Preparation

### Imputing

### Costs

-- Assume long term costs are equivalent

### Comparing

## Results

-- Start with a global analysis

### What is accurate?

- Discuss why Airbnb Actual is the only relevant one.  
-- Show charts
-- Discuss problems with Rate imputation
-- Discuss problems with Occupancy imputation

#### Comp Tables/Figs

### Heat Maps

### Submarkets

### Flexible Geo Analysis

### Logit Models (maybe?)

### Reference to Shiny App

## Future Research

- Does time of purchase (which month) matter?

### 2016-12-18 analysis_functions.R
Fix month and hm bug

@@ -65,7 +65,11 @@ imputeRatesRents <- function(ltr.df,
     }
     
  }
-  
+
+ ## Add the monthly factors
+
+  abb.df$ltr.month <- 12
+    
  ## Build regression models for rental values
   
   ltr.mod <- lm(ltr.mod.spec, data=ltr.df)
@@ -864,7 +868,7 @@ fullMarketAnalysis <- function(ltr.df,
               plot.1=abb.act.plot,
               rawocc.plot=rawocc.pplot,
               qtlocc.plot=qtlocc.pplot,
-              qtl.hm=qtl.heatmap,
+              qtl.hm=qtl.hm,
               qtl.hm.svm=qtl.hm.svm,
               rate.hm=rate.hm,
               rate.hm.svm=rate.hm.svm,

### 2016-12-18 abbReturns_Script.Rmd
add monthly variable and specification

@@
 
+```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Short term data
+
+  abb.data$abb.month <- 1
+  daily.data$abb.month <- as.numeric(as.factor(substr(daily.data$date, 1, 7)))
+
+  # Long term data
+
+  ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
+  listing.data$ltr.month <- as.numeric(as.factor(substr(listing.data$event.date, 1, 7))) - 8
+
+```
+
 ### Standardize Property Types

### 2016-12-18 abbReturns_Writeup.Rmd
add monthly variable and specification

@@
 
+With the rise of Airbnb and other self-hosting accommodation platforms, property owners and investors may consider short-term rental as a potential use for a home.
+The question to be asked then is, in which circumstances would leasing in a short-term manner produce greater returns than a traditional long-term rental?
+This work presents an examination of market transactions of both short and long-term rental aimed at answering this question.
+
+To do so, we use long-term rental data and nightly Airbnb listing information from the Melbourne (Australia) metropolitan area.
+Melbourne has a thriving Airbnb market with over 17,000 total properties listed on the portal.
+The Airbnb data does not include exact addresses and therefore no direct matches between the datasets can be made.
+As a result, we impute likely short and long-term rental rates and occupancies.
+Comparisons of actual to estimated returns are made to determine the situation in which a short term rental, such as Airbnb, is more profitable.
+
+Additionally, we break the results down by property types (apartment vs house), product type (ex.
+1 bed, 1 bath) and by location (submarket).
+Our results shows that the feasibility of a greater return through a short term rental is dependent on property type, product and location.
+In answer to our question: it depends.
+
 ## Lit Review
@@
 
-You buy a property on Sept 1, 2015. In order to maximize the return over the next 12 months, should you rent long term or AirBNB?
-- Does it depend on the property type or location?
-- 'Market' sets LTR, you set STR.  
-- We will not consider non-economic costs (time, liquidity, etc.) at this point.
+We approach answering the question of Airbnb-ing or not by examining a scenario likely to be faced by a recent purchaser of a property.  More specifically, we examine the following case:
+
+* An investor purchases a property in Melbourne on Sept 1, 2015.
+* They are looking to maximize the revenue over the 12 month period from Sept 1 2015 to August 31 2016.
+* The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental.
+* Only direct monetary costs are considered, others such as liquidity and inconvience are not considered.
+
+We will not, a priori, specify a location or property type as we hypothesize that the feasibility of a short term rental will vary by these characteristics.
+Australia has a tax policy, Negative Gearing, that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties.
+However, as this policy requires knowledge of the investor's personal income level, we will not be considering this policy in our analysis here.
+
+One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
+As the future trends are unknown at the time of purchase and the decision of long vs short term rental, we make our comparisons using a fixed nightly short term rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
+Both long and short term rates and occupancy structures will be baesd on the market conditions as of this date.
 

### 2016-12-18 abbReturns_Working.R

@@ -10,6 +10,7 @@
   library(spdep)
   library(maptools)
   library(gstat)
+  library(kernlab)
   library(ggplot2)
   library(geosphere)
   library(ggmap)
@@ -22,8 +23,6 @@
   library(stringr)
   library(RColorBrewer)
   library(Hmisc)
-  library(kernlab)
-
 
  ## Set path location
 
@@ -60,7 +59,8 @@
  ## Global model
 
   # Set model specifications
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb))
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
   abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
  
  # Make comparison between two markets  

### 2017-01-05 abbReturns_Script.Rmd
Initial data prep to writeup and re-order

@@
   ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
-  listing.data$ltr.month <- as.numeric(as.factor(substr(listing.data$event.date, 1, 7))) - 8
+  listing.data$ltr.month <- as.numeric(as.factor(substr(
+    listing.data$event.date, 1, 7))) - 8
 
@@
 As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
+
+```{r write_beforeproptypeobj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+before.PT <- list(abb.data=abb.data,
+                  daily.data=daily.data,
+                  ltr.data=ltr.data,
+                  listing.data=listing.data)
+
+save(before.PT, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
+
+```
 
@@
   abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
+
+```
+
+## Structural Characteristics
+
+&nbsp;
+
+In this section we transform and filter based on the structural characteristics of the properties.
+
+### Fix Boolean Variables
+
+Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
+
+```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
+  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
+  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
+  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
+  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
+
+```
+
+&nbsp;
+
+### Bedrooms
+
+We start by looking at bedrooms.
+We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
+We then plot the distribution of diffeltr bedrooms counts.
+From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
+
+```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove missing and data errors
+
+  # Long term data
+  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
+  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
+
+  # Short term data
+  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
+  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
+
+```
+
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Build long term bar plot
+
+   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=1:10, breaks=1:10)+
+    xlab('\nBedrooms\n') +
+    ylab('') +
+    ggtitle('Bedrooms in Long Term Rentals')
+
+ # Build short term bar plot
+
+  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=0:10, breaks=0:10)+
+    xlab('\nBedrooms\n') +
+    ylab('') +
+    ggtitle('Bedrooms in Short Term Rentals')
+
+ # Make the comparison plot
+
+  ggMultiPlots(abbbed, ltrbed, cols=1)
+
+```
+
+For both short and long term ltrals we see that most apartments have less than 4 bedrooms and houses less than 5.
+We filter the data accordingly.
+Additionally, note that short term ltrals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
+We convert the 0 bed short term units to 1 bed units.
+
+```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove all with more than 4 beds
+
+  abb.data <- abb.data[abb.data$bedrooms < 5, ]
+  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+
+ # Remove apartments with more than 3
+
+  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
+  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
+
+  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
+  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
+
+  # Convert 0 Bed to 1 Bed  
+  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
+
+```
+
+### Bathrooms
+
+We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
+
+```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove missing data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
+  abb.data <- abb.data[!is.na(abb.data$baths), ]
+
+```
+
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Build long term plot
+
+  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=1:8, breaks=1:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Long Term Rentals')
+
+ # Build short term plot
+
+  stbath <- ggplot(abb.data, aes(x=baths)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=0:8, breaks=0:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Short Term ltrals')
+
+ # Make Plots
+
+  ggMultiPlots(stbath, ltbath, cols=1)
+
+```
+
+Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
+A few short term properties state no baths, which is likely an error so we remove these as well.
+Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
+We round the baths up to whole integers.
+
+```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Filter by bath count
+
+  # Short term data
+  abb.data <- abb.data[abb.data$baths < 4, ]
+  abb.data <- abb.data[abb.data$baths > 0, ]
+
+  # Long term data
+  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+
+ # Round baths up
+
+  abb.data$baths <- round(abb.data$baths + .01, 0)
+
+```
+
+### Bed/Bath Combination
+
+In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+As a result we examine the combinations of the two.
+
+```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Create combination variable
+
+  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
+  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
+
+```
+
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Make long term plot
+
+  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    ggtitle('Long Term Rentals') + 
+    facet_wrap(~type)
+
+ # Make short term plots
+
+  stb <- ggplot(abb.data, aes(x=bedbath)) +
+    geom_bar(fill=str.col, color=str.col) + 
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    ggtitle('Short Term Rentals') + 
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    facet_wrap(~type)
+
+ # Plot
+
+  ggMultiPlots(ltb, stb, cols=1)
+
+```
+
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
+
+```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Set level of acceptable combinations
+
+  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
+
+ # Filter data
+
+  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
+  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
+
+```
+
+Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
+We additionally create a product variable that splits the bed/bath by apartment and house.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Re-order factors
+
+  abb.data$bedbath <- factor(abb.data$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  ltr.data$bedbath <- factor(ltr.data$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+  # Add product as a variable
+
+  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
+  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
+
+```
+
+## Rates and Rental values
+
+We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
+
+```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
+  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
+
+```
+
+Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
+
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Property level data
+
+  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
+  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
+  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
+  abb.data$monthly.rate <- abb.data$monthly * exch.rate
+
+  # Daily data
+
+  daily.data$price <- daily.data$price * exch.rate
+
+```
+
+```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # ltr Plot
+
+  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
+    geom_density(fill=ltr.col, alpha=.8) +
+    ylab('') +
+    xlab('Weekly Rental') + 
+    ggtitle('Long Term Rentals') + 
+    scale_x_continuous(limits=c(0, 1500)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+  # Nightly Rate plot
+  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
+    geom_density(fill=str.col, alpha=.8) + 
+    ylab('') +
+    xlab('Nightly Rate') +
+    ggtitle('Short Term Rentals') + 
+    scale_x_continuous(limits=c(0, 600)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+```
+
+```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  ggMultiPlots(ltr.plot, rate.plot, cols=2)
+
+```
+
+From these density plots we see that most weekly Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
+We filter the data accordingly.
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Filter the long term data
+
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
+
+ ## Filter the short term data
+
+  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
+                         abb.data$nightly.rate <= 500, ]
 
@@
 
+```{r write_afterspobj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+after.SP <- list(abb.data=abb.data,
+                  daily.data=daily.data,
+                  ltr.data=ltr.data,
+                  listing.data=listing.data)
+
+save(after.SP, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_afterSP.RData")
+
+```
+
 The location of the short and long term rentals, colored by submarket, are shown below
@@
 
-## Structural Characteristics
-
-&nbsp;
-
-In this section we transform and filter based on the structural characteristics of the properties.
-
-### Fix Boolean Variables
-
-Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
-
-```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
-  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
-  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
-  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
-  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
-
-```
-
-&nbsp;
-
-### Bedrooms
-
-We start by looking at bedrooms.
-We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
-We then plot the distribution of diffeltr bedrooms counts.
-From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
-
-```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove missing and data errors
-
-  # Long term data
-  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
-  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
-
-  # Short term data
-  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
-  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
-
-```
-
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Build long term bar plot
-
-   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:10, breaks=1:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Long Term Rentals')
-
- # Build short term bar plot
-
-  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:10, breaks=0:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Short Term Rentals')
-
- # Make the comparison plot
-
-  ggMultiPlots(abbbed, ltrbed, cols=1)
-
-```
-
-For both short and long term ltrals we see that most apartments have less than 4 bedrooms and houses less than 5.
-We filter the data accordingly.
-Additionally, note that short term ltrals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
-We convert the 0 bed short term units to 1 bed units.
-
-```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove all with more than 4 beds
-
-  abb.data <- abb.data[abb.data$bedrooms < 5, ]
-  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
-
- # Remove apartments with more than 3
-
-  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
-  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
-
-  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
-  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
-
-  # Convert 0 Bed to 1 Bed  
-  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
-
-```
-
-### Bathrooms
-
-We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
-
-```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove missing data
-
-  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
-  abb.data <- abb.data[!is.na(abb.data$baths), ]
-
-```
-
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Build long term plot
-
-  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:8, breaks=1:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Long Term Rentals')
-
- # Build short term plot
-
-  stbath <- ggplot(abb.data, aes(x=baths)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:8, breaks=0:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Short Term ltrals')
-
- # Make Plots
-
-  ggMultiPlots(stbath, ltbath, cols=1)
-
-```
-
-Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
-A few short term properties state no baths, which is likely an error so we remove these as well.
-Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
-We round the baths up to whole integers.
-
-```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Filter by bath count
-
-  # Short term data
-  abb.data <- abb.data[abb.data$baths < 4, ]
-  abb.data <- abb.data[abb.data$baths > 0, ]
-
-  # Long term data
-  ltr.data <- ltr.data[ltr.data$baths < 4, ]
-
- # Round baths up
-
-  abb.data$baths <- round(abb.data$baths + .01, 0)
-
-```
-
-### Bed/Bath Combination
-
-In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two.
-
-```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Create combination variable
-
-  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
-  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
-
-```
-
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Make long term plot
-
-  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ggtitle('Long Term Rentals') + 
-    facet_wrap(~type)
-
- # Make short term plots
-
-  stb <- ggplot(abb.data, aes(x=bedbath)) +
-    geom_bar(fill=str.col, color=str.col) + 
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    ggtitle('Short Term Rentals') + 
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    facet_wrap(~type)
-
- # Plot
-
-  ggMultiPlots(ltb, stb, cols=1)
-
-```
-
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
-
-```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Set level of acceptable combinations
-
-  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
-
- # Filter data
-
-  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
-  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
-
-```
-
-Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
-We additionally create a product variable that splits the bed/bath by apartment and house.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Re-order factors
-
-  abb.data$bedbath <- factor(abb.data$bedbath, 
-                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-  ltr.data$bedbath <- factor(ltr.data$bedbath, 
-                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-
-  # Add product as a variable
-
-  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
-  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
-
-```
-
-## Rates and Rental values
-
-We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
-
-```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
-  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
-
-```
-
-Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
-
-```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Property level data
-
-  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
-  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
-  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
-  abb.data$monthly.rate <- abb.data$monthly * exch.rate
-
-  # Daily data
-
-  daily.data$price <- daily.data$price * exch.rate
-
-```
-
-```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  # ltr Plot
-
-  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
-    geom_density(fill=ltr.col, alpha=.8) +
-    ylab('') +
-    xlab('Weekly Rental') + 
-    ggtitle('Long Term Rentals') + 
-    scale_x_continuous(limits=c(0, 1500)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-
-  # Nightly Rate plot
-  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
-    geom_density(fill=str.col, alpha=.8) + 
-    ylab('') +
-    xlab('Nightly Rate') +
-    ggtitle('Short Term Rentals') + 
-    scale_x_continuous(limits=c(0, 600)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-
-```
-
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  ggMultiPlots(ltr.plot, rate.plot, cols=2)
-
-```
-
-From these density plots we see that most weekly Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
-We filter the data accordingly.
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Filter the long term data
-
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
-
- ## Filter the short term data
-
-  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
-                         abb.data$nightly.rate <= 500, ]
-
-```
-
 ## Filter Transaction Data
@@
 
-  save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
+  #save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
+  save(abb.data, listing.data, daily.data, ltr.data, subs, abb.col,
+       file="C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
 

### 2017-01-05 abbReturns_Writeup.Rmd
Initial data prep to writeup and re-order

@@
 ---
-title: "Should I AirBNB My Property"
-author: "Andy Krause"
+title: "Should I AirBNB My Property?"
+author: "Andy Krause and Gideon Aschwanden"
 date: "December 17, 2016"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
+
+```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  library(spdep)
+  library(maptools)
+  library(gstat)
+  library(ggplot2)
+  library(geosphere)
+  library(ggmap)
+  library(xtable)
+  library(chron)
+  library(plyr)
+  library(sp)
+  library(rgeos)
+  library(reshape2)
+  library(stringr)
+  library(RColorBrewer)
+  library(Hmisc)
+  library(kernlab)
+
+```
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  # Get computer names
+
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+
+  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
+
+    data.path <- 'c:/dropbox/research/airBNB/data/'
+    code.path <- 'c:/code/'
+
+  } else {
+
+    data.path <- 'alternate data path'
+    code.path <- 'alternate data path'
+
+  }
+
+```
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  source(paste0(code.path, "dataviztools/ggplottools.R"))
+  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
+
+```
+
+```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+ # Set all colors
+
+  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
+                     'ebisu', 'tirol', 'foggy', 'hof')
+  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
+               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
+               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
+               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
+               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
+
+  # Set specific colors
+
+  str.col <- abb.col[1]
+  ltr.col <- abb.col[3]
+
+```
+
+```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+  load(paste0(data.path, '/analyzed/abb_working.RData'))
+
+```
 
@@
 
+Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.
+While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
+
 - Show example
@@
 
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  exch.rate <- 1.32
+
+```
+
 ### Preparation
+
+In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
+Primarily, this involves the filtering out of data errors and/or outlier values.
+However, as our data are from two different sources, number of fields also require standardization so that comparisons between the two tenure options can be made.
+
+We begin by filtering observations by time.
+Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
+To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
+Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
+In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
+
+Next, we examine property types.
+AirBNB units are classified into 19 different property types.
+The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
+For the sake of this analysis, we will collapse these twenty types into three types:
+
+1. **House**:  Includes properties labeled 'House' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
+3.
+**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
+
+Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+
+1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
+3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+
+Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
+This is most apparent when talking about apartment dwellings.
+In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
+Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
+
+As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
+Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
+As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
+
+```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}  
+  data.path <- 'c:/dropbox/research/airBNB/data/'
+  load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
+  abb.data <- before.PT$abb.data
+  ltr.data <- before.PT$ltr.data
+  daily.data <- before.PT$daily.data
+```
+
+```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+
+  # Create Airbnb plot
+
+  abb.types <- ggplot(abb.data, aes(x=type)) + 
+    geom_bar(color=str.col, fill=str.col) +
+    xlab('') + 
+    ggtitle('\n      Short Term Rentals\n')  +
+    ylab('# of Properties\n')
+
+  # Create long term rental plot
+
+  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
+    geom_bar(color=ltr.col, fill=ltr.col) +
+    xlab('') + 
+    ggtitle('\n      Long Term Rentals\n')  +
+    ylab('# of Properties\n')
+
+  # Output plots
+
+  ggMultiPlots(abb.types, ltr.types, cols=2)
+
+```
+
+```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+
+  abb.data <- subset(abb.data, type != 'Other')
+  ltr.data <- subset(ltr.data, type != 'Other')
+
+```
+
+Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+
+1. **Entire Home/Apt**: The entire home or apartment is available
+2. **Private Room**: One room within a house or apartment is available
+3. **Shared Room**: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returns, we remove all short term properties that do not lease the entire home/apt.
+Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
+
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+
+  # Fix data types and names
+
+  abb.data$listing.type <- as.character(abb.data$listing.type)
+  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'
+
+  # Make Plot
+
+  ggplot(abb.data, aes(x=listing.type)) + 
+    geom_bar(color=abb.col[1], fill=abb.col[1]) +
+    xlab('') + 
+    ggtitle('\n                           Short Term Rentals by Listing Type\n')  +
+    ylab('# of Properties\n')
+
+```
+
+#### Structural Characteristics
+
+We now turn to filtering by structural characteristics.
+As the Airbnb data provides limited information on the structural characteristics, the only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
+Additionally, as the markets and structural components of houses and apartment differ, we bifurcate our analysis between the two property types from this point forward.
+
+We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
+For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
+We filter the data accordingly.
+Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
+We convert the 0 bed short term units to 1 bed units.
+
+```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Remove missing and data errors
+
+  # Long term data
+  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
+  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
+
+  # Short term data
+  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
+  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
+
+```
+
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+
+ # Build long term bar plot
+
+   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=1:10, breaks=1:10)+
+    xlab('\nBedrooms\n') +
+    ylab('') +
+    ggtitle('Bedrooms in Long Term Rentals')
+
+ # Build short term bar plot
+
+  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=0:10, breaks=0:10)+
+    xlab('\nBedrooms\n') +
+    ylab('') +
+    ggtitle('Bedrooms in Short Term Rentals')
+
+ # Make the comparison plot
+
+  ggMultiPlots(abbbed, ltrbed, cols=1)
+
+```
+
+```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Remove all with more than 4 beds
+
+  abb.data <- abb.data[abb.data$bedrooms < 5, ]
+  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+
+ # Remove apartments with more than 3
+
+  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
+  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
+
+  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
+  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
+
+  # Convert 0 Bed to 1 Bed  
+  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
+
+```
+
+We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
+Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
+A few short term properties state no baths, which is likely an error so we remove these observations from the data.
+Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
+We round the baths in the short term data up to whole integers.
+
+```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Remove missing data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
+  abb.data <- abb.data[!is.na(abb.data$baths), ]
+
+```
+
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+
+ # Build long term plot
+
+  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=1:8, breaks=1:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Long Term Rentals')
+
+ # Build short term plot
+
+  stbath <- ggplot(abb.data, aes(x=baths)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=0:8, breaks=0:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Short Term ltrals')
+
+ # Make Plots
+
+  ggMultiPlots(stbath, ltbath, cols=1)
+
+```
+
+```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Filter by bath count
+
+  # Short term data
+  abb.data <- abb.data[abb.data$baths < 4, ]
+  abb.data <- abb.data[abb.data$baths > 0, ]
+
+  # Long term data
+  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+
+ # Round baths up
+
+  abb.data$baths <- round(abb.data$baths + .01, 0)
+
+```
+
+#### Bed/Bath Combination
+
+In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+As a result we examine the combinations of the two.
+
+```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Create combination variable
+
+  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
+  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
+
+```
+
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+
+ # Make long term plot
+
+  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    ggtitle('Long Term Rentals') + 
+    facet_wrap(~type)
+
+ # Make short term plots
+
+  stb <- ggplot(abb.data, aes(x=bedbath)) +
+    geom_bar(fill=str.col, color=str.col) + 
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    ggtitle('Short Term Rentals') + 
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    facet_wrap(~type)
+
+ # Plot
+
+  ggMultiPlots(ltb, stb, cols=1)
+
+```
+
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
+
+```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ # Set level of acceptable combinations
+
+  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
+
+ # Filter data
+
+  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
+  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
+
+```
+
+### Rates and Rental values
+
+We now turn to filtering by the prices -- the nightly rates and weekly rental values.
+We start by removing observations missing price data.
+Plotting the distribution of the rates and rents we see that most weekly rentals are greater than \$200 and less than \$1000 per week while most nightly rates are greater than \$50 and less than \$500 per night.
+We filter the data accordingly.
+
+```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
+  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
+
+```
+
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  # Property level data
+
+  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
+  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
+  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
+  abb.data$monthly.rate <- abb.data$monthly * exch.rate
+
+  # Daily data
+
+  daily.data$price <- daily.data$price * exch.rate
+
+```
+
+```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+  # ltr Plot
+
+  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
+    geom_density(fill=ltr.col, alpha=.8) +
+    ylab('') +
+    xlab('Weekly Rental') + 
+    ggtitle('Long Term Rentals') + 
+    scale_x_continuous(limits=c(0, 1500)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+  # Nightly Rate plot
+  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
+    geom_density(fill=str.col, alpha=.8) + 
+    ylab('') +
+    xlab('Nightly Rate') +
+    ggtitle('Short Term Rentals') + 
+    scale_x_continuous(limits=c(0, 600)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+```
+
+```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+  ggMultiPlots(ltr.plot, rate.plot, cols=2)
+
+```
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ ## Filter the long term data
+
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
+
+ ## Filter the short term data
+
+  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
+                         abb.data$nightly.rate <= 500, ]
+
+```
+
+### Location and Submarkets
+
+```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Build the map object
+
+  # Set colors
+  g.cols <- abb.col[c(2, 10, 9)]
+
+  # Make map
+  loc.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
+    scale_fill_manual(values=g.cols, labels=c('Inner      ',
+                                              'Middle      ',
+                                              'Outer')) +
+    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    ggtitle("Melbourne Suburb Classifications")
+
+```
+
+```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=6}
+
+  loc.map
+
+```
+
+```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}  
+  data.path <- 'c:/dropbox/research/airBNB/data/'
+  load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
+  abb.data <- after.SP$abb.data
+  ltr.data <- after.SP$ltr.data
+  daily.data <- after.SP$daily.data
+```
+
+```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  # Set submarket colors
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
+  # Make map
+
+  abb.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
+               alpha=.2) +
+    scale_color_manual(values=sm.col) +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
+    ggtitle('AirBNB Location\nBy Submarket')
+
+```
+
+```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  # Make map
+
+  ltr.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
+               alpha=.1) +
+    scale_color_manual(values=sm.col) +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
+    ggtitle('Long Term Rental Location\nBy Submarket')
+
+```
+
+```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
+
+  ggMultiPlots(abb.map, ltr.map, cols=2)
+
+```
+
+```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
+
+  # Make Airbnb submarket map
+
+  abbtype.map <- ggplot() +
+    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    scale_fill_manual(values=sm.col) +
+    facet_wrap(~type) +
+    ylab('# of Properties\n') + xlab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank()) +
+    ggtitle('AirBNB Property Type\nBy Submarket')
+
+  # Make Long term rental map
+
+  ltrtype.map <- ggplot() +
+    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    scale_fill_manual(values=sm.col) +
+    facet_wrap(~type) +
+    ylab('# of Properties\n') + xlab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank()) +
+    ggtitle('Long Term Property Type\nBy Submarket')
+
+```
+
+```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
+
+  ggMultiPlots(abbtype.map, ltrtype.map, cols=2)
+
+```
+
+## Comparison
+
+<!-- ```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   load(paste0(data.path, '/analyzed/abb_working.RData')) -->
+
+<!-- ``` -->
 

### 2017-01-05 abbReturns_Writeup.Rmd
Fixes to Data prep charts

@@
 
-```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type'}
 
@@
     xlab('') + 
-    ggtitle('\n      Short Term Rentals\n')  +
-    ylab('# of Properties\n')
+    ylab('# of Properties\n') +
+    labs(title = "Short Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
     xlab('') + 
-    ggtitle('\n      Long Term Rentals\n')  +
-    ylab('# of Properties\n')
+    ylab('# of Properties\n') +
+    labs(title = "Long Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
 
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap='Listing Type of Short Term Rentals'}
 
@@
     xlab('') + 
-    ggtitle('\n                           Short Term Rentals by Listing Type\n')  +
-    ylab('# of Properties\n')
+    ylab('# of Properties\n') +
+    labs(title = "Short Term Rentals by Listing Type\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bedrooms by Tenure & Property Type'}
 
@@
     scale_x_continuous(labels=1:10, breaks=1:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Long Term Rentals')
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bedrooms in Long Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
     scale_x_continuous(labels=0:10, breaks=0:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Short Term Rentals')
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bedrooms in Short Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bathrooms by Tenure & Property Type'}
 
@@
     scale_x_continuous(labels=1:8, breaks=1:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Long Term Rentals')
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bathrooms in Long Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
     scale_x_continuous(labels=0:8, breaks=0:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Short Term ltrals')
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bathrooms in Short Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}
 
@@
     geom_bar(fill=ltr.col, color=ltr.col) +
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ggtitle('Long Term Rentals') + 
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bed/Bath Combo in Long Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
     facet_wrap(~type)
@@
     geom_bar(fill=str.col, color=str.col) + 
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    ggtitle('Short Term Rentals') + 
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    xlab('') +
+    ylab('# of Props\n') +
+    labs(title = "Bed/Bath Combo in Short Term Rentals\n") + 
+    theme(plot.title = element_text(hjust = 0.5)) + 
+    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
     facet_wrap(~type)
@@
     geom_density(fill=ltr.col, alpha=.8) +
-    ylab('') +
+    ylab('Frequency') +
     xlab('Weekly Rental') + 
@@
           axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
+          axis.ticks.y=element_blank(), 
+          plot.title = element_text(hjust = 0.5))
 
@@
     geom_density(fill=str.col, alpha=.8) + 
-    ylab('') +
+    ylab('Frequency') +
     xlab('Nightly Rate') +
@@
 
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'}
 
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-    scale_fill_manual(values=g.cols, labels=c('Inner      ',
+    scale_fill_manual(values=c('gray10', 'gray40', 'gray70'),
+                      labels=c('Inner      ',
                                'Middle      ',
                                'Outer')) +
-    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
+    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) +
     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
@@
     theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
     ggtitle("Melbourne Suburb Classifications")
@@
 
-```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=6}
+```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Melbourne Suburb Classifications'}
 
@@
   abb.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
     geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
@@
     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
     theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
     guides(colour = guide_legend(override.aes = list(size=3,
@@
   ltr.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
     geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
@@
    theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
     guides(colour = guide_legend(override.aes = list(size=3,
@@
 
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
+```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9}
 
@@
           axis.text.x=element_blank(),
-          axis.ticks.x=element_blank()) +
-    ggtitle('AirBNB Property Type\nBy Submarket')
+          axis.ticks.x=element_blank(),
+          plot.title = element_text(hjust = 0.5)) +
+    ggtitle('AirBNB Property Type By Submarket')
 
@@
           axis.text.x=element_blank(),
-          axis.ticks.x=element_blank()) +
-    ggtitle('Long Term Property Type\nBy Submarket')
+          axis.ticks.x=element_blank(),
+          plot.title = element_text(hjust = 0.5)) +
+    ggtitle('Long Term Property Type By Submarket')
 
@@
 
-```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
+```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
 
-  ggMultiPlots(abbtype.map, ltrtype.map, cols=2)
+  abbtype.map
+
+```
+
+```{r ltrtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
+
+  ltrtype.map
 

### 2017-01-05 abbReturns_Script.Rmd
adding data cleaning counter

@@
 
+```{r}
+
+setCleanCount <- function(){
+
+  abb.orig <- nrow(abb.data)
+  daily.orig <- nrow(daily.data)
+  ltr.orig <- nrow(ltr.data)
+  list.orig <- nrow(listing.data)
+
+  clean.df <- data.frame(operation='initial',
+                         abb=abb.orig,
+                         daily=daily.orig,
+                         ltr=ltr.orig,
+                         list=list.orig)
+  assign('clean.count', clean.df, envir=.GlobalEnv)
+  assign('abb.run.total', nrow(abb.data), envir=.GlobalEnv)
+  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
+  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
+  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
+
+}
+
+countCleaning <- function(operation){
+
+  abb.cut <- abb.run.total - nrow(abb.data)
+  daily.cut <- daily.run.total - nrow(daily.data)
+  ltr.cut <- ltr.run.total - nrow(ltr.data)
+  listing.cut <- list.run.total - nrow(listing.data)
+
+  new.df <- data.frame(operation=operation,
+                       abb=abb.cut,
+                       daily=daily.cut,
+                       ltr=ltr.cut,
+                       list=listing.cut)
+  comb.df <- rbind(clean.count, new.df)
+  assign('clean.count', comb.df, envir=.GlobalEnv)
+  assign('abb.run.total', nrow(abb.data), envir=.GlobalEnv)
+  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
+  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
+  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
+
+}
+
+setCleanCount()
+
+```
+
 ```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
@@
   listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
+
+ # Count cleaning
+
+  countCleaning('time')
 
@@
 
+  countCleaning('property.type')
+
 ```
@@
   abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
+
+  countCleaning('listing.type')
 
@@
 
+  countCleaning('bedrooms')
+
 ```
@@
 
+  countCleaning('bathrooms')
+
 ```
@@
   abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
+
+  countCleaning('bedbath')
 
@@
                          abb.data$nightly.rate <= 500, ]
+
+  countCleaning('rates.rents')
 
@@
 
+  countCleaning('location')
+
 ```
@@
 
+  countCleaning('revenue')
+
 ```
@@
   #save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
-  save(abb.data, listing.data, daily.data, ltr.data, subs, abb.col,
+  save(abb.data, listing.data, daily.data, ltr.data, subs, abb.col, clean.count,
        file="C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")

### 2017-01-05 abbReturns_Writeup.Rmd
adding data cleaning counter

@@
   daily.data <- before.PT$daily.data
+
 ```
@@
     theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
+  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
 
@@
 
-#### Bed/Bath Combination
-
 In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
@@
 ### Location and Submarkets
+
+Location is clearly an important determinant in both the short and long term rental markets.
+At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+Suburbs in Melbourne are much smaller than their North American counterparts.
+The specific suburb of a property is the second, or finer scale, at which the market operates.
+The plot below shows the three large submarkets (Inner, Middle and Outer).
+
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+
+We select the 18 suburbs below to represent the 'core' of the city.
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenties for tourists.
+
+We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
+Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
+
+Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
+For those without either (3% of the total) we remove them from the dataset at this point.
+
+Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.
+
+The location of the short and long term rentals, colored by submarket, are shown below
+
+The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
 
@@
 
+### Actual Revenue
+
+We now turn to calculating the revenues for each property under an Airbnb and a long term rental scenario.  Before we start, there are few additional data prepartion tasks to undertake.
+
+First we calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed for the Airbnb properties only.
+
+Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data.
+We do this step to remove those].
+From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+
+In this section we total up the actual revenues for each short and long term rental property.
+
+For the Airbnb properties we then calculate the actual revenue over the Sep 1 2015 to Aug 31 2016 period. Those with no revenue are removed.
+
+Next, we calculate the revenue for the long term rental data, saving only those with revenue of at least $5,000 (less than this represented properties with very long days on market.)
+
 ## Comparison

### 2017-01-05 abbReturns_Writeup.Rmd
equations

@@
 
-AirbnbRev = nightly rate * occupancy - (short costs + long costs)
--- short costs = cleaning, time
--- long costs = taxes and maintenance
+In this above scenario we compare the 12-month returns from the a long term rental with those of a short term rental.
+We define returns here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
 
-LtRev = weekly rate * (52 - search time) - (short costs + long costs)
--- short costs = brokerage
--- long costs = taxes and maintenance
+$$ R_{LT} = Rev_{LT} - C_{LT} $$
+$$ R_{ST} = Rev_{ST} - C_{ST} $$
 
-When is AirbnbRev > LtRev?
+$$ Rev_{LT} = Rent_{M} * (12 - C_{S}) $$  
+where $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+
+$$ Rev_{ST} = Rate_{N} * O_{Total} $$
+
+where $O_{Total}$ are the total number of occupancies over the 12-month period.
+
+$$ C_{LT} = T + M $$
+
+where
+
+where $T$ are tax related expenses and $M$ are general maintenance expenses.
+
+$$ C_{ST} = T + M + J $$
+
+where $T$ are tax related expenses, $M$ are general maintenance expenses and $J$ are janitorial expenses incurred after each short term tenancy.
+
+We assume for the sake of this scenario that the tax $T$ and general maintenance $M$ expenses are identical between tenure options and therefore cancel out.
+With the analysis that follows we will consider short term rental to be prefable to long-term if the following inequality holds:
+
+$$ Rate_{N} * O_{Total} - J > Rent_{M} * (12 - C_{S}) $$
 
 ## Data
+
+Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
+The Airbnb online portal is used as evidence of the short-term rental market.
+Airbnb is the largest short-term rental hub in the Melbourne region, though others do exist.
+As opposed to similar sites such as VRBO.com and homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, in way ways, directly compete with more traditional long term rentals.
+The data on the AirBNB market in Melbourne have been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
+The short term data include two types of observations, property level and nightly.
+Property-level data concist of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year.
+This data indicates the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay.).
+
+The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 

### 2017-01-05 abbReturns_Writeup.Rmd
Through data prep writeup

@@
 The short term data include two types of observations, property level and nightly.
-Property-level data concist of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year.
-This data indicates the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay.).
+Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year.
+This data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
+
+The Airbnb data cover the Melbourne metropolitan region from October 1st 2014 to August 30th 2016.
+There are missing nightly observations during the time period before September 1 2015.
+While we initially imputed these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
+All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
 
 The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
+This data also includes an observation for each rental property each time a detail of the listing changed.
+For example, if a property were listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
+These four observations are grouped by an event-specific identification number.
+In each case the last observation signifies the final price of the rental contract.
+We separate this data into two sets for efficiency reasons.
+The first data set includes all information about the property, physical and economic (date and amount of rent contract), while the second contains a property ID, a rental event ID, the list price and the date of the change.
+As such, the first dataset is a set of market observations with associated characteristics and the second is a listing history of each event.
+The long-term lease data covers the period from January 2014 to December 2015.
 
-Airbnb data from AirDNA.
-All of Melbourne.
-Most of Oct 2014 to Aug 30th 2016.
-Full data from Sept 1 2015 to Aug 30 2016.
-Daily and property data.
-Is scraped weekly or so for each property.
-All prices in US dollars.
-
-Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.
-While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
-
-- Show example
-
-Long-term data from Domain.  All of Melbourne.  June 2010 to June 2016.  Rental listings and final agreed prices. All property types.
-
-- Show example
-
-No direct link between data (no addresses given in AirBNB)
+Unfortunately, there are no common identifiers between the two dataset as the Airbnb data does not include address.
+Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
+As a result of this, we are unable to directly match observations from the two datasets.
+However, the number of properties that rented long term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
 
@@
 
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bedrooms by Tenure & Property Type'}
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'}
 
@@
 
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bathrooms by Tenure & Property Type'}
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'}
 
@@
 
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}
 
@@
 We now turn to filtering by the prices -- the nightly rates and weekly rental values.
-We start by removing observations missing price data.
-Plotting the distribution of the rates and rents we see that most weekly rentals are greater than \$200 and less than \$1000 per week while most nightly rates are greater than \$50 and less than \$500 per night.
-We filter the data accordingly.
+The long term rental data have a single price observation, the asking rent each time an change in the listing occurs, including the price at closing.
+For the short term data, there are two indicators of nightly rate.
+First, each property has a average nightly rate figure that takes the average of the rates for all booked nights over the October 2014 to August 2016 period.
+Second, there is a rate for each day in the daily observations.
+For the vast majority of properties, the daily rates change very little, but for a select few there is a wide variation in the daily rates, often somewhat randomly.
+In cases where a small number of reservations have been made, the average nightly rate can deviate widely from usual rate due to outliers on the high end.
+To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1 2015 to August 31, 2016 period.
+
+We start by removing property level observations missing price data.
+Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+We filter the property level data accordingly.
+We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.
 
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
-The plot below shows the three large submarkets (Inner, Middle and Outer).
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
-While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
-We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-
-We select the 18 suburbs below to represent the 'core' of the city.
-The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenties for tourists.
-
-We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
-Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
-
-Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
-For those without either (3% of the total) we remove them from the dataset at this point.
-
-Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.
-
-The location of the short and long term rentals, colored by submarket, are shown below
-
-The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
+The plot below shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
 
@@
 
-```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Melbourne Suburb Classifications'}
+```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'}
 
@@
 ```
+
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melbourne:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We select the 18 suburbs below to represent the 'core' of the city.
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenties for tourists.
+
+```{r, results="asis", echo=FALSE}
+
+ core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
+                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
+                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
+                   'St Kilda West', 'West Melbourne', 'Windsor')
+
+ c.subs <- data.frame(A=core.suburbs[1:6],
+                      B=core.suburbs[7:12],
+                      C=core.suburbs[13:18])
+ names(c.subs) <- NULL
+ rownames(c.subs) <- NULL
+
+ print(xtable(c.subs, caption = 'List of Core Suburbs'),
+       include.rownames=F,
+       caption.placement="top",
+       hline.after=c(0,6))
+
+```
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+The location of the short and long term rentals, colored by submarket, are shown below
+
+Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
+For those without either we remove them from the dataset at this point.
+After making this correction we then assign one of the five submarket designations based on the process described above.
 
@@
 
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9}
+```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9}
 
-  ggMultiPlots(abb.map, ltr.map, cols=2)
+  ggMultiPlots(abb.map, ltr.map, cols=1)
 
 ```
+
+To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+A number of interesting observations are illustrated here.
+First, the vast majority of Airbnb units are apartments in city-core or city locations.
+As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
+Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
+Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartment, somewhat common in long term markets, are nearly absent in the Airbnb market.
+Overall, the suburban and rural Airbnb market are quite thin, later results focusing on these market will need to be examined in light of this small sample size.
 
@@
 
-We now turn to calculating the revenues for each property under an Airbnb and a long term rental scenario.  Before we start, there are few additional data prepartion tasks to undertake.
+Our final data filtering considers the observed revenue of the properties.
+For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
+In a number of extreme cases, time on market was extremely long and the total observed revenues very low.
+To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
 
-First we calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed for the Airbnb properties only.
+For the short term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+Using this data we sum up the total revenue from bookings.
+For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
 
-Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data.
-We do this step to remove those].
-From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority randing between \$12,000 to \$30,000 per year.
+Short term revenue range from neglible to highs of greater than \$80,000.
+While this simple analysis does not control for locational and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
+Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
 
-In this section we total up the actual revenues for each short and long term rental property.
+```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
-For the Airbnb properties we then calculate the actual revenue over the Sep 1 2015 to Aug 31 2016 period. Those with no revenue are removed.
+ load(paste0(data.path, '/analyzed/abb_working.RData'))
 
-Next, we calculate the revenue for the long term rental data, saving only those with revenue of at least $5,000 (less than this represented properties with very long days on market.)
+```
+
+```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  abbr <- abb.data[,c('bedbath', 'revenue')]
+  abbr$tenure <- 'short-term'
+  ltrr <- ltr.data[,c('bedbath', 'revenue')]
+  ltrr$tenure <- 'long-term'
+  allr <- rbind(abbr, ltrr)
+
+  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) + 
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col)) +
+    ggtitle('Annual Revenues by Tenure Type') + 
+    xlab('Annual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000))
+
+```
+
+### Summary of Data Cleaning
+
+We have applied nine separate filters to our two datasets.
+In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters.
+There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
+Removing those not listed during the study period removes 1/3 of all properties.
+Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
+From these 6,600 properties structural characteristics, locational issues and outlying nightly rates remove another 800 from consideration.
+Finally, 1,400 of these have never been booked and have \$0 revenue, requiring removal.
+From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
+
+For the long term data, over half of the observations fall outside of our considered time frame,reducing the sample size down to around 130,000 from 290,000.
+Further consideration regarding property types, structural characteristics, location, etc.
+remove another 10,000 observations, leaving 122,051 in the final dataset.
+
+```{r, results="asis", echo=FALSE}
+
+cc <- clean.count[,c('operation', 'abb', 'ltr')]
+abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1]))
+ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
+abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1])
+abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)])
+ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
+ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
+clean.table <- data.frame(field=cc$operation,
+                          abbcount=abb.count,
+                          abbcut=abb.cut,
+                          abbper=abb.per,
+                          ltrcount=ltr.count,
+                          ltrcut=ltr.cut,
+                          ltrper=ltr.per)
+
+rownames(clean.table) <- NULL
+clean.table$field <- c('Initial Count', 'Time', 'Property Type',
+                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
+                       'Rates & Rents', 'Location', 'Revenue')
+clean.table$abbper <- 100*round(clean.table$abbper, 2)
+clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
+names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
+                        'Long Term', 'Cut', '% Cut')
+options(xtable.comment = FALSE)
+print(xtable(clean.table,
+       digits=0),
+       include.rownames=FALSE)
+
+```
 
 ## Comparison
-
-<!-- ```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
-
-<!--   load(paste0(data.path, '/analyzed/abb_working.RData')) -->
-
-<!-- ``` -->
 

### 2017-01-07 abbReturns_Working.R
added type, sm , bb, smt analysis

@@ -59,9 +59,11 @@
  ## Global model
 
   # Set model specifications
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb) + 
                             as.factor(ltr.month))
-  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb))
  
  # Make comparison between two markets  
   imp.data <- imputeRatesRents(ltr.df=ltr.data, 
@@ -192,7 +194,7 @@
   explain.plot <- blank.plot +
     geom_text(data=ann.df,
               label=ann.df$lab,
-              size=4.5) +
+              size=3) +
     geom_text(data=num.df,
               label=num.df$count,
               size=9.5) +
@@ -205,7 +207,7 @@
               ymin = -Inf,ymax = Inf, alpha = 0.4) +
     geom_text(data=reason.df,
               label=reason.df$lab,
-              size=4.5) +
+              size=3) +
     geom_text(data=num.df,
               label=num.df$count,
               size=9.5) +
@@ -402,24 +404,146 @@
                              svm=c(mean(svm.rate$pred$pred),
                                    mean(svm.qtl$pred$pred)))
   
-
+### Split by Type -----------------------------------------------------------------------
   
-abb.apt <- which(abb.revs$type == 'Apartment')
-ltr.apt <- which(ltr.revs$type == 'Apartment')
-
-    
-abc <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
-                          abb.df=abb.revs[-abb.apt, ],
-                          ltr.mod.spec=ltr.mod.spec,
-                          abb.mod.spec=abb.mod.spec,
-                          clip.field='suburb',
-                          market.field='sub.mrkt',
-                          mrkt.col=sm.col,
-                          heat.col=c(abb.col[1], abb.col[5]))
-
-    
-      
+  # Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
[…]

### 2017-01-07 analysis_functions.R
fixed group.field but

@@ -349,7 +349,7 @@ createCompTable <- function(abb.df,
 makePrefPlot <- function(pref.data,
                          x.field,
                          y.field,
-                         group.field,
+                         group.field='none',
                          metric='mean',
                          cumulative=FALSE,
                          smooth=FALSE,
@@ -384,10 +384,18 @@ makePrefPlot <- function(pref.data,
       pref.df <- pref.data[pref.data[,x.field] == i.pl, ]
     }
     
-    # Create the table
-    pref.table <- tapply2DF(pref.df[ ,y.field], 
-                            pref.df[ ,group.field],
-                            metric.fnct)
+    
+    if(group.field != 'none'){
+      
+      # Create the table
+      pref.table <- tapply2DF(pref.df[ ,y.field], 
+                              pref.df[ ,group.field],
+                              metric.fnct)
+    } else {
+      
+      pref.table <- data.frame(ID='all', 
+                               Var=metric.fnct(pref.df[,y.field], na.rm=T))
+    }
     
     # Add the x variable
     pref.table$x.var <- i.pl
@@ -443,7 +451,7 @@ makeHeatMap <- function(hm.data,
                         return.svm=FALSE,
                         svm.opts=list(type='C-svc',
                                       kernel='polydot',
-                                      poly.degree=4,
+                                      poly.degree=2,
                                       expand.factor=100)){
   
  ## Prepare the plotting data  
@@ -649,6 +657,17 @@ fullMarketAnalysis <- function(ltr.df,
   
  ## Fix null
   
+  if(market.field != 'type'){
+    if(length(table(abb.df$type)) == 1 |
+       length(table(ltr.df$type)) == 1){
+    
+      ltr.mod.spec <- update(ltr.mod.spec, . ~ . - as.factor(type))
+      abb.mod.spec <- update(abb.mod.spec, . ~ . - as.factor(type))
+      
+    }
+  }
+  
+    
  ## Make comparison between two markets  
   
   mrkt.comp <- revCompWrapper(ltr.df=ltr.df,

### 2017-01-07 abbReturns_Writeup.Rmd
writeup on  global analysis

@@
   html_document: default
+geometry: margin=3cm
 ---
+
+<!-- <script type="text/x-mathjax-config"> -->
+<!-- MathJax.Hub.Config({ -->
+<!--   TeX: {  -->
+<!--       equationNumbers: { -->
+
+<!--             autoNumber: "all", -->
+<!--             formatNumber: function (n) {return '9.'+n} -->
+<!--       }  -->
+<!--   } -->
+<!-- }); -->
+<!-- </script> -->
 
@@
   library(kernlab)
+  library(lmtest)
 
@@
 
-$$ R_{LT} = Rev_{LT} - C_{LT} $$
-$$ R_{ST} = Rev_{ST} - C_{ST} $$
-
-$$ Rev_{LT} = Rent_{M} * (12 - C_{S}) $$  
+\begin{equation} 
+R_{LT} = Rev_{LT} - C_{LT}
+\end{equation}
+
+\begin{equation} 
+R_{ST} = Rev_{ST} - C_{ST}
+\end{equation}
+
+\begin{equation} 
+Rev_{LT} = Rent_{M} * (12 - C_{S}) 
+\end{equation}
+
 where $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
 
-$$ Rev_{ST} = Rate_{N} * O_{Total} $$
+\begin{equation} 
+Rev_{ST} = Rate_{N} * O_{Total} 
+\end{equation}
 
@@
 
-$$ C_{LT} = T + M $$
+\begin{equation} 
+C_{LT} = T + M 
+\end{equation}
 
@@
 
-$$ C_{ST} = T + M + J $$
+\begin{equation} 
+C_{ST} = T + M + J 
+\end{equation}
 
@@
 
-$$ Rate_{N} * O_{Total} - J > Rent_{M} * (12 - C_{S}) $$
+\begin{equation} 
+Rate_{N} * O_{Total} - J > Rent_{M} * (12 - C_{S}) 
+\end{equation}
 
@@
 
- load(paste0(data.path, '/analyzed/abb_working.RData'))
+ load(paste0(data.path, '/analyzed/abb_results.RData'))
 
@@
 
-### Imputing
+Data prepared, we now turn to comparing returns between long and short term rental options.
+As mentioned above, there are no direct matches between the datasets.
+In other words we have not direct observed a property which has been in a long-term rental followed by short-term or vice versa.
+We will, instead, make the comparisons between the two by imputing likely short-term (long-term) rental revenues for the long-term (short-term) data and then comparing the observed revenues to the imputed revenues of the unobserved tenure type.
+
+We make our imputations via hedonic price models, one for long-term rentals and one for short-term rentals.
+We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term rental for the short term properties.
+We do the same for the long-term properties using a modeled derived from the short-term data.
+
+For the long-term market, we use the following model specification:
+
+\begin{equation} 
+  \label{eq:test}
+ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i} 
+\end{equation}
+
+where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+
+For the short-term market the specification is similar, minus the time correction.
+We eliminate this control because the short term rates are based on the medium value over the entire period and not monthly.
+This specification is:
+
+\begin{equation} 
+ln(RentST_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \epsilon_{i} 
+\end{equation}
+
+where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
 
@@
 
-### Comparing
-
 ## Results
 
--- Start with a global analysis
-
-### What is accurate?
-
-- Discuss why Airbnb Actual is the only relevant one.  
--- Show charts
--- Discuss problems with Rate imputation
--- Discuss problems with Occupancy imputation
-
-#### Comp Tables/Figs
-
-### Heat Maps
+We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
+What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
+It is likely that different submarkets operate differently, we will explore this hypothesis after first analyzing the full metropolitan region.
+
+We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
+A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel).
+This is likely due to the fact that there are more houses (compared to apartments) in the long-term data than in the short-term data.
+Interestingly, the observed (long-term) and imputed (short term) weekly rental values are somewhat similar, suggesting that the higher rent, city-core apartments push the distribution of the imputed short-term values upwards.
+
+For each of the observed values we also create a fitted value for that observation in the model.
+This may help to reduce the influence of outlying observed values in our model.
+To be clear, Each observation will now have three estimates of rates and rents.
+For the short-term properties they will have: 1) an actual nightly rate; 2) an estimated nightly rate; and 3) an estimated long-term (weekly) rent.
+The long-term properties will have: 1) an actual long-term (weekly) rent; 2) an estimated long-term (weekly) rent; and 3) an estimated nightly rate.
+
+```{r pred.glob.imp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  abbir <- abb.imp[,c('bedbath', 'imp.rent', 'med.rate')]
+  abbir$tenure.rate <- 'short-term (observed)'
+  abbir$tenure.rent <- 'short-term (imputed)'
+
+  ltrir <- ltr.imp[,c('bedbath', 'event.price', 'imp.rate')]
+  ltrir$tenure.rate <- 'long-term (imputed)'
+  ltrir$tenure.rent <- 'long-term (observed)'
+
+  names(abbir) <- names(ltrir) <- c('bedbath', 'rent', 'rate', 'tenure.rate', 'tenure.rent')
+  allir <- rbind(abbir, ltrir)
+
+```
+
+```{r imp.rate.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  irate.plot <- ggplot(allir, aes(x=rate, fill=tenure.rate, color=tenure.rate)) + 
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col)) +
+    ggtitle('Nightly Rates by Tenure Type') + 
+    xlab('Nightly Rate') +
+    scale_x_continuous(breaks=c(seq(0,600, by=200)),
+                       labels=c('$0', '$200', '$400', '$600'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 625))
+
+```
+
+```{r imp.rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  irent.plot <- ggplot(allir, aes(x=rent, fill=tenure.rent, color=tenure.rent)) + 
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col)) +
+    ggtitle('Weekly Rents by Tenure Type') + 
+    xlab('Weekly Rents') +
+    scale_x_continuous(breaks=c(seq(0,1000, by=200)),
+                       labels=c('$0', '$200', '$400', '$600', '$800', '$1,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(150, 1000))
+
+```
+
+```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
+
+ ggMultiPlots(irate.plot, irent.plot, cols=2)
+
+```
+
+The question of whether or not the imputations are accurate remains.
+The table belows shows some simple diagnostics from the two imputation models.
+From this we see that the short-term model performs rather poorly, with a standard error of 34.6\% and over half of the residuals greater than 20\%.
+The long term model, on the other hand, performs quite well, with a standard error under 32\% and less than 19\% of fitted errors greater than 20\%.
+Given the small amount of independent variable available to the models, the long term market appear much more predictable than the short term market.
+This could be due to omitted variables in the short term market or a greater level of variability in the price setting (which is done by individuals) as opposed to the long-term market in which most owners get help with leasing from an agency.
+
+```{r, results="asis", echo=FALSE}
+
+abb.sum <- summary(imp.data$abb.mod)
+ltr.sum <- summary(imp.data$ltr.mod)
+
+abbs <- c(abb.sum$r.squared, abb.sum$adj.r.squared,
+          abb.sum$sigma, 
+          length(which(abs(abb.sum$residuals) > .2)) / length(abb.sum$residuals))
+ltrs <- c(ltr.sum$r.squared, ltr.sum$adj.r.squared,
+          ltr.sum$sigma, 
+          length(which(abs(ltr.sum$residuals) > .2)) / length(ltr.sum$residuals))
+
+summ.table <- data.frame(shortterm=round(abbs, 3),
+                         longterm=round(ltrs, 3))
+rownames(summ.table) <- c('r-squared', 'adj r-squared',
+                          'sigma', '% fit errors > 20%')
+names(summ.table) <- c('Short Term', 'Long Term')
+
+print(xtable(summ.table,
+       digits=3),
+       include.rownames=TRUE)
+
+```
+
+Next, to create an estimated short-term revenue for the long-term properties we have to create an estimate of the occupancy rate.
+For the estimated long-term rentals we have to create an estimate of the search time (days on market).
+To derive an occupancy rate, we use the weighted median value^[Weighted by the total number of days the property was offered on Airbnb over the year.] of the market, the entire metro region in this case, which is about 37%^[We attempted to use a logistic regression model to predict occupancy but were unsucessful to develop an appropriate approach.
+Work continues toward this end.].
+The range of occupancy varies widely from essentially 0 to 100%,with a standard deviation of 27%.
+
+For the long term search time, or days on market, we also use the median value of the observations.
+The median days on market is 24, with a standard deviation of 37.
+About 60\% of long term rental spent one month or less on the market and 85\% spent less than two months searching for a tenant.
+
+Using these estimated occupancy rates and days on market, we have used equations 3 and 4 to produce estimates of long-term and short-term revenues for the short and long term observations, respectively.
+We do these for the observed and the estimated rates and rents for each tenure type.
+As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as follows:
+
+```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4}
+
+  explain.plot <- blank.plot +
+    geom_text(data=ann.df,
+              label=ann.df$lab,
+              size=3) +
+    geom_text(data=num.df,
+              label=num.df$count,
+              size=9.5) +
+    coord_cartesian(ylim=c(-.5,1))
+
+ explain.plot
+
+```
+
+In other word the left hand panels are comparison made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
+In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
+
+The plot below shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
+The variation between these estimates is significant and troublesome.
+However, given our difficulty in accurately estimating short term nightly rates (see Table X) and the fact that occupancy rates are highly variable for short-term rentals, these variation are not surprising.
+As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
+Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
+
+```{r, results="asis", echo=FALSE}
+
+  one.df <- data.frame(x=rep(0, 4),
+                       y=rep(0, 4), 
+                       lab=c('31%', '87%', '54%', '79%'),
+                       est=c('Actual Rates & Rents', 'Actual Rates & Rents',
+                             'Imputed Rates & Rents', 'Imputed Rates & Rents'),
+                       data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
+
+  sizes <- c(.31, .87, .54, .79)
+
+  one.plot <- blank.plot +
+    geom_text(data=one.df,
+              label=one.df$lab,
+              size=18*sizes) +
+    ggtitle('% of Properties where \n Airbnb is more profitable') +
+    theme(legend.position='bottom',
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4,fig.height=4}
+
+ one.plot
+
+```
+
+In short, only in the upper left hand panel are we using the actual nightly rates and the actual occupancy rates from the short term market.
+We do estimate the long-term rates and days on market here, but as shown above, the models for those figures are much more robust.
+The plusses and minus of each comparison quadrant is shown below.
+As a result of these issues, we consider only those comparisons in quadrant 1 to be legitimate and use these going forward.
+
+```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4,fig.height=4}
+
+  reason.plot <- blank.plot +
+    geom_rect(data = mrkt.table, aes(fill=good),
+              xmin = -Inf,xmax = Inf,
+              ymin = -Inf,ymax = Inf, alpha = 0.4) +
+    geom_text(data=reason.df,
+              label=reason.df$lab,
+              size=3) +
+    geom_text(data=num.df,
+              label=num.df$count,
+              size=9.5) +
+    coord_cartesian(ylim=c(-.5,1))
+
+  reason.plot
+
+```
+
+```{r}
+  rawocc.pplot <- makePrefPlot(abb.revs,
+                               x.field='occ.rate',
+                               y.field='abb.act',
+                                    smooth=TRUE,
+                               smooth.span=.75)
+  rawocc.pplot <- rawocc.pplot +
+    xlab('\nOccupancy Rate') +
+    ylab('\n% of Properties where \nAirbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col) +
+    theme(legend.position='none')
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+  rawocc.pplot
+
+```
+
+```{r}
+
+  ggplot(abb.revs, aes(x=occ.rate)) +
+    geom_density(alpha=.3, fill=1) +
+    scale_color_manual(values=sm.col) +
+    scale_fill_manual(values=sm.col) +
+    scale_x_continuous(breaks=seq(0, 1, by=.5),
+                       labels=c('0%', '50%', '100%')) +
+    ylab('') +
+    xlab('Occupancy Rate') +
+    theme(legend.position='none',
+          axis.line=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks=element_blank(),
+          axis.title.y=element_blank())
+```
+
+```{r}
+
+  abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, 
+                                      return.type='rank') 
+  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, 
+                                  return.type='rank')
+
+  ## Make quartile location plot
+
+  qtlocc.pplot <- makePrefPlot(abb.revs,
+                               x.field='occ.qtl',
+                               y.field='abb.act',
+                               smooth=TRUE,
+                               smooth.span=.55)
+  qtlocc.pplot <- qtlocc.pplot +
+    xlab('\nQuantile of Occupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col) +
+    theme(legend.position='none')
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+  qtlocc.pplot
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+ rate.hm
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+  rate.hm.svm
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+ qtl.hm
+
+```
+
+```{r, fig.width=7, fig.height=5}
+
+  qtl.hm.svm
+
+```
+
+```{r, results="asis", echo=FALSE}
+
+print(xtable(market.ratio,
+       digits=3),
+       include.rownames=FALSE)
+
+```
 

### 2017-01-08 abbReturns_Working.R
Fix market.field issues

@@ -167,7 +167,7 @@
                             paste0('Long-Term Properties: \n (Imputed Airbnb Revenue \n vs.',
                                    '\n Imputed Long Term Revenue)')),
                       est=c('Actual Rates & Rents', 'Actual Rates & Rents',
-                            'Imputed Rates & Rents', 'Imputed Rates & Rents'),
+                            'Imp. Rates & Rents', 'Imp. Rates & Rents'),
                       data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
   
   reason.df <- data.frame(x=rep(0, 4),
@@ -181,7 +181,7 @@
                              paste0('- Imputed occupancy rates \n',
                                     '- Imputed nightly rate estimates')),
                        est=c('Actual Rates & Rents', 'Actual Rates & Rents',
-                             'Imputed Rates & Rents', 'Imputed Rates & Rents'),
+                             'Imp. Rates & Rents', 'Imp. Rates & Rents'),
                        data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
   
   num.df <- data.frame(x=rep(0, 4),
@@ -421,7 +421,7 @@
                               ltr.mod.spec=ltr.mod.spec,
                               abb.mod.spec=abb.mod.spec,
                               clip.field='suburb',
-                              market.field='sub.mrkt',
+                              market.field='none',
                               mrkt.col=sm.col,
                               heat.col=c(abb.col[1], abb.col[5]))
 
@@ -469,6 +469,7 @@
     sm.pos <- sm.pos + 1
   
   }
+  names(sm.results) <- as.character(s.levels)
 
 ### Estimate at bed/bath level -----------------------------------------------------------  
 
@@ -503,6 +504,7 @@
     bb.pos <- bb.pos + 1
   
   }
+  names(bb.results) <- as.character(bb.levels)
   
 ### Split by submarket and type ----------------------------------------------------------  
   
@@ -538,6 +540,7 @@
     smt.results[[smt.pos]] <- x.res
     smt.pos <- smt.pos + 1
   }
+  names(smt.results) <- as.character(smt.levels)
   
 ### Save workspace -----------------------------------------------------------------------
   

### 2017-01-08 analysis_functions.R

@@ -307,7 +307,21 @@ createCompTable <- function(abb.df,
                             ltr.df,
                             split.field=NULL){
   
-  if(is.null(split.field)){
+  if(split.field == 'none'){
+    
+    abb.imp <- mean(abb.df$abb.imp)
+    abb.act <- mean(abb.df$abb.act)
+    ltr.imp <- mean(ltr.df$abb.imp)
+    ltr.act <- mean(ltr.df$abb.act)
+    
+    rate.table <- data.frame(ID='all',
+                             var=c(abb.imp, abb.act, ltr.imp, ltr.act),
+                             est=c('Imputed Rates & Rents', 
+                                   'Actual Rates & Rent',
+                                   'Imputed Rates & Rents',
+                                   'Actual Rates & Rents'), 
+                             data=c('Airbnb', 'Airbnb',
+                                    'Long-Term', 'Long-Term'))
     
   } else {
     
@@ -334,8 +348,6 @@ createCompTable <- function(abb.df,
                                        'suburban', 'rural'))
         
     }
-    
-    
   }
   
   ## Return Values
@@ -649,7 +661,7 @@ fullMarketAnalysis <- function(ltr.df,
                                ltr.mod.spec,
                                abb.mod.spec,
                                clip.field,
-                               market.field='sub.mrkt',
+                               market.field='none',
                                mrkt.col=NULL,
                                heat.col=c('red', 'green'))
 
@@ -681,7 +693,7 @@ fullMarketAnalysis <- function(ltr.df,
   
   mrkt.table <- createCompTable(mrkt.comp$abb, mrkt.comp$ltr, market.field)
   
-  if(market.field == 'sub.mrkt'){
+  if(!is.null(market.field) && market.field == 'sub.mrkt'){
     mrkt.table$ID <- factor(mrkt.table$ID, 
                             levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
   }

### 2017-01-08 abbReturns_Writeup.Rmd
Global writeup, sm plots

@@
 ---
-
-<!-- <script type="text/x-mathjax-config"> -->
-<!-- MathJax.Hub.Config({ -->
-<!--   TeX: {  -->
-<!--       equationNumbers: { -->
-
-<!--             autoNumber: "all", -->
-<!--             formatNumber: function (n) {return '9.'+n} -->
-<!--       }  -->
-<!--   } -->
-<!-- }); -->
-<!-- </script> -->
 
@@
               label=ann.df$lab,
-              size=3) +
+              size=2.8) +
     geom_text(data=num.df,
@@
               size=9.5) +
-    coord_cartesian(ylim=c(-.5,1))
-
- explain.plot
-
-```
-
-In other word the left hand panels are comparison made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
-In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
-
-The plot below shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
-The variation between these estimates is significant and troublesome.
-However, given our difficulty in accurately estimating short term nightly rates (see Table X) and the fact that occupancy rates are highly variable for short-term rentals, these variation are not surprising.
-As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
-Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
+    coord_cartesian(ylim=c(-.5,1)) +
+    ggtitle('Explanation of \n Revenue Comparisons') +
+    theme(legend.position='bottom',
+          legend.title = element_blank(), 
+          plot.title = element_text(hjust = 0.5))
+
+```
 
@@
 
-```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4,fig.height=4}
-
- one.plot
+In other word the left hand panels are comparison made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
+In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
+
+The plot below shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
+The variation between these estimates is significant and troublesome.
+However, given our difficulty in accurately estimating short term nightly rates (see Table X) and the fact that occupancy rates are highly variable for short-term rentals, these variation are not surprising.
+As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
+Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
+
+```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center'}
+
+ ggMultiPlots(explain.plot, one.plot, cols=2)
 
@@
 
-```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4,fig.height=4}
+```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center'}
 
@@
 
-```{r}
+### Occupancy Rates
+
+Occupancy rates are one of the most important compoenent in determining the profitability of short-term rentals.
+Unfortunately, these are also the most difficult factor to estimate or impute.
+Below we plot (left-panel) the percentage of properties for which short-term rental is more profitable versus the occupancy rate.
+We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up until about 75\% occupancy.
+For occupancy rates less than 50\%, long-term rental is more likely to be the better option.
+The decrease in profitabilty after 75\% occupancy is likely due to: 1) small sample sizes in this tail of the data; and 2) that lowering overall nightly rates too low simply to boost occupancy can result in lower overall revenue.
+
+As the distribution of occupancy rates is not uniform, the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+In Figure X, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+By doing so, we see that, in general, properties need to be in the upper 1/3 of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
   rawocc.pplot <- makePrefPlot(abb.revs,
@@
     scale_color_manual(values=sm.col) +
-    theme(legend.position='none')
-
-```
-
-```{r, fig.width=7, fig.height=5}
-
-  rawocc.pplot
-
-```
-
-```{r}
-
-  ggplot(abb.revs, aes(x=occ.rate)) +
+    ggtitle('Tenure Profitability vs \n Occupancy Rate') +
+    theme(legend.position='none',
+          plot.title = element_text(hjust = 0.5)) + 
+    coord_cartesian(ylim=c(0,1)) +
+    geom_hline(aes(yintercept=.5))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+  dens.plot <- ggplot(abb.revs, aes(x=occ.rate)) +
     geom_density(alpha=.3, fill=1) +
@@
     scale_fill_manual(values=sm.col) +
-    scale_x_continuous(breaks=seq(0, 1, by=.5),
-                       labels=c('0%', '50%', '100%')) +
-    ylab('') +
-    xlab('Occupancy Rate') +
+    scale_x_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+
+    ylab('\nFrequency of Occurance') +
+    xlab('\nOccupancy Rate') +
+    ggtitle('Distribution of \n Occupancy Rates') +
     theme(legend.position='none',
+          plot.title = element_text(hjust = 0.5),
           axis.line=element_blank(),
           axis.text.y=element_blank(),
-          axis.ticks=element_blank(),
-          axis.title.y=element_blank())
-```
-
-```{r}
+          axis.ticks.y=element_blank())
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5}
+
+  ggMultiPlots(rawocc.pplot, dens.plot, cols=2)
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
 
@@
     xlab('\nQuantile of Occupancy Rate') +
-    ylab('\n% of Properties where Airbnb is more profitable') +
+    ylab('\n% of Properties where \n Airbnb is more profitable') +
     scale_x_continuous(breaks=seq(0, 100, by=25),
@@
     scale_color_manual(values=sm.col) +
-    theme(legend.position='none')
-
-```
-
-```{r, fig.width=7, fig.height=5}
+    theme(legend.position='none') + 
+    coord_cartesian(ylim=c(0,1))+
+    geom_hline(aes(yintercept=.5))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=3.5, fig.align='center'}
 
@@
 
-```{r, fig.width=7, fig.height=5}
-
- rate.hm
-
-```
-
-```{r, fig.width=7, fig.height=5}
-
-  rate.hm.svm
-
-```
-
-```{r, fig.width=7, fig.height=5}
-
- qtl.hm
-
-```
-
-```{r, fig.width=7, fig.height=5}
-
-  qtl.hm.svm
-
-```
+Along with occupancy rate, the other important consideration is the nightly rate.
+High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
+In Figure X (left panel) we plot nightly rates versus occupancy rates.
+We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
+The transparency is related to the total count of actual market properties falling into that area.
+
+A general trend is what is expected, higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
+This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
+While the left panel of Figure X helps show the general pattern is doe leave many indeterminate areas.
+In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
+
+An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+In this case, we delineate the boundary (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
+In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
+While this process does provide more flexible fit in the area of high data density, it also has the side effect of creating somewhat counter intuitive results in areas of low data (such as the far upper right corner.)  Overall, from the SVM model we see that there short-term prefernce begins at about 30\% occupancy rate, regardless of nightly rate.
+As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+
+ ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
+
+```
+
+Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in figure X may be misleading.
+We convert both axis to quantiles and replot both figures.
+Here we see a more even distibution of points across the figures.
+Additionally, a more reasonable SVM breakdown occurs as well.
+The right panel shows that , in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have is 40\%, if the nightly rate is in the top 95th percentile of the market.
+For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
+```{r, fig.width=8, fig.height=4, echo=FALSE}
+
+ ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
+
+```
+
+Finally, we summarize the entire market by looking at three metrics:
+
+1. Actual: The percentage of properties in the market in which Airbnb generates more revenue
+2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable
+3. SVM Area: The percentage of the total area in the SVM plot that represents a situation where the short-term rental is more profitable.
+
+None of these metrics on their own is perfect.
+The 'actual' measure responds directly to the sample of the current market and may not be as useful to a potential investor.
+The 'fitted' and 'svm' metric minimize some bias from the sample, but suffer from forcing all observations into a binary condition (there are no 'gray' areas) and the 'svm area' metric may be biases by large areas of the scatterplot that have few actual observations.
+This latter issue is partially limited by plotting by quantile, but, nonetheless still exists.
+
+We calculate each for the raw rates as well as for the quantile situation.
+These are show in Table X.
+Overall, 31.4\% of the observed Airbnb properties raised more actual revenue from short term lending than the estimated long-term revenue that they would have gained.
+Analyzing these by raw rates in the SVM, we find that a nearly identical 31.4\% fall within the contiguous area of short-term preference and this area takes up 40.6% of the total plotted area.
+When scale the plots by quantile, we find that 37.2\% of all observations fall in the short-term preference area and that this area takes up 37.8\% of the total plotted area.
+As the difference between the fitted and the svm area is considerably smaller in the quantile approach, there is less bias from outlying, empty areas.
 
@@
 
-### Flexible Geo Analysis
-
-### Logit Models (maybe?)
-
-### Reference to Shiny App
-
-## Future Research
-
-- Does time of purchase (which month) matter?
+A major deficit in this analysis is that the potential rents, rates, days on market and occupancy rates are estimated globally.
+As a result, there is the likelihood of significant bias within certain submarkets.
+Below, we break down the results by type (apartment vs house), by geographic market (5 submarketd listed above) and by type and submarket.
+We show only the summary tables and the quantile heat map plots.
+Full results can be found on the ....ENTER SHINY WEBSITE....
+
+#### Property Type
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+
+ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2)
+
+```
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+
+ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2)
+
+```
+
+```{r, results="asis", echo=FALSE}
+
+ type.table <- rbind(apt$mrkt.score, house$mrkt.score)
+ type.table$property.type <- c('apartment', '', 'house', '')
+ type.table <- type.table[,c(5,1:4)]
+ print(xtable(type.table,
+       digits=3),
+       include.rownames=FALSE, hline.after=c(-1,0,2,4))
+
+```
+
+#### Geographic Submarkets
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+
+names(sm.results)[[1]] <- 'core'
+
+ggMultiPlots(sm.results$core$qtl.hm.svm,
+             sm.results$city$qtl.hm.svm, cols=2)
+```
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+
+ggMultiPlots(sm.results$suburban$qtl.hm.svm, 
+             sm.results$rural$qtl.hm.svm, cols=2)
+
+```
+
+```{r, fig.width=4, fig.height=4, echo=FALSE, fig.align='center'}
+
+             sm.results$beach$qtl.hm.svm
+
+```
+
+```{r, results="asis", echo=FALSE}
+
+ sm.table <- rbind(sm.results$core$mrkt.score, 
+                     sm.results$city$mrkt.score, 
+                     sm.results$suburban$mrkt.score, 
+                     sm.results$rural$mrkt.score, 
+                     sm.results$beach$mrkt.score)
+
+ sm.table$sub.market <- c('core', '', 'city', '', 'suburban', ''
+                            , 'rural', '', 'beach', '')
+ sm.table <- sm.table[,c(5,1:4)]
+ print(xtable(sm.table,
+       digits=3),
+       include.rownames=FALSE, hline.after=c(-1,0,2,4,6,8,10))
+
+```
+
+<!-- ### Submarkets -->
+
+<!-- ### Flexible Geo Analysis -->
+
+<!-- ### Logit Models (maybe?) -->
+
+<!-- ### Reference to Shiny App -->
+
+<!-- ## Future Research -->
+
+<!-- - Does time of purchase (which month) matter? -->

### 2017-01-09 abbReturns_Writeup.Rmd
Lit rev, rewrite beg, turn off analysis

--- 2017-01-05 abbReturns_Writeup.Rmd
@@
 ---
-title: "Should I AirBNB My Property?"
+title: "Should I Airbnb My Property?"
 author: "Andy Krause and Gideon Aschwanden"
-date: "December 17, 2016"
+date: "January 9, 2017"
 output:
@@
   html_document: default
+geometry: margin=3.4cm
+bibliography: abb.bib
 ---
@@
 
-```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}
 
@@
 
-## Intro
-
-With the rise of Airbnb and other self-hosting accommodation platforms, property owners and investors may consider short-term rental as a potential use for a home.
-The question to be asked then is, in which circumstances would leasing in a short-term manner produce greater returns than a traditional long-term rental?
-This work presents an examination of market transactions of both short and long-term rental aimed at answering this question.
-
-To do so, we use long-term rental data and nightly Airbnb listing information from the Melbourne (Australia) metropolitan area.
-Melbourne has a thriving Airbnb market with over 17,000 total properties listed on the portal.
-The Airbnb data does not include exact addresses and therefore no direct matches between the datasets can be made.
-As a result, we impute likely short and long-term rental rates and occupancies.
-Comparisons of actual to estimated returns are made to determine the situation in which a short term rental, such as Airbnb, is more profitable.
-
+&nbsp;
+&nbsp;
+
+## Introduction
+
+With the rise of Airbnb and other self-hosting accommodation platforms^[Flipkey.com, VRBO.com, Homeaway.com, Tripping.com as examples.], it is easier than ever for property owners and investors to consider short-term rental (STR) as a potential use for a revenue generating residential property.
+Should they though?
+And which types of properties and in which locations would short-term leasing produce greater revenue than a traditional long-term rental (LTR), if any?
+
+To address these questions and provide some guidance to potential and current investors and owners, we use long-term rental data and nightly Airbnb listing information from the Melbourne (Australia) metropolitan area.
+Melbourne has a thriving Airbnb market with over 20,000 total properties listed on the portal.
+We adopt a scenario-based approach in which we compare potential annual revenues for properties under both a short-term rental (STR) and a long-term rental (LTR) situation.
 Additionally, we break the results down by property types (apartment vs house), product type (ex.
@@
 Our results shows that the feasibility of a greater return through a short term rental is dependent on property type, product and location.
-In answer to our question: it depends.
-
-## Lit Review
+In answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
+
+## Literature Review
+
+Existing research into short-term rental markets is sparse.
+However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields outside of real estate as evidenced by a growth in recent publications and on-going working papers.
+
+Much of the existing work focuses on price or rent formation in second home markets.
+Specifically, the impacts of amenties such as water access [@nelson2010valuing], water quality [@gibbs2002hedonic; @clapper2014water] and proximity to ski facilities  [@soguel2008impact; @nelson2010valuing] and theme parks [@tsai2015impact] are shown to positively impact sales prices in tourism-dominated areas.
+@benjamin2001value note that leasing policies, in this case smoking prohibitions, can also influence the weekly rental rates for vacation homes.
+@nilsson2015influence makes a key distinction, finding that rural vacation home markets value amenties whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
+
+Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast, the STR industry lacks sophistication and efficiency.
+Most notably, they find that most nightly or weekly rates are set by resident unit managers (RUMs) and are often under-priced as there is little accountability toward owners.
+The authors also note that very little research has been put toward understanding this growing market segment.
+
+A set of recent work has looked into the impact of short-term markets on housing prices and affordability.
+These working papers examine the influence of Airbnb on existing housing prices in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2016home].
+Though very broad analyses, all suggest that Airbnb has had a positive impact on local home prices and/or a negative impact on affordability.
+Other work examines the impact of short term rentals on the hotel market, with @gutierrez2016airbnb finding that Airbnb and hotels have similar location patterns in Barcelona and @zervas2014rise showing an inverse relationship between Airbnb listings and hotel revenues.
+
+A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short term rentals).
+Or, in other words, the factors that influence prices and rents in the two are not equivalent.
+@cho2003impacts find that the second home market is more sensitive to proximity to environmental amenities than the owner occupied market.
+In Switzerland, @soguel2008impact test to see if second homes pay a higher premium for ski resort access.
+Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.
+
+Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments.
+With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.
+As a result, the short-term rental market has garnered significant interest in the public policy and legal sphere as of late.
+As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on neighbors in the way of externalies such as noise and congestion [@frost2006commentary].
+While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].
+Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].
+Many of the key legal decisions regarding short term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
+
+Overall, the extant literature on short-term rentals is limited, but growing.
+Of the three types of research -- pricing, impacts on housing market and legalities/externalities -- none specifically address the decision faced by an owner who is trying to decide between a long- or short-term leasing strategy.
+The closest analog in the literature is a piece by @larsen2009purchase examining the choice between purchasing a time-share or simply paying for hotel rooms.
+Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
+We hypothesize that this same thinking can be extended to the difference between short-term occupants (tourists) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term tenure.
 
@@
 
-### Scenario
-
-We approach answering the question of Airbnb-ing or not by examining a scenario likely to be faced by a recent purchaser of a property.  More specifically, we examine the following case:
+We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+More specifically, we examine the following case:
 
 * An investor purchases a property in Melbourne on Sept 1, 2015.
-* They are looking to maximize the revenue over the 12 month period from Sept 1 2015 to August 31 2016.
+* They are looking to maximize the revenue over the 12-month period from September 1, 2015 to August 31, 2016.
 * The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental.
-* Only direct monetary costs are considered, others such as liquidity and inconvience are not considered.
-
-We will not, a priori, specify a location or property type as we hypothesize that the feasibility of a short term rental will vary by these characteristics.
-Australia has a tax policy, Negative Gearing, that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties.
-However, as this policy requires knowledge of the investor's personal income level, we will not be considering this policy in our analysis here.
+* Only direct monetary revenues and costs are considered, others such as liquidity and inconvience are not considered.
+
+We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
+Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.
+However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
 
 One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
-As the future trends are unknown at the time of purchase and the decision of long vs short term rental, we make our comparisons using a fixed nightly short term rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
-Both long and short term rates and occupancy structures will be baesd on the market conditions as of this date.
-
-### Equation
-
-In this above scenario we compare the 12-month returns from the a long term rental with those of a short term rental.
+As future market trends are unknown at the time of purchase and the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
+Both long- term rents and short-term rates and occupancy structures will be baesd on the market conditions as of this date.
+
+We do not directly observe properties that are utilized in both a short and long term leasing strategy.
+Therefore, comparisons are done based on estimated or imputed revenues.
+Most specifically, we will estimate short-term revenue for observations of long-term rentals (LTRs) and long-term revenue for observations of short-term rentals (STRs).
+A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
+
+### Comparison
+
+In this above scenario we compare the 12-month revenues from the a long-term rental with those of a short-term rental.
 We define returns here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
 
-$$ R_{LT} = Rev_{LT} - C_{LT} $$
-$$ R_{ST} = Rev_{ST} - C_{ST} $$
-
-$$ Rev_{LT} = Rent_{M} * (12 - C_{S}) $$  
-where $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
-
-$$ Rev_{ST} = Rate_{N} * O_{Total} $$
-
-where $O_{Total}$ are the total number of occupancies over the 12-month period.
-
-$$ C_{LT} = T + M $$
-
-where
-
-where $T$ are tax related expenses and $M$ are general maintenance expenses.
-
-$$ C_{ST} = T + M + J $$
-
-where $T$ are tax related expenses, $M$ are general maintenance expenses and $J$ are janitorial expenses incurred after each short term tenancy.
-
-We assume for the sake of this scenario that the tax $T$ and general maintenance $M$ expenses are identical between tenure options and therefore cancel out.
-With the analysis that follows we will consider short term rental to be prefable to long-term if the following inequality holds:
-
-$$ Rate_{N} * O_{Total} - J > Rent_{M} * (12 - C_{S}) $$
+\begin{equation}
+Rev_{LT} = RevG_{LT} - C_{LT}
+\end{equation}
+
+\begin{equation}
+Rev_{ST} = RevG_{ST} - C_{ST}
+\end{equation}
+
+Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the costs associated with long-term rental. The gross long-term revenue is expressed by:
+
+\begin{equation}
+RevG_{LT} = Rent_{M} * (12 - C_{S})
+\end{equation}
+
+where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+
+The short-term revenue is expresse by:
+
+\begin{equation}
+RevG_{ST} = Rate_{N} * O_{Total}
+\end{equation}
+
+where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period.
+
+We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
+Broadly speaking, these fall into three categories for long-term rental and four categories for short-term properties.
+Long-term costs are summarized as:
+
+\begin{equation}
+C_{LT} = T + M + F
+\end{equation}
+
+where $T$ are tax related expenses, $M$ are general maintenance expenses and $F$ are finaning costs.
+Short-term properies experience the same three costs ($T$, $M$ and $F$) plus additional janitorial costs between each of the short-term occupants.
+
+\begin{equation}
+C_{ST} = T + M + F + J
+\end{equation}
+
+As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
+General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
+Long-term renters spend more time in the property over the course of the year and bring their own appliance and furniture which may damage the home.
+They are also more likely to affix items to the structure.
+Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.].
+Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short or long term rentals.
+As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
+
+Finally, we have janitorial costs $J$.
+These cover the costs to 'turn-over' the property between occupants.
+For a short-term leasing strategy, these costs can be experiences every day or two, depending on the minimum length of stay and the total number of occupancies over the course of the year.
+Our data for short-term rentals comes from the Airbnb platform.
+In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.
+Some hosts add additional 'linen' fees to cover costs of laundering.
+While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
+As a result of janitorial fees being a separate line item and directly paid by the occupants can also be ignored in the comparative analysis below as they are direct.
+
+Given that the costs cancel out between the two options, we will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
+
+\begin{equation}
+RevG_{ST} > RevG_{LT} 
+\end{equation}
+
+More specifically, if:
+
+\begin{equation}
+Rate_{N} * O_{Total} > Rent_{M} * (12 - C_{S})
+\end{equation}
 
@@
 
-Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
+<!-- Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
 The Airbnb online portal is used as evidence of the short-term rental market.
@@
 This data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
-
-The Airbnb data cover the Melbourne metropolitan region from October 1st 2014 to August 30th 2016.
+-->
+
+<!-- The Airbnb data cover the Melbourne metropolitan region from October 1st 2014 to August 30th 2016.
 There are missing nightly observations during the time period before September 1 2015.
@@
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
-
-The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
+-->
+
+<!-- The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 This data also includes an observation for each rental property each time a detail of the listing changed.
@@
 The long-term lease data covers the period from January 2014 to December 2015.
-
-Unfortunately, there are no common identifiers between the two dataset as the Airbnb data does not include address.
+-->
+
+<!-- Unfortunately, there are no common identifiers between the two dataset as the Airbnb data does not include address.
 Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
@@
 However, the number of properties that rented long term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
-
-```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
-  exch.rate <- 1.32
-
-```
-
-### Preparation
-
-In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
+-->
+
+<!-- ```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'} -->
+
+<!--   exch.rate <- 1.32   -->
+
+<!-- ``` -->
+
+<!-- ### Preparation -->
+
+<!-- In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
 Primarily, this involves the filtering out of data errors and/or outlier values.
 However, as our data are from two different sources, number of fields also require standardization so that comparisons between the two tenure options can be made.
-
-We begin by filtering observations by time.
+-->
+
+<!-- We begin by filtering observations by time.
 Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
@@
 In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
-
-Next, we examine property types.
+-->
+
+<!-- Next, we examine property types.
 AirBNB units are classified into 19 different property types.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types:
-
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
-3.
+For the sake of this analysis, we will collapse these twenty types into three types: -->
+
+<!-- 1. **House**:  Includes properties labeled 'House' or 'Townhouse' -->
+<!-- 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium' -->
+<!-- 3.
 **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
-
-Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
-
-1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
-
-Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
+-->
+
+<!-- Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories: -->
+
+<!-- 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse' -->
+<!-- 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio' -->
+<!-- 3. **Other**: Includes properties labeled as 'Semi' and 'Villa' -->
+
+<!-- Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
 This is most apparent when talking about apartment dwellings.
@@
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
-
-As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
+-->
+
+Berry 2000 about unique australia market
+
+<!-- As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
 Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
 As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
-
-```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}  
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
-  abb.data <- before.PT$abb.data
-  ltr.data <- before.PT$ltr.data
-  daily.data <- before.PT$daily.data
-
-```
-
-```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type'}
-
-  # Create Airbnb plot
-
-  abb.types <- ggplot(abb.data, aes(x=type)) + 
-    geom_bar(color=str.col, fill=str.col) +
-    xlab('') + 
-    ylab('# of Properties\n') +
-    labs(title = "Short Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Create long term rental plot
-
-  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
-    geom_bar(color=ltr.col, fill=ltr.col) +
-    xlab('') + 
-    ylab('# of Properties\n') +
-    labs(title = "Long Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Output plots
-
-  ggMultiPlots(abb.types, ltr.types, cols=2)
-
-```
-
-```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  abb.data <- subset(abb.data, type != 'Other')
-  ltr.data <- subset(ltr.data, type != 'Other')
-
-```
-
-Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
-
-1. **Entire Home/Apt**: The entire home or apartment is available
-2. **Private Room**: One room within a house or apartment is available
-3. **Shared Room**: A bed within a room shared by another occupant(s) is available
-
-As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returns, we remove all short term properties that do not lease the entire home/apt.
+-->
+
+<!-- ```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}   -->
+<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
+<!--   load(paste0(data.path, '/analyzed/abb_beforePT.RData')) -->
+<!--   abb.data <- before.PT$abb.data -->
+<!--   ltr.data <- before.PT$ltr.data -->
+<!--   daily.data <- before.PT$daily.data -->
+
+<!-- ```  -->
+
+<!-- ```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type'} -->
+
+<!--   # Create Airbnb plot -->
+
+<!--   abb.types <- ggplot(abb.data, aes(x=type)) +  -->
+<!--     geom_bar(color=str.col, fill=str.col) + -->
+<!--     xlab('') +  -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Short Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Create long term rental plot -->
+
+<!--   ltr.types <- ggplot(ltr.data, aes(x=type)) +  -->
+<!--     geom_bar(color=ltr.col, fill=ltr.col) + -->
+<!--     xlab('') +  -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Long Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Output plots -->
+
+<!--   ggMultiPlots(abb.types, ltr.types, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   abb.data <- subset(abb.data, type != 'Other') -->
+<!--   ltr.data <- subset(ltr.data, type != 'Other') -->
+
+<!-- ``` -->
+
+<!-- Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked: -->
+
+<!-- 1. **Entire Home/Apt**: The entire home or apartment is available -->
+<!-- 2. **Private Room**: One room within a house or apartment is available -->
+<!-- 3. **Shared Room**: A bed within a room shared by another occupant(s) is available -->
+
+<!-- As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returns, we remove all short term properties that do not lease the entire home/apt.
 Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
-
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap='Listing Type of Short Term Rentals'}
-
-  # Fix data types and names
-
-  abb.data$listing.type <- as.character(abb.data$listing.type)
-  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'
-
-  # Make Plot
-
-  ggplot(abb.data, aes(x=listing.type)) + 
-    geom_bar(color=abb.col[1], fill=abb.col[1]) +
-    xlab('') + 
-    ylab('# of Properties\n') +
-    labs(title = "Short Term Rentals by Listing Type\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
-  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
-
-```
-
-#### Structural Characteristics
-
-We now turn to filtering by structural characteristics.
+-->
+
+<!-- ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap='Listing Type of Short Term Rentals'} -->
+
+<!--   # Fix data types and names -->
+
+<!--   abb.data$listing.type <- as.character(abb.data$listing.type) -->
+<!--   abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home' -->
+
+<!--   # Make Plot -->
+
+<!--   ggplot(abb.data, aes(x=listing.type)) +  -->
+<!--     geom_bar(color=abb.col[1], fill=abb.col[1]) + -->
+<!--     xlab('') +  -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Short Term Rentals by Listing Type\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   abb.room <- abb.data[abb.data$listing.type != 'Entire home', ] -->
+<!--   abb.data <- abb.data[abb.data$listing.type == 'Entire home', ] -->
+
+<!-- ``` -->
+
+<!-- #### Structural Characteristics -->
+
+<!-- We now turn to filtering by structural characteristics.
 As the Airbnb data provides limited information on the structural characteristics, the only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
 Additionally, as the markets and structural components of houses and apartment differ, we bifurcate our analysis between the two property types from this point forward.
-
-We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
+-->
+
+<!-- We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
 For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
@@
 We convert the 0 bed short term units to 1 bed units.
-
-```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove missing and data errors
-
-  # Long term data
-  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
-  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
-
-  # Short term data
-  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
-  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
-
-```
-
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'}
-
- # Build long term bar plot
-
-   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:10, breaks=1:10)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bedrooms in Long Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Build short term bar plot
-
-  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:10, breaks=0:10)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bedrooms in Short Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Make the comparison plot
-
-  ggMultiPlots(abbbed, ltrbed, cols=1)
-
-```
-
-```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove all with more than 4 beds
-
-  abb.data <- abb.data[abb.data$bedrooms < 5, ]
-  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
-
- # Remove apartments with more than 3
-
-  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
-  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
-
-  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
-  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
-
-  # Convert 0 Bed to 1 Bed  
-  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
-
-```
-
-We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
+-->
+
+<!-- ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove missing and data errors -->
+
+<!--   # Long term data -->
+<!--   ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ] -->
+<!--   ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ] -->
+
+<!--   # Short term data -->
+<!--   abb.data <- abb.data[!is.na(abb.data$bedrooms), ] -->
+<!--   abb.data <- abb.data[abb.data$bedrooms <= 10, ] -->
+
+<!-- ``` -->
+
+<!-- ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'} -->
+
+<!--  # Build long term bar plot -->
+
+<!--    ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) +  -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=1:10, breaks=1:10)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bedrooms in Long Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Build short term bar plot -->
+
+<!--   abbbed <- ggplot(abb.data, aes(x=bedrooms)) +  -->
+<!--     geom_bar(fill=str.col, color=str.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=0:10, breaks=0:10)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bedrooms in Short Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Make the comparison plot   -->
+
+<!--   ggMultiPlots(abbbed, ltrbed, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove all with more than 4 beds -->
+
+<!--   abb.data <- abb.data[abb.data$bedrooms < 5, ] -->
+<!--   ltr.data <- ltr.data[ltr.data$bedrooms < 5, ] -->
+
+<!--  # Remove apartments with more than 3 -->
+
+<!--   abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment') -->
+<!--   ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment') -->
+
+<!--   if(length(abba) > 0) abb.data <- abb.data[-abba, ] -->
+<!--   if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ] -->
+
+<!--   # Convert 0 Bed to 1 Bed   -->
+<!--   abb.data$bedrooms[abb.data$bedrooms == 0] <- 1 -->
+
+<!-- ``` -->
+
+<!-- We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
 Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
@@
 We round the baths in the short term data up to whole integers.
-
-```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove missing data
-
-  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
-  abb.data <- abb.data[!is.na(abb.data$baths), ]
-
-```
-
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'}
-
- # Build long term plot
-
-  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:8, breaks=1:8)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bathrooms in Long Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Build short term plot
-
-  stbath <- ggplot(abb.data, aes(x=baths)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:8, breaks=0:8)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bathrooms in Short Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Make Plots
-
-  ggMultiPlots(stbath, ltbath, cols=1)
-
-```
-
-```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Filter by bath count
-
-  # Short term data
-  abb.data <- abb.data[abb.data$baths < 4, ]
-  abb.data <- abb.data[abb.data$baths > 0, ]
-
-  # Long term data
-  ltr.data <- ltr.data[ltr.data$baths < 4, ]
-
- # Round baths up
-
-  abb.data$baths <- round(abb.data$baths + .01, 0)
-
-```
-
-In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+-->
+
+<!-- ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove missing data -->
+
+<!--   ltr.data <- ltr.data[!is.na(ltr.data$baths), ] -->
+<!--   abb.data <- abb.data[!is.na(abb.data$baths), ] -->
+
+<!-- ``` -->
+
+<!-- ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'} -->
+
+<!--  # Build long term plot -->
+
+<!--   ltbath <- ggplot(ltr.data, aes(x=baths)) +  -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=1:8, breaks=1:8)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bathrooms in Long Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Build short term plot  -->
+
+<!--   stbath <- ggplot(abb.data, aes(x=baths)) +  -->
+<!--     geom_bar(fill=str.col, color=str.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=0:8, breaks=0:8)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bathrooms in Short Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Make Plots   -->
+
+<!--   ggMultiPlots(stbath, ltbath, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Filter by bath count -->
+
+<!--   # Short term data -->
+<!--   abb.data <- abb.data[abb.data$baths < 4, ] -->
+<!--   abb.data <- abb.data[abb.data$baths > 0, ] -->
+
+<!--   # Long term data -->
+<!--   ltr.data <- ltr.data[ltr.data$baths < 4, ] -->
+
+<!--  # Round baths up   -->
+
+<!--   abb.data$baths <- round(abb.data$baths + .01, 0) -->
+
+<!-- ``` -->
+
+<!-- In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
 In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
 As a result we examine the combinations of the two.
-
-```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Create combination variable
-
-  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
-  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
-
-```
-
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}
-
- # Make long term plot
-
-  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bed/Bath Combo in Long Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
-    facet_wrap(~type)
-
- # Make short term plots
-
-  stb <- ggplot(abb.data, aes(x=bedbath)) +
-    geom_bar(fill=str.col, color=str.col) + 
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bed/Bath Combo in Short Term Rentals\n") + 
-    theme(plot.title = element_text(hjust = 0.5)) + 
-    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
-    facet_wrap(~type)
-
- # Plot
-
-  ggMultiPlots(ltb, stb, cols=1)
-
-```
-
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
-
-```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Set level of acceptable combinations
-
-  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
-
- # Filter data
-
-  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
-  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
-
-```
-
-### Rates and Rental values
-
-We now turn to filtering by the prices -- the nightly rates and weekly rental values.
+-->
+
+<!-- ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Create combination variable -->
+
+<!--   ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths) -->
+<!--   abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths) -->
+
+<!-- ``` -->
+
+<!-- ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'} -->
+
+<!--  # Make long term plot -->
+
+<!--   ltb <- ggplot(ltr.data, aes(x=bedbath)) +  -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bed/Bath Combo in Long Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
+<!--     facet_wrap(~type) -->
+
+<!--  # Make short term plots -->
+
+<!--   stb <- ggplot(abb.data, aes(x=bedbath)) + -->
+<!--     geom_bar(fill=str.col, color=str.col) +  -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bed/Bath Combo in Short Term Rentals\n") +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) +  -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
+<!--     facet_wrap(~type) -->
+
+<!--  # Plot   -->
+
+<!--   ggMultiPlots(ltb, stb, cols=1) -->
+
+<!-- ``` -->
+
+<!-- From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.   -->
+
+<!-- ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Set level of acceptable combinations -->
+
+<!--   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2') -->
+
+<!--  # Filter data -->
+
+<!--   ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ] -->
+<!--   abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ] -->
+
+<!-- ``` -->
+
+<!-- ### Rates and Rental values -->
+
+<!-- We now turn to filtering by the prices -- the nightly rates and weekly rental values.
 The long term rental data have a single price observation, the asking rent each time an change in the listing occurs, including the price at closing.
@@
 To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1 2015 to August 31, 2016 period.
-
-We start by removing property level observations missing price data.
+-->
+
+<!-- We start by removing property level observations missing price data.
 Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
@@
 We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.
-
-```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
-  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
-
-```
-
-```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Property level data
-
-  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
-  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
-  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
-  abb.data$monthly.rate <- abb.data$monthly * exch.rate
-
-  # Daily data
-
-  daily.data$price <- daily.data$price * exch.rate
-
-```
-
-```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  # ltr Plot
-
-  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
-    geom_density(fill=ltr.col, alpha=.8) +
-    ylab('Frequency') +
-    xlab('Weekly Rental') + 
-    ggtitle('Long Term Rentals') + 
-    scale_x_continuous(limits=c(0, 1500)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(), 
-          plot.title = element_text(hjust = 0.5))
-
-  # Nightly Rate plot
-  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
-    geom_density(fill=str.col, alpha=.8) + 
-    ylab('Frequency') +
-    xlab('Nightly Rate') +
-    ggtitle('Short Term Rentals') + 
-    scale_x_continuous(limits=c(0, 600)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(), 
-          plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'}
-
-  ggMultiPlots(ltr.plot, rate.plot, cols=2)
-
-```
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- ## Filter the long term data
-
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
-
- ## Filter the short term data
-
-  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
-                         abb.data$nightly.rate <= 500, ]
-
-```
-
-### Location and Submarkets
-
-Location is clearly an important determinant in both the short and long term rental markets.
+-->
+
+<!-- ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   ltr.data <- ltr.data[!is.na(ltr.data$event.price), ] -->
+<!--   abb.data <- abb.data[!is.na(abb.data$nightly.rate), ] -->
+
+<!-- ``` -->
+
+<!-- ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Property level data -->
+
+<!--   abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate -->
+<!--   abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate -->
+<!--   abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate -->
+<!--   abb.data$monthly.rate <- abb.data$monthly * exch.rate -->
+
+<!--   # Daily data -->
+
+<!--   daily.data$price <- daily.data$price * exch.rate -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   # ltr Plot -->
+
+<!--   ltr.plot <- ggplot(ltr.data, aes(x=event.price)) +  -->
+<!--     geom_density(fill=ltr.col, alpha=.8) + -->
+<!--     ylab('Frequency') + -->
+<!--     xlab('Weekly Rental') +  -->
+<!--     ggtitle('Long Term Rentals') +  -->
+<!--     scale_x_continuous(limits=c(0, 1500)) + -->
+<!--     theme(axis.title.y=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Nightly Rate plot -->
+<!--   rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) +  -->
+<!--     geom_density(fill=str.col, alpha=.8) +  -->
+<!--     ylab('Frequency') + -->
+<!--     xlab('Nightly Rate') + -->
+<!--     ggtitle('Short Term Rentals') +  -->
+<!--     scale_x_continuous(limits=c(0, 600)) + -->
+<!--     theme(axis.title.y=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'} -->
+
+<!--   ggMultiPlots(ltr.plot, rate.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  ## Filter the long term data -->
+
+<!--   ltr.data <- ltr.data[ltr.data$event.price >= 200 &  -->
+<!--                          ltr.data$event.price <= 1000, ] -->
+
+<!--  ## Filter the short term data -->
+
+<!--   abb.data <- abb.data[abb.data$nightly.rate >= 50 & -->
+<!--                          abb.data$nightly.rate <= 500, ] -->
+
+<!-- ``` -->
+
+<!-- ### Location and Submarkets -->
+
+<!-- Location is clearly an important determinant in both the short and long term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 The plot below shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Build the map object
-
-  # Set colors
-  g.cols <- abb.col[c(2, 10, 9)]
-
-  # Make map
-  loc.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-    scale_fill_manual(values=c('gray10', 'gray40', 'gray70'),
-                      labels=c('Inner      ',
-                               'Middle      ',
-                               'Outer')) +
-    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(), 
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    ggtitle("Melbourne Suburb Classifications")
-
-```
-
-```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'}
-
-  loc.map
-
-```
-
-```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}  
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
-  abb.data <- after.SP$abb.data
-  ltr.data <- after.SP$ltr.data
-  daily.data <- after.SP$daily.data
-```
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+-->
+
+<!-- ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Build the map object -->
+
+<!--   # Set colors -->
+<!--   g.cols <- abb.col[c(2, 10, 9)] -->
+
+<!--   # Make map -->
+<!--   loc.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) +  -->
+<!--     scale_fill_manual(values=c('gray10', 'gray40', 'gray70'), -->
+<!--                       labels=c('Inner      ', -->
+<!--                                'Middle      ', -->
+<!--                                'Outer')) + -->
+<!--     geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     xlab('') + ylab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(),  -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     ggtitle("Melbourne Suburb Classifications") -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'} -->
+
+<!--   loc.map   -->
+
+<!-- ``` -->
+
+<!-- ```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}   -->
+<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
+<!--   load(paste0(data.path, '/analyzed/abb_afterSP.RData')) -->
+<!--   abb.data <- after.SP$abb.data -->
+<!--   ltr.data <- after.SP$ltr.data -->
+<!--   daily.data <- after.SP$daily.data -->
+<!-- ```  -->
+
+<!-- It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melbourne:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We select the 18 suburbs below to represent the 'core' of the city.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melbourne: -->
+
+<!-- 1. Rural (Outer suburbs, not Beach) -->
+<!-- 2. Suburban (Middle suburbs, not Beach) -->
+<!-- 3. City (Inner Suburbs, not Beach, not Core) -->
+<!-- 4. City-Core (Select inner suburbs with tourist activities and near CBD) -->
+<!-- 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River) -->
+
+<!-- We select the 18 suburbs below to represent the 'core' of the city.
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
 All are well serviced by public transportation and possess abundant amenties for tourists.
-
-```{r, results="asis", echo=FALSE}
-
- core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
-                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
-                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
-                   'St Kilda West', 'West Melbourne', 'Windsor')
-
- c.subs <- data.frame(A=core.suburbs[1:6],
-                      B=core.suburbs[7:12],
-                      C=core.suburbs[13:18])
- names(c.subs) <- NULL
- rownames(c.subs) <- NULL
-
- print(xtable(c.subs, caption = 'List of Core Suburbs'),
-       include.rownames=F,
-       caption.placement="top",
-       hline.after=c(0,6))
-
-```
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!--  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands', -->
+<!--                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran', -->
+<!--                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda', -->
+<!--                    'St Kilda West', 'West Melbourne', 'Windsor') -->
+
+<!--  c.subs <- data.frame(A=core.suburbs[1:6], -->
+<!--                       B=core.suburbs[7:12], -->
+<!--                       C=core.suburbs[13:18]) -->
+<!--  names(c.subs) <- NULL -->
+<!--  rownames(c.subs) <- NULL -->
+
+<!--  print(xtable(c.subs, caption = 'List of Core Suburbs'), -->
+<!--        include.rownames=F, -->
+<!--        caption.placement="top", -->
+<!--        hline.after=c(0,6)) -->
+
+<!-- ``` -->
+
+<!-- We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short and long term data.
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short and long term rentals, colored by submarket, are shown below
-
-Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+The location of the short and long term rentals, colored by submarket, are shown below -->
+
+<!-- Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
 Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
@@
 After making this correction we then assign one of the five submarket designations based on the process described above.
-
-```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Set submarket colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
-  # Make map
-
-  abb.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
-               alpha=.2) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(), 
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) + 
-    ggtitle('AirBNB Location\nBy Submarket')
-
-```
-
-```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Make map
-
-  ltr.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
-               alpha=.1) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-   theme(legend.position = 'bottom',
-          legend.title = element_blank(), 
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) + 
-    ggtitle('Long Term Rental Location\nBy Submarket')
-
-```
-
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9}
-
-  ggMultiPlots(abb.map, ltr.map, cols=1)
-
-```
-
-To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+-->
+
+<!-- ```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Set submarket colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)] -->
+
+<!--   # Make map -->
+
+<!--   abb.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
+<!--     geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2, -->
+<!--                alpha=.2) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(),  -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
+<!--                                                      alpha=1))) +  -->
+<!--     ggtitle('AirBNB Location\nBy Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Make map -->
+
+<!--   ltr.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
+<!--     geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1, -->
+<!--                alpha=.1) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     xlab('') + ylab('')+ -->
+<!--    theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(),  -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
+<!--                                                      alpha=1))) +  -->
+<!--     ggtitle('Long Term Rental Location\nBy Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9} -->
+
+<!--   ggMultiPlots(abb.map, ltr.map, cols=1) -->
+
+<!-- ``` -->
+
+<!-- To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
 A number of interesting observations are illustrated here.
@@
 Overall, the suburban and rural Airbnb market are quite thin, later results focusing on these market will need to be examined in light of this small sample size.
-
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
-
-  # Make Airbnb submarket map
-
-  abbtype.map <- ggplot() +
-    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          plot.title = element_text(hjust = 0.5)) +
-    ggtitle('AirBNB Property Type By Submarket')
-
-  # Make Long term rental map
-
-  ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          plot.title = element_text(hjust = 0.5)) +
-    ggtitle('Long Term Property Type By Submarket')
-
-```
-
-```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
-
-  abbtype.map
-
-```
-
-```{r ltrtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
-
-  ltrtype.map
-
-```
-
-### Actual Revenue
-
-Our final data filtering considers the observed revenue of the properties.
+-->
+
+<!-- ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9} -->
+
+<!--   # Make Airbnb submarket map -->
+
+<!--   abbtype.map <- ggplot() + -->
+<!--     geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     ylab('# of Properties\n') + xlab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           axis.text.x=element_blank(), -->
+<!--           axis.ticks.x=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) + -->
+<!--     ggtitle('AirBNB Property Type By Submarket') -->
+
+<!--   # Make Long term rental map -->
+
+<!--   ltrtype.map <- ggplot() + -->
+<!--     geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     ylab('# of Properties\n') + xlab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           axis.text.x=element_blank(), -->
+<!--           axis.ticks.x=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) + -->
+<!--     ggtitle('Long Term Property Type By Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5} -->
+
+<!--   abbtype.map -->
+
+<!-- ``` -->
+
+<!-- ```{r ltrtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5} -->
+
+<!--   ltrtype.map -->
+
+<!-- ``` -->
+
+<!-- ### Actual Revenue  -->
+
+<!-- Our final data filtering considers the observed revenue of the properties.
 For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
@@
 To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
-
-For the short term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+-->
+
+<!-- For the short term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
 Using this data we sum up the total revenue from bookings.
 For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
-
-Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority randing between \$12,000 to \$30,000 per year.
+-->
+
+<!-- Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority randing between \$12,000 to \$30,000 per year.
 Short term revenue range from neglible to highs of greater than \$80,000.
@@
 Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
-
-```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- load(paste0(data.path, '/analyzed/abb_working.RData'))
-
-```
-
-```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  abbr <- abb.data[,c('bedbath', 'revenue')]
-  abbr$tenure <- 'short-term'
-  ltrr <- ltr.data[,c('bedbath', 'revenue')]
-  ltrr$tenure <- 'long-term'
-  allr <- rbind(abbr, ltrr)
-
-  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) + 
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col)) +
-    ggtitle('Annual Revenues by Tenure Type') + 
-    xlab('Annual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(), 
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
-
-```
-
-### Summary of Data Cleaning
-
-We have applied nine separate filters to our two datasets.
+-->
+
+<!-- ```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}   -->
+
+<!--  load(paste0(data.path, '/analyzed/abb_results.RData'))   -->
+
+<!-- ``` -->
+
+<!-- ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   abbr <- abb.data[,c('bedbath', 'revenue')] -->
+<!--   abbr$tenure <- 'short-term' -->
+<!--   ltrr <- ltr.data[,c('bedbath', 'revenue')] -->
+<!--   ltrr$tenure <- 'long-term' -->
+<!--   allr <- rbind(abbr, ltrr) -->
+
+<!--   ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) +  -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Annual Revenues by Tenure Type') +  -->
+<!--     xlab('Annual Revenue') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
+<!--                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 70000)) -->
+
+<!-- ``` -->
+
+<!-- ### Summary of Data Cleaning -->
+
+<!-- We have applied nine separate filters to our two datasets.
 In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters.
@@
 From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
-
-For the long term data, over half of the observations fall outside of our considered time frame,reducing the sample size down to around 130,000 from 290,000.
+-->
+
+<!-- For the long term data, over half of the observations fall outside of our considered time frame,reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
 remove another 10,000 observations, leaving 122,051 in the final dataset.
-
-```{r, results="asis", echo=FALSE}
-
-cc <- clean.count[,c('operation', 'abb', 'ltr')]
-abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1]))
-ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
-abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1])
-abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)])
-ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
-ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
-clean.table <- data.frame(field=cc$operation,
-                          abbcount=abb.count,
-                          abbcut=abb.cut,
-                          abbper=abb.per,
-                          ltrcount=ltr.count,
-                          ltrcut=ltr.cut,
-                          ltrper=ltr.per)
-
-rownames(clean.table) <- NULL
-clean.table$field <- c('Initial Count', 'Time', 'Property Type',
-                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
-                       'Rates & Rents', 'Location', 'Revenue')
-clean.table$abbper <- 100*round(clean.table$abbper, 2)
-clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
-names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
-                        'Long Term', 'Cut', '% Cut')
-options(xtable.comment = FALSE)
-print(xtable(clean.table,
-       digits=0),
-       include.rownames=FALSE)
-
-```
-
-## Comparison
-
-### Imputing
-
-### Costs
-
--- Assume long term costs are equivalent
-
-### Comparing
-
-## Results
-
--- Start with a global analysis
-
-### What is accurate?
-
-- Discuss why Airbnb Actual is the only relevant one.  
--- Show charts
--- Discuss problems with Rate imputation
--- Discuss problems with Occupancy imputation
-
-#### Comp Tables/Figs
-
-### Heat Maps
-
-### Submarkets
-
-### Flexible Geo Analysis
-
-### Logit Models (maybe?)
-
-### Reference to Shiny App
-
-## Future Research
-
-- Does time of purchase (which month) matter?
+-->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!-- cc <- clean.count[,c('operation', 'abb', 'ltr')] -->
+<!-- abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1])) -->
+<!-- ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1])) -->
+<!-- abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1]) -->
+<!-- abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)]) -->
+<!-- ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1]) -->
+<!-- ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)]) -->
+<!-- clean.table <- data.frame(field=cc$operation, -->
+<!--                           abbcount=abb.count, -->
+<!--                           abbcut=abb.cut, -->
+<!--                           abbper=abb.per, -->
+<!--                           ltrcount=ltr.count, -->
+<!--                           ltrcut=ltr.cut, -->
+<!--                           ltrper=ltr.per) -->
+
+<!-- rownames(clean.table) <- NULL -->
+<!-- clean.table$field <- c('Initial Count', 'Time', 'Property Type', -->
+<!--                        'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo', -->
+<!--                        'Rates & Rents', 'Location', 'Revenue') -->
+<!-- clean.table$abbper <- 100*round(clean.table$abbper, 2) -->
+<!-- clean.table$ltrper <- 100*round(clean.table$ltrper, 2) -->
+<!-- names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut', -->
+<!--                         'Long Term', 'Cut', '% Cut') -->
+<!-- options(xtable.comment = FALSE) -->
+<!-- print(xtable(clean.table, -->
+<!--        digits=0), -->
+<!--        include.rownames=FALSE) -->
+
+<!-- ``` -->
+
+<!-- ## Comparison -->
+
+<!-- Data prepared, we now turn to comparing returns between long and short term rental options.
+As mentioned above, there are no direct matches between the datasets.
+In other words we have not direct observed a property which has been in a long-term rental followed by short-term or vice versa.
+We will, instead, make the comparisons between the two by imputing likely short-term (long-term) rental revenues for the long-term (short-term) data and then comparing the observed revenues to the imputed revenues of the unobserved tenure type.
+-->
+
+<!-- We make our imputations via hedonic price models, one for long-term rentals and one for short-term rentals.
+We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term rental for the short term properties.
+We do the same for the long-term properties using a modeled derived from the short-term data.
+-->
+
+<!-- For the long-term market, we use the following model specification: -->
+
+<!-- \begin{equation}  -->
+<!--   \label{eq:test} -->
+<!-- ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i}  -->
+<!-- \end{equation} -->
+
+<!-- where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+-->
+
+<!-- For the short-term market the specification is similar, minus the time correction.
+We eliminate this control because the short term rates are based on the medium value over the entire period and not monthly.
+This specification is:  -->
+
+<!-- \begin{equation}  -->
+<!-- ln(RentST_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \epsilon_{i}  -->
+<!-- \end{equation} -->
+
+<!-- where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
+-->
+
+<!-- ### Costs -->
+
+<!-- -- Assume long term costs are equivalent -->
+
+<!-- ## Results -->
+
+<!-- We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
+What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
+It is likely that different submarkets operate differently, we will explore this hypothesis after first analyzing the full metropolitan region.
+-->
+
+<!-- We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
+A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel).
+This is likely due to the fact that there are more houses (compared to apartments) in the long-term data than in the short-term data.
+Interestingly, the observed (long-term) and imputed (short term) weekly rental values are somewhat similar, suggesting that the higher rent, city-core apartments push the distribution of the imputed short-term values upwards.
+-->
+
+<!-- For each of the observed values we also create a fitted value for that observation in the model.
+This may help to reduce the influence of outlying observed values in our model.
+To be clear, Each observation will now have three estimates of rates and rents.
+For the short-term properties they will have: 1) an actual nightly rate; 2) an estimated nightly rate; and 3) an estimated long-term (weekly) rent.
+The long-term properties will have: 1) an actual long-term (weekly) rent; 2) an estimated long-term (weekly) rent; and 3) an estimated nightly rate.
+-->
+
+<!-- ```{r pred.glob.imp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   abbir <- abb.imp[,c('bedbath', 'imp.rent', 'med.rate')] -->
+<!--   abbir$tenure.rate <- 'short-term (observed)' -->
+<!--   abbir$tenure.rent <- 'short-term (imputed)' -->
+
+<!--   ltrir <- ltr.imp[,c('bedbath', 'event.price', 'imp.rate')] -->
+<!--   ltrir$tenure.rate <- 'long-term (imputed)' -->
+<!--   ltrir$tenure.rent <- 'long-term (observed)' -->
+
+<!--   names(abbir) <- names(ltrir) <- c('bedbath', 'rent', 'rate', 'tenure.rate', 'tenure.rent') -->
+<!--   allir <- rbind(abbir, ltrir) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rate.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   irate.plot <- ggplot(allir, aes(x=rate, fill=tenure.rate, color=tenure.rate)) +  -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Nightly Rates by Tenure Type') +  -->
+<!--     xlab('Nightly Rate') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,600, by=200)), -->
+<!--                        labels=c('$0', '$200', '$400', '$600'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 625)) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   irent.plot <- ggplot(allir, aes(x=rent, fill=tenure.rent, color=tenure.rent)) +  -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Weekly Rents by Tenure Type') +  -->
+<!--     xlab('Weekly Rents') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,1000, by=200)), -->
+<!--                        labels=c('$0', '$200', '$400', '$600', '$800', '$1,000'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(150, 1000)) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5} -->
+
+<!--  ggMultiPlots(irate.plot, irent.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- The question of whether or not the imputations are accurate remains.
+The table belows shows some simple diagnostics from the two imputation models.
+From this we see that the short-term model performs rather poorly, with a standard error of 34.6\% and over half of the residuals greater than 20\%.
+The long term model, on the other hand, performs quite well, with a standard error under 32\% and less than 19\% of fitted errors greater than 20\%.
+Given the small amount of independent variable available to the models, the long term market appear much more predictable than the short term market.
+This could be due to omitted variables in the short term market or a greater level of variability in the price setting (which is done by individuals) as opposed to the long-term market in which most owners get help with leasing from an agency.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!-- abb.sum <- summary(imp.data$abb.mod) -->
+<!-- ltr.sum <- summary(imp.data$ltr.mod) -->
+
+<!-- abbs <- c(abb.sum$r.squared, abb.sum$adj.r.squared, -->
+<!--           abb.sum$sigma,  -->
+<!--           length(which(abs(abb.sum$residuals) > .2)) / length(abb.sum$residuals)) -->
+<!-- ltrs <- c(ltr.sum$r.squared, ltr.sum$adj.r.squared, -->
+<!--           ltr.sum$sigma,  -->
+<!--           length(which(abs(ltr.sum$residuals) > .2)) / length(ltr.sum$residuals)) -->
+
+<!-- summ.table <- data.frame(shortterm=round(abbs, 3), -->
+<!--                          longterm=round(ltrs, 3)) -->
+<!-- rownames(summ.table) <- c('r-squared', 'adj r-squared', -->
+<!--                           'sigma', '% fit errors > 20%') -->
+<!-- names(summ.table) <- c('Short Term', 'Long Term') -->
+
+<!-- print(xtable(summ.table, -->
+<!--        digits=3), -->
+<!--        include.rownames=TRUE) -->
+
+<!-- ``` -->
+
+<!-- Next, to create an estimated short-term revenue for the long-term properties we have to create an estimate of the occupancy rate.
+For the estimated long-term rentals we have to create an estimate of the search time (days on market).
+To derive an occupancy rate, we use the weighted median value^[Weighted by the total number of days the property was offered on Airbnb over the year.] of the market, the entire metro region in this case, which is about 37%^[We attempted to use a logistic regression model to predict occupancy but were unsucessful to develop an appropriate approach.
+Work continues toward this end.].
+The range of occupancy varies widely from essentially 0 to 100%,with a standard deviation of 27%.
+-->
+
+<!-- For the long term search time, or days on market, we also use the median value of the observations.
+The median days on market is 24, with a standard deviation of 37.
+About 60\% of long term rental spent one month or less on the market and 85\% spent less than two months searching for a tenant.
+-->
+
+<!-- Using these estimated occupancy rates and days on market, we have used equations 3 and 4 to produce estimates of long-term and short-term revenues for the short and long term observations, respectively.
+We do these for the observed and the estimated rates and rents for each tenure type.
+As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as follows: -->
+
+<!-- ```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4} -->
+
+<!--   explain.plot <- blank.plot + -->
+<!--     geom_text(data=ann.df, -->
+<!--               label=ann.df$lab, -->
+<!--               size=2.8) + -->
+<!--     geom_text(data=num.df, -->
+<!--               label=num.df$count, -->
+<!--               size=9.5) + -->
+<!--     coord_cartesian(ylim=c(-.5,1)) + -->
+<!--     ggtitle('Explanation of \n Revenue Comparisons') + -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!--   one.df <- data.frame(x=rep(0, 4), -->
+<!--                        y=rep(0, 4),  -->
+<!--                        lab=c('31%', '87%', '54%', '79%'), -->
+<!--                        est=c('Actual Rates & Rents', 'Actual Rates & Rents', -->
+<!--                              'Imputed Rates & Rents', 'Imputed Rates & Rents'), -->
+<!--                        data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term')) -->
+
+<!--   sizes <- c(.31, .87, .54, .79) -->
+
+<!--   one.plot <- blank.plot + -->
+<!--     geom_text(data=one.df, -->
+<!--               label=one.df$lab, -->
+<!--               size=18*sizes) + -->
+<!--     ggtitle('% of Properties where \n Airbnb is more profitable') + -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(),  -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- In other word the left hand panels are comparison made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
+In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
+-->
+
+<!-- The plot below shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
+The variation between these estimates is significant and troublesome.
+However, given our difficulty in accurately estimating short term nightly rates (see Table X) and the fact that occupancy rates are highly variable for short-term rentals, these variation are not surprising.
+As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
+Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
+-->
+
+<!-- ```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center'} -->
+
+<!--  ggMultiPlots(explain.plot, one.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- In short, only in the upper left hand panel are we using the actual nightly rates and the actual occupancy rates from the short term market.
+We do estimate the long-term rates and days on market here, but as shown above, the models for those figures are much more robust.
+The plusses and minus of each comparison quadrant is shown below.
+As a result of these issues, we consider only those comparisons in quadrant 1 to be legitimate and use these going forward.
+-->
+
+<!-- ```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center'} -->
+
+<!--   reason.plot <- blank.plot + -->
+<!--     geom_rect(data = mrkt.table, aes(fill=good), -->
+<!--               xmin = -Inf,xmax = Inf, -->
+<!--               ymin = -Inf,ymax = Inf, alpha = 0.4) + -->
+<!--     geom_text(data=reason.df, -->
+<!--               label=reason.df$lab, -->
+<!--               size=3) + -->
+<!--     geom_text(data=num.df, -->
+<!--               label=num.df$count, -->
+<!--               size=9.5) + -->
+<!--     coord_cartesian(ylim=c(-.5,1)) -->
+
+<!--   reason.plot -->
+
+<!-- ``` -->
+
+<!-- ### Occupancy Rates -->
+
+<!-- Occupancy rates are one of the most important compoenent in determining the profitability of short-term rentals.
+Unfortunately, these are also the most difficult factor to estimate or impute.
+Below we plot (left-panel) the percentage of properties for which short-term rental is more profitable versus the occupancy rate.
+We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up until about 75\% occupancy.
+For occupancy rates less than 50\%, long-term rental is more likely to be the better option.
+The decrease in profitabilty after 75\% occupancy is likely due to: 1) small sample sizes in this tail of the data; and 2) that lowering overall nightly rates too low simply to boost occupancy can result in lower overall revenue.
+-->
+
+<!-- As the distribution of occupancy rates is not uniform, the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+In Figure X, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+By doing so, we see that, in general, properties need to be in the upper 1/3 of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   rawocc.pplot <- makePrefPlot(abb.revs, -->
+<!--                                x.field='occ.rate', -->
+<!--                                y.field='abb.act', -->
+<!--                                     smooth=TRUE, -->
+<!--                                smooth.span=.75) -->
+<!--   rawocc.pplot <- rawocc.pplot + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     ylab('\n% of Properties where \nAirbnb is more profitable') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     ggtitle('Tenure Profitability vs \n Occupancy Rate') + -->
+<!--     theme(legend.position='none', -->
+<!--           plot.title = element_text(hjust = 0.5)) +  -->
+<!--     coord_cartesian(ylim=c(0,1)) + -->
+<!--     geom_hline(aes(yintercept=.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   dens.plot <- ggplot(abb.revs, aes(x=occ.rate)) + -->
+<!--     geom_density(alpha=.3, fill=1) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     scale_x_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+
+<!--     ylab('\nFrequency of Occurance') + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     ggtitle('Distribution of \n Occupancy Rates') + -->
+<!--     theme(legend.position='none', -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.line=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank()) -->
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5} -->
+
+<!--   ggMultiPlots(rawocc.pplot, dens.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate,  -->
+<!--                                       return.type='rank')  -->
+<!--   abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate,  -->
+<!--                                   return.type='rank')  -->
+
+<!--   ## Make quartile location plot -->
+
+<!--   qtlocc.pplot <- makePrefPlot(abb.revs, -->
+<!--                                x.field='occ.qtl', -->
+<!--                                y.field='abb.act', -->
+<!--                                smooth=TRUE, -->
+<!--                                smooth.span=.55) -->
+<!--   qtlocc.pplot <- qtlocc.pplot + -->
+<!--     xlab('\nQuantile of Occupancy Rate') + -->
+<!--     ylab('\n% of Properties where \n Airbnb is more profitable') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0', '25th', '50th', '75th', '100th')) + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     coord_cartesian(ylim=c(0,1))+ -->
+<!--     geom_hline(aes(yintercept=.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=3.5, fig.align='center'} -->
+
+<!--   qtlocc.pplot -->
+
+<!-- ``` -->
+
+<!-- Along with occupancy rate, the other important consideration is the nightly rate.
+High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
+In Figure X (left panel) we plot nightly rates versus occupancy rates.
+We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
+The transparency is related to the total count of actual market properties falling into that area.
+-->
+
+<!-- A general trend is what is expected, higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
+This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
+While the left panel of Figure X helps show the general pattern is doe leave many indeterminate areas.
+In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
+-->
+
+<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+In this case, we delineate the boundary (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
+In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
+While this process does provide more flexible fit in the area of high data density, it also has the side effect of creating somewhat counter intuitive results in areas of low data (such as the far upper right corner.)  Overall, from the SVM model we see that there short-term prefernce begins at about 30\% occupancy rate, regardless of nightly rate.
+As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
+-->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!--  ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in figure X may be misleading.
+We convert both axis to quantiles and replot both figures.
+Here we see a more even distibution of points across the figures.
+Additionally, a more reasonable SVM breakdown occurs as well.
+The right panel shows that , in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have is 40\%, if the nightly rate is in the top 95th percentile of the market.
+For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
+-->
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE} -->
+
+<!--  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Finally, we summarize the entire market by looking at three metrics: -->
+
+<!-- 1. Actual: The percentage of properties in the market in which Airbnb generates more revenue -->
+<!-- 2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable -->
+<!-- 3. SVM Area: The percentage of the total area in the SVM plot that represents a situation where the short-term rental is more profitable.   -->
+
+<!-- None of these metrics on their own is perfect.
+The 'actual' measure responds directly to the sample of the current market and may not be as useful to a potential investor.
+The 'fitted' and 'svm' metric minimize some bias from the sample, but suffer from forcing all observations into a binary condition (there are no 'gray' areas) and the 'svm area' metric may be biases by large areas of the scatterplot that have few actual observations.
+This latter issue is partially limited by plotting by quantile, but, nonetheless still exists.
+-->
+
+<!-- We calculate each for the raw rates as well as for the quantile situation.
+These are show in Table X.
+Overall, 31.4\% of the observed Airbnb properties raised more actual revenue from short term lending than the estimated long-term revenue that they would have gained.
+Analyzing these by raw rates in the SVM, we find that a nearly identical 31.4\% fall within the contiguous area of short-term preference and this area takes up 40.6% of the total plotted area.
+When scale the plots by quantile, we find that 37.2\% of all observations fall in the short-term preference area and that this area takes up 37.8\% of the total plotted area.
+As the difference between the fitted and the svm area is considerably smaller in the quantile approach, there is less bias from outlying, empty areas.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!-- print(xtable(market.ratio, -->
+<!--        digits=3), -->
+<!--        include.rownames=FALSE) -->
+
+<!-- ``` -->
+
+<!-- ### Submarkets -->
+
+<!-- A major deficit in this analysis is that the potential rents, rates, days on market and occupancy rates are estimated globally.
+As a result, there is the likelihood of significant bias within certain submarkets.
+Below, we break down the results by type (apartment vs house), by geographic market (5 submarketd listed above) and by type and submarket.
+We show only the summary tables and the quantile heat map plots.
+Full results can be found on the ....ENTER SHINY WEBSITE....
+-->
+
+<!-- #### Property Type -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!-- ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!-- ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!--  type.table <- rbind(apt$mrkt.score, house$mrkt.score) -->
+<!--  type.table$property.type <- c('apartment', '', 'house', '') -->
+<!--  type.table <- type.table[,c(5,1:4)] -->
+<!--  print(xtable(type.table, -->
+<!--        digits=3), -->
+<!--        include.rownames=FALSE, hline.after=c(-1,0,2,4)) -->
+
+<!-- ``` -->
+
+<!-- #### Geographic Submarkets -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!-- names(sm.results)[[1]] <- 'core' -->
+
+<!-- ggMultiPlots(sm.results$core$qtl.hm.svm, -->
+<!--              sm.results$city$qtl.hm.svm, cols=2) -->
+<!-- ``` -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!-- ggMultiPlots(sm.results$suburban$qtl.hm.svm,  -->
+<!--              sm.results$rural$qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, fig.width=4, fig.height=4, echo=FALSE, fig.align='center'} -->
+
+<!--              sm.results$beach$qtl.hm.svm -->
+
+<!-- ``` -->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!--  sm.table <- rbind(sm.results$core$mrkt.score,  -->
+<!--                      sm.results$city$mrkt.score,  -->
+<!--                      sm.results$suburban$mrkt.score,  -->
+<!--                      sm.results$rural$mrkt.score,  -->
+<!--                      sm.results$beach$mrkt.score) -->
+
+<!--  sm.table$sub.market <- c('core', '', 'city', '', 'suburban', '' -->
+<!--                             , 'rural', '', 'beach', '') -->
+<!--  sm.table <- sm.table[,c(5,1:4)] -->
+<!--  print(xtable(sm.table, -->
+<!--        digits=3), -->
+<!--        include.rownames=FALSE, hline.after=c(-1,0,2,4,6,8,10)) -->
+
+<!-- ``` -->
+
+## References
+
+<!-- ### Submarkets -->
+
+<!-- ### Flexible Geo Analysis -->
+
+<!-- ### Logit Models (maybe?) -->
+
+<!-- ### Reference to Shiny App -->
+
+<!-- ## Future Research -->
+
+<!-- - Does time of purchase (which month) matter? -->

### 2017-01-09 abbReturns_Working.R
logit model initiation

@@ -542,6 +542,44 @@
   }
   names(smt.results) <- as.character(smt.levels)
   
+### Build logit models on this -----------------------------------------------------------
+  
+ ## Create combined data
+  
+  smt.data <- rbind.fill(lapply(smt.results, function(x) x$abb))
+  
+  # Fix cancel.policy issue
+  ss60 <- which(smt.data$cancel.policy == 'Super Strict 60 Days')
+  smt.data$cancel.policy[ss60] <- 'Strict'
+  cpmiss <- which(smt.data$cancel.policy == '')
+  smt.data <- smt.data[-cpmiss, ]
+  
+ ## Build models  
+  
+  mod.str <- glm(abb.act~as.factor(bedbath)+type,
+                 family=binomial(link='logit'),
+                 data=smt.data)
+  
+  mod.sm <- glm(abb.act~as.factor(bedbath)+type+sub.mrkt,
+                 family=binomial(link='logit'),
+                 data=smt.data)
+
+  mod.host <- glm(abb.act~as.factor(bedbath)+type+
+                    sub.mrkt+
+                    max.guests+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                  family=binomial(link='logit'),
+                  data=smt.data)
+  
+  
+  mod.sub <- glm(abb.act~as.factor(bedbath)+type+suburb,
+                 family=binomial(link='logit'),
+                 data=smt.data)
+  
+  
+  #So p = 49/200 =  .245. The odds are .245/(1-.245) = .3245 
+  #and the log of the odds (logit) is log(.3245) = -1.12546.  
+  
 ### Save workspace -----------------------------------------------------------------------
   
   save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_results.RData")

### 2017-01-10 abbReturns_Working.R
add logit moels

@@ -23,6 +23,7 @@
   library(stringr)
   library(RColorBrewer)
   library(Hmisc)
+  library(ROCR)
 
  ## Set path location
 
@@ -186,8 +187,8 @@
   
   num.df <- data.frame(x=rep(0, 4),
                        y=rep(.8, 4),
-                       est=as.factor(c('Actual Rates & Rents', 'Imputed Rates & Rents',
-                             'Actual Rates & Rents', 'Imputed Rates & Rents')),
+                       est=as.factor(c('Actual Rates & Rents', 'Imp. Rates & Rents',
+                             'Actual Rates & Rents', 'Imp. Rates & Rents')),
                        data=as.factor(c('Airbnb', 'Airbnb', 'Long-Term', 'Long-Term')),
                        count=c(1,3,2,4))
   
@@ -556,35 +557,129 @@
   
  ## Build models  
   
-  mod.str <- glm(abb.act~as.factor(bedbath)+type,
+  # Structural Only model
+  mod.str <- glm(abb.act~type+as.factor(bedbath),
                  family=binomial(link='logit'),
                  data=smt.data)
   
-  mod.sm <- glm(abb.act~as.factor(bedbath)+type+sub.mrkt,
+  # +Submarket model
+  mod.sm <- glm(abb.act~type+as.factor(bedbath)+
+                  sub.mrkt,
                  family=binomial(link='logit'),
                  data=smt.data)
 
-  mod.host <- glm(abb.act~as.factor(bedbath)+type+
+  # +Host model
+  mod.host <- glm(abb.act~type+as.factor(bedbath)+
                     sub.mrkt+
-                    max.guests+min.stay+
+                    I(max.guests/bedrooms)+min.stay+
                     I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                   family=binomial(link='logit'),
                   data=smt.data)
   
-  
-  mod.sub <- glm(abb.act~as.factor(bedbath)+type+suburb,
+  # Suburb model
+  mod.sub <- glm(abb.act~type+as.factor(bedbath)+
+                   suburb,
                  family=binomial(link='logit'),
                  data=smt.data)
   
+  # Suburb Host model
+  mod.subh <- glm(abb.act~type+as.factor(bedbath)+
+                  suburb+
+                  max.guests+min.stay+
[…]

### 2017-01-10 abbReturns_Writeup.Rmd
Review of initial 80%.

--- 2017-01-08 abbReturns_Writeup.Rmd
@@
   html_document: default
-geometry: margin=3cm
+geometry: margin=3.4cm
+bibliography: abb.bib
 ---
@@
 
+ ## Set options
+
+  options(xtable.comment = FALSE)
+
 ```
@@
 
-### Scenario
-
-We approach answering the question of Airbnb-ing or not by examining a scenario likely to be faced by a recent purchaser of a property.  More specifically, we examine the following case:
+We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+More specifically, we examine the following case:
 
 * An investor purchases a property in Melbourne on Sept 1, 2015.
-* They are looking to maximize the revenue over the 12 month period from Sept 1 2015 to August 31 2016.
+* They are looking to maximize the revenue over the 12-month period from September 1, 2015 to August 31, 2016.
 * The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental.
-* Only direct monetary costs are considered, others such as liquidity and inconvience are not considered.
-
-We will not, a priori, specify a location or property type as we hypothesize that the feasibility of a short term rental will vary by these characteristics.
-Australia has a tax policy, Negative Gearing, that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties.
-However, as this policy requires knowledge of the investor's personal income level, we will not be considering this policy in our analysis here.
+* Only direct monetary revenues and costs are considered, others such as liquidity and inconvience are not considered.
+
+We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
+Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.
+However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
 
 One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
-As the future trends are unknown at the time of purchase and the decision of long vs short term rental, we make our comparisons using a fixed nightly short term rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
-Both long and short term rates and occupancy structures will be baesd on the market conditions as of this date.
-
-### Equation
-
-In this above scenario we compare the 12-month returns from the a long term rental with those of a short term rental.
+As future market trends are unknown at the time of purchase and the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
+Both long- term rents and short-term rates and occupancy structures will be baesd on the market conditions as of this date.
+
+We do not directly observe properties that are utilized in both a short and long term leasing strategy.
+Therefore, comparisons are done based on estimated or imputed revenues.
+Most specifically, we will estimate short-term revenue for observations of long-term rentals (LTRs) and long-term revenue for observations of short-term rentals (STRs).
+A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
+
+### Comparison
+
+In this above scenario we compare the 12-month revenues from the a long-term rental with those of a short-term rental.
 We define returns here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
@@
 \begin{equation}
-R_{LT} = Rev_{LT} - C_{LT}
+Rev_{LT} = RevG_{LT} - C_{LT}
 \end{equation}
@@
 \begin{equation}
-R_{ST} = Rev_{ST} - C_{ST}
+Rev_{ST} = RevG_{ST} - C_{ST}
 \end{equation}
 
+Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the costs associated with long-term rental. The gross long-term revenue is expressed by:
+
 \begin{equation}
-Rev_{LT} = Rent_{M} * (12 - C_{S}) 
+RevG_{LT} = Rent_{M} * (12 - C_{S})
 \end{equation}
 
-where $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+
+The short-term revenue is expresse by:
 
 \begin{equation}
-Rev_{ST} = Rate_{N} * O_{Total} 
+RevG_{ST} = Rate_{N} * O_{Total}
 \end{equation}
 
-where $O_{Total}$ are the total number of occupancies over the 12-month period.
+where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period.
+
+We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
+Broadly speaking, these fall into three categories for long-term rental and four categories for short-term properties.
+Long-term costs are summarized as:
 
 \begin{equation}
-C_{LT} = T + M 
+C_{LT} = T + M + F
 \end{equation}
 
-where
-
-where $T$ are tax related expenses and $M$ are general maintenance expenses.
+where $T$ are tax related expenses, $M$ are general maintenance expenses and $F$ are finaning costs.
+Short-term properies experience the same three costs ($T$, $M$ and $F$) plus additional janitorial costs between each of the short-term occupants.
 
 \begin{equation}
-C_{ST} = T + M + J 
+C_{ST} = T + M + F + J
 \end{equation}
 
-where $T$ are tax related expenses, $M$ are general maintenance expenses and $J$ are janitorial expenses incurred after each short term tenancy.
-
-We assume for the sake of this scenario that the tax $T$ and general maintenance $M$ expenses are identical between tenure options and therefore cancel out.
-With the analysis that follows we will consider short term rental to be prefable to long-term if the following inequality holds:
+As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
+General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
+Long-term renters spend more time in the property over the course of the year and bring their own appliance and furniture which may damage the home.
+They are also more likely to affix items to the structure.
+Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.].
+Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short or long term rentals.
+As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
+
+Finally, we have janitorial costs $J$.
+These cover the costs to 'turn-over' the property between occupants.
+For a short-term leasing strategy, these costs can be experiences every day or two, depending on the minimum length of stay and the total number of occupancies over the course of the year.
+Our data for short-term rentals comes from the Airbnb platform.
+In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.
+Some hosts add additional 'linen' fees to cover costs of laundering.
+While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
+As a result of janitorial fees being a separate line item and directly paid by the occupants can also be ignored in the comparative analysis below as they are direct.
+
+Given that the costs cancel out between the two options, we will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
 
 \begin{equation}
-Rate_{N} * O_{Total} - J > Rent_{M} * (12 - C_{S}) 
+RevG_{ST} > RevG_{LT} 
 \end{equation}
 
+More specifically, if:
+
+\begin{equation}
+Rate_{N} * O_{Total} > Rent_{M} * (12 - C_{S})
+\end{equation}
+
 ## Data
@@
 Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
-The Airbnb online portal is used as evidence of the short-term rental market.
-Airbnb is the largest short-term rental hub in the Melbourne region, though others do exist.
-As opposed to similar sites such as VRBO.com and homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, in way ways, directly compete with more traditional long term rentals.
+Short-term rental market observations are from the Airbnb online portal.
+Airbnb is the largest short-term rental hub in the Melbourne region.
+As opposed to similar sites such as VRBO.com and homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
 The data on the AirBNB market in Melbourne have been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
 The short term data include two types of observations, property level and nightly.
-Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year.
-This data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
-
-The Airbnb data cover the Melbourne metropolitan region from October 1st 2014 to August 30th 2016.
-There are missing nightly observations during the time period before September 1 2015.
-While we initially imputed these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
+Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
+These data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
+
+The Airbnb data cover the Melbourne metropolitan region from October 1st, 2014 to August 30th, 2016.
+There are missing nightly observations during the time period before September 1, 2015.
+After initially imputed these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
@@
 The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
-This data also includes an observation for each rental property each time a detail of the listing changed.
+In raw form, this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
 For example, if a property were listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
 These four observations are grouped by an event-specific identification number.
+This number is specific to the listing event, not the property.
 In each case the last observation signifies the final price of the rental contract.
 We separate this data into two sets for efficiency reasons.
-The first data set includes all information about the property, physical and economic (date and amount of rent contract), while the second contains a property ID, a rental event ID, the list price and the date of the change.
-As such, the first dataset is a set of market observations with associated characteristics and the second is a listing history of each event.
+The first data set includes all information about the property, physical and economic (date and amount of rental contract), while the second contains a property ID, a rental event ID, the list price and the date of the change.
+As such, the first dataset is a set of market observations with associated characteristics and the second is a listing history of each rental event.
 The long-term lease data covers the period from January 2014 to December 2015.
 
-Unfortunately, there are no common identifiers between the two dataset as the Airbnb data does not include address.
+Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
 Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
@@
 In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
-Primarily, this involves the filtering out of data errors and/or outlier values.
-However, as our data are from two different sources, number of fields also require standardization so that comparisons between the two tenure options can be made.
+Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions.
+Additionally, as our data are from two different sources, a number of fields also require standardization so that comparisons between the two leasing strategy options  -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
 
 We begin by filtering observations by time.
-Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
-To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
-Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
+Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an AirBNB-type, short-term rental approach to generating income.
+To determine the likely LTR rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
+Taking the Airbnb or STR approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
 In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
 
-Next, we examine property types.
+Next, we filter the data based on property types.
 AirBNB units are classified into 19 different property types.
-The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
+The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type].
 For the sake of this analysis, we will collapse these twenty types into three types:
@@
 
-Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
+Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
 This is most apparent when talking about apartment dwellings.
-In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
+In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure)^[Also note that 'Apartment-type' ownership is very rare in Australia.
+Nearly every multi-family dwelling is owned as a condominium.
+See @Berry2000investment for more information on the overall structure of the Australian market].
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
 
-As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
-Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
-As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
+The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
+Additionally, a large proportion of the **Others** in the short-term data are Bed & Breakfast units, a use which doesn't fit with our research question.
+As a result, we remove the 'Others' from both the short- and the long-term rental data.
 
@@
 
-```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type'}
+```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
 
@@
 
-Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
 
@@
 
-As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returns, we remove all short term properties that do not lease the entire home/apt.
-Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
-
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap='Listing Type of Short Term Rentals'}
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
+Unfortunately, this filter does remove about 40% of the short-term data (See Figure 2), however, given the research question it is unavoidable.
+
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}
 
@@
     ylab('# of Properties\n') +
-    labs(title = "Short Term Rentals by Listing Type\n") + 
+    labs(title = "Short Term Rentals \nby Listing Type\n") +
     theme(plot.title = element_text(hjust = 0.5))
@@
 We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
-For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
+For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5 (Figure 3).
 We filter the data accordingly.
@@
 
-We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
-Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
-A few short term properties state no baths, which is likely an error so we remove these observations from the data.
+We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apartment/house.
+Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly (Figure 4).
+A few short term properties indicate no baths, which is likely an error so we remove these observations from the data.
 Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
@@
 In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two.
+In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+As a result we examine the combinations of the two (Figure 5).
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
+We filter the data to these combinations.
 
@@
     labs(title = "Bed/Bath Combo in Short Term Rentals\n") +
+    scale_y_continuous(breaks=c(1000, 3000, 5000)) +
     theme(plot.title = element_text(hjust = 0.5)) +
@@
 
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
-
 ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
@@
 
-We now turn to filtering by the prices -- the nightly rates and weekly rental values.
-The long term rental data have a single price observation, the asking rent each time an change in the listing occurs, including the price at closing.
+Next we filter by the prices -- the nightly rates and weekly rental values.
+The long term rental data have a single price observation, the asking rent at closing.
 For the short term data, there are two indicators of nightly rate.
@@
 In cases where a small number of reservations have been made, the average nightly rate can deviate widely from usual rate due to outliers on the high end.
-To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1 2015 to August 31, 2016 period.
+To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1, 2015 to August 31, 2016 period.
 
 We start by removing property level observations missing price data.
-Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 6).
 We filter the property level data accordingly.
@@
 
-Location is clearly an important determinant in both the short and long term rental markets.
+Location is an important determinant in both the short- and long-term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
-The plot below shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
+Figure 7 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
 
@@
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term rentals in Melbourne:
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
 
@@
 
-We select the 18 suburbs below to represent the 'core' of the city.
+We select the 18 suburbs below to represent the 'core' of the city (Table 1).
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenties for tourists.
-
-```{r, results="asis", echo=FALSE}
+All are well serviced by public transportation and possess abundant amenities for tourists.
+
+```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
 
@@
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short and long term rentals, colored by submarket, are shown below
+The location of the short and long term rentals, colored by submarket, are shown in Figure 8.
 
 Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
-For those without either we remove them from the dataset at this point.
+Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
+For those without either set of lat/longs we remove them from the dataset at this point.
 After making this correction we then assign one of the five submarket designations based on the process described above.
@@
 
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9}
+```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
 
@@
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here.
+A number of interesting observations are illustrated here (Figure 9).
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
@@
 Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartment, somewhat common in long term markets, are nearly absent in the Airbnb market.
-Overall, the suburban and rural Airbnb market are quite thin, later results focusing on these market will need to be examined in light of this small sample size.
+Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
+Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
 
@@
 
-```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
-
-  abbtype.map
-
-```
-
-```{r ltrtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
-
-  ltrtype.map
-
-```
-
-### Actual Revenue
+```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=7, fig.cap='Observations by Submarket'}
+
+  ggMultiPlots(abbtype.map, ltrtype.map, cols=1)
+
+```
+
+### Observed Revenue
 
@@
 
-For the short term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
 Using this data we sum up the total revenue from bookings.
@@
 
-Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority randing between \$12,000 to \$30,000 per year.
-Short term revenue range from neglible to highs of greater than \$80,000.
-While this simple analysis does not control for locational and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
+Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
+Short term revenues range from neglible to highs of greater than \$80,000.
+While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
 Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
 
-```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}
 
  load(paste0(data.path, '/analyzed/abb_results.RData'))
-
-```
-
-```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+ a<-1
+
+```
+
+```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
 
@@
 We have applied nine separate filters to our two datasets.
-In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters.
+In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters (Table 2).
 There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
-Removing those not listed during the study period removes 1/3 of all properties.
+Filtering those not listed during the study period removes 1/3 of all properties.
 Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
@@
 
-For the long term data, over half of the observations fall outside of our considered time frame,reducing the sample size down to around 130,000 from 290,000.
+For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
@@
 
-```{r, results="asis", echo=FALSE}
+```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
 
@@
 
-Data prepared, we now turn to comparing returns between long and short term rental options.
+In this section we compare returns between long and short term rental options.
 As mentioned above, there are no direct matches between the datasets.
-In other words we have not direct observed a property which has been in a long-term rental followed by short-term or vice versa.
+In other words, we have not directly observed a property which has been in a long-term rental followed by short-term or vice versa.
 We will, instead, make the comparisons between the two by imputing likely short-term (long-term) rental revenues for the long-term (short-term) data and then comparing the observed revenues to the imputed revenues of the unobserved tenure type.
@@
 
-where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
 
@@
 
-where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, BedBath is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
-
-### Costs
-
--- Assume long term costs are equivalent
+where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
 
@@
 We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
-A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel).
+A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel) (Figure 11).
 This is likely due to the fact that there are more houses (compared to apartments) in the long-term data than in the short-term data.
@@
 This may help to reduce the influence of outlying observed values in our model.
-To be clear, Each observation will now have three estimates of rates and rents.
+To be clear, each observation will now have three estimates of rates and rents.
 For the short-term properties they will have: 1) an actual nightly rate; 2) an estimated nightly rate; and 3) an estimated long-term (weekly) rent.
@@
 
-```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}
+```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5, fig.cap='Rates and Rents Comparison'}
 
@@
 The question of whether or not the imputations are accurate remains.
-The table belows shows some simple diagnostics from the two imputation models.
+Table 3 shows simple diagnostics from the two imputation models.
 From this we see that the short-term model performs rather poorly, with a standard error of 34.6\% and over half of the residuals greater than 20\%.
-The long term model, on the other hand, performs quite well, with a standard error under 32\% and less than 19\% of fitted errors greater than 20\%.
+The long term model, on the other hand, performs quite well, with a standard error under 16\% and less than 19\% of fitted errors greater than 20\%.
 Given the small amount of independent variable available to the models, the long term market appear much more predictable than the short term market.
@@
 
-```{r, results="asis", echo=FALSE}
+```{r, results="asis", echo=FALSE, fig.cap='Imputation Model Diagnostics'}
 
@@
 
-print(xtable(summ.table,
-       digits=3),
+s.table <- xtable(summ.table,
+       digits=3)
+align(s.table) <- c('lcc')
+print(s.table,
        include.rownames=TRUE)
@@
 Work continues toward this end.].
-The range of occupancy varies widely from essentially 0 to 100%,with a standard deviation of 27%.
+The range of occupancy varies widely from essentially 0 to 100%, with a standard deviation of 27%.
 
@@
 We do these for the observed and the estimated rates and rents for each tenure type.
-As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as follows:
+As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as shown in Figure 11.
 
@@
 
-In other word the left hand panels are comparison made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
+In other words, the left hand panels (left side of Figure 12) are comparisons made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
 In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
 
-The plot below shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
+The right hand side of Figure 12 shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
 The variation between these estimates is significant and troublesome.
-However, given our difficulty in accurately estimating short term nightly rates (see Table X) and the fact that occupancy rates are highly variable for short-term rentals, these variation are not surprising.
+However, given our difficulty in accurately estimating short term nightly rates (see Table 2) and the fact that occupancy rates are highly variable for short-term rentals, these variations are not surprising.
 As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
@@
 We do estimate the long-term rates and days on market here, but as shown above, the models for those figures are much more robust.
-The plusses and minus of each comparison quadrant is shown below.
+The plusses and minus of each comparison quadrant are shown in Figure 13.
 As a result of these issues, we consider only those comparisons in quadrant 1 to be legitimate and use these going forward.
+This means that we will only be considering comparisons of actual Airbnb revenues to their estimated long-term rental revenues.
 
@@
 
-Occupancy rates are one of the most important compoenent in determining the profitability of short-term rentals.
+Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
 Unfortunately, these are also the most difficult factor to estimate or impute.
-Below we plot (left-panel) the percentage of properties for which short-term rental is more profitable versus the occupancy rate.
+Below we shows (left-panel, Figure 14) the percentage of properties for which short-term rental is more profitable versus the occupancy rate.
 We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up until about 75\% occupancy.
@@
 
-As the distribution of occupancy rates is not uniform, the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
-In Figure X, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+As the distribution of occupancy rates is not uniform (Figure 14, right panel), the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+In Figure 15, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
 By doing so, we see that, in general, properties need to be in the upper 1/3 of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'}
 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=3.5, fig.align='center'}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=3.5, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'}
 
@@
 
-Along with occupancy rate, the other important consideration is the nightly rate.
+Along with occupancy rates, the other important consideration is the nightly rate.
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In Figure X (left panel) we plot nightly rates versus occupancy rates.
+In Figure 15 (left panel) we plot nightly rates versus occupancy rates.
 We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
@@
 
-A general trend is what is expected, higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
+The general trend is what is expected, i.e.
+that higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
 This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
-While the left panel of Figure X helps show the general pattern is doe leave many indeterminate areas.
+While the left panel of Figure 15 helps show the general pattern is doe leave many indeterminate areas.
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
@@
 In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
-While this process does provide more flexible fit in the area of high data density, it also has the side effect of creating somewhat counter intuitive results in areas of low data (such as the far upper right corner.)  Overall, from the SVM model we see that there short-term prefernce begins at about 30\% occupancy rate, regardless of nightly rate.
+While this process does provide more flexible fit in the area of high data density, it also has the side effect of creating somewhat counter intuitive results in areas of low data (such as the far upper right corner.)  Overall, from the SVM model we see that the short-term preference begins at about 30\% occupancy rate, regardless of nightly rate.
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'}
 
@@
 
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in figure X may be misleading.
-We convert both axis to quantiles and replot both figures.
+Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 15 may be misleading.
+We convert both axis to quantiles and replot both in Figure 16.
 Here we see a more even distibution of points across the figures.
 Additionally, a more reasonable SVM breakdown occurs as well.
-The right panel shows that , in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have is 40\%, if the nightly rate is in the top 95th percentile of the market.
+The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have is 40\%, if the nightly rate is in the top 95th percentile of the market.
 For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
-```{r, fig.width=8, fig.height=4, echo=FALSE}
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
 
@@
 
-1. Actual: The percentage of properties in the market in which Airbnb generates more revenue
+1. Actual: The percentage of properties in the market in which short-term (Airbnb) generates more revenue
 2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable
@@
 The 'actual' measure responds directly to the sample of the current market and may not be as useful to a potential investor.
-The 'fitted' and 'svm' metric minimize some bias from the sample, but suffer from forcing all observations into a binary condition (there are no 'gray' areas) and the 'svm area' metric may be biases by large areas of the scatterplot that have few actual observations.
+The 'fitted' and 'svm area' metric minimize some bias from the sample, but suffer from forcing all observations into a binary condition (there are no 'gray' areas) and the 'svm area' metric may be biases by large areas of the scatterplot that have few actual observations.
 This latter issue is partially limited by plotting by quantile, but, nonetheless still exists.
@@
 We calculate each for the raw rates as well as for the quantile situation.
-These are show in Table X.
-Overall, 31.4\% of the observed Airbnb properties raised more actual revenue from short term lending than the estimated long-term revenue that they would have gained.
+These are show in Table 4.
+Overall, 31.4\% of the observed Airbnb properties raised more actual revenue from short-term lending than the estimated long-term revenue that they would have gained.
 Analyzing these by raw rates in the SVM, we find that a nearly identical 31.4\% fall within the contiguous area of short-term preference and this area takes up 40.6% of the total plotted area.
-When scale the plots by quantile, we find that 37.2\% of all observations fall in the short-term preference area and that this area takes up 37.8\% of the total plotted area.
+When we scale the plots by quantile, we find that 37.2\% of all observations fall in the short-term preference area and that this area takes up 37.8\% of the total plotted area.
 As the difference between the fitted and the svm area is considerably smaller in the quantile approach, there is less bias from outlying, empty areas.
 
-```{r, results="asis", echo=FALSE}
-
+```{r, results="asis", comment=FALSE,  echo=FALSE, fig.cap='Preference Analysis: Metro Area'}
+
+names(market.ratio) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
 print(xtable(market.ratio,
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+* Need to explain this
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'}
 
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'}
 
@@
 
-```{r, results="asis", echo=FALSE}
+```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Property Type'}
 
@@
  type.table <- type.table[,c(5,1:4)]
+ names(type.table) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
  print(xtable(type.table,
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
-
-names(sm.results)[[1]] <- 'core'
-
-ggMultiPlots(sm.results$core$qtl.hm.svm,
-             sm.results$city$qtl.hm.svm, cols=2)
-```
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center'}
-
-ggMultiPlots(sm.results$suburban$qtl.hm.svm, 
-             sm.results$rural$qtl.hm.svm, cols=2)
-
-```
-
-```{r, fig.width=4, fig.height=4, echo=FALSE, fig.align='center'}
-
-             sm.results$beach$qtl.hm.svm
-
-```
-
-```{r, results="asis", echo=FALSE}
+* Need to explain this.
+
+```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Submarket'}
 
@@
 
+Logistic Regression
+
+*Logistic regression to explain what is correlated with short-term preference
+*3 Model approach, increasing complexity
+*Need to explain log odds, interpretation, etc.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+#full.table$Str.Model <- gsub(" ", "&nbsp;", full.table$Str.Model, fixed=TRUE)
+ x.full <- xtable(full.table)
+ align(x.full) <- 'lllll'
+
+ print(x.full, 
+       include.rownames=FALSE, 
+       hline.after=c(-1,0,15,20,20))
+
+```
+
+\pagebreak
+
+## References
+
 <!-- ### Submarkets -->

### 2017-01-11 abbReturns_Script.Rmd
fixing save and load issues

@@
 before.PT <- list(abb.data=abb.data,
-                  daily.data=daily.data,
-                  ltr.data=ltr.data,
-                  listing.data=listing.data)
-
-save(before.PT, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
+                  ltr.data=ltr.data)
+
+save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
 
@@
 after.SP <- list(abb.data=abb.data,
-                  daily.data=daily.data,
-                  ltr.data=ltr.data,
-                  listing.data=listing.data)
+                 ltr.data=ltr.data)
 

### 2017-01-11 abbReturns_Writeup.Rmd
fixing save and load issues

@@
   library(lmtest)
+  library(ROCR)
 
@@
 
-```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}
-
-  load(paste0(data.path, '/analyzed/abb_working.RData'))
-
-```
+<!-- # ```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE} -->
+<!-- #  -->
+<!-- #   load(paste0(data.path, '/analyzed/abb_working.RData')) -->
+<!-- #  -->
+<!-- # ``` -->
 
@@
 Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.
-
 Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments.
@@
 A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
-
 ### Comparison
@@
 
-```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
+```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
   data.path <- 'c:/dropbox/research/airBNB/data/'
   load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
-  abb.data <- before.PT$abb.data
-  ltr.data <- before.PT$ltr.data
-  daily.data <- before.PT$daily.data
+  abb.data1 <- before.PT$abb.data
+  ltr.data1 <- before.PT$ltr.data
 
@@
 
-  abb.types <- ggplot(abb.data, aes(x=type)) +
+  abb.types <- ggplot(abb.data1, aes(x=type)) +
     geom_bar(color=str.col, fill=str.col) +
@@
 
-  ltr.types <- ggplot(ltr.data, aes(x=type)) +
+  ltr.types <- ggplot(ltr.data1, aes(x=type)) +
     geom_bar(color=ltr.col, fill=ltr.col) +
@@
 
-  abb.data <- subset(abb.data, type != 'Other')
-  ltr.data <- subset(ltr.data, type != 'Other')
+  abb.data1 <- subset(abb.data1, type != 'Other')
+  ltr.data1 <- subset(ltr.data1, type != 'Other')
 
@@
 
-  abb.data$listing.type <- as.character(abb.data$listing.type)
-  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'
+  abb.data1$listing.type <- as.character(abb.data1$listing.type)
+  abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home'
 
@@
 
-  ggplot(abb.data, aes(x=listing.type)) +
+  ggplot(abb.data1, aes(x=listing.type)) +
     geom_bar(color=abb.col[1], fill=abb.col[1]) +
@@
 
-  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
-  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
+  abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ]
 
@@
   # Long term data
-  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
-  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
+  ltr.data1 <- ltr.data1[!is.na(ltr.data1$bedrooms), ]
+  ltr.data1 <- ltr.data1[ltr.data1$bedrooms <= 10, ]
 
   # Short term data
-  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
-  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
+  abb.data1 <- abb.data1[!is.na(abb.data1$bedrooms), ]
+  abb.data1 <- abb.data1[abb.data1$bedrooms <= 10, ]
 
@@
 
-   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) +
+   ltrbed <- ggplot(ltr.data1, aes(x=bedrooms)) +
     geom_bar(fill=ltr.col, color=ltr.col) +
@@
 
-  abbbed <- ggplot(abb.data, aes(x=bedrooms)) +
+  abbbed <- ggplot(abb.data1, aes(x=bedrooms)) +
     geom_bar(fill=str.col, color=str.col) +
@@
 
-  abb.data <- abb.data[abb.data$bedrooms < 5, ]
-  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+  abb.data1 <- abb.data1[abb.data1$bedrooms < 5, ]
+  ltr.data1 <- ltr.data1[ltr.data1$bedrooms < 5, ]
 
@@
 
-  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
-  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
-
-  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
-  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
+  abba <- which(abb.data1$bedrooms > 3 & abb.data1$type =='Apartment')
+  ltra <- which(ltr.data1$bedrooms > 3 & ltr.data1$type =='Apartment')
+
+  if(length(abba) > 0) abb.data1 <- abb.data1[-abba, ]
+  if(length(ltra) > 0) ltr.data1 <- ltr.data1[-ltra, ]
 
   # Convert 0 Bed to 1 Bed
-  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
+  abb.data1$bedrooms[abb.data1$bedrooms == 0] <- 1
 
@@
 
-  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
-  abb.data <- abb.data[!is.na(abb.data$baths), ]
+  ltr.data1 <- ltr.data1[!is.na(ltr.data1$baths), ]
+  abb.data1 <- abb.data1[!is.na(abb.data1$baths), ]
 
@@
 
-  ltbath <- ggplot(ltr.data, aes(x=baths)) +
+  ltbath <- ggplot(ltr.data1, aes(x=baths)) +
     geom_bar(fill=ltr.col, color=ltr.col) +
@@
 
-  stbath <- ggplot(abb.data, aes(x=baths)) +
+  stbath <- ggplot(abb.data1, aes(x=baths)) +
     geom_bar(fill=str.col, color=str.col) +
@@
   # Short term data
-  abb.data <- abb.data[abb.data$baths < 4, ]
-  abb.data <- abb.data[abb.data$baths > 0, ]
+  abb.data1 <- abb.data1[abb.data1$baths < 4, ]
+  abb.data1 <- abb.data1[abb.data1$baths > 0, ]
 
   # Long term data
-  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+  ltr.data1 <- ltr.data1[ltr.data1$baths < 4, ]
 
@@
 
-  abb.data$baths <- round(abb.data$baths + .01, 0)
+  abb.data1$baths <- round(abb.data1$baths + .01, 0)
 
@@
 
-  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
-  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
+  ltr.data1$bedbath <- paste0(ltr.data1$bedrooms, '..', ltr.data1$baths)
+  abb.data1$bedbath <- paste0(abb.data1$bedrooms, '..', abb.data1$baths)
 
@@
 
-  ltb <- ggplot(ltr.data, aes(x=bedbath)) +
+  ltb <- ggplot(ltr.data1, aes(x=bedbath)) +
     geom_bar(fill=ltr.col, color=ltr.col) +
@@
 
-  stb <- ggplot(abb.data, aes(x=bedbath)) +
+  stb <- ggplot(abb.data1, aes(x=bedbath)) +
     geom_bar(fill=str.col, color=str.col) +
@@
 
-  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
-  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
+  ltr.data1 <- ltr.data1[ltr.data1$bedbath %in% acc.bb, ]
+  abb.data1 <- abb.data1[abb.data1$bedbath %in% acc.bb, ]
 
@@
 
-  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
-  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
+  ltr.data1 <- ltr.data1[!is.na(ltr.data1$event.price), ]
+  abb.data1 <- abb.data1[!is.na(abb.data1$nightly.rate), ]
 
@@
 
-  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
-  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
-  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
-  abb.data$monthly.rate <- abb.data$monthly * exch.rate
+  abb.data1$average.daily.rate <- abb.data1$average.daily.rate * exch.rate
+  abb.data1$nightly.rate <- abb.data1$nightly.rate * exch.rate
+  abb.data1$weekly.rate <- abb.data1$weekly.rate * exch.rate
+  abb.data1$monthly.rate <- abb.data1$monthly * exch.rate
 
@@
 
-  daily.data$price <- daily.data$price * exch.rate
+  #daily.data$price <- daily.data$price * exch.rate
 
@@
 
-  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) +
+  ltr.plot <- ggplot(ltr.data1, aes(x=event.price)) +
     geom_density(fill=ltr.col, alpha=.8) +
@@
   # Nightly Rate plot
-  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) +
+  rate.plot <- ggplot(abb.data1, aes(x=nightly.rate)) +
     geom_density(fill=str.col, alpha=.8) +
@@
 
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 &
-                         ltr.data$event.price <= 1000, ]
+  ltr.data1 <- ltr.data1[ltr.data1$event.price >= 200 &
+                         ltr.data1$event.price <= 1000, ]
 
@@
 
-  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
-                         abb.data$nightly.rate <= 500, ]
+  abb.data1 <- abb.data1[abb.data1$nightly.rate >= 50 &
+                         abb.data1$nightly.rate <= 500, ]
 
@@
   load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
-  abb.data <- after.SP$abb.data
-  ltr.data <- after.SP$ltr.data
-  daily.data <- after.SP$daily.data
+  abb.data2 <- after.SP$abb.data
+  ltr.data2 <- after.SP$ltr.data
+
 ```
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
+    geom_point(data=abb.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
                alpha=.2) +
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
+    geom_point(data=ltr.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
                alpha=.1) +
@@
   abbtype.map <- ggplot() +
-    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=abb.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
   ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=ltr.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
 
- load(paste0(data.path, '/analyzed/abb_results.RData'))
- a<-1
+ load(paste0(data.path, '/analyzed/abb_objs.RData'))
 
@@
 
-  abbr <- abb.data[,c('bedbath', 'revenue')]
+  abbr <- abb.revs[,c('bedbath', 'revenue')]
   abbr$tenure <- 'short-term'
-  ltrr <- ltr.data[,c('bedbath', 'revenue')]
+  ltrr <- ltr.revs[,c('bedbath', 'revenue')]
   ltrr$tenure <- 'long-term'
@@
 
-  abbir <- abb.imp[,c('bedbath', 'imp.rent', 'med.rate')]
+  abbir <- abb.revs[,c('bedbath', 'imp.rent', 'med.rate')]
   abbir$tenure.rate <- 'short-term (observed)'
@@
 
-  ltrir <- ltr.imp[,c('bedbath', 'event.price', 'imp.rate')]
+  ltrir <- ltr.revs[,c('bedbath', 'event.price', 'imp.rate')]
   ltrir$tenure.rate <- 'long-term (imputed)'
@@
 ```{r, results="asis", echo=FALSE, fig.cap='Imputation Model Diagnostics'}
-
-abb.sum <- summary(imp.data$abb.mod)
-ltr.sum <- summary(imp.data$ltr.mod)
 
@@
 
-A major deficit in this analysis is that the potential rents, rates, days on market and occupancy rates are estimated globally.
+A major concern about the above analysis is that the estimated rents, rates, days on market and occupancy rates are estimated globally.
 As a result, there is the likelihood of significant bias within certain submarkets.
-Below, we break down the results by type (apartment vs house), by geographic market (5 submarketd listed above) and by type and submarket.
-We show only the summary tables and the quantile heat map plots.
-Full results can be found on the ....ENTER SHINY WEBSITE....
+Below, we break down the results by type (apartment vs house), by geographic market (five geographic submarkets listed above) and by type and submarket.
 
@@
 
-* Need to explain this
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'}
-
-ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2)
-
-```
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'}
-
-ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2)
-
-```
+First, we bifurcate our data into houses and apartments.
+We then rerun the entire analysis described above for the house and the apartment markets separately.
+Table X and Figures X (houses) and Y (apartments) illustrate the metrics for these two sub-markets.
+The raw probability data shows that over 33% of apartments are more profitable in short term leasing as opposed to just 22% of houses.
+The two figures show the quantile preference plots both in the raw and with the SVM categorization.
+As is evident from these plots, the likely of short-term rental being more profitable is much greater in the apartment market than in the house market.
+For apartments, a 60th rate and a 60th percentile occupancy rate has a better than 50% chance of being more profitable in a short term leasing strategy than a long term one.
+In fact, so long as an apartment is in the top 1/4 of occupancy rates, it is more profitable in a short term strategy at almost any price point.
+Houses, on the other hand, need either very high rates or very high occupancies to justify a short-term rental.
+The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.
+First, the difference between the SVM Area and the Fitted number highlight the fact that even when transforming the axes into quantile, the data are still not uniformly distributed across the 2-dimensional space of the plot.
+This means that not all areas of the plot have equal weights in the Fitted value.
+Second, the Actual and SVM Area figures deviate because of the binary nature of the SVM process.
+For example, in many of the short-term preference in the apartment SVM plot there are some long-term preference data points, but just fewer than 50% of total, whereas in the long-term preference areas on the left hand side of the plot nearly all of the points are long-term preference.
+The results of the SVM process are the result of a sort of 'gerrymandering' where a clustering by one faction and a dispersal by another can create a result that is not representative of the underlying base population.
+Despite this fact, we feel that the SVM Area values are useful for the owner in our scenario because they provide both a value and visual guide that present the possibilities of being more profitable with a short-term strategy, not just what the current distribution of such properties are.
 
@@
 
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'}
+
+ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2)
+
+```
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'}
+
+ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2)
+
+```
+
 #### Geographic Submarkets
 
-* Need to explain this.
+1. Need to explain this.
 
 ```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Submarket'}
+ names(sm.results)[[1]] <- 'core'
 
@@
 
-*Logistic regression to explain what is correlated with short-term preference
-*3 Model approach, increasing complexity
-*Need to explain log odds, interpretation, etc.
+1. Logistic regression to explain what is correlated with short-term preference
+2. 3 Model approach, increasing complexity
+3. Need to explain log odds, interpretation, etc.
 
 ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-#full.table$Str.Model <- gsub(" ", "&nbsp;", full.table$Str.Model, fixed=TRUE)
  x.full <- xtable(full.table)
@@
 
+<!-- Heat map with other characteristics on axis
+
 <!-- ### Submarkets -->

### 2017-01-11 abbReturns_Working.R

@@ -77,6 +77,10 @@
   abb.imp <- imp.data$abb
   ltr.imp <- imp.data$ltr
   
+  # Extract models
+  abb.sum <- summary(imp.data$abb.mod)
+  ltr.sum <- summary(imp.data$ltr.mod)
+  
  # Within type imputation revenues
   
   imp.revs <- revenueEngine(abb.imp, 
@@ -674,13 +678,9 @@
   
   save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_results.RData")
 
-# 
-#  
-#  smt.data$GperBed <- smt.data$max.guests/smt.data$bedrooms
-#  smt.data$Strict <- ifelse(smt.data$cancel.policy=='Strict', 1, 0)
-#  smt.data$Flexible <- ifelse(smt.data$cancel.policy=='Flexible', 1, 0)
+  save(abb.revs, ltr.revs, clean.count, blank.plot,
+       rate.hm, rate.hm.svm, qtl.hm, qtl.hm.svm, market.ratio, 
+       house, apt, sm.results, full.table, smt.results, bb.results,
+       abb.sum, ltr.sum, ann.df, mrkt.table, num.df, reason.df,
+       file="C:/Dropbox/Research/airBNB/data/analyzed/abb_objs.RData")
  
-  
-  
-  
-  

### 2017-01-12 abbReturns_Writeup.Rmd
added logistic explanation

@@
 Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.
+
 Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments.
@@
 
-1. Need to explain this.
-
-```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Submarket'}
- names(sm.results)[[1]] <- 'core'
-
- sm.table <- rbind(sm.results$core$mrkt.score,
-                     sm.results$city$mrkt.score,
-                     sm.results$suburban$mrkt.score,
-                     sm.results$rural$mrkt.score,
-                     sm.results$beach$mrkt.score)
-
- sm.table$sub.market <- c('core', '', 'city', '', 'suburban', ''
-                            , 'rural', '', 'beach', '')
- sm.table <- sm.table[,c(5,1:4)]
- print(xtable(sm.table,
-       digits=3),
-       include.rownames=FALSE, hline.after=c(-1,0,2,4,6,8,10))
-
-```
-
-Logistic Regression
-
-1. Logistic regression to explain what is correlated with short-term preference
-2. 3 Model approach, increasing complexity
-3. Need to explain log odds, interpretation, etc.
-
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 5.
+In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
+Interestingly, the rural area has a higher probably than all other but the core.
+This is likely explained by the fact that there are few rural properties and those that are show some clustering near rural tourists activities like the Yarra Valley wine region (Figure 7).
+
+In the core and the city, apartments offer a higher probability than homes, the reverse in true in the suburban and rural areas.
+In the lower density areas it appears that tourists may prefer larger and more spacious dwellings and are willing to pay a premium for them, compared to long-term renters who may experience long commutes from these fringe locations.
+
+Looking at the 'fitted' and 'svm area' figures we see a trend that these svm figures are higher than the actual observed for the core apartment and lower for nearly all of the rest of the categories.
+This findings shows that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
+In other words, there is well defined combination or situation in which these properties can be more profitable than in a long-term lease.
+The reverse is true of the city core apartments.
+Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Quantile Market Summary; Property Type by Submarket'}
+
+sm.ms <- rbind.fill(lapply(sm.results, function(x) x$mrkt.score[2,]))
+sm.ms.apt <- rbind.fill(lapply(smt.results[1:5], function(x) x$mrkt.score[2,]))
+sm.ms.house <- rbind.fill(lapply(smt.results[6:10], function(x) x$mrkt.score[2,]))
+
+smt.table <- data.frame(sub.market=c('sub-market','beach', 'city', 'core', 'rural',
+                                     'suburban', 'all'),
+                        actual.all=c('all', round(sm.ms$actual[c(5,2,1,4,3)],2),
+                                     round(market.ratio[2,2],2)),
+                        actual.apt=c('apt', round(sm.ms.apt$actual, 2),
+                                     round(type.table[2,3],2)),
+                        actual.house=c('house', round(sm.ms.house$actual, 2),
+                                       round(type.table[4,3],2)),
+                        fitted.all=c('all',round(sm.ms$fitted[c(5,2,1,4,3)],2),
+                                     round(market.ratio[2,3],2)),
+                        fitted.apt=c('apt', round(sm.ms.apt$fitted,2),
+                                     round(type.table[2,4],2)),
+                        fitted.house=c('house', round(sm.ms.house$fitted,2),
+                                       round(type.table[4,4],2)),
+                        svmarea.all=c('all', round(sm.ms$svm[c(5,2,1,4,3)],2),
+                                      round(market.ratio[2,4],2)),
+                        svmarea.apt=c('apt', round(sm.ms.apt$svm,2),
+                                      round(type.table[2,5],2)),
+                        svmarea.house=c('house', round(sm.ms.house$svm,2),
+                                        round(type.table[4,5],2)))
+
+smt.table <- smt.table[c(1, 4, 3, 2, 6, 5, 7),]
+names(smt.table) <- c('', '', 'actual', '', '', 'fitted', '', '',
+                      'svm area', '')
+smt.full <- xtable(smt.table)
+align(smt.full) <- 'll|rrr|rrr|rrr'
+print(smt.full, 
+       include.rownames=FALSE, 
+       hline.after=c(-1,0,1,6,7,7))
+
+```
+
+## Explaining Preference
+
+The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually  more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
+This proportion, however, varied by location and property type.
+While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
+To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
+
+We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of:
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon
+\end{equation}
+
+where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+
+For model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon
+\end{equation}
+
+Finally, in Model three we add three variables describing policies set by the Airbnb hosts:
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt +
+\beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon
+\end{equation}
+
+where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
+We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
+We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).
+
+The results of all three models are shown in Table 6.
+For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.
+As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
+
+In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
+Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference.
+
+Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
+These findings mirror those found above in Table 9.
+The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
+
+Finally, in Model 3 we add in host behavior or policies.
+Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
+This variable may be operating a proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.
+The greater the minimum stay, the lower the probability of short-term preference.
+Longer minimum stay may equate to lower occupancy rates as one or two night travelers are exempted from the property.
+Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.
+Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a weak, but positive relationship with short-term preference.
+Strict policies do help maintain revenues, but may also scare off some potential guests.
+Strict cancellation may be a luxury for the best and highly desired properties on the market and, within out model, may be acting as a proxy for some unobserved measure of quality or demand.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
+
+ names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
  x.full <- xtable(full.table)

### 2017-01-14 abbReturns_Working.R
fixed imp rent bug

@@ -141,7 +141,7 @@
   
   
   # 
-  
+  mrkt.table$est[c(1:5, 11:15)] <- 'Imp. Rates & Rents'
   mrkt.table$x <- 0
   mrkt.table$y <- 0
   mrkt.table$good <- c(rep('bad', 5), rep('good', 5), rep('bad', 10))

### 2017-01-14 abbReturns_Writeup.Rmd
final pass of first draft

@@
   options(xtable.comment = FALSE)
+  options(xtable.caption.placement='top')
 
@@
 
-Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments.
+Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' @fuller2014stop has re-focused some of the problems of short term rentals on large, urban environments.
 With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.
@@
 Of the three types of research -- pricing, impacts on housing market and legalities/externalities -- none specifically address the decision faced by an owner who is trying to decide between a long- or short-term leasing strategy.
-The closest analog in the literature is a piece by @larsen2009purchase examining the choice between purchasing a time-share or simply paying for hotel rooms.
+The closest analog in the literature is a piece by @larson2009pur examining the choice between purchasing a time-share or simply paying for hotel rooms.
 Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
@@
 A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
+
 ### Comparison
@@
 Nearly every multi-family dwelling is owned as a condominium.
-See @Berry2000investment for more information on the overall structure of the Australian market].
+See @berry2000investment for more information on the overall structure of the Australian market].
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
@@
 As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
-Unfortunately, this filter does remove about 40% of the short-term data (See Figure 2), however, given the research question it is unavoidable.
+Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable.
 
@@
 We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
-For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5 (Figure 3).
+For both short and long term rentals we see that most apartments have less than four bedrooms and houses less than five (Figure 3).
 We filter the data accordingly.
@@
 We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apartment/house.
-Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly (Figure 4).
+Here we see that nearly all properties have three or fewer bathrooms and we filter the data accordingly (Figure 4).
 A few short term properties indicate no baths, which is likely an error so we remove these observations from the data.
@@
 
- print(xtable(c.subs, caption = 'List of Core Suburbs'),
+ print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
        include.rownames=F,
@@
 options(xtable.comment = FALSE)
-print(xtable(clean.table,
+print(xtable(clean.table, caption='Data Cleaning Summary\n',
        digits=0),
-       include.rownames=FALSE)
+       include.rownames=FALSE,
+       caption.placement='top')
 
@@
 
-where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
 
@@
 
-```{r, results="asis", echo=FALSE, fig.cap='Imputation Model Diagnostics'}
+```{r, results="asis", echo=FALSE}
 
@@
 s.table <- xtable(summ.table,
+                  caption='Imputation Model Diagnostics\n',
                   digits=3)
@@
 print(s.table, 
-       include.rownames=TRUE)
+       include.rownames=TRUE,
+                  caption.placement='top')
 
@@
 
-```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4}
+```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4, fig.cap='Revenue Comparison Types'}
 
@@
                        est=c('Actual Rates & Rents', 'Actual Rates & Rents',
-                             'Imputed Rates & Rents', 'Imputed Rates & Rents'),
+                             'Imp. Rates & Rents', 'Imp. Rates & Rents'),
                        data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
@@
 The variation between these estimates is significant and troublesome.
-However, given our difficulty in accurately estimating short term nightly rates (see Table 2) and the fact that occupancy rates are highly variable for short-term rentals, these variations are not surprising.
+However, given our difficulty in accurately estimating short term nightly rates (see Table 3) and the fact that occupancy rates are highly variable for short-term rentals, these variations are not surprising.
 As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
@@
 
-```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center'}
+```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center', fig.cap='Summary of Comparison Types'}
 
@@
 
-```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center'}
+```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center', fig.cap='Comparison Types: Strengths and Weaknesses'}
 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=3.5, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4, fig.height=3, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'}
 
@@
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In Figure 15 (left panel) we plot nightly rates versus occupancy rates.
+In Figure 16 (left panel) we plot nightly rates versus occupancy rates.
 We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
@@
 This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
-While the left panel of Figure 15 helps show the general pattern is doe leave many indeterminate areas.
+While the left panel of Figure 16 helps show the general pattern is does leave many indeterminate areas.
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
@@
 
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 15 may be misleading.
-We convert both axis to quantiles and replot both in Figure 16.
+Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 16 may be misleading.
+We convert both axis to quantiles and replot both in Figure 17.
 Here we see a more even distibution of points across the figures.
@@
 
-```{r, results="asis", comment=FALSE,  echo=FALSE, fig.cap='Preference Analysis: Metro Area'}
+```{r, results="asis", comment=FALSE,  echo=FALSE}
 
 names(market.ratio) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
-print(xtable(market.ratio,
+print(xtable(market.ratio, caption='Metro Level: Short-Term Preference Analysis\n',
        digits=3),
-       include.rownames=FALSE)
+       include.rownames=FALSE,
+      caption.placement='top')
 
@@
 We then rerun the entire analysis described above for the house and the apartment markets separately.
-Table X and Figures X (houses) and Y (apartments) illustrate the metrics for these two sub-markets.
+Table 5 and Figures 18 (houses) and 19 (apartments) illustrate the metrics for these two sub-markets.
 The raw probability data shows that over 33% of apartments are more profitable in short term leasing as opposed to just 22% of houses.
@@
 Houses, on the other hand, need either very high rates or very high occupancies to justify a short-term rental.
+
 The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.
@@
  names(type.table) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
- print(xtable(type.table,
+ print(xtable(type.table, caption='Short-term Preference Analysis: By Property Type\n',
        digits=3),
-       include.rownames=FALSE, hline.after=c(-1,0,2,4))
+       include.rownames=FALSE, hline.after=c(-1,0,2,4),
+       caption.placment='top')
 
@@
 
-We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 5.
+We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
 In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
 Interestingly, the rural area has a higher probably than all other but the core.
-This is likely explained by the fact that there are few rural properties and those that are show some clustering near rural tourists activities like the Yarra Valley wine region (Figure 7).
+This is likely explained by the fact that there are few rural properties and those that are show some clustering near rural tourists activities like the Yarra Valley wine region (Figure 8).
 
@@
                       'svm area', '')
-smt.full <- xtable(smt.table)
+smt.full <- xtable(smt.table,
+                   caption='Short-Term Preference Analysis: Disaggregated\n')
 align(smt.full) <- 'll|rrr|rrr|rrr'
@@
        include.rownames=FALSE, 
-       hline.after=c(-1,0,1,6,7,7))
+       hline.after=c(-1,0,1,6,7,7),
+                   caption.placement='top')
 
@@
 
-For model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
+For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
 
@@
 
-Finally, in Model three we add three variables describing policies set by the Airbnb hosts:
+Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts:
 
@@
 
-The results of all three models are shown in Table 6.
+The results of all three models are shown in Table 7.
 For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.
@@
  names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
- x.full <- xtable(full.table)
+ x.full <- xtable(full.table,
+                  caption='Logistic Modeling Results\n')
  align(x.full) <- 'lllll'
@@
        include.rownames=FALSE, 
-       hline.after=c(-1,0,15,20,20))
+       hline.after=c(-1,0,15,20,20), 
+       caption.placement='top')
 
@@
 
+## Discussion
+
+Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+This work attempts to fill this void.
+
+The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
+However, of this total, only 6,600 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
+Of these, only 4,400 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+We caution future researchers and policy analysts to look deeply at initial estimates of Airbnb counts as many of the listings on the market are either room shares and/or not active.
+
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
+However, there is long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, on Airbnb than they would on the long-term market.
+This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).
+Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
+
+To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
+The shared information that is available on both sets of properties is limited.
+Our initial work found estimating long term rental values and tenant search times for the short term properties to be feasible with these data constraints while the opposite is much more difficult.
+In other words, there appear to by many unobserved variables (presense of wi-fi, parking and laundry facilities) and/or none-property specific characteristics (such as minimum stays, pet policies, number of allowed guests, cancellation policies) that influence short term nightly rates and occupancy rates.
+As a result, we were not able to accurately estimate likely short-term rates for the long-term observations.
+
+In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
+As expected, this probability is not equal across space, property type or property size (bed and bath count).
+Apartments are much more likely than houses to be more profitable as a short term rental.
+Core city properties are more likely than more outlying properties to prefer a short-term strategy, as a larger properties versus smaller ones.
+For instance, 45\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market.
+Examining only apartments with at least three bedrooms and two baths that figure increases to 60\%.
+
+The nightly rates and total occupancies drive the profitability of short-term leasing.
+As the nightly rate vs.
+occupancy rate heat maps and SVM plots (Figures 16, 17, 18 and 19) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the median in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
+A 40\% occupancy rate means bookings at least three days out of every week all year long.
+In Melbourne summers this may be an easy feat as tourist numbers swell, but doing so on a cold week in July likely proves more difficult.
+
+In the logistic regression models than we estimate (Table 7), we see that most of the finding from the univariate and bivariate analyses done early are validated.
+Large apartments in the central city are the best bet for generating greater revenues through short term leasing.
+We also test for the impact of host behavior on the probability of short term preference.
+We find that more flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short term preference probability).
+As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
+
+### Limitations and Future Research
+
+There are a number of limitations to this research.
+There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
+Part of the difficulty in estimating potential short-term rates for long-term properties is that the short term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
+Future research should focus both on building better models to explain (and ultimately predict) short term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short term market.
+It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
+
+Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
+Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
+
+In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
+We have done so as we were unable to location any evidence to suggest that one was higher than the other.
+This may be a limitation of our study and could prove to be an avenue of future research.
+
+Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
+In reality, the possibilities may not be so rigid.
+For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourist swell in the summer months, an enterprising owner maybe able to pair long term leasing during the off-season with short-term leasing during peak times to maximize revenues.
+In general, the rise of Airbnb and related portals give properties owners more options, and therefore more opportunities, to maximize returns on their property.
+Future research should expand our scenario to look at more than just a single binary option over a fixed period.
+We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
+
 ## References

### 2017-01-20 abb_ExecSumm.Rmd
add exec summary

---
title: "Should I Airbnb my Property?:  \n Executive Summary"
author: "Andy Krause and Gideon Aschwanden"
date: "January 16, 2017"
output: pdf_document
---

This research sets out to test under which conditions, if any, a short-term leasing strategy (Airbnb) generates more revenue than a traditional long-term approach.  Our data and analysis focus on the Melbourne metropolitan region.  To make comparisons between short and long-term markets we analyze observed and estimated revenues for a particular scenario where a property owner purchases a property on September 1 2015 and makes a decision between long or short-term rental for the next 12 months.

Our exploratory analysis shows that the univariate distribution of actual short-term revenues (from Airbnb) is much more variable than observed long term revenue.  Most Airbnb'd properties makes less but some make more, much more. To form a better comparison of revenues between like properties, we impute likely long-term revenues for the short-term properties using a model based on the long-term rental market observations. Over the entire market, we find that 31\% of the Airbnb properties did collect more revenue than they would likely do so with a long-term leasing strategy.  The probability of preference for a short-term strategy, however, is not equal for all types of properties.  More specifically, we find that short-term preference is higher in:

1. Apartments versus homes
2. Larger properties versus smaller properties
3. Properties in the city core (central 18 suburbs)
4. Rural areas as opposed to suburban (but not versus city properties)

We also find the following host behaviors or policies to result in higher probability of short-term preference:

1. More allowed guests per bedroom
2. Shorter minimum stays
3. More strict cancellation policies

Overall, we find that, indeed, some properties may generate more revenue under a short-term approach than in a long-term strategy. The probability of acheiving short-term preference is highest for large apartments in the city core with low minimum stays, strict cancellation policies and a high number of guests per bedroom. However, even within the core city apartment market an owner must achieve a nightly rate and an overall occupancy rate both above the median in order to reach an equal probability of short-term preference.  In other words, there is solid competition in this market and short-term preference depends on proper pricing and high occupancy.

It is no surprise, given these results, that inner city apartment make up a large proportion of the Airbnb market in Melbourne.  The market appears aware, to some extent, of the profitability of this property type under a short-term approach.

### 2017-01-23 abbReturns_Working.R
removing surfaces

@@ -781,7 +781,7 @@
        rate.hm, rate.hm.svm, qtl.hm, qtl.hm.svm, market.ratio, 
        house, apt, sm.results, full.table, smt.results, bb.results,
        abb.sum, ltr.sum, ann.df, mrkt.table, num.df, reason.df, subs,
-       suburbs.shp, s.suburbs, surf.list, coef.df,
+       suburbs.shp, s.suburbs, coef.df,
        file="C:/Dropbox/Research/airBNB/data/analyzed/abb_objs.RData")
  
 

### 2017-01-25 abbReturns_Script.Rmd
Addin working analysis to script

@@
   source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
+  source("c:/code/spatialtools/point2surface_Tools.R")
+  source("c:/code/spatialtools/spatiallogitmodels.R")
 
@@
 
-save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
+#save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
 
@@
 
-## Cross impute rates and ltrs
-
-### Global
-
-### By submarkets
-
-### Matching for validation
-
-### - Short to Long
-
-### - Long to Short
-
-## Vacancy Models
-
-# Estimate the ltral income for all properties
-
-## Other costs/fees/income considerations
-
-## Overall rate of return calculations and comparisons
-
-### - Rates by Product Type (Bed/Bath)
-
-### - Rates by Location (Suburb)
-
-### - Rates by Proximity (Near train stations / beach / event grounds, etc.)
+## Global Market Analysis
+
+We now analyze the full metro market to test which properties are more profitable as short-term rentals.
+
+We start by specifying the imputation models for the LTR and the Airbnb datasets
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb))
+
+```
+
+We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
+                               abb.df=abb.data, 
+                               ltr.mod.spec=ltr.mod.spec, 
+                               abb.mod.spec=abb.mod.spec,
+                               clip.field='suburb')
+
+```
+
+From the imputed results, we extract the base data (with imputed values) as well as the model summaries.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Extract out DFs (only those that imputed)
+  abb.imp <- imp.data$abb
+  ltr.imp <- imp.data$ltr
+
+  # Extract models
+  abb.sum <- summary(imp.data$abb.mod)
+  ltr.sum <- summary(imp.data$ltr.mod)
+
+```
+
+We use the base data to impute the likely annual revenue for each tenure type (within tenure). These estimates are added back to the base data.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  imp.revs <- revenueEngine(abb.imp, 
+                            ltr.imp,
+                            rate.field='imp.rate',
+                            rent.field='imp.rent')
+
+  abb.imp$imp.revenue <- imp.revs$abb
+  ltr.imp$imp.revenue <- imp.revs$ltr
+
+```
+
+Next we cross impute days on market and occupancy rates.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Apply dom to abb
+  abb.imp$imp.dom <- imputeDOM(abb.imp, ltr.imp, calc.type='median')
+
+  # Apply occ.rate to ltr
+  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, abb.imp, calc.type='median')
+
+```
+
+With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  impx.revs <- revenueEngine(abb.df=ltr.imp, 
+                             ltr.df=abb.imp,
+                             rate.field='imp.rate',
+                             rent.field='imp.rent',
+                             occ.field='imp.occ',
+                             dom.field='imp.dom')
+
+  abb.imp$imp.ltr.revenue <- impx.revs$ltr
+  ltr.imp$imp.abb.revenue <- impx.revs$abb
+
+```
+
+Next, we compare the revenues from the two and extract the new datasets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  comp.revs <- compareRevenues(abb.imp, ltr.imp)
+
+  abb.revs <- comp.revs$abb
+  ltr.revs <- comp.revs$ltr
+
+```
+
+### Analyze Results
+
+First we make a comparison table of the results, broken down by submarket.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mrkt.table <- createCompTable(abb.revs, ltr.revs, 'sub.mrkt')
+  mrkt.table$ID <- factor(mrkt.table$ID, 
+                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+
+```
+
+We plot these results in a 2x2 matrix to show the preference likelihoods under the 4 possible scenarios.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ twotwo.bar.plot <- 
+    ggplot(mrkt.table, 
+                            aes(x=ID, weights=Var, fill=ID)) + 
+    geom_bar() +
+    facet_grid(est ~ data) +
+    scale_fill_manual(values=sm.col) +
+    xlab('') +
+    ylab('% of properties where Airbnb is more profitable') +
+    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none')
+
+```
+
+We find the results from the four highly variable.
+Much of this is due to the unreliability of the occupancy and nightly rate estimates for the LTR data.
+We build a set of diagrams and charts to explain the differences.
+
+First, we build out the information for each diagram
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ mrkt.table$est[c(1:5, 11:15)] <- 'Imp. Rates & Rents'
+  mrkt.table$x <- 0
+  mrkt.table$y <- 0
+  mrkt.table$good <- c(rep('bad', 5), rep('good', 5), rep('bad', 10))
+
+  blank.plot <- ggplot(mrkt.table, 
+         aes(x=x, y=y)) +
+    facet_grid(est ~ data) +
+    scale_fill_manual(values=c('salmon', 'lightgreen')) +
+    theme(legend.position='none',
+          axis.line=element_blank(),
+          axis.text.x=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.grid.major = element_blank())
+
+  ann.df <- data.frame(x=rep(0, 4),
+                      y=rep(0, 4), 
+                      lab=c(paste0('Airbnb Properties: \n (Actual Airbnb Revenue \n vs.',
+                                   '\n Imputed Long Term Revenue)'),
+                            paste0('Long-Term Properties: \n (Imputed Airbnb Revenue \n vs.',
+                                   '\n Actual Long Term Revenue)'),
+                            paste0('Airbnb Properties: \n (Imputed Airbnb Revenue \n vs.',
+                                   '\n Imputed Long Term Revenue)'),
+                            paste0('Long-Term Properties: \n (Imputed Airbnb Revenue \n vs.',
+                                   '\n Imputed Long Term Revenue)')),
+                      est=c('Actual Rates & Rents', 'Actual Rates & Rents',
+                            'Imp. Rates & Rents', 'Imp. Rates & Rents'),
+                      data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
+
+  reason.df <- data.frame(x=rep(0, 4),
+                       y=rep(0, 4), 
+                       lab=c(paste0('+ Actual occupancy rates \n',
+                                    '+ Actual nightly rates'),
+                             paste0('- Imputed occupancy rates \n',
+                                    '- Imputed nightly rate estimates'),
+                             paste0('+ Actual occupancy rates \n', 
+                                    '- Imputed nightly rate estimates'),
+                             paste0('- Imputed occupancy rates \n',
+                                    '- Imputed nightly rate estimates')),
+                       est=c('Actual Rates & Rents', 'Actual Rates & Rents',
+                             'Imp. Rates & Rents', 'Imp. Rates & Rents'),
+                       data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
+
+  num.df <- data.frame(x=rep(0, 4),
+                       y=rep(.8, 4),
+                       est=as.factor(c('Actual Rates & Rents', 'Imp. Rates & Rents',
+                             'Actual Rates & Rents', 'Imp. Rates & Rents')),
+                       data=as.factor(c('Airbnb', 'Airbnb', 'Long-Term', 'Long-Term')),
+                       count=c(1,3,2,4))
+
+```
+
+We then construct a plot explaining the data/imputations involved
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  explain.plot <- blank.plot +
+    geom_text(data=ann.df,
+              label=ann.df$lab,
+              size=3) +
+    geom_text(data=num.df,
+              label=num.df$count,
+              size=9.5) +
+    coord_cartesian(ylim=c(-.5,1))
+
+```
+
+And then a plot that gives the reasons for selecting only the upper left scenario.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  reason.plot <- blank.plot +
+    geom_rect(data = mrkt.table, aes(fill=good),
+              xmin = -Inf,xmax = Inf,
+              ymin = -Inf,ymax = Inf, alpha = 0.4) +
+    geom_text(data=reason.df,
+              label=reason.df$lab,
+              size=3) +
+    geom_text(data=num.df,
+              label=num.df$count,
+              size=9.5) +
+    coord_cartesian(ylim=c(-.5,1))
+
+```
+
+From the upper left we make a simpler table and plot the preferences by submarket.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  abb.act.table <- mrkt.table[mrkt.table$est == 'Actual Rates & Rents' &
+                               mrkt.table$data == 'Airbnb', ]
+
+  abb.act.plot <- 
+    ggplot(abb.act.table, 
+           aes(x=ID, weights=Var, fill=ID)) + 
+    geom_bar() +
+    scale_fill_manual(values=sm.col) +
+    xlab('') +
+    ylab('% of properties where Airbnb is more profitable') +
+    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') +
+    coord_cartesian(ylim=c(0,1))
+
+```
+
+Next, we plot the \% of properties that have short-term preference versus the occupancy rate
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rawocc.pplot <- makePrefPlot(abb.revs,
+                               x.field='occ.rate',
+                               y.field='abb.act',
+                               group.field='sub.mrkt',
+                               smooth=TRUE,
+                               smooth.span=.75)
+  rawocc.pplot <- rawocc.pplot +
+    xlab('\nOccupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col)
+
+```
+
+Looking at the distribution of occupancy rates, we that it is not uniform in any of the submarkets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  abb.revs$sub.mrkt <- factor(abb.revs$sub.mrkt, 
+                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+  ggplot(abb.revs, aes(x=occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
+    geom_density(alpha=.3) +
+    facet_wrap(~sub.mrkt) +
+    scale_color_manual(values=sm.col) +
+    scale_fill_manual(values=sm.col) +
+    scale_x_continuous(breaks=seq(0, 1, by=.5),
+                       labels=c('0%', '50%', '100%')) +
+    ylab('') +
+    xlab('Occupancy Rate') +
+    theme(legend.position='none',
+          axis.line=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks=element_blank(),
+          axis.title.y=element_blank())
+
+```
+
+We then calculate quantile values for rates and replot the charts
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, 
+                                      return.type='rank') 
+  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, 
+                                  return.type='rank')
+
+  ## Make quartile location plot
+
+  qtlocc.pplot <- makePrefPlot(abb.revs,
+                               x.field='occ.qtl',
+                               y.field='abb.act',
+                               group.field='sub.mrkt',
+                               smooth=TRUE,
+                               smooth.span=.75)
+  qtlocc.pplot <- qtlocc.pplot +
+    xlab('\nQualtile of Occupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col)
+
+```
+
+Next we build a heat map that shows which combinations of occ rate and nightly rate are most likely to result in short-term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm <- makeHeatMap(abb.revs,
+                x.field='occ.rate',
+                y.field='nightly.rate',
+                color.field='abb.act',
+                bins=c(.05, 25),
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+
+  rate.hm <- rate.hm +
+    xlab('\n Occupancy Rate') +
+    ylab('\n Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom')
+
+```
+
+To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm.svm <- makeHeatMap(abb.revs,
+                         x.field='occ.rate',
+                         y.field='nightly.rate',
+                         color.field='abb.act',
+                         bins=c(.05, 25),
+                         svm=T, 
+                         alpha.count=F,
+                         add.points=T,
+                         fill.colors=c(abb.col[1], abb.col[5]))
+
+  rate.hm.svm <- rate.hm.svm +
+    xlab('\n Occupancy Rate') +
+    ylab('\n Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom')
+
+```
+
+Again, due to the non-uniformity of distribution of these two axis, we convert to quantiles and re-plot.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm <- makeHeatMap(abb.revs,
+                         x.field='occ.qtl',
+                         y.field='rate.qtl',
+                         color.field='abb.act',
+                         bins=c(5, 5),
+                         svm=F, 
+                         alpha.count=T,
+                         add.points=T,
+                         fill.colors=c(abb.col[1], abb.col[5]))
+
+  qtl.hm <- qtl.hm +
+    xlab('\n Quantile of Occupancy Rate') +
+    ylab('\n Quantile of Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    theme(legend.position='bottom')
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm.svm <- makeHeatMap(abb.revs,
+                        x.field='occ.qtl',
+                        y.field='rate.qtl',
+                        color.field='abb.act',
+                        bins=c(5, 5),
+                        svm=T, 
+                        alpha.count=F,
+                        add.points=T,
+                        fill.colors=c(abb.col[1], abb.col[5]))
+
+  qtl.hm.svm <- qtl.hm.svm +
+    xlab('\n Quantile of Occupancy Rate') +
+    ylab('\n Quantile of Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    theme(legend.position='bottom')
+
+```
+
+Finally, we calculate the areas of the heat maps and combine into a table.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  svm.rate <- makeSVM(abb.revs,
+                     x.field='occ.rate',
+                     y.field='nightly.rate',
+                     z.field='abb.act',
+                     svm.type='C-svc',
+                     svm.kernel='polydot',
+                     poly.degree=4,
+                     expand.factor=100)
+
+  svm.qtl <- makeSVM(abb.revs,
+                      x.field='occ.qtl',
+                      y.field='rate.qtl',
+                      z.field='abb.act',
+                      svm.type='C-svc',
+                      svm.kernel='polydot',
+                      poly.degree=4,
+                      expand.factor=100)
+
+  market.ratio <- data.frame(type=c('rate', 'qtl'),
+                             actual=rep(mean(abb.revs$abb.act), 2),
+                             fitted=c(mean(svm.rate$orig$fitted),
+                                      mean(svm.qtl$orig$fitted)),
+                             svm=c(mean(svm.rate$pred$pred),
+                                   mean(svm.qtl$pred$pred)))
+```
+
+### Submarkets
+
+We now take the analytical process just completed on the entire metro and apply it to various submarkets.  We use a custom function that combines all the processes above into a single command.
+
+#### Property Type
+
+We start by comparing apartments to houses.  First we set a new imputation model specification
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
+
+```
+
+We then recompute the market analysis for each property type.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Select data
+  abb.apt <- which(abb.revs$type == 'Apartment')
+  ltr.apt <- which(ltr.revs$type == 'Apartment')
+
+  # Estimate House Results  
+  house <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
+                              abb.df=abb.revs[-abb.apt, ],
+                              ltr.mod.spec=ltr.mod.spec,
+                              abb.mod.spec=abb.mod.spec,
+                              clip.field='suburb',
+                              market.field='none',
+                              mrkt.col=sm.col,
+                              heat.col=c(abb.col[1], abb.col[5]))
+
+   apt <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.apt,],
+                             abb.df=abb.revs[abb.apt, ],
+                             ltr.mod.spec=ltr.mod.spec,
+                             abb.mod.spec=abb.mod.spec,
+                             clip.field='suburb',
+                             market.field='sub.mrkt',
+                             mrkt.col=sm.col,
+                             heat.col=c(abb.col[1], abb.col[5]))
+
+```
+
+Below are the quantile heat maps showing the differences in results
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ggMultiPlots(house$qtl.hm.svm, apt$qtl.hm.svm, cols=2)
+
+```
+
+#### Geographic Submarkets
+
+We now do the same for geographic submarkets
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+# Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+                          as.factor(bedbath) +
+                          as.factor(suburb) + 
+                          as.factor(ltr.month))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
+                          as.factor(bedbath) +
+                          as.factor(suburb))
+
+  #  Extract levels and set capture
+  s.levels <- levels(abb.revs$sub.mrkt)
+  sm.results <- list()
+  sm.pos <- 1
+
+  # Estimate results
+  for(sm in s.levels){
+
+    abb.x <- which(abb.revs$sub.mrkt == sm)
+    ltr.x <- which(ltr.revs$sub.mrkt == sm)
+
+    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
+                                abb.df=abb.revs[abb.x, ],
+                                ltr.mod.spec=ltr.mod.spec,
+                                abb.mod.spec=abb.mod.spec,
+                                clip.field='suburb',
+                                market.field='sub.mrkt',
+                                mrkt.col=sm.col,
+                                heat.col=c(abb.col[1], abb.col[5]))
+
+    sm.results[[sm.pos]] <- x.res
+    sm.pos <- sm.pos + 1
+
+  }
+  names(sm.results) <- as.character(s.levels)
+
+```
+
+And for bed/bath combinations
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+                            as.factor(suburb) + 
+                            as.factor(ltr.month))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
+                            as.factor(suburb))
+
+  # Set levels and capture
+  bb.levels <- levels(abb.revs$bedbath)
+  bb.results <- list()
+  bb.pos <- 1
+
+  # Estimate results
+  for(bb in bb.levels){
+
+    abb.x <- which(abb.revs$bedbath == bb)
+    ltr.x <- which(ltr.revs$bedbath == bb)
+
+    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
+                                abb.df=abb.revs[abb.x, ],
+                                ltr.mod.spec=ltr.mod.spec,
+                                abb.mod.spec=abb.mod.spec,
+                                clip.field='suburb',
+                                market.field='bedbath',
+                                mrkt.col=sm.col,
+                                heat.col=c(abb.col[1], abb.col[5]))
+
+    bb.results[[bb.pos]] <- x.res
+    bb.pos <- bb.pos + 1
+
+  }
+  names(bb.results) <- as.character(bb.levels)
+
+```
+
+And by geo submarket and property type combined
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(suburb) + 
+                            as.factor(ltr.month))
+  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(suburb))
+
+  # Create smt variable  
+  abb.revs$smt <- as.factor(paste0(abb.revs$type, '.', abb.revs$sub.mrkt))
+  ltr.revs$smt <- as.factor(paste0(ltr.revs$type, '.', ltr.revs$sub.mrkt))
+
+  # Create levels and captures
+  smt.levels <- levels(abb.revs$smt)
+  smt.results <- list()
+  smt.pos <- 1
+
+  # Estimate the smt models
+  for(smt in smt.levels){
+
+    abb.x <- which(abb.revs$smt == smt)
+    ltr.x <- which(ltr.revs$smt == smt)
+
+    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
+                                abb.df=abb.revs[abb.x, ],
+                                ltr.mod.spec=ltr.mod.spec,
+                                abb.mod.spec=abb.mod.spec,
+                                clip.field='suburb',
+                                market.field='smt',
+                                mrkt.col=sm.col,
+                                heat.col=c(abb.col[1], abb.col[5]))
+
+    smt.results[[smt.pos]] <- x.res
+    smt.pos <- smt.pos + 1
+  }
+  names(smt.results) <- as.character(smt.levels)
+
+```
+
+### Further analysis
+
+The above present, essentially, univariate analyses of each of the submarkets in question.
+While illustrative, they do not hold constant other differences in co-variates that might affect short term preference.
+To better control for these influences we estimate a set of logistic regression model to estimate the impact of various variables on short-term preference.
+
+Before we begin, we do a bit of data preparation: extracting abb data and fixing the cancellation policy variable.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  smt.data <- rbind.fill(lapply(smt.results, function(x) x$abb))
+
+  ss60 <- which(smt.data$cancel.policy == 'Super Strict 60 Days')
+  smt.data$cancel.policy[ss60] <- 'Strict'
+  cpmiss <- which(smt.data$cancel.policy == '')
+  smt.data <- smt.data[-cpmiss, ]
+
+```
+
+First, we look only at structural characteristics.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.str <- glm(abb.act~type+as.factor(bedbath),
+                 family=binomial(link='logit'),
+                 data=smt.data)
+
+```
+
+We then add geographic submarkets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+   mod.sm <- glm(abb.act~type+as.factor(bedbath)+
+                  sub.mrkt,
+                 family=binomial(link='logit'),
+                 data=smt.data)
+
+```
+
+And, finally, host policy actions.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+   mod.host <- glm(abb.act~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                  family=binomial(link='logit'),
+                  data=smt.data)
+
+```
+
+We add suburb fixed effects and re-estimate the str and host models.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Suburb model
+  mod.sub <- glm(abb.act~type+as.factor(bedbath)+
+                   suburb,
+                 family=binomial(link='logit'),
+                 data=smt.data)
+
+  # Suburb Host model
+  mod.subh <- glm(abb.act~type+as.factor(bedbath)+
+                  suburb+
+                  max.guests+min.stay+
+                  I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                  family=binomial(link='logit'),
+                  data=smt.data)
+
+```
+
+We then extract the coefficients and diagnostics and build a table for viewing purposes.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Extract Coef
+
+  str.ct <- summary(mod.str)$coef
+  sm.ct <- summary(mod.sm)$coef
+  host.ct <- summary(mod.host)$coef
+
+  # Assign SS
+  f.l <- nrow(host.ct)
+  assignSS <- function(x){
+
+    y<-rep('   ', length(x))
+    y[x<.1] <- '*  '
+    y[x<.05] <- '** '
+    y[x<.01] <- '***'
+
+    y
+  }
+
+  # Build coefs with SS
+  str.coef <- sprintf("%.3f" ,str.ct[,1])
+  str.sig <- assignSS(str.ct[,4])
+  str.coef <- c(paste0(str.coef, str.sig), rep(' ', f.l - nrow(str.ct)))
+
+  sm.coef <- sprintf("%.3f" ,sm.ct[,1])
+  sm.sig <- assignSS(sm.ct[,4])
+  sm.coef <- c(paste0(sm.coef, sm.sig), rep(' ', f.l - nrow(sm.ct)))
+
+  host.coef <- sprintf("%.3f" ,host.ct[,1])
+  host.sig <- assignSS(host.ct[,4])
+  host.coef <- c(paste0(host.coef, host.sig), rep(' ', f.l - nrow(host.ct)))
+
+  # Combine into table
+  mod.table <- data.frame(Variable=rownames(host.ct),
+                          Str.Model=str.coef,
+                          Sm.Model=sm.coef,
+                          Host.Model=host.coef)
+
+  # Fix variable names
+  mod.table$Variable <- c('Intercept', 'House', '1Bed/1Bath','2Bed/1Bath',
+                          '3Bed/1Bath', '3Bed/2Bath', '4Bed/2Bath', 'City',
+                          'Suburban','Rural', 'Beach', 'Guests/Bedroom',
+                          'Min. Stay', 'Flexible Cancel', 'Strict Cancel')
+
+ ## Create model diagnostics
+
+  # Custom function
+  logDx <- function(log.model, data, resp.var){
+
+    pred <- prediction(predict(log.model, data, type='response'), resp.var)
+    auc <- performance(pred, measure='auc')
+    ll <- logLik(log.model)
+    AIC <- AIC(log.model)
+
+    return(list(AIC=AIC,
+                logLik=ll,
+                auc=auc))
+  }
+
+  # Extract diagnostics
+  str.dx <- logDx(mod.str, smt.data, smt.data$abb.act)
+  sm.dx <- logDx(mod.sm, smt.data, smt.data$abb.act)
+  host.dx <- logDx(mod.host, smt.data, smt.data$abb.act)
+
+  # Create diagnostic table
+  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik', 'AUC'),
+                           Str.Model=c('', '', round(str.dx$AIC,0), 
+                                       round(str.dx$logLik, 0),
+                                       round(as.numeric(str.dx$auc@y.values), 3)),
+                           Sm.Model=c('', '', round(sm.dx$AIC,0), 
+                                      round(sm.dx$logLik, 0),
+                                      round(as.numeric(sm.dx$auc@y.values), 3)),
+                           Host.Model=c('', '', round(host.dx$AIC,0), 
+                                        round(host.dx$logLik, 0),
+                                        round(as.numeric(host.dx$auc@y.values), 3)))
+
+ ## Combine into full table of coef and diags
+
+ full.table <- rbind(mod.table, diag.table)
+
+```
+
+### Moving Window Logit
+
+To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.
+Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties.
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
+                              proj4string=CRS("+init=epsg:4283"),
+                              delete_null_obj=TRUE)
+
+ ssubs <- table(abb.revs$suburb)
+ s.subs <- subs[subs$id %in% names(ssubs),]
+ s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),]
+ sssubs <- fortify(s.suburbs)
+
+```
+
+Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Min, Max and Range
+ xmin <- min(s.subs$long)
+ xmax <- max(s.subs$long)
+ ymin <- min(s.subs$lat)
+ ymax <- max(s.subs$lat)
+ xrange <- xmax-xmin
+ yrange <- ymax-ymin
+
+ # Set Scale
+ scale <- mean(xrange, yrange)/100
+
+ # Create estimation points
+ est.data <- abb.revs
+ est.points <- createGridPoints(s.suburbs, scale, T)
+
+```
+
+We then specify the logistic regression model and set the moving window bandwidth.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Set model specification
+
+ mod.spec <- abb.act ~ type + as.factor(bedbath) + 
+   I(max.guests / bedrooms) + min.stay + 
+   I(cancel.policy == 'Flexible') + 
+   I(cancel.policy == 'Strict')
+
+ ## Set bandwidth
+
+ k <- 400
+
+```
+
+The results are estimated with the custom MWL function
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ mwl.results <- mwl(est.data, 
+                    est.points, 
+                    mod.spec, 
+                    k)
+
+```
+
+Coefficents are extracted and put into a data.frame
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+# Extract coef Names
+ coef.names <- rownames(mwl.results[[1]])
+
+ # Create a list to capture
+ coef.list <- list()
+
+ # Create a data.frame to capture
+ coef.df <- data.frame(lat=est.points@coords[,2],
+                       long=est.points@coords[,1])
+
+ # Loop through and extract coefficients
+ for(cn in 1:length(coef.names)){
+   coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn])
+   coef.df[,ncol(coef.df)+1] <- unlist(coef.list[[cn]])
+ }
+
+ # Add plottable names
+ colnames(coef.df)[3:13] <- c('intercept', 'house', 'bb11', 'bb21', 'bb31',
+                              'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict')
+
+```
+
+Finally, these coefficients are converted to a surface.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Make capture list
+ surf.list <- list()
+
+ # Create surfaces
+ for(sl in 1:ncol(coef.df)){
+
+   # If NAs
+   to.cut <- which(is.na(coef.df[,sl]))
+   if(length(to.cut) > 0){
+     surf.points <- est.points[-to.cut,]
+     surf.value <- coef.df[-to.cut, sl]
+   } else {
+     surf.points <- est.points
+     surf.value <- coef.df[ , sl]
+   }
+
+   # Surface estimation
+   surf.list[[sl]] <- point2Surface(surf.points, 
+                                    surf.value,
+                                    .01, 
+                                    1.5)
+ }
+
+```
+
+```{r working, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+### Save workspace -----------------------------------------------------------------------
+
+  save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_results.RData")
+
+  save(abb.revs, ltr.revs, clean.count, blank.plot,
+       rate.hm, rate.hm.svm, qtl.hm, qtl.hm.svm, market.ratio, 
+       house, apt, sm.results, full.table, smt.results, bb.results,
+       abb.sum, ltr.sum, ann.df, mrkt.table, num.df, reason.df, subs,
+       suburbs.shp, s.suburbs, coef.df,
+       file="C:/Dropbox/Research/airBNB/data/analyzed/abb_objs.RData")
+
+```

### 2017-01-25 abbReturns_Working.R
remove existing analysis, start host classifier

@@ -45,6 +45,7 @@
  ## Load working workspace   
   
   load(paste0(data.path, '/analyzed/abb_working.RData'))
+  load(paste0(data.path, '/analyzed/abb_objs.RData'))
   
  ## Load sources (custom function files)
 
@@ -58,733 +59,47 @@
   sm.col <- abb.col[c(2, 1, 3, 5, 6)]
   
 ### Working analysis ---------------------------------------------------------------------  
-
- ## Global model
-
-  # Set model specifications
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
-                            as.factor(bedbath) + as.factor(suburb) + 
-                            as.factor(ltr.month))
-  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
-                            as.factor(bedbath) + as.factor(suburb))
- 
- # Make comparison between two markets  
-  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
-                               abb.df=abb.data, 
-                               ltr.mod.spec=ltr.mod.spec, 
-                               abb.mod.spec=abb.mod.spec,
-                               clip.field='suburb')
   
-  # Extract out DFs (only those that imputed)
-  abb.imp <- imp.data$abb
-  ltr.imp <- imp.data$ltr
   
-  # Extract models
-  abb.sum <- summary(imp.data$abb.mod)
-  ltr.sum <- summary(imp.data$ltr.mod)
-  
- # Within type imputation revenues
-  
-  imp.revs <- revenueEngine(abb.imp, 
-                            ltr.imp,
-                            rate.field='imp.rate',
-                            rent.field='imp.rent')
-  
-  # Add back to DFs
-  abb.imp$imp.revenue <- imp.revs$abb
-  ltr.imp$imp.revenue <- imp.revs$ltr
-  
- # Cross type revenue estimation
-  
-  # Apply dom to abb
-  abb.imp$imp.dom <- imputeDOM(abb.imp, ltr.imp, calc.type='median')
-  
-  # Apply occ.rate to ltr
-  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, abb.imp, calc.type='median')
-  
-  # Estimate cross revenues
-  impx.revs <- revenueEngine(abb.df=ltr.imp, 
-                             ltr.df=abb.imp,
-                             rate.field='imp.rate',
-                             rent.field='imp.rent',
-                             occ.field='imp.occ',
[…]

### 2017-01-26 abbDataPrep_Script.Rmd
beginning of re-org

@@
 
-This file details the initial data preparation and the missing daily observation imputation that we have applied to the AirBNB nightly data from www.AirDNA.co.
-This is not a 'data cleaning' exercise as we are not removing data points based on observed values, with one exception:  the removal of the small set of AirBNB properties considered as 'Other' (not a house or apartment).
+This file details the initial data preparation that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).
+This is not a 'data cleaning' exercise as we are not removing data points based on observed values.
 
@@
   library(plyr)
+  library(stringr)
 
@@
 
-      data.path <- 'gideon path'
+      data.path <- 'other path'
 
@@
 &nbsp;
+
+## Short Term (Airbnb) Data
+
+We begin the data preparation with the Airbnb data.
 
@@
 
-### Remove those post Aug 31
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Daily data
-
-  prop.data <- prop.data[prop.data$created.date <= '2016-08-31', ]
-
-  daily.data <- daily.data[daily.data$property.id %in% prop.data$property.id, ]
-
-```
-
 ### Add Summary Information
@@
 
-### Impute missing daily observations
-
-Unfortunately, the data from AirDNA is missing observations.
-According to conversations with AirDNA staff only certain Melbourne area properties were monitored for daily status conditions starting on October 1, 2014.
-Over the next year, all properties were slowly brought on line.
-From October 1, 2015 to October 1, 2016 observations are believed to be complete.
-To fill in the missing observations, we will impute the status of the missing dates based on the available data.
-Some properties will have a month or less of imputation, some a full year or so.
-
-&nbsp;
-
-#### Filter 'Other' Properties
-
-AirBNB units are classified into a property type.
-There are 19 different property types within the Melbourne data.
-The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types:
-
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
-3.
-**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
-
-The analyses that follow removes the **Other** category (3% of total) and only considers the **House** and **Apartment** unit types
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-prop.data$type <- 'Other'
-prop.data$type[prop.data$property.type == 'Apartment' | 
-                  prop.data$property.type == 'Condominium' ] <- 'Apartment'
-prop.data$type[prop.data$property.type == 'House' | 
-                  prop.data$property.type == 'Townhouse' ] <- 'House'
-
-#prop.data <- prop.data[prop.data$type != 'Other', ]
-
-```
-
-&nbsp;
-
-#### Prepping for Imputation
-
-We begin the imputation process by creating a new variable indicating if the property itself was created before the data collection process began.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  prop.data$created.class <- ifelse(prop.data$created.date < '2014-10-01', 
-                                  'pre', 'post')
-
-```
-
-Most properties (`r round(100*table(prop.data$created.class)[1]/nrow(prop.data),2)`%) were created (first offered on www.airbnb.com) after October 1, 2014.
-We then add a field indicating whether or not the property needs to be imputed.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-prop.data$impute <- 'no'
-prop.data$impute[prop.data$created.class == 'pre' & 
-                   prop.data$min.date > '2014-10-01'] <- 'pre'
-prop.data$impute[prop.data$created.class == 'post' & 
-                   prop.data$min.date > prop.data$created.date] <- 'post'
-
-```
-
-About (`r round(100*(1-(table(prop.data$impute)[1]/nrow(prop.data))), 0)`%) of all properties need some measure of imputation.
-
-&nbsp;
-
-#### Imputation Process
-
-In imputing the properties will use a multiple step process that considers the property's performance during the observed periods, the overall market during the non-observed periods and the type of the property itself.
-More specifically, we follow the steps below:
-
-1. Split all properties into *j* number of AirBNB submarkets
-
-For each *j* submarket:
-
-2. Calculate the average daily occupancy rate for each *j* submarket
-
-For each individual property (*i*) in submarket *j*:
-
-3. Calculate which days are observed and which are missing
-4. Calculate the % of reserved, available and blocked days for the observed dates
-5. Create an adjustment factor that notes the ratio of the submarket *j* reserved rate during the property's observed dates to those of the property's un-observed dates
-6.
-Using the adjustment in #5, we then determine what percentage of the un-observed days should be alloted to each status type (reserved, available and blocked).
-Blocked are based on the % of blocked days in the observed period.
-Reserved are based on the observed occupancy rate during the observed dates multiplied by the overall expected occupancy rate during the unobserved days for the entire submarket as compared with the observed days.
-The available days are the remainder.
-This process creates a count of each status equal to the number of unobserved days.
-7.
-The three status types are then assigned to the unobserved days.
-First, blocked days are randomly assigned.
-Then the reserved days are randomly assigned to the remaining non-blocked days in a weighted fashion where the overall submarket's occupancy rate on a given day influences the probability of the impute status being reserved.
-The available days are the balance of the unobserved days.
-Note that we do not attempt to simulate actual bookings which are often multiple days.
-The intent of the imputation is to correct capture the overall market and submarket trends, not to accurately re-create actual booking histories of any of the unobserved periods for this sample of properties.
-8. Prices for reserved rooms are taken to be the average nightly rate of that particular property over the observed period.
-
-We begin this process by creating submarkets.
-For each of the properties we determine the submarket to be a combination of the structure type (House vs Apartment) and the listing type (Entire vs Private Room vs Shared Room).
-This creates six submarkets.
-These are assigned to the property and the daily data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  prop.data$lp.type <- paste0(substr(prop.data$type, 1, 1), '.', 
-                               substr(prop.data$listing.type, 1, 1))
-
-  daily.data$lp.type <- prop.data$lp.type[match(daily.data$property.id,
-                                                  prop.data$property.id)]
-
-```
-
-We then split the property and daily data into submarkets.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- o.prop <- prop.data[prop.data$type == 'Other', ]
- o.daily <- daily.data[daily.data$property.id %in% o.prop$property.id, ]
-
- prop.data <- prop.data[prop.data$type != 'Other', ]
- daily.data <- daily.data[daily.data$property.id %in% prop.data$property.id, ]
-
- subm.prop <- split(prop.data, prop.data$lp.type)
- subm.daily <- split(daily.data, daily.data$lp.type)
-
-```
-
-And then we calculate daily occupancy rates for each submarket.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  subm.rates <- lapply(subm.daily, abbCalcDateRates)
-
-```
-
-We take these three sets of submarket data (properties, daily and occupancy rates) and use a custom function (**abbImputeDaily()**) to impute the missing days.
-The results of each of these submarkets are then collapse into a single data.frame.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Create blank capture list
-
-  subm.list <- list()
-
- ## Loop through submarkets
-
-  for(j in 1:length(subm.prop)){
-    subm.list[[j]] <- abbImputeDaily(prop.df=subm.prop[[j]],
-                                     daily.df=subm.daily[[j]],
-                                     rates.df=subm.rates[[j]])
-  }
-
- ## Collapse into a data.frame
-
-  imp.daily <- rbind.fill(subm.list)
-
-```
-
-After imputing the missing dates we join them to the observed daily data.  The imputed data can be recognized by the label 'imputed' in the booked.date field.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Combine all together
-
-  all.daily <- rbind(daily.data, imp.daily, o.daily)
-
- ##
-
-  prop.data <- rbind(prop.data, o.prop)
-
-```
-
 Finally, we write the amended daily and property data to .csv files for future analysis.

### 2017-01-26 abbReturns_Working.R
host classificatoin

@@ -61,45 +61,114 @@
 ### Working analysis ---------------------------------------------------------------------  
   
   
-  calcBookStr <- function(id, book.data){
+  
+  
+  
+calcBookStr <- function(id, 
+                        book.data){
     
-    id.data <- book.data[book.data$property.id == id, 'status']
+  id.data <- book.data[book.data$property.id == id, 'status']
+    
+  if(length(id.data) > 1){
     
     # Divide by status and collapse
     status.string <- id.data[1]
     
-    for(ss in 2:length(b)){
+    for(ss in 2:length(id.data)){
       
-      if(b[jj] == b[[jj-1]]){
-        x <- paste0(x,b[[jj]])
+      if(id.data[ss] == id.data[[ss - 1]]){
+        status.string <- paste0(status.string, id.data[[ss]])
       } else {
-        x <- paste0(x,'.',b[[jj]])
+        status.string <- paste0(status.string, '.' ,id.data[[ss]])
       }
     }
     
-    c <- as.list(strsplit(x,'[.]')[[1]])
+    # Collapse into list objects
+    ss.list <- as.list(strsplit(status.string, '[.]')[[1]])
     
+    # Grab the first status of each
+    sg.obj <- substr(ss.list[[1]], 1, 1)
+    for(sg in 1:length(ss.list)){
+      sg.obj[sg] <- substr(ss.list[[sg]], 1, 1)  
+    }
     
+    # Find location of three types
+    id.B <- which(unlist(sg.obj) == 'B')
+    id.R <- which(unlist(sg.obj) == 'R')
+    id.A <- which(unlist(sg.obj) == 'A')
     
+    # Extract
+    if(length(id.R) > 0){
+      r.list <- ss.list[id.R]
+    }
+    if(length(id.A) > 0){
+      a.list <- ss.list[id.A]
+      avails <- unlist(lapply(a.list, nchar))
+      avail.rate <- sum(avails) / length(id.data)
+      
+    } else {
+      
+      avail.rate <- 0
     
-  }
+    }
+    
+    if(length(id.B) > 0){
+      b.list <- ss.list[id.B] 
+    
+      # Count longest and blocked times
+      blocks <- unlist(lapply(b.list, nchar))
+      
+      block.rate <- sum(blocks) / length(id.data)
+      longest.block <- max(blocks)
+      med.block <- median(blocks)
[…]

### 2017-01-31 abbDataPrep_Script.Rmd
Reorder, day 1

@@
 ---
-title: "AirBNB Data Preparation and Imputation"
-output: html_notebook
+title: "Data Preparation, Integration and Cleaning"
+output:
+  html_document: default
+  html_notebook: default
 ---
@@
 
-This file details the initial data preparation that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).
-This is not a 'data cleaning' exercise as we are not removing data points based on observed values.
+This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).
+Both datasets have had some initial pre-processing done, the details of which are found in **abb_str_PreProcess.R** and **abb_ltr_PreProcess.R**.
 
@@
 
-### Setup
+### Preliminary Commands
 
-We begin by loading the necessary libraries, set the path to the data and loading a set of custom data munging functions.
+&nbsp;
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE}
+We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.
 
- ## Load libraries
+```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
@@
   library(ggplot2)
+  library(geosphere)
   library(ggmap)
@@
   library(chron)
+  library(plyr)
+  library(sp)
+  library(rgeos)
+  library(reshape2)
+  library(stringr)
   library(RColorBrewer)
-  library(plyr)
-  library(stringr)
+  library(Hmisc)
 
- ## Set location
+```
+
+We then set the paths to the data and the code, conditional on which of the authors is running the analysis.
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
   # Get computer names
+
   comp.name <- Sys.info()['nodename']
@@
 
-      data.path <- 'other path'
+    data.path <- 'alternate data path'
+    code.path <- 'alternate data path'
 
@@
 
- ## Load sources
+```
 
-  source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+ # Current Project files
+
+  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
+
+ # Other custom files
+
+  source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
+                '/master/ggPlotTools.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
+                '/master/dataMungeTools.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
+                '/master/spatialLogitModels.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
+                '/master/point2surface_Tools.R'))
+
+```
+
+We then set the constants used in this study:
+
+1.
+**Exchange rate**: The Airbnb rates are provided in US dollars.
+We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  exch.rate <- 1.32
+
+```
+
+## Loading data
+
+&nbsp;
+
+Next we load in the raw data.  The short-term rental (Airbnb) data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.  
+```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Property Information
+
+  str.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T)
+
+  # Daily ltral information
+
+  daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T)
+
+```
+
+We then load the long term rental data.
+This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.
+
+```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Property level long term ltral information
+
+  ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
+
+ # Long term ltral listing information
+
+  listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T)
+
+```
+
+And, finally, we load three GIS shapefiles.
+The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
+We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]  After we load each we convert the names of the data fields to lower case for easier use in future coding.
+
+```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Suburb shapefile
+
+  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
+                               proj4string=CRS("+init=epsg:4283"),
+                               delete_null_obj=TRUE)
+  names(suburbs.shp@data) <- tolower(names(suburbs.shp@data))
+
+  # SA1 shapefile
+
+  sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'),
+                            proj4string=CRS("+init=epsg:4283"),
+                            delete_null_obj=TRUE)
+  names(sa1s.shp@data) <- tolower(names(sa1s.shp@data))
+
+  # Beach file
+
+  beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'),
+                             proj4string=CRS("+init=epsg:4283"),
+                             delete_null_obj=TRUE)
+  names(beach.shp@data) <- tolower(names(beach.shp@data))
+
+```
+
+## Data Preparation
+
+&nbsp;
+
+In this section we remove, convert and/or transform a number of data fields.  We also remove observations if they are missing critical data or fall outside of the scope of our research question.
+
+&nbsp;
+
+### Trim and Standardize Fields
+
+The data contain many fields that are either not fully observed and/or are not relevant to our research question.
+Additionally, the field naming conventions differ between the two datasets.
+We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.
+
+We start by trimming the property-level short term data.  No fields need to be removed from the daily data.
+
+```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.keep.flds <- c('property.id', 'host.id', 'listing.title', 'property.type',
+                     'listing.type', 'created.date', 'latitude', 'longitude',
+                     'last.scraped.date', 'average.daily.rate', 'overall.rating',
+                     'max.guests', 'cancellation.policy', 'cleaning.fee',
+                     'published.nightly.rate', 'published.weekly.rate', 
+                     'published.monthly.rate', 'minimum.stay',
+                     'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days',
+                     'blocked.days', 'available.days', 'created.year')
+
+  str.data <- str.data[, str.keep.flds]
+
+```
+
+We then limit the fields of the long-term property-specific data
+
+```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid',
+                      'flatnumber', 'streetnumber', 'streetname', 'streettype', 
+                      'suburb', 'postcode', 'property_latitude',
+                      'property_longitude', 'street_centroid_latitude',
+                      'street_centroid_longitude', 'eventdate', 'eventprice',
+                      'propertytype', 'areasize', 'bedrooms', 'baths', 'parking',
+                      'hasstudy', 'hascourtyard', 'hasbalcony', 'hasairconditioning',
+                      'hasgarage', 'dom')
+
+  ltr.data <- ltr.data[,ltr.keep.flds]
+
+```
+
+Next we standardize the field names.  Here we follow the short-term data convention of placing a period between words in the name.  We also shorten a number of the fields to make future coding easier.
+
+For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names. No changes are made to the names of the Airbnb daily data.
+
+```{r rename_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  names(str.data) <- c('property.id', 'host.id', 'listing.title', 'property.type',
+                       'listing.type', 'created.date', 'latitude', 'longitude',
+                       'last.scraped.date', 'average.daily.rate', 'overall.rating',
+                       'max.guests', 'cancel.policy', 'cleaning.fee',
+                       'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay',
+                       'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
+                       'blocked.days', 'available.days', 'created.year')
+
+```
+
+Periods are inserted between relevant words for the ltral data.
+
+```{r rename_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  names(ltr.data) <- c('id.key', 'geographical.id', 
+                        'event.id', 'address.id', 'activity.id',
+                        'flat.number', 'street.number', 'street.name', 'street.type',
+                        'suburb', 'postcode', 'latitude', 'longitude',
+                        'street.latitude', 'street.longitude', 'event.date',
+                        'event.price', 'property.type', 'area.size', 'bedrooms',
+                        'baths', 'parking', 'has.study', 'has.courtyard',
+                        'has.balcony', 'has.aircond', 'has.garage', 'dom')
+
+  names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id', 
+                           'of.record', 'event.date', 'event.price', 'first.adv.date', 
+                           'first.adv.price', 'last.adv.date', 'last.adv.price',
+                           'event.type')
 
@@
 &nbsp;
-&nbsp;
-
-## Short Term (Airbnb) Data
-
-We begin the data preparation with the Airbnb data.
-
-### Load data
-
-Next we load the raw property level and nightly level AirBNB reservation data received from AirDNA.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Property Information
-
-  prop.data <- read.csv(paste0(data.path, '/raw/melbproperties.csv'), header=T)
-
-  ## Daily rental information
-
-  daily.data  <- read.csv(paste0(data.path, '/raw/melbDaily.csv'), header=T)
-
-```
-
-&nbsp;
-&nbsp;
-
-### Data Transformations
-
-To make future coding easier, we convert all field names to lower case.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  names(prop.data) <- tolower(names(prop.data))
-  names(daily.data) <- tolower(names(daily.data))
-
-```
-
-We also then convert date values into correct R formatted dates. We also create a year created variable for the property data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Daily data
-
-  daily.data$date <- as.Date(daily.data$date)
-
- ## Property level data
-
-  prop.data$created.date <- as.Date(prop.data$created.date)
-  prop.data$created.year <- as.numeric(substr(prop.data$created.date, 1, 4))
-
-```
-
-&nbsp;
-&nbsp;
-
-### Add Summary Information
-
-We now add summary information regarding the number of bookings, number of free and blocked nights to the property level data.
-This information will assist in future imputation exercises and other analyses.
-
-We start by splitting the daily date into a list where each object is a data.frame of daily observations for a particular property.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  daily.prop <- split(daily.data, daily.data$property.id)
-
-```
-
-Next, we apply the **abbAnalyzeDaily()** function to each data.frame of daily observations.
-This process produces a list of results, by property.id.
-These lists are then collapsed into a single data.frame.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  daily.summ.list <- lapply(daily.prop, abbAnalyzeDaily)
-  daily.summ <- rbind.fill(daily.summ.list)
-
-```
-
-Finally, we add the summarized data to the existing property-level information.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  prop.data <- merge(prop.data, daily.summ, by='property.id')
-
-```
-
-&nbsp;
-&nbsp;
-
-Finally, we write the amended daily and property data to .csv files for future analysis.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- write.csv(all.daily, paste0(data.path, 'prepared/dailydata.csv'), row.names=FALSE)
-
- write.csv(prop.data, paste0(data.path, 'prepared/propdata.csv'), row.names=FALSE)
-
-```

### 2017-01-31 abbReturns_Script.Rmd
Reorder, day 1

@@
 
-### Preliminary Commands
-
-&nbsp;
-
-We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.
-
-```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
-  library(geosphere)
-  library(ggmap)
-  library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-
-```
-
-We then set the paths to the data and the code, conditional on which of the authors is running the analysis.
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  # Get computer names
-
-  comp.name <- Sys.info()['nodename']
-
-  # Assign path based on computer name
-
-  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
-
-    data.path <- 'c:/dropbox/research/airBNB/data/'
-    code.path <- 'c:/code/'
-
-  } else {
-
-    data.path <- 'alternate data path'
-    code.path <- 'alternate data path'
-
-  }
-
-```
-
-Next, we source the necessary custom code files for the analysis.
-
-```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  source(paste0(code.path, "dataviztools/ggplottools.R"))
-  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
-  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
-  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
-  source("c:/code/spatialtools/point2surface_Tools.R")
-  source("c:/code/spatialtools/spatiallogitmodels.R")
-
-```
-
-We then set the constants used in this study:
-
-1.
-**Exchange rate**: The Airbnb rates are provided in US dollars.
-We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.
-
-```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  exch.rate <- 1.32
-
-```
-
 Finally, we set the color to be used in the analysis.  We use AirBnb's official palette of 10 colors.
@@
 
-&nbsp;
-
-### Data Pre-processing
-
-&nbsp;
-
-Both the AirBNB and the long term rental data require some measure of data pre-processing and due to the run times of these processes they are done outside of this document.
+<!-- &nbsp; -->
+
+<!-- ### Data Pre-processing -->
+
+<!-- &nbsp; -->
+
+<!-- Both the AirBNB and the long term rental data require some measure of data pre-processing and due to the run times of these processes they are done outside of this document.
 For the AirBNB data, the pre-processing is primarily concerned with imputing missing daily observations for a small number of properties in the dataset.
@@
 Do note that most of the imputed data is ignored by our choice of study time period.
-
-The long term data received from the data provider is both wide and long and very inefficiently stored.
+-->
+
+<!-- The long term data received from the data provider is both wide and long and very inefficiently stored.
 To aid in computation time, the pre-processing involves the trimming of fields, labeling of observation types and reconfiguration of data and can be found in the **fixAPMData.R** script.
-
-&nbsp;
-
-## Loading data
-
-&nbsp;
-
-Next we load in the raw data.  The Airbnb data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.  
-```{r load_abb_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Property Information
-
-  abb.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T)
-
-  # Daily ltral information
-
-  daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T)
-
-```
-
-We then load the long term rental data.
+-->
+
+<!-- &nbsp; -->
+
+<!-- ## Loading data -->
+
+<!-- &nbsp; -->
+
+<!-- Next we load in the raw data.  The Airbnb data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.   -->
+<!-- ```{r load_abb_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   # Property Information -->
+
+<!--   abb.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T) -->
+
+<!--   # Daily ltral information -->
+
+<!--   daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T) -->
+
+<!-- ``` -->
+
+<!-- We then load the long term rental data.
 This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.
-
-```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Property level long term ltral information
-
-  ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
-
- # Long term ltral listing information
-
-  listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T)
-
-```
-
-And, finally, we load three GIS shapefiles.
+-->
+
+<!-- ```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Property level long term ltral information -->
+
+<!--   ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T) -->
+
+<!--  # Long term ltral listing information -->
+
+<!--   listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T) -->
+
+<!-- ``` -->
+
+<!-- And, finally, we load three GIS shapefiles.
 The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
-We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]
-
-```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Suburb shapefile
-
-  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
-                               proj4string=CRS("+init=epsg:4283"),
-                               delete_null_obj=TRUE)
-
-  # SA1 shapefile
-
-  sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'),
-                            proj4string=CRS("+init=epsg:4283"),
-                            delete_null_obj=TRUE)
-
-  # Beach file
-
-  beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'),
-                             proj4string=CRS("+init=epsg:4283"),
-                             delete_null_obj=TRUE)
-
-```
-
-&nbsp;
-
-## Data Preparation
-
-&nbsp;
-
-In this section we remove, convert and/or transform a number of data fields.  We also remove observations if they are missing critical data or fall outside of the scope of our research question.
-
-&nbsp;
-
-### Trim and Standardize Fields
-
-&nbsp;
-
-We start by converting all field names to lower case to simplify future coding.  This is important as R is case sensitive.
-
-```{r lower_names, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Short term data
-
-  names(abb.data) <- tolower(names(abb.data))
-  names(daily.data) <- tolower(names(daily.data))
-
- # Long term data
-
-  names(ltr.data) <- tolower(names(ltr.data))
-  names(listing.data) <- tolower(names(listing.data))
-
- # Geographic data
-
-  names(sa1s.shp@data) <- tolower(names(sa1s.shp@data))
-  names(suburbs.shp@data) <- tolower(names(suburbs.shp@data))
-
-```
-
-The data contain many fields that are either not fully observed and/or are not relevant to our research question.
+We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.] -->
+
+<!-- ```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   # Suburb shapefile -->
+
+<!--   suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'), -->
+<!--                                proj4string=CRS("+init=epsg:4283"), -->
+<!--                                delete_null_obj=TRUE) -->
+
+<!--   # SA1 shapefile -->
+
+<!--   sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'), -->
+<!--                             proj4string=CRS("+init=epsg:4283"), -->
+<!--                             delete_null_obj=TRUE) -->
+
+<!--   # Beach file -->
+
+<!--   beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'), -->
+<!--                              proj4string=CRS("+init=epsg:4283"), -->
+<!--                              delete_null_obj=TRUE) -->
+
+<!-- ``` -->
+
+<!-- &nbsp; -->
+
+<!-- ## Data Preparation -->
+
+<!-- &nbsp; -->
+
+<!-- In this section we remove, convert and/or transform a number of data fields.
+We also remove observations if they are missing critical data or fall outside of the scope of our research question.
+-->
+
+<!-- &nbsp; -->
+
+<!-- ### Trim and Standardize Fields -->
+
+<!-- &nbsp; -->
+
+<!-- We start by converting all field names to lower case to simplify future coding.  This is important as R is case sensitive.   -->
+
+<!-- ```{r lower_names, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Geographic data   -->
+
+<!--   names(sa1s.shp@data) <- tolower(names(sa1s.shp@data)) -->
+<!--   names(suburbs.shp@data) <- tolower(names(suburbs.shp@data)) -->
+
+<!-- ``` -->
+
+<!-- The data contain many fields that are either not fully observed and/or are not relevant to our research question.
 Additionally, the field naming conventions differ between the two datasets.
 We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.
-
-We start by trimming the property-level short term data.  No fields need to be removed from the daily data.
-
-```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  abb.keep.flds <- c('property.id', 'host.id', 'listing.title', 'property.type',
-                     'listing.type', 'created.date', 'latitude', 'longitude',
-                     'last.scraped.date', 'average.daily.rate', 'overall.rating',
-                     'max.guests', 'cancellation.policy', 'cleaning.fee',
-                     'published.nightly.rate', 'published.weekly.rate', 
-                     'published.monthly.rate', 'minimum.stay',
-                     'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days',
-                     'blocked.days', 'available.days', 'created.year')
-
-  abb.data <- abb.data[, abb.keep.flds]
-
-```
-
-We then limit the fields of the long-term property-specific data
-
-```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid',
-                      'flatnumber', 'streetnumber', 'streetname', 'streettype', 
-                      'suburb', 'postcode', 'property_latitude',
-                      'property_longitude', 'street_centroid_latitude',
-                      'street_centroid_longitude', 'eventdate', 'eventprice',
-                      'propertytype', 'areasize', 'bedrooms', 'baths', 'parking',
-                      'hasstudy', 'hascourtyard', 'hasbalcony', 'hasairconditioning',
-                      'hasgarage', 'dom')
-
-  ltr.data <- ltr.data[,ltr.keep.flds]
-
-```
-
-Next we standardize the field names.  Here we follow the short-term data convention of placing a period between words in the name.  We also shorten a number of the fields to make future coding easier.
-
-For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names. No changes are made to the names of the Airbnb daily data.
-
-```{r rename_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  names(abb.data) <- c('property.id', 'host.id', 'listing.title', 'property.type',
-                       'listing.type', 'created.date', 'latitude', 'longitude',
-                       'last.scraped.date', 'average.daily.rate', 'overall.rating',
-                       'max.guests', 'cancel.policy', 'cleaning.fee',
-                       'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay',
-                       'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
-                       'blocked.days', 'available.days', 'created.year')
-
-```
-
-Periods are inserted between relevant words for the ltral data.
-
-```{r rename_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  names(ltr.data) <- c('id.key', 'geographical.id', 
-                        'event.id', 'address.id', 'activity.id',
-                        'flat.number', 'street.number', 'street.name', 'street.type',
-                        'suburb', 'postcode', 'latitude', 'longitude',
-                        'street.latitude', 'street.longitude', 'event.date',
-                        'event.price', 'property.type', 'area.size', 'bedrooms',
-                        'baths', 'parking', 'has.study', 'has.courtyard',
-                        'has.balcony', 'has.aircond', 'has.garage', 'dom')
-
-  names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id', 
-                           'of.record', 'event.date', 'event.price', 'first.adv.date', 
-                           'first.adv.price', 'last.adv.date', 'last.adv.price',
-                           'event.type')
-
-```
-
-&nbsp;
+-->
+
+<!-- We start by trimming the property-level short term data.  No fields need to be removed from the daily data.  -->
+
+<!-- ```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   abb.keep.flds <- c('property.id', 'host.id', 'listing.title', 'property.type', -->
+<!--                      'listing.type', 'created.date', 'latitude', 'longitude', -->
+<!--                      'last.scraped.date', 'average.daily.rate', 'overall.rating', -->
+<!--                      'max.guests', 'cancellation.policy', 'cleaning.fee', -->
+<!--                      'published.nightly.rate', 'published.weekly.rate',  -->
+<!--                      'published.monthly.rate', 'minimum.stay', -->
+<!--                      'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days', -->
+<!--                      'blocked.days', 'available.days', 'created.year')  -->
+
+<!--   abb.data <- abb.data[, abb.keep.flds] -->
+
+<!-- ``` -->
+
+<!-- We then limit the fields of the long-term property-specific data -->
+
+<!-- ```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   ltr.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid', -->
+<!--                       'flatnumber', 'streetnumber', 'streetname', 'streettype',  -->
+<!--                       'suburb', 'postcode', 'property_latitude', -->
+<!--                       'property_longitude', 'street_centroid_latitude', -->
+<!--                       'street_centroid_longitude', 'eventdate', 'eventprice', -->
+<!--                       'propertytype', 'areasize', 'bedrooms', 'baths', 'parking', -->
+<!--                       'hasstudy', 'hascourtyard', 'hasbalcony', 'hasairconditioning', -->
+<!--                       'hasgarage', 'dom')  -->
+
+<!--   ltr.data <- ltr.data[,ltr.keep.flds] -->
+
+<!-- ``` -->
+
+<!-- Next we standardize the field names.
+Here we follow the short-term data convention of placing a period between words in the name.
+We also shorten a number of the fields to make future coding easier.
+-->
+
+<!-- For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names. No changes are made to the names of the Airbnb daily data.  -->
+
+<!-- ```{r rename_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   names(abb.data) <- c('property.id', 'host.id', 'listing.title', 'property.type', -->
+<!--                        'listing.type', 'created.date', 'latitude', 'longitude', -->
+<!--                        'last.scraped.date', 'average.daily.rate', 'overall.rating', -->
+<!--                        'max.guests', 'cancel.policy', 'cleaning.fee', -->
+<!--                        'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay', -->
+<!--                        'bedrooms', 'baths', 'min.date', 'max.date', 'total.days', -->
+<!--                        'blocked.days', 'available.days', 'created.year') -->
+
+<!-- ``` -->
+
+<!-- Periods are inserted between relevant words for the ltral data.  -->
+
+<!-- ```{r rename_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   names(ltr.data) <- c('id.key', 'geographical.id',  -->
+<!--                         'event.id', 'address.id', 'activity.id', -->
+<!--                         'flat.number', 'street.number', 'street.name', 'street.type', -->
+<!--                         'suburb', 'postcode', 'latitude', 'longitude', -->
+<!--                         'street.latitude', 'street.longitude', 'event.date', -->
+<!--                         'event.price', 'property.type', 'area.size', 'bedrooms', -->
+<!--                         'baths', 'parking', 'has.study', 'has.courtyard', -->
+<!--                         'has.balcony', 'has.aircond', 'has.garage', 'dom') -->
+
+<!--   names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id',  -->
+<!--                            'of.record', 'event.date', 'event.price', 'first.adv.date',  -->
+<!--                            'first.adv.price', 'last.adv.date', 'last.adv.price', -->
+<!--                            'event.type') -->
+
+<!-- ``` -->
+
+<!-- &nbsp; -->
 
@@
 
-The dates in the long term data are not standardized.
+<!-- The dates in the long term data are not standardized.
 To fix this issue we create a small function that will remove the unnecessary digits and spaces and then convert to a standard date form.
@@
 We also create a year field for the event date.
-
-```{r fix_lt_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Build custom function
-
-  fixLTDates <- function(x){
-    temp.date <- as.character(x)
-    temp.date <- str_replace_all(temp.date, ' 0:00', '')
-    temp.date <- str_replace_all(temp.date, '/20', '/')
-    return(as.Date(temp.date, "%d/%m/%y"))   
-  }
-
-  # Convert event date
-
-  ltr.data$event.date <- fixLTDates(ltr.data$event.date)
-
-  # Extract Year of event date
-  ltr.data$event.year <- as.numeric(substr(ltr.data$event.date, 1, 4))
-
-  # Converted listing data date fields
-
-  listing.data$first.adv.date <- fixLTDates(listing.data$first.adv.date)
-  listing.data$last.adv.date <- fixLTDates(listing.data$last.adv.date)
-
-```
+-->
+
+<!-- ```{r fix_lt_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Build custom function   -->
+
+<!--   fixLTDates <- function(x){ -->
+<!--     temp.date <- as.character(x) -->
+<!--     temp.date <- str_replace_all(temp.date, ' 0:00', '') -->
+<!--     temp.date <- str_replace_all(temp.date, '/20', '/') -->
+<!--     return(as.Date(temp.date, "%d/%m/%y"))    -->
+<!--   } -->
+
+<!--   # Convert event date   -->
+
+<!--   ltr.data$event.date <- fixLTDates(ltr.data$event.date) -->
+
+<!--   # Extract Year of event date -->
+<!--   ltr.data$event.year <- as.numeric(substr(ltr.data$event.date, 1, 4)) -->
+
+<!--   # Converted listing data date fields   -->
+
+<!--   listing.data$first.adv.date <- fixLTDates(listing.data$first.adv.date) -->
+<!--   listing.data$last.adv.date <- fixLTDates(listing.data$last.adv.date) -->
+
+<!-- ``` -->
 

### 2017-01-31 abb_Functions.R

@@ -1,60 +1,33 @@
 ##########################################################################################
 #                                                                                        #    
-#  Functions for working with APM and AirDNA data                                        #
+#  Custom functions for working with APM and AirDNA data in the ABB Project              #
 #                                                                                        #
 ##########################################################################################
-
-### Analyze the daily data for each property ---------------------------------------------
-
-abbAnalyzeDaily <- function(daily.df){
-  
- ## Calculate minimum and maximum dates in the range  
-  
-  min <- min(daily.df$date)
-  max <- max(daily.df$date)
-  
- ## Calculate the Total days, and count each status  
-  
-  total.days <- nrow(daily.df)
-  blocked <- length(which(daily.df$status == 'B'))
-  available <- length(which(daily.df$status == 'A'))
-  reserved <- length(which(daily.df$status == 'R'))
-  
- ## Return as a data.frame  
-  
-  return(data.frame(property.id = unique(daily.df$property.id),
-                    min.date = min,
-                    max.date = max,
-                    total.days = total.days,
-                    blocked.days = blocked,
-                    available.days = available,
-                    reserved.days = reserved))
-}
 
 ### Calculate the occupancy rates for each date in a range -------------------------------
 
 abbCalcDateRates <- function(daily.df){
   
- ## Create table of counts by status
+  ## Create table of counts by status
   
   status.table <- table(daily.df$date, daily.df$status)
   
- ## Convert to a data.frame  
+  ## Convert to a data.frame  
   
   status.df <- data.frame(Avail=status.table[,1],
                           Resv=status.table[,2],
                           Block=status.table[,3],
                           lp.type=daily.df$lp.type[1])
   
- ## Add date   
+  ## Add date   
   
   status.df$date <- as.Date(rownames(status.df))
   
- ## Add reserved rate (occupancy rate)  
+  ## Add reserved rate (occupancy rate)  
   
   status.df$occ.rate <- status.df$Resv / (status.df$Resv + status.df$Avail)
   
- ## Return values  
[…]

### 2017-01-31 abb_ltr_PreProcess.R

@@ -29,7 +29,10 @@
     
   }
   
+  # Set Raw path
   raw.path <- paste0(data.path, '/raw/')
+  
+  # Load the raw rent data
   rent16 <- read.csv(paste0(raw.path, 'rentData.csv'), header=T)
 
  ## Remove observations without sufficient keys
@@ -46,36 +49,37 @@
   
  ## Fix Dates  
   
-  r16$lastdate <- apmFixDates(r16$LastAdvertisedEventDate)
-  r16$eventdate <- apmFixDates(r16$EventDate)
-  r16$eventyear <- as.numeric(substr(r16$eventdate, 1, 4))
+  r16$last.adv.date <- apmFixDates(r16$LastAdvertisedEventDate)
+  r16$first.adv.date <- apmFixDates(r16$FirstAdvertisedEventDate)
+  r16$event.date <- apmFixDates(r16$EventDate)
+  r16$event.year <- as.numeric(substr(r16$event.date, 1, 4))
   
  ## Remove those not occuring in 2015 or later
   
-  r16 <- r16[r16$eventyear >= 2014, ]
+  r16 <- r16[r16$event.year > 2014, ]
   
  ## Add an identifier that signifies last record in a set of advertisements (of record)  
     
-  r16 <- r16[order(r16$eventdate, decreasing=T), ]
+  r16 <- r16[order(r16$event.date, decreasing=T), ]
   r16 <- r16[order(r16$id.key), ]
-  r16$AID <- paste0(r16$id.key, '..', r16$lastdate)
+  r16$AID <- paste0(r16$id.key, '..', r16$last.adv.date)
   r16$of.record <- ifelse(duplicated(r16$AID), 0 ,1)
   
  ## Split into property data and listing data
   
-  prop.data <- r16[r16$of.record == 1,]
-  list.data <- r16[, c('id.key', 'EventID', 'ActivityID', 'AddressID', 'of.record',
-                       'eventdate', 'EventPrice', 'FirstAdvertisedEventDate',
-                       'FirstAdvertisedEventPrice', 'LastAdvertisedEventDate',
-                       'LastAdvertisedEventPrice', 'EventTypeCode')]
+  ltr.data <- r16[r16$of.record == 1,]
+  listing.data <- r16[, c('id.key', 'EventID', 'ActivityID', 'AddressID', 'of.record',
+                          'event.date', 'EventPrice', 'first.adv.date',
+                          'FirstAdvertisedEventPrice', 'last.adv.date',
[…]

### 2017-01-31 abb_str_PreProcess.R

@@ -1,0 +1,82 @@
+##########################################################################################
+#                                                                                        #  
+#   Data Preprocessing for the Short-Term Rental data of the ABB project                 #
+#                                                                                        #  
+##########################################################################################
+
+ ## Load libraries
+
+  library(spdep)
+  library(maptools)
+  library(gstat)
+  library(ggplot2)
+  library(ggmap)
+  library(xtable)
+  library(chron)
+  library(RColorBrewer)
+  library(plyr)
+  library(stringr)
+
+  ## Set location
+
+  # Get computer names
+  comp.name <- Sys.info()['nodename']
+
+  # Assign path based on computer name
+  if(comp.name == '7020D-121777-W' | 
+     comp.name == 'DESKTOP-1D7JO4J'){
+  
+    data.path <- 'c:/dropbox/research/airBNB/data/'
+  
+  } else {
+  
+    data.path <- 'other path'
+  
+  }
+
+ ## Load sources
+
+  source("c:/code/research/airbnbMelbourne/abb_Functions.R")
+
+ ## Load Data  
+   
+  # Property Information
+
+  str.data <- read.csv(paste0(data.path, '/raw/melbproperties.csv'), header=T)
+
+  # Daily rental information
+
+  daily.data  <- read.csv(paste0(data.path, '/raw/melbDaily.csv'), header=T)
+
+ ## Fix Names
+  
+  names(str.data) <- tolower(names(str.data))
+  names(daily.data) <- tolower(names(daily.data))
+
+ ## Fix Dates  
+  
+  # Daily data
+  daily.data$date <- as.Date(daily.data$date)
+
+  # Property level data
+  str.data$created.date <- as.Date(str.data$created.date)
+  str.data$created.year <- as.numeric(substr(str.data$created.date, 1, 4))
+
+ ## Add Summary Information
+
+  # Summarize daily by property
+  daily.summ.list <- lapply(as.list(str.data$property.id), abbCalcBookStr,
+                            book.data=daily.data)
+
+  # Extract to a df
+  daily.summ <- rbind.fill(daily.summ.list)
+  
+  # Add summary data to property data
+  
+  str.data <- merge(str.data, daily.summ, by='property.id')
+
+ ## Write out data  
+
+  save(str.data, file=paste0(data.path, 'stpropdata.RData'))
+  save(daily.data, file=paste0(data.path, 'stdailydata.RData'))
+  

### 2017-02-04 abbDataPrep_Script.Rmd
finalizing data cleaning

@@
 output:
+  pdf_document: default
+  html_notebook: default
   html_document: default
-  html_notebook: default
 ---
@@
     code.path <- 'c:/code/'
+    fig.path <- 'c:/dropbox/research/airBNB/figures/'
 
@@
     code.path <- 'alternate data path'
+    fig.path <- 'alternate data path'
 
@@
 
+Finally, we set the color to be used in the analysis.  We use AirBnb's official palette of 10 colors.
+
+```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+ # Set all colors
+
+  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
+                     'ebisu', 'tirol', 'foggy', 'hof')
+  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
+               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
+               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
+               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
+               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
+
+  # Set specific colors
+
+  str.col <- abb.col[1]
+  ltr.col <- abb.col[3]
+
+```
+
 ## Loading data
@@
 
-  str.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T)
+  load(paste0(data.path, 'prepared/stpropdata.RData'))
 
-  # Daily ltral information
+  # Daily rental information
 
-  daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T)
+  load(paste0(data.path, 'prepared/stdailydata.RData'))
 
@@
 
-  ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T)
+  load(paste0(data.path, 'prepared/ltpropdata.RData'))
 
@@
 
-  listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T)
+  load(paste0(data.path, 'prepared/ltlistdata.RData'))
 
@@
                      'listing.type', 'created.date', 'latitude', 'longitude',
-                     'last.scraped.date', 'average.daily.rate', 'overall.rating',
+                     'average.daily.rate', 'overall.rating',
                      'max.guests', 'cancellation.policy', 'cleaning.fee',
@@
                      'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days',
-                     'blocked.days', 'available.days', 'created.year')
+                     'block.rate', 'avail.rate', 'longest.block', 'nbr.block', 
+                     'med.block', 'created.year')
 
@@
                       'property_longitude', 'street_centroid_latitude',
-                      'street_centroid_longitude', 'eventdate', 'eventprice',
+                      'street_centroid_longitude', 'event.date', 'eventprice',
                       'propertytype', 'areasize', 'bedrooms', 'baths', 'parking',
@@
 
-  ltr.data <- ltr.data[,ltr.keep.flds]
+  ltr.data <- ltr.data[ ,ltr.keep.flds]
 
@@
                        'listing.type', 'created.date', 'latitude', 'longitude',
-                       'last.scraped.date', 'average.daily.rate', 'overall.rating',
+                       'average.daily.rate', 'overall.rating',
                        'max.guests', 'cancel.policy', 'cleaning.fee',
@@
                        'bedrooms', 'baths', 'min.date', 'max.date', 'total.days',
-                       'blocked.days', 'available.days', 'created.year')
+                       'block.rate', 'avail.rate', 'longest.block', 'nbr.block', 
+                       'med.block', 'created.year')
 
@@
 &nbsp;
+
+### Trim by Time
+
+Next we trim the observations by time.
+Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
+To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
+Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
+In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
+Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.
+While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
+
+Before we begin the filter process, we initial the data cleaning counter -- a small function that keeps track of how many observations we remove.
+
+```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  setCleanCount()
+
+```
+
+We then clip by time.  For the short-term data we will consider any Airbnb property that had at least 6 months worth of listing time on the portal during the 12-month study period
+
+```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ # Limit short term data
+
+  str.data <- str.data[(str.data$max.date - str.data$min.date) >= 178, ]
+  str.data <- str.data[str.data$max.date >= '2016-03-01' &
+                         str.data$min.date <= '2016-03-01', ]
+  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]
+
+ # Limit long term data
+
+  ltr.data <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
+                            ltr.data$event.date <= '2015-08-31', ]
+  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
+
+ # Count cleaning
+
+  countCleaning('time')
+
+```
+
+Next we add a monthly variable to the data for use in future modeling exercises.
+
+```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Short term data
+
+  str.data$str.month <- 1
+  daily.data$str.month <- as.numeric(as.factor(substr(daily.data$date, 1, 7)))
+
+  # Long term data
+
+  ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
+  listing.data$ltr.month <- as.numeric(as.factor(substr(
+    listing.data$event.date, 1, 7))) - 8
+
+```
+
+### Standardize Property Types
+
+&nbsp;
+
+AirBNB units are classified into 19 different property type.
+The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
+For the sake of this analysis, we will collapse these twenty types into three types:
+
+1. **House**:  Includes properties labeled 'House' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
+3.
+**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
+
+Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+
+1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
+3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+
+Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
+This is most apparent when talking about apartment dwellings.
+In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
+Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
+
+We then create a new variable in each dataset and give each one of the three categories discussed above.
+
+```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Short Term data
+
+  str.data$type <- 'Other'
+  str.data$type[str.data$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
+  str.data$type[str.data$property.type %in% c('House', 'Townhouse')] <- 'House'
+
+ # Long Term data
+
+  ltr.data$type <- 'Other'
+  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
+                                           'Terrace', 'Townhouse')] <- 'House'
+  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
+
+```
+
+As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
+Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
+As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
+
+```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+  # Create Airbnb plot
+
+  str.types <- ggplot(str.data, aes(x=type)) + 
+    geom_bar(color=str.col, fill=str.col) +
+    xlab('\nProperty Type\n') + 
+    ggtitle('\nShort Term Rentals\n')  +
+    ylab('# of Properties\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Create long term rental plot
+
+  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
+    geom_bar(color=ltr.col, fill=ltr.col) +
+    xlab('\nProperty Type\n') + 
+    ggtitle('\nLong Term Rentals\n')  +
+    ylab('# of Properties\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Output plots
+  png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280, 
+      bg='transparent')
+    ggMultiPlots(str.types, ltr.types, cols=2)
+  dev.off()
+
+```
+
+```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+  str.data <- subset(str.data, type != 'Other')
+  ltr.data <- subset(ltr.data, type != 'Other')
+
+  # Count Cleaning
+  countCleaning('property.type')
+
+```
+
+Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+
+1. **Entire Home/Apt**: The entire home or apartment is available
+2. **Private Room**: One room within a house or apartment is available
+3. **Shared Room**: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt.
+Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
+
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+  # Fix data types and names
+  str.data$listing.type <- as.character(str.data$listing.type)
+  str.data$listing.type[str.data$listing.type == 'Entire home/apt'] <- 'Entire home'
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    ggplot(str.data, aes(x=listing.type)) + 
+      geom_bar(color=str.col, fill=str.col) +
+      xlab('\nListing Type\n') + 
+      ggtitle('\nShort Term Rentals by Listing Type\n')  +
+      ylab('# of Properties\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  dev.off()
+
+```
+
+```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.data <- str.data[str.data$listing.type == 'Entire home', ]
+
+  # Count cleaning 
+  countCleaning('listing.type')
+
+```
+
+## Structural Characteristics
+
+&nbsp;
+
+In this section we transform and filter based on the structural characteristics of the properties.
+
+### Fix Boolean Variables
+
+Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
+
+```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
+  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
+  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
+  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
+  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
+
+```
+
+&nbsp;
+
+### Bedrooms
+
+We start by looking at bedrooms.
+We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
+We then plot the distribution of diffeltr bedrooms counts.
+From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
+
+```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove missing and data errors
+
+  # Long term data
+  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
+  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
+
+  # Short term data
+  str.data <- str.data[!is.na(str.data$bedrooms), ]
+  str.data <- str.data[str.data$bedrooms <= 10, ]
+
+```
+
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Build long term bar plot
+
+   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type,scales='free_y') +
+    scale_x_continuous(labels=1:10, breaks=1:10)+
+    xlab('\nBedrooms\n') +
+    scale_y_continuous(labels=c(0,10000,20000), 
+                       breaks=c(0,10000,20000))+
+    ylab('') +
+    ggtitle('Bedrooms in Long Term Rentals') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Build short term bar plot
+
+  strbed <- ggplot(str.data, aes(x=bedrooms)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type,scales='free_y') +
+    scale_x_continuous(labels=0:10, breaks=0:10) +
+    xlab('\nBedrooms\n') +
+    ylab('') +
+    ggtitle('Bedrooms in Short Term Rentals') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataclean_bedcount.png'), width = 480, height = 280, 
+      bg='transparent')
+    ggMultiPlots(strbed, ltrbed, cols=1)
+  dev.off()
+
+```
+
+For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
+We filter the data accordingly.
+Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
+We convert the 0 bed short term units to 1 bed units.
+
+```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove all with more than 4 beds
+
+  str.data <- str.data[str.data$bedrooms < 5, ]
+  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+
+ # Remove apartments with more than 3
+
+  str.id <- which(str.data$bedrooms > 3 & str.data$type =='Apartment')
+  ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
+
+  if(length(str.id) > 0) str.data <- str.data[-str.id, ]
+  if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]
+
+  # Convert 0 Bed to 1 Bed  
+  str.data$bedrooms[str.data$bedrooms == 0] <- 1
+
+  # Count Data Cleaning
+  countCleaning('bedrooms')
+
+```
+
+### Bathrooms
+
+We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
+
+```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Remove missing data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
+  str.data <- str.data[!is.na(str.data$baths), ]
+
+```
+
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Build long term plot
+
+  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    facet_wrap(~type) +
+    scale_x_continuous(labels=1:8, breaks=1:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Long Term Rentals') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Build short term plot
+
+  stbath <- ggplot(str.data, aes(x=baths)) + 
+    geom_bar(fill=str.col, color=str.col) +
+    facet_wrap(~type, scales='free_y') +
+    scale_x_continuous(labels=0:8, breaks=0:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') + 
+    ggtitle('Bathrooms in Short Term ltrals') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Make Plots  
+  png(file=paste0(fig.path, 'dataclean_bathount.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    ggMultiPlots(stbath, ltbath, cols=1)
+
+  dev.off()
+
+```
+
+Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
+A few short term properties state no baths, which is likely an error so we remove these as well.
+Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
+We round the baths up to whole integers.
+
+```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Filter by bath count
+
+  # Short term data
+  str.data <- str.data[str.data$baths < 4, ]
+  str.data <- str.data[str.data$baths > 0, ]
+
+  # Long term data
+  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+
+ # Round baths up
+
+  str.data$baths <- round(str.data$baths + .01, 0)
+
+  # Count cleaning
+  countCleaning('baths')
+
+```
+
+### Bed/Bath Combination
+
+In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+As a result we examine the combinations of the two.
+
+```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Create combination variable
+
+  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
+  str.data$bedbath <- paste0(str.data$bedrooms, '..', str.data$baths)
+
+```
+
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Make long term plot
+
+  ltbb <- ggplot(ltr.data, aes(x=bedbath)) + 
+    geom_bar(fill=ltr.col, color=ltr.col) +
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    ggtitle('Long Term Rentals') + 
+    facet_wrap(~type, scales='free_y')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Make short term plots
+
+  stbb <- ggplot(str.data, aes(x=bedbath)) +
+    geom_bar(fill=str.col, color=str.col) + 
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    ggtitle('Short Term Rentals') + 
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    facet_wrap(~type, scales='free_y')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Make Plots  
+  png(file=paste0(fig.path, 'dataclean_bedbath.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    ggMultiPlots(ltbb, stbb, cols=1)
+
+  dev.off()
+
+```
+
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
+
+```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Set level of acceptable combinations
+
+  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
+
+ # Filter data
+
+  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
+  str.data <- str.data[str.data$bedbath %in% acc.bb, ]
+
+ # Count Cleaning
+
+  countCleaning('bedbath')
+
+```
+
+Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
+We additionally create a product variable that splits the bed/bath by apartment and house.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Re-order factors
+
+  str.data$bedbath <- factor(str.data$bedbath, 
+                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+  ltr.data$bedbath <- factor(ltr.data$bedbath, 
+                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
+
+  # Add product as a variable
+
+  str.data$product <- paste0(substr(str.data$type, 1, 1), str.data$bedbath)
+  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
+
+```
+
+## Rates and Rental values
+
+We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
+
+```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
+  str.data <- str.data[!is.na(str.data$nightly.rate), ]
+
+```
+
+Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
+
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Property level data
+
+  str.data$average.daily.rate <- str.data$average.daily.rate * exch.rate
+  str.data$nightly.rate <- str.data$nightly.rate * exch.rate
+  str.data$weekly.rate <- str.data$weekly.rate * exch.rate
+  str.data$monthly.rate <- str.data$monthly * exch.rate
+
+  # Daily data
+
+  daily.data$price <- daily.data$price * exch.rate
+
+```
+
+```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # ltr Plot
+
+  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
+    geom_density(fill=ltr.col, alpha=.8) +
+    ylab('') +
+    xlab('Weekly Rental') + 
+    ggtitle('Long Term Rentals') + 
+    scale_x_continuous(limits=c(0, 1500)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank()) +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Nightly Rate plot
+  rate.plot <- ggplot(str.data, aes(x=nightly.rate)) + 
+    geom_density(fill=str.col, alpha=.8) + 
+    ylab('') +
+    xlab('Nightly Rate') +
+    ggtitle('Short Term Rentals') + 
+    scale_x_continuous(limits=c(0, 600)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank()) +
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  png(file=paste0(fig.path, 'dataclean_rates.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    ggMultiPlots(ltr.plot, rate.plot, cols=2)
+
+  dev.off()
+
+```
+
+From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
+We filter the data accordingly.
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Filter the long term data
+
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
+
+ ## Filter the short term data
+
+  str.data <- str.data[str.data$nightly.rate >= 50 &
+                         str.data$nightly.rate <= 500, ]
+
+  # Count Cleaning
+  countCleaning('rates.rents')
+
+```
+
+### Locations and Submarkets
+
+Location is clearly an important determinant in both the short and long term rental markets.
+At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+Suburbs in Melbourne are much smaller than their North American counterparts.
+The specific suburb of a property is the second, or finer scale, at which the market operates.
+The plot below shows the three large submarkets (Inner, Middle and Outer).
+
+```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Convert shapefile to ggplot-able object
+
+  # Fix lat/long
+
+  # Limit to extent of data
+  sub.table <- table(ltr.data$suburb)
+  sub.table <- sub.table[sub.table != 0]
+
+  # Clip to only those with a ltral observation
+  study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
+
+  # Convert to an outer bound with holes
+  ss.bound <- gUnaryUnion(study.suburbs)
+
+  # Remove holes from the shapefile
+  ssb <- slot(ss.bound, "polygons") 
+  holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
+                                          slot, "hole"))
+  res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
+  IDs <- row.names(ss.bound) 
+  ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
+   Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound)))
+
+  # Identify which suburbs all in area covered by outer bound
+  ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
+  study.suburbs <- suburbs.shp[which(ss.in), ]
+
+  # Convert into an outer boundary with no holes
+  ss.bound.out <- gUnaryUnion(study.suburbs)
+  ssb.out <- slot(ss.bound.out, "polygons") 
+  holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
+                                          slot, "hole"))
+  res.out <- lapply(1:length(ssb.out), 
+                    function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
+  IDs <- row.names(ss.bound.out) 
+  ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
+                                         function(i) Polygons(res.out[[i]], 
+                                                              ID=IDs[i])),
+                                              proj4string=CRS(proj4string(ss.bound)))
+
+  # Convert into a ggplot-able format
+  subs <- fortify(study.suburbs, region='name_2006')
+
+  # Add suburb category
+  subs$des <- suburbs.shp@data$suburbdesi[
+    match(subs$id, suburbs.shp@data$name_2006)]
+
+```
+
+```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ ## Build the map object
+
+  # Set colors
+  g.cols <- abb.col[c(2, 10, 9)]
+
+  # Make map
+  loc.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
+    scale_fill_manual(values=g.cols, labels=c('Inner      ',
+                                              'Middle      ',
+                                              'Outer')) +
+    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    ggtitle("Melbourne Suburb Classifications")+
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
+  png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
+      bg='transparent')
+
+    loc.map
+
+  dev.off()
+
+  loc.map
+
+```
+
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+
+We select the 18 suburbs below to represent the 'core' of the city.
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenties for tourists.
+
+```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
+                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
+                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
+                   'St Kilda West', 'West Melbourne', 'Windsor')
+
+```
+
+We then apply a 500 meter buffer to the beach along Port Phillip Bay.
+
+```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Determine centroid of study area
+
+  latMid <- median(str.data$latitude)
+  longMid <- median(str.data$longitude)
+
+ # Calculate Degress to Meters conversion
+
+  m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
+  m.long = 111132.954 * cos (latMid)
+  m.conv <- mean(m.lat, m.long)
+
+ # Create the beach buffer
+
+  beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
+
+```
+
+Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
+
+```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Short term data
+
+  # Convert to point shapefile
+  str.prop.shp <- SpatialPointsDataFrame(cbind(str.data$longitude,
+                                               str.data$latitude),
+                                         str.data,
+                                         proj4string=CRS("+init=epsg:4283"))
+
+  # Add suburb name 
+  spJoin <- over(str.prop.shp, suburbs.shp)
+  str.data$suburb <- as.character(spJoin$name_2006)
+  str.data$suburb[is.na(str.data$suburb)] <- 'missing'
+
+  # Add suburb designation
+  str.data$sub.class <- as.character(spJoin$suburbdesi)
+  str.data$sub.class[is.na(str.data$sub.class)] <- 'missing'
+
+  # Add SA1 designation
+  spJoin <- over(str.prop.shp, sa1s.shp)
+  str.data$sa1 <- spJoin$sa1_main11
+
+  ## Add Beach Designation
+  spJoin <- over(str.prop.shp, beach.buffer)
+  str.data$beach <- ifelse(is.na(spJoin), 0 ,1)
+
+  # Remove those missing a suburb classification (out of area)
+  str.data <- str.data[str.data$sub.class != 'missing', ]
+  str.data <- str.data[str.data$sa1 != 'missing', ]
+
+```
+
+```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Add the submarket designations
+
+  # Add individual classes
+  str.data$sub.mrkt <- 'rural'
+  str.data$sub.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
+  str.data$sub.mrkt[str.data$sub.class == 'Inner'] <- 'city'
+  str.data$sub.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
+  str.data$sub.mrkt[str.data$beach == 1] <- 'beach'
+
+  # Order the factors properly
+  str.data$sub.mrkt <- factor(str.data$sub.mrkt, 
+                              levels=c('city-core', 'city', 'suburban', 
+                                        'rural', 'beach'))
+
+```
+
+Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
+For those without either (3% of the total) we remove them from the dataset at this point.
+
+```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Label those missing lat/long
+
+  miss.LL <- which(is.na(ltr.data$latitude))
+
+ # Create a field to indicate the approximate matches
+
+  ltr.data$miss.LL <- 0
+  ltr.data$miss.LL[miss.LL] <- 1
+
+ # Apply approximate match
+
+  ltr.data$latitude[miss.LL] <- ltr.data$street.latitude[miss.LL]
+  ltr.data$longitude[miss.LL] <- ltr.data$street.longitude[miss.LL]
+
+ # Remove those still missing latitude data
+
+  ltr.data <- ltr.data[!is.na(ltr.data$latitude), ]
+
+```
+
+Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.
+
+```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Long term data
+
+  # Convert to point shapefile
+
+  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.data$longitude,
+                                               ltr.data$latitude),
+                                         ltr.data,
+                                         proj4string=CRS("+init=epsg:4283"))
+
+  # Add suburb name
+
+  spJoin <- over(ltr.prop.shp, suburbs.shp)
+  ltr.data$suburb <- as.character(spJoin$name_2006)
+  ltr.data$suburb[is.na(ltr.data$suburb)] <- 'missing'
+
+  # Add suburb designation
+
+  ltr.data$sub.class <- as.character(spJoin$suburbdesi)
+  ltr.data$sub.class[is.na(ltr.data$sub.class)] <- 'missing'
+
+  # Add SA1 designation
+
+  spJoin <- over(ltr.prop.shp, sa1s.shp)
+  ltr.data$sa1 <- spJoin$sa1_main11
+
+  ## Add Beach Designation
+
+  spJoin <- over(ltr.prop.shp, beach.buffer)
+  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)
+
+  # Remove those missing a suburb classification (out of area)
+
+  ltr.data <- ltr.data[ltr.data$sub.class != 'missing', ]
+  ltr.data <- ltr.data[ltr.data$sa1 != 'missing', ]
+
+```
+
+```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Add the submarket designations
+
+  # Add individual classes
+  ltr.data$sub.mrkt <- 'rural'
+  ltr.data$sub.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
+  ltr.data$sub.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
+  ltr.data$sub.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
+  ltr.data$sub.mrkt[ltr.data$beach == 1] <- 'beach'
+
+  # Order the factors properly
+  ltr.data$sub.mrkt <- factor(ltr.data$sub.mrkt, 
+                              levels=c('city-core', 'city', 'suburban', 
+                                        'rural', 'beach'))
+
+  # Count Cleaning
+  countCleaning('location')
+
+```
+
+The location of the short and long term rentals, colored by submarket, are shown below
+
+```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set submarket colors
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
+  # Make map
+
+  str.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
+               alpha=.2) +
+    scale_color_manual(values=sm.col) +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
+    ggtitle('AirBNB Location\nBy Submarket')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Make map
+
+  ltr.map <- ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
+               alpha=.1) +
+    scale_color_manual(values=sm.col) +
+    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+    xlab('') + ylab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank()) +
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1))) + 
+    ggtitle('Long Term Rental Location\nBy Submarket')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
+
+  png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
+      bg='transparent')
+     str.map
+  dev.off()
+
+  png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
+      bg='transparent')
+     ltr.map
+  dev.off()
+
+  ggMultiPlots(str.map, ltr.map, cols=2)
+
+```
+
+The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
+
+```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
+
+  # Make Airbnb submarket map
+
+  strtype.map <- ggplot() +
+    geom_bar(data=str.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    scale_fill_manual(values=sm.col) +
+    facet_wrap(~type) +
+    ylab('# of Properties\n') + xlab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank()) +
+    ggtitle('Short Term Property Type\nBy Submarket')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Long term rental map
+
+  ltrtype.map <- ggplot() +
+    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    scale_fill_manual(values=sm.col) +
+    facet_wrap(~type) +
+    ylab('# of Properties\n') + xlab('')+
+    theme(legend.position = 'bottom',
+          legend.title = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank()) +
+    ggtitle('Long Term Property Type\nBy Submarket')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
+
+  png(file=paste0(fig.path, 'submplot.png'), width = 680, height = 590, 
+      bg='transparent')
+    ggMultiPlots(strtype.map, ltrtype.map, cols=2)
+  dev.off()
+
+  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
+
+```
+
+Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Convert suburbs from factor to character
+  str.data$suburb <- as.character(str.data$suburb)
+  ltr.data$suburb <- as.character(ltr.data$suburb)
+
+```
+
+&nbsp;
+
+## Filter Transaction Data
+
+The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets
+
+```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Short term data
+
+  daily.data <- daily.data[daily.data$property.id %in% str.data$property.id,]
+
+ ## Long term list data
+
+  listing.data <- listing.data[listing.data$activity.id %in% ltr.data$activity.id,]
+
+```
+
+## Summarize Daily Data
+
+As we have limited the time period of analysis from the expanse of the raw data, we must now re calculate the daily summary information.
+
+```{r redo.daily.summ, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Calculate the new daily summaries
+
+ daily.summ.list <- lapply(as.list(str.data$property.id), abbCalcBookStr,
+                            book.data=daily.data)
+ daily.summ <- rbind.fill(daily.summ.list)
+ daily.summ$min.date <- daily.summ$max.date <- NULL
+
+ # Remove existing 
+ cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
+                                     'longest.block', 'nbr.block', 'med.block'))
+ str.data <- str.data[ ,-cut.fields]
+
+ # Add summary data to property data
+ str.data <- merge(str.data, 
+                   daily.summ, 
+                   by.x='property.id',
+                   by.y='id')
+
+```
+
+Compute a full value of that total listing count
+
+```{r and.bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Compute bookings count
+
+  str.data$bookings <- round(str.data$total.days * (1 - (str.data$block.rate + str.data$avail.rate)), 0)
+
+ # Remove those with 0
+
+  str.data <- str.data[str.data$bookings > 0, ]
+
+```
+
+### Median rate
+
+Next we extract all of the daily reservation data that fits our criteria -- reserved and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data from the data source.
+We do this step to remove those].
+From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Get all of the reservations
+  resv.daily <- daily.data[daily.data$status == 'R' &
+                              daily.data$price < 500, ]
+
+  # Calculate the property specific median nightly rate
+  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
+
+  # Add median rate to the property  
+  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
+
+  # Remove those with no valid median rate
+  str.data <- str.data[!is.na(str.data$med.rate), ]
+
+```
+
+## Write out data
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, beach.shp, core.suburbs,
+       exch.rate, ltr.col, str.col, sa1s.shp, suburbs.shp, study.suburbs,
+       file=paste0(data.path, 'prepared/prep_workspace.RData'))
+```

### 2017-02-04 abbReturns_Script.Rmd
finalizing data cleaning

@@
 
-Finally, we set the color to be used in the analysis.  We use AirBnb's official palette of 10 colors.
-
-```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Set all colors
-
-  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
-                     'ebisu', 'tirol', 'foggy', 'hof')
-  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
-               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
-               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
-               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
-               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
-
-  # Set specific colors
-
-  str.col <- abb.col[1]
-  ltr.col <- abb.col[3]
-
-```
-
-<!-- &nbsp; -->
-
-<!-- ### Data Pre-processing -->
-
-<!-- &nbsp; -->
-
-<!-- Both the AirBNB and the long term rental data require some measure of data pre-processing and due to the run times of these processes they are done outside of this document.
-For the AirBNB data, the pre-processing is primarily concerned with imputing missing daily observations for a small number of properties in the dataset.
-Full information on this process can be found in the **airbnbDataClean.Rmd** and **dataCleanFunctions.R** files.
-Do note that most of the imputed data is ignored by our choice of study time period.
--->
-
-<!-- The long term data received from the data provider is both wide and long and very inefficiently stored.
-To aid in computation time, the pre-processing involves the trimming of fields, labeling of observation types and reconfiguration of data and can be found in the **fixAPMData.R** script.
--->
-
-<!-- &nbsp; -->
-
-<!-- ## Loading data -->
-
-<!-- &nbsp; -->
-
-<!-- Next we load in the raw data.  The Airbnb data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.   -->
-<!-- ```{r load_abb_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   # Property Information -->
-
-<!--   abb.data <- read.csv(paste0(data.path, '/prepared/propdata.csv'), header=T) -->
-
-<!--   # Daily ltral information -->
-
-<!--   daily.data  <- read.csv(paste0(data.path, '/prepared/dailydata.csv'), header=T) -->
-
-<!-- ``` -->
-
-<!-- We then load the long term rental data.
-This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.
--->
-
-<!-- ```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  # Property level long term ltral information -->
-
-<!--   ltr.data <- read.csv(paste0(data.path, '/prepared/ltpropdata.csv'), header=T) -->
-
-<!--  # Long term ltral listing information -->
-
-<!--   listing.data <- read.csv(paste0(data.path, '/prepared/ltlistdata.csv'), header=T) -->
-
-<!-- ``` -->
-
-<!-- And, finally, we load three GIS shapefiles.
-The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
-We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.] -->
-
-<!-- ```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   # Suburb shapefile -->
-
-<!--   suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'), -->
-<!--                                proj4string=CRS("+init=epsg:4283"), -->
-<!--                                delete_null_obj=TRUE) -->
-
-<!--   # SA1 shapefile -->
-
-<!--   sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'), -->
-<!--                             proj4string=CRS("+init=epsg:4283"), -->
-<!--                             delete_null_obj=TRUE) -->
-
-<!--   # Beach file -->
-
-<!--   beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'), -->
-<!--                              proj4string=CRS("+init=epsg:4283"), -->
-<!--                              delete_null_obj=TRUE) -->
-
-<!-- ``` -->
-
-<!-- &nbsp; -->
-
-<!-- ## Data Preparation -->
-
-<!-- &nbsp; -->
-
-<!-- In this section we remove, convert and/or transform a number of data fields.
-We also remove observations if they are missing critical data or fall outside of the scope of our research question.
--->
-
-<!-- &nbsp; -->
-
-<!-- ### Trim and Standardize Fields -->
-
-<!-- &nbsp; -->
-
-<!-- We start by converting all field names to lower case to simplify future coding.  This is important as R is case sensitive.   -->
-
-<!-- ```{r lower_names, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  # Geographic data   -->
-
-<!--   names(sa1s.shp@data) <- tolower(names(sa1s.shp@data)) -->
-<!--   names(suburbs.shp@data) <- tolower(names(suburbs.shp@data)) -->
-
-<!-- ``` -->
-
-<!-- The data contain many fields that are either not fully observed and/or are not relevant to our research question.
-Additionally, the field naming conventions differ between the two datasets.
-We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.
--->
-
-<!-- We start by trimming the property-level short term data.  No fields need to be removed from the daily data.  -->
-
-<!-- ```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   abb.keep.flds <- c('property.id', 'host.id', 'listing.title', 'property.type', -->
-<!--                      'listing.type', 'created.date', 'latitude', 'longitude', -->
-<!--                      'last.scraped.date', 'average.daily.rate', 'overall.rating', -->
-<!--                      'max.guests', 'cancellation.policy', 'cleaning.fee', -->
-<!--                      'published.nightly.rate', 'published.weekly.rate',  -->
-<!--                      'published.monthly.rate', 'minimum.stay', -->
-<!--                      'bedrooms', 'bathrooms', 'min.date', 'max.date', 'total.days', -->
-<!--                      'blocked.days', 'available.days', 'created.year')  -->
-
-<!--   abb.data <- abb.data[, abb.keep.flds] -->
-
-<!-- ``` -->
-
-<!-- We then limit the fields of the long-term property-specific data -->
-
-<!-- ```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   ltr.keep.flds <- c('id.key', 'geographicalid', 'eventid', 'addressid', 'activityid', -->
-<!--                       'flatnumber', 'streetnumber', 'streetname', 'streettype',  -->
-<!--                       'suburb', 'postcode', 'property_latitude', -->
-<!--                       'property_longitude', 'street_centroid_latitude', -->
-<!--                       'street_centroid_longitude', 'eventdate', 'eventprice', -->
-<!--                       'propertytype', 'areasize', 'bedrooms', 'baths', 'parking', -->
-<!--                       'hasstudy', 'hascourtyard', 'hasbalcony', 'hasairconditioning', -->
-<!--                       'hasgarage', 'dom')  -->
-
-<!--   ltr.data <- ltr.data[,ltr.keep.flds] -->
-
-<!-- ``` -->
-
-<!-- Next we standardize the field names.
-Here we follow the short-term data convention of placing a period between words in the name.
-We also shorten a number of the fields to make future coding easier.
--->
-
-<!-- For the short term data, it already uses the *word-.-word* convention.  Here our renaming is done to shorten certain field names. No changes are made to the names of the Airbnb daily data.  -->
-
-<!-- ```{r rename_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   names(abb.data) <- c('property.id', 'host.id', 'listing.title', 'property.type', -->
-<!--                        'listing.type', 'created.date', 'latitude', 'longitude', -->
-<!--                        'last.scraped.date', 'average.daily.rate', 'overall.rating', -->
-<!--                        'max.guests', 'cancel.policy', 'cleaning.fee', -->
-<!--                        'nightly.rate', 'weekly.rate', 'monthly.rate', 'min.stay', -->
-<!--                        'bedrooms', 'baths', 'min.date', 'max.date', 'total.days', -->
-<!--                        'blocked.days', 'available.days', 'created.year') -->
-
-<!-- ``` -->
-
-<!-- Periods are inserted between relevant words for the ltral data.  -->
-
-<!-- ```{r rename_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   names(ltr.data) <- c('id.key', 'geographical.id',  -->
-<!--                         'event.id', 'address.id', 'activity.id', -->
-<!--                         'flat.number', 'street.number', 'street.name', 'street.type', -->
-<!--                         'suburb', 'postcode', 'latitude', 'longitude', -->
-<!--                         'street.latitude', 'street.longitude', 'event.date', -->
-<!--                         'event.price', 'property.type', 'area.size', 'bedrooms', -->
-<!--                         'baths', 'parking', 'has.study', 'has.courtyard', -->
-<!--                         'has.balcony', 'has.aircond', 'has.garage', 'dom') -->
-
-<!--   names(listing.data) <- c('id.key', 'event.id', 'activity.id', 'address.id',  -->
-<!--                            'of.record', 'event.date', 'event.price', 'first.adv.date',  -->
-<!--                            'first.adv.price', 'last.adv.date', 'last.adv.price', -->
-<!--                            'event.type') -->
-
-<!-- ``` -->
-
-<!-- &nbsp; -->
-
-### Temporal Considerations
-
-&nbsp;
-
-Below we rename, transform and filter our data to fit the time period appropriate to our research question.
-
-&nbsp;
-
-#### Convert Time Variables
-
-We convert time variables across all dataset to an R date format.
-For the AirBNB data this is a relatively straighforword process as the data are already standardized into a consistant date representation.
-We fix dates in both the property and the daily data.
-
-```{r fix_st_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Property Data Fields
-
-  abb.data$created.date <- as.Date(abb.data$created.date)
-  abb.data$last.scraped.date <- as.Date(abb.data$last.scraped.date)
-  abb.data$min.date <- as.Date(abb.data$min.date)
-  abb.data$max.date <- as.Date(abb.data$max.date)
-
-  # Daily Data
-
-  daily.data$date <- as.Date(daily.data$date)
-
-```
-
-<!-- The dates in the long term data are not standardized.
-To fix this issue we create a small function that will remove the unnecessary digits and spaces and then convert to a standard date form.
-We then apply this formula to the three date fields in the long term data (both listing and rental).
-We also create a year field for the event date.
--->
-
-<!-- ```{r fix_lt_time, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  # Build custom function   -->
-
-<!--   fixLTDates <- function(x){ -->
-<!--     temp.date <- as.character(x) -->
-<!--     temp.date <- str_replace_all(temp.date, ' 0:00', '') -->
-<!--     temp.date <- str_replace_all(temp.date, '/20', '/') -->
-<!--     return(as.Date(temp.date, "%d/%m/%y"))    -->
-<!--   } -->
-
-<!--   # Convert event date   -->
-
-<!--   ltr.data$event.date <- fixLTDates(ltr.data$event.date) -->
-
-<!--   # Extract Year of event date -->
-<!--   ltr.data$event.year <- as.numeric(substr(ltr.data$event.date, 1, 4)) -->
-
-<!--   # Converted listing data date fields   -->
-
-<!--   listing.data$first.adv.date <- fixLTDates(listing.data$first.adv.date) -->
-<!--   listing.data$last.adv.date <- fixLTDates(listing.data$last.adv.date) -->
-
-<!-- ``` -->
-
-#### Trim by Time
-
-Next we trim the observations by time.
-Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
-To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.
-Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
-In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
-Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.
-While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.
-
-```{r}
-
-setCleanCount <- function(){
-
-  abb.orig <- nrow(abb.data)
-  daily.orig <- nrow(daily.data)
-  ltr.orig <- nrow(ltr.data)
-  list.orig <- nrow(listing.data)
-
-  clean.df <- data.frame(operation='initial',
-                         abb=abb.orig,
-                         daily=daily.orig,
-                         ltr=ltr.orig,
-                         list=list.orig)
-  assign('clean.count', clean.df, envir=.GlobalEnv)
-  assign('abb.run.total', nrow(abb.data), envir=.GlobalEnv)
-  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
-  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
-  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
-
-}
-
-countCleaning <- function(operation){
-
-  abb.cut <- abb.run.total - nrow(abb.data)
-  daily.cut <- daily.run.total - nrow(daily.data)
-  ltr.cut <- ltr.run.total - nrow(ltr.data)
-  listing.cut <- list.run.total - nrow(listing.data)
-
-  new.df <- data.frame(operation=operation,
-                       abb=abb.cut,
-                       daily=daily.cut,
-                       ltr=ltr.cut,
-                       list=listing.cut)
-  comb.df <- rbind(clean.count, new.df)
-  assign('clean.count', comb.df, envir=.GlobalEnv)
-  assign('abb.run.total', nrow(abb.data), envir=.GlobalEnv)
-  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
-  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
-  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
-
-}
-
-setCleanCount()
-
-```
-
-```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- # Limit short term data
-
-  abb.data <- abb.data[abb.data$min.date >= '2015-09-01', ]
-  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]
-
- # Limit long term data
-
-  ltr.data <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
-                            ltr.data$event.date <= '2015-08-31', ]
-  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
-
- # Count cleaning
-
-  countCleaning('time')
-
-```
-
-```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Short term data
-
-  abb.data$abb.month <- 1
-  daily.data$abb.month <- as.numeric(as.factor(substr(daily.data$date, 1, 7)))
-
-  # Long term data
-
-  ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
-  listing.data$ltr.month <- as.numeric(as.factor(substr(
-    listing.data$event.date, 1, 7))) - 8
-
-```
-
-### Standardize Property Types
-
-&nbsp;
-
-AirBNB units are classified into 19 different property type.
-The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types:
-
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
-3.
-**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
-
-Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
-
-1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
-
-Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
-This is most apparent when talking about apartment dwellings.
-In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).
-Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
-
-We then create a new variable in each dataset and give each one of the three categories discussed above.
-
-```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Short Term data
-
-  abb.data$type <- 'Other'
-  abb.data$type[abb.data$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
-  abb.data$type[abb.data$property.type %in% c('House', 'Townhouse')] <- 'House'
-
- # Long Term data
-
-  ltr.data$type <- 'Other'
-  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
-                                           'Terrace', 'Townhouse')] <- 'House'
-  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
-
-```
-
-As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
-Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
-As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
-
-```{r write_beforeproptypeobj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-before.PT <- list(abb.data=abb.data,
-                  ltr.data=ltr.data)
-
-#save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")
-
-```
-
-```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-
-  # Create Airbnb plot
-
-  abb.types <- ggplot(abb.data, aes(x=type)) + 
-    geom_bar(color=str.col, fill=str.col) +
-    xlab('\nProperty Type\n') + 
-    ggtitle('\nShort Term Rentals\n')  +
-    ylab('# of Properties\n')
-
-  # Create long term rental plot
-
-  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
-    geom_bar(color=ltr.col, fill=ltr.col) +
-    xlab('\nProperty Type\n') + 
-    ggtitle('\nLong Term Rentals\n')  +
-    ylab('# of Properties\n')
-
-  # Output plots
-
-  ggMultiPlots(abb.types, ltr.types, cols=2)
-
-```
-
-```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-
-  abb.data <- subset(abb.data, type != 'Other')
-  ltr.data <- subset(ltr.data, type != 'Other')
-
-  countCleaning('property.type')
-
-```
-
-Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
-
-1. **Entire Home/Apt**: The entire home or apartment is available
-2. **Private Room**: One room within a house or apartment is available
-3. **Shared Room**: A bed within a room shared by another occupant(s) is available
-
-As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt.
-Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
-
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-
-  # Fix data types and names
-
-  abb.data$listing.type <- as.character(abb.data$listing.type)
-  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'
-
-  # Make Plot
-
-  ggplot(abb.data, aes(x=listing.type)) + 
-    geom_bar(color=abb.col[1], fill=abb.col[1]) +
-    xlab('\nListing Type\n') + 
-    ggtitle('\nShort Term Rentals by Listing Type\n')  +
-    ylab('# of Properties\n')
-
-```
-
-```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
-  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]
-
-  countCleaning('listing.type')
-
-```
-
-## Structural Characteristics
-
-&nbsp;
-
-In this section we transform and filter based on the structural characteristics of the properties.
-
-### Fix Boolean Variables
-
-Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
-
-```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
-  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
-  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
-  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
-  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
-
-```
-
-&nbsp;
-
-### Bedrooms
-
-We start by looking at bedrooms.
-We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
-We then plot the distribution of diffeltr bedrooms counts.
-From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
-
-```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove missing and data errors
-
-  # Long term data
-  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
-  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
-
-  # Short term data
-  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
-  abb.data <- abb.data[abb.data$bedrooms <= 10, ]
-
-```
-
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Build long term bar plot
-
-   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:10, breaks=1:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Long Term Rentals')
-
- # Build short term bar plot
-
-  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:10, breaks=0:10)+
-    xlab('\nBedrooms\n') +
-    ylab('') +
-    ggtitle('Bedrooms in Short Term Rentals')
-
- # Make the comparison plot
-
-  ggMultiPlots(abbbed, ltrbed, cols=1)
-
-```
-
-For both short and long term ltrals we see that most apartments have less than 4 bedrooms and houses less than 5.
-We filter the data accordingly.
-Additionally, note that short term ltrals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
-We convert the 0 bed short term units to 1 bed units.
-
-```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove all with more than 4 beds
-
-  abb.data <- abb.data[abb.data$bedrooms < 5, ]
-  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
-
- # Remove apartments with more than 3
-
-  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
-  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
-
-  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
-  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
-
-  # Convert 0 Bed to 1 Bed  
-  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1
-
-  countCleaning('bedrooms')
-
-```
-
-### Bathrooms
-
-We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
-
-```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Remove missing data
-
-  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
-  abb.data <- abb.data[!is.na(abb.data$baths), ]
-
-```
-
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Build long term plot
-
-  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:8, breaks=1:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Long Term Rentals')
-
- # Build short term plot
-
-  stbath <- ggplot(abb.data, aes(x=baths)) + 
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:8, breaks=0:8)+
-    xlab('\nBathrooms\n') +
-    ylab('') + 
-    ggtitle('Bathrooms in Short Term ltrals')
-
- # Make Plots
-
-  ggMultiPlots(stbath, ltbath, cols=1)
-
-```
-
-Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
-A few short term properties state no baths, which is likely an error so we remove these as well.
-Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
-We round the baths up to whole integers.
-
-```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Filter by bath count
-
-  # Short term data
-  abb.data <- abb.data[abb.data$baths < 4, ]
-  abb.data <- abb.data[abb.data$baths > 0, ]
-
-  # Long term data
-  ltr.data <- ltr.data[ltr.data$baths < 4, ]
-
- # Round baths up
-
-  abb.data$baths <- round(abb.data$baths + .01, 0)
-
-  countCleaning('bathrooms')
-
-```
-
-### Bed/Bath Combination
-
-In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two.
-
-```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Create combination variable
-
-  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
-  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)
-
-```
-
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Make long term plot
-
-  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ggtitle('Long Term Rentals') + 
-    facet_wrap(~type)
-
- # Make short term plots
-
-  stb <- ggplot(abb.data, aes(x=bedbath)) +
-    geom_bar(fill=str.col, color=str.col) + 
-    xlab('\nBed/Bath Combo\n') +
-    ylab('Number of Properties\n') +
-    ggtitle('Short Term Rentals') + 
-    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    facet_wrap(~type)
-
- # Plot
-
-  ggMultiPlots(ltb, stb, cols=1)
-
-```
-
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.
-
-```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Set level of acceptable combinations
-
-  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
-
- # Filter data
-
-  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
-  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]
-
-  countCleaning('bedbath')
-
-```
-
-Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
-We additionally create a product variable that splits the bed/bath by apartment and house.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Re-order factors
-
-  abb.data$bedbath <- factor(abb.data$bedbath, 
-                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-  ltr.data$bedbath <- factor(ltr.data$bedbath, 
-                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-
-  # Add product as a variable
-
-  abb.data$product <- paste0(substr(abb.data$type, 1, 1), abb.data$bedbath)
-  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
-
-```
-
-## Rates and Rental values
-
-We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
-
-```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
-  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]
-
-```
-
-Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
-
-```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Property level data
-
-  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
-  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
-  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
-  abb.data$monthly.rate <- abb.data$monthly * exch.rate
-
-  # Daily data
-
-  daily.data$price <- daily.data$price * exch.rate
-
-```
-
-```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  # ltr Plot
-
-  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
-    geom_density(fill=ltr.col, alpha=.8) +
-    ylab('') +
-    xlab('Weekly Rental') + 
-    ggtitle('Long Term Rentals') + 
-    scale_x_continuous(limits=c(0, 1500)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-
-  # Nightly Rate plot
-  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
-    geom_density(fill=str.col, alpha=.8) + 
-    ylab('') +
-    xlab('Nightly Rate') +
-    ggtitle('Short Term Rentals') + 
-    scale_x_continuous(limits=c(0, 600)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-
-```
-
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  ggMultiPlots(ltr.plot, rate.plot, cols=2)
-
-```
-
-From these density plots we see that most weekly Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
-We filter the data accordingly.
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Filter the long term data
-
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
-
- ## Filter the short term data
-
-  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
-                         abb.data$nightly.rate <= 500, ]
-
-  countCleaning('rates.rents')
-
-```
-
-### Locations and Submarkets
-
-Location is clearly an important determinant in both the short and long term rental markets.
-At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
-Suburbs in Melbourne are much smaller than their North American counterparts.
-The specific suburb of a property is the second, or finer scale, at which the market operates.
-The plot below shows the three large submarkets (Inner, Middle and Outer).
-
-```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Convert shapefile to ggplot-able object
-
-  # Fix lat/long
-
-  # Limit to extent of data
-  sub.table <- table(ltr.data$suburb)
-  sub.table <- sub.table[sub.table != 0]
-
-  # Clip to only those with a ltral observation
-  study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
-
-  # Convert to an outer bound with holes
-  ss.bound <- gUnaryUnion(study.suburbs)
-
-  # Remove holes from the shapefile
-  ssb <- slot(ss.bound, "polygons") 
-  holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
-                                          slot, "hole"))
-  res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
-  IDs <- row.names(ss.bound) 
-  ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
-   Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound)))
-
-  # Identify which suburbs all in area covered by outer bound
-  ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
-  study.suburbs <- suburbs.shp[which(ss.in), ]
-
-  # Convert into a ggplot-able format
-  subs <- fortify(study.suburbs, region='name_2006')
-
-  # Add suburb category
-  subs$des <- suburbs.shp@data$suburbdesi[
-    match(subs$id, suburbs.shp@data$name_2006)]
-
-```
-
-```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- ## Build the map object
-
-  # Set colors
-  g.cols <- abb.col[c(2, 10, 9)]
-
-  # Make map
-  loc.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-    scale_fill_manual(values=g.cols, labels=c('Inner      ',
-                                              'Middle      ',
-                                              'Outer')) +
-    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
-    ggtitle("Melbourne Suburb Classifications")
-
-```
-
-```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
-
-  loc.map
-
-```
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
-While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
-We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-
-We select the 18 suburbs below to represent the 'core' of the city.
-The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenties for tourists.
-
-```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
-                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
-                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
-                   'St Kilda West', 'West Melbourne', 'Windsor')
-
-```
-
-We then apply a 500 meter buffer to the beach along Port Phillip Bay.
-
-```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Determine centroid of study area
-
-  latMid <- median(abb.data$latitude)
-  longMid <- median(abb.data$longitude)
-
- # Calculate Degress to Meters conversion
-
-  m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
-  m.long = 111132.954 * cos (latMid)
-  m.conv <- mean(m.lat, m.long)
-
- # Create the beach buffer
-
-  beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
-
-```
-
-Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
-
-```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Short term data
-
-  # Convert to point shapefile
-  abb.prop.shp <- SpatialPointsDataFrame(cbind(abb.data$longitude,
-                                               abb.data$latitude),
-                                         abb.data,
-                                         proj4string=CRS("+init=epsg:4283"))
-
-  # Add suburb name 
-  spJoin <- over(abb.prop.shp, suburbs.shp)
-  abb.data$suburb <- as.character(spJoin$name_2006)
-  abb.data$suburb[is.na(abb.data$suburb)] <- 'missing'
-
-  # Add suburb designation
-  abb.data$sub.class <- as.character(spJoin$suburbdesi)
-  abb.data$sub.class[is.na(abb.data$sub.class)] <- 'missing'
-
-  # Add SA1 designation
-  spJoin <- over(abb.prop.shp, sa1s.shp)
-  abb.data$sa1 <- spJoin$sa1_main11
-
-  ## Add Beach Designation
-  spJoin <- over(abb.prop.shp, beach.buffer)
-  abb.data$beach <- ifelse(is.na(spJoin), 0 ,1)
-
-  # Remove those missing a suburb classification (out of area)
-  abb.data <- abb.data[abb.data$sub.class != 'missing', ]
-  abb.data <- abb.data[abb.data$sa1 != 'missing', ]
-
-```
-
-```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Add the submarket designations
-
-  # Add individual classes
-  abb.data$sub.mrkt <- 'rural'
-  abb.data$sub.mrkt[abb.data$sub.class == 'Middle'] <- 'suburban'
-  abb.data$sub.mrkt[abb.data$sub.class == 'Inner'] <- 'city'
-  abb.data$sub.mrkt[abb.data$suburb %in% core.suburbs] <- 'city-core'
-  abb.data$sub.mrkt[abb.data$beach == 1] <- 'beach'
-
-  # Order the factors properly
-  abb.data$sub.mrkt <- factor(abb.data$sub.mrkt, 
-                              levels=c('city-core', 'city', 'suburban', 
-                                        'rural', 'beach'))
-
-```
-
-Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
-For those without either (3% of the total) we remove them from the dataset at this point.
-
-```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Label those missing lat/long
-
-  miss.LL <- which(is.na(ltr.data$latitude))
-
- # Create a field to indicate the approximate matches
-
-  ltr.data$miss.LL <- 0
-  ltr.data$miss.LL[miss.LL] <- 1
-
- # Apply approximate match
-
-  ltr.data$latitude[miss.LL] <- ltr.data$street.latitude[miss.LL]
-  ltr.data$longitude[miss.LL] <- ltr.data$street.longitude[miss.LL]
-
- # Remove those still missing latitude data
-
-  ltr.data <- ltr.data[!is.na(ltr.data$latitude), ]
-
-```
-
-Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.
-
-```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Long term data
-
-  # Convert to point shapefile
-
-  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.data$longitude,
-                                               ltr.data$latitude),
-                                         ltr.data,
-                                         proj4string=CRS("+init=epsg:4283"))
-
-  # Add suburb name
-
-  spJoin <- over(ltr.prop.shp, suburbs.shp)
-  ltr.data$suburb <- as.character(spJoin$name_2006)
-  ltr.data$suburb[is.na(ltr.data$suburb)] <- 'missing'
-
-  # Add suburb designation
-
-  ltr.data$sub.class <- as.character(spJoin$suburbdesi)
-  ltr.data$sub.class[is.na(ltr.data$sub.class)] <- 'missing'
-
-  # Add SA1 designation
-
-  spJoin <- over(ltr.prop.shp, sa1s.shp)
-  ltr.data$sa1 <- spJoin$sa1_main11
-
-  ## Add Beach Designation
-
-  spJoin <- over(ltr.prop.shp, beach.buffer)
-  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)
-
-  # Remove those missing a suburb classification (out of area)
-
-  ltr.data <- ltr.data[ltr.data$sub.class != 'missing', ]
-  ltr.data <- ltr.data[ltr.data$sa1 != 'missing', ]
-
-```
-
-```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Add the submarket designations
-
-  # Add individual classes
-  ltr.data$sub.mrkt <- 'rural'
-  ltr.data$sub.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
-  ltr.data$sub.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
-  ltr.data$sub.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
-  ltr.data$sub.mrkt[ltr.data$beach == 1] <- 'beach'
-
-  # Order the factors properly
-  ltr.data$sub.mrkt <- factor(ltr.data$sub.mrkt, 
-                              levels=c('city-core', 'city', 'suburban', 
-                                        'rural', 'beach'))
-
-  countCleaning('location')
-
-```
-
-```{r write_afterspobj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-after.SP <- list(abb.data=abb.data,
-                 ltr.data=ltr.data)
-
-save(after.SP, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_afterSP.RData")
-
-```
-
-The location of the short and long term rentals, colored by submarket, are shown below
-
-```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Set submarket colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
-  # Make map
-
-  abb.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
-               alpha=.2) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) + 
-    ggtitle('AirBNB Location\nBy Submarket')
-
-```
-
-```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Make map
-
-  ltr.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
-    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
-               alpha=.1) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) + 
-    ggtitle('Long Term Rental Location\nBy Submarket')
-
-```
-
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
-
-  ggMultiPlots(abb.map, ltr.map, cols=2)
-
-```
-
-The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
-
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
-
-  # Make Airbnb submarket map
-
-  abbtype.map <- ggplot() +
-    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank()) +
-    ggtitle('AirBNB Property Type\nBy Submarket')
-
-  # Make Long term rental map
-
-  ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank()) +
-    ggtitle('Long Term Property Type\nBy Submarket')
-
-```
-
-```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
-
-  ggMultiPlots(abbtype.map, ltrtype.map, cols=2)
-
-```
-
-Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Convert suburbs from factor to character
-  abb.data$suburb <- as.character(abb.data$suburb)
-  ltr.data$suburb <- as.character(ltr.data$suburb)
-
-```
-
-&nbsp;
-
-## Filter Transaction Data
-
-The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets
-
-```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Short term data
-
-  daily.data <- daily.data[daily.data$property.id %in% abb.data$property.id,]
-
- ## Long term list data
-
-  listing.data <- listing.data[listing.data$activity.id %in% ltr.data$activity.id,]
-
-```
-
 ## Revenue Estimation
@@
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Determine # of booking for each airbnb
-  abb.data$bookings <- (abb.data$total.days - 
-                          abb.data$blocked.days - 
-                           abb.data$available.days)
-
-  # Determine property specific occupancy rate
-  abb.data$occ.rate <- (abb.data$bookings / 
-                           (abb.data$total.days - abb.data$blocked.days))
-
-  # Set the blocked rate
-  abb.data$blocked.rate <- abb.data$blocked.days / abb.data$total.days
 
@@
   abb.data$extr.par <- 366 / abb.data$total.days
-
-```
-
-Next we extract all of the daily reservation data that fits our criteria -- reserved, not imputed and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data.
-We do this step to remove those].
-From this information we calculate the median nightly reservation price for each property and append it to the property level data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Get all of the reservations
-  resv.daily <- daily.data[daily.data$status == 'R' &
-                             daily.data$booked.date != 'imputed' &
-                              daily.data$price < 500, ]
-
-  # Calculate the property specific median nightly rate
-  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-
-  # Add median rate to the property  
-  abb.data$med.rate <- med.daily$Var[match(abb.data$property.id, med.daily$ID)]
 

### 2017-02-04 abb_Functions.R

@@ -278,4 +278,58 @@ abbCalcBookStr <- function(id,
                     med.block=med.block))
 }
 
+### Set the cleaning counter -------------------------------------------------------------
+
+setCleanCount <- function(){
+  
+  # Make counts of initial sizes
+  str.orig <- nrow(str.data)
+  daily.orig <- nrow(daily.data)
+  ltr.orig <- nrow(ltr.data)
+  list.orig <- nrow(listing.data)
+  
+  # Create initial data.frame
+  clean.df <- data.frame(operation='initial',
+                         str=str.orig,
+                         daily=daily.orig,
+                         ltr=ltr.orig,
+                         list=list.orig)
+  
+  # Assign initial values to globalEnv
+  assign('clean.count', clean.df, envir=.GlobalEnv)
+  assign('str.run.total', nrow(str.data), envir=.GlobalEnv)
+  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
+  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
+  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
+  
+}
+
+### Cleaning counting updater ------------------------------------------------------------
+
+countCleaning <- function(operation){
+
+  # Count recent cuts  
+  str.cut <- str.run.total - nrow(str.data)
+  daily.cut <- daily.run.total - nrow(daily.data)
+  ltr.cut <- ltr.run.total - nrow(ltr.data)
+  listing.cut <- list.run.total - nrow(listing.data)
+  
+  # Build new dataframe
+  new.df <- data.frame(operation=operation,
+                       str=str.cut,
+                       daily=daily.cut,
+                       ltr=ltr.cut,
+                       list=listing.cut)
+  
+  # Add to existing DF
+  comb.df <- rbind(clean.count, new.df)
+  
+  # Assign temp data to globalEnv
+  assign('clean.count', comb.df, envir=.GlobalEnv)
+  assign('str.run.total', nrow(str.data), envir=.GlobalEnv)
+  assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
+  assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
+  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
+  
+}
 

### 2017-02-04 abb_str_PreProcess.R

@@ -6,14 +6,7 @@
 
  ## Load libraries
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
-  library(ggmap)
-  library(xtable)
   library(chron)
-  library(RColorBrewer)
   library(plyr)
   library(stringr)
 
@@ -73,10 +66,12 @@
   
   # Add summary data to property data
   
-  str.data <- merge(str.data, daily.summ, by='property.id')
+  str.data <- merge(str.data, daily.summ, 
+                    by.x='property.id',
+                    by.y='id')
 
  ## Write out data  
 
-  save(str.data, file=paste0(data.path, 'stpropdata.RData'))
-  save(daily.data, file=paste0(data.path, 'stdailydata.RData'))
+  save(str.data, file=paste0(data.path, 'prepared/stpropdata.RData'))
+  save(daily.data, file=paste0(data.path, 'prepared/stdailydata.RData'))
   

### 2017-02-05 abbDataAnalysis_Script.Rmd
start analysis script

--- 2017-01-26 abbDataPrep_Script.Rmd
@@
 ---
-title: "AirBNB Data Preparation and Imputation"
-output: html_notebook
+title: "Abb Analysis"
+author: "Andy Krause and Gideon Aschwanden"
+date: "February 5, 2017"
+output: html_document
 ---
@@
 
-This file details the initial data preparation that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).
-This is not a 'data cleaning' exercise as we are not removing data points based on observed values.
+&nbsp;
+
+### Preliminary Commands
 
 &nbsp;
-&nbsp;
 
-### Setup
-
-We begin by loading the necessary libraries, set the path to the data and loading a set of custom data munging functions.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE}
-
- ## Load libraries
+```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
@@
   library(chron)
+  library(plyr)
+  library(sp)
+  library(rgeos)
+  library(reshape2)
+  library(stringr)
   library(RColorBrewer)
-  library(plyr)
-  library(stringr)
+  library(Hmisc)
 
- ## Set location
+```
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
   # Get computer names
+
   comp.name <- Sys.info()['nodename']
@@
   # Assign path based on computer name
-  if(comp.name == '7020D-121777-W' | 
-      comp.name == 'DESKTOP-1D7JO4J'){
+
+  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
 
     data.path <- 'c:/dropbox/research/airBNB/data/'
+    code.path <- 'c:/code/'
+    fig.path <- 'c:/dropbox/research/airBNB/figures/'
 
@@
 
-      data.path <- 'other path'
+    data.path <- 'alternate data path'
+    code.path <- 'alternate data path'
+    fig.path <- 'alternate data path'
 
@@
 
- ## Load sources
+```
 
-  source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+ # Current Project files
+
+  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
+
+ # Other custom files
+
+  source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
+                '/master/ggPlotTools.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
+                '/master/dataMungeTools.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
+                '/master/spatialLogitModels.R'))
+  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
+                '/master/point2surface_Tools.R'))
 
@@
 
-&nbsp;
-&nbsp;
+```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-## Short Term (Airbnb) Data
+  # Property Information
 
-We begin the data preparation with the Airbnb data.
-
-### Load data
-
-Next we load the raw property level and nightly level AirBNB reservation data received from AirDNA.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- ## Property Information
-
-  prop.data <- read.csv(paste0(data.path, '/raw/melbproperties.csv'), header=T)
-
-  ## Daily rental information
-
-  daily.data  <- read.csv(paste0(data.path, '/raw/melbDaily.csv'), header=T)
+  load(paste0(data.path, 'prepared/prep_workspace.RData'))
 
@@
 
-&nbsp;
-&nbsp;
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-### Data Transformations
+  str.data$str.revenue <- str.data$bookings * str.data$med.rate
 
-To make future coding easier, we convert all field names to lower case.
+  str.data$extr.par <- 366 / str.data$total.days
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  names(prop.data) <- tolower(names(prop.data))
-  names(daily.data) <- tolower(names(daily.data))
+  str.data$str.full.revenue <- (str.data$bookings * str.data$extr.par *
+                                  str.data$med.rate)
 
@@
 
-We also then convert date values into correct R formatted dates. We also create a year created variable for the property data.
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
+  # Calculate the actual revenue
+  ltr.data$ltr.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
 
- ## Daily data
+  # Remove those with very low revenues (due to very long DOMs)
+  ltr.data <- ltr.data[ltr.data$ltr.revenue > 10000, ]
 
-  daily.data$date <- as.Date(daily.data$date)
-
- ## Property level data
-
-  prop.data$created.date <- as.Date(prop.data$created.date)
-  prop.data$created.year <- as.numeric(substr(prop.data$created.date, 1, 4))
+  countCleaning('revenue')
 
 ```
-
-&nbsp;
-&nbsp;
-
-### Add Summary Information
-
-We now add summary information regarding the number of bookings, number of free and blocked nights to the property level data.
-This information will assist in future imputation exercises and other analyses.
-
-We start by splitting the daily date into a list where each object is a data.frame of daily observations for a particular property.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  daily.prop <- split(daily.data, daily.data$property.id)
-
-```
-
-Next, we apply the **abbAnalyzeDaily()** function to each data.frame of daily observations.
-This process produces a list of results, by property.id.
-These lists are then collapsed into a single data.frame.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  daily.summ.list <- lapply(daily.prop, abbAnalyzeDaily)
-  daily.summ <- rbind.fill(daily.summ.list)
-
-```
-
-Finally, we add the summarized data to the existing property-level information.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
-  prop.data <- merge(prop.data, daily.summ, by='property.id')
-
-```
-
-&nbsp;
-&nbsp;
-
-Finally, we write the amended daily and property data to .csv files for future analysis.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}
-
- write.csv(all.daily, paste0(data.path, 'prepared/dailydata.csv'), row.names=FALSE)
-
- write.csv(prop.data, paste0(data.path, 'prepared/propdata.csv'), row.names=FALSE)
-
-```

### 2017-02-05 abbDataPrep_Script.Rmd
start analysis script

@@
 
+  ## Remove those with less than 180 observed days (missing obs)
+  str.data <- str.data[str.data$total.days >= 180, ]
+
 ```
@@
 
-  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, beach.shp, core.suburbs,
-       exch.rate, ltr.col, str.col, sa1s.shp, suburbs.shp, study.suburbs,
+  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
+       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
+       suburbs.shp, study.suburbs,
        file=paste0(data.path, 'prepared/prep_workspace.RData'))
-```
+
+```

### 2017-02-06 abb_ltr_PreProcess.R
Fix year bug

@@ -56,7 +56,7 @@
   
  ## Remove those not occuring in 2015 or later
   
-  r16 <- r16[r16$event.year > 2014, ]
+  r16 <- r16[r16$event.year >= 2014, ]
   
  ## Add an identifier that signifies last record in a set of advertisements (of record)  
     
@@ -115,7 +115,7 @@
  ## Write out data
   
   export.path <- paste0(data.path, '/prepared/')
-  save(ltr.data, file=paste0(data.path, 'ltpropdata.RData'))
-  save(listing.data, file=paste0(data.path, 'ltlistdata.RData'))
+  save(ltr.data, file=paste0(export.path, 'ltpropdata.RData'))
+  save(listing.data, file=paste0(export.path, 'ltlistdata.RData'))
   
  

### 2017-02-06 analysis_functions.R
removal of analyis_functions file

@@ -1,924 +1,0 @@
-
-### Basic engine for calculating the revenues for abb and ltr ----------------------------
-
-revenueEngine <- function(abb.df,
-                          ltr.df,
-                          rate.field='med.rate',
-                          rent.field='event.price',
-                          occ.field='occ.rate',
-                          dom.field='dom',
-                          cost.list=NULL)
-{
-  
- ## Calculate Airbnb Revenues  
-  
-  abb.rev <- abb.df[ ,rate.field] * 365 * abb.df[ ,occ.field]
-
- ## Calculate long term rental revenues  
-    
-  ltr.rev <- ltr.df[, rent.field] * (52 - (ltr.df[ ,dom.field] / 7))
-  
- ## Save for future costs
-  
- ## Return values  
-  
-  return(list(abb=abb.rev,
-              ltr=ltr.rev))
-  
-}
-
-### Cross impute rates and rents ---------------------------------------------------------
-
-imputeRatesRents <- function(ltr.df,
-                             abb.df,
-                             ltr.mod.spec,
-                             abb.mod.spec,
-                             clip.fields=NULL)
-{
-  
- ## Arguments
-  
-  # ltr.df:  data.frame of long term rental observations
-  # abb.df:  data.frame of airbnb properties
-  # ltr.mod.spec:  specification for rent price model
-  # abb.mod.spec:  specification for airbnb properties
-  # clip.field: field to ensure factors match between rent and abb
-  
- ## Remove those within the clip field that isn't present in both  
-  
-  if(!is.null(clip.fields)){
-    
-    for(i.cf in 1:length(clip.fields)){
-    
-      # Find the fields that are used to clip
-      l.cf <- which(names(ltr.df) == clip.fields[i.cf])
-      a.cf <- which(names(abb.df) == clip.fields[i.cf])
-    
-      # Get IDs for those to be removed
-      id.l <- ltr.df[ ,l.cf] %in% names(table(as.character(abb.df[ ,a.cf])))
-      id.a <- abb.df[ ,a.cf] %in% names(table(as.character(ltr.df[ ,l.cf])))
-    
-      # Filter out obs missing matched factors  
-      ltr.df <- ltr.df[id.l, ]
-      abb.df <- abb.df[id.a, ]
-    
-    }
-    
- }
-
[…]

### 2017-02-06 abb_Functions.R
migrate all functions to one file

@@ -333,3 +333,909 @@ countCleaning <- function(operation){
   
 }
 
+### Cross impute rates and rents ---------------------------------------------------------
+
+imputeRents <- function(ltr.df,
+                        str.df,
+                        mod.specs,
+                        clip.fields=NULL)
+{
+  
+  ## Arguments
+  
+  # ltr.df:  data.frame of long term rental observations
+  # str.df:  data.frame of airbnb properties
+  # ltr.mod.spec:  specification for rent price model
+  # str.mod.spec:  specification for airbnb properties
+  # clip.field: field to ensure factors match between rent and str
+  
+  ## Remove those within the clip field that isn't present in both  
+  
+  if(!is.null(clip.fields)){
+    
+    for(i.cf in 1:length(clip.fields)){
+      
+      # Find the fields that are used to clip
+      l.cf <- which(names(ltr.df) == clip.fields[i.cf])
+      s.cf <- which(names(str.df) == clip.fields[i.cf])
+      
+      # Get IDs for those to be removed
+      id.l <- ltr.df[ ,l.cf] %in% names(table(as.character(str.df[ ,s.cf])))
+      id.s <- str.df[ ,s.cf] %in% names(table(as.character(ltr.df[ ,l.cf])))
+      
+      # Filter out obs missing matched factors  
+      ltr.df <- ltr.df[id.l, ]
+      str.df <- str.df[id.s, ]
+      
+    }
+    
+  }
+  
+  ## Add the monthly factors
+  
+  str.df$ltr.month <- 12
+  
+  ## Build regression models for rental values
+  
+  ltr.mod <- lm(ltr.mod.spec, data=ltr.df)
+  
+  ## Add the fitted values to the long term data
+  
+  ltr.df$imp.rent <- exp(ltr.mod$fitted)
+  
+  ## Add the predicted values to the short term data
+  
+  str.df$imp.rent <- exp(predict(ltr.mod, str.df))
+  
+  ## If Imputing for LTR
+  
+  if(imp.ltr){
+  
+    # Build regression models
+    str.mod <- lm(str.mod.spec, data=str.df)
+  
+    # Add the fitted values to the long term data
+    str.df$imp.rate <- exp(str.mod$fitted)
+  
+    # Add the predicted values to the short term data
+    ltr.df$imp.rate <- exp(predict(str.mod, ltr.df))
+  
+  } else {
+    
+    ltr.df <- ltr.mod <- NULL
+  
+  }
+    
+  ## Return Values  
+  
+  return(list(str=str.df,
[…]

### 2017-02-06 abbDataPrep_Script.Rmd
adding clean counting objects

@@
        beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
-       suburbs.shp, study.suburbs,
+       suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
+       ltr.run.total, str.run.total,
        file=paste0(data.path, 'prepared/prep_workspace.RData'))

### 2017-02-06 abb_Functions.R
restructure imputation options

@@ -337,7 +337,7 @@ countCleaning <- function(operation){
 
 imputeRents <- function(ltr.df,
                         str.df,
-                        mod.specs,
+                        mod.spec,
                         clip.fields=NULL)
 {
   
@@ -377,41 +377,18 @@ imputeRents <- function(ltr.df,
   
   ## Build regression models for rental values
   
-  ltr.mod <- lm(ltr.mod.spec, data=ltr.df)
-  
-  ## Add the fitted values to the long term data
-  
-  ltr.df$imp.rent <- exp(ltr.mod$fitted)
+  ltr.mod <- lm(mod.spec, data=ltr.df)
   
   ## Add the predicted values to the short term data
   
-  str.df$imp.rent <- exp(predict(ltr.mod, str.df))
-  
-  ## If Imputing for LTR
-  
-  if(imp.ltr){
-  
-    # Build regression models
-    str.mod <- lm(str.mod.spec, data=str.df)
-  
-    # Add the fitted values to the long term data
-    str.df$imp.rate <- exp(str.mod$fitted)
-  
-    # Add the predicted values to the short term data
-    ltr.df$imp.rate <- exp(predict(str.mod, ltr.df))
-  
-  } else {
-    
-    ltr.df <- ltr.mod <- NULL
-  
-  }
-    
+  imp.rent <- exp(predict(ltr.mod, str.df))
+
   ## Return Values  
   
-  return(list(str=str.df,
-              ltr=ltr.df,
-              str.mod=str.mod,
-              ltr.mod=ltr.mod))
+  return(list(str=data.frame(property.id=str.df$property.id,
+                             imp.rent=imp.rent),
+              mod=ltr.mod))
+              
 }
 
 ### Basic engine for calculating the revenues for abb and ltr ----------------------------

### 2017-02-06 abbDataAnalysis_Script.Rmd
re-working global imputation

@@
   library(Hmisc)
+  library(kernlab)
 
@@
 
-  str.data$str.revenue <- str.data$bookings * str.data$med.rate
+  str.data$str.act.revenue <- str.data$bookings * str.data$med.rate
 
@@
 
-  str.data$str.full.revenue <- (str.data$bookings * str.data$extr.par *
+  str.data$str.ext.revenue <- (str.data$bookings * str.data$extr.par *
                                   str.data$med.rate)
+
+  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)
+
+  str.data$pot.occ.rate <- str.data$bookings / (366 - (366 * str.data$block.rate))
+
+  str.data$str.pot.revenue <- (str.data$pot.occ.rate * 366 * str.data$med.rate)
 
@@
 ```
+
+### Host types
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(str.data, aes(x=block.rate)) + 
+  geom_density(fill=str.col, color=str.col) +
+  ylab('Frequency\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0,1,.2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Host Block Rate Frequency\n') +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  geom_point(fill=str.col, color=str.col, size=.2) +
+  ylab('Frequency\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Host Block Rate Frequency\n') +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
+
+str.data$host.type <- 'Unknown'
+str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
+str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
+str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
+str.data$host.type <- factor(str.data$host.type,
+                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                      'Multi-Platform User', 'Unknown'))
+
+ggplot(str.data, 
+       aes(x=block.rate, y=blockpertime, color=host.type)) + 
+  geom_point(alpha=.5, size=.8, shape=15) +
+  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ggplot(str.data, aes(host.type, fill=host.type)) +
+  geom_bar() +
+  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+  theme(legend.position='none')
+
+```
+
+## Global Market Analysis
+
+We now analyze the full metro market to test which properties are more profitable as short-term rentals.
+
+We start by specifying the imputation models for the LTR and the Airbnb datasets
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
+
+```
+
+We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  imp.rents <- imputeRents(ltr.df=ltr.data, 
+                           str.df=str.data, 
+                           mod.spec=ltr.mod.spec,
+                           clip.field='suburb')
+
+  str.glob <- merge(str.data, imp.rents$str, by='property.id')
+
+```
+
+Next we cross impute days on market and occupancy rates.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Apply dom to abb
+  str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median')
+
+```
+
+HERE HERE HERE
+
+With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  impx.revs <- revenueEngine(str.df=ltr.imp, 
+                             ltr.df=str.imp,
+                             rate.field='imp.rate',
+                             rent.field='imp.rent',
+                             occ.field='imp.occ',
+                             dom.field='imp.dom')
+
+  str.imp$ltr.imp.revenue <- impx.revs$ltr
+  ltr.imp$str.imp.revenue <- impx.revs$str
+
+```
+
+Next, we compare the revenues from the two and extract the new datasets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  comp.revs <- compareRevenues(str.imp)
+
+  str.imp <- merge(str.imp, comp.revs, by='property.id')
+
+```
+
+### Analyze Results
+
+First we make a comparison table of the results, broken down by submarket.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mrkt.table <- createCompTable(str.imp, 'sub.mrkt')
+
+  mrkt.table$ID <- factor(mrkt.table$ID, 
+                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+
+```
+
+We plot these results in a 2x2 matrix to show the preference likelihoods under the 4 possible scenarios.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
+  twotwo.bar.plot <- 
+    ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
+    geom_bar() +
+    facet_grid(~rev.type) +
+    scale_fill_manual(values=sm.col) +
+    xlab('') +
+    ylab('% of properties where Airbnb is more profitable') +
+    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none')
+
+```
+
+Next, we plot the \% of properties that have short-term preference versus the occupancy rate
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rawocc.pplot <- makePrefPlot(str.imp,
+                               x.field='pot.occ.rate',
+                               y.field='str.ext.pref',
+                               group.field='host.type',
+                               smooth=TRUE,
+                               smooth.span=.75)
+  rawocc.pplot <- rawocc.pplot +
+    xlab('\nOccupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col)
+
+```
+
+Looking at the distribution of occupancy rates, we that it is not uniform in any of the submarkets.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.revs$sub.mrkt <- factor(str.imp$sub.mrkt, 
+                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+  ggplot(str.imp, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
+    geom_density(alpha=.3) +
+    facet_wrap(~sub.mrkt) +
+    scale_color_manual(values=sm.col) +
+    scale_fill_manual(values=sm.col) +
+    scale_x_continuous(breaks=seq(0, 1, by=.5),
+                       labels=c('0%', '50%', '100%')) +
+    ylab('') +
+    xlab('Occupancy Rate') +
+    theme(legend.position='none',
+          axis.line=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks=element_blank(),
+          axis.title.y=element_blank())
+
+```
+
+We then calculate quantile values for rates and replot the charts
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.imp$occ.qtl <- makeWtdQtl(str.imp$occ.rate, 
+                                      return.type='rank') 
+  str.imp$rate.qtl <- makeWtdQtl(str.imp$med.rate, 
+                                  return.type='rank')
+
+  ## Make quartile location plot
+
+  qtlocc.pplot <- makePrefPlot(str.imp,
+                               x.field='occ.qtl',
+                               y.field='str.act.pref',
+                               group.field='sub.mrkt',
+                               smooth=TRUE,
+                               smooth.span=.75)
+  qtlocc.pplot <- qtlocc.pplot +
+    xlab('\nQualtile of Occupancy Rate') +
+    ylab('\n% of Properties where Airbnb is more profitable') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    scale_color_manual(values=sm.col)
+
+```
+
+Next we build a heat map that shows which combinations of occ rate and nightly rate are most likely to result in short-term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm <- makeHeatMap(str.imp,
+                x.field='occ.rate',
+                y.field='nightly.rate',
+                color.field='str.act',
+                bins=c(.05, 25),
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+
+  rate.hm <- rate.hm +
+    xlab('\n Occupancy Rate') +
+    ylab('\n Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom')
+
+```
+
+To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm.svm <- makeHeatMap(str.revs,
+                         x.field='occ.rate',
+                         y.field='nightly.rate',
+                         color.field='str.act',
+                         bins=c(.05, 25),
+                         svm=T, 
+                         alpha.count=F,
+                         add.points=T,
+                         fill.colors=c(abb.col[1], abb.col[5]))
+
+  rate.hm.svm <- rate.hm.svm +
+    xlab('\n Occupancy Rate') +
+    ylab('\n Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom')
+
+```
+
+Again, due to the non-uniformity of distribution of these two axis, we convert to quantiles and re-plot.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm <- makeHeatMap(str.revs,
+                         x.field='occ.qtl',
+                         y.field='rate.qtl',
+                         color.field='str.act',
+                         bins=c(5, 5),
+                         svm=F, 
+                         alpha.count=T,
+                         add.points=T,
+                         fill.colors=c(abb.col[1], abb.col[5]))
+
+  qtl.hm <- qtl.hm +
+    xlab('\n Quantile of Occupancy Rate') +
+    ylab('\n Quantile of Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    theme(legend.position='bottom')
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm.svm <- makeHeatMap(str.revs,
+                        x.field='occ.qtl',
+                        y.field='rate.qtl',
+                        color.field='str.act',
+                        bins=c(5, 5),
+                        svm=T, 
+                        alpha.count=F,
+                        add.points=T,
+                        fill.colors=c(abb.col[1], abb.col[5]))
+
+  qtl.hm.svm <- qtl.hm.svm +
+    xlab('\n Quantile of Occupancy Rate') +
+    ylab('\n Quantile of Nightly Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    scale_y_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0', '25th', '50th', '75th', '100th')) +
+    theme(legend.position='bottom')
+
+```
+
+Finally, we calculate the areas of the heat maps and combine into a table.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  svm.rate <- makeSVM(str.revs,
+                     x.field='occ.rate',
+                     y.field='nightly.rate',
+                     z.field='str.act',
+                     svm.type='C-svc',
+                     svm.kernel='polydot',
+                     poly.degree=4,
+                     expand.factor=100)
+
+  svm.qtl <- makeSVM(str.revs,
+                      x.field='occ.qtl',
+                      y.field='rate.qtl',
+                      z.field='str.act',
+                      svm.type='C-svc',
+                      svm.kernel='polydot',
+                      poly.degree=4,
+                      expand.factor=100)
+
+  market.ratio <- data.frame(type=c('rate', 'qtl'),
+                             actual=rep(mean(str.revs$str.act), 2),
+                             fitted=c(mean(svm.rate$orig$fitted),
+                                      mean(svm.qtl$orig$fitted)),
+                             svm=c(mean(svm.rate$pred$pred),
+                                   mean(svm.qtl$pred$pred)))
+```
+
+### Submarkets
+
+We now take the analytical process just completed on the entire metro and apply it to various submarkets.  We use a custom function that combines all the processes above into a single command.
+
+#### Property Type
+
+We start by comparing apartments to houses.  First we set a new imputation model specification
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set model specifications
+  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
+                            as.factor(ltr.month))
+  str.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
+
+```
+
+We then recompute the market analysis for each property type.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Select data
+  str.apt <- which(str.revs$type == 'Apartment')
+  ltr.apt <- which(ltr.revs$type == 'Apartment')
+
+  # Estimate House Results  
+  house <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
+                              str.df=str.revs[-str.apt, ],
+                              ltr.mod.spec=ltr.mod.spec,
+                              str.mod.spec=str.mod.spec,
+                              clip.field='suburb',
+                              market.field='none',
+                              mrkt.col=sm.col,
+                              heat.col=c(abb.col[1], abb.col[5]))
+
+   apt <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.apt,],
+                             str.df=str.revs[str.apt, ],
+                             ltr.mod.spec=ltr.mod.spec,
+                             str.mod.spec=str.mod.spec,
+                             clip.field='suburb',
+                             market.field='sub.mrkt',
+                             mrkt.col=sm.col,
+                             heat.col=c(abb.col[1], abb.col[5]))
+
+```

### 2017-02-07 abbDataAnalysis_Script.Rmd
glob.updates

@@
 
-  str.data$pot.occ.rate <- str.data$bookings / (366 - (366 * str.data$block.rate))
+  str.data$pot.occ.rate <- (str.data$bookings * str.data$extr.par) / (366 - (366 * str.data$block.rate))
 
@@
 
-  imp.rents <- imputeRents(ltr.df=ltr.data, 
+  imp.data <- imputeLtrRents(ltr.df=ltr.data, 
                                str.df=str.data, 
-                           mod.spec=ltr.mod.spec,
-                           clip.field='suburb')
+                               mod.specs=ltr.mod.spec,
+                               match.factor='suburb')
 
-  str.glob <- merge(str.data, imp.rents$str, by='property.id')
+```
+
+From the imputed results, we extract the base data (with imputed values) as well as the model summaries.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Extract out DFs (only those that imputed)
+  str.glob <- merge(str.data, imp.data$imp.rent, by='property.id')
 
@@
 
-HERE HERE HERE
-
 With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.
@@
 
-  impx.revs <- revenueEngine(str.df=ltr.imp, 
-                             ltr.df=str.imp,
-                             rate.field='imp.rate',
-                             rent.field='imp.rent',
-                             occ.field='imp.occ',
-                             dom.field='imp.dom')
-
-  str.imp$ltr.imp.revenue <- impx.revs$ltr
-  ltr.imp$str.imp.revenue <- impx.revs$str
+  str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7)
 
@@
 
-  comp.revs <- compareRevenues(str.imp)
+  comp.revs <- compareRevenues(str.glob)
 
-  str.imp <- merge(str.imp, comp.revs, by='property.id')
+  str.glob <- merge(str.glob, comp.revs, by='property.id')
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+abbImputeCompare <- function(str.df,
+                             ltr.df,
+                             mod.spec, 
+                             match.factor=NULL,
+                             split.field=NULL){
+
+  if(!is.null(split.field)){
+
+    str.list <- split(str.df, str.df[ ,split.field])
+    ltr.list <- split(ltr.df, ltr.df[ ,split.field])
+
+  } else {
+
+    str.list <- list(str.df)
+    ltr.list <- list(ltr.df)
+
+  }
+
+  imp.list <- list()
+
+  for(il in 1:length(str.list)){
+
+    imp.temp <- imputeLtrRents(ltr.df=ltr.df, 
+                                     str.df=str.df, 
+                                     mod.specs=mod.spec,
+                                     match.factor=match.factor)
+
+    str.list[[il]] <- merge(str.list[[il]], imp.temp$imp.rent, by='property.id')
+    imp.list[[il]] <- imp.temp
+
+    str.list[[il]]$imp.dom <- imputeDOM(str.list[[il]], 
+                                        ltr.data[[il]], 
+                                        calc.type='median')
+    str.list[[il]]$ltr.imp.revenue <- str.list[[il]]$imp.rent * (52 - str.list[[il]]$imp.dom / 7)
+
+    comp.revs <- compareRevenues(str.list[[il]])
+
+    str.list[[il]] <- merge(str.list[[il]], 
+                            comp.revs, 
+                            by='property.id')
+
+  }
+
+  str.df <- rbind.fill(str.list)
+  str.df$split.field <- split.field
+
+                             }
 
@@
 
-  mrkt.table <- createCompTable(str.imp, 'sub.mrkt')
+  mrkt.table <- createCompTable(str.glob, 'sub.mrkt')
 
@@
   sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+  ht.col <- abb.col(c(2, 4, 10, 9)]
 
-  twotwo.bar.plot <- 
+  bar.plot <- 
     ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
@@
 
-  rawocc.pplot <- makePrefPlot(str.imp,
+  rawocc.pplot <- makePrefPlot(str.glob,
                                x.field='pot.occ.rate',
-                               y.field='str.ext.pref',
-                               group.field='host.type',
+                               y.field='str.pot.pref',
+                               group.field='sub.mrkt',
                                smooth=TRUE,
@@
 
-  str.revs$sub.mrkt <- factor(str.imp$sub.mrkt, 
+  str.glob$sub.mrkt <- factor(str.glob$sub.mrkt, 
                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
-  ggplot(str.imp, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
+  ggplot(str.glob, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
     geom_density(alpha=.3) +
@@
 
-  str.imp$occ.qtl <- makeWtdQtl(str.imp$occ.rate, 
+  str.glob$occ.qtl <- makeWtdQtl(str.glob$occ.rate, 
                                       return.type='rank') 
-  str.imp$rate.qtl <- makeWtdQtl(str.imp$med.rate, 
+  str.glob$rate.qtl <- makeWtdQtl(str.glob$med.rate, 
                                   return.type='rank')
@@
 
-  qtlocc.pplot <- makePrefPlot(str.imp,
+  qtlocc.pplot <- makePrefPlot(str.glob,
                                x.field='occ.qtl',
@@
 
-  rate.hm <- makeHeatMap(str.imp,
+  rate.hm <- makeHeatMap(str.glob,
                 x.field='occ.rate',
                 y.field='nightly.rate',
-                color.field='str.act',
+                color.field='str.act.pref',
                 bins=c(.05, 25),
@@
 
-  rate.hm.svm <- makeHeatMap(str.revs,
+  rate.hm.svm <- makeHeatMap(str.glob,
                          x.field='occ.rate',
                          y.field='nightly.rate',
-                         color.field='str.act',
+                         color.field='str.act.pref',
                          bins=c(.05, 25),
@@
 
-  qtl.hm <- makeHeatMap(str.revs,
+  qtl.hm <- makeHeatMap(str.glob,
                          x.field='occ.qtl',
                          y.field='rate.qtl',
-                         color.field='str.act',
+                         color.field='str.act.pref',
                          bins=c(5, 5),
@@
 
-  qtl.hm.svm <- makeHeatMap(str.revs,
+  qtl.hm.svm <- makeHeatMap(str.glob,
                         x.field='occ.qtl',
                         y.field='rate.qtl',
-                        color.field='str.act',
+                        color.field='str.act.pref',
                         bins=c(5, 5),
@@
 
-  svm.rate <- makeSVM(str.revs,
+  svm.rate <- makeSVM(str.glob,
                      x.field='occ.rate',
                      y.field='nightly.rate',
-                     z.field='str.act',
+                     z.field='str.act.pref',
                      svm.type='C-svc',
@@
 
-  svm.qtl <- makeSVM(str.revs,
+  svm.qtl <- makeSVM(str.glob,
                       x.field='occ.qtl',
                       y.field='rate.qtl',
-                      z.field='str.act',
+                      z.field='str.act.pref',
                       svm.type='C-svc',
@@
   market.ratio <- data.frame(type=c('rate', 'qtl'),
-                             actual=rep(mean(str.revs$str.act), 2),
+                             actual=rep(mean(str.glob$str.act.pref), 2),
                              fitted=c(mean(svm.rate$orig$fitted),

### 2017-02-07 abbDataAnalysis_Script.Rmd
Revert "re-working global imputation"
This reverts commit 108f255460ac4503081432f971eb95181152d6f0.

--- 2017-02-06 abbDataAnalysis_Script.Rmd
@@
                             as.factor(ltr.month))
+  str.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
+                            as.factor(bedbath) + as.factor(suburb))
 
@@
 
-  imp.rents <- imputeRents(ltr.df=ltr.data, 
+  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
                                str.df=str.data, 
-                           mod.spec=ltr.mod.spec,
+                               ltr.mod.spec=ltr.mod.spec, 
+                               str.mod.spec=str.mod.spec,
                                clip.field='suburb')
 
-  str.glob <- merge(str.data, imp.rents$str, by='property.id')
+```
+
+From the imputed results, we extract the base data (with imputed values) as well as the model summaries.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Extract out DFs (only those that imputed)
+  str.imp <- imp.data$str
+  ltr.imp <- imp.data$ltr
+
+  # Extract models
+  str.sum <- summary(imp.data$str.mod)
+  ltr.sum <- summary(imp.data$ltr.mod)
 
@@
   # Apply dom to abb
-  str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median')
+  str.imp$imp.dom <- imputeDOM(str.imp, ltr.imp, calc.type='median')
+
+  # Apply occ.rate to ltr
+  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, str.imp, calc.type='median')
 
 ```
-
-HERE HERE HERE
 

### 2017-02-07 abb_Functions.R
Revert "restructure imputation options"
This reverts commit 35a54492ac7c830cc88c3d10c1ef3d2dd38f3f5c.

@@ -337,7 +337,7 @@ countCleaning <- function(operation){
 
 imputeRents <- function(ltr.df,
                         str.df,
-                        mod.spec,
+                        mod.specs,
                         clip.fields=NULL)
 {
   
@@ -377,18 +377,41 @@ imputeRents <- function(ltr.df,
   
   ## Build regression models for rental values
   
-  ltr.mod <- lm(mod.spec, data=ltr.df)
+  ltr.mod <- lm(ltr.mod.spec, data=ltr.df)
+  
+  ## Add the fitted values to the long term data
+  
+  ltr.df$imp.rent <- exp(ltr.mod$fitted)
   
   ## Add the predicted values to the short term data
   
-  imp.rent <- exp(predict(ltr.mod, str.df))
-
+  str.df$imp.rent <- exp(predict(ltr.mod, str.df))
+  
+  ## If Imputing for LTR
+  
+  if(imp.ltr){
+  
+    # Build regression models
+    str.mod <- lm(str.mod.spec, data=str.df)
+  
+    # Add the fitted values to the long term data
+    str.df$imp.rate <- exp(str.mod$fitted)
+  
+    # Add the predicted values to the short term data
+    ltr.df$imp.rate <- exp(predict(str.mod, ltr.df))
+  
+  } else {
+    
+    ltr.df <- ltr.mod <- NULL
+  
+  }
+    
   ## Return Values  
   
-  return(list(str=data.frame(property.id=str.df$property.id,
-                             imp.rent=imp.rent),
-              mod=ltr.mod))
-              
+  return(list(str=str.df,
+              ltr=ltr.df,
+              str.mod=str.mod,
+              ltr.mod=ltr.mod))
 }
 
 ### Basic engine for calculating the revenues for abb and ltr ----------------------------

### 2017-02-07 abb_Functions.R
New ImpComp function

@@ -1096,65 +1096,93 @@ fullMarketAnalysis <- function(ltr.df,
               mrkt.score=market.ratio))
 }
 
-### Wrapper for all numeric comparison calculations --------------------------------------
+### Wrapper function to handle all of the imputation and comparison ----------------------
 
-revCompWrapper <- function(ltr.df,
-                           str.df,
-                           ltr.mod.spec,
-                           str.mod.spec,
-                           clip.field='suburb'){  
+abbImputeCompare <- function(str.df,
+                             ltr.df,
+                             mod.spec, 
+                             match.factor=NULL,
+                             split.field=NULL,
+                             verbose=FALSE){
   
+  ## Split data by field  
   
-  ## Impute rates and rents
+  # If field is specified
+  if(!is.null(split.field)){
+    
+    str.list <- split(str.df, str.df[ ,split.field])
+    ltr.list <- split(ltr.df, ltr.df[ ,split.field])
+    
+    if(verbose){
+      split.levels <- levels(as.factor(str.data[,split.field]))
+      cat('Splitting data into: ', paste(split.levels,
+                                         collapse='\n'), '\n')
+    }
+    
+    # If no field specified  
+  } else {
+    
+    str.list <- list(str.df)
+    ltr.list <- list(ltr.df)
+    
+    if(verbose){
+      cat('Data analyzed at global level')
+    }
+    
+  }
   
-  imp.data <- imputeRatesRents(ltr.df=ltr.df, 
+  ## Loop through split dfs
+  
+  # Set up capture list
+  imp.list <- list()
+  
+  # Run Loop
+  for(il in 1:length(str.list)){
+    
+    if(verbose) cat('Imputing and Comparing: ', split.levels[il], '\n')
+    
+    # Impute long term rents
+    imp.temp <- imputeLtrRents(ltr.df=ltr.df, 
                                str.df=str.df, 
-                               ltr.mod.spec=ltr.mod.spec, 
-                               str.mod.spec=str.mod.spec,
-                               clip.field=clip.field)
+                               mod.spec=mod.spec,
+                               match.factor=match.factor)
+    
+    # Add imputed LTRs to the STR data
+    str.list[[il]] <- merge(str.list[[il]], imp.temp$imp.rent, by='property.id')
+    imp.list[[il]] <- imp.temp
+    
[…]

### 2017-02-08 abb_Functions.R
update of viz functions

@@ -492,28 +492,128 @@ compareRevenues <- function(str.df){
   
 }
 
+### Wrapper function to handle all of the imputation and comparison ----------------------
+
+abbImputeCompare <- function(str.df,
+                             ltr.df,
+                             mod.spec, 
+                             match.factor=NULL,
+                             split.field=NULL,
+                             verbose=FALSE){
+  
+  ## Split data by field  
+  
+  # If field is specified
+  if(!is.null(split.field)){
+    
+    str.list <- split(str.df, str.df[ ,split.field])
+    ltr.list <- split(ltr.df, ltr.df[ ,split.field])
+    
+    if(verbose){
+      split.levels <- levels(as.factor(str.data[,split.field]))
+      cat('Splitting data into: ', paste(split.levels,
+                                         collapse='\n'), '\n')
+    }
+    
+    # If no field specified  
+  } else {
+    
+    str.list <- list(str.df)
+    ltr.list <- list(ltr.df)
+    
+    if(verbose){
+      cat('Data analyzed at global level')
+    }
+    
+  }
+  
+  ## Loop through split dfs
+  
+  # Set up capture list
+  imp.list <- list()
+  
+  # Run Loop
+  for(il in 1:length(str.list)){
+    
+    if(verbose) cat('Imputing and Comparing: ', split.levels[il], '\n')
+    
+    # Add quartile information to the data
+    
+    str.list[[il]]$rate.qtl <- makeWtdQtl(str.list[[il]]$med.rate, 
+                                          return.type='rank') 
+    str.list[[il]]$occ.qtl <- makeWtdQtl(str.list[[il]]$occ.rate, 
+                                         return.type='rank') 
+    str.list[[il]]$pot.occ.qtl <- makeWtdQtl(str.list[[il]]$pot.occ.rate, 
+                                             return.type='rank') 
+    
+    # Impute long term rents
+    imp.temp <- imputeLtrRents(ltr.df=ltr.df, 
+                               str.df=str.df, 
+                               mod.spec=mod.spec,
+                               match.factor=match.factor)
+    
+    # Add imputed LTRs to the STR data
+    str.list[[il]] <- merge(str.list[[il]], imp.temp$imp.rent, by='property.id')
+    imp.list[[il]] <- imp.temp
+    
+    # Impute days on market
+    str.list[[il]]$imp.dom <- imputeDOM(str.list[[il]], 
+                                        ltr.list[[il]], 
+                                        calc.type='median')
[…]

### 2017-02-08 abbDataAnalysis_Script.Rmd
rewrite of analysis and viz

--- 2017-02-06 abbDataAnalysis_Script.Rmd
@@
 
-  imp.rents <- imputeRents(ltr.df=ltr.data, 
+  imp.data <- imputeLtrRents(ltr.df=ltr.data, 
                                str.df=str.data, 
                                mod.spec=ltr.mod.spec,
-                           clip.field='suburb')
+                               match.factor='suburb')
 
-  str.glob <- merge(str.data, imp.rents$str, by='property.id')
+```
+
+From the imputed results, we extract the base data (with imputed values) as well as the model summaries.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Extract out DFs (only those that imputed)
+  str.glob <- merge(str.data, imp.data$imp.rent, by='property.id')
 
@@
 
-  comp.revs <- compareRevenues(str.imp)
+  comp.revs <- compareRevenues(str.glob)
 
-  str.imp <- merge(str.imp, comp.revs, by='property.id')
+  str.glob <- merge(str.glob, comp.revs, by='property.id')
 
@@
 
-### Analyze Results
+Realizing that the imputed long term rental values may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short term rentals, broken into submarkets by type, bed/bath and geographic area.
+In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
+for all compbinations of type, bed/bath and geographic area.
+We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals.
+
+```{r build.tbg.data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Create the type, bed/bath and geo sub market variable
+
+ str.data$tbg <- paste0(str.data$product,'.', str.data$sub.mrkt)
+ ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$sub.mrkt)
+
+ # Make IC estimates at TBG level
+
+ str.data.ic <- abbImputeCompare(str.df=str.data,
+                                 ltr.df=ltr.data,
+                                 mod.spec=ltr.mod.spec,
+                                 match.factor='suburb',
+                                 split.field='tbg',
+                                 verbose=TRUE)
+
+```
+
+## Analyze Results
 
@@
 
-  mrkt.table <- createCompTable(str.imp, 'sub.mrkt')
+ # Make Basic comparison table
+  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                   split.field='sub.mrkt')
 
-  mrkt.table$ID <- factor(mrkt.table$ID, 
-                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
+ # Convert to wide format for output
+  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
+
+ # Limit to the extrapolated pref type
+  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
 
@@
 
-We plot these results in a 2x2 matrix to show the preference likelihoods under the 4 possible scenarios.
+We then turn this into a simple chart to see the differences
 
@@
 
-  twotwo.bar.plot <- 
-    ggplot(mrkt.table, aes(x=ID, weights=Var, fill=ID)) + 
+  ggplot(pref.table, aes(x=ID, weights=Var, fill=ID)) + 
     geom_bar() +
@@
 
-  rawocc.pplot <- makePrefPlot(str.imp,
-                               x.field='pot.occ.rate',
-                               y.field='str.ext.pref',
-                               group.field='host.type',
+  str.data.ic$pref <- str.data.ic$str.ext.pref
+
+  rawocc.pplot <- abbPrefPlot(str.data.ic,
+                               x.field='occ.rate',
+                               split.field='sub.mrkt',
                                smooth=TRUE,
-                               smooth.span=.75)
-  rawocc.pplot <- rawocc.pplot +
-    xlab('\nOccupancy Rate') +
-    ylab('\n% of Properties where Airbnb is more profitable') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_color_manual(values=sm.col)
+                               smooth.span=.35 ,
+                              spl.col=sm.col)
+  rawocc.pplot
 
@@
 
-  str.revs$sub.mrkt <- factor(str.imp$sub.mrkt, 
-                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
-  ggplot(str.imp, aes(x=pot.occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
+  ggplot(str.data.ic, aes(x=occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
     geom_density(alpha=.3) +
@@
 
-  str.imp$occ.qtl <- makeWtdQtl(str.imp$occ.rate, 
+  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
                                       return.type='rank') 
-  str.imp$rate.qtl <- makeWtdQtl(str.imp$med.rate, 
+  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
                                   return.type='rank')
@@
 
-  qtlocc.pplot <- makePrefPlot(str.imp,
+  qtlocc.pplot <- abbPrefPlot(str.data.ic,
                                x.field='occ.qtl',
-                               y.field='str.act.pref',
-                               group.field='sub.mrkt',
+                               split.field='sub.mrkt',
                                smooth=TRUE,
@@
 
+  qtlocc.pplot
+
 ```
@@
 
-  rate.hm <- makeHeatMap(str.imp,
+  rate.hm <- abbHeatMap(str.data.ic,
                 x.field='occ.rate',
                 y.field='nightly.rate',
-                color.field='str.act',
-                bins=c(.05, 25),
+                pref.field='str.ext.pref',
                 svm=F, 
@@
                 fill.colors=c(abb.col[1], abb.col[5]))
-
-  rate.hm <- rate.hm +
-    xlab('\n Occupancy Rate') +
-    ylab('\n Nightly Rate') +
-    scale_x_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom')
+  rate.hm
 
@@
 
-  rate.hm.svm <- makeHeatMap(str.revs,
+  rate.hm.svm <- abbHeatMap(str.data.ic,
                             x.field='occ.rate',
                             y.field='nightly.rate',
-                         color.field='str.act',
-                         bins=c(.05, 25),
+                            pref.field='str.ext.pref',
                             svm=T, 
@@
                             fill.colors=c(abb.col[1], abb.col[5]))
-
-  rate.hm.svm <- rate.hm.svm +
-    xlab('\n Occupancy Rate') +
-    ylab('\n Nightly Rate') +
-    scale_x_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom')
-
-```
-
-Again, due to the non-uniformity of distribution of these two axis, we convert to quantiles and re-plot.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm <- makeHeatMap(str.revs,
-                         x.field='occ.qtl',
-                         y.field='rate.qtl',
-                         color.field='str.act',
-                         bins=c(5, 5),
-                         svm=F, 
-                         alpha.count=T,
-                         add.points=T,
-                         fill.colors=c(abb.col[1], abb.col[5]))
-
-  qtl.hm <- qtl.hm +
-    xlab('\n Quantile of Occupancy Rate') +
-    ylab('\n Quantile of Nightly Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    scale_y_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    theme(legend.position='bottom')
+  rate.hm.svm
 
@@
 
-  qtl.hm.svm <- makeHeatMap(str.revs,
+  qtl.hm <- abbHeatMap(str.data.ic,
                 x.field='occ.qtl',
                 y.field='rate.qtl',
-                        color.field='str.act',
-                        bins=c(5, 5),
+                pref.field='str.ext.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  qtl.hm
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm.svm <- abbHeatMap(str.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
                    svm=T, 
@@
                    add.points=T,
+                   quantile=T,
                    fill.colors=c(abb.col[1], abb.col[5]))
-
-  qtl.hm.svm <- qtl.hm.svm +
-    xlab('\n Quantile of Occupancy Rate') +
-    ylab('\n Quantile of Nightly Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    scale_y_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    theme(legend.position='bottom')
+  qtl.hm.svm
 
@@
 
-Finally, we calculate the areas of the heat maps and combine into a table.
-
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-  svm.rate <- makeSVM(str.revs,
+  svm.rate <- makeSVM(str.data.ic,
                      x.field='occ.rate',
                      y.field='nightly.rate',
-                     z.field='str.act',
+                     z.field='str.act.pref',
                      svm.type='C-svc',
@@
 
-  svm.qtl <- makeSVM(str.revs,
+  svm.qtl <- makeSVM(str.data.ic,
                       x.field='occ.qtl',
                       y.field='rate.qtl',
-                      z.field='str.act',
+                      z.field='str.act.pref',
                       svm.type='C-svc',
@@
   market.ratio <- data.frame(type=c('rate', 'qtl'),
-                             actual=rep(mean(str.revs$str.act), 2),
+                             actual=rep(mean(str.data.ic$str.act.pref), 2),
                              fitted=c(mean(svm.rate$orig$fitted),
@@
 ```
-
-### Submarkets
-
-We now take the analytical process just completed on the entire metro and apply it to various submarkets.  We use a custom function that combines all the processes above into a single command.
-
-#### Property Type
-
-We start by comparing apartments to houses.  First we set a new imputation model specification
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Set model specifications
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
-                            as.factor(ltr.month))
-  str.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))
-
-```
-
-We then recompute the market analysis for each property type.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Select data
-  str.apt <- which(str.revs$type == 'Apartment')
-  ltr.apt <- which(ltr.revs$type == 'Apartment')
-
-  # Estimate House Results  
-  house <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
-                              str.df=str.revs[-str.apt, ],
-                              ltr.mod.spec=ltr.mod.spec,
-                              str.mod.spec=str.mod.spec,
-                              clip.field='suburb',
-                              market.field='none',
-                              mrkt.col=sm.col,
-                              heat.col=c(abb.col[1], abb.col[5]))
-
-   apt <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.apt,],
-                             str.df=str.revs[str.apt, ],
-                             ltr.mod.spec=ltr.mod.spec,
-                             str.mod.spec=str.mod.spec,
-                             clip.field='suburb',
-                             market.field='sub.mrkt',
-                             mrkt.col=sm.col,
-                             heat.col=c(abb.col[1], abb.col[5]))
-
-```

### 2017-02-08 abbDataAnalysis_Script.Rmd
initial add of Logit Model

@@
 ```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ss60 <- which(str.data.ic$cancel.policy == 'Super Strict 60 Days')
+  str.data.ic$cancel.policy[ss60] <- 'Strict'
+  cpmiss <- which(str.data.ic$cancel.policy == '')
+  str.data.ic <- str.data.ic[-cpmiss, ]
+
+  ps <- which(str.data.ic$host.type == 'Profit Seeker')
+  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
+  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
+  un <- which(str.data.ic$host.type == 'Unknown')
+
+  mod.str <- glm(str.pot.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[un,])
+
+```

### 2017-02-08 abbDataPrep_Script.Rmd
adding host policy data clean

@@
 
+#### Host Policies
+
+Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.
+We also remove the few observations with missing host policy data
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
+  str.data$cancel.policy[ss60] <- 'Strict'
+  cpmiss <- which(str.data.ic$cancel.policy == '')
+  str.data <- str.data[-cpmiss, ]
+
+```
+
 ## Write out data

### 2017-02-08 abbDataPrep_Script.Rmd
Finalize Cancel Policy clean

@@
 
+ ## ID those with missing cancel policies and remove
+
+  cpmiss <- which(str.data$cancel.policy == '')
+  str.data <- str.data[-cpmiss, ]
+
+ ## ID those with Super Strict and change to Strict
+
   ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
   str.data$cancel.policy[ss60] <- 'Strict'
-  cpmiss <- which(str.data.ic$cancel.policy == '')
-  str.data <- str.data[-cpmiss, ]
 

### 2017-02-08 abbDataAnalysis_Script.Rmd
removal of cancel policy clean from analysis
added costs and addt'l models

@@
 
+State gives energy costs at 330 (apt) to 520 (house).  For 2 person in apt that works out to 5 per person per day.  For house of 4 that works out to about 4 per person per day.
+
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-  str.data$str.act.revenue <- str.data$bookings * str.data$med.rate
+  str.data$cpppd <- 4.5
+  str.data$avg.guests <- str.data$bedrooms * 1.5
+
+  str.data$str.act.revenue <- ((str.data$bookings * str.data$med.rate) - 
+                                 (str.data$bookings * str.data$avg.guests * str.data$cpppd))
 
@@
 
-  str.data$str.ext.revenue <- (str.data$bookings * str.data$extr.par *
-                                  str.data$med.rate)
-
+  str.data$str.ext.revenue <- ((str.data$bookings * str.data$extr.par *
+                                  str.data$med.rate) - 
+                                 (str.data$bookings * str.data$avg.guests * 
+                                    str.data$cpppd * str.data$extr.par))
+  # 
   str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)
 
-  str.data$pot.occ.rate <- (str.data$bookings * str.data$extr.par) / (366 - (366 * str.data$block.rate))
+  str.data$pot.occ.rate <- ((str.data$bookings * str.data$extr.par) / 
+    (366 - (366 * str.data$block.rate)))
 
-  str.data$str.pot.revenue <- (str.data$pot.occ.rate * 366 * str.data$med.rate)
+  str.data$str.pot.revenue <- ((str.data$pot.occ.rate * 366 * str.data$med.rate) - 
+                                 (str.data$pot.occ.rate * 366  * str.data$avg.guests *  
+                                    str.data$cpppd))
 
@@
 
-  ss60 <- which(str.data.ic$cancel.policy == 'Super Strict 60 Days')
-  str.data.ic$cancel.policy[ss60] <- 'Strict'
-  cpmiss <- which(str.data.ic$cancel.policy == '')
-  str.data.ic <- str.data.ic[-cpmiss, ]
+  mod.ext.str <- glm(str.ext.pref~type+as.factor(bedbath),
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.ext.loc <- glm(str.ext.pref~type+as.factor(bedbath)+
+                                  sub.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
+                                  sub.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
+                        sub.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      family=binomial(link='logit'),
+                      data=str.data.ic)
+  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
+                        sub.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      family=binomial(link='logit'),
+                      data=str.data.ic)
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.ext.str <- lm(str.ext.prem~type+as.factor(bedbath),
+                    data=str.data.ic)
+  mod.pot.str <- lm(str.pot.prem~type+as.factor(bedbath),
+                    data=str.data.ic)
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.ext.host <- lm(str.ext.prem~type+as.factor(bedbath)+
+                        sub.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict') + suburb,
+                      data=str.data.ic)
+  mod.pot.host <- lm(str.pot.prem~type+as.factor(bedbath)+
+                        sub.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      data=str.data.ic)
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 

### 2017-02-13 abbReturns_Working.R
removal of unnecessary files

@@ -1,175 +1,0 @@
-
-### Preliminary Commands -----------------------------------------------------------------
-
- ## Set global options
-
-  options(xtable.comment = FALSE)
-
- ## Load libraries
-
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(kernlab)
-  library(ggplot2)
-  library(geosphere)
-  library(ggmap)
-  library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-  library(ROCR)
-
- ## Set path location
-
-  # Get computer names
-  comp.name <- Sys.info()['nodename']
-
-  # Assign path based on computer name
-  if(comp.name == '7020D-121777-W' | 
-      comp.name == 'DESKTOP-1D7JO4J'){
-  
-    data.path <- 'c:/dropbox/research/airBNB/data/'
-  
-  } else {
-  
-    data.path <- 'gideon path'
-  
-  }
-
- ## Load working workspace   
-  
-  load(paste0(data.path, '/analyzed/abb_working.RData'))
-  load(paste0(data.path, '/analyzed/abb_objs.RData'))
-  
- ## Load sources (custom function files)
-
-  source("c:/code/dataviztools/ggplottools.R")
-  source("c:/code/datamgmttools/dataMungetools.R")
-  source("c:/code/research/AirBNBMelbourne/analysis_Functions.R")
-  source("c:/code/research/AirBNBMelbourne/dataPrep_Functions.R")
-  source("c:/code/spatialtools/point2surface_Tools.R")
-  source("c:/code/spatialtools/spatiallogitmodels.R")
-  
-  sm.col <- abb.col[c(2, 1, 3, 5, 6)]
-  
-### Working analysis ---------------------------------------------------------------------  
-  
-  
-  
-  
-  
-calcBookStr <- function(id, 
-                        book.data){
-    
-  id.data <- book.data[book.data$property.id == id, 'status']
-    
-  if(length(id.data) > 1){
-    
-    # Divide by status and collapse
-    status.string <- id.data[1]
-    
-    for(ss in 2:length(id.data)){
-      
-      if(id.data[ss] == id.data[[ss - 1]]){
-        status.string <- paste0(status.string, id.data[[ss]])
-      } else {
[…]

### 2017-02-13 apmDataPrep_Script.R

@@ -1,113 +1,0 @@
-##########################################################################################
-#                                                                                        #  
-#   Data Preprocessing for the Long-Term Rental data of the ABB project                  #
-#                                                                                        #  
-##########################################################################################
-
- ## Load Libraries
-
-  library(stringr)
-  
- ## Load custom functions  
-
-  source('c:/code/research/airbnbmelbourne/abb_Functions.R')
-  
- ## Load Data  
-  
-  # Get computer names
-  comp.name <- Sys.info()['nodename']
-  
-  # Assign path based on computer name
-  if(comp.name == '7020D-121777-W' | 
-     comp.name == 'DESKTOP-1D7JO4J'){
-    
-    data.path <- 'c:/dropbox/research/airBNB/data/'
-    
-  } else {
-    
-    data.path <- 'gideon path'
-    
-  }
-  
-  raw.path <- paste0(data.path, '/raw/')
-  rent16 <- read.csv(paste0(raw.path, 'rentData.csv'), header=T)
-
- ## Remove observations without sufficient keys
-  
-  r16 <- rent16[!is.na(rent16$EventID), ]
-  r16 <- r16[!is.na(r16$AddressID), ]
-  r16 <- r16[!is.na(r16$ActivityID), ]
-  
- ## Create Unique Key
-  
-  r16$id.key <- paste0(as.numeric(as.factor(r16$ActivityID)), '..',
-                       as.numeric(as.factor(r16$AddressID)))
-  r16$id.key <- as.numeric(as.factor(r16$id.key))
-  
- ## Fix Dates  
-  
-  r16$lastdate <- apmFixDates(r16$LastAdvertisedEventDate)
-  r16$eventdate <- apmFixDates(r16$EventDate)
-  r16$eventyear <- as.numeric(substr(r16$eventdate, 1, 4))
-  
- ## Remove those not occuring in 2015 or later
-  
-  r16 <- r16[r16$eventyear >= 2014, ]
-  
- ## Add an identifier that signifies last record in a set of advertisements (of record)  
-    
-  r16 <- r16[order(r16$eventdate, decreasing=T), ]
-  r16 <- r16[order(r16$id.key), ]
-  r16$AID <- paste0(r16$id.key, '..', r16$lastdate)
-  r16$of.record <- ifelse(duplicated(r16$AID), 0 ,1)
-  
- ## Split into property data and listing data
-  
-  prop.data <- r16[r16$of.record == 1,]
[…]

### 2017-02-13 abb_Writeup.Rmd
re-org of names

--- 2017-01-14 abbReturns_Writeup.Rmd
@@
 ---
-title: "Should I Airbnb My Property?"
+title: "Should I Airbnb My Property?: \n Full Report"
 author: "Andy Krause and Gideon Aschwanden"
-date: "January 9, 2017"
+date: "January 14, 2017"
 output:
@@
 Melbourne has a thriving Airbnb market with over 20,000 total properties listed on the portal.
-We adopt a scenario-based approach in which we compare potential annual revenues for properties under both a short-term rental (STR) and a long-term rental (LTR) situation.
-Additionally, we break the results down by property types (apartment vs house), product type (ex.
+We adopt a scenario-based approach that compares potential annual revenues for properties under both a short-term rental (STR) and a long-term rental (LTR) situation.
+Additionally, we break the results down by property types (apartment vs house), product type (e.g.
 1 bed, 1 bath) and by location (submarket).
 Our results shows that the feasibility of a greater return through a short term rental is dependent on property type, product and location.
-In answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
+In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
 
@@
 Existing research into short-term rental markets is sparse.
-However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields outside of real estate as evidenced by a growth in recent publications and on-going working papers.
+However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
 
@@
 We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
-Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.
-However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
+Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.]  However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
 
@@
 What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
-It is likely that different submarkets operate differently, we will explore this hypothesis after first analyzing the full metropolitan region.
+It is likely that different submarkets operate differently, a hypothesis investigated after the full metropolitan region.
 
@@
 
+### Market Summary
+
 Finally, we summarize the entire market by looking at three metrics:
@@
 The raw probability data shows that over 33% of apartments are more profitable in short term leasing as opposed to just 22% of houses.
-The two figures show the quantile preference plots both in the raw and with the SVM categorization.
+Figures 18 and 19 show the quantile preference plots both in the raw and with the SVM categorization.
 As is evident from these plots, the likely of short-term rental being more profitable is much greater in the apartment market than in the house market.
@@
 Interestingly, the rural area has a higher probably than all other but the core.
-This is likely explained by the fact that there are few rural properties and those that are show some clustering near rural tourists activities like the Yarra Valley wine region (Figure 8).
-
-In the core and the city, apartments offer a higher probability than homes, the reverse in true in the suburban and rural areas.
-In the lower density areas it appears that tourists may prefer larger and more spacious dwellings and are willing to pay a premium for them, compared to long-term renters who may experience long commutes from these fringe locations.
-
-Looking at the 'fitted' and 'svm area' figures we see a trend that these svm figures are higher than the actual observed for the core apartment and lower for nearly all of the rest of the categories.
-This findings shows that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
-In other words, there is well defined combination or situation in which these properties can be more profitable than in a long-term lease.
-The reverse is true of the city core apartments.
+This is likely explained by the fact that there are few rural properties and many of these are clustered near rural tourists activities like the Yarra Valley wine region which see a high demand for lodging (Figure 8).
+
+In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
+In the lower density areas it appears that tourists may prefer larger and more spacious dwellings compared to long-term renters who may experience long commutes from these fringe locations.
+
+Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
+This finding suggests that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
+In other words, there is well defined combination or situation in which these properties can be more profitable short-term than in a long-term lease.
+The opposite is true of the city core apartments.
 Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
@@
 Strict policies do help maintain revenues, but may also scare off some potential guests.
-Strict cancellation may be a luxury for the best and highly desired properties on the market and, within out model, may be acting as a proxy for some unobserved measure of quality or demand.
+Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.
 
@@
 
-Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+<!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
 This work attempts to fill this void.
+-->
 
@@
 Of these, only 4,400 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+Overall, the Airbnb market is very small relative to the long-term market.
 We caution future researchers and policy analysts to look deeply at initial estimates of Airbnb counts as many of the listings on the market are either room shares and/or not active.
@@
 Apartments are much more likely than houses to be more profitable as a short term rental.
-Core city properties are more likely than more outlying properties to prefer a short-term strategy, as a larger properties versus smaller ones.
+Core city properties are more likely than other properties to prefer a short-term strategy, as are larger properties versus smaller ones.
 For instance, 45\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market.
@@
 
-In the logistic regression models than we estimate (Table 7), we see that most of the finding from the univariate and bivariate analyses done early are validated.
+The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
 Large apartments in the central city are the best bet for generating greater revenues through short term leasing.
@@
 This may be a limitation of our study and could prove to be an avenue of future research.
+
+Beyond airBNB.com other short-term platforms exist (e.g.
+www.homeaway.com).
+This project doesn't take into account that individual properties may be advertised and rented out through different platforms.
+These are additional revenue streams that are not take into account and might increase the occupancy and revenue for short-term rentals.
 
@@
 
+\pagebreak
+
 ## References

### 2017-02-13 abb_imputation.Rmd
re-org of names

---
title: "R Notebook"
output: html_notebook
---

### Impute missing daily observations

Unfortunately, the data from AirDNA is missing observations.  According to conversations with AirDNA staff only certain Melbourne area properties were monitored for daily status conditions starting on October 1, 2014.  Over the next year, all properties were slowly brought on line.  From October 1, 2015 to October 1, 2016 observations are believed to be complete. To fill in the missing observations, we will impute the status of the missing dates based on the available data. Some properties will have a month or less of imputation, some a full year or so.

&nbsp;

#### Filter 'Other' Properties

AirBNB units are classified into a property type. There are 19 different property types within the Melbourne data.  The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type]. For the sake of this analysis, we will collapse these twenty types into three types:

1. **House**:  Includes properties labeled 'House' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.

The analyses that follow removes the **Other** category (3% of total) and only considers the **House** and **Apartment** unit types

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

prop.data$type <- 'Other'
prop.data$type[prop.data$property.type == 'Apartment' | 
                  prop.data$property.type == 'Condominium' ] <- 'Apartment'
prop.data$type[prop.data$property.type == 'House' | 
                  prop.data$property.type == 'Townhouse' ] <- 'House'

#prop.data <- prop.data[prop.data$type != 'Other', ]

```

&nbsp;

#### Prepping for Imputation

We begin the imputation process by creating a new variable indicating if the property itself was created before the data collection process began.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  prop.data$created.class <- ifelse(prop.data$created.date < '2014-10-01', 
                                  'pre', 'post')

```

Most properties (`r round(100*table(prop.data$created.class)[1]/nrow(prop.data),2)`%) were created (first offered on www.airbnb.com) after October 1, 2014.  We then add a field indicating whether or not the property needs to be imputed.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

prop.data$impute <- 'no'
prop.data$impute[prop.data$created.class == 'pre' & 
                   prop.data$min.date > '2014-10-01'] <- 'pre'
prop.data$impute[prop.data$created.class == 'post' & 
                   prop.data$min.date > prop.data$created.date] <- 'post'

```

About (`r round(100*(1-(table(prop.data$impute)[1]/nrow(prop.data))), 0)`%) of all properties need some measure of imputation.

&nbsp;

#### Imputation Process

In imputing the properties will use a multiple step process that considers the property's performance during the observed periods, the overall market during the non-observed periods and the type of the property itself.  More specifically, we follow the steps below:

1. Split all properties into *j* number of AirBNB submarkets

For each *j* submarket:

2. Calculate the average daily occupancy rate for each *j* submarket

For each individual property (*i*) in submarket *j*:

3. Calculate which days are observed and which are missing
4. Calculate the % of reserved, available and blocked days for the observed dates
5. Create an adjustment factor that notes the ratio of the submarket *j* reserved rate during the property's observed dates to those of the property's un-observed dates
6. Using the adjustment in #5, we then determine what percentage of the un-observed days should be alloted to each status type (reserved, available and blocked).  Blocked are based on the % of blocked days in the observed period.  Reserved are based on the observed occupancy rate during the observed dates multiplied by the overall expected occupancy rate during the unobserved days for the entire submarket as compared with the observed days. The available days are the remainder. This process creates a count of each status equal to the number of unobserved days.
7. The three status types are then assigned to the unobserved days.  First, blocked days are randomly assigned. Then the reserved days are randomly assigned to the remaining non-blocked days in a weighted fashion where the overall submarket's occupancy rate on a given day influences the probability of the impute status being reserved. The available days are the balance of the unobserved days. Note that we do not attempt to simulate actual bookings which are often multiple days.  The intent of the imputation is to correct capture the overall market and submarket trends, not to accurately re-create actual booking histories of any of the unobserved periods for this sample of properties. 
8. Prices for reserved rooms are taken to be the average nightly rate of that particular property over the observed period.

We begin this process by creating submarkets.  For each of the properties we determine the submarket to be a combination of the structure type (House vs Apartment) and the listing type (Entire vs Private Room vs Shared Room).  This creates six submarkets. These are assigned to the property and the daily data.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  prop.data$lp.type <- paste0(substr(prop.data$type, 1, 1), '.', 
                               substr(prop.data$listing.type, 1, 1))

  daily.data$lp.type <- prop.data$lp.type[match(daily.data$property.id,
                                                  prop.data$property.id)]

```

We then split the property and daily data into submarkets.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 o.prop <- prop.data[prop.data$type == 'Other', ]
 o.daily <- daily.data[daily.data$property.id %in% o.prop$property.id, ]

 prop.data <- prop.data[prop.data$type != 'Other', ]
 daily.data <- daily.data[daily.data$property.id %in% prop.data$property.id, ]

 subm.prop <- split(prop.data, prop.data$lp.type)
 subm.daily <- split(daily.data, daily.data$lp.type)

```

And then we calculate daily occupancy rates for each submarket.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

  subm.rates <- lapply(subm.daily, abbCalcDateRates)

```

We take these three sets of submarket data (properties, daily and occupancy rates) and use a custom function (**abbImputeDaily()**) to impute the missing days. The results of each of these submarkets are then collapse into a single data.frame.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Create blank capture list

  subm.list <- list()

 ## Loop through submarkets

  for(j in 1:length(subm.prop)){
    subm.list[[j]] <- abbImputeDaily(prop.df=subm.prop[[j]],
                                     daily.df=subm.daily[[j]],
                                     rates.df=subm.rates[[j]])
  }

 ## Collapse into a data.frame

  imp.daily <- rbind.fill(subm.list)

```

After imputing the missing dates we join them to the observed daily data.  The imputed data can be recognized by the label 'imputed' in the booked.date field.

```{r message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, cache=TRUE}

 ## Combine all together

  all.daily <- rbind(daily.data, imp.daily, o.daily)

 ##

  prop.data <- rbind(prop.data, o.prop)

```

### 2017-02-13 abbDataAnalysis_Script.Rmd
updating models

@@
   mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
-                        sub.mrkt+
+                        sub.mrkt+as.factor(host.type)+
                         I(max.guests/bedrooms)+min.stay+
@@
   mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
-                        sub.mrkt+
+                        sub.mrkt+as.factor(host.type)+
                         I(max.guests/bedrooms)+min.stay+
@@
 
-  mod.ext.host <- lm(str.ext.prem~type+as.factor(bedbath)+
+  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
                         sub.mrkt+
                         I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict') + suburb,
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                       data=str.data.ic)
-  mod.pot.host <- lm(str.pot.prem~type+as.factor(bedbath)+
+  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                         sub.mrkt+
@@
 
-  mod.str <- glm(str.pot.pref~type+as.factor(bedbath)+
+  mod.ext.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[ps,])
+
+  mod.ext.os <- glm(str.pot.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[os,])
+
+  mod.ext.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[mu,])
+
+  mod.ext.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                     sub.mrkt+
@@
 ```
+
+### Moving Window Logit
+
+To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.
+Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties.
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
+                              proj4string=CRS("+init=epsg:4283"),
+                              delete_null_obj=TRUE)
+
+ ssubs <- table(str.data.ic$suburb)
+ s.subs <- subs[subs$id %in% names(ssubs),]
+ s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),]
+ sssubs <- fortify(s.suburbs)
+
+```
+
+Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Min, Max and Range
+ xmin <- min(s.subs$long)
+ xmax <- max(s.subs$long)
+ ymin <- min(s.subs$lat)
+ ymax <- max(s.subs$lat)
+ xrange <- xmax-xmin
+ yrange <- ymax-ymin
+
+ # Set Scale
+ scale <- mean(xrange, yrange)/100
+
+ # Create estimation points
+ est.data <- str.data.ic
+ est.points <- createGridPoints(s.suburbs, scale, T)
+
+```
+
+We then specify the logistic regression model and set the moving window bandwidth.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Set model specification
+
+ pot.mod.spec <- str.pot.pref ~ type + as.factor(bedbath) + 
+   I(max.guests / bedrooms) + min.stay + 
+   I(cancel.policy == 'Flexible') + 
+   I(cancel.policy == 'Strict')
+
+ ext.mod.spec <- str.ext.pref ~ type + as.factor(bedbath) + 
+   I(max.guests / bedrooms) + min.stay + 
+   I(cancel.policy == 'Flexible') + 
+   I(cancel.policy == 'Strict')
+
+ ## Set bandwidth
+
+ k <- 400
+
+```
+
+The results are estimated with the custom MWL function
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ pot.results.all <- mwl(est.data, 
+                        est.points, 
+                        pot.mod.spec, 
+                        k)
+
+ ext.results.all <- mwl(est.data, 
+                        est.points, 
+                        ext.mod.spec, 
+                        k)
+
+  pot.results.ps <- mwl(est.data[ps, ], 
+                        est.points, 
+                        pot.mod.spec, 
+                        k)
+   pot.results.os <- mwl(est.data[os, ], 
+                        est.points, 
+                        pot.mod.spec, 
+                        k)
+
+   pot.results.mu <- mwl(est.data[mu, ], 
+                        est.points, 
+                        pot.mod.spec, 
+                        k)
+
+   pot.results.un <- mwl(est.data[un, ], 
+                        est.points, 
+                        pot.mod.spec, 
+                        k)
+
+   ext.results.ps <- mwl(est.data[ps, ], 
+                        est.points, 
+                        ext.mod.spec, 
+                        k)
+   ext.results.os <- mwl(est.data[os, ], 
+                        est.points, 
+                        ext.mod.spec, 
+                        k)
+
+   ext.results.mu <- mwl(est.data[mu, ], 
+                        est.points, 
+                        ext.mod.spec, 
+                        k)
+
+   ext.results.un <- mwl(est.data[un, ], 
+                        est.points, 
+                        ext.mod.spec, 
+                        k)
+
+```
+
+Coefficents are extracted and put into a data.frame
+
+MAKE A FUNCTION BELOW HERE
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+extrMWLCoef <- function(mwl.results,
+                        est.points,
+                        names.coef){
+
+ coef.names <- rownames(mwl.results[[1]])
+
+ # Create a list to capture
+ coef.list <- list()
+
+ # Create a data.frame to capture
+ coef.df <- data.frame(lat=est.points@coords[,2],
+                       long=est.points@coords[,1])
+
+ # Loop through and extract coefficients
+ for(cn in 1:length(coef.names)){
+   coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn])
+   coef.df[ ,ncol(coef.df) + 1] <- unlist(coef.list[[cn]])
+ }
+
+ # Add plottable names
+ colnames(coef.df)[3:13] <- names.coef
+
+ return(coef.df)
+
+}
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+x.names <- c('intercept', 'house', 'bb11', 'bb21', 'bb31',
+                              'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict')
+
+pra.coef <- extrMWLCoef(pot.results.all,
+                        est.points,
+                        x.names)
+era.coef <- extrMWLCoef(ext.results.all,
+                        est.points,
+                        x.names)
+prp.coef <- extrMWLCoef(pot.results.ps,
+                        est.points,
+                        x.names)
+pro.coef <- extrMWLCoef(pot.results.os,
+                        est.points,
+                        x.names)
+prm.coef <- extrMWLCoef(pot.results.mu,
+                        est.points,
+                        x.names)
+pru.coef <- extrMWLCoef(pot.results.un,
+                        est.points,
+                        x.names)
+erp.coef <- extrMWLCoef(ext.results.ps,
+                        est.points,
+                        x.names)
+ero.coef <- extrMWLCoef(ext.results.os,
+                        est.points,
+                        x.names)
+erm.coef <- extrMWLCoef(ext.results.mu,
+                        est.points,
+                        x.names)
+eru.coef <- extrMWLCoef(ext.results.un,
+                        est.points,
+                        x.names)
+```
+
+Finally, these coefficients are converted to a surface.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+makeMWLSurfs <- function(mwl.coefs,
+                         est.points){
+
+  # Make capture list
+  surf.list <- list()
+
+  mwl.coefs <- mwl.coefs[ ,!names(mwl.coefs) %in% c('lat', 'long')]
+
+ # Create surfaces
+  for(sl in 1:ncol(mwl.coefs)){
+
+   # If NAs
+   to.cut <- which(is.na(mwl.coefs[,sl]))
+   if(length(to.cut) > 0){
+     surf.points <- est.points[-to.cut,]
+     surf.value <- mwl.coefs[-to.cut, sl]
+   } else {
+     surf.points <- est.points
+     surf.value <- mwl.coefs[ , sl]
+   }
+
+   # Surface estimation
+   surf.list[[sl]] <- point2Surface(surf.points, 
+                                    surf.value,
+                                    .01, 
+                                    1.5)
+  }
+
+  names(surf.list) <- names(mwl.coefs)
+
+return(surf.list)    
+}
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+pra.surfs <- makeMWLSurfs(pra.coef,
+                          est.points)
+era.surfs <- makeMWLSurfs(era.coef,
+                          est.points)
+
+prp.surfs <- makeMWLSurfs(prp.coef,
+                          est.points)
+pro.surfs <- makeMWLSurfs(pro.coef,
+                          est.points)
+prm.surfs <- makeMWLSurfs(prm.coef,
+                          est.points)
+pru.surfs <- makeMWLSurfs(pru.coef,
+                          est.points)
+
+erp.surfs <- makeMWLSurfs(erp.coef,
+                          est.points)
+ero.surfs <- makeMWLSurfs(ero.coef,
+                          est.points)
+erm.surfs <- makeMWLSurfs(erm.coef,
+                          est.points)
+eru.surfs <- makeMWLSurfs(eru.coef,
+                          est.points)
+
+```

### 2017-02-16 abb_Writeup.Rmd
review of Intro/lit review

@@
 ---
-title: "Should I Airbnb My Property?: \n Full Report"
+title: "Should I Airbnb My Property?"
 author: "Andy Krause and Gideon Aschwanden"
+header-includes:
+    - \usepackage{setspace}\doublespacing
 date: "January 14, 2017"
@@
   html_document: default
-geometry: margin=3.4cm
+geometry: margin=3.3cm
 bibliography: abb.bib
@@
   source(paste0(code.path, "datamgmttools/dataMungetools.R"))
-  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
-  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
+  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
 
@@
 
-<!-- # ```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE} -->
-<!-- #  -->
-<!-- #   load(paste0(data.path, '/analyzed/abb_working.RData')) -->
-<!-- #  -->
-<!-- # ``` -->
+```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}
+
+   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
+
+```
 
@@
 Should they though?
-And which types of properties and in which locations would short-term leasing produce greater revenue than a traditional long-term rental (LTR), if any?
-
-To address these questions and provide some guidance to potential and current investors and owners, we use long-term rental data and nightly Airbnb listing information from the Melbourne (Australia) metropolitan area.
-Melbourne has a thriving Airbnb market with over 20,000 total properties listed on the portal.
+Or rather, is it more profitable to do so when compared to a more traditional long term rental (LTR)?
+Are certain types of properties and certain locations, if any, more likely to show a preference for (in terms of profitability) short term leasing strategy over long-term.
+
+To address these questions and to provide some guidance to potential and current investors and owners, we examine the residential rental market, both short- and long-term in Melbourne, Australia.
+Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
 We adopt a scenario-based approach that compares potential annual revenues for properties under both a short-term rental (STR) and a long-term rental (LTR) situation.
-Additionally, we break the results down by property types (apartment vs house), product type (e.g.
-1 bed, 1 bath) and by location (submarket).
-Our results shows that the feasibility of a greater return through a short term rental is dependent on property type, product and location.
+We break the results down by property types (apartments vs houses), product type (e.g.
+1 bed/1 bath) and by location (geographic submarket).
+Our results shows that the feasibility of a greater return through a short term rental -- what we have termed ``Short Term Preference'' -- is dependent on property type, product and location.
 In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
@@
 However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
+Within the extant work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resorts.
+This focus resulted from the fact that the market itself operated almost wholly within this sphere.
+The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
 
 Much of the existing work focuses on price or rent formation in second home markets.
-Specifically, the impacts of amenties such as water access [@nelson2010valuing], water quality [@gibbs2002hedonic; @clapper2014water] and proximity to ski facilities  [@soguel2008impact; @nelson2010valuing] and theme parks [@tsai2015impact] are shown to positively impact sales prices in tourism-dominated areas.
-@benjamin2001value note that leasing policies, in this case smoking prohibitions, can also influence the weekly rental rates for vacation homes.
-@nilsson2015influence makes a key distinction, finding that rural vacation home markets value amenties whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
+Specifically, the impacts of amenities such as water access [@nelson2010valuing], water quality [@gibbs2002hedonic; @clapper2014water], proximity to ski facilities  [@soguel2008impact; @nelson2010valuing] and theme parks [@tsai2015impact] are shown to positively impact sales prices in tourism-dominated areas.
+Host policies can also matter as @benjamin2001value find that smoking prohibitions influence the weekly rental rates for vacation homes.
 
@@
 Though very broad analyses, all suggest that Airbnb has had a positive impact on local home prices and/or a negative impact on affordability.
-Other work examines the impact of short term rentals on the hotel market, with @gutierrez2016airbnb finding that Airbnb and hotels have similar location patterns in Barcelona and @zervas2014rise showing an inverse relationship between Airbnb listings and hotel revenues.
-
-A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short term rentals).
+Other research examines the impact of short-term rentals on the hotel market, with @gutierrez2016airbnb finding that Airbnb and hotels have similar location patterns in Barcelona and @zervas2014rise showing an inverse relationship between Airbnb listings and hotel revenues.
+
+A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short-term rentals).
 Or, in other words, the factors that influence prices and rents in the two are not equivalent.
@@
 Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.
+In examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction, finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
 
@@
 Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
-We hypothesize that this same thinking can be extended to the difference between short-term occupants (tourists) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term tenure.
-
-## Method
-
-We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
-More specifically, we examine the following case:
-
-* An investor purchases a property in Melbourne on Sept 1, 2015.
-* They are looking to maximize the revenue over the 12-month period from September 1, 2015 to August 31, 2016.
-* The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental.
-* Only direct monetary revenues and costs are considered, others such as liquidity and inconvience are not considered.
-
-We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
+We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term tenure.
+
+<!-- ## Method -->
+
+<!-- We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+More specifically, we examine the following case: -->
+
+<!-- * An investor purchases a property in Melbourne on Sept 1, 2015. -->
+<!-- * They are looking to maximize the revenue over the 12-month period from September 1, 2015 to August 31, 2016. -->
+<!-- * The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental. -->
+<!-- * Only direct monetary revenues and costs are considered, others such as liquidity and inconvience are not considered.   -->
+
+<!-- We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
 Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.]  However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
-
-One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
+-->
+
+<!-- One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
 As future market trends are unknown at the time of purchase and the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
 Both long- term rents and short-term rates and occupancy structures will be baesd on the market conditions as of this date.
-
-We do not directly observe properties that are utilized in both a short and long term leasing strategy.
+-->
+
+<!-- We do not directly observe properties that are utilized in both a short and long term leasing strategy.
 Therefore, comparisons are done based on estimated or imputed revenues.
@@
 A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
-
-### Comparison
-
-In this above scenario we compare the 12-month revenues from the a long-term rental with those of a short-term rental.
+-->
+
+<!-- ### Comparison -->
+
+<!-- In this above scenario we compare the 12-month revenues from the a long-term rental with those of a short-term rental.
 We define returns here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
-
-\begin{equation}
-Rev_{LT} = RevG_{LT} - C_{LT}
-\end{equation}
-
-\begin{equation}
-Rev_{ST} = RevG_{ST} - C_{ST}
-\end{equation}
-
-Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the costs associated with long-term rental. The gross long-term revenue is expressed by:
-
-\begin{equation}
-RevG_{LT} = Rent_{M} * (12 - C_{S})
-\end{equation}
-
-where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
-
-The short-term revenue is expresse by:
-
-\begin{equation}
-RevG_{ST} = Rate_{N} * O_{Total}
-\end{equation}
-
-where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period.
-
-We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
+-->
+
+<!-- \begin{equation} -->
+<!-- Rev_{LT} = RevG_{LT} - C_{LT} -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+<!-- Rev_{ST} = RevG_{ST} - C_{ST} -->
+<!-- \end{equation} -->
+
+<!-- Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the costs associated with long-term rental.
+The gross long-term revenue is expressed by:  -->
+
+<!-- \begin{equation} -->
+<!-- RevG_{LT} = Rent_{M} * (12 - C_{S}) -->
+<!-- \end{equation} -->
+
+<!-- where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant. -->
+
+<!-- The short-term revenue is expresse by: -->
+
+<!-- \begin{equation} -->
+<!-- RevG_{ST} = Rate_{N} * O_{Total} -->
+<!-- \end{equation} -->
+
+<!-- where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. -->
+
+<!-- We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
 Broadly speaking, these fall into three categories for long-term rental and four categories for short-term properties.
-Long-term costs are summarized as:
-
-\begin{equation}
-C_{LT} = T + M + F
-\end{equation}
-
-where $T$ are tax related expenses, $M$ are general maintenance expenses and $F$ are finaning costs.
+Long-term costs are summarized as: -->
+
+<!-- \begin{equation} -->
+<!-- C_{LT} = T + M + F -->
+<!-- \end{equation} -->
+
+<!-- where $T$ are tax related expenses, $M$ are general maintenance expenses and $F$ are finaning costs.
 Short-term properies experience the same three costs ($T$, $M$ and $F$) plus additional janitorial costs between each of the short-term occupants.
-
-\begin{equation}
-C_{ST} = T + M + F + J
-\end{equation}
-
-As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
+-->
+
+<!-- \begin{equation} -->
+<!-- C_{ST} = T + M + F + J -->
+<!-- \end{equation} -->
+
+<!-- As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
 General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
@@
 As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
-
-Finally, we have janitorial costs $J$.
+-->
+
+<!-- Finally, we have janitorial costs $J$.
 These cover the costs to 'turn-over' the property between occupants.
@@
 As a result of janitorial fees being a separate line item and directly paid by the occupants can also be ignored in the comparative analysis below as they are direct.
-
-Given that the costs cancel out between the two options, we will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
-
-\begin{equation}
-RevG_{ST} > RevG_{LT} 
-\end{equation}
-
-More specifically, if:
-
-\begin{equation}
-Rate_{N} * O_{Total} > Rent_{M} * (12 - C_{S})
-\end{equation}
-
-## Data
-
-Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
+-->
+
+<!-- Given that the costs cancel out between the two options, we will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds: -->
+
+<!-- \begin{equation} -->
+<!-- RevG_{ST} > RevG_{LT}  -->
+<!-- \end{equation} -->
+
+<!-- More specifically, if: -->
+
+<!-- \begin{equation} -->
+<!-- Rate_{N} * O_{Total} > Rent_{M} * (12 - C_{S}) -->
+<!-- \end{equation} -->
+
+<!-- ## Data -->
+
+<!-- Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
 Short-term rental market observations are from the Airbnb online portal.
@@
 These data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
-
-The Airbnb data cover the Melbourne metropolitan region from October 1st, 2014 to August 30th, 2016.
+-->
+
+<!-- The Airbnb data cover the Melbourne metropolitan region from October 1st, 2014 to August 30th, 2016.
 There are missing nightly observations during the time period before September 1, 2015.
@@
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
-
-The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
+-->
+
+<!-- The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 In raw form, this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
@@
 The long-term lease data covers the period from January 2014 to December 2015.
-
-Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
+-->
+
+<!-- Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
 Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
@@
 However, the number of properties that rented long term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
-
-```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
-  exch.rate <- 1.32
-
-```
-
-### Preparation
-
-In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
+-->
+
+<!-- ```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'} -->
+
+<!--   exch.rate <- 1.32 -->
+
+<!-- ``` -->
+
+<!-- ### Preparation -->
+
+<!-- In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
 Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions.
 Additionally, as our data are from two different sources, a number of fields also require standardization so that comparisons between the two leasing strategy options  -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
-
-We begin by filtering observations by time.
+-->
+
+<!-- We begin by filtering observations by time.
 Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an AirBNB-type, short-term rental approach to generating income.
@@
 In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
-
-Next, we filter the data based on property types.
+-->
+
+<!-- Next, we filter the data based on property types.
 AirBNB units are classified into 19 different property types.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types:
-
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
-3.
+For the sake of this analysis, we will collapse these twenty types into three types: -->
+
+<!-- 1. **House**:  Includes properties labeled 'House' or 'Townhouse' -->
+<!-- 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium' -->
+<!-- 3.
 **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
-
-Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
-
-1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
-
-Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
+-->
+
+<!-- Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories: -->
+
+<!-- 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse' -->
+<!-- 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio' -->
+<!-- 3. **Other**: Includes properties labeled as 'Semi' and 'Villa' -->
+
+<!-- Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
 This is most apparent when talking about apartment dwellings.
@@
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
-
-The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
+-->
+
+<!-- The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
 Additionally, a large proportion of the **Others** in the short-term data are Bed & Breakfast units, a use which doesn't fit with our research question.
 As a result, we remove the 'Others' from both the short- and the long-term rental data.
-
-```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
-  abb.data1 <- before.PT$abb.data
-  ltr.data1 <- before.PT$ltr.data
-
-```
-
-```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
-
-  # Create Airbnb plot
-
-  abb.types <- ggplot(abb.data1, aes(x=type)) +
-    geom_bar(color=str.col, fill=str.col) +
-    xlab('') +
-    ylab('# of Properties\n') +
-    labs(title = "Short Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Create long term rental plot
-
-  ltr.types <- ggplot(ltr.data1, aes(x=type)) +
-    geom_bar(color=ltr.col, fill=ltr.col) +
-    xlab('') +
-    ylab('# of Properties\n') +
-    labs(title = "Long Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Output plots
-
-  ggMultiPlots(abb.types, ltr.types, cols=2)
-
-```
-
-```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  abb.data1 <- subset(abb.data1, type != 'Other')
-  ltr.data1 <- subset(ltr.data1, type != 'Other')
-
-```
-
-Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
-
-1. **Entire Home/Apt**: The entire home or apartment is available
-2. **Private Room**: One room within a house or apartment is available
-3. **Shared Room**: A bed within a room shared by another occupant(s) is available
-
-As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
+-->
+
+<!-- ```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'} -->
+<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
+<!--   load(paste0(data.path, '/analyzed/abb_beforePT.RData')) -->
+<!--   abb.data1 <- before.PT$abb.data -->
+<!--   ltr.data1 <- before.PT$ltr.data -->
+
+<!-- ``` -->
+
+<!-- ```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'} -->
+
+<!--   # Create Airbnb plot -->
+
+<!--   abb.types <- ggplot(abb.data1, aes(x=type)) + -->
+<!--     geom_bar(color=str.col, fill=str.col) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Short Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Create long term rental plot -->
+
+<!--   ltr.types <- ggplot(ltr.data1, aes(x=type)) + -->
+<!--     geom_bar(color=ltr.col, fill=ltr.col) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Long Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Output plots -->
+
+<!--   ggMultiPlots(abb.types, ltr.types, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   abb.data1 <- subset(abb.data1, type != 'Other') -->
+<!--   ltr.data1 <- subset(ltr.data1, type != 'Other') -->
+
+<!-- ``` -->
+
+<!-- Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked: -->
+
+<!-- 1. **Entire Home/Apt**: The entire home or apartment is available -->
+<!-- 2. **Private Room**: One room within a house or apartment is available -->
+<!-- 3. **Shared Room**: A bed within a room shared by another occupant(s) is available -->
+
+<!-- As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
 Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable.
-
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}
-
-  # Fix data types and names
-
-  abb.data1$listing.type <- as.character(abb.data1$listing.type)
-  abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home'
-
-  # Make Plot
-
-  ggplot(abb.data1, aes(x=listing.type)) +
-    geom_bar(color=abb.col[1], fill=abb.col[1]) +
-    xlab('') +
-    ylab('# of Properties\n') +
-    labs(title = "Short Term Rentals \nby Listing Type\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ]
-
-```
-
-#### Structural Characteristics
-
-We now turn to filtering by structural characteristics.
+-->
+
+<!-- ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'} -->
+
+<!--   # Fix data types and names -->
+
+<!--   abb.data1$listing.type <- as.character(abb.data1$listing.type) -->
+<!--   abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home' -->
+
+<!--   # Make Plot -->
+
+<!--   ggplot(abb.data1, aes(x=listing.type)) + -->
+<!--     geom_bar(color=abb.col[1], fill=abb.col[1]) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Properties\n') + -->
+<!--     labs(title = "Short Term Rentals \nby Listing Type\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ] -->
+
+<!-- ``` -->
+
+<!-- #### Structural Characteristics -->
+
+<!-- We now turn to filtering by structural characteristics.
 As the Airbnb data provides limited information on the structural characteristics, the only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
 Additionally, as the markets and structural components of houses and apartment differ, we bifurcate our analysis between the two property types from this point forward.
-
-We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
+-->
+
+<!-- We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
 For both short and long term rentals we see that most apartments have less than four bedrooms and houses less than five (Figure 3).
@@
 We convert the 0 bed short term units to 1 bed units.
-
-```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove missing and data errors
-
-  # Long term data
-  ltr.data1 <- ltr.data1[!is.na(ltr.data1$bedrooms), ]
-  ltr.data1 <- ltr.data1[ltr.data1$bedrooms <= 10, ]
-
-  # Short term data
-  abb.data1 <- abb.data1[!is.na(abb.data1$bedrooms), ]
-  abb.data1 <- abb.data1[abb.data1$bedrooms <= 10, ]
-
-```
-
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'}
-
- # Build long term bar plot
-
-   ltrbed <- ggplot(ltr.data1, aes(x=bedrooms)) +
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:10, breaks=1:10)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bedrooms in Long Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Build short term bar plot
-
-  abbbed <- ggplot(abb.data1, aes(x=bedrooms)) +
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:10, breaks=0:10)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bedrooms in Short Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Make the comparison plot
-
-  ggMultiPlots(abbbed, ltrbed, cols=1)
-
-```
-
-```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove all with more than 4 beds
-
-  abb.data1 <- abb.data1[abb.data1$bedrooms < 5, ]
-  ltr.data1 <- ltr.data1[ltr.data1$bedrooms < 5, ]
-
- # Remove apartments with more than 3
-
-  abba <- which(abb.data1$bedrooms > 3 & abb.data1$type =='Apartment')
-  ltra <- which(ltr.data1$bedrooms > 3 & ltr.data1$type =='Apartment')
-
-  if(length(abba) > 0) abb.data1 <- abb.data1[-abba, ]
-  if(length(ltra) > 0) ltr.data1 <- ltr.data1[-ltra, ]
-
-  # Convert 0 Bed to 1 Bed
-  abb.data1$bedrooms[abb.data1$bedrooms == 0] <- 1
-
-```
-
-We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apartment/house.
+-->
+
+<!-- ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove missing and data errors -->
+
+<!--   # Long term data -->
+<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$bedrooms), ] -->
+<!--   ltr.data1 <- ltr.data1[ltr.data1$bedrooms <= 10, ] -->
+
+<!--   # Short term data -->
+<!--   abb.data1 <- abb.data1[!is.na(abb.data1$bedrooms), ] -->
+<!--   abb.data1 <- abb.data1[abb.data1$bedrooms <= 10, ] -->
+
+<!-- ``` -->
+
+<!-- ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'} -->
+
+<!--  # Build long term bar plot -->
+
+<!--    ltrbed <- ggplot(ltr.data1, aes(x=bedrooms)) + -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=1:10, breaks=1:10)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bedrooms in Long Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Build short term bar plot -->
+
+<!--   abbbed <- ggplot(abb.data1, aes(x=bedrooms)) + -->
+<!--     geom_bar(fill=str.col, color=str.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=0:10, breaks=0:10)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bedrooms in Short Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Make the comparison plot -->
+
+<!--   ggMultiPlots(abbbed, ltrbed, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove all with more than 4 beds -->
+
+<!--   abb.data1 <- abb.data1[abb.data1$bedrooms < 5, ] -->
+<!--   ltr.data1 <- ltr.data1[ltr.data1$bedrooms < 5, ] -->
+
+<!--  # Remove apartments with more than 3 -->
+
+<!--   abba <- which(abb.data1$bedrooms > 3 & abb.data1$type =='Apartment') -->
+<!--   ltra <- which(ltr.data1$bedrooms > 3 & ltr.data1$type =='Apartment') -->
+
+<!--   if(length(abba) > 0) abb.data1 <- abb.data1[-abba, ] -->
+<!--   if(length(ltra) > 0) ltr.data1 <- ltr.data1[-ltra, ] -->
+
+<!--   # Convert 0 Bed to 1 Bed -->
+<!--   abb.data1$bedrooms[abb.data1$bedrooms == 0] <- 1 -->
+
+<!-- ``` -->
+
+<!-- We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apartment/house.
 Here we see that nearly all properties have three or fewer bathrooms and we filter the data accordingly (Figure 4).
@@
 We round the baths in the short term data up to whole integers.
-
-```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Remove missing data
-
-  ltr.data1 <- ltr.data1[!is.na(ltr.data1$baths), ]
-  abb.data1 <- abb.data1[!is.na(abb.data1$baths), ]
-
-```
-
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'}
-
- # Build long term plot
-
-  ltbath <- ggplot(ltr.data1, aes(x=baths)) +
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=1:8, breaks=1:8)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bathrooms in Long Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Build short term plot
-
-  stbath <- ggplot(abb.data1, aes(x=baths)) +
-    geom_bar(fill=str.col, color=str.col) +
-    facet_wrap(~type) +
-    scale_x_continuous(labels=0:8, breaks=0:8)+
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bathrooms in Short Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5))
-
- # Make Plots
-
-  ggMultiPlots(stbath, ltbath, cols=1)
-
-```
-
-```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Filter by bath count
-
-  # Short term data
-  abb.data1 <- abb.data1[abb.data1$baths < 4, ]
-  abb.data1 <- abb.data1[abb.data1$baths > 0, ]
-
-  # Long term data
-  ltr.data1 <- ltr.data1[ltr.data1$baths < 4, ]
-
- # Round baths up
-
-  abb.data1$baths <- round(abb.data1$baths + .01, 0)
-
-```
-
-In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+-->
+
+<!-- ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Remove missing data -->
+
+<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$baths), ] -->
+<!--   abb.data1 <- abb.data1[!is.na(abb.data1$baths), ] -->
+
+<!-- ``` -->
+
+<!-- ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'} -->
+
+<!--  # Build long term plot -->
+
+<!--   ltbath <- ggplot(ltr.data1, aes(x=baths)) + -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=1:8, breaks=1:8)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bathrooms in Long Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Build short term plot -->
+
+<!--   stbath <- ggplot(abb.data1, aes(x=baths)) + -->
+<!--     geom_bar(fill=str.col, color=str.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     scale_x_continuous(labels=0:8, breaks=0:8)+ -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bathrooms in Short Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  # Make Plots -->
+
+<!--   ggMultiPlots(stbath, ltbath, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Filter by bath count -->
+
+<!--   # Short term data -->
+<!--   abb.data1 <- abb.data1[abb.data1$baths < 4, ] -->
+<!--   abb.data1 <- abb.data1[abb.data1$baths > 0, ] -->
+
+<!--   # Long term data -->
+<!--   ltr.data1 <- ltr.data1[ltr.data1$baths < 4, ] -->
+
+<!--  # Round baths up -->
+
+<!--   abb.data1$baths <- round(abb.data1$baths + .01, 0) -->
+
+<!-- ``` -->
+
+<!-- In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
 In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
@@
 We filter the data to these combinations.
-
-```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Create combination variable
-
-  ltr.data1$bedbath <- paste0(ltr.data1$bedrooms, '..', ltr.data1$baths)
-  abb.data1$bedbath <- paste0(abb.data1$bedrooms, '..', abb.data1$baths)
-
-```
-
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}
-
- # Make long term plot
-
-  ltb <- ggplot(ltr.data1, aes(x=bedbath)) +
-    geom_bar(fill=ltr.col, color=ltr.col) +
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bed/Bath Combo in Long Term Rentals\n") +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
-    facet_wrap(~type)
-
- # Make short term plots
-
-  stb <- ggplot(abb.data1, aes(x=bedbath)) +
-    geom_bar(fill=str.col, color=str.col) +
-    xlab('') +
-    ylab('# of Props\n') +
-    labs(title = "Bed/Bath Combo in Short Term Rentals\n") +
-    scale_y_continuous(breaks=c(1000, 3000, 5000)) +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
-    facet_wrap(~type)
-
- # Plot
-
-  ggMultiPlots(ltb, stb, cols=1)
-
-```
-
-```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- # Set level of acceptable combinations
-
-  acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
-
- # Filter data
-
-  ltr.data1 <- ltr.data1[ltr.data1$bedbath %in% acc.bb, ]
-  abb.data1 <- abb.data1[abb.data1$bedbath %in% acc.bb, ]
-
-```
-
-### Rates and Rental values
-
-Next we filter by the prices -- the nightly rates and weekly rental values.
+-->
+
+<!-- ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Create combination variable -->
+
+<!--   ltr.data1$bedbath <- paste0(ltr.data1$bedrooms, '..', ltr.data1$baths) -->
+<!--   abb.data1$bedbath <- paste0(abb.data1$bedrooms, '..', abb.data1$baths) -->
+
+<!-- ``` -->
+
+<!-- ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'} -->
+
+<!--  # Make long term plot -->
+
+<!--   ltb <- ggplot(ltr.data1, aes(x=bedbath)) + -->
+<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bed/Bath Combo in Long Term Rentals\n") + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
+<!--     facet_wrap(~type) -->
+
+<!--  # Make short term plots -->
+
+<!--   stb <- ggplot(abb.data1, aes(x=bedbath)) + -->
+<!--     geom_bar(fill=str.col, color=str.col) + -->
+<!--     xlab('') + -->
+<!--     ylab('# of Props\n') + -->
+<!--     labs(title = "Bed/Bath Combo in Short Term Rentals\n") + -->
+<!--     scale_y_continuous(breaks=c(1000, 3000, 5000)) + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
+<!--     facet_wrap(~type) -->
+
+<!--  # Plot -->
+
+<!--   ggMultiPlots(ltb, stb, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  # Set level of acceptable combinations -->
+
+<!--   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2') -->
+
+<!--  # Filter data -->
+
+<!--   ltr.data1 <- ltr.data1[ltr.data1$bedbath %in% acc.bb, ] -->
+<!--   abb.data1 <- abb.data1[abb.data1$bedbath %in% acc.bb, ] -->
+
+<!-- ``` -->
+
+<!-- ### Rates and Rental values -->
+
+<!-- Next we filter by the prices -- the nightly rates and weekly rental values.
 The long term rental data have a single price observation, the asking rent at closing.
@@
 To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1, 2015 to August 31, 2016 period.
-
-We start by removing property level observations missing price data.
+-->
+
+<!-- We start by removing property level observations missing price data.
 Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 6).
@@
 We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.
-
-```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  ltr.data1 <- ltr.data1[!is.na(ltr.data1$event.price), ]
-  abb.data1 <- abb.data1[!is.na(abb.data1$nightly.rate), ]
-
-```
-
-```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Property level data
-
-  abb.data1$average.daily.rate <- abb.data1$average.daily.rate * exch.rate
-  abb.data1$nightly.rate <- abb.data1$nightly.rate * exch.rate
-  abb.data1$weekly.rate <- abb.data1$weekly.rate * exch.rate
-  abb.data1$monthly.rate <- abb.data1$monthly * exch.rate
-
-  # Daily data
-
-  #daily.data$price <- daily.data$price * exch.rate
-
-```
-
-```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  # ltr Plot
-
-  ltr.plot <- ggplot(ltr.data1, aes(x=event.price)) +
-    geom_density(fill=ltr.col, alpha=.8) +
-    ylab('Frequency') +
-    xlab('Weekly Rental') +
-    ggtitle('Long Term Rentals') +
-    scale_x_continuous(limits=c(0, 1500)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          plot.title = element_text(hjust = 0.5))
-
-  # Nightly Rate plot
-  rate.plot <- ggplot(abb.data1, aes(x=nightly.rate)) +
-    geom_density(fill=str.col, alpha=.8) +
-    ylab('Frequency') +
-    xlab('Nightly Rate') +
-    ggtitle('Short Term Rentals') +
-    scale_x_continuous(limits=c(0, 600)) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'}
-
-  ggMultiPlots(ltr.plot, rate.plot, cols=2)
-
-```
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
- ## Filter the long term data
-
-  ltr.data1 <- ltr.data1[ltr.data1$event.price >= 200 &
-                         ltr.data1$event.price <= 1000, ]
-
- ## Filter the short term data
-
-  abb.data1 <- abb.data1[abb.data1$nightly.rate >= 50 &
-                         abb.data1$nightly.rate <= 500, ]
-
-```
-
-### Location and Submarkets
-
-Location is an important determinant in both the short- and long-term rental markets.
+-->
+
+<!-- ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$event.price), ] -->
+<!--   abb.data1 <- abb.data1[!is.na(abb.data1$nightly.rate), ] -->
+
+<!-- ``` -->
+
+<!-- ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Property level data -->
+
+<!--   abb.data1$average.daily.rate <- abb.data1$average.daily.rate * exch.rate -->
+<!--   abb.data1$nightly.rate <- abb.data1$nightly.rate * exch.rate -->
+<!--   abb.data1$weekly.rate <- abb.data1$weekly.rate * exch.rate -->
+<!--   abb.data1$monthly.rate <- abb.data1$monthly * exch.rate -->
+
+<!--   # Daily data -->
+
+<!--   #daily.data$price <- daily.data$price * exch.rate -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   # ltr Plot -->
+
+<!--   ltr.plot <- ggplot(ltr.data1, aes(x=event.price)) + -->
+<!--     geom_density(fill=ltr.col, alpha=.8) + -->
+<!--     ylab('Frequency') + -->
+<!--     xlab('Weekly Rental') + -->
+<!--     ggtitle('Long Term Rentals') + -->
+<!--     scale_x_continuous(limits=c(0, 1500)) + -->
+<!--     theme(axis.title.y=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Nightly Rate plot -->
+<!--   rate.plot <- ggplot(abb.data1, aes(x=nightly.rate)) + -->
+<!--     geom_density(fill=str.col, alpha=.8) + -->
+<!--     ylab('Frequency') + -->
+<!--     xlab('Nightly Rate') + -->
+<!--     ggtitle('Short Term Rentals') + -->
+<!--     scale_x_continuous(limits=c(0, 600)) + -->
+<!--     theme(axis.title.y=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'} -->
+
+<!--   ggMultiPlots(ltr.plot, rate.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--  ## Filter the long term data -->
+
+<!--   ltr.data1 <- ltr.data1[ltr.data1$event.price >= 200 & -->
+<!--                          ltr.data1$event.price <= 1000, ] -->
+
+<!--  ## Filter the short term data -->
+
+<!--   abb.data1 <- abb.data1[abb.data1$nightly.rate >= 50 & -->
+<!--                          abb.data1$nightly.rate <= 500, ] -->
+
+<!-- ``` -->
+
+<!-- ### Location and Submarkets -->
+
+<!-- Location is an important determinant in both the short- and long-term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 Figure 7 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Build the map object
-
-  # Set colors
-  g.cols <- abb.col[c(2, 10, 9)]
-
-  # Make map
-  loc.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) +
-    scale_fill_manual(values=c('gray10', 'gray40', 'gray70'),
-                      labels=c('Inner      ',
-                               'Middle      ',
-                               'Outer')) +
-    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    ggtitle("Melbourne Suburb Classifications")
-
-```
-
-```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'}
-
-  loc.map
-
-```
-
-```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
-  abb.data2 <- after.SP$abb.data
-  ltr.data2 <- after.SP$ltr.data
-
-```
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+-->
+
+<!-- ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Build the map object -->
+
+<!--   # Set colors -->
+<!--   g.cols <- abb.col[c(2, 10, 9)] -->
+
+<!--   # Make map -->
+<!--   loc.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + -->
+<!--     scale_fill_manual(values=c('gray10', 'gray40', 'gray70'), -->
+<!--                       labels=c('Inner      ', -->
+<!--                                'Middle      ', -->
+<!--                                'Outer')) + -->
+<!--     geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     xlab('') + ylab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(), -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     ggtitle("Melbourne Suburb Classifications") -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'} -->
+
+<!--   loc.map -->
+
+<!-- ``` -->
+
+<!-- ```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'} -->
+<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
+<!--   load(paste0(data.path, '/analyzed/abb_afterSP.RData')) -->
+<!--   abb.data2 <- after.SP$abb.data -->
+<!--   ltr.data2 <- after.SP$ltr.data -->
+
+<!-- ``` -->
+
+<!-- It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne: -->
+
+<!-- 1. Rural (Outer suburbs, not Beach) -->
+<!-- 2. Suburban (Middle suburbs, not Beach) -->
+<!-- 3. City (Inner Suburbs, not Beach, not Core) -->
+<!-- 4. City-Core (Select inner suburbs with tourist activities and near CBD) -->
+<!-- 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River) -->
+
+<!-- We select the 18 suburbs below to represent the 'core' of the city (Table 1).
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
 All are well serviced by public transportation and possess abundant amenities for tourists.
-
-```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
-
- core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
-                   'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
-                   'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
-                   'St Kilda West', 'West Melbourne', 'Windsor')
-
- c.subs <- data.frame(A=core.suburbs[1:6],
-                      B=core.suburbs[7:12],
-                      C=core.suburbs[13:18])
- names(c.subs) <- NULL
- rownames(c.subs) <- NULL
-
- print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
-       include.rownames=F,
-       caption.placement="top",
-       hline.after=c(0,6))
-
-```
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+-->
+
+<!-- ```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE} -->
+
+<!--  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands', -->
+<!--                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran', -->
+<!--                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda', -->
+<!--                    'St Kilda West', 'West Melbourne', 'Windsor') -->
+
+<!--  c.subs <- data.frame(A=core.suburbs[1:6], -->
+<!--                       B=core.suburbs[7:12], -->
+<!--                       C=core.suburbs[13:18]) -->
+<!--  names(c.subs) <- NULL -->
+<!--  rownames(c.subs) <- NULL -->
+
+<!--  print(xtable(c.subs, caption = 'List of Core Suburbs\n'), -->
+<!--        include.rownames=F, -->
+<!--        caption.placement="top", -->
+<!--        hline.after=c(0,6)) -->
+
+<!-- ``` -->
+
+<!-- We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short and long term data.
@@
 The location of the short and long term rentals, colored by submarket, are shown in Figure 8.
-
-Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+-->
+
+<!-- Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
 Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
@@
 After making this correction we then assign one of the five submarket designations based on the process described above.
-
-```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Set submarket colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
-  # Make map
-
-  abb.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=abb.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
-               alpha=.2) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) +
-    ggtitle('AirBNB Location\nBy Submarket')
-
-```
-
-```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  # Make map
-
-  ltr.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
-    geom_point(data=ltr.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
-               alpha=.1) +
-    scale_color_manual(values=sm.col) +
-    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-    xlab('') + ylab('')+
-   theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank(),
-          panel.background = element_rect(fill = "white"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks = element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1))) +
-    ggtitle('Long Term Rental Location\nBy Submarket')
-
-```
-
-```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
-
-  ggMultiPlots(abb.map, ltr.map, cols=1)
-
-```
-
-To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+-->
+
+<!-- ```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Set submarket colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)] -->
+
+<!--   # Make map -->
+
+<!--   abb.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
+<!--     geom_point(data=abb.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2, -->
+<!--                alpha=.2) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(), -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
+<!--                                                      alpha=1))) + -->
+<!--     ggtitle('AirBNB Location\nBy Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
+
+<!--   # Make map -->
+
+<!--   ltr.map <- ggplot() + -->
+<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
+<!--     geom_point(data=ltr.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1, -->
+<!--                alpha=.1) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
+<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
+<!--     xlab('') + ylab('')+ -->
+<!--    theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           panel.grid.major = element_blank(), -->
+<!--           panel.grid.minor = element_blank(), -->
+<!--           panel.background = element_rect(fill = "white"), -->
+<!--           axis.text.x = element_blank(), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks = element_blank(), -->
+<!--           axis.title.x=element_blank(), -->
+<!--           axis.title.y=element_blank(), -->
+<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
+<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
+<!--                                                      alpha=1))) + -->
+<!--     ggtitle('Long Term Rental Location\nBy Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'} -->
+
+<!--   ggMultiPlots(abb.map, ltr.map, cols=1) -->
+
+<!-- ``` -->
+
+<!-- To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
 A number of interesting observations are illustrated here (Figure 9).
@@
 Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
-
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}
-
-  # Make Airbnb submarket map
-
-  abbtype.map <- ggplot() +
-    geom_bar(data=abb.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          plot.title = element_text(hjust = 0.5)) +
-    ggtitle('AirBNB Property Type By Submarket')
-
-  # Make Long term rental map
-
-  ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
-    scale_fill_manual(values=sm.col) +
-    facet_wrap(~type) +
-    ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
-          legend.title = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          plot.title = element_text(hjust = 0.5)) +
-    ggtitle('Long Term Property Type By Submarket')
-
-```
-
-```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=7, fig.cap='Observations by Submarket'}
-
-  ggMultiPlots(abbtype.map, ltrtype.map, cols=1)
-
-```
-
-### Observed Revenue
-
-Our final data filtering considers the observed revenue of the properties.
+-->
+
+<!-- ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9} -->
+
+<!--   # Make Airbnb submarket map -->
+
+<!--   abbtype.map <- ggplot() + -->
+<!--     geom_bar(data=abb.data2, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     ylab('# of Properties\n') + xlab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           axis.text.x=element_blank(), -->
+<!--           axis.ticks.x=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) + -->
+<!--     ggtitle('AirBNB Property Type By Submarket') -->
+
+<!--   # Make Long term rental map -->
+
+<!--   ltrtype.map <- ggplot() + -->
+<!--     geom_bar(data=ltr.data2, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     facet_wrap(~type) + -->
+<!--     ylab('# of Properties\n') + xlab('')+ -->
+<!--     theme(legend.position = 'bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           axis.text.x=element_blank(), -->
+<!--           axis.ticks.x=element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) + -->
+<!--     ggtitle('Long Term Property Type By Submarket') -->
+
+<!-- ``` -->
+
+<!-- ```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=7, fig.cap='Observations by Submarket'} -->
+
+<!--   ggMultiPlots(abbtype.map, ltrtype.map, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ### Observed Revenue -->
+
+<!-- Our final data filtering considers the observed revenue of the properties.
 For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
@@
 To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
-
-For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+-->
+
+<!-- For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
 Using this data we sum up the total revenue from bookings.
 For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
-
-Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
+-->
+
+<!-- Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
 Short term revenues range from neglible to highs of greater than \$80,000.
@@
 Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
-
-```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}
-
- load(paste0(data.path, '/analyzed/abb_objs.RData'))
-
-```
-
-```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
-
-  abbr <- abb.revs[,c('bedbath', 'revenue')]
-  abbr$tenure <- 'short-term'
-  ltrr <- ltr.revs[,c('bedbath', 'revenue')]
-  ltrr$tenure <- 'long-term'
-  allr <- rbind(abbr, ltrr)
-
-  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
-    xlab('Annual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
-
-```
-
-### Summary of Data Cleaning
-
-We have applied nine separate filters to our two datasets.
+-->
+
+<!-- ```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE} -->
+
+<!--  load(paste0(data.path, '/analyzed/abb_objs.RData')) -->
+
+<!-- ``` -->
+
+<!-- ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'} -->
+
+<!--   abbr <- abb.revs[,c('bedbath', 'revenue')] -->
+<!--   abbr$tenure <- 'short-term' -->
+<!--   ltrr <- ltr.revs[,c('bedbath', 'revenue')] -->
+<!--   ltrr$tenure <- 'long-term' -->
+<!--   allr <- rbind(abbr, ltrr) -->
+
+<!--   ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Annual Revenues by Tenure Type') + -->
+<!--     xlab('Annual Revenue') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
+<!--                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 70000)) -->
+
+<!-- ``` -->
+
+<!-- ### Summary of Data Cleaning -->
+
+<!-- We have applied nine separate filters to our two datasets.
 In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters (Table 2).
@@
 From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
-
-For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+-->
+
+<!-- For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
 remove another 10,000 observations, leaving 122,051 in the final dataset.
-
-```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
-
-cc <- clean.count[,c('operation', 'abb', 'ltr')]
-abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1]))
-ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
-abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1])
-abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)])
-ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
-ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
-clean.table <- data.frame(field=cc$operation,
-                          abbcount=abb.count,
-                          abbcut=abb.cut,
-                          abbper=abb.per,
-                          ltrcount=ltr.count,
-                          ltrcut=ltr.cut,
-                          ltrper=ltr.per)
-
-rownames(clean.table) <- NULL
-clean.table$field <- c('Initial Count', 'Time', 'Property Type',
-                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
-                       'Rates & Rents', 'Location', 'Revenue')
-clean.table$abbper <- 100*round(clean.table$abbper, 2)
-clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
-names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
-                        'Long Term', 'Cut', '% Cut')
-options(xtable.comment = FALSE)
-print(xtable(clean.table, caption='Data Cleaning Summary\n',
-       digits=0),
-       include.rownames=FALSE,
-       caption.placement='top')
-
-```
-
-## Comparison
-
-In this section we compare returns between long and short term rental options.
+-->
+
+<!-- ```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'} -->
+
+<!-- cc <- clean.count[,c('operation', 'abb', 'ltr')] -->
+<!-- abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1])) -->
+<!-- ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1])) -->
+<!-- abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1]) -->
+<!-- abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)]) -->
+<!-- ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1]) -->
+<!-- ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)]) -->
+<!-- clean.table <- data.frame(field=cc$operation, -->
+<!--                           abbcount=abb.count, -->
+<!--                           abbcut=abb.cut, -->
+<!--                           abbper=abb.per, -->
+<!--                           ltrcount=ltr.count, -->
+<!--                           ltrcut=ltr.cut, -->
+<!--                           ltrper=ltr.per) -->
+
+<!-- rownames(clean.table) <- NULL -->
+<!-- clean.table$field <- c('Initial Count', 'Time', 'Property Type', -->
+<!--                        'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo', -->
+<!--                        'Rates & Rents', 'Location', 'Revenue') -->
+<!-- clean.table$abbper <- 100*round(clean.table$abbper, 2) -->
+<!-- clean.table$ltrper <- 100*round(clean.table$ltrper, 2) -->
+<!-- names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut', -->
+<!--                         'Long Term', 'Cut', '% Cut') -->
+<!-- options(xtable.comment = FALSE) -->
+<!-- print(xtable(clean.table, caption='Data Cleaning Summary\n', -->
+<!--        digits=0), -->
+<!--        include.rownames=FALSE, -->
+<!--        caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ## Comparison -->
+
+<!-- In this section we compare returns between long and short term rental options.
 As mentioned above, there are no direct matches between the datasets.
@@
 We will, instead, make the comparisons between the two by imputing likely short-term (long-term) rental revenues for the long-term (short-term) data and then comparing the observed revenues to the imputed revenues of the unobserved tenure type.
-
-We make our imputations via hedonic price models, one for long-term rentals and one for short-term rentals.
+-->
+
+<!-- We make our imputations via hedonic price models, one for long-term rentals and one for short-term rentals.
 We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term rental for the short term properties.
 We do the same for the long-term properties using a modeled derived from the short-term data.
-
-For the long-term market, we use the following model specification:
-
-\begin{equation}
-  \label{eq:test}
-ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i}
-\end{equation}
-
-where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
-
-For the short-term market the specification is similar, minus the time correction.
+-->
+
+<!-- For the long-term market, we use the following model specification: -->
+
+<!-- \begin{equation} -->
+<!--   \label{eq:test} -->
+<!-- ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i} -->
+<!-- \end{equation} -->
+
+<!-- where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+-->
+
+<!-- For the short-term market the specification is similar, minus the time correction.
 We eliminate this control because the short term rates are based on the medium value over the entire period and not monthly.
-This specification is:
-
-\begin{equation}
-ln(RentST_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \epsilon_{i}
-\end{equation}
-
-where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
-
-## Results
-
-We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
+This specification is: -->
+
+<!-- \begin{equation} -->
+<!-- ln(RentST_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \epsilon_{i} -->
+<!-- \end{equation} -->
+
+<!-- where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
+-->
+
+<!-- ## Results -->
+
+<!-- We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
 What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
 It is likely that different submarkets operate differently, a hypothesis investigated after the full metropolitan region.
-
-We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
+-->
+
+<!-- We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
 A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel) (Figure 11).
@@
 Interestingly, the observed (long-term) and imputed (short term) weekly rental values are somewhat similar, suggesting that the higher rent, city-core apartments push the distribution of the imputed short-term values upwards.
-
-For each of the observed values we also create a fitted value for that observation in the model.
+-->
+
+<!-- For each of the observed values we also create a fitted value for that observation in the model.
 This may help to reduce the influence of outlying observed values in our model.
@@
 The long-term properties will have: 1) an actual long-term (weekly) rent; 2) an estimated long-term (weekly) rent; and 3) an estimated nightly rate.
-
-```{r pred.glob.imp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  abbir <- abb.revs[,c('bedbath', 'imp.rent', 'med.rate')]
-  abbir$tenure.rate <- 'short-term (observed)'
-  abbir$tenure.rent <- 'short-term (imputed)'
-
-  ltrir <- ltr.revs[,c('bedbath', 'event.price', 'imp.rate')]
-  ltrir$tenure.rate <- 'long-term (imputed)'
-  ltrir$tenure.rent <- 'long-term (observed)'
-
-  names(abbir) <- names(ltrir) <- c('bedbath', 'rent', 'rate', 'tenure.rate', 'tenure.rent')
-  allir <- rbind(abbir, ltrir)
-
-```
-
-```{r imp.rate.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  irate.plot <- ggplot(allir, aes(x=rate, fill=tenure.rate, color=tenure.rate)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col)) +
-    ggtitle('Nightly Rates by Tenure Type') +
-    xlab('Nightly Rate') +
-    scale_x_continuous(breaks=c(seq(0,600, by=200)),
-                       labels=c('$0', '$200', '$400', '$600'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 625))
-
-```
-
-```{r imp.rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  irent.plot <- ggplot(allir, aes(x=rent, fill=tenure.rent, color=tenure.rent)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col)) +
-    ggtitle('Weekly Rents by Tenure Type') +
-    xlab('Weekly Rents') +
-    scale_x_continuous(breaks=c(seq(0,1000, by=200)),
-                       labels=c('$0', '$200', '$400', '$600', '$800', '$1,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(150, 1000))
-
-```
-
-```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5, fig.cap='Rates and Rents Comparison'}
-
- ggMultiPlots(irate.plot, irent.plot, cols=2)
-
-```
-
-The question of whether or not the imputations are accurate remains.
+-->
+
+<!-- ```{r pred.glob.imp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   abbir <- abb.revs[,c('bedbath', 'imp.rent', 'med.rate')] -->
+<!--   abbir$tenure.rate <- 'short-term (observed)' -->
+<!--   abbir$tenure.rent <- 'short-term (imputed)' -->
+
+<!--   ltrir <- ltr.revs[,c('bedbath', 'event.price', 'imp.rate')] -->
+<!--   ltrir$tenure.rate <- 'long-term (imputed)' -->
+<!--   ltrir$tenure.rent <- 'long-term (observed)' -->
+
+<!--   names(abbir) <- names(ltrir) <- c('bedbath', 'rent', 'rate', 'tenure.rate', 'tenure.rent') -->
+<!--   allir <- rbind(abbir, ltrir) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rate.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   irate.plot <- ggplot(allir, aes(x=rate, fill=tenure.rate, color=tenure.rate)) + -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Nightly Rates by Tenure Type') + -->
+<!--     xlab('Nightly Rate') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,600, by=200)), -->
+<!--                        labels=c('$0', '$200', '$400', '$600'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 625)) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   irent.plot <- ggplot(allir, aes(x=rent, fill=tenure.rent, color=tenure.rent)) + -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
+<!--     ggtitle('Weekly Rents by Tenure Type') + -->
+<!--     xlab('Weekly Rents') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,1000, by=200)), -->
+<!--                        labels=c('$0', '$200', '$400', '$600', '$800', '$1,000'))+ -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(150, 1000)) -->
+
+<!-- ``` -->
+
+<!-- ```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5, fig.cap='Rates and Rents Comparison'} -->
+
+<!--  ggMultiPlots(irate.plot, irent.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- The question of whether or not the imputations are accurate remains.
 Table 3 shows simple diagnostics from the two imputation models.
@@
 This could be due to omitted variables in the short term market or a greater level of variability in the price setting (which is done by individuals) as opposed to the long-term market in which most owners get help with leasing from an agency.
-
-```{r, results="asis", echo=FALSE}
-
-abbs <- c(abb.sum$r.squared, abb.sum$adj.r.squared,
-          abb.sum$sigma,
-          length(which(abs(abb.sum$residuals) > .2)) / length(abb.sum$residuals))
-ltrs <- c(ltr.sum$r.squared, ltr.sum$adj.r.squared,
-          ltr.sum$sigma,
-          length(which(abs(ltr.sum$residuals) > .2)) / length(ltr.sum$residuals))
-
-summ.table <- data.frame(shortterm=round(abbs, 3),
-                         longterm=round(ltrs, 3))
-rownames(summ.table) <- c('r-squared', 'adj r-squared',
-                          'sigma', '% fit errors > 20%')
-names(summ.table) <- c('Short Term', 'Long Term')
-
-s.table <- xtable(summ.table,
-                  caption='Imputation Model Diagnostics\n',
-                  digits=3)
-align(s.table) <- c('lcc')
-print(s.table, 
-       include.rownames=TRUE,
-                  caption.placement='top')
-
-```
-
-Next, to create an estimated short-term revenue for the long-term properties we have to create an estimate of the occupancy rate.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!-- abbs <- c(abb.sum$r.squared, abb.sum$adj.r.squared, -->
+<!--           abb.sum$sigma, -->
+<!--           length(which(abs(abb.sum$residuals) > .2)) / length(abb.sum$residuals)) -->
+<!-- ltrs <- c(ltr.sum$r.squared, ltr.sum$adj.r.squared, -->
+<!--           ltr.sum$sigma, -->
+<!--           length(which(abs(ltr.sum$residuals) > .2)) / length(ltr.sum$residuals)) -->
+
+<!-- summ.table <- data.frame(shortterm=round(abbs, 3), -->
+<!--                          longterm=round(ltrs, 3)) -->
+<!-- rownames(summ.table) <- c('r-squared', 'adj r-squared', -->
+<!--                           'sigma', '% fit errors > 20%') -->
+<!-- names(summ.table) <- c('Short Term', 'Long Term') -->
+
+<!-- s.table <- xtable(summ.table, -->
+<!--                   caption='Imputation Model Diagnostics\n', -->
+<!--                   digits=3) -->
+<!-- align(s.table) <- c('lcc') -->
+<!-- print(s.table,  -->
+<!--        include.rownames=TRUE, -->
+<!--                   caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- Next, to create an estimated short-term revenue for the long-term properties we have to create an estimate of the occupancy rate.
 For the estimated long-term rentals we have to create an estimate of the search time (days on market).
@@
 The range of occupancy varies widely from essentially 0 to 100%, with a standard deviation of 27%.
-
-For the long term search time, or days on market, we also use the median value of the observations.
+-->
+
+<!-- For the long term search time, or days on market, we also use the median value of the observations.
 The median days on market is 24, with a standard deviation of 37.
 About 60\% of long term rental spent one month or less on the market and 85\% spent less than two months searching for a tenant.
-
-Using these estimated occupancy rates and days on market, we have used equations 3 and 4 to produce estimates of long-term and short-term revenues for the short and long term observations, respectively.
+-->
+
+<!-- Using these estimated occupancy rates and days on market, we have used equations 3 and 4 to produce estimates of long-term and short-term revenues for the short and long term observations, respectively.
 We do these for the observed and the estimated rates and rents for each tenure type.
 As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as shown in Figure 11.
-
-```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4, fig.cap='Revenue Comparison Types'}
-
-  explain.plot <- blank.plot +
-    geom_text(data=ann.df,
-              label=ann.df$lab,
-              size=2.8) +
-    geom_text(data=num.df,
-              label=num.df$count,
-              size=9.5) +
-    coord_cartesian(ylim=c(-.5,1)) +
-    ggtitle('Explanation of \n Revenue Comparisons') +
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r, results="asis", echo=FALSE}
-
-  one.df <- data.frame(x=rep(0, 4),
-                       y=rep(0, 4),
-                       lab=c('31%', '87%', '54%', '79%'),
-                       est=c('Actual Rates & Rents', 'Actual Rates & Rents',
-                             'Imp. Rates & Rents', 'Imp. Rates & Rents'),
-                       data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))
-
-  sizes <- c(.31, .87, .54, .79)
-
-  one.plot <- blank.plot +
-    geom_text(data=one.df,
-              label=one.df$lab,
-              size=18*sizes) +
-    ggtitle('% of Properties where \n Airbnb is more profitable') +
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5))
-
-```
-
-In other words, the left hand panels (left side of Figure 12) are comparisons made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4, fig.cap='Revenue Comparison Types'} -->
+
+<!--   explain.plot <- blank.plot + -->
+<!--     geom_text(data=ann.df, -->
+<!--               label=ann.df$lab, -->
+<!--               size=2.8) + -->
+<!--     geom_text(data=num.df, -->
+<!--               label=num.df$count, -->
+<!--               size=9.5) + -->
+<!--     coord_cartesian(ylim=c(-.5,1)) + -->
+<!--     ggtitle('Explanation of \n Revenue Comparisons') + -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results="asis", echo=FALSE} -->
+
+<!--   one.df <- data.frame(x=rep(0, 4), -->
+<!--                        y=rep(0, 4), -->
+<!--                        lab=c('31%', '87%', '54%', '79%'), -->
+<!--                        est=c('Actual Rates & Rents', 'Actual Rates & Rents', -->
+<!--                              'Imp. Rates & Rents', 'Imp. Rates & Rents'), -->
+<!--                        data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term')) -->
+
+<!--   sizes <- c(.31, .87, .54, .79) -->
+
+<!--   one.plot <- blank.plot + -->
+<!--     geom_text(data=one.df, -->
+<!--               label=one.df$lab, -->
+<!--               size=18*sizes) + -->
+<!--     ggtitle('% of Properties where \n Airbnb is more profitable') + -->
+<!--     theme(legend.position='bottom', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5)) -->
+
+<!-- ``` -->
+
+<!-- In other words, the left hand panels (left side of Figure 12) are comparisons made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
 In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
-
-The right hand side of Figure 12 shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
+-->
+
+<!-- The right hand side of Figure 12 shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
 The variation between these estimates is significant and troublesome.
@@
 Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
-
-```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center', fig.cap='Summary of Comparison Types'}
-
- ggMultiPlots(explain.plot, one.plot, cols=2)
-
-```
-
-In short, only in the upper left hand panel are we using the actual nightly rates and the actual occupancy rates from the short term market.
+-->
+
+<!-- ```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center', fig.cap='Summary of Comparison Types'} -->
+
+<!--  ggMultiPlots(explain.plot, one.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- In short, only in the upper left hand panel are we using the actual nightly rates and the actual occupancy rates from the short term market.
 We do estimate the long-term rates and days on market here, but as shown above, the models for those figures are much more robust.
@@
 This means that we will only be considering comparisons of actual Airbnb revenues to their estimated long-term rental revenues.
-
-```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center', fig.cap='Comparison Types: Strengths and Weaknesses'}
-
-  reason.plot <- blank.plot +
-    geom_rect(data = mrkt.table, aes(fill=good),
-              xmin = -Inf,xmax = Inf,
-              ymin = -Inf,ymax = Inf, alpha = 0.4) +
-    geom_text(data=reason.df,
-              label=reason.df$lab,
-              size=3) +
-    geom_text(data=num.df,
-              label=num.df$count,
-              size=9.5) +
-    coord_cartesian(ylim=c(-.5,1))
-
-  reason.plot
-
-```
-
-### Occupancy Rates
-
-Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
+-->
+
+<!-- ```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center', fig.cap='Comparison Types: Strengths and Weaknesses'} -->
+
+<!--   reason.plot <- blank.plot + -->
+<!--     geom_rect(data = mrkt.table, aes(fill=good), -->
+<!--               xmin = -Inf,xmax = Inf, -->
+<!--               ymin = -Inf,ymax = Inf, alpha = 0.4) + -->
+<!--     geom_text(data=reason.df, -->
+<!--               label=reason.df$lab, -->
+<!--               size=3) + -->
+<!--     geom_text(data=num.df, -->
+<!--               label=num.df$count, -->
+<!--               size=9.5) + -->
+<!--     coord_cartesian(ylim=c(-.5,1)) -->
+
+<!--   reason.plot -->
+
+<!-- ``` -->
+
+<!-- ### Occupancy Rates -->
+
+<!-- Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
 Unfortunately, these are also the most difficult factor to estimate or impute.
@@
 The decrease in profitabilty after 75\% occupancy is likely due to: 1) small sample sizes in this tail of the data; and 2) that lowering overall nightly rates too low simply to boost occupancy can result in lower overall revenue.
-
-As the distribution of occupancy rates is not uniform (Figure 14, right panel), the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+-->
+
+<!-- As the distribution of occupancy rates is not uniform (Figure 14, right panel), the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
 In Figure 15, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
 By doing so, we see that, in general, properties need to be in the upper 1/3 of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  rawocc.pplot <- makePrefPlot(abb.revs,
-                               x.field='occ.rate',
-                               y.field='abb.act',
-                                    smooth=TRUE,
-                               smooth.span=.75)
-  rawocc.pplot <- rawocc.pplot +
-    xlab('\nOccupancy Rate') +
-    ylab('\n% of Properties where \nAirbnb is more profitable') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_color_manual(values=sm.col) +
-    ggtitle('Tenure Profitability vs \n Occupancy Rate') +
-    theme(legend.position='none',
-          plot.title = element_text(hjust = 0.5)) +
-    coord_cartesian(ylim=c(0,1)) +
-    geom_hline(aes(yintercept=.5))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  dens.plot <- ggplot(abb.revs, aes(x=occ.rate)) +
-    geom_density(alpha=.3, fill=1) +
-    scale_color_manual(values=sm.col) +
-    scale_fill_manual(values=sm.col) +
-    scale_x_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-
-    ylab('\nFrequency of Occurance') +
-    xlab('\nOccupancy Rate') +
-    ggtitle('Distribution of \n Occupancy Rates') +
-    theme(legend.position='none',
-          plot.title = element_text(hjust = 0.5),
-          axis.line=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'}
-
-  ggMultiPlots(rawocc.pplot, dens.plot, cols=2)
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate,
-                                      return.type='rank')
-  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate,
-                                  return.type='rank')
-
-  ## Make quartile location plot
-
-  qtlocc.pplot <- makePrefPlot(abb.revs,
-                               x.field='occ.qtl',
-                               y.field='abb.act',
-                               smooth=TRUE,
-                               smooth.span=.55)
-  qtlocc.pplot <- qtlocc.pplot +
-    xlab('\nQuantile of Occupancy Rate') +
-    ylab('\n% of Properties where \n Airbnb is more profitable') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_color_manual(values=sm.col) +
-    theme(legend.position='none') +
-    coord_cartesian(ylim=c(0,1))+
-    geom_hline(aes(yintercept=.5))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4, fig.height=3, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'}
-
-  qtlocc.pplot
-
-```
-
-Along with occupancy rates, the other important consideration is the nightly rate.
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   rawocc.pplot <- makePrefPlot(abb.revs, -->
+<!--                                x.field='occ.rate', -->
+<!--                                y.field='abb.act', -->
+<!--                                     smooth=TRUE, -->
+<!--                                smooth.span=.75) -->
+<!--   rawocc.pplot <- rawocc.pplot + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     ylab('\n% of Properties where \nAirbnb is more profitable') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     ggtitle('Tenure Profitability vs \n Occupancy Rate') + -->
+<!--     theme(legend.position='none', -->
+<!--           plot.title = element_text(hjust = 0.5)) + -->
+<!--     coord_cartesian(ylim=c(0,1)) + -->
+<!--     geom_hline(aes(yintercept=.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   dens.plot <- ggplot(abb.revs, aes(x=occ.rate)) + -->
+<!--     geom_density(alpha=.3, fill=1) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     scale_fill_manual(values=sm.col) + -->
+<!--     scale_x_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+
+<!--     ylab('\nFrequency of Occurance') + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     ggtitle('Distribution of \n Occupancy Rates') + -->
+<!--     theme(legend.position='none', -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.line=element_blank(), -->
+<!--           axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank()) -->
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'} -->
+
+<!--   ggMultiPlots(rawocc.pplot, dens.plot, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--   abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, -->
+<!--                                       return.type='rank') -->
+<!--   abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, -->
+<!--                                   return.type='rank') -->
+
+<!--   ## Make quartile location plot -->
+
+<!--   qtlocc.pplot <- makePrefPlot(abb.revs, -->
+<!--                                x.field='occ.qtl', -->
+<!--                                y.field='abb.act', -->
+<!--                                smooth=TRUE, -->
+<!--                                smooth.span=.55) -->
+<!--   qtlocc.pplot <- qtlocc.pplot + -->
+<!--     xlab('\nQuantile of Occupancy Rate') + -->
+<!--     ylab('\n% of Properties where \n Airbnb is more profitable') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0', '25th', '50th', '75th', '100th')) + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_color_manual(values=sm.col) + -->
+<!--     theme(legend.position='none') + -->
+<!--     coord_cartesian(ylim=c(0,1))+ -->
+<!--     geom_hline(aes(yintercept=.5)) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4, fig.height=3, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'} -->
+
+<!--   qtlocc.pplot -->
+
+<!-- ``` -->
+
+<!-- Along with occupancy rates, the other important consideration is the nightly rate.
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
@@
 The transparency is related to the total count of actual market properties falling into that area.
-
-The general trend is what is expected, i.e.
+-->
+
+<!-- The general trend is what is expected, i.e.
 that higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
@@
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
-
-An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+-->
+
+<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
 In this case, we delineate the boundary (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
@@
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'}
-
- ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
-
-```
-
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 16 may be misleading.
+-->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'} -->
+
+<!--  ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 16 may be misleading.
 We convert both axis to quantiles and replot both in Figure 17.
@@
 For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
-
- ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
-
-```
-
-### Market Summary
-
-Finally, we summarize the entire market by looking at three metrics:
-
-1. Actual: The percentage of properties in the market in which short-term (Airbnb) generates more revenue
-2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable
-3. SVM Area: The percentage of the total area in the SVM plot that represents a situation where the short-term rental is more profitable.
-
-None of these metrics on their own is perfect.
+-->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'} -->
+
+<!--  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ### Market Summary -->
+
+<!-- Finally, we summarize the entire market by looking at three metrics: -->
+
+<!-- 1. Actual: The percentage of properties in the market in which short-term (Airbnb) generates more revenue -->
+<!-- 2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable -->
+<!-- 3. SVM Area: The percentage of the total area in the SVM plot that represents a situation where the short-term rental is more profitable. -->
+
+<!-- None of these metrics on their own is perfect.
 The 'actual' measure responds directly to the sample of the current market and may not be as useful to a potential investor.
@@
 This latter issue is partially limited by plotting by quantile, but, nonetheless still exists.
-
-We calculate each for the raw rates as well as for the quantile situation.
+-->
+
+<!-- We calculate each for the raw rates as well as for the quantile situation.
 These are show in Table 4.
@@
 As the difference between the fitted and the svm area is considerably smaller in the quantile approach, there is less bias from outlying, empty areas.
-
-```{r, results="asis", comment=FALSE,  echo=FALSE}
-
-names(market.ratio) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
-print(xtable(market.ratio, caption='Metro Level: Short-Term Preference Analysis\n',
-       digits=3),
-       include.rownames=FALSE,
-      caption.placement='top')
-
-```
-
-### Submarkets
-
-A major concern about the above analysis is that the estimated rents, rates, days on market and occupancy rates are estimated globally.
+-->
+
+<!-- ```{r, results="asis", comment=FALSE,  echo=FALSE} -->
+
+<!-- names(market.ratio) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area') -->
+<!-- print(xtable(market.ratio, caption='Metro Level: Short-Term Preference Analysis\n', -->
+<!--        digits=3), -->
+<!--        include.rownames=FALSE, -->
+<!--       caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ### Submarkets -->
+
+<!-- A major concern about the above analysis is that the estimated rents, rates, days on market and occupancy rates are estimated globally.
 As a result, there is the likelihood of significant bias within certain submarkets.
 Below, we break down the results by type (apartment vs house), by geographic market (five geographic submarkets listed above) and by type and submarket.
-
-#### Property Type
-
-First, we bifurcate our data into houses and apartments.
+-->
+
+<!-- #### Property Type -->
+
+<!-- First, we bifurcate our data into houses and apartments.
 We then rerun the entire analysis described above for the house and the apartment markets separately.
@@
 Houses, on the other hand, need either very high rates or very high occupancies to justify a short-term rental.
-
-The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.
+-->
+
+<!-- The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.
 First, the difference between the SVM Area and the Fitted number highlight the fact that even when transforming the axes into quantile, the data are still not uniformly distributed across the 2-dimensional space of the plot.
@@
 Despite this fact, we feel that the SVM Area values are useful for the owner in our scenario because they provide both a value and visual guide that present the possibilities of being more profitable with a short-term strategy, not just what the current distribution of such properties are.
-
-```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Property Type'}
-
- type.table <- rbind(apt$mrkt.score, house$mrkt.score)
- type.table$property.type <- c('apartment', '', 'house', '')
- type.table <- type.table[,c(5,1:4)]
- names(type.table) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area')
- print(xtable(type.table, caption='Short-term Preference Analysis: By Property Type\n',
-       digits=3),
-       include.rownames=FALSE, hline.after=c(-1,0,2,4),
-       caption.placment='top')
-
-```
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'}
-
-ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2)
-
-```
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'}
-
-ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2)
-
-```
-
-#### Geographic Submarkets
-
-We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
+-->
+
+<!-- ```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Property Type'} -->
+
+<!--  type.table <- rbind(apt$mrkt.score, house$mrkt.score) -->
+<!--  type.table$property.type <- c('apartment', '', 'house', '') -->
+<!--  type.table <- type.table[,c(5,1:4)] -->
+<!--  names(type.table) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area') -->
+<!--  print(xtable(type.table, caption='Short-term Preference Analysis: By Property Type\n', -->
+<!--        digits=3), -->
+<!--        include.rownames=FALSE, hline.after=c(-1,0,2,4), -->
+<!--        caption.placment='top') -->
+
+<!-- ``` -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'} -->
+
+<!-- ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'} -->
+
+<!-- ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- #### Geographic Submarkets -->
+
+<!-- We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
 In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
@@
 This is likely explained by the fact that there are few rural properties and many of these are clustered near rural tourists activities like the Yarra Valley wine region which see a high demand for lodging (Figure 8).
-
-In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
+-->
+
+<!-- In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
 In the lower density areas it appears that tourists may prefer larger and more spacious dwellings compared to long-term renters who may experience long commutes from these fringe locations.
-
-Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
+-->
+
+<!-- Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
 This finding suggests that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
@@
 Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
-
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Quantile Market Summary; Property Type by Submarket'}
-
-sm.ms <- rbind.fill(lapply(sm.results, function(x) x$mrkt.score[2,]))
-sm.ms.apt <- rbind.fill(lapply(smt.results[1:5], function(x) x$mrkt.score[2,]))
-sm.ms.house <- rbind.fill(lapply(smt.results[6:10], function(x) x$mrkt.score[2,]))
-
-smt.table <- data.frame(sub.market=c('sub-market','beach', 'city', 'core', 'rural',
-                                     'suburban', 'all'),
-                        actual.all=c('all', round(sm.ms$actual[c(5,2,1,4,3)],2),
-                                     round(market.ratio[2,2],2)),
-                        actual.apt=c('apt', round(sm.ms.apt$actual, 2),
-                                     round(type.table[2,3],2)),
-                        actual.house=c('house', round(sm.ms.house$actual, 2),
-                                       round(type.table[4,3],2)),
-                        fitted.all=c('all',round(sm.ms$fitted[c(5,2,1,4,3)],2),
-                                     round(market.ratio[2,3],2)),
-                        fitted.apt=c('apt', round(sm.ms.apt$fitted,2),
-                                     round(type.table[2,4],2)),
-                        fitted.house=c('house', round(sm.ms.house$fitted,2),
-                                       round(type.table[4,4],2)),
-                        svmarea.all=c('all', round(sm.ms$svm[c(5,2,1,4,3)],2),
-                                      round(market.ratio[2,4],2)),
-                        svmarea.apt=c('apt', round(sm.ms.apt$svm,2),
-                                      round(type.table[2,5],2)),
-                        svmarea.house=c('house', round(sm.ms.house$svm,2),
-                                        round(type.table[4,5],2)))
-
-smt.table <- smt.table[c(1, 4, 3, 2, 6, 5, 7),]
-names(smt.table) <- c('', '', 'actual', '', '', 'fitted', '', '',
-                      'svm area', '')
-smt.full <- xtable(smt.table,
-                   caption='Short-Term Preference Analysis: Disaggregated\n')
-align(smt.full) <- 'll|rrr|rrr|rrr'
-print(smt.full, 
-       include.rownames=FALSE, 
-       hline.after=c(-1,0,1,6,7,7),
-                   caption.placement='top')
-
-```
-
-## Explaining Preference
-
-The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually  more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
+-->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Quantile Market Summary; Property Type by Submarket'} -->
+
+<!-- sm.ms <- rbind.fill(lapply(sm.results, function(x) x$mrkt.score[2,])) -->
+<!-- sm.ms.apt <- rbind.fill(lapply(smt.results[1:5], function(x) x$mrkt.score[2,])) -->
+<!-- sm.ms.house <- rbind.fill(lapply(smt.results[6:10], function(x) x$mrkt.score[2,])) -->
+
+<!-- smt.table <- data.frame(sub.market=c('sub-market','beach', 'city', 'core', 'rural', -->
+<!--                                      'suburban', 'all'), -->
+<!--                         actual.all=c('all', round(sm.ms$actual[c(5,2,1,4,3)],2), -->
+<!--                                      round(market.ratio[2,2],2)), -->
+<!--                         actual.apt=c('apt', round(sm.ms.apt$actual, 2), -->
+<!--                                      round(type.table[2,3],2)), -->
+<!--                         actual.house=c('house', round(sm.ms.house$actual, 2), -->
+<!--                                        round(type.table[4,3],2)), -->
+<!--                         fitted.all=c('all',round(sm.ms$fitted[c(5,2,1,4,3)],2), -->
+<!--                                      round(market.ratio[2,3],2)), -->
+<!--                         fitted.apt=c('apt', round(sm.ms.apt$fitted,2), -->
+<!--                                      round(type.table[2,4],2)), -->
+<!--                         fitted.house=c('house', round(sm.ms.house$fitted,2), -->
+<!--                                        round(type.table[4,4],2)), -->
+<!--                         svmarea.all=c('all', round(sm.ms$svm[c(5,2,1,4,3)],2), -->
+<!--                                       round(market.ratio[2,4],2)), -->
+<!--                         svmarea.apt=c('apt', round(sm.ms.apt$svm,2), -->
+<!--                                       round(type.table[2,5],2)), -->
+<!--                         svmarea.house=c('house', round(sm.ms.house$svm,2), -->
+<!--                                         round(type.table[4,5],2))) -->
+
+<!-- smt.table <- smt.table[c(1, 4, 3, 2, 6, 5, 7),] -->
+<!-- names(smt.table) <- c('', '', 'actual', '', '', 'fitted', '', '', -->
+<!--                       'svm area', '') -->
+<!-- smt.full <- xtable(smt.table, -->
+<!--                    caption='Short-Term Preference Analysis: Disaggregated\n') -->
+<!-- align(smt.full) <- 'll|rrr|rrr|rrr' -->
+<!-- print(smt.full,  -->
+<!--        include.rownames=FALSE,  -->
+<!--        hline.after=c(-1,0,1,6,7,7), -->
+<!--                    caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ## Explaining Preference -->
+
+<!-- The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually  more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
 This proportion, however, varied by location and property type.
@@
 To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
-
-We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of:
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon
-\end{equation}
-
-where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
-
-For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon
-\end{equation}
-
-Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts:
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt +
-\beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon
-\end{equation}
-
-where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
+-->
+
+<!-- We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of: -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon -->
+<!-- \end{equation} -->
+
+<!-- where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+-->
+
+<!-- For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.  -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon -->
+<!-- \end{equation} -->
+
+<!-- Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts: -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + -->
+<!-- \beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon -->
+<!-- \end{equation} -->
+
+<!-- where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
 We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
 We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).
-
-The results of all three models are shown in Table 7.
+-->
+
+<!-- The results of all three models are shown in Table 7.
 For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
-
-In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
+-->
+
+<!-- In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
 Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference.
-
-Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
+-->
+
+<!-- Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
 These findings mirror those found above in Table 9.
 The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
-
-Finally, in Model 3 we add in host behavior or policies.
+-->
+
+<!-- Finally, in Model 3 we add in host behavior or policies.
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
@@
 Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.
-
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
-
- names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
- x.full <- xtable(full.table,
-                  caption='Logistic Modeling Results\n')
- align(x.full) <- 'lllll'
-
- print(x.full, 
-       include.rownames=FALSE, 
-       hline.after=c(-1,0,15,20,20), 
-       caption.placement='top')
-
-```
-
-\pagebreak
-
-## Discussion
-
-<!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+-->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'} -->
+
+<!--  names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
+<!--  x.full <- xtable(full.table, -->
+<!--                   caption='Logistic Modeling Results\n') -->
+<!--  align(x.full) <- 'lllll' -->
+
+<!--  print(x.full,  -->
+<!--        include.rownames=FALSE,  -->
+<!--        hline.after=c(-1,0,15,20,20),  -->
+<!--        caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ## Discussion -->
+
+<!-- <!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
 This work attempts to fill this void.
--->
-
-The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
+--> -->
+
+<!-- The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
 However, of this total, only 6,600 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
@@
 We caution future researchers and policy analysts to look deeply at initial estimates of Airbnb counts as many of the listings on the market are either room shares and/or not active.
-
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
+-->
+
+<!-- Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
 However, there is long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, on Airbnb than they would on the long-term market.
@@
 Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
-
-To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
+-->
+
+<!-- To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
 The shared information that is available on both sets of properties is limited.
@@
 As a result, we were not able to accurately estimate likely short-term rates for the long-term observations.
-
-In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
+-->
+
+<!-- In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
 As expected, this probability is not equal across space, property type or property size (bed and bath count).
@@
 Examining only apartments with at least three bedrooms and two baths that figure increases to 60\%.
-
-The nightly rates and total occupancies drive the profitability of short-term leasing.
+-->
+
+<!-- The nightly rates and total occupancies drive the profitability of short-term leasing.
 As the nightly rate vs.
@@
 In Melbourne summers this may be an easy feat as tourist numbers swell, but doing so on a cold week in July likely proves more difficult.
-
-The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
+-->
+
+<!-- The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
 Large apartments in the central city are the best bet for generating greater revenues through short term leasing.
@@
 As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
-
-### Limitations and Future Research
-
-There are a number of limitations to this research.
+-->
+
+<!-- ### Limitations and Future Research -->
+
+<!-- There are a number of limitations to this research.
 There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
@@
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
-
-Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
+-->
+
+<!-- Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
 Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
-
-In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
+-->
+
+<!-- In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
 We have done so as we were unable to location any evidence to suggest that one was higher than the other.
 This may be a limitation of our study and could prove to be an avenue of future research.
-
-Beyond airBNB.com other short-term platforms exist (e.g.
+-->
+
+<!-- Beyond airBNB.com other short-term platforms exist (e.g.
 www.homeaway.com).
@@
 These are additional revenue streams that are not take into account and might increase the occupancy and revenue for short-term rentals.
-
-Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
+-->
+
+<!-- Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
 In reality, the possibilities may not be so rigid.
@@
 We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
+-->
 

### 2017-02-16 abbDataAnalysis_Script.Rmd
prepare for the analysis object export

@@
                       data=str.data.ic)
+
+  pref.models <- list(mod.ext.str, mod.ext.loc, mod.ext.host, 
+                      mod.pot.str, mod.pot.loc, mod.pot.host)
+  names(pref.models) <- c('ext.str', 'ext.loc', 'ext.host',
+                          'pot.str', 'pot.loc', 'pot.host')
+
 ```
@@
 
-  mod.ext.str <- lm(str.ext.prem~type+as.factor(bedbath),
+  mod.ext.str.prem <- lm(str.ext.prem~type+as.factor(bedbath),
                     data=str.data.ic)
-  mod.pot.str <- lm(str.pot.prem~type+as.factor(bedbath),
+  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
+                    data=str.data.ic)
+
+  mod.ext.loc.prem <- glm(str.ext.pref~type+as.factor(bedbath)+
+                                  sub.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
+                                  sub.mrkt,
+                     family=binomial(link='logit'),
                      data=str.data.ic)
@@
                       data=str.data.ic)
+
+    prem.models <- list(mod.ext.str.prem, mod.ext.loc.prem, mod.ext.host.prem, 
+                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
+    names(prem.models) <- c('ext.str', 'ext.loc', 'ext.host',
+                          'pot.str', 'pot.loc', 'pot.host')
+
 ```
@@
 
-  mod.ext.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
+  mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                     sub.mrkt+
@@
 
-  mod.ext.os <- glm(str.pot.pref~type+as.factor(bedbath)+
+  mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                     sub.mrkt+
@@
 
-  mod.ext.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
+  mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                     sub.mrkt+
@@
 
-  mod.ext.un <- glm(str.pot.pref~type+as.factor(bedbath)+
+  mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                     sub.mrkt+
@@
                  data=str.data.ic[un,])
+
+  mod.ext.ps <- glm(str.ext.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[ps,])
+
+  mod.ext.os <- glm(str.ext.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[os,])
+
+  mod.ext.mu <- glm(str.ext.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[mu,])
+
+  mod.ext.un <- glm(str.ext.pref~type+as.factor(bedbath)+
+                    sub.mrkt+
+                    I(max.guests/bedrooms)+min.stay+
+                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                 family=binomial(link='logit'),
+                 data=str.data.ic[un,])
+
+host.models <- list(mod.ext.ps, mod.ext.os, mod.ext.mu, mod.ext.un,
+                    mod.pot.ps, mod.pot.os, mod.pot.mu, mod.pot.un)
+names(host.models) <- c('ext.ps', 'ext.os', 'ext.mu', 'ext.un',
+                        'pot.ps', 'pot.os', 'pot.mu', 'pot.un')
 
@@
                         x.names)
+all.mwl.coefs <- list(pra.coef, era.coef, prp.coef, pro.coef, prm.coef, pru.coef,
+                  erp.coef, ero.coef, erm.coef, eru.coef)
+names(all.mwl.coefs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru', 
+                          'erp', 'ero', 'erm', 'eru')
+
 ```
@@
                           est.points)
+all.mwl.surfs <- list(pra.surfs, era.surfs, prp.surfs, pro.surfs, prm.surfs, pru.surfs,
+                      erp.surfs, ero.surfs, erm.surfs, eru.surfs)
+names(all.mwl.surfs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru',
+                          'erp', 'ero', 'erm', 'eru')
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+save(clean.count, daily.data, listing.data, ltr.data, pref.table, pref.table.wide,
+     s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,
+     core.suburbs, est.points, exch.rate, host.models, pref.models, prem.models,
+     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))
 

### 2017-02-16 abb_Writeup.Rmd
rewrite of data and method

@@
     - \usepackage{setspace}\doublespacing
-date: "January 14, 2017"
+date: "February 17, 2017"
 output:
@@
 
-<!-- ## Method -->
-
-<!-- We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
-More specifically, we examine the following case: -->
-
-<!-- * An investor purchases a property in Melbourne on Sept 1, 2015. -->
-<!-- * They are looking to maximize the revenue over the 12-month period from September 1, 2015 to August 31, 2016. -->
-<!-- * The choices are 1) traditional year long rental (long term), or: 2) short-term, Airbnb type rental. -->
-<!-- * Only direct monetary revenues and costs are considered, others such as liquidity and inconvience are not considered.   -->
-
-<!-- We will not, a priori, specify a location or property type as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
-Additionally, Australia implements a particular tax policy, often termed `negative gearing', that does allow for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.]  However, as the negative gearing policy requires knowledge of the investor's personal income situation, we will not be considering any effects of this policy in our analysis here.
--->
-
-<!-- One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
+## Method
+
+We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+More specifically, we examine the following case:
+
+* An investor purchases a property in Melbourne, Australia on September 1, 2015.
+* They are looking to maximize the net revenue over the 12-month period from September 1, 2015 to August 31, 2016.
+* The choices are 1) traditional year long rental (long term), or: 2) short-term, nightly Airbnb-type rental.
+* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are not considered.
+* As most long-term rental use a leasing agency, we will assume use of an agency.
+
+We will not, a priori, specify a location or property type for the scenario as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
+The extent to which location, property type and property characteristics impact the probabilit of short-term preference are examined in the results section.
+
+Australia implements a particular tax policy, often termed `negative gearing', that allows for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
+While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
+As we do not have access to this information in the marketplace, we will not be considering any effects of this policy in our analysis here.
+
+One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
 As future market trends are unknown at the time of purchase and the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
-Both long- term rents and short-term rates and occupancy structures will be baesd on the market conditions as of this date.
--->
-
-<!-- We do not directly observe properties that are utilized in both a short and long term leasing strategy.
+Both long-term rents and short-term rates and occupancy structures will be based on the market conditions as of this date.
+
+We do not directly observe properties that are utilized in both a short- and long-term leasing strategy.
 Therefore, comparisons are done based on estimated or imputed revenues.
-Most specifically, we will estimate short-term revenue for observations of long-term rentals (LTRs) and long-term revenue for observations of short-term rentals (STRs).
-A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.
--->
-
-<!-- ### Comparison -->
-
-<!-- In this above scenario we compare the 12-month revenues from the a long-term rental with those of a short-term rental.
-We define returns here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
--->
-
-<!-- \begin{equation} -->
-<!-- Rev_{LT} = RevG_{LT} - C_{LT} -->
-<!-- \end{equation} -->
-
-<!-- \begin{equation} -->
-<!-- Rev_{ST} = RevG_{ST} - C_{ST} -->
-<!-- \end{equation} -->
-
-<!-- Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the costs associated with long-term rental.
-The gross long-term revenue is expressed by:  -->
-
-<!-- \begin{equation} -->
-<!-- RevG_{LT} = Rent_{M} * (12 - C_{S}) -->
-<!-- \end{equation} -->
-
-<!-- where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant. -->
-
-<!-- The short-term revenue is expresse by: -->
-
-<!-- \begin{equation} -->
-<!-- RevG_{ST} = Rate_{N} * O_{Total} -->
-<!-- \end{equation} -->
-
-<!-- where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. -->
-
-<!-- We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
-Broadly speaking, these fall into three categories for long-term rental and four categories for short-term properties.
-Long-term costs are summarized as: -->
-
-<!-- \begin{equation} -->
-<!-- C_{LT} = T + M + F -->
-<!-- \end{equation} -->
-
-<!-- where $T$ are tax related expenses, $M$ are general maintenance expenses and $F$ are finaning costs.
-Short-term properies experience the same three costs ($T$, $M$ and $F$) plus additional janitorial costs between each of the short-term occupants.
--->
-
-<!-- \begin{equation} -->
-<!-- C_{ST} = T + M + F + J -->
-<!-- \end{equation} -->
-
-<!-- As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
+Most specifically, we will estimate the long-term revenue for observations of properties currently listed on a short-term rental portal (Airbnb).
+Initially, we attempted to also estimate short-term rental revenue for long-term properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
+
+### Comparison
+
+In this scenario we compare the observed 12-month revenues from short-term rental properties with their hypothetical long-term rental revenues.
+We define revenue here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
+Costs which are equivalent between the two strategies are ignored.
+
+\begin{equation}
+Rev_{ST} = RevG_{ST} - C_{ST}
+\end{equation}
+
+The gross short-term revenue is expressed by:
+
+\begin{equation}
+RevG_{ST} = Rate_{N} * O_{Total}
+\end{equation}
+
+where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. For long-term revenues:
+
+\begin{equation}
+Rev_{LT} = RevG_{LT} - C_{LT}
+\end{equation}
+
+Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the specific costs associated with long-term rental.
+The gross long-term revenue is expressed by:
+
+\begin{equation}
+RevG_{LT} = Rent_{M} * (12 - C_{S})
+\end{equation}
+
+where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+
+We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
+Broadly speaking, these fall into four categories long-term rental and five for short-term properties.
+Long-term costs are summarized as:
+
+\begin{equation}
+C_{LT} = T + M + F + L
+\end{equation}
+
+where $T$ are tax related expenses, $M$ are general maintenance expenses, $F$ are financing costs and $L$ are leasing agency fees.
+Short-term properies experience three of the same costs ($T$, $M$ and $F$) plus additional janitorial costs $J$ between each of the short-term occupants as well as property utility costs, $U$ over the course of the year.
+
+\begin{equation}
+C_{ST} = T + M + F + J + U
+\end{equation}
+
+As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
 General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
-Long-term renters spend more time in the property over the course of the year and bring their own appliance and furniture which may damage the home.
+Long-term renters spend more time in the property over the course of the year and bring their own appliances^[White goods are usually not supplied in the Australian rental market.] and furniture which may damage the home.
 They are also more likely to affix items to the structure.
@@
 As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
--->
-
-<!-- Finally, we have janitorial costs $J$.
-These cover the costs to 'turn-over' the property between occupants.
-For a short-term leasing strategy, these costs can be experiences every day or two, depending on the minimum length of stay and the total number of occupancies over the course of the year.
+
+Leasing costs $L$ are the fees paid to the rental agency to find and manage tenants over the life of the lease.
+In Melbourne, rates generally range from 5\% to 7\% per annum.
+We have assumed leasing costs of 6\% of the total gross revenue of the long-term lease contract.
+
+Janitorial costs, $J$, cover the costs to 'turn-over' the property between occupants.
+For a short-term leasing strategy, these costs can be experienced every day or two, depending on the minimum length of stay and the total number of occupancies over the course of the year.
 Our data for short-term rentals comes from the Airbnb platform.
-In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.
+In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay].
 Some hosts add additional 'linen' fees to cover costs of laundering.
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
-As a result of janitorial fees being a separate line item and directly paid by the occupants can also be ignored in the comparative analysis below as they are direct.
--->
-
-<!-- Given that the costs cancel out between the two options, we will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds: -->
-
-<!-- \begin{equation} -->
-<!-- RevG_{ST} > RevG_{LT}  -->
-<!-- \end{equation} -->
-
-<!-- More specifically, if: -->
-
-<!-- \begin{equation} -->
-<!-- Rate_{N} * O_{Total} > Rent_{M} * (12 - C_{S}) -->
-<!-- \end{equation} -->
-
-<!-- ## Data -->
-
-<!-- Data for this studies were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
+As a result of janitorial fees being a separate line item and directly paid by the occupants they can also be ignored in the comparative analysis below as they are direct.
+
+Finally, there are utility costs, $U$, that are borne by the property owner in a short-term leasing strategy but by the tenant in a long-term option.
+The State of Victoria estimates energy costs for an apartment at A\$330 per month and for a larger house at A\$520 per month.
+For two people in an apartment the cost is approximately A\$5 per person per day and for a four person household in a detached house the cost is around A\$4 per person per day person.
+For the purposes of estimating utility costs for the short-term rentals we use a mid-point value of A\$4.50 per person per day.
+As we don't know total number of guests in each reservation we use a figure of 1.7 guests per bedroom and sum up the total costs for all bookings over the year.
+
+\begin{equation}
+U = (4.5 * B * 1.7) * O
+\end{equation}
+
+We will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
+
+\begin{equation}
+Rev_{ST} > Rev_{LT}
+\end{equation}
+
+More specifically, if:
+
+\begin{equation}
+(Rate_{N} * O_{Total}) - U > (Rent_{M} * (12 - C_{S})) - L
+\end{equation}
+
+## Data
+
+Data for this study were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
 Short-term rental market observations are from the Airbnb online portal.
 Airbnb is the largest short-term rental hub in the Melbourne region.
-As opposed to similar sites such as VRBO.com and homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
-The data on the AirBNB market in Melbourne have been purchased from www.airdna.co, a data provider specializing in AirBNB data collection and analysis.
-The short term data include two types of observations, property level and nightly.
+As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
+The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
+The short-term data include two types of observations, property level and nightly.
 Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
-These data indicate the advertised price, the occupancy status and a unique reservation identification (useful for determining the length of stay).
--->
-
-<!-- The Airbnb data cover the Melbourne metropolitan region from October 1st, 2014 to August 30th, 2016.
+These nightly data indicate the advertised price, the occupancy status and a unique reservation identification.
+
+The Airbnb data cover the Melbourne metropolitan region from October 1st, 2014 to August 30th, 2016.
 There are missing nightly observations during the time period before September 1, 2015.
@@
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
--->
-
-<!-- The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
+
+The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
 In raw form, this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
@@
 As such, the first dataset is a set of market observations with associated characteristics and the second is a listing history of each rental event.
-The long-term lease data covers the period from January 2014 to December 2015.
--->
-
-<!-- Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
+The long-term lease data cover the period from January 2014 to December 2015.
+
+Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
 Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
 As a result of this, we are unable to directly match observations from the two datasets.
-However, the number of properties that rented long term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
--->
-
-<!-- ```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'} -->
-
-<!--   exch.rate <- 1.32 -->
-
-<!-- ``` -->
-
-<!-- ### Preparation -->
-
-<!-- In this section we describe the operations that we have performed to prepare the two sets of raw data for analysis.
+However, the number of properties that rented long-term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  exch.rate <- 1.32
+
+```
+
+### Preparation
+
+Here we describe the operations that we have performed to prepare the two sets of raw data for analysis.
 Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions.
 Additionally, as our data are from two different sources, a number of fields also require standardization so that comparisons between the two leasing strategy options  -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
--->
-
-<!-- We begin by filtering observations by time.
+
+We begin by filtering observations by time.
 Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an AirBNB-type, short-term rental approach to generating income.
@@
 In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
--->
-
-<!-- Next, we filter the data based on property types.
+
+Next, we filter the data based on property types.
 AirBNB units are classified into 19 different property types.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types: -->
-
-<!-- 1. **House**:  Includes properties labeled 'House' or 'Townhouse' -->
-<!-- 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium' -->
-<!-- 3.
+For the sake of this analysis, we will collapse these twenty types into three types:
+
+1. **House**:  Includes properties labeled 'House' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
+3.
 **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
--->
-
-<!-- Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories: -->
-
-<!-- 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse' -->
-<!-- 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio' -->
-<!-- 3. **Other**: Includes properties labeled as 'Semi' and 'Villa' -->
-
-<!-- Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
+
+Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+
+1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
+3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+
+Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
 This is most apparent when talking about apartment dwellings.
-In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure)^[Also note that 'Apartment-type' ownership is very rare in Australia.
+In Australia these are referred to as Units or Studios, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure)^[Also note that 'Apartment-type' ownership is very rare in Australia.
 Nearly every multi-family dwelling is owned as a condominium.
@@
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
--->
-
-<!-- The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
+
+The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
 Additionally, a large proportion of the **Others** in the short-term data are Bed & Breakfast units, a use which doesn't fit with our research question.
 As a result, we remove the 'Others' from both the short- and the long-term rental data.
--->
-
-<!-- ```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'} -->
-<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
-<!--   load(paste0(data.path, '/analyzed/abb_beforePT.RData')) -->
-<!--   abb.data1 <- before.PT$abb.data -->
-<!--   ltr.data1 <- before.PT$ltr.data -->
-
-<!-- ``` -->
+
+```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+  data.path <- 'c:/dropbox/research/airBNB/data/'
+  load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
+```
 

### 2017-02-17 abbDataPrep_Script.Rmd
outputting figures as rdata

@@
 
+  save(str.types, file=paste0(fig.path, 'strtypes.RData'))
+  save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))
+
 ```
@@
 
-  # Make Plot
-  png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    ggplot(str.data, aes(x=listing.type)) + 
+  list.types <- ggplot(str.data, aes(x=listing.type)) + 
       geom_bar(color=str.col, fill=str.col) +
@@
 
+  # Make Plot
+  png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    list.types
+
   dev.off()
+
+  save(list.types, file=paste0(fig.path, 'listtypes.RData'))
 
@@
 
+  save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
+  save(strbed, file=paste0(fig.path, 'strbed.RData'))
+
 ```
@@
 
+  save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
+  save(stbath, file=paste0(fig.path, 'strbath.RData'))
+
 ```
@@
   dev.off()
+
+  save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
+  save(stbb, file=paste0(fig.path, 'strbb.RData'))
 
@@
   dev.off()
+
+  save(ltr.plot, file=paste0(fig.path, 'rentplot.RData'))
+  save(rate.plot, file=paste0(fig.path, 'rateplot.RData'))
 
@@
 
+  save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
+
 ```
@@
 
+  save(str.map, file=paste0(fig.path, 'strMap.RData'))
+  save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
+
 ```
@@
 
+  save(strtype.map, file=paste0(fig.path, 'strsubplot.RData'))
+  save(ltrtype.map, file=paste0(fig.path, 'ltrsubplot.RData'))
+
 ```

### 2017-02-17 abb_Writeup.Rmd
dc prop and list  type review

@@
 Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions.
-Additionally, as our data are from two different sources, a number of fields also require standardization so that comparisons between the two leasing strategy options  -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
+Additionally, as our data are from two different sources, a number of fields require standardization so that comparisons between the two leasing strategy options -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
 
@@
 
-```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
   data.path <- 'c:/dropbox/research/airBNB/data/'
@@
 
-<!-- ```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'} -->
-
-<!--   # Create Airbnb plot -->
-
-<!--   abb.types <- ggplot(abb.data1, aes(x=type)) + -->
-<!--     geom_bar(color=str.col, fill=str.col) + -->
-<!--     xlab('') + -->
-<!--     ylab('# of Properties\n') + -->
-<!--     labs(title = "Short Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Create long term rental plot -->
-
-<!--   ltr.types <- ggplot(ltr.data1, aes(x=type)) + -->
-<!--     geom_bar(color=ltr.col, fill=ltr.col) + -->
-<!--     xlab('') + -->
-<!--     ylab('# of Properties\n') + -->
-<!--     labs(title = "Long Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Output plots -->
-
-<!--   ggMultiPlots(abb.types, ltr.types, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   abb.data1 <- subset(abb.data1, type != 'Other') -->
-<!--   ltr.data1 <- subset(ltr.data1, type != 'Other') -->
-
-<!-- ``` -->
-
-<!-- Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked: -->
-
-<!-- 1. **Entire Home/Apt**: The entire home or apartment is available -->
-<!-- 2. **Private Room**: One room within a house or apartment is available -->
-<!-- 3. **Shared Room**: A bed within a room shared by another occupant(s) is available -->
-
-<!-- As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
+```{r load_ptplot, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
+
+  load(paste0(fig.path, 'ltrtypes.RData'))
+  load(paste0(fig.path, 'strtypes.RData'))
+
+  ggMultiPlots(str.types, ltr.types, cols=2)
+
+```
+
+Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+
+1. **Entire Home/Apt**: The entire home or apartment is available
+2. **Private Room**: One room within a house or apartment is available
+3. **Shared Room**: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
 Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable.
--->
-
-<!-- ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'} -->
-
-<!--   # Fix data types and names -->
-
-<!--   abb.data1$listing.type <- as.character(abb.data1$listing.type) -->
-<!--   abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home' -->
-
-<!--   # Make Plot -->
-
-<!--   ggplot(abb.data1, aes(x=listing.type)) + -->
-<!--     geom_bar(color=abb.col[1], fill=abb.col[1]) + -->
-<!--     xlab('') + -->
-<!--     ylab('# of Properties\n') + -->
-<!--     labs(title = "Short Term Rentals \nby Listing Type\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!-- ``` -->
-
-<!-- ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ] -->
-
-<!-- ``` -->
+
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}
+
+ load(paste0(fig.path, 'listtypes.RData'))
+
+ list.types
+
+```
 

### 2017-02-17 abb_Writeup.Rmd
Updating dc str char

@@
 
-<!-- #### Structural Characteristics -->
-
-<!-- We now turn to filtering by structural characteristics.
+#### Structural Characteristics
+
+We now turn to filtering by structural characteristics.
 As the Airbnb data provides limited information on the structural characteristics, the only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
-Additionally, as the markets and structural components of houses and apartment differ, we bifurcate our analysis between the two property types from this point forward.
--->
-
-<!-- We begin by removing all properties that are missing bedroom information or have a likely data error in this fields (more than 14 bedrooms).
-For both short and long term rentals we see that most apartments have less than four bedrooms and houses less than five (Figure 3).
+Additionally, as the markets and structural components of houses and apartments differ, we bifurcate our analysis between the two property types from this point forward.
+
+We begin by removing all properties that are missing bedroom or bathroom information or have a likely data error in this fields (more than 14 bedrooms or 10 bathrooms).
+For both short and long term rentals we find that most apartments have fewer than four bedrooms and houses fewer than five.
+For both property types, the vast majority of properties have three or fewer bathrooms.
 We filter the data accordingly.
@@
 We convert the 0 bed short term units to 1 bed units.
--->
-
-<!-- ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Remove missing and data errors -->
-
-<!--   # Long term data -->
-<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$bedrooms), ] -->
-<!--   ltr.data1 <- ltr.data1[ltr.data1$bedrooms <= 10, ] -->
-
-<!--   # Short term data -->
-<!--   abb.data1 <- abb.data1[!is.na(abb.data1$bedrooms), ] -->
-<!--   abb.data1 <- abb.data1[abb.data1$bedrooms <= 10, ] -->
-
-<!-- ``` -->
-
-<!-- ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bedrooms by Tenure & Property Type'} -->
-
-<!--  # Build long term bar plot -->
-
-<!--    ltrbed <- ggplot(ltr.data1, aes(x=bedrooms)) + -->
-<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     scale_x_continuous(labels=1:10, breaks=1:10)+ -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bedrooms in Long Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  # Build short term bar plot -->
-
-<!--   abbbed <- ggplot(abb.data1, aes(x=bedrooms)) + -->
-<!--     geom_bar(fill=str.col, color=str.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     scale_x_continuous(labels=0:10, breaks=0:10)+ -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bedrooms in Short Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  # Make the comparison plot -->
-
-<!--   ggMultiPlots(abbbed, ltrbed, cols=1) -->
-
-<!-- ``` -->
-
-<!-- ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Remove all with more than 4 beds -->
-
-<!--   abb.data1 <- abb.data1[abb.data1$bedrooms < 5, ] -->
-<!--   ltr.data1 <- ltr.data1[ltr.data1$bedrooms < 5, ] -->
-
-<!--  # Remove apartments with more than 3 -->
-
-<!--   abba <- which(abb.data1$bedrooms > 3 & abb.data1$type =='Apartment') -->
-<!--   ltra <- which(ltr.data1$bedrooms > 3 & ltr.data1$type =='Apartment') -->
-
-<!--   if(length(abba) > 0) abb.data1 <- abb.data1[-abba, ] -->
-<!--   if(length(ltra) > 0) ltr.data1 <- ltr.data1[-ltra, ] -->
-
-<!--   # Convert 0 Bed to 1 Bed -->
-<!--   abb.data1$bedrooms[abb.data1$bedrooms == 0] <- 1 -->
-
-<!-- ``` -->
-
-<!-- We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apartment/house.
-Here we see that nearly all properties have three or fewer bathrooms and we filter the data accordingly (Figure 4).
 A few short term properties indicate no baths, which is likely an error so we remove these observations from the data.
@@
 We round the baths in the short term data up to whole integers.
--->
-
-<!-- ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Remove missing data -->
-
-<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$baths), ] -->
-<!--   abb.data1 <- abb.data1[!is.na(abb.data1$baths), ] -->
-
-<!-- ``` -->
-
-<!-- ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bathrooms by Tenure & Property Type'} -->
-
-<!--  # Build long term plot -->
-
-<!--   ltbath <- ggplot(ltr.data1, aes(x=baths)) + -->
-<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     scale_x_continuous(labels=1:8, breaks=1:8)+ -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bathrooms in Long Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  # Build short term plot -->
-
-<!--   stbath <- ggplot(abb.data1, aes(x=baths)) + -->
-<!--     geom_bar(fill=str.col, color=str.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     scale_x_continuous(labels=0:8, breaks=0:8)+ -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bathrooms in Short Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  # Make Plots -->
-
-<!--   ggMultiPlots(stbath, ltbath, cols=1) -->
-
-<!-- ``` -->
-
-<!-- ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Filter by bath count -->
-
-<!--   # Short term data -->
-<!--   abb.data1 <- abb.data1[abb.data1$baths < 4, ] -->
-<!--   abb.data1 <- abb.data1[abb.data1$baths > 0, ] -->
-
-<!--   # Long term data -->
-<!--   ltr.data1 <- ltr.data1[ltr.data1$baths < 4, ] -->
-
-<!--  # Round baths up -->
-
-<!--   abb.data1$baths <- round(abb.data1$baths + .01, 0) -->
-
-<!-- ``` -->
-
-<!-- In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+
+In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
 In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two (Figure 5).
+As a result we examine the combinations of the two (Figure 3).
 From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
 We filter the data to these combinations.
--->
-
-<!-- ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Create combination variable -->
-
-<!--   ltr.data1$bedbath <- paste0(ltr.data1$bedrooms, '..', ltr.data1$baths) -->
-<!--   abb.data1$bedbath <- paste0(abb.data1$bedrooms, '..', abb.data1$baths) -->
-
-<!-- ``` -->
-
-<!-- ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Bed/Bath Combo by Tenure & Property Type'} -->
-
-<!--  # Make long term plot -->
-
-<!--   ltb <- ggplot(ltr.data1, aes(x=bedbath)) + -->
-<!--     geom_bar(fill=ltr.col, color=ltr.col) + -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bed/Bath Combo in Long Term Rentals\n") + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
-<!--     facet_wrap(~type) -->
-
-<!--  # Make short term plots -->
-
-<!--   stb <- ggplot(abb.data1, aes(x=bedbath)) + -->
-<!--     geom_bar(fill=str.col, color=str.col) + -->
-<!--     xlab('') + -->
-<!--     ylab('# of Props\n') + -->
-<!--     labs(title = "Bed/Bath Combo in Short Term Rentals\n") + -->
-<!--     scale_y_continuous(breaks=c(1000, 3000, 5000)) + -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust=0.4)) + -->
-<!--     facet_wrap(~type) -->
-
-<!--  # Plot -->
-
-<!--   ggMultiPlots(ltb, stb, cols=1) -->
-
-<!-- ``` -->
-
-<!-- ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  # Set level of acceptable combinations -->
-
-<!--   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2') -->
-
-<!--  # Filter data -->
-
-<!--   ltr.data1 <- ltr.data1[ltr.data1$bedbath %in% acc.bb, ] -->
-<!--   abb.data1 <- abb.data1[abb.data1$bedbath %in% acc.bb, ] -->
-
-<!-- ``` -->
-
-<!-- ### Rates and Rental values -->
+
+```{r bb_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type'}
+
+ load(paste0(fig.path, 'ltrbb.RData'))
+ load(paste0(fig.path, 'strbb.RData'))
+
+ stbb <- stbb + ylab('# of Obs')
+ ltbb <- ltbb + ylab('# of Obs')
+
+ ggMultiPlots(stbb, ltbb)
+
+```
+
+### Rates and Rental values
 

### 2017-02-18 abbDataPrep_Script.Rmd
re-org of median rates, etc.

@@
                          str.data$min.date <= '2016-03-01', ]
+
   daily.data <- daily.data[daily.data$date >= '2015-09-01', ]
@@
   daily.data$price <- daily.data$price * exch.rate
+
+```
+
+Next we extract all of the daily reservation data that fits our criteria -- reserved and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data from the data source.
+We do this step to remove those].
+From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+
+From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
+We filter the data accordingly.
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Filter the long term data
+
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
+
+  # Get all of the reservations
+  resv.daily <- daily.data[daily.data$status == 'R' &
+                              daily.data$price < 500, ]
+
+  # Calculate the property specific median nightly rate
+  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
+
+  # Add median rate to the property  
+  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
+
+  # Remove those with no valid median rate
+  str.data <- str.data[!is.na(str.data$med.rate), ]
 
@@
 
-From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
-We filter the data accordingly.
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Filter the long term data
-
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
   str.data <- str.data[str.data$nightly.rate >= 50 &
-                         str.data$nightly.rate <= 500, ]
+                         str.data$med.rate <= 500, ]
 
@@
   countCleaning('rates.rents')
+
+```
+
+#### Observed Revenue
+
+Our final data filtering considers the observed revenue of the properties.
+For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
+In a number of extreme cases, time on market was extremely long and the total observed revenues very low.
+To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
+
+For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+Using this data we sum up the total revenue from bookings.
+For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
+
+Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
+Short term revenues range from neglible to highs of greater than \$80,000.
+While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
+Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
+
+```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
+
+ # Compute bookings count
+
+  str.data$bookings <- round(str.data$total.days * 
+                               (1 - (str.data$block.rate + str.data$avail.rate)), 0)
+
+ # Remove those with 0
+
+  str.data <- str.data[str.data$bookings > 0, ]
+
+  str.data$gross.revenue <- (str.data$bookings * str.data$med.rate) 
+  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
+
+  str.small <- str.data[,c('baths', 'gross.revenue')]
+  str.small$tenure <- 'short-term'
+  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
+  ltr.small$tenure <- 'long-term'
+  all.small <- rbind(str.small, ltr.small)
+
+  revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col)) +
+    ggtitle('Annual Revenues by Tenure Type') +
+    xlab('Annual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000))
+
+```
+
+```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
+      bg='transparent')
+
+    revdens
+
+  dev.off()
+
+  save(revdens, file=paste0(fig.path, 'revdens.RData'))
+
+  ltr.data <- ltr.data[ltr.data$gross.revenue > 10000, ]
 
@@
 
-  str.data$bookings <- round(str.data$total.days * (1 - (str.data$block.rate + str.data$avail.rate)), 0)
+  str.data$bookings <- round(str.data$total.days * 
+                               (1 - (str.data$block.rate + str.data$avail.rate)), 0)
 
@@
   str.data <- str.data[str.data$bookings > 0, ]
-
-```
-
-### Median rate
-
-Next we extract all of the daily reservation data that fits our criteria -- reserved and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data from the data source.
-We do this step to remove those].
-From this information we calculate the median nightly reservation price for each property and append it to the property level data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Get all of the reservations
-  resv.daily <- daily.data[daily.data$status == 'R' &
-                              daily.data$price < 500, ]
-
-  # Calculate the property specific median nightly rate
-  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-
-  # Add median rate to the property  
-  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
-
-  # Remove those with no valid median rate
-  str.data <- str.data[!is.na(str.data$med.rate), ]
-
-  ## Remove those with less than 180 observed days (missing obs)
-  str.data <- str.data[str.data$total.days >= 180, ]
 

### 2017-02-18 abb_Writeup.Rmd
rates discussion

@@
 
-<!-- Next we filter by the prices -- the nightly rates and weekly rental values.
+Next we filter by the prices -- the nightly rates and weekly rental values.
 The long term rental data have a single price observation, the asking rent at closing.
@@
 To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1, 2015 to August 31, 2016 period.
--->
-
-<!-- We start by removing property level observations missing price data.
-Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 6).
+
+We start by removing property level observations missing price data.
+Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 4).
 We filter the property level data accordingly.
 We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.
--->
-
-<!-- ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   ltr.data1 <- ltr.data1[!is.na(ltr.data1$event.price), ] -->
-<!--   abb.data1 <- abb.data1[!is.na(abb.data1$nightly.rate), ] -->
-
-<!-- ``` -->
-
-<!-- ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   # Property level data -->
-
-<!--   abb.data1$average.daily.rate <- abb.data1$average.daily.rate * exch.rate -->
-<!--   abb.data1$nightly.rate <- abb.data1$nightly.rate * exch.rate -->
-<!--   abb.data1$weekly.rate <- abb.data1$weekly.rate * exch.rate -->
-<!--   abb.data1$monthly.rate <- abb.data1$monthly * exch.rate -->
-
-<!--   # Daily data -->
-
-<!--   #daily.data$price <- daily.data$price * exch.rate -->
-
-<!-- ``` -->
-
-<!-- ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--   # ltr Plot -->
-
-<!--   ltr.plot <- ggplot(ltr.data1, aes(x=event.price)) + -->
-<!--     geom_density(fill=ltr.col, alpha=.8) + -->
-<!--     ylab('Frequency') + -->
-<!--     xlab('Weekly Rental') + -->
-<!--     ggtitle('Long Term Rentals') + -->
-<!--     scale_x_continuous(limits=c(0, 1500)) + -->
-<!--     theme(axis.title.y=element_blank(), -->
-<!--           axis.text.y=element_blank(), -->
-<!--           axis.ticks.y=element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Nightly Rate plot -->
-<!--   rate.plot <- ggplot(abb.data1, aes(x=nightly.rate)) + -->
-<!--     geom_density(fill=str.col, alpha=.8) + -->
-<!--     ylab('Frequency') + -->
-<!--     xlab('Nightly Rate') + -->
-<!--     ggtitle('Short Term Rentals') + -->
-<!--     scale_x_continuous(limits=c(0, 600)) + -->
-<!--     theme(axis.title.y=element_blank(), -->
-<!--           axis.text.y=element_blank(), -->
-<!--           axis.ticks.y=element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) -->
-
-<!-- ``` -->
-
-<!-- ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'} -->
-
-<!--   ggMultiPlots(ltr.plot, rate.plot, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--  ## Filter the long term data -->
-
-<!--   ltr.data1 <- ltr.data1[ltr.data1$event.price >= 200 & -->
-<!--                          ltr.data1$event.price <= 1000, ] -->
-
-<!--  ## Filter the short term data -->
-
-<!--   abb.data1 <- abb.data1[abb.data1$nightly.rate >= 50 & -->
-<!--                          abb.data1$nightly.rate <= 500, ] -->
-
-<!-- ``` -->
-
-<!-- ### Location and Submarkets -->
-
-<!-- Location is an important determinant in both the short- and long-term rental markets.
-At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
-Suburbs in Melbourne are much smaller than their North American counterparts.
-The specific suburb of a property is the second, or finer scale, at which the market operates.
-Figure 7 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
--->
-
-<!-- ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--  ## Build the map object -->
-
-<!--   # Set colors -->
-<!--   g.cols <- abb.col[c(2, 10, 9)] -->
-
-<!--   # Make map -->
-<!--   loc.map <- ggplot() + -->
-<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + -->
-<!--     scale_fill_manual(values=c('gray10', 'gray40', 'gray70'), -->
-<!--                       labels=c('Inner      ', -->
-<!--                                'Middle      ', -->
-<!--                                'Outer')) + -->
-<!--     geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) + -->
-<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
-<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
-<!--     xlab('') + ylab('')+ -->
-<!--     theme(legend.position = 'bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           panel.grid.major = element_blank(), -->
-<!--           panel.grid.minor = element_blank(), -->
-<!--           panel.background = element_rect(fill = "white"), -->
-<!--           axis.text.x = element_blank(), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks = element_blank(), -->
-<!--           axis.title.x=element_blank(), -->
-<!--           axis.title.y=element_blank(), -->
-<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
-<!--     ggtitle("Melbourne Suburb Classifications") -->
-
-<!-- ``` -->
-
-<!-- ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.width=5.5, fig.cap='Melbourne Suburb Classifications'} -->
-
-<!--   loc.map -->
-
-<!-- ``` -->
-
-<!-- ```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'} -->
-<!--   data.path <- 'c:/dropbox/research/airBNB/data/' -->
-<!--   load(paste0(data.path, '/analyzed/abb_afterSP.RData')) -->
-<!--   abb.data2 <- after.SP$abb.data -->
-<!--   ltr.data2 <- after.SP$ltr.data -->
-
-<!-- ``` -->
-
-<!-- It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
-While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne: -->
-
-<!-- 1. Rural (Outer suburbs, not Beach) -->
-<!-- 2. Suburban (Middle suburbs, not Beach) -->
-<!-- 3. City (Inner Suburbs, not Beach, not Core) -->
-<!-- 4. City-Core (Select inner suburbs with tourist activities and near CBD) -->
-<!-- 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River) -->
-
-<!-- We select the 18 suburbs below to represent the 'core' of the city (Table 1).
-The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenities for tourists.
--->
-
-<!-- ```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE} -->
-
-<!--  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands', -->
-<!--                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran', -->
-<!--                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda', -->
-<!--                    'St Kilda West', 'West Melbourne', 'Windsor') -->
-
-<!--  c.subs <- data.frame(A=core.suburbs[1:6], -->
-<!--                       B=core.suburbs[7:12], -->
-<!--                       C=core.suburbs[13:18]) -->
-<!--  names(c.subs) <- NULL -->
-<!--  rownames(c.subs) <- NULL -->
-
-<!--  print(xtable(c.subs, caption = 'List of Core Suburbs\n'), -->
-<!--        include.rownames=F, -->
-<!--        caption.placement="top", -->
-<!--        hline.after=c(0,6)) -->
-
-<!-- ``` -->
-
-<!-- We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short and long term rentals, colored by submarket, are shown in Figure 8.
--->
-
-<!-- Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
-For those without either set of lat/longs we remove them from the dataset at this point.
-After making this correction we then assign one of the five submarket designations based on the process described above.
--->
-
-<!-- ```{r abb.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   # Set submarket colors -->
-
-<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)] -->
-
-<!--   # Make map -->
-
-<!--   abb.map <- ggplot() + -->
-<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
-<!--     geom_point(data=abb.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2, -->
-<!--                alpha=.2) + -->
-<!--     scale_color_manual(values=sm.col) + -->
-<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
-<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
-<!--     theme(legend.position = 'bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           panel.grid.major = element_blank(), -->
-<!--           panel.grid.minor = element_blank(), -->
-<!--           panel.background = element_rect(fill = "white"), -->
-<!--           axis.text.x = element_blank(), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks = element_blank(), -->
-<!--           axis.title.x=element_blank(), -->
-<!--           axis.title.y=element_blank(), -->
-<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
-<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
-<!--                                                      alpha=1))) + -->
-<!--     ggtitle('AirBNB Location\nBy Submarket') -->
-
-<!-- ``` -->
-
-<!-- ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->
-
-<!--   # Make map -->
-
-<!--   ltr.map <- ggplot() + -->
-<!--     geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') + -->
-<!--     geom_point(data=ltr.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1, -->
-<!--                alpha=.1) + -->
-<!--     scale_color_manual(values=sm.col) + -->
-<!--     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) + -->
-<!--     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) + -->
-<!--     xlab('') + ylab('')+ -->
-<!--    theme(legend.position = 'bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           panel.grid.major = element_blank(), -->
-<!--           panel.grid.minor = element_blank(), -->
-<!--           panel.background = element_rect(fill = "white"), -->
-<!--           axis.text.x = element_blank(), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks = element_blank(), -->
-<!--           axis.title.x=element_blank(), -->
-<!--           axis.title.y=element_blank(), -->
-<!--           panel.border = element_rect(colour = "black", fill=NA, size=1)) + -->
-<!--     guides(colour = guide_legend(override.aes = list(size=3, -->
-<!--                                                      alpha=1))) + -->
-<!--     ggtitle('Long Term Rental Location\nBy Submarket') -->
-
-<!-- ``` -->
-
-<!-- ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'} -->
-
-<!--   ggMultiPlots(abb.map, ltr.map, cols=1) -->
-
-<!-- ``` -->
-
-<!-- To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (Figure 9).
-First, the vast majority of Airbnb units are apartments in city-core or city locations.
-As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
-Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
-Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
--->
-
-<!-- ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9} -->
-
-<!--   # Make Airbnb submarket map -->
-
-<!--   abbtype.map <- ggplot() + -->
-<!--     geom_bar(data=abb.data2, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
-<!--     scale_fill_manual(values=sm.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     ylab('# of Properties\n') + xlab('')+ -->
-<!--     theme(legend.position = 'bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           axis.text.x=element_blank(), -->
-<!--           axis.ticks.x=element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) + -->
-<!--     ggtitle('AirBNB Property Type By Submarket') -->
-
-<!--   # Make Long term rental map -->
-
-<!--   ltrtype.map <- ggplot() + -->
-<!--     geom_bar(data=ltr.data2, aes(x=sub.mrkt, fill=sub.mrkt)) + -->
-<!--     scale_fill_manual(values=sm.col) + -->
-<!--     facet_wrap(~type) + -->
-<!--     ylab('# of Properties\n') + xlab('')+ -->
-<!--     theme(legend.position = 'bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           axis.text.x=element_blank(), -->
-<!--           axis.ticks.x=element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) + -->
-<!--     ggtitle('Long Term Property Type By Submarket') -->
-
-<!-- ``` -->
-
-<!-- ```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=7, fig.cap='Observations by Submarket'} -->
-
-<!--   ggMultiPlots(abbtype.map, ltrtype.map, cols=1) -->
-
-<!-- ``` -->
-
-<!-- ### Observed Revenue -->
+
+```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Melbourne Suburb Classifications'}
+
+ load(paste0(fig.path, 'rateplot.RData'))
+ load(paste0(fig.path, 'rentplot.RData'))
+
+ ggMultiPlots(rate.plot, ltr.plot, cols=2)
+
+```
+
+<!-- #### Observed Revenue -->
 
@@
 <!-- ``` -->
+
+### Location and Submarkets
+
+Location is an important determinant in both the short- and long-term rental markets.
+At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+Suburbs in Melbourne are much smaller than their North American counterparts.
+The specific suburb of a property is the second, or finer scale, at which the market operates.
+Figure 5 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
+
+```{r locmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets'}
+
+ load(paste0(fig.path, 'suburbMap.RData'))
+
+ loc.map
+
+```
+
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenities for tourists.
+
+```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
+
+ c.subs <- data.frame(A=core.suburbs[1:6],
+                      B=core.suburbs[7:12],
+                      C=core.suburbs[13:18])
+ names(c.subs) <- NULL
+ rownames(c.subs) <- NULL
+
+ print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
+       include.rownames=F,
+       caption.placement="top",
+       hline.after=c(0,6))
+
+```
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+The location of the short and long term rentals, colored by submarket, are shown in Figure 6.
+
+Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
+For those without either set of lat/longs we remove them from the dataset at this point.
+After making this correction we then assign one of the five submarket designations based on the process described above.
+
+```{r loc.plots, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
+
+  load(paste0(fig.path, 'ltrMap.RData'))
+  load(paste0(fig.path, 'strMap.RData'))
+
+  ggMultiPlots(str.map, ltr.map, cols=1)
+
+```
+
+To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+A number of interesting observations are illustrated here (Figure 7).
+First, the vast majority of Airbnb units are apartments in city-core or city locations.
+As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
+Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
+Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
+Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
+
+```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Location Maps'}
+
+  load(paste0(fig.path, 'ltrsubplot.RData'))
+  load(paste0(fig.path, 'strsubplot.RData'))
+  ltrtype.map <- ltrtype.map + ylab("")
+
+  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
+
+```
 

### 2017-02-18 abbDataPrep_Script.Rmd
Fixed order of $500 cut

@@
 
-Next we extract all of the daily reservation data that fits our criteria -- reserved and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data from the data source.
-We do this step to remove those].
+Next we extract all of the daily reservation data for the reserved nightly.
 From this information we calculate the median nightly reservation price for each property and append it to the property level data.
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+   # Get all of the reservations
+  resv.daily <- daily.data[daily.data$status == 'R', ]
+
+  # Calculate the property specific median nightly rate
+  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
+
+  # Add median rate to the property  
+  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
+
+  # Remove those with no valid median rate
+  str.data <- str.data[!is.na(str.data$med.rate), ]
+
+```
 
@@
 We filter the data accordingly.
-
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Filter the long term data
-
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
-
-  # Get all of the reservations
-  resv.daily <- daily.data[daily.data$status == 'R' &
-                              daily.data$price < 500, ]
-
-  # Calculate the property specific median nightly rate
-  med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-
-  # Add median rate to the property  
-  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
-
-  # Remove those with no valid median rate
-  str.data <- str.data[!is.na(str.data$med.rate), ]
-
-```
 
@@
 
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- ## Filter the short term data
+```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  ## Filter the long term data
+
+  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
+                         ltr.data$event.price <= 1000, ]
 
@@
 
+    countCleaning('revenue')
+
 ```

### 2017-02-19 abbDataAnalysis_Script.Rmd
add figure writeouts

@@
 
-  # Calculate the actual revenue
-  ltr.data$ltr.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
-
-  # Remove those with very low revenues (due to very long DOMs)
-  ltr.data <- ltr.data[ltr.data$ltr.revenue > 10000, ]
-
-  countCleaning('revenue')
-
+  ltr.data$ltr.revenue <- ltr.data$gross.revenue
 ```
@@
 
-  ggplot(str.data, aes(x=block.rate)) + 
+  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
   geom_density(fill=str.col, color=str.col) +
@@
 
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.block.freq
+
+  dev.off()
+
+  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
+
 ```
@@
 
-  ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
   geom_point(fill=str.col, color=str.col, size=.2) +
-  ylab('Frequency\n') + 
+  ylab('Nbr of Blocked Periods\n') + 
   xlab('\n% of Time Property is Blocked') +
@@
                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Host Block Rate Frequency\n') +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    block.rate.period
+
+  dev.off()
+
+  block.rate.period
+
+  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
 
@@
 
-ggplot(str.data, 
+host.type <- ggplot(str.data, 
        aes(x=block.rate, y=blockpertime, color=host.type)) + 
-  geom_point(alpha=.5, size=.8, shape=15) +
-  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))
+  geom_point(alpha=.5, size=.8, shape=16) +
+  ylab('Number of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+
+  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
+  theme(legend.position='bottom',
+          legend.title = element_blank(),
+        plot.title = element_text(hjust = 0.5))+
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1)))
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type
+
+  dev.off()
+
+  host.type
+
+  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
 
@@
 
-ggplot(str.data, aes(host.type, fill=host.type)) +
+host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
   geom_bar() +
   scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-  theme(legend.position='none')
+  theme(legend.position='none') +
+  ylab('Frequency\n') + 
+  xlab('\nHost Type') +
+  ggtitle('Short Term Host Types') + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type.bar
+
+  dev.off()
+
+  host.type.bar
+
+  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
 

### 2017-02-27 abb_Writeup.Rmd
data cleaning text

@@
 
-We start by removing property level observations missing price data.
-Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 4).
+After removing property level observations that are missing price data, we plot the distribution of the rates and rents.
+In Figure 4 we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
 We filter the property level data accordingly.
@@
 
-```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Melbourne Suburb Classifications'}
+```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}
 
@@
 
+### Location and Submarkets
+
+Location is an important determinant in both the short- and long-term rental markets.
+At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+Suburbs in Melbourne are much smaller than their North American counterparts.
+The specific suburb of a property is the second, or finer scale, at which the market operates.
+Figure 5 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
+
+```{r locmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets'}
+
+ load(paste0(fig.path, 'suburbMap.RData'))
+
+ loc.map <- loc.map +     
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+ loc.map
+
+```
+
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenities for tourists.
+
+```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
+
+ c.subs <- data.frame(A=core.suburbs[1:6],
+                      B=core.suburbs[7:12],
+                      C=core.suburbs[13:18])
+ names(c.subs) <- NULL
+ rownames(c.subs) <- NULL
+
+ print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
+       include.rownames=F,
+       caption.placement="top",
+       hline.after=c(0,6))
+
+```
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+The location of the short and long term rentals, colored by submarket, are shown in Figure 6.
+
+Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
+To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
+For those without either set of lat/longs we remove them from the dataset at this point.
+After making this correction we then assign one of the five submarket designations based on the process described above.
+
+```{r loc.plots, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
+
+  load(paste0(fig.path, 'ltrMap.RData'))
+  load(paste0(fig.path, 'strMap.RData'))
+
+  str.map <- str.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+  ltr.map <- ltr.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+  ggMultiPlots(str.map, ltr.map, cols=1)
+
+```
+
+To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+A number of interesting observations are illustrated here (Figure 7).
+First, the vast majority of Airbnb units are apartments in city-core or city locations.
+As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
+Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
+Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
+Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
+
+```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts'}
+
+  load(paste0(fig.path, 'ltrsubplot.RData'))
+  load(paste0(fig.path, 'strsubplot.RData'))
+  ltrtype.map <- ltrtype.map + ylab("")
+
+  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
+
+```
+
+<!-- ### Summary of Data Cleaning -->
+
+<!-- We have applied nine separate filters to our two datasets.
+In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters (Table 2).
+There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
+Filtering those not listed during the study period removes 1/3 of all properties.
+Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
+From these 6,600 properties structural characteristics, locational issues and outlying nightly rates remove another 800 from consideration.
+Finally, 1,400 of these have never been booked and have \$0 revenue, requiring removal.
+From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
+-->
+
+<!-- For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+Further consideration regarding property types, structural characteristics, location, etc.
+remove another 10,000 observations, leaving 122,051 in the final dataset.
+-->
+
+```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
+
+cc <- clean.count[,c('operation', 'str', 'ltr')]
+str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
+ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
+str.cut <- c(0, str.count[-length(str.count)] - str.count[-1])
+str.per <- c(0, str.cut[-1] / str.count[-length(str.count)])
+ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
+ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
+clean.table <- data.frame(field=cc$operation,
+                          strcount=str.count,
+                          strcut=str.cut,
+                          strper=str.per,
+                          ltrcount=ltr.count,
+                          ltrcut=ltr.cut,
+                          ltrper=ltr.per)
+
+rownames(clean.table) <- NULL
+clean.table$field <- c('Initial Count', 'Time', 'Property Type',
+                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
+                       'Rates & Rents', 'Location', 'Revenue')
+clean.table$strper <- 100*round(clean.table$strper, 2)
+clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
+names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
+                        'Long Term', 'Cut', '% Cut')
+options(xtable.comment = FALSE)
+print(xtable(clean.table, caption='Data Cleaning Summary\n',
+       digits=0),
+       include.rownames=FALSE,
+       caption.placement='top')
+
+```
+
+<!-- ## Comparison -->
+
 <!-- #### Observed Revenue -->
 
-<!-- Our final data filtering considers the observed revenue of the properties.
-For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
+<!-- Our final data filtering considers the observed gross revenue of the properties.
+For the long-term rentals the observed gross revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
 In a number of extreme cases, time on market was extremely long and the total observed revenues very low.
-To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
+To remove these outlying observations, we filter out any properties with less than $10,000 in revenue.
 -->
@@
 
-<!-- ```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE} -->
-
-<!--  load(paste0(data.path, '/analyzed/abb_objs.RData')) -->
-
-<!-- ``` -->
-
 <!-- ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'} -->
 
-<!--   abbr <- abb.revs[,c('bedbath', 'revenue')] -->
-<!--   abbr$tenure <- 'short-term' -->
-<!--   ltrr <- ltr.revs[,c('bedbath', 'revenue')] -->
+<!--   strr <- str.data[,c('bedrooms', 'gross.revenue')] -->
+<!--   strr$tenure <- 'short-term' -->
+<!--   ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')] -->
 <!--   ltrr$tenure <- 'long-term' -->
-<!--   allr <- rbind(abbr, ltrr) -->
-
-<!--   ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--   allr <- rbind(strr, ltrr) -->
+
+<!--   ggplot(allr, aes(x=gross.revenue, fill=tenure, color=tenure)) + -->
 <!--     geom_density(alpha=.5) + -->
@@
 <!-- ``` -->
-
-### Location and Submarkets
-
-Location is an important determinant in both the short- and long-term rental markets.
-At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
-Suburbs in Melbourne are much smaller than their North American counterparts.
-The specific suburb of a property is the second, or finer scale, at which the market operates.
-Figure 5 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-```{r locmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets'}
-
- load(paste0(fig.path, 'suburbMap.RData'))
-
- loc.map
-
-```
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
-While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We select the 18 suburbs below to represent the 'core' of the city (Table 1).
-The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenities for tourists.
-
-```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
-
- c.subs <- data.frame(A=core.suburbs[1:6],
-                      B=core.suburbs[7:12],
-                      C=core.suburbs[13:18])
- names(c.subs) <- NULL
- rownames(c.subs) <- NULL
-
- print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
-       include.rownames=F,
-       caption.placement="top",
-       hline.after=c(0,6))
-
-```
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short and long term rentals, colored by submarket, are shown in Figure 6.
-
-Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
-For those without either set of lat/longs we remove them from the dataset at this point.
-After making this correction we then assign one of the five submarket designations based on the process described above.
-
-```{r loc.plots, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
-
-  load(paste0(fig.path, 'ltrMap.RData'))
-  load(paste0(fig.path, 'strMap.RData'))
-
-  ggMultiPlots(str.map, ltr.map, cols=1)
-
-```
-
-To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (Figure 7).
-First, the vast majority of Airbnb units are apartments in city-core or city locations.
-As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
-Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
-Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
-
-```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Location Maps'}
-
-  load(paste0(fig.path, 'ltrsubplot.RData'))
-  load(paste0(fig.path, 'strsubplot.RData'))
-  ltrtype.map <- ltrtype.map + ylab("")
-
-  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
-
-```
-
-<!-- ### Summary of Data Cleaning -->
-
-<!-- We have applied nine separate filters to our two datasets.
-In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters (Table 2).
-There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
-Filtering those not listed during the study period removes 1/3 of all properties.
-Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
-From these 6,600 properties structural characteristics, locational issues and outlying nightly rates remove another 800 from consideration.
-Finally, 1,400 of these have never been booked and have \$0 revenue, requiring removal.
-From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
--->
-
-<!-- For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
-Further consideration regarding property types, structural characteristics, location, etc.
-remove another 10,000 observations, leaving 122,051 in the final dataset.
--->
-
-<!-- ```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'} -->
-
-<!-- cc <- clean.count[,c('operation', 'abb', 'ltr')] -->
-<!-- abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1])) -->
-<!-- ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1])) -->
-<!-- abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1]) -->
-<!-- abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)]) -->
-<!-- ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1]) -->
-<!-- ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)]) -->
-<!-- clean.table <- data.frame(field=cc$operation, -->
-<!--                           abbcount=abb.count, -->
-<!--                           abbcut=abb.cut, -->
-<!--                           abbper=abb.per, -->
-<!--                           ltrcount=ltr.count, -->
-<!--                           ltrcut=ltr.cut, -->
-<!--                           ltrper=ltr.per) -->
-
-<!-- rownames(clean.table) <- NULL -->
-<!-- clean.table$field <- c('Initial Count', 'Time', 'Property Type', -->
-<!--                        'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo', -->
-<!--                        'Rates & Rents', 'Location', 'Revenue') -->
-<!-- clean.table$abbper <- 100*round(clean.table$abbper, 2) -->
-<!-- clean.table$ltrper <- 100*round(clean.table$ltrper, 2) -->
-<!-- names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut', -->
-<!--                         'Long Term', 'Cut', '% Cut') -->
-<!-- options(xtable.comment = FALSE) -->
-<!-- print(xtable(clean.table, caption='Data Cleaning Summary\n', -->
-<!--        digits=0), -->
-<!--        include.rownames=FALSE, -->
-<!--        caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- ## Comparison -->
 

### 2017-02-27 abbDataPrep_Script.Rmd
adding offline option

@@
 
+  offline <- TRUE
+
   # Get computer names
@@
  # Other custom files
+
+  if(offline){
+
+  source(paste0(code.path, '/dataVizTools/ggPlotTools.R'))
+  source(paste0(code.path, '/datamgmttools/dataMungeTools.R'))
+  source(paste0(code.path, '/spatialTools/spatialLogitModels.R'))
+  source(paste0(code.path, '/spatialTools/point2surface_Tools.R'))
+
+  } else {
 
@@
                 '/master/point2surface_Tools.R'))
+
+  }
 
@@
 
-  str.data <- str.data[str.data$nightly.rate >= 50 &
+  str.data <- str.data[str.data$med.rate >= 50 &
                          str.data$med.rate <= 500, ]
@@
 
-  ltr.data <- ltr.data[ltr.data$gross.revenue > 10000, ]
+  ltr.data <- ltr.data[ltr.data$dom <= 180, ]
 
@@
 
-Compute a full value of that total listing count
-
-```{r and.bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Compute bookings count
-
-  str.data$bookings <- round(str.data$total.days * 
-                               (1 - (str.data$block.rate + str.data$avail.rate)), 0)
-
- # Remove those with 0
-
-  str.data <- str.data[str.data$bookings > 0, ]
-
-```
-
 #### Host Policies
@@
   str.data$cancel.policy[ss60] <- 'Strict'
+
+  # Count Cleaning
+  countCleaning('hostpolicy')
 

### 2017-03-03 abb_Writeup.Rmd
adding host block images

@@
    load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
+a <- 1
 
@@
 * Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are not considered.
-* As most long-term rental use a leasing agency, we will assume use of an agency.
+* As most long-term rentals use a leasing agency, we will assume use of an agency.
 
@@
 
-<!-- ### Summary of Data Cleaning -->
-
-<!-- We have applied nine separate filters to our two datasets.
-In the name of transparency and to highlight the bounds of our research questions it is useful to review this filters (Table 2).
+### Summary of Data Cleaning
+
+We have applied ten separate filters to our two datasets.
+In the name of transparency and to highlight the bounds of our research questions it is useful to review these filters (Table 2).
 There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
-Filtering those not listed during the study period removes 1/3 of all properties.
+Filtering those not listed during the study period removes nearly 1/3 of all properties.
 Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
-From these 6,600 properties structural characteristics, locational issues and outlying nightly rates remove another 800 from consideration.
-Finally, 1,400 of these have never been booked and have \$0 revenue, requiring removal.
-From over 20,000, we have 4,446 Airbnb properties that meet the requirements of our research question.
--->
-
-<!-- For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+From these 7,200 properties structural characteristics remove another 480 from consideration.
+Over 1,000 of the remaining properties were never been booked and/or had outlying nightly rates and were removed.
+Finally, 14 properties had either bad location data or missing information host policy.
+From over 20,000, we have 5,788 Airbnb properties meet the requirements of our research question.
+
+For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
-remove another 10,000 observations, leaving 122,051 in the final dataset.
--->
+remove another 12,000 observations, leaving 120,092 in the final dataset.
 
@@
                        'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
-                       'Rates & Rents', 'Location', 'Revenue')
+                       'Rates & Rents', 'Revenue', 'Location', 'Host Policy')
 clean.table$strper <- 100*round(clean.table$strper, 2)
@@
 
-<!-- ## Comparison -->
-
-<!-- #### Observed Revenue -->
-
-<!-- Our final data filtering considers the observed gross revenue of the properties.
-For the long-term rentals the observed gross revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
-In a number of extreme cases, time on market was extremely long and the total observed revenues very low.
-To remove these outlying observations, we filter out any properties with less than $10,000 in revenue.
--->
-
-<!-- For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
-Using this data we sum up the total revenue from bookings.
-For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
--->
+## Revenues, More Explanation
+
+#### Revenue Calculations
+
+Calculations of revenue for the observed and hypothetical long-term rentals are straightforward, weekly rent -- real or imputed -- times 52 minus search cost time and agency fees.
+For the short-term rental it is somewhat more complicated.
+First, we must deal with those properties that were not listed for the entire 12 month period.
+Our data cleaning eliminated all properties that were listed for less than six months, however, it would be incorrect to compare the revenue of a property listed on Airbnb for seven months with the hypothetical annual revenue from a long term rental.
+
+Second, many of the short term properties have a significant number of blocked days, days in which the property was not offered on Airbnb.
+Here too, there is a problem with comparing observed revenues from a property with a 40\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portal during those blocked days.
+And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.
+In short, in either case, the actual observed short-term revenue would be biased on the low end compared to what a revenue maximizing owner would be likely able to accomplish.
+
+As a result, we have calculated three separate revenues values for the short-term properties:
+
+1. \textbf{Actual ($REV_a$)}: Observed bookings multiplied by median nightly rate
+2.
+\textbf{Extrapolated ($REV_e$)}: Observed bookings extrapolated to a full year^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
+3. \textbf{Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
 
@@
 
-<!-- ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'} -->
-
-<!--   strr <- str.data[,c('bedrooms', 'gross.revenue')] -->
-<!--   strr$tenure <- 'short-term' -->
-<!--   ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')] -->
-<!--   ltrr$tenure <- 'long-term' -->
-<!--   allr <- rbind(strr, ltrr) -->
-
-<!--   ggplot(allr, aes(x=gross.revenue, fill=tenure, color=tenure)) + -->
-<!--     geom_density(alpha=.5) + -->
-<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
-<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
-<!--     ggtitle('Annual Revenues by Tenure Type') + -->
-<!--     xlab('Annual Revenue') + -->
-<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
-<!--                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+ -->
-<!--     theme(legend.position='bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks.y = element_blank(), -->
-<!--           axis.title.y=element_blank()) + -->
-<!--     coord_cartesian(xlim=c(0, 70000)) -->
-
-<!-- ``` -->
+```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
+
+  stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
+  stre$tenure <- 'short-term extrapolated   '
+  names(stre)[2] <- 'revenue'
+  strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
+  strp$tenure <- 'short-term potential   '
+  names(strp)[2] <- 'revenue'
+  ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')]
+  ltrr$tenure <- 'long-term   '
+  names(ltrr)[2] <- 'revenue'
+  allr <- rbind(stre, strp, ltrr)
+
+  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) +
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
+    ggtitle('Annual Revenues by Tenure Type') +
+    xlab('Annual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000))
+
+```
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  #host.block.freq <- 
+  ggplot(str.data, aes(x=block.rate)) + 
+  geom_density(fill=str.col, color=str.col) +
+  ylab('Frequency\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0,1,.2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Host Block Rate Frequency\n') +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  #block.rate.period <- 
+ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  geom_point(fill=str.col, color=str.col, size=.2) +
+  ylab('Nbr of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
+
+str.data$host.type <- 'Unknown'
+str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
+str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
+str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
+str.data$host.type <- factor(str.data$host.type,
+                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                      'Multi-Platform User', 'Unknown'))
+
+#host.type <-
+
+ggplot(str.data, 
+       aes(x=block.rate, y=blockpertime, color=host.type)) + 
+  geom_point(alpha=.5, size=.8, shape=16) +
+  ylab('Number of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+
+  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
+  theme(legend.position='bottom',
+          legend.title = element_blank(),
+        plot.title = element_text(hjust = 0.5))+
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1)))
+
+```
+
+## Comparison
 
@@
 This work attempts to fill this void.
---> -->
+-->
 

### 2017-03-04 abb_Writeup.Rmd
host classificatoin, p1

@@
 
-<!-- Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
-Short term revenues range from neglible to highs of greater than \$80,000.
+Below we chart the distribution of the Extrapolated ($REV_e$) and Potential ($REV_p$) Short Term revenues against a distribution of the oserved long term revenues for the long term properties.
+Revenues from the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 8).
+Extrapolated short term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
+The range of the distribution for the Potential Short Term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.
+
 While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
-Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
--->
+When looking at potential revenues, however, a great deal more may have the potential to produce more revenue.
+The high number of very low yield Airbnb properties in the Extrapoted condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
 
@@
   names(strp)[2] <- 'revenue'
-  ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')]
+  ltrr <- ltr.data[,c('bedrooms', 'ltr.revenue')]
   ltrr$tenure <- 'long-term   '
@@
 ```
+
+#### Classifying Hosts
+
+As the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.
+There may be, therefore, different types of hosts operating in the Airbnb market.
+from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
+If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right.
+The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
+There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property.
+
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
-  #host.block.freq <- 
-  ggplot(str.data, aes(x=block.rate)) + 
+  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
   geom_density(fill=str.col, color=str.col) +
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  #block.rate.period <- 
-ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5}
+
+  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
   geom_point(fill=str.col, color=str.col, size=.2) +
@@
 
+ggMultiPlots(host.block.freq, block.rate.period, cols=2)
+
 ```
@@
 
-#host.type <-
-
-ggplot(str.data, 
-       aes(x=block.rate, y=blockpertime, color=host.type)) + 
-  geom_point(alpha=.5, size=.8, shape=16) +
-  ylab('Number of Blocked Periods\n') + 
+base.host <- ggplot(str.data, 
+                    aes(x=block.rate, y=blockpertime)) + 
+                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
+                ylab('# Blckd Periods\n') + 
                 xlab('\n% of Time Property is Blocked') +
                 ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-
                 scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-
-  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
+                                   labels=c('0%', '20%', '40%', 
+                                            '60%', '80%', '100%')) +
+                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
+                #                            abb.col[7], abb.col[9])) + 
                 theme(legend.position='bottom',
@@
 
+ps.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
+  ggtitle('Profit Seekers')
+os.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
+             size=.4)  +
+  ggtitle('Opportunistic Sharer')
+mu.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
+             size=.4)  +
+  ggtitle('Multi-Platform User')
+un.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
+  ggtitle('Unknown')
+
+ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+
+host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
+  geom_bar() +
+  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+  theme(legend.position='none') +
+  ylab('Frequency\n') + 
+  xlab('\nHost Type') +
+  ggtitle('Short Term Host Types') + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+host.type.bar
 ```

### 2017-03-04 abb_Writeup.Rmd
adding host type writeup

@@
 The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
-There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property.
+There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property.
+A potential method to identify these hosts is to look at the number of individual periods of blocked days.
+A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
+We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9.
+We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.
 
@@
 ```
+
+Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories.
+As a more subjective approach, we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
+Profit seekers are those host who have blocked percentages less than 25\% of the time.
+Opportunistic Sharers have blocked their properties at least 75\% of the time.
+Within those two extremes, we consider users who have at least 12 blocked periods during a year to be 'Multi-Platform Users' and the remaining set to be 'Unknown'.
+See Figure 10 for a breakdown of these group by the two variables.
 
@@
 ```
+
+Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
+The remainder 'Unknown' category contains just over 28\% of all properties.
+The classification of these hosts is not convincing enough to base our entire analytical process on so we will use these breakdowns to add context to the results and to test the sensitivity of our results to the assumptions underlying the extrapolated and potential revenue calculations.
 

### 2017-03-06 abb_Writeup.Rmd
Moving comparison to short only

@@
 
-<!-- In this section we compare returns between long and short term rental options.
+In this section we compare net revenues between long and short term rental options.
 As mentioned above, there are no direct matches between the datasets.
 In other words, we have not directly observed a property which has been in a long-term rental followed by short-term or vice versa.
-We will, instead, make the comparisons between the two by imputing likely short-term (long-term) rental revenues for the long-term (short-term) data and then comparing the observed revenues to the imputed revenues of the unobserved tenure type.
--->
-
-<!-- We make our imputations via hedonic price models, one for long-term rentals and one for short-term rentals.
+We will, instead, make the comparisons between the two by imputing likely long-term rental revenues for the observed short-term properties and then comparing the observed revenues to the imputed revenues.
+
+We make our imputations via a hedonic price models.
 We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term rental for the short term properties.
-We do the same for the long-term properties using a modeled derived from the short-term data.
--->
-
-<!-- For the long-term market, we use the following model specification: -->
-
-<!-- \begin{equation} -->
-<!--   \label{eq:test} -->
-<!-- ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i} -->
-<!-- \end{equation} -->
-
-<!-- where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
--->
-
-<!-- For the short-term market the specification is similar, minus the time correction.
-We eliminate this control because the short term rates are based on the medium value over the entire period and not monthly.
-This specification is: -->
-
-<!-- \begin{equation} -->
-<!-- ln(RentST_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \epsilon_{i} -->
-<!-- \end{equation} -->
-
-<!-- where *$ ln(RentLT_{i})$* is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property and $\epsilon$ a random error term.
--->
-
-<!-- ## Results -->
-
-<!-- We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
+We use the following model specification:
+
+\begin{equation}
+  \label{eq:test}
+ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i}
+\end{equation}
+
+where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+
+We then compare the projected net revenue of the short-term properties to their observed revenues, both Extrapolated ($REV_e$) and Potential ($REV_p$), to judge the likelihood of short-term preference.
+
+Realizing that the imputed long term rental values may be more accurate when estimated at smaller scales, we impute long term rental rates at submarket level, specifically by type, bed/bath and geographic area.
+In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
+for all combinations of type, bed/bath and geographic area.
+We then combine the results form all estimates back into a single dataset that contains all of the short-term rentals.
+
+## Results
+
+We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
 What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
@@
 -->
-
-<!-- We begin by imputing the likely long-term rents for the short-term observations, and vice versa at a metro level.
-A comparison between the actual (observed) and imputed rates and rents shows that, in general, the long-term properties are composed of properties that have a higher nightly rate than the short term observations (left-panel) (Figure 11).
-This is likely due to the fact that there are more houses (compared to apartments) in the long-term data than in the short-term data.
-Interestingly, the observed (long-term) and imputed (short term) weekly rental values are somewhat similar, suggesting that the higher rent, city-core apartments push the distribution of the imputed short-term values upwards.
--->
-
-<!-- For each of the observed values we also create a fitted value for that observation in the model.
-This may help to reduce the influence of outlying observed values in our model.
-To be clear, each observation will now have three estimates of rates and rents.
-For the short-term properties they will have: 1) an actual nightly rate; 2) an estimated nightly rate; and 3) an estimated long-term (weekly) rent.
-The long-term properties will have: 1) an actual long-term (weekly) rent; 2) an estimated long-term (weekly) rent; and 3) an estimated nightly rate.
--->
-
-<!-- ```{r pred.glob.imp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
-
-<!--   abbir <- abb.revs[,c('bedbath', 'imp.rent', 'med.rate')] -->
-<!--   abbir$tenure.rate <- 'short-term (observed)' -->
-<!--   abbir$tenure.rent <- 'short-term (imputed)' -->
-
-<!--   ltrir <- ltr.revs[,c('bedbath', 'event.price', 'imp.rate')] -->
-<!--   ltrir$tenure.rate <- 'long-term (imputed)' -->
-<!--   ltrir$tenure.rent <- 'long-term (observed)' -->
-
-<!--   names(abbir) <- names(ltrir) <- c('bedbath', 'rent', 'rate', 'tenure.rate', 'tenure.rent') -->
-<!--   allir <- rbind(abbir, ltrir) -->
-
-<!-- ``` -->
-
-<!-- ```{r imp.rate.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
-
-<!--   irate.plot <- ggplot(allir, aes(x=rate, fill=tenure.rate, color=tenure.rate)) + -->
-<!--     geom_density(alpha=.5) + -->
-<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
-<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
-<!--     ggtitle('Nightly Rates by Tenure Type') + -->
-<!--     xlab('Nightly Rate') + -->
-<!--     scale_x_continuous(breaks=c(seq(0,600, by=200)), -->
-<!--                        labels=c('$0', '$200', '$400', '$600'))+ -->
-<!--     theme(legend.position='bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks.y = element_blank(), -->
-<!--           axis.title.y=element_blank()) + -->
-<!--     coord_cartesian(xlim=c(0, 625)) -->
-
-<!-- ``` -->
-
-<!-- ```{r imp.rent.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
-
-<!--   irent.plot <- ggplot(allir, aes(x=rent, fill=tenure.rent, color=tenure.rent)) + -->
-<!--     geom_density(alpha=.5) + -->
-<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
-<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
-<!--     ggtitle('Weekly Rents by Tenure Type') + -->
-<!--     xlab('Weekly Rents') + -->
-<!--     scale_x_continuous(breaks=c(seq(0,1000, by=200)), -->
-<!--                        labels=c('$0', '$200', '$400', '$600', '$800', '$1,000'))+ -->
-<!--     theme(legend.position='bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks.y = element_blank(), -->
-<!--           axis.title.y=element_blank()) + -->
-<!--     coord_cartesian(xlim=c(150, 1000)) -->
-
-<!-- ``` -->
-
-<!-- ```{r imp.rr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5, fig.cap='Rates and Rents Comparison'} -->
-
-<!--  ggMultiPlots(irate.plot, irent.plot, cols=2) -->
-
-<!-- ``` -->
-
-<!-- The question of whether or not the imputations are accurate remains.
-Table 3 shows simple diagnostics from the two imputation models.
-From this we see that the short-term model performs rather poorly, with a standard error of 34.6\% and over half of the residuals greater than 20\%.
-The long term model, on the other hand, performs quite well, with a standard error under 16\% and less than 19\% of fitted errors greater than 20\%.
-Given the small amount of independent variable available to the models, the long term market appear much more predictable than the short term market.
-This could be due to omitted variables in the short term market or a greater level of variability in the price setting (which is done by individuals) as opposed to the long-term market in which most owners get help with leasing from an agency.
--->
-
-<!-- ```{r, results="asis", echo=FALSE} -->
-
-<!-- abbs <- c(abb.sum$r.squared, abb.sum$adj.r.squared, -->
-<!--           abb.sum$sigma, -->
-<!--           length(which(abs(abb.sum$residuals) > .2)) / length(abb.sum$residuals)) -->
-<!-- ltrs <- c(ltr.sum$r.squared, ltr.sum$adj.r.squared, -->
-<!--           ltr.sum$sigma, -->
-<!--           length(which(abs(ltr.sum$residuals) > .2)) / length(ltr.sum$residuals)) -->
-
-<!-- summ.table <- data.frame(shortterm=round(abbs, 3), -->
-<!--                          longterm=round(ltrs, 3)) -->
-<!-- rownames(summ.table) <- c('r-squared', 'adj r-squared', -->
-<!--                           'sigma', '% fit errors > 20%') -->
-<!-- names(summ.table) <- c('Short Term', 'Long Term') -->
-
-<!-- s.table <- xtable(summ.table, -->
-<!--                   caption='Imputation Model Diagnostics\n', -->
-<!--                   digits=3) -->
-<!-- align(s.table) <- c('lcc') -->
-<!-- print(s.table,  -->
-<!--        include.rownames=TRUE, -->
-<!--                   caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- Next, to create an estimated short-term revenue for the long-term properties we have to create an estimate of the occupancy rate.
-For the estimated long-term rentals we have to create an estimate of the search time (days on market).
-To derive an occupancy rate, we use the weighted median value^[Weighted by the total number of days the property was offered on Airbnb over the year.] of the market, the entire metro region in this case, which is about 37%^[We attempted to use a logistic regression model to predict occupancy but were unsucessful to develop an appropriate approach.
-Work continues toward this end.].
-The range of occupancy varies widely from essentially 0 to 100%, with a standard deviation of 27%.
--->
-
-<!-- For the long term search time, or days on market, we also use the median value of the observations.
-The median days on market is 24, with a standard deviation of 37.
-About 60\% of long term rental spent one month or less on the market and 85\% spent less than two months searching for a tenant.
--->
-
-<!-- Using these estimated occupancy rates and days on market, we have used equations 3 and 4 to produce estimates of long-term and short-term revenues for the short and long term observations, respectively.
-We do these for the observed and the estimated rates and rents for each tenure type.
-As we have imputed and actual observations for one of each dataset in the comparison, this creates 4 different comparisons, roughly broken down as shown in Figure 11.
--->
-
-<!-- ```{r, results="asis", echo=FALSE, fig.width=4,fig.height=4, fig.cap='Revenue Comparison Types'} -->
-
-<!--   explain.plot <- blank.plot + -->
-<!--     geom_text(data=ann.df, -->
-<!--               label=ann.df$lab, -->
-<!--               size=2.8) + -->
-<!--     geom_text(data=num.df, -->
-<!--               label=num.df$count, -->
-<!--               size=9.5) + -->
-<!--     coord_cartesian(ylim=c(-.5,1)) + -->
-<!--     ggtitle('Explanation of \n Revenue Comparisons') + -->
-<!--     theme(legend.position='bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results="asis", echo=FALSE} -->
-
-<!--   one.df <- data.frame(x=rep(0, 4), -->
-<!--                        y=rep(0, 4), -->
-<!--                        lab=c('31%', '87%', '54%', '79%'), -->
-<!--                        est=c('Actual Rates & Rents', 'Actual Rates & Rents', -->
-<!--                              'Imp. Rates & Rents', 'Imp. Rates & Rents'), -->
-<!--                        data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term')) -->
-
-<!--   sizes <- c(.31, .87, .54, .79) -->
-
-<!--   one.plot <- blank.plot + -->
-<!--     geom_text(data=one.df, -->
-<!--               label=one.df$lab, -->
-<!--               size=18*sizes) + -->
-<!--     ggtitle('% of Properties where \n Airbnb is more profitable') + -->
-<!--     theme(legend.position='bottom', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5)) -->
-
-<!-- ``` -->
-
-<!-- In other words, the left hand panels (left side of Figure 12) are comparisons made on Airbnb properties, where the top is the actual Airbnb revenue and the bottom is the estimated (fitted) with the imputed rates and median-based occupancy rates.
-In the right hand panels we have the comparison on the long-term properties, again with top being of the actual long term revenue and the bottom with the estimated (fitted) rents and median based days on market.
--->
-
-<!-- The right hand side of Figure 12 shows the percent of properties in which a short-term rental would bring in more revenue over the coures of the year, across these four scenarios.
-The variation between these estimates is significant and troublesome.
-However, given our difficulty in accurately estimating short term nightly rates (see Table 3) and the fact that occupancy rates are highly variable for short-term rentals, these variations are not surprising.
-As we have a difficult time estimating short-term market performance, both measures in the right hand column are immediately suspicious.
-Additionally, the estimates in the lower left also depend on estimate nightly rate, causing their accuracy to be questioned.
--->
-
-<!-- ```{r 22r.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7.5,fig.height=3.5, fig.align='center', fig.cap='Summary of Comparison Types'} -->
-
-<!--  ggMultiPlots(explain.plot, one.plot, cols=2) -->
-
-<!-- ``` -->
-
-<!-- In short, only in the upper left hand panel are we using the actual nightly rates and the actual occupancy rates from the short term market.
-We do estimate the long-term rates and days on market here, but as shown above, the models for those figures are much more robust.
-The plusses and minus of each comparison quadrant are shown in Figure 13.
-As a result of these issues, we consider only those comparisons in quadrant 1 to be legitimate and use these going forward.
-This means that we will only be considering comparisons of actual Airbnb revenues to their estimated long-term rental revenues.
--->
-
-<!-- ```{r reason.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4.5, fig.height=3.5, fig.align='center', fig.cap='Comparison Types: Strengths and Weaknesses'} -->
-
-<!--   reason.plot <- blank.plot + -->
-<!--     geom_rect(data = mrkt.table, aes(fill=good), -->
-<!--               xmin = -Inf,xmax = Inf, -->
-<!--               ymin = -Inf,ymax = Inf, alpha = 0.4) + -->
-<!--     geom_text(data=reason.df, -->
-<!--               label=reason.df$lab, -->
-<!--               size=3) + -->
-<!--     geom_text(data=num.df, -->
-<!--               label=num.df$count, -->
-<!--               size=9.5) + -->
-<!--     coord_cartesian(ylim=c(-.5,1)) -->
-
-<!--   reason.plot -->
-
-<!-- ``` -->
 

### 2017-03-06 abb_Writeup.Rmd
Metro and Type analysis writeup

@@
 
-## Results
-
-We will begin our analysis by making a comparison of the short and long-term markets at a metro-level.
-What we mean by this is that we will treat the entire region as the functional market and will impute rates and rents with a model using all data.
-It is likely that different submarkets operate differently, a hypothesis investigated after the full metropolitan region.
--->
-
-<!-- ### Occupancy Rates -->
-
-<!-- Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
-Unfortunately, these are also the most difficult factor to estimate or impute.
-Below we shows (left-panel, Figure 14) the percentage of properties for which short-term rental is more profitable versus the occupancy rate.
-We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up until about 75\% occupancy.
-For occupancy rates less than 50\%, long-term rental is more likely to be the better option.
-The decrease in profitabilty after 75\% occupancy is likely due to: 1) small sample sizes in this tail of the data; and 2) that lowering overall nightly rates too low simply to boost occupancy can result in lower overall revenue.
--->
-
-<!-- As the distribution of occupancy rates is not uniform (Figure 14, right panel), the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
-In Figure 15, we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
-By doing so, we see that, in general, properties need to be in the upper 1/3 of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
--->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--   rawocc.pplot <- makePrefPlot(abb.revs, -->
-<!--                                x.field='occ.rate', -->
-<!--                                y.field='abb.act', -->
-<!--                                     smooth=TRUE, -->
-<!--                                smooth.span=.75) -->
-<!--   rawocc.pplot <- rawocc.pplot + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     ylab('\n% of Properties where \nAirbnb is more profitable') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     scale_color_manual(values=sm.col) + -->
-<!--     ggtitle('Tenure Profitability vs \n Occupancy Rate') + -->
-<!--     theme(legend.position='none', -->
-<!--           plot.title = element_text(hjust = 0.5)) + -->
-<!--     coord_cartesian(ylim=c(0,1)) + -->
-<!--     geom_hline(aes(yintercept=.5)) -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--   dens.plot <- ggplot(abb.revs, aes(x=occ.rate)) + -->
-<!--     geom_density(alpha=.3, fill=1) + -->
-<!--     scale_color_manual(values=sm.col) + -->
-<!--     scale_fill_manual(values=sm.col) + -->
-<!--     scale_x_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-
-<!--     ylab('\nFrequency of Occurance') + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     ggtitle('Distribution of \n Occupancy Rates') + -->
-<!--     theme(legend.position='none', -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           axis.line=element_blank(), -->
-<!--           axis.text.y=element_blank(), -->
-<!--           axis.ticks.y=element_blank()) -->
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'} -->
-
-<!--   ggMultiPlots(rawocc.pplot, dens.plot, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--   abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, -->
-<!--                                       return.type='rank') -->
-<!--   abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, -->
-<!--                                   return.type='rank') -->
-
-<!--   ## Make quartile location plot -->
-
-<!--   qtlocc.pplot <- makePrefPlot(abb.revs, -->
-<!--                                x.field='occ.qtl', -->
-<!--                                y.field='abb.act', -->
-<!--                                smooth=TRUE, -->
-<!--                                smooth.span=.55) -->
-<!--   qtlocc.pplot <- qtlocc.pplot + -->
-<!--     xlab('\nQuantile of Occupancy Rate') + -->
-<!--     ylab('\n% of Properties where \n Airbnb is more profitable') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0', '25th', '50th', '75th', '100th')) + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     scale_color_manual(values=sm.col) + -->
-<!--     theme(legend.position='none') + -->
-<!--     coord_cartesian(ylim=c(0,1))+ -->
-<!--     geom_hline(aes(yintercept=.5)) -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=4, fig.height=3, fig.align='center', fig.cap='Probability of Short Term Pref. vs Occ. Rate Quantile'} -->
-
-<!--   qtlocc.pplot -->
-
-<!-- ``` -->
-
-<!-- Along with occupancy rates, the other important consideration is the nightly rate.
+### Results
+
+We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
+Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
+
+Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
+Below we show (left-panel, Figure 9) the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
+We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up from about 25\% up to 75\% occupancy.
+For occupancy rates less than 40\%, long-term rental is more likely to be preferable.
+
+As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+In the right hand panel of Figure 9 we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
+As a matter of reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'}
+
+  str.data.ic$pref <- str.data.ic$str.ext.pref
+
+  rawocc <- abbPrefPlot(str.data.ic,
+                         x.field='occ.rate',
+                         smooth=TRUE,
+                         smooth.span=.5)
+
+  rawocc <- ggplot(rawocc$data,
+                   aes(x=x.var, y=Var))+
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
+                                      return.type='rank') 
+  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
+                                  return.type='rank') 
+  qtlocc <- abbPrefPlot(str.data.ic,
+                        x.field='occ.qtl',
+                        smooth=TRUE,
+                        smooth.span=.5)
+
+  qtlocc <- ggplot(qtlocc$data,
+                   aes(x=x.var, y=Var))+
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Quantile)') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') + 
+    ggtitle('Quantile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggMultiPlots(rawocc, qtlocc, cols=2)
+```
+
+Along with occupancy rates, the other important consideration is the nightly rate.
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In Figure 16 (left panel) we plot nightly rates versus occupancy rates.
+In Figure 10 (left panel) we plot nightly rates versus occupancy rates.
 We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
 The transparency is related to the total count of actual market properties falling into that area.
--->
-
-<!-- The general trend is what is expected, i.e.
+
+The general trend is what is expected, i.e.
 that higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
@@
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
--->
-
-<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+
+An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
 In this case, we delineate the boundary (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
@@
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
--->
-
-<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'} -->
-
-<!--  ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 16 may be misleading.
-We convert both axis to quantiles and replot both in Figure 17.
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'}
+
+  rate.hm <- abbHeatMap(str.data.ic,
+                x.field='occ.rate',
+                y.field='med.rate',
+                pref.field='str.ext.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  rate.hm <- rate.hm + ylab('Nightly Rate')
+
+  rate.hm.svm <- abbHeatMap(str.data.ic,
+                            x.field='occ.rate',
+                            y.field='med.rate',
+                            pref.field='str.ext.pref',
+                            svm=T, 
+                            alpha.count=F,
+                            add.points=T,
+                            fill.colors=c(abb.col[1], abb.col[5]))
+  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')
+
+  ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
+
+```
+
+Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 10 may be misleading.
+We convert both axis to quantiles and replot both in Figure 11.
 Here we see a more even distibution of points across the figures.
@@
 For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
--->
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+
+  qtl.hm <- abbHeatMap(str.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.ext.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  qtl.hm <- qtl.hm + ylab('Nightly Rate')
+
+  qtl.hm.svm <- abbHeatMap(str.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate')
+
+  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
+
+```
+
+### Submarkets
+
+To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
+First, we bifurcate our data into houses and apartments.
+Within the houses, 17.5\% of the properties are short-term preferable, while for the apartment that figure is nearly double at 30.5\%.
+Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (Figure 12).
+The only measurable difference is in that for houses a properties occupancy rate needs to be about in a higher quantile (by about 10) than apartments to show the same likelihood of short-term preference as apartment.
+Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preferenc.e
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Preferency vs Occ. Rates: By Type'}
+
+  apt.id <- which(str.data.ic$type == 'Apartment')
+  house.id <- which(str.data.ic$type == 'House')
+  type.data.ic <- str.data.ic
+
+  ptrocc <- abbPrefPlot(type.data.ic,
+                         x.field='occ.rate',
+                         split.field='type',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=c('black', 'grey40'))
+
+  ptr.occ <- ggplot(ptrocc$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_color_manual(values=c('black', 'grey60'),
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
+                                      return.type='rank')
+  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$occ.rate[house.id], return.type='rank')
+
+  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
+                                  return.type='rank')
+  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$med.rate[house.id], return.type='rank')
+
+  ptqocc <- abbPrefPlot(type.data.ic,
+                         x.field='occ.qtl',
+                         split.field='type',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=c('black', 'grey40'))
+
+  ptq.occ <- ggplot(ptqocc$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Quantile)') +
+    scale_color_manual(values=c('black', 'grey60'),
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Quantile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
+
+```
+
+Extending this analysis to also include nightly rates shows a similar situation (Figure 13).
+For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
+As an example, a median nightly rate requires a 90\% occupancy rate.
+The market for apartment (right panel) is more forgiving and occupancy rates as low as the 60th percentile can equate to a greater than even chance of short-term prefence is coupled with nightly rates near the top of the market.
+A median nightly rate requires a 70\% occupancy rate for short-term prefernce likelihood.
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: By Type'}
+
+### UPDATE THE QTL VALUES
+
+  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
+                                          'House', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5])) +
+  theme(legend.position='none') +
+  annotate("text", x = 50, y = 50, label = "Houses", size=9)
+
+  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
+                                          'Apartment', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+  annotate("text", x = 50, y = 50, label = "Apartments", size=9)
+
+  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
+
+```
 
@@
 
-<!--  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
+<!-- ### UPDATE THE QTL VALUES -->
+
+<!--   core.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
+<!--                                           'city-core', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none') +  -->
+<!--     ylab('') + -->
+<!--     xlab('') +  -->
+<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
+
+<!--     city.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
+<!--                                           'city', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+  -->
+<!--     ylab('') + -->
+<!--     xlab('')+  -->
+<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
+
+<!--       sub.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
+<!--                                           'suburban', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+  -->
+<!--     ylab('') + -->
+<!--     xlab('')+  -->
+<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
+
+<!--       rural.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
+<!--                                           'rural', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+  -->
+<!--     ylab('') + -->
+<!--     xlab('')+  -->
+<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
+
+<!--       beach.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
+<!--                                           'beach', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+  -->
+<!--     ylab('') + -->
+<!--     xlab('')+  -->
+<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
+
+<!-- #### Geographic Submarkets -->
+
+<!-- We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
+In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
+Interestingly, the rural area has a higher probably than all other but the core.
+This is likely explained by the fact that there are few rural properties and many of these are clustered near rural tourists activities like the Yarra Valley wine region which see a high demand for lodging (Figure 8).
+-->
+
+<!-- In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
+In the lower density areas it appears that tourists may prefer larger and more spacious dwellings compared to long-term renters who may experience long commutes from these fringe locations.
+-->
+
+<!-- Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
+This finding suggests that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
+In other words, there is well defined combination or situation in which these properties can be more profitable short-term than in a long-term lease.
+The opposite is true of the city core apartments.
+Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'} -->
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)] -->
+<!--   str.data.ic$pref <- str.data.ic$str.ext.pref -->
+
+<!--   rawocc <- abbPrefPlot(str.data.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          split.field='sub.mrkt', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.35 , -->
+<!--                          spl.col=sm.col) -->
+
+<!--   str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate,  -->
+<!--                                       return.type='rank')  -->
+<!--   str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate,  -->
+<!--                                   return.type='rank')  -->
+<!--   qtlocc <- abbPrefPlot(str.data.ic, -->
+<!--                                x.field='occ.qtl', -->
+<!--                                split.field='sub.mrkt', -->
+<!--                                smooth=TRUE, -->
+<!--                                smooth.span=.75) -->
+
+<!--    raw.data <- rawocc$data -->
+<!--    qtl.data <- qtlocc$data -->
+
+<!--    raw.data$type <- 'Raw Occ. Rate' -->
+<!--    qtl.data$type <- 'Qtl. Occ. Rate' -->
+<!--    raw.data$type <- factor(raw.data$type,  -->
+<!--                            levels=c('Raw Occ. Rate', 'Qtl. Occ. Rate')) -->
+<!--    rq.data <- rbind(raw.data, qtl.data)  -->
+
+<!--   ## Make quartile location plot -->
+
+<!--   rq.pplot <- ggplot(rq.data, -->
+<!--                      aes(x=x.var, y=Var, group=ID, color=ID)) + -->
+<!--                 stat_smooth(se=FALSE, size=2, span=.7) + -->
+<!--                 xlab('\nOccupancy Rate') + -->
+<!--                 scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                                    labels=c('0%', '25%', '50%', '75%', -->
+<!--                                             '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     scale_colour_manual(values=sm.col, -->
+<!--                         name='') + -->
+<!--     theme(legend.position='bottom') + -->
+<!--     facet_wrap(~type) -->
+
+<!--   rq.pplot -->
 
@@
 
-<!-- ### Market Summary -->
-
-<!-- Finally, we summarize the entire market by looking at three metrics: -->
-
-<!-- 1. Actual: The percentage of properties in the market in which short-term (Airbnb) generates more revenue -->
-<!-- 2. Fitted: The percentage of properties (when plotted by occupancy rate and nightly rate) that fall in the SVM area considered profitable -->
-<!-- 3. SVM Area: The percentage of the total area in the SVM plot that represents a situation where the short-term rental is more profitable. -->
-
-<!-- None of these metrics on their own is perfect.
-The 'actual' measure responds directly to the sample of the current market and may not be as useful to a potential investor.
-The 'fitted' and 'svm area' metric minimize some bias from the sample, but suffer from forcing all observations into a binary condition (there are no 'gray' areas) and the 'svm area' metric may be biases by large areas of the scatterplot that have few actual observations.
-This latter issue is partially limited by plotting by quantile, but, nonetheless still exists.
--->
-
-<!-- We calculate each for the raw rates as well as for the quantile situation.
-These are show in Table 4.
-Overall, 31.4\% of the observed Airbnb properties raised more actual revenue from short-term lending than the estimated long-term revenue that they would have gained.
-Analyzing these by raw rates in the SVM, we find that a nearly identical 31.4\% fall within the contiguous area of short-term preference and this area takes up 40.6% of the total plotted area.
-When we scale the plots by quantile, we find that 37.2\% of all observations fall in the short-term preference area and that this area takes up 37.8\% of the total plotted area.
-As the difference between the fitted and the svm area is considerably smaller in the quantile approach, there is less bias from outlying, empty areas.
--->
-
-<!-- ```{r, results="asis", comment=FALSE,  echo=FALSE} -->
-
-<!-- names(market.ratio) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area') -->
-<!-- print(xtable(market.ratio, caption='Metro Level: Short-Term Preference Analysis\n', -->
-<!--        digits=3), -->
+<!-- ```{r message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table <- abbCreateCompTable(ic.df=str.data.ic, -->
+<!--                                    split.field='sub.mrkt') -->
+
+<!--  # Convert to wide format for output -->
+<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ] -->
+<!--   pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
+<!--   pref.table[,2] <- pref.table[,2]*100 -->
+
+<!--   names(pref.table) <- c('Sub-Market', '% Short Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+<!--   print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n', -->
+<!--                digits=1), -->
 <!--                include.rownames=FALSE, -->
@@
 
-<!-- ### Submarkets -->
-
-<!-- A major concern about the above analysis is that the estimated rents, rates, days on market and occupancy rates are estimated globally.
-As a result, there is the likelihood of significant bias within certain submarkets.
-Below, we break down the results by type (apartment vs house), by geographic market (five geographic submarkets listed above) and by type and submarket.
--->
-
-<!-- #### Property Type -->
-
-<!-- First, we bifurcate our data into houses and apartments.
-We then rerun the entire analysis described above for the house and the apartment markets separately.
-Table 5 and Figures 18 (houses) and 19 (apartments) illustrate the metrics for these two sub-markets.
-The raw probability data shows that over 33% of apartments are more profitable in short term leasing as opposed to just 22% of houses.
-Figures 18 and 19 show the quantile preference plots both in the raw and with the SVM categorization.
-As is evident from these plots, the likely of short-term rental being more profitable is much greater in the apartment market than in the house market.
-For apartments, a 60th rate and a 60th percentile occupancy rate has a better than 50% chance of being more profitable in a short term leasing strategy than a long term one.
-In fact, so long as an apartment is in the top 1/4 of occupancy rates, it is more profitable in a short term strategy at almost any price point.
-Houses, on the other hand, need either very high rates or very high occupancies to justify a short-term rental.
--->
-
-<!-- The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.
-First, the difference between the SVM Area and the Fitted number highlight the fact that even when transforming the axes into quantile, the data are still not uniformly distributed across the 2-dimensional space of the plot.
-This means that not all areas of the plot have equal weights in the Fitted value.
-Second, the Actual and SVM Area figures deviate because of the binary nature of the SVM process.
-For example, in many of the short-term preference in the apartment SVM plot there are some long-term preference data points, but just fewer than 50% of total, whereas in the long-term preference areas on the left hand side of the plot nearly all of the points are long-term preference.
-The results of the SVM process are the result of a sort of 'gerrymandering' where a clustering by one faction and a dispersal by another can create a result that is not representative of the underlying base population.
-Despite this fact, we feel that the SVM Area values are useful for the owner in our scenario because they provide both a value and visual guide that present the possibilities of being more profitable with a short-term strategy, not just what the current distribution of such properties are.
--->
+<!-- broken down by the five geographic submarkets -- City-Core, City, Suburban, Rural and beach.
+Looking at different market segments such as property type, host type and home characteristics will follow.
+-->
+
+<!-- Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
+That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.
+-->
+
+<!-- ```{r, fig.width=8, fig.height=8, echo=FALSE, fig.cap='xxx'} -->
+
+<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
+<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
+
+<!-- ``` -->
 
@@
 <!-- ``` -->
-
-<!-- #### Geographic Submarkets -->
-
-<!-- We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
-In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
-Interestingly, the rural area has a higher probably than all other but the core.
-This is likely explained by the fact that there are few rural properties and many of these are clustered near rural tourists activities like the Yarra Valley wine region which see a high demand for lodging (Figure 8).
--->
-
-<!-- In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
-In the lower density areas it appears that tourists may prefer larger and more spacious dwellings compared to long-term renters who may experience long commutes from these fringe locations.
--->
-
-<!-- Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
-This finding suggests that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
-In other words, there is well defined combination or situation in which these properties can be more profitable short-term than in a long-term lease.
-The opposite is true of the city core apartments.
-Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
--->
 
@@
 
-<!-- ## Explaining Preference -->
+## Explaining Preference
 

### 2017-03-06 abb_Functions.R
fixing pref bug

@@ -688,22 +688,28 @@ abbPrefPlot <- function(pref.data,
     
     if(split.field != 'none'){
       
-      # Create the table
-      pref.table <- tapply2DF(pref.df$pref, 
-                              pref.df[ ,split.field],
-                              metric.fnct)
+      if(nrow(pref.df) > 0){
+        # Create the table
+        pref.table <- tapply2DF(pref.df$pref, 
+                                pref.df[ ,split.field],
+                                metric.fnct)
+      } else {
+        pref.table <- NULL
+      }  
     } else {
       
       pref.table <- data.frame(ID='all', 
                                Var=metric.fnct(pref.df$pref, na.rm=T))
     }
     
-    # Add the x variable
-    pref.table$x.var <- i.pl
+    if(nrow(pref.df) > 0){
     
-    # Add to the capture list
-    pref.list[[i.pl]] <- pref.table
+      # Add the x variable
+      pref.table$x.var <- i.pl
     
+      # Add to the capture list
+      pref.list[[i.pl]] <- pref.table
+    }
   }
   
  ## Convert to a data.frame  
@@ -765,7 +771,8 @@ abbPrefPlot <- function(pref.data,
   
  ## Return Values
   
-  return(pref.plot)
+  return(list(data=pref.full,
+              plot=pref.plot))
   
 }
 
@@ -797,7 +804,7 @@ abbHeatMap <- function(hm.data,
     bins <- c(0, 0)
     if(x.field == 'occ' | x.field == 'occ.rate') bins[1] <- .05
     if(x.field == 'occ.qtl') bins[1] <- 5
-    if(y.field == 'nightly.rate') bins[2] <- 25
+    if(y.field == 'med.rate') bins[2] <- 25
     if(y.field == 'rate.qtl') bins[2] <- 5
   }
   

### 2017-03-06 abbDataAnalysis_Script.Rmd
adding offline option
outputing data from pref analysis

@@
 
+  offline <- TRUE
+
 ```
@@
 
+  if(offline){
+
+  source(paste0(code.path, '/dataVizTools/ggPlotTools.R'))
+  source(paste0(code.path, '/datamgmttools/dataMungeTools.R'))
+  source(paste0(code.path, '/spatialTools/spatialLogitModels.R'))
+  source(paste0(code.path, '/spatialTools/point2surface_Tools.R'))
+
+  } else {
+
   source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
@@
                               spl.col=sm.col)
-  rawocc.pplot
+  rawocc.pplot$plot
 
@@
                                smooth.span=.75)
-  qtlocc.pplot <- qtlocc.pplot +
+  qtlocc.pplot <- qtlocc.pplot$plot +
     xlab('\nQualtile of Occupancy Rate') +
@@
                 x.field='occ.rate',
-                y.field='nightly.rate',
+                y.field='med.rate',
                 pref.field='str.ext.pref',
@@
                             x.field='occ.rate',
-                            y.field='nightly.rate',
+                            y.field='med.rate',
                             pref.field='str.ext.pref',

### 2017-03-06 abb_Writeup.Rmd
adding geo market writeup

@@
 
-<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'} -->
-
-<!-- ### UPDATE THE QTL VALUES -->
-
-<!--   core.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
-<!--                                           'city-core', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none') +  -->
-<!--     ylab('') + -->
-<!--     xlab('') +  -->
-<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
-
-<!--     city.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
-<!--                                           'city', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+  -->
-<!--     ylab('') + -->
-<!--     xlab('')+  -->
-<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
-
-<!--       sub.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
-<!--                                           'suburban', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+  -->
-<!--     ylab('') + -->
-<!--     xlab('')+  -->
-<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
-
-<!--       rural.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
-<!--                                           'rural', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+  -->
-<!--     ylab('') + -->
-<!--     xlab('')+  -->
-<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
-
-<!--       beach.hm.svm <- abbHeatMap(str.data.ic[str.data.ic$sub.mrkt ==  -->
-<!--                                           'beach', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+  -->
-<!--     ylab('') + -->
-<!--     xlab('')+  -->
-<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
-
-<!-- #### Geographic Submarkets -->
-
-<!-- We break the data down further by geographic submarket and property type and compare the results (quantile) in Table 6.
-In the Actual (observed) revenues, the probabilty of short-term preference is highest in the core area of the city and lowest in the city, beach and suburban areas.
-Interestingly, the rural area has a higher probably than all other but the core.
-This is likely explained by the fact that there are few rural properties and many of these are clustered near rural tourists activities like the Yarra Valley wine region which see a high demand for lodging (Figure 8).
--->
-
-<!-- In the core and the city, apartments offer a higher probability than homes, the reverse is true in the suburban and rural areas.
-In the lower density areas it appears that tourists may prefer larger and more spacious dwellings compared to long-term renters who may experience long commutes from these fringe locations.
--->
-
-<!-- Looking at the 'fitted' and 'svm area' figures we see a trend that the svm values are higher than the actual observed probabilities for the core apartment and lower for nearly all of the rest of the categories.
-This finding suggests that for all but the core apartments, those properties that are more profitable as short-term cluster tightly in the area (the combination of nightly rate and occupancy rate) that are preferable for a short-term strategy.
-In other words, there is well defined combination or situation in which these properties can be more profitable short-term than in a long-term lease.
-The opposite is true of the city core apartments.
-Here, the area of the plots occupied by short term preference is larger than the total proporation, suggesting that a wide variety of combinations of nightly rates and occupancy rates will result in a short term preference.
--->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'} -->
-<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)] -->
-<!--   str.data.ic$pref <- str.data.ic$str.ext.pref -->
-
-<!--   rawocc <- abbPrefPlot(str.data.ic, -->
-<!--                          x.field='occ.rate', -->
-<!--                          split.field='sub.mrkt', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.35 , -->
-<!--                          spl.col=sm.col) -->
-
-<!--   str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate,  -->
-<!--                                       return.type='rank')  -->
-<!--   str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate,  -->
-<!--                                   return.type='rank')  -->
-<!--   qtlocc <- abbPrefPlot(str.data.ic, -->
-<!--                                x.field='occ.qtl', -->
-<!--                                split.field='sub.mrkt', -->
-<!--                                smooth=TRUE, -->
-<!--                                smooth.span=.75) -->
-
-<!--    raw.data <- rawocc$data -->
-<!--    qtl.data <- qtlocc$data -->
-
-<!--    raw.data$type <- 'Raw Occ. Rate' -->
-<!--    qtl.data$type <- 'Qtl. Occ. Rate' -->
-<!--    raw.data$type <- factor(raw.data$type,  -->
-<!--                            levels=c('Raw Occ. Rate', 'Qtl. Occ. Rate')) -->
-<!--    rq.data <- rbind(raw.data, qtl.data)  -->
-
-<!--   ## Make quartile location plot -->
-
-<!--   rq.pplot <- ggplot(rq.data, -->
-<!--                      aes(x=x.var, y=Var, group=ID, color=ID)) + -->
-<!--                 stat_smooth(se=FALSE, size=2, span=.7) + -->
-<!--                 xlab('\nOccupancy Rate') + -->
-<!--                 scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                                    labels=c('0%', '25%', '50%', '75%', -->
-<!--                                             '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     scale_colour_manual(values=sm.col, -->
-<!--                         name='') + -->
-<!--     theme(legend.position='bottom') + -->
-<!--     facet_wrap(~type) -->
-
-<!--   rq.pplot -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->
-
-<!--  # Make Basic comparison table -->
-<!--   pref.table <- abbCreateCompTable(ic.df=str.data.ic, -->
-<!--                                    split.field='sub.mrkt') -->
-
-<!--  # Convert to wide format for output -->
-<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
-
-<!--  # Limit to the extrapolated pref type -->
-<!--   pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ] -->
-<!--   pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
-<!--   pref.table[,2] <- pref.table[,2]*100 -->
-
-<!--   names(pref.table) <- c('Sub-Market', '% Short Term Preferable') -->
-<!--   options(xtable.comment = FALSE) -->
-<!--   print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n', -->
-<!--                digits=1), -->
-<!--                include.rownames=FALSE, -->
-<!--                caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- broken down by the five geographic submarkets -- City-Core, City, Suburban, Rural and beach.
-Looking at different market segments such as property type, host type and home characteristics will follow.
--->
-
-<!-- Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
+#### By Geography
+
+Next, we divide the data by the five geographic sub-market shown in Figure 6.
+Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
 That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.
--->
-
-<!-- ```{r, fig.width=8, fig.height=8, echo=FALSE, fig.cap='xxx'} -->
-
-<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
-<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Property Type'} -->
-
-<!--  type.table <- rbind(apt$mrkt.score, house$mrkt.score) -->
-<!--  type.table$property.type <- c('apartment', '', 'house', '') -->
-<!--  type.table <- type.table[,c(5,1:4)] -->
-<!--  names(type.table) <- c('Property Type', 'Actual', 'Fitted', 'SVM Area') -->
-<!--  print(xtable(type.table, caption='Short-term Preference Analysis: By Property Type\n', -->
-<!--        digits=3), -->
-<!--        include.rownames=FALSE, hline.after=c(-1,0,2,4), -->
-<!--        caption.placment='top') -->
-
-<!-- ``` -->
-
-<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Houses'} -->
-
-<!-- ggMultiPlots(house$qtl.hm, house$qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', , fig.cap='Analysis of Quantile Rates: Apartment'} -->
-
-<!-- ggMultiPlots(apt$qtl.hm, apt$qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Quantile Market Summary; Property Type by Submarket'} -->
-
-<!-- sm.ms <- rbind.fill(lapply(sm.results, function(x) x$mrkt.score[2,])) -->
-<!-- sm.ms.apt <- rbind.fill(lapply(smt.results[1:5], function(x) x$mrkt.score[2,])) -->
-<!-- sm.ms.house <- rbind.fill(lapply(smt.results[6:10], function(x) x$mrkt.score[2,])) -->
-
-<!-- smt.table <- data.frame(sub.market=c('sub-market','beach', 'city', 'core', 'rural', -->
-<!--                                      'suburban', 'all'), -->
-<!--                         actual.all=c('all', round(sm.ms$actual[c(5,2,1,4,3)],2), -->
-<!--                                      round(market.ratio[2,2],2)), -->
-<!--                         actual.apt=c('apt', round(sm.ms.apt$actual, 2), -->
-<!--                                      round(type.table[2,3],2)), -->
-<!--                         actual.house=c('house', round(sm.ms.house$actual, 2), -->
-<!--                                        round(type.table[4,3],2)), -->
-<!--                         fitted.all=c('all',round(sm.ms$fitted[c(5,2,1,4,3)],2), -->
-<!--                                      round(market.ratio[2,3],2)), -->
-<!--                         fitted.apt=c('apt', round(sm.ms.apt$fitted,2), -->
-<!--                                      round(type.table[2,4],2)), -->
-<!--                         fitted.house=c('house', round(sm.ms.house$fitted,2), -->
-<!--                                        round(type.table[4,4],2)), -->
-<!--                         svmarea.all=c('all', round(sm.ms$svm[c(5,2,1,4,3)],2), -->
-<!--                                       round(market.ratio[2,4],2)), -->
-<!--                         svmarea.apt=c('apt', round(sm.ms.apt$svm,2), -->
-<!--                                       round(type.table[2,5],2)), -->
-<!--                         svmarea.house=c('house', round(sm.ms.house$svm,2), -->
-<!--                                         round(type.table[4,5],2))) -->
-
-<!-- smt.table <- smt.table[c(1, 4, 3, 2, 6, 5, 7),] -->
-<!-- names(smt.table) <- c('', '', 'actual', '', '', 'fitted', '', '', -->
-<!--                       'svm area', '') -->
-<!-- smt.full <- xtable(smt.table, -->
-<!--                    caption='Short-Term Preference Analysis: Disaggregated\n') -->
-<!-- align(smt.full) <- 'll|rrr|rrr|rrr' -->
-<!-- print(smt.full,  -->
-<!--        include.rownames=FALSE,  -->
-<!--        hline.after=c(-1,0,1,6,7,7), -->
-<!--                    caption.placement='top') -->
-
-<!-- ``` -->
+
+```{r message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
+
+ # Make Basic comparison table
+  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                   split.field='sub.mrkt')
+
+ # Convert to wide format for output
+  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
+
+ # Limit to the extrapolated pref type
+  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
+  pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
+  pref.table[,2] <- pref.table[,2]*100
+
+  names(pref.table) <- c('Sub-Market', '% Short Term Preferable')
+  options(xtable.comment = FALSE)
+  print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n',
+               digits=1),
+               include.rownames=FALSE,
+               caption.placement='top')
+
+```
+
+There is a noticable variability in the relationship between occupancy rates and short-term prefernce across the submarkets.
+For raw rates (Figure 14, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
+This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city.
+Transforming to quantiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the other, with suburban and city as the most difficult markets.
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+
+  cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
+  city.id <- which(str.data.ic$sub.mrkt == 'city')
+  sub.id <- which(str.data.ic$sub.mrkt == 'suburban')
+  rural.id <- which(str.data.ic$sub.mrkt == 'rural')
+  beach.id <- which(str.data.ic$sub.mrkt == 'beach')
+
+  subm.data.ic <- str.data.ic
+
+  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
+      subm.data.ic$occ.rate[city.id], return.type='rank')
+  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
+    subm.data.ic$med.rate[city.id], return.type='rank')
+
+  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
+                                  return.type='rank')
+
+```
+
+```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)] 
+  smrocc <- abbPrefPlot(subm.data.ic,
+                         x.field='occ.rate',
+                         split.field='sub.mrkt',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=sm.col)
+
+  smr.occ <- ggplot(smrocc$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_color_manual(values=sm.col,
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  smqocc <- abbPrefPlot(subm.data.ic,
+                         x.field='occ.qtl',
+                         split.field='sub.mrkt',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=sm.col)
+
+  smq.occ <- ggplot(smqocc$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Quantile)') +
+    scale_color_manual(values=sm.col,
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Quantile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggMultiPlots(smr.occ, smq.occ, cols=2)
+```
+
+Plotting out the nigthly rate versus occupancy rate heat maps for all five geographic submarkets tells a similar story.
+The 'City-Core' market offers the most potential for short term prefernce with suburban and city the least.
+The rural market achieves very sold short-term preference for the most expensive home, again likely those with special amenities or links to the wine region.
+Beach properties do not perform as well as might be expected in the short term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+
+  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+                                          'city-core', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none') +
+    ylab('') +
+    xlab('') +
+  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
+
+    city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+                                          'city', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "City", size=9)
+
+      sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+                                          'suburban', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
+
+      rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+                                          'rural', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Rural", size=9)
+
+      beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+                                          'beach', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Beach", size=9)
+
+```
+
+```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='xxx'}
+
+  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
+               rural.hm.svm, beach.hm.svm, cols=2)
+
+```
 

### 2017-03-06 abb_Writeup.Rmd
logit model tables and chunk cleanup

@@
 author: "Andy Krause and Gideon Aschwanden"
-header-includes:
-    - \usepackage{setspace}\doublespacing
 date: "February 17, 2017"
@@
   html_document: default
+header-includes: \usepackage{setspace}\doublespacing
 geometry: margin=3.3cm
@@
    load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
-a <- 1
 
@@
 
-```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
-```
-
-```{r load_ptplot, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
+&nbsp;
+
+```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
 
@@
 ```
+
+&nbsp;
 
@@
 
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}
+&nbsp;
+
+```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals', fig.lp='ltcomp'}
 
@@
 
-```{r bb_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type'}
+&nbsp;
+
+```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type', fig.lp='bbcomp'}
 
@@
 
-```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}
+&nbsp;
+
+```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}
 
@@
 
-```{r locmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets'}
+&nbsp;
+
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets', fig.lp='submap'}
 
@@
 
+&nbsp;
+
 It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
@@
 
-```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
+&nbsp;
+
+```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='List of Core Suburbs', fig.lp='coresuburbs'}
 
@@
 
+&nbsp;
+
 We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
@@
 
-```{r loc.plots, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}
+&nbsp;
+
+```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps', fig.lp='locmaps'}
 
@@
 
+&nbsp;
+
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
@@
 
-```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts'}
+&nbsp;
+
+```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts', fig.lp='locbars'}
 
@@
 
-```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
+&nbsp;
+
+```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary', fig.lp='cleansumm'}
 
@@
 
+&nbsp;
+
 ## Revenues, More Explanation
@@
 
-```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
+&nbsp;
+
+```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions', fig.lp='revdens'}
 
@@
 
+&nbsp;
+
 #### Classifying Hosts
@@
 from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
+
 If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right.
 The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
+
 There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property.
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+&nbsp;
+
+```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5}
+```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
 
+```
+
+```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Blocking Tendencies', fig.lp='hostblock'}
+
 ggMultiPlots(host.block.freq, block.rate.period, cols=2)
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+&nbsp;
+
+```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
                                       'Multi-Platform User', 'Unknown'))
+```
+
+```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
                       plot.title = element_text(hjust = 0.5))+
-                guides(colour = guide_legend(override.aes = list(size=3,
-                                                                 alpha=1)))
+                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
+
+```
+
+```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
 
@@
 
+```
+
+```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Categories', fig.lp='hosttypes'}
+
 ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}
+&nbsp;
+
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.caption='Host Type Counts', fig.lp='hostbar'}
 
@@
 host.type.bar
-```
+
+```
+
+&nbsp;
 
@@
 As a matter of reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 Along with occupancy rates, the other important consideration is the nightly rate.
@@
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 10 may be misleading.
@@
 For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
+
+&nbsp;
 
@@
 
+&nbsp;
+
+\pagebreak
+
 ### Submarkets
@@
 Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preferenc.e
+
+&nbsp;
 
@@
 
+&nbsp;
+
 Extending this analysis to also include nightly rates shows a similar situation (Figure 13).
@@
 A median nightly rate requires a 70\% occupancy rate for short-term prefernce likelihood.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 #### By Geography
@@
 That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 There is a noticable variability in the relationship between occupancy rates and short-term prefernce across the submarkets.
@@
 Transforming to quantiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the other, with suburban and city as the most difficult markets.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 Plotting out the nigthly rate versus occupancy rate heat maps for all five geographic submarkets tells a similar story.
@@
 Beach properties do not perform as well as might be expected in the short term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
+
+&nbsp;
 
@@
 
+&nbsp;
+
 ## Explaining Preference
 
-<!-- The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually  more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
-This proportion, however, varied by location and property type.
+The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
+This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-erm preference.
 While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
 To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
--->
-
-<!-- We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of: -->
-
-<!-- \begin{equation} -->
-<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon -->
-<!-- \end{equation} -->
-
-<!-- where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
--->
-
-<!-- For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.  -->
-
-<!-- \begin{equation} -->
-<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon -->
-<!-- \end{equation} -->
-
-<!-- Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts: -->
-
-<!-- \begin{equation} -->
-<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + -->
-<!-- \beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon -->
-<!-- \end{equation} -->
-
-<!-- where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
+
+We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of:
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon
+\end{equation}
+
+where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+
+For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon
+\end{equation}
+
+Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts:
+
+\begin{equation}
+ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + 
+\beta_{2} BedBath + \beta_{3} SubMrkt +
+\beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon
+\end{equation}
+
+where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
 We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
 We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).
--->
-
-<!-- The results of all three models are shown in Table 7.
+
+The results of all three models are shown in Table 7.
 For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
--->
-
-<!-- In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
+
+In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
 Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference.
--->
-
-<!-- Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
+
+Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
 These findings mirror those found above in Table 9.
 The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
--->
-
-<!-- Finally, in Model 3 we add in host behavior or policies.
+
+Finally, in Model 3 we add in host behavior or policies.
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
@@
 Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.
--->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'} -->
-
-<!--  names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
-<!--  x.full <- xtable(full.table, -->
-<!--                   caption='Logistic Modeling Results\n') -->
-<!--  align(x.full) <- 'lllll' -->
-
-<!--  print(x.full,  -->
-<!--        include.rownames=FALSE,  -->
-<!--        hline.after=c(-1,0,15,20,20),  -->
-<!--        caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- \pagebreak -->
+
+&nbsp;
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
+
+ m1 <- as.data.frame(summary(pref.models[[1]])$coefficients)
+ m2 <- as.data.frame(summary(pref.models[[2]])$coefficients)
+ m3 <- as.data.frame(summary(pref.models[[3]])$coefficients)
+
+ makeStatSig <- function(x){
+   x <- as.numeric(x)
+   y <- rep('***', length(x))
+   y[x>.01] <- '** '
+   y[x>.05] <- '*  '
+   y[x>.1] <- '   '
+   y
+ }
+ m1sig <- makeStatSig(m1[,4])
+ m2sig <- makeStatSig(m2[,4])
+ m3sig <- makeStatSig(m3[,4])
+
+ m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''), 
+                         sprintf('%.3f', round(m1$Estimate,3)),
+                         m1sig)
+ m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(m2$Estimate,3)),
+                         m2sig)
+ m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(m3$Estimate,3)),
+                         m3sig)
+
+ m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
+ m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2)))
+ m3c <- m3$table.coef
+
+ full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
+ names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+ full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
+                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
+                          '4 Bed & 2 Bath', 'City (Submarket)',
+                          'Suburban (Submarket)', 'Rural (Submarket)', 
+                          'Beach (Submarket)', 'Guests per Bedroom', 
+                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
+
+ ## Create model diagnostics
+
+  # Custom function
+  logDx <- function(log.model, data, resp.var){
+
+    pred <- prediction(predict(log.model, data, type='response'), resp.var)
+    auc <- performance(pred, measure='auc')
+    ll <- logLik(log.model)
+    AIC <- AIC(log.model)
+
+    return(list(AIC=AIC,
+                logLik=ll,
+                auc=auc))
+  }
+
+  # Extract diagnostics
+  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
+  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.ext.pref)
+  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.ext.pref)
+
+  # Create diagnostic table
+  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
+                                      'AUC'),
+                           Str.Model=c('', '', round(str.dx$AIC,0), 
+                                       round(str.dx$logLik, 0),
+                                       round(as.numeric(str.dx$auc@y.values),
+                                             3)),
+                           Sm.Model=c('', '', round(sm.dx$AIC,0), 
+                                      round(sm.dx$logLik, 0),
+                                      round(as.numeric(sm.dx$auc@y.values), 3)),
+                           Host.Model=c('', '', round(host.dx$AIC,0), 
+                                        round(host.dx$logLik, 0),
+                                        round(as.numeric(host.dx$auc@y.values),
+                                              3)))
+  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+
+ ## Combine into full table of coef and diags
+  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)
+
+ full.table <- rbind(full.table, diag.table)
+
+ x.full <- xtable(full.table,
+                  caption='Logistic Modeling Results\n')
+ align(x.full) <- 'lllll'
+
+ print(x.full,
+       include.rownames=FALSE,
+       hline.after=c(-1,0,15,20,20),
+       caption.placement='top')
+
+```
+
+&nbsp;
+
+### Sensitivity Tests
+
+#### Potential Revenue
+
+Look at difference if using potential revenue
+
+-- Show differences in global numbers and heat maps
+-- Re-do the logistic models with potential revenue
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+
+ pm1 <- as.data.frame(summary(pref.models[[4]])$coefficients)
+ pm2 <- as.data.frame(summary(pref.models[[5]])$coefficients)
+ pm3 <- as.data.frame(summary(pref.models[[6]])$coefficients)
+
+ pm1sig <- makeStatSig(pm1[,4])
+ pm2sig <- makeStatSig(pm2[,4])
+ pm3sig <- makeStatSig(pm3[,4])
+
+ pm1$table.coef <- paste0(ifelse(pm1$Estimate>0, ' ', ''), 
+                         sprintf('%.3f', round(pm1$Estimate,3)),
+                         pm1sig)
+ pm2$table.coef <- paste0(ifelse(pm2$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(pm2$Estimate,3)),
+                         pm2sig)
+ pm3$table.coef <- paste0(ifelse(pm3$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(pm3$Estimate,3)),
+                         pm3sig)
+
+ pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1)))
+ pm2c <- c(pm2$table.coef, rep(' ', nrow(pm3)-nrow(pm2)))
+ pm3c <- pm3$table.coef
+
+ pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
+ names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+ pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
+                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
+                          '4 Bed & 2 Bath', 'City (Submarket)',
+                          'Suburban (Submarket)', 'Rural (Submarket)', 
+                          'Beach (Submarket)', 'Guests per Bedroom', 
+                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
+
+ ## Create model diagnostics
+
+  # Extract diagnostics
+  pstr.dx <- logDx(pref.models[[4]], str.data.ic, str.data.ic$str.pot.pref)
+  psm.dx <- logDx(pref.models[[5]], str.data.ic, str.data.ic$str.pot.pref)
+  phost.dx <- logDx(pref.models[[6]], str.data.ic, str.data.ic$str.pot.pref)
+
+  # Create diagnostic table
+  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
+                                      'AUC'),
+                           Str.Model=c('', '', round(pstr.dx$AIC,0), 
+                                       round(pstr.dx$logLik, 0),
+                                       round(as.numeric(pstr.dx$auc@y.values),
+                                             3)),
+                           Sm.Model=c('', '', round(psm.dx$AIC,0), 
+                                      round(psm.dx$logLik, 0),
+                                      round(as.numeric(psm.dx$auc@y.values),
+                                            3)),
+                           Host.Model=c('', '', round(phost.dx$AIC,0), 
+                                        round(phost.dx$logLik, 0),
+                                        round(as.numeric(phost.dx$auc@y.values),
+                                              3)))
+  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+
+ ## Combine into full table of coef and diags
+  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)
+
+ pfull.table <- rbind(pfull.table, pdiag.table)
+
+ px.full <- xtable(pfull.table,
+                   caption='Logistic Modeling Results\n')
+ align(px.full) <- 'lllll'
+
+ print(px.full,
+       include.rownames=FALSE,
+       hline.after=c(-1, 0, 15, 20, 20),
+       caption.placement='top')
+
+```
+
+#### Host Classification
+
+Look at difference if breaking down by host type
+-- Show new numbers and heat maps
+-- Re-do logistic models, extrapolate but divided by hosts
+
+Note that ability to examine different facets of the data is coming to an interactive website soon.
+
+\pagebreak
 

### 2017-03-06 abbDataAnalysis_Script.Rmd
change model specifications

@@
 
+  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
+                                levels=c('1..1', '2..1', '2..2',
+                                         '3..1', '3..2', '4..2'))
+
   mod.ext.str <- glm(str.ext.pref~type+as.factor(bedbath),
@@
   mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
-                        sub.mrkt+as.factor(host.type)+
+                        sub.mrkt+
                         I(max.guests/bedrooms)+min.stay+
@@
   mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
-                        sub.mrkt+as.factor(host.type)+
+                        sub.mrkt+
                         I(max.guests/bedrooms)+min.stay+

### 2017-03-07 abb_Functions.R
fix 0 binary bug

@@ -971,6 +971,9 @@ makeSVM <- function(svm.data,
   # Create XY data
   xy.data <- cbind(svm.data[,x.field], svm.data[,y.field])
   
+  # Hack if all 0s
+  if(sum(svm.data[,z.field]) == 0) svm.data[1,z.field] <- 1
+  
   # Specificy SVM
   svm.obj <- ksvm(x=xy.data,
                   y=svm.data[,z.field],

### 2017-03-07 abb_Writeup.Rmd
adding sensitivity plots

@@
 -- Show differences in global numbers and heat maps
+
+53.3%
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+
+  pot.data.ic <- str.data.ic
+
+  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
+
+  pqtl.hm <- abbHeatMap(pot.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.pot.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
+
+  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.pot.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Qtl)')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preferencexxx', fig.lp='xxxx'}
+
+  ggMultiPlots(pqtl.hm, pqtl.hm.svm, cols=2)
+
+```
+
 -- Re-do the logistic models with potential revenue
@@
 
+Ext is what is happening, potential is what could happening
+
 #### Host Classification
@@
 Look at difference if breaking down by host type
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Make Basic comparison table
+  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                   split.field='host.type')
+
+ # Convert to wide format for output
+  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
+
+ # Limit to the extrapolated pref type
+  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+
+  host.data.ic <- str.data.ic
+
+  ps <- which(str.data.ic$host.type == 'Profit Seeker')
+  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
+  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
+  un <- which(str.data.ic$host.type == 'Unknown')
+
+  host.data.ic$occ.qtl[ps] <- makeWtdQtl(
+      host.data.ic$occ.rate[ps], return.type='rank')
+  host.data.ic$rate.qtl[ps] <- makeWtdQtl(
+    host.data.ic$med.rate[ps], return.type='rank')
+
+  host.data.ic$occ.qtl[os] <- makeWtdQtl(
+      host.data.ic$occ.rate[os], return.type='rank')
+  host.data.ic$rate.qtl[os] <- makeWtdQtl(
+    host.data.ic$med.rate[os], return.type='rank')
+
+  host.data.ic$occ.qtl[mu] <- makeWtdQtl(
+      host.data.ic$occ.rate[mu], return.type='rank')
+  host.data.ic$rate.qtl[mu] <- makeWtdQtl(
+    host.data.ic$med.rate[mu], return.type='rank')
+
+  host.data.ic$occ.qtl[un] <- makeWtdQtl(
+      host.data.ic$occ.rate[un], return.type='rank')
+  host.data.ic$rate.qtl[un] <- makeWtdQtl(
+    host.data.ic$med.rate[un], return.type='rank')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx55'}
+
+  ps.raw.hm.svm <- abbHeatMap(host.data.ic[ps, ],
+                   x.field='occ.rate',
+                   y.field='med.rate',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=F,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  ps.raw.hm.svm <- ps.raw.hm.svm + ylab('Nightly Rate')
+
+  ps.qtl.hm.svm <- abbHeatMap(host.data.ic[ps, ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  ps.qtl.hm.svm <- ps.qtl.hm.svm + ylab('Nightly Rate (Qtl)')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx44'}
+
+ggMultiPlots(ps.raw.hm.svm, ps.qtl.hm.svm, cols=2)
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx33'}
+
+  os.raw.hm.svm <- abbHeatMap(host.data.ic[os, ],
+                   x.field='occ.rate',
+                   y.field='med.rate',
+                   pref.field='str.ext.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=F,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  os.raw.hm.svm <- os.raw.hm.svm + ylab('Nightly Rate')
+
+  os.qtl.hm.svm <- abbHeatMap(host.data.ic[os, ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  os.qtl.hm.svm <- os.qtl.hm.svm + ylab('Nightly Rate (Qtl)')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx22'}
+
+ggMultiPlots(os.raw.hm.svm, os.qtl.hm.svm, cols=2)
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx11'}
+
+  mu.raw.hm.svm <- abbHeatMap(host.data.ic[mu, ],
+                   x.field='occ.rate',
+                   y.field='med.rate',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=F,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  mu.raw.hm.svm <- mu.raw.hm.svm + ylab('Nightly Rate')
+
+  mu.qtl.hm.svm <- abbHeatMap(host.data.ic[mu, ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  mu.qtl.hm.svm <- mu.qtl.hm.svm + ylab('Nightly Rate (Qtl)')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx1'}
+
+ggMultiPlots(mu.raw.hm.svm, mu.qtl.hm.svm, cols=2)
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx2'}
+
+  un.raw.hm.svm <- abbHeatMap(host.data.ic[un, ],
+                   x.field='occ.rate',
+                   y.field='med.rate',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=F,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  un.raw.hm.svm <- un.raw.hm.svm + ylab('Nightly Rate')
+
+  un.qtl.hm.svm <- abbHeatMap(host.data.ic[un, ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.ext.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  un.qtl.hm.svm <- un.qtl.hm.svm + ylab('Nightly Rate (Qtl)')
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx23'}
+
+ggMultiPlots(un.raw.hm.svm, un.qtl.hm.svm, cols=2)
+
+```
+
 -- Show new numbers and heat maps
@@
 
+vertical SVM lines suggest occ rate is biggest issue.  
 <!-- <!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.

### 2017-03-07 abb_Writeup.Rmd
add sensitivity, conclusions

--- 2017-03-06 abb_Writeup.Rmd
@@
 
-#### Classifying Hosts
-
-As the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.
-There may be, therefore, different types of hosts operating in the Airbnb market.
-from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-
-If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right.
-The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
-
-There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property.
-A potential method to identify these hosts is to look at the number of individual periods of blocked days.
-A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
-We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9.
-We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.
-
-&nbsp;
-
-```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
-  geom_density(fill=str.col, color=str.col) +
-  ylab('Frequency\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0,1,.2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Host Block Rate Frequency\n') +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-```
-
-```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
-  geom_point(fill=str.col, color=str.col, size=.2) +
-  ylab('Nbr of Blocked Periods\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Blocking Tendencies', fig.lp='hostblock'}
-
-ggMultiPlots(host.block.freq, block.rate.period, cols=2)
-
-```
-
-&nbsp;
-
-Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories.
-As a more subjective approach, we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
-Profit seekers are those host who have blocked percentages less than 25\% of the time.
-Opportunistic Sharers have blocked their properties at least 75\% of the time.
-Within those two extremes, we consider users who have at least 12 blocked periods during a year to be 'Multi-Platform Users' and the remaining set to be 'Unknown'.
-See Figure 10 for a breakdown of these group by the two variables.
-
-&nbsp;
-
-```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
-
-str.data$host.type <- 'Unknown'
-str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
-str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
-str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
-str.data$host.type <- factor(str.data$host.type,
-                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                      'Multi-Platform User', 'Unknown'))
-```
-
-```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-base.host <- ggplot(str.data, 
-                    aes(x=block.rate, y=blockpertime)) + 
-                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
-                ylab('# Blckd Periods\n') + 
-                xlab('\n% of Time Property is Blocked') +
-                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-                scale_x_continuous(breaks=seq(0, 1, .2),
-                                   labels=c('0%', '20%', '40%', 
-                                            '60%', '80%', '100%')) +
-                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
-                #                            abb.col[7], abb.col[9])) + 
-                theme(legend.position='bottom',
-                      legend.title = element_blank(),
-                      plot.title = element_text(hjust = 0.5))+
-                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
-
-```
-
-```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
-
-ps.host <- base.host + 
-  geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
-  ggtitle('Profit Seekers')
-os.host <- base.host + 
-  geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
-             size=.4)  +
-  ggtitle('Opportunistic Sharer')
-mu.host <- base.host + 
-  geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
-             size=.4)  +
-  ggtitle('Multi-Platform User')
-un.host <- base.host + 
-  geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
-  ggtitle('Unknown')
-
-```
-
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Categories', fig.lp='hosttypes'}
-
-ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
-
-```
-
-&nbsp;
-
-Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
-The remainder 'Unknown' category contains just over 28\% of all properties.
-The classification of these hosts is not convincing enough to base our entire analytical process on so we will use these breakdowns to add context to the results and to test the sensitivity of our results to the assumptions underlying the extrapolated and potential revenue calculations.
-
-&nbsp;
-
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.caption='Host Type Counts', fig.lp='hostbar'}
-
-host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
-  geom_bar() +
-  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-  theme(legend.position='none') +
-  ylab('Frequency\n') + 
-  xlab('\nHost Type') +
-  ggtitle('Short Term Host Types') + 
-  theme(plot.title = element_text(hjust = 0.5))
-
-host.type.bar
-
-```
-
-&nbsp;
-
 ## Comparison
@@
 
-The results of all three models are shown in Table 7.
-For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.
+The results of all three models are shown in Table 4.
+For $PType$ apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ `Moderate' is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
 
-In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.
-Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference.
-
-Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.
-These findings mirror those found above in Table 9.
-The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
+In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
+There is very little significant difference between 1 bed / 1 bath units and the remaining categories, with the exception of 2 bed / 2 bath.
+This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
+Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity on holiday than in day-to-day living.
+
+Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core(the reference category) when controlling for structural characteristics.
+The difference between the Rural and City-Core is not significant, however,  The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
+The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.
+This is likely due to the fact that houses are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.
 
@@
 Strict policies do help maintain revenues, but may also scare off some potential guests.
-Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.
+Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
 
@@
 
+To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
+First, we examine how the results changes if potential revenue, not observed revenue, of the short-term properties is used in the comparisons.
+Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothetical motivations and actions of the hosts.
+
 #### Potential Revenue
 
-Look at difference if using potential revenue
-
--- Show differences in global numbers and heat maps
--- Re-do the logistic models with potential revenue
+The above uses the observed^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
+Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to the treatment of blocked days.
+If we, instead, assume that blocked days could be leased out on the short-term market at the same overall occupancy rate as the unblocked (observed) days we can produce a potential revenue figure.
+Note that it is possible (likely?) that the large oversupply of available units onto the market that would happen if no properties blocked their units would decrease both prices and occupancy rates.
+We do not attempt to correct for this likelihood, rather we offer these figures as high end estimates.
+
+Using the potential revenue, 53.3% of all properties are short-term preferable.
+Breaking that down by type and by geographic submarket shows similar finding to the actual revenue analysis above.
+Apartments have a higher short-term preference than do Houses and City-Core properties dominate the other geographic regions.
+One notable difference here is that the Rural properties perform rather poorly under a potential revenue scenario, relatively speaking, suggesting that they may be operating near their peak in the current condition.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+
+ # Make Basic comparison table
+  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='type')
+
+  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
+  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='sub.mrkt')
+
+  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
+  st.table <- rbind(tpref.table, spref.table)
+  st.table[,2] <- st.table[,2]*100
+  names(st.table) <- c('Sub-Market', '% Short Term Preferable')
+  options(xtable.comment = FALSE)
+  print(xtable(st.table[,1:2], 
+               caption='Potential Revenue Preferability\n',
+               digits=1),
+               include.rownames=FALSE,
+               caption.placement='top',
+               hline.after=c(-1, 0, 2, 7, 7))
+
+```
+
+Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, Figure 19) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combination that lead to short-term preference.
+Under a potential revenue scenario, a median occupancy rate and median nightly rate is results in greater than 50\% chance of short-term preference.
+Even with very low nightly rates (10th percentile), an occupancy rate around the 65th percentile will achieve short-term prefernce likelihood.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+
+  pot.data.ic <- str.data.ic
+
+  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
+
+  pqtl.hm <- abbHeatMap(pot.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.pot.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
+
+  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.pot.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Qtl)')+
+  annotate("text", x = 50, y = 50, label = "Potential", size=9)
+
+  qtl.hm.svm.p <- qtl.hm.svm +
+  annotate("text", x = 50, y = 50, label = "Actual", size=9)
+
+```
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preferencexxx', fig.lp='xxxx'}
+
+  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
+
+```
+
+Our final test of the potential revenue is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
+Generally speaking, the results from the new series of models (Table 6) are qualitatively similar to those derived in teh Actual revenue case (Table 4).
+The overall magnitude of the coefficient for House (vs Apartments) is lowered in the Potential case, suggesting that houses may be blocked off more that Apartments.
+The product types (bed/bath) show similar trends, though with larger discounts for the 2 Bed / 1 Bath and 2 Bed/2 Bath units.
+Likewise the geographic submarkets and host policies show similar effects in terms of direction with some slight deviations in magnitude.
 
@@
 
+Overall, the choice of revenue type, Actual or Potential, does affect some of the conclusions to be derived from the results above.
+As expected, under the Potential case there are more properties (50\% vs 27\%) that exhibit short-term preference.
+Under the scenario, the possibilities of increasing revenue by moving from long to short term leasing appear much better.
+Again, however, we have not attempted to measure or estimate how this flood of properties onto the market (due to the elimation of blocked days) would impact overall market dynamics.
+Suffice it to say that it would like drive down occupancies and maybe price, therefore leading to a decrease in short-term preference likelihood.
+
+In explaining the drivers of short-term preference, the logistic regression models do not change materially with the switch in dependent variable.
+This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate, only the base probability of short-term preference increases.
+
+More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for leasing for the entire calendar year and the remainder of the market does not do so.
+
 #### Host Classification
 
-Look at difference if breaking down by host type
--- Show new numbers and heat maps
--- Re-do logistic models, extrapolate but divided by hosts
-
-Note that ability to examine different facets of the data is coming to an interactive website soon.
+As hinted at above in the Actual versus Potential comparison and as indicated in the logistic regression models in Tables 5 and 6, host behavior may be an important determinant of achieving short-term preference.
+Additionally, as the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.
+There may be, therefore, different types of hosts operating in the Airbnb market.
+from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
+
+If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right.
+The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
+
+There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property.
+A potential method to identify these hosts is to look at the number of individual periods of blocked days.
+A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
+We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9.
+We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.
+
+&nbsp;
+
+```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
+  geom_density(fill=str.col, color=str.col) +
+  ylab('Frequency\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0,1,.2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Host Block Rate Frequency\n') +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+```
+
+```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  geom_point(fill=str.col, color=str.col, size=.2) +
+  ylab('Nbr of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Blocking Tendencies', fig.lp='hostblock'}
+
+ggMultiPlots(host.block.freq, block.rate.period, cols=2)
+
+```
+
+&nbsp;
+
+Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories.
+As a more subjective approach, we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
+Profit seekers are those host who have blocked percentages less than 25\% of the time.
+Opportunistic Sharers have blocked their properties at least 75\% of the time.
+Within those two extremes, we consider users who have at least 12 blocked periods during a year to be 'Multi-Platform Users' and the remaining set to be 'Unknown'.
+See Figure 10 for a breakdown of these group by the two variables.
+
+&nbsp;
+
+```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
+
+str.data$host.type <- 'Unknown'
+str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
+str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
+str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
+str.data$host.type <- factor(str.data$host.type,
+                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                      'Multi-Platform User', 'Unknown'))
+```
+
+```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+base.host <- ggplot(str.data, 
+                    aes(x=block.rate, y=blockpertime)) + 
+                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
+                ylab('# Blckd Periods\n') + 
+                xlab('\n% of Time Property is Blocked') +
+                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+                scale_x_continuous(breaks=seq(0, 1, .2),
+                                   labels=c('0%', '20%', '40%', 
+                                            '60%', '80%', '100%')) +
+                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
+                #                            abb.col[7], abb.col[9])) + 
+                theme(legend.position='bottom',
+                      legend.title = element_blank(),
+                      plot.title = element_text(hjust = 0.5))+
+                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
+
+```
+
+```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+ps.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
+  ggtitle('Profit Seekers')
+os.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
+             size=.4)  +
+  ggtitle('Opportunistic Sharer')
+mu.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
+             size=.4)  +
+  ggtitle('Multi-Platform User')
+un.host <- base.host + 
+  geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
+  ggtitle('Unknown')
+
+```
+
+```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Categories', fig.lp='hosttypes'}
+
+ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
+
+```
+
+&nbsp;
+
+Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
+The remainder 'Unknown' category contains just over 28\% of all properties.
+The classification of these hosts is not convincing enough to base our entire analytical process on so we will use these breakdowns to add context to the results and to test the sensitivity of our results to the assumptions underlying the extrapolated and potential revenue calculations.
+
+&nbsp;
+
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.caption='Host Type Counts', fig.lp='hostbar'}
+
+host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
+  geom_bar() +
+  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+  theme(legend.position='none') +
+  ylab('Frequency\n') + 
+  xlab('\nHost Type') +
+  ggtitle('Short Term Host Types') + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+host.type.bar
+
+```
+
+&nbsp;
+
+Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Actual case and a much smaller variation in the Potential case, as expected.
+There is little change for the 'Profit Seekers' as most of these hosts already operating with few blocked days.
+For the other three sets, considerable gains could be had with a more aggresive leasing approach.
+As the potential figures are somewhat similar here, we will only examine the differences in the Actual number going forward.
+
+```{r results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+ # Make Basic comparison table
+  apref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='host.type')
+
+ # Limit to the extrapolated pref type
+  hpref.table <- apref.table[apref.table$rev.type == 'Extrapolated', ]
+  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
+  hpref.table <- hpref.table[,1:2]
+  hpref.table[,3] <- phpref.table[,2]
+  hpref.table[,2] <- hpref.table[,2]*100
+  hpref.table[,3] <- hpref.table[,3]*100
+
+  names(hpref.table) <- c('Host Type', '% STP - Actual', '% STP - Potential')
+  options(xtable.comment = FALSE)
+  print(xtable(hpref.table, 
+               caption='Host Type Preferability\n',
+               digits=1),
+               include.rownames=FALSE,
+               caption.placement='top')
+
+```
+
+Table 9 compares logistic models results from three of the host types.
+The Opportunistic Sharers show no instances of short-term preference and therefore could not be estimated.
+The left hand column, that of the Profit-Seekers, is the most representative of a sample of property owners that are seeking to maximize revenue.
+Overall, the coefficients from this sub-sample match up well to the results from the entire sample shown in Table 5.
+In short, the conclusions are the same: small, apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
+The models for the multi-platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
+
+ h1 <- as.data.frame(summary(host.models[[1]])$coefficients)
+ h2 <- as.data.frame(summary(host.models[[3]])$coefficients)
+ h3 <- as.data.frame(summary(host.models[[4]])$coefficients)
+
+ h1sig <- makeStatSig(h1[,4])
+ h2sig <- makeStatSig(h2[,4])
+ h3sig <- makeStatSig(h3[,4])
+
+ h1$table.coef <- paste0(ifelse(h1$Estimate>0, ' ', ''), 
+                         sprintf('%.3f', round(h1$Estimate,3)),
+                         h1sig)
+ h2$table.coef <- paste0(ifelse(h2$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(h2$Estimate,3)),
+                         h2sig)
+ h3$table.coef <- paste0(ifelse(h3$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(h3$Estimate,3)),
+                         h3sig)
+
+ hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef,
+                                    h2$table.coef, h3$table.coef))
+ names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
+ hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
+                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
+                          '4 Bed & 2 Bath', 'City (Submarket)',
+                          'Suburban (Submarket)', 'Rural (Submarket)', 
+                          'Beach (Submarket)', 'Guests per Bedroom', 
+                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
+
+ ## Create model diagnostics
+
+  # Extract diagnostics
+  hstr.dx <- logDx(host.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
+  hsm.dx <- logDx(host.models[[3]], str.data.ic, str.data.ic$str.ext.pref)
+  hhost.dx <- logDx(host.models[[4]], str.data.ic, str.data.ic$str.ext.pref)
+
+  # Create diagnostic table
+  hdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
+                                      'AUC'),
+                           Str.Model=c('', '', round(hstr.dx$AIC,0), 
+                                       round(hstr.dx$logLik, 0),
+                                       round(as.numeric(hstr.dx$auc@y.values),
+                                             3)),
+                           Sm.Model=c('', '', round(hsm.dx$AIC,0), 
+                                      round(hsm.dx$logLik, 0),
+                                      round(as.numeric(hsm.dx$auc@y.values), 3)),
+                           Host.Model=c('', '', round(hhost.dx$AIC,0), 
+                                        round(hhost.dx$logLik, 0),
+                                        round(as.numeric(hhost.dx$auc@y.values),
+                                              3)))
+  names(hdiag.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
+
+ ## Combine into full table of coef and diags
+  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)
+
+ hfull.table <- rbind(hfull.table, hdiag.table)
+
+ xh.full <- xtable(hfull.table,
+                  caption='Logistic Modeling Results\n')
+ align(xh.full) <- 'lllll'
+
+ print(xh.full,
+       include.rownames=FALSE,
+       hline.after=c(-1,0,15,20,20),
+       caption.placement='top')
+
+```
 
@@
 
-<!-- ## Discussion -->
-
-<!-- <!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+## Discussion
+
+Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
 This work attempts to fill this void.
--->
-
-<!-- The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
+
+The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
 However, of this total, only 6,600 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
@@
 We caution future researchers and policy analysts to look deeply at initial estimates of Airbnb counts as many of the listings on the market are either room shares and/or not active.
--->
-
-<!-- Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
+
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
 However, there is long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, on Airbnb than they would on the long-term market.
@@
 Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
--->
-
-<!-- To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
+
+To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
 The shared information that is available on both sets of properties is limited.
@@
 As a result, we were not able to accurately estimate likely short-term rates for the long-term observations.
--->
-
-<!-- In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
+
+In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
 As expected, this probability is not equal across space, property type or property size (bed and bath count).
@@
 Core city properties are more likely than other properties to prefer a short-term strategy, as are larger properties versus smaller ones.
-For instance, 45\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market.
-Examining only apartments with at least three bedrooms and two baths that figure increases to 60\%.
--->
-
-<!-- The nightly rates and total occupancies drive the profitability of short-term leasing.
+For instance, 35\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market while only 8\% of suburban houses did.
+Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
+
+The nightly rates and total occupancies drive the profitability of short-term leasing.
 As the nightly rate vs.
-occupancy rate heat maps and SVM plots (Figures 16, 17, 18 and 19) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the median in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
+occupancy rate heat maps and SVM plots (Figures 16, 17, 18 and 19) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
 A 40\% occupancy rate means bookings at least three days out of every week all year long.
 In Melbourne summers this may be an easy feat as tourist numbers swell, but doing so on a cold week in July likely proves more difficult.
--->
-
-<!-- The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
-Large apartments in the central city are the best bet for generating greater revenues through short term leasing.
+The verticalness of the divide between short and long term preference in the SVM plots suggests that occupancy rate is critical to reaching short-term preference in most markets.
+
+The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
+Small apartments in the central city are the best bet for generating greater revenues through short term leasing.
 We also test for the impact of host behavior on the probability of short term preference.
@@
 As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
--->
-
-<!-- ### Limitations and Future Research -->
-
-<!-- There are a number of limitations to this research.
+
+Testing for the sensitivity of the initial results through consideration of potential revenue figures and by dividing the sample up by likely host motivation, we find the qualitative finding to be generally robust.
+While the use of potential revenue does increase the base probability of short-term preference, the same factors -- small, inner city apartment with low minimum stays, strict cancellation and liberal guest capacity -- explain a higher likelihood of short-term preference.
+
+In short, about 1/4 of current Airbnb properties are outperforming their potential in the long-term market.
+If owners all operated as profit maximizers this figure could be closer to 50\% or slightly higher, if the overall demand for short-term rental could match the assumed supply increase in such a case.
+
+### Limitations and Future Research
+
+There are a number of limitations to this research.
 There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
@@
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
--->
-
-<!-- Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
+
+Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
 Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
--->
-
-<!-- In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
+
+In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
 We have done so as we were unable to location any evidence to suggest that one was higher than the other.
 This may be a limitation of our study and could prove to be an avenue of future research.
--->
-
-<!-- Beyond airBNB.com other short-term platforms exist (e.g.
+
+Beyond airBNB.com other short-term platforms exist (e.g.
 www.homeaway.com).
@@
 These are additional revenue streams that are not take into account and might increase the occupancy and revenue for short-term rentals.
--->
-
-<!-- Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
+We do suggest that, due to block patterns, a number of host do appear to be employing this approach but cannot confirm the extend to which this is actually happening.
+
+Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
 In reality, the possibilities may not be so rigid.
@@
 We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
--->
 
@@
 <!-- - Does time of purchase (which month) matter? -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'} -->
+
+<!--   host.data.ic <- str.data.ic -->
+
+<!--   ps <- which(str.data.ic$host.type == 'Profit Seeker') -->
+<!--   os <- which(str.data.ic$host.type == 'Opportunistic Sharer') -->
+<!--   mu <- which(str.data.ic$host.type == 'Multi-Platform User') -->
+<!--   un <- which(str.data.ic$host.type == 'Unknown') -->
+
+<!--   host.data.ic$occ.qtl[ps] <- makeWtdQtl( -->
+<!--       host.data.ic$occ.rate[ps], return.type='rank') -->
+<!--   host.data.ic$rate.qtl[ps] <- makeWtdQtl( -->
+<!--     host.data.ic$med.rate[ps], return.type='rank') -->
+
+<!--   host.data.ic$occ.qtl[os] <- makeWtdQtl( -->
+<!--       host.data.ic$occ.rate[os], return.type='rank') -->
+<!--   host.data.ic$rate.qtl[os] <- makeWtdQtl( -->
+<!--     host.data.ic$med.rate[os], return.type='rank') -->
+
+<!--   host.data.ic$occ.qtl[mu] <- makeWtdQtl( -->
+<!--       host.data.ic$occ.rate[mu], return.type='rank') -->
+<!--   host.data.ic$rate.qtl[mu] <- makeWtdQtl( -->
+<!--     host.data.ic$med.rate[mu], return.type='rank') -->
+
+<!--   host.data.ic$occ.qtl[un] <- makeWtdQtl( -->
+<!--       host.data.ic$occ.rate[un], return.type='rank') -->
+<!--   host.data.ic$rate.qtl[un] <- makeWtdQtl( -->
+<!--     host.data.ic$med.rate[un], return.type='rank') -->
+
+<!-- ```     -->
+
+<!-- For the profit-seekers,  -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx55'} -->
+
+<!--   ps.raw.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
+<!--                    x.field='occ.rate', -->
+<!--                    y.field='med.rate', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=F, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   ps.raw.hm.svm <- ps.raw.hm.svm + ylab('Nightly Rate') -->
+
+<!--   ps.qtl.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   ps.qtl.hm.svm <- ps.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx44'} -->
+
+<!-- ggMultiPlots(ps.raw.hm.svm, ps.qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx33'} -->
+
+<!--   os.raw.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
+<!--                    x.field='occ.rate', -->
+<!--                    y.field='med.rate', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=F, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   os.raw.hm.svm <- os.raw.hm.svm + ylab('Nightly Rate') -->
+
+<!--   os.qtl.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   os.qtl.hm.svm <- os.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx22'} -->
+
+<!-- ggMultiPlots(os.raw.hm.svm, os.qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx11'} -->
+
+<!--   mu.raw.hm.svm <- abbHeatMap(host.data.ic[mu, ], -->
+<!--                    x.field='occ.rate', -->
+<!--                    y.field='med.rate', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=F, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   mu.raw.hm.svm <- mu.raw.hm.svm + ylab('Nightly Rate') -->
+
+<!--   mu.qtl.hm.svm <- abbHeatMap(host.data.ic[mu, ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   mu.qtl.hm.svm <- mu.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx1'} -->
+
+<!-- ggMultiPlots(mu.raw.hm.svm, mu.qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx2'} -->
+
+<!--   un.raw.hm.svm <- abbHeatMap(host.data.ic[un, ], -->
+<!--                    x.field='occ.rate', -->
+<!--                    y.field='med.rate', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=F, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   un.raw.hm.svm <- un.raw.hm.svm + ylab('Nightly Rate') -->
+
+<!--   un.qtl.hm.svm <- abbHeatMap(host.data.ic[un, ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.ext.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   un.qtl.hm.svm <- un.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx23'} -->
+
+<!-- ggMultiPlots(un.raw.hm.svm, un.qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->

### 2017-03-08 abb_Writeup.Rmd
review of intro

@@
 author: "Andy Krause and Gideon Aschwanden"
-date: "February 17, 2017"
+date: "March 10, 2017"
 output:
@@
 
-With the rise of Airbnb and other self-hosting accommodation platforms^[Flipkey.com, VRBO.com, Homeaway.com, Tripping.com as examples.], it is easier than ever for property owners and investors to consider short-term rental (STR) as a potential use for a revenue generating residential property.
+With the rise of Airbnb and other self-hosting accommodation platforms^[Flipkey.com, VRBO.com, Homeaway.com, Tripping.com, Stayz.com.au as examples.], it is easier than ever for property owners and investors to consider short-term rental (STR) as a potential leasing strategy for a revenue generating residential property.
 Should they though?
-Or rather, is it more profitable to do so when compared to a more traditional long term rental (LTR)?
-Are certain types of properties and certain locations, if any, more likely to show a preference for (in terms of profitability) short term leasing strategy over long-term.
-
-To address these questions and to provide some guidance to potential and current investors and owners, we examine the residential rental market, both short- and long-term in Melbourne, Australia.
+Or rather, is it more profitable to do so when compared to a more traditional long-term rental (LTR)?
+And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one.
+
+To address these questions and to provide some guidance to potential and current investors and owners, we examine the short- and long-term residential rental market in Melbourne, Australia.
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
-We adopt a scenario-based approach that compares potential annual revenues for properties under both a short-term rental (STR) and a long-term rental (LTR) situation.
-We break the results down by property types (apartments vs houses), product type (e.g.
-1 bed/1 bath) and by location (geographic submarket).
-Our results shows that the feasibility of a greater return through a short term rental -- what we have termed ``Short Term Preference'' -- is dependent on property type, product and location.
+We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues.
+Our results show that the feasibility of a greater return through a short term rental -- what we have termed ``Short Term Preference'' -- is dependent on property type, product, location and host policies.
 In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
@@
 
-```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets', fig.lp='submap'}
-
- load(paste0(fig.path, 'suburbMap.RData'))
-
- loc.map <- loc.map +     
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
- loc.map
-
-```
+<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets', fig.lp='submap'} -->
+
+<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
+
+<!--  loc.map <- loc.map +      -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--  loc.map  -->
+
+<!-- ``` -->
 
@@
 
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps', fig.lp='locmaps'}
-
-  load(paste0(fig.path, 'ltrMap.RData'))
-  load(paste0(fig.path, 'strMap.RData'))
-
-  str.map <- str.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ltr.map <- ltr.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ggMultiPlots(str.map, ltr.map, cols=1)
-
-```
+<!-- ```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps', fig.lp='locmaps'} -->
+
+<!--   load(paste0(fig.path, 'ltrMap.RData')) -->
+<!--   load(paste0(fig.path, 'strMap.RData')) -->
+
+<!--   str.map <- str.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--   ltr.map <- ltr.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--   ggMultiPlots(str.map, ltr.map, cols=1) -->
+
+<!-- ``` -->
 

### 2017-03-08 abb_Writeup.Rmd
review - Lit review

@@
 However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
-Within the extant work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resorts.
-This focus resulted from the fact that the market itself operated almost wholly within this sphere.
+Within the extant work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resort access properties.
+This focus resulted from the fact that, until a few years ago, the STR market itself operated almost wholly within this sphere.
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
@@
 
-A set of recent work has looked into the impact of short-term markets on housing prices and affordability.
+A collection of recent work has looked into the impact of short-term markets on housing prices and affordability.
 These working papers examine the influence of Airbnb on existing housing prices in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2016home].
@@
 In Switzerland, @soguel2008impact test to see if second homes pay a higher premium for ski resort access.
-Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.
-In examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction, finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
-
-Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' @fuller2014stop has re-focused some of the problems of short term rentals on large, urban environments.
+Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two markets.
+In examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
+
+Though issues of second homes have been primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' Fuller and Michel [@fuller2014stop] has re-focused some of the problems of short-term rentals on large, urban environments.
 With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.
@@
 Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].
-Many of the key legal decisions regarding short term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
+Many of the key legal decisions regarding short-term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
 
@@
 Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
-We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term tenure.
+We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term leasing strategy.
 

### 2017-03-08 abb_Writeup.Rmd
review - method

@@
 
-We approach answering the question of whether to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
 More specifically, we examine the following case:
@@
 * They are looking to maximize the net revenue over the 12-month period from September 1, 2015 to August 31, 2016.
-* The choices are 1) traditional year long rental (long term), or: 2) short-term, nightly Airbnb-type rental.
-* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are not considered.
-* As most long-term rentals use a leasing agency, we will assume use of an agency.
+* The choices are 1) traditional year long rental (long-term), or: 2) short-term, nightly Airbnb-type rental.
+* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored.
+* As most long-term rentals in Melbourne use a leasing agency, we will assume use of an agency.
 
 We will not, a priori, specify a location or property type for the scenario as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
-The extent to which location, property type and property characteristics impact the probabilit of short-term preference are examined in the results section.
-
-Australia implements a particular tax policy, often termed `negative gearing', that allows for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
+The extent to which location, property type and property characteristics impact the probability of short-term preference are examined in the results section.
+
+Australia implements a particular tax policy, often termed `negative gearing', that allows for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
 While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
@@
 One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
-As future market trends are unknown at the time of purchase and the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
+As future market trends are unknown at the time of purchase and, within the span of 12 months, the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
 Both long-term rents and short-term rates and occupancy structures will be based on the market conditions as of this date.
@@
 Costs which are equivalent between the two strategies are ignored.
+For short-term properties the net revenue is expressed as:
 
 \begin{equation}
-Rev_{ST} = RevG_{ST} - C_{ST}
+RevN_{ST} = RevG_{ST} - C_{ST}
 \end{equation}
 
-The gross short-term revenue is expressed by:
+where the gross short-term revenue, $RevG_{ST}$, is expressed as:
 
@@
 
-where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. For long-term revenues:
+where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. For long-term rentals the net revenue, $Rev_{LT}$, is defined as:
 
@@
 
-where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.
+where $Rent_{M}$ is the nominal monthly rent and $C_{S}$ are search costs defined in terms of the time (in months) spent to find a long-term tenant.^[Note that such cost are considered here at the revenue stage because they are specific to the revenue generation process and not to the on-going maintenance of the tenancy or property.]
 
 We have limited our consideration of costs in this case to be those undergone during a single year of ownership.
-Broadly speaking, these fall into four categories long-term rental and five for short-term properties.
+Broadly speaking, these fall into four categories for long-term rental and five for short-term properties.
 Long-term costs are summarized as:
@@
 where $T$ are tax related expenses, $M$ are general maintenance expenses, $F$ are financing costs and $L$ are leasing agency fees.
-Short-term properies experience three of the same costs ($T$, $M$ and $F$) plus additional janitorial costs $J$ between each of the short-term occupants as well as property utility costs, $U$ over the course of the year.
+Short-term properies experience three of the same costs ($T$, $M$ and $F$) plus additional janitorial costs, $J$, between each of the short-term occupants as well as property utility costs, $U$, over the course of the year.
 
@@
 Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.].
-Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short or long term rentals.
+Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short- or long-term rentals.
 As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
 
-Leasing costs $L$ are the fees paid to the rental agency to find and manage tenants over the life of the lease.
+Leasing costs $L$ are the fees paid to the rental agency to find and manage tenants over the life of the long-term lease.
 In Melbourne, rates generally range from 5\% to 7\% per annum.
@@
 
-We will consider short-term rental (STR) strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
+We will consider short-term rental (STR) leasting strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
 
@@
 \end{equation}
+
+Though the analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference'.
+For the purposes of this study we consider this a binary position leading to a binary decision of which leasing strategy to follow.
 

### 2017-03-08 abb_Writeup.Rmd
review - data

@@
 Costs which are equivalent between the two strategies are ignored.
-For short-term properties the net revenue is expressed as:
+For short-term properties the net revenue, $RevN_{ST}$, is expressed as:
 
@@
 \begin{equation}
-Rev_{LT} = RevG_{LT} - C_{LT}
+RevN_{LT} = RevG_{LT} - C_{LT}
 \end{equation}
 
-Where $Rev_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the specific costs associated with long-term rental.
+Where $RevN_{LT}$ is the net revenue for a long-term rental, $RevG_{LT}$ is the gross revenue and $C_{LT}$ are the specific costs associated with long-term rental.
 The gross long-term revenue is expressed by:
@@
 \begin{equation}
-Rev_{ST} > Rev_{LT}
+RevN_{ST} > RevN_{LT}
 \end{equation}
@@
 The short-term data include two types of observations, property level and nightly.
-Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
+Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period.^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
 These nightly data indicate the advertised price, the occupancy status and a unique reservation identification.
@@
 There are missing nightly observations during the time period before September 1, 2015.
-After initially imputed these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
+After initially imputing these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
 
-The data on long-term leases was provided by Australia Property Monitors (APM), a Fairfax Group company.
-In raw form, this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
+Data on the long-term rental market was provided by Australia Property Monitors (APM), a Fairfax Group company.
+In raw form this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
 For example, if a property were listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
@@
 
-### Preparation
-
-Here we describe the operations that we have performed to prepare the two sets of raw data for analysis.
-Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions.
+### Data Preparation
+
+Our data preparation primarily involved the filtering out of data errors, outlier values and other observations than contain data that do not fit our research questions.
 Additionally, as our data are from two different sources, a number of fields require standardization so that comparisons between the two leasing strategy options -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
@@
 We begin by filtering observations by time.
-Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an AirBNB-type, short-term rental approach to generating income.
+Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
 To determine the likely LTR rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
@@
 AirBNB units are classified into 19 different property types.
-The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type].
-For the sake of this analysis, we will collapse these twenty types into three types:
-
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
+The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt.^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type] For the sake of this analysis, we will collapse these twenty types into three types:
+
+1. House:  Includes properties labeled 'House' or 'Townhouse'
+2. Apartment: Includes properties labeled as 'Apartment' or 'Condominium'
 3.
-**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
+Other: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
 
@@
 
-1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
-2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+1. House:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+2. Apartment: Includes properties labeled as 'Unit' or 'Studio'
+3. Other: Includes properties labeled as 'Semi' and 'Villa'
 
@@
 This is most apparent when talking about apartment dwellings.
-In Australia these are referred to as Units or Studios, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure)^[Also note that 'Apartment-type' ownership is very rare in Australia.
+In Australia these are referred to as Units or Studios, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).^[Also note that 'Apartment-type' ownership is very rare in Australia.
 Nearly every multi-family dwelling is owned as a condominium.
-See @berry2000investment for more information on the overall structure of the Australian market].
-Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
-
-The **Other** category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (Figure 1) .
-Additionally, a large proportion of the **Others** in the short-term data are Bed & Breakfast units, a use which doesn't fit with our research question.
+See @berry2000investment for more information on the overall structure of the Australian market] Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
+
+The Other category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (\autoref{typecomp}) .
+Additionally, a large proportion of the 'Others' in the short-term data are Bed & Breakfast units, a use which doesn't fit within our research question.
 As a result, we remove the 'Others' from both the short- and the long-term rental data.
@@
 
-```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}
+```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
 
@@
 
-1. **Entire Home/Apt**: The entire home or apartment is available
-2. **Private Room**: One room within a house or apartment is available
-3. **Shared Room**: A bed within a room shared by another occupant(s) is available
-
-As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
-Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable.
-
-&nbsp;
-
-```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals', fig.lp='ltcomp'}
+1. Entire Home/Apt: The entire home or apartment is available
+2. Private Room: One room within a house or apartment is available
+3. Shared Room: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer Private Room or Shared Room options^[Our long-term rental dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
+Unfortunately, this filter does remove about 40% of the short-term data (\autoref{ltypecomp}), however, given the research question it is unavoidable.
+
+&nbsp;
+
+```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}
 
@@
 
- list.types
+ list.types + ggtitle('')
 
@@
 
-We now turn to filtering by structural characteristics.
-As the Airbnb data provides limited information on the structural characteristics, the only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
+The Airbnb data provides limited information on the structural characteristics.
+The only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
 Additionally, as the markets and structural components of houses and apartments differ, we bifurcate our analysis between the two property types from this point forward.
 
-We begin by removing all properties that are missing bedroom or bathroom information or have a likely data error in this fields (more than 14 bedrooms or 10 bathrooms).
-For both short and long term rentals we find that most apartments have fewer than four bedrooms and houses fewer than five.
+We begin by removing all properties that are missing bedroom or bathroom information or have a likely data error in these fields (more than 14 bedrooms or 10 bathrooms).
+For both short- and long-term rentals we find that most apartments have fewer than four bedrooms and houses fewer than five.
 For both property types, the vast majority of properties have three or fewer bathrooms.
@@
 A few short term properties indicate no baths, which is likely an error so we remove these observations from the data.
-Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
-We round the baths in the short term data up to whole integers.
+Also, here we notice that the short-term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
+We round the baths in the short-term data up to whole integers.
 
@@
 In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two (Figure 3).
+As a result we examine the combinations of the two (\autoref{bbtype}).
 From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
@@
 
-```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type', fig.lp='bbcomp'}
+```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure'}
 
@@
 
- stbb <- stbb + ylab('# of Obs')
- ltbb <- ltbb + ylab('# of Obs')
+ stbb <- stbb + ylab('# of Obs') + ggtitle('Short-Term Rentals')
+ ltbb <- ltbb + ylab('# of Obs') + ggtitle('Long-Term Rentals')
 
@@
 
-### Rates and Rental values
-
-Next we filter by the prices -- the nightly rates and weekly rental values.
-The long term rental data have a single price observation, the asking rent at closing.
-For the short term data, there are two indicators of nightly rate.
+### Rates and Rental Values
+
+Next we filter by the prices -- the nightly rates and weekly^[Rents are quoted in weekly values but paid in monthly installments in Melbourne] rental prices.
+The long-term rental data have a single price observation, the asking rent at closing.
+For the short-term data, there are two indicators of nightly rate.
 First, each property has a average nightly rate figure that takes the average of the rates for all booked nights over the October 2014 to August 2016 period.
@@
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high-end neighborhoods in the east and southeastern areas of the middle suburbs.
 Suburbs in Melbourne are much smaller than their North American counterparts.
 The specific suburb of a property is the second, or finer scale, at which the market operates.
-Figure 5 shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-&nbsp;
-
-<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets', fig.lp='submap'} -->
-
-<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
-
-<!--  loc.map <- loc.map +      -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--  loc.map  -->
-
-<!-- ``` -->
+\autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
+
+&nbsp;
+
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='\\label{locmap}Melbourne Submarkets', fig.lp='submap'}
+
+ load(paste0(fig.path, 'suburbMap.RData'))
+
+ loc.map <- loc.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+ loc.map
+
+```
 
@@
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenities for tourists.
-
-&nbsp;
-
-```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='List of Core Suburbs', fig.lp='coresuburbs'}
+All are well served by public transportation and possess abundant amenities for tourists.
+
+&nbsp;
+
+```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs', fig.lp='coresuburbs'}
 
@@
 We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
+This process is repeated for both the short- and long-term data.
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short and long term rentals, colored by submarket, are shown in Figure 6.
+The location of the short- and long-term rentals, colored by submarket, are shown in \autoref{pointmaps}.
 
 Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a latitude and longitudeg value for the centroid of the street that the property faces.
+Half of these do, however, have a latitude and longitude values for the centroid of the street that the property faces.
 To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
@@
 
-<!-- ```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps', fig.lp='locmaps'} -->
-
-<!--   load(paste0(fig.path, 'ltrMap.RData')) -->
-<!--   load(paste0(fig.path, 'strMap.RData')) -->
-
-<!--   str.map <- str.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--   ltr.map <- ltr.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--   ggMultiPlots(str.map, ltr.map, cols=1) -->
-
-<!-- ``` -->
+```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='\\label{pointmaps}Location Maps', fig.lp='locmaps'}
+
+  load(paste0(fig.path, 'ltrMap.RData'))
+  load(paste0(fig.path, 'strMap.RData'))
+
+  str.map <- str.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+  ltr.map <- ltr.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+
+  ggMultiPlots(str.map, ltr.map, cols=1)
+
+```
 
@@
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (Figure 7).
+A number of interesting observations are illustrated here (\autoref{smcounts}).
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
-As expected and as shown by the map, the long term properties are more evenly spread across the metro region than the short term properties.
-Long term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long term markets, are nearly absent in the short-term market.
+As expected and as shown by the map, the long-term properties are more evenly spread across the metro region than the short-term properties.
+Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
+Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
 Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
@@
 
-```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts', fig.lp='locbars'}
+```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts', fig.lp='locbars'}
 
@@
 We have applied ten separate filters to our two datasets.
-In the name of transparency and to highlight the bounds of our research questions it is useful to review these filters (Table 2).
+In the name of transparency and to highlight the bounds of our research question it is useful to review these filters (Table 2).
 There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
@@
 Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
-From these 7,200 properties structural characteristics remove another 480 from consideration.
+From these 7,200 properties structural characteristics filters remove another 480 from consideration.
 Over 1,000 of the remaining properties were never been booked and/or had outlying nightly rates and were removed.
@@
 
-## Revenues, More Explanation
+## Revenues
 

### 2017-03-08 abb_Writeup.Rmd
review - revenues

@@
 
+Within the remainder of this report when we refer to revenues we mean the net revenues from equations 1 and 3, respectively.
 Calculations of revenue for the observed and hypothetical long-term rentals are straightforward, weekly rent -- real or imputed -- times 52 minus search cost time and agency fees.
-For the short-term rental it is somewhat more complicated.
-First, we must deal with those properties that were not listed for the entire 12 month period.
-Our data cleaning eliminated all properties that were listed for less than six months, however, it would be incorrect to compare the revenue of a property listed on Airbnb for seven months with the hypothetical annual revenue from a long term rental.
+For the short-term rentals it is somewhat more complicated.
+First, we must deal with those properties that were not listed for the entire 12-month period.
+Our data cleaning eliminated all properties that were listed for less than six months, however, it would be incorrect to compare the revenue of a property listed on Airbnb for seven months with the hypothetical annual revenue from a long-term rental.
 
@@
 
-1. \textbf{Actual ($REV_a$)}: Observed bookings multiplied by median nightly rate
+1. Observed ($REV_o$)}: Observed bookings multiplied by median nightly rate
 2.
-\textbf{Extrapolated ($REV_e$)}: Observed bookings extrapolated to a full year^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
-3. \textbf{Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
-
-Below we chart the distribution of the Extrapolated ($REV_e$) and Potential ($REV_p$) Short Term revenues against a distribution of the oserved long term revenues for the long term properties.
-Revenues from the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 8).
-Extrapolated short term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
-The range of the distribution for the Potential Short Term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.
+Actual ($REV_a$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
+3. Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
+
+As the observed calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the Actual revenue metric to be a better measure of actual market performance.
+We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long term revenues for the long term properties.
+Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 8).
+Actual short-term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
+The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.
 
@@
 When looking at potential revenues, however, a great deal more may have the potential to produce more revenue.
-The high number of very low yield Airbnb properties in the Extrapoted condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
+The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
 
@@
 
-## Comparison
-
-In this section we compare net revenues between long and short term rental options.
+### Comparison
+
+In this section we compare net revenues between long- and short-term rental options.
 As mentioned above, there are no direct matches between the datasets.
-In other words, we have not directly observed a property which has been in a long-term rental followed by short-term or vice versa.
-We will, instead, make the comparisons between the two by imputing likely long-term rental revenues for the observed short-term properties and then comparing the observed revenues to the imputed revenues.
-
-We make our imputations via a hedonic price models.
-We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term rental for the short term properties.
+In other words, we have not directly observed a property which has been in a long-term rental followed by short-term rental or vice versa.
+We will, instead, make the comparisons between the two by imputing likely long-term rental revenues for the observed short-term properties and then comparing the measured net revenues of the short-term properties to their estimated imputed long-term revenues.
+We first focus on using the Actual measure of net revenue for the short-term properties as discussed above.
+We save discussion and analysis of the Potential revenue for the sensitivity tests later in the study.
+
+We make our imputations via hedonic price models.
+We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term weekly rental prices for the short-term properties.
 We use the following model specification:
@@
 
-We then compare the projected net revenue of the short-term properties to their observed revenues, both Extrapolated ($REV_e$) and Potential ($REV_p$), to judge the likelihood of short-term preference.
-
-Realizing that the imputed long term rental values may be more accurate when estimated at smaller scales, we impute long term rental rates at submarket level, specifically by type, bed/bath and geographic area.
+Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
 In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
 for all combinations of type, bed/bath and geographic area.
-We then combine the results form all estimates back into a single dataset that contains all of the short-term rentals.
-
-### Results
+We then combine the results from all estimates back into a single dataset that contains all of the short-term rentals.
+
+## Results
 

### 2017-03-08 abb_Writeup.Rmd
results - metro and type

@@
 We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long term revenues for the long term properties.
-Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 8).
+Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (\autoref{revdens}).
 Actual short-term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
@@
 
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions', fig.lp='revdens'}
+```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions', fig.lp='revdens'}
 
   stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
-  stre$tenure <- 'short-term extrapolated   '
+  stre$tenure <- 'short-term actual   '
   names(stre)[2] <- 'revenue'
@@
 Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
-Below we show (left-panel, Figure 9) the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
+For reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
+In \autoref{occpref} (left panel) we show the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
 We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up from about 25\% up to 75\% occupancy.
@@
 As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
-In the right hand panel of Figure 9 we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
 By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
-As a matter of reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
-
-&nbsp;
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Probability of Short Term Pref. vs Occ. Rate'}
+
+&nbsp;
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short Term Pref. vs Occ. Rate'}
 
@@
 In Figure 10 (left panel) we plot nightly rates versus occupancy rates.
-We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short term or long term revenue.
+We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short-term or long-term revenue.
 The transparency is related to the total count of actual market properties falling into that area.
 
-The general trend is what is expected, i.e.
-that higher rates and occupancies, ceteris paribus, means more profitability for short term rentals.
+The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
 This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
-While the left panel of Figure 16 helps show the general pattern is does leave many indeterminate areas.
+While the left panel of \autoref{metrohm} helps show the general pattern it does leave many indeterminate areas.
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
@@
 An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
-In this case, we delineate the boundary (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
+In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
 In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
-While this process does provide more flexible fit in the area of high data density, it also has the side effect of creating somewhat counter intuitive results in areas of low data (such as the far upper right corner.)  Overall, from the SVM model we see that the short-term preference begins at about 30\% occupancy rate, regardless of nightly rate.
+Overall, from the SVM model we see that the short-term preference begins at about 325% occupancy rate, regardless of nightly rate.
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='Analysis of Raw Rates: Metro Level'}
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
 
@@
 
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in Figure 10 may be misleading.
-We convert both axis to quantiles and replot both in Figure 11.
+Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
+We convert both axis to percentiles and replot both in \autoref{metrohmp}.
 Here we see a more even distibution of points across the figures.
 Additionally, a more reasonable SVM breakdown occurs as well.
-The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have is 40\%, if the nightly rate is in the top 95th percentile of the market.
-For example, if we drop the nightly rate to the median, the occupancy rate need to be at the 60th percentile.
-
-&nbsp;
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have at around the 60th percentile of the market it is in.
+And that only holds if the nightly rate is in the top 95th percentile of the market.
+For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
+
+&nbsp;
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}
 
@@
                 fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm <- qtl.hm + ylab('Nightly Rate')
+  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
 
@@
                    fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate')
+  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
 
@@
 Within the houses, 17.5\% of the properties are short-term preferable, while for the apartment that figure is nearly double at 30.5\%.
-Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (Figure 12).
-The only measurable difference is in that for houses a properties occupancy rate needs to be about in a higher quantile (by about 10) than apartments to show the same likelihood of short-term preference as apartment.
-Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preferenc.e
-
-&nbsp;
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='Preferency vs Occ. Rates: By Type'}
+Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (\autoref{smocc}).
+The only measurable difference is in that for houses a property's occupancy rate needs to be 10 percentiles higher than apartments to show the same likelihood of short-term preference as an apartment.
+Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preference.
+
+&nbsp;
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
 
@@
     stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Quantile)') +
+    xlab('\nOccupancy Rate (Pcntl)') +
     scale_color_manual(values=c('black', 'grey60'),
@@
     theme(legend.position='bottom') + 
-    ggtitle('Quantile Rates') + 
+    ggtitle('Percentile Rates') + 
     theme(plot.title = element_text(hjust = 0.5))
@@
 
-Extending this analysis to also include nightly rates shows a similar situation (Figure 13).
+Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
 For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
-As an example, a median nightly rate requires a 90\% occupancy rate.
+As an example, a median nightly rate requires a 90th percentile occupancy rate.
 The market for apartment (right panel) is more forgiving and occupancy rates as low as the 60th percentile can equate to a greater than even chance of short-term prefence is coupled with nightly rates near the top of the market.
-A median nightly rate requires a 70\% occupancy rate for short-term prefernce likelihood.
-
-&nbsp;
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: By Type'}
+A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
+
+&nbsp;
+
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
 
@@
   theme(legend.position='none') +
-  annotate("text", x = 50, y = 50, label = "Houses", size=9)
+  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
+  ylab('Nightly Rate (Pcntl)') +
+  xlab('Occupancy Rate (Pcntl)')
 
@@
   theme(legend.position='none')+
-  annotate("text", x = 50, y = 50, label = "Apartments", size=9)
+  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
+  ylab('Nightly Rate (Pcntl)') +
+  xlab('Occupancy Rate (Pcntl)')
 

### 2017-03-08 abb_Writeup.Rmd
review - log model

@@
 
-### UPDATE THE QTL VALUES
-
   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
@@
 
-Next, we divide the data by the five geographic sub-market shown in Figure 6.
+Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
 Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
 That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.
-
-&nbsp;
 
@@
 
-&nbsp;
-
-There is a noticable variability in the relationship between occupancy rates and short-term prefernce across the submarkets.
-For raw rates (Figure 14, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
+There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
+For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
 This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city.
-Transforming to quantiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the other, with suburban and city as the most difficult markets.
-
-&nbsp;
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
+
+&nbsp;
+
+```{r, fig.width=8, fig.height=4, echo=FALSE}
 
@@
 
-```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Quantile Rates: Metro Level'}
 
@@
 
-Plotting out the nigthly rate versus occupancy rate heat maps for all five geographic submarkets tells a similar story.
-The 'City-Core' market offers the most potential for short term prefernce with suburban and city the least.
-The rural market achieves very sold short-term preference for the most expensive home, again likely those with special amenities or links to the wine region.
+Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
+The 'City-Core' market offers the most potential for short term preference with suburban and city the least.
+The rural market achieves very solid short-term preference for the most expensive homes, again likely those with special amenities or links to the wine region.
 Beach properties do not perform as well as might be expected in the short term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
@@
 
-```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='xxx'}
+```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
 

### 2017-03-08 abb_Writeup.Rmd
review - logit models

@@
 
-The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually more profitable as a short-term rental then it would have been if rented long-term over the course of the year.
-This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-erm preference.
+The analyses above show that, overall, just less than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference.
 While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
@@
 
-where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term preference, $PType$ is the property type (apartment or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
 
@@
 The results of all three models are shown in Table 4.
-For $PType$ apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ `Moderate' is the reference category.
+For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Moderate is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
@@
 This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
-Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity on holiday than in day-to-day living.
-
-Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core(the reference category) when controlling for structural characteristics.
-The difference between the Rural and City-Core is not significant, however,  The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
+Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.
+
+Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
+The difference between the Rural and City-Core is not significant, however.
+The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
 The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.
@@
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
-This variable may be operating a proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.
+This variable may be operating as proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.
 The greater the minimum stay, the lower the probability of short-term preference.
-Longer minimum stay may equate to lower occupancy rates as one or two night travelers are exempted from the property.
+Longer minimum stays may equate to lower occupancy rates as one or two night travelers are exempted from the property.
 Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.

### 2017-03-08 abb_Writeup.Rmd
review - sensitivity analysis

@@
 To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
-First, we examine how the results changes if potential revenue, not observed revenue, of the short-term properties is used in the comparisons.
+First, we examine how the results change if Potential revenue, not Actual revenue, of the short-term properties is used in the comparisons.
 Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothetical motivations and actions of the hosts.
@@
 
-The above uses the observed^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
+The above uses the Actual^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
 Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to the treatment of blocked days.
@@
 Using the potential revenue, 53.3% of all properties are short-term preferable.
-Breaking that down by type and by geographic submarket shows similar finding to the actual revenue analysis above.
+Breaking that down by type and by geographic submarket (Table 5) shows similar findings, in terms of relative comparativeness, to the actual revenue analysis above.
 Apartments have a higher short-term preference than do Houses and City-Core properties dominate the other geographic regions.
@@
 
-Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, Figure 19) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combination that lead to short-term preference.
+Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{potlog}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
 Under a potential revenue scenario, a median occupancy rate and median nightly rate is results in greater than 50\% chance of short-term preference.
-Even with very low nightly rates (10th percentile), an occupancy rate around the 65th percentile will achieve short-term prefernce likelihood.
-
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+Even with very low nightly rates (10th percentile), an occupancy rate around the 65th percentile will achieve short-term preference likelihood in the potential case.
+
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{potlog}Logistic Model Results of Short Term Preference', fig.lp='xxx'}
 
@@
 
-Our final test of the potential revenue is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
-Generally speaking, the results from the new series of models (Table 6) are qualitatively similar to those derived in teh Actual revenue case (Table 4).
+Our final test of the potential revenue case is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
+Generally speaking, the results from the new series of models (Table 6) are qualitatively similar to those derived in the Actual revenue case (Table 4).
 The overall magnitude of the coefficient for House (vs Apartments) is lowered in the Potential case, suggesting that houses may be blocked off more that Apartments.
 The product types (bed/bath) show similar trends, though with larger discounts for the 2 Bed / 1 Bath and 2 Bed/2 Bath units.
-Likewise the geographic submarkets and host policies show similar effects in terms of direction with some slight deviations in magnitude.
+Likewise the geographic submarkets and host policies show similar effects in terms of direction of impact with some slight deviations in magnitude.
 
@@
 Under the scenario, the possibilities of increasing revenue by moving from long to short term leasing appear much better.
-Again, however, we have not attempted to measure or estimate how this flood of properties onto the market (due to the elimation of blocked days) would impact overall market dynamics.
+Again, however, we have not attempted to measure or estimate how this hypothetical flood of properties onto the market (due to the elimation of blocked days) would impact overall market dynamics.
 Suffice it to say that it would like drive down occupancies and maybe price, therefore leading to a decrease in short-term preference likelihood.
@@
 In explaining the drivers of short-term preference, the logistic regression models do not change materially with the switch in dependent variable.
-This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate, only the base probability of short-term preference increases.
+This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate.
+Only the base probability of short-term preference increases in the the potential revenue case
 
@@
 There may be, therefore, different types of hosts operating in the Airbnb market.
-from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-
-If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right.
-The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.
-
-There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property.
+From anecdotal evidence there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
+
+If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked should be highly bi-modal with profit seekers on the left and opportunistic sharers on the right.
+The left hand panel of \autoref{hostblock} shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some (25\% to 75\%) of the time.
+
+There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property, of which Airbnb may just be one.
 A potential method to identify these hosts is to look at the number of individual periods of blocked days.
-A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
-We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9.
-We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.
+A host using multiple platforms will likely have many small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
+We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of \autoref{hostblock}.
+We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
 
@@
                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Host Block Rate Frequency\n') +
+    #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5)) +
@@
 
-```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Blocking Tendencies', fig.lp='hostblock'}
+```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='\\label{hostblock}Host Blocking Tendencies', fig.lp='hostblock'}
 
@@
 
-Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories.
-As a more subjective approach, we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
+Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
+As a more subjective, but implementable, approach we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
 Profit seekers are those host who have blocked percentages less than 25\% of the time.
@@
 Within those two extremes, we consider users who have at least 12 blocked periods during a year to be 'Multi-Platform Users' and the remaining set to be 'Unknown'.
-See Figure 10 for a breakdown of these group by the two variables.
+Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
+The remainder 'Unknown' category contains just over 28\% of all properties.
+See \autoref{hostcat} and \autoref{htc} for a breakdown of these group by the two variables.
 
@@
 
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Categories', fig.lp='hosttypes'}
+```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='\\label{hostcat}Host Categories', fig.lp='hosttypes'}
 
@@
 
-&nbsp;
-
-Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
-The remainder 'Unknown' category contains just over 28\% of all properties.
-The classification of these hosts is not convincing enough to base our entire analytical process on so we will use these breakdowns to add context to the results and to test the sensitivity of our results to the assumptions underlying the extrapolated and potential revenue calculations.
-
-&nbsp;
-
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.caption='Host Type Counts', fig.lp='hostbar'}
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=4 fig.caption='\\label{htc}Host Type Counts', fig.lp='hostbar'}
 
@@
   xlab('\nHost Type') +
-  ggtitle('Short Term Host Types') + 
+  #ggtitle('Short Term Host Types') + 
   theme(plot.title = element_text(hjust = 0.5))
@@
 Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Actual case and a much smaller variation in the Potential case, as expected.
-There is little change for the 'Profit Seekers' as most of these hosts already operating with few blocked days.
+There is little change for the 'Profit Seekers' as most of these hosts are already operating with few blocked days.
 For the other three sets, considerable gains could be had with a more aggresive leasing approach.
-As the potential figures are somewhat similar here, we will only examine the differences in the Actual number going forward.
+As the potential figures are somewhat similar here, we will only examine the differences for host types in the Actual number going forward.
 
@@
 
-Table 9 compares logistic models results from three of the host types.
+Table 8 compares logistic models results from three of the host types.
 The Opportunistic Sharers show no instances of short-term preference and therefore could not be estimated.
@@
 Overall, the coefficients from this sub-sample match up well to the results from the entire sample shown in Table 5.
-In short, the conclusions are the same: small, apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
+In short, the conclusions are the same: small apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
 The models for the multi-platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short Term Preference'}
 
@@
  xh.full <- xtable(hfull.table,
-                  caption='Logistic Modeling Results\n')
+                  caption='Logistic Model Results of Potential Short-Term Preference\n')
  align(xh.full) <- 'lllll'

### 2017-03-08 abb_Writeup.Rmd
review - discussion

@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short Term Preference'}
 
@@
 
-Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{potlog}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
+Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{pothm}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
 Under a potential revenue scenario, a median occupancy rate and median nightly rate is results in greater than 50\% chance of short-term preference.
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{potlog}Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preferencexxx', fig.lp='xxxx'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{pothm}Heatmaps of Potential Short Term Preference'}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short Term Preference'}
 
@@
 
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=4 fig.caption='\\label{htc}Host Type Counts', fig.lp='hostbar'}
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=4, fig.caption='\\label{htc}Host Type Counts'}
 
@@
 
-Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
-This work attempts to fill this void.
-
-The Airbnb market is Melbourne is rapidly expanding, as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
-However, of this total, only 6,600 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
-Of these, only 4,400 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+Although it gathers considerable interest in both economic and public policy circles, analyses of short-term markets and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+The Airbnb market is Melbourne is rapidly expanding as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
+However, of this total only 7,400 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
+Of these, only 5,788 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
 Overall, the Airbnb market is very small relative to the long-term market.
@@
 
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 10).
-However, there is long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, on Airbnb than they would on the long-term market.
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).
+However, there is a long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
 This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).
@@
 
-To control for these differences, we set out to make direct comparison of short and long term revenues on both the short and long term market observations.
-The shared information that is available on both sets of properties is limited.
-Our initial work found estimating long term rental values and tenant search times for the short term properties to be feasible with these data constraints while the opposite is much more difficult.
-In other words, there appear to by many unobserved variables (presense of wi-fi, parking and laundry facilities) and/or none-property specific characteristics (such as minimum stays, pet policies, number of allowed guests, cancellation policies) that influence short term nightly rates and occupancy rates.
-As a result, we were not able to accurately estimate likely short-term rates for the long-term observations.
-
-In looking only at the short-term observation with estimated long-term rents we found that approximately one in three Airbnb properties brought in more revenue with its short term strategy than it would have with a long-term approach.
+In analyzing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
 As expected, this probability is not equal across space, property type or property size (bed and bath count).
-Apartments are much more likely than houses to be more profitable as a short term rental.
-Core city properties are more likely than other properties to prefer a short-term strategy, as are larger properties versus smaller ones.
-For instance, 35\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market while only 8\% of suburban houses did.
+Apartments are much more likely than houses to be more profitable as a short-term rental.
+Core city properties are more likely than other properties to prefer a short-term strategy, as are smaller properties versus larger ones.
+For instance, 36\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market while only 8\% of suburban houses did.
 Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
@@
 As the nightly rate vs.
-occupancy rate heat maps and SVM plots (Figures 16, 17, 18 and 19) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
+occupancy rate heat maps and SVM plots (\autoref{metrohmp}, \ref{smhm}, \ref{smhmps}, \ref{pothm}) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
 A 40\% occupancy rate means bookings at least three days out of every week all year long.
 In Melbourne summers this may be an easy feat as tourist numbers swell, but doing so on a cold week in July likely proves more difficult.
-The verticalness of the divide between short and long term preference in the SVM plots suggests that occupancy rate is critical to reaching short-term preference in most markets.
-
-The logistic regression models than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated (Table 7).
+The vertical-ness of the divide between short- and long-term preference in the SVM plots suggests that occupancy rate is the most critical factor in reaching short-term preference in most markets.
+
+The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated .
 Small apartments in the central city are the best bet for generating greater revenues through short term leasing.
@@
 Testing for the sensitivity of the initial results through consideration of potential revenue figures and by dividing the sample up by likely host motivation, we find the qualitative finding to be generally robust.
-While the use of potential revenue does increase the base probability of short-term preference, the same factors -- small, inner city apartment with low minimum stays, strict cancellation and liberal guest capacity -- explain a higher likelihood of short-term preference.
+While the use of potential revenue does increase the base probability of short-term preference, the same factors -- small inner city apartments with low minimum stays, strict cancellation and liberal guest capacity -- explain a higher likelihood of short-term preference.
 
@@
 Part of the difficulty in estimating potential short-term rates for long-term properties is that the short term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
-Future research should focus both on building better models to explain (and ultimately predict) short term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short term market.
+Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short term market.
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
 
-Additionally, we have opted to make comparisons between short and long-term strategies by cross estimating likely rates and rents.
+Additionally, we have opted to make comparisons between short- and long-term strategies by imputing long-term rents for short-term properties with a hedonic price model.
 Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
@@
 We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
+
+#### Data, Code and Interactivity
+
+Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
+All the code used to complete this analysis, done in the R language, is available for download at www.github.com/andykrause/airbnbmelbourne.
+An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at shinyapps.io/somename.
 

### 2017-03-08 abb_Writeup.Rmd
find and replace terms

@@
   source(paste0(code.path, "datamgmttools/dataMungetools.R"))
-  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
+  source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))
 
@@
 ```
-
-&nbsp;
-&nbsp;
 
@@
 Taking the Airbnb or STR approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
-In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.
+In this simulated example we will use Airbnb data from September 1, 2015 to August 31, 2016 to represent the actual Airbnb market conditions over the time period in question.
 
 Next, we filter the data based on property types.
-AirBNB units are classified into 19 different property types.
+Airbnb units are classified into 19 different property types.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt.^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type] For the sake of this analysis, we will collapse these twenty types into three types:
@@
 
-Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+Within the long-term rental data, property types fall into eight categories.  Like the Airbnb data we group these into three categories matching as best as possible to the Airbnb categories:
 
@@
 
-&nbsp;
-
 ```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
@@
 ```
-
-&nbsp;
 
@@
 
-&nbsp;
-
 ```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}
@@
 
-&nbsp;
-
 ```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure'}
@@
 
-&nbsp;
-
 ```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}
@@
 \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
@@
 
-&nbsp;
-
 ```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs', fig.lp='coresuburbs'}
@@
 
-&nbsp;
-
 We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
@@
 After making this correction we then assign one of the five submarket designations based on the process described above.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
@@
 
-&nbsp;
-
 ```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts', fig.lp='locbars'}
@@
 remove another 12,000 observations, leaving 120,092 in the final dataset.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 ## Revenues
@@
 The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
-
-&nbsp;
 
@@
 
-&nbsp;
-
 ### Comparison
@@
 As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
-In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the quantile of the full distribution of occupancy rates.
+In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
 By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
-
-&nbsp;
 
@@
     stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Quantile)') +
+    xlab('\nOccupancy Rate (Pcntl)') +
     scale_x_continuous(breaks=seq(0, 100, by=25),
@@
     theme(legend.position='none') + 
-    ggtitle('Quantile Rates') + 
+    ggtitle('Percentile Rates') + 
     theme(plot.title = element_text(hjust = 0.5))
@@
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
@@
 For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 \pagebreak
@@
 Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preference.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
@@
 A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 #### By Geography
@@
 
-&nbsp;
-
 ```{r, fig.width=8, fig.height=4, echo=FALSE}
@@
 
-```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Quantile Rates: Metro Level'}
+```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Metro Level'}
 
@@
     stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Quantile)') +
+    xlab('\nOccupancy Rate (Pcntl)') +
     scale_color_manual(values=sm.col,
@@
 
-&nbsp;
-
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Quantile Rates: Metro Level'}
+```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
 
@@
 
-&nbsp;
-
 ## Explaining Preference
@@
 Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
-
-&nbsp;
 
@@
  ## Combine into full table of coef and diags
-  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)
+  #full.table[,2] <- gsub(" ", "", full.table[,2], fixed=TRUE)
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{pothm}Heatmaps of Potential Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Potential Short Term Preference'}
 
@@
 We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
-
-&nbsp;
 
@@
 
-```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
     theme(plot.title = element_text(hjust = 0.5))
@@
 
-```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='\\label{hostblock}Host Blocking Tendencies', fig.lp='hostblock'}
+```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostblock}Host Blocking Tendencies'}
 
@@
 See \autoref{hostcat} and \autoref{htc} for a breakdown of these group by the two variables.
-
-&nbsp;
 
@@
 
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='\\label{hostcat}Host Categories', fig.lp='hosttypes'}
+```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories', fig.lp='hosttypes'}
 
@@
 
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=4, fig.caption='\\label{htc}Host Type Counts'}
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}
 
@@
   xlab('\nHost Type') +
+  scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
   #ggtitle('Short Term Host Types') + 

### 2017-03-09 abb_Writeup.Rmd
Fixed maps and vizs

@@
   html_document: default
-header-includes: \usepackage{setspace}\doublespacing
+header-includes: 
+   - \usepackage{setspace}\doublespacing
+   - \usepackage{caption}
+   - \captionsetup[table]{skip=10pt}
 geometry: margin=3.3cm
@@
 We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues.
-Our results show that the feasibility of a greater return through a short term rental -- what we have termed ``Short Term Preference'' -- is dependent on property type, product, location and host policies.
+Our results show that the feasibility of a greater return through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
 In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
@@
 
-The Other category only makes up a very small percentage of the properties in both the short and long term market; especially so in the long-term market (\autoref{typecomp}) .
+The Other category only makes up a very small percentage of the properties in both the short and long-term market; especially so in the long-term market (\autoref{typecomp}) .
 Additionally, a large proportion of the 'Others' in the short-term data are Bed & Breakfast units, a use which doesn't fit within our research question.
@@
   load(paste0(fig.path, 'strtypes.RData'))
+
+  str.types <- str.types + xlab('')
+  ltr.types <- ltr.types + xlab('')
 
@@
 We filter the data accordingly.
-Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom.
-We convert the 0 bed short term units to 1 bed units.
-A few short term properties indicate no baths, which is likely an error so we remove these observations from the data.
-Also, here we notice that the short-term data gives bathrooms in halves, while the long term data presents baths in whole numbers.
+Additionally, note that short-term rentals consider studio apartments to be 0 bed units while the long-term data considers these as 1 bedroom.
+We convert the 0 bed short-term units to 1 bed units.
+A few short-term properties indicate no baths, which is likely an error so we remove these observations from the data.
+Also, here we notice that the short-term data gives bathrooms in halves, while the long-term data presents baths in whole numbers.
 We round the baths in the short-term data up to whole integers.
@@
 
-```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure'}
+```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
 
@@
 After removing property level observations that are missing price data, we plot the distribution of the rates and rents.
-In Figure 4 we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+In Figure 4 we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
 We filter the property level data accordingly.
-We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.
+We also filter the short-term daily data to include only those observations with nightly rates between \$50 and \$500.
 
@@
 
-```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='\\label{locmap}Melbourne Submarkets', fig.lp='submap'}
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets', fig.lp='submap'}
 
@@
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long term rentals in Melbourne:
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
 
@@
 
-```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs', fig.lp='coresuburbs'}
+```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs'}
 
@@
 
-Before assigning submarkets to the long term property we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
+Before assigning submarkets to the long-term property we must remedy the fact that about 5% of the long-term rental observations have missing latitude and longitude values.
 Half of these do, however, have a latitude and longitude values for the centroid of the street that the property faces.
@@
 
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='\\label{pointmaps}Location Maps', fig.lp='locmaps'}
+```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
 
@@
   load(paste0(fig.path, 'strMap.RData'))
+
+```
+
+```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.lp='locmaps', fig.ext='png'}
 
@@
 Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short term market, especially in apartments, while suburban and rural apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
+Beach properties are, relatively speaking, over-represented in the short-term market, especially in apartments, while suburban and rural apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
 Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
@@
 
-For the long term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
@@
 
-```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary', fig.lp='cleansumm'}
+```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
 
@@
 clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
-names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
-                        'Long Term', 'Cut', '% Cut')
+names(clean.table) <- c('Filter', 'Short-term', 'Cut', '% Cut',
+                        'Long-term', 'Cut', '% Cut')
 options(xtable.comment = FALSE)
-print(xtable(clean.table, caption='Data Cleaning Summary\n',
+print(xtable(clean.table, caption='Data Cleaning Summary',
        digits=0),
@@
 
-Second, many of the short term properties have a significant number of blocked days, days in which the property was not offered on Airbnb.
+Second, many of the short-term properties have a significant number of blocked days, days in which the property was not offered on Airbnb.
 Here too, there is a problem with comparing observed revenues from a property with a 40\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portal during those blocked days.
@@
 As the observed calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the Actual revenue metric to be a better measure of actual market performance.
-We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long term revenues for the long term properties.
+We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties.
 Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (\autoref{revdens}).
@@
   stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
-  stre$tenure <- 'short-term actual   '
+  stre$tenure <- 'Short-Term (Actual)   '
   names(stre)[2] <- 'revenue'
   strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
-  strp$tenure <- 'short-term potential   '
+  strp$tenure <- 'Short-Term (potential)   '
   names(strp)[2] <- 'revenue'
   ltrr <- ltr.data[,c('bedrooms', 'ltr.revenue')]
-  ltrr$tenure <- 'long-term   '
+  ltrr$tenure <- 'Long-Term   '
   names(ltrr)[2] <- 'revenue'
@@
     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
-    xlab('Annual Revenue') +
+    #ggtitle('Annual Revenues by Tenure Type') +
+    xlab('\nAnnual Revenue') +
     scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
+                       labels=c('$0', '$20k', '$40k', '$60k'))+
+    theme(legend.position='none',
           legend.title = element_blank(),
@@
           axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
+    coord_cartesian(xlim=c(0, 70000)) +
+    facet_wrap(~tenure)
 
@@
 
-As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long term.
+As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
 In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
-By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long term one.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short Term Pref. vs Occ. Rate'}
+By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long-term one.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
 
@@
 An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
-In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short term are (green).
+In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short-term are (green).
 In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
@@
 The only measurable difference is in that for houses a property's occupancy rate needs to be 10 percentiles higher than apartments to show the same likelihood of short-term preference as an apartment.
-Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short term preference.
+Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
 
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
+```{r, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
 
@@
   pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[,2] <- pref.table[,2]*100
-
-  names(pref.table) <- c('Sub-Market', '% Short Term Preferable')
+  pref.table[,2] <- paste0(sprintf('%.1f', pref.table[,2]*100), '%')
+
+  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
   options(xtable.comment = FALSE)
   print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n',
-               digits=1),
+               digits=1,
+               align='llr'),
                include.rownames=FALSE,
@@
 Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
-The 'City-Core' market offers the most potential for short term preference with suburban and city the least.
+The 'City-Core' market offers the most potential for short-term preference with suburban and city the least.
 The rural market achieves very solid short-term preference for the most expensive homes, again likely those with special amenities or links to the wine region.
-Beach properties do not perform as well as might be expected in the short term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
+Beach properties do not perform as well as might be expected in the short-term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
 
@@
   st.table <- rbind(tpref.table, spref.table)
-  st.table[,2] <- st.table[,2]*100
-  names(st.table) <- c('Sub-Market', '% Short Term Preferable')
+  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%') 
+  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
   options(xtable.comment = FALSE)
@@
                caption='Potential Revenue Preferability\n',
-               digits=1),
+               digits=1, align='llr'),
                include.rownames=FALSE,
@@
                    fill.colors=c(abb.col[1], abb.col[5]))
-  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Qtl)')+
+  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
+    xlab('Occupancy Rate (Pcntl)') +
   annotate("text", x = 50, y = 50, label = "Potential", size=9)
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Potential Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}
 
@@
 As expected, under the Potential case there are more properties (50\% vs 27\%) that exhibit short-term preference.
-Under the scenario, the possibilities of increasing revenue by moving from long to short term leasing appear much better.
+Under the scenario, the possibilities of increasing revenue by moving from long- to short-term leasing appear much better.
 Again, however, we have not attempted to measure or estimate how this hypothetical flood of properties onto the market (due to the elimation of blocked days) would impact overall market dynamics.
@@
   scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
-  #ggtitle('Short Term Host Types') + 
+  #ggtitle('short-term Host Types') + 
   theme(plot.title = element_text(hjust = 0.5))
@@
   hpref.table[,3] <- phpref.table[,2]
-  hpref.table[,2] <- hpref.table[,2]*100
-  hpref.table[,3] <- hpref.table[,3]*100
-
-  names(hpref.table) <- c('Host Type', '% STP - Actual', '% STP - Potential')
+  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
+  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
+
+  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
   options(xtable.comment = FALSE)
@@
                caption='Host Type Preferability\n',
-               digits=1),
+               digits=1,
+               align='llrr'),
                include.rownames=FALSE,
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short Term Preference'}
+```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}
 
@@
 Core city properties are more likely than other properties to prefer a short-term strategy, as are smaller properties versus larger ones.
-For instance, 36\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long term market while only 8\% of suburban houses did.
+For instance, 36\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 8\% of suburban houses did.
 Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
@@
 As the nightly rate vs.
-occupancy rate heat maps and SVM plots (\autoref{metrohmp}, \ref{smhm}, \ref{smhmps}, \ref{pothm}) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long term one.
+occupancy rate heat maps and SVM plots (\autoref{metrohmp}, \ref{smhm}, \ref{smhmps}, \ref{pothm}) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long-term one.
 A 40\% occupancy rate means bookings at least three days out of every week all year long.
@@
 The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated .
-Small apartments in the central city are the best bet for generating greater revenues through short term leasing.
-We also test for the impact of host behavior on the probability of short term preference.
-We find that more flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short term preference probability).
+Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
+We also test for the impact of host behavior on the probability of short-term preference.
+We find that more flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability).
 As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
@@
 There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
-Part of the difficulty in estimating potential short-term rates for long-term properties is that the short term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
-Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short term market.
+Part of the difficulty in estimating potential short-term rates for long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
+Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
@@
 
-Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short or long term leasing strategy.
+Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short- or long-term leasing strategy.
 In reality, the possibilities may not be so rigid.
-For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourist swell in the summer months, an enterprising owner maybe able to pair long term leasing during the off-season with short-term leasing during peak times to maximize revenues.
+For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourist swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
 In general, the rise of Airbnb and related portals give properties owners more options, and therefore more opportunities, to maximize returns on their property.
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx55'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx55'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx44'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx44'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx33'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx33'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx22'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx22'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx11'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx11'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx1'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx1'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx2'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx2'} -->
 
@@
 
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx23'} -->
+<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx23'} -->
 

### 2017-03-09 abbDataPrep_Script.Rmd
Updates to maps

@@
   # Set colors
-  g.cols <- abb.col[c(2, 10, 9)]
+  g.cols <- c('grey10', 'grey40', 'grey70')
 
@@
                                               'Outer')) +
-    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
+    geom_path(data=subs[subs$des=='Outer', ], 
+              aes(x=long, y=lat, group=group), col='white', size=.1,
+              linetype=1) +
+
+    geom_path(data=subs[subs$des=='Middle', ], 
+              aes(x=long, y=lat, group=group), col='grey70', size=.1,
+              linetype=1) +
+
+    geom_path(data=subs[subs$des=='Inner', ], 
+              aes(x=long, y=lat, group=group), col='grey40', size=.1,
+              linetype=1) +
+
     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
@@
     theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
-    ggtitle("Melbourne Suburb Classifications")+
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
+    #ggtitle("Melbourne Suburb Classifications")+
     theme(plot.title = element_text(hjust = 0.5))
@@
   str.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
     geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
@@
     theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
     guides(colour = guide_legend(override.aes = list(size=3,
                                                      alpha=1))) + 
-    ggtitle('AirBNB Location\nBy Submarket')+
+    ggtitle('Short-Term Rental Locations')+
     theme(plot.title = element_text(hjust = 0.5))
@@
   ltr.map <- ggplot() +
-    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
     geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
@@
     theme(legend.position = 'bottom',
-          legend.title = element_blank()) +
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_rect(fill = "white"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),
+          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
     guides(colour = guide_legend(override.aes = list(size=3,
                                                      alpha=1))) + 
-    ggtitle('Long Term Rental Location\nBy Submarket')+
+    ggtitle('Long-Term Rental Locations')+
     theme(plot.title = element_text(hjust = 0.5))
@@
           axis.ticks.x=element_blank()) +
-    ggtitle('Short Term Property Type\nBy Submarket')+
+    #ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))
@@
           axis.ticks.x=element_blank()) +
-    ggtitle('Long Term Property Type\nBy Submarket')+
+    #ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

### 2017-03-09 abbDataAnalysis_Script.Rmd
added libraries and options

@@
   library(kernlab)
+  library(lmtest)
+  library(ROCR)
 
@@
   }
+
+ ## Set options
+
+  options(xtable.comment = FALSE)
+  options(xtable.caption.placement='top')
 

### 2017-03-09 abb_Writeup.Rmd
Cosmetic cleanup

@@
 
-```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
+```{r plot_pt, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
 
@@
 
-```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}
+```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}
 
@@
 
-```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
+```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
 
@@
 
-```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}
+```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}
 
@@
 
-```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets', fig.lp='submap'}
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}
 
@@
   load(paste0(fig.path, 'strsubplot.RData'))
-  ltrtype.map <- ltrtype.map + ylab("")
+
+  ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties')
+  strtype.map <- strtype.map + ggtitle('Short-Term Properties')
 
@@
 
-```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}
+```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
+
+ ## Extract data
 
   cc <- clean.count[,c('operation', 'str', 'ltr')]
+
+ ## Sum counts and create percentages
+
   str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
@@
   ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
+
+ ## Compile into data.frame
+
   clean.table <- data.frame(field=cc$operation,
@@
 
+  ## Fix fields and names
+
   rownames(clean.table) <- NULL
   clean.table$field <- c('Initial Count', 'Time', 'Property Type',
-                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
+                         'Listing Type', 'Bedrooms', 'Baths', 'Bed & Bath Combo',
                          'Rates & Rents', 'Revenue', 'Location', 'Host Policy')
@@
                           'Long-term', 'Cut', '% Cut')
+
+ ## Conver to xtable and print
+
   options(xtable.comment = FALSE)
-print(xtable(clean.table, caption='Data Cleaning Summary',
-       digits=0),
+  print(xtable(clean.table, 
+               digits=0,
+               caption='Data Cleaning Summary'),
        include.rownames=FALSE,
@@
 
-  stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
-  stre$tenure <- 'Short-Term (Actual)   '
-  names(stre)[2] <- 'revenue'
-  strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
-  strp$tenure <- 'Short-Term (potential)   '
-  names(strp)[2] <- 'revenue'
-  ltrr <- ltr.data[,c('bedrooms', 'ltr.revenue')]
-  ltrr$tenure <- 'Long-Term   '
-  names(ltrr)[2] <- 'revenue'
-  allr <- rbind(stre, strp, ltrr)
+  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
+  stra.rev$tenure <- 'Short-Term (Actual)   '
+  names(stra.rev)[2] <- 'revenue'
+  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
+  strp.rev$tenure <- 'Short-Term (potential)   '
+  names(strp.rev)[2] <- 'revenue'
+  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
+  ltr.rev$tenure <- 'Long-Term   '
+  names(ltr.rev)[2] <- 'revenue'
+  revdens.data <- rbind(stra.rev, strp.rev, ltrrev)
 

### 2017-03-09 abb_Writeup.Rmd
Chunk Cosmetics

@@
 
-  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
-  stra.rev$tenure <- 'Short-Term (Actual)   '
-  names(stra.rev)[2] <- 'revenue'
-  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
-  strp.rev$tenure <- 'Short-Term (potential)   '
-  names(strp.rev)[2] <- 'revenue'
-  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
-  ltr.rev$tenure <- 'Long-Term   '
-  names(ltr.rev)[2] <- 'revenue'
-  revdens.data <- rbind(stra.rev, strp.rev, ltrrev)
-
-  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) +
+  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
     geom_density(alpha=.5) +
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
-
-  str.data.ic$pref <- str.data.ic$str.ext.pref
-
-  rawocc <- abbPrefPlot(str.data.ic,
-                         x.field='occ.rate',
-                         smooth=TRUE,
-                         smooth.span=.5)
-
-  rawocc <- ggplot(rawocc$data,
+```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
+
+ ## Make plots
+
+  # Raw
+  raw.occ.metro <- ggplot(rawocc.metro$data,
                    aes(x=x.var, y=Var))+
@@
 
-  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
-                                      return.type='rank') 
-  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
-                                  return.type='rank') 
-  qtlocc <- abbPrefPlot(str.data.ic,
-                        x.field='occ.qtl',
-                        smooth=TRUE,
-                        smooth.span=.5)
-
-  qtlocc <- ggplot(qtlocc$data,
+  # Quantile
+  qtl.occ.metro <- ggplot(qtlocc.metro$data,
                    aes(x=x.var, y=Var))+
@@
 
+  # Make Plot
   ggMultiPlots(rawocc, qtlocc, cols=2)
+
 ```
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
+```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
+
+ ## Create the rate heat map
 
@@
 
+ ## Create raw SVM heatmap
+
   rate.hm.svm <- abbHeatMap(str.data.ic,
@@
 
+ ## Plot
+
   ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}
+```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}
+
+ ## Build percentile heatmap
 
@@
   qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
+
+ ## Build percentile SVM
 
@@
 
+  ## Make Plots
+
   ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
-
+```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Create dataset
+
+  type.data.ic <- str.data.ic
+
+  # Id the types
   apt.id <- which(str.data.ic$type == 'Apartment')
   house.id <- which(str.data.ic$type == 'House')
-  type.data.ic <- str.data.ic
+
+  # Recalculate the percentiles
+  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
+                                      return.type='rank')
+  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$occ.rate[house.id], return.type='rank')
+
+  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
+                                  return.type='rank')
+  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$med.rate[house.id], return.type='rank')
+
+ ## Calc the occ rate numbers
 
@@
                          spl.col=c('black', 'grey40'))
+
+  ptqocc <- abbPrefPlot(type.data.ic,
+                         x.field='occ.qtl',
+                         split.field='type',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=c('black', 'grey40'))
+
+```
+
+```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
+
+ ## Build raw plot
 
@@
 
-  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
-                                      return.type='rank')
-  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$occ.rate[house.id], return.type='rank')
-
-  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
-                                  return.type='rank')
-  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$med.rate[house.id], return.type='rank')
-
-  ptqocc <- abbPrefPlot(type.data.ic,
-                         x.field='occ.qtl',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
+ ## Build Percentile Plots
 
@@
 
+ ## Plot
+
   ggMultiPlots(ptr.occ, ptq.occ, cols=2)
@@
 
-```{r, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
+```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
+
+ ## Make House SVM Heatmap
 
@@
 
+ ## Make Apartment SVM Heat Map
+
   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
@@
 
+ ## Plot
+
   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
@@
 
-```{r message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
+```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
 
@@
   pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
-  pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[,2] <- paste0(sprintf('%.1f', pref.table[,2]*100), '%')
-
+  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
+  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
+
+ # Fix names  
   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
   options(xtable.comment = FALSE)
-  print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n',
+
+ ## Make printable table
+
+  print(xtable(pref.table[,1:2], 
+               caption='Geographic Submarket Preferability\n',
                digits=1,
@@
 Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
-
-```{r, fig.width=8, fig.height=4, echo=FALSE}
-
+```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}
+
+ ## Build data
+
+  subm.data.ic <- str.data.ic
+
+  # Get IDs
   cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
@@
 
-  subm.data.ic <- str.data.ic
-
+  # Recalc the percentiles
   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
@@
 
-```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Metro Level'}
+```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
+
+ ## Set colors
 
   sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
+ ## Create plot data
+
   smrocc <- abbPrefPlot(subm.data.ic,
@@
                         spl.col=sm.col)
+
+  smqocc <- abbPrefPlot(subm.data.ic,
+                         x.field='occ.qtl',
+                         split.field='sub.mrkt',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=sm.col)
+
+ ## Make plot objects
 
@@
 
-  smqocc <- abbPrefPlot(subm.data.ic,
-                         x.field='occ.qtl',
-                         split.field='sub.mrkt',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=sm.col)
-
   smq.occ <- ggplot(smqocc$data,
@@
 
+ ## Plot
+
   ggMultiPlots(smr.occ, smq.occ, cols=2)
+
 ```
@@
 
-```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
+```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
+
+  # Build the SVM Heatmaps
 
@@
                    quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
+                   fill.colors=c(abb.col[1], abb.col[5])) +
   theme(legend.position='none') +
@@
 
-```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
+```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
 
@@
 Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.
-
 Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}
+```{r log_model, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}
+
+ ## Extract data
 
@@
 
- makeStatSig <- function(x){
-   x <- as.numeric(x)
-   y <- rep('***', length(x))
-   y[x>.01] <- '** '
-   y[x>.05] <- '*  '
-   y[x>.1] <- '   '
-   y
- }
- m1sig <- makeStatSig(m1[,4])
- m2sig <- makeStatSig(m2[,4])
- m3sig <- makeStatSig(m3[,4])
+ ## Create vector with significance stars
+
+  m1sig <- makeStatSig(m1[ ,4])
+  m2sig <- makeStatSig(m2[ ,4])
+  m3sig <- makeStatSig(m3[ ,4])
+
+ ## Create coefficients for the table (with stars)
 
@@
 
+ ## Even out the lengths
+
   m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
@@
 
+ ##  Create the variable section of table 
  full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
@@
  ## Create model diagnostics
-
-  # Custom function
-  logDx <- function(log.model, data, resp.var){
-
-    pred <- prediction(predict(log.model, data, type='response'), resp.var)
-    auc <- performance(pred, measure='auc')
-    ll <- logLik(log.model)
-    AIC <- AIC(log.model)
-
-    return(list(AIC=AIC,
-                logLik=ll,
-                auc=auc))
-  }
 
@@
 
- ## Combine into full table of coef and diags
-  #full.table[,2] <- gsub(" ", "", full.table[,2], fixed=TRUE)
+ ## Combine into full table
 
@@
 
+  # XTable 
   x.full <- xtable(full.table,
@@
 
+  # Print
   print(x.full,
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
-
- # Make Basic comparison table
+```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
+
+ # Make Basic comparison table of type
   tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                     split.field='type')
-
+ # Extract Potential Results
   tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
+
+ # Make baseic comparison table of submarkets  
   spref.table <- abbCreateCompTable(ic.df=str.data.ic,
@@
 
+ # Extract potential results  
   spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
+
+ # Combine and round  
   st.table <- rbind(tpref.table, spref.table)
   st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
+
+ ## Fix names and print
+
   names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+
+ ## create data and re-estimate the percentiles
 
@@
   pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
+
+ ## Make the pecentile heatmap
 
@@
   pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
+
+ ## Make percentile SVM heatmap
 
@@
 
+ ## Add annotations to previous SVM
+
   qtl.hm.svm.p <- qtl.hm.svm +
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
+```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}
+```{r pot_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}
+
+ ## Extract coefficients
 
@@
 
+ ## Make Significance stars
+
   pm1sig <- makeStatSig(pm1[,4])
@@
   pm3sig <- makeStatSig(pm3[,4])
+
+ ## Create Table coef vectors
 
@@
 
+ ## Snap to same length
+
  pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1)))
@@
  pm3c <- pm3$table.coef
+
+ ## Put together as variables table
 
@@
                                               3)))
+ ## Fix names
+
   names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 
- ## Combine into full table of coef and diags
-  #full.table[,2] <- gsub(" ", "", full.table[,2], fixed=TRUE)
+ # Bind together
 
  pfull.table <- rbind(pfull.table, pdiag.table)
+
+ # XTable
 
@@
 
+ # Print
  print(px.full,
@@
 ```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  ## Create table of host block frequencies
 
@@
 
+ ## Create scatter of block rate vs block periods
+
   block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
@@
 
+ ## Split Hosts into groups
+
   str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
@@
 ```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+
+  # Create a background plot for the host location plots
 
@@
 
+  ## Create individual host location plots
+
   ps.host <- base.host + 
@@
     ggtitle('Profit Seekers')
+
   os.host <- base.host + 
@@
     ggtitle('Opportunistic Sharer')
+
   mu.host <- base.host + 
@@
     ggtitle('Multi-Platform User')
+
   un.host <- base.host + 
@@
 ```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}
+
+ ## Build plot
 
@@
 
+ ## Plot
+
   host.type.bar
@@
 
-```{r results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}
+```{r host_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}
+
+ ## Extract coefficients
 
@@
 
- h1sig <- makeStatSig(h1[,4])
- h2sig <- makeStatSig(h2[,4])
- h3sig <- makeStatSig(h3[,4])
+ ## Build significance stars
+
+   h1sig <- makeStatSig(h1[ ,4])
+   h2sig <- makeStatSig(h2[ ,4])
+   h3sig <- makeStatSig(h3[ ,4])
+
+ ## Create Table coefficients
 
@@
                          h3sig)
+
+ ## Convert to variable table
 
@@
 ## References
-
-<!-- Heat map with other characteristics on axis
-
-<!-- ### Submarkets -->
-
-<!-- ### Flexible Geo Analysis -->
-
-<!-- ### Logit Models (maybe?) -->
-
-<!-- ### Reference to Shiny App -->
-
-<!-- ## Future Research -->
-
-<!-- - Does time of purchase (which month) matter? -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx'} -->
-
-<!--   host.data.ic <- str.data.ic -->
-
-<!--   ps <- which(str.data.ic$host.type == 'Profit Seeker') -->
-<!--   os <- which(str.data.ic$host.type == 'Opportunistic Sharer') -->
-<!--   mu <- which(str.data.ic$host.type == 'Multi-Platform User') -->
-<!--   un <- which(str.data.ic$host.type == 'Unknown') -->
-
-<!--   host.data.ic$occ.qtl[ps] <- makeWtdQtl( -->
-<!--       host.data.ic$occ.rate[ps], return.type='rank') -->
-<!--   host.data.ic$rate.qtl[ps] <- makeWtdQtl( -->
-<!--     host.data.ic$med.rate[ps], return.type='rank') -->
-
-<!--   host.data.ic$occ.qtl[os] <- makeWtdQtl( -->
-<!--       host.data.ic$occ.rate[os], return.type='rank') -->
-<!--   host.data.ic$rate.qtl[os] <- makeWtdQtl( -->
-<!--     host.data.ic$med.rate[os], return.type='rank') -->
-
-<!--   host.data.ic$occ.qtl[mu] <- makeWtdQtl( -->
-<!--       host.data.ic$occ.rate[mu], return.type='rank') -->
-<!--   host.data.ic$rate.qtl[mu] <- makeWtdQtl( -->
-<!--     host.data.ic$med.rate[mu], return.type='rank') -->
-
-<!--   host.data.ic$occ.qtl[un] <- makeWtdQtl( -->
-<!--       host.data.ic$occ.rate[un], return.type='rank') -->
-<!--   host.data.ic$rate.qtl[un] <- makeWtdQtl( -->
-<!--     host.data.ic$med.rate[un], return.type='rank') -->
-
-<!-- ```     -->
-
-<!-- For the profit-seekers,  -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx55'} -->
-
-<!--   ps.raw.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
-<!--                    x.field='occ.rate', -->
-<!--                    y.field='med.rate', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=F, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   ps.raw.hm.svm <- ps.raw.hm.svm + ylab('Nightly Rate') -->
-
-<!--   ps.qtl.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   ps.qtl.hm.svm <- ps.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx44'} -->
-
-<!-- ggMultiPlots(ps.raw.hm.svm, ps.qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx33'} -->
-
-<!--   os.raw.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
-<!--                    x.field='occ.rate', -->
-<!--                    y.field='med.rate', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=F, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   os.raw.hm.svm <- os.raw.hm.svm + ylab('Nightly Rate') -->
-
-<!--   os.qtl.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   os.qtl.hm.svm <- os.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx22'} -->
-
-<!-- ggMultiPlots(os.raw.hm.svm, os.qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx11'} -->
-
-<!--   mu.raw.hm.svm <- abbHeatMap(host.data.ic[mu, ], -->
-<!--                    x.field='occ.rate', -->
-<!--                    y.field='med.rate', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=F, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   mu.raw.hm.svm <- mu.raw.hm.svm + ylab('Nightly Rate') -->
-
-<!--   mu.qtl.hm.svm <- abbHeatMap(host.data.ic[mu, ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   mu.qtl.hm.svm <- mu.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx1'} -->
-
-<!-- ggMultiPlots(mu.raw.hm.svm, mu.qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx2'} -->
-
-<!--   un.raw.hm.svm <- abbHeatMap(host.data.ic[un, ], -->
-<!--                    x.field='occ.rate', -->
-<!--                    y.field='med.rate', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=F, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   un.raw.hm.svm <- un.raw.hm.svm + ylab('Nightly Rate') -->
-
-<!--   un.qtl.hm.svm <- abbHeatMap(host.data.ic[un, ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.ext.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   un.qtl.hm.svm <- un.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->
-
-<!-- ``` -->
-
-<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx23'} -->
-
-<!-- ggMultiPlots(un.raw.hm.svm, un.qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->

### 2017-03-09 abb_Functions.R
adding statsig and logdx functions

@@ -1213,3 +1213,26 @@ abbPrefAnalysisViz <- function(ic.df,
   
 }
 
+### Create a vector of significance stars for regression results -------------------------
+
+makeStatSig <- function(x){
+  x <- as.numeric(x)
+  y <- rep('***', length(x))
+  y[x > .01] <- '** '
+  y[x > .05] <- '*  '
+  y[x > .1] <- '   '
+  y
+}
+
+### Diagnostics for logistic regression models -------------------------------------------
+logDx <- function(log.model, data, resp.var){
+  
+  pred <- prediction(predict(log.model, data, type='response'), resp.var)
+  auc <- performance(pred, measure='auc')
+  ll <- logLik(log.model)
+  AIC <- AIC(log.model)
+  
+  return(list(AIC=AIC,
+              logLik=ll,
+              auc=auc))
+}

### 2017-03-09 abbDataAnalysis_Script.Rmd
adding revdens

@@
   str.data$str.act.revenue <- ((str.data$bookings * str.data$med.rate) - 
-                                 (str.data$bookings * str.data$avg.guests * str.data$cpppd))
+                                 (str.data$bookings * str.data$avg.guests *
+                                    str.data$cpppd))
 
@@
   str.data$str.pot.revenue <- ((str.data$pot.occ.rate * 366 * str.data$med.rate) - 
-                                 (str.data$pot.occ.rate * 366  * str.data$avg.guests *  
-                                    str.data$cpppd))
+                                 (str.data$pot.occ.rate * 366 * 
+                                    str.data$avg.guests * str.data$cpppd))
 
@@
   ltr.data$ltr.revenue <- ltr.data$gross.revenue
+
+```
+
+#### Compute revenue densities
+
+```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
+  stra.rev$tenure <- 'Short-Term (Actual)   '
+  names(stra.rev)[2] <- 'revenue'
+  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
+  strp.rev$tenure <- 'Short-Term (potential)   '
+  names(strp.rev)[2] <- 'revenue'
+  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
+  ltr.rev$tenure <- 'Long-Term   '
+  names(ltr.rev)[2] <- 'revenue'
+  revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)
+
+  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
+    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
+    #ggtitle('Annual Revenues by Tenure Type') +
+    xlab('\nAnnual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20k', '$40k', '$60k'))+
+    theme(legend.position='none',
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000)) +
+    facet_wrap(~tenure)
+
 ```
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Set Preference data field
 
@@
 
-  rawocc.pplot <- abbPrefPlot(str.data.ic,
-                               x.field='occ.rate',
-                               split.field='sub.mrkt',
-                               smooth=TRUE,
-                               smooth.span=.35 ,
-                              spl.col=sm.col)
-  rawocc.pplot$plot
-
-```
-
-Looking at the distribution of occupancy rates, we that it is not uniform in any of the submarkets.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ggplot(str.data.ic, aes(x=occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
-    geom_density(alpha=.3) +
-    facet_wrap(~sub.mrkt) +
-    scale_color_manual(values=sm.col) +
-    scale_fill_manual(values=sm.col) +
-    scale_x_continuous(breaks=seq(0, 1, by=.5),
-                       labels=c('0%', '50%', '100%')) +
-    ylab('') +
-    xlab('Occupancy Rate') +
-    theme(legend.position='none',
-          axis.line=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks=element_blank(),
-          axis.title.y=element_blank())
-
-```
-
-We then calculate quantile values for rates and replot the charts
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+ ## Calculate the percentile fields
 
@@
 
-  ## Make quartile location plot
+ ## Calculate raw and percentile occupancies
 
-  qtlocc.pplot <- abbPrefPlot(str.data.ic,
+  rawocc.metro <- abbPrefPlot(str.data.ic,
+                         x.field='occ.rate',
+                         smooth=TRUE,
+                         smooth.span=.5)
+
+  qtlocc.metro <- abbPrefPlot(str.data.ic,
                         x.field='occ.qtl',
-                               split.field='sub.mrkt',
                         smooth=TRUE,
-                               smooth.span=.75)
-  qtlocc.pplot <- qtlocc.pplot$plot +
-    xlab('\nQualtile of Occupancy Rate') +
-    ylab('\n% of Properties where Airbnb is more profitable') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0', '25th', '50th', '75th', '100th')) +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    scale_color_manual(values=sm.col)
-
-  qtlocc.pplot
+                        smooth.span=.5)
 
@@
 
-save(clean.count, daily.data, listing.data, ltr.data, pref.table, pref.table.wide,
+save(clean.count, daily.data, listing.data, ltr.data, pref.table,
+     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro,
      s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,

### 2017-03-09 abb_Functions.R
add revdens function

@@ -471,13 +471,13 @@ compareRevenues <- function(str.df){
   
   ## Actual Revenue
   
-  str.df$str.act.prem <- str.df$str.act.revenue - str.df$ltr.imp.revenue
-  str.df$str.act.pref <- ifelse(str.df$str.act.prem > 0, 1, 0)
+  str.df$str.obs.prem <- str.df$str.obs.revenue - str.df$ltr.imp.revenue
+  str.df$str.obs.pref <- ifelse(str.df$str.obs.prem > 0, 1, 0)
   
   ## Extrapolated Revenue
   
-  str.df$str.ext.prem <- str.df$str.ext.revenue - str.df$ltr.imp.revenue
-  str.df$str.ext.pref <- ifelse(str.df$str.ext.prem > 0, 1, 0)
+  str.df$str.act.prem <- str.df$str.act.revenue - str.df$ltr.imp.revenue
+  str.df$str.act.pref <- ifelse(str.df$str.act.prem > 0, 1, 0)
   
   ## Potential Revenue
   
@@ -486,8 +486,8 @@ compareRevenues <- function(str.df){
   
   ## Return Values 
   
-  return(str.df[,c('property.id', 'str.act.prem', 'str.act.pref',
-                   'str.ext.prem', 'str.ext.pref', 
+  return(str.df[,c('property.id', 'str.obs.prem', 'str.obs.pref',
+                   'str.act.prem', 'str.act.pref', 
                    'str.pot.prem', 'str.pot.pref')])  
   
 }
@@ -1236,3 +1236,67 @@ logDx <- function(log.model, data, resp.var){
               logLik=ll,
               auc=auc))
 }
+
+### Custom function for building revenue density plots -----------------------------------
+
+
+buildRevDensPlot <- function(str.data,
+                             rev.types=c('act', 'pot'),
+                             rev.cols=1:(length(rev.types) + 1),
+                             facet=TRUE){
+  
+  ## Build the dataset  
+  
+  # Actual
+  if('act' %in% rev.types){
+    stra.rev <- str.data[,c('property.id', 'str.act.revenue')]
+    stra.rev$tenure <- 'Short-Term (Actual)   '
+    names(stra.rev)[2] <- 'revenue'
+  } else {
+    stra.rev <- NULL
+  }
+  
+  # Potential
+  if('pot' %in% rev.types){
[…]

### 2017-03-09 abb_Writeup.Rmd
fix occplot bug

@@
    load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
+   a<-1
 
@@
 For the purposes of estimating utility costs for the short-term rentals we use a mid-point value of A\$4.50 per person per day.
-As we don't know total number of guests in each reservation we use a figure of 1.7 guests per bedroom and sum up the total costs for all bookings over the year.
+As we don't know total number of guests in each reservation we use a figure of 1.5 guests per bedroom and sum up the total costs for all bookings over the year.
 
@@
 
-```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}
+```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}
 
@@
 
-```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}
+```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}
 
@@
 
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.lp='locmaps', fig.ext='png'}
+```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}
 
@@
 
-```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts', fig.lp='locbars'}
+```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}
 
@@
   # Make Plot
-  ggMultiPlots(rawocc, qtlocc, cols=2)
+  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
 

### 2017-03-09 abbDataAnalysis_Script.Rmd
reorg:  revdens

@@
 ---
-title: "Abb Analysis"
+title: "Should I Airbnb My Property: Analytic Code Explanation"
 author: "Andy Krause and Gideon Aschwanden"
-date: "February 5, 2017"
+date: "March 10, 2017"
 output: html_document
@@
 
-&nbsp;
+This document describes all of the code used to the generate the output included in the 'Should I Airbnb my Property' study.
+Additional analysis that were not included in the final report are also found within this document.
+This analysis uses the output from the **abbDataClean_Script.rmd** file found in the same online repository.
+### Preliminary Commands
 
-### Preliminary Commands
+We begin by loading the libraries necessary to do this analysis.
 
@@
 ```
+
+We then set the paths to the data, code and figures, based on the user of the document.  We also set a variable indicating whether or not we are working offline.
 
@@
 
-Next, we source the necessary custom code files for the analysis.
+Next, we source the necessary custom code files for the analysis.  We also set a few options here.
 
@@
 
+We load the workspace from the data clean script that includes the prepared data objects.
+
 ```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
 
-State gives energy costs at 330 (apt) to 520 (house).  For 2 person in apt that works out to 5 per person per day.  For house of 4 that works out to about 4 per person per day.
+### Calculating Net Revenues
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+We begin the analysis by calculating the net revenues for the short term data.
+We calculate three types of net revenues, Observed, Extrapolated (Actual) and Potential.
+The difference are described more fully in the writeup.
+
+Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
+For 2 persons in an apartment that works out to \$5 per person per day.
+For a house of 4 persons that works out to about \$4 per person per day.
+We use a mid point value of \$4.50 per person per day.
+We use an estimate of 1.5 persons per bedroom in each unit.
+
+```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
@@
 
-  str.data$str.act.revenue <- ((str.data$bookings * str.data$med.rate) - 
+```
+
+```{r obs_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.data$str.obs.revenue <- ((str.data$bookings * str.data$med.rate) - 
                                  (str.data$bookings * str.data$avg.guests *
@@
 
+```
+
+```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
   str.data$extr.par <- 366 / str.data$total.days
 
-  str.data$str.ext.revenue <- ((str.data$bookings * str.data$extr.par *
+  str.data$str.act.revenue <- ((str.data$bookings * str.data$extr.par *
                                   str.data$med.rate) - 
@@
                                     str.data$cpppd * str.data$extr.par))
-  # 
+```
+
+```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
   str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)
@@
 
-#### Compute revenue densities
-
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
-  stra.rev$tenure <- 'Short-Term (Actual)   '
-  names(stra.rev)[2] <- 'revenue'
-  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
-  strp.rev$tenure <- 'Short-Term (potential)   '
-  names(strp.rev)[2] <- 'revenue'
-  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
-  ltr.rev$tenure <- 'Long-Term   '
-  names(ltr.rev)[2] <- 'revenue'
-  revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)
-
-  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    #ggtitle('Annual Revenues by Tenure Type') +
-    xlab('\nAnnual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20k', '$40k', '$60k'))+
-    theme(legend.position='none',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000)) +
-    facet_wrap(~tenure)
-
-```
-
-### Host types
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
-  geom_density(fill=str.col, color=str.col) +
-  ylab('Frequency\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0,1,.2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Host Block Rate Frequency\n') +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.block.freq
-
-  dev.off()
-
-  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
-  geom_point(fill=str.col, color=str.col, size=.2) +
-  ylab('Nbr of Blocked Periods\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    block.rate.period
-
-  dev.off()
-
-  block.rate.period
-
-  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
-
-str.data$host.type <- 'Unknown'
-str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
-str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
-str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
-str.data$host.type <- factor(str.data$host.type,
-                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                      'Multi-Platform User', 'Unknown'))
-
-host.type <- ggplot(str.data, 
-       aes(x=block.rate, y=blockpertime, color=host.type)) + 
-  geom_point(alpha=.5, size=.8, shape=16) +
-  ylab('Number of Blocked Periods\n') + 
-  xlab('\n% of Time Property is Blocked') +
-      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-
-    scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-
-  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
-  theme(legend.position='bottom',
-          legend.title = element_blank(),
-        plot.title = element_text(hjust = 0.5))+
-    guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1)))
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type
-
-  dev.off()
-
-  host.type
-
-  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
-  geom_bar() +
-  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-  theme(legend.position='none') +
-  ylab('Frequency\n') + 
-  xlab('\nHost Type') +
-  ggtitle('Short Term Host Types') + 
-  theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type.bar
-
-  dev.off()
-
-  host.type.bar
-
-  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
-
-```
+#### Compare Revenue Distributions
 
@@
 
-We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.
+<!-- We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.  -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  imp.data <- imputeLtrRents(ltr.df=ltr.data, 
-                               str.df=str.data, 
-                               mod.spec=ltr.mod.spec,
-                               match.factor='suburb')
+<!--   imp.data <- imputeLtrRents(ltr.df=ltr.data,  -->
+<!--                                str.df=str.data,  -->
+<!--                                mod.spec=ltr.mod.spec, -->
+<!--                                match.factor='suburb') -->
 
-```
+<!-- ``` -->
 
-From the imputed results, we extract the base data (with imputed values) as well as the model summaries.
+<!-- From the imputed results, we extract the base data (with imputed values) as well as the model summaries.  -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  # Extract out DFs (only those that imputed)
-  str.glob <- merge(str.data, imp.data$imp.rent, by='property.id')
+<!--   # Extract out DFs (only those that imputed) -->
+<!--   str.glob <- merge(str.data, imp.data$imp.rent, by='property.id') -->
 
-```
+<!-- ``` -->
 
-Next we cross impute days on market and occupancy rates.
+<!-- Next we cross impute days on market and occupancy rates. -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  # Apply dom to abb
-  str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median')
+<!--   # Apply dom to abb -->
+<!--   str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median') -->
 
-```
+<!-- ``` -->
 
-With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.
+<!-- With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.  -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7)
+<!--   str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7) -->
 
-```
+<!-- ``` -->
 
-Next, we compare the revenues from the two and extract the new datasets.
+<!-- Next, we compare the revenues from the two and extract the new datasets. -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  comp.revs <- compareRevenues(str.glob)
+<!--   comp.revs <- compareRevenues(str.glob) -->
 
-  str.glob <- merge(str.glob, comp.revs, by='property.id')
+<!--   str.glob <- merge(str.glob, comp.revs, by='property.id') -->
 
-```
+<!-- ``` -->
 
@@
                                  split.field='tbg',
-                                 verbose=TRUE)
+                                 verbose=FALSE)
+
+```
+
+Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties
+
+```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
+
+  buildRevDensPlot(str.data.ic,
+                   rev.cols=c(ltr.col, abb.col[2], str.col))
 
@@
                           'pot.str', 'pot.loc', 'pot.host')
+
+```
+
+### Sensitivity
+
+### Host types
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
+  geom_density(fill=str.col, color=str.col) +
+  ylab('Frequency\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0,1,.2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Host Block Rate Frequency\n') +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.block.freq
+
+  dev.off()
+
+  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  geom_point(fill=str.col, color=str.col, size=.2) +
+  ylab('Nbr of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    block.rate.period
+
+  dev.off()
+
+  block.rate.period
+
+  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
+
+str.data$host.type <- 'Unknown'
+str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
+str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
+str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
+str.data$host.type <- factor(str.data$host.type,
+                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                      'Multi-Platform User', 'Unknown'))
+
+host.type <- ggplot(str.data, 
+       aes(x=block.rate, y=blockpertime, color=host.type)) + 
+  geom_point(alpha=.5, size=.8, shape=16) +
+  ylab('Number of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+
+  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
+  theme(legend.position='bottom',
+          legend.title = element_blank(),
+        plot.title = element_text(hjust = 0.5))+
+    guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1)))
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type
+
+  dev.off()
+
+  host.type
+
+  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
+  geom_bar() +
+  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+  theme(legend.position='none') +
+  ylab('Frequency\n') + 
+  xlab('\nHost Type') +
+  ggtitle('Short Term Host Types') + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type.bar
+
+  dev.off()
+
+  host.type.bar
+
+  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
 

### 2017-03-09 abb_Functions.R
renaming ext and sub.mrkt

@@ -598,33 +598,33 @@ abbCreateCompTable <- function(ic.df,
   
   if(split.field == 'none'){
     
+    str.obs <- mean(ic.df$str.obs.pref)
     str.act <- mean(ic.df$str.act.pref)
-    str.ext <- mean(ic.df$str.ext.pref)
     str.pot <- mean(ltr.df$str.pot.pref)
     
     rate.table <- data.frame(ID='all',
-                             var=c(str.act, str.ext, str.pot),
-                             rev.type=c('Actual', 
-                                        'Extrapolated', 
+                             var=c(str.obs, str.act, str.pot),
+                             rev.type=c('Observed', 
+                                        'Actual', 
                                         'Potential'))
     
   } else {
     
     # Calculate cross-tab values
+    str.obs <- tapply2DF(ic.df$str.obs.pref, ic.df[ ,split.field], mean)
     str.act <- tapply2DF(ic.df$str.act.pref, ic.df[ ,split.field], mean)
-    str.ext <- tapply2DF(ic.df$str.ext.pref, ic.df[ ,split.field], mean)
     str.pot <- tapply2DF(ic.df$str.pot.pref, ic.df[, split.field], mean)
     
     # Add names
+    str.obs$rev.type <- 'Observed'
     str.act$rev.type <- 'Actual'
-    str.ext$rev.type <- 'Extrapolated'
     str.pot$rev.type <- 'Potential'
     
     # Combine into table
-    rate.table <- rbind(str.act, str.ext, str.pot)
+    rate.table <- rbind(str.obs, str.act, str.pot)
     
     # Reorder factors for common split fields
-    if(split.field == 'sub.mrkt'){
+    if(split.field == 'geo.mrkt'){
       
       rate.table$ID <- factor(rate.table$ID, 
                               levels=c('city-core', 'city', 'beach',
@@ -718,7 +718,7 @@ abbPrefPlot <- function(pref.data,
   
  ## Fix Factor Levels
   
-  if(split.field == 'sub.mrkt'){
+  if(split.field == 'geo.mrkt'){
     pref.full$ID <- factor(pref.full$ID, 
                            levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
   }
@@ -1088,7 +1088,7 @@ abbPrefAnalysisViz <- function(ic.df,
   
   spl.col <- 1:nrow(pref.table)
   
[…]

### 2017-03-09 abbDataAnalysis_Script.Rmd
moving analyses from Writeup

@@
 
-## Global Market Analysis
-
-We now analyze the full metro market to test which properties are more profitable as short-term rentals.
-
-We start by specifying the imputation models for the LTR and the Airbnb datasets
+Before we examine the distributions of the observed short-term revenues and the estimated long-term revenues, we must produce the estimates of long-term revenue for the short-term properties.
+
+We start by specifying the imputation model specification we will use to estimated likely long-term (weekly) rental prices for each short-term property.
 
@@
 
-<!-- We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   imp.data <- imputeLtrRents(ltr.df=ltr.data,  -->
-<!--                                str.df=str.data,  -->
-<!--                                mod.spec=ltr.mod.spec, -->
-<!--                                match.factor='suburb') -->
-
-<!-- ``` -->
-
-<!-- From the imputed results, we extract the base data (with imputed values) as well as the model summaries.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   # Extract out DFs (only those that imputed) -->
-<!--   str.glob <- merge(str.data, imp.data$imp.rent, by='property.id') -->
-
-<!-- ``` -->
-
-<!-- Next we cross impute days on market and occupancy rates. -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   # Apply dom to abb -->
-<!--   str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median') -->
-
-<!-- ``` -->
-
-<!-- With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7) -->
-
-<!-- ``` -->
-
-<!-- Next, we compare the revenues from the two and extract the new datasets. -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   comp.revs <- compareRevenues(str.glob) -->
-
-<!--   str.glob <- merge(str.glob, comp.revs, by='property.id') -->
-
-<!-- ``` -->
-
-Realizing that the imputed long term rental values may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short term rentals, broken into submarkets by type, bed/bath and geographic area.
+We then employ a custom function to impute the long term rents for the short-term properties.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  imp.data <- imputeLtrRents(ltr.df=ltr.data,
+                               str.df=str.data,
+                               mod.spec=ltr.mod.spec,
+                               match.factor='suburb')
+
+```
+
+From the imputed results, we extract the imputed rental values and merge to the original short-term data.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Extract out DFs (only those that imputed)
+  str.metro <- merge(str.data, imp.data$imp.rent, by='property.id')
+
+```
+
+Next we impute the likely long-term search cost (days on market) for the short-term properties.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Apply dom to abb
+  str.metro$imp.dom <- imputeDOM(str.metro, ltr.data, calc.type='median')
+
+```
+
+With the imputed DOMs and weekly rental rates we now make the an estimate of likely annual revenue if leased on the long term market. We append this to the original dataset.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.metro$ltr.imp.revenue <- str.metro$imp.rent * (52 - str.metro$imp.dom / 7)
+
+```
+
+Finally we make a comparison of the observed short term revenues and the imputed long term revenue and add these field back onto the original data.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  comp.revs <- compareRevenues(str.metro)
+
+  str.metro <- merge(str.metro, comp.revs, by='property.id')
+
+```
+
+The above process of long-term revenue estimation treated the entire market as operating similarly.
+Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.
 In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
@@
 We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals.
+We use these finer scale estimates going forward (the data in the **str.data.ic** object).
 
@@
 
- str.data$tbg <- paste0(str.data$product,'.', str.data$sub.mrkt)
- ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$sub.mrkt)
+ str.data$tbg <- paste0(str.data$product,'.', str.data$geo.mrkt)
+ ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)
 
@@
 
-  buildRevDensPlot(str.data.ic,
-                   rev.cols=c(ltr.col, abb.col[2], str.col))
-
-```
-
-## Analyze Results
-
-First we make a comparison table of the results, broken down by submarket.
+  # Actual
+   stra.rev <- str.data.ic[,c('property.id', 'str.act.revenue')]
+   stra.rev$tenure <- 'Short-Term (Actual)   '
+   names(stra.rev)[2] <- 'revenue'
+
+  # Potential
+   strp.rev <- str.data.ic[,c('property.id', 'str.pot.revenue')]
+   strp.rev$tenure <- 'Short-Term (Potential)   '
+   names(strp.rev)[2] <- 'revenue'
+
+  # Long-Term
+   ltr.rev <- str.data.ic[,c('property.id', 'ltr.imp.revenue')]
+   ltr.rev$tenure <- 'Long-Term   '
+   names(ltr.rev)[2] <- 'revenue'
+
+  # Combine
+   revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)
+
+  ## Build a plot
+
+   rd.plot <- ggplot(revdens.data, 
+                     aes(x=revenue, fill=tenure, color=tenure)) +
+     geom_density(alpha=.5) +
+     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
+     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
+     xlab('\nAnnual Revenue') +
+     scale_x_continuous(breaks=c(seq(0, 75000, by=25000)),
+                        labels=c('$0', '$25k', '$50k', '$75k'))+
+     theme(legend.position='none',
+           legend.title = element_blank(),
+           plot.title = element_text(hjust = 0.5),
+           axis.text.y = element_blank(),
+           axis.ticks.y = element_blank(),
+           axis.title.y=element_blank()) +
+     coord_cartesian(xlim=c(0, 85000))
+     rd.plot <- rd.plot + facet_wrap(~tenure)
+
+  ## Plot
+
+     rd.plot
+
+```
+
+## Results
+
+We will begin by analyzing the above estimates at the entire metro scale.
+Analyses of various submarkets will follow.
+Overall, we see that 31.1\% of properties raised more revenue via short term rental than expected in the long term market.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  table(str.data.ic$str.act.pref) / nrow(str.data.ic)
+
+```
+
+Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Set Preference data field
+
+  str.data.ic$pref <- str.data.ic$str.act.pref
+
+ ## Calculate the percentile fields
+
+  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
+                                      return.type='rank') 
+  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
+                                  return.type='rank')
+
+ ## Calculate raw and percentile occupancies
+
+  rawocc.metro <- abbPrefPlot(str.data.ic,
+                         x.field='occ.rate',
+                         smooth=TRUE,
+                         smooth.span=.5)
+
+  qtlocc.metro <- abbPrefPlot(str.data.ic,
+                        x.field='occ.qtl',
+                        smooth=TRUE,
+                        smooth.span=.5)
+
+   ## Make plots
+
+  # Raw
+  raw.occ.metro <- ggplot(rawocc.metro$data,
+                   aes(x=x.var, y=Var))+
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Quantile
+  qtl.occ.metro <- ggplot(qtlocc.metro$data,
+                   aes(x=x.var, y=Var))+
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Pcntl)') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='none') + 
+    ggtitle('Percentile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
+
+```
+
+Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm <- abbHeatMap(str.data.ic,
+                x.field='occ.rate',
+                y.field='med.rate',
+                pref.field='str.act.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  rate.hm + ylab('Nightly Rate')
+
+```
+
+To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  rate.hm.svm <- abbHeatMap(str.data.ic,
+                            x.field='occ.rate',
+                            y.field='med.rate',
+                            pref.field='str.act.pref',
+                            svm=T, 
+                            alpha.count=F,
+                            add.points=T,
+                            fill.colors=c(abb.col[1], abb.col[5]))
+  rate.hm.svm+ ylab('Nightly Rate')
+
+```
+
+As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm <- abbHeatMap(str.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.act.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  qtl.hm+ ylab('Nightly  (Pcntl)')
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  qtl.hm.svm <- abbHeatMap(str.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  qtl.hm.svm+ ylab('Nightly  (Pcntl)')
+
+```
+
+### Submarkets
+
+Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.
+
+First we make a comparison table of the results.
 
@@
  # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
-                                   split.field='sub.mrkt')
-
- # Convert to wide format for output
-  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
+  pref.table.type <- abbCreateCompTable(ic.df=str.data.ic,
+                                   split.field='type')
 
  # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
-
-```
-
-We then turn this into a simple chart to see the differences
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
-  ggplot(pref.table, aes(x=ID, weights=Var, fill=ID)) + 
+  pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ]
+
+```
+
+We then turn this into a simple chart to see the differences.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) + 
     geom_bar() +
-    facet_grid(~rev.type) +
-    scale_fill_manual(values=sm.col) +
+    scale_fill_manual(values=c('red', 'blue')) +
     xlab('') +
@@
 
-Next, we plot the \% of properties that have short-term preference versus the occupancy rate
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Set Preference data field
-
-  str.data.ic$pref <- str.data.ic$str.ext.pref
-
- ## Calculate the percentile fields
-
-  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
+We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.
+
+```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Create dataset
+
+  type.data.ic <- str.data.ic
+
+  # Id the types
+  apt.id <- which(str.data.ic$type == 'Apartment')
+  house.id <- which(str.data.ic$type == 'House')
+
+  # Recalculate the percentiles
+  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
                                       return.type='rank')
-  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
+  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$occ.rate[house.id], return.type='rank')
+
+  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
                                   return.type='rank')
-
- ## Calculate raw and percentile occupancies
-
-  rawocc.metro <- abbPrefPlot(str.data.ic,
+  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
+    type.data.ic$med.rate[house.id], return.type='rank')
+
+```
+
+Then we calculate the preference figures
+
+```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+ ## Calc the occ rate numbers
+
+  rawocc.type <- abbPrefPlot(type.data.ic,
                          x.field='occ.rate',
+                         split.field='type',
                          smooth=TRUE,
-                         smooth.span=.5)
-
-  qtlocc.metro <- abbPrefPlot(str.data.ic,
+                         smooth.span=.5 ,
+                         spl.col=c('black', 'grey40'))
+
+  pctocc.type <- abbPrefPlot(type.data.ic,
                          x.field='occ.qtl',
+                         split.field='type',
                          smooth=TRUE,
-                        smooth.span=.5)
-
-```
-
-Next we build a heat map that shows which combinations of occ rate and nightly rate are most likely to result in short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm <- abbHeatMap(str.data.ic,
+                         smooth.span=.5 ,
+                         spl.col=c('black', 'grey40'))
+
+```
+
+And then plot.
+
+```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
+
+ ## Build raw plot
+
+  ptr.occ <- ggplot(rawocc.type$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_color_manual(values=c('black', 'grey60'),
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+ ## Build Percentile Plots
+
+  ptq.occ <- ggplot(pctocc.type$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Pcntl)') +
+    scale_color_manual(values=c('black', 'grey60'),
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Percentile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+ ## Plot
+
+  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
+
+```
+
+Finally, we make percentile SVM heatmaps for both apartments and houses.
+
+```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
+
+ ## Make House SVM Heatmap
+
+  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
+                                          'House', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5])) +
+  theme(legend.position='none') +
+  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
+  ylab('Nightly Rate (Pcntl)') +
+  xlab('Occupancy Rate (Pcntl)')
+
+ ## Make Apartment SVM Heat Map
+
+  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
+                                          'Apartment', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
+  ylab('Nightly Rate (Pcntl)') +
+  xlab('Occupancy Rate (Pcntl)')
+
+ ## Plot
+
+  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
+
+```
+
+#### Geographic Submarkets
+
+We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets.
+
+```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
+
+ # Make Basic comparison table
+  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                   split.field='geo.mrkt')
+
+ # Convert to wide format for output
+  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
+
+ # Limit to the extrapolated pref type
+  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
+  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
+  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
+
+ # Fix names  
+  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
+  options(xtable.comment = FALSE)
+
+ ## Make printable table
+
+  print(xtable(pref.table[,1:2], 
+               caption='Geographic Submarket Preferability\n',
+               digits=1,
+               align='llr'),
+        include.rownames=FALSE,
+        caption.placement='top')
+
+```
+
+```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}
+
+ ## Build data
+
+  subm.data.ic <- str.data.ic
+
+  # Get IDs
+  cc.id <- which(str.data.ic$geo.mrkt == 'city-core')
+  city.id <- which(str.data.ic$geo.mrkt == 'city')
+  sub.id <- which(str.data.ic$geo.mrkt == 'suburban')
+  rural.id <- which(str.data.ic$geo.mrkt == 'rural')
+  beach.id <- which(str.data.ic$geo.mrkt == 'beach')
+
+  # Recalc the percentiles
+  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
+      subm.data.ic$occ.rate[city.id], return.type='rank')
+  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
+    subm.data.ic$med.rate[city.id], return.type='rank')
+
+  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
+                                  return.type='rank')
+
+  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
+                                      return.type='rank')
+  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
+                                  return.type='rank')
+
+```
+
+```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
+
+ ## Set colors
+
+  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+
+ ## Create plot data
+
+  rawocc.geo <- abbPrefPlot(subm.data.ic,
                         x.field='occ.rate',
-                y.field='med.rate',
-                pref.field='str.ext.pref',
+                        split.field='geo.mrkt',
+                        smooth=TRUE,
+                        smooth.span=.5 ,
+                        spl.col=sm.col)
+
+  pctocc.geo <- abbPrefPlot(subm.data.ic,
+                         x.field='occ.qtl',
+                         split.field='geo.mrkt',
+                         smooth=TRUE,
+                         smooth.span=.5 ,
+                         spl.col=sm.col)
+
+ ## Make plot objects
+
+  smr.occ <- ggplot(rawocc.geo$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate') +
+    scale_color_manual(values=sm.col,
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Raw Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+  smq.occ <- ggplot(pctocc.geo$data,
+                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
+    geom_point(alpha=.5, size=.4) +
+    stat_smooth(se=FALSE, size=2, span=.5) +
+    xlab('\nOccupancy Rate (Pcntl)') +
+    scale_color_manual(values=sm.col,
+                       name='') +
+    scale_x_continuous(breaks=seq(0, 100, by=25),
+                       labels=c('0%', '25th', '50th', '75th', '100th')) +
+    ylab('\nSTR Preferability %') +
+    scale_y_continuous(breaks=seq(0, 1, by=.25),
+                       labels=c('0%', '25%', '50%', '75%', '100%')) +
+    theme(legend.position='bottom') + 
+    ggtitle('Percentile Rates') + 
+    theme(plot.title = element_text(hjust = 0.5))
+
+ ## Plot
+
+  ggMultiPlots(smr.occ, smq.occ, cols=2)
+
+```
+
+```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
+
+  # Build the SVM Heatmaps
+
+  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
+                                          'city-core', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5])) +
+  theme(legend.position='none') +
+    ylab('') +
+    xlab('') +
+  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
+
+  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
+                                          'city', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "City", size=9)
+
+  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
+                                          'suburban', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
+
+  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
+                                          'rural', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Rural", size=9)
+
+  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
+                                          'beach', ],
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.act.pref',
+                   svm=T,
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))+
+  theme(legend.position='none')+
+    ylab('') +
+    xlab('')+
+  annotate("text", x = 50, y = 50, label = "Beach", size=9)
+
+```
+
+```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
+
+  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
+               rural.hm.svm, beach.hm.svm, cols=2)
+
+```
+
+## Logit models
+
+Now we attempt to explain the drivers of preference with a set of logistic regression models.
+
+First, a basic model with just structural characteristics.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
+                                levels=c('1..1', '2..1', '2..2',
+                                         '3..1', '3..2', '4..2'))
+
+  mod.act.str <- glm(str.act.pref~type+as.factor(bedbath),
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+```
+
+Then a model that adds in the geographic submarkets
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.act.loc <- glm(str.act.pref~type+as.factor(bedbath)+
+                                  geo.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
+                                  geo.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+```
+
+Finally a model that adds in host policies.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.act.host <- glm(str.act.pref~type+as.factor(bedbath)+
+                        geo.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      family=binomial(link='logit'),
+                      data=str.data.ic)
+  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
+                        geo.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      family=binomial(link='logit'),
+                      data=str.data.ic)
+```
+
+We combine all model results in to a list for easy export.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  pref.models <- list(mod.act.str, mod.act.loc, mod.act.host, 
+                      mod.pot.str, mod.pot.loc, mod.pot.host)
+  names(pref.models) <- c('act.str', 'act.loc', 'act.host',
+                          'pot.str', 'pot.loc', 'pot.host')
+
+```
+
+We then also run a set of regression models where the premium (or discount) for short-term leasing is the dependent variable.  We use the same three model specifications as above.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
+                    data=str.data.ic)
+  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
+                    data=str.data.ic)
+
+  mod.act.loc.prem <- glm(str.act.pref~type+as.factor(bedbath)+
+                                  geo.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
+                                  geo.mrkt,
+                     family=binomial(link='logit'),
+                     data=str.data.ic)
+
+  mod.act.host.prem <- lm(str.act.prem~type+as.factor(bedbath)+
+                        geo.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      data=str.data.ic)
+  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
+                        geo.mrkt+
+                        I(max.guests/bedrooms)+min.stay+
+                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      data=str.data.ic)
+```
+
+We then package these into a list for easy export
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+    prem.models <- list(mod.act.str.prem, mod.act.loc.prem, mod.act.host.prem, 
+                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
+    names(prem.models) <- c('act.str', 'act.loc', 'act.host',
+                          'pot.str', 'pot.loc', 'pot.host')
+
+```
+
+## Sensitivity
+
+### Potential Revenue
+
+To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.
+
+```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
+
+ # Make Basic comparison table of type
+  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='type')
+ # Extract Potential Results
+  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
+
+ # Make baseic comparison table of submarkets  
+  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='geo.mrkt')
+
+ # Extract potential results  
+  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
+
+ # Combine and round  
+  st.table <- rbind(tpref.table, spref.table)
+  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
+
+ ## Fix names and print
+
+  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
+  options(xtable.comment = FALSE)
+  print(xtable(st.table[,1:2], 
+               caption='Potential Revenue Preferability\n',
+               digits=1, align='llr'),
+               include.rownames=FALSE,
+               caption.placement='top',
+               hline.after=c(-1, 0, 2, 7, 7))
+
+```
+
+Next we recrate the SVM percentile heat maps.
+
+```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+
+ ## create data and re-estimate the percentiles
+
+  pot.data.ic <- str.data.ic
+
+  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
+
+ ## Make the pecentile heatmap
+
+  pqtl.hm <- abbHeatMap(pot.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.pot.pref',
                 svm=F, 
@@
                 fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm
-
-```
-
-To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm.svm <- abbHeatMap(str.data.ic,
-                            x.field='occ.rate',
-                            y.field='med.rate',
-                            pref.field='str.ext.pref',
-                            svm=T, 
-                            alpha.count=F,
-                            add.points=T,
-                            fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm.svm
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm <- abbHeatMap(str.data.ic,
+  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
+
+ ## Make percentile SVM heatmap
+
+  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
                    x.field='occ.qtl',
                    y.field='rate.qtl',
-                pref.field='str.ext.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm.svm <- abbHeatMap(str.data.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.ext.pref',
+                   pref.field='str.pot.pref',
                    svm=T, 
@@
                    fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm.svm
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  svm.rate <- makeSVM(str.data.ic,
-                     x.field='occ.rate',
-                     y.field='nightly.rate',
-                     z.field='str.act.pref',
-                     svm.type='C-svc',
-                     svm.kernel='polydot',
-                     poly.degree=4,
-                     expand.factor=100)
-
-  svm.qtl <- makeSVM(str.data.ic,
-                      x.field='occ.qtl',
-                      y.field='rate.qtl',
-                      z.field='str.act.pref',
-                      svm.type='C-svc',
-                      svm.kernel='polydot',
-                      poly.degree=4,
-                      expand.factor=100)
-
-  market.ratio <- data.frame(type=c('rate', 'qtl'),
-                             actual=rep(mean(str.data.ic$str.act.pref), 2),
-                             fitted=c(mean(svm.rate$orig$fitted),
-                                      mean(svm.qtl$orig$fitted)),
-                             svm=c(mean(svm.rate$pred$pred),
-                                   mean(svm.qtl$pred$pred)))
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
-                                levels=c('1..1', '2..1', '2..2',
-                                         '3..1', '3..2', '4..2'))
-
-  mod.ext.str <- glm(str.ext.pref~type+as.factor(bedbath),
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  mod.ext.loc <- glm(str.ext.pref~type+as.factor(bedbath)+
-                                  sub.mrkt,
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
-                                  sub.mrkt,
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
-                        sub.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      family=binomial(link='logit'),
-                      data=str.data.ic)
-  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
-                        sub.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      family=binomial(link='logit'),
-                      data=str.data.ic)
-
-  pref.models <- list(mod.ext.str, mod.ext.loc, mod.ext.host, 
-                      mod.pot.str, mod.pot.loc, mod.pot.host)
-  names(pref.models) <- c('ext.str', 'ext.loc', 'ext.host',
-                          'pot.str', 'pot.loc', 'pot.host')
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  mod.ext.str.prem <- lm(str.ext.prem~type+as.factor(bedbath),
-                    data=str.data.ic)
-  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
-                    data=str.data.ic)
-
-  mod.ext.loc.prem <- glm(str.ext.pref~type+as.factor(bedbath)+
-                                  sub.mrkt,
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
-                                  sub.mrkt,
-                     family=binomial(link='logit'),
-                     data=str.data.ic)
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
-                        sub.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str.data.ic)
-  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
-                        sub.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str.data.ic)
-
-    prem.models <- list(mod.ext.str.prem, mod.ext.loc.prem, mod.ext.host.prem, 
-                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
-    names(prem.models) <- c('ext.str', 'ext.loc', 'ext.host',
-                          'pot.str', 'pot.loc', 'pot.host')
-
-```
-
-### Sensitivity
+  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
+    xlab('Occupancy Rate (Pcntl)') +
+  annotate("text", x = 50, y = 50, label = "Potential", size=9)
+
+ ## Add annotations to previous SVM
+
+  qtl.hm.svm.p <- qtl.hm.svm +
+  annotate("text", x = 50, y = 50, label = "Actual", size=9)
+
+```
+
+```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
+
+  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
+
+```
 
 ### Host types
+
+Finally, we test to see if grouping by hosts types has any impact.
+
+First we must divide hosts up.  We start by looking at block rate.
 
@@
 
+We then add the number of blocked periods
+
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
-
-str.data$host.type <- 'Unknown'
-str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
-str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
-str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
-str.data$host.type <- factor(str.data$host.type,
+No real pattern emerges, so we divide manually.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+str.data.ic$blockpertime <- round(str.data.ic$nbr.block * str.data.ic$extr.par, 1)
+
+str.data.ic$host.type <- 'Unknown'
+str.data.ic$host.type[str.data.ic$blockpertime > 12] <- 'Multi-Platform User'
+str.data.ic$host.type[str.data.ic$block.rate <= .25] <- 'Profit Seeker'
+str.data.ic$host.type[str.data.ic$block.rate >= .75] <- 'Opportunistic Sharer'
+str.data.ic$host.type <- factor(str.data.ic$host.type,
                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
@@
 
-host.type <- ggplot(str.data, 
+host.type <- ggplot(str.data.ic, 
        aes(x=block.rate, y=blockpertime, color=host.type)) + 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
+See the counts of each group
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+host.type.bar <- ggplot(str.data.ic, aes(host.type, fill=host.type)) +
   geom_bar() +
@@
 
+We then re-estimate the preference table.
+
+```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+ # Make Basic comparison table
+  apref.table <- abbCreateCompTable(ic.df=str.data.ic,
+                                    split.field='host.type')
+
+ # Limit to the extrapolated pref type
+  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
+  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
+  hpref.table <- hpref.table[,1:2]
+  hpref.table[,3] <- phpref.table[,2]
+  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
+  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
+
+  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
+  options(xtable.comment = FALSE)
+  print(xtable(hpref.table, 
+               caption='Host Type Preferability\n',
+               digits=1,
+               align='llrr'),
+               include.rownames=FALSE,
+               caption.placement='top')
+
+```
+
+And re-run the logistic regression models.
+
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
   mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
   mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
   mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
   mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
 
-  mod.ext.ps <- glm(str.ext.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+  mod.act.ps <- glm(str.act.pref~type+as.factor(bedbath)+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
 
-  mod.ext.os <- glm(str.ext.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+  mod.act.os <- glm(str.act.pref~type+as.factor(bedbath)+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
 
-  mod.ext.mu <- glm(str.ext.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+  mod.act.mu <- glm(str.act.pref~type+as.factor(bedbath)+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
 
-  mod.ext.un <- glm(str.ext.pref~type+as.factor(bedbath)+
-                    sub.mrkt+
+  mod.act.un <- glm(str.act.pref~type+as.factor(bedbath)+
+                    geo.mrkt+
                     I(max.guests/bedrooms)+min.stay+
@@
 
-host.models <- list(mod.ext.ps, mod.ext.os, mod.ext.mu, mod.ext.un,
+host.models <- list(mod.act.ps, mod.act.os, mod.act.mu, mod.act.un,
                     mod.pot.ps, mod.pot.os, mod.pot.mu, mod.pot.un)
-names(host.models) <- c('ext.ps', 'ext.os', 'ext.mu', 'ext.un',
+names(host.models) <- c('act.ps', 'act.os', 'act.mu', 'act.un',
                         'pot.ps', 'pot.os', 'pot.mu', 'pot.un')
@@
 
-### Moving Window Logit
-
-To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.
-Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties.
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
-                              proj4string=CRS("+init=epsg:4283"),
-                              delete_null_obj=TRUE)
-
- ssubs <- table(str.data.ic$suburb)
- s.subs <- subs[subs$id %in% names(ssubs),]
- s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),]
- sssubs <- fortify(s.suburbs)
-
-```
-
-Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Min, Max and Range
- xmin <- min(s.subs$long)
- xmax <- max(s.subs$long)
- ymin <- min(s.subs$lat)
- ymax <- max(s.subs$lat)
- xrange <- xmax-xmin
- yrange <- ymax-ymin
-
- # Set Scale
- scale <- mean(xrange, yrange)/100
-
- # Create estimation points
- est.data <- str.data.ic
- est.points <- createGridPoints(s.suburbs, scale, T)
-
-```
-
-We then specify the logistic regression model and set the moving window bandwidth.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Set model specification
-
- pot.mod.spec <- str.pot.pref ~ type + as.factor(bedbath) + 
-   I(max.guests / bedrooms) + min.stay + 
-   I(cancel.policy == 'Flexible') + 
-   I(cancel.policy == 'Strict')
-
- ext.mod.spec <- str.ext.pref ~ type + as.factor(bedbath) + 
-   I(max.guests / bedrooms) + min.stay + 
-   I(cancel.policy == 'Flexible') + 
-   I(cancel.policy == 'Strict')
-
- ## Set bandwidth
-
- k <- 400
-
-```
-
-The results are estimated with the custom MWL function
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- pot.results.all <- mwl(est.data, 
-                        est.points, 
-                        pot.mod.spec, 
-                        k)
-
- ext.results.all <- mwl(est.data, 
-                        est.points, 
-                        ext.mod.spec, 
-                        k)
-
-  pot.results.ps <- mwl(est.data[ps, ], 
-                        est.points, 
-                        pot.mod.spec, 
-                        k)
-   pot.results.os <- mwl(est.data[os, ], 
-                        est.points, 
-                        pot.mod.spec, 
-                        k)
-
-   pot.results.mu <- mwl(est.data[mu, ], 
-                        est.points, 
-                        pot.mod.spec, 
-                        k)
-
-   pot.results.un <- mwl(est.data[un, ], 
-                        est.points, 
-                        pot.mod.spec, 
-                        k)
-
-   ext.results.ps <- mwl(est.data[ps, ], 
-                        est.points, 
-                        ext.mod.spec, 
-                        k)
-   ext.results.os <- mwl(est.data[os, ], 
-                        est.points, 
-                        ext.mod.spec, 
-                        k)
-
-   ext.results.mu <- mwl(est.data[mu, ], 
-                        est.points, 
-                        ext.mod.spec, 
-                        k)
-
-   ext.results.un <- mwl(est.data[un, ], 
-                        est.points, 
-                        ext.mod.spec, 
-                        k)
-
-```
-
-Coefficents are extracted and put into a data.frame
-
-MAKE A FUNCTION BELOW HERE
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-extrMWLCoef <- function(mwl.results,
-                        est.points,
-                        names.coef){
-
- coef.names <- rownames(mwl.results[[1]])
-
- # Create a list to capture
- coef.list <- list()
-
- # Create a data.frame to capture
- coef.df <- data.frame(lat=est.points@coords[,2],
-                       long=est.points@coords[,1])
-
- # Loop through and extract coefficients
- for(cn in 1:length(coef.names)){
-   coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn])
-   coef.df[ ,ncol(coef.df) + 1] <- unlist(coef.list[[cn]])
- }
-
- # Add plottable names
- colnames(coef.df)[3:13] <- names.coef
-
- return(coef.df)
-
-}
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-x.names <- c('intercept', 'house', 'bb11', 'bb21', 'bb31',
-                              'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict')
-
-pra.coef <- extrMWLCoef(pot.results.all,
-                        est.points,
-                        x.names)
-era.coef <- extrMWLCoef(ext.results.all,
-                        est.points,
-                        x.names)
-prp.coef <- extrMWLCoef(pot.results.ps,
-                        est.points,
-                        x.names)
-pro.coef <- extrMWLCoef(pot.results.os,
-                        est.points,
-                        x.names)
-prm.coef <- extrMWLCoef(pot.results.mu,
-                        est.points,
-                        x.names)
-pru.coef <- extrMWLCoef(pot.results.un,
-                        est.points,
-                        x.names)
-erp.coef <- extrMWLCoef(ext.results.ps,
-                        est.points,
-                        x.names)
-ero.coef <- extrMWLCoef(ext.results.os,
-                        est.points,
-                        x.names)
-erm.coef <- extrMWLCoef(ext.results.mu,
-                        est.points,
-                        x.names)
-eru.coef <- extrMWLCoef(ext.results.un,
-                        est.points,
-                        x.names)
-all.mwl.coefs <- list(pra.coef, era.coef, prp.coef, pro.coef, prm.coef, pru.coef,
-                  erp.coef, ero.coef, erm.coef, eru.coef)
-names(all.mwl.coefs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru', 
-                          'erp', 'ero', 'erm', 'eru')
-
-```
-
-Finally, these coefficients are converted to a surface.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-makeMWLSurfs <- function(mwl.coefs,
-                         est.points){
-
-  # Make capture list
-  surf.list <- list()
-
-  mwl.coefs <- mwl.coefs[ ,!names(mwl.coefs) %in% c('lat', 'long')]
-
- # Create surfaces
-  for(sl in 1:ncol(mwl.coefs)){
-
-   # If NAs
-   to.cut <- which(is.na(mwl.coefs[,sl]))
-   if(length(to.cut) > 0){
-     surf.points <- est.points[-to.cut,]
-     surf.value <- mwl.coefs[-to.cut, sl]
-   } else {
-     surf.points <- est.points
-     surf.value <- mwl.coefs[ , sl]
-   }
-
-   # Surface estimation
-   surf.list[[sl]] <- point2Surface(surf.points, 
-                                    surf.value,
-                                    .01, 
-                                    1.5)
-  }
-
-  names(surf.list) <- names(mwl.coefs)
-
-return(surf.list)    
-}
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-pra.surfs <- makeMWLSurfs(pra.coef,
-                          est.points)
-era.surfs <- makeMWLSurfs(era.coef,
-                          est.points)
-
-prp.surfs <- makeMWLSurfs(prp.coef,
-                          est.points)
-pro.surfs <- makeMWLSurfs(pro.coef,
-                          est.points)
-prm.surfs <- makeMWLSurfs(prm.coef,
-                          est.points)
-pru.surfs <- makeMWLSurfs(pru.coef,
-                          est.points)
-
-erp.surfs <- makeMWLSurfs(erp.coef,
-                          est.points)
-ero.surfs <- makeMWLSurfs(ero.coef,
-                          est.points)
-erm.surfs <- makeMWLSurfs(erm.coef,
-                          est.points)
-eru.surfs <- makeMWLSurfs(eru.coef,
-                          est.points)
-all.mwl.surfs <- list(pra.surfs, era.surfs, prp.surfs, pro.surfs, prm.surfs, pru.surfs,
-                      erp.surfs, ero.surfs, erm.surfs, eru.surfs)
-names(all.mwl.surfs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru',
-                          'erp', 'ero', 'erm', 'eru')
-```
-
 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
 save(clean.count, daily.data, listing.data, ltr.data, pref.table,
-     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro,
+     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
+     pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
      s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,
@@
 ```
+
+<!-- ### Moving Window Logit -->
+
+<!-- To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.
+Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties.
+-->
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'), -->
+<!--                               proj4string=CRS("+init=epsg:4283"), -->
+<!--                               delete_null_obj=TRUE) -->
+
+<!--  ssubs <- table(str.data.ic$suburb) -->
+<!--  s.subs <- subs[subs$id %in% names(ssubs),] -->
+<!--  s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),] -->
+<!--  sssubs <- fortify(s.suburbs) -->
+
+<!-- ``` -->
+
+<!-- Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Min, Max and Range -->
+<!--  xmin <- min(s.subs$long) -->
+<!--  xmax <- max(s.subs$long) -->
+<!--  ymin <- min(s.subs$lat) -->
+<!--  ymax <- max(s.subs$lat) -->
+<!--  xrange <- xmax-xmin -->
+<!--  yrange <- ymax-ymin -->
+
+<!--  # Set Scale -->
+<!--  scale <- mean(xrange, yrange)/100 -->
+
+<!--  # Create estimation points -->
+<!--  est.data <- str.data.ic -->
+<!--  est.points <- createGridPoints(s.suburbs, scale, T) -->
+
+<!-- ``` -->
+
+<!-- We then specify the logistic regression model and set the moving window bandwidth.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  ## Set model specification   -->
+
+<!--  pot.mod.spec <- str.pot.pref ~ type + as.factor(bedbath) +  -->
+<!--    I(max.guests / bedrooms) + min.stay +  -->
+<!--    I(cancel.policy == 'Flexible') +  -->
+<!--    I(cancel.policy == 'Strict') -->
+
+<!--  act.mod.spec <- str.act.pref ~ type + as.factor(bedbath) +  -->
+<!--    I(max.guests / bedrooms) + min.stay +  -->
+<!--    I(cancel.policy == 'Flexible') +  -->
+<!--    I(cancel.policy == 'Strict') -->
+
+<!--  ## Set bandwidth -->
+
+<!--  k <- 400 -->
+
+<!-- ``` -->
+
+<!-- The results are estimated with the custom MWL function -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  pot.results.all <- mwl(est.data,  -->
+<!--                         est.points,  -->
+<!--                         pot.mod.spec,  -->
+<!--                         k) -->
+
+<!--  act.results.all <- mwl(est.data,  -->
+<!--                         est.points,  -->
+<!--                         act.mod.spec,  -->
+<!--                         k) -->
+
+<!--   pot.results.ps <- mwl(est.data[ps, ],  -->
+<!--                         est.points,  -->
+<!--                         pot.mod.spec,  -->
+<!--                         k) -->
+<!--    pot.results.os <- mwl(est.data[os, ],  -->
+<!--                         est.points,  -->
+<!--                         pot.mod.spec,  -->
+<!--                         k) -->
+
+<!--    pot.results.mu <- mwl(est.data[mu, ],  -->
+<!--                         est.points,  -->
+<!--                         pot.mod.spec,  -->
+<!--                         k) -->
+
+<!--    pot.results.un <- mwl(est.data[un, ],  -->
+<!--                         est.points,  -->
+<!--                         pot.mod.spec,  -->
+<!--                         k) -->
+
+<!--    act.results.ps <- mwl(est.data[ps, ],  -->
+<!--                         est.points,  -->
+<!--                         act.mod.spec,  -->
+<!--                         k) -->
+<!--    act.results.os <- mwl(est.data[os, ],  -->
+<!--                         est.points,  -->
+<!--                         act.mod.spec,  -->
+<!--                         k) -->
+
+<!--    act.results.mu <- mwl(est.data[mu, ],  -->
+<!--                         est.points,  -->
+<!--                         act.mod.spec,  -->
+<!--                         k) -->
+
+<!--    act.results.un <- mwl(est.data[un, ],  -->
+<!--                         est.points,  -->
+<!--                         act.mod.spec,  -->
+<!--                         k) -->
+
+<!-- ``` -->
+
+<!-- Coefficents are extracted and put into a data.frame -->
+
+<!-- MAKE A FUNCTION BELOW HERE -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!-- extrMWLCoef <- function(mwl.results, -->
+<!--                         est.points, -->
+<!--                         names.coef){ -->
+
+<!--  coef.names <- rownames(mwl.results[[1]]) -->
+
+<!--  # Create a list to capture -->
+<!--  coef.list <- list() -->
+
+<!--  # Create a data.frame to capture -->
+<!--  coef.df <- data.frame(lat=est.points@coords[,2], -->
+<!--                        long=est.points@coords[,1]) -->
+
+<!--  # Loop through and extract coefficients -->
+<!--  for(cn in 1:length(coef.names)){ -->
+<!--    coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn]) -->
+<!--    coef.df[ ,ncol(coef.df) + 1] <- unlist(coef.list[[cn]]) -->
+<!--  } -->
+
+<!--  # Add plottable names -->
+<!--  colnames(coef.df)[3:13] <- names.coef -->
+
+<!--  return(coef.df) -->
+
+<!-- } -->
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!-- x.names <- c('intercept', 'house', 'bb11', 'bb21', 'bb31', -->
+<!--                               'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict') -->
+
+<!-- pra.coef <- extrMWLCoef(pot.results.all, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- era.coef <- extrMWLCoef(act.results.all, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- prp.coef <- extrMWLCoef(pot.results.ps, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- pro.coef <- extrMWLCoef(pot.results.os, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- prm.coef <- extrMWLCoef(pot.results.mu, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- pru.coef <- extrMWLCoef(pot.results.un, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- erp.coef <- extrMWLCoef(act.results.ps, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- ero.coef <- extrMWLCoef(act.results.os, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- erm.coef <- extrMWLCoef(act.results.mu, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- eru.coef <- extrMWLCoef(act.results.un, -->
+<!--                         est.points, -->
+<!--                         x.names) -->
+<!-- all.mwl.coefs <- list(pra.coef, era.coef, prp.coef, pro.coef, prm.coef, pru.coef, -->
+<!--                   erp.coef, ero.coef, erm.coef, eru.coef) -->
+<!-- names(all.mwl.coefs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru',  -->
+<!--                           'erp', 'ero', 'erm', 'eru') -->
+
+<!-- ``` -->
+
+<!-- Finally, these coefficients are converted to a surface.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!-- makeMWLSurfs <- function(mwl.coefs, -->
+<!--                          est.points){ -->
+
+<!--   # Make capture list -->
+<!--   surf.list <- list() -->
+
+<!--   mwl.coefs <- mwl.coefs[ ,!names(mwl.coefs) %in% c('lat', 'long')] -->
+
+<!--  # Create surfaces -->
+<!--   for(sl in 1:ncol(mwl.coefs)){ -->
+
+<!--    # If NAs -->
+<!--    to.cut <- which(is.na(mwl.coefs[,sl])) -->
+<!--    if(length(to.cut) > 0){ -->
+<!--      surf.points <- est.points[-to.cut,] -->
+<!--      surf.value <- mwl.coefs[-to.cut, sl] -->
+<!--    } else { -->
+<!--      surf.points <- est.points -->
+<!--      surf.value <- mwl.coefs[ , sl] -->
+<!--    } -->
+
+<!--    # Surface estimation -->
+<!--    surf.list[[sl]] <- point2Surface(surf.points,  -->
+<!--                                     surf.value, -->
+<!--                                     .01,  -->
+<!--                                     1.5) -->
+<!--   } -->
+
+<!--   names(surf.list) <- names(mwl.coefs) -->
+
+<!-- return(surf.list)     -->
+<!-- } -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!-- pra.surfs <- makeMWLSurfs(pra.coef, -->
+<!--                           est.points) -->
+<!-- era.surfs <- makeMWLSurfs(era.coef, -->
+<!--                           est.points) -->
+
+<!-- prp.surfs <- makeMWLSurfs(prp.coef, -->
+<!--                           est.points) -->
+<!-- pro.surfs <- makeMWLSurfs(pro.coef, -->
+<!--                           est.points) -->
+<!-- prm.surfs <- makeMWLSurfs(prm.coef, -->
+<!--                           est.points) -->
+<!-- pru.surfs <- makeMWLSurfs(pru.coef, -->
+<!--                           est.points) -->
+
+<!-- erp.surfs <- makeMWLSurfs(erp.coef, -->
+<!--                           est.points) -->
+<!-- ero.surfs <- makeMWLSurfs(ero.coef, -->
+<!--                           est.points) -->
+<!-- erm.surfs <- makeMWLSurfs(erm.coef, -->
+<!--                           est.points) -->
+<!-- eru.surfs <- makeMWLSurfs(eru.coef, -->
+<!--                           est.points) -->
+<!-- all.mwl.surfs <- list(pra.surfs, era.surfs, prp.surfs, pro.surfs, prm.surfs, pru.surfs, -->
+<!--                       erp.surfs, ero.surfs, erm.surfs, eru.surfs) -->
+<!-- names(all.mwl.surfs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru', -->
+<!--                           'erp', 'ero', 'erm', 'eru') -->
+<!-- ``` -->

### 2017-03-09 abb_Writeup.Rmd
moving analyses to analysis

@@
     data.path <- 'alternate data path'
-    code.path <- 'alternate data path'
+    code.path <- 'alternate code path'
+    fig.path <- 'alternate fig path'
 
@@
                rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
-               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
-               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
+               rgb(77,226,110, maxColorValue=255), rgb(252,179,14,
+                                                       maxColorValue=255),
+               rgb(249,177,139, maxColorValue=255), rgb(191,166,100,
+                                                        maxColorValue=255),
                rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
@@
 
-```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}
+```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}
 
@@
 
-```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r plot_pt, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
+```{r plot_pt, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
 
@@
 
-```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}
+```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}
 
@@
 
-```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
+```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
 
@@
 After removing property level observations that are missing price data, we plot the distribution of the rates and rents.
-In Figure 4 we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+In \autoref{rrdist} we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
 We filter the property level data accordingly.
@@
 
-```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}
+```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'}
 
@@
 
-```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}
 
@@
 
-```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs'}
+```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
 
@@
 
-```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}
+```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}
 
@@
 
-```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}
+```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}
 
@@
 
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions', fig.lp='revdens'}
+```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'}
 
@@
     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    #ggtitle('Annual Revenues by Tenure Type') +
     xlab('\nAnnual Revenue') +
@@
 We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
-Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
+Of our sample of 5,783 short-term rental units, 1,600 or 31.6\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
 
@@
 
-```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
+```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
 
@@
 
-```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
+```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
 
@@
                 y.field='med.rate',
-                pref.field='str.ext.pref',
+                pref.field='str.act.pref',
                 svm=F, 
@@
                             y.field='med.rate',
-                            pref.field='str.ext.pref',
+                            pref.field='str.act.pref',
                             svm=T, 
@@
                 y.field='rate.qtl',
-                pref.field='str.ext.pref',
+                pref.field='str.act.pref',
                 svm=F, 
@@
                    y.field='rate.qtl',
-                   pref.field='str.ext.pref',
+                   pref.field='str.act.pref',
                    svm=T, 
@@
 
-```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Create dataset
-
-  type.data.ic <- str.data.ic
-
-  # Id the types
-  apt.id <- which(str.data.ic$type == 'Apartment')
-  house.id <- which(str.data.ic$type == 'House')
-
-  # Recalculate the percentiles
-  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
-                                      return.type='rank')
-  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$occ.rate[house.id], return.type='rank')
-
-  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
-                                  return.type='rank')
-  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$med.rate[house.id], return.type='rank')
-
- ## Calc the occ rate numbers
-
-  ptrocc <- abbPrefPlot(type.data.ic,
-                         x.field='occ.rate',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-  ptqocc <- abbPrefPlot(type.data.ic,
-                         x.field='occ.qtl',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-```
-
-```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
+<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--  ## Create dataset -->
+
+<!--   type.data.ic <- str.data.ic -->
+
+<!--   # Id the types -->
+<!--   apt.id <- which(str.data.ic$type == 'Apartment') -->
+<!--   house.id <- which(str.data.ic$type == 'House') -->
+
+<!--   # Recalculate the percentiles -->
+<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
+<!--                                       return.type='rank') -->
+<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->
+
+<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
+<!--                                   return.type='rank') -->
+<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$med.rate[house.id], return.type='rank') -->
+
+<!--  ## Calc the occ rate numbers -->
+
+<!--   ptrocc <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!--   ptqocc <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.qtl', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!-- ``` -->
+
+```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
 
@@
 
-  ptr.occ <- ggplot(ptrocc$data,
+  ptr.occ <- ggplot(rawocc.type$data,
                     aes(x=x.var, y=Var, group=ID, color=ID)) +  
@@
 
-  ptq.occ <- ggplot(ptqocc$data,
+  ptq.occ <- ggplot(pctocc.type$data,
                     aes(x=x.var, y=Var, group=ID, color=ID)) +  
@@
                    y.field='rate.qtl',
-                   pref.field='str.ext.pref',
+                   pref.field='str.act.pref',
                    svm=T,
@@
 Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
-Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
-That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.
-
-```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
+Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
+That figure drops to three in ten for rural, one in four for beach , one in fix for other city location and about one in six for suburban locations.
+
+```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE}
 
@@
   pref.table <- abbCreateCompTable(ic.df=str.data.ic,
-                                   split.field='sub.mrkt')
+                                   split.field='geo.mrkt')
 
@@
  # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
+  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
@@
 Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
-```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}
-
- ## Build data
-
-  subm.data.ic <- str.data.ic
-
-  # Get IDs
-  cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
-  city.id <- which(str.data.ic$sub.mrkt == 'city')
-  sub.id <- which(str.data.ic$sub.mrkt == 'suburban')
-  rural.id <- which(str.data.ic$sub.mrkt == 'rural')
-  beach.id <- which(str.data.ic$sub.mrkt == 'beach')
-
-  # Recalc the percentiles
-  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
-      subm.data.ic$occ.rate[city.id], return.type='rank')
-  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
-    subm.data.ic$med.rate[city.id], return.type='rank')
-
-  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
-                                  return.type='rank')
-
-```
 
@@
 
- ## Create plot data
-
-  smrocc <- abbPrefPlot(subm.data.ic,
-                        x.field='occ.rate',
-                        split.field='sub.mrkt',
-                        smooth=TRUE,
-                        smooth.span=.5 ,
-                        spl.col=sm.col)
-
-  smqocc <- abbPrefPlot(subm.data.ic,
-                         x.field='occ.qtl',
-                         split.field='sub.mrkt',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=sm.col)
-
  ## Make plot objects
 
-  smr.occ <- ggplot(smrocc$data,
+  smr.occ <- ggplot(rawocc.geo$data,
                     aes(x=x.var, y=Var, group=ID, color=ID)) +  
@@
 
-  smq.occ <- ggplot(smqocc$data,
+  smq.occ <- ggplot(pctocc.geo$data,
                     aes(x=x.var, y=Var, group=ID, color=ID)) +  
@@
 
-```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
+```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 
-  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                           'city-core', ],
@@
 
-  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                           'city', ],
@@
 
-  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                           'suburban', ],
@@
 
-  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                           'rural', ],
@@
 
-  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
+  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                           'beach', ],
@@
 
-```{r log_model, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}
+```{r log_model, echo=FALSE, message=FALSE, comment=FALSE}
 
@@
   # Extract diagnostics
-  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
-  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.ext.pref)
-  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.ext.pref)
+  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.act.pref)
+  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.act.pref)
+  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.act.pref)
 
@@
   full.table <- rbind(full.table, diag.table)
+```
+
+```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
 
@@
 
-```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
+```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
 
@@
   spref.table <- abbCreateCompTable(ic.df=str.data.ic,
-                                    split.field='sub.mrkt')
+                                    split.field='geo.mrkt')
 
@@
 
-```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+```{r pot_svm, echo=FALSE, message=FALSE, comment=FALSE}
 
  ## create data and re-estimate the percentiles
-
-  pot.data.ic <- str.data.ic
-
-  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
 
@@
 
-```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
+```{r plot_pot_svm, echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
 
@@
 
-```{r pot_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}
+```{r pot_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
 
@@
 
+```
+
+```{r table_potlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+
  # XTable
@@
 
-```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}
+```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
 
@@
 
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories', fig.lp='hosttypes'}
+```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories'}
 
@@
  # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Extrapolated', ]
+  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
   phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
@@
 
-```{r host_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}
+```{r host_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
 
@@
   # Extract diagnostics
-  hstr.dx <- logDx(host.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
-  hsm.dx <- logDx(host.models[[3]], str.data.ic, str.data.ic$str.ext.pref)
-  hhost.dx <- logDx(host.models[[4]], str.data.ic, str.data.ic$str.ext.pref)
+  hstr.dx <- logDx(host.models[[1]], str.data.ic, str.data.ic$str.act.pref)
+  hsm.dx <- logDx(host.models[[3]], str.data.ic, str.data.ic$str.act.pref)
+  hhost.dx <- logDx(host.models[[4]], str.data.ic, str.data.ic$str.act.pref)
 
@@
  hfull.table <- rbind(hfull.table, hdiag.table)
+```
+
+```{r table_hostlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
 
@@
 
-In short, about 1/4 of current Airbnb properties are outperforming their potential in the long-term market.
-If owners all operated as profit maximizers this figure could be closer to 50\% or slightly higher, if the overall demand for short-term rental could match the assumed supply increase in such a case.
+In short, about 30\% of current Airbnb properties are outperforming their potential in the long-term market.
+If owners all operated as profit maximizers this figure could be 50\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
 

### 2017-03-09 abbDataPrep_Script.Rmd
rename geo market

@@
   # Add individual classes
-  str.data$sub.mrkt <- 'rural'
-  str.data$sub.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
-  str.data$sub.mrkt[str.data$sub.class == 'Inner'] <- 'city'
-  str.data$sub.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
-  str.data$sub.mrkt[str.data$beach == 1] <- 'beach'
+  str.data$geo.mrkt <- 'rural'
+  str.data$geo.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
+  str.data$geo.mrkt[str.data$sub.class == 'Inner'] <- 'city'
+  str.data$geo.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
+  str.data$geo.mrkt[str.data$beach == 1] <- 'beach'
 
   # Order the factors properly
-  str.data$sub.mrkt <- factor(str.data$sub.mrkt, 
+  str.data$geo.mrkt <- factor(str.data$geo.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
@@
   # Add individual classes
-  ltr.data$sub.mrkt <- 'rural'
-  ltr.data$sub.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
-  ltr.data$sub.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
-  ltr.data$sub.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
-  ltr.data$sub.mrkt[ltr.data$beach == 1] <- 'beach'
+  ltr.data$geo.mrkt <- 'rural'
+  ltr.data$geo.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
+  ltr.data$geo.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
+  ltr.data$geo.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
+  ltr.data$geo.mrkt[ltr.data$beach == 1] <- 'beach'
 
   # Order the factors properly
-  ltr.data$sub.mrkt <- factor(ltr.data$sub.mrkt, 
+  ltr.data$geo.mrkt <- factor(ltr.data$geo.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-    geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
+    geom_point(data=str.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
                alpha=.2) +
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
+    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
                alpha=.1) +
@@
   strtype.map <- ggplot() +
-    geom_bar(data=str.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
     ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',
+    theme(legend.position = 'bottom',gc()
           legend.title = element_blank(),
@@
   ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
+    geom_bar(data=ltr.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
     scale_fill_manual(values=sm.col) +

### 2017-03-09 abbDataAnalysis_Script.Rmd
clean up and integration of workflow

@@
      pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
-     s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,
-     core.suburbs, est.points, exch.rate, host.models, pref.models, prem.models,
+     str.data, str.data.ic, subs,
+     core.suburbs,  exch.rate, host.models, pref.models, prem.models,
      file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))
+
+ #all.mwl.coefs, all.mwl.surfs,est.points,  s.subs, sssubs,
 

### 2017-03-09 abbDataPrep_Script.Rmd
clean up and integration of workflow

@@
     ylab('# of Properties\n') + xlab('')+
-    theme(legend.position = 'bottom',gc()
+    theme(legend.position = 'bottom',
           legend.title = element_blank(),

### 2017-03-09 abb_Functions.R

@@ -4,6 +4,7 @@
 #                                                                                        #
 ##########################################################################################
 
+
 ### Calculate the occupancy rates for each date in a range -------------------------------
 
 abbCalcDateRates <- function(daily.df){

### 2017-03-10 server.R
initial changes to Shiny input

@@ -15,393 +15,639 @@ library(ggplot2)
 library(hexbin)
 library(Hmisc)
 
-load("C:/Dropbox/Research/airBNB/data/analyzed/abb_working.RData")
+load("C:/Dropbox/Research/airBNB/data/analyzed/shinyinput.RData")
+source('c:/code/research/AirBNBMelbourne/abb_Functions.R')
 
 ######################################################################################
 ### Shiny Server ---------------------------------------------------------------------
 
 shinyServer(function(input, output) {
 
-## Extract the county data ---------------------------------------------------------------  
+## Filter the desired data  --------------------------------------------------------------  
+  
+  filterData <- eventReactive(input$plot, {
     
-  getCountyData <- eventReactive(input$county, {
-    if(input$county != 'none'){
-      res.obj <- ww[[which(names(ww) == input$county)]]
-    } else {
-      res.obj <- 'none'
+    x.data <- str.data.ic
+    
+    ## Type
+    
+    if(!input$apt){
+      x.data <- x.data[x.data$type != 'Apartment',]
     }
-    return(res.obj)
+    if(!input$house){
+      x.data <- x.data[x.data$type != 'House',]
+    }
+    
+    ## Geo Market
+    
+    if(!input$core){
+      x.data <- x.data[x.data$geo.mrkt != 'city-core',]
+    }
+    if(!input$city){
+      x.data <- x.data[x.data$geo.mrkt != 'city',]
+    }
+    if(!input$suburban){
+      x.data <- x.data[x.data$geo.mrkt != 'suburban',]
+    }
+    if(!input$rural){
+      x.data <- x.data[x.data$geo.mrkt != 'rural',]
+    }
+    if(!input$beach){
+      x.data <- x.data[x.data$geo.mrkt != 'beach',]
+    }
+    
+    ## Product Type
+    if(!input$bb11){
+      x.data <- x.data[x.data$bedbath != '1..1',]
+    }
+    if(!input$bb21){
+      x.data <- x.data[x.data$bedbath != '2..1',]
+    }
+    if(!input$bb22){
+      x.data <- x.data[x.data$bedbath != '2..2',]
+    }
+    if(!input$bb31){
+      x.data <- x.data[x.data$bedbath != '3..1',]
+    }
+    if(!input$bb32){
+      x.data <- x.data[x.data$bedbath != '3..2',]
+    }
+    if(!input$bb42){
[…]

### 2017-03-10 ui.r

@@ -23,109 +23,53 @@
         actionButton('plot', "Plot/Re-Plot Data", icon("paper-plane"), 
                      style="color: #fff; background-color: #FF5A5F; border-color: #FF5A5F"),
         hr(),
-        
-    ## Select county to view --------------------------------------------------
-        
-        selectInput('county', 'Select a Market to Analyze',
-          c('Choose a market' = 'none', 
-            'All properites' = 'all',
-            'Houses only' = 'houses',
-            'Apartments only' = 'apts',
-            'City-core' = 'city-core',
-            'City' = 'city',
-            'Suburban' = 'suburban',
-            'Rural' = 'rural',
-            'Beach' = 'beach')
-        ),
-        hr(),
-        hr()#,
-    #     
-    # ## Select which options to alter ------------------------------------------
-    #     
-    #     selectInput(
-    #       'opt', 'Select Options to Update',
-    #       c('Choose a option' = 'none',
-    #         'Graphical Aesthetics' = 'aeth',
-    #         'Data Specifics' = 'spec')
-    #     ),
-    #     hr(),
-    #     hr(),
-    #     
-    #  ## If 'aeth' option chosen ----------------------------------------------
-    # 
-    #     conditionalPanel(
-    #      condition = "input.opt == 'aeth'",
-    #   
-    #    ## Select Y value
-    #      
-    #       selectInput('yVar', "Select Y Variable",
-    #         c('Prediction Error' = "raw.error")
-    #       ), # Ends Select Y Value
-    #      
-    #    ## Select X variable
-    #       
-    #      selectInput("xVar", "Select X Variable",
-    #         c('Data/Model/Estimator' = 'dme',
-    #           'Prediction Month' = 'pred.time',
-    #           'Forecast Distance' = 'time.diff')
-    #         ), # Ends Select X Variable
-    #    
-    #    ## Select Color variable
-    #     selectInput('col', "Select Color Variable",
-    #                  c('None' = 'none',
-    #                    'Data/Model/Estimator' = 'dme',
-    #                    'Hierarchical Blend' = 'hrb')
-    #    ), # Ends Color colour
-    #    
-    #    # Select Facet Variable
-    #    selectInput("f1Var", "Select Facet Variable",
-    #                c('none' = 'none',
[…]

### 2017-03-10 server.R
added occ and revdens plots

@@ -98,177 +98,465 @@ shinyServer(function(input, output) {
    
   buildOccPlot <- eventReactive(input$plot, {
     
+    ## Obtain data
+    
     occ.data <- filterData()
     
-    ## Get correct occupancy rate field
+    ## If no data is returned
+    if(nrow(occ.data) == 0){
+      xx <- data.frame(x=c(0, 1),
+                       y=c(0, 1))
+      null.plot <- list(plot=ggplot(xx, aes(x=x, y=y)) + 
+                        annotate("text", x = .5, y = .5, 
+                                 label = "You have selected\n no properites",
+                                 size=9))
+      return(null.plot)
+    }  
+      
+    ## Get correct occupancy rate and preference field
     
-    if(input$rev.type=='Potential'){
+    if(input$rev.type=='pot'){
+      
       occ.data$occ <- occ.data$pot.occ.rate
+      occ.data$pref <- occ.data$str.pot.pref
+      
     } else {
-      odd.data$occ <- occ.data$occ.rate
+      
+      occ.data$occ <- occ.data$occ.rate
+      occ.data$pref <- occ.data$str.act.pref
+    
     }
     
     ## Tranform in pcntl is needed
     
-    ## If facet then transform by facet variable
-    
-    
-    
-    # 
-    # 
-    # ## Fixing some variables
-    # 
-    # if(x.field == 'occ' | x.field == 'occ.rate'){
-    #   
-    #   pref.data[, x.field] <- round(100 * pref.data[, x.field], 0)
-    #   
-    # }
-    # 
-    # ## Extract function of analysis
-    # 
-    # metric.fnct <- get(metric)
-    # 
-    # ## Set up capture list
-    # 
-    # pref.list <- list()
-    # 
-    # ## Loop through and create the preference plots  
-    # 
-    # for(i.pl in 1:100){
-    #   
-    #   # Extract the ith data
-    #   if(cumulative){
-    #     pref.df <- pref.data[pref.data[ ,x.field] >= i.pl, ]
-    #   } else {
-    #     pref.df <- pref.data[pref.data[ ,x.field] == i.pl, ]
-    #   }
-    #   
-    #   
-    #   if(split.field != 'none'){
-    #     
-    #     if(nrow(pref.df) > 0){
-    #       # Create the table
-    #       pref.table <- tapply2DF(pref.df$pref, 
-    #                               pref.df[ ,split.field],
-    #                               metric.fnct)
-    #     } else {
[…]

### 2017-03-10 ui.r

@@ -62,14 +62,42 @@
       checkboxInput('hostmu', "Hosts - Multiplatform Users", TRUE),
       checkboxInput('hostun', "Host - Unknowns", TRUE)
       
-    ) # Ends Conditional Panel
+    ), # Ends Conditional Panel
+    
+    # Analysis Panel
+    conditionalPanel(
+      
+      condition = "input.opt == 'anys'", 
+      
+      selectInput('rev.type', 'Select Revenue Type to Use',
+                  c('Actual' = 'act', 
+                    'Potential' = 'pot')
+      ),
+      
+      selectInput('transform', 'Use Percentiles?',
+                  c('No' = 'Raw', 
+                    'Yes' = 'Pcntl')
+      ),
+      
+      selectInput('facet.var', 'Choose Comparison Variable',
+                  c('None'= 'none',
+                    'Property Type' = 'type', 
+                    'Geographic Submarket' = 'geo.mrkt',
+                    'Product (Bed/Bath)' = 'bedbath',
+                    'Host Type' = 'host.type'),
+                  selected='none'
+      )
+    ) # Ends conditional panel
    ), # Ends sidebarPanel(
     
 ## Show main panel -----------------------------------------------------  
     
     # Show the caption and plot of the requested variable against mpg
     mainPanel(
-      tabPanel("Plot", plotOutput("occplot"))
+     tabsetPanel(
+      tabPanel("Occupancy Plot", plotOutput("occplot")),
+      tabPanel("Revenue Plot", plotOutput("rdplot"))
+     ) # Ends Tab Set Panel  
     ) # Ends MainPanel(
    ) # Ends sidebarLayout(
   ) # Ends FluidPage(

### 2017-03-10 abbDataPrep_Script.Rmd
Fixed bookings bug

@@
  cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
-                                     'longest.block', 'nbr.block', 'med.block'))
+                                     'longest.block', 'nbr.block', 'med.block', 'bookings'))
  str.data <- str.data[ ,-cut.fields]

### 2017-03-10 abb_Functions.R

@@ -219,7 +219,11 @@ abbCalcBookStr <- function(id,
     # Extract
     if(length(id.R) > 0){
       r.list <- ss.list[id.R]
+      bookings <- sum(nchar(unlist(r.list)))
+    } else {
+      bookings <- 0
     }
+    
     if(length(id.A) > 0){
       a.list <- ss.list[id.A]
       avails <- unlist(lapply(a.list, nchar))
@@ -263,6 +267,7 @@ abbCalcBookStr <- function(id,
     id.min <- NA
     id.max <- NA
     avail.rate <- NA
+    bookings <- NA
 
   }  
   
@@ -276,7 +281,8 @@ abbCalcBookStr <- function(id,
                     avail.rate=avail.rate,
                     longest.block=longest.block,
                     nbr.block=nbr.block,
-                    med.block=med.block))
+                    med.block=med.block,
+                    bookings=bookings))
 }
 
 ### Set the cleaning counter -------------------------------------------------------------

### 2017-03-10 abb_Writeup.Rmd
adding output for shiny example
Fix writeup from Booking bug

@@
 We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
-Of our sample of 5,783 short-term rental units, 1,600 or 31.6\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
+Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
 
@@
 Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
-
-<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
-
-<!--  ## Create dataset -->
-
-<!--   type.data.ic <- str.data.ic -->
-
-<!--   # Id the types -->
-<!--   apt.id <- which(str.data.ic$type == 'Apartment') -->
-<!--   house.id <- which(str.data.ic$type == 'House') -->
-
-<!--   # Recalculate the percentiles -->
-<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
-<!--                                       return.type='rank') -->
-<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
-<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->
-
-<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
-<!--                                   return.type='rank') -->
-<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
-<!--     type.data.ic$med.rate[house.id], return.type='rank') -->
-
-<!--  ## Calc the occ rate numbers -->
-
-<!--   ptrocc <- abbPrefPlot(type.data.ic, -->
-<!--                          x.field='occ.rate', -->
-<!--                          split.field='type', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5 , -->
-<!--                          spl.col=c('black', 'grey40')) -->
-
-<!--   ptqocc <- abbPrefPlot(type.data.ic, -->
-<!--                          x.field='occ.qtl', -->
-<!--                          split.field='type', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5 , -->
-<!--                          spl.col=c('black', 'grey40')) -->
-
-<!-- ``` -->
 
@@
 Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
-That figure drops to three in ten for rural, one in four for beach , one in fix for other city location and about one in six for suburban locations.
+That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.
 
@@
 
-The analyses above show that, overall, just less than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+The analyses above show that, overall, more than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
 This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference.
@@
 Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).
-However, there is a long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
+However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
 This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).
@@
 
-In short, about 30\% of current Airbnb properties are outperforming their potential in the long-term market.
+In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
 If owners all operated as profit maximizers this figure could be 50\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.

### 2017-03-10 server.R
add heatmaps, map and pref table

@@ -9,6 +9,7 @@
 library(shiny)
 library(xtable)
 library(sp)
+library(plyr)
 library(spdep)
 library(maptools)
 library(ggplot2)
@@ -90,6 +91,47 @@ shinyServer(function(input, output) {
       x.data <- x.data[x.data$host.type != 'Unknown', ]
     }
     
+    ## Get correct occupancy rate and preference field
+    
+    if(input$rev.type=='pot'){
+      
+      x.data$occ <- x.data$pot.occ.rate
+      x.data$pref <- x.data$str.pot.pref
+      
+    } else {
+      
+      x.data$occ <- x.data$occ.rate
+      x.data$pref <- x.data$str.act.pref
+      
+    }
+    
+    ## Transform in pcntl is needed
+    
+    if(input$transform=='Pcntl'){
+      
+      x.data$occ <- makeWtdQtl(x.data$occ, 
+                                 return.type='rank')
+      x.data$rate <- makeWtdQtl(x.data$med.rate, 
+                                return.type='rank')
+    } else {
+      
+      x.data$occ <- round(100 * x.data$occ, 0)
+      x.data$rate <- x.data$med.rate
+      
+    }
+    
+    ## If doing comparison, calc percentiles separately
+    
+    if(input$facet.var != 'none'){
+      
+      x.list <- split(x.data, x.data[,input$facet.var])
+      for(ix in 1:length(x.list)){
+        x.list[[ix]] <- makeWtdQtl(x.list[[ix]]$occ, return.type='rank')
+      }
+      x.data <- rbind.fill(x.data)
+    }
+    
+    
     return(x.data)
         
   })
@@ -113,32 +155,6 @@ shinyServer(function(input, output) {
       return(null.plot)
     }  
       
-    ## Get correct occupancy rate and preference field
-    
-    if(input$rev.type=='pot'){
-      
-      occ.data$occ <- occ.data$pot.occ.rate
-      occ.data$pref <- occ.data$str.pot.pref
-      
-    } else {
-      
-      occ.data$occ <- occ.data$occ.rate
-      occ.data$pref <- occ.data$str.act.pref
-    
-    }
-    
-    ## Tranform in pcntl is needed
-    
-    if(input$transform=='Pcntl'){
-
-      occ.data$occ <- makeWtdQtl(occ.data$occ, 
-                                 return.type='rank')
-    } else {
-      
-      occ.data$occ <- round(100 * occ.data$occ, 0)
-      
-    }
-    
[…]

### 2017-03-10 ui.r

@@ -86,7 +86,10 @@
                     'Product (Bed/Bath)' = 'bedbath',
                     'Host Type' = 'host.type'),
                   selected='none'
-      )
+      ),
+      
+      checkboxInput('svm', "Use SVM Heat Map", TRUE)
+      
     ) # Ends conditional panel
    ), # Ends sidebarPanel(
     
@@ -95,8 +98,12 @@
     # Show the caption and plot of the requested variable against mpg
     mainPanel(
      tabsetPanel(
+      tabPanel("Preference Summary", tableOutput("prefTable")),
       tabPanel("Occupancy Plot", plotOutput("occplot")),
+      tabPanel("Heat map", plotOutput("hmplot")),
+      tabPanel("Location map", plotOutput("locplot")),
       tabPanel("Revenue Plot", plotOutput("rdplot"))
+      
      ) # Ends Tab Set Panel  
     ) # Ends MainPanel(
    ) # Ends sidebarLayout(

### 2017-03-10 server.R
Add Logistic Model Table

@@ -506,58 +506,144 @@ shinyServer(function(input, output) {
     
     pt.data <- filterData() 
     
-    
     if(input$facet.var == 'none'){
       
       rate.table <- data.frame(ID='All Metro',
-                               var=mean(pt.data$pref))
+                               count=nrow(pt.data),
+                               var=mean(pt.data$pref),
+                               occ=mean(pt.data$occ))
       
     } else {
       
       # Calculate cross-tab values
-      rate.table <- tapply2DF(pt.data$pref, pt.data[ ,input$facet.var], mean)
-
+      counts <- as.numeric(table(pt.data[ ,input$facet.var]))
+      prefs <- tapply2DF(pt.data$pref, pt.data[ ,input$facet.var], mean)
+      occs <- tapply2DF(pt.data$occ, pt.data[ ,input$facet.var], mean)
+      rate.table <- data.frame('Market'=prefs[,1],
+                               'Observations'=counts,
+                               'STP'=prefs[,2],
+                               'occs'=occs[,2])
     } 
     
-    rate.table[,2] <- paste0(sprintf('%.2f', round(rate.table[,2] * 100, 2)), '%')
-    names(rate.table) <- c('Market', '% Short-Term Preference')
+    rate.table[,2] <- sprintf('%.0f', round(rate.table[,2], 0))
+    rate.table[,3] <- paste0(sprintf('%.2f', round(rate.table[,3] * 100, 2)), '%')
+    rate.table[,4] <- paste0(sprintf('%.2f', round(rate.table[,4], 2)), '%')
+    
+    names(rate.table) <- c('Market', 'Observations', '% Short-Term Preference',
+                           'Mean Occupancy Rate')
     rate.table <- xtable(rate.table)
+    align(rate.table) <- 'llrrr'
     
   ## Return Values
   
   return(rate.table)
     
  })
-  # 
-  # createCoefTable <- eventReactive(input$rerun, {
-  #   rNames <- buildModSpec()$namesRows
-  #   modRes <- try(estimateModel(), silent=T)
-  #   if(class(modRes) == 'try-error'){
-  #     xtable(data.frame(
-  #       message="You have filtered out too many sales, include more sales and try again"))
-  #   } else {
-  #     if(class(modRes) == 'sarlm'){
-  #       valTable <- data.frame(Coef = modRes$coefficients,
-  #                              StErr = modRes$rest.se)
[…]

### 2017-03-10 ui.r

@@ -28,9 +28,9 @@
            
     selectInput(
       'opt', 'Select Options to Update',
-      c('Choose a option' = 'none',
-        'Data Parameters' = 'data',
-        'Analysis Parameters' = 'anys')
+      c('Analysis Parameters' = 'anys',
+        'Data Parameters' = 'data'
+        )
     ),
 
     # Data Panel
@@ -102,6 +102,7 @@
       tabPanel("Occupancy Plot", plotOutput("occplot")),
       tabPanel("Heat map", plotOutput("hmplot")),
       tabPanel("Location map", plotOutput("locplot")),
+      tabPanel("Logistic Model", tableOutput("coefTable")),
       tabPanel("Revenue Plot", plotOutput("rdplot"))
       
      ) # Ends Tab Set Panel  

### 2017-03-10 server.R
add extra functions

@@ -17,7 +17,7 @@ library(hexbin)
 library(Hmisc)
 
 load("C:/Dropbox/Research/airBNB/data/analyzed/shinyinput.RData")
-source('c:/code/research/AirBNBMelbourne/abb_Functions.R')
+#load("shinyinput.RData")
 
 ######################################################################################
 ### Shiny Server ---------------------------------------------------------------------
@@ -690,4 +690,149 @@ shinyServer(function(input, output) {
 
 }) # Close Shiny Server
 
+makeSVM <- function(svm.data,
+                    x.field,
+                    y.field,
+                    z.field,
+                    svm.type='C-svc',
+                    svm.kernel='polydot',
+                    poly.degree=4,
+                    expand.factor=100,
+                    quantile=FALSE,
+                    bins=c(1, 1)){
+  
+  
+  # Create XY data
+  xy.data <- cbind(svm.data[,x.field], svm.data[,y.field])
+  
+  # Hack if all 0s
+  if(sum(svm.data[,z.field]) == 0) svm.data[1,z.field] <- 1
+  
+  # Specificy SVM
+  svm.obj <- ksvm(x=xy.data,
+                  y=svm.data[,z.field],
+                  data=xy.data,
+                  type=svm.type,
+                  kernel=svm.kernel,
+                  kpar=list(degree=poly.degree))
+  
+  # Add the fitted to the data
+  svm.data$fitted <- svm.obj@fitted
+  
+  ## Make predictions over grid
+  
+  # Set up grid
+  if(quantile){
+    
+    pred.grid <- expand.grid(seq(.5, 99.5, by=bins[1]),
+                             seq(.5, 99.5, by=bins[2]))
+    
+  } else {
+    
+    x.range <- max(svm.data[ ,x.field]) - min(svm.data[ ,x.field])
+    x.inc <- x.range / expand.factor
+    xx.min <- min(svm.data[, x.field]) 
+    xx.max <- max(svm.data[, x.field]) 
+    
+    y.range <- max(svm.data[ ,y.field]) - min(svm.data[ ,y.field])
+    y.inc <- y.range / expand.factor
+    yy.min <- min(svm.data[, y.field]) 
+    yy.max <- max(svm.data[, y.field]) 
+    
+    pred.grid <- expand.grid(seq(.5, 99.5, by=bins[1]),
[…]

### 2017-03-10 server.R
Faceted HMs and WTD bug

@@ -122,13 +122,14 @@ shinyServer(function(input, output) {
     
     ## If doing comparison, calc percentiles separately
     
-    if(input$facet.var != 'none'){
+    if(input$facet.var != 'none' & input$transform == 'Pcntl'){
       
       x.list <- split(x.data, x.data[,input$facet.var])
       for(ix in 1:length(x.list)){
-        x.list[[ix]] <- makeWtdQtl(x.list[[ix]]$occ, return.type='rank')
+        x.list[[ix]]$occ <- makeWtdQtl(x.list[[ix]]$occ, return.type='rank')
+        x.list[[ix]]$occ <- makeWtdQtl(x.list[[ix]]$occ, return.type='rank')
       }
-      x.data <- rbind.fill(x.data)
+      x.data <- rbind.fill(x.list)
     }
     
     
@@ -401,7 +402,20 @@ shinyServer(function(input, output) {
        
   })
  
-### Make the Revenue Density Plot  
+### Make a wrapper for heatmaps ----------------------------------------------------------
+  
+  heatMapWrapper <- eventReactive(input$plot, {
+    
+    hm.data <- filterData()
+   
+    hm.list <- split(hm.data, hm.data[, input$facet.var])
+    hm.plots <- lapply(hm.list, makeOneHeatMap, transform=input$transform,
+                       svm=input$svm, name.field=input$facet.var)
+    return(hm.plots)
+  
+  })
+  
+### Make the Revenue Density Plot -------------------------------------------------------- 
   
   buildRevDensPlot <- eventReactive(input$plot, {
     
@@ -664,7 +678,12 @@ shinyServer(function(input, output) {
   
   output$hmplot <- renderPlot({
     
-    buildHeatMap()
+    if(input$facet.var == 'none'){
+      buildHeatMap()
+    } else {
+      ggMultiPlots(plotlist=heatMapWrapper(), cols=2)
+    }  
+    
     
   }, height = 500, width = 500 )
   
@@ -689,6 +708,8 @@ shinyServer(function(input, output) {
   })  
 
 }) # Close Shiny Server
+
+### Additional Functions -----------------------------------------------------------------
 
 makeSVM <- function(svm.data,
                     x.field,
@@ -803,8 +824,6 @@ makeWtdQtl <- function(data.vec,
   
 }
 
-
-
 tapply2DF <- function(xData,          # Vector being tapply'd 
                       byField,        # Field to split vector by
[…]

### 2017-03-10 server.R
Map facets

@@ -480,7 +480,8 @@ shinyServer(function(input, output) {
     
     loc.data <- filterData()
     
-    loc.data$pref.x <- ifelse(loc.data$pref == 1, 'Short-Term', 'Long-Term')
+    loc.data$pref.x <- ifelse(loc.data$pref == 1, 'Short-Term Preference',
+                              'Long-Term Preference')
     loc.data$pref.x <- as.factor(loc.data$pref.x)
     
     xlims <- c(min(loc.data$longitude), max(loc.data$longitude))
@@ -514,6 +515,18 @@ shinyServer(function(input, output) {
 
   })
 
+### Location map wrapper -----------------------------------------------------------------
+  
+  locMapWrapper <- eventReactive(input$plot, {
+    
+    loc.data <- filterData()
+    
+    loc.list <- split(loc.data, loc.data[, input$facet.var])
+    loc.plots <- lapply(loc.list, makeOneLocMap, name.field=input$facet.var)
+    return(loc.plots)
+    
+  })
+  
 ### Create Preference Table --------------------------------------------------------------  
   
   createPrefTable <- eventReactive(input$plot, {
@@ -691,8 +704,12 @@ shinyServer(function(input, output) {
   
   output$locplot <- renderPlot({
     
-    buildLocMap()
-    
+    if(input$facet.var == 'none'){
+      buildLocMap()
+    } else {
+      ggMultiPlots(plotlist=locMapWrapper(), cols=2)
+    }  
+
   }, height = 500, width = 500 )
   
 ### Output preference table  ------------------------------------------------------------- 
@@ -1015,4 +1032,44 @@ ggMultiPlots <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
                                       layout.pos.col = matchidx$col))
     }
   }
+}
+
+
+makeOneLocMap <- function(loc.data,
+                          name.field){
+  
+  loc.name <- names(table(as.character(loc.data[ ,name.field])))
+  
+  loc.data$pref.x <- ifelse(loc.data$pref == 1, 'Short-Term Preference',
+                            'Long-Term Preference')
+  loc.data$pref.x <- as.factor(loc.data$pref.x)
+  
+  xlims <- c(min(loc.data$longitude), max(loc.data$longitude))
+  ylims <- c(min(loc.data$latitude), max(loc.data$latitude))
+  
+  ggplot() +
+    geom_polygon(data=subs, aes(x=long, y=lat, group=group), 
+                 fill='white', color='grey70') +
[…]

### 2017-03-10 server.R
larger output plots

@@ -1,6 +1,6 @@
 ################################################################################
 #                                                                              #
-#   Server for Reproducible Real Estate Analysis                               #
+#   Server for Should I Airbnb My Property Research                            #
 #                                                                              #  
 ################################################################################
 
@@ -15,9 +15,21 @@ library(maptools)
 library(ggplot2)
 library(hexbin)
 library(Hmisc)
+library(gstat)
+library(geosphere)
+library(ggmap)
+library(chron)
+library(rgeos)
+library(reshape2)
+library(stringr)
+library(RColorBrewer)
+library(kernlab)
+library(lmtest)
+library(ROCR)
 
-load("C:/Dropbox/Research/airBNB/data/analyzed/shinyinput.RData")
-#load("shinyinput.RData")
+
+#load("C:/Dropbox/Research/airBNB/data/analyzed/shinyinput.RData")
+load("shinyinput.RData")
 
 ######################################################################################
 ### Shiny Server ---------------------------------------------------------------------
@@ -677,7 +689,7 @@ shinyServer(function(input, output) {
     
     buildOccPlot()
     
-  }, height = 500, width = 500 )
+  }, height = 1000, width = 1000 )
   
 ### Output the revenue density plot ------------------------------------------------------------  
   
@@ -685,7 +697,7 @@ shinyServer(function(input, output) {
     
     buildRevDensPlot()
     
-  }, height = 500, width = 500 )
+  }, height = 1000, width = 1000 )
   
 ### Output the revenue density plot ------------------------------------------------------------  
   
@@ -698,7 +710,7 @@ shinyServer(function(input, output) {
     }  
     
     
-  }, height = 500, width = 500 )
+  }, height = 1000, width = 1000 )
   
 ### Output Location Map ------------------------------------------------------------------  
   
@@ -710,7 +722,7 @@ shinyServer(function(input, output) {
       ggMultiPlots(plotlist=locMapWrapper(), cols=2)
     }  
 
-  }, height = 500, width = 500 )
+  }, height = 1000, width = 1000 )
   
 ### Output preference table  ------------------------------------------------------------- 
   

### 2017-03-10 ui.r

@@ -1,6 +1,6 @@
 ################################################################################
 #                                                                              #
-#   User Interface for Zesimate MD Shiny App                                   #                                               #
+#   User Interface for Should I Airbnb My Property                             #                                               #
 #                                                                              #
 ################################################################################
 

### 2017-03-10 abb_Writeup.Rmd
Hypertext links and acknowledgements

@@
 Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
-All the code used to complete this analysis, done in the R language, is available for download at www.github.com/andykrause/airbnbmelbourne.
-An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at shinyapps.io/somename.
+All the code used to complete this analysis, done in the R language, is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
+An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
+
+### Acknowledgements
+
+The authors would like to thank the Real Estate Research Institute (RERI) for funding this work and the Australian Property Monitors (APM) for providing the long-term rental data.
 

### 2017-03-10 abb_ExecSumm.Rmd
Adding new results to Exec Summary

@@
 author: "Andy Krause and Gideon Aschwanden"
-date: "January 16, 2017"
+date: "March 13, 2017"
 output: pdf_document
@@
 
-This research sets out to test under which conditions, if any, a short-term leasing strategy (Airbnb) generates more revenue than a traditional long-term approach.
+This research sets out to test under which conditions, if any, a short-term leasing strategy (Airbnb) generates more net revenue than a traditional long-term approach.
 Our data and analysis focus on the Melbourne metropolitan region.
-To make comparisons between short and long-term markets we analyze observed and estimated revenues for a particular scenario where a property owner purchases a property on September 1 2015 and makes a decision between long or short-term rental for the next 12 months.
+To make comparisons between short- and long-term markets we analyze observed and estimated revenues for a particular scenario where a property owner purchases a property on September 1 2015 and makes a decision between long- or short-term rental for the next 12 months.
 
-Our exploratory analysis shows that the univariate distribution of actual short-term revenues (from Airbnb) is much more variable than observed long term revenue.
+Our exploratory analysis shows that the univariate distribution of actual short-term revenues (from Airbnb) is much more variable than observed long-term revenue.
 Most Airbnb'd properties makes less but some make more, much more.
 To form a better comparison of revenues between like properties, we impute likely long-term revenues for the short-term properties using a model based on the long-term rental market observations.
-Over the entire market, we find that 31\% of the Airbnb properties did collect more revenue than they would likely do so with a long-term leasing strategy.
+Over the entire market, we find that 27.7\% of the Airbnb properties did collect more revenue than they would likely do so with a long-term leasing strategy.
 The probability of preference for a short-term strategy, however, is not equal for all types of properties.
@@
 1. Apartments versus homes
-2. Larger properties versus smaller properties
-3. Properties in the city core (central 18 suburbs)
+2. Smaller versus larger properties
+3. Properties in the city-core (central 18 suburbs)
 4. Rural areas as opposed to suburban (but not versus city properties)
 
-We also find the following host behaviors or policies to result in higher probability of short-term preference:
+We also find the following host behaviors or policies result in higher probability of short-term preference:
 
@@
 Overall, we find that, indeed, some properties may generate more revenue under a short-term approach than in a long-term strategy.
-The probability of acheiving short-term preference is highest for large apartments in the city core with low minimum stays, strict cancellation policies and a high number of guests per bedroom.
+The probability of acheiving short-term preference is highest for small apartments in the city-core with low minimum stays, strict cancellation policies and a high number of guests per bedroom.
 However, even within the core city apartment market an owner must achieve a nightly rate and an overall occupancy rate both above the median in order to reach an equal probability of short-term preference.
-In other words, there is solid competition in this market and short-term preference depends on proper pricing and high occupancy.
+In other words, there is solid competition in this market and short-term preference depends on proper pricing, high occupancy and host policies.
 
-It is no surprise, given these results, that inner city apartment make up a large proportion of the Airbnb market in Melbourne.
+Sensitivity test suggest that using a measure of potential revenue (ignoring effect of blocked days) equates to a higher baseline probability for short-term preference, however, the direction and magnitude of influence of the various structural, location and policy factors on determine preference remains similar between the two revenue types (actual or potential).
+Additional sensitivity tests also show that, based on availability schedules, not all users appear to be using the Airbnb portal for the purpose of profit maximization.
+When we limit the sample to those user who appear to be attempting to maximize revenues we find that the baseline short-term preference rate is much higher, slightly greater than 50\%, but that, like the use of potential revenue, the imnpacts of the various structural, location and policy factors remain similar to the analyses using the entire market.
+
+In sum, slightly more than one in four Airbnb'd units is making more than they would on the long-term market.
+If we look only at those host who are aggressively chasing revenue this proportion increases to just over 50\%.
+In both instances, the cases of short-term preference are not evenly distributed but focused on small apartments in the city center leased by hosts with liberal use but strict cancellation policies.
+It is no surprise, given these results, that inner city apartments make up a large proportion of the Airbnb market in Melbourne.
 The market appears aware, to some extent, of the profitability of this property type under a short-term approach.
+It will be interesting to examine the market moving forward to see if supply in these area has already or will eventually outstrip demand.

### 2017-03-19 abb_ExecSumm.Rmd
Adding websites to Exec Summary

@@
 ---
-title: "Should I Airbnb my Property?:  \n Executive Summary"
-author: "Andy Krause and Gideon Aschwanden"
+title: 'Should I Airbnb my Property?: Executive Summary'
+author:
+- Andy Krause
+- '&'
+- Gideon Aschwanden
+- University of Melbourne
 date: "March 13, 2017"
-output: pdf_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 It will be interesting to examine the market moving forward to see if supply in these area has already or will eventually outstrip demand.
+
+Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).
+An interactive website that allows for deeper exploration of the data and intermediate results is available at: [andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).

### 2017-03-19 abb_ExecSumm.Rmd
final changes to exec summary

--- 2017-03-10 abb_ExecSumm.Rmd
@@
 ---
-title: "Should I Airbnb my Property?:  \n Executive Summary"
-author: "Andy Krause and Gideon Aschwanden"
-date: "March 13, 2017"
-output: pdf_document
+title:    |
+    | Should I Airbnb my Property:    
+    | Executive Summary
+    |   
+    |
+
+author:
+- Andy Krause
+- '&'
+- Gideon Aschwanden
+- University of Melbourne
+date: "March 17, 2017"
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 Our data and analysis focus on the Melbourne metropolitan region.
-To make comparisons between short- and long-term markets we analyze observed and estimated revenues for a particular scenario where a property owner purchases a property on September 1 2015 and makes a decision between long- or short-term rental for the next 12 months.
+To make comparisons between short- and long-term markets we analyze observed short-term and imputed long-term revenues for a particular scenario where a property owner purchases a property on September 1 2015 and makes a decision between long- or short-term rental for the next 12 months.
 
-Our exploratory analysis shows that the univariate distribution of actual short-term revenues (from Airbnb) is much more variable than observed long-term revenue.
+Our exploratory analysis shows that the univariate distribution of observed short-term revenues (from Airbnb) is much more variable than observed long-term revenue from the traditional rental market.
 Most Airbnb'd properties makes less but some make more, much more.
-To form a better comparison of revenues between like properties, we impute likely long-term revenues for the short-term properties using a model based on the long-term rental market observations.
+To form a better comparison of revenues between similar properties, we impute likely long-term revenues for the short-term properties using a model based on the long-term rental market observations.
 Over the entire market, we find that 27.7\% of the Airbnb properties did collect more revenue than they would likely do so with a long-term leasing strategy.
@@
 
-Sensitivity test suggest that using a measure of potential revenue (ignoring effect of blocked days) equates to a higher baseline probability for short-term preference, however, the direction and magnitude of influence of the various structural, location and policy factors on determine preference remains similar between the two revenue types (actual or potential).
+Sensitivity tests suggest that using a measure of potential revenue (ignoring effect of blocked days) equates to a higher baseline probability for short-term preference, however, the direction and magnitude of influence of the various structural, location and policy factors on determining preference remains similar between the two revenue types (actual or potential).
 Additional sensitivity tests also show that, based on availability schedules, not all users appear to be using the Airbnb portal for the purpose of profit maximization.
-When we limit the sample to those user who appear to be attempting to maximize revenues we find that the baseline short-term preference rate is much higher, slightly greater than 50\%, but that, like the use of potential revenue, the imnpacts of the various structural, location and policy factors remain similar to the analyses using the entire market.
+When we limit the sample to those hosts who appear to be attempting to maximize revenues we find that the baseline short-term preference rate is much higher, slightly greater than 50\%, but that, like the use of potential revenue, the imnpacts of the various structural, location and policy factors remain similar to the analyses using the entire market.
 
 In sum, slightly more than one in four Airbnb'd units is making more than they would on the long-term market.
-If we look only at those host who are aggressively chasing revenue this proportion increases to just over 50\%.
+If we look only at those hosts who are aggressively chasing revenue this proportion increases to just over 50\%.
 In both instances, the cases of short-term preference are not evenly distributed but focused on small apartments in the city center leased by hosts with liberal use but strict cancellation policies.
-It is no surprise, given these results, that inner city apartments make up a large proportion of the Airbnb market in Melbourne.
+It is no surprise given these results that inner city apartments make up a large proportion of the Airbnb market in Melbourne.
 The market appears aware, to some extent, of the profitability of this property type under a short-term approach.
 It will be interesting to examine the market moving forward to see if supply in these area has already or will eventually outstrip demand.
+
+Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).
+An interactive website that allows for deeper exploration the results is available at: [andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).

### 2017-03-20 abb_Writeup.Rmd
Add R package citations

@@
 Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
-All the code used to complete this analysis, done in the R language, is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
+All the code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
 An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.

### 2017-03-21 abb_Writeup.Rmd
GA edits, intro litreview

@@
 author: "Andy Krause and Gideon Aschwanden"
-date: "March 10, 2017"
+date: "March 17, 2017"
 output:
@@
 Should they though?
-Or rather, is it more profitable to do so when compared to a more traditional long-term rental (LTR)?
+Or rather, is it more profitable to do so when compared to long-term rental (LTR)?
 And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one.
@@
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
+
 We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues.
@@
 However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
-Within the extant work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resort access properties.
-This focus resulted from the fact that, until a few years ago, the STR market itself operated almost wholly within this sphere.
+Within the existing work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resort access properties.
+This focus resulted from the fact that, until a few years ago, the STR market itself operated almost wholly within these market segments.
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
@@
 As a result, the short-term rental market has garnered significant interest in the public policy and legal sphere as of late.
-As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on neighbors in the way of externalies such as noise and congestion [@frost2006commentary].
+As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on immediate neighbors in the way of externalies such as noise and congestion [@frost2006commentary].
 While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].
@@
 
-Australia implements a particular tax policy, often termed `negative gearing', that allows for favourable tax treatment to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
+Australia implements a particular tax policy, often termed `negative gearing', that allows for income tax deduction to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
 While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
@@
 Leasing costs $L$ are the fees paid to the rental agency to find and manage tenants over the life of the long-term lease.
-In Melbourne, rates generally range from 5\% to 7\% per annum.
+In Melbourne, agency rates generally range from 5\% to 7\% per annum.
 We have assumed leasing costs of 6\% of the total gross revenue of the long-term lease contract.

### 2017-03-21 abb_Writeup.Rmd
ga edits, exploratory results

@@
 Airbnb is the largest short-term rental hub in the Melbourne region.
-As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beaches and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
+As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas as well and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
 The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
-The short-term data include two types of observations, property level and nightly.
+The short-term data include two types of observations, property-level and nightly-per-property.
 Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period.^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
-These nightly data indicate the advertised price, the occupancy status and a unique reservation identification.
+The nightly data indicate the advertised price, the occupancy status and a unique reservation identification.
 
@@
 There are missing nightly observations during the time period before September 1, 2015.
-After initially imputing these observations we found the results unreliable and have structured the analysis to only cover the time period containing complete data.
+After initially imputing these observations we found the results unreliable and have structured the analysis to cover only the time period containing complete data.
 All monetary values in the Airbnb data are in US dollars and have been converted to Australian dollars using the median of the exchange rate during this time period, 1.32 Australian dollars to 1 US dollar.
@@
 In raw form this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
-For example, if a property were listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
+For example, if a property was listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
 These four observations are grouped by an event-specific identification number.
@@
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+Inner suburbs are < 10km from the CBD, Middle suburbs 10 to 20km from CBD and Outer suburbs > 20km from CBD.
 In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high-end neighborhoods in the east and southeastern areas of the middle suburbs.
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
-\autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
-
-```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}
-
- load(paste0(fig.path, 'suburbMap.RData'))
-
- loc.map <- loc.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
- loc.map
-
-```
+
+<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->
+
+<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->
+
+<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
+
+<!--  loc.map <- loc.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--  loc.map -->
+
+<!-- ``` -->
 
@@
 For the short-term rentals it is somewhat more complicated.
+
 First, we must deal with those properties that were not listed for the entire 12-month period.
@@
 Second, many of the short-term properties have a significant number of blocked days, days in which the property was not offered on Airbnb.
-Here too, there is a problem with comparing observed revenues from a property with a 40\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portal during those blocked days.
+Here too, there is a problem with comparing observed revenues from a property with a 40\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portals during those blocked days.
 And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.
@@
 While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
-When looking at potential revenues, however, a great deal more may have the potential to produce more revenue.
+When looking at potential revenues, however, a great deal more may have the potential to produce additional revenue.
 The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
@@
     geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
+    stat_smooth(se=FALSE, size=1.5, span=.5) +
     xlab('\nOccupancy Rate') +
@@
     geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
+    stat_smooth(se=FALSE, size=1.5, span=.5) +
     xlab('\nOccupancy Rate (Pcntl)') +
@@
   theme(legend.position='none') +
-    ylab('') +
-    xlab('') +
+    ylab('Nightly Rate Percentile') +
+    xlab('Occupancy Rate Percentile') +
   annotate("text", x = 50, y = 50, label = "City-Core", size=9)
@@
   theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
+    ylab('Nightly Rate Percentile') +
+    xlab('Occupancy Rate Percentile') +
   annotate("text", x = 50, y = 50, label = "City", size=9)
@@
   theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
+    ylab('Nightly Rate Percentile') +
+    xlab('Occupancy Rate Percentile') +
   annotate("text", x = 50, y = 50, label = "Suburban", size=9)
@@
   theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
+    ylab('Nightly Rate Percentile') +
+    xlab('Occupancy Rate Percentile') +
   annotate("text", x = 50, y = 50, label = "Rural", size=9)
@@
   theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
+    ylab('Nightly Rate Percentile') +
+    xlab('Occupancy Rate Percentile') +
   annotate("text", x = 50, y = 50, label = "Beach", size=9)
@@
 
-```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
+```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'}
 

### 2017-03-21 abb_Writeup.Rmd
ga comments, results

@@
 
-We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of:
+We specify three, increasingly complex, logistic regression models.
+We use the actual revenue (not potential) as the dependent variable here, saving an anaylsis of potential revenue for the subsequent sensitivity tests.
+
+Model 1 takes the form of:
 
@@
 
-where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term preference, $PType$ is the property type (apartment or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+where $STPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term preference, $PType$ is the property type (apartment or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
 
@@
 Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.
+
 Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
 The difference between the Rural and City-Core is not significant, however.
-The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.
+The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking to the robustness of those estimates.
 The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.
-This is likely due to the fact that houses are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.
+This is likely due to the fact that there are sturctural differences between the geographic submarkets.
+Houses, for example, are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.
 
@@
 The above uses the Actual^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
-Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to the treatment of blocked days.
+Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to not factoring in the impact of blocked days.
 If we, instead, assume that blocked days could be leased out on the short-term market at the same overall occupancy rate as the unblocked (observed) days we can produce a potential revenue figure.
-Note that it is possible (likely?) that the large oversupply of available units onto the market that would happen if no properties blocked their units would decrease both prices and occupancy rates.
+Note that it is possible (likely?) that the large oversupply of available units in the market that would occur if no properties blocked their units would decrease both prices and occupancy rates.
 We do not attempt to correct for this likelihood, rather we offer these figures as high end estimates.
@@
 Overall, the choice of revenue type, Actual or Potential, does affect some of the conclusions to be derived from the results above.
-As expected, under the Potential case there are more properties (50\% vs 27\%) that exhibit short-term preference.
+As expected, under the Potential case there are more properties (53\% vs 28\%) that exhibit short-term preference.
 Under the scenario, the possibilities of increasing revenue by moving from long- to short-term leasing appear much better.
-Again, however, we have not attempted to measure or estimate how this hypothetical flood of properties onto the market (due to the elimation of blocked days) would impact overall market dynamics.
+Again, however, we have not attempted to measure or estimate how this hypothetical increase of properties in the market (due to the elimation of blocked days) would impact overall market dynamics.
 Suffice it to say that it would like drive down occupancies and maybe price, therefore leading to a decrease in short-term preference likelihood.
@@
 This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate.
-Only the base probability of short-term preference increases in the the potential revenue case
-
-More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for leasing for the entire calendar year and the remainder of the market does not do so.
+Only the base probability of short-term preference increases in the potential revenue case.
+
+More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for short-term leasing for the entire calendar year and, ceteris paribus, the remainder of the market does not do so.
 
@@
 
-The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated .
+The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
@@
 In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
-If owners all operated as profit maximizers this figure could be 50\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
+If owners all operated as profit maximizers this figure could be 53\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
 

### 2017-03-21 abb_Writeup.Rmd
Final edits

@@
 
+  abb.col[1] <- abb.col[3]
+  abb.col[5] <- abb.col[6]
+
 ```
@@
 They are also more likely to affix items to the structure.
-Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.].
-Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short- or long-term rentals.
+Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left.^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.]  Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short- or long-term rentals.
 As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
@@
 Our data for short-term rentals comes from the Airbnb platform.
-In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay].
-Some hosts add additional 'linen' fees to cover costs of laundering.
+In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
@@
 When looking at potential revenues, however, a great deal more may have the potential to produce additional revenue.
-The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].
+The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
 
@@
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In Figure 10 (left panel) we plot nightly rates versus occupancy rates.
+In \autoref{metrohm} (left panel) we plot nightly rates versus occupancy rates.
 We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short-term or long-term revenue.
@@
 However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
-This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).
+This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (\autoref{pointmaps}).
 Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.

### 2017-03-21 server.R
color change

@@ -31,6 +31,7 @@ library(ROCR)
 #load("C:/Dropbox/Research/airBNB/data/analyzed/shinyinput.RData")
 load("shinyinput.RData")
 
+
 ######################################################################################
 ### Shiny Server ---------------------------------------------------------------------
 
@@ -404,7 +405,7 @@ shinyServer(function(input, output) {
   ## Add legend   
      
     hm.plot <- hm.plot +
-      scale_fill_manual(values=c('red', 'forestgreen'),
+      scale_fill_manual(values=c("#00758C", "#FCB30E"),
                         name='',
                         labels=c('Long Term Preferred     ',
                                  'Short Term Preferred     ')) +
@@ -466,8 +467,8 @@ shinyServer(function(input, output) {
     rd.plot <- ggplot(revdens.data, 
                       aes(x=revenue, fill=tenure, color=tenure)) +
       geom_density(alpha=.5) +
-      scale_fill_manual(values=c('red', 'green')) +
-      scale_color_manual(values=c('red', 'green')) +
+      scale_fill_manual(values=c("#00758C", '#FCB30E')) +
+      scale_color_manual(values=c("#00758C", '#FCB30E')) +
       xlab('\nAnnual Revenue') +
       scale_x_continuous(breaks=c(seq(0, 75000, by=25000)),
                          labels=c('$0', '$25k', '$50k', '$75k'))+
@@ -504,7 +505,7 @@ shinyServer(function(input, output) {
                    fill='white', color='grey70') +
       geom_point(data=loc.data, aes(x=longitude, y=latitude, color=pref.x),
                  size=.4, alpha=.5) +
-      scale_color_manual(values=c('red', 'forestgreen'),
+      scale_color_manual(values=c("#00758C", "#FCB30E"),
                          name='Preference    ') +
       xlab('') + ylab('')+
       theme(legend.position = 'bottom',
@@ -994,7 +995,7 @@ makeOneHeatMap <- function(hm.data,
   ## Add legend   
   
   hm.plot <- hm.plot +
-    scale_fill_manual(values=c('red', 'forestgreen'),
+    scale_fill_manual(values=c("#00758C", "#FCB30E"),
                       name='',
                       labels=c('Long Term Preferred     ',
                                'Short Term Preferred     ')) +
@@ -1064,7 +1065,7 @@ makeOneLocMap <- function(loc.data,
                  fill='white', color='grey70') +
[…]

### 2017-03-21 abb_ExecSumm.Rmd
typo fix

@@
 Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).
-An interactive website that allows for deeper exploration the results is available at: [andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).
+An interactive website that allows for deeper exploration of the results is available at: [https://andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).

### 2017-10-22 abb_str_PreProcess.R
Add: Update to include data up to Mar 2017

@@ -6,80 +6,88 @@
 
  ## Load libraries
 
-  library(chron)
   library(plyr)
   library(stringr)
   library(lubridate)
   library(dplyr)
   library(multidplyr)
 
-  ## Set location
-
-  # Get computer names
-  comp.name <- Sys.info()['nodename']
+  ## Set locations
 
   # Assign path based on computer name
-  if(comp.name == '7020D-121777-W' | 
-     comp.name == 'DESKTOP-1D7JO4J' |
-     comp.name == 'GREENFIELD15'){
+  data_path <- 'c:/dropbox/research/airBNB/data/'
   
-    data.path <- 'c:/dropbox/research/airBNB/data/'
+  # Code Path
+  code_path <- getwd()
   
-  } else {
-  
-    data.path <- 'other path'
-  
-  }
-
  ## Load sources
 
-  source("c:/code/research/airbnbMelbourne/abb_Functions.R")
+  source(file.path(code_path, "abb_Functions.R"))
 
  ## Load Data  
    
   # Property Information
 
   str.data <- read.csv(file.path(data.path, '/raw/melbproperties.csv'), header=T)
-
+  str.data2 <- read.csv(file.path(data.path, '/raw/melbproperties_to_mar2017.csv'), 
+                        header=T)
+  
   # Daily rental information
 
   daily.data  <- read.csv(file.path(data.path, '/raw/melbDaily.csv'), header=T)
-
+  daily.data2  <- read.csv(file.path(data.path, '/raw/melbDaily_to_mar2017.csv'), header=T)
+  
  ## Fix Names
   
   names(str.data) <- tolower(names(str.data))
+  names(str.data2) <- tolower(names(str.data2))
   names(daily.data) <- tolower(names(daily.data))
-
+  names(daily.data2) <- tolower(names(daily.data2))
+  
+ ## Determine unique observations
+  
+  # Structure Data
+  str_df <- dplyr::bind_rows(str.data2, str.data)
+  str_df <- str_df %>% dplyr::filter(!duplicated(property.id))  
+  
+  # Daily Data
+  daily_df <- dplyr::bind_rows(daily.data2, daily.data) %>%
+    dplyr::mutate(uniq_id = paste0(property.id, '_', date)) %>%
+    dplyr::filter(!duplicated(uniq_id)) %>%
+    dplyr::select(property.id, date, status, price, booked.date, reservation.id)
+  
  ## Fix Dates  
   
   # Daily data
-  daily.data$date <- as.Date(daily.data$date)
-
[…]

### 2017-10-23 abbDataPrep_Script.Rmd
co
Add:  Seasonality sensitivity test prep

--- 2017-03-09 abbDataPrep_Script.Rmd
@@
 &nbsp;
+```{r set_dates}
+
+  library(lubridate)
+  data_name <- 'jun'
+  strike_date <- lubridate::as_date('2015-06-01')
+
+```
 
@@
   library(xtable)
-  library(chron)
+  # library(chron)
   library(plyr)
@@
   library(Hmisc)
+  library(dplyr)
+  library(multidplyr)
+  library(lubridate)
 
@@
   # Get computer names
-
-  comp.name <- Sys.info()['nodename']
-
-  # Assign path based on computer name
-
-  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
 
@@
 
-  } else {
-
-    data.path <- 'alternate data path'
-    code.path <- 'alternate data path'
-    fig.path <- 'alternate data path'
-
-  }
-
 ```
@@
 
-  source(paste0(code.path, '/dataVizTools/ggPlotTools.R'))
-  source(paste0(code.path, '/datamgmttools/dataMungeTools.R'))
-  source(paste0(code.path, '/spatialTools/spatialLogitModels.R'))
-  source(paste0(code.path, '/spatialTools/point2surface_Tools.R'))
+  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
+  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
+  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
+  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))
 
@@
 
-  str.data <- str.data[, str.keep.flds]
+  str_df <- str_df[, str.keep.flds]
 
@@
 
-  names(str.data) <- c('property.id', 'host.id', 'listing.title', 'property.type',
+  names(str_df) <- c('property.id', 'host.id', 'listing.title', 'property.type',
                        'listing.type', 'created.date', 'latitude', 'longitude',
@@
 
-  str.data <- str.data[(str.data$max.date - str.data$min.date) >= 178, ]
-  str.data <- str.data[str.data$max.date >= '2016-03-01' &
-                         str.data$min.date <= '2016-03-01', ]
-
-  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]
+  str_df <- str_df[(str_df$max.date - str_df$min.date) >= 178, ]
+
+  str_df <- str_df[str_df$max.date >= (strike_date + 182) &
+                         str_df$min.date <= (strike_date + 182), ]
+
+  daily_df <- daily_df[daily_df$date >= strike_date, ]
 
@@
 
-  ltr.data <- ltr.data[ltr.data$event.date >= '2014-09-01' & 
-                            ltr.data$event.date <= '2015-08-31', ]
+  ltr.data <- ltr.data[ltr.data$event.date >= (strike_date - 365) & 
+                            ltr.data$event.date <= (strike_date - 1), ]
   listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
@@
 
-  str.data$str.month <- 1
-  daily.data$str.month <- as.numeric(as.factor(substr(daily.data$date, 1, 7)))
+  str_df$str.month <- 1
+  daily_df$str.month <- as.numeric(as.factor(substr(daily_df$date, 1, 7)))
 
@@
 
-  str.data$type <- 'Other'
-  str.data$type[str.data$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
-  str.data$type[str.data$property.type %in% c('House', 'Townhouse')] <- 'House'
+  str_df$type <- 'Other'
+  str_df$type[str_df$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
+  str_df$type[str_df$property.type %in% c('House', 'Townhouse')] <- 'House'
 
@@
 
-  str.types <- ggplot(str.data, aes(x=type)) + 
+  str.types <- ggplot(str_df, aes(x=type)) + 
     geom_bar(color=str.col, fill=str.col) +
@@
 
-  str.data <- subset(str.data, type != 'Other')
+  str_df <- subset(str_df, type != 'Other')
   ltr.data <- subset(ltr.data, type != 'Other')
@@
   # Fix data types and names
-  str.data$listing.type <- as.character(str.data$listing.type)
-  str.data$listing.type[str.data$listing.type == 'Entire home/apt'] <- 'Entire home'
-
-  list.types <- ggplot(str.data, aes(x=listing.type)) + 
+  str_df$listing.type <- as.character(str_df$listing.type)
+  str_df$listing.type[str_df$listing.type == 'Entire home/apt'] <- 'Entire home'
+
+  list.types <- ggplot(str_df, aes(x=listing.type)) + 
       geom_bar(color=str.col, fill=str.col) +
@@
 
-  str.data <- str.data[str.data$listing.type == 'Entire home', ]
+  str_df <- str_df[str_df$listing.type == 'Entire home', ]
 
@@
   # Short term data
-  str.data <- str.data[!is.na(str.data$bedrooms), ]
-  str.data <- str.data[str.data$bedrooms <= 10, ]
+  str_df <- str_df[!is.na(str_df$bedrooms), ]
+  str_df <- str_df[str_df$bedrooms <= 10, ]
 
@@
 
-  strbed <- ggplot(str.data, aes(x=bedrooms)) + 
+  strbed <- ggplot(str_df, aes(x=bedrooms)) + 
     geom_bar(fill=str.col, color=str.col) +
@@
 
-  str.data <- str.data[str.data$bedrooms < 5, ]
+  str_df <- str_df[str_df$bedrooms < 5, ]
   ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
@@
 
-  str.id <- which(str.data$bedrooms > 3 & str.data$type =='Apartment')
+  str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
   ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
 
-  if(length(str.id) > 0) str.data <- str.data[-str.id, ]
+  if(length(str.id) > 0) str_df <- str_df[-str.id, ]
   if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]
@@
   # Convert 0 Bed to 1 Bed  
-  str.data$bedrooms[str.data$bedrooms == 0] <- 1
+  str_df$bedrooms[str_df$bedrooms == 0] <- 1
 
@@
   ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
-  str.data <- str.data[!is.na(str.data$baths), ]
+  str_df <- str_df[!is.na(str_df$baths), ]
 
@@
 
-  stbath <- ggplot(str.data, aes(x=baths)) + 
+  stbath <- ggplot(str_df, aes(x=baths)) + 
     geom_bar(fill=str.col, color=str.col) +
@@
   # Short term data
-  str.data <- str.data[str.data$baths < 4, ]
-  str.data <- str.data[str.data$baths > 0, ]
+  str_df <- str_df[str_df$baths < 4, ]
+  str_df <- str_df[str_df$baths > 0, ]
 
@@
 
-  str.data$baths <- round(str.data$baths + .01, 0)
+  str_df$baths <- round(str_df$baths + .01, 0)
 
@@
   ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
-  str.data$bedbath <- paste0(str.data$bedrooms, '..', str.data$baths)
+  str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)
 
@@
 
-  stbb <- ggplot(str.data, aes(x=bedbath)) +
+  stbb <- ggplot(str_df, aes(x=bedbath)) +
     geom_bar(fill=str.col, color=str.col) + 
@@
   ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
-  str.data <- str.data[str.data$bedbath %in% acc.bb, ]
+  str_df <- str_df[str_df$bedbath %in% acc.bb, ]
 
@@
 
-  str.data$bedbath <- factor(str.data$bedbath, 
+  str_df$bedbath <- factor(str_df$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
@@
 
-  str.data$product <- paste0(substr(str.data$type, 1, 1), str.data$bedbath)
+  str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
   ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
@@
   ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
-  str.data <- str.data[!is.na(str.data$nightly.rate), ]
+  str_df <- str_df[!is.na(str_df$nightly.rate), ]
 
@@
 
-  str.data$average.daily.rate <- str.data$average.daily.rate * exch.rate
-  str.data$nightly.rate <- str.data$nightly.rate * exch.rate
-  str.data$weekly.rate <- str.data$weekly.rate * exch.rate
-  str.data$monthly.rate <- str.data$monthly * exch.rate
+  str_df$average.daily.rate <- str_df$average.daily.rate * exch.rate
+  str_df$nightly.rate <- str_df$nightly.rate * exch.rate
+  str_df$weekly.rate <- str_df$weekly.rate * exch.rate
+  str_df$monthly.rate <- str_df$monthly * exch.rate
 
@@
 
-  daily.data$price <- daily.data$price * exch.rate
+  daily_df$price <- daily_df$price * exch.rate
 
@@
    # Get all of the reservations
-  resv.daily <- daily.data[daily.data$status == 'R', ]
+  resv.daily <- daily_df[daily_df$status == 'R', ]
 
@@
   # Add median rate to the property  
-  str.data$med.rate <- med.daily$Var[match(str.data$property.id, med.daily$ID)]
+  str_df$med.rate <- med.daily$Var[match(str_df$property.id, med.daily$ID)]
 
   # Remove those with no valid median rate
-  str.data <- str.data[!is.na(str.data$med.rate), ]
+  str_df <- str_df[!is.na(str_df$med.rate), ]
 
@@
   # Nightly Rate plot
-  rate.plot <- ggplot(str.data, aes(x=nightly.rate)) + 
+  rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
     geom_density(fill=str.col, alpha=.8) + 
@@
 
-  str.data <- str.data[str.data$med.rate >= 50 &
-                         str.data$med.rate <= 500, ]
+  str_df <- str_df[str_df$med.rate >= 50 &
+                         str_df$med.rate <= 500, ]
 
@@
 
-  str.data$bookings <- round(str.data$total.days * 
-                               (1 - (str.data$block.rate + str.data$avail.rate)), 0)
+  str_df$bookings <- round(str_df$total.days * 
+                               (1 - (str_df$block.rate + str_df$avail.rate)), 0)
 
@@
 
-  str.data <- str.data[str.data$bookings > 0, ]
-
-  str.data$gross.revenue <- (str.data$bookings * str.data$med.rate) 
+  str_df <- str_df[str_df$bookings > 0, ]
+
+  str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
   ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
 
-  str.small <- str.data[,c('baths', 'gross.revenue')]
+  str.small <- str_df[,c('baths', 'gross.revenue')]
   str.small$tenure <- 'short-term'
@@
 
-  latMid <- median(str.data$latitude)
-  longMid <- median(str.data$longitude)
+  latMid <- median(str_df$latitude)
+  longMid <- median(str_df$longitude)
 
@@
   # Convert to point shapefile
-  str.prop.shp <- SpatialPointsDataFrame(cbind(str.data$longitude,
-                                               str.data$latitude),
-                                         str.data,
+  str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
+                                               str_df$latitude),
+                                         str_df,
                                          proj4string=CRS("+init=epsg:4283"))
@@
   spJoin <- over(str.prop.shp, suburbs.shp)
-  str.data$suburb <- as.character(spJoin$name_2006)
-  str.data$suburb[is.na(str.data$suburb)] <- 'missing'
+  str_df$suburb <- as.character(spJoin$name_2006)
+  str_df$suburb[is.na(str_df$suburb)] <- 'missing'
 
   # Add suburb designation
-  str.data$sub.class <- as.character(spJoin$suburbdesi)
-  str.data$sub.class[is.na(str.data$sub.class)] <- 'missing'
+  str_df$sub.class <- as.character(spJoin$suburbdesi)
+  str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'
 
@@
   spJoin <- over(str.prop.shp, sa1s.shp)
-  str.data$sa1 <- spJoin$sa1_main11
+  str_df$sa1 <- spJoin$sa1_main11
 
@@
   spJoin <- over(str.prop.shp, beach.buffer)
-  str.data$beach <- ifelse(is.na(spJoin), 0 ,1)
+  str_df$beach <- ifelse(is.na(spJoin), 0 ,1)
 
   # Remove those missing a suburb classification (out of area)
-  str.data <- str.data[str.data$sub.class != 'missing', ]
-  str.data <- str.data[str.data$sa1 != 'missing', ]
+  str_df <- str_df[str_df$sub.class != 'missing', ]
+  str_df <- str_df[str_df$sa1 != 'missing', ]
 
@@
   # Add individual classes
-  str.data$geo.mrkt <- 'rural'
-  str.data$geo.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
-  str.data$geo.mrkt[str.data$sub.class == 'Inner'] <- 'city'
-  str.data$geo.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
-  str.data$geo.mrkt[str.data$beach == 1] <- 'beach'
+  str_df$geo.mrkt <- 'rural'
+  str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
+  str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
+  str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
+  str_df$geo.mrkt[str_df$beach == 1] <- 'beach'
 
   # Order the factors properly
-  str.data$geo.mrkt <- factor(str.data$geo.mrkt, 
+  str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-    geom_point(data=str.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
+    geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
                alpha=.2) +
@@
   strtype.map <- ggplot() +
-    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
+    geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
     scale_fill_manual(values=sm.col) +
@@
   # Convert suburbs from factor to character
-  str.data$suburb <- as.character(str.data$suburb)
+  str_df$suburb <- as.character(str_df$suburb)
   ltr.data$suburb <- as.character(ltr.data$suburb)
@@
 
-  daily.data <- daily.data[daily.data$property.id %in% str.data$property.id,]
+  daily_df <- daily_df[daily_df$property.id %in% str_df$property.id,]
 
@@
 
- # Calculate the new daily summaries
-
- daily.summ.list <- lapply(as.list(str.data$property.id), abbCalcBookStr,
-                            book.data=daily.data)
- daily.summ <- rbind.fill(daily.summ.list)
- daily.summ$min.date <- daily.summ$max.date <- NULL
+    # Create new cluster
+  abb_cl <- get_default_cluster()
+
+  # Register function and variable
+  cluster_copy(abb_cl, abbCalcBookStr)
+
+  # Summarize daily by property
+  daily_summ <- daily_df %>% 
+    multidplyr::partition(property.id, cluster=abb_cl) %>% 
+    dplyr::do(abbCalcBookStr(.)) %>% 
+    dplyr::collect()
 
  # Remove existing 
- cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
-                                     'longest.block', 'nbr.block', 'med.block'))
- str.data <- str.data[ ,-cut.fields]
+ str_df <- str_df %>%
+   dplyr::select(-c(total.days, block.rate, avail.rate, longest.block, nbr.block,
+                    med.block, bookings))
 
  # Add summary data to property data
- str.data <- merge(str.data, 
-                   daily.summ, 
-                   by.x='property.id',
-                   by.y='id')
+ str_df <- str_df %>% dplyr::left_join(daily_summ, by='property.id')
 
@@
 
-  cpmiss <- which(str.data$cancel.policy == '')
-  str.data <- str.data[-cpmiss, ]
+  str_df <- str_df %>% 
+    dplyr::filter(cancel.policy %in% c('Flexible', 'Moderate', 'Strict'))
 
@@
 
-  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
-  str.data$cancel.policy[ss60] <- 'Strict'
+  ss60 <- which(str_df$cancel.policy == 'Super Strict 60 Days')
+  str_df$cancel.policy[ss60] <- 'Strict'
 
@@
 
-  save(str.data, ltr.data, daily.data, listing.data, subs, abb.col, 
+  save(str_df, ltr.data, daily_df, listing.data, subs, abb.col, 
        beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
@@
        ltr.run.total, str.run.total,
-       file=paste0(data.path, 'prepared/prep_workspace.RData'))
-
-```
+       file=paste0(data.path, 'prepared/prep_workspace_', data_name, '.RData'))
+
+```

### 2017-10-23 abb_Functions.R

@@ -174,6 +174,7 @@ apmFixDates <- function(x.date){
   ## Return values as date format  
   
   return(as.Date(temp.date, "%d/%m/%y"))   
+  
 }
 
 ### Calculate the booking status ---------------------------------------------------------
@@ -288,8 +289,8 @@ abbCalcBookStr <- function(id.book.data){
 setCleanCount <- function(){
   
   # Make counts of initial sizes
-  str.orig <- nrow(str.data)
-  daily.orig <- nrow(daily.data)
+  str.orig <- nrow(str_df)
+  daily.orig <- nrow(daily_df)
   ltr.orig <- nrow(ltr.data)
   list.orig <- nrow(listing.data)
   
@@ -302,10 +303,10 @@ setCleanCount <- function(){
   
   # Assign initial values to globalEnv
   assign('clean.count', clean.df, envir=.GlobalEnv)
-  assign('str.run.total', nrow(str.data), envir=.GlobalEnv)
+  assign('str.run.total', nrow(str_df), envir=.GlobalEnv)
   assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
   assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
-  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
+  assign('daily.run.total', nrow(daily_df), envir=.GlobalEnv)
   
 }
 
@@ -314,8 +315,8 @@ setCleanCount <- function(){
 countCleaning <- function(operation){
 
   # Count recent cuts  
-  str.cut <- str.run.total - nrow(str.data)
-  daily.cut <- daily.run.total - nrow(daily.data)
+  str.cut <- str.run.total - nrow(str_df)
+  daily.cut <- daily.run.total - nrow(daily_df)
   ltr.cut <- ltr.run.total - nrow(ltr.data)
   listing.cut <- list.run.total - nrow(listing.data)
   
@@ -331,10 +332,10 @@ countCleaning <- function(operation){
   
   # Assign temp data to globalEnv
   assign('clean.count', comb.df, envir=.GlobalEnv)
-  assign('str.run.total', nrow(str.data), envir=.GlobalEnv)
+  assign('str.run.total', nrow(str_df), envir=.GlobalEnv)
   assign('ltr.run.total', nrow(ltr.data), envir=.GlobalEnv)
   assign('list.run.total', nrow(listing.data), envir=.GlobalEnv)
-  assign('daily.run.total', nrow(daily.data), envir=.GlobalEnv)
[…]

### 2017-10-25 abb_Writeup.Rmd
Initial Update for ARES 2018
Update to Writeup for ARES 2018

@@
 ---
-title: "Should I Airbnb My Property?"
-author: "Andy Krause and Gideon Aschwanden"
-date: "March 17, 2017"
+title: "To Airbnb?: A Question of Returns"
+subtitle: "Andy Krause and Gideon Aschwanden"
+author: "Greenfield Advisors and University of Melbourne"
+date: "October 25th, 2017"
 output:
@@
 
-  # Get computer names
-
-  comp.name <- Sys.info()['nodename']
-
-  # Assign path based on computer name
-
-  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
-
  data.path <- 'c:/dropbox/research/airBNB/data/'
@@
 
-  } else {
-
-    data.path <- 'alternate data path'
-    code.path <- 'alternate code path'
-    fig.path <- 'alternate fig path'
-
-  }
-
  ## Set options
@@
 
-  source(paste0(code.path, "dataviztools/ggplottools.R"))
-  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
+  source(paste0(code.path, "tools/dataviztools/ggplottools.R"))
+  source(paste0(code.path, "tools/datamgmttools/dataMungetools.R"))
   source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))
@@
 
-  abb.col[1] <- abb.col[3]
-  abb.col[5] <- abb.col[6]
+  strp.col <- abb.col[3]
+  ltrp.col <- abb.col[6]
 
@@
 
-   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
+   load(paste0(data.path, '/analyzed/analyzed_workspace_sep.RData'))
    a<-1
@@
 
-  rate.hm <- abbHeatMap(str.data.ic,
+  rate.hm <- abbHeatMap(str_df.ic,
                 x.field='occ.rate',
@@
                 add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
+                fill.colors=c(strp.col, ltrp.col))
   rate.hm <- rate.hm + ylab('Nightly Rate')
@@
 
-  rate.hm.svm <- abbHeatMap(str.data.ic,
+  rate.hm.svm <- abbHeatMap(str_df.ic,
                             x.field='occ.rate',
@@
                             add.points=T,
-                            fill.colors=c(abb.col[1], abb.col[5]))
+                            fill.colors=c(strp.col, ltrp.col))
   rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')
@@
 
-  qtl.hm <- abbHeatMap(str.data.ic,
+  qtl.hm <- abbHeatMap(str_df.ic,
                 x.field='occ.qtl',
@@
                 add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
+                fill.colors=c(strp.col, ltrp.col))
   qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
@@
 
-  qtl.hm.svm <- abbHeatMap(str.data.ic,
+  qtl.hm.svm <- abbHeatMap(str_df.ic,
                    x.field='occ.qtl',
@@
                    quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
+                   fill.colors=c(strp.col, ltrp.col))
   qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
@@
                    quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5])) +
+                   fill.colors=c(strp.col, ltrp.col)) +
   theme(legend.position='none') +
@@
                    quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
+                   fill.colors=c(strp.col, ltrp.col))+
   theme(legend.position='none')+
@@
  # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
+  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='geo.mrkt')
@@
   # Extract diagnostics
-  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.act.pref)
-  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.act.pref)
-  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.act.pref)
+  str.dx <- logDx(pref.models[[1]], str_df.ic, str_df.ic$str.act.pref)
+  sm.dx <- logDx(pref.models[[2]], str_df.ic, str_df.ic$str.act.pref)
+  host.dx <- logDx(pref.models[[3]], str_df.ic, str_df.ic$str.act.pref)
 
@@
  # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
+  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                     split.field='type')
@@
  # Make baseic comparison table of submarkets  
-  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
+  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                     split.field='geo.mrkt')
@@
                 add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
+                fill.colors=c(strp.col, ltrp.col))
   pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
@@
                    quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
+                   fill.colors=c(strp.col, ltrp.col))
   pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
@@
   # Extract diagnostics
-  pstr.dx <- logDx(pref.models[[4]], str.data.ic, str.data.ic$str.pot.pref)
-  psm.dx <- logDx(pref.models[[5]], str.data.ic, str.data.ic$str.pot.pref)
-  phost.dx <- logDx(pref.models[[6]], str.data.ic, str.data.ic$str.pot.pref)
+  pstr.dx <- logDx(pref.models[[4]], str_df.ic, str_df.ic$str.pot.pref)
+  psm.dx <- logDx(pref.models[[5]], str_df.ic, str_df.ic$str.pot.pref)
+  phost.dx <- logDx(pref.models[[6]], str_df.ic, str_df.ic$str.pot.pref)
 
@@
 
-  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
+  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
   geom_density(fill=str.col, color=str.col) +
@@
 
-  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
   geom_point(fill=str.col, color=str.col, size=.2) +
@@
 
-  str.data$blockpertime <- round(str.data$nbr.block * str.data$extr.par, 1)
-
-  str.data$host.type <- 'Unknown'
-  str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
-  str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
-  str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
-  str.data$host.type <- factor(str.data$host.type,
+  str_df$blockpertime <- round(str_df$nbr.block * str_df$extr.par, 1)
+
+  str_df$host.type <- 'Unknown'
+  str_df$host.type[str_df$blockpertime > 12] <- 'Multi-Platform User'
+  str_df$host.type[str_df$block.rate <= .25] <- 'Profit Seeker'
+  str_df$host.type[str_df$block.rate >= .75] <- 'Opportunistic Sharer'
+  str_df$host.type <- factor(str_df$host.type,
                                levels=c('Profit Seeker', 'Opportunistic Sharer', 
@@
 
-  base.host <- ggplot(str.data, 
+  base.host <- ggplot(str_df, 
                     aes(x=block.rate, y=blockpertime)) + 
@@
   ps.host <- base.host + 
-    geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
+    geom_point(data=str_df[str_df$host.type == 'Profit Seeker', ], size=.4)  +
     ggtitle('Profit Seekers')
@@
   os.host <- base.host + 
-    geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
+    geom_point(data=str_df[str_df$host.type == 'Opportunistic Sharer', ], 
                size=.4)  +
@@
   mu.host <- base.host + 
-    geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
+    geom_point(data=str_df[str_df$host.type == 'Multi-Platform User', ], 
                size=.4)  +
@@
   un.host <- base.host + 
-    geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
+    geom_point(data=str_df[str_df$host.type == 'Unknown', ], size=.4)  +
     ggtitle('Unknown')
@@
 
-  host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
+  host.type.bar <- ggplot(str_df, aes(host.type, fill=host.type)) +
     geom_bar() +
@@
  # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str.data.ic,
+  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                     split.field='host.type')
@@
   # Extract diagnostics
-  hstr.dx <- logDx(host.models[[1]], str.data.ic, str.data.ic$str.act.pref)
-  hsm.dx <- logDx(host.models[[3]], str.data.ic, str.data.ic$str.act.pref)
-  hhost.dx <- logDx(host.models[[4]], str.data.ic, str.data.ic$str.act.pref)
+  hstr.dx <- logDx(host.models[[1]], str_df.ic, str_df.ic$str.act.pref)
+  hsm.dx <- logDx(host.models[[3]], str_df.ic, str_df.ic$str.act.pref)
+  hhost.dx <- logDx(host.models[[4]], str_df.ic, str_df.ic$str.act.pref)
 

### 2017-10-25 abbDataAnalysis_Script.Rmd
adding output for shiny example
fix writeout options

@@
 
+&nbsp;
+
+```{r set_dates}
+
+  data_name <- 'jun'
+  strike_date <- lubridate::as_date('2015-06-01')
+
+```
+
 We then set the paths to the data, code and figures, based on the user of the document.  We also set a variable indicating whether or not we are working offline.
@@
 ```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  # Get computer names
-
-  comp.name <- Sys.info()['nodename']
-
-  # Assign path based on computer name
-
-  if(comp.name == '7020D-121777-W' | comp.name == 'DESKTOP-1D7JO4J'){
 
@@
 
-  } else {
-
-    data.path <- 'alternate data path'
-    code.path <- 'alternate data path'
-    fig.path <- 'alternate data path'
-
-  }
-
-  offline <- TRUE
-
 ```
@@
 
-  load(paste0(data.path, 'prepared/prep_workspace.RData'))
+  load(file.path(data.path, 'prepared', paste0('prep_workspace_', data_name, '.RData')))
 
@@
 
-  str.data$cpppd <- 4.5
-  str.data$avg.guests <- str.data$bedrooms * 1.5
+  str_df$cpppd <- 4.5
+  str_df$avg.guests <- str_df$bedrooms * 1.5
 
@@
 
-  str.data$str.obs.revenue <- ((str.data$bookings * str.data$med.rate) - 
-                                 (str.data$bookings * str.data$avg.guests *
-                                    str.data$cpppd))
+  str_df$str.obs.revenue <- ((str_df$bookings * str_df$med.rate) - 
+                                 (str_df$bookings * str_df$avg.guests *
+                                    str_df$cpppd))
 
@@
 
-  str.data$extr.par <- 366 / str.data$total.days
-
-  str.data$str.act.revenue <- ((str.data$bookings * str.data$extr.par *
-                                  str.data$med.rate) - 
-                                 (str.data$bookings * str.data$avg.guests * 
-                                    str.data$cpppd * str.data$extr.par))
+  str_df$extr.par <- 366 / str_df$total.days
+
+  str_df$str.act.revenue <- ((str_df$bookings * str_df$extr.par *
+                                  str_df$med.rate) - 
+                                 (str_df$bookings * str_df$avg.guests * 
+                                    str_df$cpppd * str_df$extr.par))
 ```
@@
 
-  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)
-
-  str.data$pot.occ.rate <- ((str.data$bookings * str.data$extr.par) / 
-    (366 - (366 * str.data$block.rate)))
-
-  str.data$str.pot.revenue <- ((str.data$pot.occ.rate * 366 * str.data$med.rate) - 
-                                 (str.data$pot.occ.rate * 366 * 
-                                    str.data$avg.guests * str.data$cpppd))
+  str_df$occ.rate <- 1 - (str_df$block.rate + str_df$avail.rate)
+
+  str_df$pot.occ.rate <- ((str_df$bookings * str_df$extr.par) / 
+    (366 - (366 * str_df$block.rate)))
+
+  str_df$str.pot.revenue <- ((str_df$pot.occ.rate * 366 * str_df$med.rate) - 
+                                 (str_df$pot.occ.rate * 366 * 
+                                    str_df$avg.guests * str_df$cpppd))
 
@@
   imp.data <- imputeLtrRents(ltr.df=ltr.data,
-                               str.df=str.data,
+                               str.df=str_df,
                                mod.spec=ltr.mod.spec,
@@
   # Extract out DFs (only those that imputed)
-  str.metro <- merge(str.data, imp.data$imp.rent, by='property.id')
+  str.metro <- merge(str_df, imp.data$imp.rent, by='property.id')
 
@@
 We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals.
-We use these finer scale estimates going forward (the data in the **str.data.ic** object).
+We use these finer scale estimates going forward (the data in the **str_df.ic** object).
 
@@
 
- str.data$tbg <- paste0(str.data$product,'.', str.data$geo.mrkt)
+ str_df$tbg <- paste0(str_df$product,'.', str_df$geo.mrkt)
  ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)
@@
 
- str.data.ic <- abbImputeCompare(str.df=str.data,
+ str_df.ic <- abbImputeCompare(str.df=str_df,
                                  ltr.df=ltr.data,
@@
   # Actual
-   stra.rev <- str.data.ic[,c('property.id', 'str.act.revenue')]
+   stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')]
    stra.rev$tenure <- 'Short-Term (Actual)   '
@@
   # Potential
-   strp.rev <- str.data.ic[,c('property.id', 'str.pot.revenue')]
+   strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')]
    strp.rev$tenure <- 'Short-Term (Potential)   '
@@
   # Long-Term
-   ltr.rev <- str.data.ic[,c('property.id', 'ltr.imp.revenue')]
+   ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')]
    ltr.rev$tenure <- 'Long-Term   '
@@
 
-  table(str.data.ic$str.act.pref) / nrow(str.data.ic)
+  table(str_df.ic$str.act.pref) / nrow(str_df.ic)
 
@@
 
-  str.data.ic$pref <- str.data.ic$str.act.pref
+  str_df.ic$pref <- str_df.ic$str.act.pref
 
@@
 
-  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
+  str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate, 
                                       return.type='rank') 
-  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
+  str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate, 
                                   return.type='rank')
@@
 
-  rawocc.metro <- abbPrefPlot(str.data.ic,
+  rawocc.metro <- abbPrefPlot(str_df.ic,
                          x.field='occ.rate',
@@
 
-  qtlocc.metro <- abbPrefPlot(str.data.ic,
+  qtlocc.metro <- abbPrefPlot(str_df.ic,
                         x.field='occ.qtl',
@@
  # Make Basic comparison table
-  pref.table.type <- abbCreateCompTable(ic.df=str.data.ic,
+  pref.table.type <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='type')
@@
 
-  type.data.ic <- str.data.ic
+  type.data.ic <- str_df.ic
 
   # Id the types
-  apt.id <- which(str.data.ic$type == 'Apartment')
-  house.id <- which(str.data.ic$type == 'House')
+  apt.id <- which(str_df.ic$type == 'Apartment')
+  house.id <- which(str_df.ic$type == 'House')
 
@@
 
-  subm.data.ic <- str.data.ic
+  subm.data.ic <- str_df.ic
 
   # Get IDs
-  cc.id <- which(str.data.ic$geo.mrkt == 'city-core')
-  city.id <- which(str.data.ic$geo.mrkt == 'city')
-  sub.id <- which(str.data.ic$geo.mrkt == 'suburban')
-  rural.id <- which(str.data.ic$geo.mrkt == 'rural')
-  beach.id <- which(str.data.ic$geo.mrkt == 'beach')
+  cc.id <- which(str_df.ic$geo.mrkt == 'city-core')
+  city.id <- which(str_df.ic$geo.mrkt == 'city')
+  sub.id <- which(str_df.ic$geo.mrkt == 'suburban')
+  rural.id <- which(str_df.ic$geo.mrkt == 'rural')
+  beach.id <- which(str_df.ic$geo.mrkt == 'beach')
 
@@
 
-  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
+  str_df.ic$bedbath <- factor(str_df.ic$bedbath,
                                 levels=c('1..1', '2..1', '2..2',
@@
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
   mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
 ```
@@
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
   mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
@@
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
 ```
@@
                       family=binomial(link='logit'),
-                      data=str.data.ic)
+                      data=str_df.ic)
   mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
@@
                       family=binomial(link='logit'),
-                      data=str.data.ic)
+                      data=str_df.ic)
 ```
@@
   mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
-                    data=str.data.ic)
+                    data=str_df.ic)
   mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
-                    data=str.data.ic)
+                    data=str_df.ic)
 
@@
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
   mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
@@
                      family=binomial(link='logit'),
-                     data=str.data.ic)
+                     data=str_df.ic)
 
@@
                         I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str.data.ic)
+                      data=str_df.ic)
   mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
@@
                         I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str.data.ic)
+                      data=str_df.ic)
 ```
@@
 
-  pot.data.ic <- str.data.ic
+  pot.data.ic <- str_df.ic
 
@@
 
-str.data.ic$blockpertime <- round(str.data.ic$nbr.block * str.data.ic$extr.par, 1)
-
-str.data.ic$host.type <- 'Unknown'
-str.data.ic$host.type[str.data.ic$blockpertime > 12] <- 'Multi-Platform User'
-str.data.ic$host.type[str.data.ic$block.rate <= .25] <- 'Profit Seeker'
-str.data.ic$host.type[str.data.ic$block.rate >= .75] <- 'Opportunistic Sharer'
-str.data.ic$host.type <- factor(str.data.ic$host.type,
+str_df.ic$blockpertime <- round(str_df.ic$nbr.block * str_df.ic$extr.par, 1)
+
+str_df.ic$host.type <- 'Unknown'
+str_df.ic$host.type[str_df.ic$blockpertime > 12] <- 'Multi-Platform User'
+str_df.ic$host.type[str_df.ic$block.rate <= .25] <- 'Profit Seeker'
+str_df.ic$host.type[str_df.ic$block.rate >= .75] <- 'Opportunistic Sharer'
+str_df.ic$host.type <- factor(str_df.ic$host.type,
                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
@@
 
-host.type <- ggplot(str.data.ic, 
+host.type <- ggplot(str_df.ic, 
        aes(x=block.rate, y=blockpertime, color=host.type)) + 
@@
 
-host.type.bar <- ggplot(str.data.ic, aes(host.type, fill=host.type)) +
+host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
   geom_bar() +
@@
 
-  ps <- which(str.data.ic$host.type == 'Profit Seeker')
-  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
-  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
-  un <- which(str.data.ic$host.type == 'Unknown')
+  ps <- which(str_df.ic$host.type == 'Profit Seeker')
+  os <- which(str_df.ic$host.type == 'Opportunistic Sharer')
+  mu <- which(str_df.ic$host.type == 'Multi-Platform User')
+  un <- which(str_df.ic$host.type == 'Unknown')
 
@@
                  family=binomial(link='logit'),
-                 data=str.data.ic[ps,])
+                 data=str_df.ic[ps,])
 
@@
                  family=binomial(link='logit'),
-                 data=str.data.ic[os,])
+                 data=str_df.ic[os,])
 
@@
                  family=binomial(link='logit'),
-                 data=str.data.ic[mu,])
+                 data=str_df.ic[mu,])
 
@@
                  family=binomial(link='logit'),
-                 data=str.data.ic[un,])
+                 data=str_df.ic[un,])
 
@@
 
-save(clean.count, daily.data, listing.data, ltr.data, pref.table,
+  save(clean.count, daily_df, listing.data, ltr.data, pref.table,
        pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
        pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
-     str.data, str.data.ic, subs,
+       str_df, str_df.ic, subs,
        core.suburbs,  exch.rate, host.models, pref.models, prem.models,
-     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))
+       file=file.path(data.path, 'analyzed', paste0('analyzed_workspace_', data_name, 
+                                                    '.RData')))
+
+  save(str_df.ic, subs, abb.col, file=file.path(data.path,'analyzed', 
+                                                paste0('shinyinput_', data_name, 
+                                                       '.RData')))
 
@@
 
-<!--  ssubs <- table(str.data.ic$suburb) -->
+<!--  ssubs <- table(str_df.ic$suburb) -->
 <!--  s.subs <- subs[subs$id %in% names(ssubs),] -->
@@
 <!--  # Create estimation points -->
-<!--  est.data <- str.data.ic -->
+<!--  est.data <- str_df.ic -->
 <!--  est.points <- createGridPoints(s.suburbs, scale, T) -->

### 2018-04-05 abb_Functions.R
Reorg: separate script, functions,etc.

@@ -1,1308 +1,0 @@
-##########################################################################################
-#                                                                                        #    
-#  Custom functions for working with APM and AirDNA data in the ABB Project              #
-#                                                                                        #
-##########################################################################################
-
-
-### Calculate the occupancy rates for each date in a range -------------------------------
-
-abbCalcDateRates <- function(daily.df){
-  
-  ## Create table of counts by status
-  
-  status.table <- table(daily.df$date, daily.df$status)
-  
-  ## Convert to a data.frame  
-  
-  status.df <- data.frame(Avail=status.table[,1],
-                          Resv=status.table[,2],
-                          Block=status.table[,3],
-                          lp.type=daily.df$lp.type[1])
-  
-  ## Add date   
-  
-  status.df$date <- as.Date(rownames(status.df))
-  
-  ## Add reserved rate (occupancy rate)  
-  
-  status.df$occ.rate <- status.df$Resv / (status.df$Resv + status.df$Avail)
-  
-  ## Return values  
-  
-  return(status.df)
-  
-}
-
-### Impute the missing daily observations ------------------------------------------------
-
-abbImputeDaily <- function(prop.df, 
-                           daily.df, 
-                           rates.df){
-  
-  # prop.df: data.frame of AirBNB property data
-  # daily.df: data.frame of existing AirBNB daily observations
-  # rates.df: data.frame of daily rate data (from abbCalcDateRates() function)
-  
-  ## Isolate those needing imputation  
-  
-  # Isolate
-  imp.df <- prop.df[prop.df$impute != 'no',]
-  
-  # Compute property specific rates
-  imp.df$avail.rate <- imp.df$available.days/imp.df$total.days
-  imp.df$block.rate <- imp.df$blocked.days/imp.df$total.days
-  imp.df$resv.rate <- imp.df$reserved.days/imp.df$total.days
-  
-  ## Loop through each property and impute  
-  
-  # Create capture list
-  imp.list <- list()
-  
-  # Start loop
-  for(i.i in 1:nrow(imp.df)){
-    
-    # Extract ith property data and daily data
-    i.imp <- imp.df[i.i, ]
[…]

### 2018-04-05 functions/abb_Functions.R
Update: Short term data preprocess

@@ -1,0 +1,1308 @@
+##########################################################################################
+#                                                                                        #    
+#  Custom functions for working with APM and AirDNA data in the ABB Project              #
+#                                                                                        #
+##########################################################################################
+
+
+### Calculate the occupancy rates for each date in a range -------------------------------
+
+abbCalcDateRates <- function(daily.df){
+  
+  ## Create table of counts by status
+  
+  status.table <- table(daily.df$date, daily.df$status)
+  
+  ## Convert to a data.frame  
+  
+  status.df <- data.frame(Avail=status.table[,1],
+                          Resv=status.table[,2],
+                          Block=status.table[,3],
+                          lp.type=daily.df$lp.type[1])
+  
+  ## Add date   
+  
+  status.df$date <- as.Date(rownames(status.df))
+  
+  ## Add reserved rate (occupancy rate)  
+  
+  status.df$occ.rate <- status.df$Resv / (status.df$Resv + status.df$Avail)
+  
+  ## Return values  
+  
+  return(status.df)
+  
+}
+
+### Impute the missing daily observations ------------------------------------------------
+
+abbImputeDaily <- function(prop.df, 
+                           daily.df, 
+                           rates.df){
+  
+  # prop.df: data.frame of AirBNB property data
+  # daily.df: data.frame of existing AirBNB daily observations
+  # rates.df: data.frame of daily rate data (from abbCalcDateRates() function)
+  
+  ## Isolate those needing imputation  
+  
+  # Isolate
+  imp.df <- prop.df[prop.df$impute != 'no',]
+  
+  # Compute property specific rates
+  imp.df$avail.rate <- imp.df$available.days/imp.df$total.days
+  imp.df$block.rate <- imp.df$blocked.days/imp.df$total.days
+  imp.df$resv.rate <- imp.df$reserved.days/imp.df$total.days
+  
+  ## Loop through each property and impute  
+  
+  # Create capture list
+  imp.list <- list()
+  
+  # Start loop
+  for(i.i in 1:nrow(imp.df)){
+    
+    # Extract ith property data and daily data
+    i.imp <- imp.df[i.i, ]
[…]

### 2018-04-05 scripts/1_str_preprocess.R

@@ -25,30 +25,31 @@
    
   # Property Information
 
-  str.data <- read.csv(file.path(data_path, '/raw/melbproperties.csv'), header=T)
-  str.data2 <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
+  str_raw <- read.csv(file.path(data_path, 'raw', 'melbproperties.csv'), header=T)
+  st2_raw <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
                         header=T)
   
   # Daily rental information
 
-  daily.data  <- read.csv(file.path(data_path, '/raw/melbDaily.csv'), header=T)
-  daily.data2  <- read.csv(file.path(data_path, '/raw/melbDaily_to_mar2017.csv'), header=T)
+  daily_raw  <- read.csv(file.path(data_path, '/raw/melbDaily.csv'), header=T)
+  daily2_raw  <- read.csv(file.path(data_path, '/raw/melbDaily_to_mar2017.csv'), 
+                           header=T)
   
  ## Fix Names
   
-  names(str.data) <- tolower(names(str.data))
-  names(str.data2) <- tolower(names(str.data2))
-  names(daily.data) <- tolower(names(daily.data))
-  names(daily.data2) <- tolower(names(daily.data2))
+  names(str_raw) <- tolower(names(str_raw))
+  names(str2_raw) <- tolower(names(str2_raw))
+  names(daily_raw) <- tolower(names(daily_raw))
+  names(daily2_raw) <- tolower(names(daily2_raw))
   
  ## Determine unique observations
   
   # Structure Data
-  str_df <- dplyr::bind_rows(str.data2, str.data)
+  str_df <- dplyr::bind_rows(str2_raw, str_raw)
   str_df <- str_df %>% dplyr::filter(!duplicated(property.id))  
   
   # Daily Data
-  daily_df <- dplyr::bind_rows(daily.data2, daily.data) %>%
+  daily_df <- dplyr::bind_rows(daily2_raw, daily_raw) %>%
     dplyr::mutate(uniq_id = paste0(property.id, '_', date)) %>%
     dplyr::filter(!duplicated(uniq_id)) %>%
     dplyr::select(property.id, date, status, price, booked.date, reservation.id)
@@ -82,9 +83,10 @@
     dplyr::inner_join(daily_summ, 
                       by='property.id')
   
-
  ## Write out data  
 
-  save(str_df, file=paste0(data_path, 'prepared/stpropdata.RData'))
[…]

### 2018-04-05 abb_str_PreProcess.R
Update: long-term data pre-process

@@ -1,90 +1,0 @@
-##########################################################################################
-#                                                                                        #  
-#   Data Preprocessing for the Short-Term Rental data of the ABB project                 #
-#                                                                                        #  
-##########################################################################################
-
- ## Load libraries
-
-  library(plyr)
-  library(stringr)
-  library(lubridate)
-  library(dplyr)
-  library(multidplyr)
-
-  ## Set locations
-
-  # Assign path based on computer name
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  
-  ## Load sources
-
-  source(file.path(getwd(), 'functions', "abb_Functions.R"))
-
- ## Load Data  
-   
-  # Property Information
-
-  str.data <- read.csv(file.path(data_path, '/raw/melbproperties.csv'), header=T)
-  str.data2 <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
-                        header=T)
-  
-  # Daily rental information
-
-  daily.data  <- read.csv(file.path(data_path, '/raw/melbDaily.csv'), header=T)
-  daily.data2  <- read.csv(file.path(data_path, '/raw/melbDaily_to_mar2017.csv'), header=T)
-  
- ## Fix Names
-  
-  names(str.data) <- tolower(names(str.data))
-  names(str.data2) <- tolower(names(str.data2))
-  names(daily.data) <- tolower(names(daily.data))
-  names(daily.data2) <- tolower(names(daily.data2))
-  
- ## Determine unique observations
-  
-  # Structure Data
-  str_df <- dplyr::bind_rows(str.data2, str.data)
-  str_df <- str_df %>% dplyr::filter(!duplicated(property.id))  
-  
-  # Daily Data
-  daily_df <- dplyr::bind_rows(daily.data2, daily.data) %>%
-    dplyr::mutate(uniq_id = paste0(property.id, '_', date)) %>%
-    dplyr::filter(!duplicated(uniq_id)) %>%
-    dplyr::select(property.id, date, status, price, booked.date, reservation.id)
-  
- ## Fix Dates  
-  
-  # Daily data
-  daily_df$date <- lubridate::as_date(daily_df$date)
-  
-  # Property level data
-  str_df$created.date <- lubridate::as_date(str_df$created.date)
-  str_df$created.year <- lubridate::year(str_df$created.date)
[…]

### 2018-04-05 scripts/2_ltr_preprocess.R

@@ -1,0 +1,102 @@
+##########################################################################################
+#                                                                                        #  
+#   Data Preprocessing for the Long-Term Rental data of the ABB project                  #
+#                                                                                        #  
+##########################################################################################
+
+
+ ## Load Libraries
+
+  library(plyr)
+  library(stringr)
+  library(lubridate)
+  library(dplyr)
+  library(multidplyr)
+  
+  ## Set locations
+
+  # Assign path based on computer name
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+
+ ## Load sources
+
+  source(file.path(getwd(), 'functions', "abb_Functions.R"))
+  
+  # Load the raw rent data
+  rent_df <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)
+
+ ## Remove observations without sufficient keys
+  
+  r_df <- rent_df[!is.na(rent_df$EventID), ]
+  r_df <- r_df[!is.na(r_df$AddressID), ]
+  r_df <- r_df[!is.na(r_df$ActivityID), ]
+  
+ ## Create Unique Key
+  
+  r_df$id.key <- paste0(as.numeric(as.factor(r_df$ActivityID)), '..',
+                       as.numeric(as.factor(r_df$AddressID)))
+  r_df$id.key <- as.numeric(as.factor(r_df$id.key))
+  
+ ## Fix Dates  
+  
+  r_df$last.adv.date <- apmFixDates(r_df$LastAdvertisedEventDate)
+  r_df$first.adv.date <- apmFixDates(r_df$FirstAdvertisedEventDate)
+  r_df$event.date <- apmFixDates(r_df$EventDate)
+  r_df$event.year <- lubridate::year(r_df$event.date)
+  
+ ## Remove those not occuring in 2015 or later
+  
+  r_df <- r_df %>% dplyr::filter(event.year >= 2014)
+  
+ ## Add an identifier that signifies last record in a set of advertisements (of record)  
+    
+  r_df <- r_df[order(r_df$event.date, decreasing=T), ]
+  r_df <- r_df[order(r_df$id.key), ]
+  r_df$AID <- paste0(r_df$id.key, '..', r_df$last.adv.date)
+  r_df$of.record <- ifelse(duplicated(r_df$AID), 0 ,1)
+  
+ ## Split into property data and listing data
+  
+  ltr_df <- r_df[r_df$of.record == 1,]
[…]

### 2018-04-05 abbDataPrep_Script.Rmd
Updates: Data load in prep

@@
 
-  data.path <- 'c:/dropbox/research/airBNB/data/'
-  code.path <- 'c:/code/'
-  fig.path <- 'c:/dropbox/research/airBNB/figures/'
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code')
+  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
 
@@
 
-  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
+  source(file.path(getwd(), 'functions', 'abb_Functions.R'))
 
@@
 
-  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
-  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
-  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
-  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))
+    source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
+    source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
+    source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
+    source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))
 
@@
 
+### HERE
+
 ```
@@
 
-  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
+  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                      'ebisu', 'tirol', 'foggy', 'hof')
-  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
+  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
                rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
@@
 
-  str.col <- abb.col[1]
-  ltr.col <- abb.col[3]
+  str_col <- abb_col[1]
+  ltr_col <- abb_col[3]
 
@@
 
-  load(paste0(data.path, 'prepared/stpropdata.RData'))
+  str_df <- readRDS(file.path(data_path, 'prepared', 'st_prop.RDS'))
 
@@
 
-  load(paste0(data.path, 'prepared/stdailydata.RData'))
+  daily_df <- readRDS(file.path(data_path, 'prepared', 'st_daily.RDS'))
 
@@
 
-  load(paste0(data.path, 'prepared/ltpropdata.RData'))
+  ltr_df <- readRDS(file.path(data_path, 'prepared', 'lt_prop.RDS'))
 
@@
 
-  load(paste0(data.path, 'prepared/ltlistdata.RData'))
+  list_df <- readRDS(file.path(data_path, 'prepared', 'lt_list.RDS'))
 
@@
 
-  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
+  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
                                proj4string=CRS("+init=epsg:4283"),
                                delete_null_obj=TRUE)
-  names(suburbs.shp@data) <- tolower(names(suburbs.shp@data))
+  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))
 
@@
 
-  sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'),
+  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
-  names(sa1s.shp@data) <- tolower(names(sa1s.shp@data))
+  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))
 
@@
 
-  beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'),
+  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
                              proj4string=CRS("+init=epsg:4283"),
                              delete_null_obj=TRUE)
-  names(beach.shp@data) <- tolower(names(beach.shp@data))
+  names(beach_shp@data) <- tolower(names(beach_shp@data))
 
@@
 
-  ltr.data <- ltr.data[ ,ltr.keep.flds]
+  ltr_df <- ltr_df[ ,ltr.keep.flds]
 
@@
 
-  names(ltr.data) <- c('id.key', 'geographical.id', 
+  names(ltr_df) <- c('id.key', 'geographical.id', 
                         'event.id', 'address.id', 'activity.id',
@@
 
-  ltr.data <- ltr.data[ltr.data$event.date >= (strike_date - 365) & 
-                            ltr.data$event.date <= (strike_date - 1), ]
-  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]
+  ltr_df <- ltr_df[ltr_df$event.date >= (strike_date - 365) & 
+                            ltr_df$event.date <= (strike_date - 1), ]
+  listing.data <- listing.data[listing.data$id.key %in% ltr_df$id.key, ]
 
@@
 
-  ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
+  ltr_df$ltr.month <- as.numeric(as.factor(substr(ltr_df$event.date, 1, 7)))
   listing.data$ltr.month <- as.numeric(as.factor(substr(
@@
 
-  ltr.data$type <- 'Other'
-  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
+  ltr_df$type <- 'Other'
+  ltr_df$type[ltr_df$property.type %in% c('Duplex', 'House',
                                            'Terrace', 'Townhouse')] <- 'House'
-  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
+  ltr_df$type[ltr_df$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
 
@@
   str.types <- ggplot(str_df, aes(x=type)) + 
-    geom_bar(color=str.col, fill=str.col) +
+    geom_bar(color=str_col, fill=str_col) +
     xlab('\nProperty Type\n') + 
@@
 
-  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
-    geom_bar(color=ltr.col, fill=ltr.col) +
+  ltr.types <- ggplot(ltr_df, aes(x=type)) + 
+    geom_bar(color=ltr_col, fill=ltr_col) +
     xlab('\nProperty Type\n') + 
@@
   str_df <- subset(str_df, type != 'Other')
-  ltr.data <- subset(ltr.data, type != 'Other')
+  ltr_df <- subset(ltr_df, type != 'Other')
 
@@
   list.types <- ggplot(str_df, aes(x=listing.type)) + 
-      geom_bar(color=str.col, fill=str.col) +
+      geom_bar(color=str_col, fill=str_col) +
       xlab('\nListing Type\n') + 
@@
 
-  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
-  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
-  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
-  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
-  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)
+  ltr_df$has.study <- ifelse(ltr_df$has.study == 'True', 1, 0)
+  ltr_df$has.courtyard <- ifelse(ltr_df$has.courtyard == 'True', 1, 0)
+  ltr_df$has.aircon <- ifelse(ltr_df$has.aircon == 'True', 1, 0)
+  ltr_df$has.balcony <- ifelse(ltr_df$has.balcony == 'True', 1, 0)
+  ltr_df$has.garage <- ifelse(ltr_df$has.garage == 'True', 1, 0)
 
@@
   # Long term data
-  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
-  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]
+  ltr_df <- ltr_df[!is.na(ltr_df$bedrooms), ]
+  ltr_df <- ltr_df[ltr_df$bedrooms <= 10, ]
 
@@
 
-   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
+   ltrbed <- ggplot(ltr_df, aes(x=bedrooms)) + 
+    geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type,scales='free_y') +
@@
   strbed <- ggplot(str_df, aes(x=bedrooms)) + 
-    geom_bar(fill=str.col, color=str.col) +
+    geom_bar(fill=str_col, color=str_col) +
     facet_wrap(~type,scales='free_y') +
@@
   str_df <- str_df[str_df$bedrooms < 5, ]
-  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]
+  ltr_df <- ltr_df[ltr_df$bedrooms < 5, ]
 
@@
   str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
-  ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')
+  ltr.id <- which(ltr_df$bedrooms > 3 & ltr_df$type =='Apartment')
 
   if(length(str.id) > 0) str_df <- str_df[-str.id, ]
-  if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]
+  if(length(ltr.id) > 0) ltr_df <- ltr_df[-ltr.id, ]
 
@@
 
-  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
+  ltr_df <- ltr_df[!is.na(ltr_df$baths), ]
   str_df <- str_df[!is.na(str_df$baths), ]
@@
 
-  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
+  ltbath <- ggplot(ltr_df, aes(x=baths)) + 
+    geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type) +
@@
   stbath <- ggplot(str_df, aes(x=baths)) + 
-    geom_bar(fill=str.col, color=str.col) +
+    geom_bar(fill=str_col, color=str_col) +
     facet_wrap(~type, scales='free_y') +
@@
   # Long term data
-  ltr.data <- ltr.data[ltr.data$baths < 4, ]
+  ltr_df <- ltr_df[ltr_df$baths < 4, ]
 
@@
 
-  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
+  ltr_df$bedbath <- paste0(ltr_df$bedrooms, '..', ltr_df$baths)
   str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)
@@
 
-  ltbb <- ggplot(ltr.data, aes(x=bedbath)) + 
-    geom_bar(fill=ltr.col, color=ltr.col) +
+  ltbb <- ggplot(ltr_df, aes(x=bedbath)) + 
+    geom_bar(fill=ltr_col, color=ltr_col) +
     xlab('\nBed/Bath Combo\n') +
@@
   stbb <- ggplot(str_df, aes(x=bedbath)) +
-    geom_bar(fill=str.col, color=str.col) + 
+    geom_bar(fill=str_col, color=str_col) + 
     xlab('\nBed/Bath Combo\n') +
@@
 
-  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
+  ltr_df <- ltr_df[ltr_df$bedbath %in% acc.bb, ]
   str_df <- str_df[str_df$bedbath %in% acc.bb, ]
@@
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-  ltr.data$bedbath <- factor(ltr.data$bedbath, 
+  ltr_df$bedbath <- factor(ltr_df$bedbath, 
                                levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
@@
   str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
-  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)
+  ltr_df$product <- paste0(substr(ltr_df$type, 1, 1), ltr_df$bedbath)
 
@@
 
-  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
+  ltr_df <- ltr_df[!is.na(ltr_df$event.price), ]
   str_df <- str_df[!is.na(str_df$nightly.rate), ]
@@
 
-  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
-    geom_density(fill=ltr.col, alpha=.8) +
+  ltr.plot <- ggplot(ltr_df, aes(x=event.price)) + 
+    geom_density(fill=ltr_col, alpha=.8) +
     ylab('') +
@@
   rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
-    geom_density(fill=str.col, alpha=.8) + 
+    geom_density(fill=str_col, alpha=.8) + 
     ylab('') +
@@
 
-  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
-                         ltr.data$event.price <= 1000, ]
+  ltr_df <- ltr_df[ltr_df$event.price >= 200 & 
+                         ltr_df$event.price <= 1000, ]
 
@@
   str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
-  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)
+  ltr_df$gross.revenue <- ltr_df$event.price * (52 - ltr_df$dom / 7)
 
@@
   str.small$tenure <- 'short-term'
-  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
+  ltr.small <- ltr_df[,c('baths', 'gross.revenue')]
   ltr.small$tenure <- 'long-term'
@@
     geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col)) +
+    scale_fill_manual(values=c(ltr_col, abb_col)) +
+    scale_color_manual(values=c(ltr_col, abb_col)) +
     ggtitle('Annual Revenues by Tenure Type') +
@@
 
-  ltr.data <- ltr.data[ltr.data$dom <= 180, ]
+  ltr_df <- ltr_df[ltr_df$dom <= 180, ]
 
@@
   # Limit to extent of data
-  sub.table <- table(ltr.data$suburb)
+  sub.table <- table(ltr_df$suburb)
   sub.table <- sub.table[sub.table != 0]
@@
   # Set colors
-  g.cols <- c('grey10', 'grey40', 'grey70')
+  g_cols <- c('grey10', 'grey40', 'grey70')
 
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-    scale_fill_manual(values=g.cols, labels=c('Inner      ',
+    scale_fill_manual(values=g_cols, labels=c('Inner      ',
                                               'Middle      ',
@@
 
-  miss.LL <- which(is.na(ltr.data$latitude))
+  miss.LL <- which(is.na(ltr_df$latitude))
 
@@
 
-  ltr.data$miss.LL <- 0
-  ltr.data$miss.LL[miss.LL] <- 1
+  ltr_df$miss.LL <- 0
+  ltr_df$miss.LL[miss.LL] <- 1
 
@@
 
-  ltr.data$latitude[miss.LL] <- ltr.data$street.latitude[miss.LL]
-  ltr.data$longitude[miss.LL] <- ltr.data$street.longitude[miss.LL]
+  ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
+  ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]
 
@@
 
-  ltr.data <- ltr.data[!is.na(ltr.data$latitude), ]
+  ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]
 
@@
 
-  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.data$longitude,
-                                               ltr.data$latitude),
-                                         ltr.data,
+  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
+                                               ltr_df$latitude),
+                                         ltr_df,
                                          proj4string=CRS("+init=epsg:4283"))
@@
   spJoin <- over(ltr.prop.shp, suburbs.shp)
-  ltr.data$suburb <- as.character(spJoin$name_2006)
-  ltr.data$suburb[is.na(ltr.data$suburb)] <- 'missing'
+  ltr_df$suburb <- as.character(spJoin$name_2006)
+  ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'
 
@@
 
-  ltr.data$sub.class <- as.character(spJoin$suburbdesi)
-  ltr.data$sub.class[is.na(ltr.data$sub.class)] <- 'missing'
+  ltr_df$sub.class <- as.character(spJoin$suburbdesi)
+  ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'
 
@@
   spJoin <- over(ltr.prop.shp, sa1s.shp)
-  ltr.data$sa1 <- spJoin$sa1_main11
+  ltr_df$sa1 <- spJoin$sa1_main11
 
@@
   spJoin <- over(ltr.prop.shp, beach.buffer)
-  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)
+  ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)
 
@@
 
-  ltr.data <- ltr.data[ltr.data$sub.class != 'missing', ]
-  ltr.data <- ltr.data[ltr.data$sa1 != 'missing', ]
+  ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
+  ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]
 
@@
   # Add individual classes
-  ltr.data$geo.mrkt <- 'rural'
-  ltr.data$geo.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
-  ltr.data$geo.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
-  ltr.data$geo.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
-  ltr.data$geo.mrkt[ltr.data$beach == 1] <- 'beach'
+  ltr_df$geo.mrkt <- 'rural'
+  ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
+  ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
+  ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
+  ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'
 
   # Order the factors properly
-  ltr.data$geo.mrkt <- factor(ltr.data$geo.mrkt, 
+  ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
                               levels=c('city-core', 'city', 'suburban', 
@@
 
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
+  sm_col <- abb_col[c(1, 3, 6, 5, 2)]
 
@@
                alpha=.2) +
-    scale_color_manual(values=sm.col) +
+    scale_color_manual(values=sm_col) +
     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
@@
     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
+    geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
                alpha=.1) +
-    scale_color_manual(values=sm.col) +
+    scale_color_manual(values=sm_col) +
     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
@@
     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
-    scale_fill_manual(values=sm.col) +
+    scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
@@
   ltrtype.map <- ggplot() +
-    geom_bar(data=ltr.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
-    scale_fill_manual(values=sm.col) +
+    geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
+    scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
@@
   str_df$suburb <- as.character(str_df$suburb)
-  ltr.data$suburb <- as.character(ltr.data$suburb)
+  ltr_df$suburb <- as.character(ltr_df$suburb)
 
@@
 
-  listing.data <- listing.data[listing.data$activity.id %in% ltr.data$activity.id,]
+  listing.data <- listing.data[listing.data$activity.id %in% ltr_df$activity.id,]
 
@@
 
-  save(str_df, ltr.data, daily_df, listing.data, subs, abb.col, 
-       beach.shp, core.suburbs, exch.rate, ltr.col, str.col, sa1s.shp, 
+  save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
+       beach.shp, core.suburbs, exch.rate, ltr_col, str_col, sa1s.shp, 
        suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
        ltr.run.total, str.run.total,
-       file=paste0(data.path, 'prepared/prep_workspace_', data_name, '.RData'))
-
-```
+       file=paste0(data_path, 'prepared/prep_workspace_', data_name, '.RData'))
+
+```N

### 2018-04-05 abb_ltr_PreProcess.R

@@ -1,105 +1,0 @@
-##########################################################################################
-#                                                                                        #  
-#   Data Preprocessing for the Long-Term Rental data of the ABB project                  #
-#                                                                                        #  
-##########################################################################################
-
-
- ## Load Libraries
-
-  library(plyr)
-  library(stringr)
-  library(lubridate)
-  library(dplyr)
-  library(multidplyr)
-  
-  ## Set locations
-
-  # Assign path based on computer name
-  data_path <- 'c:/dropbox/research/airBNB/data/'
-
-  # Code Path
-  code_path <- getwd()
-
- ## Load sources
-
-  source(file.path(code_path, "abb_Functions.R"))
-  
-  # Load the raw rent data
-  rent16 <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)
-
- ## Remove observations without sufficient keys
-  
-  r16 <- rent16[!is.na(rent16$EventID), ]
-  r16 <- r16[!is.na(r16$AddressID), ]
-  r16 <- r16[!is.na(r16$ActivityID), ]
-  
- ## Create Unique Key
-  
-  r16$id.key <- paste0(as.numeric(as.factor(r16$ActivityID)), '..',
-                       as.numeric(as.factor(r16$AddressID)))
-  r16$id.key <- as.numeric(as.factor(r16$id.key))
-  
- ## Fix Dates  
-  
-  r16$last.adv.date <- apmFixDates(r16$LastAdvertisedEventDate)
-  r16$first.adv.date <- apmFixDates(r16$FirstAdvertisedEventDate)
-  r16$event.date <- apmFixDates(r16$EventDate)
-  r16$event.year <- lubridate::year(r16$event.date)
-  
- ## Remove those not occuring in 2015 or later
-  
-  r16 <- r16 %>% dplyr::filter(event.year >= 2014)
-  
- ## Add an identifier that signifies last record in a set of advertisements (of record)  
-    
-  r16 <- r16[order(r16$event.date, decreasing=T), ]
-  r16 <- r16[order(r16$id.key), ]
-  r16$AID <- paste0(r16$id.key, '..', r16$last.adv.date)
-  r16$of.record <- ifelse(duplicated(r16$AID), 0 ,1)
-  
- ## Split into property data and listing data
-  
-  ltr.data <- r16[r16$of.record == 1,]
-  listing.data <- r16[, c('id.key', 'EventID', 'ActivityID', 'AddressID', 'of.record',
[…]

### 2018-04-05 scripts/1_str_preprocess.R

@@ -26,7 +26,7 @@
   # Property Information
 
   str_raw <- read.csv(file.path(data_path, 'raw', 'melbproperties.csv'), header=T)
-  st2_raw <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
+  str2_raw <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
                         header=T)
   
   # Daily rental information
@@ -85,8 +85,8 @@
   
  ## Write out data  
 
-  saveRDS(str_df, file=file.path(data_path, 'prepared', 'stpropdata.RDS'))
-  saveRDS(daily_df, file=file.path(data_path, 'prepared', 'stdailydata.RDS'))
+  saveRDS(str_df, file=file.path(data_path, 'prepared', 'st_prop.RDS'))
+  saveRDS(daily_df, file=file.path(data_path, 'prepared', 'st_daily.RDS'))
   
 #*****************************************************************************************
 #*****************************************************************************************

### 2018-04-05 scripts/2_ltr_preprocess.R

@@ -87,7 +87,7 @@
                      dom=as.numeric(max-min))
   
   # Add to property data
-  ltr_df$DOM <- dom.data$dom[match(ltr_df$id.key, dom.data$id.key)]
+  ltr_df$DOM <- dom_df$dom[match(ltr_df$id.key, dom_df$id.key)]
   
   # Convert all names to lower case
   names(ltr_df) <- tolower(names(ltr_df))
@@ -96,7 +96,7 @@
  ## Write out data
   
   export_path <- file.path(data_path, 'prepared')
-  saveRDS(ltr_df, file=paste0(export_path, 'ltpropdata.RDS'))
-  saveRDS(listing_df, file=paste0(export_path, 'ltlistdata.RDS'))
+  saveRDS(ltr_df, file=file.path(export_path, 'lt_prop.RDS'))
+  saveRDS(listing_df, file=file.path(export_path, 'lt_list.RDS'))
   
  

### 2018-04-16 scripts/1_str_preprocessing.Rmd
Updated preprocess to RMD

---
title: "Pre Processing of the Short Term Data"
author: "Andy Krause"
date: "April 14, 2018"
output: html_document
---

This script executes a number of very long running data preparation process necessary to analyze the short term rental (Airbnb) data.  If you re-knit (with RMarkdown) this file the code will not evaluate.  To actually evaluate the code you must manually re-run the code chunks

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Preliminary Commands

We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions

```{r saf}

 options(stringsAsFactors=FALSE)

```

Next, we load the necessary libraries

```{r load_libraries}

  library(plyr)
  library(stringr)
  library(lubridate)
  library(dplyr)
  library(multidplyr)
  library(tidyr)
  library(tibble)
  library(magrittr)

```

We then set the paths to the data

```{r set_paths, echo=TRUE}

  # Assign path based on computer name
  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')

  ## Load sources
  code_path <- file.path('c:', 'code', 'research', 'airBNBmelbourne')

  source(file.path(code_path, 'functions', "abb_Functions.R"))

```

Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size

```{r anl_date}

  anl_date <- as.Date('2015-09-01')

```

## Load and Combine Data

Next, we load the data. There are two files for each the property level data as well as the daily observation data.

```{r load_data}

  # Property Information
  str_raw <- read.csv(file.path(data_path, 'raw', 'melbproperties.csv'), header=T)
  str_raw2 <- read.csv(file.path(data_path, 'raw', 'melbproperties_to_mar2017.csv'), 
                        header=T)

  # Daily rental information
  daily_raw  <- read.csv(file.path(data_path, 'raw', 'melbDaily.csv'), header=T)
  daily_raw2  <- read.csv(file.path(data_path, 'raw', 'melbDaily_to_mar2017.csv'), 
                           header=T)

```

We then combine the two files for each type, standardize the field names and select only those fields which we need going forward.

```{r tcr_data}

  # Property Level
  str_df <- dplyr::bind_rows(str_raw, str_raw2) %>%
    dplyr::select(property_id=Property.ID, host_id=Host.ID, listing_title=Listing.Title, 
                  property_type=Property.Type, listing_type=Listing.Type,
                  created_date=Created.Date, latitude=Latitude, longitude=Longitude,
                  rating=Overall.Rating, max_guests=Max.Guests, 
                  canc_policy=Cancellation.Policy, cleaning_fee=Cleaning.Fee, 
                  nightly_rate=Published.Nightly.Rate, 
                  weekly_rate=Published.Weekly.Rate, monthly_rate=Published.Monthly.Rate, 
                  avg_nightly_rate=Average.Daily.Rate, min_stay=Minimum.Stay, 
                  bedrooms=Bedrooms, bathrooms=Bathrooms)

  # Clean up
  rm(str_raw); rm(str_raw2)

  # Daily Data
  daily_df <- dplyr::bind_rows(daily_raw2, daily_raw) %>%
    dplyr::select(property_id=Property.ID, date=Date, status=Status, price=Price,
                  book_date=Booked.Date, resv_id=Reservation.ID)

  # Clean up
  rm(daily_raw); rm(daily_raw2);gc()

```

## Prepare Data

Due to our combining of data, we have many duplicate observations.  We new remove any duplicates.  Note that the daily data in its raw format does not have a unique identifier, so we much first create one by combining the property id with the date of the observation.

```{r uniq_ids}

  # Structure Data
  str_df <- str_df %>% dplyr::filter(!duplicated(property_id))

  # Daily Data
  daily_df <- daily_df %>%
    dplyr::mutate(uniq_id = paste0(property_id, '_', date)) %>%
    dplyr::filter(!duplicated(uniq_id))

```

The date fields read in as characters, so we also must convert these to an R date format.

```{r fix_dates}

  # Daily data
  daily_df$date <- lubridate::as_date(daily_df$date)
  daily_df$book_date <- lubridate::as_date(daily_df$book_date)

  # Property level data
  str_df$created_date <- lubridate::as_date(str_df$created_date)
  str_df$created_year <- lubridate::year(str_df$created_date)

```

Next, we trim the daily data by date, limiting the observations to the one month period from September 1 2015 to August 31, 2016. We'll eliminate the property-level observations which are outside of the range through a future join. 
```{r date_trim}

  daily_df <- daily_df %>%
    dplyr::filter(date >= anl_date &
                    date <= anl_date + 365)

```

For each property in the short term data, we then calculate some summary statistics of its listing history such as the earliers and latest date for each, the total days on Airbnb, number of blocked periods, its occupancy/available/blocked rate, median length of block period and total number of bookings.

To speed up this calculate, we compute these summary statistics in parallel.  Total run time will depend on your system.

```{r summ_stats}

  # Create new cluster
  abb_cl <- get_default_cluster()

  # Register function and variable
  cluster_copy(abb_cl, abbCalcBookStr)

  # Summarize daily by property
  daily_summ <- daily_df %>% 
    multidplyr::partition(property_id, cluster=abb_cl) %>% 
    dplyr::do(abbCalcBookStr(.)) %>% 
    dplyr::collect()

```

We then join the summary stats to the property-level data with an inner join, meaning that any properties without oservations in this period are removed.

```{r join_summ}

  str_df <- str_df %>%
    dplyr::inner_join(daily_summ, 
                      by='property_id')

```

In order to store all of our data efficiency in a single object, we now **nest** the daily observations for each property into a list-column (each property observation will contain a data.frame of daily observations).

```{r join_nest}

  # Nest daily data
  daily_tdf <- daily_df %>%
    as.tibble() %>%
    multidplyr::partition(property_id, cluster=abb_cl) %>% 
    dplyr::do(tidyr::nest(., -property_id, .key='daily_data')) %>% 
    dplyr::collect()

  # Add nested daily data to structural data
  str_df <- str_df %>%
    as.tibble() %>%
    left_join(daily_tdf, by='property_id')

```

### Export Data

Finally, we write out the date to an RDS object for future use.

```{r write_out}

 saveRDS(str_df, file=file.path(data_path, 'prepared', 'str_data.RDS'))

```

### 2018-04-16 scripts/2_ltr_preprocessing.Rmd
Updated preprocess to RMD

---
title: "Pre Processing of the Long Term Data"
author: "Andy Krause"
date: "April 14, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script executes a number of long running data preparation process necessary to analyze the long term rental data.  If you re-knit (with RMarkdown) this file the code will not evaluate.  To actually evaluate the code you must manually re-run the code chunks

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Preliminaty Commands

We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions

```{r saf}

 options(stringsAsFactors=FALSE)

```

Next, we load the necessary libraries

```{r load_libraries}

  library(plyr)
  library(stringr)
  library(lubridate)
  library(dplyr)
  library(multidplyr)
  library(tidyr)
  library(tibble)
  library(magrittr)

```

We then set the paths to the data

```{r set_paths}

  # Assign path based on computer name
  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airBNBmelbourne')

  ## Load sources
  source(file.path(code_path, 'functions', "abb_Functions.R"))

```

Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size

```{r anl_date}

  anl_date <- as.Date('2015-09-01')

```

## Load Data

Next, we load the data.

```{r load_data}

  # Load the raw rent data
  ltr_df <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)

```

We then trim the data fields to those that are needed in the future analyses

```{r trim_fields}

  names(ltr_df) <- tolower(names(ltr_df))

  ltr_df <- ltr_df %>%
    dplyr::select(geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude,
                  date=eventdate, price=eventprice,
                  first_date=firstadvertisedeventdate,
                  first_price=firstadvertisedeventprice, 
                  last_date=lastadvertisedeventdate,
                  last_price=lastadvertisedeventprice,property_type=propertytype, 
                  area_size=areasize, bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage)

```

A small portion of the observations are missing the necessary identification fields to proceed.  These are removed here.

```{r filter_NA_ids}

  ltr_df <- ltr_df %>%
    dplyr::filter(!is.na(event_id)) %>%
    dplyr::filter(!is.na(addr_id)) %>%
    dplyr::filter(!is.na(activity_id))

```

The dates in the data are not consistent, some have time stamps, others not.  We have created a custom function to correct these and convert them to R standard format.

```{r fix_dates}

  ltr_df$last_date <- apmFixDates(ltr_df$last_date)
  ltr_df$first_date <- apmFixDates(ltr_df$first_date)
  ltr_df$date <- apmFixDates(ltr_df$date)

```

In order to speed up the future calculations, we then remove an observations prior to 2014.

```{r trim_2014}

  ltr_df <- ltr_df %>% 
    dplyr::filter(lubridate::year(date) >= 2014)

```

Next, we create a unique identifier for each rental transaction.  Note that there are still, often, multiple observation per transaction due to the listing change data.

```{r uniq_trans}

 ## Create Unique Key

  ltr_df <- ltr_df %>%
    dplyr::group_by(addr_id) %>%
    dplyr::arrange(date) %>%
    mutate(trans_id = as.numeric(as.factor(activity_id)),
           uniq_id = paste0(addr_id, '_', trans_id)) %>%
    dplyr::select(uniq_id, addr_id, trans_id, everything()) %>%
    ungroup()

```

## Property vs Transaction Data

Next, we split the data into property specific information and transasction specific information and carry out individual preparation on each (and will re-combine later)

```{r split_infotype}

  # Split off transaction information
  ltr_trans <- ltr_df %>%
    dplyr::select(addr_id, uniq_id, trans_id, date, price, first_date, first_price, 
                  last_date, last_price)

  # Split off property information
  ltr_prop <- ltr_df %>%
    dplyr::select(addr_id, uniq_id, flat_nbr, str_nbr, str_name, str_type, suburb,
                  postcode, latitude, longitude, str_latitude, str_longitude,
                  property_type, area_size, bedrooms, baths, parking, has_study,
                  has_courtyard, has_balcony, has_ac, has_garage)

```

For the transaction data, we condense it down to one observation per rental.  Here we take the latest activitiy record (without an NA in price) for all observations that were first list on or after Jan 1, 2014.  We also calculate a total days on market as well.

```{r}

  ltr_trans <- ltr_trans %>%
    dplyr::group_by(uniq_id) %>%
    dplyr::arrange(desc(date)) %>%
    dplyr::filter(!is.na(price)) %>%
    dplyr::slice(1) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(date=if_else(date < last_date, last_date, date),
                  dom=as.numeric(last_date - first_date)) %>%
    dplyr::filter(first_date >= as.Date('2014-01-01')) %>%
    dplyr::select(addr_id, uniq_id, trans_id, date, price, dom) %>%
    tidyr::nest(-addr_id, .key='trans_data')

```

Because some of the property data shows different information at different listing times, we must reconcile this information.  Since the properties span a short time frame, we reconcile the data for each address.

We start by splitting off the location data.  Across properties this data has shown to be very robust, so we take one record set for each address.

```{r}

  ltr_loc <- ltr_prop %>%
    dplyr::group_by(addr_id) %>%
    dplyr::slice(1) %>%
    dplyr::select(addr_id, flat_nbr, str_nbr, str_name, str_type, suburb, postcode,
                  latitude, longitude, str_longitude, str_latitude) %>%
    dplyr::mutate(latitude = if_else(is.na(latitude), str_latitude, latitude),
                  longitude = if_else(is.na(longitude), str_longitude, longitude)) %>%
    dplyr::select(-str_latitude, -str_longitude) %>%
    dplyr::ungroup() %>%
    dplyr::mutate_at(.vars=c('flat_nbr', 'str_nbr', 'str_name', 'str_type', 'suburb'),
                     .funs=trimws)

```

Next, we isolate property characteristics data.  Here is where most of the discrepancies are located.  To fix any anomolies and fix missing values, we take reconcile each address based on simple set of rules: always take a value over an NA, take the greater of integer values.

```{r}

  ltr_pc <- ltr_prop %>%
    dplyr::select(addr_id, uniq_id, property_type, area_size, bedrooms, baths, parking,
                  has_study, has_courtyard, has_balcony, has_ac, has_garage) %>%
    dplyr::group_by(uniq_id) %>%
    dplyr::slice(1) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(addr_id) %>%
    dplyr::summarize(property_type = property_type[1],
                     area_size = max(area_size, na.rm=T),
                     bedrooms = max(bedrooms, na.rm=T),
                     baths = max(baths, na.rm=T),
                     parking = max(parking, na.rm=T),
                     has_study = if_else('True' %in% has_study, TRUE, FALSE),
                     has_courtyard = if_else('True' %in% has_courtyard, TRUE, FALSE),
                     has_balcony = if_else('True' %in% has_balcony, TRUE, FALSE),
                     has_ac = if_else('True' %in% has_ac, TRUE, FALSE),
                     has_garage = if_else('True' %in% has_garage, TRUE, FALSE)) %>%
   dplyr::mutate_at(.vars=c('area_size', 'bedrooms', 'baths', 'parking'),
                    .funs=function(x) ifelse(!is.finite(x), NA, x))

```

Recombine the location and property characteristics data.

```{r}

  ltr_prop <- ltr_loc %>%
    inner_join(ltr_pc, by='addr_id')

```

We then recombine the property and transaction data (which is nested for efficiency).

```{r}

 ltr_tdf <- ltr_prop %>%
   dplyr::inner_join(ltr_trans, by='addr_id')

```

### Output Data

Finally, we write out the long term rental data to an R object

```{r}

 saveRDS(ltr_tdf, file=file.path(data_path, 'prepared', 'ltr_data.RDS'))

```

### 2018-04-16 functions/abb_Functions.R

@@ -187,8 +187,8 @@ abbCalcBookStr <- function(id.book.data){
   if(length(id.data) > 1){
     
     # Find min and max date
-    id.min <- min(id.book.data$date)
-    id.max <- max(id.book.data$date)
+    id_min <- min(id.book.data$date)
+    id_max <- max(id.book.data$date)
     
     # Divide by status and collapse
     status.string <- id.data[1]
@@ -227,11 +227,11 @@ abbCalcBookStr <- function(id.book.data){
     if(length(id.A) > 0){
       a.list <- ss.list[id.A]
       avails <- unlist(lapply(a.list, nchar))
-      avail.rate <- sum(avails) / length(id.data)
+      avail_rate <- sum(avails) / length(id.data)
       
     } else {
       
-      avail.rate <- 0
+      avail_rate <- 0
       
     }
     
@@ -241,46 +241,46 @@ abbCalcBookStr <- function(id.book.data){
       # Count longest and blocked times
       blocks <- unlist(lapply(b.list, nchar))
       
-      block.rate <- sum(blocks) / length(id.data)
-      longest.block <- max(blocks)
-      med.block <- median(blocks)
-      nbr.block <- length(id.B)
+      block_rate <- sum(blocks) / length(id.data)
+      longest_block <- max(blocks)
+      med_block <- median(blocks)
+      nbr_block <- length(id.B)
       
     } else {
       
-      block.rate <- 0
-      longest.block <- 0
-      med.block <- 0
-      nbr.block <- 0
+      block_rate <- 0
+      longest_block <- 0
+      med_block <- 0
+      nbr_block <- 0
       
     }
     
-    total.days <- length(id.data)  
+    total_days <- length(id.data)  
     
   } else {
     
-    block.rate <- NA
-    longest.block <- NA
-    med.block <- NA
-    nbr.block <- NA
-    total.days <- NA
-    id.min <- NA
-    id.max <- NA
-    avail.rate <- NA
+    block_rate <- NA
+    longest_block <- NA
+    med_block <- NA
+    nbr_block <- NA
+    days <- NA
+    id_min <- NA
+    id_max <- NA
+    avail_rate <- NA
     bookings <- NA
 
   }  
   
   ## Return Values
   
-  return(data.frame(min.date=id.min,
-                    max.date=id.max,
-                    total.days=total.days,
-                    block.rate=block.rate,
[…]

### 2018-04-30 scripts/3_data_prep.Rmd
Move to list-col tidy data.frames

---
title: "Data Preparation, Integration and Cleaning"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

### Introduction

This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).  Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocess.R** and **2_ltr_preprocess.R**.

&nbsp;
&nbsp;

### Preliminary Commands

&nbsp;

We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.

```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)

```

We then set the paths to the data and the code, conditional on which of the authors is running the analysis.

```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')

```

Next, we source the necessary custom code files for the analysis.

```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  source(file.path(code_path, 'functions', 'abb_Functions.R'))

#
#  # Other custom files
# 
#   if(offline){
# 
#     source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
#     source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))
#     
#   } else {
#     
#   source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
#                 '/master/ggPlotTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
#                 '/master/dataMungeTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/spatialLogitModels.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/point2surface_Tools.R'))
# 
#   }
```

### Constants and Parameters

We then set the constants used in this study:

1. **Exchange rate**: The Airbnb rates are provided in US dollars.  We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.

```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

 exch_rate <- 1.32

```

2. **Date of Purchase**: In our analyzis we assume a date on which the decision to Airbnb or to enter into a long-term rental strategy is undertaken.  We set this to September 1, 2015.

```{r set_date}

  decision_date <- lubridate::as_date('2015-09-01')

```

3. Colors for visualizations.  We use the official Airbnb palette of colors for our ongoing data vizualizations.

```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

 # Set all colors

  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255),
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

 # Set specific colors

  str_col <- abb_col[1]
  ltr_col <- abb_col[3]

```

## Loading data

&nbsp;

Next we load in the raw data.  The short-term rental (Airbnb) data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  str_tdf <- readRDS(file.path(data_path, 'prepared', 'str_data.RDS'))

  ltr_tdf <- readRDS(file.path(data_path, 'prepared', 'ltr_data.RDS'))

```

And, finally, we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]  After we load each we convert the names of the data fields to lower case for easier use in future coding.

```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Suburb shapefile

  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)
  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))

  # SA1 shapefile

  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)
  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))

  # Beach file

  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
  names(beach_shp@data) <- tolower(names(beach_shp@data))

```

## Data Preparation

&nbsp;

In this section we remove, convert and/or transform a number of data fields. We also remove observations if they are missing critical data or fall outside of the scope of our research question.

&nbsp;

### Trim and Standardize Fields

The data contain many fields that are either not fully observed and/or are not relevant to our research question.  Additionally, the field naming conventions differ between the two datasets. We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.

We start by trimming the property-level short term data.  No fields need to be removed from the daily data.

While trimming the fields we also we standardize the field names.  Here we follow the convention of placing an underscore between words in the name.  We also shorten a number of the fields to make future coding easier.

```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

   str_df <- str_df %>% 
     dplyr::select(property_id=property.id, host_id=host.id, listing_title=listing.title, 
                   property_type=property.type, listing_type=listing.type,
                   created_date=created.date, latitude, longitude, rating=overall.rating,
                   max_guests=max.guests, canc_policy=cancellation.policy, 
                   cleaning_fee=cleaning.fee, nightly_rate=published.nightly.rate, 
                   weekly_rate=published.weekly.rate, monthly_rate=published.monthly.rate, 
                   avg_nightly_rate=average.daily.rate, min_stay=minimum.stay, bedrooms, 
                   bathrooms, min_date=min.date, max_date=max.date, days=total.days, 
                   block_rate=block.rate, avail_rate=avail.rate, 
                   longest_block=longest.block, nbr_blocks=nbr.block, med_block=med.block,
                   created_year=created.year)

  daily_df <- daily_df %>%
    dplyr::select(property_id=property.id, date, status, price, booked_date=booked.date,
                  resv_id=reservation.id)

```

We then limit the fields of the long-term property-specific data

```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ltr_df <- ltr_df %>%
    dplyr::select(id_key=id.key, geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude, event_date=event.date,
                  event_price=eventprice, property_type=propertytype, area_size=areasize,
                  bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage, dom)

  list_df <- list_df %>%
    dplyr::select(id_key=id.key, event_id=eventid, activity_id=activityid, 
                  addr_id=addressid, of_record=of.record, event_date=event.date,
                  event_price=eventprice, first_date=first.adv.date, 
                  first_price=firstadvertisedeventprice, last_date=last.adv.date,
                  last_price=lastadvertisedeventprice, event_code=eventtypecode)

```

### Trim by Time

Next we filter the observations by time.  Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.  To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.  Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).  In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.  Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.  While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.

Before we begin the filter process, we initial the data cleaning counter -- a small function that keeps track of how many observations we remove.

```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

   setCleanCount()

```

We then clip by time.  For the short-term data we will consider any Airbnb property that had at least 6 months worth of listing time on the portal during the 12-month study period

```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Limit short term data

  str_df <- str_df[(str_df$max_date - str_df$min_date) >= 178, ]
  str_df <- str_df[str_df$max_date >= (decision_date + 182) &
                    str_df$min_date <= (decision_date + 182), ]

  daily_df <- daily_df[daily_df$date >= decision_date, ]

  # Limit long term data

  ltr_df <- ltr_df[ltr_df$event_date >= (decision_date - 365) &
                    ltr_df$event_date <= (decision_date - 1), ]
  list_df <- list_df[list_df$id_key %in% ltr_df$id_key, ]

 # Count cleaning

  countCleaning('time')

```

Next we add a monthly variable to the data for use in future modeling exercises.

```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Short term data

  str_df$month <- 1
  daily_df$month <- paste0(lubridate::year(daily_df$date), "_", 
                           lubridate::month(daily_df$date))

  # Long term data

  ltr_df$month <- paste0(lubridate::year(ltr_df$event_date), "_",
                          lubridate::month(ltr_df$event_date))

#   listing.data$ltr.month <- as.numeric(as.factor(substr(
#     listing.data$event.date, 1, 7))) - 8
#   
```
# 
# ### Standardize Property Types
# 
# &nbsp;
# 
# AirBNB units are classified into 19 different property type.  The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type]. For the sake of this analysis, we will collapse these twenty types into three types:
#   
# 1. **House**:  Includes properties labeled 'House' or 'Townhouse'
# 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
# 3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt. 
# 
# Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
#   
# 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
# 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
# 3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
# 
# Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.  This is most apparent when talking about apartment dwellings.  In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).  Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context. 
# 
# We then create a new variable in each dataset and give each one of the three categories discussed above.
# 
# ```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Short Term data  
# 
#   str_df$type <- 'Other'
#   str_df$type[str_df$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
#   str_df$type[str_df$property.type %in% c('House', 'Townhouse')] <- 'House'
# 
#  # Long Term data  
# 
#   ltr_df$type <- 'Other'
#   ltr_df$type[ltr_df$property.type %in% c('Duplex', 'House',
#                                            'Terrace', 'Townhouse')] <- 'House'
#   ltr_df$type[ltr_df$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
# 
# ```
# 
# As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.  Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.  As a result, we remove the 'Others' from both the Airbnb and the long term rental data. 
# 
# ```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   # Create Airbnb plot
# 
#   str.types <- ggplot(str_df, aes(x=type)) + 
#     geom_bar(color=str_col, fill=str_col) +
#     xlab('\nProperty Type\n') + 
#     ggtitle('\nShort Term Rentals\n')  +
#     ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#   # Create long term rental plot
# 
#   ltr.types <- ggplot(ltr_df, aes(x=type)) + 
#     geom_bar(color=ltr_col, fill=ltr_col) +
#     xlab('\nProperty Type\n') + 
#     ggtitle('\nLong Term Rentals\n')  +
#     ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#   
#   
#   # Output plots
#   png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280, 
#       bg='transparent')
#     ggMultiPlots(str.types, ltr.types, cols=2)
#   dev.off()
#   
#   save(str.types, file=paste0(fig.path, 'strtypes.RData'))
#   save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))
#   
# ```
# 
# ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   str_df <- subset(str_df, type != 'Other')
#   ltr_df <- subset(ltr_df, type != 'Other')
#   
#   # Count Cleaning
#   countCleaning('property.type')
# 
# ```
# 
# Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
# 
# 1. **Entire Home/Apt**: The entire home or apartment is available
# 2. **Private Room**: One room within a house or apartment is available
# 3. **Shared Room**: A bed within a room shared by another occupant(s) is available
# 
# As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt. Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable. 
# 
# ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   # Fix data types and names
#   str_df$listing.type <- as.character(str_df$listing.type)
#   str_df$listing.type[str_df$listing.type == 'Entire home/apt'] <- 'Entire home'
# 
#   list.types <- ggplot(str_df, aes(x=listing.type)) + 
#       geom_bar(color=str_col, fill=str_col) +
#       xlab('\nListing Type\n') + 
#       ggtitle('\nShort Term Rentals by Listing Type\n')  +
#       ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#   
#   # Make Plot
#   png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280, 
#       bg='transparent')
# 
#     list.types
#   
#   dev.off()
#   
#   save(list.types, file=paste0(fig.path, 'listtypes.RData'))
#   
#   
# ```
# 
# ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   str_df <- str_df[str_df$listing.type == 'Entire home', ]
#   
#   # Count cleaning 
#   countCleaning('listing.type')
#   
# ```
# 
# ## Structural Characteristics
# 
# &nbsp;
# 
# In this section we transform and filter based on the structural characteristics of the properties. 
# 
# ### Fix Boolean Variables
# 
# Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
# 
# ```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   ltr_df$has.study <- ifelse(ltr_df$has.study == 'True', 1, 0)
#   ltr_df$has.courtyard <- ifelse(ltr_df$has.courtyard == 'True', 1, 0)
#   ltr_df$has.aircon <- ifelse(ltr_df$has.aircon == 'True', 1, 0)
#   ltr_df$has.balcony <- ifelse(ltr_df$has.balcony == 'True', 1, 0)
#   ltr_df$has.garage <- ifelse(ltr_df$has.garage == 'True', 1, 0)
# 
# ```
# 
# &nbsp;
# 
# ### Bedrooms
# 
# We start by looking at bedrooms. We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms). We then plot the distribution of diffeltr bedrooms counts.  From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types. 
# 
# ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove missing and data errors
# 
#   # Long term data
#   ltr_df <- ltr_df[!is.na(ltr_df$bedrooms), ]
#   ltr_df <- ltr_df[ltr_df$bedrooms <= 10, ]
# 
#   # Short term data
#   str_df <- str_df[!is.na(str_df$bedrooms), ]
#   str_df <- str_df[str_df$bedrooms <= 10, ]
# 
# ```
# 
# ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Build long term bar plot
# 
#    ltrbed <- ggplot(ltr_df, aes(x=bedrooms)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     facet_wrap(~type,scales='free_y') +
#     scale_x_continuous(labels=1:10, breaks=1:10)+
#     xlab('\nBedrooms\n') +
#     scale_y_continuous(labels=c(0,10000,20000), 
#                        breaks=c(0,10000,20000))+
#     ylab('') +
#     ggtitle('Bedrooms in Long Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#  # Build short term bar plot
# 
#   strbed <- ggplot(str_df, aes(x=bedrooms)) + 
#     geom_bar(fill=str_col, color=str_col) +
#     facet_wrap(~type,scales='free_y') +
#     scale_x_continuous(labels=0:10, breaks=0:10) +
#     xlab('\nBedrooms\n') +
#     ylab('') +
#     ggtitle('Bedrooms in Short Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#   # Make Plot
#   png(file=paste0(fig.path, 'dataclean_bedcount.png'), width = 480, height = 280, 
#       bg='transparent')
#     ggMultiPlots(strbed, ltrbed, cols=1)
#   dev.off()
#   
#   save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
#   save(strbed, file=paste0(fig.path, 'strbed.RData'))
# 
# ```
# 
# For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.  We filter the data accordingly. Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom. We convert the 0 bed short term units to 1 bed units.   
# 
# ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove all with more than 4 beds
# 
#   str_df <- str_df[str_df$bedrooms < 5, ]
#   ltr_df <- ltr_df[ltr_df$bedrooms < 5, ]
# 
#  # Remove apartments with more than 3
#   
#   str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
#   ltr.id <- which(ltr_df$bedrooms > 3 & ltr_df$type =='Apartment')
# 
#   if(length(str.id) > 0) str_df <- str_df[-str.id, ]
#   if(length(ltr.id) > 0) ltr_df <- ltr_df[-ltr.id, ]
# 
#   # Convert 0 Bed to 1 Bed  
#   str_df$bedrooms[str_df$bedrooms == 0] <- 1
#   
#   # Count Data Cleaning
#   countCleaning('bedrooms')
# 
# ```
# 
# ### Bathrooms
# 
# We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.  
# 
# ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove missing data
#   
#   ltr_df <- ltr_df[!is.na(ltr_df$baths), ]
#   str_df <- str_df[!is.na(str_df$baths), ]
# 
# ```
# 
# ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Build long term plot
# 
#   ltbath <- ggplot(ltr_df, aes(x=baths)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     facet_wrap(~type) +
#     scale_x_continuous(labels=1:8, breaks=1:8)+
#     xlab('\nBathrooms\n') +
#     ylab('') + 
#     ggtitle('Bathrooms in Long Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#  # Build short term plot 
# 
#   stbath <- ggplot(str_df, aes(x=baths)) + 
#     geom_bar(fill=str_col, color=str_col) +
#     facet_wrap(~type, scales='free_y') +
#     scale_x_continuous(labels=0:8, breaks=0:8)+
#     xlab('\nBathrooms\n') +
#     ylab('') + 
#     ggtitle('Bathrooms in Short Term ltrals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bathount.png'), width = 480, height = 280, 
#       bg='transparent')
#   
#     ggMultiPlots(stbath, ltbath, cols=1)
#     
#   dev.off()
#    
#   save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
#   save(stbath, file=paste0(fig.path, 'strbath.RData'))
#  
# ```
# 
# Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly. A few short term properties state no baths, which is likely an error so we remove these as well. Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.  We round the baths up to whole integers. 
# 
# ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Filter by bath count
# 
#   # Short term data
#   str_df <- str_df[str_df$baths < 4, ]
#   str_df <- str_df[str_df$baths > 0, ]
# 
#   # Long term data
#   ltr_df <- ltr_df[ltr_df$baths < 4, ]
#   
#  # Round baths up  
# 
#   str_df$baths <- round(str_df$baths + .01, 0)
# 
#   # Count cleaning
#   countCleaning('baths')
#   
# ```
# 
# ### Bed/Bath Combination
# 
# In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.  In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.  As a result we examine the combinations of the two. 
# 
# ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Create combination variable
# 
#   ltr_df$bedbath <- paste0(ltr_df$bedrooms, '..', ltr_df$baths)
#   str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)
# 
# ```
# 
# ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Make long term plot
# 
#   ltbb <- ggplot(ltr_df, aes(x=bedbath)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     xlab('\nBed/Bath Combo\n') +
#     ylab('Number of Properties\n') +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#     ggtitle('Long Term Rentals') + 
#     facet_wrap(~type, scales='free_y')+
#     theme(plot.title = element_text(hjust = 0.5))
# 
#  # Make short term plots
# 
#   stbb <- ggplot(str_df, aes(x=bedbath)) +
#     geom_bar(fill=str_col, color=str_col) + 
#     xlab('\nBed/Bath Combo\n') +
#     ylab('Number of Properties\n') +
#     ggtitle('Short Term Rentals') + 
#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#     facet_wrap(~type, scales='free_y')+
#     theme(plot.title = element_text(hjust = 0.5))
# 
#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bedbath.png'), width = 480, height = 280, 
#       bg='transparent')
#   
#     ggMultiPlots(ltbb, stbb, cols=1)
# 
#   dev.off()  
#   
#   save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
#   save(stbb, file=paste0(fig.path, 'strbb.RData'))
# 
#     
# ```
# 
# From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.  
# 
# ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Set level of acceptable combinations
# 
#   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
# 
#  # Filter data
# 
#   ltr_df <- ltr_df[ltr_df$bedbath %in% acc.bb, ]
#   str_df <- str_df[str_df$bedbath %in% acc.bb, ]
# 
#  # Count Cleaning
#   
#   countCleaning('bedbath')
# 
# ```
# 
# Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.  We additionally create a product variable that splits the bed/bath by apartment and house.
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Re-order factors
# 
#   str_df$bedbath <- factor(str_df$bedbath, 
#                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
#   ltr_df$bedbath <- factor(ltr_df$bedbath, 
#                                levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
# 
#   # Add product as a variable
#   
#   str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
#   ltr_df$product <- paste0(substr(ltr_df$type, 1, 1), ltr_df$bedbath)
# 
# ```
# 
# 
# ## Rates and Rental values
# 
# We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data. 
# 
# ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   ltr_df <- ltr_df[!is.na(ltr_df$event.price), ]
#   str_df <- str_df[!is.na(str_df$nightly.rate), ]
#   
# ```
# 
# Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
# 
# ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Property level data
# 
#   str_df$average.daily.rate <- str_df$average.daily.rate * exch.rate
#   str_df$nightly.rate <- str_df$nightly.rate * exch.rate
#   str_df$weekly.rate <- str_df$weekly.rate * exch.rate
#   str_df$monthly.rate <- str_df$monthly * exch.rate
#   
#   # Daily data
#   
#   daily_df$price <- daily_df$price * exch.rate
# 
# ```
# 
# Next we extract all of the daily reservation data for the reserved nightly. From this information we calculate the median nightly reservation price for each property and append it to the property level data. 
# 
# ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#    # Get all of the reservations
#   resv.daily <- daily_df[daily_df$status == 'R', ]
# 
#   # Calculate the property specific median nightly rate
#   med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
#   
#   # Add median rate to the property  
#   str_df$med.rate <- med.daily$Var[match(str_df$property.id, med.daily$ID)] 
#   
#   # Remove those with no valid median rate
#   str_df <- str_df[!is.na(str_df$med.rate), ]
#    
# ```
# 
# From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night. We filter the data accordingly. 
# 
# ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # ltr Plot
#   
#   ltr.plot <- ggplot(ltr_df, aes(x=event.price)) + 
#     geom_density(fill=ltr_col, alpha=.8) +
#     ylab('') +
#     xlab('Weekly Rental') + 
#     ggtitle('Long Term Rentals') + 
#     scale_x_continuous(limits=c(0, 1500)) +
#     theme(axis.title.y=element_blank(),
#           axis.text.y=element_blank(),
#           axis.ticks.y=element_blank()) +
#     theme(plot.title = element_text(hjust = 0.5))
# 
# 
#   # Nightly Rate plot
#   rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
#     geom_density(fill=str_col, alpha=.8) + 
#     ylab('') +
#     xlab('Nightly Rate') +
#     ggtitle('Short Term Rentals') + 
#     scale_x_continuous(limits=c(0, 600)) +
#     theme(axis.title.y=element_blank(),
#           axis.text.y=element_blank(),
#           axis.ticks.y=element_blank()) +
#     theme(plot.title = element_text(hjust = 0.5))
# 
# 
# ```
# 
# ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   png(file=paste0(fig.path, 'dataclean_rates.png'), width = 480, height = 280, 
#       bg='transparent')
#     
#     ggMultiPlots(ltr.plot, rate.plot, cols=2)
#   
#   dev.off()
#   
#   save(ltr.plot, file=paste0(fig.path, 'rentplot.RData'))
#   save(rate.plot, file=paste0(fig.path, 'rateplot.RData'))
# 
#   
# ```
# 
# ```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   ## Filter the long term data
# 
#   ltr_df <- ltr_df[ltr_df$event.price >= 200 & 
#                          ltr_df$event.price <= 1000, ]
# 
#   str_df <- str_df[str_df$med.rate >= 50 &
#                          str_df$med.rate <= 500, ]
# 
#   # Count Cleaning
#   countCleaning('rates.rents')
#   
# ```  
# 
# #### Observed Revenue
# 
# Our final data filtering considers the observed revenue of the properties. For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.  In a number of extreme cases, time on market was extremely long and the total observed revenues very low. To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
# 
# For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.  Using this data we sum up the total revenue from bookings. For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
# 
# Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
# 
# ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
# 
#  # Compute bookings count
# 
#   str_df$bookings <- round(str_df$total.days * 
#                                (1 - (str_df$block.rate + str_df$avail.rate)), 0)
#  
#  # Remove those with 0 
# 
#   str_df <- str_df[str_df$bookings > 0, ]
# 
#   str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
#   ltr_df$gross.revenue <- ltr_df$event.price * (52 - ltr_df$dom / 7)
#  
#   str.small <- str_df[,c('baths', 'gross.revenue')]
#   str.small$tenure <- 'short-term'
#   ltr.small <- ltr_df[,c('baths', 'gross.revenue')]
#   ltr.small$tenure <- 'long-term'
#   all.small <- rbind(str.small, ltr.small)
# 
#   revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
#     geom_density(alpha=.5) +
#     scale_fill_manual(values=c(ltr_col, abb_col)) +
#     scale_color_manual(values=c(ltr_col, abb_col)) +
#     ggtitle('Annual Revenues by Tenure Type') +
#     xlab('Annual Revenue') +
#     scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
#                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+
#     theme(legend.position='bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           axis.text.y = element_blank(),
#           axis.ticks.y = element_blank(),
#           axis.title.y=element_blank()) +
#     coord_cartesian(xlim=c(0, 70000))
#   
# ```
# 
# ```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
#       bg='transparent')
#     
#     revdens
#   
#   dev.off()
#   
#   save(revdens, file=paste0(fig.path, 'revdens.RData'))
#   
#   ltr_df <- ltr_df[ltr_df$dom <= 180, ]
#   
#     countCleaning('revenue')
#   
# ```
# 
# ### Locations and Submarkets
# 
# Location is clearly an important determinant in both the short and long term rental markets. At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.  In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.  Suburbs in Melbourne are much smaller than their North American counterparts.  The specific suburb of a property is the second, or finer scale, at which the market operates. The plot below shows the three large submarkets (Inner, Middle and Outer).
# 
# ```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Convert shapefile to ggplot-able object
#   
#   # Fix lat/long
#  
#   # Limit to extent of data
#   sub.table <- table(ltr_df$suburb)
#   sub.table <- sub.table[sub.table != 0]
#   
#   # Clip to only those with a ltral observation
#   study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
#   
#   # Convert to an outer bound with holes
#   ss.bound <- gUnaryUnion(study.suburbs)
#   
#   # Remove holes from the shapefile
#   ssb <- slot(ss.bound, "polygons") 
#   holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound) 
#   ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
#    Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
#   
#   # Identify which suburbs all in area covered by outer bound
#   ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
#   study.suburbs <- suburbs.shp[which(ss.in), ]
#   
#   # Convert into an outer boundary with no holes
#   ss.bound.out <- gUnaryUnion(study.suburbs)
#   ssb.out <- slot(ss.bound.out, "polygons") 
#   holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res.out <- lapply(1:length(ssb.out), 
#                     function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound.out) 
#   ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
#                                          function(i) Polygons(res.out[[i]], 
#                                                               ID=IDs[i])),
#                                               proj4string=CRS(proj4string(ss.bound))) 
#   
#   # Convert into a ggplot-able format
#   subs <- fortify(study.suburbs, region='name_2006')
# 
#   # Add suburb category
#   subs$des <- suburbs.shp@data$suburbdesi[
#     match(subs$id, suburbs.shp@data$name_2006)]
# 
# ```
# 
# ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#  ## Build the map object
# 
#   # Set colors
#   g_cols <- c('grey10', 'grey40', 'grey70')
# 
#   # Make map
#   loc.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
#     scale_fill_manual(values=g_cols, labels=c('Inner      ',
#                                               'Middle      ',
#                                               'Outer')) +
#     geom_path(data=subs[subs$des=='Outer', ], 
#               aes(x=long, y=lat, group=group), col='white', size=.1,
#               linetype=1) +
#   
#     geom_path(data=subs[subs$des=='Middle', ], 
#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
#               linetype=1) +
#     
#     geom_path(data=subs[subs$des=='Inner', ], 
#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
#               linetype=1) +
#     
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     #ggtitle("Melbourne Suburb Classifications")+
#     theme(plot.title = element_text(hjust = 0.5))
# 
# ```
# 
# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
#       bg='transparent')
#   
#     loc.map
#     
#   dev.off()
#   
#   loc.map
#   
#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
# 
#     
# ```
# 
# It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
# 
# 1. Rural (Outer suburbs, not Beach)
# 2. Suburban (Middle suburbs, not Beach)
# 3. City (Inner Suburbs, not Beach, not Core)
# 4. City-Core (Select inner suburbs with tourist activities and near CBD)
# 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
# 
# We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.  This process is repeated for both the short and long term data.  We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on. Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs). 
# 
# We select the 18 suburbs below to represent the 'core' of the city.  The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.  All are well serviced by public transportation and possess abundant amenties for tourists. 
# 
# ```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
#                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
#                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
#                    'St Kilda West', 'West Melbourne', 'Windsor')
# 
# ```
# 
# We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
# 
# ```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Determine centroid of study area
#  
#   latMid <- median(str_df$latitude)
#   longMid <- median(str_df$longitude)
# 
#  # Calculate Degress to Meters conversion 
#  
#   m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
#   m.long = 111132.954 * cos (latMid)
#   m.conv <- mean(m.lat, m.long)
#  
#  # Create the beach buffer  
#   
#   beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
# 
# ```
# 
# Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.  
# 
# ```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Short term data  
# 
#   # Convert to point shapefile
#   str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
#                                                str_df$latitude),
#                                          str_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
# 
#   # Add suburb name 
#   spJoin <- over(str.prop.shp, suburbs.shp)
#   str_df$suburb <- as.character(spJoin$name_2006)
#   str_df$suburb[is.na(str_df$suburb)] <- 'missing'
# 
#   # Add suburb designation
#   str_df$sub.class <- as.character(spJoin$suburbdesi)
#   str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'
#   
#   # Add SA1 designation
#   spJoin <- over(str.prop.shp, sa1s.shp)
#   str_df$sa1 <- spJoin$sa1_main11
#  
#   ## Add Beach Designation
#   spJoin <- over(str.prop.shp, beach.buffer)
#   str_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   
#   # Remove those missing a suburb classification (out of area)
#   str_df <- str_df[str_df$sub.class != 'missing', ]
#   str_df <- str_df[str_df$sa1 != 'missing', ]
# 
# ```
# 
# ```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Add the submarket designations
# 
#   # Add individual classes
#   str_df$geo.mrkt <- 'rural'
#   str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
#   str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
#   str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
#   str_df$geo.mrkt[str_df$beach == 1] <- 'beach'
#   
#   # Order the factors properly
#   str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
#   
# ```
# 
# Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.  Half of these do, however, have a lat/long value for the centroid of the street that the property faces.  To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.  For those without either (3% of the total) we remove them from the dataset at this point. 
# 
# ```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Label those missing lat/long  
# 
#   miss.LL <- which(is.na(ltr_df$latitude))  
# 
#  # Create a field to indicate the approximate matches  
# 
#   ltr_df$miss.LL <- 0
#   ltr_df$miss.LL[miss.LL] <- 1
# 
#  # Apply approximate match    
# 
#   ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
#   ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]
# 
#  # Remove those still missing latitude data   
# 
#   ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]
# 
# ```
# 
# Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.  
# 
# ```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Long term data  
# 
#   # Convert to point shapefile
# 
#   ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
#                                                ltr_df$latitude),
#                                          ltr_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
# 
#   # Add suburb name 
#   
#   spJoin <- over(ltr.prop.shp, suburbs.shp)
#   ltr_df$suburb <- as.character(spJoin$name_2006)
#   ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'
# 
#   # Add suburb designation
#   
#   ltr_df$sub.class <- as.character(spJoin$suburbdesi)
#   ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'
#   
#   # Add SA1 designation
#   
#   spJoin <- over(ltr.prop.shp, sa1s.shp)
#   ltr_df$sa1 <- spJoin$sa1_main11
#  
#   ## Add Beach Designation
#   
#   spJoin <- over(ltr.prop.shp, beach.buffer)
#   ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   
#   # Remove those missing a suburb classification (out of area)
#   
#   ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
#   ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]
# 
# ```
# 
# ```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Add the submarket designations
# 
#   # Add individual classes
#   ltr_df$geo.mrkt <- 'rural'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
#   ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
#   ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'
#   
#   # Order the factors properly
#   ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
#   
#   # Count Cleaning
#   countCleaning('location')
#   
# ```
# 
# The location of the short and long term rentals, colored by submarket, are shown below
# 
# ```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Set submarket colors
#   
#   sm_col <- abb_col[c(1, 3, 6, 5, 2)]
# 
#   # Make map
# 
#   str.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
# 
# ```
# 
# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
# 
# ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
# 
#   # Make Airbnb submarket map
#   
#   strtype.map <- ggplot() +
#     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
#     scale_fill_manual(values=sm_col) +
#     facet_wrap(~type) +
#     ylab('# of Properties\n') + xlab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     #ggtitle('Short Term Property Type\nBy Submarket')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
#   # Make Long term rental map
# 
#   ltrtype.map <- ggplot() +
#     geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
#     scale_fill_manual(values=sm_col) +
#     facet_wrap(~type) +
#     ylab('# of Properties\n') + xlab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     #ggtitle('Long Term Property Type\nBy Submarket')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
# 
#   png(file=paste0(fig.path, 'submplot.png'), width = 680, height = 590, 
#       bg='transparent')
#     ggMultiPlots(strtype.map, ltrtype.map, cols=2)
#   dev.off()
#     
#   ggMultiPlots(strtype.map, ltrtype.map, cols=2)
#   
#   save(strtype.map, file=paste0(fig.path, 'strsubplot.RData'))
#   save(ltrtype.map, file=paste0(fig.path, 'ltrsubplot.RData'))
# 
#   
# ```
# 
# Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on. 
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Convert suburbs from factor to character
#   str_df$suburb <- as.character(str_df$suburb)
#   ltr_df$suburb <- as.character(ltr_df$suburb)
#   
# ```
# 
# &nbsp;
# 
# ## Filter Transaction Data
# 
# The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets
# 
# ```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Short term data
#   
#   daily_df <- daily_df[daily_df$property.id %in% str_df$property.id,]
# 
#  ## Long term list data
#   
#   listing.data <- listing.data[listing.data$activity.id %in% ltr_df$activity.id,]
# 
# ```
# 
# ## Summarize Daily Data
# 
# As we have limited the time period of analysis from the expanse of the raw data, we must now re calculate the daily summary information. 
# 
# ```{r redo.daily.summ, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
# 
#     # Create new cluster
#   abb_cl <- get_default_cluster() 
#   
#   # Register function and variable
#   cluster_copy(abb_cl, abbCalcBookStr)
# 
#   # Summarize daily by property
#   daily_summ <- daily_df %>% 
#     multidplyr::partition(property.id, cluster=abb_cl) %>% 
#     dplyr::do(abbCalcBookStr(.)) %>% 
#     dplyr::collect()
#   
#  # Remove existing 
#  str_df <- str_df %>%
#    dplyr::select(-c(total.days, block.rate, avail.rate, longest.block, nbr.block,
#                     med.block, bookings))
#  
#  # Add summary data to property data
#  str_df <- str_df %>% dplyr::left_join(daily_summ, by='property.id')
# 
# 
# ```
# 
# 
# #### Host Policies
# 
# Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.  We also remove the few observations with missing host policy data
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## ID those with missing cancel policies and remove
# 
#   str_df <- str_df %>% 
#     dplyr::filter(cancel.policy %in% c('Flexible', 'Moderate', 'Strict'))
# 
#  ## ID those with Super Strict and change to Strict  
#   
#   ss60 <- which(str_df$cancel.policy == 'Super Strict 60 Days')
#   str_df$cancel.policy[ss60] <- 'Strict'
# 
#   # Count Cleaning
#   countCleaning('hostpolicy')
#   
#   
# ```
# 
# ## Write out data  
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
#        beach.shp, core.suburbs, exch.rate, ltr_col, str_col, sa1s.shp, 
#        suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
#        ltr.run.total, str.run.total,
#        file=paste0(data_path, 'prepared/prep_workspace_', data_name, '.RData'))
# 
# ```N

### 2018-04-30 scripts/1_str_preprocess.R

@@ -1,92 +1,0 @@
-##########################################################################################
-#                                                                                        #  
-#   Data Preprocessing for the Short-Term Rental data of the ABB project                 #
-#                                                                                        #  
-##########################################################################################
-
- ## Load libraries
-
-  library(plyr)
-  library(stringr)
-  library(lubridate)
-  library(dplyr)
-  library(multidplyr)
-
-  ## Set locations
-
-  # Assign path based on computer name
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  
-  ## Load sources
-
-  source(file.path(getwd(), 'functions', "abb_Functions.R"))
-
- ## Load Data  
-   
-  # Property Information
-
-  str_raw <- read.csv(file.path(data_path, 'raw', 'melbproperties.csv'), header=T)
-  str2_raw <- read.csv(file.path(data_path, '/raw/melbproperties_to_mar2017.csv'), 
-                        header=T)
-  
-  # Daily rental information
-
-  daily_raw  <- read.csv(file.path(data_path, '/raw/melbDaily.csv'), header=T)
-  daily2_raw  <- read.csv(file.path(data_path, '/raw/melbDaily_to_mar2017.csv'), 
-                           header=T)
-  
- ## Fix Names
-  
-  names(str_raw) <- tolower(names(str_raw))
-  names(str2_raw) <- tolower(names(str2_raw))
-  names(daily_raw) <- tolower(names(daily_raw))
-  names(daily2_raw) <- tolower(names(daily2_raw))
-  
- ## Determine unique observations
-  
-  # Structure Data
-  str_df <- dplyr::bind_rows(str2_raw, str_raw)
-  str_df <- str_df %>% dplyr::filter(!duplicated(property.id))  
-  
-  # Daily Data
-  daily_df <- dplyr::bind_rows(daily2_raw, daily_raw) %>%
-    dplyr::mutate(uniq_id = paste0(property.id, '_', date)) %>%
-    dplyr::filter(!duplicated(uniq_id)) %>%
-    dplyr::select(property.id, date, status, price, booked.date, reservation.id)
-  
- ## Fix Dates  
-  
-  # Daily data
-  daily_df$date <- lubridate::as_date(daily_df$date)
-  
-  # Property level data
-  str_df$created.date <- lubridate::as_date(str_df$created.date)
-  str_df$created.year <- lubridate::year(str_df$created.date)
-
- ## Add Summary Information
-
[…]

### 2018-04-30 scripts/2_ltr_preprocess.R

@@ -1,102 +1,0 @@
-##########################################################################################
-#                                                                                        #  
-#   Data Preprocessing for the Long-Term Rental data of the ABB project                  #
-#                                                                                        #  
-##########################################################################################
-
-
- ## Load Libraries
-
-  library(plyr)
-  library(stringr)
-  library(lubridate)
-  library(dplyr)
-  library(multidplyr)
-  
-  ## Set locations
-
-  # Assign path based on computer name
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-
- ## Load sources
-
-  source(file.path(getwd(), 'functions', "abb_Functions.R"))
-  
-  # Load the raw rent data
-  rent_df <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)
-
- ## Remove observations without sufficient keys
-  
-  r_df <- rent_df[!is.na(rent_df$EventID), ]
-  r_df <- r_df[!is.na(r_df$AddressID), ]
-  r_df <- r_df[!is.na(r_df$ActivityID), ]
-  
- ## Create Unique Key
-  
-  r_df$id.key <- paste0(as.numeric(as.factor(r_df$ActivityID)), '..',
-                       as.numeric(as.factor(r_df$AddressID)))
-  r_df$id.key <- as.numeric(as.factor(r_df$id.key))
-  
- ## Fix Dates  
-  
-  r_df$last.adv.date <- apmFixDates(r_df$LastAdvertisedEventDate)
-  r_df$first.adv.date <- apmFixDates(r_df$FirstAdvertisedEventDate)
-  r_df$event.date <- apmFixDates(r_df$EventDate)
-  r_df$event.year <- lubridate::year(r_df$event.date)
-  
- ## Remove those not occuring in 2015 or later
-  
-  r_df <- r_df %>% dplyr::filter(event.year >= 2014)
-  
- ## Add an identifier that signifies last record in a set of advertisements (of record)  
-    
-  r_df <- r_df[order(r_df$event.date, decreasing=T), ]
-  r_df <- r_df[order(r_df$id.key), ]
-  r_df$AID <- paste0(r_df$id.key, '..', r_df$last.adv.date)
-  r_df$of.record <- ifelse(duplicated(r_df$AID), 0 ,1)
-  
- ## Split into property data and listing data
-  
-  ltr_df <- r_df[r_df$of.record == 1,]
[…]

### 2018-05-04 scripts/3_data_prep.Rmd
Update:  filter function

@@
   html_document: default
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-&nbsp;
-
-### Trim and Standardize Fields
-
-The data contain many fields that are either not fully observed and/or are not relevant to our research question.
-Additionally, the field naming conventions differ between the two datasets.
-We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.
-
-We start by trimming the property-level short term data.  No fields need to be removed from the daily data.
-
-While trimming the fields we also we standardize the field names.
-Here we follow the convention of placing an underscore between words in the name.
-We also shorten a number of the fields to make future coding easier.
-
-```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-   str_df <- str_df %>% 
-     dplyr::select(property_id=property.id, host_id=host.id, listing_title=listing.title, 
-                   property_type=property.type, listing_type=listing.type,
-                   created_date=created.date, latitude, longitude, rating=overall.rating,
-                   max_guests=max.guests, canc_policy=cancellation.policy, 
-                   cleaning_fee=cleaning.fee, nightly_rate=published.nightly.rate, 
-                   weekly_rate=published.weekly.rate, monthly_rate=published.monthly.rate, 
-                   avg_nightly_rate=average.daily.rate, min_stay=minimum.stay, bedrooms, 
-                   bathrooms, min_date=min.date, max_date=max.date, days=total.days, 
-                   block_rate=block.rate, avail_rate=avail.rate, 
-                   longest_block=longest.block, nbr_blocks=nbr.block, med_block=med.block,
-                   created_year=created.year)
-
-  daily_df <- daily_df %>%
-    dplyr::select(property_id=property.id, date, status, price, booked_date=booked.date,
-                  resv_id=reservation.id)
-
-```
-
-We then limit the fields of the long-term property-specific data
-
-```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr_df <- ltr_df %>%
-    dplyr::select(id_key=id.key, geo_id=geographicalid, event_id=eventid, 
-                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
-                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
-                  suburb, postcode, latitude=property_latitude,
-                  longitude=property_longitude, str_latitude=street_centroid_latitude,
-                  str_longitude=street_centroid_longitude, event_date=event.date,
-                  event_price=eventprice, property_type=propertytype, area_size=areasize,
-                  bedrooms, baths, parking, has_study=hasstudy, 
-                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
-                  has_ac=hasairconditioning, has_garage=hasgarage, dom)
-
-  list_df <- list_df %>%
-    dplyr::select(id_key=id.key, event_id=eventid, activity_id=activityid, 
-                  addr_id=addressid, of_record=of.record, event_date=event.date,
-                  event_price=eventprice, first_date=first.adv.date, 
-                  first_price=firstadvertisedeventprice, last_date=last.adv.date,
-                  last_price=lastadvertisedeventprice, event_code=eventtypecode)
-
-```
-
 ### Trim by Time
@@
 
-  str_df <- str_df[(str_df$max_date - str_df$min_date) >= 178, ]
-  str_df <- str_df[str_df$max_date >= (decision_date + 182) &
-                    str_df$min_date <= (decision_date + 182), ]
-
-  daily_df <- daily_df[daily_df$date >= decision_date, ]
+  str_tdf <- str_tdf %>%
+    dplyr::filter((max_date - min_date) >= 178) %>%
+    dplyr::filter((max_date >= (decision_date + 182) &
+                    min_date <= (decision_date + 182)))
+
+  str_tdf <- str_tdf %>%
+    tidyr::unnest() %>% 
+    dplyr::filter(date >= decision_date) %>%
+    tidyr::nest(date:uniq_id, .key=daily_data)
 
   # Limit long term data
-
-  ltr_df <- ltr_df[ltr_df$event_date >= (decision_date - 365) &
-                    ltr_df$event_date <= (decision_date - 1), ]
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::filter((event_date >= (decision_date - 365) &
+                    event_date <= (decision_date - 1)))
+
   list_df <- list_df[list_df$id_key %in% ltr_df$id_key, ]

### 2018-05-04 functions/abb_Functions.R

@@ -289,25 +289,19 @@ abbCalcBookStr <- function(id.book.data){
 setCleanCount <- function(){
   
   # Make counts of initial sizes
-  str_orig <- nrow(str_df)
-  daily_orig <- nrow(daily_df)
-  ltr_orig <- nrow(ltr_df)
-  list_orig <- nrow(list_df)
+  str_orig <- nrow(str_tdf)
+  ltr_orig <- nrow(ltr_tdf)
   
   # Create initial data.frame
   clean_df <- data.frame(operation='initial',
                          str=str_orig,
-                         daily=daily_orig,
-                         ltr=ltr_orig,
-                         list=list_orig)
+                         ltr=ltr_orig)
   
   # Assign initial values to globalEnv
   assign('clean_count', clean_df, envir=.GlobalEnv)
-  assign('str_run_total', nrow(str_df), envir=.GlobalEnv)
-  assign('ltr_run_total', nrow(ltr_df), envir=.GlobalEnv)
-  assign('list_run_total', nrow(list_df), envir=.GlobalEnv)
-  assign('daily_run_total', nrow(daily_df), envir=.GlobalEnv)
-  
+  assign('str_run_total', nrow(str_tdf), envir=.GlobalEnv)
+  assign('ltr_run_total', nrow(ltr_tdf), envir=.GlobalEnv)
+
 }
 
 ### Cleaning counting updater ------------------------------------------------------------

### 2018-05-07 scripts/3_data_prep.Rmd
Move to SF spatial handling

@@
   library(tidyverse)
+  library(sf)
 
@@
 
-  # Suburb shapefile
-
-  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
-                               proj4string=CRS("+init=epsg:4283"),
-                               delete_null_obj=TRUE)
-  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))
-
-  # SA1 shapefile
-
-  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
-                            proj4string=CRS("+init=epsg:4283"),
-                            delete_null_obj=TRUE)
-  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))
-
-  # Beach file
-
-  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
-                             proj4string=CRS("+init=epsg:4283"),
-                             delete_null_obj=TRUE)
-  names(beach_shp@data) <- tolower(names(beach_shp@data))
+  sub_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
+    st_transform(crs=4283)
+  sa1_sf <- sf::st_read(file.path(data_path, 'geographic', 'sa1s.shp')) %>%
+    st_transform(crs=4283)
+  beach_sf <- sf::st_read(file.path(data_path, 'geographic','portPhillipBeach.shp')) %>%
+    st_transform(crs=4283)
 

### 2018-05-08 scripts/3_data_prep.Rmd
Updating filter to tidyverse compliant.

@@
 
+  # Trim properties by min and max date
   str_tdf <- str_tdf %>%
@@
 
+   # Trim actual nightly observation by the decision date
    str_tdf <- str_tdf %>% 
-    tidyr::unnest() %>% 
-    dplyr::filter(date >= decision_date) %>%
-    tidyr::nest(date:uniq_id, .key=daily_data)
+     mutate(daily_data = map(daily_data, ~filter(., date >= decision_date)))
 
@@
   ltr_tdf <- ltr_tdf %>% 
-    dplyr::filter((event_date >= (decision_date - 365) &
-                    event_date <= (decision_date - 1)))
-
-  list_df <- list_df[list_df$id_key %in% ltr_df$id_key, ]
-
+     mutate(trans_data = map(trans_data, ~filter(., (date <= decision_date - 1) & 
+                                                     date >= decision_date - 365)))
  # Count cleaning
@@
   # Short term data
-
-  str_df$month <- 1
-  daily_df$month <- paste0(lubridate::year(daily_df$date), "_", 
-                           lubridate::month(daily_df$date))
-
+   str_tdf <- str_tdf %>% 
+     mutate(daily_data = map(daily_data, 
+                             ~mutate(., month = paste0(lubridate::year(date), "_",
+                                                       lubridate::month(date)))))
   # Long term data
-
-  ltr_df$month <- paste0(lubridate::year(ltr_df$event_date), "_",
-                          lubridate::month(ltr_df$event_date))
-
-#   listing.data$ltr.month <- as.numeric(as.factor(substr(
-#     listing.data$event.date, 1, 7))) - 8
-#   
-```
-# 
-# ### Standardize Property Types
-# 
-# &nbsp;
-# 
-# AirBNB units are classified into 19 different property type.
+  ltr_tdf <- ltr_tdf %>% 
+     mutate(trans_data = map(trans_data, 
+                             ~mutate(., month = paste0(lubridate::year(date), "_",
+                                                       lubridate::month(date)))))
+
+```
+
+### Standardize Property Types
+
+&nbsp;
+
+AirBNB units are classified into 19 different property type.
 The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type].
 For the sake of this analysis, we will collapse these twenty types into three types:
-#   
-# 1. **House**:  Includes properties labeled 'House' or 'Townhouse'
-# 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
-# 3.
+
+1. **House**:  Includes properties labeled 'House' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
+3.
 **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
-# 
-# Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
-#   
-# 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
-# 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-# 3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
-# 
-# Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
+
+Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
+
+1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
+3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+
+Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.
 This is most apparent when talking about apartment dwellings.
@@
 Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
-# 
-# We then create a new variable in each dataset and give each one of the three categories discussed above.
-# 
-# ```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Short Term data  
-# 
-#   str_df$type <- 'Other'
-#   str_df$type[str_df$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
-#   str_df$type[str_df$property.type %in% c('House', 'Townhouse')] <- 'House'
-# 
-#  # Long Term data  
-# 
-#   ltr_df$type <- 'Other'
-#   ltr_df$type[ltr_df$property.type %in% c('Duplex', 'House',
-#                                            'Terrace', 'Townhouse')] <- 'House'
-#   ltr_df$type[ltr_df$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
-# 
-# ```
-# 
-# As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
+
+We then create a new variable in each dataset and give each one of the three categories discussed above.
+
+```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Short Term data
+
+  str_tdf <- str_tdf %>%
+    dplyr::mutate(type = 'Other')
+  str_tdf$type[str_tdf$property_type %in% 
+               c('Apartment', 'Condominium', 'Loft')] <- 'Apartment'
+  str_tdf$type[str_tdf$property_type %in% c('House', 'Townhouse', 'Villa')] <- 'House'
+
+  # Long Term data
+
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::mutate(type = 'Other')
+  ltr_tdf$type[ltr_tdf$property_type %in% c('Duplex', 'House',
+                                             'Terrace', 'Townhouse', 'Villa')] <- 'House'
+  ltr_tdf$type[ltr_tdf$property_type %in% c('Studio', 'Unit')] <- 'Apartment'
+
+```
+
+As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.
 Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.
 As a result, we remove the 'Others' from both the Airbnb and the long term rental data.
-# 
-# ```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-# 
-#   # Create Airbnb plot
-# 
-#   str.types <- ggplot(str_df, aes(x=type)) + 
-#     geom_bar(color=str_col, fill=str_col) +
-#     xlab('\nProperty Type\n') + 
-#     ggtitle('\nShort Term Rentals\n')  +
-#     ylab('# of Properties\n') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-# 
-#   # Create long term rental plot
-# 
-#   ltr.types <- ggplot(ltr_df, aes(x=type)) + 
-#     geom_bar(color=ltr_col, fill=ltr_col) +
-#     xlab('\nProperty Type\n') + 
-#     ggtitle('\nLong Term Rentals\n')  +
-#     ylab('# of Properties\n') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-# 
-#   
-#   
-#   # Output plots
+
+```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+   # Create Airbnb plot
+
+   str_types <- ggplot(str_tdf, aes(x=type)) + 
+     geom_bar(color=str_col, fill=str_col) +
+     xlab('\nProperty Type\n') + 
+     ggtitle('\nShort Term Rentals\n')  +
+     ylab('# of Properties\n') +
+     theme(plot.title = element_text(hjust = 0.5))
+
+  # Create long term rental plot
+
+  ltr_types <- ggplot(ltr_tdf, aes(x=type)) +
+    geom_bar(color=ltr_col, fill=ltr_col) +
+    xlab('\nProperty Type\n') +
+    ggtitle('\nLong Term Rentals\n')  +
+    ylab('# of Properties\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  str_types
+  ltr_types
+
+  # Output plots
   # png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280,
   #     bg='transparent')
-#     ggMultiPlots(str.types, ltr.types, cols=2)
+  #  ggMultiPlots(str_types, ltr_types, cols=2)
   # dev.off()
@@
 #   save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))
-#   
-# ```
-# 
-# ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-# 
-#   str_df <- subset(str_df, type != 'Other')
-#   ltr_df <- subset(ltr_df, type != 'Other')
-#   
-#   # Count Cleaning
-#   countCleaning('property.type')
-# 
-# ```
-# 
-# Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
-# 
-# 1. **Entire Home/Apt**: The entire home or apartment is available
-# 2. **Private Room**: One room within a house or apartment is available
-# 3. **Shared Room**: A bed within a room shared by another occupant(s) is available
-# 
-# As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt.
+
+```
+
+```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+   str_tdf <- str_tdf %>% dplyr::filter(type != 'Other')
+   ltr_tdf <- ltr_tdf %>% dplyr::filter(type != 'Other')
+
+   # Count Cleaning
+   countCleaning('property.type')
+
+```
+
+Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+
+1. **Entire Home/Apt**: The entire home or apartment is available
+2. **Private Room**: One room within a house or apartment is available
+3. **Shared Room**: A bed within a room shared by another occupant(s) is available
+
+As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt.
 Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable.
-# 
-# ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-# 
-#   # Fix data types and names
-#   str_df$listing.type <- as.character(str_df$listing.type)
-#   str_df$listing.type[str_df$listing.type == 'Entire home/apt'] <- 'Entire home'
-# 
-#   list.types <- ggplot(str_df, aes(x=listing.type)) + 
-#       geom_bar(color=str_col, fill=str_col) +
-#       xlab('\nListing Type\n') + 
-#       ggtitle('\nShort Term Rentals by Listing Type\n')  +
-#       ylab('# of Properties\n') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-#   
+
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+
+   # Fix data types and names
+   str_tdf <- str_tdf %>%
+     dplyr::mutate(listing_type = as.character(listing_type),
+                   listing_type = if_else(listing_type == 'Entire home/apt', 
+                                          'Entire home', listing_type))
+
+   list_types <- ggplot(str_tdf, aes(x=listing_type)) + 
+      geom_bar(color=str_col, fill=str_col) +
+      xlab('\nListing Type\n') +
+      ggtitle('\nShort Term Rentals by Listing Type\n')  +
+      ylab('# of Properties\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
   # # Make Plot
@@
   # save(list.types, file=paste0(fig.path, 'listtypes.RData'))
-#   
-#   
-# ```
-# 
-# ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   str_df <- str_df[str_df$listing.type == 'Entire home', ]
-#   
-#   # Count cleaning 
-#   countCleaning('listing.type')
-#   
-# ```
-# 
-# ## Structural Characteristics
-# 
-# &nbsp;
-# 
-# In this section we transform and filter based on the structural characteristics of the properties. 
-# 
-# ### Fix Boolean Variables
-# 
-# Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
-# 
-# ```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   ltr_df$has.study <- ifelse(ltr_df$has.study == 'True', 1, 0)
-#   ltr_df$has.courtyard <- ifelse(ltr_df$has.courtyard == 'True', 1, 0)
-#   ltr_df$has.aircon <- ifelse(ltr_df$has.aircon == 'True', 1, 0)
-#   ltr_df$has.balcony <- ifelse(ltr_df$has.balcony == 'True', 1, 0)
-#   ltr_df$has.garage <- ifelse(ltr_df$has.garage == 'True', 1, 0)
-# 
-# ```
-# 
-# &nbsp;
-# 
-# ### Bedrooms
-# 
-# We start by looking at bedrooms.
+
+```
+
+```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf <- str_tdf %>% 
+    dplyr::filter(listing_type == 'Entire home')
+
+  # Count cleaning
+  countCleaning('listing_type')
+
+```
+
+## Structural Characteristics
+
+&nbsp;
+
+In this section we transform and filter based on the structural characteristics of the properties.
+
+### Bedrooms
+
+We start by looking at bedrooms.
 We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
@@
 From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
-# 
-# ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Remove missing and data errors
-# 
-#   # Long term data
-#   ltr_df <- ltr_df[!is.na(ltr_df$bedrooms), ]
-#   ltr_df <- ltr_df[ltr_df$bedrooms <= 10, ]
-# 
-#   # Short term data
-#   str_df <- str_df[!is.na(str_df$bedrooms), ]
-#   str_df <- str_df[str_df$bedrooms <= 10, ]
-# 
-# ```
-# 
-# ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-# 
-#  # Build long term bar plot
-# 
-#    ltrbed <- ggplot(ltr_df, aes(x=bedrooms)) + 
-#     geom_bar(fill=ltr_col, color=ltr_col) +
-#     facet_wrap(~type,scales='free_y') +
-#     scale_x_continuous(labels=1:10, breaks=1:10)+
-#     xlab('\nBedrooms\n') +
-#     scale_y_continuous(labels=c(0,10000,20000), 
-#                        breaks=c(0,10000,20000))+
-#     ylab('') +
-#     ggtitle('Bedrooms in Long Term Rentals') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-#  
-#  # Build short term bar plot
-# 
-#   strbed <- ggplot(str_df, aes(x=bedrooms)) + 
-#     geom_bar(fill=str_col, color=str_col) +
-#     facet_wrap(~type,scales='free_y') +
-#     scale_x_continuous(labels=0:10, breaks=0:10) +
-#     xlab('\nBedrooms\n') +
-#     ylab('') +
-#     ggtitle('Bedrooms in Short Term Rentals') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-#  
+
+```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Remove missing and data errors
+
+   # Long term data
+   ltr_tdf <- ltr_tdf %>%
+     dplyr::filter(!is.na(bedrooms)) %>%
+     dplyr::filter(bedrooms <= 10)
+
+   # Short term data
+   str_tdf <- str_tdf %>%
+     dplyr::filter(!is.na(bedrooms)) %>%
+     dplyr::filter(bedrooms <= 10)
+
+```
+
+```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+  # Build long term bar plot
+
+    ltrbed <- ggplot(ltr_tdf, aes(x=bedrooms)) + 
+     geom_bar(fill=ltr_col, color=ltr_col) +
+     facet_wrap(~type,scales='free_y') +
+     scale_x_continuous(labels=1:10, breaks=1:10)+
+     xlab('\nBedrooms\n') +
+     scale_y_continuous(labels=c(0,10000,20000), 
+                        breaks=c(0,10000,20000))+
+     ylab('') +
+     ggtitle('Bedrooms in Long Term Rentals') +
+     theme(plot.title = element_text(hjust = 0.5))
+
+  # Build short term bar plot
+
+   strbed <- ggplot(str_tdf, aes(x=bedrooms)) + 
+     geom_bar(fill=str_col, color=str_col) +
+     facet_wrap(~type,scales='free_y') +
+     scale_x_continuous(labels=0:10, breaks=0:10) +
+     xlab('\nBedrooms\n') +
+     ylab('') +
+     ggtitle('Bedrooms in Short Term Rentals') +
+     theme(plot.title = element_text(hjust = 0.5))
+
 #   # Make Plot
@@
 #   save(strbed, file=paste0(fig.path, 'strbed.RData'))
-# 
-# ```
-# 
-# For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
+
+```
+
+For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.
 We filter the data accordingly.
@@
 We convert the 0 bed short term units to 1 bed units.
-# 
-# ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Remove all with more than 4 beds
-# 
-#   str_df <- str_df[str_df$bedrooms < 5, ]
-#   ltr_df <- ltr_df[ltr_df$bedrooms < 5, ]
-# 
-#  # Remove apartments with more than 3
-#   
-#   str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
-#   ltr.id <- which(ltr_df$bedrooms > 3 & ltr_df$type =='Apartment')
-# 
-#   if(length(str.id) > 0) str_df <- str_df[-str.id, ]
-#   if(length(ltr.id) > 0) ltr_df <- ltr_df[-ltr.id, ]
-# 
-#   # Convert 0 Bed to 1 Bed  
-#   str_df$bedrooms[str_df$bedrooms == 0] <- 1
-#   
-#   # Count Data Cleaning
-#   countCleaning('bedrooms')
-# 
-# ```
-# 
-# ### Bathrooms
-# 
-# We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.  
-# 
-# ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Remove missing data
-#   
-#   ltr_df <- ltr_df[!is.na(ltr_df$baths), ]
-#   str_df <- str_df[!is.na(str_df$baths), ]
-# 
-# ```
-# 
-# ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-# 
-#  # Build long term plot
-# 
-#   ltbath <- ggplot(ltr_df, aes(x=baths)) + 
-#     geom_bar(fill=ltr_col, color=ltr_col) +
-#     facet_wrap(~type) +
-#     scale_x_continuous(labels=1:8, breaks=1:8)+
-#     xlab('\nBathrooms\n') +
-#     ylab('') + 
-#     ggtitle('Bathrooms in Long Term Rentals') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-# 
-#  # Build short term plot 
-# 
-#   stbath <- ggplot(str_df, aes(x=baths)) + 
-#     geom_bar(fill=str_col, color=str_col) +
-#     facet_wrap(~type, scales='free_y') +
-#     scale_x_continuous(labels=0:8, breaks=0:8)+
-#     xlab('\nBathrooms\n') +
-#     ylab('') + 
-#     ggtitle('Bathrooms in Short Term ltrals') +
-#     theme(plot.title = element_text(hjust = 0.5)) 
-#  
+
+```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Remove all with more than 4 beds for house, 3 beds for apt and convert studio to 1 bed
+
+   str_df <- str_tdf %>% 
+     dplyr::filter(bedrooms < 5) %>%
+     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
+     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1L, bedrooms))
+
+   ltr_df <- ltr_tdf %>% 
+     dplyr::filter(bedrooms < 5) %>%
+     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
+     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1, bedrooms))
+
+ # Count Data Cleaning
+ countCleaning('bedrooms')
+
+```
+
+### Bathrooms
+
+We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.
+
+```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Remove missing data
+  ltr_tdf <- ltr_tdf %>% dplyr::filter(!is.na(baths))
+  str_tdf <- str_tdf %>% dplyr::filter(!is.na(baths))
+
+```
+
+```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+  # Build long term plot
+
+   ltbath <- ggplot(ltr_tdf, aes(x=baths)) + 
+     geom_bar(fill=ltr_col, color=ltr_col) +
+     facet_wrap(~type) +
+     scale_x_continuous(labels=1:8, breaks=1:8)+
+     xlab('\nBathrooms\n') +
+     ylab('') +
+     ggtitle('Bathrooms in Long Term Rentals') +
+     theme(plot.title = element_text(hjust = 0.5))
+
+ # Build short term plot
+
+  stbath <- ggplot(str_tdf, aes(x=baths)) +
+    geom_bar(fill=str_col, color=str_col) +
+    facet_wrap(~type, scales='free_y') +
+    scale_x_continuous(labels=0:8, breaks=0:8)+
+    xlab('\nBathrooms\n') +
+    ylab('') +
+    ggtitle('Bathrooms in Short Term ltrals') +
+    theme(plot.title = element_text(hjust = 0.5))
+
 #  # Make Plots  
@@
 #   save(stbath, file=paste0(fig.path, 'strbath.RData'))
-#  
-# ```
-# 
-# Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
+
+```
+
+Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly.
 A few short term properties state no baths, which is likely an error so we remove these as well.
@@
 We round the baths up to whole integers.
-# 
-# ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Filter by bath count
-# 
-#   # Short term data
-#   str_df <- str_df[str_df$baths < 4, ]
-#   str_df <- str_df[str_df$baths > 0, ]
-# 
-#   # Long term data
-#   ltr_df <- ltr_df[ltr_df$baths < 4, ]
-#   
-#  # Round baths up  
-# 
-#   str_df$baths <- round(str_df$baths + .01, 0)
-# 
-#   # Count cleaning
-#   countCleaning('baths')
-#   
-# ```
-# 
-# ### Bed/Bath Combination
-# 
-# In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
+
+```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf <- str_tdf %>%
+    dplyr::mutate(bathrooms = round(bathrooms + .01, 0)) %>%
+    dplyr::filter(bathrooms < 4 & bathrooms > 0)
+
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::rename(bathrooms = baths) %>%
+    dplyr::filter(bathrooms < 4 & bathrooms > 0)
+
+   # Count cleaning
+   countCleaning('baths')
+
+```
+
+### Bed/Bath Combination
+
+In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
 In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
 As a result we examine the combinations of the two.
-# 
-# ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Create combination variable
-# 
-#   ltr_df$bedbath <- paste0(ltr_df$bedrooms, '..', ltr_df$baths)
-#   str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)
-# 
-# ```
-# 
-# ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-# 
-#  # Make long term plot
-# 
-#   ltbb <- ggplot(ltr_df, aes(x=bedbath)) + 
-#     geom_bar(fill=ltr_col, color=ltr_col) +
-#     xlab('\nBed/Bath Combo\n') +
-#     ylab('Number of Properties\n') +
-#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-#     ggtitle('Long Term Rentals') + 
-#     facet_wrap(~type, scales='free_y')+
-#     theme(plot.title = element_text(hjust = 0.5))
-# 
-#  # Make short term plots
-# 
-#   stbb <- ggplot(str_df, aes(x=bedbath)) +
-#     geom_bar(fill=str_col, color=str_col) + 
-#     xlab('\nBed/Bath Combo\n') +
-#     ylab('Number of Properties\n') +
-#     ggtitle('Short Term Rentals') + 
-#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-#     facet_wrap(~type, scales='free_y')+
-#     theme(plot.title = element_text(hjust = 0.5))
-# 
+
+```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Create combination variable
+  str_tdf <- str_tdf %>% 
+    dplyr::mutate(bedbath = paste0(bedrooms, "_", bathrooms))
+
+  ltr_tdf <- ltr_tdf %>% 
+    dplyr::mutate(bedbath = paste0(bedrooms, "_", bathrooms))
+
+```
+
+```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+ # Make long term plot
+
+  ltbb <- ggplot(ltr_tdf, aes(x=bedbath)) +
+    geom_bar(fill=ltr_col, color=ltr_col) +
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    ggtitle('Long Term Rentals') +
+    facet_wrap(~type, scales='free_y')+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ # Make short term plots
+
+  stbb <- ggplot(str_tdf, aes(x=bedbath)) +
+    geom_bar(fill=str_col, color=str_col) +
+    xlab('\nBed/Bath Combo\n') +
+    ylab('Number of Properties\n') +
+    ggtitle('Short Term Rentals') +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+    facet_wrap(~type, scales='free_y')+
+    theme(plot.title = element_text(hjust = 0.5))
+
 #  # Make Plots  
@@
 #       bg='transparent')
-#   
+
 #     ggMultiPlots(ltbb, stbb, cols=1)
-# 
+
 #   dev.off()
-#   
+
 #   save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
 #   save(stbb, file=paste0(fig.path, 'strbb.RData'))
-# 
-#     
-# ```
-# 
-# From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.  
-# 
-# ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Set level of acceptable combinations
-# 
-#   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
-# 
-#  # Filter data
-# 
-#   ltr_df <- ltr_df[ltr_df$bedbath %in% acc.bb, ]
-#   str_df <- str_df[str_df$bedbath %in% acc.bb, ]
-# 
-#  # Count Cleaning
-#   
-#   countCleaning('bedbath')
-# 
-# ```
-# 
-# Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.
-We additionally create a product variable that splits the bed/bath by apartment and house.
-# 
-# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   # Re-order factors
-# 
-#   str_df$bedbath <- factor(str_df$bedbath, 
-#                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-#   ltr_df$bedbath <- factor(ltr_df$bedbath, 
-#                                levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
-# 
-#   # Add product as a variable
-#   
-#   str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
-#   ltr_df$product <- paste0(substr(ltr_df$type, 1, 1), ltr_df$bedbath)
-# 
-# ```
-# 
-# 
-# ## Rates and Rental values
-# 
-# We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data. 
-# 
-# ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   ltr_df <- ltr_df[!is.na(ltr_df$event.price), ]
-#   str_df <- str_df[!is.na(str_df$nightly.rate), ]
-#   
-# ```
-# 
-# Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
+
+```
+
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
+We filter the data to these combinations.
+We also combine type and bed bath combination to create a 'product'.
+
+```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ # Set level of acceptable combinations
+
+  acc_bb <- c('1_1', '2_1', '2_2', '3_1', '3_2', '4_2')
+
+ # Filter data
+  str_tdf <- str_tdf %>%
+    dplyr::filter(bedbath %in% acc_bb) %>%
+    dplyr::mutate(product = paste0(substr(type, 1, 1), "_", bedbath))
+
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::filter(bedbath %in% acc_bb) %>%
+    dplyr::mutate(product = paste0(substr(type, 1, 1), "_", bedbath))
+
+ # Count Cleaning
+
+  countCleaning('bedbath')
+
+```
+
+## Rates and Rental values
+
+We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data.
+
+```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ltr_tdf <- ltr_tdf %>% 
+     mutate(trans_data = map(trans_data, ~filter(., (date <= decision_date - 1) & 
+                                                     date >= decision_date - 365)))
+
+   ltr_tdf <- ltr_tdf %>% dplyr::filter(!is.na(price))
+   str_tdf <- str_tdf %>% dplyr::filter(!is.na(price))
+
+   str_df <- str_df[!is.na(str_df$nightly.rate), ]
+
+```
+
+TODO:  At the end, filter all that have no observations in teh list-cols
+
+Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
 # 

### 2018-05-08 functions/abb_Functions.R

@@ -309,28 +309,22 @@ setCleanCount <- function(){
 countCleaning <- function(operation){
 
   # Count recent cuts  
-  str_cut <- str_run_total - nrow(str_df)
-  daily_cut <- daily_run_total - nrow(daily_df)
-  ltr_cut <- ltr_run_total - nrow(ltr_df)
-  list_cut <- list_run_total - nrow(list_df)
+  str_cut <- str_run_total - nrow(str_tdf)
+  ltr_cut <- ltr_run_total - nrow(ltr_tdf)
   
   # Build new dataframe
   new_df <- data.frame(operation=operation,
                        str=str_cut,
-                       daily=daily_cut,
-                       ltr=ltr_cut,
-                       list=list_cut)
+                       ltr=ltr_cut)
   
   # Add to existing DF
   comb_df <- rbind(clean_count, new_df)
   
   # Assign initial values to globalEnv
   assign('clean_count', comb_df, envir=.GlobalEnv)
-  assign('str_run_total', nrow(str_df), envir=.GlobalEnv)
-  assign('ltr_run_total', nrow(ltr_df), envir=.GlobalEnv)
-  assign('list_run_total', nrow(list_df), envir=.GlobalEnv)
-  assign('daily_run_total', nrow(daily_df), envir=.GlobalEnv)
-  
+  assign('str_run_total', nrow(str_tdf), envir=.GlobalEnv)
+  assign('ltr_run_total', nrow(ltr_tdf), envir=.GlobalEnv)
+
 }
 
 ### Cross impute rates and rents ---------------------------------------------------------

### 2018-05-08 scripts/3_data_prep.Rmd
Updating data prep up to revenue plots

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(eval=TRUE)
+```
 
@@
   ltr_tdf <- ltr_tdf %>% 
-     mutate(trans_data = map(trans_data, ~filter(., (date <= decision_date - 1) & 
-                                                     date >= decision_date - 365)))
-
-   ltr_tdf <- ltr_tdf %>% dplyr::filter(!is.na(price))
-   str_tdf <- str_tdf %>% dplyr::filter(!is.na(price))
-
-   str_df <- str_df[!is.na(str_df$nightly.rate), ]
-
-```
-
-TODO:  At the end, filter all that have no observations in teh list-cols
+     mutate(trans_data = map(trans_data, ~filter(., !is.na(price)))) %>%
+     filter(map(trans_data, ~nrow(.)) > 0)
+
+  str_tdf <- str_tdf %>% 
+     mutate(daily_data = map(daily_data, ~filter(., !is.na(price)))) %>%
+     filter(map(daily_data, ~nrow(.)) > 0) %>%
+     filter(!is.na(nightly_rate))
+
+```
 
 Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
-# 
-# ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   # Property level data
-# 
-#   str_df$average.daily.rate <- str_df$average.daily.rate * exch.rate
-#   str_df$nightly.rate <- str_df$nightly.rate * exch.rate
-#   str_df$weekly.rate <- str_df$weekly.rate * exch.rate
-#   str_df$monthly.rate <- str_df$monthly * exch.rate
-#   
-#   # Daily data
-#   
-#   daily_df$price <- daily_df$price * exch.rate
-# 
-# ```
-# 
-# Next we extract all of the daily reservation data for the reserved nightly.
+
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Property level data
+  str_tdf <- str_tdf %>%
+    dplyr::mutate_at(vars(monthly_rate, weekly_rate, nightly_rate, 
+                          avg_nightly_rate, cleaning_fee), 
+                     .funs=function(x) x*exch_rate)
+
+  # Nightly Data
+  str_tdf <- str_tdf %>%
+    mutate(daily_data = map(daily_data, ~mutate(., price = price * exch_rate)))
+
+```
+
+Next we extract all of the daily reservation data for the reserved nightly.
 From this information we calculate the median nightly reservation price for each property and append it to the property level data.
-# 
-# ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#    # Get all of the reservations
-#   resv.daily <- daily_df[daily_df$status == 'R', ]
-# 
-#   # Calculate the property specific median nightly rate
-#   med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
-#   
-#   # Add median rate to the property  
-#   str_df$med.rate <- med.daily$Var[match(str_df$property.id, med.daily$ID)] 
-#   
-#   # Remove those with no valid median rate
-#   str_df <- str_df[!is.na(str_df$med.rate), ]
-#    
-# ```
-# 
-# From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
+
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+   # Custom function
+   medReserved <- function(x){
+     median(x$price[x$status == 'R'])
+   }
+
+   str_tdf <- str_tdf %>%
+     dplyr::mutate(med_rate = unlist(map(daily_data, ~medReserved(.)))) %>%
+     dplyr::filter(!is.na(med_rate))
+
+```
+
+From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night.
 We filter the data accordingly.
-# 
-# ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   # ltr Plot
-#   
-#   ltr.plot <- ggplot(ltr_df, aes(x=event.price)) + 
-#     geom_density(fill=ltr_col, alpha=.8) +
-#     ylab('') +
-#     xlab('Weekly Rental') + 
-#     ggtitle('Long Term Rentals') + 
-#     scale_x_continuous(limits=c(0, 1500)) +
-#     theme(axis.title.y=element_blank(),
-#           axis.text.y=element_blank(),
-#           axis.ticks.y=element_blank()) +
-#     theme(plot.title = element_text(hjust = 0.5))
-# 
-# 
-#   # Nightly Rate plot
-#   rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
-#     geom_density(fill=str_col, alpha=.8) + 
-#     ylab('') +
-#     xlab('Nightly Rate') +
-#     ggtitle('Short Term Rentals') + 
-#     scale_x_continuous(limits=c(0, 600)) +
-#     theme(axis.title.y=element_blank(),
-#           axis.text.y=element_blank(),
-#           axis.ticks.y=element_blank()) +
-#     theme(plot.title = element_text(hjust = 0.5))
-# 
-# 
-# ```
-# 
-# ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # ltr Plot
+
+  ltr_price <- ggplot(ltr_tdf %>% tidyr::unnest(), aes(x=price)) +
+    geom_density(fill=ltr_col, alpha=.8) +
+    ylab('') +
+    xlab('Weekly Rental') +
+    ggtitle('Long Term Rentals') +
+    scale_x_continuous(limits=c(0, 1500)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank()) +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Nightly Rate plot
+  str_plot <- ggplot(str_tdf, aes(x=med_rate)) +
+    geom_density(fill=str_col, alpha=.8) +
+    ylab('') +
+    xlab('Nightly Rate') +
+    ggtitle('Short Term Rentals') +
+    scale_x_continuous(limits=c(0, 600)) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank()) +
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 # 
@@
 #   
-# ```
-# 
-# ```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   ## Filter the long term data
-# 
-#   ltr_df <- ltr_df[ltr_df$event.price >= 200 & 
-#                          ltr_df$event.price <= 1000, ]
-# 
-#   str_df <- str_df[str_df$med.rate >= 50 &
-#                          str_df$med.rate <= 500, ]
-# 
-#   # Count Cleaning
-#   countCleaning('rates.rents')
-#   
-# ```  
-# 
-# #### Observed Revenue
-# 
-# Our final data filtering considers the observed revenue of the properties.
+```
+
+```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+   ## Filter the long term data
+  ltr_tdf <- ltr_tdf %>% 
+     mutate(trans_data = map(trans_data, ~filter(., price >= 200 &
+                                                   price <= 1000))) %>%
+     filter(map(trans_data, ~nrow(.)) > 0)
+
+  str_tdf <- str_tdf %>% 
+    filter(., med_rate >= 50 & med_rate <= 500)
+
+   # Count Cleaning
+   countCleaning('rates_rents')
+
+```
+
+#### Observed Revenue
+
+Our final data filtering considers the observed revenue of the properties.
 For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.
@@
 To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
-# 
-# For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
+
+For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
 Using this data we sum up the total revenue from bookings.
 For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
-# 
-# Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
+
+Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
 Short term revenues range from neglible to highs of greater than \$80,000.
@@
 Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
-# 
-# ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
-# 
-#  # Compute bookings count
-# 
-#   str_df$bookings <- round(str_df$total.days * 
-#                                (1 - (str_df$block.rate + str_df$avail.rate)), 0)
-#  
-#  # Remove those with 0 
-# 
-#   str_df <- str_df[str_df$bookings > 0, ]
-# 
-#   str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
-#   ltr_df$gross.revenue <- ltr_df$event.price * (52 - ltr_df$dom / 7)
-#  
-#   str.small <- str_df[,c('baths', 'gross.revenue')]
-#   str.small$tenure <- 'short-term'
-#   ltr.small <- ltr_df[,c('baths', 'gross.revenue')]
-#   ltr.small$tenure <- 'long-term'
-#   all.small <- rbind(str.small, ltr.small)
-# 
-#   revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
-#     geom_density(alpha=.5) +
-#     scale_fill_manual(values=c(ltr_col, abb_col)) +
-#     scale_color_manual(values=c(ltr_col, abb_col)) +
-#     ggtitle('Annual Revenues by Tenure Type') +
-#     xlab('Annual Revenue') +
-#     scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-#                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-#     theme(legend.position='bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           axis.text.y = element_blank(),
-#           axis.ticks.y = element_blank(),
-#           axis.title.y=element_blank()) +
-#     coord_cartesian(xlim=c(0, 70000))
-#   
-# ```
-# 
-# ```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
+
+   # Compute bookings count and str revenue
+   countBookings <- function(x){
+     length(which(x$status == 'R'))
+   } 
+   makePotBookings <- function(x){
+     round(nrow(x) * (length(which(x$status == 'R')) / 
+                        length(which(x$status != 'B'))), 0)
+   }
+
+   str_tdf <- str_tdf %>%
+     mutate(bookings = unlist(map(daily_data, ~countBookings(.))),
+            pot_bookings = unlist(map(daily_data, ~makePotBookings(.))),
+            gross_revenue = bookings * med_rate,
+            pot_revenue = pot_bookings * med_rate)
+
+   # compute long term revenue
+   ltr_tdf <- ltr_tdf %>%
+     dplyr::mutate(trans_data = map(trans_data, 
+                                    ~mutate(., 
+                                            gross_revenue = price * (52 - dom / 7))))
+
+   # Add together for plotting
+   rev_df <- bind_rows(str_tdf %>% 
+                         dplyr::select(type, gross_revenue) %>%
+                         dplyr::mutate(tenure = 'str'),
+                       ltr_tdf %>%
+                         tidyr::unnest() %>%
+                         dplyr::select(type, gross_revenue) %>%
+                         dplyr::mutate(tenure = 'ltr'))
+
+   revdens <- ggplot(rev_df, 
+                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr_col, abb_col)) +
+    scale_color_manual(values=c(ltr_col, abb_col)) +
+    ggtitle('Annual Revenues by Tenure Type') +
+    xlab('Annual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000))
+
+   # Add together for plotting potential revenues
+   prev_df <- bind_rows(str_tdf %>% 
+                         dplyr::select(type, gross_revenue=pot_revenue) %>%
+                         dplyr::mutate(tenure = 'str'),
+                       ltr_tdf %>%
+                         tidyr::unnest() %>%
+                         dplyr::select(type, gross_revenue) %>%
+                         dplyr::mutate(tenure = 'ltr'))
+
+   prevdens <- ggplot(prev_df, 
+                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
+    geom_density(alpha=.5) +
+    scale_fill_manual(values=c(ltr_col, abb_col)) +
+    scale_color_manual(values=c(ltr_col, abb_col)) +
+    ggtitle('Annual Revenues by Tenure Type') +
+    xlab('Annual Revenue') +
+    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
+                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+    theme(legend.position='bottom',
+          legend.title = element_blank(),
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y=element_blank()) +
+    coord_cartesian(xlim=c(0, 70000))
+
+```
+
+```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 # 
@@
 #     countCleaning('revenue')
-#   
-# ```
-# 
-# ### Locations and Submarkets
-# 
-# Location is clearly an important determinant in both the short and long term rental markets.
+```
+
+### Locations and Submarkets
+
+Location is clearly an important determinant in both the short and long term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 # 
-# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+   save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
 #        beach.shp, core.suburbs, exch.rate, ltr_col, str_col, sa1s.shp, 

### 2018-05-08 scripts/3_data_prep.Rmd
Update to mapping.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(eval=TRUE)
+#knitr::opts_chunk$set(eval=TRUE)
 ```
@@
   library(xtable)
-  library(plyr)
   library(sp)
@@
   library(RColorBrewer)
-  library(Hmisc)
-  library(dplyr)
+  # library(Hmisc)
   library(multidplyr)
@@
   library(sf)
+
+  options(stringsAsFactors=FALSE)
 
@@
   # Remove missing data
-  ltr_tdf <- ltr_tdf %>% dplyr::filter(!is.na(baths))
-  str_tdf <- str_tdf %>% dplyr::filter(!is.na(baths))
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::rename(bathrooms = baths) %>%
+    dplyr::filter(!is.na(bathrooms))
+  str_tdf <- str_tdf %>% dplyr::filter(!is.na(bathrooms))
 
@@
 
-   ltbath <- ggplot(ltr_tdf, aes(x=baths)) + 
+   ltbath <- ggplot(ltr_tdf, aes(x=bathrooms)) + 
      geom_bar(fill=ltr_col, color=ltr_col) +
@@
 
-  stbath <- ggplot(str_tdf, aes(x=baths)) +
+  stbath <- ggplot(str_tdf, aes(x=bathrooms)) +
     geom_bar(fill=str_col, color=str_col) +
@@
   ltr_tdf <- ltr_tdf %>%
-    dplyr::rename(bathrooms = baths) %>%
     dplyr::filter(bathrooms < 4 & bathrooms > 0)
@@
 The plot below shows the three large submarkets (Inner, Middle and Outer).
-# 
-# ```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Convert shapefile to ggplot-able object
-#   
-#   # Fix lat/long
-#  
-#   # Limit to extent of data
-#   sub.table <- table(ltr_df$suburb)
-#   sub.table <- sub.table[sub.table != 0]
-#   
-#   # Clip to only those with a ltral observation
-#   study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
-#   
-#   # Convert to an outer bound with holes
+
+```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Convert shapefile to ggplot-able object
+
+   # Limit to extent of data
+   ltr_subs <- ltr_tdf %>%
+    dplyr::select(suburb) %>%
+    group_by(suburb) %>%
+    summarize(count=n())
+
+   # Clip to only those with a ltral observation
+   studysubs_sf <- sub_sf %>%
+     filter(NAME_2006 %in% ltr_subs$suburb)
+
+   # Convert to an outer bound with holes
+   ss_bound <- st_union(studysubs_sf)
+
    # ss.bound <- gUnaryUnion(study.suburbs)
@@
    #   match(subs$id, suburbs.shp@data$name_2006)]
-# 
-# ```
-# 
-# ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#  ## Build the map object
-# 
+
+```
+
+```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ ## Build the map object
+
 #    # Set colors
@@
 #    # Make map
-#   loc.map <- ggplot() +
-#     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-#     scale_fill_manual(values=g_cols, labels=c('Inner      ',
+#    ggplot(studysubs_sf) %>%
+#      geom_sf(aes(group=group, fill=suburbDesi))
+# 
+#    loc_map <- ggplot() +
+#      geom_polygon(data=studysubs_sf, 
+#                   aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
+# #     scale_fill_manual(values=g_cols, labels=c('Inner      ',
 #                                               'Middle      ',
@@
 #     
-# ```
-# 
-# It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+```
+# 
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
 Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
-# 
-# 1. Rural (Outer suburbs, not Beach)
-# 2. Suburban (Middle suburbs, not Beach)
-# 3. City (Inner Suburbs, not Beach, not Core)
-# 4. City-Core (Select inner suburbs with tourist activities and near CBD)
-# 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-# 
-# We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short and long term data.
@@
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-# 
-# We select the 18 suburbs below to represent the 'core' of the city.
+
+We select the 18 suburbs below to represent the 'core' of the city.
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
 All are well serviced by public transportation and possess abundant amenties for tourists.
-# 
-# ```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
-#                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
-#                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
-#                    'St Kilda West', 'West Melbourne', 'Windsor')
-# 
-# ```
-# 
-# We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
-# 
-# ```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Determine centroid of study area
-#  
-#   latMid <- median(str_df$latitude)
-#   longMid <- median(str_df$longitude)
-# 
-#  # Calculate Degress to Meters conversion 
-#  
-#   m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
-#   m.long = 111132.954 * cos (latMid)
-#   m.conv <- mean(m.lat, m.long)
-#  
-#  # Create the beach buffer  
-#   
-#   beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
-# 
-# ```
-# 
-# Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.  
-# 
-# ```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  ## Short term data  
-# 
-#   # Convert to point shapefile
-#   str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
-#                                                str_df$latitude),
-#                                          str_df,
-#                                          proj4string=CRS("+init=epsg:4283")) 
-# 
-#   # Add suburb name 
-#   spJoin <- over(str.prop.shp, suburbs.shp)
-#   str_df$suburb <- as.character(spJoin$name_2006)
-#   str_df$suburb[is.na(str_df$suburb)] <- 'missing'
-# 
-#   # Add suburb designation
-#   str_df$sub.class <- as.character(spJoin$suburbdesi)
-#   str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'
-#   
-#   # Add SA1 designation
-#   spJoin <- over(str.prop.shp, sa1s.shp)
-#   str_df$sa1 <- spJoin$sa1_main11
-#  
-#   ## Add Beach Designation
-#   spJoin <- over(str.prop.shp, beach.buffer)
-#   str_df$beach <- ifelse(is.na(spJoin), 0 ,1)
-#   
-#   # Remove those missing a suburb classification (out of area)
-#   str_df <- str_df[str_df$sub.class != 'missing', ]
-#   str_df <- str_df[str_df$sa1 != 'missing', ]
-# 
-# ```
-# 
-# ```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  ## Add the submarket designations
-# 
-#   # Add individual classes
-#   str_df$geo.mrkt <- 'rural'
-#   str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
-#   str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
-#   str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
-#   str_df$geo.mrkt[str_df$beach == 1] <- 'beach'
+
+```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  core_suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
+                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
+                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
+                    'St Kilda West', 'West Melbourne', 'Windsor')
+
+```
+
+We then apply a 500 meter buffer to the beach along Port Phillip Bay.
+
+```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Determine centroid of study area
+
+   lat_mid <- median(str_tdf$latitude)
+   long_mid <- median(str_tdf$longitude)
+
+ # Calculate Degress to Meters conversion
+
+   m_lat = 111132.954 - 559.822 * cos(2 * lat_mid) + 1.175 * cos(4 * lat_mid)
+   m_long = 111132.954 * cos (lat_mid)
+   m_conv <- mean(c(m_lat, m_long))
+
+  # Create the beach buffer
+
+  beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv))
+
+```
+
+Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
+
+```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+ ## Short term data
+
+ # Convert to point shapefile
+   str_tdf <- st_as_sf(str_tdf,
+                       coords = c('longitude', 'latitude'),
+                       crs = 4283)
+
+   ltr_tdf <- st_as_sf(ltr_tdf %>% dplyr::filter(!is.na(latitude)),
+                       coords = c('longitude', 'latitude'),
+                       crs = 4283)
+
+    str_tdf <- st_join(str_tdf, 
+                       sub_sf %>% 
+                        dplyr::select(suburb = NAME_2006,
+                                      sub_des = suburbDesi,
+                                      geometry)) %>%
+    dplyr::filter(!is.na(sub_des))
+
+    ltr_tdf <- st_join(ltr_tdf %>%
+                         dplyr::select(-suburb), 
+                       sub_sf %>% 
+                        dplyr::select(suburb = NAME_2006,
+                                      sub_des = suburbDesi,
+                                      geometry)) %>%
+    dplyr::filter(!is.na(sub_des))
+
+    sub_str <- str_tdf %>% 
+      dplyr::select(suburb, -geometry) %>% 
+      as.tibble() %>%
+      dplyr::group_by(suburb) %>% 
+      dplyr::summarize(count=n())
+
+    sub_ltr <- ltr_tdf %>% 
+      dplyr::select(suburb, -geometry) %>% 
+      as.tibble() %>%
+      dplyr::group_by(suburb) %>% 
+      dplyr::summarize(count=n())
+
+    sub_all <- sub_ltr %>%
+      dplyr::inner_join(sub_str, by='suburb')
+
+    str_tdf <- str_tdf %>%
+      dplyr::filter(suburb %in% sub_all$suburb)
+
+    ltr_tdf <- ltr_tdf %>%
+      dplyr::filter(suburb %in% sub_all$suburb)
+
+    str_tdf <- st_join(str_tdf, 
+                       sa1_sf %>%
+                         dplyr::select(sa1=SA1_MAIN11,
+                                       geometry)) %>%
+    dplyr::filter(!is.na(sa1))
+
+        ltr_tdf <- st_join(ltr_tdf, 
+                       sa1_sf %>%
+                         dplyr::select(sa1=SA1_MAIN11,
+                                       geometry)) %>%
+    dplyr::filter(!is.na(sa1))
+
+   str_tdf <- st_join(str_tdf, 
+                       beach_buffer %>%
+                         dplyr::select(beach=id,
+                                       geometry)) %>%
+      mutate(beach = ifelse(is.na(beach), 0, beach))
+
+    ltr_tdf <- st_join(ltr_tdf, 
+                       beach_buffer %>%
+                         dplyr::select(beach=id,
+                                       geometry)) %>%
+    mutate(beach = ifelse(is.na(beach), 0, beach))
+
+```
+
+```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ## Add the submarket designations
+
+   # Add individual classes
+   str_tdf$geo_mrkt <- 'rural'
+   str_tdf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
+   str_tdf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
+   str_tdf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
+   str_tdf$geo_mrkt[str_tdf$beach == 1] <- 'beach'
 #   
 #   # Order the factors properly
-#   str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
-#                               levels=c('city-core', 'city', 'suburban', 
-#                                         'rural', 'beach'))
-#   
-# ```
-# 
-# Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.
-Half of these do, however, have a lat/long value for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.
-For those without either (3% of the total) we remove them from the dataset at this point.
-# 
-# ```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  # Label those missing lat/long  
-# 
-#   miss.LL <- which(is.na(ltr_df$latitude))  
-# 
-#  # Create a field to indicate the approximate matches  
-# 
-#   ltr_df$miss.LL <- 0
-#   ltr_df$miss.LL[miss.LL] <- 1
-# 
-#  # Apply approximate match    
-# 
-#   ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
-#   ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]
-# 
-#  # Remove those still missing latitude data   
-# 
-#   ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]
-# 
-# ```
-# 
-# Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.  
-# 
-# ```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   # Long term data  
-# 
-#   # Convert to point shapefile
-# 
-#   ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
-#                                                ltr_df$latitude),
-#                                          ltr_df,
-#                                          proj4string=CRS("+init=epsg:4283")) 
-# 
-#   # Add suburb name 
-#   
-#   spJoin <- over(ltr.prop.shp, suburbs.shp)
-#   ltr_df$suburb <- as.character(spJoin$name_2006)
-#   ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'
-# 
-#   # Add suburb designation
-#   
-#   ltr_df$sub.class <- as.character(spJoin$suburbdesi)
-#   ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'
-#   
-#   # Add SA1 designation
-#   
-#   spJoin <- over(ltr.prop.shp, sa1s.shp)
-#   ltr_df$sa1 <- spJoin$sa1_main11
-#  
-#   ## Add Beach Designation
-#   
-#   spJoin <- over(ltr.prop.shp, beach.buffer)
-#   ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)
-#   
-#   # Remove those missing a suburb classification (out of area)
-#   
-#   ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
-#   ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]
-# 
-# ```
-# 
-# ```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  ## Add the submarket designations
-# 
-#   # Add individual classes
-#   ltr_df$geo.mrkt <- 'rural'
-#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
-#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
-#   ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
-#   ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'
+    str_tdf$geo_mrkt <- factor(str_tdf$geo_mrkt,
+                               levels=c('city-core', 'city', 'suburban',
+                                        'rural', 'beach'))
+
+       # Add individual classes
+   ltr_tdf$geo_mrkt <- 'rural'
+   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Middle'] <- 'suburban'
+   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Inner'] <- 'city'
+   ltr_tdf$geo_mrkt[ltr_tdf$suburb %in% core_suburbs] <- 'city-core'
+   ltr_tdf$geo_mrkt[ltr_tdf$beach == 1] <- 'beach'
 #   
 #   # Order the factors properly
-#   ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
-#                               levels=c('city-core', 'city', 'suburban', 
-#                                         'rural', 'beach'))
-#   
-#   # Count Cleaning
-#   countCleaning('location')
-#   
-# ```
-# 
-# The location of the short and long term rentals, colored by submarket, are shown below
-# 
-# ```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+   ltr_tdf$geo_mrkt <- factor(ltr_tdf$geo_mrkt,
+                               levels=c('city-core', 'city', 'suburban',
+                                        'rural', 'beach'))
+ # Count Cleaning
+   countCleaning('location')
+
+```
+
+The location of the short and long term rentals, colored by submarket, are shown below
+
+#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 # 

### 2018-05-09 scripts/3_data_prep.Rmd
Reorder and clean up past Location

@@
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
+  library(tidyverse)
+  library(sf)
   library(geosphere)
   library(ggmap)
-  library(xtable)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  # library(Hmisc)
   library(multidplyr)
-  library(lubridate)
-  library(tidyverse)
-  library(sf)
+  # library(lubridate)
+  # library(spdep)
+  # library(maptools)
+  # library(ggplot2)
 
@@
 ```
-
-We then set the paths to the data and the code, conditional on which of the authors is running the analysis.
 
@@
   source(file.path(code_path, 'functions', 'abb_Functions.R'))
-
-#
-#  # Other custom files
-# 
-#   if(offline){
-# 
-#     source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
-#     source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
-#     source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
-#     source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))
-#     
-#   } else {
-#     
-#   source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
-#                 '/master/ggPlotTools.R'))
-#   source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
-#                 '/master/dataMungeTools.R'))
-#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-#                 '/master/spatialLogitModels.R'))
-#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-#                 '/master/point2surface_Tools.R'))
-# 
-#   }
+  source(file.path(code_path, 'functions', 'geom_sf.R'))
+
 ```
@@
  # Set all colors
-
-  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
-                     'ebisu', 'tirol', 'foggy', 'hof')
-  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
-               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255),
-               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
-               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
-               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
+  col_df <- data.frame(names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 
+                               'beach', 'ebisu', 'tirol', 'foggy', 'hof'),
+                       rgb = c(rgb(250,88,99, maxColorValue=255), 
+                               rgb(139,14,82, maxColorValue=255),
+                               rgb(0,117,140, maxColorValue=255), 
+                               rgb(4,211,191, maxColorValue=255),
+                               rgb(77,226,110, maxColorValue=255), 
+                               rgb(252,179,14, maxColorValue=255),
+                               rgb(249,177,139, maxColorValue=255), 
+                               rgb(191,166,100, maxColorValue=255),
+                               rgb(156,161,155, maxColorValue=255), 
+                               rgb(86,94,97, maxColorValue=255)))
 
  # Set specific colors
-
-  str_col <- abb_col[1]
-  ltr_col <- abb_col[3]
+  str_col <- col_df$rgb[1]
+  ltr_col <- col_df$rgb[3]
+  sm_col <- col_df$rgb[c(2,4,5,8,6)]
 
@@
 
-```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
-We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]  After we load each we convert the names of the data fields to lower case for easier use in future coding.
-
-```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]
+
+```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
-
-   # Create Airbnb plot
-
-   str_types <- ggplot(str_tdf, aes(x=type)) + 
+```{r plot_str_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}
+
+   ggplot(str_tdf, aes(x=type)) + 
      geom_bar(color=str_col, fill=str_col) +
@@
 
+```
+
+```{r plot_ltr_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}
+
   # Create long term rental plot
 
-  ltr_types <- ggplot(ltr_tdf, aes(x=type)) +
+  ggplot(ltr_tdf, aes(x=type)) +
     geom_bar(color=ltr_col, fill=ltr_col) +
@@
 
-  str_types
-  ltr_types
-
-  # Output plots
-  # png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280,
-  #     bg='transparent')
-  #  ggMultiPlots(str_types, ltr_types, cols=2)
-  # dev.off()
-# 
-#   save(str.types, file=paste0(fig.path, 'strtypes.RData'))
-#   save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))
-
-```
-
-```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+```
+
+```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}
 
@@
    # Count Cleaning
-   countCleaning('property.type')
+   countCleaning('property_type')
 
@@
 
-```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
+```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}
 
@@
 
-   list_types <- ggplot(str_tdf, aes(x=listing_type)) + 
+   ggplot(str_tdf, aes(x=listing_type)) + 
       geom_bar(color=str_col, fill=str_col) +
@@
 
-  # # Make Plot
-  # png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280,
-  #     bg='transparent')
-  # 
-  #   list.types
-  # 
-  # dev.off()
-  # 
-  # save(list.types, file=paste0(fig.path, 'listtypes.RData'))
-
-```
-
-```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```
+
+```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
-  # Build long term bar plot
-
-    ltrbed <- ggplot(ltr_tdf, aes(x=bedrooms)) + 
+```{r plot_ltr_bed, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+   ggplot(ltr_tdf, aes(x=bedrooms)) + 
      geom_bar(fill=ltr_col, color=ltr_col) +
@@
 
-  # Build short term bar plot
-
-   strbed <- ggplot(str_tdf, aes(x=bedrooms)) + 
+```
+
+```{r plot_str_bed, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+   ggplot(str_tdf, aes(x=bedrooms)) + 
      geom_bar(fill=str_col, color=str_col) +
@@
 
-#   # Make Plot
-#   png(file=paste0(fig.path, 'dataclean_bedcount.png'), width = 480, height = 280, 
-#       bg='transparent')
-#     ggMultiPlots(strbed, ltrbed, cols=1)
-#   dev.off()
-#   
-#   save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
-#   save(strbed, file=paste0(fig.path, 'strbed.RData'))
-
 ```
@@
 
-```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Remove all with more than 4 beds for house, 3 beds for apt and convert studio to 1 bed
-
-   str_df <- str_tdf %>% 
+```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Remove all with more than 4 beds for house, 3 beds for apt 
+  str_tdf <- str_tdf %>% 
     dplyr::filter(bedrooms < 5) %>%
-     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
-     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1L, bedrooms))
-
+    dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) 
   ltr_df <- ltr_tdf %>% 
     dplyr::filter(bedrooms < 5) %>%
-     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
-     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1, bedrooms))
+    dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4))
+
+  # Convert any studio to 1 bedrooms
+  str_tdf$bedrooms <- ifelse(str_tdf$bedrooms == 0, 1L, str_tdf$bedrooms)
+  ltr_tdf$bedrooms  <- ifelse(ltr_tdf$bedrooms == 0, 1, ltr_tdf$bedrooms)
 
@@
 
-```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Remove missing data
+```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  if ('baths' %in% names(ltr_tdf)) ltr_tdf <- ltr_tdf %>% rename(bathrooms = baths)
+
   ltr_tdf <- ltr_tdf %>%
-    dplyr::rename(bathrooms = baths) %>%
     dplyr::filter(!is.na(bathrooms))
-  str_tdf <- str_tdf %>% dplyr::filter(!is.na(bathrooms))
-
-```
-
-```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
-  # Build long term plot
-
-   ltbath <- ggplot(ltr_tdf, aes(x=bathrooms)) + 
+
+  str_tdf <- str_tdf %>% 
+    dplyr::filter(!is.na(bathrooms))
+
+```
+
+```{r plot_ltr_bath, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+   ggplot(ltr_tdf, aes(x=bathrooms)) + 
      geom_bar(fill=ltr_col, color=ltr_col) +
@@
 
- # Build short term plot
-
-  stbath <- ggplot(str_tdf, aes(x=bathrooms)) +
+```
+
+```{r plot_str_bath, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+  ggplot(str_tdf, aes(x=bathrooms)) +
     geom_bar(fill=str_col, color=str_col) +
@@
 
-#  # Make Plots  
-#   png(file=paste0(fig.path, 'dataclean_bathount.png'), width = 480, height = 280, 
-#       bg='transparent')
-#   
-#     ggMultiPlots(stbath, ltbath, cols=1)
-#     
-#   dev.off()
-#    
-#   save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
-#   save(stbath, file=paste0(fig.path, 'strbath.RData'))
-
 ```
@@
 
-```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Create combination variable
+```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
   str_tdf <- str_tdf %>% 
@@
 
-```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
-
- # Make long term plot
-
-  ltbb <- ggplot(ltr_tdf, aes(x=bedbath)) +
+```{r plot_ltr_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+  ggplot(ltr_tdf, aes(x=bedbath)) +
     geom_bar(fill=ltr_col, color=ltr_col) +
@@
 
- # Make short term plots
-
-  stbb <- ggplot(str_tdf, aes(x=bedbath)) +
+```
+
+```{r plot_str_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
+
+  ggplot(str_tdf, aes(x=bedbath)) +
     geom_bar(fill=str_col, color=str_col) +
@@
 
-#  # Make Plots  
-#   png(file=paste0(fig.path, 'dataclean_bedbath.png'), width = 480, height = 280, 
-#       bg='transparent')
-
-#     ggMultiPlots(ltbb, stbb, cols=1)
-
-#   dev.off()
-
-#   save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
-#   save(stbb, file=paste0(fig.path, 'strbb.RData'))
-
-```
-
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
+```
+
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
 We filter the data to these combinations.
@@
 
-```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-  acc_bb <- c('1_1', '2_1', '2_2', '3_1', '3_2', '4_2')
+  acc_bb <- c('1_1', '2_1', '2_2', '3_1', '3_2', '3_3', '4_2', '4_3')
 
@@
 
+#### Host Policies
+
+Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.
+We also remove the few observations with missing host policy data
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  str_tdf <- str_tdf %>%
+    dplyr::mutate(canc_policy = ifelse(canc_policy == 'Super Strict 60 Days',
+                                         'Strict', canc_policy)) %>%
+    dplyr::filter(canc_policy %in% c('Flexible', 'Moderate', 'Strict'))
+
+  # Count Cleaning
+  countCleaning('hostpolicy')
+
+```
+
+### Location
+
+### Locations and Submarkets
+
+Location is clearly an important determinant in both the short and long term rental markets.
+At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
+In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
+Suburbs in Melbourne are much smaller than their North American counterparts.
+The specific suburb of a property is the second, or finer scale, at which the market operates.
+The plot below shows the three large submarkets (Inner, Middle and Outer).
+
+```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ ## Build the map object
+
+  # Set colors
+  tm_shape(sub_sf) +
+    tm_polygons('suburbDesi',
+                title='Suburb Designation',
+                border.col='white',
+                palette=c('gray10', 'gray40', 'gray70'))
+
+```
+# 
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+This process is repeated for both the short and long term data.
+We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
+Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
+
+We select the 18 suburbs below to represent the 'core' of the city.
+The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
+All are well serviced by public transportation and possess abundant amenties for tourists.
+
+```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  core_suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
+                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
+                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
+                    'St Kilda West', 'West Melbourne', 'Windsor')
+
+```
+
+We then apply a 500 meter buffer to the beach along Port Phillip Bay.
+
+```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Determine centroid of study area
+
+   lat_mid <- median(str_tdf$latitude)
+   long_mid <- median(str_tdf$longitude)
+
+ # Calculate Degress to Meters conversion
+
+   m_lat = 111132.954 - 559.822 * cos(2 * lat_mid) + 1.175 * cos(4 * lat_mid)
+   m_long = 111132.954 * cos (lat_mid)
+   m_conv <- mean(c(m_lat, m_long))
+
+  # Create the beach buffer
+
+  suppressWarnings(beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv)))
+
+```
+
+Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
+
+```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Convert to point sf data
+   str_sf <- st_as_sf(str_tdf %>% 
+                        dplyr::select(property_id, longitude, latitude),
+                      coords = c('longitude', 'latitude'),
+                      crs = 4283)
+
+   ltr_sf <- st_as_sf(ltr_tdf %>% 
+                        dplyr::select(addr_id, longitude, latitude) %>%
+                        dplyr::filter(!is.na(latitude)),
+                      coords = c('longitude', 'latitude'),
+                      crs = 4283)
+
+  # Add suburb designation and remove those that are outside
+
+   str_sf <- st_join(str_sf, 
+                     sub_sf %>% 
+                      dplyr::select(suburb = NAME_2006,
+                                    sub_des = suburbDesi,
+                                    geometry)) %>%
+   dplyr::filter(!is.na(sub_des))
+
+   ltr_sf <- st_join(ltr_sf, 
+                     sub_sf %>% 
+                       dplyr::select(suburb = NAME_2006,
+                                     sub_des = suburbDesi,
+                                     geometry)) %>%
+   dplyr::filter(!is.na(sub_des))
+
+```
+
+Determine which suburbs are represented in both datasets and trim to those observations
+
+```{r match_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+    sub_str <- str_sf %>% 
+      dplyr::select(suburb, -geometry) %>% 
+      as.tibble() %>%
+      dplyr::group_by(suburb) %>% 
+      dplyr::summarize(count=n())
+
+    sub_ltr <- ltr_sf %>% 
+      dplyr::select(suburb, -geometry) %>% 
+      as.tibble() %>%
+      dplyr::group_by(suburb) %>% 
+      dplyr::summarize(count=n())
+
+    sub_all <- sub_ltr %>%
+      dplyr::inner_join(sub_str, by='suburb')
+
+    str_sf <- str_sf %>%
+      dplyr::filter(suburb %in% sub_all$suburb)
+
+    ltr_sf <- ltr_sf %>%
+      dplyr::filter(suburb %in% sub_all$suburb)
+
+```
+
+Next we add the sa1 and beach designations
+
+```{r add_sa1_beach, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Add SA1
+    str_sf <- st_join(str_sf, 
+                       sa1_sf %>%
+                         dplyr::select(sa1=SA1_MAIN11,
+                                       geometry)) %>%
+    dplyr::filter(!is.na(sa1))
+
+    ltr_sf <- st_join(ltr_sf, 
+                       sa1_sf %>%
+                         dplyr::select(sa1=SA1_MAIN11,
+                                       geometry)) %>%
+    dplyr::filter(!is.na(sa1))
+
+  # Add Beach
+   str_sf <- st_join(str_sf, 
+                       beach_buffer %>%
+                         dplyr::select(beach=id,
+                                       geometry)) %>%
+             dplyr::mutate(beach = ifelse(is.na(beach), 0, beach))
+
+   ltr_sf <- st_join(ltr_sf, 
+                       beach_buffer %>%
+                         dplyr::select(beach=id,
+                                       geometry)) %>%
+             dplyr::mutate(beach = ifelse(is.na(beach), 0, beach))
+
+```
+
+Add market designations.
+
+```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  ## Add to STR
+
+   # Add individual classes
+   str_sf$geo_mrkt <- 'rural'
+   str_sf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
+   str_sf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
+   str_sf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
+   str_sf$geo_mrkt[str_tdf$beach == 1] <- 'beach'
+
+   # Order the factors properly
+   str_sf$geo_mrkt <- factor(str_sf$geo_mrkt,
+                               levels=c('city-core', 'city', 'suburban',
+                                        'rural', 'beach'))
+
+   ## Add to LTR
+
+   # Add individual classes
+   ltr_sf$geo_mrkt <- 'rural'
+   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Middle'] <- 'suburban'
+   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Inner'] <- 'city'
+   ltr_sf$geo_mrkt[ltr_sf$suburb %in% core_suburbs] <- 'city-core'
+   ltr_sf$geo_mrkt[ltr_sf$beach == 1] <- 'beach'
+
+   # Order the factors properly
+   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
+                               levels=c('city-core', 'city', 'suburban',
+                                        'rural', 'beach'))
+   # Count Cleaning
+   countCleaning('location')
+
+```
+
 ## Rates and Rental values
@@
 
-```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
-### Locations and Submarkets
-
-Location is clearly an important determinant in both the short and long term rental markets.
-At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.
-Suburbs in Melbourne are much smaller than their North American counterparts.
-The specific suburb of a property is the second, or finer scale, at which the market operates.
-The plot below shows the three large submarkets (Inner, Middle and Outer).
-
-```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Convert shapefile to ggplot-able object
-
-   # Limit to extent of data
-   ltr_subs <- ltr_tdf %>%
-    dplyr::select(suburb) %>%
-    group_by(suburb) %>%
-    summarize(count=n())
-
-   # Clip to only those with a ltral observation
-   studysubs_sf <- sub_sf %>%
-     filter(NAME_2006 %in% ltr_subs$suburb)
-
-   # Convert to an outer bound with holes
-   ss_bound <- st_union(studysubs_sf)
-
-   # ss.bound <- gUnaryUnion(study.suburbs)
-   # 
-   # # Remove holes from the shapefile
-   # ssb <- slot(ss.bound, "polygons") 
-   # holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
-   #                                         slot, "hole"))
-   # res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
-   # IDs <- row.names(ss.bound) 
-   # ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
-   #  Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
-   # 
-   # # Identify which suburbs all in area covered by outer bound
-   # ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
-   # study.suburbs <- suburbs.shp[which(ss.in), ]
-   # 
-   # # Convert into an outer boundary with no holes
-   # ss.bound.out <- gUnaryUnion(study.suburbs)
-   # ssb.out <- slot(ss.bound.out, "polygons") 
-   # holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
-   #                                         slot, "hole"))
-   # res.out <- lapply(1:length(ssb.out), 
-   #                   function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
-   # IDs <- row.names(ss.bound.out) 
-   # ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
-   #                                        function(i) Polygons(res.out[[i]], 
-   #                                                             ID=IDs[i])),
-   #                                             proj4string=CRS(proj4string(ss.bound))) 
-   # 
-   # # Convert into a ggplot-able format
-   # subs <- fortify(study.suburbs, region='name_2006')
-   # 
-   # # Add suburb category
-   # subs$des <- suburbs.shp@data$suburbdesi[
-   #   match(subs$id, suburbs.shp@data$name_2006)]
-
-```
-
-```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- ## Build the map object
-
-#    # Set colors
-#    g_cols <- c('grey10', 'grey40', 'grey70')
-#  
-#    # Make map
-#    ggplot(studysubs_sf) %>%
-#      geom_sf(aes(group=group, fill=suburbDesi))
-# 
-#    loc_map <- ggplot() +
-#      geom_polygon(data=studysubs_sf, 
-#                   aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
-# #     scale_fill_manual(values=g_cols, labels=c('Inner      ',
-#                                               'Middle      ',
-#                                               'Outer')) +
-#     geom_path(data=subs[subs$des=='Outer', ], 
-#               aes(x=long, y=lat, group=group), col='white', size=.1,
-#               linetype=1) +
-#   
-#     geom_path(data=subs[subs$des=='Middle', ], 
-#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
-#               linetype=1) +
-#     
-#     geom_path(data=subs[subs$des=='Inner', ], 
-#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
-#               linetype=1) +
-#     
-#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-#     xlab('') + ylab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_rect(fill = "white"),
-#           axis.text.x = element_blank(),
-#           axis.text.y = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.title.x=element_blank(),
-#           axis.title.y=element_blank(),
-#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-#     #ggtitle("Melbourne Suburb Classifications")+
-#     theme(plot.title = element_text(hjust = 0.5))
-# 
-# ```
-# 
-# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
-#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
-#       bg='transparent')
-#   
-#     loc.map
-#     
-#   dev.off()
-#   
-#   loc.map
-#   
-#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
-# 
-#     
-```
-# 
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
-While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
-This process is repeated for both the short and long term data.
-We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-
-We select the 18 suburbs below to represent the 'core' of the city.
-The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
-All are well serviced by public transportation and possess abundant amenties for tourists.
-
-```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  core_suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
-                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
-                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
-                    'St Kilda West', 'West Melbourne', 'Windsor')
-
-```
-
-We then apply a 500 meter buffer to the beach along Port Phillip Bay.
-
-```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Determine centroid of study area
-
-   lat_mid <- median(str_tdf$latitude)
-   long_mid <- median(str_tdf$longitude)
-
- # Calculate Degress to Meters conversion
-
-   m_lat = 111132.954 - 559.822 * cos(2 * lat_mid) + 1.175 * cos(4 * lat_mid)
-   m_long = 111132.954 * cos (lat_mid)
-   m_conv <- mean(c(m_lat, m_long))
-
-  # Create the beach buffer
-
-  beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv))
-
-```
-
-Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.
-
-```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- ## Short term data
-
- # Convert to point shapefile
-   str_tdf <- st_as_sf(str_tdf,
-                       coords = c('longitude', 'latitude'),
-                       crs = 4283)
-
-   ltr_tdf <- st_as_sf(ltr_tdf %>% dplyr::filter(!is.na(latitude)),
-                       coords = c('longitude', 'latitude'),
-                       crs = 4283)
-
-    str_tdf <- st_join(str_tdf, 
-                       sub_sf %>% 
-                        dplyr::select(suburb = NAME_2006,
-                                      sub_des = suburbDesi,
-                                      geometry)) %>%
-    dplyr::filter(!is.na(sub_des))
-
-    ltr_tdf <- st_join(ltr_tdf %>%
-                         dplyr::select(-suburb), 
-                       sub_sf %>% 
-                        dplyr::select(suburb = NAME_2006,
-                                      sub_des = suburbDesi,
-                                      geometry)) %>%
-    dplyr::filter(!is.na(sub_des))
-
-    sub_str <- str_tdf %>% 
-      dplyr::select(suburb, -geometry) %>% 
-      as.tibble() %>%
-      dplyr::group_by(suburb) %>% 
-      dplyr::summarize(count=n())
-
-    sub_ltr <- ltr_tdf %>% 
-      dplyr::select(suburb, -geometry) %>% 
-      as.tibble() %>%
-      dplyr::group_by(suburb) %>% 
-      dplyr::summarize(count=n())
-
-    sub_all <- sub_ltr %>%
-      dplyr::inner_join(sub_str, by='suburb')
-
-    str_tdf <- str_tdf %>%
-      dplyr::filter(suburb %in% sub_all$suburb)
-
-    ltr_tdf <- ltr_tdf %>%
-      dplyr::filter(suburb %in% sub_all$suburb)
-
-    str_tdf <- st_join(str_tdf, 
-                       sa1_sf %>%
-                         dplyr::select(sa1=SA1_MAIN11,
-                                       geometry)) %>%
-    dplyr::filter(!is.na(sa1))
-
-        ltr_tdf <- st_join(ltr_tdf, 
-                       sa1_sf %>%
-                         dplyr::select(sa1=SA1_MAIN11,
-                                       geometry)) %>%
-    dplyr::filter(!is.na(sa1))
-
-   str_tdf <- st_join(str_tdf, 
-                       beach_buffer %>%
-                         dplyr::select(beach=id,
-                                       geometry)) %>%
-      mutate(beach = ifelse(is.na(beach), 0, beach))
-
-    ltr_tdf <- st_join(ltr_tdf, 
-                       beach_buffer %>%
-                         dplyr::select(beach=id,
-                                       geometry)) %>%
-    mutate(beach = ifelse(is.na(beach), 0, beach))
-
-```
-
-```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ## Add the submarket designations
-
-   # Add individual classes
-   str_tdf$geo_mrkt <- 'rural'
-   str_tdf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
-   str_tdf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
-   str_tdf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
-   str_tdf$geo_mrkt[str_tdf$beach == 1] <- 'beach'
-#   
-#   # Order the factors properly
-    str_tdf$geo_mrkt <- factor(str_tdf$geo_mrkt,
-                               levels=c('city-core', 'city', 'suburban',
-                                        'rural', 'beach'))
-
-       # Add individual classes
-   ltr_tdf$geo_mrkt <- 'rural'
-   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Middle'] <- 'suburban'
-   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Inner'] <- 'city'
-   ltr_tdf$geo_mrkt[ltr_tdf$suburb %in% core_suburbs] <- 'city-core'
-   ltr_tdf$geo_mrkt[ltr_tdf$beach == 1] <- 'beach'
-#   
-#   # Order the factors properly
-   ltr_tdf$geo_mrkt <- factor(ltr_tdf$geo_mrkt,
-                               levels=c('city-core', 'city', 'suburban',
-                                        'rural', 'beach'))
- # Count Cleaning
-   countCleaning('location')
-
-```
-
 The location of the short and long term rentals, colored by submarket, are shown below
 
-#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 # 
@@
 # 
-# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 # 
@@
 # 
-# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
+# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
 #   
@@
 # 
-# ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
-# 
-#   # Make Airbnb submarket map
-#   
-#   strtype.map <- ggplot() +
-#     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
-#     scale_fill_manual(values=sm_col) +
-#     facet_wrap(~type) +
-#     ylab('# of Properties\n') + xlab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           axis.text.x=element_blank(),
-#           axis.ticks.x=element_blank()) +
-#     #ggtitle('Short Term Property Type\nBy Submarket')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-#   # Make Long term rental map
-# 
-#   ltrtype.map <- ggplot() +
-#     geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
-#     scale_fill_manual(values=sm_col) +
-#     facet_wrap(~type) +
-#     ylab('# of Properties\n') + xlab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           axis.text.x=element_blank(),
-#           axis.ticks.x=element_blank()) +
-#     #ggtitle('Long Term Property Type\nBy Submarket')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-# ```
-# 
-# ```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
+```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
+
+   # Make Airbnb submarket map
+
+   strtype.map <- ggplot() +
+     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     #ggtitle('Short Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+   # Make Long term rental map
+
+   ltrtype.map <- ggplot() +
+     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     #ggtitle('Long Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+```
+# 
+# ```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
 # 
@@
 #
-# ```
-# 
-# Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on. 
-# 
-# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#   # Convert suburbs from factor to character
-#   str_df$suburb <- as.character(str_df$suburb)
-#   ltr_df$suburb <- as.character(ltr_df$suburb)
-#   
-# ```
-# 
-# &nbsp;
-# 
-# ## Filter Transaction Data
-# 
-# The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets
-# 
-# ```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  ## Short term data
-#   
-#   daily_df <- daily_df[daily_df$property.id %in% str_df$property.id,]
-# 
-#  ## Long term list data
-#   
-#   listing.data <- listing.data[listing.data$activity.id %in% ltr_df$activity.id,]
-# 
-# ```
-# 
-# ## Summarize Daily Data
-# 
-# As we have limited the time period of analysis from the expanse of the raw data, we must now re calculate the daily summary information. 
-# 
-# ```{r redo.daily.summ, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-# 
-#     # Create new cluster
-#   abb_cl <- get_default_cluster() 
-#   
-#   # Register function and variable
-#   cluster_copy(abb_cl, abbCalcBookStr)
-# 
-#   # Summarize daily by property
-#   daily_summ <- daily_df %>% 
-#     multidplyr::partition(property.id, cluster=abb_cl) %>% 
-#     dplyr::do(abbCalcBookStr(.)) %>% 
-#     dplyr::collect()
-#   
-#  # Remove existing 
-#  str_df <- str_df %>%
-#    dplyr::select(-c(total.days, block.rate, avail.rate, longest.block, nbr.block,
-#                     med.block, bookings))
-#  
-#  # Add summary data to property data
-#  str_df <- str_df %>% dplyr::left_join(daily_summ, by='property.id')
-# 
-# 
-# ```
-# 
-# 
-# #### Host Policies
-# 
-# Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.
-We also remove the few observations with missing host policy data
-# 
-# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-# 
-#  ## ID those with missing cancel policies and remove
-# 
-#   str_df <- str_df %>% 
-#     dplyr::filter(cancel.policy %in% c('Flexible', 'Moderate', 'Strict'))
-# 
-#  ## ID those with Super Strict and change to Strict  
-#   
-#   ss60 <- which(str_df$cancel.policy == 'Super Strict 60 Days')
-#   str_df$cancel.policy[ss60] <- 'Strict'
-# 
-#   # Count Cleaning
-#   countCleaning('hostpolicy')
-#   
-#   
-# ```
-# 
-# ## Write out data  
-# 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+## Write out data
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 

### 2018-05-09 functions/geom_sf.R

@@ -1,0 +1,445 @@
+#' Visualise sf objects
+#'
+#' This set of geom, stat, and coord are used to visualise simple feature (sf)
+#' objects. For simple plots, you will only need `geom_sf` as it
+#' uses `stat_sf` and adds `coord_sf` for you. `geom_sf` is
+#' an unusual geom because it will draw different geometric objects depending
+#' on what simple features are present in the data: you can get points, lines,
+#' or polygons.
+#'
+#' @section Geometry aesthetic:
+#' `geom_sf` uses a unique aesthetic: `geometry`, giving an
+#' column of class `sfc` containg simple features data. There
+#' are three ways to supply the `geometry` aesthetic:
+#'
+#'   - Do nothing: by default `geom_sf` assumes it is stored in
+#'     the `geometry` column.
+#'   - Explicitly pass an `sf` object to the `data` argument.
+#'     This will use the primary geometry column, no matter what it's called.
+#'   - Supply your own using `aes(geometry = my_column)`
+#'
+#' Unlike other aesthetics, `geometry` will never be inherited from
+#' the plot.
+#'
+#' @section CRS:
+#' `coord_sf()` ensures that all layers use a common CRS. You can
+#' either specify it using the `CRS` param, or `coord_sf` will
+#' take it from the first layer that defines a CRS.
+#'
+#' @param show.legend logical. Should this layer be included in the legends?
+#'   `NA`, the default, includes if any aesthetics are mapped.
+#'   `FALSE` never includes, and `TRUE` always includes.
+#'
+#'   You can also set this to one of "polygon", "line", and "point" to
+#'   override the default legend.
+#' @examples
+#' if (requireNamespace("sf", quietly = TRUE)) {
+#' nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
+#' ggplot(nc) +
+#'   geom_sf(aes(fill = AREA))
+#'
+#' # If not supplied, coord_sf() will take the CRS from the first layer
+#' # and automatically transform all other layers to use that CRS. This
+#' # ensures that all data will correctly line up
+#' nc_3857 <- sf::st_transform(nc, "+init=epsg:3857")
+#' ggplot() +
+#'   geom_sf(data = nc) +
+#'   geom_sf(data = nc_3857, colour = "red", fill = NA)
+#'
+#' # Unfortunately if you plot other types of feature you'll need to use
[…]

### 2018-05-09 scripts/3_data_prep.Rmd
Simplify code up to write section

@@
   library(multidplyr)
-  # library(lubridate)
-  # library(spdep)
-  # library(maptools)
-  # library(ggplot2)
+  library(tmap)
 
@@
 
-Determine which suburbs are represented in both datasets and trim to those observations
+Determine which suburbs are represented in both datasets and trim to those observations to suburbs with at least three transactions
 
@@
       dplyr::group_by(suburb) %>% 
-      dplyr::summarize(count=n())
+      dplyr::summarize(count=n()) %>%
+      dplyr::filter(count >= 3 & 
+                      suburb != 'Maddingley')
 
@@
       dplyr::filter(suburb %in% sub_all$suburb)
+
+```
+
+Create a polygon of the new study area
+
+```{r new_study_area, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  all_sf <- rbind(str_sf %>% 
+                    rename(uniq_id = property_id),
+                  ltr_sf %>%
+                    rename(uniq_id = addr_id))
+  ssub_sf <- sub_sf %>% filter(NAME_2006 %in% sub_all$suburb)
+
+  all_ch <- st_buffer(st_convex_hull(st_union(ssub_sf)), .001)
+  within_ch <- st_contains(all_ch, sub_sf$geometry)
+  subs_within <- sub_sf[unlist(within_ch), ]
+  study_area <- st_union(subs_within)
+  plot(study_area)
 
@@
                                         'rural', 'beach'))
+
+  ltr_tdf %>% 
+    dplyr::mutate(geometry = NULL) %>%
+    as.tibble()
+
+  str_tdf %>% 
+    dplyr::mutate(geometry = NULL) %>%
+    as.tibble()
+
    # Count Cleaning
    countCleaning('location')
+
+```
+
+Finally we add the spatial data back onto the tabular data (filtering out those outside of the study area using an inner join).
+
+```{r merge_spatial, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  str_tdf <- str_tdf %>%
+    dplyr::inner_join(str_sf, 
+                      by='property_id')
+
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::inner_join(ltr_sf,
+                      by='addr_id')
 
@@
   # Nightly Rate plot
-  str_plot <- ggplot(str_tdf, aes(x=med_rate)) +
+  str_price <- ggplot(str_tdf, aes(x=med_rate)) +
     geom_density(fill=str_col, alpha=.8) +
@@
                        ltr_tdf %>%
-                         tidyr::unnest() %>%
                          dplyr::select(type, gross_revenue) %>%
@@
     geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, abb_col)) +
-    scale_color_manual(values=c(ltr_col, abb_col)) +
+    scale_fill_manual(values=c(ltr_col, str_col)) +
+    scale_color_manual(values=c(ltr_col, str_col)) +
     ggtitle('Annual Revenues by Tenure Type') +
@@
 
-```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
-#       bg='transparent')
-#     
-#     revdens
-#   
-#   dev.off()
-#   
-#   save(revdens, file=paste0(fig.path, 'revdens.RData'))
-#   
-#   ltr_df <- ltr_df[ltr_df$dom <= 180, ]
-#   
-#     countCleaning('revenue')
-```
-
 The location of the short and long term rentals, colored by submarket, are shown below
 
-#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   # Set submarket colors
-#   
-#   sm_col <- abb_col[c(1, 3, 6, 5, 2)]
-# 
-#   # Make map
-# 
-#   str.map <- ggplot() +
-#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
+```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+ # Set submarket colors
+   # Make map
+  tm_shape(sub_sf) +
+    tm_polygons() + 
+  tm_shape(study_area) + 
+    tm_polygons(col='dodgerblue3') +
+  tm_shape(ltr_sf) +
+    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)
+
+  tm_shape(sub_sf) +
+    tm_polygons() + 
+  tm_shape(study_area) + 
+    tm_polygons(col='dodgerblue3') +
+  tm_shape(str_sf) +
+    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)
+
+  str_map <- ggplot() +
+     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
 #     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,

### 2018-05-10 scripts/3_data_prep.Rmd
Complete prep re-write.  Start viz script

@@
   pdf_document: default
-  html_notebook: default
-  html_document: default
 editor_options: 
@@
 
-### Introduction
+## Introduction
 
@@
 
-### Preliminary Commands
+## Preliminary Commands
 
@@
 
+Then we set the paths to the data
+
 ```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
@@
   source(file.path(code_path, 'functions', 'abb_Functions.R'))
-  source(file.path(code_path, 'functions', 'geom_sf.R'))
-
-```
-
-### Constants and Parameters
+
+```
+
+## Constants and Parameters
 
@@
                                'beach', 'ebisu', 'tirol', 'foggy', 'hof'),
-                       rgb = c(rgb(250,88,99, maxColorValue=255), 
-                               rgb(139,14,82, maxColorValue=255),
-                               rgb(0,117,140, maxColorValue=255), 
-                               rgb(4,211,191, maxColorValue=255),
-                               rgb(77,226,110, maxColorValue=255), 
-                               rgb(252,179,14, maxColorValue=255),
-                               rgb(249,177,139, maxColorValue=255), 
-                               rgb(191,166,100, maxColorValue=255),
-                               rgb(156,161,155, maxColorValue=255), 
-                               rgb(86,94,97, maxColorValue=255)))
+                       rgb = c(rgb(250, 88, 99, maxColorValue=255), 
+                               rgb(139, 14, 82, maxColorValue=255),
+                               rgb(0, 117, 140, maxColorValue=255), 
+                               rgb(4, 211, 191, maxColorValue=255),
+                               rgb(77, 226, 110, maxColorValue=255), 
+                               rgb(252, 179, 14, maxColorValue=255),
+                               rgb(249, 177, 139, maxColorValue=255), 
+                               rgb(191, 166, 100, maxColorValue=255),
+                               rgb(156, 161, 155, maxColorValue=255), 
+                               rgb(86, 94, 97, maxColorValue=255)))
 
@@
   ltr_col <- col_df$rgb[3]
-  sm_col <- col_df$rgb[c(2,4,5,8,6)]
+  sm_col <- col_df$rgb[c(2, 4, 5, 8, 6)]
 
@@
 
-  sub_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
+  suburb_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
     st_transform(crs=4283)
@@
 
-We then clip by time.  For the short-term data we will consider any Airbnb property that had at least 6 months worth of listing time on the portal during the 12-month study period
+We then clip by time.
+For the short-term data we will consider any Airbnb property that had at least 6 months worth of listing time on the portal during the 12-month study period.
+We also filter the long term data to include only observations with one year prior to the decision date.
 
@@
   # Short Term data  
-
   str_tdf <- str_tdf %>%
@@
   # Long Term data  
-
   ltr_tdf <- ltr_tdf %>%
@@
 
-  # Create long term rental plot
-
   ggplot(ltr_tdf, aes(x=type)) +
@@
 
+   # Plot by listing type
    ggplot(str_tdf, aes(x=listing_type)) + 
@@
 We start by looking at bedrooms.
-We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms).
-We then plot the distribution of diffeltr bedrooms counts.
+We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 10 bedrooms).
+We then plot the distribution of different bedrooms counts.
 From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types.
@@
 ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  # Remove missing and data errors
 
@@
 
-### Location
-
 ### Locations and Submarkets
@@
   # Set colors
-  tm_shape(sub_sf) +
+  tm_shape(suburb_sf) +
     tm_polygons('suburbDesi',
@@
   # Add suburb designation and remove those that are outside   
-
    str_sf <- st_join(str_sf, 
-                     sub_sf %>% 
+                     suburb_sf %>% 
                       dplyr::select(suburb = NAME_2006,
@@
    ltr_sf <- st_join(ltr_sf, 
-                     sub_sf %>% 
+                     suburb_sf %>% 
                        dplyr::select(suburb = NAME_2006,
@@
 
+    # Count those with at least 3 transactions
     sub_str <- str_sf %>% 
@@
 
+    # Join to create unified list
     sub_all <- sub_ltr %>%
@@
 
+    # Remove those with insufficient observations
     str_sf <- str_sf %>%
@@
 
-  all_sf <- rbind(str_sf %>% 
-                    rename(uniq_id = property_id),
-                  ltr_sf %>%
-                    rename(uniq_id = addr_id))
-  ssub_sf <- sub_sf %>% filter(NAME_2006 %in% sub_all$suburb)
-
-  all_ch <- st_buffer(st_convex_hull(st_union(ssub_sf)), .001)
-  within_ch <- st_contains(all_ch, sub_sf$geometry)
-  subs_within <- sub_sf[unlist(within_ch), ]
-  study_area <- st_union(subs_within)
-  plot(study_area)
+  # Get ids of study suburbs
+  sa_ids <- suburb_sf %>%
+    dplyr::filter(NAME_2006 %in% sub_all$suburb) %>%
+    sf::st_union() %>%
+    sf::st_convex_hull() %>%
+    sf::st_buffer(., .001) %>%
+    st_contains(., suburb_sf$geometry) %>%
+    unlist()
+
+  # Study Area
+  studyarea_sf <- suburb_sf %>% 
+    slice(sa_ids) %>%
+    st_union()
+  plot(studyarea_sf)
+
+  # Create Indicators in main sf fle
+  suburb_sf <- suburb_sf %>%
+    dplyr::select(name = NAME_2006, class = suburbDesi, geometry) %>%
+    dplyr::mutate(in_study = if_else(name %in% sub_all$suburb, 1, 0),
+                  in_studyarea = 0)
+  suburb_sf$in_studyarea[sa_ids] <- 1
 
@@
 
-  ltr_tdf %>% 
+```
+
+Finally we add the spatial data back onto the tabular data and filtering out those outside of the study area using an inner join.
+We then have to remove the geometry field as it causes issues with future analyses (for now)
+
+```{r merge_spatial, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  str_tdf <- str_tdf %>%
+    dplyr::inner_join(str_sf, 
+                      by='property_id') %>% 
      dplyr::mutate(geometry = NULL) %>%
@@
 
-  str_tdf %>% 
+  ltr_tdf <- ltr_tdf %>%
+    dplyr::inner_join(ltr_sf,
+                      by='addr_id') %>% 
      dplyr::mutate(geometry = NULL) %>%
@@
    countCleaning('location')
-
-```
-
-Finally we add the spatial data back onto the tabular data (filtering out those outside of the study area using an inner join).
-
-```{r merge_spatial, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  str_tdf <- str_tdf %>%
-    dplyr::inner_join(str_sf, 
-                      by='property_id')
-
-  ltr_tdf <- ltr_tdf %>%
-    dplyr::inner_join(ltr_sf,
-                      by='addr_id')
 
@@
 
-  ltr_price <- ggplot(ltr_tdf %>% tidyr::unnest(), aes(x=price)) +
+  ggplot(ltr_tdf %>% tidyr::unnest(), aes(x=price)) +
     geom_density(fill=ltr_col, alpha=.8) +
@@
   # Nightly Rate plot
-  str_price <- ggplot(str_tdf, aes(x=med_rate)) +
+  ggplot(str_tdf, aes(x=med_rate)) +
     geom_density(fill=str_col, alpha=.8) +
@@
 
-```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   png(file=paste0(fig.path, 'dataclean_rates.png'), width = 480, height = 280, 
-#       bg='transparent')
-#     
-#     ggMultiPlots(ltr.plot, rate.plot, cols=2)
-#   
-#   dev.off()
-#   
-#   save(ltr.plot, file=paste0(fig.path, 'rentplot.RData'))
-#   save(rate.plot, file=paste0(fig.path, 'rateplot.RData'))
-# 
-#   
-```
-
 ```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
@@
 
-   # Add together for plotting
-   rev_df <- bind_rows(str_tdf %>% 
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'str'),
-                       ltr_tdf %>%
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'ltr'))
-
-   revdens <- ggplot(rev_df, 
-                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, str_col)) +
-    scale_color_manual(values=c(ltr_col, str_col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
-    xlab('Annual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
-
-   # Add together for plotting potential revenues
-   prev_df <- bind_rows(str_tdf %>% 
-                         dplyr::select(type, gross_revenue=pot_revenue) %>%
-                         dplyr::mutate(tenure = 'str'),
-                       ltr_tdf %>%
-                         tidyr::unnest() %>%
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'ltr'))
-
-   prevdens <- ggplot(prev_df, 
-                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, str_col)) +
-    scale_color_manual(values=c(ltr_col, str_col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
-    xlab('Annual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
-
-```
-
-The location of the short and long term rentals, colored by submarket, are shown below
-
-```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- # Set submarket colors
-   # Make map
-  tm_shape(sub_sf) +
-    tm_polygons() + 
-  tm_shape(study_area) + 
-    tm_polygons(col='dodgerblue3') +
-  tm_shape(ltr_sf) +
-    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)
-
-  tm_shape(sub_sf) +
-    tm_polygons() + 
-  tm_shape(study_area) + 
-    tm_polygons(col='dodgerblue3') +
-  tm_shape(str_sf) +
-    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)
-
-  str_map <- ggplot() +
-     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
-#                alpha=.2) +
-#     scale_color_manual(values=sm_col) +
-#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-#     xlab('') + ylab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_rect(fill = "white"),
-#           axis.text.x = element_blank(),
-#           axis.text.y = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.title.x=element_blank(),
-#           axis.title.y=element_blank(),
-#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-#     guides(colour = guide_legend(override.aes = list(size=3,
-#                                                      alpha=1))) + 
-#     ggtitle('Short-Term Rental Locations')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-# ```
-# 
-# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   # Make map
-# 
-#   ltr.map <- ggplot() +
-#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
-#                alpha=.1) +
-#     scale_color_manual(values=sm_col) +
-#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-#     xlab('') + ylab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_rect(fill = "white"),
-#           axis.text.x = element_blank(),
-#           axis.text.y = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.title.x=element_blank(),
-#           axis.title.y=element_blank(),
-#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-#     guides(colour = guide_legend(override.aes = list(size=3,
-#                                                      alpha=1))) + 
-#     ggtitle('Long-Term Rental Locations')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-# ```
-# 
-# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-#   
-#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
-#       bg='transparent')
-#      str.map
-#   dev.off()
-#   
-#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
-#       bg='transparent')
-#      ltr.map
-#   dev.off()
-# 
-#   ggMultiPlots(str.map, ltr.map, cols=2)
-#   
-#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
-#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
-# 
-# 
-# ```
-# 
-# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
-# 
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-
-   # Make Airbnb submarket map
-
-   strtype.map <- ggplot() +
-     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     #ggtitle('Short Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-   # Make Long term rental map
-
-   ltrtype.map <- ggplot() +
-     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     #ggtitle('Long Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-```
-# 
-# ```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-# 
-#   png(file=paste0(fig.path, 'submplot.png'), width = 680, height = 590, 
-#       bg='transparent')
-#     ggMultiPlots(strtype.map, ltrtype.map, cols=2)
-#   dev.off()
-#     
-#   ggMultiPlots(strtype.map, ltrtype.map, cols=2)
-#   
-#   save(strtype.map, file=paste0(fig.path, 'strsubplot.RData'))
-#   save(ltrtype.map, file=paste0(fig.path, 'ltrsubplot.RData'))
-# 
-#
+```
 
@@
 
-   save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
-#        beach.shp, core.suburbs, exch.rate, ltr_col, str_col, sa1s.shp, 
-#        suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
-#        ltr.run.total, str.run.total,
-#        file=paste0(data_path, 'prepared/prep_workspace_', data_name, '.RData'))
-# 
-# ```N
+   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
+        file=paste0(data_path, '/prepared/prepared_data.RData'))
+
+```

### 2018-05-10 scripts/5_data_viz.Rmd
Complete prep re-write.  Start viz script

---
title: "5_data_viz"
author: "Andy Krause"
date: "May 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   revdens <- ggplot(rev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

   # Add together for plotting potential revenues
   prev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue=pot_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         tidyr::unnest() %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   prevdens <- ggplot(prev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

```

The location of the short and long term rentals, colored by submarket, are shown below

```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 # Set submarket colors
   # Make map
  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(ltr_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)

  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(str_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)

  str_map <- ggplot() +
     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') 
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
```
#

```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}

   # Make Airbnb submarket map

   strtype.map <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

   # Make Long term rental map

   ltrtype.map <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

```

# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
#

### 2018-05-10 scripts/4_data_analysis.Rmd
Start re-write of data analysis script

--- 2017-10-25 abbDataAnalysis_Script.Rmd
@@
 Additional analysis that were not included in the final report are also found within this document.
-This analysis uses the output from the **abbDataClean_Script.rmd** file found in the same online repository.
-### Preliminary Commands
-
-We begin by loading the libraries necessary to do this analysis.
+This analysis uses the output from the **3_data_prep.rmd** file found in the same online repository.
+
+## Preliminary Commands
 
@@
 
+We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.
+
 ```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
+  library(tidyverse)
+  library(sf)
   library(geosphere)
   library(ggmap)
-  library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-  library(kernlab)
-  library(lmtest)
-  library(ROCR)
-
-```
-
-&nbsp;
-
-```{r set_dates}
-
-  data_name <- 'jun'
-  strike_date <- lubridate::as_date('2015-06-01')
-
-```
-
-We then set the paths to the data, code and figures, based on the user of the document.  We also set a variable indicating whether or not we are working offline.
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-    data.path <- 'c:/dropbox/research/airBNB/data/'
-    code.path <- 'c:/code/'
-    fig.path <- 'c:/dropbox/research/airBNB/figures/'
-
-```
-
-Next, we source the necessary custom code files for the analysis.  We also set a few options here.
-
-```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
- # Current Project files
-
-  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
-
- # Other custom files
-
-  if(offline){
-
-  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
-  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
-  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
-  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))
-
-  } else {
-
-  source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
-                '/master/ggPlotTools.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
-                '/master/dataMungeTools.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-                '/master/spatialLogitModels.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-                '/master/point2surface_Tools.R'))
-
-  }
-
- ## Set options
-
+  library(multidplyr)
+  library(tmap)
+
+  options(stringsAsFactors=FALSE)
   options(xtable.comment = FALSE)
@@
 
-We load the workspace from the data clean script that includes the prepared data objects.
-
-```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Property Information
-
-  load(file.path(data.path, 'prepared', paste0('prep_workspace_', data_name, '.RData')))
-
-```
-
-### Calculating Net Revenues
-
-We begin the analysis by calculating the net revenues for the short term data.
+Then we set the paths to the data
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
+  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
+
+```
+
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+
+```
+
+### Set Parameters
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  exch_rate <- 1.32
+
+  decision_date <- lubridate::as_date('2015-09-01')
+
+```
+
+## Load Data
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  load(file.path(data.path, 'prepared', 'prepared_data.RData'))
+
+```
+
+<!-- ### Calculating Net Revenues -->
+
+<!-- We begin the analysis by calculating the net revenues for the short term data.
 We calculate three types of net revenues, Observed, Extrapolated (Actual) and Potential.
 The difference are described more fully in the writeup.
-
-Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
+-->
+
+<!-- Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
 For 2 persons in an apartment that works out to \$5 per person per day.
@@
 We use an estimate of 1.5 persons per bedroom in each unit.
-
-```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_df$cpppd <- 4.5
-  str_df$avg.guests <- str_df$bedrooms * 1.5
-
-```
-
-```{r obs_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_df$str.obs.revenue <- ((str_df$bookings * str_df$med.rate) - 
-                                 (str_df$bookings * str_df$avg.guests *
-                                    str_df$cpppd))
-
-```
-
-```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_df$extr.par <- 366 / str_df$total.days
-
-  str_df$str.act.revenue <- ((str_df$bookings * str_df$extr.par *
-                                  str_df$med.rate) - 
-                                 (str_df$bookings * str_df$avg.guests * 
-                                    str_df$cpppd * str_df$extr.par))
-```
-
-```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_df$occ.rate <- 1 - (str_df$block.rate + str_df$avail.rate)
-
-  str_df$pot.occ.rate <- ((str_df$bookings * str_df$extr.par) / 
-    (366 - (366 * str_df$block.rate)))
-
-  str_df$str.pot.revenue <- ((str_df$pot.occ.rate * 366 * str_df$med.rate) - 
-                                 (str_df$pot.occ.rate * 366 * 
-                                    str_df$avg.guests * str_df$cpppd))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data$ltr.revenue <- ltr.data$gross.revenue
-
-```
-
-#### Compare Revenue Distributions
-
-Before we examine the distributions of the observed short-term revenues and the estimated long-term revenues, we must produce the estimates of long-term revenue for the short-term properties.
-
-We start by specifying the imputation model specification we will use to estimated likely long-term (weekly) rental prices for each short-term property.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
-                            as.factor(bedbath) + as.factor(suburb) + 
-                            as.factor(ltr.month))
-
-```
-
-We then employ a custom function to impute the long term rents for the short-term properties.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  imp.data <- imputeLtrRents(ltr.df=ltr.data,
-                               str.df=str_df,
-                               mod.spec=ltr.mod.spec,
-                               match.factor='suburb')
-
-```
-
-From the imputed results, we extract the imputed rental values and merge to the original short-term data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Extract out DFs (only those that imputed)
-  str.metro <- merge(str_df, imp.data$imp.rent, by='property.id')
-
-```
-
-Next we impute the likely long-term search cost (days on market) for the short-term properties.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Apply dom to abb
-  str.metro$imp.dom <- imputeDOM(str.metro, ltr.data, calc.type='median')
-
-```
-
-With the imputed DOMs and weekly rental rates we now make the an estimate of likely annual revenue if leased on the long term market. We append this to the original dataset.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str.metro$ltr.imp.revenue <- str.metro$imp.rent * (52 - str.metro$imp.dom / 7)
-
-```
-
-Finally we make a comparison of the observed short term revenues and the imputed long term revenue and add these field back onto the original data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  comp.revs <- compareRevenues(str.metro)
-
-  str.metro <- merge(str.metro, comp.revs, by='property.id')
-
-```
-
-The above process of long-term revenue estimation treated the entire market as operating similarly.
+-->
+
+<!-- ```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   str_df$cpppd <- 4.5 -->
+<!--   str_df$avg.guests <- str_df$bedrooms * 1.5 -->
+
+<!-- ``` -->
+
+<!-- ```{r obs_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   str_df$str.obs.revenue <- ((str_df$bookings * str_df$med.rate) -  -->
+<!--                                  (str_df$bookings * str_df$avg.guests * -->
+<!--                                     str_df$cpppd)) -->
+
+<!-- ``` -->
+
+<!-- ```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   str_df$extr.par <- 366 / str_df$total.days -->
+
+<!--   str_df$str.act.revenue <- ((str_df$bookings * str_df$extr.par * -->
+<!--                                   str_df$med.rate) -  -->
+<!--                                  (str_df$bookings * str_df$avg.guests *  -->
+<!--                                     str_df$cpppd * str_df$extr.par)) -->
+<!-- ``` -->
+
+<!-- ```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   str_df$occ.rate <- 1 - (str_df$block.rate + str_df$avail.rate) -->
+
+<!--   str_df$pot.occ.rate <- ((str_df$bookings * str_df$extr.par) /  -->
+<!--     (366 - (366 * str_df$block.rate)))  -->
+
+<!--   str_df$str.pot.revenue <- ((str_df$pot.occ.rate * 366 * str_df$med.rate) -  -->
+<!--                                  (str_df$pot.occ.rate * 366 *  -->
+<!--                                     str_df$avg.guests * str_df$cpppd)) -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   ltr.data$ltr.revenue <- ltr.data$gross.revenue -->
+
+<!-- ``` -->
+
+<!-- #### Compare Revenue Distributions -->
+
+<!-- Before we examine the distributions of the observed short-term revenues and the estimated long-term revenues, we must produce the estimates of long-term revenue for the short-term properties.
+-->
+
+<!-- We start by specifying the imputation model specification we will use to estimated likely long-term (weekly) rental prices for each short-term property.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) +  -->
+<!--                             as.factor(bedbath) + as.factor(suburb) +  -->
+<!--                             as.factor(ltr.month)) -->
+
+<!-- ``` -->
+
+<!-- We then employ a custom function to impute the long term rents for the short-term properties.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.   -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   imp.data <- imputeLtrRents(ltr.df=ltr.data, -->
+<!--                                str.df=str_df, -->
+<!--                                mod.spec=ltr.mod.spec, -->
+<!--                                match.factor='suburb') -->
+
+<!-- ``` -->
+
+<!-- From the imputed results, we extract the imputed rental values and merge to the original short-term data.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   # Extract out DFs (only those that imputed) -->
+<!--   str.metro <- merge(str_df, imp.data$imp.rent, by='property.id') -->
+
+<!-- ``` -->
+
+<!-- Next we impute the likely long-term search cost (days on market) for the short-term properties. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   # Apply dom to abb -->
+<!--   str.metro$imp.dom <- imputeDOM(str.metro, ltr.data, calc.type='median') -->
+
+<!-- ``` -->
+
+<!-- With the imputed DOMs and weekly rental rates we now make the an estimate of likely annual revenue if leased on the long term market. We append this to the original dataset. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   str.metro$ltr.imp.revenue <- str.metro$imp.rent * (52 - str.metro$imp.dom / 7) -->
+
+<!-- ``` -->
+
+<!-- Finally we make a comparison of the observed short term revenues and the imputed long term revenue and add these field back onto the original data.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   comp.revs <- compareRevenues(str.metro) -->
+
+<!--   str.metro <- merge(str.metro, comp.revs, by='property.id') -->
+
+<!-- ``` -->
+
+<!-- The above process of long-term revenue estimation treated the entire market as operating similarly.
 Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.
@@
 We use these finer scale estimates going forward (the data in the **str_df.ic** object).
-
-```{r build.tbg.data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Create the type, bed/bath and geo sub market variable
-
- str_df$tbg <- paste0(str_df$product,'.', str_df$geo.mrkt)
- ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)
-
- # Make IC estimates at TBG level
-
- str_df.ic <- abbImputeCompare(str.df=str_df,
-                                 ltr.df=ltr.data,
-                                 mod.spec=ltr.mod.spec,
-                                 match.factor='suburb',
-                                 split.field='tbg',
-                                 verbose=FALSE)
-
-```
-
-Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties
-
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  # Actual
-   stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')]
-   stra.rev$tenure <- 'Short-Term (Actual)   '
-   names(stra.rev)[2] <- 'revenue'
-
-  # Potential
-   strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')]
-   strp.rev$tenure <- 'Short-Term (Potential)   '
-   names(strp.rev)[2] <- 'revenue'
-
-  # Long-Term
-   ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')]
-   ltr.rev$tenure <- 'Long-Term   '
-   names(ltr.rev)[2] <- 'revenue'
-
-  # Combine
-   revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)
-
-  ## Build a plot
-
-   rd.plot <- ggplot(revdens.data, 
-                     aes(x=revenue, fill=tenure, color=tenure)) +
-     geom_density(alpha=.5) +
-     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
-     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-     xlab('\nAnnual Revenue') +
-     scale_x_continuous(breaks=c(seq(0, 75000, by=25000)),
-                        labels=c('$0', '$25k', '$50k', '$75k'))+
-     theme(legend.position='none',
-           legend.title = element_blank(),
-           plot.title = element_text(hjust = 0.5),
-           axis.text.y = element_blank(),
-           axis.ticks.y = element_blank(),
-           axis.title.y=element_blank()) +
-     coord_cartesian(xlim=c(0, 85000))
-     rd.plot <- rd.plot + facet_wrap(~tenure)
-
-  ## Plot
-
-     rd.plot
-
-```
-
-## Results
-
-We will begin by analyzing the above estimates at the entire metro scale.
+-->
+
+<!-- ```{r build.tbg.data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Create the type, bed/bath and geo sub market variable -->
+
+<!--  str_df$tbg <- paste0(str_df$product,'.', str_df$geo.mrkt) -->
+<!--  ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt) -->
+
+<!--  # Make IC estimates at TBG level -->
+
+<!--  str_df.ic <- abbImputeCompare(str.df=str_df, -->
+<!--                                  ltr.df=ltr.data, -->
+<!--                                  mod.spec=ltr.mod.spec, -->
+<!--                                  match.factor='suburb', -->
+<!--                                  split.field='tbg', -->
+<!--                                  verbose=FALSE) -->
+
+<!-- ``` -->
+
+<!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->
+
+<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   # Actual -->
+<!--    stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')] -->
+<!--    stra.rev$tenure <- 'Short-Term (Actual)   ' -->
+<!--    names(stra.rev)[2] <- 'revenue' -->
+
+<!--   # Potential -->
+<!--    strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')] -->
+<!--    strp.rev$tenure <- 'Short-Term (Potential)   ' -->
+<!--    names(strp.rev)[2] <- 'revenue' -->
+
+<!--   # Long-Term -->
+<!--    ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')] -->
+<!--    ltr.rev$tenure <- 'Long-Term   ' -->
+<!--    names(ltr.rev)[2] <- 'revenue' -->
+
+<!--   # Combine -->
+<!--    revdens.data <- rbind(stra.rev, strp.rev, ltr.rev) -->
+
+<!--   ## Build a plot -->
+
+<!--    rd.plot <- ggplot(revdens.data,  -->
+<!--                      aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--      geom_density(alpha=.5) + -->
+<!--      scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--      scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--      xlab('\nAnnual Revenue') + -->
+<!--      scale_x_continuous(breaks=c(seq(0, 75000, by=25000)), -->
+<!--                         labels=c('$0', '$25k', '$50k', '$75k'))+ -->
+<!--      theme(legend.position='none', -->
+<!--            legend.title = element_blank(), -->
+<!--            plot.title = element_text(hjust = 0.5), -->
+<!--            axis.text.y = element_blank(), -->
+<!--            axis.ticks.y = element_blank(), -->
+<!--            axis.title.y=element_blank()) + -->
+<!--      coord_cartesian(xlim=c(0, 85000)) -->
+<!--      rd.plot <- rd.plot + facet_wrap(~tenure) -->
+
+<!--   ## Plot -->
+
+<!--      rd.plot -->
+
+<!-- ``` -->
+
+<!-- ## Results -->
+
+<!-- We will begin by analyzing the above estimates at the entire metro scale.
 Analyses of various submarkets will follow.
 Overall, we see that 31.1\% of properties raised more revenue via short term rental than expected in the long term market.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  table(str_df.ic$str.act.pref) / nrow(str_df.ic)
-
-```
-
-Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Set Preference data field
-
-  str_df.ic$pref <- str_df.ic$str.act.pref
-
- ## Calculate the percentile fields
-
-  str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate, 
-                                      return.type='rank') 
-  str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate, 
-                                  return.type='rank')
-
- ## Calculate raw and percentile occupancies
-
-  rawocc.metro <- abbPrefPlot(str_df.ic,
-                         x.field='occ.rate',
-                         smooth=TRUE,
-                         smooth.span=.5)
-
-  qtlocc.metro <- abbPrefPlot(str_df.ic,
-                        x.field='occ.qtl',
-                        smooth=TRUE,
-                        smooth.span=.5)
-
-   ## Make plots
-
-  # Raw
-  raw.occ.metro <- ggplot(rawocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Quantile
-  qtl.occ.metro <- ggplot(qtlocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
-
-```
-
-Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.rate',
-                y.field='med.rate',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm + ylab('Nightly Rate')
-
-```
-
-To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm.svm <- abbHeatMap(str_df.ic,
-                            x.field='occ.rate',
-                            y.field='med.rate',
-                            pref.field='str.act.pref',
-                            svm=T, 
-                            alpha.count=F,
-                            add.points=T,
-                            fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm.svm+ ylab('Nightly Rate')
-
-```
-
-As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm+ ylab('Nightly  (Pcntl)')
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm.svm <- abbHeatMap(str_df.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm.svm+ ylab('Nightly  (Pcntl)')
-
-```
-
-### Submarkets
-
-Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.
-
-First we make a comparison table of the results.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Make Basic comparison table
-  pref.table.type <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='type')
-
- # Limit to the extrapolated pref type
-  pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ]
-
-```
-
-We then turn this into a simple chart to see the differences.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) + 
-    geom_bar() +
-    scale_fill_manual(values=c('red', 'blue')) +
-    xlab('') +
-    ylab('% of properties where Airbnb is more profitable') +
-    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none')
-
-```
-
-We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.
-
-```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Create dataset
-
-  type.data.ic <- str_df.ic
-
-  # Id the types
-  apt.id <- which(str_df.ic$type == 'Apartment')
-  house.id <- which(str_df.ic$type == 'House')
-
-  # Recalculate the percentiles
-  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
-                                      return.type='rank')
-  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$occ.rate[house.id], return.type='rank')
-
-  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
-                                  return.type='rank')
-  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$med.rate[house.id], return.type='rank')
-
-```
-
-Then we calculate the preference figures
-
-```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Calc the occ rate numbers
-
-  rawocc.type <- abbPrefPlot(type.data.ic,
-                         x.field='occ.rate',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-  pctocc.type <- abbPrefPlot(type.data.ic,
-                         x.field='occ.qtl',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-```
-
-And then plot.
-
-```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
-
- ## Build raw plot
-
-  ptr.occ <- ggplot(rawocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Build Percentile Plots
-
-  ptq.occ <- ggplot(pctocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
-
-```
-
-Finally, we make percentile SVM heatmaps for both apartments and houses.
-
-```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
-
- ## Make House SVM Heatmap
-
-  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'House', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5])) +
-  theme(legend.position='none') +
-  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Make Apartment SVM Heat Map
-
-  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'Apartment', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Plot
-
-  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
-
-```
-
-#### Geographic Submarkets
-
-We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets.
-
-```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
-
- # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='geo.mrkt')
-
- # Convert to wide format for output
-  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
-
- # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
-  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
-
- # Fix names  
-  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-
- ## Make printable table
-
-  print(xtable(pref.table[,1:2], 
-               caption='Geographic Submarket Preferability\n',
-               digits=1,
-               align='llr'),
-        include.rownames=FALSE,
-        caption.placement='top')
-
-```
-
-```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}
-
- ## Build data
-
-  subm.data.ic <- str_df.ic
-
-  # Get IDs
-  cc.id <- which(str_df.ic$geo.mrkt == 'city-core')
-  city.id <- which(str_df.ic$geo.mrkt == 'city')
-  sub.id <- which(str_df.ic$geo.mrkt == 'suburban')
-  rural.id <- which(str_df.ic$geo.mrkt == 'rural')
-  beach.id <- which(str_df.ic$geo.mrkt == 'beach')
-
-  # Recalc the percentiles
-  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
-      subm.data.ic$occ.rate[city.id], return.type='rank')
-  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
-    subm.data.ic$med.rate[city.id], return.type='rank')
-
-  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
-                                  return.type='rank')
-
-```
-
-```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
-
- ## Set colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
- ## Create plot data
-
-  rawocc.geo <- abbPrefPlot(subm.data.ic,
-                        x.field='occ.rate',
-                        split.field='geo.mrkt',
-                        smooth=TRUE,
-                        smooth.span=.5 ,
-                        spl.col=sm.col)
-
-  pctocc.geo <- abbPrefPlot(subm.data.ic,
-                         x.field='occ.qtl',
-                         split.field='geo.mrkt',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=sm.col)
-
- ## Make plot objects
-
-  smr.occ <- ggplot(rawocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  smq.occ <- ggplot(pctocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(smr.occ, smq.occ, cols=2)
-
-```
-
-```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
-
-  # Build the SVM Heatmaps
-
-  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city-core', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5])) +
-  theme(legend.position='none') +
-    ylab('') +
-    xlab('') +
-  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
-
-  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "City", size=9)
-
-  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'suburban', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
-
-  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'rural', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Rural", size=9)
-
-  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'beach', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Beach", size=9)
-
-```
-
-```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
-
-  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
-               rural.hm.svm, beach.hm.svm, cols=2)
-
-```
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE} -->
+
+<!--   table(str_df.ic$str.act.pref) / nrow(str_df.ic) -->
+
+<!-- ``` -->
+
+<!-- Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Set Preference data field -->
+
+<!--   str_df.ic$pref <- str_df.ic$str.act.pref -->
+
+<!--  ## Calculate the percentile fields -->
+
+<!--   str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate,  -->
+<!--                                       return.type='rank')  -->
+<!--   str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate,  -->
+<!--                                   return.type='rank')  -->
+
+<!--  ## Calculate raw and percentile occupancies -->
+
+<!--   rawocc.metro <- abbPrefPlot(str_df.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5) -->
+
+<!--   qtlocc.metro <- abbPrefPlot(str_df.ic, -->
+<!--                         x.field='occ.qtl', -->
+<!--                         smooth=TRUE, -->
+<!--                         smooth.span=.5) -->
+
+<!--    ## Make plots   -->
+
+<!--   # Raw -->
+<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Quantile -->
+<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Make Plot -->
+<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   rate.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.rate', -->
+<!--                 y.field='med.rate', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   rate.hm + ylab('Nightly Rate') -->
+
+<!-- ``` -->
+
+<!-- To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                             x.field='occ.rate', -->
+<!--                             y.field='med.rate', -->
+<!--                             pref.field='str.act.pref', -->
+<!--                             svm=T,  -->
+<!--                             alpha.count=F, -->
+<!--                             add.points=T, -->
+<!--                             fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   rate.hm.svm+ ylab('Nightly Rate') -->
+
+<!-- ``` -->
+
+<!-- As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.qtl', -->
+<!--                 y.field='rate.qtl', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   qtl.hm+ ylab('Nightly  (Pcntl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   qtl.hm.svm+ ylab('Nightly  (Pcntl)') -->
+
+<!-- ``` -->
+
+<!-- ### Submarkets -->
+
+<!-- Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.  -->
+
+<!-- First we make a comparison table of the results.   -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table.type <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='type') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ] -->
+
+<!-- ``` -->
+
+<!-- We then turn this into a simple chart to see the differences. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) +  -->
+<!--     geom_bar() + -->
+<!--     scale_fill_manual(values=c('red', 'blue')) + -->
+<!--     xlab('') + -->
+<!--     ylab('% of properties where Airbnb is more profitable') + -->
+<!--     scale_y_continuous(breaks=c(0,.25,.5,.75,1), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') -->
+
+<!-- ``` -->
+
+<!-- We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.  -->
+
+<!-- ```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Create dataset -->
+
+<!--   type.data.ic <- str_df.ic -->
+
+<!--   # Id the types -->
+<!--   apt.id <- which(str_df.ic$type == 'Apartment') -->
+<!--   house.id <- which(str_df.ic$type == 'House') -->
+
+<!--   # Recalculate the percentiles -->
+<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
+<!--                                       return.type='rank') -->
+<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->
+
+<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
+<!--                                   return.type='rank') -->
+<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$med.rate[house.id], return.type='rank') -->
+
+<!-- ```  -->
+
+<!-- Then we calculate the preference figures -->
+
+<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Calc the occ rate numbers -->
+
+<!--   rawocc.type <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!--   pctocc.type <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.qtl', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!-- ``` -->
+
+<!-- And then plot.  -->
+
+<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
+
+<!--  ## Build raw plot -->
+
+<!--   ptr.occ <- ggplot(rawocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Build Percentile Plots -->
+
+<!--   ptq.occ <- ggplot(pctocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Finally, we make percentile SVM heatmaps for both apartments and houses.  -->
+
+<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
+
+<!--  ## Make House SVM Heatmap -->
+
+<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'House', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
+<!--   theme(legend.position='none') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Make Apartment SVM Heat Map -->
+
+<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'Apartment', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Plot -->
+
+<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- #### Geographic Submarkets -->
+
+<!-- We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets. -->
+
+<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='geo.mrkt') -->
+
+<!--  # Convert to wide format for output -->
+<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
+<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
+<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
+
+<!--  # Fix names   -->
+<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+
+<!--  ## Make printable table -->
+
+<!--   print(xtable(pref.table[,1:2],  -->
+<!--                caption='Geographic Submarket Preferability\n', -->
+<!--                digits=1, -->
+<!--                align='llr'), -->
+<!--         include.rownames=FALSE, -->
+<!--         caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}  -->
+
+<!--  ## Build data -->
+
+<!--   subm.data.ic <- str_df.ic -->
+
+<!--   # Get IDs -->
+<!--   cc.id <- which(str_df.ic$geo.mrkt == 'city-core') -->
+<!--   city.id <- which(str_df.ic$geo.mrkt == 'city') -->
+<!--   sub.id <- which(str_df.ic$geo.mrkt == 'suburban') -->
+<!--   rural.id <- which(str_df.ic$geo.mrkt == 'rural') -->
+<!--   beach.id <- which(str_df.ic$geo.mrkt == 'beach') -->
+
+<!--   # Recalc the percentiles -->
+<!--   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[city.id] <- makeWtdQtl( -->
+<!--       subm.data.ic$occ.rate[city.id], return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[city.id] <- makeWtdQtl( -->
+<!--     subm.data.ic$med.rate[city.id], return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id], -->
+<!--                                   return.type='rank') -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
+
+<!--  ## Set colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
+
+<!--  ## Create plot data -->
+
+<!--   rawocc.geo <- abbPrefPlot(subm.data.ic, -->
+<!--                         x.field='occ.rate', -->
+<!--                         split.field='geo.mrkt', -->
+<!--                         smooth=TRUE, -->
+<!--                         smooth.span=.5 , -->
+<!--                         spl.col=sm.col) -->
+
+<!--   pctocc.geo <- abbPrefPlot(subm.data.ic, -->
+<!--                          x.field='occ.qtl', -->
+<!--                          split.field='geo.mrkt', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=sm.col) -->
+
+<!--  ## Make plot objects   -->
+
+<!--   smr.occ <- ggplot(rawocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   smq.occ <- ggplot(pctocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'} -->
+
+<!--   # Build the SVM Heatmaps -->
+
+<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city-core', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
+<!--   theme(legend.position='none') + -->
+<!--     ylab('') + -->
+<!--     xlab('') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
+
+<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
+
+<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'suburban', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
+
+<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'rural', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
+
+<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'beach', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'} -->
+
+<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
+<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
+
+<!-- ``` -->
 

### 2018-05-21 scripts/3_data_prep.Rmd
Start re-write of data analysis script
Bug fix: ;geo_mrkt definition error

@@
    str_sf$geo_mrkt <- 'rural'
-   str_sf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
-   str_sf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
-   str_sf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
-   str_sf$geo_mrkt[str_tdf$beach == 1] <- 'beach'
+   str_sf$geo_mrkt[str_sf$sub_des == 'Middle'] <- 'suburban'
+   str_sf$geo_mrkt[str_sf$sub_des == 'Inner'] <- 'city'
+   str_sf$geo_mrkt[str_sf$suburb %in% core_suburbs] <- 'city-core'
+   str_sf$geo_mrkt[str_sf$beach == 1] <- 'beach'
 
@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        file=paste0(data_path, '/prepared/prepared_data.RData'))
+        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))
 

### 2018-05-21 scripts/4_data_analysis.Rmd
Re-org Analysis, move viz, etc.

--- 2017-10-25 abbDataAnalysis_Script.Rmd
@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 Additional analysis that were not included in the final report are also found within this document.
-This analysis uses the output from the **abbDataClean_Script.rmd** file found in the same online repository.
-### Preliminary Commands
+This analysis uses the output from the **3_data_prep.rmd** file found in the same online repository.
 
-We begin by loading the libraries necessary to do this analysis.
+## Preliminary Commands
 
@@
 
+We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.
+
 ```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
+  library(tidyverse)
+  library(sf)
   library(geosphere)
   library(ggmap)
-  library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-  library(kernlab)
-  library(lmtest)
-  library(ROCR)
+  library(multidplyr)
+  library(tmap)
 
-```
-
-&nbsp;
-
-```{r set_dates}
-
-  data_name <- 'jun'
-  strike_date <- lubridate::as_date('2015-06-01')
-
-```
-
-We then set the paths to the data, code and figures, based on the user of the document.  We also set a variable indicating whether or not we are working offline.
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-    data.path <- 'c:/dropbox/research/airBNB/data/'
-    code.path <- 'c:/code/'
-    fig.path <- 'c:/dropbox/research/airBNB/figures/'
-
-```
-
-Next, we source the necessary custom code files for the analysis.  We also set a few options here.
-
-```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
- # Current Project files
-
-  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))
-
- # Other custom files
-
-  if(offline){
-
-  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
-  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
-  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
-  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))
-
-  } else {
-
-  source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
-                '/master/ggPlotTools.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
-                '/master/dataMungeTools.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-                '/master/spatialLogitModels.R'))
-  source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
-                '/master/point2surface_Tools.R'))
-
-  }
-
- ## Set options
-
+  options(stringsAsFactors=FALSE)
   options(xtable.comment = FALSE)
@@
 
-We load the workspace from the data clean script that includes the prepared data objects.
+Then we set the paths to the data
 
-```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
 
-  # Property Information
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
+  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
 
-  load(file.path(data.path, 'prepared', paste0('prep_workspace_', data_name, '.RData')))
+```
+
+Next, we source the necessary custom code files for the analysis.
+
+```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+
+```
+
+### Set Parameters
+
+```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  exch_rate <- 1.32
+
+  decision_date <- lubridate::as_date('2015-09-01')
+
+```
+
+## Load Data
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  load(file.path(data_path, 'prepared', 'prepared_data.RData'))
 
@@
 
-  str_df$cpppd <- 4.5
-  str_df$avg.guests <- str_df$bedrooms * 1.5
+  # Set cost per person per day
+  cpppd <- 4.5
 
-```
-
-```{r obs_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_df$str.obs.revenue <- ((str_df$bookings * str_df$med.rate) - 
-                                 (str_df$bookings * str_df$avg.guests *
-                                    str_df$cpppd))
+  # Calculate avg number of guests
+  str_tdf$avg_guests <- str_tdf$bedrooms * 1.5
 
@@
 
-  str_df$extr.par <- 366 / str_df$total.days
+  str_tdf$act_revenue <- ((str_tdf$bookings * str_tdf$med_rate) -
+                                 (str_tdf$bookings * str_tdf$avg_guests * cpppd))
 
-  str_df$str.act.revenue <- ((str_df$bookings * str_df$extr.par *
-                                  str_df$med.rate) - 
-                                 (str_df$bookings * str_df$avg.guests * 
-                                    str_df$cpppd * str_df$extr.par))
+```
+
+```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Create Extrapolation parameter
+  str_tdf$extr_par <- 366 / str_tdf$total_days
+
+  # Calculate likely revenue
+  str_tdf$lik_revenue <- ((str_tdf$bookings * str_tdf$extr_par * str_tdf$med_rate) -
+                           (str_tdf$bookings * str_tdf$avg_guests *
+                             cpppd * str_tdf$extr_par))
 ```
@@
 
-  str_df$occ.rate <- 1 - (str_df$block.rate + str_df$avail.rate)
+  str_tdf$occ_rate <- 1 - (str_tdf$block_rate + str_tdf$avail_rate)
 
-  str_df$pot.occ.rate <- ((str_df$bookings * str_df$extr.par) / 
-    (366 - (366 * str_df$block.rate)))
+  str_tdf$pot_occ_rate <- ((str_tdf$bookings * str_tdf$extr_par) /
+                             (366 - (366 * str_tdf$block_rate)))
 
-  str_df$str.pot.revenue <- ((str_df$pot.occ.rate * 366 * str_df$med.rate) - 
-                                 (str_df$pot.occ.rate * 366 * 
-                                    str_df$avg.guests * str_df$cpppd))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ltr.data$ltr.revenue <- ltr.data$gross.revenue
+  str_tdf$pot_revenue <- ((str_tdf$pot_occ_rate * 366 * str_tdf$med_rate) -
+                           (str_tdf$pot_occ_rate * 366 * str_tdf$avg_guests * cpppd))
 
@@
 #### Compare Revenue Distributions
+
+```{r flatten_ltr}
+
+  ltr_df <- ltr_tdf %>% 
+    unnest() %>%
+    select(-suburb.x) %>%
+    rename(suburb=suburb.y)
+
+```
 
@@
 
-  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
+  ltr_mod_spec <- formula(log(price) ~ as.factor(type) +
                             as.factor(bedbath) + as.factor(suburb) +
-                            as.factor(ltr.month))
+                            as.factor(month))
 
@@
 
-  imp.data <- imputeLtrRents(ltr.df=ltr.data,
-                               str.df=str_df,
-                               mod.spec=ltr.mod.spec,
-                               match.factor='suburb')
+  str_tdf$tbg <- paste0(str_tdf$product,'_', str_tdf$geo_mrkt)
+  ltr_df$tbg <- paste0(ltr_df$product,'_', ltr_df$geo_mrkt)
+
+  imp_df <- abbImputeCompare(str.df=str_tdf, 
+                                ltr.df=ltr_df, 
+                                mod.spec=ltr_mod_spec, 
+                                match.factor='suburb',
+                                split.field='tbg', 
+                                verbose=FALSE)
 
@@
   # Extract out DFs (only those that imputed)
-  str.metro <- merge(str_df, imp.data$imp.rent, by='property.id')
-
-```
-
-Next we impute the likely long-term search cost (days on market) for the short-term properties.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Apply dom to abb
-  str.metro$imp.dom <- imputeDOM(str.metro, ltr.data, calc.type='median')
-
-```
-
-With the imputed DOMs and weekly rental rates we now make the an estimate of likely annual revenue if leased on the long term market. We append this to the original dataset.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str.metro$ltr.imp.revenue <- str.metro$imp.rent * (52 - str.metro$imp.dom / 7)
-
-```
-
-Finally we make a comparison of the observed short term revenues and the imputed long term revenue and add these field back onto the original data.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  comp.revs <- compareRevenues(str.metro)
-
-  str.metro <- merge(str.metro, comp.revs, by='property.id')
-
-```
-
-The above process of long-term revenue estimation treated the entire market as operating similarly.
-Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.
-In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
-for all compbinations of type, bed/bath and geographic area.
-We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals.
-We use these finer scale estimates going forward (the data in the **str_df.ic** object).
-
-```{r build.tbg.data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Create the type, bed/bath and geo sub market variable
-
- str_df$tbg <- paste0(str_df$product,'.', str_df$geo.mrkt)
- ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)
-
- # Make IC estimates at TBG level
-
- str_df.ic <- abbImputeCompare(str.df=str_df,
-                                 ltr.df=ltr.data,
-                                 mod.spec=ltr.mod.spec,
-                                 match.factor='suburb',
-                                 split.field='tbg',
-                                 verbose=FALSE)
-
-```
-
-Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties
-
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5}
-
-  # Actual
-   stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')]
-   stra.rev$tenure <- 'Short-Term (Actual)   '
-   names(stra.rev)[2] <- 'revenue'
-
-  # Potential
-   strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')]
-   strp.rev$tenure <- 'Short-Term (Potential)   '
-   names(strp.rev)[2] <- 'revenue'
-
-  # Long-Term
-   ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')]
-   ltr.rev$tenure <- 'Long-Term   '
-   names(ltr.rev)[2] <- 'revenue'
-
-  # Combine
-   revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)
-
-  ## Build a plot
-
-   rd.plot <- ggplot(revdens.data, 
-                     aes(x=revenue, fill=tenure, color=tenure)) +
-     geom_density(alpha=.5) +
-     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
-     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-     xlab('\nAnnual Revenue') +
-     scale_x_continuous(breaks=c(seq(0, 75000, by=25000)),
-                        labels=c('$0', '$25k', '$50k', '$75k'))+
-     theme(legend.position='none',
-           legend.title = element_blank(),
-           plot.title = element_text(hjust = 0.5),
-           axis.text.y = element_blank(),
-           axis.ticks.y = element_blank(),
-           axis.title.y=element_blank()) +
-     coord_cartesian(xlim=c(0, 85000))
-     rd.plot <- rd.plot + facet_wrap(~tenure)
-
-  ## Plot
-
-     rd.plot
-
-```
-
-## Results
-
-We will begin by analyzing the above estimates at the entire metro scale.
-Analyses of various submarkets will follow.
-Overall, we see that 31.1\% of properties raised more revenue via short term rental than expected in the long term market.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
-  table(str_df.ic$str.act.pref) / nrow(str_df.ic)
-
-```
-
-Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Set Preference data field
-
-  str_df.ic$pref <- str_df.ic$str.act.pref
-
- ## Calculate the percentile fields
-
-  str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate, 
-                                      return.type='rank') 
-  str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate, 
-                                  return.type='rank')
-
- ## Calculate raw and percentile occupancies
-
-  rawocc.metro <- abbPrefPlot(str_df.ic,
-                         x.field='occ.rate',
-                         smooth=TRUE,
-                         smooth.span=.5)
-
-  qtlocc.metro <- abbPrefPlot(str_df.ic,
-                        x.field='occ.qtl',
-                        smooth=TRUE,
-                        smooth.span=.5)
-
-   ## Make plots
-
-  # Raw
-  raw.occ.metro <- ggplot(rawocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Quantile
-  qtl.occ.metro <- ggplot(qtlocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
-
-```
-
-Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.rate',
-                y.field='med.rate',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm + ylab('Nightly Rate')
-
-```
-
-To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  rate.hm.svm <- abbHeatMap(str_df.ic,
-                            x.field='occ.rate',
-                            y.field='med.rate',
-                            pref.field='str.act.pref',
-                            svm=T, 
-                            alpha.count=F,
-                            add.points=T,
-                            fill.colors=c(abb.col[1], abb.col[5]))
-  rate.hm.svm+ ylab('Nightly Rate')
-
-```
-
-As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm+ ylab('Nightly  (Pcntl)')
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  qtl.hm.svm <- abbHeatMap(str_df.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
-  qtl.hm.svm+ ylab('Nightly  (Pcntl)')
-
-```
-
-### Submarkets
-
-Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.
-
-First we make a comparison table of the results.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
- # Make Basic comparison table
-  pref.table.type <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='type')
-
- # Limit to the extrapolated pref type
-  pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ]
-
-```
-
-We then turn this into a simple chart to see the differences.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) + 
-    geom_bar() +
-    scale_fill_manual(values=c('red', 'blue')) +
-    xlab('') +
-    ylab('% of properties where Airbnb is more profitable') +
-    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none')
-
-```
-
-We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.
-
-```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Create dataset
-
-  type.data.ic <- str_df.ic
-
-  # Id the types
-  apt.id <- which(str_df.ic$type == 'Apartment')
-  house.id <- which(str_df.ic$type == 'House')
-
-  # Recalculate the percentiles
-  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
-                                      return.type='rank')
-  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$occ.rate[house.id], return.type='rank')
-
-  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
-                                  return.type='rank')
-  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
-    type.data.ic$med.rate[house.id], return.type='rank')
-
-```
-
-Then we calculate the preference figures
-
-```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
- ## Calc the occ rate numbers
-
-  rawocc.type <- abbPrefPlot(type.data.ic,
-                         x.field='occ.rate',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-  pctocc.type <- abbPrefPlot(type.data.ic,
-                         x.field='occ.qtl',
-                         split.field='type',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=c('black', 'grey40'))
-
-```
-
-And then plot.
-
-```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
-
- ## Build raw plot
-
-  ptr.occ <- ggplot(rawocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Build Percentile Plots
-
-  ptq.occ <- ggplot(pctocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
-
-```
-
-Finally, we make percentile SVM heatmaps for both apartments and houses.
-
-```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
-
- ## Make House SVM Heatmap
-
-  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'House', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5])) +
-  theme(legend.position='none') +
-  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Make Apartment SVM Heat Map
-
-  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'Apartment', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Plot
-
-  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
-
-```
-
-#### Geographic Submarkets
-
-We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets.
-
-```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}
-
- # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='geo.mrkt')
-
- # Convert to wide format for output
-  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
-
- # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
-  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
-
- # Fix names  
-  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-
- ## Make printable table
-
-  print(xtable(pref.table[,1:2], 
-               caption='Geographic Submarket Preferability\n',
-               digits=1,
-               align='llr'),
-        include.rownames=FALSE,
-        caption.placement='top')
-
-```
-
-```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}
-
- ## Build data
-
-  subm.data.ic <- str_df.ic
-
-  # Get IDs
-  cc.id <- which(str_df.ic$geo.mrkt == 'city-core')
-  city.id <- which(str_df.ic$geo.mrkt == 'city')
-  sub.id <- which(str_df.ic$geo.mrkt == 'suburban')
-  rural.id <- which(str_df.ic$geo.mrkt == 'rural')
-  beach.id <- which(str_df.ic$geo.mrkt == 'beach')
-
-  # Recalc the percentiles
-  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
-      subm.data.ic$occ.rate[city.id], return.type='rank')
-  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
-    subm.data.ic$med.rate[city.id], return.type='rank')
-
-  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
-                                  return.type='rank')
-
-  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
-                                      return.type='rank')
-  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
-                                  return.type='rank')
-
-```
-
-```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
-
- ## Set colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
- ## Create plot data
-
-  rawocc.geo <- abbPrefPlot(subm.data.ic,
-                        x.field='occ.rate',
-                        split.field='geo.mrkt',
-                        smooth=TRUE,
-                        smooth.span=.5 ,
-                        spl.col=sm.col)
-
-  pctocc.geo <- abbPrefPlot(subm.data.ic,
-                         x.field='occ.qtl',
-                         split.field='geo.mrkt',
-                         smooth=TRUE,
-                         smooth.span=.5 ,
-                         spl.col=sm.col)
-
- ## Make plot objects
-
-  smr.occ <- ggplot(rawocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  smq.occ <- ggplot(pctocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(smr.occ, smq.occ, cols=2)
-
-```
-
-```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}
-
-  # Build the SVM Heatmaps
-
-  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city-core', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5])) +
-  theme(legend.position='none') +
-    ylab('') +
-    xlab('') +
-  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
-
-  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "City", size=9)
-
-  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'suburban', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
-
-  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'rural', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Rural", size=9)
-
-  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'beach', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))+
-  theme(legend.position='none')+
-    ylab('') +
-    xlab('')+
-  annotate("text", x = 50, y = 50, label = "Beach", size=9)
-
-```
-
-```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}
-
-  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
-               rural.hm.svm, beach.hm.svm, cols=2)
+  str_tdf <- str_tdf %>%
+    dplyr::left_join(imp_df, by='property_id') %>%
+    dplyr::mutate(act_pref = ifelse(act_revenue > ltr_imp_revenue, 1, 0),
+                  lik_pref = ifelse(lik_revenue > ltr_imp_revenue, 1, 0),
+                  pot_pref = ifelse(pot_revenue > ltr_imp_revenue, 1, 0))
 
@@
 
-  str_df.ic$bedbath <- factor(str_df.ic$bedbath,
-                                levels=c('1..1', '2..1', '2..2',
-                                         '3..1', '3..2', '4..2'))
+  glm_lik_str <- glm(lik_pref ~ type + as.factor(bedbath),
+                     family=binomial(link='logit'),
+                     data=str_tdf)
 
-  mod.act.str <- glm(str.act.pref~type+as.factor(bedbath),
+  glm_pot_str <- glm(pot_pref~type+as.factor(bedbath),
                        family=binomial(link='logit'),
-                     data=str_df.ic)
-  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
-                     family=binomial(link='logit'),
-                     data=str_df.ic)
+                       data=str_tdf)
 ```
@@
 
-  mod.act.loc <- glm(str.act.pref~type+as.factor(bedbath)+
-                                  geo.mrkt,
+  glm_lik_loc <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt),
                      family=binomial(link='logit'),
-                     data=str_df.ic)
-  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
-                                  geo.mrkt,
+                     data=str_tdf)
+
+  glm_pot_loc <- glm(pot_pref ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                      family=binomial(link='logit'),
-                     data=str_df.ic)
+                     data=str_tdf)
 ```
@@
 
-  mod.act.host <- glm(str.act.pref~type+as.factor(bedbath)+
-                        geo.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+  glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
                       family=binomial(link='logit'),
-                      data=str_df.ic)
-  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
-                        geo.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
+                      data=str_tdf)
+
+  glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
                       family=binomial(link='logit'),
-                      data=str_df.ic)
-```
+                      data=str_tdf)
 
-We combine all model results in to a list for easy export.
+  lik_glms <- list(str=glm_lik_str,
+                   loc=glm_lik_loc,
+                   host=glm_lik_host)
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  pref.models <- list(mod.act.str, mod.act.loc, mod.act.host, 
-                      mod.pot.str, mod.pot.loc, mod.pot.host)
-  names(pref.models) <- c('act.str', 'act.loc', 'act.host',
-                          'pot.str', 'pot.loc', 'pot.host')
-
-```
-
-We then also run a set of regression models where the premium (or discount) for short-term leasing is the dependent variable.  We use the same three model specifications as above.
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
-                    data=str_df.ic)
-  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
-                    data=str_df.ic)
-
-  mod.act.loc.prem <- glm(str.act.pref~type+as.factor(bedbath)+
-                                  geo.mrkt,
-                     family=binomial(link='logit'),
-                     data=str_df.ic)
-  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
-                                  geo.mrkt,
-                     family=binomial(link='logit'),
-                     data=str_df.ic)
-
-  mod.act.host.prem <- lm(str.act.prem~type+as.factor(bedbath)+
-                        geo.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str_df.ic)
-  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
-                        geo.mrkt+
-                        I(max.guests/bedrooms)+min.stay+
-                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                      data=str_df.ic)
-```
-
-We then package these into a list for easy export
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-    prem.models <- list(mod.act.str.prem, mod.act.loc.prem, mod.act.host.prem, 
-                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
-    names(prem.models) <- c('act.str', 'act.loc', 'act.host',
-                          'pot.str', 'pot.loc', 'pot.host')
-
-```
-
-## Sensitivity
-
-### Potential Revenue
-
-To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.
-
-```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
-
- # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='type')
- # Extract Potential Results
-  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
-
- # Make baseic comparison table of submarkets  
-  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='geo.mrkt')
-
- # Extract potential results  
-  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
-
- # Combine and round  
-  st.table <- rbind(tpref.table, spref.table)
-  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
-
- ## Fix names and print
-
-  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-  print(xtable(st.table[,1:2], 
-               caption='Potential Revenue Preferability\n',
-               digits=1, align='llr'),
-               include.rownames=FALSE,
-               caption.placement='top',
-               hline.after=c(-1, 0, 2, 7, 7))
-
-```
-
-Next we recrate the SVM percentile heat maps.
-
-```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- ## create data and re-estimate the percentiles
-
-  pot.data.ic <- str_df.ic
-
-  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
-
- ## Make the pecentile heatmap
-
-  pqtl.hm <- abbHeatMap(pot.data.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.pot.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
-
- ## Make percentile SVM heatmap
-
-  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.pot.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
-  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
-    xlab('Occupancy Rate (Pcntl)') +
-  annotate("text", x = 50, y = 50, label = "Potential", size=9)
-
- ## Add annotations to previous SVM
-
-  qtl.hm.svm.p <- qtl.hm.svm +
-  annotate("text", x = 50, y = 50, label = "Actual", size=9)
-
-```
-
-```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
-
-  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
+  pot_glms <- list(str=glm_pot_str,
+                   loc=glm_pot_loc,
+                   host=glm_pot_host)
 
@@
 
-  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
-  geom_density(fill=str.col, color=str.col) +
+  ggplot(str_tdf, aes(x=block_rate)) + 
+    geom_density(fill=str_col, color=str_col) +
     ylab('Frequency\n') + 
@@
 
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.block.freq
-
-  dev.off()
-
-  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
-
 ```
@@
 
-  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
-  geom_point(fill=str.col, color=str.col, size=.2) +
+  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * extr_par)) + 
+    geom_point(fill=str_col, color=str_col, size=.2) +
     ylab('Nbr of Blocked Periods\n') + 
@@
 
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    block.rate.period
-
-  dev.off()
-
-  block.rate.period
-
-  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
-
 ```
@@
 
-str_df.ic$blockpertime <- round(str_df.ic$nbr.block * str_df.ic$extr.par, 1)
+  str_tdf$blockpertime <- round(str_tdf$nbr_block * str_tdf$extr_par, 1)
 
-str_df.ic$host.type <- 'Unknown'
-str_df.ic$host.type[str_df.ic$blockpertime > 12] <- 'Multi-Platform User'
-str_df.ic$host.type[str_df.ic$block.rate <= .25] <- 'Profit Seeker'
-str_df.ic$host.type[str_df.ic$block.rate >= .75] <- 'Opportunistic Sharer'
-str_df.ic$host.type <- factor(str_df.ic$host.type,
+  str_tdf$host_type <- 'Unknown'
+  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
+  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
+  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
+  str_tdf$host_type <- factor(str_tdf$host_type,
                               levels=c('Profit Seeker', 'Opportunistic Sharer', 
@@
 
-host.type <- ggplot(str_df.ic, 
-       aes(x=block.rate, y=blockpertime, color=host.type)) + 
+ ggplot(str_tdf, 
+       aes(x=block_rate, y=blockpertime, color=host_type)) + 
   geom_point(alpha=.5, size=.8, shape=16) +
@@
                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-
-  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
+    scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
+                                col_df$rgb[9])) + 
     theme(legend.position='bottom',
@@
                                                      alpha=1)))
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type
-
-  dev.off()
-
-  host.type
-
-  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
-
-```
-
-See the counts of each group
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
-  geom_bar() +
-  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-  theme(legend.position='none') +
-  ylab('Frequency\n') + 
-  xlab('\nHost Type') +
-  ggtitle('Short Term Host Types') + 
-  theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type.bar
-
-  dev.off()
-
-  host.type.bar
-
-  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
-
-```
-
-We then re-estimate the preference table.
-
-```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='host.type')
-
- # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
-  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
-  hpref.table <- hpref.table[,1:2]
-  hpref.table[,3] <- phpref.table[,2]
-  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
-  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
-
-  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
-  options(xtable.comment = FALSE)
-  print(xtable(hpref.table, 
-               caption='Host Type Preferability\n',
-               digits=1,
-               align='llrr'),
-               include.rownames=FALSE,
-               caption.placement='top')
 
@@
 
-  ps <- which(str_df.ic$host.type == 'Profit Seeker')
-  os <- which(str_df.ic$host.type == 'Opportunistic Sharer')
-  mu <- which(str_df.ic$host.type == 'Multi-Platform User')
-  un <- which(str_df.ic$host.type == 'Unknown')
+  ht_. <- split(str_tdf, str_tdf$host_type)
 
-  mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[ps,])
+  lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))
 
-  mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[os,])
+  pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))
 
-  mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[mu,])
+  lik_ht_glms <- purrr::map(ht_.,
+                         .f=glm,
+                         formula=lik_spec,
+                         family=binomial(link='logit'))
 
-  mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[un,])
-
-  mod.act.ps <- glm(str.act.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[ps,])
-
-  mod.act.os <- glm(str.act.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[os,])
-
-  mod.act.mu <- glm(str.act.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[mu,])
-
-  mod.act.un <- glm(str.act.pref~type+as.factor(bedbath)+
-                    geo.mrkt+
-                    I(max.guests/bedrooms)+min.stay+
-                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
-                 family=binomial(link='logit'),
-                 data=str_df.ic[un,])
-
-host.models <- list(mod.act.ps, mod.act.os, mod.act.mu, mod.act.un,
-                    mod.pot.ps, mod.pot.os, mod.pot.mu, mod.pot.un)
-names(host.models) <- c('act.ps', 'act.os', 'act.mu', 'act.un',
-                        'pot.ps', 'pot.os', 'pot.mu', 'pot.un')
+  pot_ht_glms <- purrr::map(ht_.,
+                         .f=glm,
+                         formula=pot_spec,
+                         family=binomial(link='logit'))
 
@@
 
-  save(clean.count, daily_df, listing.data, ltr.data, pref.table,
-       pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
-       pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
-       str_df, str_df.ic, subs,
-       core.suburbs,  exch.rate, host.models, pref.models, prem.models,
-       file=file.path(data.path, 'analyzed', paste0('analyzed_workspace_', data_name, 
-                                                    '.RData')))
-
-  save(str_df.ic, subs, abb.col, file=file.path(data.path,'analyzed', 
-                                                paste0('shinyinput_', data_name, 
-                                                       '.RData')))
-
- #all.mwl.coefs, all.mwl.surfs,est.points,  s.subs, sssubs,
+  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
+       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, 
+       file=file.path(data_path, 'analyzed', 'analyzed_data.RData'))
 
 ```
-
-<!-- ### Moving Window Logit -->
-
-<!-- To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.
-Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties.
--->
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'), -->
-<!--                               proj4string=CRS("+init=epsg:4283"), -->
-<!--                               delete_null_obj=TRUE) -->
-
-<!--  ssubs <- table(str_df.ic$suburb) -->
-<!--  s.subs <- subs[subs$id %in% names(ssubs),] -->
-<!--  s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),] -->
-<!--  sssubs <- fortify(s.suburbs) -->
-
-<!-- ``` -->
-
-<!-- Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  # Min, Max and Range -->
-<!--  xmin <- min(s.subs$long) -->
-<!--  xmax <- max(s.subs$long) -->
-<!--  ymin <- min(s.subs$lat) -->
-<!--  ymax <- max(s.subs$lat) -->
-<!--  xrange <- xmax-xmin -->
-<!--  yrange <- ymax-ymin -->
-
-<!--  # Set Scale -->
-<!--  scale <- mean(xrange, yrange)/100 -->
-
-<!--  # Create estimation points -->
-<!--  est.data <- str_df.ic -->
-<!--  est.points <- createGridPoints(s.suburbs, scale, T) -->
-
-<!-- ``` -->
-
-<!-- We then specify the logistic regression model and set the moving window bandwidth.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  ## Set model specification   -->
-
-<!--  pot.mod.spec <- str.pot.pref ~ type + as.factor(bedbath) +  -->
-<!--    I(max.guests / bedrooms) + min.stay +  -->
-<!--    I(cancel.policy == 'Flexible') +  -->
-<!--    I(cancel.policy == 'Strict') -->
-
-<!--  act.mod.spec <- str.act.pref ~ type + as.factor(bedbath) +  -->
-<!--    I(max.guests / bedrooms) + min.stay +  -->
-<!--    I(cancel.policy == 'Flexible') +  -->
-<!--    I(cancel.policy == 'Strict') -->
-
-<!--  ## Set bandwidth -->
-
-<!--  k <- 400 -->
-
-<!-- ``` -->
-
-<!-- The results are estimated with the custom MWL function -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  pot.results.all <- mwl(est.data,  -->
-<!--                         est.points,  -->
-<!--                         pot.mod.spec,  -->
-<!--                         k) -->
-
-<!--  act.results.all <- mwl(est.data,  -->
-<!--                         est.points,  -->
-<!--                         act.mod.spec,  -->
-<!--                         k) -->
-
-<!--   pot.results.ps <- mwl(est.data[ps, ],  -->
-<!--                         est.points,  -->
-<!--                         pot.mod.spec,  -->
-<!--                         k) -->
-<!--    pot.results.os <- mwl(est.data[os, ],  -->
-<!--                         est.points,  -->
-<!--                         pot.mod.spec,  -->
-<!--                         k) -->
-
-<!--    pot.results.mu <- mwl(est.data[mu, ],  -->
-<!--                         est.points,  -->
-<!--                         pot.mod.spec,  -->
-<!--                         k) -->
-
-<!--    pot.results.un <- mwl(est.data[un, ],  -->
-<!--                         est.points,  -->
-<!--                         pot.mod.spec,  -->
-<!--                         k) -->
-
-<!--    act.results.ps <- mwl(est.data[ps, ],  -->
-<!--                         est.points,  -->
-<!--                         act.mod.spec,  -->
-<!--                         k) -->
-<!--    act.results.os <- mwl(est.data[os, ],  -->
-<!--                         est.points,  -->
-<!--                         act.mod.spec,  -->
-<!--                         k) -->
-
-<!--    act.results.mu <- mwl(est.data[mu, ],  -->
-<!--                         est.points,  -->
-<!--                         act.mod.spec,  -->
-<!--                         k) -->
-
-<!--    act.results.un <- mwl(est.data[un, ],  -->
-<!--                         est.points,  -->
-<!--                         act.mod.spec,  -->
-<!--                         k) -->
-
-<!-- ``` -->
-
-<!-- Coefficents are extracted and put into a data.frame -->
-
-<!-- MAKE A FUNCTION BELOW HERE -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!-- extrMWLCoef <- function(mwl.results, -->
-<!--                         est.points, -->
-<!--                         names.coef){ -->
-
-<!--  coef.names <- rownames(mwl.results[[1]]) -->
-
-<!--  # Create a list to capture -->
-<!--  coef.list <- list() -->
-
-<!--  # Create a data.frame to capture -->
-<!--  coef.df <- data.frame(lat=est.points@coords[,2], -->
-<!--                        long=est.points@coords[,1]) -->
-
-<!--  # Loop through and extract coefficients -->
-<!--  for(cn in 1:length(coef.names)){ -->
-<!--    coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn]) -->
-<!--    coef.df[ ,ncol(coef.df) + 1] <- unlist(coef.list[[cn]]) -->
-<!--  } -->
-
-<!--  # Add plottable names -->
-<!--  colnames(coef.df)[3:13] <- names.coef -->
-
-<!--  return(coef.df) -->
-
-<!-- } -->
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!-- x.names <- c('intercept', 'house', 'bb11', 'bb21', 'bb31', -->
-<!--                               'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict') -->
-
-<!-- pra.coef <- extrMWLCoef(pot.results.all, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- era.coef <- extrMWLCoef(act.results.all, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- prp.coef <- extrMWLCoef(pot.results.ps, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- pro.coef <- extrMWLCoef(pot.results.os, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- prm.coef <- extrMWLCoef(pot.results.mu, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- pru.coef <- extrMWLCoef(pot.results.un, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- erp.coef <- extrMWLCoef(act.results.ps, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- ero.coef <- extrMWLCoef(act.results.os, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- erm.coef <- extrMWLCoef(act.results.mu, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- eru.coef <- extrMWLCoef(act.results.un, -->
-<!--                         est.points, -->
-<!--                         x.names) -->
-<!-- all.mwl.coefs <- list(pra.coef, era.coef, prp.coef, pro.coef, prm.coef, pru.coef, -->
-<!--                   erp.coef, ero.coef, erm.coef, eru.coef) -->
-<!-- names(all.mwl.coefs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru',  -->
-<!--                           'erp', 'ero', 'erm', 'eru') -->
-
-<!-- ``` -->
-
-<!-- Finally, these coefficients are converted to a surface.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!-- makeMWLSurfs <- function(mwl.coefs, -->
-<!--                          est.points){ -->
-
-<!--   # Make capture list -->
-<!--   surf.list <- list() -->
-
-<!--   mwl.coefs <- mwl.coefs[ ,!names(mwl.coefs) %in% c('lat', 'long')] -->
-
-<!--  # Create surfaces -->
-<!--   for(sl in 1:ncol(mwl.coefs)){ -->
-
-<!--    # If NAs -->
-<!--    to.cut <- which(is.na(mwl.coefs[,sl])) -->
-<!--    if(length(to.cut) > 0){ -->
-<!--      surf.points <- est.points[-to.cut,] -->
-<!--      surf.value <- mwl.coefs[-to.cut, sl] -->
-<!--    } else { -->
-<!--      surf.points <- est.points -->
-<!--      surf.value <- mwl.coefs[ , sl] -->
-<!--    } -->
-
-<!--    # Surface estimation -->
-<!--    surf.list[[sl]] <- point2Surface(surf.points,  -->
-<!--                                     surf.value, -->
-<!--                                     .01,  -->
-<!--                                     1.5) -->
-<!--   } -->
-
-<!--   names(surf.list) <- names(mwl.coefs) -->
-
-<!-- return(surf.list)     -->
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!-- pra.surfs <- makeMWLSurfs(pra.coef, -->
-<!--                           est.points) -->
-<!-- era.surfs <- makeMWLSurfs(era.coef, -->
-<!--                           est.points) -->
-
-<!-- prp.surfs <- makeMWLSurfs(prp.coef, -->
-<!--                           est.points) -->
-<!-- pro.surfs <- makeMWLSurfs(pro.coef, -->
-<!--                           est.points) -->
-<!-- prm.surfs <- makeMWLSurfs(prm.coef, -->
-<!--                           est.points) -->
-<!-- pru.surfs <- makeMWLSurfs(pru.coef, -->
-<!--                           est.points) -->
-
-<!-- erp.surfs <- makeMWLSurfs(erp.coef, -->
-<!--                           est.points) -->
-<!-- ero.surfs <- makeMWLSurfs(ero.coef, -->
-<!--                           est.points) -->
-<!-- erm.surfs <- makeMWLSurfs(erm.coef, -->
-<!--                           est.points) -->
-<!-- eru.surfs <- makeMWLSurfs(eru.coef, -->
-<!--                           est.points) -->
-<!-- all.mwl.surfs <- list(pra.surfs, era.surfs, prp.surfs, pro.surfs, prm.surfs, pru.surfs, -->
-<!--                       erp.surfs, ero.surfs, erm.surfs, eru.surfs) -->
-<!-- names(all.mwl.surfs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru', -->
-<!--                           'erp', 'ero', 'erm', 'eru') -->
-<!-- ``` -->

### 2018-05-21 scripts/5_data_viz.Rmd
Re-org Analysis, move viz, etc.

@@
 #
+
+<!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->
+
+<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
+
+<!--   # Actual -->
+<!--    stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')] -->
+<!--    stra.rev$tenure <- 'Short-Term (Actual)   ' -->
+<!--    names(stra.rev)[2] <- 'revenue' -->
+
+<!--   # Potential -->
+<!--    strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')] -->
+<!--    strp.rev$tenure <- 'Short-Term (Potential)   ' -->
+<!--    names(strp.rev)[2] <- 'revenue' -->
+
+<!--   # Long-Term -->
+<!--    ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')] -->
+<!--    ltr.rev$tenure <- 'Long-Term   ' -->
+<!--    names(ltr.rev)[2] <- 'revenue' -->
+
+<!--   # Combine -->
+<!--    revdens.data <- rbind(stra.rev, strp.rev, ltr.rev) -->
+
+<!--   ## Build a plot -->
+
+<!--    rd.plot <- ggplot(revdens.data,  -->
+<!--                      aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--      geom_density(alpha=.5) + -->
+<!--      scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--      scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--      xlab('\nAnnual Revenue') + -->
+<!--      scale_x_continuous(breaks=c(seq(0, 75000, by=25000)), -->
+<!--                         labels=c('$0', '$25k', '$50k', '$75k'))+ -->
+<!--      theme(legend.position='none', -->
+<!--            legend.title = element_blank(), -->
+<!--            plot.title = element_text(hjust = 0.5), -->
+<!--            axis.text.y = element_blank(), -->
+<!--            axis.ticks.y = element_blank(), -->
+<!--            axis.title.y=element_blank()) + -->
+<!--      coord_cartesian(xlim=c(0, 85000)) -->
+<!--      rd.plot <- rd.plot + facet_wrap(~tenure) -->
+
+<!--   ## Plot -->
+
+<!--      rd.plot -->
+
+<!-- ``` -->
+
+<!-- ## Results -->
+
+<!-- Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Set Preference data field -->
+
+<!--   str_df.ic$pref <- str_df.ic$str.act.pref -->
+
+<!--  ## Calculate the percentile fields -->
+
+<!--   str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate,  -->
+<!--                                       return.type='rank')  -->
+<!--   str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate,  -->
+<!--                                   return.type='rank')  -->
+
+<!--  ## Calculate raw and percentile occupancies -->
+
+<!--   rawocc.metro <- abbPrefPlot(str_df.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5) -->
+
+<!--   qtlocc.metro <- abbPrefPlot(str_df.ic, -->
+<!--                         x.field='occ.qtl', -->
+<!--                         smooth=TRUE, -->
+<!--                         smooth.span=.5) -->
+
+<!--    ## Make plots   -->
+
+<!--   # Raw -->
+<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Quantile -->
+<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Make Plot -->
+<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   rate.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.rate', -->
+<!--                 y.field='med.rate', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   rate.hm + ylab('Nightly Rate') -->
+
+<!-- ``` -->
+
+<!-- To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.  -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                             x.field='occ.rate', -->
+<!--                             y.field='med.rate', -->
+<!--                             pref.field='str.act.pref', -->
+<!--                             svm=T,  -->
+<!--                             alpha.count=F, -->
+<!--                             add.points=T, -->
+<!--                             fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   rate.hm.svm+ ylab('Nightly Rate') -->
+
+<!-- ``` -->
+
+<!-- As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
+-->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.qtl', -->
+<!--                 y.field='rate.qtl', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   qtl.hm+ ylab('Nightly  (Pcntl)') -->
+
+<!-- ``` -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
+<!--   qtl.hm.svm+ ylab('Nightly  (Pcntl)') -->
+
+<!-- ``` -->
+
+<!-- ### Submarkets -->
+
+<!-- Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.  -->
+
+<!-- First we make a comparison table of the results.   -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table.type <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='type') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ] -->
+
+<!-- ``` -->
+
+<!-- We then turn this into a simple chart to see the differences. -->
+
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) +  -->
+<!--     geom_bar() + -->
+<!--     scale_fill_manual(values=c('red', 'blue')) + -->
+<!--     xlab('') + -->
+<!--     ylab('% of properties where Airbnb is more profitable') + -->
+<!--     scale_y_continuous(breaks=c(0,.25,.5,.75,1), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') -->
+
+<!-- ``` -->
+
+<!-- We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.  -->
+
+<!-- ```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Create dataset -->
+
+<!--   type.data.ic <- str_df.ic -->
+
+<!--   # Id the types -->
+<!--   apt.id <- which(str_df.ic$type == 'Apartment') -->
+<!--   house.id <- which(str_df.ic$type == 'House') -->
+
+<!--   # Recalculate the percentiles -->
+<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
+<!--                                       return.type='rank') -->
+<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->
+
+<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
+<!--                                   return.type='rank') -->
+<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
+<!--     type.data.ic$med.rate[house.id], return.type='rank') -->
+
+<!-- ```  -->
+
+<!-- Then we calculate the preference figures -->
+
+<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
+
+<!--  ## Calc the occ rate numbers -->
+
+<!--   rawocc.type <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.rate', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!--   pctocc.type <- abbPrefPlot(type.data.ic, -->
+<!--                          x.field='occ.qtl', -->
+<!--                          split.field='type', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=c('black', 'grey40')) -->
+
+<!-- ``` -->
+
+<!-- And then plot.  -->
+
+<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
+
+<!--  ## Build raw plot -->
+
+<!--   ptr.occ <- ggplot(rawocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Build Percentile Plots -->
+
+<!--   ptq.occ <- ggplot(pctocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Finally, we make percentile SVM heatmaps for both apartments and houses.  -->
+
+<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
+
+<!--  ## Make House SVM Heatmap -->
+
+<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'House', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
+<!--   theme(legend.position='none') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Make Apartment SVM Heat Map -->
+
+<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'Apartment', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Plot -->
+
+<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- #### Geographic Submarkets -->
+
+<!-- We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets. -->
+
+<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='geo.mrkt') -->
+
+<!--  # Convert to wide format for output -->
+<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
+<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
+<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
+
+<!--  # Fix names   -->
+<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+
+<!--  ## Make printable table -->
+
+<!--   print(xtable(pref.table[,1:2],  -->
+<!--                caption='Geographic Submarket Preferability\n', -->
+<!--                digits=1, -->
+<!--                align='llr'), -->
+<!--         include.rownames=FALSE, -->
+<!--         caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}  -->
+
+<!--  ## Build data -->
+
+<!--   subm.data.ic <- str_df.ic -->
+
+<!--   # Get IDs -->
+<!--   cc.id <- which(str_df.ic$geo.mrkt == 'city-core') -->
+<!--   city.id <- which(str_df.ic$geo.mrkt == 'city') -->
+<!--   sub.id <- which(str_df.ic$geo.mrkt == 'suburban') -->
+<!--   rural.id <- which(str_df.ic$geo.mrkt == 'rural') -->
+<!--   beach.id <- which(str_df.ic$geo.mrkt == 'beach') -->
+
+<!--   # Recalc the percentiles -->
+<!--   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[city.id] <- makeWtdQtl( -->
+<!--       subm.data.ic$occ.rate[city.id], return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[city.id] <- makeWtdQtl( -->
+<!--     subm.data.ic$med.rate[city.id], return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id], -->
+<!--                                   return.type='rank') -->
+
+<!--   subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id], -->
+<!--                                       return.type='rank') -->
+<!--   subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id], -->
+<!--                                   return.type='rank') -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
+
+<!--  ## Set colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
+
+<!--  ## Create plot data -->
+
+<!--   rawocc.geo <- abbPrefPlot(subm.data.ic, -->
+<!--                         x.field='occ.rate', -->
+<!--                         split.field='geo.mrkt', -->
+<!--                         smooth=TRUE, -->
+<!--                         smooth.span=.5 , -->
+<!--                         spl.col=sm.col) -->
+
+<!--   pctocc.geo <- abbPrefPlot(subm.data.ic, -->
+<!--                          x.field='occ.qtl', -->
+<!--                          split.field='geo.mrkt', -->
+<!--                          smooth=TRUE, -->
+<!--                          smooth.span=.5 , -->
+<!--                          spl.col=sm.col) -->
+
+<!--  ## Make plot objects   -->
+
+<!--   smr.occ <- ggplot(rawocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   smq.occ <- ggplot(pctocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'} -->
+
+<!--   # Build the SVM Heatmaps -->
+
+<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city-core', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
+<!--   theme(legend.position='none') + -->
+<!--     ylab('') + -->
+<!--     xlab('') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
+
+<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
+
+<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'suburban', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
+
+<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'rural', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
+
+<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'beach', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('') + -->
+<!--     xlab('')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'} -->
+
+<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
+<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+## Sensitivity
+
+### Potential Revenue
+
+To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.
+
+```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
+
+ # Make Basic comparison table of type
+  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
+                                    split.field='type')
+ # Extract Potential Results
+  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
+
+ # Make baseic comparison table of submarkets  
+  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
+                                    split.field='geo.mrkt')
+
+ # Extract potential results  
+  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
+
+ # Combine and round  
+  st.table <- rbind(tpref.table, spref.table)
+  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
+
+ ## Fix names and print
+
+  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
+  options(xtable.comment = FALSE)
+  print(xtable(st.table[,1:2], 
+               caption='Potential Revenue Preferability\n',
+               digits=1, align='llr'),
+               include.rownames=FALSE,
+               caption.placement='top',
+               hline.after=c(-1, 0, 2, 7, 7))
+
+```
+
+Next we recrate the SVM percentile heat maps.
+
+```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+
+ ## create data and re-estimate the percentiles
+
+  pot.data.ic <- str_df.ic
+
+  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
+
+ ## Make the pecentile heatmap
+
+  pqtl.hm <- abbHeatMap(pot.data.ic,
+                x.field='occ.qtl',
+                y.field='rate.qtl',
+                pref.field='str.pot.pref',
+                svm=F, 
+                alpha.count=T,
+                add.points=T,
+                fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
+
+ ## Make percentile SVM heatmap
+
+  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
+                   x.field='occ.qtl',
+                   y.field='rate.qtl',
+                   pref.field='str.pot.pref',
+                   svm=T, 
+                   alpha.count=F,
+                   add.points=T,
+                   quantile=T,
+                   fill.colors=c(abb.col[1], abb.col[5]))
+  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
+    xlab('Occupancy Rate (Pcntl)') +
+  annotate("text", x = 50, y = 50, label = "Potential", size=9)
+
+ ## Add annotations to previous SVM
+
+  qtl.hm.svm.p <- qtl.hm.svm +
+  annotate("text", x = 50, y = 50, label = "Actual", size=9)
+
+```
+
+```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
+
+  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
+
+```
+
+ ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(str_tdf, aes(x=block_rate)) + 
+    geom_density(fill=str_col, color=str_col) +
+    ylab('Frequency\n') + 
+    xlab('\n% of Time Property is Blocked') +
+    scale_x_continuous(breaks=seq(0,1,.2),
+                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+      ggtitle('Host Block Rate Frequency\n') +
+      theme(plot.title = element_text(hjust = 0.5)) +
+      theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.block.freq
+
+  dev.off()
+
+  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  geom_point(fill=str.col, color=str.col, size=.2) +
+  ylab('Nbr of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+  scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    block.rate.period
+
+  dev.off()
+
+  block.rate.period
+
+  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
+
+```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf$blockpertime <- round(str_tdf$nbr_block * str_tdf$extr_par, 1)
+
+  str_tdf$host_type <- 'Unknown'
+  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
+  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
+  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
+  str_tdf$host_type <- factor(str_tdf$host_type,
+                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                        'Multi-Platform User', 'Unknown'))
+
+ ggplot(str_tdf, 
+       aes(x=block_rate, y=blockpertime, color=host_type)) + 
+  geom_point(alpha=.5, size=.8, shape=16) +
+  ylab('Number of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    scale_color_manual(values=c(col.df$rgb[2], col.df$rgb[4], col.df$rgb[7], col.df$rgb[9])) + 
+    theme(legend.position='bottom',
+           legend.title = element_blank(),
+         plot.title = element_text(hjust = 0.5))+
+     guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1)))
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type
+
+  dev.off()
+
+  host.type
+
+  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
+
+```
+
+See the counts of each group
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
+  geom_bar() +
+  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+  theme(legend.position='none') +
+  ylab('Frequency\n') + 
+  xlab('\nHost Type') +
+  ggtitle('Short Term Host Types') + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+  # Make Plot
+  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
+      bg='transparent')
+
+    host.type.bar
+
+  dev.off()
+
+  host.type.bar
+
+  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
+
+```
+
+We then re-estimate the preference table.
+
+```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
+
+ # Make Basic comparison table
+  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
+                                    split.field='host.type')
+
+ # Limit to the extrapolated pref type
+  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
+  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
+  hpref.table <- hpref.table[,1:2]
+  hpref.table[,3] <- phpref.table[,2]
+  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
+  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
+
+  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
+  options(xtable.comment = FALSE)
+  print(xtable(hpref.table, 
+               caption='Host Type Preferability\n',
+               digits=1,
+               align='llrr'),
+               include.rownames=FALSE,
+               caption.placement='top')
+
+```

### 2018-05-21 functions/abb_Functions.R

@@ -354,12 +354,15 @@ imputeLtrRents <- function(ltr.df,
       s.cf <- which(names(str.df) == match.factor[i.cf])
       
       # Get IDs for those to be removed
-      id.l <- ltr.df[ ,l.cf] %in% names(table(as.character(str.df[ ,s.cf])))
-      id.s <- str.df[ ,s.cf] %in% names(table(as.character(ltr.df[ ,l.cf])))
+      ltr.df <- ltr.df[ltr.df[[l.cf]] %in% str.df[[s.cf]], ]
+      str.df <- str.df[str.df[[s.cf]] %in% ltr.df[[l.cf]], ]
       
-      # Filter out obs missing matched factors  
-      ltr.df <- ltr.df[id.l, ]
-      str.df <- str.df[id.s, ]
+      # id.l <- ltr.df[ ,l.cf] %in% names(table(as.character(str.df[ ,s.cf])))
+      # id.s <- str.df[ ,s.cf] %in% names(table(as.character(ltr.df[ ,l.cf])))
+      # 
+      # # Filter out obs missing matched factors  
+      # ltr.df <- ltr.df[id.l, ]
+      # str.df <- str.df[id.s, ]
       
     }
     
@@ -367,7 +370,7 @@ imputeLtrRents <- function(ltr.df,
   
   ## Add the monthly factors
   
-  str.df$ltr.month <- 12
+  str.df$month <- '2015_8'
   
   ## Build regression models for rental values
   
@@ -379,8 +382,8 @@ imputeLtrRents <- function(ltr.df,
   
   ## Return Values  
   
-  return(list(imp.rent=data.frame(property.id=str.df$property.id,
-                                  imp.rent=imp.rent),
+  return(list(imp_rent=data.frame(property_id=str.df$property_id,
+                                  imp_rent=round(imp.rent, 0)),
               model=ltr.mod))
 }
 
@@ -407,7 +410,7 @@ imputeDOM <- function(str.df,
   
   ## Return Values
   
-  return(str.df$imp.dom)
+  return(round(str.df$imp.dom, 0))
   
 }
 
@@ -495,6 +498,8 @@ abbImputeCompare <- function(str.df,
                              split.field=NULL,
                              verbose=FALSE){
   
+  init_names <- names(str.df)
+  
   ## Split data by field  
   
   # If field is specified
@@ -533,11 +538,11 @@ abbImputeCompare <- function(str.df,
     
[…]

### 2018-05-21 _old/abbDataPrep_Script.Rmd
isolating old code

---
title: "Data Preparation, Integration and Cleaning"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

### Introduction

This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).  Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocess.R** and **2_ltr_preprocess.R**.

&nbsp;
&nbsp;

### Preliminary Commands

&nbsp;

We begin with a number of preliminary commands.  First we load all of the necessary R libraries for this analysis.

```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)

```

We then set the paths to the data and the code, conditional on which of the authors is running the analysis.

```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- getwd()
  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')

```

Next, we source the necessary custom code files for the analysis.

```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

source(file.path(code_path, 'functions', 'abb_Functions.R'))

#
#  # Other custom files
# 
#   if(offline){
# 
#     source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
#     source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))
#     
#   } else {
#     
#   source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
#                 '/master/ggPlotTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
#                 '/master/dataMungeTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/spatialLogitModels.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/point2surface_Tools.R'))
# 
#   }
```

### Constants and Parameters

We then set the constants used in this study:

1. **Exchange rate**: The Airbnb rates are provided in US dollars.  We convert these to Australian dollars based on the average exchange rate over the Sep 1 2015 to Aug 30 2015 period, or about 1.32 Australian dollars to 1 US dollar.

```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

 exch_rate <- 1.32

```

2. **Date of Purchase**: In our analyzis we assume a date on which the decision to Airbnb or to enter into a long-term rental strategy is undertaken.  We set this to September 1, 2015.

```{r set_date}

  decision_date <- lubridate::as_date('2015-09-01')

```

3. Colors for visualizations.  We use the official Airbnb palette of colors for our ongoing data vizualizations.

```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

 # Set all colors

  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255),
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

 # Set specific colors

  str_col <- abb_col[1]
  ltr_col <- abb_col[3]

```

## Loading data

&nbsp;

Next we load in the raw data.  The short-term rental (Airbnb) data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Property Information

  str_df <- readRDS(file.path(data_path, 'prepared', 'st_prop.RDS'))

  # Daily rental information

  daily_df <- readRDS(file.path(data_path, 'prepared', 'st_daily.RDS'))

```

We then load the long term rental data.  This includes property level data (including the final lease rate) and listing-level data containing information on all changes to listing prices and dates, etc.

```{r load_ltr_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 # Property level long term ltral information

  ltr_df <- readRDS(file.path(data_path, 'prepared', 'lt_prop.RDS'))

 # Long term ltral listing information

  list_df <- readRDS(file.path(data_path, 'prepared', 'lt_list.RDS'))

```

And, finally, we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]  After we load each we convert the names of the data fields to lower case for easier use in future coding.

```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Suburb shapefile

  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)
  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))

  # SA1 shapefile

  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)
  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))

  # Beach file

  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
  names(beach_shp@data) <- tolower(names(beach_shp@data))

```

## Data Preparation

&nbsp;

In this section we remove, convert and/or transform a number of data fields. We also remove observations if they are missing critical data or fall outside of the scope of our research question.

&nbsp;

### Trim and Standardize Fields

The data contain many fields that are either not fully observed and/or are not relevant to our research question.  Additionally, the field naming conventions differ between the two datasets. We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.

We start by trimming the property-level short term data.  No fields need to be removed from the daily data.

While trimming the fields we also we standardize the field names.  Here we follow the convention of placing an underscore between words in the name.  We also shorten a number of the fields to make future coding easier.

```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

   str_df <- str_df %>% 
     dplyr::select(property_id=property.id, host_id=host.id, listing_title=listing.title, 
                   property_type=property.type, listing_type=listing.type,
                   created_date=created.date, latitude, longitude, rating=overall.rating,
                   max_guests=max.guests, canc_policy=cancellation.policy, 
                   cleaning_fee=cleaning.fee, nightly_rate=published.nightly.rate, 
                   weekly_rate=published.weekly.rate, monthly_rate=published.monthly.rate, 
                   avg_nightly_rate=average.daily.rate, min_stay=minimum.stay, bedrooms, 
                   bathrooms, min_date=min.date, max_date=max.date, days=total.days, 
                   block_rate=block.rate, avail_rate=avail.rate, 
                   longest_block=longest.block, nbr_blocks=nbr.block, med_block=med.block,
                   created_year=created.year)

  daily_df <- daily_df %>%
    dplyr::select(property_id=property.id, date, status, price, booked_date=booked.date,
                  resv_id=reservation.id)

```

We then limit the fields of the long-term property-specific data

```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ltr_df <- ltr_df %>%
    dplyr::select(id_key=id.key, geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude, event_date=event.date,
                  event_price=eventprice, property_type=propertytype, area_size=areasize,
                  bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage, dom)

  list_df <- list_df %>%
    dplyr::select(id_key=id.key, event_id=eventid, activity_id=activityid, 
                  addr_id=addressid, of_record=of.record, event_date=event.date,
                  event_price=eventprice, first_date=first.adv.date, 
                  first_price=firstadvertisedeventprice, last_date=last.adv.date,
                  last_price=lastadvertisedeventprice, event_code=eventtypecode)

```

### Trim by Time

Next we filter the observations by time.  Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.  To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.  Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).  In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.  Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.  While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.

Before we begin the filter process, we initial the data cleaning counter -- a small function that keeps track of how many observations we remove.

```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

   setCleanCount()

```

# We then clip by time.  For the short-term data we will consider any Airbnb property that had at least 6 months worth of listing time on the portal during the 12-month study period
# 
# ```{r clip_time, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
#  
#  # Limit short term data
#   
#   str_df <- str_df[(str_df$max.date - str_df$min.date) >= 178, ]
#   
#   str_df <- str_df[str_df$max.date >= (strike_date + 182) &
#                          str_df$min.date <= (strike_date + 182), ]
#  
#   daily_df <- daily_df[daily_df$date >= strike_date, ]
# 
#  # Limit long term data  
#   
#   ltr_df <- ltr_df[ltr_df$event.date >= (strike_date - 365) & 
#                             ltr_df$event.date <= (strike_date - 1), ]
#   listing.data <- listing.data[listing.data$id.key %in% ltr_df$id.key, ]
#    
#  # Count cleaning
#   
#   countCleaning('time')
#   
# ```
# 
# Next we add a monthly variable to the data for use in future modeling exercises. 
# 
# ```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Short term data
# 
#   str_df$str.month <- 1
#   daily_df$str.month <- as.numeric(as.factor(substr(daily_df$date, 1, 7)))
# 
#   # Long term data
# 
#   ltr_df$ltr.month <- as.numeric(as.factor(substr(ltr_df$event.date, 1, 7)))
#   listing.data$ltr.month <- as.numeric(as.factor(substr(
#     listing.data$event.date, 1, 7))) - 8
#   
# ```
# 
# ### Standardize Property Types
# 
# &nbsp;
# 
# AirBNB units are classified into 19 different property type.  The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt^[Property types are owner/lister defined, therfore it is likely that the Igloo, at the very least, is not a completely true representation of the property type]. For the sake of this analysis, we will collapse these twenty types into three types:
#   
# 1. **House**:  Includes properties labeled 'House' or 'Townhouse'
# 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
# 3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt. 
# 
# Within the long-term rental data, property types fall into eight categories.  Like the AirBNB data we group these into three categories matching as best as possible to the AirBNB categories:
#   
# 1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
# 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
# 3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
# 
# Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the AirBNB data conforms to North American lexicon.  This is most apparent when talking about apartment dwellings.  In Australia these are referred to as Units, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).  Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context. 
# 
# We then create a new variable in each dataset and give each one of the three categories discussed above.
# 
# ```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Short Term data  
# 
#   str_df$type <- 'Other'
#   str_df$type[str_df$property.type %in% c('Apartment', 'Condominium')] <- 'Apartment'
#   str_df$type[str_df$property.type %in% c('House', 'Townhouse')] <- 'House'
# 
#  # Long Term data  
# 
#   ltr_df$type <- 'Other'
#   ltr_df$type[ltr_df$property.type %in% c('Duplex', 'House',
#                                            'Terrace', 'Townhouse')] <- 'House'
#   ltr_df$type[ltr_df$property.type %in% c('Studio', 'Unit')] <- 'Apartment'
# 
# ```
# 
# As the chart below show, the **Other** category only makes up a very small percentage of the properties in both the short and long term market, especially in the long-term market.  Additionally, a good portion of the **Others** in the Airbnb data are Bed & Breakfast units, a use which doesn't fit with our research question.  As a result, we remove the 'Others' from both the Airbnb and the long term rental data. 
# 
# ```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   # Create Airbnb plot
# 
#   str.types <- ggplot(str_df, aes(x=type)) + 
#     geom_bar(color=str_col, fill=str_col) +
#     xlab('\nProperty Type\n') + 
#     ggtitle('\nShort Term Rentals\n')  +
#     ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#   # Create long term rental plot
# 
#   ltr.types <- ggplot(ltr_df, aes(x=type)) + 
#     geom_bar(color=ltr_col, fill=ltr_col) +
#     xlab('\nProperty Type\n') + 
#     ggtitle('\nLong Term Rentals\n')  +
#     ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#   
#   
#   # Output plots
#   png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280, 
#       bg='transparent')
#     ggMultiPlots(str.types, ltr.types, cols=2)
#   dev.off()
#   
#   save(str.types, file=paste0(fig.path, 'strtypes.RData'))
#   save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))
#   
# ```
# 
# ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   str_df <- subset(str_df, type != 'Other')
#   ltr_df <- subset(ltr_df, type != 'Other')
#   
#   # Count Cleaning
#   countCleaning('property.type')
# 
# ```
# 
# Next, for the short term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
# 
# 1. **Entire Home/Apt**: The entire home or apartment is available
# 2. **Private Room**: One room within a house or apartment is available
# 3. **Shared Room**: A bed within a room shared by another occupant(s) is available
# 
# As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accomodations and other types of rental which may offer private or shared room options] and our purpose here is a comparison of long and short term returnw, we remove all short term properties that do not lease the entire home/apt. Unfortunately, this filter does remove about 40% of the short term data, however, given the research question it is unavoidable. 
# 
# ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}
# 
#   # Fix data types and names
#   str_df$listing.type <- as.character(str_df$listing.type)
#   str_df$listing.type[str_df$listing.type == 'Entire home/apt'] <- 'Entire home'
# 
#   list.types <- ggplot(str_df, aes(x=listing.type)) + 
#       geom_bar(color=str_col, fill=str_col) +
#       xlab('\nListing Type\n') + 
#       ggtitle('\nShort Term Rentals by Listing Type\n')  +
#       ylab('# of Properties\n') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#   
#   # Make Plot
#   png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280, 
#       bg='transparent')
# 
#     list.types
#   
#   dev.off()
#   
#   save(list.types, file=paste0(fig.path, 'listtypes.RData'))
#   
#   
# ```
# 
# ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   str_df <- str_df[str_df$listing.type == 'Entire home', ]
#   
#   # Count cleaning 
#   countCleaning('listing.type')
#   
# ```
# 
# ## Structural Characteristics
# 
# &nbsp;
# 
# In this section we transform and filter based on the structural characteristics of the properties. 
# 
# ### Fix Boolean Variables
# 
# Before beginning, we fix a few of the boolean variables in the long term data that are stored in a non-compatible format.
# 
# ```{r fix_lt_bools, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   ltr_df$has.study <- ifelse(ltr_df$has.study == 'True', 1, 0)
#   ltr_df$has.courtyard <- ifelse(ltr_df$has.courtyard == 'True', 1, 0)
#   ltr_df$has.aircon <- ifelse(ltr_df$has.aircon == 'True', 1, 0)
#   ltr_df$has.balcony <- ifelse(ltr_df$has.balcony == 'True', 1, 0)
#   ltr_df$has.garage <- ifelse(ltr_df$has.garage == 'True', 1, 0)
# 
# ```
# 
# &nbsp;
# 
# ### Bedrooms
# 
# We start by looking at bedrooms. We begin by removing all properties that are missing bedrooms information or have a likely data error in this fields (more than 14 bedrooms). We then plot the distribution of diffeltr bedrooms counts.  From this point onwards we bifurcate our analysis between houses and apartments as the markets (prices, rates, and properties) differ between the two property types. 
# 
# ```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove missing and data errors
# 
#   # Long term data
#   ltr_df <- ltr_df[!is.na(ltr_df$bedrooms), ]
#   ltr_df <- ltr_df[ltr_df$bedrooms <= 10, ]
# 
#   # Short term data
#   str_df <- str_df[!is.na(str_df$bedrooms), ]
#   str_df <- str_df[str_df$bedrooms <= 10, ]
# 
# ```
# 
# ```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Build long term bar plot
# 
#    ltrbed <- ggplot(ltr_df, aes(x=bedrooms)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     facet_wrap(~type,scales='free_y') +
#     scale_x_continuous(labels=1:10, breaks=1:10)+
#     xlab('\nBedrooms\n') +
#     scale_y_continuous(labels=c(0,10000,20000), 
#                        breaks=c(0,10000,20000))+
#     ylab('') +
#     ggtitle('Bedrooms in Long Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#  # Build short term bar plot
# 
#   strbed <- ggplot(str_df, aes(x=bedrooms)) + 
#     geom_bar(fill=str_col, color=str_col) +
#     facet_wrap(~type,scales='free_y') +
#     scale_x_continuous(labels=0:10, breaks=0:10) +
#     xlab('\nBedrooms\n') +
#     ylab('') +
#     ggtitle('Bedrooms in Short Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#   # Make Plot
#   png(file=paste0(fig.path, 'dataclean_bedcount.png'), width = 480, height = 280, 
#       bg='transparent')
#     ggMultiPlots(strbed, ltrbed, cols=1)
#   dev.off()
#   
#   save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
#   save(strbed, file=paste0(fig.path, 'strbed.RData'))
# 
# ```
# 
# For both short and long term rentals we see that most apartments have less than 4 bedrooms and houses less than 5.  We filter the data accordingly. Additionally, note that short term rentals consider studio apartments to be 0 bed units while the long term data considers these as 1 bedroom. We convert the 0 bed short term units to 1 bed units.   
# 
# ```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove all with more than 4 beds
# 
#   str_df <- str_df[str_df$bedrooms < 5, ]
#   ltr_df <- ltr_df[ltr_df$bedrooms < 5, ]
# 
#  # Remove apartments with more than 3
#   
#   str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
#   ltr.id <- which(ltr_df$bedrooms > 3 & ltr_df$type =='Apartment')
# 
#   if(length(str.id) > 0) str_df <- str_df[-str.id, ]
#   if(length(ltr.id) > 0) ltr_df <- ltr_df[-ltr.id, ]
# 
#   # Convert 0 Bed to 1 Bed  
#   str_df$bedrooms[str_df$bedrooms == 0] <- 1
#   
#   # Count Data Cleaning
#   countCleaning('bedrooms')
# 
# ```
# 
# ### Bathrooms
# 
# We then turn to bathrooms, starting by looking at the distribution of baths between short/long and apt/house.  
# 
# ```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Remove missing data
#   
#   ltr_df <- ltr_df[!is.na(ltr_df$baths), ]
#   str_df <- str_df[!is.na(str_df$baths), ]
# 
# ```
# 
# ```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Build long term plot
# 
#   ltbath <- ggplot(ltr_df, aes(x=baths)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     facet_wrap(~type) +
#     scale_x_continuous(labels=1:8, breaks=1:8)+
#     xlab('\nBathrooms\n') +
#     ylab('') + 
#     ggtitle('Bathrooms in Long Term Rentals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
# 
#  # Build short term plot 
# 
#   stbath <- ggplot(str_df, aes(x=baths)) + 
#     geom_bar(fill=str_col, color=str_col) +
#     facet_wrap(~type, scales='free_y') +
#     scale_x_continuous(labels=0:8, breaks=0:8)+
#     xlab('\nBathrooms\n') +
#     ylab('') + 
#     ggtitle('Bathrooms in Short Term ltrals') +
#     theme(plot.title = element_text(hjust = 0.5)) 
#  
#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bathount.png'), width = 480, height = 280, 
#       bg='transparent')
#   
#     ggMultiPlots(stbath, ltbath, cols=1)
#     
#   dev.off()
#    
#   save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
#   save(stbath, file=paste0(fig.path, 'strbath.RData'))
#  
# ```
# 
# Here we see that nearly all properties have 3 or fewer bathrooms and we filter the data accordingly. A few short term properties state no baths, which is likely an error so we remove these as well. Also, here we notice that the short term data gives bathrooms in halves, while the long term data presents baths in whole numbers.  We round the baths up to whole integers. 
# 
# ```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Filter by bath count
# 
#   # Short term data
#   str_df <- str_df[str_df$baths < 4, ]
#   str_df <- str_df[str_df$baths > 0, ]
# 
#   # Long term data
#   ltr_df <- ltr_df[ltr_df$baths < 4, ]
#   
#  # Round baths up  
# 
#   str_df$baths <- round(str_df$baths + .01, 0)
# 
#   # Count cleaning
#   countCleaning('baths')
#   
# ```
# 
# ### Bed/Bath Combination
# 
# In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.  In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.  As a result we examine the combinations of the two. 
# 
# ```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Create combination variable
# 
#   ltr_df$bedbath <- paste0(ltr_df$bedrooms, '..', ltr_df$baths)
#   str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)
# 
# ```
# 
# ```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}
# 
#  # Make long term plot
# 
#   ltbb <- ggplot(ltr_df, aes(x=bedbath)) + 
#     geom_bar(fill=ltr_col, color=ltr_col) +
#     xlab('\nBed/Bath Combo\n') +
#     ylab('Number of Properties\n') +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#     ggtitle('Long Term Rentals') + 
#     facet_wrap(~type, scales='free_y')+
#     theme(plot.title = element_text(hjust = 0.5))
# 
#  # Make short term plots
# 
#   stbb <- ggplot(str_df, aes(x=bedbath)) +
#     geom_bar(fill=str_col, color=str_col) + 
#     xlab('\nBed/Bath Combo\n') +
#     ylab('Number of Properties\n') +
#     ggtitle('Short Term Rentals') + 
#     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#     facet_wrap(~type, scales='free_y')+
#     theme(plot.title = element_text(hjust = 0.5))
# 
#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bedbath.png'), width = 480, height = 280, 
#       bg='transparent')
#   
#     ggMultiPlots(ltbb, stbb, cols=1)
# 
#   dev.off()  
#   
#   save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
#   save(stbb, file=paste0(fig.path, 'strbb.RData'))
# 
#     
# ```
# 
# From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.  
# 
# ```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Set level of acceptable combinations
# 
#   acc.bb <- c('1..1', '2..1', '2..2', '3..1', '3..2', '4..2')
# 
#  # Filter data
# 
#   ltr_df <- ltr_df[ltr_df$bedbath %in% acc.bb, ]
#   str_df <- str_df[str_df$bedbath %in% acc.bb, ]
# 
#  # Count Cleaning
#   
#   countCleaning('bedbath')
# 
# ```
# 
# Finally, we re-order the factor levels on the bed/bath combinations to make a 2-bed, 2-bath house or apartment the control case in future statistical models.  We additionally create a product variable that splits the bed/bath by apartment and house.
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Re-order factors
# 
#   str_df$bedbath <- factor(str_df$bedbath, 
#                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
#   ltr_df$bedbath <- factor(ltr_df$bedbath, 
#                                levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
# 
#   # Add product as a variable
#   
#   str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
#   ltr_df$product <- paste0(substr(ltr_df$type, 1, 1), ltr_df$bedbath)
# 
# ```
# 
# 
# ## Rates and Rental values
# 
# We now turn to filtering by the prices -- the nightly rates and weekly rental values.  We start by removing observations missing price data. 
# 
# ```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   ltr_df <- ltr_df[!is.na(ltr_df$event.price), ]
#   str_df <- str_df[!is.na(str_df$nightly.rate), ]
#   
# ```
# 
# Next, we convert the Airbnb values to Australian dollars from US dollars using the exchange rate specified above (1.32).
# 
# ```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Property level data
# 
#   str_df$average.daily.rate <- str_df$average.daily.rate * exch.rate
#   str_df$nightly.rate <- str_df$nightly.rate * exch.rate
#   str_df$weekly.rate <- str_df$weekly.rate * exch.rate
#   str_df$monthly.rate <- str_df$monthly * exch.rate
#   
#   # Daily data
#   
#   daily_df$price <- daily_df$price * exch.rate
# 
# ```
# 
# Next we extract all of the daily reservation data for the reserved nightly. From this information we calculate the median nightly reservation price for each property and append it to the property level data. 
# 
# ```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#    # Get all of the reservations
#   resv.daily <- daily_df[daily_df$status == 'R', ]
# 
#   # Calculate the property specific median nightly rate
#   med.daily <- tapply2DF(resv.daily$price, resv.daily$property.id, median)
#   
#   # Add median rate to the property  
#   str_df$med.rate <- med.daily$Var[match(str_df$property.id, med.daily$ID)] 
#   
#   # Remove those with no valid median rate
#   str_df <- str_df[!is.na(str_df$med.rate), ]
#    
# ```
# 
# From these density plots we see that most long-term Rentals are greater than $200 and less than $1000 per week while most nightly rates are greater than $50 and less than $500 per night. We filter the data accordingly. 
# 
# ```{r ltprice_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # ltr Plot
#   
#   ltr.plot <- ggplot(ltr_df, aes(x=event.price)) + 
#     geom_density(fill=ltr_col, alpha=.8) +
#     ylab('') +
#     xlab('Weekly Rental') + 
#     ggtitle('Long Term Rentals') + 
#     scale_x_continuous(limits=c(0, 1500)) +
#     theme(axis.title.y=element_blank(),
#           axis.text.y=element_blank(),
#           axis.ticks.y=element_blank()) +
#     theme(plot.title = element_text(hjust = 0.5))
# 
# 
#   # Nightly Rate plot
#   rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
#     geom_density(fill=str_col, alpha=.8) + 
#     ylab('') +
#     xlab('Nightly Rate') +
#     ggtitle('Short Term Rentals') + 
#     scale_x_continuous(limits=c(0, 600)) +
#     theme(axis.title.y=element_blank(),
#           axis.text.y=element_blank(),
#           axis.ticks.y=element_blank()) +
#     theme(plot.title = element_text(hjust = 0.5))
# 
# 
# ```
# 
# ```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   png(file=paste0(fig.path, 'dataclean_rates.png'), width = 480, height = 280, 
#       bg='transparent')
#     
#     ggMultiPlots(ltr.plot, rate.plot, cols=2)
#   
#   dev.off()
#   
#   save(ltr.plot, file=paste0(fig.path, 'rentplot.RData'))
#   save(rate.plot, file=paste0(fig.path, 'rateplot.RData'))
# 
#   
# ```
# 
# ```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   ## Filter the long term data
# 
#   ltr_df <- ltr_df[ltr_df$event.price >= 200 & 
#                          ltr_df$event.price <= 1000, ]
# 
#   str_df <- str_df[str_df$med.rate >= 50 &
#                          str_df$med.rate <= 500, ]
# 
#   # Count Cleaning
#   countCleaning('rates.rents')
#   
# ```  
# 
# #### Observed Revenue
# 
# Our final data filtering considers the observed revenue of the properties. For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.  In a number of extreme cases, time on market was extremely long and the total observed revenues very low. To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.
# 
# For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.  Using this data we sum up the total revenue from bookings. For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
# 
# Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.
# 
# ```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
# 
#  # Compute bookings count
# 
#   str_df$bookings <- round(str_df$total.days * 
#                                (1 - (str_df$block.rate + str_df$avail.rate)), 0)
#  
#  # Remove those with 0 
# 
#   str_df <- str_df[str_df$bookings > 0, ]
# 
#   str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
#   ltr_df$gross.revenue <- ltr_df$event.price * (52 - ltr_df$dom / 7)
#  
#   str.small <- str_df[,c('baths', 'gross.revenue')]
#   str.small$tenure <- 'short-term'
#   ltr.small <- ltr_df[,c('baths', 'gross.revenue')]
#   ltr.small$tenure <- 'long-term'
#   all.small <- rbind(str.small, ltr.small)
# 
#   revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
#     geom_density(alpha=.5) +
#     scale_fill_manual(values=c(ltr_col, abb_col)) +
#     scale_color_manual(values=c(ltr_col, abb_col)) +
#     ggtitle('Annual Revenues by Tenure Type') +
#     xlab('Annual Revenue') +
#     scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
#                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+
#     theme(legend.position='bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           axis.text.y = element_blank(),
#           axis.ticks.y = element_blank(),
#           axis.title.y=element_blank()) +
#     coord_cartesian(xlim=c(0, 70000))
#   
# ```
# 
# ```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
#       bg='transparent')
#     
#     revdens
#   
#   dev.off()
#   
#   save(revdens, file=paste0(fig.path, 'revdens.RData'))
#   
#   ltr_df <- ltr_df[ltr_df$dom <= 180, ]
#   
#     countCleaning('revenue')
#   
# ```
# 
# ### Locations and Submarkets
# 
# Location is clearly an important determinant in both the short and long term rental markets. At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.  In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high end neighborhoods in the east and southeastern areas of the middle suburbs.  Suburbs in Melbourne are much smaller than their North American counterparts.  The specific suburb of a property is the second, or finer scale, at which the market operates. The plot below shows the three large submarkets (Inner, Middle and Outer).
# 
# ```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Convert shapefile to ggplot-able object
#   
#   # Fix lat/long
#  
#   # Limit to extent of data
#   sub.table <- table(ltr_df$suburb)
#   sub.table <- sub.table[sub.table != 0]
#   
#   # Clip to only those with a ltral observation
#   study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
#   
#   # Convert to an outer bound with holes
#   ss.bound <- gUnaryUnion(study.suburbs)
#   
#   # Remove holes from the shapefile
#   ssb <- slot(ss.bound, "polygons") 
#   holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound) 
#   ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
#    Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
#   
#   # Identify which suburbs all in area covered by outer bound
#   ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
#   study.suburbs <- suburbs.shp[which(ss.in), ]
#   
#   # Convert into an outer boundary with no holes
#   ss.bound.out <- gUnaryUnion(study.suburbs)
#   ssb.out <- slot(ss.bound.out, "polygons") 
#   holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res.out <- lapply(1:length(ssb.out), 
#                     function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound.out) 
#   ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
#                                          function(i) Polygons(res.out[[i]], 
#                                                               ID=IDs[i])),
#                                               proj4string=CRS(proj4string(ss.bound))) 
#   
#   # Convert into a ggplot-able format
#   subs <- fortify(study.suburbs, region='name_2006')
# 
#   # Add suburb category
#   subs$des <- suburbs.shp@data$suburbdesi[
#     match(subs$id, suburbs.shp@data$name_2006)]
# 
# ```
# 
# ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#  ## Build the map object
# 
#   # Set colors
#   g_cols <- c('grey10', 'grey40', 'grey70')
# 
#   # Make map
#   loc.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
#     scale_fill_manual(values=g_cols, labels=c('Inner      ',
#                                               'Middle      ',
#                                               'Outer')) +
#     geom_path(data=subs[subs$des=='Outer', ], 
#               aes(x=long, y=lat, group=group), col='white', size=.1,
#               linetype=1) +
#   
#     geom_path(data=subs[subs$des=='Middle', ], 
#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
#               linetype=1) +
#     
#     geom_path(data=subs[subs$des=='Inner', ], 
#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
#               linetype=1) +
#     
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     #ggtitle("Melbourne Suburb Classifications")+
#     theme(plot.title = element_text(hjust = 0.5))
# 
# ```
# 
# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
#       bg='transparent')
#   
#     loc.map
#     
#   dev.off()
#   
#   loc.map
#   
#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
# 
#     
# ```
# 
# It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
# 
# 1. Rural (Outer suburbs, not Beach)
# 2. Suburban (Middle suburbs, not Beach)
# 3. City (Inner Suburbs, not Beach, not Core)
# 4. City-Core (Select inner suburbs with tourist activities and near CBD)
# 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
# 
# We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.  This process is repeated for both the short and long term data.  We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on. Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs). 
# 
# We select the 18 suburbs below to represent the 'core' of the city.  The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.  All are well serviced by public transportation and possess abundant amenties for tourists. 
# 
# ```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
#                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
#                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
#                    'St Kilda West', 'West Melbourne', 'Windsor')
# 
# ```
# 
# We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
# 
# ```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Determine centroid of study area
#  
#   latMid <- median(str_df$latitude)
#   longMid <- median(str_df$longitude)
# 
#  # Calculate Degress to Meters conversion 
#  
#   m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
#   m.long = 111132.954 * cos (latMid)
#   m.conv <- mean(m.lat, m.long)
#  
#  # Create the beach buffer  
#   
#   beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
# 
# ```
# 
# Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.  
# 
# ```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Short term data  
# 
#   # Convert to point shapefile
#   str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
#                                                str_df$latitude),
#                                          str_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
# 
#   # Add suburb name 
#   spJoin <- over(str.prop.shp, suburbs.shp)
#   str_df$suburb <- as.character(spJoin$name_2006)
#   str_df$suburb[is.na(str_df$suburb)] <- 'missing'
# 
#   # Add suburb designation
#   str_df$sub.class <- as.character(spJoin$suburbdesi)
#   str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'
#   
#   # Add SA1 designation
#   spJoin <- over(str.prop.shp, sa1s.shp)
#   str_df$sa1 <- spJoin$sa1_main11
#  
#   ## Add Beach Designation
#   spJoin <- over(str.prop.shp, beach.buffer)
#   str_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   
#   # Remove those missing a suburb classification (out of area)
#   str_df <- str_df[str_df$sub.class != 'missing', ]
#   str_df <- str_df[str_df$sa1 != 'missing', ]
# 
# ```
# 
# ```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Add the submarket designations
# 
#   # Add individual classes
#   str_df$geo.mrkt <- 'rural'
#   str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
#   str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
#   str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
#   str_df$geo.mrkt[str_df$beach == 1] <- 'beach'
#   
#   # Order the factors properly
#   str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
#   
# ```
# 
# Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.  Half of these do, however, have a lat/long value for the centroid of the street that the property faces.  To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.  For those without either (3% of the total) we remove them from the dataset at this point. 
# 
# ```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  # Label those missing lat/long  
# 
#   miss.LL <- which(is.na(ltr_df$latitude))  
# 
#  # Create a field to indicate the approximate matches  
# 
#   ltr_df$miss.LL <- 0
#   ltr_df$miss.LL[miss.LL] <- 1
# 
#  # Apply approximate match    
# 
#   ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
#   ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]
# 
#  # Remove those still missing latitude data   
# 
#   ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]
# 
# ```
# 
# Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.  
# 
# ```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Long term data  
# 
#   # Convert to point shapefile
# 
#   ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
#                                                ltr_df$latitude),
#                                          ltr_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
# 
#   # Add suburb name 
#   
#   spJoin <- over(ltr.prop.shp, suburbs.shp)
#   ltr_df$suburb <- as.character(spJoin$name_2006)
#   ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'
# 
#   # Add suburb designation
#   
#   ltr_df$sub.class <- as.character(spJoin$suburbdesi)
#   ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'
#   
#   # Add SA1 designation
#   
#   spJoin <- over(ltr.prop.shp, sa1s.shp)
#   ltr_df$sa1 <- spJoin$sa1_main11
#  
#   ## Add Beach Designation
#   
#   spJoin <- over(ltr.prop.shp, beach.buffer)
#   ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   
#   # Remove those missing a suburb classification (out of area)
#   
#   ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
#   ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]
# 
# ```
# 
# ```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Add the submarket designations
# 
#   # Add individual classes
#   ltr_df$geo.mrkt <- 'rural'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
#   ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
#   ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'
#   
#   # Order the factors properly
#   ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
#   
#   # Count Cleaning
#   countCleaning('location')
#   
# ```
# 
# The location of the short and long term rentals, colored by submarket, are shown below
# 
# ```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Set submarket colors
#   
#   sm_col <- abb_col[c(1, 3, 6, 5, 2)]
# 
#   # Make map
# 
#   str.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
# 
# ```
# 
# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
# 
# ```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
# 
#   # Make Airbnb submarket map
#   
#   strtype.map <- ggplot() +
#     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
#     scale_fill_manual(values=sm_col) +
#     facet_wrap(~type) +
#     ylab('# of Properties\n') + xlab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     #ggtitle('Short Term Property Type\nBy Submarket')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
#   # Make Long term rental map
# 
#   ltrtype.map <- ggplot() +
#     geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
#     scale_fill_manual(values=sm_col) +
#     facet_wrap(~type) +
#     ylab('# of Properties\n') + xlab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     #ggtitle('Long Term Property Type\nBy Submarket')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.width=9}
# 
#   png(file=paste0(fig.path, 'submplot.png'), width = 680, height = 590, 
#       bg='transparent')
#     ggMultiPlots(strtype.map, ltrtype.map, cols=2)
#   dev.off()
#     
#   ggMultiPlots(strtype.map, ltrtype.map, cols=2)
#   
#   save(strtype.map, file=paste0(fig.path, 'strsubplot.RData'))
#   save(ltrtype.map, file=paste0(fig.path, 'ltrsubplot.RData'))
# 
#   
# ```
# 
# Finally, we convert the suburb names from factors to character, which will help with the imputation exercises later on. 
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   # Convert suburbs from factor to character
#   str_df$suburb <- as.character(str_df$suburb)
#   ltr_df$suburb <- as.character(ltr_df$suburb)
#   
# ```
# 
# &nbsp;
# 
# ## Filter Transaction Data
# 
# The previous exercises filtered the property-level data.  We now filter the transaction level datasets so that they only include those property that remain in the filtered property-level datasets
# 
# ```{r filttransdata, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## Short term data
#   
#   daily_df <- daily_df[daily_df$property.id %in% str_df$property.id,]
# 
#  ## Long term list data
#   
#   listing.data <- listing.data[listing.data$activity.id %in% ltr_df$activity.id,]
# 
# ```
# 
# ## Summarize Daily Data
# 
# As we have limited the time period of analysis from the expanse of the raw data, we must now re calculate the daily summary information. 
# 
# ```{r redo.daily.summ, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
# 
#     # Create new cluster
#   abb_cl <- get_default_cluster() 
#   
#   # Register function and variable
#   cluster_copy(abb_cl, abbCalcBookStr)
# 
#   # Summarize daily by property
#   daily_summ <- daily_df %>% 
#     multidplyr::partition(property.id, cluster=abb_cl) %>% 
#     dplyr::do(abbCalcBookStr(.)) %>% 
#     dplyr::collect()
#   
#  # Remove existing 
#  str_df <- str_df %>%
#    dplyr::select(-c(total.days, block.rate, avail.rate, longest.block, nbr.block,
#                     med.block, bookings))
#  
#  # Add summary data to property data
#  str_df <- str_df %>% dplyr::left_join(daily_summ, by='property.id')
# 
# 
# ```
# 
# 
# #### Host Policies
# 
# Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.  We also remove the few observations with missing host policy data
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#  ## ID those with missing cancel policies and remove
# 
#   str_df <- str_df %>% 
#     dplyr::filter(cancel.policy %in% c('Flexible', 'Moderate', 'Strict'))
# 
#  ## ID those with Super Strict and change to Strict  
#   
#   ss60 <- which(str_df$cancel.policy == 'Super Strict 60 Days')
#   str_df$cancel.policy[ss60] <- 'Strict'
# 
#   # Count Cleaning
#   countCleaning('hostpolicy')
#   
#   
# ```
# 
# ## Write out data  
# 
# ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
# 
#   save(str_df, ltr_df, daily_df, listing.data, subs, abb_col, 
#        beach.shp, core.suburbs, exch.rate, ltr_col, str_col, sa1s.shp, 
#        suburbs.shp, study.suburbs, clean.count, daily.run.total, list.run.total,
#        ltr.run.total, str.run.total,
#        file=paste0(data_path, 'prepared/prep_workspace_', data_name, '.RData'))
# 
# ```N

### 2018-05-21 _old/abb_Writeup_ARES.Rmd
isolating old code

--- 2017-10-25 abb_Writeup.Rmd
@@
 
-<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->
-
-<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->
-
-<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
-
-<!--  loc.map <- loc.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--  loc.map -->
-
-<!-- ``` -->
+\autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.
+
+```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}
+
+ load(paste0(fig.path, 'suburbMap.RData'))
+
+ loc.map <- loc.map +
+   theme(axis.title.y=element_blank(),
+         axis.text.y=element_blank(),
+         axis.ticks.y=element_blank(),
+         axis.title.x=element_blank(),
+         axis.text.x=element_blank(),
+         axis.ticks.x=element_blank())
+  ggsave(loc.map, filename=file.path(fig.path, 'loc_map.png'),
+         bg='transparent',
+         width=6, height=6)
+ # loc.map
+
+```
+
+![Suburb Categories](c://dropbox/research/airBnb/figures/loc_map.png)
 
@@
 
-  ggMultiPlots(str.map, ltr.map, cols=1)
-
-```
+    ggsave(str.map, filename=file.path(fig.path, 'str_map.png'),
+         bg='transparent',
+         width=6, height=6)
+    ggsave(ltr.map, filename=file.path(fig.path, 'ltr_map.png'),
+         bg='transparent',
+         width=6, height=6)
+
+  # ggMultiPlots(str.map, ltr.map, cols=1)
+
+```
+
+![Short Term Rental Locations](c://dropbox/research/airBnb/figures/str_map.png)
+
+![Long Term Rental Locations](c://dropbox/research/airBnb/figures/ltr_map.png)
 

### 2018-05-22 papers/full_paper.Rmd
Begin conversion of paper

--- 2017-10-25 abb_Writeup.Rmd
@@
 author: "Greenfield Advisors and University of Melbourne"
-date: "October 25th, 2017"
+date: "May 5th, 2018"
 output:
@@
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
+  library(tidyverse)
+  library(sf)
   library(geosphere)
   library(ggmap)
-  library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-  library(kernlab)
-  library(lmtest)
-  library(ROCR)
-
-```
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
- data.path <- 'c:/dropbox/research/airBNB/data/'
- code.path <- 'c:/code/'
- fig.path <- 'c:/dropbox/research/airBNB/figures/'
-
- ## Set options
-
+  library(multidplyr)
+  library(tmap)
+
+  options(stringsAsFactors=FALSE)
   options(xtable.comment = FALSE)
@@
 
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
+  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
+
+  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+
 ```
 
-```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
-  source(paste0(code.path, "tools/dataviztools/ggplottools.R"))
-  source(paste0(code.path, "tools/datamgmttools/dataMungetools.R"))
-  source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))
-
-```
-
-```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Set all colors
-
-  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
-                     'ebisu', 'tirol', 'foggy', 'hof')
-  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
-               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
-               rgb(77,226,110, maxColorValue=255), rgb(252,179,14,
-                                                       maxColorValue=255),
-               rgb(249,177,139, maxColorValue=255), rgb(191,166,100,
-                                                        maxColorValue=255),
-               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
-
-  # Set specific colors
-
-  str.col <- abb.col[1]
-  ltr.col <- abb.col[3]
-
-  strp.col <- abb.col[3]
-  ltrp.col <- abb.col[6]
-
-```
-
-```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}
-
-   load(paste0(data.path, '/analyzed/analyzed_workspace_sep.RData'))
-   a<-1
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
+
+  load(file.path(data_path, 'analyzed', 'analyzed_data.RData'))
 
@@
 
-```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  exch.rate <- 1.32
-
-```
-
 ### Data Preparation
@@
 We begin by filtering observations by time.
-Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
+Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental (LTR) versus an Airbnb-type, short-term rental (STR) approach to generating income.
 To determine the likely LTR rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
@@
 
-1. House:  Includes properties labeled 'House' or 'Townhouse'
-2. Apartment: Includes properties labeled as 'Apartment' or 'Condominium'
-3.
-Other: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
+1. House:  Includes properties labeled 'House', 'Townhouse' or 'Villa'
+2. Apartment: Includes properties labeled as 'Apartment', 'Condominium' or 'Loft'
+3. Other: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Other', 'Tent', 'Treehouse' and 'Yurt.
 
@@
 
-1. House:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+1. House:  Includes properties labeled 'Duplex', 'House', 'Terrace', 'Townhouse' or 'Villa'
 2. Apartment: Includes properties labeled as 'Unit' or 'Studio'
-3. Other: Includes properties labeled as 'Semi' and 'Villa'
+3. Other: Includes properties labeled as 'Semi'
 
@@
 
-The Other category only makes up a very small percentage of the properties in both the short and long-term market; especially so in the long-term market (\autoref{typecomp}) .
+The Other category only makes up a small percentage of the properties in both the short (3.78%) and long-term (0.02%) markets.
 Additionally, a large proportion of the 'Others' in the short-term data are Bed & Breakfast units, a use which doesn't fit within our research question.
 As a result, we remove the 'Others' from both the short- and the long-term rental data.
-
-```{r plot_pt, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}
-
-  load(paste0(fig.path, 'ltrtypes.RData'))
-  load(paste0(fig.path, 'strtypes.RData'))
-
-  str.types <- str.types + xlab('')
-  ltr.types <- ltr.types + xlab('')
-
-  ggMultiPlots(str.types, ltr.types, cols=2)
-
-```
 
@@
 As long-term rentals do not offer Private Room or Shared Room options^[Our long-term rental dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
-Unfortunately, this filter does remove about 40% of the short-term data (\autoref{ltypecomp}), however, given the research question it is unavoidable.
-
-```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}
-
- load(paste0(fig.path, 'listtypes.RData'))
-
- list.types + ggtitle('')
-
-```
+Unfortunately, this filter does remove about 46% of the short-term data, however, given the research question it is unavoidable.
 
@@
 In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two (\autoref{bbtype}).
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2.
+As a result we examine the combinations of the two.
+From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
+The four bedrooms options are only present in the house category.
 We filter the data to these combinations.
-
-```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}
-
- load(paste0(fig.path, 'ltrbb.RData'))
- load(paste0(fig.path, 'strbb.RData'))
-
- stbb <- stbb + ylab('# of Obs') + ggtitle('Short-Term Rentals')
- ltbb <- ltbb + ylab('# of Obs') + ggtitle('Long-Term Rentals')
-
- ggMultiPlots(stbb, ltbb)
-
-```
 
@@
 
-```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'}
-
- load(paste0(fig.path, 'rateplot.RData'))
- load(paste0(fig.path, 'rentplot.RData'))
-
- ggMultiPlots(rate.plot, ltr.plot, cols=2)
-
-```
+..HOLD FOR DENSITY OF RATE AND RENTS PLOT..
+
+<!-- ```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'} -->
+
+<!--  load(paste0(fig.path, 'rateplot.RData')) -->
+<!--  load(paste0(fig.path, 'rentplot.RData')) -->
+
+<!--  ggMultiPlots(rate.plot, ltr.plot, cols=2) -->
+
+<!-- ``` -->
 
@@
 
-Location is an important determinant in both the short- and long-term rental markets.
+<!-- Location is an important determinant in both the short- and long-term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
+-->
 
@@
 <!--          axis.ticks.x=element_blank()) -->
-
-<!--  loc.map -->
-
-<!-- ``` -->
-
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+<!--   ggsave(loc.map, filename=file.path(fig.path, 'loc_map.png'), -->
+<!--          bg='transparent', -->
+<!--          width=6, height=6) -->
+<!--  # loc.map -->
+
+<!-- ``` -->
+
+<!-- ![Suburb Categories](c://dropbox/research/airBnb/figures/loc_map.png) -->
+
+<!-- It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
-
-We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:  -->
+
+<!-- 1. Rural (Outer suburbs, not Beach) -->
+<!-- 2. Suburban (Middle suburbs, not Beach) -->
+<!-- 3. City (Inner Suburbs, not Beach, not Core) -->
+<!-- 4. City-Core (Select inner suburbs with tourist activities and near CBD) -->
+<!-- 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River) -->
+
+<!-- We select the 18 suburbs below to represent the 'core' of the city (Table 1).
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
 All are well served by public transportation and possess abundant amenities for tourists.
-
-```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
-
- c.subs <- data.frame(A=core.suburbs[1:6],
-                      B=core.suburbs[7:12],
-                      C=core.suburbs[13:18])
- names(c.subs) <- NULL
- rownames(c.subs) <- NULL
-
- print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
-       include.rownames=F,
-       caption.placement="top",
-       hline.after=c(0,6))
-
-```
-
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+-->
+
+<!-- ```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE} -->
+
+<!--  c.subs <- data.frame(A=core.suburbs[1:6], -->
+<!--                       B=core.suburbs[7:12], -->
+<!--                       C=core.suburbs[13:18]) -->
+<!--  names(c.subs) <- NULL -->
+<!--  rownames(c.subs) <- NULL -->
+
+<!--  print(xtable(c.subs, caption = 'List of Core Suburbs\n'), -->
+<!--        include.rownames=F, -->
+<!--        caption.placement="top", -->
+<!--        hline.after=c(0,6)) -->
+
+<!-- ``` -->
+
+<!-- We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short- and long-term data.
@@
 The location of the short- and long-term rentals, colored by submarket, are shown in \autoref{pointmaps}.
-
-Before assigning submarkets to the long-term property we must remedy the fact that about 5% of the long-term rental observations have missing latitude and longitude values.
+-->
+
+<!-- Before assigning submarkets to the long-term property we must remedy the fact that about 5% of the long-term rental observations have missing latitude and longitude values.
 Half of these do, however, have a latitude and longitude values for the centroid of the street that the property faces.
@@
 After making this correction we then assign one of the five submarket designations based on the process described above.
-
-```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  load(paste0(fig.path, 'ltrMap.RData'))
-  load(paste0(fig.path, 'strMap.RData'))
-
-```
-
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}
-
-  str.map <- str.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ltr.map <- ltr.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ggMultiPlots(str.map, ltr.map, cols=1)
-
-```
-
- To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+-->
+
+<!-- ```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   load(paste0(fig.path, 'ltrMap.RData')) -->
+<!--   load(paste0(fig.path, 'strMap.RData')) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'} -->
+
+<!--   str.map <- str.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--   ltr.map <- ltr.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--     ggsave(str.map, filename=file.path(fig.path, 'str_map.png'), -->
+<!--          bg='transparent', -->
+<!--          width=6, height=6) -->
+<!--     ggsave(ltr.map, filename=file.path(fig.path, 'ltr_map.png'), -->
+<!--          bg='transparent', -->
+<!--          width=6, height=6) -->
+
+<!--   # ggMultiPlots(str.map, ltr.map, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ![Short Term Rental Locations](c://dropbox/research/airBnb/figures/str_map.png) -->
+
+<!-- ![Long Term Rental Locations](c://dropbox/research/airBnb/figures/ltr_map.png) -->
+
+<!--  To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
 A number of interesting observations are illustrated here (\autoref{smcounts}).
@@
 Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
-
-```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}
-
-  load(paste0(fig.path, 'ltrsubplot.RData'))
-  load(paste0(fig.path, 'strsubplot.RData'))
-
-  ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties')
-  strtype.map <- strtype.map + ggtitle('Short-Term Properties')
-
-  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
-
-```
-
-### Summary of Data Cleaning
-
-We have applied ten separate filters to our two datasets.
+-->
+
+<!-- ```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'} -->
+
+<!--   load(paste0(fig.path, 'ltrsubplot.RData')) -->
+<!--   load(paste0(fig.path, 'strsubplot.RData')) -->
+
+<!--   ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties') -->
+<!--   strtype.map <- strtype.map + ggtitle('Short-Term Properties') -->
+
+<!--   ggMultiPlots(strtype.map, ltrtype.map, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ### Summary of Data Cleaning -->
+
+<!-- We have applied ten separate filters to our two datasets.
 In the name of transparency and to highlight the bounds of our research question it is useful to review these filters (Table 2).
@@
 From over 20,000, we have 5,788 Airbnb properties meet the requirements of our research question.
-
-For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+-->
+
+<!-- For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
 remove another 12,000 observations, leaving 120,092 in the final dataset.
-
-```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
-
- ## Extract data
-
-  cc <- clean.count[,c('operation', 'str', 'ltr')]
-
- ## Sum counts and create percentages
-
-  str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
-  ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
-  str.cut <- c(0, str.count[-length(str.count)] - str.count[-1])
-  str.per <- c(0, str.cut[-1] / str.count[-length(str.count)])
-  ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
-  ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
-
- ## Compile into data.frame
-
-  clean.table <- data.frame(field=cc$operation,
-                          strcount=str.count,
-                          strcut=str.cut,
-                          strper=str.per,
-                          ltrcount=ltr.count,
-                          ltrcut=ltr.cut,
-                          ltrper=ltr.per)
-
-  ## Fix fields and names
-
-  rownames(clean.table) <- NULL
-  clean.table$field <- c('Initial Count', 'Time', 'Property Type',
-                         'Listing Type', 'Bedrooms', 'Baths', 'Bed & Bath Combo',
-                         'Rates & Rents', 'Revenue', 'Location', 'Host Policy')
-  clean.table$strper <- 100*round(clean.table$strper, 2)
-  clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
-  names(clean.table) <- c('Filter', 'Short-term', 'Cut', '% Cut',
-                          'Long-term', 'Cut', '% Cut')
-
- ## Conver to xtable and print
-
-  options(xtable.comment = FALSE)
-  print(xtable(clean.table, 
-               digits=0,
-               caption='Data Cleaning Summary'),
-       include.rownames=FALSE,
-       caption.placement='top')
-
-```
+-->
 
@@
 
-1. Observed ($REV_o$)}: Observed bookings multiplied by median nightly rate
+1. Actual ($REV_o$)}: Observed bookings multiplied by median nightly rate
 2.
-Actual ($REV_a$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
+Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
 3. Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
 
-As the observed calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the Actual revenue metric to be a better measure of actual market performance.
-We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties.
+As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Likely' revenue metric to be a better measure of actual market performance.
+We chart the distribution of the Likely ($REV_l$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties.
 Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (\autoref{revdens}).
@@
 When looking at potential revenues, however, a great deal more may have the potential to produce additional revenue.
-The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
-
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'}
-
-  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    xlab('\nAnnual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20k', '$40k', '$60k'))+
-    theme(legend.position='none',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000)) +
-    facet_wrap(~tenure)
-
-```
-
-### Comparison
-
-In this section we compare net revenues between long- and short-term rental options.
+The high number of very low yield Airbnb properties in the Likely condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
+
+<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'} -->
+
+<!--   ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--     xlab('\nAnnual Revenue') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
+<!--                        labels=c('$0', '$20k', '$40k', '$60k'))+ -->
+<!--     theme(legend.position='none', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 70000)) + -->
+<!--     facet_wrap(~tenure) -->
+
+<!-- ``` -->
+
+<!-- ### Comparison -->
+
+<!-- In this section we compare net revenues between long- and short-term rental options.
 As mentioned above, there are no direct matches between the datasets.
@@
 We save discussion and analysis of the Potential revenue for the sensitivity tests later in the study.
-
-We make our imputations via hedonic price models.
+-->
+
+<!-- We make our imputations via hedonic price models.
 We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term weekly rental prices for the short-term properties.
-We use the following model specification:
-
-\begin{equation}
-  \label{eq:test}
-ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i}
-\end{equation}
-
-where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
-
-Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
+We use the following model specification: -->
+
+<!-- \begin{equation} -->
+<!--   \label{eq:test} -->
+<!-- ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i} -->
+<!-- \end{equation} -->
+
+<!-- where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+-->
+
+<!-- Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
 In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
@@
 We then combine the results from all estimates back into a single dataset that contains all of the short-term rentals.
-
-## Results
-
-We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
+-->
+
+<!-- ## Results -->
+
+<!-- We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
 Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
-
-Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
+-->
+
+<!-- Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
 For reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
@@
 For occupancy rates less than 40\%, long-term rental is more likely to be preferable.
-
-As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
+-->
+
+<!-- As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
 In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
 By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long-term one.
-
-```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
-
- ## Make plots
-
-  # Raw
-  raw.occ.metro <- ggplot(rawocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Quantile
-  qtl.occ.metro <- ggplot(qtlocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
-
-```
-
-Along with occupancy rates, the other important consideration is the nightly rate.
+-->
+
+<!-- ```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'} -->
+
+<!--  ## Make plots   -->
+
+<!--   # Raw -->
+<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Quantile -->
+<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Make Plot -->
+<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Along with occupancy rates, the other important consideration is the nightly rate.
 High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
@@
 The transparency is related to the total count of actual market properties falling into that area.
-
-The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
+-->
+
+<!-- The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
 This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
@@
 In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
-
-An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+-->
+
+<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
 In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short-term are (green).
@@
 As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
-
-```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
-
- ## Create the rate heat map
-
-  rate.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.rate',
-                y.field='med.rate',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  rate.hm <- rate.hm + ylab('Nightly Rate')
-
- ## Create raw SVM heatmap
-
-  rate.hm.svm <- abbHeatMap(str_df.ic,
-                            x.field='occ.rate',
-                            y.field='med.rate',
-                            pref.field='str.act.pref',
-                            svm=T, 
-                            alpha.count=F,
-                            add.points=T,
-                            fill.colors=c(strp.col, ltrp.col))
-  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')
-
- ## Plot
-
-  ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
-
-```
-
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
+-->
+
+<!-- ```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'} -->
+
+<!--  ## Create the rate heat map -->
+
+<!--   rate.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.rate', -->
+<!--                 y.field='med.rate', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(strp.col, ltrp.col)) -->
+<!--   rate.hm <- rate.hm + ylab('Nightly Rate') -->
+
+<!--  ## Create raw SVM heatmap   -->
+
+<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                             x.field='occ.rate', -->
+<!--                             y.field='med.rate', -->
+<!--                             pref.field='str.act.pref', -->
+<!--                             svm=T,  -->
+<!--                             alpha.count=F, -->
+<!--                             add.points=T, -->
+<!--                             fill.colors=c(strp.col, ltrp.col)) -->
+<!--   rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate') -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
 We convert both axis to percentiles and replot both in \autoref{metrohmp}.
@@
 For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
-
-```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}
-
- ## Build percentile heatmap
-
-  qtl.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
-
- ## Build percentile SVM
-
-  qtl.hm.svm <- abbHeatMap(str_df.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))
-  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
-
-  ## Make Plots
-
-  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
-
-```
-
-\pagebreak
-
-### Submarkets
-
-To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
+-->
+
+<!-- ```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'} -->
+
+<!--  ## Build percentile heatmap -->
+
+<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.qtl', -->
+<!--                 y.field='rate.qtl', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(strp.col, ltrp.col)) -->
+<!--   qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Build percentile SVM   -->
+
+<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) -->
+<!--   qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
+
+<!--   ## Make Plots -->
+
+<!--   ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ### Submarkets -->
+
+<!-- To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
 First, we bifurcate our data into houses and apartments.
@@
 Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
-
-```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
-
- ## Build raw plot
-
-  ptr.occ <- ggplot(rawocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Build Percentile Plots
-
-  ptq.occ <- ggplot(pctocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
-
-```
-
-Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
+-->
+
+<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
+
+<!--  ## Build raw plot -->
+
+<!--   ptr.occ <- ggplot(rawocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Build Percentile Plots -->
+
+<!--   ptq.occ <- ggplot(pctocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
 For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
@@
 A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
-
-```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
-
- ## Make House SVM Heatmap
-
-  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'House', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col)) +
-  theme(legend.position='none') +
-  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Make Apartment SVM Heat Map
-
-  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'Apartment', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Plot
-
-  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
-
-```
-
-#### By Geography
-
-Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
+-->
+
+<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
+
+<!--  ## Make House SVM Heatmap -->
+
+<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'House', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
+<!--   theme(legend.position='none') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Make Apartment SVM Heat Map -->
+
+<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'Apartment', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Plot -->
+
+<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- #### By Geography -->
+
+<!-- Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
 Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
 That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.
-
-```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='geo.mrkt')
-
- # Convert to wide format for output
-  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
-
- # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
-  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
-
- # Fix names  
-  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-
- ## Make printable table
-
-  print(xtable(pref.table[,1:2], 
-               caption='Geographic Submarket Preferability\n',
-               digits=1,
-               align='llr'),
-        include.rownames=FALSE,
-        caption.placement='top')
-
-```
-
-There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
+-->
+
+<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='geo.mrkt') -->
+
+<!--  # Convert to wide format for output -->
+<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
+<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
+<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
+
+<!--  # Fix names   -->
+<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+
+<!--  ## Make printable table -->
+
+<!--   print(xtable(pref.table[,1:2],  -->
+<!--                caption='Geographic Submarket Preferability\n', -->
+<!--                digits=1, -->
+<!--                align='llr'), -->
+<!--         include.rownames=FALSE, -->
+<!--         caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
 For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
@@
 Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
-
-```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
-
- ## Set colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
- ## Make plot objects
-
-  smr.occ <- ggplot(rawocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=1.5, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  smq.occ <- ggplot(pctocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=1.5, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(smr.occ, smq.occ, cols=2)
-
-```
-
-Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
+-->
+
+<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
+
+<!--  ## Set colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
+
+<!--  ## Make plot objects   -->
+
+<!--   smr.occ <- ggplot(rawocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   smq.occ <- ggplot(pctocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
 The 'City-Core' market offers the most potential for short-term preference with suburban and city the least.
@@
 Beach properties do not perform as well as might be expected in the short-term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
-
-```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE}
-
-  # Build the SVM Heatmaps
-
-  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city-core', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col)) +
-  theme(legend.position='none') +
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
-
-  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "City", size=9)
-
-  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'suburban', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
-
-  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'rural', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Rural", size=9)
-
-  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'beach', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Beach", size=9)
-
-```
-
-```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'}
-
-  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
-               rural.hm.svm, beach.hm.svm, cols=2)
-
-```
-
-## Explaining Preference
-
-The analyses above show that, overall, more than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+-->
+
+<!-- ```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE} -->
+
+<!--   # Build the SVM Heatmaps -->
+
+<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city-core', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
+<!--   theme(legend.position='none') + -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
+
+<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
+
+<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'suburban', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
+
+<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'rural', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
+
+<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'beach', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'} -->
+
+<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
+<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ## Explaining Preference -->
+
+<!-- The analyses above show that, overall, more than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
 This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference.
@@
 To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
-
-We specify three, increasingly complex, logistic regression models.
+-->
+
+<!-- We specify three, increasingly complex, logistic regression models.
 We use the actual revenue (not potential) as the dependent variable here, saving an anaylsis of potential revenue for the subsequent sensitivity tests.
-
-Model 1 takes the form of:
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon
-\end{equation}
-
-where $STPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term preference, $PType$ is the property type (apartment or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
-
-For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon
-\end{equation}
-
-Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts:
-
-\begin{equation}
-ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + 
-\beta_{2} BedBath + \beta_{3} SubMrkt +
-\beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon
-\end{equation}
-
-where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
+-->
+
+<!-- Model 1 takes the form of: -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon -->
+<!-- \end{equation} -->
+
+<!-- where $STPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term preference, $PType$ is the property type (apartment or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.
+-->
+
+<!-- For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities. -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon -->
+<!-- \end{equation} -->
+
+<!-- Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts: -->
+
+<!-- \begin{equation} -->
+<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType +  -->
+<!-- \beta_{2} BedBath + \beta_{3} SubMrkt + -->
+<!-- \beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon -->
+<!-- \end{equation} -->
+
+<!-- where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.
 We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
 We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).
-
-The results of all three models are shown in Table 4.
+-->
+
+<!-- The results of all three models are shown in Table 4.
 For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Moderate is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
-
-In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
+-->
+
+<!-- In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
 There is very little significant difference between 1 bed / 1 bath units and the remaining categories, with the exception of 2 bed / 2 bath.
@@
 Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.
-
-Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
+-->
+
+<!-- Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
 The difference between the Rural and City-Core is not significant, however.
@@
 Houses, for example, are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.
-
-Finally, in Model 3 we add in host behavior or policies.
+-->
+
+<!-- Finally, in Model 3 we add in host behavior or policies.
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
@@
 Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
-
-```{r log_model, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## Extract data
-
-  m1 <- as.data.frame(summary(pref.models[[1]])$coefficients)
-  m2 <- as.data.frame(summary(pref.models[[2]])$coefficients)
-  m3 <- as.data.frame(summary(pref.models[[3]])$coefficients)
-
- ## Create vector with significance stars
-
-  m1sig <- makeStatSig(m1[ ,4])
-  m2sig <- makeStatSig(m2[ ,4])
-  m3sig <- makeStatSig(m3[ ,4])
-
- ## Create coefficients for the table (with stars)
-
-  m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''), 
-                          sprintf('%.3f', round(m1$Estimate,3)),
-                          m1sig)
-  m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''),
-                          sprintf('%.3f',round(m2$Estimate,3)),
-                          m2sig)
-  m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''),
-                          sprintf('%.3f',round(m3$Estimate,3)),
-                          m3sig)
-
- ## Even out the lengths
-
-  m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
-  m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2)))
-  m3c <- m3$table.coef
-
- ##  Create the variable section of table 
- full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
- names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
- full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
-                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
-                          '4 Bed & 2 Bath', 'City (Submarket)',
-                          'Suburban (Submarket)', 'Rural (Submarket)', 
-                          'Beach (Submarket)', 'Guests per Bedroom', 
-                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
-
- ## Create model diagnostics
-
-  # Extract diagnostics
-  str.dx <- logDx(pref.models[[1]], str_df.ic, str_df.ic$str.act.pref)
-  sm.dx <- logDx(pref.models[[2]], str_df.ic, str_df.ic$str.act.pref)
-  host.dx <- logDx(pref.models[[3]], str_df.ic, str_df.ic$str.act.pref)
-
-  # Create diagnostic table
-  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
-                                      'AUC'),
-                           Str.Model=c('', '', round(str.dx$AIC,0), 
-                                       round(str.dx$logLik, 0),
-                                       round(as.numeric(str.dx$auc@y.values),
-                                             3)),
-                           Sm.Model=c('', '', round(sm.dx$AIC,0), 
-                                      round(sm.dx$logLik, 0),
-                                      round(as.numeric(sm.dx$auc@y.values), 3)),
-                           Host.Model=c('', '', round(host.dx$AIC,0), 
-                                        round(host.dx$logLik, 0),
-                                        round(as.numeric(host.dx$auc@y.values),
-                                              3)))
-  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
-
- ## Combine into full table
-
-  full.table <- rbind(full.table, diag.table)
-```
-
-```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
-  # XTable 
-  x.full <- xtable(full.table,
-                  caption='Logistic Modeling Results\n')
-  align(x.full) <- 'lllll'
-
-  # Print
-  print(x.full,
-       include.rownames=FALSE,
-       hline.after=c(-1,0,15,20,20),
-       caption.placement='top')
-
-```
-
-### Sensitivity Tests
-
-To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
+-->
+
+<!-- ```{r log_model, echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  ## Extract data -->
+
+<!--   m1 <- as.data.frame(summary(pref.models[[1]])$coefficients) -->
+<!--   m2 <- as.data.frame(summary(pref.models[[2]])$coefficients) -->
+<!--   m3 <- as.data.frame(summary(pref.models[[3]])$coefficients) -->
+
+<!--  ## Create vector with significance stars -->
+
+<!--   m1sig <- makeStatSig(m1[ ,4]) -->
+<!--   m2sig <- makeStatSig(m2[ ,4]) -->
+<!--   m3sig <- makeStatSig(m3[ ,4]) -->
+
+<!--  ## Create coefficients for the table (with stars)   -->
+
+<!--   m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''),  -->
+<!--                           sprintf('%.3f', round(m1$Estimate,3)), -->
+<!--                           m1sig) -->
+<!--   m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''), -->
+<!--                           sprintf('%.3f',round(m2$Estimate,3)), -->
+<!--                           m2sig) -->
+<!--   m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''), -->
+<!--                           sprintf('%.3f',round(m3$Estimate,3)), -->
+<!--                           m3sig) -->
+
+<!--  ## Even out the lengths -->
+
+<!--   m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1))) -->
+<!--   m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2))) -->
+<!--   m3c <- m3$table.coef -->
+
+<!--  ##  Create the variable section of table  -->
+<!--  full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c)) -->
+<!--  names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
+<!--  full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath', -->
+<!--                           '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath', -->
+<!--                           '4 Bed & 2 Bath', 'City (Submarket)', -->
+<!--                           'Suburban (Submarket)', 'Rural (Submarket)',  -->
+<!--                           'Beach (Submarket)', 'Guests per Bedroom',  -->
+<!--                           'Minimum Stay', 'Flexible Cancel', 'Strict Cancel') -->
+
+<!--  ## Create model diagnostics   -->
+
+<!--   # Extract diagnostics -->
+<!--   str.dx <- logDx(pref.models[[1]], str_df.ic, str_df.ic$str.act.pref) -->
+<!--   sm.dx <- logDx(pref.models[[2]], str_df.ic, str_df.ic$str.act.pref) -->
+<!--   host.dx <- logDx(pref.models[[3]], str_df.ic, str_df.ic$str.act.pref) -->
+
+<!--   # Create diagnostic table -->
+<!--   diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik', -->
+<!--                                       'AUC'), -->
+<!--                            Str.Model=c('', '', round(str.dx$AIC,0),  -->
+<!--                                        round(str.dx$logLik, 0), -->
+<!--                                        round(as.numeric(str.dx$auc@y.values), -->
+<!--                                              3)), -->
+<!--                            Sm.Model=c('', '', round(sm.dx$AIC,0),  -->
+<!--                                       round(sm.dx$logLik, 0), -->
+<!--                                       round(as.numeric(sm.dx$auc@y.values), 3)), -->
+<!--                            Host.Model=c('', '', round(host.dx$AIC,0),  -->
+<!--                                         round(host.dx$logLik, 0), -->
+<!--                                         round(as.numeric(host.dx$auc@y.values), -->
+<!--                                               3))) -->
+<!--   names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
+
+<!--  ## Combine into full table -->
+
+<!--   full.table <- rbind(full.table, diag.table) -->
+<!-- ``` -->
+
+<!-- ```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--   # XTable  -->
+<!--   x.full <- xtable(full.table, -->
+<!--                   caption='Logistic Modeling Results\n') -->
+<!--   align(x.full) <- 'lllll' -->
+
+<!--   # Print -->
+<!--   print(x.full, -->
+<!--        include.rownames=FALSE, -->
+<!--        hline.after=c(-1,0,15,20,20), -->
+<!--        caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- ### Sensitivity Tests -->
+
+<!-- To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
 First, we examine how the results change if Potential revenue, not Actual revenue, of the short-term properties is used in the comparisons.
 Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothetical motivations and actions of the hosts.
-
-#### Potential Revenue
-
-The above uses the Actual^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
+-->
+
+<!-- #### Potential Revenue  -->
+
+<!-- The above uses the Actual^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
 Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to not factoring in the impact of blocked days.
@@
 We do not attempt to correct for this likelihood, rather we offer these figures as high end estimates.
-
-Using the potential revenue, 53.3% of all properties are short-term preferable.
+-->
+
+<!-- Using the potential revenue, 53.3% of all properties are short-term preferable.
 Breaking that down by type and by geographic submarket (Table 5) shows similar findings, in terms of relative comparativeness, to the actual revenue analysis above.
@@
 One notable difference here is that the Rural properties perform rather poorly under a potential revenue scenario, relatively speaking, suggesting that they may be operating near their peak in the current condition.
-
-```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='type')
- # Extract Potential Results
-  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
-
- # Make baseic comparison table of submarkets  
-  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='geo.mrkt')
-
- # Extract potential results  
-  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
-
- # Combine and round  
-  st.table <- rbind(tpref.table, spref.table)
-  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
-
- ## Fix names and print
-
-  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-  print(xtable(st.table[,1:2], 
-               caption='Potential Revenue Preferability\n',
-               digits=1, align='llr'),
-               include.rownames=FALSE,
-               caption.placement='top',
-               hline.after=c(-1, 0, 2, 7, 7))
-
-```
-
-Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{pothm}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
+-->
+
+<!-- ```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  # Make Basic comparison table of type -->
+<!--   tpref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                     split.field='type') -->
+<!--  # Extract Potential Results -->
+<!--   tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ] -->
+
+<!--  # Make baseic comparison table of submarkets   -->
+<!--   spref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                     split.field='geo.mrkt') -->
+
+<!--  # Extract potential results   -->
+<!--   spref.table <- spref.table[spref.table$rev.type == 'Potential', ] -->
+
+<!--  # Combine and round   -->
+<!--   st.table <- rbind(tpref.table, spref.table) -->
+<!--   st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')  -->
+
+<!--  ## Fix names and print   -->
+
+<!--   names(st.table) <- c('Sub-Market', 'Short-Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+<!--   print(xtable(st.table[,1:2],  -->
+<!--                caption='Potential Revenue Preferability\n', -->
+<!--                digits=1, align='llr'), -->
+<!--                include.rownames=FALSE, -->
+<!--                caption.placement='top', -->
+<!--                hline.after=c(-1, 0, 2, 7, 7)) -->
+
+<!-- ``` -->
+
+<!-- Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{pothm}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
 Under a potential revenue scenario, a median occupancy rate and median nightly rate is results in greater than 50\% chance of short-term preference.
 Even with very low nightly rates (10th percentile), an occupancy rate around the 65th percentile will achieve short-term preference likelihood in the potential case.
-
-```{r pot_svm, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## create data and re-estimate the percentiles
-
- ## Make the pecentile heatmap
-
-  pqtl.hm <- abbHeatMap(pot.data.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.pot.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
-
- ## Make percentile SVM heatmap
-
-  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.pot.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))
-  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
-    xlab('Occupancy Rate (Pcntl)') +
-  annotate("text", x = 50, y = 50, label = "Potential", size=9)
-
- ## Add annotations to previous SVM
-
-  qtl.hm.svm.p <- qtl.hm.svm +
-  annotate("text", x = 50, y = 50, label = "Actual", size=9)
-
-```
-
-```{r plot_pot_svm, echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
-
-  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
-
-```
-
-Our final test of the potential revenue case is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
+-->
+
+<!-- ```{r pot_svm, echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  ## create data and re-estimate the percentiles -->
+
+<!--  ## Make the pecentile heatmap   -->
+
+<!--   pqtl.hm <- abbHeatMap(pot.data.ic, -->
+<!--                 x.field='occ.qtl', -->
+<!--                 y.field='rate.qtl', -->
+<!--                 pref.field='str.pot.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(strp.col, ltrp.col)) -->
+<!--   pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)') -->
+
+<!--  ## Make percentile SVM heatmap   -->
+
+<!--   pqtl.hm.svm <- abbHeatMap(pot.data.ic, -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.pot.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) -->
+<!--   pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+ -->
+<!--     xlab('Occupancy Rate (Pcntl)') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Potential", size=9) -->
+
+<!--  ## Add annotations to previous SVM   -->
+
+<!--   qtl.hm.svm.p <- qtl.hm.svm + -->
+<!--   annotate("text", x = 50, y = 50, label = "Actual", size=9) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_pot_svm, echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'} -->
+
+<!--   ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2) -->
+
+<!-- ```  -->
+
+<!-- Our final test of the potential revenue case is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
 Generally speaking, the results from the new series of models (Table 6) are qualitatively similar to those derived in the Actual revenue case (Table 4).
@@
 Likewise the geographic submarkets and host policies show similar effects in terms of direction of impact with some slight deviations in magnitude.
-
-```{r pot_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## Extract coefficients
-
-  pm1 <- as.data.frame(summary(pref.models[[4]])$coefficients)
-  pm2 <- as.data.frame(summary(pref.models[[5]])$coefficients)
-  pm3 <- as.data.frame(summary(pref.models[[6]])$coefficients)
-
- ## Make Significance stars
-
-  pm1sig <- makeStatSig(pm1[,4])
-  pm2sig <- makeStatSig(pm2[,4])
-  pm3sig <- makeStatSig(pm3[,4])
-
- ## Create Table coef vectors
-
- pm1$table.coef <- paste0(ifelse(pm1$Estimate>0, ' ', ''), 
-                         sprintf('%.3f', round(pm1$Estimate,3)),
-                         pm1sig)
- pm2$table.coef <- paste0(ifelse(pm2$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(pm2$Estimate,3)),
-                         pm2sig)
- pm3$table.coef <- paste0(ifelse(pm3$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(pm3$Estimate,3)),
-                         pm3sig)
-
- ## Snap to same length
-
- pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1)))
- pm2c <- c(pm2$table.coef, rep(' ', nrow(pm3)-nrow(pm2)))
- pm3c <- pm3$table.coef
-
- ## Put together as variables table
-
- pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
- names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
- pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
-                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
-                          '4 Bed & 2 Bath', 'City (Submarket)',
-                          'Suburban (Submarket)', 'Rural (Submarket)', 
-                          'Beach (Submarket)', 'Guests per Bedroom', 
-                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
-
- ## Create model diagnostics
-
-  # Extract diagnostics
-  pstr.dx <- logDx(pref.models[[4]], str_df.ic, str_df.ic$str.pot.pref)
-  psm.dx <- logDx(pref.models[[5]], str_df.ic, str_df.ic$str.pot.pref)
-  phost.dx <- logDx(pref.models[[6]], str_df.ic, str_df.ic$str.pot.pref)
-
-  # Create diagnostic table
-  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
-                                      'AUC'),
-                           Str.Model=c('', '', round(pstr.dx$AIC,0), 
-                                       round(pstr.dx$logLik, 0),
-                                       round(as.numeric(pstr.dx$auc@y.values),
-                                             3)),
-                           Sm.Model=c('', '', round(psm.dx$AIC,0), 
-                                      round(psm.dx$logLik, 0),
-                                      round(as.numeric(psm.dx$auc@y.values),
-                                            3)),
-                           Host.Model=c('', '', round(phost.dx$AIC,0), 
-                                        round(phost.dx$logLik, 0),
-                                        round(as.numeric(phost.dx$auc@y.values),
-                                              3)))
- ## Fix names
-
-  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
-
- # Bind together
-
- pfull.table <- rbind(pfull.table, pdiag.table)
-
-```
-
-```{r table_potlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- # XTable
-
- px.full <- xtable(pfull.table,
-                   caption='Logistic Modeling Results\n')
- align(px.full) <- 'lllll'
-
- # Print
- print(px.full,
-       include.rownames=FALSE,
-       hline.after=c(-1, 0, 15, 20, 20),
-       caption.placement='top')
-
-```
-
-Overall, the choice of revenue type, Actual or Potential, does affect some of the conclusions to be derived from the results above.
+-->
+
+<!-- ```{r pot_logmodel, echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  ## Extract coefficients -->
+
+<!--   pm1 <- as.data.frame(summary(pref.models[[4]])$coefficients) -->
+<!--   pm2 <- as.data.frame(summary(pref.models[[5]])$coefficients) -->
+<!--   pm3 <- as.data.frame(summary(pref.models[[6]])$coefficients) -->
+
+<!--  ## Make Significance stars   -->
+
+<!--   pm1sig <- makeStatSig(pm1[,4]) -->
+<!--   pm2sig <- makeStatSig(pm2[,4]) -->
+<!--   pm3sig <- makeStatSig(pm3[,4]) -->
+
+<!--  ## Create Table coef vectors   -->
+
+<!--  pm1$table.coef <- paste0(ifelse(pm1$Estimate>0, ' ', ''),  -->
+<!--                          sprintf('%.3f', round(pm1$Estimate,3)), -->
+<!--                          pm1sig) -->
+<!--  pm2$table.coef <- paste0(ifelse(pm2$Estimate>0, ' ', ''), -->
+<!--                          sprintf('%.3f',round(pm2$Estimate,3)), -->
+<!--                          pm2sig) -->
+<!--  pm3$table.coef <- paste0(ifelse(pm3$Estimate>0, ' ', ''), -->
+<!--                          sprintf('%.3f',round(pm3$Estimate,3)), -->
+<!--                          pm3sig) -->
+
+<!--  ## Snap to same length -->
+
+<!--  pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1))) -->
+<!--  pm2c <- c(pm2$table.coef, rep(' ', nrow(pm3)-nrow(pm2))) -->
+<!--  pm3c <- pm3$table.coef -->
+
+<!--  ## Put together as variables table -->
+
+<!--  pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c)) -->
+<!--  names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
+<!--  pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath', -->
+<!--                           '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath', -->
+<!--                           '4 Bed & 2 Bath', 'City (Submarket)', -->
+<!--                           'Suburban (Submarket)', 'Rural (Submarket)',  -->
+<!--                           'Beach (Submarket)', 'Guests per Bedroom',  -->
+<!--                           'Minimum Stay', 'Flexible Cancel', 'Strict Cancel') -->
+
+<!--  ## Create model diagnostics   -->
+
+<!--   # Extract diagnostics -->
+<!--   pstr.dx <- logDx(pref.models[[4]], str_df.ic, str_df.ic$str.pot.pref) -->
+<!--   psm.dx <- logDx(pref.models[[5]], str_df.ic, str_df.ic$str.pot.pref) -->
+<!--   phost.dx <- logDx(pref.models[[6]], str_df.ic, str_df.ic$str.pot.pref) -->
+
+<!--   # Create diagnostic table -->
+<!--   pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik', -->
+<!--                                       'AUC'), -->
+<!--                            Str.Model=c('', '', round(pstr.dx$AIC,0),  -->
+<!--                                        round(pstr.dx$logLik, 0), -->
+<!--                                        round(as.numeric(pstr.dx$auc@y.values), -->
+<!--                                              3)), -->
+<!--                            Sm.Model=c('', '', round(psm.dx$AIC,0),  -->
+<!--                                       round(psm.dx$logLik, 0), -->
+<!--                                       round(as.numeric(psm.dx$auc@y.values), -->
+<!--                                             3)), -->
+<!--                            Host.Model=c('', '', round(phost.dx$AIC,0),  -->
+<!--                                         round(phost.dx$logLik, 0), -->
+<!--                                         round(as.numeric(phost.dx$auc@y.values), -->
+<!--                                               3))) -->
+<!--  ## Fix names -->
+
+<!--   names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
+
+<!--  # Bind together -->
+
+<!--  pfull.table <- rbind(pfull.table, pdiag.table) -->
+
+<!-- ``` -->
+
+<!-- ```{r table_potlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  # XTable -->
+
+<!--  px.full <- xtable(pfull.table, -->
+<!--                    caption='Logistic Modeling Results\n') -->
+<!--  align(px.full) <- 'lllll' -->
+
+<!--  # Print -->
+<!--  print(px.full, -->
+<!--        include.rownames=FALSE, -->
+<!--        hline.after=c(-1, 0, 15, 20, 20), -->
+<!--        caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- Overall, the choice of revenue type, Actual or Potential, does affect some of the conclusions to be derived from the results above.
 As expected, under the Potential case there are more properties (53\% vs 28\%) that exhibit short-term preference.
@@
 Suffice it to say that it would like drive down occupancies and maybe price, therefore leading to a decrease in short-term preference likelihood.
-
-In explaining the drivers of short-term preference, the logistic regression models do not change materially with the switch in dependent variable.
+-->
+
+<!-- In explaining the drivers of short-term preference, the logistic regression models do not change materially with the switch in dependent variable.
 This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate.
 Only the base probability of short-term preference increases in the potential revenue case.
-
-More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for short-term leasing for the entire calendar year and, ceteris paribus, the remainder of the market does not do so.
-
-#### Host Classification
-
-As hinted at above in the Actual versus Potential comparison and as indicated in the logistic regression models in Tables 5 and 6, host behavior may be an important determinant of achieving short-term preference.
+-->
+
+<!-- More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for short-term leasing for the entire calendar year and, ceteris paribus, the remainder of the market does not do so.
+-->
+
+<!-- #### Host Classification -->
+
+<!-- As hinted at above in the Actual versus Potential comparison and as indicated in the logistic regression models in Tables 5 and 6, host behavior may be an important determinant of achieving short-term preference.
 Additionally, as the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.
@@
 From anecdotal evidence there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-
-If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked should be highly bi-modal with profit seekers on the left and opportunistic sharers on the right.
+-->
+
+<!-- If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked should be highly bi-modal with profit seekers on the left and opportunistic sharers on the right.
 The left hand panel of \autoref{hostblock} shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some (25\% to 75\%) of the time.
-
-There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property, of which Airbnb may just be one.
+-->
+
+<!-- There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property, of which Airbnb may just be one.
 A potential method to identify these hosts is to look at the number of individual periods of blocked days.
@@
 We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
-
-```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  ## Create table of host block frequencies
-
-  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
-  geom_density(fill=str.col, color=str.col) +
-  ylab('Frequency\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0,1,.2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    #ggtitle('Host Block Rate Frequency\n') +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-```
-
-```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- ## Create scatter of block rate vs block periods
-
-  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
-  geom_point(fill=str.col, color=str.col, size=.2) +
-  ylab('Nbr of Blocked Periods\n') + 
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostblock}Host Blocking Tendencies'}
-
-ggMultiPlots(host.block.freq, block.rate.period, cols=2)
-
-```
-
-Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
+-->
+
+<!-- ```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   ## Create table of host block frequencies -->
+
+<!--   host.block.freq <- ggplot(str_df, aes(x=block.rate)) +  -->
+<!--   geom_density(fill=str.col, color=str.col) + -->
+<!--   ylab('Frequency\n') +  -->
+<!--   xlab('\n% of Time Property is Blocked') + -->
+<!--   scale_x_continuous(breaks=seq(0,1,.2), -->
+<!--                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
+<!--     #ggtitle('Host Block Rate Frequency\n') + -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
+<!--     theme(axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank()) -->
+<!-- ``` -->
+
+<!-- ```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--  ## Create scatter of block rate vs block periods -->
+
+<!--   block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) +  -->
+<!--   geom_point(fill=str.col, color=str.col, size=.2) + -->
+<!--   ylab('Nbr of Blocked Periods\n') +  -->
+<!--   xlab('\n% of Time Property is Blocked') + -->
+<!--   scale_x_continuous(breaks=seq(0, 1, .2), -->
+<!--                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
+<!--     #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->
+<!--     theme(plot.title = element_text(hjust = 0.5))  -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostblock}Host Blocking Tendencies'} -->
+
+<!-- ggMultiPlots(host.block.freq, block.rate.period, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
 As a more subjective, but implementable, approach we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
@@
 See \autoref{hostcat} and \autoref{htc} for a breakdown of these group by the two variables.
-
-```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- ## Split Hosts into groups
-
-  str_df$blockpertime <- round(str_df$nbr.block * str_df$extr.par, 1)
-
-  str_df$host.type <- 'Unknown'
-  str_df$host.type[str_df$blockpertime > 12] <- 'Multi-Platform User'
-  str_df$host.type[str_df$block.rate <= .25] <- 'Profit Seeker'
-  str_df$host.type[str_df$block.rate >= .75] <- 'Opportunistic Sharer'
-  str_df$host.type <- factor(str_df$host.type,
-                               levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                        'Multi-Platform User', 'Unknown'))
-```
-
-```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  # Create a background plot for the host location plots
-
-  base.host <- ggplot(str_df, 
-                    aes(x=block.rate, y=blockpertime)) + 
-                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
-                ylab('# Blckd Periods\n') + 
-                xlab('\n% of Time Property is Blocked') +
-                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-                scale_x_continuous(breaks=seq(0, 1, .2),
-                                   labels=c('0%', '20%', '40%', 
-                                            '60%', '80%', '100%')) +
-                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
-                #                            abb.col[7], abb.col[9])) + 
-                theme(legend.position='bottom',
-                      legend.title = element_blank(),
-                      plot.title = element_text(hjust = 0.5))+
-                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
-
-```
-
-```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  ## Create individual host location plots
-
-  ps.host <- base.host + 
-    geom_point(data=str_df[str_df$host.type == 'Profit Seeker', ], size=.4)  +
-    ggtitle('Profit Seekers')
-
-  os.host <- base.host + 
-    geom_point(data=str_df[str_df$host.type == 'Opportunistic Sharer', ], 
-               size=.4)  +
-    ggtitle('Opportunistic Sharer')
-
-  mu.host <- base.host + 
-    geom_point(data=str_df[str_df$host.type == 'Multi-Platform User', ], 
-               size=.4)  +
-    ggtitle('Multi-Platform User')
-
-  un.host <- base.host + 
-    geom_point(data=str_df[str_df$host.type == 'Unknown', ], size=.4)  +
-    ggtitle('Unknown')
-
-```
-
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories'}
-
-  ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
-
-```
-
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}
-
- ## Build plot
-
-  host.type.bar <- ggplot(str_df, aes(host.type, fill=host.type)) +
-    geom_bar() +
-    scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-    theme(legend.position='none') +
-    ylab('Frequency\n') + 
-    xlab('\nHost Type') +
-    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
-    #ggtitle('short-term Host Types') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  host.type.bar
-
-```
-
-Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Actual case and a much smaller variation in the Potential case, as expected.
+-->
+
+<!-- ```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--  ## Split Hosts into groups -->
+
+<!--   str_df$blockpertime <- round(str_df$nbr.block * str_df$extr.par, 1) -->
+
+<!--   str_df$host.type <- 'Unknown' -->
+<!--   str_df$host.type[str_df$blockpertime > 12] <- 'Multi-Platform User' -->
+<!--   str_df$host.type[str_df$block.rate <= .25] <- 'Profit Seeker' -->
+<!--   str_df$host.type[str_df$block.rate >= .75] <- 'Opportunistic Sharer' -->
+<!--   str_df$host.type <- factor(str_df$host.type, -->
+<!--                                levels=c('Profit Seeker', 'Opportunistic Sharer',  -->
+<!--                                         'Multi-Platform User', 'Unknown')) -->
+<!-- ``` -->
+
+<!-- ```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   # Create a background plot for the host location plots -->
+
+<!--   base.host <- ggplot(str_df,  -->
+<!--                     aes(x=block.rate, y=blockpertime)) +  -->
+<!--                 geom_point(alpha=.7, size=.4, shape=16, color='gray70') + -->
+<!--                 ylab('# Blckd Periods\n') +  -->
+<!--                 xlab('\n% of Time Property is Blocked') + -->
+<!--                 ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->
+<!--                 scale_x_continuous(breaks=seq(0, 1, .2), -->
+<!--                                    labels=c('0%', '20%', '40%',  -->
+<!--                                             '60%', '80%', '100%')) + -->
+<!--                 #scale_color_manual(values=c(abb.col[2], abb.col[4],  -->
+<!--                 #                            abb.col[7], abb.col[9])) +  -->
+<!--                 theme(legend.position='bottom', -->
+<!--                       legend.title = element_blank(), -->
+<!--                       plot.title = element_text(hjust = 0.5))+ -->
+<!--                 guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1))) -->
+
+<!-- ``` -->
+
+<!-- ```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   ## Create individual host location plots -->
+
+<!--   ps.host <- base.host +  -->
+<!--     geom_point(data=str_df[str_df$host.type == 'Profit Seeker', ], size=.4)  + -->
+<!--     ggtitle('Profit Seekers') -->
+
+<!--   os.host <- base.host +  -->
+<!--     geom_point(data=str_df[str_df$host.type == 'Opportunistic Sharer', ],  -->
+<!--                size=.4)  + -->
+<!--     ggtitle('Opportunistic Sharer') -->
+
+<!--   mu.host <- base.host +  -->
+<!--     geom_point(data=str_df[str_df$host.type == 'Multi-Platform User', ],  -->
+<!--                size=.4)  + -->
+<!--     ggtitle('Multi-Platform User') -->
+
+<!--   un.host <- base.host +  -->
+<!--     geom_point(data=str_df[str_df$host.type == 'Unknown', ], size=.4)  + -->
+<!--     ggtitle('Unknown') -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories'} -->
+
+<!--   ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'} -->
+
+<!--  ## Build plot -->
+
+<!--   host.type.bar <- ggplot(str_df, aes(host.type, fill=host.type)) + -->
+<!--     geom_bar() + -->
+<!--     scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+ -->
+<!--     theme(legend.position='none') + -->
+<!--     ylab('Frequency\n') +  -->
+<!--     xlab('\nHost Type') + -->
+<!--     scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+ -->
+<!--     #ggtitle('short-term Host Types') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot -->
+
+<!--   host.type.bar -->
+
+<!-- ``` -->
+
+<!-- Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Actual case and a much smaller variation in the Potential case, as expected.
 There is little change for the 'Profit Seekers' as most of these hosts are already operating with few blocked days.
@@
 As the potential figures are somewhat similar here, we will only examine the differences for host types in the Actual number going forward.
-
-```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='host.type')
-
- # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
-  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
-  hpref.table <- hpref.table[,1:2]
-  hpref.table[,3] <- phpref.table[,2]
-  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
-  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
-
-  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
-  options(xtable.comment = FALSE)
-  print(xtable(hpref.table, 
-               caption='Host Type Preferability\n',
-               digits=1,
-               align='llrr'),
-               include.rownames=FALSE,
-               caption.placement='top')
-
-```
-
-Table 8 compares logistic models results from three of the host types.
+-->
+
+<!-- ```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--  # Make Basic comparison table -->
+<!--   apref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                     split.field='host.type') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   hpref.table <- apref.table[apref.table$rev.type == 'Actual', ] -->
+<!--   phpref.table <- apref.table[apref.table$rev.type == 'Potential', ] -->
+<!--   hpref.table <- hpref.table[,1:2] -->
+<!--   hpref.table[,3] <- phpref.table[,2] -->
+<!--   hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%') -->
+<!--   hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%') -->
+
+<!--   names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)') -->
+<!--   options(xtable.comment = FALSE) -->
+<!--   print(xtable(hpref.table,  -->
+<!--                caption='Host Type Preferability\n', -->
+<!--                digits=1, -->
+<!--                align='llrr'), -->
+<!--                include.rownames=FALSE, -->
+<!--                caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- Table 8 compares logistic models results from three of the host types.
 The Opportunistic Sharers show no instances of short-term preference and therefore could not be estimated.
@@
 The models for the multi-platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
-
-```{r host_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## Extract coefficients
-
-   h1 <- as.data.frame(summary(host.models[[1]])$coefficients)
-   h2 <- as.data.frame(summary(host.models[[3]])$coefficients)
-   h3 <- as.data.frame(summary(host.models[[4]])$coefficients)
-
- ## Build significance stars
-
-   h1sig <- makeStatSig(h1[ ,4])
-   h2sig <- makeStatSig(h2[ ,4])
-   h3sig <- makeStatSig(h3[ ,4])
-
- ## Create Table coefficients
-
-   h1$table.coef <- paste0(ifelse(h1$Estimate>0, ' ', ''), 
-                         sprintf('%.3f', round(h1$Estimate,3)),
-                         h1sig)
-   h2$table.coef <- paste0(ifelse(h2$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(h2$Estimate,3)),
-                         h2sig)
-   h3$table.coef <- paste0(ifelse(h3$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(h3$Estimate,3)),
-                         h3sig)
-
- ## Convert to variable table
-
- hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef,
-                                    h2$table.coef, h3$table.coef))
- names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
- hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
-                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
-                          '4 Bed & 2 Bath', 'City (Submarket)',
-                          'Suburban (Submarket)', 'Rural (Submarket)', 
-                          'Beach (Submarket)', 'Guests per Bedroom', 
-                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
-
- ## Create model diagnostics
-
-  # Extract diagnostics
-  hstr.dx <- logDx(host.models[[1]], str_df.ic, str_df.ic$str.act.pref)
-  hsm.dx <- logDx(host.models[[3]], str_df.ic, str_df.ic$str.act.pref)
-  hhost.dx <- logDx(host.models[[4]], str_df.ic, str_df.ic$str.act.pref)
-
-  # Create diagnostic table
-  hdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
-                                      'AUC'),
-                           Str.Model=c('', '', round(hstr.dx$AIC,0), 
-                                       round(hstr.dx$logLik, 0),
-                                       round(as.numeric(hstr.dx$auc@y.values),
-                                             3)),
-                           Sm.Model=c('', '', round(hsm.dx$AIC,0), 
-                                      round(hsm.dx$logLik, 0),
-                                      round(as.numeric(hsm.dx$auc@y.values), 3)),
-                           Host.Model=c('', '', round(hhost.dx$AIC,0), 
-                                        round(hhost.dx$logLik, 0),
-                                        round(as.numeric(hhost.dx$auc@y.values),
-                                              3)))
-  names(hdiag.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
-
- ## Combine into full table of coef and diags
-  #full.table[,2] <- gsub(" ", "", full.table[,2], fixed=TRUE)
-
- hfull.table <- rbind(hfull.table, hdiag.table)
-```
-
-```{r table_hostlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- xh.full <- xtable(hfull.table,
-                  caption='Logistic Model Results of Potential Short-Term Preference\n')
- align(xh.full) <- 'lllll'
-
- print(xh.full,
-       include.rownames=FALSE,
-       hline.after=c(-1,0,15,20,20),
-       caption.placement='top')
-
-```
-
-\pagebreak
-
-## Discussion
-
-Although it gathers considerable interest in both economic and public policy circles, analyses of short-term markets and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
+-->
+
+<!-- ```{r host_logmodel, echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  ## Extract coefficients -->
+
+<!--    h1 <- as.data.frame(summary(host.models[[1]])$coefficients) -->
+<!--    h2 <- as.data.frame(summary(host.models[[3]])$coefficients) -->
+<!--    h3 <- as.data.frame(summary(host.models[[4]])$coefficients) -->
+
+<!--  ## Build significance stars    -->
+
+<!--    h1sig <- makeStatSig(h1[ ,4]) -->
+<!--    h2sig <- makeStatSig(h2[ ,4]) -->
+<!--    h3sig <- makeStatSig(h3[ ,4]) -->
+
+<!--  ## Create Table coefficients    -->
+
+<!--    h1$table.coef <- paste0(ifelse(h1$Estimate>0, ' ', ''),  -->
+<!--                          sprintf('%.3f', round(h1$Estimate,3)), -->
+<!--                          h1sig) -->
+<!--    h2$table.coef <- paste0(ifelse(h2$Estimate>0, ' ', ''), -->
+<!--                          sprintf('%.3f',round(h2$Estimate,3)), -->
+<!--                          h2sig) -->
+<!--    h3$table.coef <- paste0(ifelse(h3$Estimate>0, ' ', ''), -->
+<!--                          sprintf('%.3f',round(h3$Estimate,3)), -->
+<!--                          h3sig) -->
+
+<!--  ## Convert to variable table    -->
+
+<!--  hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef, -->
+<!--                                     h2$table.coef, h3$table.coef)) -->
+<!--  names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown") -->
+<!--  hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath', -->
+<!--                           '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath', -->
+<!--                           '4 Bed & 2 Bath', 'City (Submarket)', -->
+<!--                           'Suburban (Submarket)', 'Rural (Submarket)',  -->
+<!--                           'Beach (Submarket)', 'Guests per Bedroom',  -->
+<!--                           'Minimum Stay', 'Flexible Cancel', 'Strict Cancel') -->
+
+<!--  ## Create model diagnostics   -->
+
+<!--   # Extract diagnostics -->
+<!--   hstr.dx <- logDx(host.models[[1]], str_df.ic, str_df.ic$str.act.pref) -->
+<!--   hsm.dx <- logDx(host.models[[3]], str_df.ic, str_df.ic$str.act.pref) -->
+<!--   hhost.dx <- logDx(host.models[[4]], str_df.ic, str_df.ic$str.act.pref) -->
+
+<!--   # Create diagnostic table -->
+<!--   hdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik', -->
+<!--                                       'AUC'), -->
+<!--                            Str.Model=c('', '', round(hstr.dx$AIC,0),  -->
+<!--                                        round(hstr.dx$logLik, 0), -->
+<!--                                        round(as.numeric(hstr.dx$auc@y.values), -->
+<!--                                              3)), -->
+<!--                            Sm.Model=c('', '', round(hsm.dx$AIC,0),  -->
+<!--                                       round(hsm.dx$logLik, 0), -->
+<!--                                       round(as.numeric(hsm.dx$auc@y.values), 3)), -->
+<!--                            Host.Model=c('', '', round(hhost.dx$AIC,0),  -->
+<!--                                         round(hhost.dx$logLik, 0), -->
+<!--                                         round(as.numeric(hhost.dx$auc@y.values), -->
+<!--                                               3))) -->
+<!--   names(hdiag.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown") -->
+
+<!--  ## Combine into full table of coef and diags -->
+<!--   #full.table[,2] <- gsub(" ", "", full.table[,2], fixed=TRUE) -->
+
+<!--  hfull.table <- rbind(hfull.table, hdiag.table) -->
+<!-- ``` -->
+
+<!-- ```{r table_hostlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE} -->
+
+<!--  xh.full <- xtable(hfull.table, -->
+<!--                   caption='Logistic Model Results of Potential Short-Term Preference\n') -->
+<!--  align(xh.full) <- 'lllll' -->
+
+<!--  print(xh.full, -->
+<!--        include.rownames=FALSE, -->
+<!--        hline.after=c(-1,0,15,20,20), -->
+<!--        caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ## Discussion -->
+
+<!-- Although it gathers considerable interest in both economic and public policy circles, analyses of short-term markets and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
 The Airbnb market is Melbourne is rapidly expanding as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
@@
 We caution future researchers and policy analysts to look deeply at initial estimates of Airbnb counts as many of the listings on the market are either room shares and/or not active.
-
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).
+-->
+
+<!-- Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).
 However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
@@
 Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
-
-In analyzing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
+-->
+
+<!-- In analyzing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
 As expected, this probability is not equal across space, property type or property size (bed and bath count).
@@
 Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
-
-The nightly rates and total occupancies drive the profitability of short-term leasing.
+-->
+
+<!-- The nightly rates and total occupancies drive the profitability of short-term leasing.
 As the nightly rate vs.
@@
 The vertical-ness of the divide between short- and long-term preference in the SVM plots suggests that occupancy rate is the most critical factor in reaching short-term preference in most markets.
-
-The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated.
+-->
+
+<!-- The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
@@
 As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
-
-Testing for the sensitivity of the initial results through consideration of potential revenue figures and by dividing the sample up by likely host motivation, we find the qualitative finding to be generally robust.
+-->
+
+<!-- Testing for the sensitivity of the initial results through consideration of potential revenue figures and by dividing the sample up by likely host motivation, we find the qualitative finding to be generally robust.
 While the use of potential revenue does increase the base probability of short-term preference, the same factors -- small inner city apartments with low minimum stays, strict cancellation and liberal guest capacity -- explain a higher likelihood of short-term preference.
-
-In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
+-->
+
+<!-- In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
 If owners all operated as profit maximizers this figure could be 53\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
-
-### Limitations and Future Research
-
-There are a number of limitations to this research.
+-->
+
+<!-- ### Limitations and Future Research -->
+
+<!-- There are a number of limitations to this research.
 There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
@@
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
-
-Additionally, we have opted to make comparisons between short- and long-term strategies by imputing long-term rents for short-term properties with a hedonic price model.
+-->
+
+<!-- Additionally, we have opted to make comparisons between short- and long-term strategies by imputing long-term rents for short-term properties with a hedonic price model.
 Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
-
-In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
+-->
+
+<!-- In this work, we have made the assumption that, over the course of a year, the general maintenance costs (excluding basic janitorial) are identical between short and long-term leasing options.
 We have done so as we were unable to location any evidence to suggest that one was higher than the other.
 This may be a limitation of our study and could prove to be an avenue of future research.
-
-Beyond airBNB.com other short-term platforms exist (e.g.
+-->
+
+<!-- Beyond airBNB.com other short-term platforms exist (e.g.
 www.homeaway.com).
@@
 We do suggest that, due to block patterns, a number of host do appear to be employing this approach but cannot confirm the extend to which this is actually happening.
-
-Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short- or long-term leasing strategy.
+-->
+
+<!-- Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short- or long-term leasing strategy.
 In reality, the possibilities may not be so rigid.
@@
 We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
-
-#### Data, Code and Interactivity
-
-Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
+-->
+
+<!-- #### Data, Code and Interactivity -->
+
+<!-- Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
 All the code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
 An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
-
-### Acknowledgements
-
-The authors would like to thank the Real Estate Research Institute (RERI) for funding this work and the Australian Property Monitors (APM) for providing the long-term rental data.
+-->
+
+<!-- ### Acknowledgements -->
+
+<!-- The authors would like to thank the Real Estate Research Institute (RERI) for funding this work and the Australian Property Monitors (APM) for providing the long-term rental data.  -->
 

### 2018-05-22 scripts/3_data_prep.Rmd
Begin conversion of paper

@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))
+        col_df, clean_count,
+        file=paste0(data_path, '/prepared/prepared_data.RData'))
 

### 2018-05-22 scripts/5_data_viz.Rmd
create loc map

@@
 ```{r setup, include=FALSE}
+
   knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  library(tmap)
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
+  fig_path <- file.path(getwd(), 'images')
+
+```
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
+
+  load(file.path(data_path, 'analyzed', 'analyzed_data.RData'))
+
+```
+
+## Suburb Location Map
+
+```{r sub_loc.map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Set submarket colors
+  suburb_sf$col <- 'gray80'
+  suburb_sf$col[suburb_sf$class == 'Middle'] <- 'gray50'
+  suburb_sf$col[suburb_sf$class == 'Inner'] <- 'gray20'
+
+   # Make map
+
+  png(filename = file.path(fig_path, "sub_loc_map.png"), 
+       width = 6.5, height = 6.5, units = 'in', res = 300)
+
+  tm_shape(suburb_sf) +
+    tm_polygons("class", palette=c('gray20', 'gray50', 'gray80'), title='Suburb Class') +
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='black', lwd=5) +
+    tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
+                  title='Study Area')
+
+  dev.off()
+
+```
+
+## Point Location Maps
+
+```{r location map}
+
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='gray50', lwd=2) +
+  tm_shape(ltr_sf) +
+    tm_symbols('geo_mrkt', size=.05, 
+               palette = sm_col,
+               border.alpha=0, alpha=.03, shape=15)
+
+```
+
+```{r maps}
 
@@
 
+## RATE and RENT Density
+
+<!-- ```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'} -->
+
+<!--  load(paste0(fig.path, 'rateplot.RData')) -->
+<!--  load(paste0(fig.path, 'rentplot.RData')) -->
+
+<!--  ggMultiPlots(rate.plot, ltr.plot, cols=2) -->
+
+<!-- ``` -->
+
+## SUBURB LOCATION MAP
+
+<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->
+
+<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->
+
+<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
+
+<!--  loc.map <- loc.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+<!--   ggsave(loc.map, filename=file.path(fig.path, 'loc_map.png'), -->
+<!--           bg='transparent', -->
+<!--          width=6, height=6) -->
+<!--  # loc.map -->
+
+<!-- ``` -->
+
+<!-- ![Suburb Categories](c://dropbox/research/airBnb/figures/loc_map.png) -->
+
+## OBSERVATION LOCATION MAPS
+
+<!-- ```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
+
+<!--   load(paste0(fig.path, 'ltrMap.RData')) -->
+<!--   load(paste0(fig.path, 'strMap.RData')) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'} -->
+
+<!--   str.map <- str.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--   ltr.map <- ltr.map + -->
+<!--    theme(axis.title.y=element_blank(), -->
+<!--          axis.text.y=element_blank(), -->
+<!--          axis.ticks.y=element_blank(), -->
+<!--          axis.title.x=element_blank(), -->
+<!--          axis.text.x=element_blank(), -->
+<!--          axis.ticks.x=element_blank()) -->
+
+<!--     ggsave(str.map, filename=file.path(fig.path, 'str_map.png'), -->
+<!--          bg='transparent', -->
+<!--          width=6, height=6) -->
+<!--     ggsave(ltr.map, filename=file.path(fig.path, 'ltr_map.png'), -->
+<!--          bg='transparent', -->
+<!--          width=6, height=6) -->
+
+<!--   # ggMultiPlots(str.map, ltr.map, cols=1) -->
+
+<!-- ``` -->
+
+<!-- ![Short Term Rental Locations](c://dropbox/research/airBnb/figures/str_map.png) -->
+
+<!-- ![Long Term Rental Locations](c://dropbox/research/airBnb/figures/ltr_map.png) -->
+
+## Location Bar Charts
+
+<!-- ```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'} -->
+
+<!--   load(paste0(fig.path, 'ltrsubplot.RData')) -->
+<!--   load(paste0(fig.path, 'strsubplot.RData')) -->
+
+<!--   ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties') -->
+<!--   strtype.map <- strtype.map + ggtitle('Short-Term Properties') -->
+
+<!--   ggMultiPlots(strtype.map, ltrtype.map, cols=2) -->
+
+<!-- ``` -->
+
+## Revenue Density Comparison
+
+<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'} -->
+
+<!--   ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) + -->
+<!--     geom_density(alpha=.5) + -->
+<!--     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
+<!--     xlab('\nAnnual Revenue') + -->
+<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
+<!--                        labels=c('$0', '$20k', '$40k', '$60k'))+ -->
+<!--     theme(legend.position='none', -->
+<!--           legend.title = element_blank(), -->
+<!--           plot.title = element_text(hjust = 0.5), -->
+<!--           axis.text.y = element_blank(), -->
+<!--           axis.ticks.y = element_blank(), -->
+<!--           axis.title.y=element_blank()) + -->
+<!--     coord_cartesian(xlim=c(0, 70000)) + -->
+<!--     facet_wrap(~tenure) -->
+
+<!-- ``` -->
+
 <!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->
@@
 ```
+
+<!-- We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
+Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
+-->
+
+<!-- Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
+For reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
+In \autoref{occpref} (left panel) we show the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
+We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up from about 25\% up to 75\% occupancy.
+For occupancy rates less than 40\%, long-term rental is more likely to be preferable.
+-->
+
+<!-- As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
+In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
+By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long-term one.
+-->
+
+<!-- ```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'} -->
+
+<!--  ## Make plots   -->
+
+<!--   # Raw -->
+<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Quantile -->
+<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
+<!--                    aes(x=x.var, y=Var))+ -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='none') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   # Make Plot -->
+<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Along with occupancy rates, the other important consideration is the nightly rate.
+High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
+In \autoref{metrohm} (left panel) we plot nightly rates versus occupancy rates.
+We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short-term or long-term revenue.
+The transparency is related to the total count of actual market properties falling into that area.
+-->
+
+<!-- The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
+This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
+While the left panel of \autoref{metrohm} helps show the general pattern it does leave many indeterminate areas.
+In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
+-->
+
+<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
+In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short-term are (green).
+In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
+Overall, from the SVM model we see that the short-term preference begins at about 325% occupancy rate, regardless of nightly rate.
+As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
+-->
+
+<!-- ```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'} -->
+
+<!--  ## Create the rate heat map -->
+
+<!--   rate.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.rate', -->
+<!--                 y.field='med.rate', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(strp.col, ltrp.col)) -->
+<!--   rate.hm <- rate.hm + ylab('Nightly Rate') -->
+
+<!--  ## Create raw SVM heatmap   -->
+
+<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                             x.field='occ.rate', -->
+<!--                             y.field='med.rate', -->
+<!--                             pref.field='str.act.pref', -->
+<!--                             svm=T,  -->
+<!--                             alpha.count=F, -->
+<!--                             add.points=T, -->
+<!--                             fill.colors=c(strp.col, ltrp.col)) -->
+<!--   rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate') -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
+We convert both axis to percentiles and replot both in \autoref{metrohmp}.
+Here we see a more even distibution of points across the figures.
+Additionally, a more reasonable SVM breakdown occurs as well.
+The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have at around the 60th percentile of the market it is in.
+And that only holds if the nightly rate is in the top 95th percentile of the market.
+For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
+-->
+
+<!-- ```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'} -->
+
+<!--  ## Build percentile heatmap -->
+
+<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
+<!--                 x.field='occ.qtl', -->
+<!--                 y.field='rate.qtl', -->
+<!--                 pref.field='str.act.pref', -->
+<!--                 svm=F,  -->
+<!--                 alpha.count=T, -->
+<!--                 add.points=T, -->
+<!--                 fill.colors=c(strp.col, ltrp.col)) -->
+<!--   qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Build percentile SVM   -->
+
+<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T,  -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) -->
+<!--   qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
+
+<!--   ## Make Plots -->
+
+<!--   ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- \pagebreak -->
+
+<!-- ### Submarkets -->
+
+<!-- To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
+First, we bifurcate our data into houses and apartments.
+Within the houses, 17.5\% of the properties are short-term preferable, while for the apartment that figure is nearly double at 30.5\%.
+Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (\autoref{smocc}).
+The only measurable difference is in that for houses a property's occupancy rate needs to be 10 percentiles higher than apartments to show the same likelihood of short-term preference as an apartment.
+Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
+-->
+
+<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
+
+<!--  ## Build raw plot -->
+
+<!--   ptr.occ <- ggplot(rawocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Build Percentile Plots -->
+
+<!--   ptq.occ <- ggplot(pctocc.type$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=c('black', 'grey60'), -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
+For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
+As an example, a median nightly rate requires a 90th percentile occupancy rate.
+The market for apartment (right panel) is more forgiving and occupancy rates as low as the 60th percentile can equate to a greater than even chance of short-term prefence is coupled with nightly rates near the top of the market.
+A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
+-->
+
+<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
+
+<!--  ## Make House SVM Heatmap -->
+
+<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'House', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
+<!--   theme(legend.position='none') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Make Apartment SVM Heat Map -->
+
+<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
+<!--                                           'Apartment', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
+<!--   ylab('Nightly Rate (Pcntl)') + -->
+<!--   xlab('Occupancy Rate (Pcntl)') -->
+
+<!--  ## Plot -->
+
+<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- #### By Geography -->
+
+<!-- Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
+Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
+That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.
+-->
+
+<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE} -->
+
+<!--  # Make Basic comparison table -->
+<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
+<!--                                    split.field='geo.mrkt') -->
+
+<!--  # Convert to wide format for output -->
+<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
+
+<!--  # Limit to the extrapolated pref type -->
+<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
+<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
+<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
+
+<!--  # Fix names   -->
+<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
+<!--   options(xtable.comment = FALSE) -->
+
+<!--  ## Make printable table -->
+
+<!--   print(xtable(pref.table[,1:2],  -->
+<!--                caption='Geographic Submarket Preferability\n', -->
+<!--                digits=1, -->
+<!--                align='llr'), -->
+<!--         include.rownames=FALSE, -->
+<!--         caption.placement='top') -->
+
+<!-- ``` -->
+
+<!-- There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
+For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
+This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city.
+Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
+-->
+
+<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
+
+<!--  ## Set colors -->
+
+<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
+
+<!--  ## Make plot objects   -->
+
+<!--   smr.occ <- ggplot(rawocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
+<!--     xlab('\nOccupancy Rate') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Raw Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--   smq.occ <- ggplot(pctocc.geo$data, -->
+<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
+<!--     geom_point(alpha=.5, size=.4) + -->
+<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
+<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
+<!--     scale_color_manual(values=sm.col, -->
+<!--                        name='') + -->
+<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
+<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
+<!--     ylab('\nSTR Preferability %') + -->
+<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
+<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
+<!--     theme(legend.position='bottom') +  -->
+<!--     ggtitle('Percentile Rates') +  -->
+<!--     theme(plot.title = element_text(hjust = 0.5)) -->
+
+<!--  ## Plot   -->
+
+<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
+
+<!-- ``` -->
+
+<!-- Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
+The 'City-Core' market offers the most potential for short-term preference with suburban and city the least.
+The rural market achieves very solid short-term preference for the most expensive homes, again likely those with special amenities or links to the wine region.
+Beach properties do not perform as well as might be expected in the short-term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
+-->
+
+<!-- ```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE} -->
+
+<!--   # Build the SVM Heatmaps -->
+
+<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city-core', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
+<!--   theme(legend.position='none') + -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
+
+<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'city', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
+
+<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'suburban', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
+
+<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'rural', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
+
+<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
+<!--                                           'beach', ], -->
+<!--                    x.field='occ.qtl', -->
+<!--                    y.field='rate.qtl', -->
+<!--                    pref.field='str.act.pref', -->
+<!--                    svm=T, -->
+<!--                    alpha.count=F, -->
+<!--                    add.points=T, -->
+<!--                    quantile=T, -->
+<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
+<!--   theme(legend.position='none')+ -->
+<!--     ylab('Nightly Rate Percentile') + -->
+<!--     xlab('Occupancy Rate Percentile') + -->
+<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
+
+<!-- ``` -->
+
+<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'} -->
+
+<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
+<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
+
+<!-- ``` -->
+
+<!-- ## Explaining Preference -->

### 2018-05-22 papers/full_paper.Rmd
remove extra viz from paper

@@
   library(tmap)
+  library(xtable)
 
@@
 
-After removing property level observations that are missing price data, we plot the distribution of the rates and rents.
-In \autoref{rrdist} we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+After removing property level observations that are missing price data, we find that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
 We filter the property level data accordingly.
@@
 
-..HOLD FOR DENSITY OF RATE AND RENTS PLOT..
-
-<!-- ```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'} -->
-
-<!--  load(paste0(fig.path, 'rateplot.RData')) -->
-<!--  load(paste0(fig.path, 'rentplot.RData')) -->
-
-<!--  ggMultiPlots(rate.plot, ltr.plot, cols=2) -->
-
-<!-- ``` -->
-
 ### Location and Submarkets
 
-<!-- Location is an important determinant in both the short- and long-term rental markets.
+Location is an important determinant in both the short- and long-term rental markets.
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
@@
 The specific suburb of a property is the second, or finer scale, at which the market operates.
--->
-
-<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->
-
-<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->
-
-<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
-
-<!--  loc.map <- loc.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-<!--   ggsave(loc.map, filename=file.path(fig.path, 'loc_map.png'), -->
-<!--          bg='transparent', -->
-<!--          width=6, height=6) -->
-<!--  # loc.map -->
-
-<!-- ``` -->
-
-<!-- ![Suburb Categories](c://dropbox/research/airBnb/figures/loc_map.png) -->
-
-<!-- It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+
+![Suburb Categories](C:/Code/research/airbnbMelbourne/images/sub_loc_map.png)
+It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:  -->
-
-<!-- 1. Rural (Outer suburbs, not Beach) -->
-<!-- 2. Suburban (Middle suburbs, not Beach) -->
-<!-- 3. City (Inner Suburbs, not Beach, not Core) -->
-<!-- 4. City-Core (Select inner suburbs with tourist activities and near CBD) -->
-<!-- 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River) -->
-
-<!-- We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
+
+1. Rural (Outer suburbs, not Beach)
+2. Suburban (Middle suburbs, not Beach)
+3. City (Inner Suburbs, not Beach, not Core)
+4. City-Core (Select inner suburbs with tourist activities and near CBD)
+5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+
+We select the 18 suburbs below to represent the 'core' of the city (Table 1).
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
 All are well served by public transportation and possess abundant amenities for tourists.
--->
-
-<!-- ```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE} -->
-
-<!--  c.subs <- data.frame(A=core.suburbs[1:6], -->
-<!--                       B=core.suburbs[7:12], -->
-<!--                       C=core.suburbs[13:18]) -->
-<!--  names(c.subs) <- NULL -->
-<!--  rownames(c.subs) <- NULL -->
-
-<!--  print(xtable(c.subs, caption = 'List of Core Suburbs\n'), -->
-<!--        include.rownames=F, -->
-<!--        caption.placement="top", -->
-<!--        hline.after=c(0,6)) -->
-
-<!-- ``` -->
-
-<!-- We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+
+```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
+
+ c.subs <- data.frame(A=core_suburbs[1:6],
+                      B=core_suburbs[7:12],
+                      C=core_suburbs[13:18])
+ names(c.subs) <- NULL
+ rownames(c.subs) <- NULL
+
+ print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
+       include.rownames=F,
+       caption.placement="top",
+       hline.after=c(0,6))
+
+```
+
+We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short- and long-term data.
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short- and long-term rentals, colored by submarket, are shown in \autoref{pointmaps}.
--->
-
-<!-- Before assigning submarkets to the long-term property we must remedy the fact that about 5% of the long-term rental observations have missing latitude and longitude values.
-Half of these do, however, have a latitude and longitude values for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
-For those without either set of lat/longs we remove them from the dataset at this point.
-After making this correction we then assign one of the five submarket designations based on the process described above.
--->
-
-<!-- ```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->
-
-<!--   load(paste0(fig.path, 'ltrMap.RData')) -->
-<!--   load(paste0(fig.path, 'strMap.RData')) -->
-
-<!-- ``` -->
-
-<!-- ```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'} -->
-
-<!--   str.map <- str.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--   ltr.map <- ltr.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--     ggsave(str.map, filename=file.path(fig.path, 'str_map.png'), -->
-<!--          bg='transparent', -->
-<!--          width=6, height=6) -->
-<!--     ggsave(ltr.map, filename=file.path(fig.path, 'ltr_map.png'), -->
-<!--          bg='transparent', -->
-<!--          width=6, height=6) -->
-
-<!--   # ggMultiPlots(str.map, ltr.map, cols=1) -->
-
-<!-- ``` -->
-
-<!-- ![Short Term Rental Locations](c://dropbox/research/airBnb/figures/str_map.png) -->
-
-<!-- ![Long Term Rental Locations](c://dropbox/research/airBnb/figures/ltr_map.png) -->
-
-<!--  To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
+The location of the short- and long-term rentals, colored by submarket, are shown in .
+
+..HOLD FOR POINT LOCATION MAPS..
+
+(These should be done a priori and converted to .tiff or other raster format)
+
+ To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
 A number of interesting observations are illustrated here (\autoref{smcounts}).
@@
 Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
--->
-
-<!-- ```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'} -->
-
-<!--   load(paste0(fig.path, 'ltrsubplot.RData')) -->
-<!--   load(paste0(fig.path, 'strsubplot.RData')) -->
-
-<!--   ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties') -->
-<!--   strtype.map <- strtype.map + ggtitle('Short-Term Properties') -->
-
-<!--   ggMultiPlots(strtype.map, ltrtype.map, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ### Summary of Data Cleaning -->
-
-<!-- We have applied ten separate filters to our two datasets.
+
+.. HOLD FOR LOCATION BAR CHARTS..
+
+### Summary of Data Cleaning
+
+We have applied ten separate filters to our two datasets.
 In the name of transparency and to highlight the bounds of our research question it is useful to review these filters (Table 2).
@@
 From over 20,000, we have 5,788 Airbnb properties meet the requirements of our research question.
--->
-
-<!-- For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
+
+For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
 Further consideration regarding property types, structural characteristics, location, etc.
 remove another 12,000 observations, leaving 120,092 in the final dataset.
--->
 
@@
 
-<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'} -->
-
-<!--   ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) + -->
-<!--     geom_density(alpha=.5) + -->
-<!--     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
-<!--     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
-<!--     xlab('\nAnnual Revenue') + -->
-<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
-<!--                        labels=c('$0', '$20k', '$40k', '$60k'))+ -->
-<!--     theme(legend.position='none', -->
-<!--           legend.title = element_blank(), -->
-<!--           plot.title = element_text(hjust = 0.5), -->
-<!--           axis.text.y = element_blank(), -->
-<!--           axis.ticks.y = element_blank(), -->
-<!--           axis.title.y=element_blank()) + -->
-<!--     coord_cartesian(xlim=c(0, 70000)) + -->
-<!--     facet_wrap(~tenure) -->
-
-<!-- ``` -->
-
-<!-- ### Comparison -->
-
-<!-- In this section we compare net revenues between long- and short-term rental options.
+...HOLD FOR REV DENSITY COMPARISON...
+
+### Comparison
+
+In this section we compare net revenues between long- and short-term rental options.
 As mentioned above, there are no direct matches between the datasets.
@@
 We save discussion and analysis of the Potential revenue for the sensitivity tests later in the study.
--->
-
-<!-- We make our imputations via hedonic price models.
+
+We make our imputations via hedonic price models.
 We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term weekly rental prices for the short-term properties.
-We use the following model specification: -->
-
-<!-- \begin{equation} -->
-<!--   \label{eq:test} -->
-<!-- ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i} -->
-<!-- \end{equation} -->
-
-<!-- where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
--->
-
-<!-- Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
+We use the following model specification:
+
+\begin{equation}
+  \label{eq:test}
+ln(RentLT_{i}) = \beta_{1} BedBath_{i} + \gamma_{2} Suburb_{i} + \tau_{3} Time_{i} + \epsilon_{i}
+\end{equation}
+
+where $ln(RentLT_{i})$ is the natural log of the weekly rent, *BedBath* is the bedroom/bathroom combination, *Suburb* is a fixed effect for the location of the property, *Time* is the month of rental and $\epsilon$ a random error term.
+
+Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
 In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
@@
 We then combine the results from all estimates back into a single dataset that contains all of the short-term rentals.
--->
-
-<!-- ## Results -->
-
-<!-- We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
-Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
--->
-
-<!-- Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
-For reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
-In \autoref{occpref} (left panel) we show the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
-We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up from about 25\% up to 75\% occupancy.
-For occupancy rates less than 40\%, long-term rental is more likely to be preferable.
--->
-
-<!-- As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
-In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
-By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long-term one.
--->
-
-<!-- ```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'} -->
-
-<!--  ## Make plots   -->
-
-<!--   # Raw -->
-<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
-<!--                    aes(x=x.var, y=Var))+ -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='none') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Quantile -->
-<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
-<!--                    aes(x=x.var, y=Var))+ -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='none') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Make Plot -->
-<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Along with occupancy rates, the other important consideration is the nightly rate.
-High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In \autoref{metrohm} (left panel) we plot nightly rates versus occupancy rates.
-We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short-term or long-term revenue.
-The transparency is related to the total count of actual market properties falling into that area.
--->
-
-<!-- The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
-This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
-While the left panel of \autoref{metrohm} helps show the general pattern it does leave many indeterminate areas.
-In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
--->
-
-<!-- An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
-In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short-term are (green).
-In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
-Overall, from the SVM model we see that the short-term preference begins at about 325% occupancy rate, regardless of nightly rate.
-As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
--->
-
-<!-- ```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'} -->
-
-<!--  ## Create the rate heat map -->
-
-<!--   rate.hm <- abbHeatMap(str_df.ic, -->
-<!--                 x.field='occ.rate', -->
-<!--                 y.field='med.rate', -->
-<!--                 pref.field='str.act.pref', -->
-<!--                 svm=F,  -->
-<!--                 alpha.count=T, -->
-<!--                 add.points=T, -->
-<!--                 fill.colors=c(strp.col, ltrp.col)) -->
-<!--   rate.hm <- rate.hm + ylab('Nightly Rate') -->
-
-<!--  ## Create raw SVM heatmap   -->
-
-<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
-<!--                             x.field='occ.rate', -->
-<!--                             y.field='med.rate', -->
-<!--                             pref.field='str.act.pref', -->
-<!--                             svm=T,  -->
-<!--                             alpha.count=F, -->
-<!--                             add.points=T, -->
-<!--                             fill.colors=c(strp.col, ltrp.col)) -->
-<!--   rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate') -->
-
-<!--  ## Plot   -->
-
-<!--   ggMultiPlots(rate.hm, rate.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
-We convert both axis to percentiles and replot both in \autoref{metrohmp}.
-Here we see a more even distibution of points across the figures.
-Additionally, a more reasonable SVM breakdown occurs as well.
-The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have at around the 60th percentile of the market it is in.
-And that only holds if the nightly rate is in the top 95th percentile of the market.
-For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
--->
-
-<!-- ```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'} -->
-
-<!--  ## Build percentile heatmap -->
-
-<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
-<!--                 x.field='occ.qtl', -->
-<!--                 y.field='rate.qtl', -->
-<!--                 pref.field='str.act.pref', -->
-<!--                 svm=F,  -->
-<!--                 alpha.count=T, -->
-<!--                 add.points=T, -->
-<!--                 fill.colors=c(strp.col, ltrp.col)) -->
-<!--   qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
-
-<!--  ## Build percentile SVM   -->
-
-<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col)) -->
-<!--   qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)') -->
-
-<!--   ## Make Plots -->
-
-<!--   ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- \pagebreak -->
-
-<!-- ### Submarkets -->
-
-<!-- To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
-First, we bifurcate our data into houses and apartments.
-Within the houses, 17.5\% of the properties are short-term preferable, while for the apartment that figure is nearly double at 30.5\%.
-Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (\autoref{smocc}).
-The only measurable difference is in that for houses a property's occupancy rate needs to be 10 percentiles higher than apartments to show the same likelihood of short-term preference as an apartment.
-Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
--->
-
-<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
-
-<!--  ## Build raw plot -->
-
-<!--   ptr.occ <- ggplot(rawocc.type$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_color_manual(values=c('black', 'grey60'), -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Build Percentile Plots -->
-
-<!--   ptq.occ <- ggplot(pctocc.type$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_color_manual(values=c('black', 'grey60'), -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Plot   -->
-
-<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
-For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
-As an example, a median nightly rate requires a 90th percentile occupancy rate.
-The market for apartment (right panel) is more forgiving and occupancy rates as low as the 60th percentile can equate to a greater than even chance of short-term prefence is coupled with nightly rates near the top of the market.
-A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
--->
-
-<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
-
-<!--  ## Make House SVM Heatmap -->
-
-<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
-<!--                                           'House', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
-<!--   theme(legend.position='none') + -->
-<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
-<!--   ylab('Nightly Rate (Pcntl)') + -->
-<!--   xlab('Occupancy Rate (Pcntl)') -->
-
-<!--  ## Make Apartment SVM Heat Map -->
-
-<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
-<!--                                           'Apartment', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
-<!--   ylab('Nightly Rate (Pcntl)') + -->
-<!--   xlab('Occupancy Rate (Pcntl)') -->
-
-<!--  ## Plot -->
-
-<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- #### By Geography -->
-
-<!-- Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
-Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
-That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.
--->
-
-<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE} -->
-
-<!--  # Make Basic comparison table -->
-<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
-<!--                                    split.field='geo.mrkt') -->
-
-<!--  # Convert to wide format for output -->
-<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
-
-<!--  # Limit to the extrapolated pref type -->
-<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
-<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
-<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
-
-<!--  # Fix names   -->
-<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
-<!--   options(xtable.comment = FALSE) -->
-
-<!--  ## Make printable table -->
-
-<!--   print(xtable(pref.table[,1:2],  -->
-<!--                caption='Geographic Submarket Preferability\n', -->
-<!--                digits=1, -->
-<!--                align='llr'), -->
-<!--         include.rownames=FALSE, -->
-<!--         caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
-For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
-This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city.
-Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
--->
-
-<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
-
-<!--  ## Set colors -->
-
-<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
-
-<!--  ## Make plot objects   -->
-
-<!--   smr.occ <- ggplot(rawocc.geo$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_color_manual(values=sm.col, -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   smq.occ <- ggplot(pctocc.geo$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=1.5, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_color_manual(values=sm.col, -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Plot   -->
-
-<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
-The 'City-Core' market offers the most potential for short-term preference with suburban and city the least.
-The rural market achieves very solid short-term preference for the most expensive homes, again likely those with special amenities or links to the wine region.
-Beach properties do not perform as well as might be expected in the short-term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
--->
-
-<!-- ```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE} -->
-
-<!--   # Build the SVM Heatmaps -->
-
-<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'city-core', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col)) + -->
-<!--   theme(legend.position='none') + -->
-<!--     ylab('Nightly Rate Percentile') + -->
-<!--     xlab('Occupancy Rate Percentile') + -->
-<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
-
-<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'city', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('Nightly Rate Percentile') + -->
-<!--     xlab('Occupancy Rate Percentile') + -->
-<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
-
-<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'suburban', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('Nightly Rate Percentile') + -->
-<!--     xlab('Occupancy Rate Percentile') + -->
-<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
-
-<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'rural', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('Nightly Rate Percentile') + -->
-<!--     xlab('Occupancy Rate Percentile') + -->
-<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
-
-<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'beach', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(strp.col, ltrp.col))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('Nightly Rate Percentile') + -->
-<!--     xlab('Occupancy Rate Percentile') + -->
-<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
-
-<!-- ``` -->
-
-<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'} -->
-
-<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
-<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ## Explaining Preference -->
+
+## Results
 

### 2018-05-22 scripts/3_data_prep.Rmd
bug fix: studyareasf obj

--- 2018-05-21 scripts/3_data_prep.Rmd
@@
   # Study Area
-  studyarea_sf <- suburb_sf %>% 
+  studyarea <- suburb_sf %>% 
     slice(sa_ids) %>%
     st_union()
+  studyarea_sf <- st_sf(name='studyarea', geometry=studyarea)
+
   plot(studyarea_sf)
@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))
+        col_df, clean_count, core_suburbs,
+        file=paste0(data_path, '/prepared/prepared_data.RData'))
 

### 2018-05-22 scripts/4_data_analysis.Rmd
bug fix: studyareasf obj

@@
   save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
-       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, 
+       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
        file=file.path(data_path, 'analyzed', 'analyzed_data.RData'))

### 2018-05-23 papers/full_paper.Rmd
Adding tables and figures to paper

--- 2017-10-25 abb_Writeup.Rmd
@@
 bibliography: abb.bib
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-  library(spdep)
-  library(maptools)
-  library(gstat)
-  library(ggplot2)
+  library(tidyverse)
+  library(sf)
   library(geosphere)
   library(ggmap)
+  library(multidplyr)
+  library(tmap)
   library(xtable)
-  library(chron)
-  library(plyr)
-  library(sp)
-  library(rgeos)
-  library(reshape2)
-  library(stringr)
-  library(RColorBrewer)
-  library(Hmisc)
-  library(kernlab)
-  library(lmtest)
   library(ROCR)
-
-```
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
- data.path <- 'c:/dropbox/research/airBNB/data/'
- code.path <- 'c:/code/'
- fig.path <- 'c:/dropbox/research/airBNB/figures/'
-
- ## Set options
-
+  library(xtable)
+
+  options(stringsAsFactors=FALSE)
   options(xtable.comment = FALSE)
@@
 
-```
-
-```{r source_files, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
-
-  source(paste0(code.path, "tools/dataviztools/ggplottools.R"))
-  source(paste0(code.path, "tools/datamgmttools/dataMungetools.R"))
-  source(paste0(code.path, "research/AirbnbMelbourne/abb_Functions.R"))
-
-```
-
-```{r set_colors, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Set all colors
-
-  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
-                     'ebisu', 'tirol', 'foggy', 'hof')
-  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
-               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
-               rgb(77,226,110, maxColorValue=255), rgb(252,179,14,
-                                                       maxColorValue=255),
-               rgb(249,177,139, maxColorValue=255), rgb(191,166,100,
-                                                        maxColorValue=255),
-               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))
-
-  # Set specific colors
-
-  str.col <- abb.col[1]
-  ltr.col <- abb.col[3]
-
-  strp.col <- abb.col[3]
-  ltrp.col <- abb.col[6]
-
-```
-
-```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}
-
-   load(paste0(data.path, '/analyzed/analyzed_workspace_sep.RData'))
-   a<-1
+  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
+  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
+  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
+
+  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+
+```
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
+
+  load(file.path(data_path, 'analyzed', 'analyzed_data.RData'))
 
@@
 
-After removing property level observations that are missing price data, we plot the distribution of the rates and rents.
-In \autoref{rrdist} we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
+After removing property level observations that are missing price data, we find that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
 We filter the property level data accordingly.
 We also filter the short-term daily data to include only those observations with nightly rates between \$50 and \$500.
-
-```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'}
-
- load(paste0(fig.path, 'rateplot.RData'))
- load(paste0(fig.path, 'rentplot.RData'))
-
- ggMultiPlots(rate.plot, ltr.plot, cols=2)
-
-```
 
@@
 
-<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->
-
-<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->
-
-<!--  load(paste0(fig.path, 'suburbMap.RData')) -->
-
-<!--  loc.map <- loc.map + -->
-<!--    theme(axis.title.y=element_blank(), -->
-<!--          axis.text.y=element_blank(), -->
-<!--          axis.ticks.y=element_blank(), -->
-<!--          axis.title.x=element_blank(), -->
-<!--          axis.text.x=element_blank(), -->
-<!--          axis.ticks.x=element_blank()) -->
-
-<!--  loc.map -->
-
-<!-- ``` -->
-
 It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
@@
 
- c.subs <- data.frame(A=core.suburbs[1:6],
-                      B=core.suburbs[7:12],
-                      C=core.suburbs[13:18])
+ c.subs <- data.frame(A=core_suburbs[1:6],
+                      B=core_suburbs[7:12],
+                      C=core_suburbs[13:18])
  names(c.subs) <- NULL
@@
 
+![Suburb Categories](C:/Code/research/airbnbMelbourne/images/sub_loc_map.png)
+
 We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
@@
 Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short- and long-term rentals, colored by submarket, are shown in \autoref{pointmaps}.
-
-Before assigning submarkets to the long-term property we must remedy the fact that about 5% of the long-term rental observations have missing latitude and longitude values.
-Half of these do, however, have a latitude and longitude values for the centroid of the street that the property faces.
-To retain as many observations as possible in these intial steps we apply the street centroid value to the observations with missing lat/long values.
-For those without either set of lat/longs we remove them from the dataset at this point.
-After making this correction we then assign one of the five submarket designations based on the process described above.
-
-```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  load(paste0(fig.path, 'ltrMap.RData'))
-  load(paste0(fig.path, 'strMap.RData'))
-
-```
-
-```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}
-
-  str.map <- str.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ltr.map <- ltr.map +
-   theme(axis.title.y=element_blank(),
-         axis.text.y=element_blank(),
-         axis.ticks.y=element_blank(),
-         axis.title.x=element_blank(),
-         axis.text.x=element_blank(),
-         axis.ticks.x=element_blank())
-
-  ggMultiPlots(str.map, ltr.map, cols=1)
-
-```
+The location of the short- and long-term rentals, colored by submarket, are shown in .
+
+![Long Term Observations](C:/Code/research/airbnbMelbourne/images/ltr_loc_map.png)
+
+![Short Term Observations](C:/Code/research/airbnbMelbourne/images/str_loc_map.png)
 
@@
 
-```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}
-
-  load(paste0(fig.path, 'ltrsubplot.RData'))
-  load(paste0(fig.path, 'strsubplot.RData'))
-
-  ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties')
-  strtype.map <- strtype.map + ggtitle('Short-Term Properties')
-
-  ggMultiPlots(strtype.map, ltrtype.map, cols=2)
-
-```
-
-### Summary of Data Cleaning
-
-We have applied ten separate filters to our two datasets.
+![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/loc_bar.png)
+
+<!-- ### Summary of Data Cleaning -->
+
+<!-- We have applied ten separate filters to our two datasets.
 In the name of transparency and to highlight the bounds of our research question it is useful to review these filters (Table 2).
@@
 When looking at potential revenues, however, a great deal more may have the potential to produce additional revenue.
-The high number of very low yield Airbnb properties in the Actual condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
-
-```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'}
-
-  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
-    xlab('\nAnnual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20k', '$40k', '$60k'))+
-    theme(legend.position='none',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000)) +
-    facet_wrap(~tenure)
-
-```
+The high number of very low yield Airbnb properties in the Likely condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
+
+![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/rev_dens.png)
 
@@
 ## Results
-
-We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.
-Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.
-
-Occupancy rates are one of the most important components in determining the profitability of short-term rentals.
-For reference, the mean occupancy rate in the sample is 27.6\%, with a median value of 19.4\%.
-In \autoref{occpref} (left panel) we show the percentage of properties for which short-term rental is more profitable versus the occupancy rate over the year analyzed.
-We see that likelihood of short-term rental being a better option increases sharply with occupancy rate up from about 25\% up to 75\% occupancy.
-For occupancy rates less than 40\%, long-term rental is more likely to be preferable.
-
-As the distribution of occupancy rates is not uniform the initial plot may be misleading as to the frequency of short-term rentals being more profitable than long-term.
-In the right hand panel of \autoref{occpref} (right panel) we transform the x-axis to represent the percentile of the full distribution of occupancy rates.
-By doing so, we see that, in general, properties need to be in the upper 25th percentile of occupancy rates across the entire market in order to have a equal likelihood of being more profitable as a short-term rental than as a more traditional long-term one.
-
-```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}
-
- ## Make plots
-
-  # Raw
-  raw.occ.metro <- ggplot(rawocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Quantile
-  qtl.occ.metro <- ggplot(qtlocc.metro$data,
-                   aes(x=x.var, y=Var))+
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='none') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)
-
-```
-
-Along with occupancy rates, the other important consideration is the nightly rate.
-High occupancy rates with low nightly rates may not be any better than lower occupancy rate with a higher nightly rate.
-In \autoref{metrohm} (left panel) we plot nightly rates versus occupancy rates.
-We then divide the area of the scatter plot into 400 equal areas (20 x 20) and color each based on which is more common in the area, short-term or long-term revenue.
-The transparency is related to the total count of actual market properties falling into that area.
-
-The general trend is what is expected; that is that higher rates and occupancies, ceteris paribus, means greater profitability for short-term rentals.
-This relationship is not a perfectly linear because the long-term rental revenue varies greatly based on the characteristics of the property.
-While the left panel of \autoref{metrohm} helps show the general pattern it does leave many indeterminate areas.
-In order to better delimit the situations where short-term rentals are more profitable we turn to a support vector machine (SVM) algorithm.
-
-An SVM can be used as a classifier to delineate the boundaries between two (or more) classes of observations.
-In this case, we delineate the boundary, \autoref{metrohm} (right panel) between situations where long-term rentals are more profitable (red) and where short-term are (green).
-In order to avoid an overly broad straight line delineation we use a polynomial fitting technique.
-Overall, from the SVM model we see that the short-term preference begins at about 325% occupancy rate, regardless of nightly rate.
-As the occupancy rate increases, the required nighly rate decreases, down to near $100 once occupancies hit 65\% or greater.
-
-```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}
-
- ## Create the rate heat map
-
-  rate.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.rate',
-                y.field='med.rate',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  rate.hm <- rate.hm + ylab('Nightly Rate')
-
- ## Create raw SVM heatmap
-
-  rate.hm.svm <- abbHeatMap(str_df.ic,
-                            x.field='occ.rate',
-                            y.field='med.rate',
-                            pref.field='str.act.pref',
-                            svm=T, 
-                            alpha.count=F,
-                            add.points=T,
-                            fill.colors=c(strp.col, ltrp.col))
-  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')
-
- ## Plot
-
-  ggMultiPlots(rate.hm, rate.hm.svm, cols=2)
-
-```
-
-Both the occupancy rates and the nightly rates are not uniformly distributed and therefore the plots in \autoref{metrohm} may be misleading.
-We convert both axis to percentiles and replot both in \autoref{metrohmp}.
-Here we see a more even distibution of points across the figures.
-Additionally, a more reasonable SVM breakdown occurs as well.
-The right panel shows that in order for the likelihood of a property to be more profitable in short-term rental to be above 50\% the lowest occupancy rate it can have at around the 60th percentile of the market it is in.
-And that only holds if the nightly rate is in the top 95th percentile of the market.
-For example, if we drop the nightly rate to the median, the occupancy rate needs to be at the 75th percentile or above.
-
-```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}
-
- ## Build percentile heatmap
-
-  qtl.hm <- abbHeatMap(str_df.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.act.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
-
- ## Build percentile SVM
-
-  qtl.hm.svm <- abbHeatMap(str_df.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))
-  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')
-
-  ## Make Plots
-
-  ggMultiPlots(qtl.hm, qtl.hm.svm, cols=2)
-
-```
-
-\pagebreak
-
-### Submarkets
-
-To gain a deeper understanding of the differences in short-term preference, we break the data down across a variety of characteristics and examine the preferability metrics in these submarkets.
-First, we bifurcate our data into houses and apartments.
-Within the houses, 17.5\% of the properties are short-term preferable, while for the apartment that figure is nearly double at 30.5\%.
-Plotting the changes in short-term preferability against occupancy rates shows considerable similarity between houses and apartments (\autoref{smocc}).
-The only measurable difference is in that for houses a property's occupancy rate needs to be 10 percentiles higher than apartments to show the same likelihood of short-term preference as an apartment.
-Or, in other words, a given house needs to outperform its peers by a greater extent than an apartment to achieve short-term preference.
-
-```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}
-
- ## Build raw plot
-
-  ptr.occ <- ggplot(rawocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Build Percentile Plots
-
-  ptq.occ <- ggplot(pctocc.type$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=2, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=c('black', 'grey60'),
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(ptr.occ, ptq.occ, cols=2)
-
-```
-
-Extending this analysis to include nightly rates shows a similar situation (\autoref{smhm}).
-For houses (left panel) there are very few combinations of occupancy rate and nightly rate that offer a greater than even likelihood of short-term preference.
-As an example, a median nightly rate requires a 90th percentile occupancy rate.
-The market for apartment (right panel) is more forgiving and occupancy rates as low as the 60th percentile can equate to a greater than even chance of short-term prefence is coupled with nightly rates near the top of the market.
-A median nightly rate requires a 70th percentile occupancy rate for short-term preference likelihood.
-
-```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}
-
- ## Make House SVM Heatmap
-
-  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'House', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col)) +
-  theme(legend.position='none') +
-  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Make Apartment SVM Heat Map
-
-  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
-                                          'Apartment', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
-  ylab('Nightly Rate (Pcntl)') +
-  xlab('Occupancy Rate (Pcntl)')
-
- ## Plot
-
-  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)
-
-```
-
-#### By Geography
-
-Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}.
-Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.
-That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.
-
-```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  pref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                   split.field='geo.mrkt')
-
- # Convert to wide format for output
-  pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var')
-
- # Limit to the extrapolated pref type
-  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
-  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
-  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')
-
- # Fix names  
-  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-
- ## Make printable table
-
-  print(xtable(pref.table[,1:2], 
-               caption='Geographic Submarket Preferability\n',
-               digits=1,
-               align='llr'),
-        include.rownames=FALSE,
-        caption.placement='top')
-
-```
-
-There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets.
-For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas.
-This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city.
-Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.
-
-```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}
-
- ## Set colors
-
-  sm.col <- abb.col[c(1, 3, 6, 5, 2)]
-
- ## Make plot objects
-
-  smr.occ <- ggplot(rawocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=1.5, span=.5) +
-    xlab('\nOccupancy Rate') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Raw Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
-  smq.occ <- ggplot(pctocc.geo$data,
-                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
-    geom_point(alpha=.5, size=.4) +
-    stat_smooth(se=FALSE, size=1.5, span=.5) +
-    xlab('\nOccupancy Rate (Pcntl)') +
-    scale_color_manual(values=sm.col,
-                       name='') +
-    scale_x_continuous(breaks=seq(0, 100, by=25),
-                       labels=c('0%', '25th', '50th', '75th', '100th')) +
-    ylab('\nSTR Preferability %') +
-    scale_y_continuous(breaks=seq(0, 1, by=.25),
-                       labels=c('0%', '25%', '50%', '75%', '100%')) +
-    theme(legend.position='bottom') + 
-    ggtitle('Percentile Rates') + 
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  ggMultiPlots(smr.occ, smq.occ, cols=2)
-
-```
-
-Plotting out the nightly rate versus occupancy rate heat maps for all five geographic submarkets (\autoref{smhmps}) tells a similar story.
-The 'City-Core' market offers the most potential for short-term preference with suburban and city the least.
-The rural market achieves very solid short-term preference for the most expensive homes, again likely those with special amenities or links to the wine region.
-Beach properties do not perform as well as might be expected in the short-term market, however, it should be kept in mind that the winter climate in Melbourne is not conducive to beach activity and therefore short-term beach properties may suffer during winter months.
-
-```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE}
-
-  # Build the SVM Heatmaps
-
-  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city-core', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col)) +
-  theme(legend.position='none') +
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "City-Core", size=9)
-
-  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'city', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "City", size=9)
-
-  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'suburban', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Suburban", size=9)
-
-  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'rural', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Rural", size=9)
-
-  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
-                                          'beach', ],
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.act.pref',
-                   svm=T,
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))+
-  theme(legend.position='none')+
-    ylab('Nightly Rate Percentile') +
-    xlab('Occupancy Rate Percentile') +
-  annotate("text", x = 50, y = 50, label = "Beach", size=9)
-
-```
-
-```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps (SVM)'}
-
-  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
-               rural.hm.svm, beach.hm.svm, cols=2)
-
-```
-
-## Explaining Preference
 
@@
 
-  m1 <- as.data.frame(summary(pref.models[[1]])$coefficients)
-  m2 <- as.data.frame(summary(pref.models[[2]])$coefficients)
-  m3 <- as.data.frame(summary(pref.models[[3]])$coefficients)
+  m1 <- as.data.frame(summary(lik_glms$str)$coefficients)
+  m2 <- as.data.frame(summary(lik_glms$loc)$coefficients)
+  m3 <- as.data.frame(summary(lik_glms$host)$coefficients)
 
@@
                           '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
-                          '4 Bed & 2 Bath', 'City (Submarket)',
+                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
+                          'City (Submarket)',
                           'Suburban (Submarket)', 'Rural (Submarket)',
@@
   # Extract diagnostics
-  str.dx <- logDx(pref.models[[1]], str_df.ic, str_df.ic$str.act.pref)
-  sm.dx <- logDx(pref.models[[2]], str_df.ic, str_df.ic$str.act.pref)
-  host.dx <- logDx(pref.models[[3]], str_df.ic, str_df.ic$str.act.pref)
+  str.dx <- logDx(lik_glms$str, str_tdf, str_tdf$lik_pref)
+  sm.dx <- logDx(lik_glms$loc, str_tdf, str_tdf$lik_pref)
+  host.dx <- logDx(lik_glms$host, str_tdf, str_tdf$lik_pref)
 
@@
        include.rownames=FALSE,
-       hline.after=c(-1,0,15,20,20),
+       hline.after=c(-1,0,17,22,22),
        caption.placement='top')
@@
  # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
+  tpref.table <- abbCreateCompTable(ic.df=str_tdf,
                                     split.field='type')
+
  # Extract Potential Results
@@
  # Make baseic comparison table of submarkets
-  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='geo.mrkt')
+  spref.table <- abbCreateCompTable(ic.df=str_tdf,
+                                    split.field='geo_mrkt')
 
@@
 
-Examining the SVM heat maps for the entire metro region under the Actual revenue (left panel, \autoref{pothm}) and the Potential revenue (right panel) show the large increase in possible occupancy rate and nightly rate combinations that lead to short-term preference.
-Under a potential revenue scenario, a median occupancy rate and median nightly rate is results in greater than 50\% chance of short-term preference.
-Even with very low nightly rates (10th percentile), an occupancy rate around the 65th percentile will achieve short-term preference likelihood in the potential case.
-
-```{r pot_svm, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## create data and re-estimate the percentiles
-
- ## Make the pecentile heatmap
-
-  pqtl.hm <- abbHeatMap(pot.data.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.pot.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(strp.col, ltrp.col))
-  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
-
- ## Make percentile SVM heatmap
-
-  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.pot.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(strp.col, ltrp.col))
-  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
-    xlab('Occupancy Rate (Pcntl)') +
-  annotate("text", x = 50, y = 50, label = "Potential", size=9)
-
- ## Add annotations to previous SVM
-
-  qtl.hm.svm.p <- qtl.hm.svm +
-  annotate("text", x = 50, y = 50, label = "Actual", size=9)
-
-```
-
-```{r plot_pot_svm, echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
-
-  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
-
-```
-
 Our final test of the potential revenue case is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
@@
 
-  pm1 <- as.data.frame(summary(pref.models[[4]])$coefficients)
-  pm2 <- as.data.frame(summary(pref.models[[5]])$coefficients)
-  pm3 <- as.data.frame(summary(pref.models[[6]])$coefficients)
+  pm1 <- as.data.frame(summary(pot_glms$str)$coefficients)
+  pm2 <- as.data.frame(summary(pot_glms$loc)$coefficients)
+  pm3 <- as.data.frame(summary(pot_glms$host)$coefficients)
 
@@
   # Extract diagnostics
-  pstr.dx <- logDx(pref.models[[4]], str_df.ic, str_df.ic$str.pot.pref)
-  psm.dx <- logDx(pref.models[[5]], str_df.ic, str_df.ic$str.pot.pref)
-  phost.dx <- logDx(pref.models[[6]], str_df.ic, str_df.ic$str.pot.pref)
+  pstr.dx <- logDx(pot_glms$str, str_tdf, str_tdf$pot_pref)
+  psm.dx <- logDx(pot_glms$loc, str_tdf, str_tdf$pot_pref)
+  phost.dx <- logDx(pot_glms$host, str_tdf, str_tdf$pot_pref)
 
@@
        include.rownames=FALSE,
-       hline.after=c(-1, 0, 15, 20, 20),
+       hline.after=c(-1, 0, 17, 22, 22),
        caption.placement='top')
@@
 
+  str.col <- col_df$rgb[1]
+
   ## Create table of host block frequencies
 
-  host.block.freq <- ggplot(str_df, aes(x=block.rate)) + 
+  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
   geom_density(fill=str.col, color=str.col) +
@@
 
-  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
+  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * extr_par)) +
   geom_point(fill=str.col, color=str.col, size=.2) +
@@
 
-```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- ## Split Hosts into groups
-
-  str_df$blockpertime <- round(str_df$nbr.block * str_df$extr.par, 1)
-
-  str_df$host.type <- 'Unknown'
-  str_df$host.type[str_df$blockpertime > 12] <- 'Multi-Platform User'
-  str_df$host.type[str_df$block.rate <= .25] <- 'Profit Seeker'
-  str_df$host.type[str_df$block.rate >= .75] <- 'Opportunistic Sharer'
-  str_df$host.type <- factor(str_df$host.type,
-                               levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                        'Multi-Platform User', 'Unknown'))
-```
-
 ```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
@@
 
-  base.host <- ggplot(str_df, 
-                    aes(x=block.rate, y=blockpertime)) + 
+  base.host <- ggplot(str_tdf,
+                    aes(x=block_rate, y=blockpertime)) +
                 geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
@@
   ps.host <- base.host +
-    geom_point(data=str_df[str_df$host.type == 'Profit Seeker', ], size=.4)  +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
     ggtitle('Profit Seekers')
@@
   os.host <- base.host +
-    geom_point(data=str_df[str_df$host.type == 'Opportunistic Sharer', ], 
+    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
                size=.4)  +
@@
   mu.host <- base.host +
-    geom_point(data=str_df[str_df$host.type == 'Multi-Platform User', ], 
+    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
                size=.4)  +
@@
   un.host <- base.host +
-    geom_point(data=str_df[str_df$host.type == 'Unknown', ], size=.4)  +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
     ggtitle('Unknown')
@@
 
-  host.type.bar <- ggplot(str_df, aes(host.type, fill=host.type)) +
+  host.type.bar <- ggplot(str_tdf, aes(host_type, fill=host_type)) +
     geom_bar() +
-    scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
+    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
+                               col_df$rgb[9]))+
     theme(legend.position='none') +
@@
     xlab('\nHost Type') +
-    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unk'))+
+    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
     #ggtitle('short-term Host Types') +
@@
  # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='host.type')
+  apref.table <- abbCreateCompTable(ic.df=str_tdf,
+                                    split.field='host_type')
 
  # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
+  hpref.table <- apref.table[apref.table$rev.type == 'Likely', ]
   phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
@@
 
-  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
+  names(hpref.table) <- c('Host Type', 'STP (Likely)', 'STP (Potential)')
   options(xtable.comment = FALSE)
@@
 
-   h1 <- as.data.frame(summary(host.models[[1]])$coefficients)
-   h2 <- as.data.frame(summary(host.models[[3]])$coefficients)
-   h3 <- as.data.frame(summary(host.models[[4]])$coefficients)
+  h1 <- as.data.frame(summary(pot_ht_glms[[1]])$coefficients)
+  h2 <- as.data.frame(summary(pot_ht_glms[[3]])$coefficients)
+  h3 <- as.data.frame(summary(pot_ht_glms[[4]])$coefficients)
 
@@
   # Extract diagnostics
-  hstr.dx <- logDx(host.models[[1]], str_df.ic, str_df.ic$str.act.pref)
-  hsm.dx <- logDx(host.models[[3]], str_df.ic, str_df.ic$str.act.pref)
-  hhost.dx <- logDx(host.models[[4]], str_df.ic, str_df.ic$str.act.pref)
+  hstr.dx <- logDx(pot_ht_glms[[1]], str_tdf, str_tdf$pot_pref)
+  hsm.dx <- logDx(pot_ht_glms[[3]], str_tdf, str_tdf$pot_pref)
+  hhost.dx <- logDx(pot_ht_glms[[4]], str_tdf, str_tdf$pot_pref)
 

### 2018-05-23 scripts/5_data_viz.Rmd
Adding tables and figures to paper

@@
   library(tmap)
+  library(magrittr)
+  library(dplyr)
+  library(ggplot2)
   data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
@@
 
+  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
+              col_df$rgb[6], col_df$rgb[1])
+
+  png(filename = file.path(fig_path, "ltr_loc_map.png"), 
+       width = 4, height = 4, units = 'in', res = 300)
   tm_shape(studyarea_sf) + 
     tm_borders(col='gray50', lwd=2) +
-  tm_shape(ltr_sf) +
-    tm_symbols('geo_mrkt', size=.05, 
-               palette = sm_col,
-               border.alpha=0, alpha=.03, shape=15)
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray90', lwd=.5) +
+  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
+  dev.off()
+
+  png(filename = file.path(fig_path, "str_loc_map.png"), 
+       width = 4, height = 4, units = 'in', res = 300)
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='gray50', lwd=2) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray90', lwd=.5) +
+  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.3, shape=16)
+  dev.off()
 
@@
 
+```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
+
+   # Make Airbnb submarket map
+
+   strtype_bar <- ggplot() +
+     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=sm_col, name='Submarket') +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     ggtitle('Short Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+   # Make Long term rental map
+
+   ltrtype_bar <- ggplot() +
+     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=sm_col) +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     ggtitle('Long Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+     png(filename = file.path(fig_path, "loc_bar.png"), 
+       width = 8, height = 4, units = 'in', res = 300)
+
+     ggMultiPlots(strtype_bar, ltrtype_bar, cols=2)
+     dev.off()
+
+```
+
 ```{r maps}
+
+   dens_cols <- c(col_df$rgb[3], col_df$rgb[1], col_df$rgb[2])
 
@@
    rev_df <- bind_rows(str_tdf %>% 
+                         dplyr::select(type, gross_revenue=lik_revenue) %>%
+                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
+                                       alpha = .5),
+                       str_tdf %>% 
+                         dplyr::select(type, gross_revenue=pot_revenue) %>%
+                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
+                                       alpha = .4),
+                       ltr_df %>%
                          dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'str'),
-                       ltr_tdf %>%
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'ltr'))
-
-   revdens <- ggplot(rev_df, 
+                         dplyr::mutate(tenure = 'Long-Term   ',
+                                       alpha = .9))
+
+  png(filename = file.path(fig_path, "rev_dens.png"), 
+       width = 5.5, height = 4, units = 'in', res = 300)
+
+   ggplot(rev_df,
           aes(x=gross_revenue, fill=tenure, color=tenure)) +
     geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, str_col)) +
-    scale_color_manual(values=c(ltr_col, str_col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
+    scale_fill_manual(values=dens_cols) +
+    scale_color_manual(values=dens_cols) +
+    ggtitle('Short Term Revenue vs Long Term Revenue') +
     xlab('Annual Revenue') +
@@
 
-   # Add together for plotting potential revenues
-   prev_df <- bind_rows(str_tdf %>% 
-                         dplyr::select(type, gross_revenue=pot_revenue) %>%
-                         dplyr::mutate(tenure = 'str'),
-                       ltr_tdf %>%
-                         tidyr::unnest() %>%
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'ltr'))
-
-   prevdens <- ggplot(prev_df, 
-                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
-    geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, str_col)) +
-    scale_color_manual(values=c(ltr_col, str_col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
-    xlab('Annual Revenue') +
-    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
-    theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
-    coord_cartesian(xlim=c(0, 70000))
+    dev.off()
 
@@
 
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-
-   # Make Airbnb submarket map
+# The chart below break down the relative frequency of short and long term rental properties across the five submarkets.
 
    strtype.map <- ggplot() +
-     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
+     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
+     scale_fill_manual(values=sm_col) +
      facet_wrap(~type) +
@@
            axis.ticks.x=element_blank()) +
-     #ggtitle('Short Term Property Type\nBy Submarket')+
      theme(plot.title = element_text(hjust = 0.5))
-
-   # Make Long term rental map
-
-   ltrtype.map <- ggplot() +
-     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     #ggtitle('Long Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
+#
+#   # Make Long term rental map
+#
+#   ltrtype.map <- ggplot() +
+#     geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
+#     scale_fill_manual(values=sm_col) +
+#     facet_wrap(~type) +
+#     ylab('# of Properties\n') + xlab('')+
+#     theme(legend.position = 'bottom',
+#           legend.title = element_blank(),
+#           axis.text.x=element_blank(),
+#           axis.ticks.x=element_blank()) +
+#     #ggtitle('Long Term Property Type\nBy Submarket')+
+#     theme(plot.title = element_text(hjust = 0.5))
 #

### 2018-05-23 functions/abb_Functions.R

@@ -597,40 +597,40 @@ abbCreateCompTable <- function(ic.df,
   
   if(split.field == 'none'){
     
-    str.obs <- mean(ic.df$str.obs.pref)
-    str.act <- mean(ic.df$str.act.pref)
-    str.pot <- mean(ltr.df$str.pot.pref)
+    str.act <- mean(ic.df$act_pref)
+    str.lik <- mean(ic.df$lik_pref)
+    str.pot <- mean(ltr.df$pot_pref)
     
     rate.table <- data.frame(ID='all',
-                             var=c(str.obs, str.act, str.pot),
-                             rev.type=c('Observed', 
-                                        'Actual', 
+                             var=c(str.act, str.lik, str.pot),
+                             rev.type=c('Actual', 
+                                        'Likely', 
                                         'Potential'))
     
   } else {
     
     # Calculate cross-tab values
-    str.obs <- tapply2DF(ic.df$str.obs.pref, ic.df[ ,split.field], mean)
-    str.act <- tapply2DF(ic.df$str.act.pref, ic.df[ ,split.field], mean)
-    str.pot <- tapply2DF(ic.df$str.pot.pref, ic.df[, split.field], mean)
+    str.act <- tapply2DF(ic.df$act_pref, ic.df[ ,split.field], mean)
+    str.lik <- tapply2DF(ic.df$lik_pref, ic.df[ ,split.field], mean)
+    str.pot <- tapply2DF(ic.df$pot_pref, ic.df[, split.field], mean)
     
     # Add names
-    str.obs$rev.type <- 'Observed'
     str.act$rev.type <- 'Actual'
+    str.lik$rev.type <- 'Likely'
     str.pot$rev.type <- 'Potential'
     
     # Combine into table
-    rate.table <- rbind(str.obs, str.act, str.pot)
+    rate.table <- rbind(str.act, str.lik, str.pot)
     
     # Reorder factors for common split fields
-    if(split.field == 'geo.mrkt'){
+    if(split.field == 'geo_mrkt'){
       
       rate.table$ID <- factor(rate.table$ID, 
                               levels=c('city-core', 'city', 'beach',
                                        'suburban', 'rural'))
     }
     
-    if(split.field == 'host.type'){
+    if(split.field == 'host_type'){
[…]

### 2018-05-26 scripts/1_str_preprocessing.Rmd
Update to intro:
Update: Str Preprocessing Script to include relative paths.

@@
 title: "Pre Processing of the Short Term Data"
-author: "Andy Krause"
-date: "April 14, 2018"
+subtitle:  "For the 'To Airbnb' paper"
+author: "Andy Krause and Gideon Aschwanden"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 This script executes a number of very long running data preparation process necessary to analyze the short term rental (Airbnb) data.
-If you re-knit (with RMarkdown) this file the code will not evaluate.
-To actually evaluate the code you must manually re-run the code chunks
+If you re-knit this file the code will not evaluate.
+To actually evaluate the code you must manually re-run the code chunks individually in RStudio.
 
 ```{r setup, include=FALSE}
+
   knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
+
 ```
@@
 
-```{r load_libraries}
+```{r load_libraries, warnings=FALSE, message=FALSE}
 
@@
   library(dplyr)
-  library(multidplyr)
+  library(multidplyr) # Note you have to instal from the github site hadley/multidplyr
   library(tidyr)
@@
 
-  # Assign path based on computer name
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-
-  ## Load sources
-  code_path <- file.path('c:', 'code', 'research', 'airBNBmelbourne')
-
-  source(file.path(code_path, 'functions', "abb_Functions.R"))
+  source(file.path(getwd(), 'functions', "abb_Functions.R"))
 
@@
 
-  # Property Information
-  str_raw <- read.csv(file.path(data_path, 'raw', 'melbproperties.csv'), header=T)
-  str_raw2 <- read.csv(file.path(data_path, 'raw', 'melbproperties_to_mar2017.csv'), 
-                        header=T)
+  # Property information
+  str_prop_1 <- read.csv(file.path(getwd(), 'data', 'raw', 'str_prop_1.csv'), header=T)
+  str_prop_2 <- read.csv(file.path(getwd(), 'data', 'raw', 'str_prop_2.csv'), header=T)
 
   # Daily rental information
-  daily_raw  <- read.csv(file.path(data_path, 'raw', 'melbDaily.csv'), header=T)
-  daily_raw2  <- read.csv(file.path(data_path, 'raw', 'melbDaily_to_mar2017.csv'), 
-                           header=T)
+  str_daily_1 <- read.csv(file.path(getwd(), 'data', 'raw', 'str_daily_1.csv'), header=T)
+  str_daily_2 <- read.csv(file.path(getwd(), 'data', 'raw', 'str_daily_2.csv'), header=T)
 
@@
 We then combine the two files for each type, standardize the field names and select only those fields which we need going forward.
+We add a data origin field to the property level information so that we can take the most recent observation in later de-duplication processes.
 
@@
 
-  # Property Level
-  str_df <- dplyr::bind_rows(str_raw, str_raw2) %>%
+  # Property data
+  str_df <- dplyr::bind_rows(str_prop_1 %>% 
+                               dplyr::mutate(origin = 1), 
+                             str_prop_2 %>% 
+                               dplyr::mutate(origin = 2)) %>%
     dplyr::select(property_id=Property.ID, host_id=Host.ID, listing_title=Listing.Title, 
@@
                   avg_nightly_rate=Average.Daily.Rate, min_stay=Minimum.Stay, 
-                  bedrooms=Bedrooms, bathrooms=Bathrooms)
+                  bedrooms=Bedrooms, bathrooms=Bathrooms, origin)
 
   # Clean up
-  rm(str_raw); rm(str_raw2)
+  rm(str_prop_1); rm(str_prop_2)
 
-  # Daily Data
-  daily_df <- dplyr::bind_rows(daily_raw2, daily_raw) %>%
+  # Daily data
+  daily_df <- dplyr::bind_rows(str_daily_1, str_daily_2) %>%
     dplyr::select(property_id=Property.ID, date=Date, status=Status, price=Price,
@@
   # Clean up
-  rm(daily_raw); rm(daily_raw2);gc()
+  rm(str_daily_1); rm(str_daily_2);gc()
 
@@
 Due to our combining of data, we have many duplicate observations.
-We new remove any duplicates.
+We now remove any duplicates.
 Note that the daily data in its raw format does not have a unique identifier, so we much first create one by combining the property id with the date of the observation.
@@
 
-  # Structure Data
-  str_df <- str_df %>% dplyr::filter(!duplicated(property_id))
+  # Property data
+  str_df <- str_df %>% 
+    dplyr::arrange(desc(origin)) %>%
+    dplyr::filter(!duplicated(property_id)) %>%
+    dplyr::select(-origin)
 
-  # Daily Data
+  # Daily data
   daily_df <- daily_df %>%
@@
 
- saveRDS(str_df, file=file.path(data_path, 'prepared', 'str_data.RDS'))
+ dir.create(file.path(getwd(), 'data', 'prepared'))
+ saveRDS(str_df, file=file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))
 

### 2018-05-26 functions/abb_Functions.R

@@ -4,6 +4,140 @@
 #                                                                                        #
 ##########################################################################################
 
+### Calculate the booking status ---------------------------------------------------------
+
+abbCalcBookStr <- function(book_data){
+  
+  # If property has more than one status (one daily booking) find summaries
+  if (nrow(book_data) > 1){
+    
+    # Find min and max date
+    id_min <- min(book_data$date)
+    id_max <- max(book_data$date)
+    
+    # Divide by status and collapse
+    st_v <- book_data$status[1]
+    
+    for(ss in 2:length(book_data$status)){
+      
+      if(book_data$status[ss] == book_data$status[[ss - 1]]){
+        st_v <- paste0(st_v, book_data$status[[ss]])
+      } else {
+        st_v <- paste0(st_v, '.' ,book_data$status[[ss]])
+      }
+    }
+    
+    # Collapse into list objects
+    ss_. <- strsplit(st_v, '[.]')[[1]]
+    
+    # Grab the first status of each
+    sg_. <- substr(ss_.[[1]], 1, 1)
+    for(sg in 1:length(ss_.)){
+      sg_.[sg] <- substr(ss_.[[sg]], 1, 1)  
+    }
+    
+    # Find location of three types
+    id_B <- which(unlist(sg_.) == 'B')
+    id_R <- which(unlist(sg_.) == 'R')
+    id_A <- which(unlist(sg_.) == 'A')
+    
+    # Extract
+    if (length(id_R) > 0){
+      r_. <- ss_.[id_R]
+      bookings <- sum(nchar(unlist(r_.)))
+    } else {
+      bookings <- 0
+    }
+    
+    if (length(id_A) > 0){
+      a_. <- ss_.[id_A]
+      avails <- unlist(lapply(a_., nchar))
+      avail_rate <- sum(avails) / length(book_data$status)
+      
+    } else {
+      
+      avail_rate <- 0
+      
+    }
+    
+    if (length(id_B) > 0){
+      b_. <- ss_.[id_B] 
+      
+      # Count longest and blocked times
+      blocks <- unlist(lapply(b_., nchar))
+      
+      block_rate <- sum(blocks) / length(book_data$status)
+      longest_block <- max(blocks)
+      med_block <- median(blocks)
+      nbr_block <- length(id_B)
+      
+    } else {
+      
+      block_rate <- 0
+      longest_block <- 0
+      med_block <- 0
+      nbr_block <- 0
+      
+    }
+    
[…]

### 2018-05-26 papers/full_paper.Rmd

@@
 Should they though?
-Or rather, is it more profitable to do so when compared to long-term rental (LTR)?
+Or rather, is it more profitable to do so when compared to traditional long-term rental (LTR)?
 And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one.
 
-To address these questions and to provide some guidance to potential and current investors and owners, we examine the short- and long-term residential rental market in Melbourne, Australia.
+To address these questions and to provide some guidance to potential and current investors and owners, we examine the short- and long-term residential rental markets in Melbourne, Australia.
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
@@
 Existing research into short-term rental markets is sparse.
-However, with the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
 Within the existing work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resort access properties.
@@
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
+With the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
 
@@
 Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast, the STR industry lacks sophistication and efficiency.
-Most notably, they find that most nightly or weekly rates are set by resident unit managers (RUMs) and are often under-priced as there is little accountability toward owners.
+Most notably, they find that most nightly or weekly rates are set by resident unit managers (RUMs) and are often under-priced as there is little accountability to owners.
 The authors also note that very little research has been put toward understanding this growing market segment.
@@
 
-A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short-term rentals).
+A critical theme that arises out of the extant literature is that market fundamentals for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short-term rentals).
 Or, in other words, the factors that influence prices and rents in the two are not equivalent.
@@
 
-Though issues of second homes have been primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' Fuller and Michel [@fuller2014stop] has re-focused some of the problems of short-term rentals on large, urban environments.
+Though issues of second homes have been primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism.'' Fuller and Michel [-@fuller2014stop] has re-focused some of the problems of short-term rentals on large, urban environments.
 With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.
@@
 Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].
-Many of the key legal decisions regarding short-term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
+Many of the key legal decisions regarding short-term rentals, particulary through Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
 
@@
 Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
-We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term leasing strategy.
+We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (local workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term leasing strategy.
 
@@
 
-We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a property.
+We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a resdiential investment property.
 More specifically, we examine the following case:
@@
 Most specifically, we will estimate the long-term revenue for observations of properties currently listed on a short-term rental portal (Airbnb).
-Initially, we attempted to also estimate short-term rental revenue for long-term properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
+Initially, we attempted to also estimate short-term rental revenue for long-term rental properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
 
@@
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
-As a result of janitorial fees being a separate line item and directly paid by the occupants they can also be ignored in the comparative analysis below as they are direct.
+As a result of janitorial fees being a separate line item in the STR data and directly paid by the occupants they can also be ignored in the comparative analysis below.
 
@@
 
-We will consider short-term rental (STR) leasting strategy to be prefable to long-term rental (LTR) strategy if the following inequality holds:
+We will consider a short-term rental (STR) leasing strategy to be preferable to a long-term rental (LTR) strategy if the following inequality holds:
 
@@
 
-Though the analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference'.
+Throughout this analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference'.
 For the purposes of this study we consider this a binary position leading to a binary decision of which leasing strategy to follow.
@@
 
-Data for this study were gathered from two different sources, one for short-term rental market and one for the long-term rental market.
+Data for this study were gathered from two different sources, one for the short-term rental market and one for the long-term rental market.
 Short-term rental market observations are from the Airbnb online portal.
 Airbnb is the largest short-term rental hub in the Melbourne region.
-As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas as well and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
+As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
 The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
@@
 Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
-Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on a two-dimensional coordinates.
+Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on two-dimensional coordinates.
 As a result of this, we are unable to directly match observations from the two datasets.
@@
 We begin by filtering observations by time.
-Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental (LTR) versus an Airbnb-type, short-term rental (STR) approach to generating income.
+Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
 To determine the likely LTR rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
@@
 Nearly every multi-family dwelling is owned as a condominium.
-See @berry2000investment for more information on the overall structure of the Australian market] Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, likely, Townhomes in the North American context.
+See @berry2000investment for more information on the overall structure of the Australian market] Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, possibly, Townhomes in the North American context.
 
@@
 As a result we examine the combinations of the two.
-From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
+From this analysis we see that there are 8 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
 The four bedrooms options are only present in the house category.
@@
 At the broadest scale, the long-term Melbourne residential market is usually discussed in terms of Inner, Middle and Outer suburbs.
-Inner suburbs are < 10km from the CBD, Middle suburbs 10 to 20km from CBD and Outer suburbs > 20km from CBD.
+Inner suburbs are < 10km from the CBD, Middle suburbs 10km to 20km from CBD and Outer suburbs > 20km from CBD.
 In general, prices are highest in the inner suburbs and lowest in the outer, with a number of exceptions in the high-end neighborhoods in the east and southeastern areas of the middle suburbs.
 Suburbs in Melbourne are much smaller than their North American counterparts.
-The specific suburb of a property is the second, or finer scale, at which the market operates.
 
@@
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
-
-1. Rural (Outer suburbs, not Beach)
-2. Suburban (Middle suburbs, not Beach)
-3. City (Inner Suburbs, not Beach, not Core)
-4. City-Core (Select inner suburbs with tourist activities and near CBD)
+Using the three broad submarkets from the long-term market (Inner, Middle and Outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
+
+1. City-Core (Select inner suburbs with tourist activities and near CBD)
+2. City (Inner Suburbs, not Beach, not Core)
+3. Suburban (Middle suburbs, not Beach)
+4. Rural (Outer suburbs, not Beach)
 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
@@
 This process is repeated for both the short- and long-term data.
-Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).
-The location of the short- and long-term rentals, colored by submarket, are shown in .
+Finally, we filter our data to observations in suburbs that contain at least three STR and LTR observations.
+The location of the short- and long-term rentals, colored by submarket, are shown in Figures 2 and 3.
 
@@
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (\autoref{smcounts}).
+A number of interesting observations are illustrated here (Figure 4).
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
@@
 
-Within the remainder of this report when we refer to revenues we mean the net revenues from equations 1 and 3, respectively.
+Within the remainder of this study when we refer to revenues we mean the net revenues from equations 1 and 3, respectively.
 Calculations of revenue for the observed and hypothetical long-term rentals are straightforward, weekly rent -- real or imputed -- times 52 minus search cost time and agency fees.
@@
 2.
-Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
+Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long,^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
 3. Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
@@
 As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Likely' revenue metric to be a better measure of actual market performance.
-We chart the distribution of the Likely ($REV_l$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties.
-Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (\autoref{revdens}).
-Actual short-term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
+We chart the distribution of the Likely ($REV_l$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 5).
+Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.
+Likely short-term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
 The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.
@@
 We will, instead, make the comparisons between the two by imputing likely long-term rental revenues for the observed short-term properties and then comparing the measured net revenues of the short-term properties to their estimated imputed long-term revenues.
-We first focus on using the Actual measure of net revenue for the short-term properties as discussed above.
+We first focus on using the Likely measure of net revenue for the short-term properties as discussed above.
 We save discussion and analysis of the Potential revenue for the sensitivity tests later in the study.
@@
 
-Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type, bed/bath and geographic area.
-In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc.
-for all combinations of type, bed/bath and geographic area.
+Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type and geographic area.
+In other words, we separately estimate the LTR model in Equation 10 for Apartments in the city core, Apartments with  in the beach submarket, etc.
+for all combinations of type and geographic area.
 We then combine the results from all estimates back into a single dataset that contains all of the short-term rentals.
@@
 
-The analyses above show that, overall, more than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
-This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference.
-While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
+Overall, 28.4% short-term rental properties were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+While illustrative, a simple univariate analysis does not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
 To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
@@
 We specify three, increasingly complex, logistic regression models.
-We use the actual revenue (not potential) as the dependent variable here, saving an anaylsis of potential revenue for the subsequent sensitivity tests.
+We use the likely revenue (not potential) as the dependent variable here, saving an anaylsis of potential revenue for the subsequent sensitivity tests.
 
@@
 In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
-There is very little significant difference between 1 bed / 1 bath units and the remaining categories, with the exception of 2 bed / 2 bath.
-This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
-Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.
+Additionally, 1 bed / 1 bath units show greater likelihood of short-term preference than 2 bed / 1 bath and 2 bed / 2 bath combinations.
+This could be due to the fact that 2 bed units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
+Larger units, 3 bedrooms plus, generally show no statistical difference in preference porbability to the 1 bed / 1 bath reference unit, with the exception of the 4 bed / 2 bath properties.
 
@@
 Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.
-Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a weak, but positive relationship with short-term preference.
+Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a positive relationship with short-term preference.
 Strict policies do help maintain revenues, but may also scare off some potential guests.
@@
 To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
-First, we examine how the results change if Potential revenue, not Actual revenue, of the short-term properties is used in the comparisons.
-Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothetical motivations and actions of the hosts.
+First, we examine how the results change if Potential revenue, not Likely revenue, of the short-term properties is used in the comparisons.
+Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothesized motivations and actions of the hosts.
 
@@
 
-The above uses the Actual^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
+The above uses the Likely^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
 Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to not factoring in the impact of blocked days.
@@
 Using the potential revenue, 53.3% of all properties are short-term preferable.
-Breaking that down by type and by geographic submarket (Table 5) shows similar findings, in terms of relative comparativeness, to the actual revenue analysis above.
+Breaking that down by type and by geographic submarket (Table 3) shows similar findings, in terms of relative comparativeness, to the Likely revenue analysis above.
 Apartments have a higher short-term preference than do Houses and City-Core properties dominate the other geographic regions.
@@
 
-Our final test of the potential revenue case is to re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
-Generally speaking, the results from the new series of models (Table 6) are qualitatively similar to those derived in the Actual revenue case (Table 4).
+Next, we re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
+Generally speaking, the results from the new series of models (Table 4) are qualitatively similar to those derived in the Likely revenue case (Table 2).
 The overall magnitude of the coefficient for House (vs Apartments) is lowered in the Potential case, suggesting that houses may be blocked off more that Apartments.
@@
 
-Overall, the choice of revenue type, Actual or Potential, does affect some of the conclusions to be derived from the results above.
+Overall, the choice of revenue type, Likely or Potential, does affect some of the conclusions to be derived from the results above.
 As expected, under the Potential case there are more properties (53\% vs 28\%) that exhibit short-term preference.
@@
 
-As hinted at above in the Actual versus Potential comparison and as indicated in the logistic regression models in Tables 5 and 6, host behavior may be an important determinant of achieving short-term preference.
-Additionally, as the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.
+As hinted at above in the Likely versus Potential comparison and as indicated in the logistic regression models in Tables 2 and 4, host behavior may be an important determinant of achieving short-term preference.
+Additionally, as the difference between Likely and Potential revenue suggests, many short-term hosts are not listing their properties full-time.
 There may be, therefore, different types of hosts operating in the Airbnb market.
@@
 
-Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Actual case and a much smaller variation in the Potential case, as expected.
+Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Likely case and a much smaller variation in the Potential case, as expected.
 There is little change for the 'Profit Seekers' as most of these hosts are already operating with few blocked days.
 For the other three sets, considerable gains could be had with a more aggresive leasing approach.
-As the potential figures are somewhat similar here, we will only examine the differences for host types in the Actual number going forward.
+As the potential figures are somewhat similar here, we will only examine the differences for host types in the Likely number going forward.
 
@@
 
-Table 8 compares logistic models results from three of the host types.
+Table 6 compares logistic models results from three of the host types.
 The Opportunistic Sharers show no instances of short-term preference and therefore could not be estimated.
@@
 In short, the conclusions are the same: small apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
-The models for the multi-platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
+The models for the Multi-Platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
 
@@
 However, of this total only 7,400 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
-Of these, only 5,788 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+Of these, only 5,913 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
 Overall, the Airbnb market is very small relative to the long-term market.
@@
 
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 5).
 However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
-This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (\autoref{pointmaps}).
+This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figures 2 and 3).
 Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
 
-In analyzing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
+In comparing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
 As expected, this probability is not equal across space, property type or property size (bed and bath count).
@@
 Core city properties are more likely than other properties to prefer a short-term strategy, as are smaller properties versus larger ones.
-For instance, 36\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 8\% of suburban houses did.
+For instance, 35\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 12\% of suburban houses did.
 Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
 
-The nightly rates and total occupancies drive the profitability of short-term leasing.
+<!-- The nightly rates and total occupancies drive the profitability of short-term leasing.
 As the nightly rate vs.
@@
 The vertical-ness of the divide between short- and long-term preference in the SVM plots suggests that occupancy rate is the most critical factor in reaching short-term preference in most markets.
-
-The logistic regression models (Table 4, 6 and 8) than we estimate show that most of the finding from the univariate and bivariate analyses done earlier are validated.
+-->
+
+The logistic regression models (Table 2, 4 and 6) than we estimate show that most of the finding from the univariate analyses done earlier are validated.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
@@
 In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
-If owners all operated as profit maximizers this figure could be 53\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
+If owners all operated as profit maximizers this figure could be 54\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
 
@@
 
-Beyond airBNB.com other short-term platforms exist (e.g.
+Beyond Airbnb.com other short-term platforms exist (e.g.
 www.homeaway.com).
@@
 
-#### Data, Code and Interactivity
+#### Data and Code
 
@@
 All the code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
-An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
+
+<!-- An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
+-->
 

### 2018-05-27 scripts/1_str_preprocessing.Rmd
Update ltr prep.

@@
   # Add nested daily data to structural data
-  str_df <- str_df %>%
+  str_tdf <- str_df %>%
     as.tibble() %>%
@@
  dir.create(file.path(getwd(), 'data', 'prepared'))
- saveRDS(str_df, file=file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))
+ saveRDS(str_tdf, file=file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))
 

### 2018-05-27 scripts/2_ltr_preprocessing.Rmd
Update ltr prep.

@@
 title: "Pre Processing of the Long Term Data"
-author: "Andy Krause"
-date: "April 14, 2018"
+author: "Andy Krause and Gideon Aschwanden"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output: html_document
@@
 This script executes a number of long running data preparation process necessary to analyze the long term rental data.
-If you re-knit (with RMarkdown) this file the code will not evaluate.
-To actually evaluate the code you must manually re-run the code chunks
+If you re-knit this file (with RMarkdown) the code will not evaluate.
+To actually evaluate the code you must manually re-run the code chunks in RStudio.
 
 ```{r setup, include=FALSE}
+
   knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
+
 ```
@@
 
-We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions
+We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions.
 
@@
   library(dplyr)
-  library(multidplyr)
+  library(multidplyr) # Note you have to install from the github site hadley/multidplyr
   library(tidyr)
@@
 
-We then set the paths to the data
+We then load the custom functions.
 
@@
 
-  # Assign path based on computer name
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  code_path <- file.path('c:', 'code', 'research', 'airBNBmelbourne')
-
-  ## Load sources
-  source(file.path(code_path, 'functions', "abb_Functions.R"))
+  source(file.path(getwd(), 'functions', "abb_Functions.R"))
 
@@
 
-Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size
+Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size.
 
@@
 
-Next, we load the data.
+Next, we load the long term rental data.
 
@@
 
-  # Load the raw rent data
-  ltr_df <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)
+  ltr_df <- read.csv(file.path(getwd(), 'data', 'raw', 'ltr_data.csv'), header=T)
 
@@
 
+  # Convert to lower case
   names(ltr_df) <- tolower(names(ltr_df))
 
+  # Trim Fields
   ltr_df <- ltr_df %>%
@@
 
-A small portion of the observations are missing the necessary identification fields to proceed.  These are removed here.
+A small portion of the observations are missing the necessary identification fields (Event, Address or Activity ID) to proceed.  These are removed.
 
@@
 
-  ltr_df$last_date <- apmFixDates(ltr_df$last_date)
-  ltr_df$first_date <- apmFixDates(ltr_df$first_date)
-  ltr_df$date <- apmFixDates(ltr_df$date)
+  ltr_df$last_date <- fixAPMDates(ltr_df$last_date)
+  ltr_df$first_date <- fixAPMDates(ltr_df$first_date)
+  ltr_df$date <- fixAPMDates(ltr_df$date)
 
@@
 
-Next, we create a unique identifier for each rental transaction.  Note that there are still, often, multiple observation per transaction due to the listing change data.
-
+Next, we create a unique identifier (by market transaction, not by observation in the data) for each rental transaction.
+Note that there are still, often, multiple observations per transaction due to the listing change data.
 ```{r uniq_trans}
-
- ## Create Unique Key
 
@@
 
-Next, we split the data into property specific information and transasction specific information and carry out individual preparation on each (and will re-combine later)
+Next, we split the data into property specific information and transaction specific information and carry out individual preparation on each (and will re-combine later).
 
@@
 
-```{r}
+```{r rec_trans}
 
@@
 
-```{r}
+```{r rec_prop_1}
 
@@
 
-```{r}
+```{r rec_prop_2}
 
@@
 
-```{r}
+```{r merge_loc_prop}
 
@@
 
-```{r}
+```{r merge_prop_trans}
 
@@
 
-```{r}
+```{r write_out}
 
- saveRDS(ltr_tdf, file=file.path(data_path, 'prepared', 'ltr_data.RDS'))
+ dir.create(file.path(getwd(), 'data', 'prepared'))
+ saveRDS(ltr_tdf, file=file.path(getwd(), 'data', 'prepared', 'ltr_data.RDS'))
 

### 2018-05-27 functions/abb_Functions.R

@@ -1,10 +1,10 @@
-##########################################################################################
-#                                                                                        #    
-#  Custom functions for working with APM and AirDNA data in the ABB Project              #
-#                                                                                        #
-##########################################################################################
+#*****************************************************************************************
+#                                                                                        *    
+#  Custom functions for working with APM and AirDNA data in the ABB Project              *
+#                                                                                        *
+#*****************************************************************************************
 
-### Calculate the booking status ---------------------------------------------------------
+### Calculate the booking status ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
 abbCalcBookStr <- function(book_data){
   
@@ -109,6 +109,29 @@ abbCalcBookStr <- function(book_data){
                     bookings=bookings))
 }
 
+### Correct the APM data dates ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+fixAPMDates <- function(x_date){
+  
+  # x.date:  date vector
+  
+  ## Convert to character (from factor or numberic)
+  
+  if (class(x_date) != 'character') x_date <- as.character(x_date)
+  
+  ## Remove Time suffixes  
+  
+  x_date <- str_replace_all(x_date, ' 0:00', '')
+  
+  ## Standardize all years to 2000s  
+  
+  x_date <- str_replace_all(x_date, '/20', '/')
+  
+  ## Return values as standardized, British/Australian date format  
+  
+  as.Date(x_date, "%d/%m/%y")   
+  
+}
 
 
 
@@ -284,30 +307,6 @@ abbImputeDaily <- function(prop.df,
   ## Return Values  
   
   return(imp.daily)
-  
-}
-
-### Correct the APM data dates -----------------------------------------------------------
-
-apmFixDates <- function(x.date){
-  
-  # x.date:  date vector
-  
-  ## Convert to character (from factor or numberic)
-  
-  temp.date <- as.character(x.date)
-  
-  ## Remove Time suffixes  
-  
-  temp.date <- str_replace_all(temp.date, ' 0:00', '')
-  
-  ## Standardize all years to 2000s  
-  
-  temp.date <- str_replace_all(temp.date, '/20', '/')
-  
-  ## Return values as date format  
-  
-  return(as.Date(temp.date, "%d/%m/%y"))   
   
 }
 

### 2018-05-29 scripts/3_data_prep.Rmd
Set data_prep eval to FALSE
Update data prep to relative paths

@@
 output:
-  pdf_document: default
+  htlm_document: default
 editor_options: 
@@
 ```{r setup, include=FALSE}
-#knitr::opts_chunk$set(eval=TRUE)
+
+  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
+
 ```
@@
 This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).
-Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocess.R** and **2_ltr_preprocess.R**.
+Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocessing.RMD** and **2_ltr_preprocessing.RMD**.
 
@@
   library(sf)
-  library(geosphere)
-  library(ggmap)
-  library(multidplyr)
+  library(multidplyr) # Note you have to install from the github site hadley/multidplyr
   library(tmap)
-
-  options(stringsAsFactors=FALSE)
 
@@
 
-Then we set the paths to the data
+```{r saf}
 
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
-  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
+  options(stringsAsFactors=FALSE)
 
@@
 
-  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+  source(file.path(getwd(), 'functions', 'abb_Functions.R'))
 
@@
   ltr_col <- col_df$rgb[3]
-  sm_col <- col_df$rgb[c(2, 4, 5, 8, 6)]
+  sm_cols <- col_df$rgb[c(2, 4, 5, 8, 6)]
 
@@
 
-Next we load in the raw data.  The short-term rental (Airbnb) data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.
+Next we load in the raw data from the previous pre-processing activities.
 
-```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE}
 
-  str_tdf <- readRDS(file.path(data_path, 'prepared', 'str_data.RDS'))
+  str_tdf <- readRDS(file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))
 
-  ltr_tdf <- readRDS(file.path(data_path, 'prepared', 'ltr_data.RDS'))
+  ltr_tdf <- readRDS(file.path(getwd(), 'data', 'prepared', 'ltr_data.RDS'))
 
@@
 
-And, finally, we load three GIS shapefiles.
+Then we load three GIS shapefiles.
 The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area.
@@
 
-  suburb_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
+  suburb_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'melbSuburbs.shp')) %>%
     st_transform(crs=4283)
-  sa1_sf <- sf::st_read(file.path(data_path, 'geographic', 'sa1s.shp')) %>%
+  sa1_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'sa1s.shp')) %>%
     st_transform(crs=4283)
-  beach_sf <- sf::st_read(file.path(data_path, 'geographic','portPhillipBeach.shp')) %>%
+  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach.shp')) %>%
     st_transform(crs=4283)
@@
 
-Next we filter the observations by time.
+We begin by filtering the observations by time.
 Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.
@@
 
-1. **House**:  Includes properties labeled 'House' or 'Townhouse'
+1. **House**:  Includes properties labeled 'House', 'Townhouse' or 'Villa'
 2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
 3.
-**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.
+**Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse' and 'Yurt.
 
@@
 
-1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
+1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace', 'Townhouse' or 'Villa'
 2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
-3. **Other**: Includes properties labeled as 'Semi' and 'Villa'
+3. **Other**: Includes properties labeled as 'Semi'
 
@@
 In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
+In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
 As a result we examine the combinations of the two.
@@
 ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-
- ## Build the map object
 
@@
 
-  plot(studyarea_sf)
+  plot(studyarea_sf$geometry)
 
@@
 Finally we add the spatial data back onto the tabular data and filtering out those outside of the study area using an inner join.
-We then have to remove the geometry field as it causes issues with future analyses (for now)
+We then have to remove the geometry field as it causes issues with future analyses (for now).
 
@@
 
-Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).
+Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.
 Short term revenues range from neglible to highs of greater than \$80,000.
@@
         col_df, clean_count, core_suburbs,
-        file=paste0(data_path, '/prepared/prepared_data.RData'))
+        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))
 

### 2018-05-29 scripts/3_data_prep.Rmd
Update functions in data_prep

@@
 
-   setCleanCount()
+   clean_obj <- setCleanCount()
 
@@
 
-  countCleaning('time')
+  clean_obj <- countCleaning(clean_obj, 'time')
 
@@
 
-   # Count Cleaning
-   countCleaning('property_type')
+   # Count 
+   clean_obj <- countCleaning(clean_obj, 'property_type')
 
@@
   # Count cleaning
-  countCleaning('listing_type')
+  clean_obj <- countCleaning(clean_obj, 'listing_type')
 
@@
   # Count Data Cleaning
-  countCleaning('bedrooms')
+    clean_obj <- countCleaning(clean_obj, 'bedrooms')
 
@@
    # Count cleaning
-   countCleaning('baths')
+  clean_obj <- countCleaning(clean_obj, 'baths')
 
@@
  # Count Cleaning
-
-  countCleaning('bedbath')
+  clean_obj <- countCleaning(clean_obj, 'bedbath')
 
@@
   # Count Cleaning
-  countCleaning('hostpolicy')
+  clean_obj <- countCleaning(clean_obj, 'hostpolicy')
 
@@
    # Count Cleaning
-   countCleaning('location')
+  clean_obj <- countCleaning(clean_obj, 'location')
 
@@
    # Count Cleaning
-   countCleaning('rates_rents')
+  clean_obj <- countCleaning(clean_obj, 'rates_rents')
 
@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        col_df, clean_count, core_suburbs,
+        col_df, clean_obj, core_suburbs,
         file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

### 2018-05-29 functions/abb_Functions.R

@@ -133,8 +133,55 @@ fixAPMDates <- function(x_date){
   
 }
 
+### Set the cleaning counter ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
+setCleanCount <- function(){
+  
+  # Make counts of initial sizes
+  str_orig <- nrow(str_tdf)
+  ltr_orig <- nrow(ltr_tdf)
+  
+  # Create initial data.frame
+  clean_df <- data.frame(operation='initial',
+                         str=str_orig,
+                         ltr=ltr_orig)
+  
+  # Return
+  structure(list(count_df = clean_df,
+                 str_running = str_orig,
+                 ltr_running = ltr_orig),
+            class='clean')
 
+}
+
+### Cleaning counting updater ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+countCleaning <- function(clean_obj, operation){
+  
+  if (!'clean' %in% class(clean_obj)){
+    message('"clean_obj" not an object of class "clean"')
+    return(NULL)
+  } 
+  
+  # Count recent cuts  
+  str_cut <- clean_obj$str_running - nrow(str_tdf)
+  ltr_cut <- clean_obj$ltr_running - nrow(ltr_tdf)
+  
+  # Build new dataframe
+  new_df <- data.frame(operation=operation,
+                       str=str_cut,
+                       ltr=ltr_cut)
+  
+  # Add to existing DF
+  comb_df <- rbind(clean_obj$count_df, new_df)
+
+  # Return
+  structure(list(count_df = comb_df,
+                 str_running = nrow(str_tdf),
+                 ltr_running = nrow(ltr_tdf)),
+            class='clean')
+
+}
 
 
 
@@ -312,48 +359,8 @@ abbImputeDaily <- function(prop.df,
 
 
 
-### Set the cleaning counter -------------------------------------------------------------
 
-setCleanCount <- function(){
-  
-  # Make counts of initial sizes
-  str_orig <- nrow(str_tdf)
-  ltr_orig <- nrow(ltr_tdf)
-  
-  # Create initial data.frame
-  clean_df <- data.frame(operation='initial',
-                         str=str_orig,
-                         ltr=ltr_orig)
-  
-  # Assign initial values to globalEnv
[…]

### 2018-05-30 scripts/1_str_preprocessing.Rmd
Add imputation of likely bookings

@@
 title: "Pre Processing of the Short Term Data"
-subtitle:  "For the 'To Airbnb' paper"
-author: "Andy Krause and Gideon Aschwanden"
 date: '`r format(Sys.Date(), "%B %d, %Y")`'

### 2018-05-30 scripts/2_ltr_preprocessing.Rmd
Add imputation of likely bookings

@@
 title: "Pre Processing of the Long Term Data"
-author: "Andy Krause and Gideon Aschwanden"
 date: '`r format(Sys.Date(), "%B %d, %Y")`'

### 2018-05-30 scripts/3_data_prep.Rmd
Add imputation of likely bookings

@@
 title: "Data Preparation, Integration and Cleaning"
-output:
-  htlm_document: default
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
+output: html_document
 editor_options: 

### 2018-05-30 scripts/4_data_analysis.Rmd
Add imputation of likely bookings

@@
 ---
-title: "Should I Airbnb My Property: Analytic Code Explanation"
-author: "Andy Krause and Gideon Aschwanden"
-date: "March 10, 2017"
+title: "Data Analysis and Modeling"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output: html_document
@@
 
-This document describes all of the code used to the generate the output included in the 'Should I Airbnb my Property' study.
-Additional analysis that were not included in the final report are also found within this document.
+This document describes all of the code used to the generate the output included in the 'To Airbnb?' study.
 This analysis uses the output from the **3_data_prep.rmd** file found in the same online repository.
@@
 
+```
+
+```{r set_options, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
   options(stringsAsFactors=FALSE)
@@
   options(xtable.caption.placement='top')
-
-```
-
-Then we set the paths to the data
-
-```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
-
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
-  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
 
@@
 
+  # Exchange rate: AUS to US 
   exch_rate <- 1.32
 
+  # Date of investment decision
   decision_date <- lubridate::as_date('2015-09-01')
@@
 
+We then load the data.
+
 ```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
 
-  load(file.path(data_path, 'prepared', 'prepared_data.RData'))
+  load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))
 
@@
 We begin the analysis by calculating the net revenues for the short term data.
-We calculate three types of net revenues, Observed, Extrapolated (Actual) and Potential.
-The difference are described more fully in the writeup.
+We calculate three types of net revenues, Actual, Likely (Extrapolated) and Potential.
+The differences are described more fully in the writeup.
 
-Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
+Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.
+The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
 For 2 persons in an apartment that works out to \$5 per person per day.
@@
 
+We then calculate the actual net revenue by multiplying booking times median rate - utility costs.
+
 ```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
@@
 
+Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties
+
 ```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Create daily rate summary
+  rate_summ <- str_tdf %>% 
+   dplyr::select(property_id, daily_data) %>%
+    tidyr::unnest() %>%
+    dplyr::filter(status != 'B') %>%
+    dplyr::group_by(date) %>%
+    summarize(rate = length(which(status == 'R')) / n(),
+            obs = n())
+
+  # Create new cluster
+  abb_cl <- get_default_cluster()
+
+  # Register function and variable
+  cluster_copy(abb_cl, impLikelyBookings)
+  cluster_copy(abb_cl, rate_summ)
+  cluster_library(abb_cl, c("magrittr", 'dplyr', 'tidyr'))
+
+  # Summarize daily by property
+  lik_book_df <- str_tdf %>%
+    dplyr::filter(total_days != 366) %>%
+    multidplyr::partition(property_id, cluster=abb_cl) %>% 
+    dplyr::do(impLikelyBookings(., std=g)) %>% 
+    dplyr::collect()
+
+  # Add to the existing data
+  str_tdf <- str_tdf %>%
+    left_join(lik_book_df, by='property_id') %>%
+    dplyr::mutate(lik_bookings = if_else(is.na(lik_bookings), bookings, as.integer(lik_bookings)))
+
+  # Calculate likely revenue
+  str_tdf$lik_revenue <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
+                           (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))
 
@@
 
-  # Calculate likely revenue
-  str_tdf$lik_revenue <- ((str_tdf$bookings * str_tdf$extr_par * str_tdf$med_rate) -
-                           (str_tdf$bookings * str_tdf$avg_guests *
-                             cpppd * str_tdf$extr_par))
 ```
@@
 
-  str_tdf$pot_occ_rate <- ((str_tdf$bookings * str_tdf$extr_par) /
-                             (366 - (366 * str_tdf$block_rate)))
+  str_tdf$pot_occ_rate <- ((str_tdf$lik_bookings) / (366 - (366 * str_tdf$block_rate)))
 

### 2018-05-30 functions/abb_Functions.R

@@ -183,6 +183,37 @@ countCleaning <- function(clean_obj, operation){
 
 }
 
+### Impute likely bookings ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+impLikelyBookings <- function(prop_df, 
+                              rate_summ){
+  
+  # Unnest the str prop data
+  prop_df <- prop_df %>% 
+    tidy::unnest()
+  
+  # Get relative booking rate (prop versus other props on those days)
+  rsp <- rate_summ %>%
+    dplyr::filter(date %in% prop_df$date)
+  w_obs <- sum(rsp$obs * rsp$rate) / sum(rsp$obs)
+  rel_rate <- (1 - prop_df$block_rate - prop_df$avail_rate) / w_obs
+  
+  # Estimate likely bookings with dates not currently in property
+  rso <- rate_summ %>%
+    dplyr::filter(!date %in% prop_df$date)
+  lik_book <- round(sum(rso$obs * rso$rate) / sum(rso$obs) * nrow(rso) * rel_rate, 0)
+  
+  # Add to existing to create likely and limit columns
+  p_df <- prop_df %>% 
+    dplyr::mutate(lik_bookings = bookings + lik_book) %>%
+    dplyr::select(property_id, lik_bookings) %>%
+    dplyr::slice(1)
+  
+  # Return
+  p_df
+  
+}
+
 
 
 

### 2018-05-30 scripts/5_data_viz.Rmd
Reorg: deprecate plots and functions

--- 2018-05-21 scripts/5_data_viz.Rmd
@@
 ```{r setup, include=FALSE}
+
   knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}
+
+  library(tmap)
+  library(magrittr)
+  library(dplyr)
+  library(ggplot2)
+
+```
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
+
+  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
+
+  dir.create(file.path(getwd(), 'images'))
+
+  str_col = col_df$rgb[1]
+
+```
+
+## Suburb Location Map
+
+```{r sub_loc.map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  # Set submarket colors
+  suburb_sf$col <- 'gray80'
+  suburb_sf$col[suburb_sf$class == 'Middle'] <- 'gray50'
+  suburb_sf$col[suburb_sf$class == 'Inner'] <- 'gray20'
+
+   # Make map
+
+  png(filename = file.path(getwd(), 'images', "sub_loc_map.png"), 
+       width = 6.5, height = 6.5, units = 'in', res = 300)
+
+  tm_shape(suburb_sf) +
+    tm_polygons("class", palette=c('gray20', 'gray50', 'gray80'), title='Suburb Class') +
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='black', lwd=5) +
+    tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
+                  title='Study Area')
+
+  dev.off()
+
+```
+
+## Point Location Maps
+
+```{r location map}
+
+  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
+              col_df$rgb[6], col_df$rgb[1])
+
+  png(filename = file.path(getwd(), 'images', "ltr_loc_map.png"), 
+       width = 4, height = 4, units = 'in', res = 300)
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='gray50', lwd=2) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray90', lwd=.5) +
+  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
+  dev.off()
+
+  png(filename = file.path(getwd(), 'images', "str_loc_map.png"), 
+       width = 4, height = 4, units = 'in', res = 300)
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='gray50', lwd=2) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray90', lwd=.5) +
+  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.3, shape=16)
+  dev.off()
+
+```
+
+```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
+
+   # Make Airbnb submarket map
+
+   strtype_bar <- ggplot() +
+     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=sm_col, name='Submarket') +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     ggtitle('Short Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+   # Make Long term rental map
+
+   ltrtype_bar <- ggplot() +
+     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     scale_fill_manual(values=sm_col) +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'bottom',
+           legend.title = element_blank(),
+           axis.text.x=element_blank(),
+           axis.ticks.x=element_blank()) +
+     ggtitle('Long Term Property Type\nBy Submarket')+
+     theme(plot.title = element_text(hjust = 0.5))
+
+     png(filename = file.path(getwd(), 'images', "loc_bar.png"), 
+       width = 8, height = 4, units = 'in', res = 300)
+
+     ggMultiPlots(strtype_bar, ltrtype_bar, cols=2)
+     dev.off()
+
+```
+
+```{r maps}
+
+   dens_cols <- c(col_df$rgb[3], col_df$rgb[1], col_df$rgb[2])
 
@@
    rev_df <- bind_rows(str_tdf %>% 
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'str'),
-                       ltr_tdf %>%
-                         dplyr::select(type, gross_revenue) %>%
-                         dplyr::mutate(tenure = 'ltr'))
+                         dplyr::select(type, revenue=lik_revenue_net) %>%
+                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
+                                       alpha = .5),
+                       str_tdf %>% 
+                         dplyr::select(type, revenue=pot_revenue_net) %>%
+                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
+                                       alpha = .4),
+                       ltr_df %>%
+                         dplyr::select(type, revenue=gross_revenue) %>%
+                         dplyr::mutate(tenure = 'Long-Term   ',
+                                       alpha = .9))
 
-   revdens <- ggplot(rev_df, 
-                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
+  png(filename = file.path(getwd(), 'images', "rev_dens.png"), 
+       width = 5.5, height = 4, units = 'in', res = 300)
+
+   ggplot(rev_df,
+          aes(x=revenue, fill=tenure, color=tenure)) +
     geom_density(alpha=.5) +
-    scale_fill_manual(values=c(ltr_col, str_col)) +
-    scale_color_manual(values=c(ltr_col, str_col)) +
-    ggtitle('Annual Revenues by Tenure Type') +
+    scale_fill_manual(values=dens_cols) +
+    scale_color_manual(values=dens_cols) +
+    ggtitle('Short Term Revenue vs Long Term Revenue') +
     xlab('Annual Revenue') +
@@
 
-The location of the short and long term rentals, colored by submarket, are shown below
+Host type investigation
 
-```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+```{r host_types}
 
- # Set submarket colors
-   # Make map
-  tm_shape(sub_sf) +
-    tm_polygons() + 
-  tm_shape(study_area) + 
-    tm_polygons(col='dodgerblue3') +
-  tm_shape(ltr_sf) +
-    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)
-
-  tm_shape(sub_sf) +
-    tm_polygons() + 
-  tm_shape(study_area) + 
-    tm_polygons(col='dodgerblue3') +
-  tm_shape(str_sf) +
-    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)
-
-  str_map <- ggplot() +
-     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') 
-#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
-#                alpha=.2) +
-#     scale_color_manual(values=sm_col) +
-#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-#     xlab('') + ylab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_rect(fill = "white"),
-#           axis.text.x = element_blank(),
-#           axis.text.y = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.title.x=element_blank(),
-#           axis.title.y=element_blank(),
-#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-#     guides(colour = guide_legend(override.aes = list(size=3,
-#                                                      alpha=1))) + 
-#     ggtitle('Short-Term Rental Locations')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-# ```
-# 
-# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
-# 
-#   # Make map
-# 
-#   ltr.map <- ggplot() +
-#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
-#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
-#                alpha=.1) +
-#     scale_color_manual(values=sm_col) +
-#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
-#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
-#     xlab('') + ylab('')+
-#     theme(legend.position = 'bottom',
-#           legend.title = element_blank(),
-#           plot.title = element_text(hjust = 0.5),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_rect(fill = "white"),
-#           axis.text.x = element_blank(),
-#           axis.text.y = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.title.x=element_blank(),
-#           axis.title.y=element_blank(),
-#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
-#     guides(colour = guide_legend(override.aes = list(size=3,
-#                                                      alpha=1))) + 
-#     ggtitle('Long-Term Rental Locations')+
-#     theme(plot.title = element_text(hjust = 0.5))
-#   
-# ```
-# 
-# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-#   
-#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
-#       bg='transparent')
-#      str.map
-#   dev.off()
-#   
-#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
-#       bg='transparent')
-#      ltr.map
-#   dev.off()
-# 
-#   ggMultiPlots(str.map, ltr.map, cols=2)
-#   
-#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
-#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
-# 
-```
-#
-
-```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
-
-   # Make Airbnb submarket map
-
-   strtype.map <- ggplot() +
-     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     #ggtitle('Short Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-   # Make Long term rental map
-
-   ltrtype.map <- ggplot() +
-     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     #ggtitle('Long Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
-#
-
-<!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->
-
-<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->
-
-<!--   # Actual -->
-<!--    stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')] -->
-<!--    stra.rev$tenure <- 'Short-Term (Actual)   ' -->
-<!--    names(stra.rev)[2] <- 'revenue' -->
-
-<!--   # Potential -->
-<!--    strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')] -->
-<!--    strp.rev$tenure <- 'Short-Term (Potential)   ' -->
-<!--    names(strp.rev)[2] <- 'revenue' -->
-
-<!--   # Long-Term -->
-<!--    ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')] -->
-<!--    ltr.rev$tenure <- 'Long-Term   ' -->
-<!--    names(ltr.rev)[2] <- 'revenue' -->
-
-<!--   # Combine -->
-<!--    revdens.data <- rbind(stra.rev, strp.rev, ltr.rev) -->
-
-<!--   ## Build a plot -->
-
-<!--    rd.plot <- ggplot(revdens.data,  -->
-<!--                      aes(x=revenue, fill=tenure, color=tenure)) + -->
-<!--      geom_density(alpha=.5) + -->
-<!--      scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
-<!--      scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
-<!--      xlab('\nAnnual Revenue') + -->
-<!--      scale_x_continuous(breaks=c(seq(0, 75000, by=25000)), -->
-<!--                         labels=c('$0', '$25k', '$50k', '$75k'))+ -->
-<!--      theme(legend.position='none', -->
-<!--            legend.title = element_blank(), -->
-<!--            plot.title = element_text(hjust = 0.5), -->
-<!--            axis.text.y = element_blank(), -->
-<!--            axis.ticks.y = element_blank(), -->
-<!--            axis.title.y=element_blank()) + -->
-<!--      coord_cartesian(xlim=c(0, 85000)) -->
-<!--      rd.plot <- rd.plot + facet_wrap(~tenure) -->
-
-<!--   ## Plot -->
-
-<!--      rd.plot -->
-
-<!-- ``` -->
-
-<!-- ## Results -->
-
-<!-- Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--  ## Set Preference data field -->
-
-<!--   str_df.ic$pref <- str_df.ic$str.act.pref -->
-
-<!--  ## Calculate the percentile fields -->
-
-<!--   str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate,  -->
-<!--                                       return.type='rank')  -->
-<!--   str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate,  -->
-<!--                                   return.type='rank')  -->
-
-<!--  ## Calculate raw and percentile occupancies -->
-
-<!--   rawocc.metro <- abbPrefPlot(str_df.ic, -->
-<!--                          x.field='occ.rate', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5) -->
-
-<!--   qtlocc.metro <- abbPrefPlot(str_df.ic, -->
-<!--                         x.field='occ.qtl', -->
-<!--                         smooth=TRUE, -->
-<!--                         smooth.span=.5) -->
-
-<!--    ## Make plots   -->
-
-<!--   # Raw -->
-<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
-<!--                    aes(x=x.var, y=Var))+ -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='none') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Quantile -->
-<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
-<!--                    aes(x=x.var, y=Var))+ -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='none') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   # Make Plot -->
-<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference. -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   rate.hm <- abbHeatMap(str_df.ic, -->
-<!--                 x.field='occ.rate', -->
-<!--                 y.field='med.rate', -->
-<!--                 pref.field='str.act.pref', -->
-<!--                 svm=F,  -->
-<!--                 alpha.count=T, -->
-<!--                 add.points=T, -->
-<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   rate.hm + ylab('Nightly Rate') -->
-
-<!-- ``` -->
-
-<!-- To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.  -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
-<!--                             x.field='occ.rate', -->
-<!--                             y.field='med.rate', -->
-<!--                             pref.field='str.act.pref', -->
-<!--                             svm=T,  -->
-<!--                             alpha.count=F, -->
-<!--                             add.points=T, -->
-<!--                             fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   rate.hm.svm+ ylab('Nightly Rate') -->
-
-<!-- ``` -->
-
-<!-- As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.
--->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
-<!--                 x.field='occ.qtl', -->
-<!--                 y.field='rate.qtl', -->
-<!--                 pref.field='str.act.pref', -->
-<!--                 svm=F,  -->
-<!--                 alpha.count=T, -->
-<!--                 add.points=T, -->
-<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   qtl.hm+ ylab('Nightly  (Pcntl)') -->
-
-<!-- ``` -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T,  -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
-<!--   qtl.hm.svm+ ylab('Nightly  (Pcntl)') -->
-
-<!-- ``` -->
-
-<!-- ### Submarkets -->
-
-<!-- Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.  -->
-
-<!-- First we make a comparison table of the results.   -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--  # Make Basic comparison table -->
-<!--   pref.table.type <- abbCreateCompTable(ic.df=str_df.ic, -->
-<!--                                    split.field='type') -->
-
-<!--  # Limit to the extrapolated pref type -->
-<!--   pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ] -->
-
-<!-- ``` -->
-
-<!-- We then turn this into a simple chart to see the differences. -->
-
-<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
-
-<!--   ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) +  -->
-<!--     geom_bar() + -->
-<!--     scale_fill_manual(values=c('red', 'blue')) + -->
-<!--     xlab('') + -->
-<!--     ylab('% of properties where Airbnb is more profitable') + -->
-<!--     scale_y_continuous(breaks=c(0,.25,.5,.75,1), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='none') -->
-
-<!-- ``` -->
-
-<!-- We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.  -->
-
-<!-- ```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--  ## Create dataset -->
-
-<!--   type.data.ic <- str_df.ic -->
-
-<!--   # Id the types -->
-<!--   apt.id <- which(str_df.ic$type == 'Apartment') -->
-<!--   house.id <- which(str_df.ic$type == 'House') -->
-
-<!--   # Recalculate the percentiles -->
-<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
-<!--                                       return.type='rank') -->
-<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
-<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->
-
-<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
-<!--                                   return.type='rank') -->
-<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
-<!--     type.data.ic$med.rate[house.id], return.type='rank') -->
-
-<!-- ```  -->
-
-<!-- Then we calculate the preference figures -->
-
-<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->
-
-<!--  ## Calc the occ rate numbers -->
-
-<!--   rawocc.type <- abbPrefPlot(type.data.ic, -->
-<!--                          x.field='occ.rate', -->
-<!--                          split.field='type', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5 , -->
-<!--                          spl.col=c('black', 'grey40')) -->
-
-<!--   pctocc.type <- abbPrefPlot(type.data.ic, -->
-<!--                          x.field='occ.qtl', -->
-<!--                          split.field='type', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5 , -->
-<!--                          spl.col=c('black', 'grey40')) -->
-
-<!-- ``` -->
-
-<!-- And then plot.  -->
-
-<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->
-
-<!--  ## Build raw plot -->
-
-<!--   ptr.occ <- ggplot(rawocc.type$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_color_manual(values=c('black', 'grey60'), -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Build Percentile Plots -->
-
-<!--   ptq.occ <- ggplot(pctocc.type$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_color_manual(values=c('black', 'grey60'), -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Plot   -->
-
-<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->
-
-<!-- ``` -->
-
-<!-- Finally, we make percentile SVM heatmaps for both apartments and houses.  -->
-
-<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->
-
-<!--  ## Make House SVM Heatmap -->
-
-<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
-<!--                                           'House', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
-<!--   theme(legend.position='none') + -->
-<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
-<!--   ylab('Nightly Rate (Pcntl)') + -->
-<!--   xlab('Occupancy Rate (Pcntl)') -->
-
-<!--  ## Make Apartment SVM Heat Map -->
-
-<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
-<!--                                           'Apartment', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
-<!--   ylab('Nightly Rate (Pcntl)') + -->
-<!--   xlab('Occupancy Rate (Pcntl)') -->
-
-<!--  ## Plot -->
-
-<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-<!-- #### Geographic Submarkets -->
-
-<!-- We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets. -->
-
-<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->
-
-<!--  # Make Basic comparison table -->
-<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
-<!--                                    split.field='geo.mrkt') -->
-
-<!--  # Convert to wide format for output -->
-<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->
-
-<!--  # Limit to the extrapolated pref type -->
-<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
-<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
-<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->
-
-<!--  # Fix names   -->
-<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
-<!--   options(xtable.comment = FALSE) -->
-
-<!--  ## Make printable table -->
-
-<!--   print(xtable(pref.table[,1:2],  -->
-<!--                caption='Geographic Submarket Preferability\n', -->
-<!--                digits=1, -->
-<!--                align='llr'), -->
-<!--         include.rownames=FALSE, -->
-<!--         caption.placement='top') -->
-
-<!-- ``` -->
-
-<!-- ```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}  -->
-
-<!--  ## Build data -->
-
-<!--   subm.data.ic <- str_df.ic -->
-
-<!--   # Get IDs -->
-<!--   cc.id <- which(str_df.ic$geo.mrkt == 'city-core') -->
-<!--   city.id <- which(str_df.ic$geo.mrkt == 'city') -->
-<!--   sub.id <- which(str_df.ic$geo.mrkt == 'suburban') -->
-<!--   rural.id <- which(str_df.ic$geo.mrkt == 'rural') -->
-<!--   beach.id <- which(str_df.ic$geo.mrkt == 'beach') -->
-
-<!--   # Recalc the percentiles -->
-<!--   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id], -->
-<!--                                       return.type='rank') -->
-<!--   subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id], -->
-<!--                                   return.type='rank') -->
-
-<!--   subm.data.ic$occ.qtl[city.id] <- makeWtdQtl( -->
-<!--       subm.data.ic$occ.rate[city.id], return.type='rank') -->
-<!--   subm.data.ic$rate.qtl[city.id] <- makeWtdQtl( -->
-<!--     subm.data.ic$med.rate[city.id], return.type='rank') -->
-
-<!--   subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id], -->
-<!--                                       return.type='rank') -->
-<!--   subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id], -->
-<!--                                   return.type='rank') -->
-
-<!--   subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id], -->
-<!--                                       return.type='rank') -->
-<!--   subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id], -->
-<!--                                   return.type='rank') -->
-
-<!--   subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id], -->
-<!--                                       return.type='rank') -->
-<!--   subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id], -->
-<!--                                   return.type='rank') -->
-
-<!-- ``` -->
-
-<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->
-
-<!--  ## Set colors -->
-
-<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->
-
-<!--  ## Create plot data -->
-
-<!--   rawocc.geo <- abbPrefPlot(subm.data.ic, -->
-<!--                         x.field='occ.rate', -->
-<!--                         split.field='geo.mrkt', -->
-<!--                         smooth=TRUE, -->
-<!--                         smooth.span=.5 , -->
-<!--                         spl.col=sm.col) -->
-
-<!--   pctocc.geo <- abbPrefPlot(subm.data.ic, -->
-<!--                          x.field='occ.qtl', -->
-<!--                          split.field='geo.mrkt', -->
-<!--                          smooth=TRUE, -->
-<!--                          smooth.span=.5 , -->
-<!--                          spl.col=sm.col) -->
-
-<!--  ## Make plot objects   -->
-
-<!--   smr.occ <- ggplot(rawocc.geo$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate') + -->
-<!--     scale_color_manual(values=sm.col, -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Raw Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--   smq.occ <- ggplot(pctocc.geo$data, -->
-<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
-<!--     geom_point(alpha=.5, size=.4) + -->
-<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
-<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
-<!--     scale_color_manual(values=sm.col, -->
-<!--                        name='') + -->
-<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
-<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
-<!--     ylab('\nSTR Preferability %') + -->
-<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
-<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
-<!--     theme(legend.position='bottom') +  -->
-<!--     ggtitle('Percentile Rates') +  -->
-<!--     theme(plot.title = element_text(hjust = 0.5)) -->
-
-<!--  ## Plot   -->
-
-<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'} -->
-
-<!--   # Build the SVM Heatmaps -->
-
-<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'city-core', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
-<!--   theme(legend.position='none') + -->
-<!--     ylab('') + -->
-<!--     xlab('') + -->
-<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->
-
-<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'city', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('') + -->
-<!--     xlab('')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->
-
-<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'suburban', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('') + -->
-<!--     xlab('')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->
-
-<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'rural', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('') + -->
-<!--     xlab('')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->
-
-<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
-<!--                                           'beach', ], -->
-<!--                    x.field='occ.qtl', -->
-<!--                    y.field='rate.qtl', -->
-<!--                    pref.field='str.act.pref', -->
-<!--                    svm=T, -->
-<!--                    alpha.count=F, -->
-<!--                    add.points=T, -->
-<!--                    quantile=T, -->
-<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
-<!--   theme(legend.position='none')+ -->
-<!--     ylab('') + -->
-<!--     xlab('')+ -->
-<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->
-
-<!-- ``` -->
-
-<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'} -->
-
-<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
-<!--                rural.hm.svm, beach.hm.svm, cols=2) -->
-
-<!-- ``` -->
-
-## Sensitivity
-
-### Potential Revenue
-
-To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.
-
-```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}
-
- # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='type')
- # Extract Potential Results
-  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
-
- # Make baseic comparison table of submarkets  
-  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='geo.mrkt')
-
- # Extract potential results  
-  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
-
- # Combine and round  
-  st.table <- rbind(tpref.table, spref.table)
-  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
-
- ## Fix names and print
-
-  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-  print(xtable(st.table[,1:2], 
-               caption='Potential Revenue Preferability\n',
-               digits=1, align='llr'),
-               include.rownames=FALSE,
-               caption.placement='top',
-               hline.after=c(-1, 0, 2, 7, 7))
-
-```
-
-Next we recrate the SVM percentile heat maps.
-
-```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- ## create data and re-estimate the percentiles
-
-  pot.data.ic <- str_df.ic
-
-  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')
-
- ## Make the pecentile heatmap
-
-  pqtl.hm <- abbHeatMap(pot.data.ic,
-                x.field='occ.qtl',
-                y.field='rate.qtl',
-                pref.field='str.pot.pref',
-                svm=F, 
-                alpha.count=T,
-                add.points=T,
-                fill.colors=c(abb.col[1], abb.col[5]))
-  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')
-
- ## Make percentile SVM heatmap
-
-  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
-                   x.field='occ.qtl',
-                   y.field='rate.qtl',
-                   pref.field='str.pot.pref',
-                   svm=T, 
-                   alpha.count=F,
-                   add.points=T,
-                   quantile=T,
-                   fill.colors=c(abb.col[1], abb.col[5]))
-  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
-    xlab('Occupancy Rate (Pcntl)') +
-  annotate("text", x = 50, y = 50, label = "Potential", size=9)
-
- ## Add annotations to previous SVM
-
-  qtl.hm.svm.p <- qtl.hm.svm +
-  annotate("text", x = 50, y = 50, label = "Actual", size=9)
-
-```
-
-```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}
-
-  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)
-
-```
-
- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+  png(filename = file.path(getwd(), 'images', "block_rate_hist.png"), 
+       width = 5.5, height = 4, units = 'in', res = 300)
 
@@
 
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.block.freq
-
   dev.off()
 
-  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))
+  png(filename = file.path(getwd(), 'images', "block_periods_scat.png"), 
+       width = 5.5, height = 4, units = 'in', res = 300)
 
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
-  geom_point(fill=str.col, color=str.col, size=.2) +
+  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
+    geom_point(fill=str_col, color=str_col, size=.2) +
     ylab('Nbr of Blocked Periods\n') + 
@@
 
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    block.rate.period
-
   dev.off()
 
-  block.rate.period
-
-  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))
-
-```
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_tdf$blockpertime <- round(str_tdf$nbr_block * str_tdf$extr_par, 1)
-
-  str_tdf$host_type <- 'Unknown'
-  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
-  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
-  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
-  str_tdf$host_type <- factor(str_tdf$host_type,
-                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                        'Multi-Platform User', 'Unknown'))
+  png(filename = file.path(getwd(), 'images', "host_type_scat.png"), 
+       width = 5.5, height = 4, units = 'in', res = 300)
 
@@
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    scale_color_manual(values=c(col.df$rgb[2], col.df$rgb[4], col.df$rgb[7], col.df$rgb[9])) + 
+      scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
+                                  col_df$rgb[9])) + 
       theme(legend.position='bottom',
@@
                                                      alpha=1)))
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type
 
@@
 
-  host.type
-
-  save(host.type, file=paste0(fig.path, 'hosttype.RData'))
-
 ```
-
-See the counts of each group
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
-  geom_bar() +
-  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
-  theme(legend.position='none') +
-  ylab('Frequency\n') + 
-  xlab('\nHost Type') +
-  ggtitle('Short Term Host Types') + 
-  theme(plot.title = element_text(hjust = 0.5))
-
-  # Make Plot
-  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
-      bg='transparent')
-
-    host.type.bar
-
-  dev.off()
-
-  host.type.bar
-
-  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))
-
-```
-
-We then re-estimate the preference table.
-
-```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
-                                    split.field='host.type')
-
- # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
-  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
-  hpref.table <- hpref.table[,1:2]
-  hpref.table[,3] <- phpref.table[,2]
-  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
-  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
-
-  names(hpref.table) <- c('Host Type', 'STP (Actual)', 'STP (Potential)')
-  options(xtable.comment = FALSE)
-  print(xtable(hpref.table, 
-               caption='Host Type Preferability\n',
-               digits=1,
-               align='llrr'),
-               include.rownames=FALSE,
-               caption.placement='top')
-
-```

### 2018-05-30 _old/deprecated_functions.R

@@ -1,0 +1,837 @@
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+### Calculate the occupancy rates for each date in a range -------------------------------
+
+abbCalcDateRates <- function(daily.df){
+  
+  ## Create table of counts by status
+  
+  status.table <- table(daily.df$date, daily.df$status)
+  
+  ## Convert to a data.frame  
+  
+  status.df <- data.frame(Avail=status.table[,1],
+                          Resv=status.table[,2],
+                          Block=status.table[,3],
+                          lp.type=daily.df$lp.type[1])
+  
+  ## Add date   
+  
+  status.df$date <- as.Date(rownames(status.df))
+  
+  ## Add reserved rate (occupancy rate)  
+  
+  status.df$occ.rate <- status.df$Resv / (status.df$Resv + status.df$Avail)
+  
+  ## Return values  
+  
+  return(status.df)
+  
+}
+
+### Impute the missing daily observations ------------------------------------------------
+
+abbImputeDaily <- function(prop.df, 
+                           daily.df, 
+                           rates.df){
+  
+  # prop.df: data.frame of AirBNB property data
+  # daily.df: data.frame of existing AirBNB daily observations
+  # rates.df: data.frame of daily rate data (from abbCalcDateRates() function)
+  
+  ## Isolate those needing imputation  
+  
+  # Isolate
+  imp.df <- prop.df[prop.df$impute != 'no',]
+  
+  # Compute property specific rates
+  imp.df$avail.rate <- imp.df$available.days/imp.df$total.days
+  imp.df$block.rate <- imp.df$blocked.days/imp.df$total.days
+  imp.df$resv.rate <- imp.df$reserved.days/imp.df$total.days
+  
+  ## Loop through each property and impute  
+  
+  # Create capture list
+  imp.list <- list()
+  
+  # Start loop
+  for(i.i in 1:nrow(imp.df)){
+    
+    # Extract ith property data and daily data
+    i.imp <- imp.df[i.i, ]
+    i.daily <- daily.df[daily.df$property.id == i.imp$property.id,]
+    i.min <- min(i.daily$date)
+    
+    # Calculate the days that are missing
+    miss.days <- rates.df$date[!rates.df$date %in% i.daily$date]
+    miss.days <- miss.days[miss.days < i.min]
+    
+    # Calculate the occupancy rates for missing and matching days
[…]

### 2018-05-30 _old/deprecated_plots.R

@@ -1,0 +1,1461 @@
+
+The location of the short and long term rentals, colored by submarket, are shown below
+
+```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+# Set submarket colors
+# Make map
+tm_shape(sub_sf) +
+  tm_polygons() + 
+  tm_shape(study_area) + 
+  tm_polygons(col='dodgerblue3') +
+  tm_shape(ltr_sf) +
+  tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)
+
+tm_shape(sub_sf) +
+  tm_polygons() + 
+  tm_shape(study_area) + 
+  tm_polygons(col='dodgerblue3') +
+  tm_shape(str_sf) +
+  tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)
+
+
+str_map <- ggplot() +
+  geom_polygon(data=ssub_sf, 
+               aes(x=long, y=lat, group=group), fill='white', color='grey70') 
+#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
+#                alpha=.2) +
+#     scale_color_manual(values=sm_col) +
+#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
+#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
+#     xlab('') + ylab('')+
+#     theme(legend.position = 'bottom',
+#           legend.title = element_blank(),
+#           plot.title = element_text(hjust = 0.5),
+#           panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_rect(fill = "white"),
+#           axis.text.x = element_blank(),
+#           axis.text.y = element_blank(),
+#           axis.ticks = element_blank(),
+#           axis.title.x=element_blank(),
+#           axis.title.y=element_blank(),
+#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
+#     guides(colour = guide_legend(override.aes = list(size=3,
+#                                                      alpha=1))) + 
+#     ggtitle('Short-Term Rental Locations')+
+#     theme(plot.title = element_text(hjust = 0.5))
+#   
+# ```
+# 
[…]

### 2018-05-30 functions/abb_Functions.R

@@ -190,7 +190,7 @@ impLikelyBookings <- function(prop_df,
   
   # Unnest the str prop data
   prop_df <- prop_df %>% 
-    tidy::unnest()
+    tidyr::unnest()
   
   # Get relative booking rate (prop versus other props on those days)
   rsp <- rate_summ %>%
@@ -214,186 +214,187 @@ impLikelyBookings <- function(prop_df,
   
 }
 
+### Impute likely bookings ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-### Calculate the occupancy rates for each date in a range -------------------------------
-
-abbCalcDateRates <- function(daily.df){
+impPotentialBookings <- function(prop_df, 
+                                 rate_summ){
   
-  ## Create table of counts by status
+  prop_df <- prop_df %>% tidyr::unnest()
   
-  status.table <- table(daily.df$date, daily.df$status)
+  # Unnest the str prop data
+  notblock_df <- prop_df %>% 
+    tidyr::unnest() %>%
+    dplyr::filter(status != 'B')
+
+  block_df <- prop_df %>% 
+    tidyr::unnest() %>%
+    dplyr::filter(status == 'B')
   
-  ## Convert to a data.frame  
+  # Get relative booking rate (prop versus other props on those days)
+  rsp <- rate_summ %>%
+    dplyr::filter(date %in% notblock_df$date)
+  w_obs <- sum(rsp$obs * rsp$rate) / sum(rsp$obs)
+  rel_rate <- unique((1 - prop_df$block_rate - prop_df$avail_rate) / w_obs)
   
-  status.df <- data.frame(Avail=status.table[,1],
-                          Resv=status.table[,2],
-                          Block=status.table[,3],
-                          lp.type=daily.df$lp.type[1])
+  # Estimate likely bookings with dates not currently in property
+  rso <- rate_summ %>%
+    dplyr::filter(date %in% block_df$date)
+  pot_book <- round(sum(rso$obs * rso$rate) / sum(rso$obs) * nrow(rso) * rel_rate, 0)
   
-  ## Add date   
+  # Add to existing to create likely and limit columns
+  p_df <- prop_df %>% 
[…]

### 2018-05-30 scripts/3_data_prep.Rmd
Move revenue estimates to data prep

@@
 
+```{r ltr_rev}
+
+   ltr_tdf <- ltr_tdf %>%
+     dplyr::mutate(trans_data = map(trans_data, 
+                                    ~mutate(., 
+                                            gross_revenue = price * (52 - dom / 7)))) %>%
+     dplyr::mutate(trans_data = map(trans_data, 
+                                    ~filter(., gross_revenue >= 5000)))
+
+```
+
 For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.
 Using this data we sum up the total revenue from bookings.
+
  For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.
@@
 
-```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}
+```{r obs_bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE}
 
@@
    }
-   makePotBookings <- function(x){
-     round(nrow(x) * (length(which(x$status == 'R')) / 
-                        length(which(x$status != 'B'))), 0)
-   }
 
@@
      mutate(bookings = unlist(map(daily_data, ~countBookings(.))),
-            pot_bookings = unlist(map(daily_data, ~makePotBookings(.))),
-            gross_revenue = bookings * med_rate,
-            pot_revenue = pot_bookings * med_rate)
+            occ_rate = bookings / 366,
+            revenue = bookings * med_rate)
 
-   # compute long term revenue
-   ltr_tdf <- ltr_tdf %>%
-     dplyr::mutate(trans_data = map(trans_data, 
-                                    ~mutate(., 
-                                            gross_revenue = price * (52 - dom / 7))))
+```
+
+Next we impute the likely bookings for properties which were not listed on the portal for the entire year.
+
+```{r lik_bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE}
+
+  # Create daily rate summary
+  rate_summ <- str_tdf %>% 
+   dplyr::select(property_id, daily_data) %>%
+    tidyr::unnest() %>%
+    dplyr::filter(status != 'B') %>%
+    dplyr::group_by(date) %>%
+    dplyr::summarize(rate = length(which(status == 'R')) / n(),
+                     obs = n())
+
+  # Create new cluster
+  abb_cl <- get_default_cluster()
+
+  # Register function and variable
+  cluster_copy(abb_cl, impLikelyBookings)
+  cluster_copy(abb_cl, rate_summ)
+  cluster_library(abb_cl, c("magrittr", 'dplyr', 'tidyr'))
+
+  # Summarize daily by property
+  lik_book_df <- str_tdf %>%
+    dplyr::filter(total_days != 366) %>%
+    multidplyr::partition(property_id, cluster = abb_cl) %>% 
+    dplyr::do(impLikelyBookings(., rate_summ = rate_summ)) %>% 
+    dplyr::collect()
+
+  # Add to the existing data
+  str_tdf <- str_tdf %>%
+    left_join(lik_book_df, by='property_id') %>%
+    dplyr::mutate(lik_bookings = if_else(is.na(lik_bookings), 
+                                         bookings, 
+                                         as.integer(lik_bookings)),
+                  lik_occ_rate = lik_bookings / 366)
+
+```
+
+Finally, we compute the potential bookings, assuming that blocked periods were rented at the same rate as the non-block, controlling for dates and property specific performance on non-blocked dates.
+
+```{r pot_bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE}
+
+    # Create new cluster
+  abb_cl <- get_default_cluster()
+
+  # Register function and variable
+  cluster_copy(abb_cl, impPotentialBookings)
+  cluster_copy(abb_cl, rate_summ)
+  cluster_library(abb_cl, c("magrittr", 'dplyr', 'tidyr'))
+
+  # Summarize daily by property
+  pot_book_df <- str_tdf %>%
+    dplyr::filter(block_rate > 0) %>%
+    multidplyr::partition(property_id, cluster = abb_cl) %>% 
+    dplyr::do(impPotentialBookings(., rate_summ = rate_summ)) %>% 
+    dplyr::collect()
+
+  # Add to the existing data
+  str_tdf <- str_tdf %>%
+    left_join(pot_book_df, by='property_id') %>%
+    dplyr::mutate(pot_bookings = if_else(is.na(pot_bookings), 
+                                         bookings, 
+                                         as.integer(pot_bookings)),
+                  pot_bookings = if_else(pot_bookings > 366L, 366L, pot_bookings),
+                  pot_occ_rate = pot_bookings / 366)
+
+```
+
+### Calculating Net Revenues
+
+We begin the analysis by calculating the net revenues for the short term data.
+We calculate three types of net revenues, Actual, Likely (Extrapolated) and Potential.
+The differences are described more fully in the writeup.
+
+Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.
+The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
+For 2 persons in an apartment that works out to \$5 per person per day.
+For a house of 4 persons that works out to about \$4 per person per day.
+We use a mid point value of \$4.50 per person per day.
+We use an estimate of 1.5 persons per bedroom in each unit.
+
+```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Set cost per person per day
+  cpppd <- 4.5
+
+  # Calculate avg number of guests
+  str_tdf$avg_guests <- str_tdf$bedrooms * 1.5
+
+```
+
+We then calculate the actual net revenue by multiplying booking times median rate - utility costs.
+
+```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf$revenue_net <- ((str_tdf$bookings * str_tdf$med_rate) -
+                             (str_tdf$bookings * str_tdf$avg_guests * cpppd))
+
+```
+
+Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties,
+
+```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  # Calculate likely revenue
+  str_tdf$lik_revenue_net <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
+                                (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))
+
+```
+
+Then we create Potential Revenue, by imputing occupancy rates and revenues for blocked periods.
+
+```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf$pot_revenue_net <- ((str_tdf$pot_bookings * str_tdf$med_rate) -
+                                (str_tdf$pot_bookings * str_tdf$avg_guests * cpppd))
 

### 2018-05-30 scripts/4_data_analysis.Rmd
Move revenue estimates to data prep

@@
 
+  str_col = col_df$rgb[1]
+
 ```
@@
   load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))
-
-```
-
-### Calculating Net Revenues
-
-We begin the analysis by calculating the net revenues for the short term data.
-We calculate three types of net revenues, Actual, Likely (Extrapolated) and Potential.
-The differences are described more fully in the writeup.
-
-Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.
-The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).
-For 2 persons in an apartment that works out to \$5 per person per day.
-For a house of 4 persons that works out to about \$4 per person per day.
-We use a mid point value of \$4.50 per person per day.
-We use an estimate of 1.5 persons per bedroom in each unit.
-
-```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Set cost per person per day
-  cpppd <- 4.5
-
-  # Calculate avg number of guests
-  str_tdf$avg_guests <- str_tdf$bedrooms * 1.5
-
-```
-
-We then calculate the actual net revenue by multiplying booking times median rate - utility costs.
-
-```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_tdf$act_revenue <- ((str_tdf$bookings * str_tdf$med_rate) -
-                                 (str_tdf$bookings * str_tdf$avg_guests * cpppd))
-
-```
-
-Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties
-
-```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Create daily rate summary
-  rate_summ <- str_tdf %>% 
-   dplyr::select(property_id, daily_data) %>%
-    tidyr::unnest() %>%
-    dplyr::filter(status != 'B') %>%
-    dplyr::group_by(date) %>%
-    summarize(rate = length(which(status == 'R')) / n(),
-            obs = n())
-
-  # Create new cluster
-  abb_cl <- get_default_cluster()
-
-  # Register function and variable
-  cluster_copy(abb_cl, impLikelyBookings)
-  cluster_copy(abb_cl, rate_summ)
-  cluster_library(abb_cl, c("magrittr", 'dplyr', 'tidyr'))
-
-  # Summarize daily by property
-  lik_book_df <- str_tdf %>%
-    dplyr::filter(total_days != 366) %>%
-    multidplyr::partition(property_id, cluster=abb_cl) %>% 
-    dplyr::do(impLikelyBookings(., std=g)) %>% 
-    dplyr::collect()
-
-  # Add to the existing data
-  str_tdf <- str_tdf %>%
-    left_join(lik_book_df, by='property_id') %>%
-    dplyr::mutate(lik_bookings = if_else(is.na(lik_bookings), bookings, as.integer(lik_bookings)))
-
-  # Calculate likely revenue
-  str_tdf$lik_revenue <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
-                           (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))
-
-  # Create Extrapolation parameter
-  str_tdf$extr_par <- 366 / str_tdf$total_days
-
-```
-
-```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  str_tdf$occ_rate <- 1 - (str_tdf$block_rate + str_tdf$avail_rate)
-
-  str_tdf$pot_occ_rate <- ((str_tdf$lik_bookings) / (366 - (366 * str_tdf$block_rate)))
-
-  str_tdf$pot_revenue <- ((str_tdf$pot_occ_rate * 366 * str_tdf$med_rate) -
-                           (str_tdf$pot_occ_rate * 366 * str_tdf$avg_guests * cpppd))
 
@@
     dplyr::left_join(imp_df, by='property_id') %>%
-    dplyr::mutate(act_pref = ifelse(act_revenue > ltr_imp_revenue, 1, 0),
-                  lik_pref = ifelse(lik_revenue > ltr_imp_revenue, 1, 0),
-                  pot_pref = ifelse(pot_revenue > ltr_imp_revenue, 1, 0))
+    dplyr::mutate(act_pref = ifelse(revenue_net > ltr_imp_revenue, 1, 0),
+                  lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
+                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0))
 
@@
 
-  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * extr_par)) + 
+  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
     geom_point(fill=str_col, color=str_col, size=.2) +
@@
 
-  str_tdf$blockpertime <- round(str_tdf$nbr_block * str_tdf$extr_par, 1)
+  str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1)
 
@@
 
+  dir.create(file.path(getwd(), 'data', 'analyzed'))
   save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
        pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
-       file=file.path(data_path, 'analyzed', 'analyzed_data.RData'))
+       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
 

### 2018-05-30 scripts/5_data_viz.Rmd
Image updates

@@
 
-  png(filename = file.path(getwd(), 'images', "block_rate_hist.png"), 
-       width = 5.5, height = 4, units = 'in', res = 300)
+  str.col <- col_df$rgb[1]
 
-    ggplot(str_tdf, aes(x=block_rate)) + 
-      geom_density(fill=str_col, color=str_col) +
+  ## Create table of host block frequencies
+
+  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
+     geom_density(fill=str.col, color=str.col) +
      ylab('Frequency\n') +
@@
                         labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-        ggtitle('Host Block Rate Frequency\n') +
+     #ggtitle('Host Block Rate Frequency\n') +
      theme(plot.title = element_text(hjust = 0.5)) +
@@
 
-  dev.off()
-
-  png(filename = file.path(getwd(), 'images', "block_periods_scat.png"), 
-       width = 5.5, height = 4, units = 'in', res = 300)
-
-  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
-    geom_point(fill=str_col, color=str_col, size=.2) +
+  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +
+    geom_point(fill=str.col, color=str.col, size=.2) +
     ylab('Nbr of Blocked Periods\n') +
@@
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+    png(filename = file.path(getwd(), 'images', "block_rate.png"), 
+       width = 5.5, height = 3, units = 'in', res = 300)
+
+       ggMultiPlots(host.block.freq, block.rate.period, cols=2)
+
+    dev.off()
+
+```
+
+```{r host_types2}
+
+  base.host <- ggplot(str_tdf,
+                    aes(x=block_rate, y=blockpertime)) +
+                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
+                ylab('# Blckd Periods\n') +
+                xlab('\n% of Time Property is Blocked') +
                 ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+                scale_x_continuous(breaks=seq(0, 1, .2),
+                                   labels=c('0%', '20%', '40%',
+                                            '60%', '80%', '100%')) +
+                #scale_color_manual(values=c(abb.col[2], abb.col[4],
+                #                            abb.col[7], abb.col[9])) +
+                theme(legend.position='bottom',
+                      legend.title = element_blank(),
+                      plot.title = element_text(hjust = 0.5))+
+                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
+
+   ps.host <- base.host +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
+    ggtitle('Profit Seekers')
+
+  os.host <- base.host +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
+               size=.4)  +
+    ggtitle('Opportunistic Sharer')
+
+  mu.host <- base.host +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
+               size=.4)  +
+    ggtitle('Multi-Platform User')
+
+  un.host <- base.host +
+    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
+    ggtitle('Unknown')
+
+  png(filename = file.path(getwd(), 'images', "host_scat.png"), 
+       width = 5.5, height = 3, units = 'in', res = 300)
+
+    ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
+
+  dev.off()
+
+```
+
+```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}
+
+ ## Build plot
+
+  png(filename = file.path(getwd(), 'images', "host_bar.png"), 
+       width = 3, height = 3, units = 'in', res = 300)
+
+ ggplot(str_tdf, aes(host_type, fill=host_type)) +
+    geom_bar() +
+    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
+                               col_df$rgb[9]))+
+    theme(legend.position='none') +
+    ylab('Frequency\n') +
+    xlab('\nHost Type') +
+    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
+    #ggtitle('short-term Host Types') +
     theme(plot.title = element_text(hjust = 0.5))
@@
 
-  png(filename = file.path(getwd(), 'images', "host_type_scat.png"), 
-       width = 5.5, height = 4, units = 'in', res = 300)
-
-   ggplot(str_tdf, 
-          aes(x=block_rate, y=blockpertime, color=host_type)) + 
-     geom_point(alpha=.5, size=.8, shape=16) +
-     ylab('Number of Blocked Periods\n') + 
-     xlab('\n% of Time Property is Blocked') +
-        ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-
-      scale_x_continuous(breaks=seq(0, 1, .2),
-                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-      scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
-                                  col_df$rgb[9])) + 
-      theme(legend.position='bottom',
-           legend.title = element_blank(),
-         plot.title = element_text(hjust = 0.5))+
-       guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1)))
-
-   dev.off()
-
 ```

### 2018-05-30 papers/full_paper.Rmd
Fix host models

@@
   options(xtable.caption.placement='top')
-
-  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
-  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
-  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')
-
-  source(file.path(code_path, 'functions', 'abb_Functions.R'))
+  setwd('..')
+  source(file.path(getwd(), 'functions', 'abb_Functions.R'))
 
@@
 
-```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
-
-  load(file.path(data_path, 'analyzed', 'analyzed_data.RData'))
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, results='hide'}
+
+  setwd('..')
+  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
 
@@
                           'Beach (Submarket)', 'Guests per Bedroom',
-                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')
+                          'Minimum Stay', 'Flexible Cancel')
 
@@
        include.rownames=FALSE,
-       hline.after=c(-1,0,17,22,22),
+       hline.after=c(-1,0,16,21,21),
        caption.placement='top')
@@
        include.rownames=FALSE,
-       hline.after=c(-1, 0, 17, 22, 22),
+       hline.after=c(-1, 0, 16, 21, 21),
        caption.placement='top')
@@
 
-```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  str.col <- col_df$rgb[1]
-
-  ## Create table of host block frequencies
-
-  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
-  geom_density(fill=str.col, color=str.col) +
-  ylab('Frequency\n') +
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0,1,.2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    #ggtitle('Host Block Rate Frequency\n') +
-    theme(plot.title = element_text(hjust = 0.5)) +
-    theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
-```
-
-```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- ## Create scatter of block rate vs block periods
-
-  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * extr_par)) +
-  geom_point(fill=str.col, color=str.col, size=.2) +
-  ylab('Nbr of Blocked Periods\n') +
-  xlab('\n% of Time Property is Blocked') +
-  scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostblock}Host Blocking Tendencies'}
-
-  ggMultiPlots(host.block.freq, block.rate.period, cols=2)
-
-```
+![Host Blocking Tendencies](C:/Code/research/airbnbMelbourne/images/block_rate.png)
 
@@
 
-```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  # Create a background plot for the host location plots
-
-  base.host <- ggplot(str_tdf,
-                    aes(x=block_rate, y=blockpertime)) +
-                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
-                ylab('# Blckd Periods\n') +
-                xlab('\n% of Time Property is Blocked') +
-                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-                scale_x_continuous(breaks=seq(0, 1, .2),
-                                   labels=c('0%', '20%', '40%',
-                                            '60%', '80%', '100%')) +
-                #scale_color_manual(values=c(abb.col[2], abb.col[4],
-                #                            abb.col[7], abb.col[9])) +
-                theme(legend.position='bottom',
-                      legend.title = element_blank(),
-                      plot.title = element_text(hjust = 0.5))+
-                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))
-
-```
-
-```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
-  ## Create individual host location plots
-
-  ps.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
-    ggtitle('Profit Seekers')
-
-  os.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
-               size=.4)  +
-    ggtitle('Opportunistic Sharer')
-
-  mu.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
-               size=.4)  +
-    ggtitle('Multi-Platform User')
-
-  un.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
-    ggtitle('Unknown')
-
-```
-
-```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories'}
-
-  ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
-
-```
-
-```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}
-
- ## Build plot
-
-  host.type.bar <- ggplot(str_tdf, aes(host_type, fill=host_type)) +
-    geom_bar() +
-    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
-                               col_df$rgb[9]))+
-    theme(legend.position='none') +
-    ylab('Frequency\n') +
-    xlab('\nHost Type') +
-    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
-    #ggtitle('short-term Host Types') +
-    theme(plot.title = element_text(hjust = 0.5))
-
- ## Plot
-
-  host.type.bar
-
-```
+![Host Categories](C:/Code/research/airbnbMelbourne/images/host_scat.png)
+
+![Host Category Counts](C:/Code/research/airbnbMelbourne/images/host_bar.png)
 

### 2018-05-30 scripts/3_data_prep.Rmd
Fix host models

@@
 
+Next, a small number of properties have very long minimum stays, we round any minimum stay greater than 7 days to be 7 days.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
+
+  str_tdf <- str_tdf %>%
+   dplyr::mutate(min_stay = if_else(min_stay > 7L, 7L, min_stay))
+
+  str_tdf <- str_tdf %>%
+   dplyr::mutate(guest_per_bed = round(max_guests / bedrooms, 2)) %>%
+   dplyr::mutate(guest_per_bed = if_else(guest_per_bed > 4, 4, guest_per_bed))
+
+```
+
 ### Locations and Submarkets

### 2018-05-30 scripts/4_data_analysis.Rmd
Fix host models

@@
 
-  str_col = col_df$rgb[1]
-
 ```
@@
   load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))
+  str_col = col_df$rgb[1]
 
@@
   glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
+                        guest_per_bed + min_stay + I(canc_policy == 'Flexible'),
                       family=binomial(link='logit'),
@@
   glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                       family=binomial(link='logit'),
@@
   lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))
+                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))
 
   pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))
+                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))
 

### 2018-05-31 papers/full_paper.Rmd
Title Change and Final updates for anonymous submission

@@
 ---
-title: "To Airbnb?: A Question of Returns"
+title: "To Airbnb?: A Question of Revenue"
 subtitle: "Andy Krause and Gideon Aschwanden"
@@
 
+```
+
+```{r options_functions, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
   options(stringsAsFactors=FALSE)
@@
 Or rather, is it more profitable to do so when compared to traditional long-term rental (LTR)?
-And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one.
+And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
 
@@
 Our results show that the feasibility of a greater return through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
-In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy: it depends.
+In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy is ''it depends''.
 
@@
 Within the existing work, the focus remains centered on rural and/or amenity-based STRs such as beach-front and ski-resort access properties.
-This focus resulted from the fact that, until a few years ago, the STR market itself operated almost wholly within these market segments.
+This focus results from the fact that, until a few years ago, the STR market itself operated almost wholly within these market segments.
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
-With the arrival of Airbnb, and the controversies surrounding it, the topic is creating interest both in real estate and economics as well as in a wide variety of fields as evidenced by a growth in recent publications and on-going working papers.
+With the rapid growth of Airbnb, and the controversies surrounding it, interest in the short-term rental market has increased among research as well as investors and industry analysts.
 
@@
 
-Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast, the STR industry lacks sophistication and efficiency.
+Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast the STR industry lacks sophistication and efficiency.
 Most notably, they find that most nightly or weekly rates are set by resident unit managers (RUMs) and are often under-priced as there is little accountability to owners.
@@
 
-Though issues of second homes have been primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism.'' Fuller and Michel [-@fuller2014stop] has re-focused some of the problems of short-term rentals on large, urban environments.
+Though issues surrounding second homes have been primarily treated as a rural phenomenon for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has focused some of the problems of short-term rentals on large, urban environments.
 With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.
@@
 
-Australia implements a particular tax policy, often termed `negative gearing', that allows for income tax deduction to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
+Australia implements a particular tax policy, often termed `negative gearing', that allows for an income tax deduction to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
 While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
@@
 As future market trends are unknown at the time of purchase and, within the span of 12 months, the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
-Both long-term rents and short-term rates and occupancy structures will be based on the market conditions as of this date.
+Both long-term rents and short-term rates will be based on the market conditions as of this date.
 
@@
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
-As a result of janitorial fees being a separate line item in the STR data and directly paid by the occupants they can also be ignored in the comparative analysis below.
+As a result of janitorial fees being a separate line item in the STR data (paid separately and in addition to the nightly rate) they can also be ignored in the comparative analysis below.
 
@@
 \begin{equation}
-U = (4.5 * B * 1.7) * O
+U = (4.5 * B * 1.5) * O
 \end{equation}
@@
 
-Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include address.
+Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include addresses.
 Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on two-dimensional coordinates.
@@
 
-Our data preparation primarily involved the filtering out of data errors, outlier values and other observations than contain data that do not fit our research questions.
+Our data preparation primarily involved the filtering out of data errors, outlier values and other observations than contain data that do not fit our research question.
 Additionally, as our data are from two different sources, a number of fields require standardization so that comparisons between the two leasing strategy options -- long-term rental (LTR) vs short-term rental (STR) -- can be made.
@@
 Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
-To determine the likely LTR rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
+To determine the likely LTR nightly rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
 Taking the Airbnb or STR approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
@@
 After removing property level observations that are missing price data, we find that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
-We filter the property level data accordingly.
-We also filter the short-term daily data to include only those observations with nightly rates between \$50 and \$500.
+We remove observations outside of these ranges.
 
@@
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
-As expected and as shown by the map, the long-term properties are more evenly spread across the metro region than the short-term properties.
+As expected and as shown by the map (Figure 2), the long-term properties are more evenly spread across the metro region than the short-term properties.
 Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
@@
 ![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/loc_bar.png)
-
-<!-- ### Summary of Data Cleaning -->
-
-<!-- We have applied ten separate filters to our two datasets.
-In the name of transparency and to highlight the bounds of our research question it is useful to review these filters (Table 2).
-There are more than 20,000 properties that are or have been listed on the Airbnb portal in Melbourne during the 2014 to 2016 period.
-Filtering those not listed during the study period removes nearly 1/3 of all properties.
-Further removing by property type and listing type (not entire home) elimates another 50% of the remaining properties.
-From these 7,200 properties structural characteristics filters remove another 480 from consideration.
-Over 1,000 of the remaining properties were never been booked and/or had outlying nightly rates and were removed.
-Finally, 14 properties had either bad location data or missing information host policy.
-From over 20,000, we have 5,788 Airbnb properties meet the requirements of our research question.
--->
-
-<!-- For the long-term data, over half of the observations fall outside of our considered time frame, reducing the sample size down to around 130,000 from 290,000.
-Further consideration regarding property types, structural characteristics, location, etc.
-remove another 12,000 observations, leaving 120,092 in the final dataset.
--->
 
@@
 
-First, we must deal with those properties that were not listed for the entire 12-month period.
+First, we must deal with those properties that were not listed on Airbnb for the entire 12-month period.
 Our data cleaning eliminated all properties that were listed for less than six months, however, it would be incorrect to compare the revenue of a property listed on Airbnb for seven months with the hypothetical annual revenue from a long-term rental.
@@
 
-1. Actual ($REV_o$)}: Observed bookings multiplied by median nightly rate
+1. Actual ($REV_a$)}: Observed bookings multiplied by median nightly rate
 2.
-Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long,^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] based on observed occupancy rate multiplied by median nightly rate
-3. Potential ($REV_p$)}: Observed occupancy rate of non-blocked days multiplied by 366 multiplied by median nightly rate
+Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.
+The additional bookings are imputed by comparing the property specific performance during the listed days to overall market performance and then applying that relative ratio to the overall market performance on the non-list days.
+3.
+Potential ($REV_p$)}: Observed bookings plus imputed bookings during blocked days.
+The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance and then applying that relative ratio to the overall market performance on the blocked days.
 
-As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Likely' revenue metric to be a better measure of actual market performance.
+As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Likely' revenue metric to be a better estimate of market performance.
 We chart the distribution of the Likely ($REV_l$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 5).
@@
 While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
-When looking at potential revenues, however, a great deal more may have the potential to produce additional revenue.
 The high number of very low yield Airbnb properties in the Likely condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
 
-![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/rev_dens.png)
+![Revenue Comparison between Tenure Types](C:/Code/research/airbnbMelbourne/images/rev_dens.png)
 
@@
 Realizing that the imputed long-term rental values may be more accurate when estimated at smaller scales, we impute long-term rental rates at submarket level, specifically by type and geographic area.
-In other words, we separately estimate the LTR model in Equation 10 for Apartments in the city core, Apartments with  in the beach submarket, etc.
+In other words, we separately estimate the LTR model in Equation 10 for Apartments in the city core, Apartments within the beach submarket, etc.
 for all combinations of type and geographic area.
-We then combine the results from all estimates back into a single dataset that contains all of the short-term rentals.
 
@@
 We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
-We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).
+We have grouped the cancellation policies into Flexible (24 hour notice), and Strict (those requiring 5 or more days notice, often with less than 100% refunds).
 
 The results of all three models are shown in Table 4.
-For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Moderate is the reference category.
+For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Strict is the reference category.
 As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.
@@
 In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
-Additionally, 1 bed / 1 bath units show greater likelihood of short-term preference than 2 bed / 1 bath and 2 bed / 2 bath combinations.
+Additionally, 1 bed / 1 bath units show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
 This could be due to the fact that 2 bed units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
@@
 The difference between the Rural and City-Core is not significant, however.
-The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking to the robustness of those estimates.
+The coefficients for the structural characteristics show the same signs and relatively small changes in magnitude from Model 1 to Model 2, speaking to the robustness of those estimates.
 The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.
@@
 Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a positive relationship with short-term preference.
-Strict policies do help maintain revenues, but may also scare off some potential guests.
 Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
@@
   x.full <- xtable(full.table,
-                  caption='Logistic Modeling Results\n')
+                  caption='Logistic Modeling Results (Likely Revenue)\n')
   align(x.full) <- 'lllll'
@@
 Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to not factoring in the impact of blocked days.
-If we, instead, assume that blocked days could be leased out on the short-term market at the same overall occupancy rate as the unblocked (observed) days we can produce a potential revenue figure.
+If we, instead, assume that blocked days could be leased out on the short-term market at the same overall occupancy rate (relative for each property and the market as a whole on those days) as the unblocked (observed) days we can produce a potential revenue figure.
 Note that it is possible (likely?) that the large oversupply of available units in the market that would occur if no properties blocked their units would decrease both prices and occupancy rates.
@@
 
-Using the potential revenue, 53.3% of all properties are short-term preferable.
+Using the potential revenue, 36.1% of all properties are short-term preferable.
 Breaking that down by type and by geographic submarket (Table 3) shows similar findings, in terms of relative comparativeness, to the Likely revenue analysis above.
 Apartments have a higher short-term preference than do Houses and City-Core properties dominate the other geographic regions.
-One notable difference here is that the Rural properties perform rather poorly under a potential revenue scenario, relatively speaking, suggesting that they may be operating near their peak in the current condition.
+One notable difference here is that the Suburban and Rural properties perform rather poorly under a potential revenue scenario, relatively speaking, suggesting that they may be operating near their peak in the current condition.
 
@@
  px.full <- xtable(pfull.table,
-                   caption='Logistic Modeling Results\n')
+                   caption='Logistic Modeling Results (Potential Revenue)\n')
  align(px.full) <- 'lllll'
@@
 Overall, the choice of revenue type, Likely or Potential, does affect some of the conclusions to be derived from the results above.
-As expected, under the Potential case there are more properties (53\% vs 28\%) that exhibit short-term preference.
-Under the scenario, the possibilities of increasing revenue by moving from long- to short-term leasing appear much better.
+As expected, under the Potential case there are more properties (36\% vs 28\%) that exhibit short-term preference.
+Under the scenario, the possibility of increasing revenue by moving from long- to short-term leasing appears much better.
 Again, however, we have not attempted to measure or estimate how this hypothetical increase of properties in the market (due to the elimation of blocked days) would impact overall market dynamics.
@@
 If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked should be highly bi-modal with profit seekers on the left and opportunistic sharers on the right.
-The left hand panel of \autoref{hostblock} shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some (25\% to 75\%) of the time.
+The left hand panel of Figure 6 shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some (25\% to 75\%) of the time.
 
@@
 A host using multiple platforms will likely have many small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
-We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of \autoref{hostblock}.
+We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 6.
 We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
@@
 The remainder 'Unknown' category contains just over 28\% of all properties.
-See \autoref{hostcat} and \autoref{htc} for a breakdown of these group by the two variables.
+See Figures 7 and 8 for a breakdown of these group by the two variables.
 
@@
 
-Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Likely case and a much smaller variation in the Potential case, as expected.
+Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Likely case and a slightly smaller variation in the Potential case, as expected.
 There is little change for the 'Profit Seekers' as most of these hosts are already operating with few blocked days.
@@
 Table 6 compares logistic models results from three of the host types.
-The Opportunistic Sharers show no instances of short-term preference and therefore could not be estimated.
+The Opportunistic Sharers show very few instances of short-term preference and therefore could not be estimated.
 The left hand column, that of the Profit-Seekers, is the most representative of a sample of property owners that are seeking to maximize revenue.
-Overall, the coefficients from this sub-sample match up well to the results from the entire sample shown in Table 5.
+Overall, the coefficients from this sub-sample match up well to the results from the entire sample shown in Table 4.
 In short, the conclusions are the same: small apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
@@
  xh.full <- xtable(hfull.table,
-                  caption='Logistic Model Results of Potential Short-Term Preference\n')
+                  caption='Logistic Modeling Results (Potential Revenue by Host Type)\n')
  align(xh.full) <- 'lllll'
@@
 However, of this total only 7,400 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
-Of these, only 5,913 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+Of these, only 5,925 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
 Overall, the Airbnb market is very small relative to the long-term market.
@@
 For instance, 35\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 12\% of suburban houses did.
-Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference considerably.
-
-<!-- The nightly rates and total occupancies drive the profitability of short-term leasing.
-As the nightly rate vs.
-occupancy rate heat maps and SVM plots (\autoref{metrohmp}, \ref{smhm}, \ref{smhmps}, \ref{pothm}) show, even with very high nightly rates, owners would need to achieve an occupancy rate of at least the 75th percentile in market (around 40\%) in order to achieve a better than 50\% probability of being more profitable in a short-term strategy than a long-term one.
-A 40\% occupancy rate means bookings at least three days out of every week all year long.
-In Melbourne summers this may be an easy feat as tourist numbers swell, but doing so on a cold week in July likely proves more difficult.
-The vertical-ness of the divide between short- and long-term preference in the SVM plots suggests that occupancy rate is the most critical factor in reaching short-term preference in most markets.
--->
+Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference from 28% to 36%.
 
@@
 In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
-If owners all operated as profit maximizers this figure could be 54\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
+If owners all operated as profit maximizers this figure could be 36\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
 
@@
 Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.
-It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com, our data provider.
+It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com.
 
@@
 In reality, the possibilities may not be so rigid.
-For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourist swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
+For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourists swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
 In general, the rise of Airbnb and related portals give properties owners more options, and therefore more opportunities, to maximize returns on their property.
@@
 
-#### Data and Code
+#### Reproducibility
 
-Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.
-All the code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
-
-<!-- An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
--->
+All code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
 

### 2018-05-31 scripts/5_data_viz.Rmd
Title Change and Final updates for anonymous submission

@@
 ---
-title: "5_data_viz"
-author: "Andy Krause"
-date: "May 10, 2018"
+title: "Data Visualization"
+date: '`r format(Sys.Date(), "%B %d, %Y")`'
 output: html_document
@@
     scale_color_manual(values=dens_cols) +
-    ggtitle('Short Term Revenue vs Long Term Revenue') +
+    ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
     xlab('Annual Revenue') +

### 2018-05-31 papers/full_paper.Rmd
Updating readme and title

@@
 author: "Greenfield Advisors and University of Melbourne"
-date: "May 5th, 2018"
+date: "May 30th, 2018"
 output:

### 2018-05-31 papers/full_paper.Rmd
Add: Abstract

@@
 ```
+## Abstract
+
+The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
+In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
+We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.
 

### 2018-07-18 review/response_to_reviewers.Rmd
Reviews:  Review 1 responses

---
title: "Reviewer Responses: To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

## Reviewer #1

Thank you for your helpful and encouraging comments.

* Thank you for pointing out the three typographical errors on pages 10, 30 and 31.  We have corrected these.

* We agree that there are many future avenue of research that can be pursued here, especially as data quality and quantity in this direction improves.  We appreciate your understanding of the difficulty of working with limited data and the necessity of our assumptions.

* Regarding the structure of cities and the generalizability of the findings.  We agree that Melbourne, as a world class tourist destination and (arguably) the world's most livable city, does provide an example that does not necessarily translate well to a second or third tier city in many other parts of the world. As you noted, this desire for both tourists and residents to occupy the same space is what, in our minds, made this the ideal city for this analysis. We do feel that many of the world's first class cities are experiencing the same phenomenon -- namely that a large segment of the local population desires the same walkable, vibrant locations that tourists do, thus leading to increased demand and increasingly contentious discussions over the negative externalities of a thriving short-term rental market.  We've added some language in the beginning of the 'Limitations' section that addresses the issues of generalizability.  Finally, we are in the process of additional data collection to expand the research to a more representative sample.

## Reviewer #2

5. Thank you for pointing out this typographic error.  We have corrected it.

### 2018-07-18 papers/full_paper.Rmd
Reviews:  Review 1 responses

@@
 There are a number of limitations to this research.
-There are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
+First and foremost may be the generalizability of this work.
+Melbourne is one of the primary examples of a world-class city in which local residents and tourists often (and fiercely) compete for the same urban spaces.
+As such, the results we find here are likely to be much more applicable and generalizable to large, thriving cities with attractive urban neighborhoods such as London, San Francisco and Hong Kong, rather than secondary or tertiary metropolitan areas.
+From investment and policy perspectives, however, it is in these larger centers that the findings of this research are most useful in a practical sense.
+
+Next, there are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
 Part of the difficulty in estimating potential short-term rates for long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.

### 2018-07-18 review/response_to_reviewers.Rmd
Review: Response to reviewer 2 - part 1

@@
 geometry: margin=3.3cm
-bibliography: abb.bib
 editor_options: 
@@
 
-Thank you for your helpful and encouraging comments.
+*I reviewed this paper from the comfort of a beachside Airbnb, one that I suspect is booked
+by short-‐term tenants like myself when the owner is elsewhere. I frequently book
+accommodation through the Airbnb portal, thus I found this paper quite interesting. Not
+only is it a welcome contribution to the body of research on short-‐term rentals, it also
+contributes to a broader category of research, namely how technology is impacting real
+estate via the sharing economy.*
+
+* Thank you for your helpful and encouraging comments.
+
+*Firstly, a few minor changes.*
+
+1. *Page 10, line 48: the word ‘American’ should be changed to ‘America’*
+2. *Page 30, line 37: the word ‘than’ should be changed to ‘that’*
+3. *Page 31, line 57: the word ‘extend’ should be changed to ‘extent’*
 
@@
 
-* We agree that there are many future avenue of research that can be pursued here, especially as data quality and quantity in this direction improves.
+*Next, there are two issues embedded in this research that have the potential to be
+problematic but are adequately addressed by the researcher(s). Firstly, the difficulty of
+combining the data sets and the lack of shared property characteristics can lead to
+unreliable findings. To alleviate these problems, the author(s) make reasonable
+assumptions justifying their approach to variable selection and manipulation. These
+assumptions are methodically detailed and defended thus, should better data be made
+available in the future, the results can be retested to ensure they are reliable.*
+
+* We agree that there are many future avenues of research that can be pursued here, especially as data quality and quantity in this direction improves.
 We appreciate your understanding of the difficulty of working with limited data and the necessity of our assumptions.
+
+*Further, Melbourne is in a class of cities that support large, short-term rental markets based
+on their desirability as tourist destinations and also support large, long-term rental markets
+due to the number of amenities found in the central city and surrounding suburbs.
+Melbourne is arguably the premiere example of these types of urban areas and is frequently
+cited as the world’s most liveable city. However, while incomes, property values, and rents
+tend to increase based on proximity to the CBD, the situation is reversed in many North
+American markets. Because every urban area is different, the generalizability of the results
+is limited. Regardless, the author(s) present a framework for conducting similar studies in
+other urban areas that can be relatively easily replicated. Hopefully they will expand this
+research as it will be interesting to see how these results compare to other markets,
+including those that are less tourism-intensive.*
 
@@
 
-5. Thank you for pointing out this typographic error.  We have corrected it.
+1.
+*The authors state “And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.” I agree with this statement.
+However, if the majority of the properties are vacation homes that owners rent out when they are not using them personally, then the hypothetical exercise performed in the paper is for naught.
+By definition, the owners cannot use a LTR strategy since it would preclude personal use throughout the year.
+In which case, the question “To Airbnb?” is not a question at all.*
+
+* We agree that this exercise wouldn't apply to an owner who leases out their home while away but occupies it at other times.
+If an investor were to buy that home they would have the choice of doing either an LTR or an STR which is why we framed the hypothetical situation as that of an investor.
+In the sensitivity analysis we attempted to address this potential bias in the sample by separately looking at those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time.
+We believe that these are clearly situations where it is not an owner-occupied who is being opportunistic, but rather a profit-seeking owner/investor.
+For context, the "Opportunistic Sharers", those owners who only list their home very periodically (less than 25\% of the time), make up only 18% of all owners in our sample.
+
+*This is an issue as the authors state “Beach properties are, relatively speaking, over-represented in the short-term market...
+Given the over-representation of beach properties, the differing STR and LTR revenues may be a product of the property-type (vacation vs.
+non-vacation) or a clientele effect (vacation homeowners vs.
+investor).
+The owner of a vacation home rents their property to subsidize its cost when they are not consuming its services personally.
+Thus, the only choice for the vacation home is the STR strategy.
+Short-term vacation rentals existed prior to Airbnb, so this is not a new phenomenon.*
+
+* It is true that beach properties (mostly beach apartments) are overrepresented in the STR data.
+As are city-core apartment.
+In a situation with much greater quantities of data and the ability to match exact properties from STR and LTR markets, a matching approach would be the preferred method to eliminate these sample differences.
+We also considered some down-sampling of these two over-represented classes, but felt that further restricting an already small sample was not advantageous.
+What we have done to limit the impact of these differences is three fold:
+
+1) We have limited the study area (along the beach) to the 'urban' area of Melbourne where employment opportunities abound and where long-term renters are likely to demand to live.
+More simply, we have not considered homes in the Mornington Peninsula, the tradition summer beach vacation area for Melburnians -- an area where there are many beach (and inland) homes whose highest and best use is heavily favored towards short term rentals (they are set up for large groups, include hot tubs, game rooms, extensive parking, etc.
+)
+
+2) When estimating the long-term rental values we segment the models by submarket, so that we are only using beach properties to create beach rental values.
+In this way, our comparison become a comparison of relative willingness to pay between short and long term renters for beach properties, not all properties.
+
+3) We control for submarket type in statistical models that we run.
+
+Certainly, not all of the clientele effects are covered by these controls, but we feel that we have done what is available given the data quantity and quality.
+The results, which show that beach properties have a considerably higher long-term preferance rate, suggest that many of the obvious 'beach house'-type dwellings used by owners for vacations have been controlled for in the study.
+
+ * Response
+
+2.
+*Sample selection issues are a big concern given the limited amount of property-level information available in the Airbnb data.
+If the properties in the STR and LTR samples systematically differ then the hypothetical exercise and imputed values provide little insight (garbage in, garbage out).*
+
+ * It is certainly true that is there are unobserved and systematic differences between the two samples -- say in quality and condition -- then the imputed values are biased.
+Much like our search for supporting evidence on the differences in costs, we were unable to find any existing research on the differences in quality and condition between STR and LTR properties.
+The literature does offer solid evidence for a differences in quality and condition between rental and owner occupied dwellings, however, we felt uncomfortable making this same assumption for short and long term rentals.
+One could argue that short term rentals pay a steeper price (in terms of bad reviews and the resulting immediate negative revenue) for possessing substandard internal amenities and, therefore, are likely to be kept in a better condition and offer higher quality finishes internally.
+On the other hand, long term rentals are inspected by potential occupants prior to occupancy and therefore less likely to deceive via a few good photographs and therefore, perhaps, LTR properties would be more likely to keep quality and condition levels high.
+We struggled with which of the two scenario to believe and settled on making no assumption here at all.
+For the sake of comparison, in the current scenario about 28% of properties were STR preferable.
+If we were to have overestimated the LTR imputed rents by 10%, this number rises to 32%, if we had underestimated by 10% this number falls to 25%.
+So there is some sensitivity to the long term rent numbers, but it is not dramatic.
+Further, this sensitivity represents a change in the base rate of STR preference (model intercept) and not necessarily a change in the impacts of any of the variables on STR preference itself.
+Overall the coefficients themselves are relatively stable across Tables 2, 4 and 6 suggesting that the influences of individual variable are robust across different base rates of STR preference.
+
+3.
+*The short-term costs in Eq.
+6 are understated.
+The authors note that short-term rentals are furnished by the owner, but do not include them as a cost.
+Given the feedback system built into Airbnb the furnishings may be a non-trivial expense.
+In other words, if the furnishing are in disrepair it may hurt the owners’ ratings and increase the vacancy rate of the STR.
+For this reason, I also expect the maintenance costs to be higher for the STR (especially since LTR has a security deposit to cover repairs that are not “normal wear and tear”).
+In addition, the authors do not address the question of who is managing the STR and responding to the Airbnb requests.
+Given the weekly (perhaps even nightly) turnover associated with STRs this is another cost that should be included/considered.*
+
+ * As furnishings are a durable good, only some small percentage of the costs is truly experienced during the first year, the period this exercise examines.
+While furniture is a bit like automobilies, the minute you sleep on a mattress, it loses a good bit of value, year old furniture -- especially non-beds/sofa items do hold value relatively well.
+Thus, furnishing costs are borne over a long time period.
+Further, we were not able to determine which of the LTR rental are furnished so likely there is a bit of upward bias in those estimated values as well.
+Neither of these facts eliminates the need to buy furniture to outfit an Airbnb, we simply did not have enough information on what the likely one year cost of furniture would be.
+This is a relevant comment and we've tried to address its potential impact in sensivity analysis discussed a few paragraphs below.
+
+ * We do agree that on-going (month by month) maintenance costs will likely be higher in an STR, however, large improvements, new carpets, painting, etc.
+do burden LTRs at tenant turnover.
+As we mentioned on page 6, we believe there is an argument to be made that LTR tenants actually burden a property as much if not more by virtue of moving furniture in and out, hanging decorations and, likely, spending more actual time in the dwelling than a tourist would.
+As a result of this and the fact that we were not able to find any evidence of greater maintenance costs on either side, we decided on assumming equivalent costs.
+
+  * Certainly there are time costs of managing an STR.
+These costs vary widely based on the owner's proximity to the STR and their individual imputed wage (the value of their time).
+In general, these costs are somewhat idiosyncratic to the owner and we struggled with producing a standardized estimate.
+On the converse, STR does allow for an early exit strategy, occupation or transfer to LTR on short notice, options which also have an unknown (or at least very owner-specific) value.
+We opted to allow these two forces to 'balance' out and have not accounted for either.
+The intent of the hypothetical exercise was to present the case of a simple investor (say a family) making one investment, not a large STR aggregation firm.
+Note that there are firms in Melbourne and other cities that will manage your Airbnb for you.
+Anecdotally, we've seen fees ranging from 8% to 15% for this service.
+
+  * All of the above concerns, seem to point to a potential over-estimate of STR costs, which would lower STR net revenues.
+As a further senitivit analysis, we reduced net revenues by 15% (10% for management fee and 5% for a furnishing costs) **Do a 15% reduction in lik_revenue_net simulation**
+
+4.
+*The STR vs.
+LTR decision may not apply to every property.
+In the United States, some HOAs ban short-term rentals and impose substantial fines.
+Are there similar situations in Melbourne?
+Similarly, some cities in the United States have proposed legislature to ban STR if it is not the homeowner’s primary residence (example here).
+Are there similar situations in Australia?*
+
+ * Very true.
+The legality of short term rentals is very much in flux at the moment and varies from municipality to municipality, even building to building.
+One could imagine that in an area with high demand and a large number of dwelling being ineligible for STR leasing, that a premium might accrue to those that were eligible.
+At the time of this research, there were no governmental restrictions on short term use in Melbourne, though they were being hotly debated (which was the original impetus for this research).
+Fines are now able to be levied for noise violations.
+Additionally, currently, the State of Victoria has regulations that directly impact properties that allow more than five occupants (business license required).
+The City of Sydney has moved from being opposed to any regulations to now proposing that individual condominium buildings enact rules that they see fit.
+Of course, rules can only be enforced if adequate data on occupancies is available.
+
+5. 
+a) *The abstract states “The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").” This option was available prior to Airbnb and the internet.
+Airbnb has “disrupted” the STR market, but it did not create it.*
+
+* Great point.
+The short-term market for large, natural amenitiy-rich (ski + beach) properties is decades (if not centuries old).
+We believe that Airbnb and its sister-sites have opened up this market to small, urban properties as well decreased search costs to the point that, from an owner perspective,  very short stays, even of a single night, can be economically feasible.
+We have updated the abstract to represent the distinction that you have made.
+
+b) *The next sentence in the abstract states “In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.” I think sitations is a typo.
+I only point it out because it is in the abstract.*
+
+* Thank you for pointing out this typographic error.  We have corrected it.
+
+6. The tables and figures do not have any supporting notes.
+
+ * Response

### 2018-07-18 scripts/4_data_analysis_15s.Rmd
Review: Response to reviewer 2 - part 1

--- 2018-05-30 scripts/4_data_analysis.Rmd
@@
     dplyr::left_join(imp_df, by='property_id') %>%
-    dplyr::mutate(act_pref = ifelse(revenue_net > ltr_imp_revenue, 1, 0),
-                  lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
-                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0))
+    dplyr::mutate(act_pref = ifelse(.85*revenue_net > ltr_imp_revenue, 1, 0),
+                  lik_pref = ifelse(.85*lik_revenue_net > ltr_imp_revenue, 1, 0),
+                  pot_pref = ifelse(.85*pot_revenue_net > ltr_imp_revenue, 1, 0))
 

### 2018-07-19 review/response_to_reviewers.Rmd
Review: Response to reviewer 2

@@
 
-  * All of the above concerns, seem to point to a potential over-estimate of STR costs, which would lower STR net revenues.
-As a further senitivit analysis, we reduced net revenues by 15% (10% for management fee and 5% for a furnishing costs) **Do a 15% reduction in lik_revenue_net simulation**
+  * All of the above concerns seem to point to a potential underestimate of STR costs, which would lower STR net revenues.
+As a further senitivity analysis, we reduced net STR revenues by 15% (10% for management fee and 5% for a furnishing costs), the results of which are found in the Table below.
+These should be compared to Table 2 in the paper.
+Reducing STR revenues by 15% has the likely impact of decreasing the base rate of STR preference from 28% down to 22% (also evidenced in the intercept terms Table 1.)  The coefficients on the set of variables tested (while moving) have generally remained stable in both terms of magnitude and direction.
+We feel that your comments regarding management and furniture are worthwhile.
+We worry about adding another table of sensitivity results to the paper in terms of confusion.
+We have added additional language to the Discussion section to note these omission, explain our rationale for doing so and discuss the sensitivity test shown in Table 1 of this response.
+
+```{r load_libraries, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  library(tidyverse)
+  library(sf)
+  library(geosphere)
+  library(ggmap)
+  library(multidplyr)
+  library(tmap)
+  library(xtable)
+  library(ROCR)
+  library(xtable)
+
+```
+
+```{r options_functions, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}
+
+  options(stringsAsFactors=FALSE)
+  options(xtable.comment = FALSE)
+  options(xtable.caption.placement='top')
+  setwd('..')
+  source(file.path(getwd(), 'functions', 'abb_Functions.R'))
+
+```
+
+```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, results='hide'}
+
+  setwd('..')
+  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data_15s.RData'))
+
+```
+
+```{r log_model, echo=FALSE, message=FALSE, comment=FALSE}
+
+ ## Extract data
+
+  m1 <- as.data.frame(summary(lik_glms$str)$coefficients)
+  m2 <- as.data.frame(summary(lik_glms$loc)$coefficients)
+  m3 <- as.data.frame(summary(lik_glms$host)$coefficients)
+
+ ## Create vector with significance stars
+
+  m1sig <- makeStatSig(m1[ ,4])
+  m2sig <- makeStatSig(m2[ ,4])
+  m3sig <- makeStatSig(m3[ ,4])
+
+ ## Create coefficients for the table (with stars)
+
+  m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''),
+                          sprintf('%.3f', round(m1$Estimate,3)),
+                          m1sig)
+  m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''),
+                          sprintf('%.3f',round(m2$Estimate,3)),
+                          m2sig)
+  m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''),
+                          sprintf('%.3f',round(m3$Estimate,3)),
+                          m3sig)
+
+ ## Even out the lengths
+
+  m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
+  m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2)))
+  m3c <- m3$table.coef
+
+ ##  Create the variable section of table
+ full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
+ names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+ full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
+                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
+                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
+                          'City (Submarket)',
+                          'Suburban (Submarket)', 'Rural (Submarket)',
+                          'Beach (Submarket)', 'Guests per Bedroom',
+                          'Minimum Stay', 'Flexible Cancel')
+
+ ## Create model diagnostics
+
+  # Extract diagnostics
+  str.dx <- logDx(lik_glms$str, str_tdf, str_tdf$lik_pref)
+  sm.dx <- logDx(lik_glms$loc, str_tdf, str_tdf$lik_pref)
+  host.dx <- logDx(lik_glms$host, str_tdf, str_tdf$lik_pref)
+
+  # Create diagnostic table
+  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
+                                      'AUC'),
+                           Str.Model=c('', '', round(str.dx$AIC,0),
+                                       round(str.dx$logLik, 0),
+                                       round(as.numeric(str.dx$auc@y.values),
+                                             3)),
+                           Sm.Model=c('', '', round(sm.dx$AIC,0),
+                                      round(sm.dx$logLik, 0),
+                                      round(as.numeric(sm.dx$auc@y.values), 3)),
+                           Host.Model=c('', '', round(host.dx$AIC,0),
+                                        round(host.dx$logLik, 0),
+                                        round(as.numeric(host.dx$auc@y.values),
+                                              3)))
+  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+
+ ## Combine into full table
+
+  full.table <- rbind(full.table, diag.table)
+```
+
+```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+
+  # XTable
+  x.full <- xtable(full.table,
+                  caption='Logistic Modeling Results (15% Cost Increase: Likely Revenue)\n')
+  align(x.full) <- 'lllll'
+
+  # comment          <- list()
+  # comment$pos      <- list()
+  # comment$pos[[1]] <- c(nrow(x.full))
+  # comment$command  <- c("your footnote, caption or whatever.  \n")
+
+  # Print
+  print(x.full,
+       include.rownames=FALSE,
+       hline.after=c(-1,0,16,21,21),
+       # add.to.row = comment,
+       caption.placement='top')
+
+```
 
@@
 
-6. The tables and figures do not have any supporting notes.
+6. *The tables and figures do not have any supporting notes.*
 
- * Response
+ * We are unclear as to what sort of supporting notes are desired.
+Information on data sources are provided in the accompanying text.
+We are happy to add whatever is necessary to help the reader, if you can provide some examples here.

### 2018-07-19 papers/full_paper.Rmd
Review: Response to reviewer 2

@@
 author: "Greenfield Advisors and University of Melbourne"
-date: "May 30th, 2018"
+date: "July 22nd, 2018"
 output:
@@
   setwd('..')
-  source(file.path(getwd(), 'functions', 'abb_Functions.R'))
+  #source(file.path(getwd(), 'functions', 'abb_Functions.R'))
+  source(file.path('c:/code', 'research', 'airbnbMelbourne', 'functions', 'abb_Functions.R'))
 
@@
 
-  setwd('..')
-  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
+  # setwd('..')
+  # load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
+  load(file.path('c:', 'code', 'research', 'airbnbMelbourne','data', 'analyzed',
+                 'analyzed_data.RData'))
 
@@
 We have done so as we were unable to location any evidence to suggest that one was higher than the other.
-This may be a limitation of our study and could prove to be an avenue of future research.
+Additionally, in the reported results we have not made allowances for furniture and the turnover costs associated with managing an STR.
+This omission is intentional as we felt these costs were highly idiosyncratic (turnover) and/or not limited to the one-year scenario period (furniture).
+Sensitivity tests on these two costs (both of which lower STR revenues) do create decrease in the base rate of STR preference, but show little change to the coefficients across the various regression models.
+There is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.
 

### 2018-07-19 scripts/4_data_analysis_15s.Rmd
Review: Response to reviewer 2

@@
        pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
-       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
+       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data_15s.RData'))
 

### 2018-07-23 review/response_to_reviewers.Rmd
Review: Finalizing responses to reviewers

@@
 ---
-title: "Reviewer Responses: To Airbnb?: A Question of Revenue"
-subtitle: "Andy Krause and Gideon Aschwanden"
-author: "Greenfield Advisors and University of Melbourne"
+title: "Responses to Reviewers for: To Airbnb?: A Question of Revenue"
+#subtitle: "Andy Krause and Gideon Aschwanden"
+#author: "Greenfield Advisors and University of Melbourne"
 date: "July 22nd, 2018"
@@
 If an investor were to buy that home they would have the choice of doing either an LTR or an STR which is why we framed the hypothetical situation as that of an investor.
-In the sensitivity analysis we attempted to address this potential bias in the sample by separately looking at those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time.
+In the sensitivity analysis we attempted to address this potential bias in the sample by separately looking at those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time (Tables 5 and 6).
 We believe that these are clearly situations where it is not an owner-occupied who is being opportunistic, but rather a profit-seeking owner/investor.
@@
 
-*This is an issue as the authors state “Beach properties are, relatively speaking, over-represented in the short-term market...
-Given the over-representation of beach properties, the differing STR and LTR revenues may be a product of the property-type (vacation vs.
+*This is an issue as the authors state “Beach properties are, relatively speaking, over-represented in the short-term market."* *Given the over-representation of beach properties, the differing STR and LTR revenues may be a product of the property-type (vacation vs.
 non-vacation) or a clientele effect (vacation homeowners vs.
-investor).
-The owner of a vacation home rents their property to subsidize its cost when they are not consuming its services personally.
+investor).* *The owner of a vacation home rents their property to subsidize its cost when they are not consuming its services personally.
 Thus, the only choice for the vacation home is the STR strategy.
@@
 
-* It is true that beach properties (mostly beach apartments) are overrepresented in the STR data.
-As are city-core apartment.
+* It is true that beach properties (mostly beach apartments) are over-represented in the STR data.
+As are city-core apartments.
 In a situation with much greater quantities of data and the ability to match exact properties from STR and LTR markets, a matching approach would be the preferred method to eliminate these sample differences.
@@
 
-1) We have limited the study area (along the beach) to the 'urban' area of Melbourne where employment opportunities abound and where long-term renters are likely to demand to live.
-More simply, we have not considered homes in the Mornington Peninsula, the tradition summer beach vacation area for Melburnians -- an area where there are many beach (and inland) homes whose highest and best use is heavily favored towards short term rentals (they are set up for large groups, include hot tubs, game rooms, extensive parking, etc.
+A) We have limited the study area (along the beach) to the 'urban' area of Melbourne where employment opportunities abound and where long-term renters are likely to demand to live.
+More simply, we have not considered homes in the Mornington Peninsula, the traditional summer beach vacation area for Melburnians -- an area where there are many beach (and inland) homes whose highest and best use is heavily favored towards short term rentals (they are set up for large groups, include hot tubs, game rooms, extensive parking, etc.
 )
 
-2) When estimating the long-term rental values we segment the models by submarket, so that we are only using beach properties to create beach rental values.
+B) When estimating the long-term rental values we segment the models by submarket, so that we are only using beach properties to create beach rental values.
 In this way, our comparison become a comparison of relative willingness to pay between short and long term renters for beach properties, not all properties.
 
-3) We control for submarket type in statistical models that we run.
+C) We control for submarket type in the statistical models that we estimate.
 
 Certainly, not all of the clientele effects are covered by these controls, but we feel that we have done what is available given the data quantity and quality.
-The results, which show that beach properties have a considerably higher long-term preferance rate, suggest that many of the obvious 'beach house'-type dwellings used by owners for vacations have been controlled for in the study.
-
- * Response
+The results, which show that beach properties have a considerably higher long-term preference rate, suggest that many of the obvious 'beach house'-type dwellings used by owners for vacations have been controlled for (or not included) in the study.
 
@@
  * As furnishings are a durable good, only some small percentage of the costs is truly experienced during the first year, the period this exercise examines.
-While furniture is a bit like automobilies, the minute you sleep on a mattress, it loses a good bit of value, year old furniture -- especially non-beds/sofa items do hold value relatively well.
+While furniture is a bit like automobilies, the minute you sleep on a mattress, it loses a good bit of value, one year old furniture -- especially non-beds/sofa items do hold value relatively well (common rates of depreciation for tax purposes are 10% annually).
 Thus, furnishing costs are borne over a long time period.
-Further, we were not able to determine which of the LTR rental are furnished so likely there is a bit of upward bias in those estimated values as well.
+Further, we were not able to determine which of the LTR rentas are furnished so likely there is a bit of upward bias in those estimated values as well.
 Neither of these facts eliminates the need to buy furniture to outfit an Airbnb, we simply did not have enough information on what the likely one year cost of furniture would be.
-This is a relevant comment and we've tried to address its potential impact in sensivity analysis discussed a few paragraphs below.
+This is a relevant comment and we've tried to address its potential impact in the sensivity analysis discussed a few paragraphs below.
 
@@
 
-  * All of the above concerns seem to point to a potential underestimate of STR costs, which would lower STR net revenues.
+  * All of the above concerns could point to a potential underestimate of STR costs, which would lower STR net revenues.
 As a further senitivity analysis, we reduced net STR revenues by 15% (10% for management fee and 5% for a furnishing costs), the results of which are found in the Table below.
 These should be compared to Table 2 in the paper.
-Reducing STR revenues by 15% has the likely impact of decreasing the base rate of STR preference from 28% down to 22% (also evidenced in the intercept terms Table 1.)  The coefficients on the set of variables tested (while moving) have generally remained stable in both terms of magnitude and direction.
+Reducing STR revenues by 15% has the likely impact of decreasing the base rate of STR preference from 28% down to 22% (also evidenced in the intercept terms in the below table.)  The coefficients on the set of variables tested (while moving a bit) have generally remained stable in both terms of magnitude and direction.
 We feel that your comments regarding management and furniture are worthwhile.
 We worry about adding another table of sensitivity results to the paper in terms of confusion.
-We have added additional language to the Discussion section to note these omission, explain our rationale for doing so and discuss the sensitivity test shown in Table 1 of this response.
+We have added additional language to the Discussion section to note these omissions, explain our rationale for doing so and discuss the sensitivity test shown in Table 1 of this response.
+We open to further addressing this issue if you feel it would be of assistance to readers.
 
@@
 The legality of short term rentals is very much in flux at the moment and varies from municipality to municipality, even building to building.
-One could imagine that in an area with high demand and a large number of dwelling being ineligible for STR leasing, that a premium might accrue to those that were eligible.
+One could imagine that in an area with high demand and a large number of dwellings being ineligible for STR leasing, that a premium might accrue to those that were eligible.
 At the time of this research, there were no governmental restrictions on short term use in Melbourne, though they were being hotly debated (which was the original impetus for this research).
 Fines are now able to be levied for noise violations.
-Additionally, currently, the State of Victoria has regulations that directly impact properties that allow more than five occupants (business license required).
+currently, the State of Victoria has regulations that directly impact properties that allow more than five occupants (business license required).
 The City of Sydney has moved from being opposed to any regulations to now proposing that individual condominium buildings enact rules that they see fit.
@@
 5.
-a) *The abstract states “The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").” This option was available prior to Airbnb and the internet.
+*The abstract states “The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").” This option was available prior to Airbnb and the internet.
 Airbnb has “disrupted” the STR market, but it did not create it.*
@@
 
-b) *The next sentence in the abstract states “In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.” I think sitations is a typo.
+*The next sentence in the abstract states “In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.” I think sitations is a typo.
 I only point it out because it is in the abstract.*

### 2018-07-23 papers/full_paper.Rmd
Review: Finalizing responses to reviewers

@@
   options(xtable.caption.placement='top')
-  setwd('..')
+  #setwd('..')
   #source(file.path(getwd(), 'functions', 'abb_Functions.R'))
@@
   # load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
-  load(file.path('c:', 'code', 'research', 'airbnbMelbourne','data', 'analyzed',
+  load(file.path('c:/code', 'research', 'airbnbMelbourne','data', 'analyzed',
                  'analyzed_data.RData'))
@@
 
-The logistic regression models (Table 2, 4 and 6) than we estimate show that most of the finding from the univariate analyses done earlier are validated.
+The logistic regression models (Table 2, 4 and 6) than we estimate show that most of the findings from the univariate analyses done earlier are validated.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
@@
 There are a number of limitations to this research.
-First and foremost may be the generalizability of this work.
+First, and foremost, may be the generalizability of this work.
 Melbourne is one of the primary examples of a world-class city in which local residents and tourists often (and fiercely) compete for the same urban spaces.
@@
 Next, there are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
-Part of the difficulty in estimating potential short-term rates for long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
+Part of the difficulty in estimating potential short-term rates for existing long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
 Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.
-It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.com.
+It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.co.
 
@@
 This omission is intentional as we felt these costs were highly idiosyncratic (turnover) and/or not limited to the one-year scenario period (furniture).
-Sensitivity tests on these two costs (both of which lower STR revenues) do create decrease in the base rate of STR preference, but show little change to the coefficients across the various regression models.
-There is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.
+Sensitivity tests on these two costs (both of which lower STR revenues) do create decreases in the base rate of STR preference, but show little change to the coefficients across the various regression models.
+overall, there is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.
 
@@
 These are additional revenue streams that are not take into account and might increase the occupancy and revenue for short-term rentals.
-We do suggest that, due to block patterns, a number of host do appear to be employing this approach but cannot confirm the extend to which this is actually happening.
+We do suggest that, due to block patterns, a number of host do appear to be employing this approach but cannot confirm the extent to which this is actually happening.
 
@@
 In reality, the possibilities may not be so rigid.
-For example,given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourists swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
+For example, given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourists swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
 In general, the rise of Airbnb and related portals give properties owners more options, and therefore more opportunities, to maximize returns on their property.

### 2018-07-24 papers/full_paper.Rmd
Anonymization

@@
 title: "To Airbnb?: A Question of Revenue"
-subtitle: "Andy Krause and Gideon Aschwanden"
-author: "Greenfield Advisors and University of Melbourne"
-date: "July 22nd, 2018"
+#subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
+#author: "Greenfield Advisors and University of Melbourne"
+date: "Revised: July 22nd, 2018"
 output:
@@
 The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
-In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
+In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
 We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.
@@
 
-All code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.
+All code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/anonymousreauthor/to_airbnb](https://www.github.com/anonymousreauthor/to_airbnb)**.
+
+<!--  -->
 

### 2018-10-18 papers/full_paper.Rmd
Add round 2 reviews to repo

@@
 #author: "Greenfield Advisors and University of Melbourne"
-date: "Revised: July 22nd, 2018"
+date: "Revised: October 16th, 2018"
 output:

### 2018-10-18 papers/round_2_reviews.Rmd
Add round 2 reviews to repo

---
title: "Round_2_Reviews"
author: "Andy Krause"
date: "10/17/2018"
output: html_document
---

Reviewer 1

This is an interesting paper. It is clear that, given the data limitation, the author has made a significant effort to conduct a detailed analysis to address the performance issues on short term versus long term leases. However, at this moment, the paper seems to be more like a very high quality consulting report than an academic paper. I have two suggestions for the author to improve the paper.

The first issue is on the motivation of the paper. There is a long literature on the selection of long term versus short term bonds and the trade-off between fixed rate versus adjustable rate mortgages. The general issues on the selection of short-term lease versus long-term lease should not differ too much from the term structure issues of bonds and mortgages. The author should try to tie the issues they would like to examine (using leases) to the general issues reported in the term structure literature. After the author has identified the general issues, they can motivate the paper much better and the paper will contribute more to the main literature. At this moment, the main finding of this paper that short leases sometimes perform much better (and sometimes worse) than long term leases is something practitioners might be interested in, but is not an important contribution to the literature. This is the reason why I said that this paper is more like a consulting report than an academic research.

The second issue is on the empirical design. I understand that it is difficult to gather a perfect data set. However, to use hedonic pricing model to estimate the long run rent might not provide the accuracy level that is required for the purpose of the study. This is especially true because I suspect that there is self-selection bias built into the samples.  Certain types of investors and certain types of properties might be the determining factors for the use of long term versus short term leases. Given this, the long run rent derived from a hedonic estimation will have identification problem. I suggest that the author also uses the matched pair method to see if the hedonic result holds. I understand that the author might not be able to gather perfect matched pairs. However, a matched pair based first on same building (in the same condominium or the same complex) and then adjusted by size might provide a much more accurate estimate than that provided by a hedonic price model with few independent variables.

Reviewer 2

The primary goal of this paper is to characterize the property features – location, structure type, and property characteristics – that lead to the highest likelihood of favoring a short-term rental (STR) over a long-term rental (LTR) strategy.

In my opinion, the research question is misguided. A clientele effect likely determines whether a property owner uses a STR over a LTR strategy. For simplicity’s sake, let us assume there are three distinct user groups on Airbnb:

- Owner-occupiers
- Vacation home owners
- Investors

By definition, two of the three groups cannot choose a LTR strategy. If owner-occupiers use a LTR strategy they would have to find new housing. Similarly, vacation home owners cannot use a LTR strategy as it would preclude their use of the property for vacation purposes. If either group did use a LTR strategy, then they would no longer be a part of that group and would, by definition, transition to the investors group. Thus, for the purposes of this paper we are only interested in the investors decision between LTR and STR. Unfortunately, due to data limitations, the authors cannot identify and isolate the Airbnb listings by the investors group.

The authors note that they isolate “those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time (Tables 5 and 6). We believe that these are clearly situations where it is not an owner-occupied who is being opportunistic, but rather a profit-seeking owner/investor.” However, the filter does not remove properties listed by vacation home owners. Again, the vacation home owners do not have the option to choose a LTR strategy, so for them the question “To Airbnb?” is not a question at all – it is their only option. Instead, the vacation home owners use the STR strategy to subsidize the cost of their vacation home when they are not using it themselves. If vacation home owners represent a large fraction of the Airbnb users, then the proposed research question is incorrect.

The authors also fail to address the relationship between risk and return. Even if the STR strategy offers a higher return (i.e. more revenue), it is also carries a higher risk given the nightly/weekly turnover and susceptibility to economic conditions. Thus, the investor group would consider the risk adjusted returns of the two strategies. In other words, the question “To Airbnb?” cannot be answered by simply comparing imputed revenue streams.

Overall, I think the authors did the best they could with the data provided to them. However, I fail to see a major contribution in the paper. In essence, the paper proposes that investors will choose a strategy that nets them the highest revenue. However, the paper does not control for several important factors such as the riskiness of the cash flows or the amount of time/effort expended to manage a STR vs. a LTR.

Minor Comment

Most academic journals require figures and tables to be self-contained. In other words, a reader should be able to interpret a table or figure without reading the text. Including a short note that describes each figure and table is an easy way to accomplish this goal. See, for example, the figures and tables in the latest version of Journal of Real Estate Research (v40, n2, 2018).

### 2018-10-28 scripts/4_data_analysis.Rmd
Add: Knn imputation method.

@@
                                 verbose=FALSE)
+
+  kimp_df <- knnImputeWrap(ltr_df = ltr_df, 
+                           str_df = str_tdf,
+                           knns = c(3, 5, 7))
+
+  imp_df$ltr_imp_revenueK <- kimp_df$year[match(imp_df$property_id,
+                                               kimp_df$property_id)]
+  imp_df <- imp_df %>%
+    rename(ltr_imp_revenueH = ltr_imp_revenue) %>%
+    mutate(ltr_imp_revenueK = ((365-imp_dom)/365) * ltr_imp_revenueK,
+           ltr_imp_revenue = .5 * (ltr_imp_revenueH + ltr_imp_revenueK),
+           lir_hi = ltr_imp_revenue * 1.15,
+           lir_lo = ltr_imp_revenue * .85)
 

### 2018-10-28 functions/abb_Functions.R

@@ -454,6 +454,53 @@ imputeLtrRents <- function(ltr.df,
               model=ltr.mod))
 }
 
+
+
+knnImputeWrap <- function(ltr_df, 
+                          str_df,
+                          knns = c(3, 5, 7)){
+  
+  # Create Split Lists
+  ltr_ <- plyr::dlply(ltr_df, .variables = c('bedrooms', 'bathrooms', 
+                                             'type'))
+  str_ <- plyr::dlply(str_tdf, .variables = c('bedrooms', 'bathrooms', 
+                                              'type'))
+  ltr_ <- ltr_[names(ltr_) %in% names(str_)]
+  
+  k_ <- list()
+  
+  for (j in knns){
+    
+    k_[[j]] <- purrr::map2(.x = str_,
+                           .y = ltr_,
+                           .f = knnImpute,
+                           k = j) %>%
+      dplyr::bind_rows()
+  }
+  
+  x <- tidyr::spread(k_ %>% bind_rows(), k, weekly_rent)
+  x$mean <- rowMeans(x[,grepl('k_', names(x))])
+  x$year <- x$mean * 52
+  x
+}
+
+knnImpute <- function(s_df, l_df, k){
+  
+  nn <- RANN::nn2(data=l_df[, c('longitude', 'latitude')],
+                  query = s_df[, c('longitude', 'latitude')],
+                  k = k)
+  
+  getMed <- function(x,y){median(y$price[x])}
+  
+  kp_df <- plyr::adply(nn$nn.idx, 1, getMed, y=l_df)
+  
+  return(data.frame(property_id = s_df$property_id,
+                    weekly_rent = kp_df$V1,
+                    k = paste0('k_', k)))
+  
+}
+
+
 ### Impute days on market for the airbnb properties ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
 imputeDOM <- function(str.df,

### 2018-10-28 papers/round_2_reviews.Rmd
Add: Summary of reviewer comments
Review: Add figure, language around items 1, 3 and 4

@@
 title: "Round_2_Reviews"
-author: "Andy Krause"
-date: "10/17/2018"
+author: "Andy Krause and Gideon Aschwanden"
+date: "10/25/2018"
 output: html_document
@@
 
-Reviewer 1
+### Key Points:
 
-This is an interesting paper.
+#### Reviewer 1
+
+* ~~Add in something on Short term vs long term bonds~~
+* ~~Doesn't trust hedonic estimation.  Do matched pairs.~~
+
+#### Reviewer 2
+
+* (in Progress) Can't determine who are actually investors, so the research question isn't valid
+* ~~Make tables/figures self contained~~
+
+### Full comments
+
+#### Reviewer 1
+
+*This is an interesting paper.
 It is clear that, given the data limitation, the author has made a significant effort to conduct a detailed analysis to address the performance issues on short term versus long term leases.
 However, at this moment, the paper seems to be more like a very high quality consulting report than an academic paper.
-I have two suggestions for the author to improve the paper.
+I have two suggestions for the author to improve the paper.*
 
-The first issue is on the motivation of the paper.
+*The first issue is on the motivation of the paper.
 There is a long literature on the selection of long term versus short term bonds and the trade-off between fixed rate versus adjustable rate mortgages.
@@
 At this moment, the main finding of this paper that short leases sometimes perform much better (and sometimes worse) than long term leases is something practitioners might be interested in, but is not an important contribution to the literature.
-This is the reason why I said that this paper is more like a consulting report than an academic research.
+This is the reason why I said that this paper is more like a consulting report than an academic research.*
 
-The second issue is on the empirical design.
+**As Real Estate is an asset class much like bonds there likely warrants a larger theoretical discussion on the short vs.
+long term holding structure.
+However, we do not feel that this paper is the correct place to do so given its empirical focus.
+The fact that this comment was raised (and the input from another reviewer regarding our research question) has led us to re-focus our research question and the aim of this study.
+In short, we want to focus on the built environment side of the question, not the financial structuring side.
+In other words, what types of properties in which locations are short term preferable, rather than attempting to make a judgement about the financial decision-making of an owner -- a situation whereby many individual and idiosyncratic factors play a large role  We appreciate you raising this concern as it has helped us think through the ultimate goal of our work.**
+
+*The second issue is on the empirical design.
 I understand that it is difficult to gather a perfect data set.
@@
 I understand that the author might not be able to gather perfect matched pairs.
-However, a matched pair based first on same building (in the same condominium or the same complex) and then adjusted by size might provide a much more accurate estimate than that provided by a hedonic price model with few independent variables.
+However, a matched pair based first on same building (in the same condominium or the same complex) and then adjusted by size might provide a much more accurate estimate than that provided by a hedonic price model with few independent variables.*
 
-Reviewer 2
+**To address this issue we have added a 'matched-pairs'-type estimation to our imputation of long-term rents.
+More specifically we do an ensemble of 3, 5, and 7 comparable matched-pairs type valuations using the nearest 3, 5, and 7 transactions that have identical bedrooms, bathrooms and structure type (apartment/detached).
+For apartments this often pulled in transactions in the same building, for detached dwelling on the same block or street.
+Results from this estimation show a 91% correlation with our hedonic results, though there did seem to be a deviation in the high end apartment market, especially for 1 bedroom units.
+As a result, we take the average of the matched pairs ensemble and the hedonic model.**
 
-The primary goal of this paper is to characterize the property features – location, structure type, and property characteristics – that lead to the highest likelihood of favoring a short-term rental (STR) over a long-term rental (LTR) strategy.
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
 
-In my opinion, the research question is misguided.
+  library(ggplot2)
+
+   load(file.path('c:/code', 'research', 'airbnbMelbourne',
+                  'data', 'analyzed', 'reviewers.RData'))
+
+  imp_df$bed_lab <- paste0(imp_df$bedrooms, ' Beds')
+  fig_cap <- paste0('This figure compares the estimated long term rent for short term rental properties via the hedonic\n imputation method (X-axis) and the matched pairs-type method (Y-axis).
+It is broken down by\n structure type (Apartment vs House) and by bedroom count.')
+
+  ggplot(imp_df,
+         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
+    geom_point(alpha = .5, size=.5) + 
+    facet_grid(type ~ bed_lab) + 
+    xlab('\nHedonic Revenue\n') + 
+    ylab('Matched Pairs Revenue\n') + 
+    theme(legend.position = 'none',
+          plot.caption=element_text(hjust = 0.3),
+          plot.title = element_text(hjust = 0.5)) +
+    scale_color_manual(values = c('red', 'blue')) + 
+    scale_x_continuous(breaks = c(15000, 30000, 45000),
+                       labels = c('$15k', '$30k', '$45k'))+
+    scale_y_continuous(breaks = c(15000, 30000, 45000),
+                       labels = c('$15k', '$30k', '$45k'))+
+    geom_abline(intercept = 0, slope = 1, linetype = 2,
+                color = 'gray50') +
+    labs(caption = fig_cap,
+         title = 'Comparison of Hedonic and Matched Pairs Imputation')
+
+```
+
+#### Reviewer 2
+
+*The primary goal of this paper is to characterize the property features – location, structure type, and property characteristics – that lead to the highest likelihood of favoring a short-term rental (STR) over a long-term rental (LTR) strategy.*
+
+*In my opinion, the research question is misguided.
 A clientele effect likely determines whether a property owner uses a STR over a LTR strategy.
-For simplicity’s sake, let us assume there are three distinct user groups on Airbnb:
+For simplicity’s sake, let us assume there are three distinct user groups on Airbnb:*
 
-- Owner-occupiers
-- Vacation home owners
-- Investors
+* *Owner-occupiers*  **(Wait, what?  How do these factor in?  You can't occupy given our study design.)**
+* *Vacation home owners* **(Our study design eliminates most of these give our boundary)**
+* *Investors*
 
-By definition, two of the three groups cannot choose a LTR strategy.
+*By definition, two of the three groups cannot choose a LTR strategy.
 If owner-occupiers use a LTR strategy they would have to find new housing.
@@
 Thus, for the purposes of this paper we are only interested in the investors decision between LTR and STR.
-Unfortunately, due to data limitations, the authors cannot identify and isolate the Airbnb listings by the investors group.
+Unfortunately, due to data limitations, the authors cannot identify and isolate the Airbnb listings by the investors group.*
 
-The authors note that they isolate “those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time (Tables 5 and 6).
+*The authors note that they isolate “those properties which were listed as Available or Reserved (not Blocked) at least 75% of the time (Tables 5 and 6).
 We believe that these are clearly situations where it is not an owner-occupied who is being opportunistic, but rather a profit-seeking owner/investor.” However, the filter does not remove properties listed by vacation home owners.
@@
 Instead, the vacation home owners use the STR strategy to subsidize the cost of their vacation home when they are not using it themselves.
-If vacation home owners represent a large fraction of the Airbnb users, then the proposed research question is incorrect.
+If vacation home owners represent a large fraction of the Airbnb users, then the proposed research question is incorrect.*
 
-The authors also fail to address the relationship between risk and return.
+**[Forthcoming] Discuss how our study design eliminated most vacation homes.  Move the Sensitive test on Maximizers to be the key focus of the paper**
+
+*The authors also fail to address the relationship between risk and return.
 Even if the STR strategy offers a higher return (i.e.
@@
 Thus, the investor group would consider the risk adjusted returns of the two strategies.
-In other words, the question “To Airbnb?” cannot be answered by simply comparing imputed revenue streams.
+In other words, the question “To Airbnb?” cannot be answered by simply comparing imputed revenue streams.*
 
-Overall, I think the authors did the best they could with the data provided to them.
+**[Forthcoming] Make a note about pivoting away from financial calculus to location/utility argument**
+
+*Overall, I think the authors did the best they could with the data provided to them.
 However, I fail to see a major contribution in the paper.
@@
 However, the paper does not control for several important factors such as the riskiness of the cash flows or the amount of time/effort expended to manage a STR vs.
-a LTR.
+a LTR.*
 
@@
 
-Most academic journals require figures and tables to be self-contained.
+*Most academic journals require figures and tables to be self-contained.
 In other words, a reader should be able to interpret a table or figure without reading the text.
 Including a short note that describes each figure and table is an easy way to accomplish this goal.
-See, for example, the figures and tables in the latest version of Journal of Real Estate Research (v40, n2, 2018).
+See, for example, the figures and tables in the latest version of Journal of Real Estate Research (v40, n2, 2018).*
+
+**Great suggestion.  We've updated our figures and table to contain such.**

### 2018-10-28 scripts/4_data_analysis.Rmd
Review: Add figure, language around items 1, 3 and 4

--- 2018-05-30 scripts/4_data_analysis.Rmd
@@
                                 verbose=FALSE)
+
+  kimp_df <- knnImputeWrap(ltr_df = ltr_df, 
+                           str_df = str_tdf,
+                           knns = c(3, 5, 7))
+
+  imp_df$ltr_imp_revenueK <- kimp_df$year[match(imp_df$property_id,
+                                               kimp_df$property_id)]
+  imp_df <- imp_df %>%
+    rename(ltr_imp_revenueH = ltr_imp_revenue) %>%
+    mutate(ltr_imp_revenueK = ((365-imp_dom)/365) * ltr_imp_revenueK,
+           ltr_imp_revenue = .5 * (ltr_imp_revenueH + ltr_imp_revenueK),
+           lir_hi = ltr_imp_revenue * 1.15,
+           lir_lo = ltr_imp_revenue * .85)
+  imp_df <- imp_df %>%
+    left_join(str_tdf %>%
+                dplyr::select(property_id, bedrooms, bathrooms, type, latitude,
+                              longitude),
+              by='property_id')
+
+    save(imp_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))
 
@@
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
 
+  save(ltr_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))
+
 ```

### 2018-10-31 papers/full_paper.Rmd
Paper updates to Owner characteristics in data.

--- 2018-07-24 papers/full_paper.Rmd
@@
 ---
-title: "To Airbnb?: A Question of Revenue"
-#subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
-#author: "Greenfield Advisors and University of Melbourne"
-date: "Revised: July 22nd, 2018"
+title: "To Airbnb?: A look at Long vs Shorm Term Leasing"
+subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
+author: "Greenfield Advisors and University of Melbourne"
+date: "Revised: October 16th, 2018"
 output:
@@
 
-The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
+The growth of Airbnb and other short-term rental platforms have presented absentee owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
 In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
-We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.
+We also find that hosting policies matter, suggesting that even the right property may need the right owner(s) or strategy to make short-term rental the more profitable approach.
 
@@
 Or rather, is it more profitable to do so when compared to traditional long-term rental (LTR)?
-And further, are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
+Are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
+Do host policies matter?
 
@@
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
-
-We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues.
-Our results show that the feasibility of a greater return through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
+To avoid confounding market dynamics caused by traditional vacation rentals (beach, ski and other recreation) we limit our study area to metropolitan area and suburban/rural areas lacking these recreational amenities.
+Additionally, for any individual property the choice between short and long term leasing may be influenced by individual financial situations (tax and mortgage financing) as well as non-financial concerns such as time availability and personal attachement to the property.
+While we analyze individual properties, we acknowledge that there are many unobserved condiseration and, therefore, we generalize our findings to market segments, locations and host policy decisions.
+
+We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues, netting out costs that can be estimated or assumed with some generality.
+We handle potential undercounting of costs through sensitivity tests that follow our initial assessment.
+
+Our results show that the feasibility of a greater revenues through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
 In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy is ''it depends''.
@@
 
-We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a resdiential investment property.
+We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a residential investment property.
 More specifically, we examine the following case:
@@
 * They are looking to maximize the net revenue over the 12-month period from September 1, 2015 to August 31, 2016.
+* They do not intend to inhabit the home themselves. 
 * The choices are 1) traditional year long rental (long-term), or: 2) short-term, nightly Airbnb-type rental.
-* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored.
+* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored as these concerns are influenced by owner situations, not property characteristics or hosting policies.
 * As most long-term rentals in Melbourne use a leasing agency, we will assume use of an agency.
-
-We will not, a priori, specify a location or property type for the scenario as we hypothesize that the preference of a short-term rental over a long-term one will vary by the location and property characteristics.
-The extent to which location, property type and property characteristics impact the probability of short-term preference are examined in the results section.
 
@@
 
-As our scenario compares a hypothetical and particular owner over the course of a single  year the tax $T$ and $F$ costs are identical between the two leasing strategy and therefore cancel out.
+As our scenario compares a hypothetical and particular owner over the course of a single year the tax $T$ and $F$ costs are identical between the two leasing strategies and therefore cancel out.
 General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
@@
 Our data for short-term rentals comes from the Airbnb platform.
-In addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
+On Airbnb, in addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
-As a result of janitorial fees being a separate line item in the STR data (paid separately and in addition to the nightly rate) they can also be ignored in the comparative analysis below.
+As a result of janitorial fees being a separate line item in the Airbnb data (paid separately and in addition to the nightly rate) they can also be ignored in the comparative analysis below.
 
@@
 
-Throughout this analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference'.
+Throughout this analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference' (STP).
 For the purposes of this study we consider this a binary position leading to a binary decision of which leasing strategy to follow.
@@
 Airbnb is the largest short-term rental hub in the Melbourne region.
-As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.
-The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
+As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.^[In fact, our choice of study area was done so to specifically minimize the number of potential traditional vacation homes in our sample.] The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
 The short-term data include two types of observations, property-level and nightly-per-property.
@@
 In each case the last observation signifies the final price of the rental contract.
-We separate this data into two sets for efficiency reasons.
-The first data set includes all information about the property, physical and economic (date and amount of rental contract), while the second contains a property ID, a rental event ID, the list price and the date of the change.
-As such, the first dataset is a set of market observations with associated characteristics and the second is a listing history of each rental event.
 The long-term lease data cover the period from January 2014 to December 2015.
@@
 Unfortunately, there are no common identifiers between the two datasets as the Airbnb data does not include addresses.
-Both sets of data do include latitude and longitude, but in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on two-dimensional coordinates.
+Both sets of data do include latitude and longitude, however the accuracy of the Airbnb coordinates is suspect as these are often purposefully jittered to protect property anonymity and, as a result, in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on imprecise two-dimensional coordinates.
 As a result of this, we are unable to directly match observations from the two datasets.
-However, the number of properties that rented long-term for the 2014 to 2015 period and then switched to Airbnb for the 2015 to 2016 period are likely very small and this inability to directly match properties does not greatly impact our modeling strategy.
 
@@
 
-As long-term rentals do not offer Private Room or Shared Room options^[Our long-term rental dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment.
+As long-term rentals do not offer Private Room or Shared Room options^[Our long-term rental dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term revenues, we remove all short-term properties that do not lease the entire home or apartment.
 Unfortunately, this filter does remove about 46% of the short-term data, however, given the research question it is unavoidable.
@@
 ![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/loc_bar.png)
+
+### Owner Types
 

### 2018-11-04 papers/full_paper.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

@@
 title: "To Airbnb?: A look at Long vs Shorm Term Leasing"
-subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
-author: "Greenfield Advisors and University of Melbourne"
-date: "Revised: October 16th, 2018"
+subtitle: "Andy Krause and Gideon Aschwanden"
+author: "Zillow and University of Melbourne"
+date: "Revised: November 10th, 2018"
 output:
@@
   library(xtable)
-
 ```
@@
 ```
+
 ## Abstract
@@
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
-To avoid confounding market dynamics caused by traditional vacation rentals (beach, ski and other recreation) we limit our study area to metropolitan area and suburban/rural areas lacking these recreational amenities.
+To avoid confounding market dynamics caused by traditional vacation rentals (beach, ski and other recreation) we limit our study area to the urbanized areas of Melbourne.
 Additionally, for any individual property the choice between short and long term leasing may be influenced by individual financial situations (tax and mortgage financing) as well as non-financial concerns such as time availability and personal attachement to the property.
@@
 Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
-To determine the likely LTR nightly rate for any given property, we will use the observed rental transactions from September 1, 2014 to August 31, 2015.
+To determine the likely LTR nightly rate for any given property we use the observed rental transactions from September 1, 2014 to August 31, 2015.
 Taking the Airbnb or STR approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
@@
 
+#### Host Classification
+
+Both anecdotal evidence and Airbnb's own marketing campaigns suggest that there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
+For the purposes of this research we are focused on Profit Seekers; those owner who would be faced with deciding between a long- and short-term leasing strategy.
+
+If these are the two dominant forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked (not listed on the portal) should be highly bimodal with Profit Seekers in one group and Opportunistic Sharers in another.
+The left hand panel of Figure 1 shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time (25\% to 75\%) .
+
+Based on the data it appears there may also be a third potential host type, that of the host who utilizies multiple platforms to list their short-term property, of which Airbnb may just be one.
+A potential method to identify these hosts is to look at the number of individual periods of blocked days.
+A host using multiple platforms will likely have many small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
+We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 1.
+We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
+
+![Host Blocking Tendencies](C:/Code/research/airbnbMelbourne/images/block_rate.png)
+
+Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
+As a more subjective, but implementable, approach we have divided the hosts up into three categories based on the original two variables considered: block percentage and number of blocked periods.
+Profit Seekers are those host who have blocked percentages less than 25\% of the time.
+Opportunistic Sharers have blocked their properties at least 75\% of the time.
+Within those two extremes, we consider users we consider as Unknown as they may be multiple plaform users (who are profit seeking), very opportunistic sharers or driven by some other, unknown motivation.
+Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 19\% and the remainder 'Unknown' category contains just over 38\% of all properties.
+To best approximate the scenario considered in our research question, we keep only the Profit Seekers in our dataset.
+See Figure 2 for a breakdown of these group by the two variables.
+
+<!-- ![Host Categories](C:/Code/research/airbnbMelbourne/images/host_scat.png) -->
+
+![Host Category Counts](C:/Code/research/airbnbMelbourne/images/host_bar.png)
+
 #### Structural Characteristics
@@
 
-### Rates and Rental Values
+#### Rates and Rental Values
 
@@
 
-### Location and Submarkets
+#### Location and Submarkets
 
@@
 
-It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.
+We begin by eliminating any observations in the outer suburbs.
+Very few short-term rentals were located in these areas and those that were have a much higher likelihood of being vacation homes; a group of properties uses that doesn't match well to our research question.
+While the Inner and Middle suburb designation is a useful starting place, we can imagine that a few different spatial features can influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
-Using the three broad submarkets from the long-term market (Inner, Middle and Outer) we have created a five sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
+
+Using the two remaining broad submarkets (Inner and Middle) we have created a four sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
 
@@
 3. Suburban (Middle suburbs, not Beach)
-4. Rural (Outer suburbs, not Beach)
-5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
+4. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
 
@@
 Finally, we filter our data to observations in suburbs that contain at least three STR and LTR observations.
-The location of the short- and long-term rentals, colored by submarket, are shown in Figures 2 and 3.
+The boundary of the suburbs meeting these criteria compose our study area (Figure 3).
+The location of the short- and long-term rentals, colored by submarket, are shown in Figures 4 and 5.
 
@@
 Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short-term market, especially in apartments, while suburban and rural apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
-Overall, the suburban and rural Airbnb markets are quite thin, later results focusing on these markets will need to be examined in light of this small sample size.
+Beach properties are, relatively speaking, over-represented in the short-term market, especially in apartments, while suburban apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
+Overall, the suburban Airbnb market is somewhat thin, later results focusing on these markets will need to be examined in light of this small sample size.
 
 ![Observations by Submarket](C:/Code/research/airbnbMelbourne/images/loc_bar.png)
-
-### Owner Types
 
@@
 
-First, we must deal with those properties that were not listed on Airbnb for the entire 12-month period.
+First, we must deal with those properties that were not listed on Airbnb for the entire 12-month period of our study.
 Our data cleaning eliminated all properties that were listed for less than six months, however, it would be incorrect to compare the revenue of a property listed on Airbnb for seven months with the hypothetical annual revenue from a long-term rental.
 
-Second, many of the short-term properties have a significant number of blocked days, days in which the property was not offered on Airbnb.
-Here too, there is a problem with comparing observed revenues from a property with a 40\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portals during those blocked days.
+Second, many of the short-term properties have a significant number of blocked days (up to 255), days in which the property was not offered on Airbnb.
+Here too, there is a problem with comparing observed revenues from a property with a 20\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portals during those blocked days.
 And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.
@@
 
-As a result, we have calculated three separate revenues values for the short-term properties:
+As a result, we have calculated two separate revenues values for the short-term properties:
 
 1. Actual ($REV_a$)}: Observed bookings multiplied by median nightly rate
+
 2.
-Likely ($REV_l$)}: Observed bookings extrapolated to a full year representing the likely actual revenue if the property had been listed all year long.
-The additional bookings are imputed by comparing the property specific performance during the listed days to overall market performance and then applying that relative ratio to the overall market performance on the non-list days.
-3.
-Potential ($REV_p$)}: Observed bookings plus imputed bookings during blocked days.
-The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance and then applying that relative ratio to the overall market performance on the blocked days.
+Potential ($REV_p$)}: Observed bookings extrapolated to a full year plus imputed bookings during observed blocked days.
+Our attempt here is to represent the potential revenue if the property had been listed all year long.
+The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance and then applying that relative ratio to the overall market performance on the extrapolated and blocked days.
 
-As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Likely' revenue metric to be a better estimate of market performance.
-We chart the distribution of the Likely ($REV_l$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 5).
+As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Potential' revenue metric to be a better estimate of market performance.
+We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 7).
 Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.
-Likely short-term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue.
-The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.
+Actual short-term revenues range from neglible to highs of greater than \$60,000, with many of the properties showing very limited (less than \$10,000) revenue.
+The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is shifted slightly to the right due to our time extrapolation and blocked days imputation.
 
 While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
-The high number of very low yield Airbnb properties in the Likely condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
+The high number of very low yield Airbnb properties suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
 
@@
 In other words, we have not directly observed a property which has been in a long-term rental followed by short-term rental or vice versa.
-We will, instead, make the comparisons between the two by imputing likely long-term rental revenues for the observed short-term properties and then comparing the measured net revenues of the short-term properties to their estimated imputed long-term revenues.
-We first focus on using the Likely measure of net revenue for the short-term properties as discussed above.
-We save discussion and analysis of the Potential revenue for the sensitivity tests later in the study.
+We will, instead, make the comparisons between the two by imputing long-term rental revenues for the observed short-term properties and then comparing the measured net revenues of the short-term properties to their estimated imputed long-term revenues.
 
-We make our imputations via hedonic price models.
-We model the long-term market with the long-term data and then use this model to predict or impute the likely long-term weekly rental prices for the short-term properties.
-We use the following model specification:
+We make our imputations via an average from a two model ensemble. First we impute long term rental rates for the short methods with a hedonic price model. We use the following model specification:
 
@@
 
+To limit the potential impacts of systematic bias from omitted variables or misspecification in our hedonic model on later analyses, we've also used a matched-pairs or clustering approach as the other half of our ensemble.
+In this method, we first group properties based on structure type, bedroom and bathroom combination and then find the geographically nearest 7 long-term observations.
+For example, all 2-bed, 2-bath apartments are grouped.
+For each short-term rental in this group we find the nearest 7 comparables (geographically), many of which are in the same building.
+We compute the median of these seven comparables as our matched pairs estimation.
+
+We then average the hedonic model and matched pairs prediction for each short term property to create an estimate of its long-term rental rate.
+
 ## Results
 
-Overall, 28.4% short-term rental properties were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+Overall, 57.3%^[If we just look at actual revenue, ignoring blocked days and properties with less than a full 12 months of listing, the figure is 42.5%] of the 2,415 short-term rental properties in our sample were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
 While illustrative, a simple univariate analysis does not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
@@
 
-The results of all three models are shown in Table 4.
+The results of all three models are shown in Table 2.
 For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Strict is the reference category.
@@
 Additionally, 1 bed / 1 bath units show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
-This could be due to the fact that 2 bed units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
-Larger units, 3 bedrooms plus, generally show no statistical difference in preference porbability to the 1 bed / 1 bath reference unit, with the exception of the 4 bed / 2 bath properties.
+This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
+Larger units, 3 bedrooms plus, generally show no statistical difference in preference porbability to the 1 bed / 1 bath reference unit.
 
 Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.
-The difference between the Rural and City-Core is not significant, however.
+The largest difference is, unsurprisingly, between Suburban and City-Core properties.
 The coefficients for the structural characteristics show the same signs and relatively small changes in magnitude from Model 1 to Model 2, speaking to the robustness of those estimates.
-The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.
-This is likely due to the fact that there are sturctural differences between the geographic submarkets.
-Houses, for example, are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.
 
-Finally, in Model 3 we add in host behavior or policies.
+Finally, in Model 3 we add in hostpolicies.
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
@@
 Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a positive relationship with short-term preference.
-Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
+Strict cancellation may be a luxury available only for the best and most highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
 
@@
 
-  m1 <- as.data.frame(summary(lik_glms$str)$coefficients)
-  m2 <- as.data.frame(summary(lik_glms$loc)$coefficients)
-  m3 <- as.data.frame(summary(lik_glms$host)$coefficients)
+  m1 <- as.data.frame(summary(pot_glms$str)$coefficients)
+  m2 <- as.data.frame(summary(pot_glms$loc)$coefficients)
+  m3 <- as.data.frame(summary(pot_glms$host)$coefficients)
 
@@
                           'City (Submarket)',
-                          'Suburban (Submarket)', 'Rural (Submarket)',
+                          'Suburban (Submarket)',
                           'Beach (Submarket)', 'Guests per Bedroom',
@@
   # Extract diagnostics
-  str.dx <- logDx(lik_glms$str, str_tdf, str_tdf$lik_pref)
-  sm.dx <- logDx(lik_glms$loc, str_tdf, str_tdf$lik_pref)
-  host.dx <- logDx(lik_glms$host, str_tdf, str_tdf$lik_pref)
+  str.dx <- logDx(pot_glms$str, str_tdf, str_tdf$pot_pref)
+  sm.dx <- logDx(pot_glms$loc, str_tdf, str_tdf$pot_pref)
+  host.dx <- logDx(pot_glms$host, str_tdf, str_tdf$pot_pref)
 
@@
        include.rownames=FALSE,
-       hline.after=c(-1,0,16,21,21),
+       hline.after=c(-1,0,15,20,20),
        caption.placement='top')
@@
 
-To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sets of sensitivity tests.
-First, we examine how the results change if Potential revenue, not Likely revenue, of the short-term properties is used in the comparisons.
-Second, we categorize the hosts, split the data and re-analyze the performance of properties based on hypothesized motivations and actions of the hosts.
+To test if the above results are influence by the assumptions we have made throughout this analysis, we perform a sensitivity test.
+The most influential assumptions that we make are in regards to; 1) unobserved costs of short term leasing (furnishings, additional maintenance, turnover, etc.) and that the properties in the two markets in our datasets are equivalent in terms of unobserved variables, such as quality and condition.
+To approximate how these assumption may be influencing our results, we re-estimating our models under two new conditions:
 
-#### Potential Revenue
+1) **Missed Costs**:  Assume that there are extra costs for short term leasing that were not accounted for in our earlier analysis. Lowers relative preference of short-term option.
 
-The above uses the Likely^[Extrapolated out in cases of Airbnb properties on the market for less than a year] revenue in the comparisons with the imputed long-term revenue.
-Doing so may underestimate the possible revenue -- what may matter most to the hypothetical buyer in our scenario -- due to not factoring in the impact of blocked days.
-If we, instead, assume that blocked days could be leased out on the short-term market at the same overall occupancy rate (relative for each property and the market as a whole on those days) as the unblocked (observed) days we can produce a potential revenue figure.
-Note that it is possible (likely?) that the large oversupply of available units in the market that would occur if no properties blocked their units would decrease both prices and occupancy rates.
-We do not attempt to correct for this likelihood, rather we offer these figures as high end estimates.
+* Net short term revenues for short term rentals are systematically decreased 15%
 
-Using the potential revenue, 36.1% of all properties are short-term preferable.
-Breaking that down by type and by geographic submarket (Table 3) shows similar findings, in terms of relative comparativeness, to the Likely revenue analysis above.
-Apartments have a higher short-term preference than do Houses and City-Core properties dominate the other geographic regions.
-One notable difference here is that the Suburban and Rural properties perform rather poorly under a potential revenue scenario, relatively speaking, suggesting that they may be operating near their peak in the current condition.
+2) **Uneven Sampling**: Assume that short term rental units are of a lower quality and condition than those in the long term market. Raises relative preference of short term option.
 
-```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
+* Net long term revenues for short term rental are systematically decreased 15%
 
- # Make Basic comparison table of type
-  tpref.table <- abbCreateCompTable(ic.df=str_tdf,
-                                    split.field='type')
+Table 3 shows the results of our sensitivity testing, with the original model results shown for comparison.
+For the five variables with the strongest relationship in the original model -- House, City, Suburban, Guests Per Bedroom and Flexible Cancel -- the signs of the coefficient remain identical across the sensitivity tests and the variation in magnitudes are small, relatively speaking.
+A few of the originally less significant variables do show relatively larger deviations in coefficient magnitude, but in general, the models appear to be stable across the sentivity tests.
+Do note that the intercept terms does change across models, which would be expected as this represents the base probability of short-term preference which we'd expect to move in concert with our changing assumptions
 
- # Extract Potential Results
-  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
-
- # Make baseic comparison table of submarkets
-  spref.table <- abbCreateCompTable(ic.df=str_tdf,
-                                    split.field='geo_mrkt')
-
- # Extract potential results
-  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
-
- # Combine and round
-  st.table <- rbind(tpref.table, spref.table)
-  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')
-
- ## Fix names and print
-
-  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
-  options(xtable.comment = FALSE)
-  print(xtable(st.table[,1:2],
-               caption='Potential Revenue Preferability\n',
-               digits=1, align='llr'),
-               include.rownames=FALSE,
-               caption.placement='top',
-               hline.after=c(-1, 0, 2, 7, 7))
-
-```
-
-Next, we re-run the logistic regression models using short-term preference in the potential case as the dependent variable.
-Generally speaking, the results from the new series of models (Table 4) are qualitatively similar to those derived in the Likely revenue case (Table 2).
-The overall magnitude of the coefficient for House (vs Apartments) is lowered in the Potential case, suggesting that houses may be blocked off more that Apartments.
-The product types (bed/bath) show similar trends, though with larger discounts for the 2 Bed / 1 Bath and 2 Bed/2 Bath units.
-Likewise the geographic submarkets and host policies show similar effects in terms of direction of impact with some slight deviations in magnitude.
-
-```{r pot_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
+```{r host_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
 
@@
 
-  pm1 <- as.data.frame(summary(pot_glms$str)$coefficients)
-  pm2 <- as.data.frame(summary(pot_glms$loc)$coefficients)
-  pm3 <- as.data.frame(summary(pot_glms$host)$coefficients)
+  h0 <- as.data.frame(summary(pot_glms$host)$coefficients)
+  h1 <- as.data.frame(summary(pot_mc_glms[[3]])$coefficients)
+  h2 <- as.data.frame(summary(pot_us_glms[[3]])$coefficients)
 
- ## Make Significance stars
+ ## Build significance stars
 
-  pm1sig <- makeStatSig(pm1[,4])
-  pm2sig <- makeStatSig(pm2[,4])
-  pm3sig <- makeStatSig(pm3[,4])
+   h0sig <- makeStatSig(h0[ ,4])
+   h1sig <- makeStatSig(h1[ ,4])
+   h2sig <- makeStatSig(h2[ ,4])
 
- ## Create Table coef vectors
+ ## Create Table coefficients
 
- pm1$table.coef <- paste0(ifelse(pm1$Estimate>0, ' ', ''),
-                         sprintf('%.3f', round(pm1$Estimate,3)),
-                         pm1sig)
- pm2$table.coef <- paste0(ifelse(pm2$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(pm2$Estimate,3)),
-                         pm2sig)
- pm3$table.coef <- paste0(ifelse(pm3$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(pm3$Estimate,3)),
-                         pm3sig)
+   h0$table.coef <- paste0(ifelse(h0$Estimate>0, ' ', ''),
+                         sprintf('%.3f', round(h0$Estimate,3)),
+                         h0sig)
+   h1$table.coef <- paste0(ifelse(h1$Estimate>0, ' ', ''),
+                         sprintf('%.3f', round(h1$Estimate,3)),
+                         h1sig)
+   h2$table.coef <- paste0(ifelse(h2$Estimate>0, ' ', ''),
+                         sprintf('%.3f',round(h2$Estimate,3)),
+                         h2sig)
 
- ## Snap to same length
+ ## Convert to variable table
 
- pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1)))
- pm2c <- c(pm2$table.coef, rep(' ', nrow(pm3)-nrow(pm2)))
- pm3c <- pm3$table.coef
+ hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), 
+                                    h0$table.coef,
+                                    h1$table.coef,
+                                    h2$table.coef))
 
- ## Put together as variables table
-
- pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
- names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
- pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
+ names(hfull.table) <- c('Variable', 'Original   ', 'Missing Costs   ', 
+                         "Uneven Sample   ")
+ hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                           '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
@@
   # Extract diagnostics
-  pstr.dx <- logDx(pot_glms$str, str_tdf, str_tdf$pot_pref)
-  psm.dx <- logDx(pot_glms$loc, str_tdf, str_tdf$pot_pref)
-  phost.dx <- logDx(pot_glms$host, str_tdf, str_tdf$pot_pref)
-
-  # Create diagnostic table
-  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
-                                      'AUC'),
-                           Str.Model=c('', '', round(pstr.dx$AIC,0),
-                                       round(pstr.dx$logLik, 0),
-                                       round(as.numeric(pstr.dx$auc@y.values),
-                                             3)),
-                           Sm.Model=c('', '', round(psm.dx$AIC,0),
-                                      round(psm.dx$logLik, 0),
-                                      round(as.numeric(psm.dx$auc@y.values),
-                                            3)),
-                           Host.Model=c('', '', round(phost.dx$AIC,0),
-                                        round(phost.dx$logLik, 0),
-                                        round(as.numeric(phost.dx$auc@y.values),
-                                              3)))
- ## Fix names
-
-  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
-
- # Bind together
-
- pfull.table <- rbind(pfull.table, pdiag.table)
-
-```
-
-```{r table_potlogmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
-
- # XTable
-
- px.full <- xtable(pfull.table,
-                   caption='Logistic Modeling Results (Potential Revenue)\n')
- align(px.full) <- 'lllll'
-
- # Print
- print(px.full,
-       include.rownames=FALSE,
-       hline.after=c(-1, 0, 16, 21, 21),
-       caption.placement='top')
-
-```
-
-Overall, the choice of revenue type, Likely or Potential, does affect some of the conclusions to be derived from the results above.
-As expected, under the Potential case there are more properties (36\% vs 28\%) that exhibit short-term preference.
-Under the scenario, the possibility of increasing revenue by moving from long- to short-term leasing appears much better.
-Again, however, we have not attempted to measure or estimate how this hypothetical increase of properties in the market (due to the elimation of blocked days) would impact overall market dynamics.
-Suffice it to say that it would like drive down occupancies and maybe price, therefore leading to a decrease in short-term preference likelihood.
-
-In explaining the drivers of short-term preference, the logistic regression models do not change materially with the switch in dependent variable.
-This suggests that the underlying drivers of short-term preference remain relatively constant regardless of the choice of revenue estimate.
-Only the base probability of short-term preference increases in the potential revenue case.
-
-More broadly speaking, we explain the differences between the two revenue estimates as follows:  The actual revenue case shows what is happening in the market while the potential revenue case highlights what a given property owner may be able to achieve if they are willing to open their property for short-term leasing for the entire calendar year and, ceteris paribus, the remainder of the market does not do so.
-
-#### Host Classification
-
-As hinted at above in the Likely versus Potential comparison and as indicated in the logistic regression models in Tables 2 and 4, host behavior may be an important determinant of achieving short-term preference.
-Additionally, as the difference between Likely and Potential revenue suggests, many short-term hosts are not listing their properties full-time.
-There may be, therefore, different types of hosts operating in the Airbnb market.
-From anecdotal evidence there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-
-If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked should be highly bi-modal with profit seekers on the left and opportunistic sharers on the right.
-The left hand panel of Figure 6 shows that this breakdown holds somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some (25\% to 75\%) of the time.
-
-There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property, of which Airbnb may just be one.
-A potential method to identify these hosts is to look at the number of individual periods of blocked days.
-A host using multiple platforms will likely have many small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms.
-We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 6.
-We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
-
-![Host Blocking Tendencies](C:/Code/research/airbnbMelbourne/images/block_rate.png)
-
-Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
-As a more subjective, but implementable, approach we have divided the hosts up into four categories based on the original two variables considered: block percentage and number of blocked periods.
-Profit seekers are those host who have blocked percentages less than 25\% of the time.
-Opportunistic Sharers have blocked their properties at least 75\% of the time.
-Within those two extremes, we consider users who have at least 12 blocked periods during a year to be 'Multi-Platform Users' and the remaining set to be 'Unknown'.
-Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 18\% and Multi-Platform Users 10\%.
-The remainder 'Unknown' category contains just over 28\% of all properties.
-See Figures 7 and 8 for a breakdown of these group by the two variables.
-
-![Host Categories](C:/Code/research/airbnbMelbourne/images/host_scat.png)
-
-![Host Category Counts](C:/Code/research/airbnbMelbourne/images/host_bar.png)
-
-Looking at the differences in short-term preference under both revenue cases, we see large variation in short-term preference between host types in the Likely case and a slightly smaller variation in the Potential case, as expected.
-There is little change for the 'Profit Seekers' as most of these hosts are already operating with few blocked days.
-For the other three sets, considerable gains could be had with a more aggresive leasing approach.
-As the potential figures are somewhat similar here, we will only examine the differences for host types in the Likely number going forward.
-
-```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}
-
- # Make Basic comparison table
-  apref.table <- abbCreateCompTable(ic.df=str_tdf,
-                                    split.field='host_type')
-
- # Limit to the extrapolated pref type
-  hpref.table <- apref.table[apref.table$rev.type == 'Likely', ]
-  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
-  hpref.table <- hpref.table[,1:2]
-  hpref.table[,3] <- phpref.table[,2]
-  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
-  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
-
-  names(hpref.table) <- c('Host Type', 'STP (Likely)', 'STP (Potential)')
-  options(xtable.comment = FALSE)
-  print(xtable(hpref.table,
-               caption='Host Type Preferability\n',
-               digits=1,
-               align='llrr'),
-               include.rownames=FALSE,
-               caption.placement='top')
-
-```
-
-Table 6 compares logistic models results from three of the host types.
-The Opportunistic Sharers show very few instances of short-term preference and therefore could not be estimated.
-The left hand column, that of the Profit-Seekers, is the most representative of a sample of property owners that are seeking to maximize revenue.
-Overall, the coefficients from this sub-sample match up well to the results from the entire sample shown in Table 4.
-In short, the conclusions are the same: small apartments in the central city with short minimal stays, inflexible cancelation policies and a high guest limit offer the highest probability of short-term preference.
-The models for the Multi-Platform users (middle panel) and the Unknowns (right) are not as clear as the Profit-Seekers but do suggest overall similar dynamics.
-
-```{r host_logmodel, echo=FALSE, message=FALSE, comment=FALSE}
-
- ## Extract coefficients
-
-  h1 <- as.data.frame(summary(pot_ht_glms[[1]])$coefficients)
-  h2 <- as.data.frame(summary(pot_ht_glms[[3]])$coefficients)
-  h3 <- as.data.frame(summary(pot_ht_glms[[4]])$coefficients)
-
- ## Build significance stars
-
-   h1sig <- makeStatSig(h1[ ,4])
-   h2sig <- makeStatSig(h2[ ,4])
-   h3sig <- makeStatSig(h3[ ,4])
-
- ## Create Table coefficients
-
-   h1$table.coef <- paste0(ifelse(h1$Estimate>0, ' ', ''),
-                         sprintf('%.3f', round(h1$Estimate,3)),
-                         h1sig)
-   h2$table.coef <- paste0(ifelse(h2$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(h2$Estimate,3)),
-                         h2sig)
-   h3$table.coef <- paste0(ifelse(h3$Estimate>0, ' ', ''),
-                         sprintf('%.3f',round(h3$Estimate,3)),
-                         h3sig)
-
- ## Convert to variable table
-
- hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef,
-                                    h2$table.coef, h3$table.coef))
- names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
- hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
-                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
-                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
-                          'City (Submarket)',
-                          'Suburban (Submarket)', 'Rural (Submarket)',
-                          'Beach (Submarket)', 'Guests per Bedroom',
-                          'Minimum Stay', 'Flexible Cancel')
-
- ## Create model diagnostics
-
-  # Extract diagnostics
-  hstr.dx <- logDx(pot_ht_glms[[1]], str_tdf, str_tdf$pot_pref)
-  hsm.dx <- logDx(pot_ht_glms[[3]], str_tdf, str_tdf$pot_pref)
-  hhost.dx <- logDx(pot_ht_glms[[4]], str_tdf, str_tdf$pot_pref)
+  h0.dx <- logDx(pot_glms[[3]], str_tdf, str_tdf$pot_pref)
+  h1.dx <- logDx(pot_mc_glms[[3]], str_tdf, str_tdf$pot_pref_mc)
+  h2.dx <- logDx(pot_us_glms[[3]], str_tdf, str_tdf$pot_pref_us)
 
@@
                                       'AUC'),
-                           Str.Model=c('', '', round(hstr.dx$AIC,0),
-                                       round(hstr.dx$logLik, 0),
-                                       round(as.numeric(hstr.dx$auc@y.values),
+                            og=c('', '', round(h0.dx$AIC,0),
+                                       round(h0.dx$logLik, 0),
+                                       round(as.numeric(h0.dx$auc@y.values),
                                              3)),
-                           Sm.Model=c('', '', round(hsm.dx$AIC,0),
-                                      round(hsm.dx$logLik, 0),
-                                      round(as.numeric(hsm.dx$auc@y.values), 3)),
-                           Host.Model=c('', '', round(hhost.dx$AIC,0),
-                                        round(hhost.dx$logLik, 0),
-                                        round(as.numeric(hhost.dx$auc@y.values),
-                                              3)))
-  names(hdiag.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
+                            mc=c('', '', round(h1.dx$AIC,0),
+                                       round(h1.dx$logLik, 0),
+                                       round(as.numeric(h1.dx$auc@y.values),
+                                             3)),
+                           us=c('', '', round(h2.dx$AIC,0),
+                                      round(h2.dx$logLik, 0),
+                                      round(as.numeric(h2.dx$auc@y.values), 3)))
+  names(hdiag.table) <- names(hfull.table)
 
@@
 However, of this total only 7,400 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
-Of these, only 5,925 are common bed/bath configurations with non-outlying rates and were booked for at least one night over the period of study.
+Of these, only 2,415 are common bed/bath configurations with non-outlying rates and were offered for short term lease at least 75% of the year.
 Overall, the Airbnb market is very small relative to the long-term market.
@@
 
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (Figure 5).
-However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
-This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figures 2 and 3).
-Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, similar to those from Profit Seeking short term rentals, however, the long-term revenues are much less variable (Figure 7).
+The long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
+This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figures 4 and 5).
+Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations.
 
-In comparing the short-term observations with estimated long-term rents we found that approximately one in four Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
-As expected, this probability is not equal across space, property type or property size (bed and bath count).
+In comparing the short-term observations with estimated long-term rents we found that just over half of our selected Airbnb properties brought in more revenue with its short-term leasing strategy than it would have with a long-term approach.
+As expected, this probability is not equal across space or property type.
 Apartments are much more likely than houses to be more profitable as a short-term rental.
-Core city properties are more likely than other properties to prefer a short-term strategy, as are smaller properties versus larger ones.
-For instance, 35\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 12\% of suburban houses did.
-Looking at potential revenues -- through eliminating the impact of blocked days -- increases the overall likelihood of short-term preference from 28% to 36%.
+Core city properties are more likely than other properties to prefer a short-term strategy.
+For instance, 65\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 23\% of suburban houses did.
 
-The logistic regression models (Table 2, 4 and 6) than we estimate show that most of the findings from the univariate analyses done earlier are validated.
+The logistic regression models (Tables 2 and 3) that we estimate show that most of the findings from the univariate analyses done earlier are validated.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
@@
 
-Testing for the sensitivity of the initial results through consideration of potential revenue figures and by dividing the sample up by likely host motivation, we find the qualitative finding to be generally robust.
-While the use of potential revenue does increase the base probability of short-term preference, the same factors -- small inner city apartments with low minimum stays, strict cancellation and liberal guest capacity -- explain a higher likelihood of short-term preference.
+Testing for the sensitivity of the initial results through changes two of our core assumptions -- short term leasing costs and sample similarity between LTR and STR properties -- we find the qualitative finding to be generally robust.
+While the base probability of short-term preference change with changing assumptions (as expected), the sign and magnitudes of the co-variates remains relatively robust to changes in key assumption.
 
-In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.
-If owners all operated as profit maximizers this figure could be 36\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
+In short, about 56\% of profit-seeking Airbnb properties in our study area are outperforming their potential in the long-term market.
+Performance varies widely based on location, structure type and the short term leasing policies employed by the hosts.
 
@@
 It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.co.
-
-Additionally, we have opted to make comparisons between short- and long-term strategies by imputing long-term rents for short-term properties with a hedonic price model.
-Alternatively, a matching procedure could be employed that would match like properties between the two markets and use comparisons between the two as evidence of potential short and long-term revenues.
 
@@
 
-<!--  -->
-
 ### Acknowledgements
@@
 The authors would like to thank the Real Estate Research Institute (RERI) for funding this work and the Australian Property Monitors (APM) for providing the long-term rental data.
+We'd also like to thank an anonymous reviewer for suggesting the matched pairs approach as a check on our hedonic model.
 

### 2018-11-04 scripts/3_data_prep.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

@@
     st_transform(crs=4283)
-  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach.shp')) %>%
+  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach_no_outer.shp')) %>%
     st_transform(crs=4283)
@@
   clean_obj <- countCleaning(clean_obj, 'listing_type')
+
+```
+
+### Host types
+
+Finally, we test to see if grouping by hosts types has any impact.
+
+First we must divide hosts up.  We start by looking at block rate.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(str_tdf, aes(x=block_rate)) + 
+    geom_density(fill=str_col, color=str_col) +
+    ylab('Frequency\n') + 
+    xlab('\n% of Time Property is Blocked') +
+    scale_x_continuous(breaks=seq(0,1,.2),
+                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+      ggtitle('Host Block Rate Frequency\n') +
+      theme(plot.title = element_text(hjust = 0.5)) +
+      theme(axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+
+```
+
+We then add the number of blocked periods
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
+    geom_point(fill=str_col, color=str_col, size=.2) +
+    ylab('Nbr of Blocked Periods\n') + 
+    xlab('\n% of Time Property is Blocked') +
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+    theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+No real pattern emerges, so we divide manually.
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+
+  str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1)
+
+  str_tdf$host_type <- 'Unknown'
+  #str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
+  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
+  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
+  # str_tdf$host_type <- factor(str_tdf$host_type,
+  #                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
+  #                                       'Multi-Platform User', 'Unknown'))
+  str_tdf$host_type <- factor(str_tdf$host_type,
+                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
+                                       'Unknown'))
+
+ ggplot(str_tdf, 
+       aes(x=block_rate, y=blockpertime, color=host_type)) + 
+  geom_point(alpha=.5, size=.8, shape=16) +
+  ylab('Number of Blocked Periods\n') + 
+  xlab('\n% of Time Property is Blocked') +
+      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+
+    scale_x_continuous(breaks=seq(0, 1, .2),
+                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7])) + 
+    theme(legend.position='bottom',
+           legend.title = element_blank(),
+         plot.title = element_text(hjust = 0.5))+
+     guides(colour = guide_legend(override.aes = list(size=3,
+                                                     alpha=1)))
+
+ str_tdf_all <- str_tdf
+ str_tdf <- str_tdf %>% dplyr::filter(host_type == 'Profit Seeker')
 
@@
                                     geometry)) %>%
-   dplyr::filter(!is.na(sub_des))
+   dplyr::filter(!is.na(sub_des) & sub_des != 'Outer')
 
@@
                                      geometry)) %>%
-   dplyr::filter(!is.na(sub_des))
+   dplyr::filter(!is.na(sub_des) & sub_des != 'Outer')
 
@@
    # Add individual classes
-   str_sf$geo_mrkt <- 'rural'
-   str_sf$geo_mrkt[str_sf$sub_des == 'Middle'] <- 'suburban'
+   str_sf$geo_mrkt <- 'suburban'
    str_sf$geo_mrkt[str_sf$sub_des == 'Inner'] <- 'city'
@@
    str_sf$geo_mrkt <- factor(str_sf$geo_mrkt,
-                               levels=c('city-core', 'city', 'suburban',
-                                        'rural', 'beach'))
+                               levels=c('city-core', 'city', 'suburban', 'beach'))
 
@@
    # Add individual classes
-   ltr_sf$geo_mrkt <- 'rural'
-   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Middle'] <- 'suburban'
+   ltr_sf$geo_mrkt <- 'suburban'
    ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Inner'] <- 'city'
@@
    ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
-                               levels=c('city-core', 'city', 'suburban',
-                                        'rural', 'beach'))
+                               levels=c('city-core', 'city', 'suburban', 'beach'))
 
@@
 
-Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties,
-
-```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
-
-  # Calculate likely revenue
-  str_tdf$lik_revenue_net <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
-                                (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))
-
-```
+<!-- Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties, -->
+
+<!-- ```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
+
+<!--   # Calculate likely revenue -->
+<!--   str_tdf$lik_revenue_net <- ((str_tdf$lik_bookings * str_tdf$med_rate) - -->
+<!--                                 (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd)) -->
+
+<!-- ``` -->
 
@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        col_df, clean_obj, core_suburbs,
+        col_df, clean_obj, core_suburbs, str_tdf_all,
         file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

### 2018-11-04 scripts/4_data_analysis.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

--- 2018-05-30 scripts/4_data_analysis.Rmd
@@
 
+  kimp_df <- knnImputeWrap(ltr_df = ltr_df, 
+                           str_df = str_tdf,
+                           knns = c(7,7))
+
+  imp_df$ltr_imp_revenueK <- kimp_df$year[match(imp_df$property_id,
+                                               kimp_df$property_id)]
+  imp_df <- imp_df %>%
+    rename(ltr_imp_revenueH = ltr_imp_revenue) %>%
+    mutate(ltr_imp_revenueK = ((365-imp_dom)/365) * ltr_imp_revenueK,
+           ltr_imp_revenue = .5 * (ltr_imp_revenueH + ltr_imp_revenueK))
+  imp_df <- imp_df %>%
+    left_join(str_tdf %>%
+                dplyr::select(property_id, bedrooms, bathrooms, type, latitude,
+                              longitude),
+              by='property_id')
+
+    save(imp_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))
+
 ```
@@
   str_tdf <- str_tdf %>%
-    dplyr::left_join(imp_df, by='property_id') %>%
+    dplyr::left_join(imp_df %>%
+                       dplyr::select(-c(bedrooms, bathrooms, type, latitude, longitude)),
+                     by='property_id') %>%
     dplyr::mutate(act_pref = ifelse(revenue_net > ltr_imp_revenue, 1, 0),
-                  lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
-                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0))
+                  # lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
+                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0),
+                  pot_pref_mc = ifelse(pot_revenue_net * .85 > ltr_imp_revenue, 1, 0),
+                  pot_pref_us = ifelse(pot_revenue_net > ltr_imp_revenue * .85, 1, 0))
 
@@
 
-  glm_lik_str <- glm(lik_pref ~ type + as.factor(bedbath),
+  glm_pot_str <- glm(pot_pref~type+as.factor(bedbath),
+                       family=binomial(link='logit'),
+                       data=str_tdf)
+  glm_pot_str_mc <- glm(pot_pref_mc~type+as.factor(bedbath),
+                       family=binomial(link='logit'),
+                       data=str_tdf)
+  glm_pot_str_us <- glm(pot_pref_us~type+as.factor(bedbath),
                        family=binomial(link='logit'),
@@
 
-  glm_pot_str <- glm(pot_pref~type+as.factor(bedbath),
-                       family=binomial(link='logit'),
-                       data=str_tdf)
 ```
@@
 
-  glm_lik_loc <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt),
+  glm_pot_loc <- glm(pot_pref ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                      family=binomial(link='logit'),
                      data=str_tdf)
-
-  glm_pot_loc <- glm(pot_pref ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
+  glm_pot_loc_mc <- glm(pot_pref_mc ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
+                     family=binomial(link='logit'),
+                     data=str_tdf)
+  glm_pot_loc_us <- glm(pot_pref_us ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                      family=binomial(link='logit'),
@@
 
-  glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                        guest_per_bed + min_stay + I(canc_policy == 'Flexible'),
-                      family=binomial(link='logit'),
-                      data=str_tdf)
-
   glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
@@
                       data=str_tdf)
-
-  lik_glms <- list(str=glm_lik_str,
-                   loc=glm_lik_loc,
-                   host=glm_lik_host)
+  glm_pot_host_mc <- glm(pot_pref_mc ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_tdf)
+  glm_pot_host_us <- glm(pot_pref_us ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_tdf)
 
@@
                    host=glm_pot_host)
+  pot_mc_glms <- list(str=glm_pot_str_mc,
+                   loc=glm_pot_loc_mc,
+                   host=glm_pot_host_mc)
+  pot_us_glms <- list(str=glm_pot_str_us,
+                   loc=glm_pot_loc_us,
+                   host=glm_pot_host_us)
 
@@
 
-### Host types
+<!-- ### Host types -->
 
-Finally, we test to see if grouping by hosts types has any impact.
+<!-- Finally, we test to see if grouping by hosts types has any impact.   -->
 
-First we must divide hosts up.  We start by looking at block rate.
+<!-- First we must divide hosts up.  We start by looking at block rate.   -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  ggplot(str_tdf, aes(x=block_rate)) + 
-    geom_density(fill=str_col, color=str_col) +
-    ylab('Frequency\n') + 
-    xlab('\n% of Time Property is Blocked') +
-    scale_x_continuous(breaks=seq(0,1,.2),
-                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-      ggtitle('Host Block Rate Frequency\n') +
-      theme(plot.title = element_text(hjust = 0.5)) +
-      theme(axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
+<!--   ggplot(str_tdf, aes(x=block_rate)) +  -->
+<!--     geom_density(fill=str_col, color=str_col) + -->
+<!--     ylab('Frequency\n') +  -->
+<!--     xlab('\n% of Time Property is Blocked') + -->
+<!--     scale_x_continuous(breaks=seq(0,1,.2), -->
+<!--                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
+<!--       ggtitle('Host Block Rate Frequency\n') + -->
+<!--       theme(plot.title = element_text(hjust = 0.5)) + -->
+<!--       theme(axis.text.y=element_blank(), -->
+<!--           axis.ticks.y=element_blank()) -->
 
-```
+<!-- ``` -->
 
-We then add the number of blocked periods
+<!-- We then add the number of blocked periods -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
-    geom_point(fill=str_col, color=str_col, size=.2) +
-    ylab('Nbr of Blocked Periods\n') + 
-    xlab('\n% of Time Property is Blocked') +
-    scale_x_continuous(breaks=seq(0, 1, .2),
-                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
+<!--   ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +  -->
+<!--     geom_point(fill=str_col, color=str_col, size=.2) + -->
+<!--     ylab('Nbr of Blocked Periods\n') +  -->
+<!--     xlab('\n% of Time Property is Blocked') + -->
+<!--     scale_x_continuous(breaks=seq(0, 1, .2), -->
+<!--                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
+<!--     ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->
+<!--     theme(plot.title = element_text(hjust = 0.5))  -->
 
-```
+<!-- ``` -->
 
-No real pattern emerges, so we divide manually.
+<!-- No real pattern emerges, so we divide manually.  -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1)
+<!--   str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1) -->
 
-  str_tdf$host_type <- 'Unknown'
-  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
-  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
-  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
-  str_tdf$host_type <- factor(str_tdf$host_type,
-                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
-                                        'Multi-Platform User', 'Unknown'))
+<!--   str_tdf$host_type <- 'Unknown' -->
+<!--   str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User' -->
+<!--   str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker' -->
+<!--   str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer' -->
+<!--   str_tdf$host_type <- factor(str_tdf$host_type, -->
+<!--                               levels=c('Profit Seeker', 'Opportunistic Sharer',  -->
+<!--                                         'Multi-Platform User', 'Unknown')) -->
 
- ggplot(str_tdf, 
-       aes(x=block_rate, y=blockpertime, color=host_type)) + 
-  geom_point(alpha=.5, size=.8, shape=16) +
-  ylab('Number of Blocked Periods\n') + 
-  xlab('\n% of Time Property is Blocked') +
-      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
+<!--  ggplot(str_tdf,  -->
+<!--        aes(x=block_rate, y=blockpertime, color=host_type)) +  -->
+<!--   geom_point(alpha=.5, size=.8, shape=16) + -->
+<!--   ylab('Number of Blocked Periods\n') +  -->
+<!--   xlab('\n% of Time Property is Blocked') + -->
+<!--       ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->
 
-    scale_x_continuous(breaks=seq(0, 1, .2),
-                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
-    scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
-                                col_df$rgb[9])) + 
-    theme(legend.position='bottom',
-           legend.title = element_blank(),
-         plot.title = element_text(hjust = 0.5))+
-     guides(colour = guide_legend(override.aes = list(size=3,
-                                                     alpha=1)))
+<!--     scale_x_continuous(breaks=seq(0, 1, .2), -->
+<!--                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
+<!--     scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7],  -->
+<!--                                 col_df$rgb[9])) +  -->
+<!--     theme(legend.position='bottom', -->
+<!--            legend.title = element_blank(), -->
+<!--          plot.title = element_text(hjust = 0.5))+ -->
+<!--      guides(colour = guide_legend(override.aes = list(size=3, -->
+<!--                                                      alpha=1))) -->
 
-```
+<!-- ``` -->
 
-And re-run the logistic regression models.
+<!-- And re-run the logistic regression models.  -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->
 
-  ht_. <- split(str_tdf, str_tdf$host_type)
+<!--   ht_. <- split(str_tdf, str_tdf$host_type) -->
 
-  lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))
+<!--   lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) + -->
+<!--                           guest_per_bed + min_stay + I(canc_policy == 'Flexible')) -->
 
-  pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
-                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))
+<!--   pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) + -->
+<!--                           guest_per_bed + min_stay + I(canc_policy == 'Flexible')) -->
 
-  lik_ht_glms <- purrr::map(ht_.,
-                         .f=glm,
-                         formula=lik_spec,
-                         family=binomial(link='logit'))
+<!--   lik_ht_glms <- purrr::map(ht_., -->
+<!--                          .f=glm, -->
+<!--                          formula=lik_spec, -->
+<!--                          family=binomial(link='logit')) -->
 
-  pot_ht_glms <- purrr::map(ht_.,
-                         .f=glm,
-                         formula=pot_spec,
-                         family=binomial(link='logit'))
+<!--   pot_ht_glms <- purrr::map(ht_., -->
+<!--                          .f=glm, -->
+<!--                          formula=pot_spec, -->
+<!--                          family=binomial(link='logit')) -->
 
-```
+<!-- ``` -->
 
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
 
@@
   save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
-       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
+       pot_glms, core_suburbs, str_tdf_all, pot_mc_glms, pot_us_glms,
+       #pot_ht_glms, lik_ht_glms,
        file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))
 
+  save(ltr_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))
+
 ```

### 2018-11-04 scripts/5_data_viz.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

@@
    rev_df <- bind_rows(str_tdf %>% 
-                         dplyr::select(type, revenue=lik_revenue_net) %>%
-                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
+                         dplyr::select(type, revenue=revenue_net) %>%
+                         dplyr::mutate(tenure = '  Short Term (Actual)   ',
                                        alpha = .5),
@@
                          dplyr::select(type, revenue=pot_revenue_net) %>%
-                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
+                         dplyr::mutate(tenure = '  Short Term (Potential)   ',
                                        alpha = .4),
@@
                          dplyr::select(type, revenue=gross_revenue) %>%
-                         dplyr::mutate(tenure = 'Long-Term   ',
+                         dplyr::mutate(tenure = '  Long-Term   ',
                                        alpha = .9))
@@
 
-  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
+  host.block.freq <- ggplot(str_tdf_all, aes(x=block_rate)) +
      geom_density(fill=str.col, color=str.col) +
@@
 
-  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +
+  block.rate.period <- ggplot(str_tdf_all, aes(x=block_rate, y=nbr_block * (366/total_days))) +
     geom_point(fill=str.col, color=str.col, size=.2) +
@@
 
-  base.host <- ggplot(str_tdf,
+  base.host <- ggplot(str_tdf_all,
                     aes(x=block_rate, y=blockpertime)) +
@@
    ps.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
+    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Profit Seeker', ], size=.4)  +
     ggtitle('Profit Seekers')
@@
   os.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
+    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Opportunistic Sharer', ],
                size=.4)  +
@@
 
-  mu.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
-               size=.4)  +
-    ggtitle('Multi-Platform User')
+  # mu.host <- base.host +
+  #   geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Multi-Platform User', ],
+  #              size=.4)  +
+  #   ggtitle('Multi-Platform User')
 
   un.host <- base.host +
-    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
+    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Unknown', ], size=.4)  +
     ggtitle('Unknown')
@@
   png(filename = file.path(getwd(), 'images', "host_scat.png"), 
-       width = 5.5, height = 3, units = 'in', res = 300)
+       width = 4, height = 6.5, units = 'in', res = 300)
 
-    ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)
+    ggMultiPlots(ps.host, un.host, os.host, cols=1)
 
@@
 
- ggplot(str_tdf, aes(host_type, fill=host_type)) +
+ ggplot(str_tdf_all, aes(host_type, fill=host_type)) +
     geom_bar() +
-    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
-                               col_df$rgb[9]))+
+    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[9]))+
     theme(legend.position='none') +
@@
     xlab('\nHost Type') +
-    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
+    scale_x_discrete(labels=c('Profit-Seekers','Opportunistic Sharers','Unknowns'))+
     #ggtitle('short-term Host Types') +

### 2018-11-04 functions/abb_Functions.R

@@ -479,7 +479,11 @@ knnImputeWrap <- function(ltr_df,
   }
   
   x <- tidyr::spread(k_ %>% bind_rows(), k, weekly_rent)
-  x$mean <- rowMeans(x[,grepl('k_', names(x))])
+  if (length(unique(knns)) > 1){
+   x$mean <- rowMeans(x[,grepl('k_', names(x))])
+  } else {
+    x$mean <- x[,grepl('k_', names(x))]
+  }
   x$year <- x$mean * 52
   x
 }

### 2018-11-06 papers/full_paper.Rmd
Revision 2, edits.

@@
 
-The growth of Airbnb and other short-term rental platforms have presented absentee owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
+The growth of Airbnb and other short-term rental platforms have presented absentee owners of urban residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").
 In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
@@
 
-With the rise of Airbnb and other self-hosting accommodation platforms^[Flipkey.com, VRBO.com, Homeaway.com, Tripping.com, Stayz.com.au as examples.], it is easier than ever for property owners and investors to consider short-term rental (STR) as a potential leasing strategy for a revenue generating residential property.
+With the rise of Airbnb and other self-hosting accommodation platforms^[Flipkey.com, VRBO.com, Homeaway.com, Tripping.com, Stayz.com.au as examples.], it is easier than ever for property owners and investors to consider short-term rental (STR) as a potential leasing strategy for a revenue generating urban residential property.
 Should they though?
@@
 Are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
-Do host policies matter?
+And, finally, do host policies matter?
 
-To address these questions and to provide some guidance to potential and current investors and owners, we examine the short- and long-term residential rental markets in Melbourne, Australia.
+To address these questions and to provide some guidance to potential and current investors and owners, we examine the short- and long-term urban residential rental markets in Melbourne, Australia.
 Melbourne has a thriving short-term rental market with over 20,000 total properties listed on the Airbnb portal, the source of our short-term market data.
@@
 Additionally, for any individual property the choice between short and long term leasing may be influenced by individual financial situations (tax and mortgage financing) as well as non-financial concerns such as time availability and personal attachement to the property.
-While we analyze individual properties, we acknowledge that there are many unobserved condiseration and, therefore, we generalize our findings to market segments, locations and host policy decisions.
+While we analyze individual properties, we acknowledge that there are many unobserved considerations and, therefore, we generalize our findings to market segments, locations and host policy decisions.
 
@@
 Our results show that the feasibility of a greater revenues through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
-In short, the answer to whether or not a owner or investor should opt for a short-term leasing strategy is ''it depends''.
+In short, the answer to whether or not a owner or investor of an urban residential property should opt for a short-term leasing strategy is ''it depends''.
 
@@
 
-Much of the existing work focuses on price or rent formation in second home markets.
+Much of the existing work focuses on price or rent formation in amenity-driven second home markets.
 Specifically, the impacts of amenities such as water access [@nelson2010valuing], water quality [@gibbs2002hedonic; @clapper2014water], proximity to ski facilities  [@soguel2008impact; @nelson2010valuing] and theme parks [@tsai2015impact] are shown to positively impact sales prices in tourism-dominated areas.
@@
 As a result, the short-term rental market has garnered significant interest in the public policy and legal sphere as of late.
-As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on immediate neighbors in the way of externalies such as noise and congestion [@frost2006commentary].
+As many urban residential properties are not permitted for or regulated as commercial entities, STRs can have serious effects on immediate neighbors in the way of externalies such as noise and congestion [@frost2006commentary].
 While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].
@@
 
-We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of a residential investment property.
+We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of an urban residential investment property.
 More specifically, we examine the following case:
 
-* An investor purchases a property in Melbourne, Australia on September 1, 2015.
+* An investor purchases a property in the urbanized area of Melbourne, Australia on September 1, 2015.
 * They are looking to maximize the net revenue over the 12-month period from September 1, 2015 to August 31, 2016.
 * They do not intend to inhabit the home themselves. 
-* The choices are 1) traditional year long rental (long-term), or: 2) short-term, nightly Airbnb-type rental.
+* The choices are 1) traditional year-long rental (long-term), or: 2) short-term, nightly Airbnb-type rental.
 * Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored as these concerns are influenced by owner situations, not property characteristics or hosting policies.
-* As most long-term rentals in Melbourne use a leasing agency, we will assume use of an agency.
+* As most long-term rentals in Melbourne use a leasing agency, we assume use of an agency.
 
@@
 While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
-As we do not have access to this information in the marketplace, we will not be considering any effects of this policy in our analysis here.
+As we do not have access to this information in the marketplace, we will not be considering any effects of this policy in this analysis.
 
@@
 Most specifically, we will estimate the long-term revenue for observations of properties currently listed on a short-term rental portal (Airbnb).
-Initially, we attempted to also estimate short-term rental revenue for long-term rental properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
+Initially, we also attempted to estimate short-term rental revenue for long-term rental properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
 
@@
 For a short-term leasing strategy, these costs can be experienced every day or two, depending on the minimum length of stay and the total number of occupancies over the course of the year.
-Our data for short-term rentals comes from the Airbnb platform.
-On Airbnb, in addition to the nightly rate that an occupant pays to the owner there is also a separate 'cleaning fee' that is attached, as is a booking fee to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
+The Airbnb platform serves as the source of our short-term rentals data.
+On Airbnb, in addition to the nightly rate that an occupant pays to the owner, there is also a separate 'cleaning fee' that is attached, as is a booking fee payable to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
@@
 Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period.^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
-The nightly data indicate the advertised price, the occupancy status and a unique reservation identification.
+The nightly data indicate the advertised price, the occupancy status and a unique reservation identifier.
 
@@
 As long-term rentals do not offer Private Room or Shared Room options^[Our long-term rental dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term revenues, we remove all short-term properties that do not lease the entire home or apartment.
-Unfortunately, this filter does remove about 46% of the short-term data, however, given the research question it is unavoidable.
+Unfortunately, this filter removes about 46% of the short-term data, however, given the research question it is unavoidable.
 
@@
 Both anecdotal evidence and Airbnb's own marketing campaigns suggest that there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-For the purposes of this research we are focused on Profit Seekers; those owner who would be faced with deciding between a long- and short-term leasing strategy.
+For the purposes of this research we are focused on Profit Seekers; those owners who would be faced with deciding between a long- and short-term leasing strategy.
 
@@
 Attempts to divide the hosts up with unsupervised^[As there are no official host types we could not run more reliable supervised models.] clustering algorithms -- including the use of more variables -- failed to produce robust categories of hosts.
-As a more subjective, but implementable, approach we have divided the hosts up into three categories based on the original two variables considered: block percentage and number of blocked periods.
-Profit Seekers are those host who have blocked percentages less than 25\% of the time.
+As a more subjective, but implementable, approach we have divided the hosts up into three categories based on the block rate alone.
+Profit Seekers are those hosts who have blocked percentages of less than 25\%.
 Opportunistic Sharers have blocked their properties at least 75\% of the time.
-Within those two extremes, we consider users we consider as Unknown as they may be multiple plaform users (who are profit seeking), very opportunistic sharers or driven by some other, unknown motivation.
-Profit Seekers make up 43\% of the hosts, with Opportunistic Sharers capturing 19\% and the remainder 'Unknown' category contains just over 38\% of all properties.
+Within those two extremes, we consider users as "Unknown" as they may be multiple plaform users (who are profit seeking), very opportunistic sharers or driven by some other, unknown motivation.
+Profit Seekers make up 41\% of the hosts, with Opportunistic Sharers capturing 23\% and the remainder 'Unknown' category contains just over 36\% of all properties.
 To best approximate the scenario considered in our research question, we keep only the Profit Seekers in our dataset.
@@
 
-Using the two remaining broad submarkets (Inner and Middle) we have created a four sub-market system as a starting point for spatially analyzing short and long-term rentals in Melbourne:
+Using the two remaining broad submarkets (Inner and Middle) we have created a four sub-market system as a starting point for spatially analyzing short and long-term urban rentals in Melbourne:
 
@@
 The boundary of the suburbs meeting these criteria compose our study area (Figure 3).
-The location of the short- and long-term rentals, colored by submarket, are shown in Figures 4 and 5.
+The location of the short- and long-term rentals, colored by submarket, are shown in Figure 4.
+It should be noted that the beach areas in our study are densely developed and represently, generally speaking, higher end residential suburbs, not vacation-based communities (as one might find much farther down the coast).
 
@@
 
-![Short Term Observations](C:/Code/research/airbnbMelbourne/images/str_loc_map.png)
+<!-- ![Short Term Observations](C:/Code/research/airbnbMelbourne/images/str_loc_map.png) -->
 
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (Figure 4).
+A number of interesting observations are illustrated here (Figure 5).
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
@@
 Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
-Beach properties are, relatively speaking, over-represented in the short-term market, especially in apartments, while suburban apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
+Suburban apartments, somewhat common in long-term markets, are nearly absent in the short-term market.
 Overall, the suburban Airbnb market is somewhat thin, later results focusing on these markets will need to be examined in light of this small sample size.
@@
 And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.
-In short, in either case, the actual observed short-term revenue would be biased on the low end compared to what a revenue maximizing owner would be likely able to accomplish.
+In short, in either case the actual observed short-term revenue would be biased on the low end compared to what a revenue maximizing owner would be likely able to accomplish.
 
@@
 Potential ($REV_p$)}: Observed bookings extrapolated to a full year plus imputed bookings during observed blocked days.
-Our attempt here is to represent the potential revenue if the property had been listed all year long.
-The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance and then applying that relative ratio to the overall market performance on the extrapolated and blocked days.
+Our attempt here is to represent the potential revenue if the property had been listed on Airbnb all year long.
+The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance on those days and then applying that relative ratio to the overall market performance on the extrapolated and blocked days.
 
 As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Potential' revenue metric to be a better estimate of market performance.
-We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 7).
+We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 6).
 Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.
-Actual short-term revenues range from neglible to highs of greater than \$60,000, with many of the properties showing very limited (less than \$10,000) revenue.
+Actual short-term revenues range from neglible to highs of greater than \$60,000, with a collection of the properties showing very limited (less than \$10,000) revenue.
 The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is shifted slightly to the right due to our time extrapolation and blocked days imputation.
 
-While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.
+While this simple analysis does not control for location and product differences, it does highlight the fact that some profit seeking Airbnb owners are likely making greater revenues than in long-term rentals, but that many are not.
 The high number of very low yield Airbnb properties suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
@@
 For example, all 2-bed, 2-bath apartments are grouped.
-For each short-term rental in this group we find the nearest 7 comparables (geographically), many of which are in the same building.
+For each short-term rental in this group we find the nearest 7 long-term rental comparables (geographically), many of which are in the same building.
 We compute the median of these seven comparables as our matched pairs estimation.
@@
 We then average the hedonic model and matched pairs prediction for each short term property to create an estimate of its long-term rental rate.
+As a validation check, we find some variation between the predictions from the two models for specific properties, however, the overall correlation between the two estimates is 97.6%.
 
@@
 
-Overall, 57.3%^[If we just look at actual revenue, ignoring blocked days and properties with less than a full 12 months of listing, the figure is 42.5%] of the 2,415 short-term rental properties in our sample were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
+Overall, 57.3%^[If we just look at actual revenue, ignoring blocked days and properties with less than a full 12 months of listing, the figure is 42.5%] of the 2,415 short-term urban rental properties in our sample were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
 While illustrative, a simple univariate analysis does not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
@@
 We specify three, increasingly complex, logistic regression models.
-We use the likely revenue (not potential) as the dependent variable here, saving an anaylsis of potential revenue for the subsequent sensitivity tests.
 
@@
 
-For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
+For Model 2 we add the four geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.
 
@@
 We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.
-We have grouped the cancellation policies into Flexible (24 hour notice), and Strict (those requiring 5 or more days notice, often with less than 100% refunds).
+We have grouped the cancellation policies into Flexible (24 hour notice), and Strict (those requiring five or more days notice, often with less than 100% refunds).
 
@@
 In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
-Additionally, 1 bed / 1 bath units show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
+Additionally, 1 bed / 1 bath units (reference category) show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
 This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
 Larger units, 3 bedrooms plus, generally show no statistical difference in preference porbability to the 1 bed / 1 bath reference unit.
+In other words, larger units are equally desirable to tourists and local residents alike.
 
@@
 
-Finally, in Model 3 we add in hostpolicies.
+Finally, in Model 3 we add in host policies.
 Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.
@@
 Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.
-Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a positive relationship with short-term preference.
+Finally, flexible cancellation policies result in a considerably lower probability of short-term preference.
 Strict cancellation may be a luxury available only for the best and most highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand while a flexible cancellation may be signalling the opposite.
@@
 
-To test if the above results are influence by the assumptions we have made throughout this analysis, we perform a sensitivity test.
-The most influential assumptions that we make are in regards to; 1) unobserved costs of short term leasing (furnishings, additional maintenance, turnover, etc.) and that the properties in the two markets in our datasets are equivalent in terms of unobserved variables, such as quality and condition.
-To approximate how these assumption may be influencing our results, we re-estimating our models under two new conditions:
+To test if the above results are influence by the assumptions we have made throughout this analysis, we perform two sensitivity tests.
+The most influential assumptions that we make are in regards to; 1) unobserved costs of short term leasing (furnishings, additional maintenance, turnover, etc.) and; 2) that the properties in the two markets in our datasets are equivalent in terms of unobserved variables, such as quality and condition.
+We chose these sensitivity tests so that we consider situations that each favor one of leasing strategy options.
+To approximate how these assumption may be influencing our results, we re-estimate our models under two new conditions:
 
@@
 Table 3 shows the results of our sensitivity testing, with the original model results shown for comparison.
-For the five variables with the strongest relationship in the original model -- House, City, Suburban, Guests Per Bedroom and Flexible Cancel -- the signs of the coefficient remain identical across the sensitivity tests and the variation in magnitudes are small, relatively speaking.
+For the five variables with the strongest relationship in the original model -- House, City, Suburban, Guests per Bedroom and Flexible Cancel -- the signs of the coefficient remain identical across the sensitivity tests and the variation in magnitudes are small, relatively speaking.
 A few of the originally less significant variables do show relatively larger deviations in coefficient magnitude, but in general, the models appear to be stable across the sentivity tests.
-Do note that the intercept terms does change across models, which would be expected as this represents the base probability of short-term preference which we'd expect to move in concert with our changing assumptions
+Do note that the intercept terms does change across models, which would be expected as this represents the base probability of short-term preference which we'd expect to move in concert with our changing assumptions.
 
@@
 
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, similar to those from Profit Seeking short term rentals, however, the long-term revenues are much less variable (Figure 7).
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, similar to those from Profit Seeking short term rentals, however, the long-term revenues are much less variable (Figure 6).
 The long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
-This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figures 4 and 5).
-Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations.
+This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 4).
+Simply put, short-term leasing is much more common in the central areas of the city, as would be expected.
 
@@
 Apartments are much more likely than houses to be more profitable as a short-term rental.
-Core city properties are more likely than other properties to prefer a short-term strategy.
+City-Core properties are more likely than other properties to prefer a short-term strategy.
 For instance, 65\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 23\% of suburban houses did.
 
-The logistic regression models (Tables 2 and 3) that we estimate show that most of the findings from the univariate analyses done earlier are validated.
+The logistic regression models (Tables 2 and 3) highlight which characteristics lead to increased short term preference.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
-We also test for the impact of host behavior on the probability of short-term preference.
-We find that more flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability).
+More flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability).
 As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
@@
 Testing for the sensitivity of the initial results through changes two of our core assumptions -- short term leasing costs and sample similarity between LTR and STR properties -- we find the qualitative finding to be generally robust.
-While the base probability of short-term preference change with changing assumptions (as expected), the sign and magnitudes of the co-variates remains relatively robust to changes in key assumption.
+While the base probability of short-term preference changes with changing assumptions (as expected), the sign and magnitudes of the co-variates remains relatively robust to changes in key assumptions.
 
@@
 
-Next, there are few shared property characterstics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
+Next, there are few shared property characteristics between the two datasets, which make cross-estimating rents and rates difficult, especially from the short-term market.
 Part of the difficulty in estimating potential short-term rates for existing long-term properties is that the short-term market appears to be heavily influenced by non-property specific factors such as the leasing policies (minimum stay, number of guests, etc.) themselves.
@@
 Sensitivity tests on these two costs (both of which lower STR revenues) do create decreases in the base rate of STR preference, but show little change to the coefficients across the various regression models.
-overall, there is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.
+Overall, there is limited research around STR rental hosting costs and this uncertainty around cost estimates is a limitation of our study and could prove to be an avenue of future research.
 
@@
 In reality, the possibilities may not be so rigid.
-For example, given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourists swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the off-season with short-term leasing during peak times to maximize revenues.
-In general, the rise of Airbnb and related portals give properties owners more options, and therefore more opportunities, to maximize returns on their property.
+For example, given the fact that Melbourne's large university student population (many of whom are international) require housing during Autumn, Winter and Spring, while tourists swell in the summer months, an enterprising owner maybe able to pair long-term leasing during the school year with short-term leasing during peak times to maximize revenues.
+In general, the rise of Airbnb and related portals give urban property owners more options, and therefore more opportunities, to maximize returns on their property.
 Future research should expand our scenario to look at more than just a single binary option over a fixed period.

### 2018-11-09 papers/full_paper.Rmd
Revision, Round 2, Iteration 2

@@
 ---
-title: "To Airbnb?: A look at Long vs Shorm Term Leasing"
+title: "To Airbnb?: Factors impacting short-term leasing preference"
 subtitle: "Andy Krause and Gideon Aschwanden"
@@
 
+  # library(knitr)
+  # knit_hooks$set(plot = function(x, options) {
+  # paste('<figure><figcaption>', options$fig.cap, '</figcaption><img src="',
+  #       opts_knit$get('base.url'), paste(x, collapse = '.'),
+  #       '"></figure>',
+  #       sep = '')})
+
 ```
@@
 In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
-We also find that hosting policies matter, suggesting that even the right property may need the right owner(s) or strategy to make short-term rental the more profitable approach.
+Additionally, tests on the impacts of hosting policies suggest that even the right property may need the right owner(s) or strategy to make short-term rental the more profitable approach.
 
@@
 Should they though?
-Or rather, is it more profitable to do so when compared to traditional long-term rental (LTR)?
-Are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
-And, finally, do host policies matter?
+More specifically,  are certain types of properties in specific locations more likely to show a preference for a short-term leasing strategy over long-term one?
+And, finally, do short-term hosting policies matter?
 
@@
 To avoid confounding market dynamics caused by traditional vacation rentals (beach, ski and other recreation) we limit our study area to the urbanized areas of Melbourne.
-Additionally, for any individual property the choice between short and long term leasing may be influenced by individual financial situations (tax and mortgage financing) as well as non-financial concerns such as time availability and personal attachement to the property.
+Additionally, for any individual property the choice between short and long term leasing may be influenced by individual financial situations (tax and mortgage financing) as well as non-financial concerns such as time availability and personal attachment to the property.
 While we analyze individual properties, we acknowledge that there are many unobserved considerations and, therefore, we generalize our findings to market segments, locations and host policy decisions.
@@
 
-Our results show that the feasibility of a greater revenues through a short-term rental -- what we have termed ``Short-Term Preference'' -- is dependent on property type, product, location and host policies.
-In short, the answer to whether or not a owner or investor of an urban residential property should opt for a short-term leasing strategy is ''it depends''.
+Our results show that the feasibility of a greater revenues through a short-term rental -- what we have termed ''Short-Term Preference'' -- is dependent on property type, product, location and host policies.
+In short, the answer to whether or not a owner of an urban residential property is likely to earn more through a short-term leasing strategy than a long-term one is ''it depends''.
 
@@
 Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast the STR industry lacks sophistication and efficiency.
-Most notably, they find that most nightly or weekly rates are set by resident unit managers (RUMs) and are often under-priced as there is little accountability to owners.
+Most notably, they find that most nightly or weekly rates are set by resident unit managers and are often under-priced as there is little accountability to owners.
 The authors also note that very little research has been put toward understanding this growing market segment.
@@
 A collection of recent work has looked into the impact of short-term markets on housing prices and affordability.
-These working papers examine the influence of Airbnb on existing housing prices in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2016home].
+This research examines the influence of Airbnb on existing housing prices nationally [@barron2018sharing] as well as focused work in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2017home].
 Though very broad analyses, all suggest that Airbnb has had a positive impact on local home prices and/or a negative impact on affordability.
@@
 While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].
-Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].
+Other, rights-based, regulatory approaches have been suggested [@miller2014transferable; @gurran2018urban].
 Many of the key legal decisions regarding short-term rentals, particulary through Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.
@@
 
-We approach answering the question of whether it is more profitable to pursue a short- or long-term leasing strategy by creating and assessing a scenario likely to be faced by a recent purchaser of an urban residential investment property.
-More specifically, we examine the following case:
+We approach answering the question of which property, location and hosting factors are related to Short Term Preference by gathering market evidence from both the short and long term rental markets.
+Using this market data, we compare the actual short term revenues of known Airbnb properties to their expected long-term rental revenues had they employed a long-term strategy.
+Properties whose revenues were higher with a short-term strategy are considered to have shown Short-Term Preference (STP).
+We then use this binary classification to construct statistical models aimed at assessing the impacts of property, location and hosting factors on the likelihood of Short-Term Preference.
+Our study examines the Melbourne, Australia market over the September 1, 2015 to August 31, 2016 time frame.
 
-* An investor purchases a property in the urbanized area of Melbourne, Australia on September 1, 2015.
-* They are looking to maximize the net revenue over the 12-month period from September 1, 2015 to August 31, 2016.
-* They do not intend to inhabit the home themselves. 
-* The choices are 1) traditional year-long rental (long-term), or: 2) short-term, nightly Airbnb-type rental.
-* Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored as these concerns are influenced by owner situations, not property characteristics or hosting policies.
-* As most long-term rentals in Melbourne use a leasing agency, we assume use of an agency.
+The following assumptions are made:
 
+1.
+Only direct monetary revenues and costs are considered, others such as liquidity and inconvenience are ignored as these concerns are influenced by owner situations, not property characteristics or hosting policies.
+
+2. As most long-term rentals in Melbourne use a leasing agency, we assume use of an agency.
+
+3.
 Australia implements a particular tax policy, often termed `negative gearing', that allows for an income tax deduction to real estate investors who experience greater costs than revenues on investment properties.^[See @fane2004negative for a complete explanation of negative gearing.] To date, this policy only applies to long-term rental properties.
 While this policy can influence the net revenue (post tax) of a property, the negative gearing policy requires knowledge of the investor's personal income situation.
-As we do not have access to this information in the marketplace, we will not be considering any effects of this policy in this analysis.
+As we do not have access to this information in the marketplace, any impacts from tax considerations are ignored.
 
 One benefit of a short-term rental may be the ability to adjust the nightly rate over the course of the year to reflect changing demand and market trends.
-As future market trends are unknown at the time of purchase and, within the span of 12 months, the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a fixed nightly (short-term) rate to respresent the most likely state of knowledge for our hypothetical investor on September 1, 2015.
-Both long-term rents and short-term rates will be based on the market conditions as of this date.
+As future market trends are unknown at the time of purchase and, within the span of 12 months (standard lease length), the decision of long- vs short-term leasing strategy is asymetrically irreversable (can go from short to long, but not long to short), we make our comparisons using a long term rental rate this is fixed as of September 1, 2015 but a short-term nightly rate that varies with the market over the course of the year.
 
-We do not directly observe properties that are utilized in both a short- and long-term leasing strategy.
-Therefore, comparisons are done based on estimated or imputed revenues.
-Most specifically, we will estimate the long-term revenue for observations of properties currently listed on a short-term rental portal (Airbnb).
+Unfortunately, we cannot not directly observe properties that are utilized in both a short- and long-term leasing strategy.
+Therefore, comparisons are done with actual short-term but estimated or imputed long-term revenues.
 Initially, we also attempted to estimate short-term rental revenue for long-term rental properties but found the process of imputing occupancy rates and nightly rate structures too inaccurate to provide valid comparisons.
 
-### Comparison
-
-In this scenario we compare the observed 12-month revenues from short-term rental properties with their hypothetical long-term rental revenues.
-We define revenue here as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
+For our comparisons we define (net) revenue as the gross revenue minus the direct costs associated with each of the two tenure possibilities.
 Costs which are equivalent between the two strategies are ignored.
@@
 
-As our scenario compares a hypothetical and particular owner over the course of a single year the tax $T$ and $F$ costs are identical between the two leasing strategies and therefore cancel out.
-General maintenance $M$ expenses may differ between the two strategies, and an argument could be made for either to be higher.
+As our scenario compares a hypothetical and particular owner over the course of a single year the tax, $T$, and, $F$, costs are identical between the two leasing strategies and therefore cancel out.
+General maintenance, $M$, expenses may differ between the two strategies, and an argument could be made for either to be higher.
 Long-term renters spend more time in the property over the course of the year and bring their own appliances^[White goods are usually not supplied in the Australian rental market.] and furniture which may damage the home.
 They are also more likely to affix items to the structure.
-Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is not often uncovered until after they have left.^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.]  Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short- or long-term rentals.
+Conversely, short-term rentals are usually furnished and the occupants have less incentive not to be evicted as their damage is often not uncovered until after they have left.^[Note that Airbnb's rating policy may help protect hosts as bad guests can be flagged on the platform.]  Both arguments are meritous and we were unable to find any evidence to support maintenance costs being higher in short- or long-term rentals.
 As a result we have made the assumption that the maintenance costs will be identical, and they too cancel out.
 
-Leasing costs $L$ are the fees paid to the rental agency to find and manage tenants over the life of the long-term lease.
+Leasing costs, $L$, are the fees paid to the rental agency to find and manage tenants over the life of the long-term lease.
 In Melbourne, agency rates generally range from 5\% to 7\% per annum.
@@
 The Airbnb platform serves as the source of our short-term rentals data.
-On Airbnb, in addition to the nightly rate that an occupant pays to the owner, there is also a separate 'cleaning fee' that is attached, as is a booking fee payable to Airbnb.^[This fee could be considered analogous to the leasing fees $L$ that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
+On Airbnb, in addition to the nightly rate that an occupant pays to the owner, there is also a separate 'cleaning fee' that is attached, as is a booking fee payable to Airbnb.^[This fee could be considered analogous to the leasing fees, $L$, that long-term rentals pay.] Some hosts add additional 'linen' fees to cover costs of laundering.
 While it may be advantageous for hosts in competitive markets to underquote their cleaning fees to keep occupancies up, we have no evidence to suggest that owners are exhibiting such behavior.
@@
 Throughout this analysis we will refer to any situations where the short-term net revenue exceeds the long-term net revenue as 'Short-Term Preferable' or a situation of 'Short-Term Preference' (STP).
-For the purposes of this study we consider this a binary position leading to a binary decision of which leasing strategy to follow.
+For the purposes of this study we consider this a binary position.
 
@@
 As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.^[In fact, our choice of study area was done so to specifically minimize the number of potential traditional vacation homes in our sample.] The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
-The short-term data include two types of observations, property-level and nightly-per-property.
-Property-level data consists of a single observation for each property that is or has been listed on the Airbnb portal over the October 2014 to August 2016 period.^[This time period represents the period in which AirDNA was engaged in data collection in Melbourne.]  The nightly data offer one observation for each property for each night of the year during its time on the portal.
-The nightly data indicate the advertised price, the occupancy status and a unique reservation identifier.
+The data offers both nightly observations indicating the advertised price, the occupancy status and a unique reservation identifier as well as general property and host policy information.
 
@@
 Data on the long-term rental market was provided by Australia Property Monitors (APM), a Fairfax Group company.
-In raw form this dataset includes an observation for each rental property listing for each time a detail of the listing changed.
-For example, if a property was listed for rent for one month and the price was dropped once each week there would be four observations in the dataset.
-These four observations are grouped by an event-specific identification number.
-This number is specific to the listing event, not the property.
-In each case the last observation signifies the final price of the rental contract.
-The long-term lease data cover the period from January 2014 to December 2015.
+The long-term lease contains both property specific information (beds, baths, location, etc.) as well as a history of listing prices.
+These data cover the period from January 2014 to December 2015.
 
@@
 Both sets of data do include latitude and longitude, however the accuracy of the Airbnb coordinates is suspect as these are often purposefully jittered to protect property anonymity and, as a result, in a dense urban area with many multiple-family dwellings it is impossible to match apartments based on imprecise two-dimensional coordinates.
-As a result of this, we are unable to directly match observations from the two datasets.
+As a result, we are unable to directly match observations from the two datasets.
 
@@
 We begin by filtering observations by time.
-Our hypothetical leasing strategy decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long-term rental versus an Airbnb-type, short-term rental approach to generating income.
-To determine the likely LTR nightly rate for any given property we use the observed rental transactions from September 1, 2014 to August 31, 2015.
-Taking the Airbnb or STR approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
-In this simulated example we will use Airbnb data from September 1, 2015 to August 31, 2016 to represent the actual Airbnb market conditions over the time period in question.
+Our study design treats September 1, 2015 as the 'decision date' on which a property owner would decide between a long or short term strategy.
+To determine the likely LTR nightly rate for the subsequent 12 months we use the observed rental transactions from September 1, 2014 to August 31, 2015 to build a model to estimate market rent as of August 31, 2015.
+A short term leasing approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
+In this example we will use the observed Airbnb data from September 1, 2015 to August 31, 2016 to represent the actual Airbnb market conditions over the time period in question.
 
@@
 Both anecdotal evidence and Airbnb's own marketing campaigns suggest that there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property very infrequently, for example when they are away on vacation (Opportunistic Sharers).
-For the purposes of this research we are focused on Profit Seekers; those owners who would be faced with deciding between a long- and short-term leasing strategy.
-
+For the purposes of this research we are focused on the Profit Seekers; the properties mostly likely to be available for long or short term rentals.
 If these are the two dominant forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked (not listed on the portal) should be highly bimodal with Profit Seekers in one group and Opportunistic Sharers in another.
@@
 We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 1.
-We do find many hosts with a large number of blocked periods, but, unfortunately, no true pattern emerges.
+We do find many hosts with a large number of blocked periods, but, also many with few and, unfortunately, no true pattern emerges.
 
@@
 The Airbnb data provides limited information on the structural characteristics.
-The only overlapping fields that we have between the two datasets are bedrooms and bathrooms.
+The only overlapping fields that we have between the two datasets are structure type, bedrooms and bathrooms.
 Additionally, as the markets and structural components of houses and apartments differ, we bifurcate our analysis between the two property types from this point forward.
@@
 For both property types, the vast majority of properties have three or fewer bathrooms.
-We filter the data accordingly.
-Additionally, note that short-term rentals consider studio apartments to be 0 bed units while the long-term data considers these as 1 bedroom.
-We convert the 0 bed short-term units to 1 bed units.
-A few short-term properties indicate no baths, which is likely an error so we remove these observations from the data.
+We filter the data accordingly.^[Additionally, note that short-term rentals consider studio apartments to be 0 bed units while the long-term data considers these as 1 bedroom.
+We convert the 0 bed short-term units to 1 bed units.] A few short-term properties indicate no baths, which is likely an error so we remove these observations from the data.
 Also, here we notice that the short-term data gives bathrooms in halves, while the long-term data presents baths in whole numbers.
@@
 As a result we examine the combinations of the two.
-From this analysis we see that there are 8 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
+From this analysis we see that there are eight combinations that make up the bulk of the properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
 The four bedrooms options are only present in the house category.
@@
 Very few short-term rentals were located in these areas and those that were have a much higher likelihood of being vacation homes; a group of properties uses that doesn't match well to our research question.
-While the Inner and Middle suburb designation is a useful starting place, we can imagine that a few different spatial features can influence the short-term market.
+While the Inner and Middle suburb designation is a useful starting place, we belief that a few additional spatial features can also influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
@@
 
-![Suburb Categories](C:/Code/research/airbnbMelbourne/images/sub_loc_map.png)
+<!-- ![Suburb Categories](C:/Code/research/airbnbMelbourne/images/sub_loc_map.png) -->
 
-We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
+We assign submarket designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-3 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
 This process is repeated for both the short- and long-term data.
 Finally, we filter our data to observations in suburbs that contain at least three STR and LTR observations.
-The boundary of the suburbs meeting these criteria compose our study area (Figure 3).
+The boundary of the suburbs meeting these criteria compose our study area.
 The location of the short- and long-term rentals, colored by submarket, are shown in Figure 4.
-It should be noted that the beach areas in our study are densely developed and represently, generally speaking, higher end residential suburbs, not vacation-based communities (as one might find much farther down the coast).
+It should be noted that the beach areas in our study are densely developed and represently, generally speaking, higher end residential suburbs, not vacation-based communities as one might find much farther south along the coast.
 
-![Long Term Observations](C:/Code/research/airbnbMelbourne/images/ltr_loc_map.png)
+![Study Area and Observation Locations](C:/Code/research/airbnbMelbourne/images/ltr_loc_map.png)
 
@@
 Here too, there is a problem with comparing observed revenues from a property with a 20\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portals during those blocked days.
-And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should not necessarily apply to the hypothetical investor in our examined scenario.
+And, even if we knew that the blocked days were simply due to the host wanting to use the property themselves during that time, this deduction in revenue should factor into the comparative analyses we make.
 In short, in either case the actual observed short-term revenue would be biased on the low end compared to what a revenue maximizing owner would be likely able to accomplish.
@@
 
-1. Actual ($REV_a$)}: Observed bookings multiplied by median nightly rate
+1. Actual ($REV_a$): Observed bookings multiplied by median nightly rate
 
 2.
-Potential ($REV_p$)}: Observed bookings extrapolated to a full year plus imputed bookings during observed blocked days.
-Our attempt here is to represent the potential revenue if the property had been listed on Airbnb all year long.
-The imputed bookings are imputed by comparing the property specific performance during the non-blocked days to overall market performance on those days and then applying that relative ratio to the overall market performance on the extrapolated and blocked days.
+Potential ($REV_p$): Observed bookings extrapolated to a full year plus imputed bookings during observed blocked days.
+Our attempt is to represent the potential revenue if the property had been listed on Airbnb all year long.
+The imputed bookings are calculated by comparing the property specific performance during the non-blocked days to overall market performance on those days and then applying that relative ratio to the overall market performance on the extrapolated and blocked days.
 
@@
 We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 6).
-Revenues from the long-term rentals are far more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.
-Actual short-term revenues range from neglible to highs of greater than \$60,000, with a collection of the properties showing very limited (less than \$10,000) revenue.
+Revenues from the long-term rentals are far more consistent, with the vast majority totaling between A\$12,000 to A\$30,000 per year.
+Actual short-term revenues range from neglible to highs of greater than A\$60,000, with a collection of the properties showing very limited (less than A\$10,000) revenue.
 The range of the distribution for the Potential short-term revenue is similar, however, the distribution itself is shifted slightly to the right due to our time extrapolation and blocked days imputation.
-
 While this simple analysis does not control for location and product differences, it does highlight the fact that some profit seeking Airbnb owners are likely making greater revenues than in long-term rentals, but that many are not.
-The high number of very low yield Airbnb properties suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.]
 
@@
 We then average the hedonic model and matched pairs prediction for each short term property to create an estimate of its long-term rental rate.
-As a validation check, we find some variation between the predictions from the two models for specific properties, however, the overall correlation between the two estimates is 97.6%.
+As a validation check, we find some variation between the predictions from the two models for specific properties, however, the overall correlation between the two estimates is 89.4%.
 
@@
 Overall, 57.3%^[If we just look at actual revenue, ignoring blocked days and properties with less than a full 12 months of listing, the figure is 42.5%] of the 2,415 short-term urban rental properties in our sample were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
-While illustrative, a simple univariate analysis does not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.
-To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.
-
-We specify three, increasingly complex, logistic regression models.
+While illustrative, a simple univariate analysis does not fully control for location, property characteristics or owner actions -- which are a key component of short-term rental success.
+To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of three increasingly complex, logistic regression models.
 
@@
 
-In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
+In Model 1, we see that when controlling for structural characteristics, houses have a significantly lower probability of being more profitable in short-term leasing than apartments.
 Additionally, 1 bed / 1 bath units (reference category) show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
 This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
-Larger units, 3 bedrooms plus, generally show no statistical difference in preference porbability to the 1 bed / 1 bath reference unit.
+Larger units, 3 bedrooms plus, generally show no statistical difference in preference probability to the 1 bed / 1 bath reference unit.
 In other words, larger units are equally desirable to tourists and local residents alike.
@@
 The greater the minimum stay, the lower the probability of short-term preference.
-Longer minimum stays may equate to lower occupancy rates as one or two night travelers are exempted from the property.
+Longer minimum stays may equate to lower occupancy rates as one or two night travelers are prevented from booking.
 Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.
@@
  full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
- names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+ names(full.table) <- c('Variable', 'Model 1: Structural  ', "Model 2: + Location  ", 
+                        "Model 3: +Host Policies")
  full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
@@
                                               3)))
-  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
+  names(diag.table) <- names(full.table)
 
@@
 
+  xf_cap <- paste0('Dependent Variable = Short Term Preference.  These three logistic',
+                   ' regression models use 2,415 short term rental observations to ',
+                   'examine the impacts of various features on short term preference (',
+                   ' the likelihood of greater net revenues from a short term vs a long',
+                   ' term leasing strategy).')
+
   # XTable
   x.full <- xtable(full.table,
-                  caption='Logistic Modeling Results (Likely Revenue)\n')
+                   caption = xf_cap)
   align(x.full) <- 'lllll'
@@
        hline.after=c(-1,0,15,20,20),
-       caption.placement='top')
+       caption.placement='bottom')
 
@@
 
-* Net long term revenues for short term rental are systematically decreased 15%
+* Net estimated long term revenues for short term rental are systematically decreased 15%
 
@@
 A few of the originally less significant variables do show relatively larger deviations in coefficient magnitude, but in general, the models appear to be stable across the sentivity tests.
-Do note that the intercept terms does change across models, which would be expected as this represents the base probability of short-term preference which we'd expect to move in concert with our changing assumptions.
+We note that the intercept terms does change across models, which would be expected as this represents the base probability of short-term preference which we'd expect to move in concert with our changing assumptions.
 
@@
 
- names(hfull.table) <- c('Variable', 'Original   ', 'Missing Costs   ', 
-                         "Uneven Sample   ")
+ names(hfull.table) <- c('Variable', '   Original Model   ', '    Test 1: Missing Costs   ', 
+                         "   Test 2: Uneven Sample   ")
  hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
@@
  hfull.table <- rbind(hfull.table, hdiag.table)
+
 ```
@@
 
+  xh_cap <- paste0('Dependent Variable = Short Term Preference.  These three logistic',
+                   ' regression models use 2,415 short term rental observations to ',
+                   'examine the impacts of various features on short term preference (',
+                   ' the likelihood of greater net revenues from a short term vs a long',
+                   ' term leasing strategy). Model 1 is the original model from Table 1',
+                   ' above.  Model 2 is a sensitivity test where we account for the ',
+                   'possibility of additional short term costs (15 percent decrease in short term net revenues) and Model 3 is a ',
+                   'sensivity test where we account for the potential of short term ',
+                   'properties being, on average, of a lower quality and condition ',
+                   'than long term properties (15 percent decrease in imputed long-term revenues)')
+
  xh.full <- xtable(hfull.table,
-                  caption='Logistic Modeling Results (Potential Revenue by Host Type)\n')
+                  caption=xh_cap)
  align(xh.full) <- 'lllll'
@@
 Apartments are much more likely than houses to be more profitable as a short-term rental.
-City-Core properties are more likely than other properties to prefer a short-term strategy.
+City-Core properties are more likely than properties in other locations to prefer a short-term strategy.
 For instance, 65\% of apartments in the city core generated more revenue on Airbnb than they likely would have on the long-term market while only 23\% of suburban houses did.
@@
 
-Testing for the sensitivity of the initial results through changes two of our core assumptions -- short term leasing costs and sample similarity between LTR and STR properties -- we find the qualitative finding to be generally robust.
+Testing for the sensitivity of the initial results through changes two of our core assumptions -- short term leasing costs and sample similarity between LTR and STR properties -- we find the qualitative findings to be generally robust.
 While the base probability of short-term preference changes with changing assumptions (as expected), the sign and magnitudes of the co-variates remains relatively robust to changes in key assumptions.
@@
 Future research should focus both on building better models to explain (and ultimately predict) short-term rates and occupancies as well as to understand the impact of policies such as strict cancellation or no pets on the short-term market.
-It is likely that this work is being done proprietarily by Airbnb.com itself and other complementary firms such as AirDNA.co.
 
@@
 
-Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which the property owner is given a binary option of either short- or long-term leasing strategy.
+Finally, our analysis looks at a single year, beginning in September (spring) and ending in August in which we constrain the property to either a one of a short- or long-term leasing strategy.
 In reality, the possibilities may not be so rigid.
@@
 Future research should expand our scenario to look at more than just a single binary option over a fixed period.
-We feel there may be significant opportunities for new ventures in industry to exploit the changing market for housing.
 

### 2018-11-09 papers/round_2_reviews.Rmd
Revision, Round 2, Iteration 2

@@
 ---
-title: "Round_2_Reviews"
+title: "To Airbnb?: Factors impacting short-term leasing preference"
+subtitle: "Round 2 Reviews"
 author: "Andy Krause and Gideon Aschwanden"
-date: "10/25/2018"
-output: html_document
+date: "11/8/2018"
+output: pdf_document
 ---
 
-### Key Points:
+### What's Changed
+
+1. Refined sample to better fit research question
+* Further focused on urban properties by removing rural homes from the sample due to likelihood of being second homes occasionally used by owners
+* Removed all host types except "Profit Seekers" to minimize potential for remaining owner-occupiers and vacation homes in the sample
+
+2. Added a 'matched-pairs' approach to long term rental imputation
+* Blended with hedonic model to create an ensemble approach
+
+3. Added two new sensitivity tests
+* Examine the possible impacts of under estimates of short term costs
+* Examine the possible impacts of over estimate of imputed long term rent estimates
+
+4. Added captions to tables and figures to make them more self-contained
+
+5. Updated title to represent change in focus
+
+&nbsp;
+&nbsp;
+&nbsp;
+
+### Direct responses to reviewers
+
+&nbsp;
+&nbsp;
 
@@
 
-* ~~Add in something on Short term vs long term bonds~~
-* ~~Doesn't trust hedonic estimation.  Do matched pairs.~~
-
-#### Reviewer 2
-
-* (in Progress) Can't determine who are actually investors, so the research question isn't valid
-* ~~Make tables/figures self contained~~
-
-### Full comments
-
-#### Reviewer 1
+&nbsp;
 
@@
 
+&nbsp;
+
 **As Real Estate is an asset class much like bonds there likely warrants a larger theoretical discussion on the short vs.
@@
 However, we do not feel that this paper is the correct place to do so given its empirical focus.
-The fact that this comment was raised (and the input from another reviewer regarding our research question) has led us to re-focus our research question and the aim of this study.
-In short, we want to focus on the built environment side of the question, not the financial structuring side.
-In other words, what types of properties in which locations are short term preferable, rather than attempting to make a judgement about the financial decision-making of an owner -- a situation whereby many individual and idiosyncratic factors play a large role  We appreciate you raising this concern as it has helped us think through the ultimate goal of our work.**
+The fact that this comment was raised (and the input from another reviewer regarding our research question) has led us to re-focus our research question and pivot the aim of this study.
+In short, we focus on the built environment side of the question, not the financial structuring side.
+In other words, how do location, home characeristics and host policies impact short term preferability, rather than attempting to make a judgement about the financial decision-making of an owner -- a situation whereby many individual and idiosyncratic factors play a large role  We appreciate you raising this concern as it has helped us think through our research question and the ultimate goal of our work.**
+
+&nbsp;
 
@@
 
+&nbsp;
+
 **To address this issue we have added a 'matched-pairs'-type estimation to our imputation of long-term rents.
-More specifically we do an ensemble of 3, 5, and 7 comparable matched-pairs type valuations using the nearest 3, 5, and 7 transactions that have identical bedrooms, bathrooms and structure type (apartment/detached).
+More specifically we match homes based on structure type (apartment/detached), bedrooms and bathrooms and then take the median of the 7 nearest (geographically) comparables.
 For apartments this often pulled in transactions in the same building, for detached dwelling on the same block or street.
-Results from this estimation show a 91% correlation with our hedonic results, though there did seem to be a deviation in the high end apartment market, especially for 1 bedroom units.
-As a result, we take the average of the matched pairs ensemble and the hedonic model.**
+Results from this estimation show a 89% correlation with our hedonic results, though there did seem to be a deviation in the high end apartment market, especially for 1 bedroom units.
+As a result, we take the average of the matched pairs and the hedonic model estimates.**
+
+&nbsp;
 
@@
     xlab('\nHedonic Revenue\n') + 
-    ylab('Matched Pairs Revenue\n') + 
+    ylab('Matched Pairs Revenue (A$)\n') + 
     theme(legend.position = 'none',
@@
 
+&nbsp;
+&nbsp;
+
 #### Reviewer 2
+
+&nbsp;
 
@@
 
-* *Owner-occupiers*  **(Wait, what?  How do these factor in?  You can't occupy given our study design.)**
-* *Vacation home owners* **(Our study design eliminates most of these give our boundary)**
+* *Owner-occupiers*  (**Eliminated via the 75% non-blocked filter**)
+* *Vacation home owners*  (**Mostly eliminated via limiting to urbanized area**)
 * *Investors*
@@
 
-**[Forthcoming] Discuss how our study design eliminated most vacation homes.  Move the Sensitive test on Maximizers to be the key focus of the paper**
+&nbsp;
+
+**We have re-focused our sample, both geographically and by host behavior to attempt to elminate both Owner-Occupiers and Vacation Home owners.
+Rather than working with this more limited sample of owners in a sensitivity test, we now focus the entire study on them.**
+
+&nbsp;
 
@@
 
-**[Forthcoming] Make a note about pivoting away from financial calculus to location/utility argument**
+&nbsp;
+
+**Thank you for the comment.
+We agree and we've altered our research question to focus the paper on to the spatial, structural and behavior (host policies) contributions to determining short term preference and away from the strict financial calculus of the decision of whether or not to Airbnb.**
+
+&nbsp;
 
@@
 a LTR.*
+
+&nbsp;
 

### 2018-11-09 scripts/5_data_viz.Rmd
Revision, Round 2, Iteration 2

@@
 
+  inn_sf <- suburb_sf %>% dplyr::filter(class == 'Inner') %>% st_union()
+  mid_sf <- suburb_sf %>% dplyr::filter(class == 'Middle' & 
+                                          name != 'Seabrook' &  
+                                           name != 'Altona Meadows') %>% st_union()
+
    # Make map
@@
   png(filename = file.path(getwd(), 'images', "sub_loc_map.png"), 
-       width = 6.5, height = 6.5, units = 'in', res = 300)
+       width = 4.5, height = 4.5, units = 'in', res = 300)
 
-  tm_shape(suburb_sf) +
-    tm_polygons("class", palette=c('gray20', 'gray50', 'gray80'), title='Suburb Class') +
+  tm_shape(suburb_sf %>% dplyr::filter(class != 'Outer')) +
+    tm_polygons("class", palette=c('gray50', 'gray80'), title='Suburb Class') +
   tm_shape(studyarea_sf) + 
@@
     tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
-                  title='Study Area')
+                  title='Study Area')+
+  tm_layout(
+    legend.position = c("left","bottom"),
+    legend.text.size = 0.5)
 
@@
   sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
-              col_df$rgb[6], col_df$rgb[1])
+              col_df$rgb[6])
+
+  ltr_map <-   tm_shape(mid_sf) + 
+    tm_fill(col='gray95', lwd=1) +
+  tm_shape(inn_sf) + 
+    tm_fill(col='gray90', lwd=1) +
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='black', lwd=2) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray80', lwd=.5) +
+  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.9, shape=16, legend.col.show=TRUE)+
+    tm_layout(title = "LTR Observations",
+              title.position = c("center", "top"),
+              title.size = .8)
+
+  str_map <- tm_shape(mid_sf) + 
+    tm_fill(col='gray95', lwd=1) +
+  tm_shape(inn_sf) + 
+    tm_fill(col='gray90', lwd=1) +
+  tm_shape(studyarea_sf) + 
+    tm_borders(col='black', lwd=2) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray80', lwd=.5) +
+  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
+    tm_symbols('Submarket', size=.02,
+               palette = sm_col, alpha=.9, shape=16) + 
+    tm_layout(title = "STR Observations",
+              title.position = c("center", "top"),
+              title.size = .8)
+
+  sltr_map <- tmap_arrange(ltr_map, str_map)
 
   png(filename = file.path(getwd(), 'images', "ltr_loc_map.png"), 
-       width = 4, height = 4, units = 'in', res = 300)
-  tm_shape(studyarea_sf) + 
-    tm_borders(col='gray50', lwd=2) +
-  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
-    tm_borders(col='gray90', lwd=.5) +
-  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
-    tm_symbols('Submarket', size=.02,
-               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
-  dev.off()
-
-  png(filename = file.path(getwd(), 'images', "str_loc_map.png"), 
-       width = 4, height = 4, units = 'in', res = 300)
-  tm_shape(studyarea_sf) + 
-    tm_borders(col='gray50', lwd=2) +
-  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
-    tm_borders(col='gray90', lwd=.5) +
-  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
-    tm_symbols('Submarket', size=.02,
-               palette = sm_col, alpha=.3, shape=16)
+       width = 7, height = 3.5, units = 'in', res = 300)
+    sltr_map
   dev.off()
@@
    # Make Airbnb submarket map
+   str_tdf$Submarket <- as.character(str_tdf$geo_mrkt)
+   str_tdf$Submarket[str_tdf$Submarket == 'city-core'] <- '   City-Core   '
+   str_tdf$Submarket[str_tdf$Submarket == 'city'] <- '   City   '
+   str_tdf$Submarket[str_tdf$Submarket == 'beach'] <- '   Beach   '
+   str_tdf$Submarket[str_tdf$Submarket == 'suburban'] <- '   Suburban   '
+   str_tdf$Submarket <- factor(str_tdf$Submarket, 
+                                  levels = c('   City-Core   ', '   City   ', 
+                                             '   Suburban   ', '   Beach   '))
 
    strtype_bar <- ggplot() +
-     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
+     geom_bar(data=str_tdf, aes(x=Submarket, fill=Submarket)) +
      scale_fill_manual(values=sm_col, name='Submarket') +
@@
      ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
+     theme(legend.position = 'none',
+           legend.title = element_blank(),
+           axis.ticks.x=element_blank()) +
+     ggtitle('Short Term Properties')+
+     theme(plot.title = element_text(size = 10, hjust = 0.5),
+           axis.text.y=element_blank(),
+           axis.text.x=element_text(size = 6),
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=.5)) + 
+     labs(caption = paste0('\nBreakdown of 2,415 short-term properties by submarket and ',
+                           ' structure type.\n'))
+  # strtype_bar
+
+   # Make Long term rental map
+
+   ltr_tdf$Submarket <- as.character(ltr_tdf$geo_mrkt)
+   ltr_tdf$Submarket[ltr_tdf$Submarket == 'city-core'] <- '   City-Core   '
+   ltr_tdf$Submarket[ltr_tdf$Submarket == 'city'] <- '   City   '
+   ltr_tdf$Submarket[ltr_tdf$Submarket == 'beach'] <- '   Beach   '
+   ltr_tdf$Submarket[ltr_tdf$Submarket == 'suburban'] <- '   Suburban   '
+   ltr_tdf$Submarket <- factor(ltr_tdf$Submarket, 
+                                  levels = c('   City-Core   ', '   City   ', 
+                                             '   Suburban   ', '   Beach   '))
+   ltrtype_bar <- ggplot() +
+     geom_bar(data=ltr_tdf, aes(x=Submarket, fill=Submarket)) +
+     scale_fill_manual(values=sm_col) +
+     facet_wrap(~type) +
+     ylab('# of Properties\n') + xlab('')+
+     theme(legend.position = 'none',
            legend.title = element_blank(),
@@
            axis.ticks.x=element_blank()) +
-     ggtitle('Short Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
-
-   # Make Long term rental map
-
-   ltrtype_bar <- ggplot() +
-     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
-     scale_fill_manual(values=sm_col) +
-     facet_wrap(~type) +
-     ylab('# of Properties\n') + xlab('')+
-     theme(legend.position = 'bottom',
-           legend.title = element_blank(),
-           axis.text.x=element_blank(),
-           axis.ticks.x=element_blank()) +
-     ggtitle('Long Term Property Type\nBy Submarket')+
-     theme(plot.title = element_text(hjust = 0.5))
+     ggtitle('Long Term Properties')+
+     theme(plot.title = element_text(size = 10, hjust = 0.5),
+           axis.text.y=element_blank(),
+           axis.text.x=element_text(size = 6),
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=.5)) + 
+     labs(caption = paste0('\nBreakdown of 64,305 long-term properties by submarket and ',
+                           ' structure type\n'))
+     #ltrtype_bar
 
@@
     scale_color_manual(values=dens_cols) +
-    ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
-    xlab('Annual Revenue') +
+    # ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
+    xlab('Annual Revenue (A$)') +
+    ylab('')+
     scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
-                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
+                       labels=c('A$0', 'A$20,000', 'A$40,000', 'A$60,000'))+
     theme(legend.position='bottom',
-          legend.title = element_blank(),
-          plot.title = element_text(hjust = 0.5),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.title.y=element_blank()) +
+          legend.title = element_blank())+
+     theme(plot.title = element_text(size = 10, hjust = 0.5),
+           axis.text.y=element_blank(),
+           axis.text.x=element_text(size = 6),
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=0)) + 
+     labs(caption = paste0('\nComparison of the distribution of observed long-term rental',
+                           ' revenues of 64,305 properties (blue) to observed revenues of ', 
+                           ' 2,415 short\nterm properties (pink).  The purple curve ',
+                           ' represents the potential revenues of the 2,415 short term ',
+                           ' properties (includes imputed bookings).')) +
     coord_cartesian(xlim=c(0, 70000))
@@
      ylab('Frequency\n') +
-     xlab('\n% of Time Property is Blocked') +
+     xlab('\n\n% of Time Property is Blocked') +
      scale_x_continuous(breaks=seq(0,1,.2),
@@
      #ggtitle('Host Block Rate Frequency\n') +
-     theme(plot.title = element_text(hjust = 0.5)) +
+     theme(plot.title = element_text(hjust = 0.5, size = 10)) +
      theme(axis.text.y=element_blank(),
-           axis.ticks.y=element_blank())
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=0)) + 
+     labs(caption = paste0('\nDensity plot of frequency of blocking schedule for short term ',
+                           '\nleasing observations. Blocking indicates that the property ',
+                           'is \nnot available for nightly rental on Airbnb. Vertical lines',
+                           '\ndelineate the three host type groupings.'),
+          title = 'Host Blocking Frequency\n') +
+    geom_vline(xintercept = .25, linetype="dashed", color = "black", size=.5, alpha=.5)+
+    geom_vline(xintercept = .75, linetype="dashed", color = "black", size=.5, alpha=.5)
 
-  block.rate.period <- ggplot(str_tdf_all, aes(x=block_rate, y=nbr_block * (366/total_days))) +
-    geom_point(fill=str.col, color=str.col, size=.2) +
+  block.rate.period <- ggplot(str_tdf_all, 
+                              aes(x=block_rate, y=nbr_block * (366/total_days))) +
+    geom_point(fill=alpha(str.col,.3), color=alpha(str.col,.3), size=.1, shape=16) +
     ylab('Nbr of Blocked Periods\n') +
-    xlab('\n% of Time Property is Blocked') +
+    xlab('\n\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0, 1, .2),
@@
     #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
-    theme(plot.title = element_text(hjust = 0.5))
+     theme(plot.title = element_text(size = 10, hjust = 0.5),
+           axis.text.y=element_blank(),
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=0)) + 
+     labs(caption = paste0('\nCumulative time of blocking for short term properties ',
+                           '(x-axis) \nversus the total number of periods where the ',
+                           'property was \nblocked from nightly rental.',
+                           'Vertical lines delineate the three \nhost type groupings.'),
+          title = 'Block Rate vs Blocked Periods\n')+
+    geom_vline(xintercept = .25, linetype="dashed", color = "black", size=.5, alpha=.5)+
+    geom_vline(xintercept = .75, linetype="dashed", color = "black", size=.5, alpha=.5)
 
@@
     theme(legend.position='none') +
-    ylab('Frequency\n') +
-    xlab('\nHost Type') +
+    ylab('') +
+    xlab('') +
     scale_x_discrete(labels=c('Profit-Seekers','Opportunistic Sharers','Unknowns'))+
-    #ggtitle('short-term Host Types') +
-    theme(plot.title = element_text(hjust = 0.5))
+    # ggtitle('short-term Host Types') +
+     theme(plot.title = element_text(size = 10, hjust = 0.5),
+           axis.text.y=element_blank(),
+           axis.text.x=element_text(size = 6),
+           axis.ticks.y=element_blank(),
+           plot.caption=element_text(size=6, hjust=0)) + 
+     labs(caption = paste0('\nBreakdown of Host Types for Short Term Properties:\n\n',
+                           '1) Profit Seekers:               <= 25% Blocked             3,056 Obs.\n',
+                           '2) Opportunistic Sharers:   >= 75% Blocked             1,743 Obs.\n',
+                           '3) Unknowns:                     25% > 75% Blocked       2,707 Obs.\n')) + 
+   annotate("text", x = 1, y = 3300, label = "41%") +
+   annotate("text", x = 2, y = 2000, label = "23%") +
+   annotate("text", x = 3, y = 2949, label = "36%") +
+   coord_cartesian(ylim=c(0,3500))
 

### 2018-11-10 papers/full_paper.Rmd
Fix beach data issue, join maps, simplify data preparation discussion

@@
 
-We begin by filtering observations by time.
-Our study design treats September 1, 2015 as the 'decision date' on which a property owner would decide between a long or short term strategy.
-To determine the likely LTR nightly rate for the subsequent 12 months we use the observed rental transactions from September 1, 2014 to August 31, 2015 to build a model to estimate market rent as of August 31, 2015.
-A short term leasing approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).
-In this example we will use the observed Airbnb data from September 1, 2015 to August 31, 2016 to represent the actual Airbnb market conditions over the time period in question.
+Table 1 highlights the filters applied to the data.
+Filters were applied in the order listed in the table.
+Details on two filters -- property extent, host classification and location -- are described more fully below, more information on the other filter can be found in the online code repository for this research (see the Reproducibility section at the end of this paper).
+After employing all filters we were left with 2,415 short term and 64,305 long term observations.
 
-Next, we filter the data based on property types.
-Airbnb units are classified into 19 different property types.
-The most common are Apartments and Houses, the least common are Igloo, Tent, Treehouse and Yurt.^[Property types are owner/lister defined, therfore it is likely that some designation, such as Igloo, at the very least, are not completely true representations of the property type] For the sake of this analysis, we will collapse these twenty types into three types:
+```{r table_coret, results="asis", comment=FALSE, message=FALSE, echo=FALSE}
 
-1. House:  Includes properties labeled 'House', 'Townhouse' or 'Villa'
-2. Apartment: Includes properties labeled as 'Apartment', 'Condominium' or 'Loft'
-3. Other: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Other', 'Tent', 'Treehouse' and 'Yurt.
+  df_cap <- paste0('Sequential list of filters applied during data preparation. Descriptions\n.',
+                   'indicate the values that were kept in the data.' )
 
-Within the long-term rental data, property types fall into eight categories.  Like the Airbnb data we group these into three categories matching as best as possible to the Airbnb categories:
+dp_tbl <- data.frame(Filter = c('Time', 'Property Type', 'Property Extent',
+                                'Host Classification', 'Bed/Bath',
+                                'Rates and Rents', 'Location'),
+                     Long_Term = c('2014-09-01 to 2015-08-31',
+                                   'House, Apartment',
+                                   'NA', 'NA', '1/1, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2, 4/3',
+                                   'A$200 to A$1,000 Weekly',  
+                                   'City-Core, City, Suburban, Beach'),
+                     Short_Term = c('2015-09-01 to 2016-08-31',
+                                   'House, Apartment',
+                                   'Full Unit', 'Profit Seekers', 
+                                   '1/1, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2, 4/3',
+                                   'A$50 to A$500 Nightly',  
+                                   'City-Core, City, Suburban, Beach')
+                     )
+ names(dp_tbl) <- c('Filter', 'Long-Term Market', 'Short-Term Market')
+ print(xtable(dp_tbl, caption = df_cap),
+       include.rownames=F,
+       caption.placement="bottom",
+       hline.after=c(0,7))
+```
 
-1. House:  Includes properties labeled 'Duplex', 'House', 'Terrace', 'Townhouse' or 'Villa'
-2. Apartment: Includes properties labeled as 'Unit' or 'Studio'
-3. Other: Includes properties labeled as 'Semi'
+#### Property Extent
 
-Part of the difficulty in perfectly mapping property types from these two datasets is due to the fact that the long-term data uses Australian terms while the short-term data conforms to North American lexicon.
-This is most apparent when talking about apartment dwellings.
-In Australia these are referred to as Units or Studios, while in North American they are referred to as Apartments or Condominiums (depending on ownership structure).^[Also note that 'Apartment-type' ownership is very rare in Australia.
-Nearly every multi-family dwelling is owned as a condominium.
-See @berry2000investment for more information on the overall structure of the Australian market] Additionally, Terrace homes are very common in many of the older suburbs of Melbourne and would be considered Rowhouses or, possibly, Townhomes in the North American context.
-
-The Other category only makes up a small percentage of the properties in both the short (3.78%) and long-term (0.02%) markets.
-Additionally, a large proportion of the 'Others' in the short-term data are Bed & Breakfast units, a use which doesn't fit within our research question.
-As a result, we remove the 'Others' from both the short- and the long-term rental data.
-
-Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
+Short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:
 
@@
 For the purposes of this research we are focused on the Profit Seekers; the properties mostly likely to be available for long or short term rentals.
+
 If these are the two dominant forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked (not listed on the portal) should be highly bimodal with Profit Seekers in one group and Opportunistic Sharers in another.
@@
 Within those two extremes, we consider users as "Unknown" as they may be multiple plaform users (who are profit seeking), very opportunistic sharers or driven by some other, unknown motivation.
-Profit Seekers make up 41\% of the hosts, with Opportunistic Sharers capturing 23\% and the remainder 'Unknown' category contains just over 36\% of all properties.
+Profit Seekers make up 41\% of the hosts, with Opportunistic Sharers capturing 23\% and the remainder 'Unknown' category contains just over 36\% of all properties (Figure 2).
 To best approximate the scenario considered in our research question, we keep only the Profit Seekers in our dataset.
-See Figure 2 for a breakdown of these group by the two variables.
 
@@
 ![Host Category Counts](C:/Code/research/airbnbMelbourne/images/host_bar.png)
-
-#### Structural Characteristics
-
-The Airbnb data provides limited information on the structural characteristics.
-The only overlapping fields that we have between the two datasets are structure type, bedrooms and bathrooms.
-Additionally, as the markets and structural components of houses and apartments differ, we bifurcate our analysis between the two property types from this point forward.
-
-We begin by removing all properties that are missing bedroom or bathroom information or have a likely data error in these fields (more than 14 bedrooms or 10 bathrooms).
-For both short- and long-term rentals we find that most apartments have fewer than four bedrooms and houses fewer than five.
-For both property types, the vast majority of properties have three or fewer bathrooms.
-We filter the data accordingly.^[Additionally, note that short-term rentals consider studio apartments to be 0 bed units while the long-term data considers these as 1 bedroom.
-We convert the 0 bed short-term units to 1 bed units.] A few short-term properties indicate no baths, which is likely an error so we remove these observations from the data.
-Also, here we notice that the short-term data gives bathrooms in halves, while the long-term data presents baths in whole numbers.
-We round the baths in the short-term data up to whole integers.
-
-In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.
-In other words, it is very common in the industry (and when looking for a short-term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.
-As a result we examine the combinations of the two.
-From this analysis we see that there are eight combinations that make up the bulk of the properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3.
-The four bedrooms options are only present in the house category.
-We filter the data to these combinations.
-
-#### Rates and Rental Values
-
-Next we filter by the prices -- the nightly rates and weekly^[Rents are quoted in weekly values but paid in monthly installments in Melbourne] rental prices.
-The long-term rental data have a single price observation, the asking rent at closing.
-For the short-term data, there are two indicators of nightly rate.
-First, each property has a average nightly rate figure that takes the average of the rates for all booked nights over the October 2014 to August 2016 period.
-Second, there is a rate for each day in the daily observations.
-For the vast majority of properties, the daily rates change very little, but for a select few there is a wide variation in the daily rates, often somewhat randomly.
-In cases where a small number of reservations have been made, the average nightly rate can deviate widely from usual rate due to outliers on the high end.
-To remedy this, we create a new property-level variable that is the median nightly rate of successful bookings over the September 1, 2015 to August 31, 2016 period.
-
-After removing property level observations that are missing price data, we find that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night.
-We remove observations outside of these ranges.
 
@@
 
-We select the 18 suburbs below to represent the 'core' of the city (Table 1).
+We select the 18 suburbs below to represent the 'core' of the city (Table 2).
 The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.
@@
 
- print(xtable(c.subs, caption = 'List of Core Suburbs\n'),
+ print(xtable(c.subs, caption = 'List of City-Core Suburbs\n'),
        include.rownames=F,
@@
 
-<!-- ![Suburb Categories](C:/Code/research/airbnbMelbourne/images/sub_loc_map.png) -->
-
 We assign submarket designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-3 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.
@@
 The boundary of the suburbs meeting these criteria compose our study area.
-The location of the short- and long-term rentals, colored by submarket, are shown in Figure 4.
+The location of the short- and long-term rentals, colored by submarket, are shown in Figure 3.
 It should be noted that the beach areas in our study are densely developed and represently, generally speaking, higher end residential suburbs, not vacation-based communities as one might find much farther south along the coast.
@@
 To better visualize the relative frequency of the submarkets in the two tenure types we have broken down the data by submarket by property type by tenure type.
-A number of interesting observations are illustrated here (Figure 5).
+A number of interesting observations are illustrated here (Figure 4).
 First, the vast majority of Airbnb units are apartments in city-core or city locations.
-As expected and as shown by the map (Figure 2), the long-term properties are more evenly spread across the metro region than the short-term properties.
+As expected and as shown by the map (Figure 3), the long-term properties are more evenly spread across the metro region than the short-term properties.
 Long-term houses are more peripheral than apartments, a result of urban development patterns and land economics.
@@
 As the 'Actual' calculation systematically under counts the revenue from properties that were not on the Airbnb portal for the entire year we disregard it going forward and consider the 'Potential' revenue metric to be a better estimate of market performance.
-We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 6).
+We chart the distribution of the Actual ($REV_a$) and Potential ($REV_p$) short-term revenues against a distribution of the observed long-term revenues for the long-term properties (Figure 5).
 Revenues from the long-term rentals are far more consistent, with the vast majority totaling between A\$12,000 to A\$30,000 per year.
@@
 As a validation check, we find some variation between the predictions from the two models for specific properties, however, the overall correlation between the two estimates is 89.4%.
+Figure 6 shows a breakdown of the relationship between the two esitmates by structure type and bedroom count.
+
+![LTR Estimate Correlations](C:/Code/research/airbnbMelbourne/images/imp_cor.png)
 
@@
 
-The results of all three models are shown in Table 2.
+The results of all three models are shown in Table 3.
 For $PType$ Apartments are the reference category,  for $BedBath$, 1 Bed / 1Bath is the reference category, for $Submrkt$ the City-Core is the reference category and for $CancelPolicy$ Strict is the reference category.
@@
 
-Table 3 shows the results of our sensitivity testing, with the original model results shown for comparison.
+Table 4 shows the results of our sensitivity testing, with the original model results shown for comparison.
 For the five variables with the strongest relationship in the original model -- House, City, Suburban, Guests per Bedroom and Flexible Cancel -- the signs of the coefficient remain identical across the sensitivity tests and the variation in magnitudes are small, relatively speaking.
@@
 
-Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, similar to those from Profit Seeking short term rentals, however, the long-term revenues are much less variable (Figure 6).
+Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, similar to those from Profit Seeking short term rentals, however, the long-term revenues are much less variable (Figure 5).
 The long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market.
@@
 
-The logistic regression models (Tables 2 and 3) highlight which characteristics lead to increased short term preference.
+The logistic regression models (Tables 3 and 4) highlight which characteristics lead to increased short term preference.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.

### 2018-11-10 scripts/3_data_prep.Rmd
Fix beach data issue, join maps, simplify data preparation discussion

@@
     st_transform(crs=4283)
-  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach_no_outer.shp')) %>%
+  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach_saclip.shp')) %>%
     st_transform(crs=4283)
@@
    save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
-        col_df, clean_obj, core_suburbs, str_tdf_all,
+        col_df, clean_obj, core_suburbs, str_tdf_all, beach_buffer,
         file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

### 2018-11-10 scripts/4_data_analysis.Rmd
Fix beach data issue, join maps, simplify data preparation discussion

@@
 
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
+  str_cc <- str_tdf %>% dplyr::filter(geo_mrkt == 'city-core')
+  str_city <- str_tdf %>% dplyr::filter(geo_mrkt == 'city')
+  str_sub <- str_tdf %>% dplyr::filter(geo_mrkt == 'suburban')
+  str_beach <- str_tdf %>% dplyr::filter(geo_mrkt == 'beach')
+
+  glm_pot_host_cc <- glm(pot_pref_us ~ type + as.factor(bedbath) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_cc)
+  glm_pot_host_city <- glm(pot_pref_us ~ type + as.factor(bedbath) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_city)
+  glm_pot_host_sub <- glm(pot_pref_us ~ type + as.factor(bedbath) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_sub)
+  glm_pot_host_beach <- glm(pot_pref_us ~ type + as.factor(bedbath) +
+                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
+                      family=binomial(link='logit'),
+                      data=str_beach)
+
+  pot_sub_glms <- list(cc=glm_pot_host_cc,
+                       cc=glm_pot_host_city,
+                       cc=glm_pot_host_sub,
+                       cc=glm_pot_host_beach)
+
+```
+
 <!-- ### Host types -->

### 2018-11-10 scripts/5_data_viz.Rmd
Fix beach data issue, join maps, simplify data preparation discussion

@@
 ```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}
+  load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))
 
@@
                                            name != 'Altona Meadows') %>% st_union()
+
+  sub_sdf <- ltr_tdf %>%
+    group_by(suburb.x, Submarket) %>%
+    dplyr::summarize(count=n())
+  sub_sf <- suburb_sf %>%
+    dplyr::left_join(sub_sdf %>%
+                       dplyr::select(name = suburb.x, Submarket))
+
+  cc_sf <- sub_sf %>% dplyr::filter(Submarket == '   City-Core   ') %>% st_union()
+  beach_sf <- sub_sf %>% dplyr::filter(Submarket == '   Beach   ') %>% st_union()
 
@@
     tm_fill(col='gray95', lwd=1) +
+    tm_borders(col = 'gray40', lwd=1) +
   tm_shape(inn_sf) + 
-    tm_fill(col='gray90', lwd=1) +
+    tm_fill(col='gray85', lwd=1) +  
+  tm_shape(cc_sf) + 
+    tm_fill(col='gray75', lwd=1) +
+  tm_shape(beach_buffer) + 
+    tm_fill(col='gray65', lwd=1) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray70', lwd=.5) +
   tm_shape(studyarea_sf) + 
     tm_borders(col='black', lwd=2) +
-  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
-    tm_borders(col='gray80', lwd=.5) +
   tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
@@
     tm_layout(title = "LTR Observations",
-              title.position = c("center", "top"),
-              title.size = .8)
+              title.position = c("left", "top"),
+              title.size = .8) +
+  tm_shape(inn_sf) + 
+    tm_borders(col = 'gray40', lwd=1) +
+  tm_shape(cc_sf) + 
+    tm_borders(col = 'gray40', lwd=1) +
+  tm_shape(beach_buffer) + 
+    tm_borders(col = 'gray40', lwd=1)
 
@@
     tm_fill(col='gray95', lwd=1) +
+    tm_borders(col = 'gray40', lwd=1) +
   tm_shape(inn_sf) + 
-    tm_fill(col='gray90', lwd=1) +
+    tm_fill(col='gray85', lwd=1) +  
+  tm_shape(cc_sf) + 
+    tm_fill(col='gray75', lwd=1) +
+  tm_shape(beach_buffer) + 
+    tm_fill(col='gray65', lwd=1) +
+  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
+    tm_borders(col='gray70', lwd=.5) +
   tm_shape(studyarea_sf) + 
     tm_borders(col='black', lwd=2) +
-  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
-    tm_borders(col='gray80', lwd=.5) +
   tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
     tm_symbols('Submarket', size=.02,
-               palette = sm_col, alpha=.9, shape=16) + 
-    tm_layout(title = "STR Observations",
-              title.position = c("center", "top"),
-              title.size = .8)
+               palette = sm_col, alpha=.9, shape=16, legend.col.show=TRUE)+
+    tm_layout(title = "LTR Observations",
+              title.position = c("left", "top"),
+              title.size = .8) +
+  tm_shape(inn_sf) + 
+    tm_borders(col = 'gray40', lwd=1) +
+  tm_shape(cc_sf) + 
+    tm_borders(col = 'gray40', lwd=1) +
+  tm_shape(beach_buffer) + 
+    tm_borders(col = 'gray40', lwd=1)
 
@@
 ```
+
+```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
+
+  library(ggplot2)
+
+   load(file.path('c:/code', 'research', 'airbnbMelbourne',
+                  'data', 'analyzed', 'reviewers.RData'))
+
+  imp_df$bed_lab <- paste0(imp_df$bedrooms, ' Beds')
+  fig_cap <- paste0('This figure compares the estimated long term rent for short term rental properties via the hedonic imputation\nmethod (X-axis) and the matched pairs-type method (Y-axis).
+It is broken down by bedroom count and\nstructure type (Apartment vs House).
+Overall correlation is 89.4%')
+
+  # imp_cor <- imp_df %>%
+  #   dplyr::group_by(type, bed_lab) %>%
+  #   dplyr::summarize(count = n(),
+  #                    cor = cor(ltr_imp_revenueH, ltr_imp_revenueK))
+  # 
+  #   
+  # d1 + geom_text(data=data.frame(x=0.25, y=1.5e+04, label=1:7, 
+  #                              color=c("D","E","F","G","H","I","J")), 
+  #              aes(x,y,label=label), inherit.aes=FALSE)
+
+  png(filename = file.path(getwd(), 'images', "imp_cor.png"), 
+       width = 7, height = 4, units = 'in', res = 300)
+
+  ggplot(imp_df,
+         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
+    geom_point(alpha = .5, size=.5) + 
+    facet_grid(type ~ bed_lab) + 
+    xlab('\nHedonic Revenue (A$)\n') + 
+    ylab('Matched Pairs Revenue (A$)\n') + 
+    theme(legend.position = 'none',
+          plot.caption=element_text(hjust = 0),
+          plot.title = element_text(hjust = 0.5)) +
+    scale_color_manual(values = c(col_df$rgb[8], col_df$rgb[10])) + 
+    scale_x_continuous(breaks = c(15000, 30000, 45000),
+                       labels = c('$15k', '$30k', '$45k'))+
+    scale_y_continuous(breaks = c(15000, 30000, 45000),
+                       labels = c('$15k', '$30k', '$45k'))+
+    geom_abline(intercept = 0, slope = 1, linetype = 2,
+                color = 'gray50') +
+    labs(caption = fig_cap)
+
+  dev.off()
+
+```

### 2018-11-10 papers/round_2_reviews.Rmd
Finalize reviewer response

@@
 
-### What's Changed
+## What's Changed
 
@@
 
+6. Shortened data preparation section
+
 &nbsp;
@@
 
-### Direct responses to reviewers
+## Direct responses to reviewers
 
@@
 
-&nbsp;
-
-```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}
-
-  library(ggplot2)
-
-   load(file.path('c:/code', 'research', 'airbnbMelbourne',
-                  'data', 'analyzed', 'reviewers.RData'))
-
-  imp_df$bed_lab <- paste0(imp_df$bedrooms, ' Beds')
-  fig_cap <- paste0('This figure compares the estimated long term rent for short term rental properties via the hedonic\n imputation method (X-axis) and the matched pairs-type method (Y-axis).
-It is broken down by\n structure type (Apartment vs House) and by bedroom count.')
-
-  ggplot(imp_df,
-         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
-    geom_point(alpha = .5, size=.5) + 
-    facet_grid(type ~ bed_lab) + 
-    xlab('\nHedonic Revenue\n') + 
-    ylab('Matched Pairs Revenue (A$)\n') + 
-    theme(legend.position = 'none',
-          plot.caption=element_text(hjust = 0.3),
-          plot.title = element_text(hjust = 0.5)) +
-    scale_color_manual(values = c('red', 'blue')) + 
-    scale_x_continuous(breaks = c(15000, 30000, 45000),
-                       labels = c('$15k', '$30k', '$45k'))+
-    scale_y_continuous(breaks = c(15000, 30000, 45000),
-                       labels = c('$15k', '$30k', '$45k'))+
-    geom_abline(intercept = 0, slope = 1, linetype = 2,
-                color = 'gray50') +
-    labs(caption = fig_cap,
-         title = 'Comparison of Hedonic and Matched Pairs Imputation')
-
-```
-
-&nbsp;
 &nbsp;

### 2018-11-14 papers/full_paper.Rmd
Final edits for submission #3

@@
 In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one.
-Additionally, tests on the impacts of hosting policies suggest that even the right property may need the right owner(s) or strategy to make short-term rental the more profitable approach.
+Additionally, we test the impacts of hosting policies the results of which suggest that even the right property may need the right owner(s) or strategy to make short-term rental the more profitable approach.
 
@@
 
-We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues, netting out costs that can be estimated or assumed with some generality.
-We handle potential undercounting of costs through sensitivity tests that follow our initial assessment.
+We adopt a scenario-based approach that compares observed annual revenues for short-term rental (STR) properties with an estimate of their expected long-term rental revenues, netting out costs that can be estimated or assumed based on property, and not owner, characteristics.
+We handle potential undercounting of costs or over-estimation of long-term revenues through sensitivity tests that follow our initial assessment.
 
 Our results show that the feasibility of a greater revenues through a short-term rental -- what we have termed ''Short-Term Preference'' -- is dependent on property type, product, location and host policies.
-In short, the answer to whether or not a owner of an urban residential property is likely to earn more through a short-term leasing strategy than a long-term one is ''it depends''.
+In short, the answer to whether or not the owner of an urban residential property is likely to earn more through a short-term leasing strategy than a long-term one is ''it depends''.
 
@@
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
-With the rapid growth of Airbnb, and the controversies surrounding it, interest in the short-term rental market has increased among research as well as investors and industry analysts.
+With the rapid growth of Airbnb, and the controversies surrounding it, interest in the short-term rental market has increased among researchers as well as investors and industry analysts.
 
@@
 Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two markets.
-In examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
+Finally, in examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
 
@@
 
-Unfortunately, we cannot not directly observe properties that are utilized in both a short- and long-term leasing strategy.
+Unfortunately, we cannot directly observe properties that are utilized in both a short- and long-term leasing strategy.
 Therefore, comparisons are done with actual short-term but estimated or imputed long-term revenues.
@@
 
-where $Rate_{N}$ is the average nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. For long-term rentals the net revenue, $Rev_{LT}$, is defined as:
+where $Rate_{N}$ is the median nightly rate and $O_{Total}$ are the total number of occupancies (bookings) over the 12-month period. For long-term rentals the net revenue, $Rev_{LT}$, is defined as:
 
@@
 As opposed to similar sites such as VRBO.com and Homeaway.com which focus on vacation homes in tourist dominated areas such as beach towns and ski resorts, Airbnb offers considerable coverage in urban areas and, therefore, directly competes to a greater degree with more traditional long-term rentals than the other sites.^[In fact, our choice of study area was done so to specifically minimize the number of potential traditional vacation homes in our sample.] The data on the Airbnb market in Melbourne have been purchased from www.airdna.co, a data provider specializing in Airbnb data collection and analysis.
-The data offers both nightly observations indicating the advertised price, the occupancy status and a unique reservation identifier as well as general property and host policy information.
+The data offer both nightly observations indicating the advertised price, the occupancy status and a unique reservation identifier as well as general property and host policy information.
 
@@
 
-Data on the long-term rental market was provided by Australia Property Monitors (APM), a Fairfax Group company.
+Data on the long-term rental market were provided by Australia Property Monitors (APM), a Fairfax Group company.
 The long-term lease contains both property specific information (beds, baths, location, etc.) as well as a history of listing prices.
@@
 Filters were applied in the order listed in the table.
-Details on two filters -- property extent, host classification and location -- are described more fully below, more information on the other filter can be found in the online code repository for this research (see the Reproducibility section at the end of this paper).
+Details on three of the filters -- property extent, host classification and location -- are described more fully below, more information on the other filter can be found in the online code repository for this research (see the Reproducibility section at the end of this paper).
 After employing all filters we were left with 2,415 short term and 64,305 long term observations.
@@
 Very few short-term rentals were located in these areas and those that were have a much higher likelihood of being vacation homes; a group of properties uses that doesn't match well to our research question.
-While the Inner and Middle suburb designation is a useful starting place, we belief that a few additional spatial features can also influence the short-term market.
+While the Inner and Middle suburb designation is a useful starting place, we believe that a few additional spatial features can also influence the short-term market.
 While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beaches; and 2) Proximity to key tourist activities and events.
@@
 
-Second, many of the short-term properties have a significant number of blocked days (up to 255), days in which the property was not offered on Airbnb.
+Second, many of the short-term properties have a significant number of blocked days (up to 91), days in which the property was not offered on Airbnb.
 Here too, there is a problem with comparing observed revenues from a property with a 20\% block rate with a hypothetical year long revenue stream, especially if the property was leased out on other portals during those blocked days.
@@
 Overall, 57.3%^[If we just look at actual revenue, ignoring blocked days and properties with less than a full 12 months of listing, the figure is 42.5%] of the 2,415 short-term urban rental properties in our sample were more profitable as a short-term rental than it would have been if rented long-term over the course of the year.
-While illustrative, a simple univariate analysis does not fully control for location, property characteristics or owner actions -- which are a key component of short-term rental success.
+While illustrative, a simple univariate analysis does not fully control for location, property characteristics or owner actions -- all of which are a key component of short-term rental success.
 To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of three increasingly complex, logistic regression models.
@@
 Additionally, 1 bed / 1 bath units (reference category) show greater likelihood of short-term preference than 2 bed / 2 bath combinations.
-This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share.
+This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roommates to share.
 Larger units, 3 bedrooms plus, generally show no statistical difference in preference probability to the 1 bed / 1 bath reference unit.
@@
 This variable may be operating as proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.
-The greater the minimum stay, the lower the probability of short-term preference.
+The greater the required minimum stay, the lower the probability of short-term preference.
 Longer minimum stays may equate to lower occupancy rates as one or two night travelers are prevented from booking.
-Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.
 Finally, flexible cancellation policies result in a considerably lower probability of short-term preference.
@@
 Although it gathers considerable interest in both economic and public policy circles, analyses of short-term markets and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.
-The Airbnb market is Melbourne is rapidly expanding as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
+The Airbnb market in Melbourne is rapidly expanding as total listings on the portal have jumped from around 7,000 in 2014 to more than 20,000 in August 2016.
 However, of this total only 7,400 or so of the properties are entire homes or apartments that were listed as available for at least one day during the September 1, 2015 to August 31, 2016 time frame.
@@
 The authors would like to thank the Real Estate Research Institute (RERI) for funding this work and the Australian Property Monitors (APM) for providing the long-term rental data.
-We'd also like to thank an anonymous reviewer for suggesting the matched pairs approach as a check on our hedonic model.
+We'd also like to thank an anonymous reviewer for suggesting the matched pairs approach as a check on our hedonic model and another for helping to shape our reseearch question.
 

### 2018-11-23 papers/full_paper.Rmd
Update to literature review.

@@
 The shift to small, urban dwellings within the STR market is relatively new and explains the dearth of past work in this direction.
-With the rapid growth of Airbnb, and the controversies surrounding it, interest in the short-term rental market has increased among researchers as well as investors and industry analysts.
+With the rapid growth of Airbnb, and the controversies surrounding it, interest in the short-term rental market has increased among researchers as well as investors and industry analysts [@manning2018hotel].
 
@@
 Host policies can also matter as @benjamin2001value find that smoking prohibitions influence the weekly rental rates for vacation homes.
-
-Focusing specifically on the short-term rental market, @cassidy2007tourist suggest that within Australia's Gold Coast the STR industry lacks sophistication and efficiency.
-Most notably, they find that most nightly or weekly rates are set by resident unit managers and are often under-priced as there is little accountability to owners.
-The authors also note that very little research has been put toward understanding this growing market segment.
-
-A collection of recent work has looked into the impact of short-term markets on housing prices and affordability.
-This research examines the influence of Airbnb on existing housing prices nationally [@barron2018sharing] as well as focused work in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2017home].
-Though very broad analyses, all suggest that Airbnb has had a positive impact on local home prices and/or a negative impact on affordability.
-Other research examines the impact of short-term rentals on the hotel market, with @gutierrez2016airbnb finding that Airbnb and hotels have similar location patterns in Barcelona and @zervas2014rise showing an inverse relationship between Airbnb listings and hotel revenues.
+More recent work by Gibbs and co-authors [-@gibbs2018pricing] examine short-term rental pricing formation in large, urban areas throughout Canada.
+Much like decades of work on house prices [@sirmans2006value], they find that location and physical characteristics are the primary drivers of short term rental price differentials.
+Additionally, host policies are shown to play a significant role as well in these Canadian markets.
 
@@
 Finally, in examining the difference between the urban and rural STR markets,  @nilsson2015influence makes a key distinction finding that rural vacation home markets value amenities whereas urban holiday properties tend to derive large premiums from proximity to attractive residential areas.
+
+Looking from the supply-side, many short-term rental markets are characteristized by a highly bifurcated set of owners and hosts.
+On one side are the small-time owners and hosts who manage a single or a few short-term properties.
+They are constrasted by "professionals", those who have have dozens or more listings [@gibbs2018use].
+Professionals are more likely to manage the more expensive, better performing and better located listings.
+Additionally, they are much more likely to use dynamic pricing models [@oskam2018s; @gibbs2018use] than simply setting a price and leaving it for months at a time, regardless of daily changes in demand.
+
+Not all "professionals", however, appear to be using the most efficient or economically sound pricing methods.
+Having a vested interest in the occupancy rate matters as well.
+Within Australia's Gold Coast work by @cassidy2007tourist suggest that the STR industry lacks sophistication and efficiency.
+Most notably, they find that most nightly or weekly rates are set by resident unit managers and are often under-priced as there is little accountability to owners.
+The authors also note that very little research has been put toward understanding how property managers influence this growing market segment.
+
+#### Externalities
+
+The growth of the short-term market is not only a concern of profit-minded investors; the externalities, real or perceived, that have come with have gathered significant attention.
+A collection of recent work has looked into the impact of short-term markets on housing prices and affordability.
+This research examines the influence of Airbnb on existing housing prices nationally [@barron2018sharing] as well as focused work in New York [@sheppard2016airbnb], Los Angeles [@lee2016airbnb] and Boston [@merante2017home].
+Though very broad analyses, all suggest that Airbnb has had a positive impact on local home prices and/or a negative impact on affordability.
+Other research examines the impact of short-term rentals on the hotel market, with @gutierrez2016airbnb finding that Airbnb and hotels have similar location patterns in Barcelona and @zervas2014rise showing an inverse relationship between Airbnb listings and hotel revenues.
 
@@
 
+Finally, Airbnb's unique and highly transparent peer-to-peer leasing platform has produced some concerns over equity and discrimination [@cheng2018sharing].
+While official Airbnb policy addresses potential discrimination by hosts, the behaviors by guests in choosing lodging may be influencing pricing and hosting decisions as evidenced by an analysis of the San Francisco market [@kakar2018visible].
+With its substantial growth and significant share of the overall urban short-term market Airbnb as a company will be the likely target of many nuisance and externality concerns in the near future.
+
+#### Summary and Motivation
+
 Overall, the extant literature on short-term rentals is limited, but growing.
-Of the three types of research -- pricing, impacts on housing market and legalities/externalities -- none specifically address the decision faced by an owner who is trying to decide between a long- or short-term leasing strategy.
+Of the three types of research -- pricing, housing market impacts and legalities/externalities -- none specifically address the decision faced by an owner who is trying to decide between a long- or short-term leasing strategy.
 The closest analog in the literature is a piece by @larson2009pur examining the choice between purchasing a time-share or simply paying for hotel rooms.
-Theoretically, the literature shows that in most cases there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
-We hypothesize that this same thinking can be extended to the difference between short-term rental occupants (tourists and business travelers) and long-term rental occupants (local workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term leasing strategy.
+
+Two key findings from the existing work motivate this study.
+First, short-term market pricing is influenced by the same characteristics as for sale and long-term rental housing -- namely physical characteristics and location -- as well as by hosting policies [@gibbs2018pricing].
+Second, there is a demonstratable difference between first and second home market dynamics due to the use differences of the occupants.
+We hypothesize that these findings can be extended to investigate the differences between short-term rental occupants (tourists and business travelers) and long-term rental occupants (local workers and retirees) and, as a result, there should be differences in the market which make certain housing products and locations preferable (more profitable) under a short-term versus long-term leasing strategy.
 

### 2018-11-23 papers/round_2_reviews.Rmd
Update to literature review.

@@
 title: "To Airbnb?: Factors impacting short-term leasing preference"
-subtitle: "Round 2 Reviews"
-author: "Andy Krause and Gideon Aschwanden"
+subtitle: 'Reviewer Responses'
 date: "11/8/2018"

### 2018-11-23 papers/round_3_reviews.Rmd
Update to literature review.

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: 'Reviewer Responses'
date: "11/8/2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

## What's Changed

1. Bolstered the literature review
* Provided larger coverage of the short-term rental issues by extending discussion to some non-Real Estate centric work [@kakar2018visible; @cheng2018sharing]
* Added in a few very recent publications to help solidify the importance of this work [@manning2018hotel] and to provide deeper look at previous short term rental pricing work[@gibbs2018use; @gibbs2018pricing; @oskam2018s]

## References

### 2018-11-24 papers/full_paper.Rmd
Add: Conditional expectations analysis

@@
   options(xtable.caption.placement='top')
-  #setwd('..')
-  #source(file.path(getwd(), 'functions', 'abb_Functions.R'))
   source(file.path('c:/code', 'research', 'airbnbMelbourne', 'functions', 'abb_Functions.R'))
-
-  # library(knitr)
-  # knit_hooks$set(plot = function(x, options) {
-  # paste('<figure><figcaption>', options$fig.cap, '</figcaption><img src="',
-  #       opts_knit$get('base.url'), paste(x, collapse = '.'),
-  #       '"></figure>',
-  #       sep = '')})
 
@@
 
+### Conditional Expecations
+
+To better understand how the various factors impact the probability of short term preference we have estimated conditional expectations for a pair of exemplar homes -- a 1 bedroom, 1 bathroom and a 3 bedroom, 2 bathroom property.
+The conditional probability expectations are generated by using Model 3 from Table 3 above to predict the short-term probability for most of the possible permutations of structure type, location, cancellation policy, guests per bedroom and minimum stay for the exemplar homes.
+We plot these conditional probabilities in Figures 7 and 8.
+
+![1 Bed, 1 Bath Conditional STP Probabilities](C:/Code/research/airbnbMelbourne/images/cpp_11.png)
+
+For 1 bedroom 1 bathroom homes, investors looking for properties and strategies likely to lead to short-term preference should focus on factors in the upper left hand corner of Figure 7.
+Specifically, this means locations in the City-Core and City location and hosting policies that include strict cancellation policies.
+Additionally, they should allow a high number of guests per bedrooms -- possibly by adding impromtu sleeping arrangements such as pull-out couches and sleeping dens.
+Nearly all combination of the above locations, types and policies create at least a 50% probabilty of short-term preference.
+Conversely, in the lower right hand corner of Figure 7 we see factor combination of which none create a short-term probability of 50% or greater.
+In short, suburban locations and any properties managed with flexible cancellation policies, long minimum stays and few guests per bedroom are better off in the long-term market.
+
+![3 Bed, 2 Bath Conditional STP Probabilities](C:/Code/research/airbnbMelbourne/images/cpp_32.png)
+
+Overall, the trends for 3 bedroom, 2 bathroom homes (Figure 8) are similar to those of 1 bedroom, 1 bathroom homes, though with slighly lower probabilities of STP across all factor permutations.
+Again, apartments in the City-Core and City offer good short-term rental opportunties if managed properly (short term stay minimums and reasonably high number of guests allowed).
+
+\pagebreak
+
 ## Discussion
@@
 
-The logistic regression models (Tables 3 and 4) highlight which characteristics lead to increased short term preference.
+The logistic regression models (Tables 3 and 4) and the conditional expectation plots (Figures 7 and 8) highlight which characteristics lead to increased short term preference.
 Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.
 More flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability).
-As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.
+In short, investors should look for apartment units in central city locations and then,  as a host, aggressively attract bookings and then make it difficult for those bookings to be cancelled.
 
@@
 
+The cancellation policy variable carries a stronger signal than might be expected.
+We suspect that some of this signal may be a result of strict cancellation policies being a luxury that only the best -- both in terms of the property as well as the management -- short-term rentals can get away with.
+As such, this variable may be serving as a proxy for one or more unobserved variables and, we believe, warrants more attention in future work.
+
 Beyond Airbnb.com other short-term platforms exist (e.g.

### 2018-11-24 papers/round_3_reviews.Rmd
Add: Conditional expectations analysis

@@
 title: "To Airbnb?: Factors impacting short-term leasing preference"
-subtitle: 'Reviewer Responses'
-date: "11/8/2018"
+subtitle: 'Review Update'
+date: "11/22/2018"
 output:
@@
 
-1. Bolstered the literature review
-* Provided larger coverage of the short-term rental issues by extending discussion to some non-Real Estate centric work [@kakar2018visible; @cheng2018sharing]
-* Added in a few very recent publications to help solidify the importance of this work [@manning2018hotel] and to provide deeper look at previous short term rental pricing work[@gibbs2018use; @gibbs2018pricing; @oskam2018s]
+#### 1. Bolstered the literature review
+
+* Provides larger coverage of the short-term rental issues by extending discussion to some non-Real Estate centric work [@kakar2018visible; @cheng2018sharing]
+
+* Adds in a few very recent publications to help solidify the importance of this work [@manning2018hotel] and to provide deeper look at previous short term rental pricing work[@gibbs2018use; @gibbs2018pricing; @oskam2018s]
+
+&nbsp; 
+&nbsp;
+
+#### 2. Added Conditional Expectations Section
+
+* Provides a clearer look at how the various factor influence short-term preference
+
+* Provides more explicit advise on which situations and strategies are most promising for investors looking for short-term preferable properties.
+
+&nbsp; 
+&nbsp;
 

### 2018-11-24 scripts/4_data_analysis.Rmd
Add: Conditional expectations analysis

@@
 
+### Prediction Chart
+
+```{r}
+
+# Create New variables
+
+ str_tdf$gpb <- str_tdf$max_guests / str_tdf$bedrooms
+ str_tdf$canc <- ifelse(str_tdf$canc_policy == 'Flexible', 1, 0)
+
+# Recreate Model
+
+ pred_model <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
+                    gpb + min_stay + canc,
+                      family=binomial(link='logit'),
+                      data=str_tdf)
+
+```
+
+```{r}
+
+### Create variables for pred
+
+  bedbath <- unique(str_tdf$bedbath)
+  type <- unique(str_tdf$type)
+  geo_mrkt <- unique(str_tdf$geo_mrkt)
+  canc <- c(0,1)
+  min_stay <- c(1,2,3,4,7)
+  gpb <- 1:5
+
+  pred_df <- expand.grid(bedbath, type, geo_mrkt, canc, min_stay, gpb)
+  names(pred_df) <- c('bedbath', 'type', 'geo_mrkt', 'canc', 'min_stay', 'gpb')
+
+  pred_df$id <- apply(pred_df, 1, function(x) paste0(substr(x['type'], 1,1),
+                                                     x['bedbath'], 
+                                                     substr(x['geo_mrkt'], 1, 5)))
+
+  str_tdf$id <- apply(str_tdf, 1, function(x) paste0(substr(x['type'], 1,1),
+                                                     x['bedbath'], 
+                                                     substr(x['geo_mrkt'], 1, 5)))
+  pred_df$aid <- apply(pred_df, 1, function(x) paste0(x['bedbath'], 
+                                                      substr(x['geo_mrkt'], 1, 5)))
+  str_tdf$aid <- apply(str_tdf, 1, function(x) paste0(x['bedbath'], 
+                                                      substr(x['geo_mrkt'], 1, 5)))
+
+```
+
+```{r}
+
+# Make predictions
+  pred_df$raw <- predict(pred_model, newdata = pred_df)
+  pred_df$prob <-  exp(pred_df$raw)/(1+exp(pred_df$raw))
+  pred_df$sh <- ifelse(pred_df$prob > .5, 1, 0)
+  pred_df$sh <- factor(pred_df$sh, levels = c(1,0))
+
+  #pred_df$min_stay <- as.factor(pred_df$min_stay)
+  pred_df$gpb <- as.factor(pred_df$gpb)
+  pred_df$cc <- ifelse(pred_df$canc == 1, 'Flexible', 'Strict')
+  pred_df$ct <- paste0(ifelse(pred_df$type == 'House', 'House', 'Apt'), 
+                       " - ",  pred_df$cc)
+
+  pred_df$ms <- as.character(pred_df$min_stay)
+  pred_df$ms[pred_df$ms == '4'] <- '4-6'
+  pred_df$ms[pred_df$ms == '7'] <- '7+'
+  pred_df$ms <- factor(pred_df$ms, levels=c('1', '2', '3', '4-6', '7+'))
+
+  pred_df$sm <- as.character(pred_df$geo_mrkt)
+  pred_df$sm[pred_df$sm == 'city-core'] <- 'City-Core'
+  pred_df$sm[pred_df$sm == 'city'] <- 'City'
+  pred_df$sm[pred_df$sm == 'beach'] <- 'Beach'
+  pred_df$sm[pred_df$sm == 'suburban'] <- 'Suburban'
+  pred_df$sm <- factor(pred_df$sm, levels = c('City-Core', 'City', 'Beach', 'Suburban'))
+
+  pred_df$ct <- factor(pred_df$ct, levels = c('Apt - Strict', 'House - Strict', 
+                                              'Apt - Flexible', 'House - Flexible'))
+
+```
+
 <!-- ### Host types -->
@@
        pot_glms, core_suburbs, str_tdf_all, pot_mc_glms, pot_us_glms,
-       #pot_ht_glms, lik_ht_glms,
+       #pot_ht_glms, lik_ht_glms, pred_df, 
        file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

### 2018-11-24 scripts/5_data_viz.Rmd
Add: Conditional expectations analysis

@@
 ```
+
+```{r}
+ ## 1/1 plots
+  x <- pred_df[pred_df$bedbath == "1_1", ]
+  cap11 <- paste0('Plot shows the conditional probability of short term preference for ',
+                  '1 bedroom, 1 bathroom homes given differences\n',
+                  'in their structure type (Apt vs House), cancellation policy (strict',
+                  ' vs flexible), location (City-Core, City, Beach, Suburban),\n',
+                  'Number of allowed guest per bedroom and minimum number of night stay ',
+                  'reguired. Larger and darker dots indicate\na higher probabilty ',
+                  'of short-term preference with full dots showing 50%+.')
+
+  ggplot(x, aes(x=ms, y=gpb, color = prob)) + 
+    geom_point(aes(shape = sh, size = prob)) + 
+    facet_grid(sm~ct) +
+    scale_color_gradient(low='gray80', high='black', name='STP Probability',
+                         labels = c('0%', '25%', '50%', '75%'),
+                         breaks = c(0,.25, .50, .75)) +
+    scale_shape_manual(values = c(16,1), name = 'Is STP?', labels=c('True', 'False')) + 
+    scale_size(range = c(.5, 3), guide = FALSE) + 
+    xlab('\n Minimum Stay  (In Days)\n') +
+    ylab('Allowed Guests per Bedroom\n') + 
+    labs(title = '1 Bed, 1 Bath Home - Conditional STP Probabilities\n',
+         caption = cap11) + 
+    theme(plot.caption=element_text(hjust = 0),
+          plot.title = element_text(hjust = 0.5)) -> cpp_11
+
+  png(filename = file.path(getwd(), 'images', "cpp_11.png"), 
+       width = 7, height = 5, units = 'in', res = 300)
+     cpp_11
+  dev.off()
+
+```
+
+```{r}
+
+ ## 1/1 plots
+  x <- pred_df[pred_df$bedbath == "3_2", ]
+  cap11 <- paste0('Plot shows the conditional probability of short term preference for ',
+                  '3 bedroom, 2 bathroom homes given differences\n',
+                  'in their structure type (Apt vs House), cancellation policy (strict',
+                  ' vs flexible), location (City-Core, City, Beach, Suburban),\n',
+                  'Number of allowed guest per bedroom and minimum number of night stay ',
+                  'reguired. Larger and darker dots indicate\na higher probabilty ',
+                  'of short-term preference with full dots showing 50%+.')
+
+  ggplot(x, aes(x=ms, y=gpb, color = prob)) + 
+    geom_point(aes(shape = sh, size = prob)) + 
+    facet_grid(sm~ct) +
+    scale_color_gradient(low='gray80', high='black', name='STP Probability',
+                         labels = c('0%', '25%', '50%', '75%'),
+                         breaks = c(0,.25, .50, .75)) +
+    scale_shape_manual(values = c(16,1), name = 'Is STP?', labels=c('True', 'False')) + 
+    scale_size(range = c(.5, 3), guide = FALSE) + 
+    xlab('\n Minimum Stay (In Days)\n') +
+    ylab('Allowed Guests per Bedroom\n') + 
+    labs(title = '3 Bed, 2 Bath Home - Conditional STP Probabilities\n',
+         caption = cap11) + 
+    theme(plot.caption=element_text(hjust = 0),
+          plot.title = element_text(hjust = 0.5)) -> cpp_32
+
+  png(filename = file.path(getwd(), 'images', "cpp_32.png"), 
+       width = 7, height = 5, units = 'in', res = 300)
+     cpp_32
+  dev.off()
+
+```

### 2018-11-28 papers/full_paper_no_authors.Rmd
Revision #3

--- 2018-11-24 papers/full_paper.Rmd
@@
 title: "To Airbnb?: Factors impacting short-term leasing preference"
-subtitle: "Andy Krause and Gideon Aschwanden"
-author: "Zillow and University of Melbourne"
-date: "Revised: November 10th, 2018"
+# subtitle: "Andy Krause and Gideon Aschwanden"
+# author: "Zillow and University of Melbourne"
+date: "Revised: November 25th, 2018"
 output:

### 2018-11-28 papers/round_3_reviews.Rmd
Revision #3

@@
 subtitle: 'Review Update'
-date: "11/22/2018"
+date: "11/25/2018"
 output:
@@
 
-#### 1. Bolstered the literature review
+#### 1. Bolstered the literature review (pgs 2-5)
 
@@
 
-#### 2. Added Conditional Expectations Section
+#### 2. Added Conditional Expectations Section (pgs 24 - 26)
 
